### 2018-05-15 main.tex
first commit

\documentclass[a4paper,man,natbib,floatsintext]{apa6}

\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[font=small,labelfont=bf]{caption}
\newcommand{\rpm}{\raisebox{.2ex}{$\scriptstyle\pm$}}
\usepackage{amsmath}
\DeclareMathOperator*{\argmax}{arg\,max}

\title{Sherlock topic model paper}
% A common space for dynamic experiences and memories
% Geometric principles of episodic recall for naturalistic experiences
% The geometry of episodic recall for naturalistic experiences
% Recasting episodic memory as a weighted blend of prior experiences
% Capturing the moment-by-moment flow of information in naturalistic stimuli
% A continuous, content-general approach to characterizing memory for naturalistic events
% A common model for naturalistic stimuli, memories, and brains
% \title{A dynamic, content-general encoding signal to characterize memory for naturalistic stimuli}
% Topic models as a bridge between naturalistic stimuli, memories, and brains
% Automated analysis of memory for naturalistic stimuli using topic modeling
% Topic modeling as a link between videos and memories
% Topic models as a bridge between dynamic experiences and memories

\shorttitle{Your APA6-Style Manuscript}
\author{Andrew C. Heusser \& Jeremy R. Manning}
\affiliation{Dartmouth College}

\abstract{
}

\begin{document}
\maketitle

\section{Introduction}

\subsection{Results}

\begin{figure}[t!]
\centering
\includegraphics[width=1\textwidth]{figs/0_analysis_schematic.pdf}
\caption{\label{fig:schematic}Schematic of the analysis approach. For each moment of the video, text descriptions were manually generated. Three exemplary time points are displayed here.  Below the video descriptions are text samples from an example participant's verbal recall transcript.  We trained a topic model on the moment-by-moment video description text and transformed participant's recall transcripts using this same model. The bar charts display the resulting topic model weights for the video (in blue) and recall (in orange) for three example topic dimensions.}
\end{figure}

\subsubsection{A model to capture the moment-by-moment flow of information in naturalistic stimuli}
We fit a topic model to overlapping windows of manually annotated text descriptions of scenes from an episode of the BBC series, Sherlock. The text description contained details of the scene such as the characters, location, and a short summary of the scene (see \ref{fig:schematic} for example text, see \ref{sec:methods} for analysis details). We then transformed the text descriptions with the (same) topic model, resulting in a scene (1000) by topics (100) matrix where each row of the matrix represents a probabalistic mixture of topics discovered in that scene. We expanded this matrix from 1000 to 1976 timepoints by copying the vectors for scenes that spanned multiple TRs. As depicted in \ref{fig:model}a, the topics are sparse and change slowly over time. This gradual change was anticipated, since we used overlapping windows of text (50 sentences) as input to the model. The sparsity was also expected since the topic modeling approach we used (Latent Dirichlet Allocation) assumes a sparse Dirichlet prior. By eye, there are clear transitions from one topic `state' to the next, likely indexing scene transitions in the stimulus.  To get a better handle on this temporal structure, we computed the timepoint-by-timepoint correlation matrix of the video model (\ref{fig:model}b).  This correlation matrix reveals that the model has a strong, blocky structure along the diagonal.  Another interesting feature is that there is very little correlation between events (i.e. the off-diagonal values are small). This is an important feature of the model because the `event' representations are unique and highly discriminable.

\subsubsection{Projecting verbal recall into stimulus space}
After watching the episode, participants verbally recalled (in order) as much of the episode as they could.  We used the same topic model (fit with the text descriptions of the video) to transform participants' verbal recall transcripts (split by sentence in overlapping chunks of 10 sentences). The result was a sentences (range: X to X) by topics (100) matrix for each participant, where each row represented the estimated mixture of topics for a given window of sentences during recall. In order to average the recall models across participants, we resampled each model at the resolution of the video model (1976 timepoints). The individual models can be seen in Supp Fig X and the group average is plotted in \ref{fig:model}c. Note that the topics were derived solely from the text descriptions of the stimulus, and so the topic models estimated for recall are entirely dependent on the topics in the episode. In effect, this approach projects the recall transcripts into the video 'stimulus space', allowing us to quantify the dynamics of verbally reported memories as well as relate them to the experiences from which they were born.

Next, we investigated the temporal structure of the recall matrices. For each participant, we computed a timepoint-by-timepoint correlation matrix from the recall model. Like the video model, the recall correlation matrices exhibited blocky structure along the diagonal, albeit .

\begin{figure}[t!]
\centering
\includegraphics[width=1\textwidth]{figs/1_video_recall_models.pdf}
\caption{\label{fig:model}Topic models for the video and verbal recall. A. A timepoints (1976) by topics (100) matrix was created by fitting a topic model to overlapping segments of the moment-by-moment video text descriptions.  Each row represents the most likely mixture of topics for a given timepoint. Each columns represents a different topic. The darker the color, the higher the probability that the topic is contained in that timepoint. B. A timepoints (1976) by topics (100) matrix representing group average topic model of the recall transcripts.  All participant's recall transcripts were transformed using the topic model fit to the video descriptions and then resampled to the same length (1976). C. A viewing-time (1976) by recall-time (1976) correlation matrix representing the correlation of each moment of the video model with every moment of the average recall model. The darker the color, the higher the correlation between the video and recall models at a given timepoint. D. A 3D embedding of the video and recall topic models reduced using spectral embedding. }
\end{figure}

 However, the size/number of blocks varied across participants.  To quantify this structure, we estimated the number of recall `events' (k)  discovered in each participants' recall matrix (see Methods for details) using the event segmentation approach developed by Baldassano et al 2017.  Briefly, this algorithm implements a variant of a Hidden Markov Model to estimate a set of events (or states) given a multivariate time series and a k value (number of states). Figure X displays example correlation matrices for the participants with the lowest and highest k value.  We found that the estimated k value strongly correlated with the number of (hand-annotated) correctly remembered scenes across participants (Figure Xx, r=.67, p=.003). Thus, the blocky temporal structure of the recall matrices computed with our model is related to the variability in memory performance across participants.

Another interesting feature of the recall matrices is the off-diagonal structure, which represents the use of language that generalizes to more than one event. To characterize this aspect of the recall structure, we averaged the rows of the recall matrices according to the k events computed in the analysis described above.  This reduced the recall matrices from \# of sentences to k rows. Then, we computed k by k correlation matrices, representing the similarity of each event to each other event. To visualize these recall `networks', we embedded the k by topics matrices into a 2-dimensional space using Multidimensional Scaling (MDS), where each dot represents an event and the color of the dot represents the event index.  Then, we connected each event with a line where the color and line weight was proportional to the strength of the correlation between the events. These network plots can be seen in Fig X. To hypothesized that stronger correlations between recall events would

\subsubsection{Temporally aligning the stimulus and recall}
While most participants were able to recall most of the scenes in order, the rate of verbal description varied by participant and timepoint (Supp Fig X). Because of this participant-dependent non-linear relationship between stimulus and recall time, averaging the video-recall correlation plots across participants attenuates the robust within-participant effects. While further exploration of individual differences in recall rates is interesting, our primary goal here was to develop a model capable of accurately characterizing the content recovered during recall and explore how that varied across participants.  To that end, we leveraged dynamic time warping (DTW, REF) to temporally align the stimulus and recall matrices.  The algorithm returns a path of indices that bring the two timeseries into maximal temporal alignment (within constraints, see Methods for details).  For each participant, we computed the path and then warped the video model and recall model according to it. The length of the warp path varied by participant, and so the length (number of timepoints) of the warped video/recall matrices also varied by participant (range: X-X). To account for these differences, we resampled the timeseries back to the length of the stimulus (1976 time samples).

\begin{figure}[t!]
\centering
\includegraphics[width=.75\textwidth]{figs/2_eventseg.pdf}
\caption{\label{fig:eventseg} Event segmentation analysis of the video and recall models. A. A recall-time (294) by topics (100) matrix representing a recall model for a single participant (participant \#13).  B. A recall-time (294) by recall-time (294) correlation matrix for participant \#13. The white squares along the diagonal outline events, i.e. neighboring timepoints with a stable and similar topic vector. C. An events (34) by topics (100) matrix where each row represents the average topic vector for each event in the video model.  D. An events (27) by topics (100) matrix where each row represents the average topic vector for each event in the recall model. E. A recall events (27) by video events (34) correlation matrix representing the `match' between each video and recall event. The black squares identify the video event with the highest correlation to a given recall event. F. A group averaged recall events (34) by video events (34) correlation matrix.  The black squares identify the video event with the highest correlation to a given average recall event. G. 2D embeddings (reduced with UMAP algorithm) of each participants' recall event model (example shown in D). Each dot represents a recall event and the connecting lines indicate the order of recall. Colors indicate the most likely video event that the participant was describing as determined by the video-recall matching model.  H. 2D embedding of video and average recall event models.  }
\end{figure}

\subsubsection{Naturalistic extensions of classic memory analyses}

\begin{figure}[t!]
\centering
\includegraphics[width=1\textwidth]{figs/3_behav_eventseg.pdf}
\caption{\label{fig:behav}Naturalistic extensions of classic memory analyses. A-C use the `smooth' approach and D-F use the `best' approach (see Methods for details). A/D. The probability of first recall as a function of the serial position the the event during encoding. B/E. Given recall of event i, the probability that the next recalled item will be from serial position i \rpm~lag. C/F. Proportion recalled as a function of serial position. All error bars are the standard error of the mean derived from a bootstrap resampling procedure.
}
\end{figure}

\section{Methods}
\label{sec:methods}

\subsection{Participants and Experimental Design}
How much detail here? or just point to janice's paper?

\subsubsection{Fitting a topic model from text descriptions of Sherlock}
To quantify the flow of information from scene to scene, we used a topic model. A topic model estimates the most likely mixture of topics in a sample of text. First, the video was manually segmented into 1000 scenes, and a collection of descriptive features were manually transcribed.  For each scene, we considered the following features: scene details (i.e. a sentence or two describing what happened in that scene, space (indoor or outdoor), name of all the characters in the scene, name of the character in focus, name of the character speaking, location, camera angle, music presence, and words on the screen. We concatenated the text for all of these features within each segment, creating a 'bag of words' describing each scene. We then transformed the text descriptions into overlapping windows of 50 scene segments. For example, the first text sample comprised the text from the first 50 segments, the second comprised the text from n+1:n+51, and so on. We trained our model using these overlapping text samples using scikit-learn's `CountVectorizer' and `LatentDirichletAllocation' classes.  First, the text was transformed into a vector of word counts (default scikit-learn parameters). This gave a word count vector for each scene in the video.  Then, the word count vectors were used to fit a topic model (number of topics=100, method=batch).

\subsubsection{Projecting the video and verbal recall into a common space}
We used the model described above to transform the video text descriptions and verbal recall transcripts into a common space.  We created the video model by transforming exactly the same text (overlapping scene descriptions) with the topic model, resulting in a scene (1000) by topic (100) matrix that summarized the topics in each scene (Fig. \ref{fig:model}a). The scene descriptions often spanned multiple timepoints (i.e. TRs). To account for this, we expanded the video model by copying the rows of the model for as many timepoints that the scene description spanned. After this expansion, the shape of the model was the length of the duration of the video (1976 TRs).

To create the recall models, for each participant we tokenized the recall transcript into a list of sentences and then mapped the list to overlapping windows of 10 sentences.  We transformed the list of overlapping recall sentences using the model that was trained on the video text. The result of this was a matrix (\# of sentences by 100 topics) that represented the most likely mixture of topics for a given chunk of sentences. We resampled the recall model to be the same length as the video model (1976 samples). The result was 17 participant-specific recall models (1976 timepoints by 100 topics). Intuitively, if the recall transcript for a given participant correctly described each video scene in order, the video and recall models should match closely.  However, if the scenes were recalled out of order, omitted, or described using language that was very different from the video scene descriptions, the video and recall models would look very different. Figure \ref{fig:model}b shows the group average recall model. Qualitatively, the two matrices appear to be similar. Our next set of analyses sought to quantify this relationship.

To quantify the similarity between the movie and recall models, for each participant we correlated every moment of the video model with every moment of the recall models, resulting in a timepoints (1976) by timepoints (1976) correlation matrix for each participant.  The individual matrices for each participant can be seen in Supp Fig. X and the group average is displayed in \ref{fig:model}c.

\subsubsection{Estimating the number of recall events for each participant}
Our metric for choosing k was to select the value that maximized the ratio of the average `within-event' correlation (i.e. blocks of time the model identified as an event) and the average `across-event' correlation.

% \subsubsection{Accounting for nonlinearities between video and recall models}
% For many participants, the rate of recall changed over time (see Supp Fig X for an example). This becomes problematic if averaging the video/recall correlation matrices because the different recall rates distort the group average matrix. To correct for differences in recall rates across participants, we used dynamic time warping (DTW).  Briefly, DTW finds the path that maximizes the temporal alignment between two timeseries (REF). For each participant, we used DTW to temporally align the video model and the participant-specific recall model. Because the path is different for each participant, the length of the warped matrices varied across participants (range: X to X). To account for this, we resampled the matrices back to their original shape (1976 x 100).

\subsubsection{Characterizing memory performance}
We used a few different metrics to assess memory that were all designed to capture the relationship between the video and recall models.  First, to get a general sense for the match between the video and recall matrices, we vectorized the the matrices and correlated them.  This resulted in a single number representing how well a given participant recalled the video. To get a temporally dynamic measure of memory, for each participant we computed the pairwise correlation between matching video/recall timepoints.  This allowed us to assess memory for individual moments of the video. Finally to get a more nuanced representation of memory for the video, we computed a video/recall model correlation matrix for each participant. These timepoint (1976) by timepoint (1976) matrices represent the correlation between every moment of the video model and every moment of the recall model. To provide some intuition, if a participant recalled every scene at the same rate and in exactly the same order as the video, we would expect high correlation values along the diagonal of this matrix. However, if a participant recalls the scenes out of order, or at different rates for different scenes, this will result in high values off the diagonal.

% \subsection{fMRI analyses}
% Seventeen participants watched the first 50 minutes of Episode 1 of BBC's Sherlock. The video was split into two parts of approximately equal length (946 and 1030 TRs). All data were preprocessed and transformed to 3mm MNI space as described in the paper. Data were zscored across time at every voxel. 6mm smoothing was applied.
% Files are cropped so that all video-viewing data are aligned across participants, and all recall data are aligned to the scene timestamps below. The cropping includes a constant 3-TR (4.5 sec) shift to correct for hemodynamic lag.
%
% \subsubsection{Univariate subsequent memory analysis}
% To characterize brain regions involved in memory encoding, we conducted an analysis inspired by prior studies investigating the  `subsequent memory effect' (Paller and Wagner).  For each participant, we computed the correlation between topic vectors at each timepoint of the video model and recall model (they were temporally aligned with DTW and resampled to 1976 timesamples). The result was a 1 x 1976 vector of correlation values representing how similar each moment of the video model was to each moment of the recall model. Then, to compute the average correlation, we Fisher's z transformed the correlation vectors, averaged them together, and then inverse Fisher's z transformed them.  Finally, we mean centered the vector.  This 1 x 1976 vector represents memorable/unmemorable parts of the video, and be thought of as a `continuous' extension of a subsequent memory regressor.  We convolved the timeseries with a double gamma function (PARAMS) to account for the hemodynamic response, and used it as a model for each voxel's activity timeseries (using FSL software).  Finally, to aggregate across participants, we performed a mixed effects (ordinary least squares) analysis, thresholding at p<.001 and cluster correcting a p<.05.
%
% \subsubsection{Multivariate searchlight analyses}
% Our multivariate analyses were designed to capture brain regions whose timepoint-by-timepoint correlational structure mirrors the correlational structure of the video and recall topic models during video viewing. To that end, we conducted a searchlight analysis (5x5x5 voxel cube) where for each cube, we correlated the model timepoint-by-timepoint correlation matrix with the neural correlation matrix. To aggregate across participants, we computed Fisher's z transformed the correlations and then averaged.  To assess significance, we recomputed this group analysis 100 times, but randomly phase shifted the model (by \# of timepoints - 1) by the same amount for each participant but different amounts for each permutation to build a null distribution of correlation values. Finally, we thresholded the group averaged correlation maps where the `real' correlation value for a given voxel exceeded the 95th percentile of the null distribution.
%
% We first performed this analysis using the unwarped video model. Thus, the same model was applied to each participant and each searchlight cube. We then performed this analysis on the participant-wise recall models. To correct for non-linearities between the video model and recall models, for each participant we used DTW to temporally align the matrices. The algorithm recovers a path of coordinates that would bring the video and recall model in maximal temporal alignment. We used this path to warp the fMRI data and the recall model into alignment (separately for each participant). Then, we performed the exact same analysis as described above, using a searchlight to correlate the timepoint-by-timepoint recall and neural correlation matrices. The statistics for both analyses were computed as described above.

\subsection{References}

LaTeX automatically generates a bibliography in the APA style from your .bib file. The citep command generates a formatted citation in parentheses \citep{Lamport1986}. The cite command generates one without parentheses. LaTeX was first discovered by \cite{Lamport1986}.

% \subsection{Tables and Figures}

% Use the table and tabular commands for basic tables --- see Table~\ref{tab:widgets}, for example. You can upload a figure (JPEG, PNG or PDF) using the files menu. To include it in your document, use the includegraphics command as in the code for Figure~\ref{fig:frog} below.

\bibliography{memlab}

\end{document}

%
% Please see the package documentation for more information
% on the APA6 document class:
%
% http://www.ctan.org/pkg/apa6
%

### 2018-05-15 boneyard.tex
saving progress half way through the event segmentation results section

Another interesting feature of the recall matrices is the off-diagonal structure, which represents the use of language that generalizes to more than one event. To characterize this aspect of the recall structure, we averaged the rows of the recall matrices according to the k events computed in the analysis described above.  This reduced the recall matrices from \# of sentences to k rows. Then, we computed k by k correlation matrices, representing the similarity of each event to each other event. To visualize these recall `networks', we embedded the k by topics matrices into a 2-dimensional space using Multidimensional Scaling (MDS), where each dot represents an event and the color of the dot represents the event index.  Then, we connected each event with a line where the color and line weight was proportional to the strength of the correlation between the events. These network plots can be seen in Fig X. To hypothesized that stronger correlations between recall events would

\subsubsection{Temporally aligning the stimulus and recall}
While most participants were able to recall most of the scenes in order, the rate of verbal description varied by participant and timepoint (Supp Fig X). Because of this participant-dependent non-linear relationship between stimulus and recall time, averaging the video-recall correlation plots across participants attenuates the robust within-participant effects. While further exploration of individual differences in recall rates is interesting, our primary goal here was to develop a model capable of accurately characterizing the content recovered during recall and explore how that varied across participants.  To that end, we leveraged dynamic time warping (DTW, REF) to temporally align the stimulus and recall matrices.  The algorithm returns a path of indices that bring the two timeseries into maximal temporal alignment (within constraints, see Methods for details).  For each participant, we computed the path and then warped the video model and recall model according to it. The length of the warp path varied by participant, and so the length (number of timepoints) of the warped video/recall matrices also varied by participant (range: X-X). To account for these differences, we resampled the timeseries back to the length of the stimulus (1976 time samples).

\subsection{fMRI analyses}
Seventeen participants watched the first 50 minutes of Episode 1 of BBC's Sherlock. The video was split into two parts of approximately equal length (946 and 1030 TRs). All data were preprocessed and transformed to 3mm MNI space as described in the paper. Data were zscored across time at every voxel. 6mm smoothing was applied.
Files are cropped so that all video-viewing data are aligned across participants, and all recall data are aligned to the scene timestamps below. The cropping includes a constant 3-TR (4.5 sec) shift to correct for hemodynamic lag.

\subsubsection{Univariate subsequent memory analysis}
To characterize brain regions involved in memory encoding, we conducted an analysis inspired by prior studies investigating the  `subsequent memory effect' (Paller and Wagner).  For each participant, we computed the correlation between topic vectors at each timepoint of the video model and recall model (they were temporally aligned with DTW and resampled to 1976 timesamples). The result was a 1 x 1976 vector of correlation values representing how similar each moment of the video model was to each moment of the recall model. Then, to compute the average correlation, we Fisher's z transformed the correlation vectors, averaged them together, and then inverse Fisher's z transformed them.  Finally, we mean centered the vector.  This 1 x 1976 vector represents memorable/unmemorable parts of the video, and be thought of as a `continuous' extension of a subsequent memory regressor.  We convolved the timeseries with a double gamma function (PARAMS) to account for the hemodynamic response, and used it as a model for each voxel's activity timeseries (using FSL software).  Finally, to aggregate across participants, we performed a mixed effects (ordinary least squares) analysis, thresholding at p<.001 and cluster correcting a p<.05.

\subsubsection{Multivariate searchlight analyses}
Our multivariate analyses were designed to capture brain regions whose timepoint-by-timepoint correlational structure mirrors the correlational structure of the video and recall topic models during video viewing. To that end, we conducted a searchlight analysis (5x5x5 voxel cube) where for each cube, we correlated the model timepoint-by-timepoint correlation matrix with the neural correlation matrix. To aggregate across participants, we computed Fisher's z transformed the correlations and then averaged.  To assess significance, we recomputed this group analysis 100 times, but randomly phase shifted the model (by \# of timepoints - 1) by the same amount for each participant but different amounts for each permutation to build a null distribution of correlation values. Finally, we thresholded the group averaged correlation maps where the `real' correlation value for a given voxel exceeded the 95th percentile of the null distribution.

We first performed this analysis using the unwarped video model. Thus, the same model was applied to each participant and each searchlight cube. We then performed this analysis on the participant-wise recall models. To correct for non-linearities between the video model and recall models, for each participant we used DTW to temporally align the matrices. The algorithm recovers a path of coordinates that would bring the video and recall model in maximal temporal alignment. We used this path to warp the fMRI data and the recall model into alignment (separately for each participant). Then, we performed the exact same analysis as described above, using a searchlight to correlate the timepoint-by-timepoint recall and neural correlation matrices. The statistics for both analyses were computed as described above.

\subsubsection{Accounting for nonlinearities between video and recall models}
For many participants, the rate of recall changed over time (see Supp Fig X for an example). This becomes problematic if averaging the video/recall correlation matrices because the different recall rates distort the group average matrix. To correct for differences in recall rates across participants, we used dynamic time warping (DTW).  Briefly, DTW finds the path that maximizes the temporal alignment between two timeseries (REF). For each participant, we used DTW to temporally align the video model and the participant-specific recall model. Because the path is different for each participant, the length of the warped matrices varied across participants (range: X to X). To account for this, we resampled the matrices back to their original shape (1976 x 100).

### 2018-05-15 main.tex
saving progress half way through the event segmentation results section

@@
 Note that the topics were derived solely from the text descriptions of the stimulus, and so the topic models estimated for recall are entirely dependent on the topics in the episode.
-In effect, this approach projects the recall transcripts into the video 'stimulus space', allowing us to quantify the dynamics of verbally reported memories as well as relate them to the experiences from which they were born.
+In effect, this approach projects the participants' verbal recall into the video 'stimulus space', allowing us to quantify the dynamics of verbally reported memories as well as relate them to the experiences from which they were born.
 
 Next, we investigated the temporal structure of the recall matrices.
-For each participant, we computed a timepoint-by-timepoint correlation matrix from the recall model.
-Like the video model, the recall correlation matrices exhibited blocky structure along the diagonal, albeit .
+For each participant, we computed a timepoint-by-timepoint correlation matrix from recall models.
+Like the video model, the recall correlation matrices exhibited blocky structure along the diagonal (Supp Fig X).
+To visualize the group average, we resampled all of the recall models to the duration of the video model (1976 timepoints), computed the timepoint-by-timepoint correlation matrices and then averaged across partcipants.
+Like the video correlation matrix, the average recall matrix was blocky along the diagonal, albeit noisier (\ref{fig:model}d).
+Presumably this noise stems from the fact that there was variability in the amount of time each participant spent describing each event.
+We will come back to this point later in the paper.
+
+\subsubsection{Correlating the video and recall models}
+The participants in this study were instructed to recall as much of the episode as they could in the order it happened.
+Thus, we expected that to the extent that participants followed these instructions and had reasonably good memory accuracy, the recall models should resemble the video model.
+In our first approach to test this hypothesis, we correlated each moment of the video model with each moment of each participants' resampled recall model.
+We then averaged these matrices together to get a single group averaged matrix.
+The result was a viewing time (1976) by recall time (1976) correlation matrix representing the average relationship between every moment of the movie and recall models (\ref{fig:model}e).
+Notably, we observe significant correlation values (p<.05, permutation test described in \ref{sec:methods}) primarily along the diagonal, suggesting that our model captures the fact that participants recalled the episode in order.
+We also visualized this effect by projecting the matrices into a 3D space (reduced using Spectral Embedding [cite]) where the proximity of the trajectories at every timepoint represents how similar the topic vectors were.
+Visualizing the data in this way makes it clear that the overall shape and correlational structure of the video and average recall matrices is quite similar.
 
@@
 
- However, the size/number of blocks varied across participants.
-To quantify this structure, we estimated the number of recall `events' (k)  discovered in each participants' recall matrix (see Methods for details) using the event segmentation approach developed by Baldassano et al 2017.
-Briefly, this algorithm implements a variant of a Hidden Markov Model to estimate a set of events (or states) given a multivariate time series and a k value (number of states).
+\subsubsection{Segmenting the video and recall models into events}
+One prominent feature of the video and recall correlation matrices (see \ref{fig:model}) is the strong blocky structure along the diagonal.
+We hypothesized that this structure arises from transient stability in the language used to describe each scene of the video.
+If that were true, we reasoned that it would be possible to decode which particular scene a participant is describing by comparing the average topic model for a particular recall `event' with the average topic vector for each video event.
+The video event that is most similar to the given recall event is the event the participant is most likely describing.
+To test this idea it is first necessary to systematically parse the matrices into events.
+To do this, we leveraged the event segmentation approach developed by Baldassano et al 2017.
+Briefly, this algorithm implements a variant of a Hidden Markov Model to estimate k events given a (multivariate) time series and a k value (number of states).
+We automatically determined a k value for the video model and each participant's recall model using the following equation:
+
+% ADD EQUATION HERE
+
+The algorithm determined 34 events for the movie model and a range of values (range=8-27, mean= 15.41, SD=5.6) for the recall models.
+The events discovered for a representative participant can be seen in \ref{fig:eventseg}b.
+Importantly, the k values were highly correlated to hand annotated accuracy (r(16)=.67, p=.003) across participants.
+Thus, the blocky temporal structure in the recall matrices computed by our model is strongly related to the variability in memory performance across participants.
+
+Next, we tested the hypothesis that the individual `blocks' along the diagonals of the recall matrices represent the recall of a particular video event.
+To this end, we created a video event model, which averaged together neighboring topic vectors that the were classified to be in the same event (\ref{fig:eventseg}c), resulting in an events (34) by topics (100) matrix.
+We performed the same procedure for the recall matrices (see \ref{fig:eventseg}d for example).
+Then, we computed the correlation between these two event models, resulting in a video events (34) by recall events (8-27, depending on the participant) correlation matrix (see \ref{fig:eventseg}e).
+These matrices represent the extent to which each recall event is similar to each video event (for each participant).
+To determine which video events the recall events most likely referred to, for event recall event, we computed video event with the highest correlation (i.e.
+the argmax).
+This is depicted in \ref{fig:eventseg}e as the cell highlighted with the black box for each column in the video-recall event correlation matrix.
+
 Figure X displays example correlation matrices for the participants with the lowest and highest k value.
 We found that the estimated k value strongly correlated with the number of (hand-annotated) correctly remembered scenes across participants (Figure Xx, r=.67, p=.003).
-Thus, the blocky temporal structure of the recall matrices computed with our model is related to the variability in memory performance across participants.
-
-Another interesting feature of the recall matrices is the off-diagonal structure, which represents the use of language that generalizes to more than one event.
-To characterize this aspect of the recall structure, we averaged the rows of the recall matrices according to the k events computed in the analysis described above.
-This reduced the recall matrices from \# of sentences to k rows.
-Then, we computed k by k correlation matrices, representing the similarity of each event to each other event.
-To visualize these recall `networks', we embedded the k by topics matrices into a 2-dimensional space using Multidimensional Scaling (MDS), where each dot represents an event and the color of the dot represents the event index.
-Then, we connected each event with a line where the color and line weight was proportional to the strength of the correlation between the events.
-These network plots can be seen in Fig X.
-To hypothesized that stronger correlations between recall events would
-
-\subsubsection{Temporally aligning the stimulus and recall}
-While most participants were able to recall most of the scenes in order, the rate of verbal description varied by participant and timepoint (Supp Fig X).
-Because of this participant-dependent non-linear relationship between stimulus and recall time, averaging the video-recall correlation plots across participants attenuates the robust within-participant effects.
-While further exploration of individual differences in recall rates is interesting, our primary goal here was to develop a model capable of accurately characterizing the content recovered during recall and explore how that varied across participants.
-To that end, we leveraged dynamic time warping (DTW, REF) to temporally align the stimulus and recall matrices.
-The algorithm returns a path of indices that bring the two timeseries into maximal temporal alignment (within constraints, see Methods for details).
-For each participant, we computed the path and then warped the video model and recall model according to it.
-The length of the warp path varied by participant, and so the length (number of timepoints) of the warped video/recall matrices also varied by participant (range: X-X).
-To account for these differences, we resampled the timeseries back to the length of the stimulus (1976 time samples).
 
@@
 
-% \subsubsection{Accounting for nonlinearities between video and recall models}
-% For many participants, the rate of recall changed over time (see Supp Fig X for an example).
-This becomes problematic if averaging the video/recall correlation matrices because the different recall rates distort the group average matrix.
-To correct for differences in recall rates across participants, we used dynamic time warping (DTW).
-Briefly, DTW finds the path that maximizes the temporal alignment between two timeseries (REF).
-For each participant, we used DTW to temporally align the video model and the participant-specific recall model.
-Because the path is different for each participant, the length of the warped matrices varied across participants (range: X to X).
-To account for this, we resampled the matrices back to their original shape (1976 x 100).
-
 \subsubsection{Characterizing memory performance}
@@
 However, if a participant recalls the scenes out of order, or at different rates for different scenes, this will result in high values off the diagonal.
-
-% \subsection{fMRI analyses}
-% Seventeen participants watched the first 50 minutes of Episode 1 of BBC's Sherlock.
-The video was split into two parts of approximately equal length (946 and 1030 TRs).
-All data were preprocessed and transformed to 3mm MNI space as described in the paper.
-Data were zscored across time at every voxel.
-6mm smoothing was applied.
-% Files are cropped so that all video-viewing data are aligned across participants, and all recall data are aligned to the scene timestamps below.
-The cropping includes a constant 3-TR (4.5 sec) shift to correct for hemodynamic lag.
-%
-% \subsubsection{Univariate subsequent memory analysis}
-% To characterize brain regions involved in memory encoding, we conducted an analysis inspired by prior studies investigating the  `subsequent memory effect' (Paller and Wagner).
-For each participant, we computed the correlation between topic vectors at each timepoint of the video model and recall model (they were temporally aligned with DTW and resampled to 1976 timesamples).
-The result was a 1 x 1976 vector of correlation values representing how similar each moment of the video model was to each moment of the recall model.
-Then, to compute the average correlation, we Fisher's z transformed the correlation vectors, averaged them together, and then inverse Fisher's z transformed them.
-Finally, we mean centered the vector.
-This 1 x 1976 vector represents memorable/unmemorable parts of the video, and be thought of as a `continuous' extension of a subsequent memory regressor.
-We convolved the timeseries with a double gamma function (PARAMS) to account for the hemodynamic response, and used it as a model for each voxel's activity timeseries (using FSL software).
-Finally, to aggregate across participants, we performed a mixed effects (ordinary least squares) analysis, thresholding at p<.001 and cluster correcting a p<.05.
-%
-% \subsubsection{Multivariate searchlight analyses}
-% Our multivariate analyses were designed to capture brain regions whose timepoint-by-timepoint correlational structure mirrors the correlational structure of the video and recall topic models during video viewing.
-To that end, we conducted a searchlight analysis (5x5x5 voxel cube) where for each cube, we correlated the model timepoint-by-timepoint correlation matrix with the neural correlation matrix.
-To aggregate across participants, we computed Fisher's z transformed the correlations and then averaged.
-To assess significance, we recomputed this group analysis 100 times, but randomly phase shifted the model (by \# of timepoints - 1) by the same amount for each participant but different amounts for each permutation to build a null distribution of correlation values.
-Finally, we thresholded the group averaged correlation maps where the `real' correlation value for a given voxel exceeded the 95th percentile of the null distribution.
-%
-% We first performed this analysis using the unwarped video model.
-Thus, the same model was applied to each participant and each searchlight cube.
-We then performed this analysis on the participant-wise recall models.
-To correct for non-linearities between the video model and recall models, for each participant we used DTW to temporally align the matrices.
-The algorithm recovers a path of coordinates that would bring the video and recall model in maximal temporal alignment.
-We used this path to warp the fMRI data and the recall model into alignment (separately for each participant).
-Then, we performed the exact same analysis as described above, using a searchlight to correlate the timepoint-by-timepoint recall and neural correlation matrices.
-The statistics for both analyses were computed as described above.
 

### 2018-05-18 main.tex
finished event segmentation results section

@@
 The text description contained details of the scene such as the characters, location, and a short summary of the scene (see \ref{fig:schematic} for example text, see \ref{sec:methods} for analysis details).
-We then transformed the text descriptions with the (same) topic model, resulting in a scene (1000) by topics (100) matrix where each row of the matrix represents a probabalistic mixture of topics discovered in that scene.
+We then transformed the text descriptions with the (same) topic model, resulting in a scenes (1000) by topics (100) matrix where each row of the matrix represents a probabalistic mixture of topics discovered in that scene.
 We expanded this matrix from 1000 to 1976 timepoints by copying the vectors for scenes that spanned multiple TRs.
@@
 \subsubsection{Segmenting the video and recall models into events}
-One prominent feature of the video and recall correlation matrices (see \ref{fig:model}) is the strong blocky structure along the diagonal.
-We hypothesized that this structure arises from transient stability in the language used to describe each scene of the video.
-If that were true, we reasoned that it would be possible to decode which particular scene a participant is describing by comparing the average topic model for a particular recall `event' with the average topic vector for each video event.
+One prominent feature of the video and recall correlation matrices (see \ref{fig:model}) is the strong, blocky structure along the diagonal.
+We hypothesized that this structure arises from transient stability in the language used to describe each event of the video.
+If that were true, we reasoned that it would be possible to decode which particular event a participant is describing by comparing the average topic model for a particular recall `event' with the average topic vector for each video event.
 The video event that is most similar to the given recall event is the event the participant is most likely describing.
@@
 Next, we tested the hypothesis that the individual `blocks' along the diagonals of the recall matrices represent the recall of a particular video event.
-To this end, we created a video event model, which averaged together neighboring topic vectors that the were classified to be in the same event (\ref{fig:eventseg}c), resulting in an events (34) by topics (100) matrix.
+To this end, first we created a video event model, which was done by averaging together neighboring topic vectors that the were classified to be in the same event (\ref{fig:eventseg}c), resulting in an events (34) by topics (100) matrix.
 We performed the same procedure for the recall matrices (see \ref{fig:eventseg}d for example).
@@
 These matrices represent the extent to which each recall event is similar to each video event (for each participant).
-To determine which video events the recall events most likely referred to, for event recall event, we computed video event with the highest correlation (i.e.
+To determine which video events the recall events most likely referred to, for each recall event, we found the index of the video event with the highest correlation (i.e.
 the argmax).
 This is depicted in \ref{fig:eventseg}e as the cell highlighted with the black box for each column in the video-recall event correlation matrix.
+Notably, our algorithm suggests that the example participant recalled the events largely in order, occasionally skipping over an event.
 
-Figure X displays example correlation matrices for the participants with the lowest and highest k value.
-We found that the estimated k value strongly correlated with the number of (hand-annotated) correctly remembered scenes across participants (Figure Xx, r=.67, p=.003).
+Next, we computed a group average recall event model and video-recall event correlation matrix (\ref{fig:eventseg}f).
+To do this, for each participant (and each recall event), we grouped the recall event vectors by the video event that they were most highly correlated to.
+We then averaged the recall event vectors across subjects.
+This gave an average recall event vector for all but one (of 34) events since no subjects remembered this events (according to our model).
+Lastly, we computed an average recall event (34) by video event (34) correlation matrix, and highlighted the highest correlation in the column with a black box (\ref{fig:eventseg}f).
+Notably, this matrix displayed high correlation values along the diagonal and low correlations in the off-diagonal cells.
+
+To better visualize the relationship between the video and recall models, we embedded the video and average recall model into a 2D space (using the UMAP dimensionality reduction algorithm, for details see \ref{sec:methods}) where the points represent video/recall events and the distance between them represents their similarity in 'topic space' (\ref{fig:eventseg}g).
+We computed the group average transition probabilites from each event to each other event and plotted the values as lines where the tranparency is proportional to the probability of the transition.
+By eye, it is clear that the two models have a very similar geometric structure, and the transition probabilities tend to be strongest between events that occured sequentially (or nearby) in time.
+
+To explore individual variability (and consistency) in the recall event models, we embedded each participant's recall event model in the same 2D 'topics space' described above (\ref{fig:eventseg}h).
+Despite the variability in the number of events remembered, the overall shape of most of the participants' recall trajectories are similar to the video model (\ref{fig:eventseg}h), particularly the participants with a greater number of recalled events.
+To quantify the similarity between the video model and individual recall models, we considered a number of metrics.
+First, we tested whether each participant's recall model matched the movie model in a general sense.
+To do this, for each participant we filtered the video model to only include the events that the participant remembered.
+Then, we computed the root mean squared difference (RMSD) between the video model and the recall model.
+As an example, if the participant remembered all the events in order (with perfect precision), the expected distance value would be 0.
+However, if they remembered a subset of events, events our of order or with low precision the expected distance would be greater than 0.
+To assess significance, we permformed a permutation test where we circularly shifted the recall model (10000 times) and recomputed the RMSD.
+The recall model significantly matched the video model for nine of the participants (p<.05; participants: 3-4, 8-13, 17) and the p-value for the rest of the participants was less than .25.
+Furthermore, the RMSD values were significantly correlated to memory performance across participants (Pearson's r=-.57, p=.016)  Next, we tested whether participants who recalled more events were also more precise in their recollections.
+For each participant, we computed the correlation between each recall event and its matching video event (only for the events which they recalled) and averaged the correlation within participant.
+In line with our prediction, there was a strong correlation between memory performance and precision suggesting that participants who remembered more events also remembered them more veridically (Pearson's r=.74, p=.0006).
+Related to this last measure, we considered the distinctiveness of each recall event.
+That is, how unique each recall event is with respect to all other recall events.
+We hypothesized that participants with high memory performance might describe each event in a more distinctive way (compared to those with lower memory performance who might describe events in a more general way).
+To this end, we computed a 'distinctiveness' score for each participant, i.e.
+1 - correlation between the given recall event and all other recall events for the participant.
+Then, we averaged this measure across recall events.
+We found that participants with higher memory performance also had higher distinctiveness scores (Pearson's r=.8, p=.0001).
+Finally, we tested whether participants with better memory performance were more likely to remember the events in order.
+For each participant, we computed the Spearman rank correlation between the order of events that the participant recalled and the actual order of events, sampling out only events that were actually recalled.
+We found that participants who recalled more events also recalled more of them in order (Pearson's r=.5, p=.04).
 

### 2018-05-18 main.tex
intro framing notes, commented out methods

@@
 \section{Introduction}
+
+- using list-learning / trial based experiments, we've learned a great deal about the human memory system.
+- however, its undeniable that many lab-based experiments are severely contrived as compared to real life experiences
+- for example, real life experiences are typically highly autocorrelated in space and time, a feature that is not typically present in traditional laboratory studies.
+- nonetheless, we want to leverage the tools and knowledge gained over the past few decades
+- here, we present a methodological and theoretical advance in our understanding of memory for naturalistic experiences.
+- our approach is model the semantic information contained in a stimulus and project memory responses into this stimulus space, allowing for fine-grained analysis of the mnemonic reprsentations.
 
@@
 \subsubsection{Naturalistic extensions of classic memory analyses}
+s
+Traditionally, a major limitation of 'naturalistic' memory experiments has been quantifying memory dynamics in a principled way.
+In the next section, we extend a set of classic memory analyses that were originally designed to measure memory in 'free recall' list-learning experiments to naturalistic settings. Just like recall
 
@@
 
-\subsection{Participants and Experimental Design}
-How much detail here? or just point to janice's paper?
-
-\subsubsection{Fitting a topic model from text descriptions of Sherlock}
-To quantify the flow of information from scene to scene, we used a topic model.
+% \subsection{Participants and Experimental Design}
+% How much detail here? or just point to janice's paper?
+%
+% \subsubsection{Fitting a topic model from text descriptions of Sherlock}
+% To quantify the flow of information from scene to scene, we used a topic model.
 A topic model estimates the most likely mixture of topics in a sample of text.
@@
 Then, the word count vectors were used to fit a topic model (number of topics=100, method=batch).
-
-\subsubsection{Projecting the video and verbal recall into a common space}
-We used the model described above to transform the video text descriptions and verbal recall transcripts into a common space.
+%
+% \subsubsection{Projecting the video and verbal recall into a common space}
+% We used the model described above to transform the video text descriptions and verbal recall transcripts into a common space.
 We created the video model by transforming exactly the same text (overlapping scene descriptions) with the topic model, resulting in a scene (1000) by topic (100) matrix that summarized the topics in each scene (Fig.
@@
 After this expansion, the shape of the model was the length of the duration of the video (1976 TRs).
-
-To create the recall models, for each participant we tokenized the recall transcript into a list of sentences and then mapped the list to overlapping windows of 10 sentences.
+%
+% To create the recall models, for each participant we tokenized the recall transcript into a list of sentences and then mapped the list to overlapping windows of 10 sentences.
 We transformed the list of overlapping recall sentences using the model that was trained on the video text.
@@
 Our next set of analyses sought to quantify this relationship.
-
-To quantify the similarity between the movie and recall models, for each participant we correlated every moment of the video model with every moment of the recall models, resulting in a timepoints (1976) by timepoints (1976) correlation matrix for each participant.
+%
+% To quantify the similarity between the movie and recall models, for each participant we correlated every moment of the video model with every moment of the recall models, resulting in a timepoints (1976) by timepoints (1976) correlation matrix for each participant.
 The individual matrices for each participant can be seen in Supp Fig.
 X and the group average is displayed in \ref{fig:model}c.
-
-\subsubsection{Estimating the number of recall events for each participant}
-Our metric for choosing k was to select the value that maximized the ratio of the average `within-event' correlation (i.e.
+%
+% \subsubsection{Estimating the number of recall events for each participant}
+% Our metric for choosing k was to select the value that maximized the ratio of the average `within-event' correlation (i.e.
 blocks of time the model identified as an event) and the average `across-event' correlation.
-
-\subsubsection{Characterizing memory performance}
-We used a few different metrics to assess memory that were all designed to capture the relationship between the video and recall models.
+%
+% \subsubsection{Characterizing memory performance}
+% We used a few different metrics to assess memory that were all designed to capture the relationship between the video and recall models.
 First, to get a general sense for the match between the video and recall matrices, we vectorized the the matrices and correlated them.

### 2018-05-21 main.tex
saving progress, writing up classic memory analyses

@@
 - using list-learning / trial based experiments, we've learned a great deal about the human memory system.
+
 - however, its undeniable that many lab-based experiments are severely contrived as compared to real life experiences
+
 - for example, real life experiences are typically highly autocorrelated in space and time, a feature that is not typically present in traditional laboratory studies.
+
 - nonetheless, we want to leverage the tools and knowledge gained over the past few decades
+
 - here, we present a methodological and theoretical advance in our understanding of memory for naturalistic experiences.
+
 - our approach is model the semantic information contained in a stimulus and project memory responses into this stimulus space, allowing for fine-grained analysis of the mnemonic reprsentations.
@@
 
-Next, we tested the hypothesis that the individual `blocks' along the diagonals of the recall matrices represent the recall of a particular video event.
-To this end, first we created a video event model, which was done by averaging together neighboring topic vectors that the were classified to be in the same event (\ref{fig:eventseg}c), resulting in an events (34) by topics (100) matrix.
-We performed the same procedure for the recall matrices (see \ref{fig:eventseg}d for example).
-Then, we computed the correlation between these two event models, resulting in a video events (34) by recall events (8-27, depending on the participant) correlation matrix (see \ref{fig:eventseg}e).
-These matrices represent the extent to which each recall event is similar to each video event (for each participant).
-To determine which video events the recall events most likely referred to, for each recall event, we found the index of the video event with the highest correlation (i.e.
-the argmax).
-This is depicted in \ref{fig:eventseg}e as the cell highlighted with the black box for each column in the video-recall event correlation matrix.
-Notably, our algorithm suggests that the example participant recalled the events largely in order, occasionally skipping over an event.
-
-Next, we computed a group average recall event model and video-recall event correlation matrix (\ref{fig:eventseg}f).
-To do this, for each participant (and each recall event), we grouped the recall event vectors by the video event that they were most highly correlated to.
-We then averaged the recall event vectors across subjects.
-This gave an average recall event vector for all but one (of 34) events since no subjects remembered this events (according to our model).
-Lastly, we computed an average recall event (34) by video event (34) correlation matrix, and highlighted the highest correlation in the column with a black box (\ref{fig:eventseg}f).
-Notably, this matrix displayed high correlation values along the diagonal and low correlations in the off-diagonal cells.
-
-To better visualize the relationship between the video and recall models, we embedded the video and average recall model into a 2D space (using the UMAP dimensionality reduction algorithm, for details see \ref{sec:methods}) where the points represent video/recall events and the distance between them represents their similarity in 'topic space' (\ref{fig:eventseg}g).
-We computed the group average transition probabilites from each event to each other event and plotted the values as lines where the tranparency is proportional to the probability of the transition.
-By eye, it is clear that the two models have a very similar geometric structure, and the transition probabilities tend to be strongest between events that occured sequentially (or nearby) in time.
-
-To explore individual variability (and consistency) in the recall event models, we embedded each participant's recall event model in the same 2D 'topics space' described above (\ref{fig:eventseg}h).
-Despite the variability in the number of events remembered, the overall shape of most of the participants' recall trajectories are similar to the video model (\ref{fig:eventseg}h), particularly the participants with a greater number of recalled events.
-To quantify the similarity between the video model and individual recall models, we considered a number of metrics.
-First, we tested whether each participant's recall model matched the movie model in a general sense.
-To do this, for each participant we filtered the video model to only include the events that the participant remembered.
-Then, we computed the root mean squared difference (RMSD) between the video model and the recall model.
-As an example, if the participant remembered all the events in order (with perfect precision), the expected distance value would be 0.
-However, if they remembered a subset of events, events our of order or with low precision the expected distance would be greater than 0.
-To assess significance, we permformed a permutation test where we circularly shifted the recall model (10000 times) and recomputed the RMSD.
-The recall model significantly matched the video model for nine of the participants (p<.05; participants: 3-4, 8-13, 17) and the p-value for the rest of the participants was less than .25.
-Furthermore, the RMSD values were significantly correlated to memory performance across participants (Pearson's r=-.57, p=.016)  Next, we tested whether participants who recalled more events were also more precise in their recollections.
-For each participant, we computed the correlation between each recall event and its matching video event (only for the events which they recalled) and averaged the correlation within participant.
-In line with our prediction, there was a strong correlation between memory performance and precision suggesting that participants who remembered more events also remembered them more veridically (Pearson's r=.74, p=.0006).
-Related to this last measure, we considered the distinctiveness of each recall event.
-That is, how unique each recall event is with respect to all other recall events.
-We hypothesized that participants with high memory performance might describe each event in a more distinctive way (compared to those with lower memory performance who might describe events in a more general way).
-To this end, we computed a 'distinctiveness' score for each participant, i.e.
-1 - correlation between the given recall event and all other recall events for the participant.
-Then, we averaged this measure across recall events.
-We found that participants with higher memory performance also had higher distinctiveness scores (Pearson's r=.8, p=.0001).
-Finally, we tested whether participants with better memory performance were more likely to remember the events in order.
-For each participant, we computed the Spearman rank correlation between the order of events that the participant recalled and the actual order of events, sampling out only events that were actually recalled.
-We found that participants who recalled more events also recalled more of them in order (Pearson's r=.5, p=.04).
-
 \begin{figure}[t!]
@@
 
-\subsubsection{Naturalistic extensions of classic memory analyses}
-s
-Traditionally, a major limitation of 'naturalistic' memory experiments has been quantifying memory dynamics in a principled way.
-In the next section, we extend a set of classic memory analyses that were originally designed to measure memory in 'free recall' list-learning experiments to naturalistic settings. Just like recall
+Next, we tested the hypothesis that the individual `blocks' along the diagonals of the recall matrices represent the recall of a particular video event.
+To test this, first we created a video event model, which was done by averaging together neighboring topic vectors that the were classified to be in the same event (\ref{fig:eventseg}c), resulting in an events (34) by topics (100) matrix.
+We performed the same procedure for the recall matrices (see \ref{fig:eventseg}d for example).
+Then, we computed the correlation between these two event models, resulting in a video events (34) by recall events (8-27, depending on the participant) correlation matrix (see \ref{fig:eventseg}e).
+These matrices represent the extent to which each recall event is similar to each video event (for each participant).
+To determine which video events the recall events most likely referred to, for each recall event, we found the index of the video event with the highest correlation (i.e.
+the argmax).
+This is depicted in \ref{fig:eventseg}e as the cell highlighted with the black box for each column in the video-recall event correlation matrix.
+Notably, our algorithm suggests that the example participant recalled the events largely in order, occasionally skipping over an event.
+
+Next, we computed a group average recall event model and video-recall event correlation matrix (\ref{fig:eventseg}f).
+To do this, for each participant (and each recall event), we grouped the recall event vectors by the video event that they were most highly correlated to.
+We then averaged the recall event vectors across subjects.
+This gave an average recall event vector for all but one (of 34) events since no subjects remembered this events (according to our model).
+Lastly, we computed an average recall event (34) by video event (34) correlation matrix, and highlighted the highest correlation in the column with a black box (\ref{fig:eventseg}f).
+Notably, this matrix displayed high correlation values along the diagonal and low correlations in the off-diagonal cells.
+
+To better visualize the relationship between the video and recall models, we embedded the video and average recall model into a 2D space (using the UMAP dimensionality reduction algorithm, for details see \ref{sec:methods}) where the points represent video/recall events and the distance between them represents their similarity in 'topic space' (\ref{fig:eventseg}g).
+We computed the group average transition probabilites from each event to each other event and plotted the values as lines where the tranparency is proportional to the probability of the transition.
+By eye, it is clear that the two models have a very similar geometric structure, and the transition probabilities tend to be strongest between events that occured sequentially (or nearby) in time.
+To explore individual variability (and consistency) in the recall event models, we embedded each participant's recall event model in the same 2D 'topics space' described above (\ref{fig:eventseg}h).
+Despite the variability in the number of events remembered, the overall shape of most of the participants' recall trajectories are similar to the video model (\ref{fig:eventseg}h), particularly the participants with a greater number of recalled events.
+
+\subsubsection{Measuring the quality of recall events}
+Representing the video and verbal recall as events in `topic space' affords us the ability to characterize the quality of recall in a more fine-grained and nuanced way than what is typically possible.
+To quantify the similarity between the video model and individual recall models, we considered a number of novel metrics.
+First, we tested whether each participant's recall model matched the movie model in a general sense.
+To do this, for each participant we filtered the video model to only include the events that the participant remembered.
+Then, we computed the root mean squared difference (RMSD) between the video model and the recall model.
+As an example, if the participant remembered all the events in order (with perfect precision), the expected distance value would be 0.
+However, if they remembered a subset of events, events our of order or with low precision the expected distance would be greater than 0.
+To assess significance, we performed a permutation test where we circularly shifted the recall model (10000 times) and recomputed the RMSD.
+The recall model significantly matched the video model for nine of the participants (p<.05; participants: 3-4, 8-13, 17 and the p-value for the rest of the participants was less than .25).
+Furthermore, the RMSD values were significantly correlated to memory performance across participants (Pearson's r=-.57, p=.016).
+Thus, a closer match between the video and recall event models was related to better recall performance.
+
+Next, we tested whether participants who recalled more events were also more precise in their recollections.
+For each participant, we computed the correlation between each recall event and its matching video event (only for the events which they recalled).
+This resulted in a single number for each recalled event indexing how similar the recall event was to its matching movie event (i.e the `precision' of the recall).
+We then averaged the correlations within participant.
+In line with our prediction, there was a strong correlation between memory performance and precision suggesting that participants who remembered more events also remembered them more veridically (Pearson's r=.74, p=.0006).
+Next, we considered the distinctiveness of each recall event.
+That is, how uniquely a recall event matched a given video event compared to all other video events.
+We hypothesized that participants with high memory performance might describe each event in a more distinctive way (relative to those with lower memory performance who might describe events in a more general way).
+To this end, we computed a `distinctiveness' score for each participant (i.e.
+1 - the correlation between a recall event and all non-matching video events).
+Then, we averaged this measure over recall events within participant.
+We found that participants with higher memory performance also had higher distinctiveness scores (Pearson's r=.8, p=.0001).
+Lastly, we tested whether participants with better memory performance were also more likely to remember the events in order.
+For each participant, we computed the Spearman rank correlation between the order of events that the participant recalled and the actual order of events (filtering events that were actually recalled).
+We found that participants who recalled more events also recalled more of them in order (Pearson's r=.5, p=.04).
+In summary, we found that better memory performance was associated with more precise and distinctive recall.
 
@@
 \centering
-\includegraphics[width=1\textwidth]{figs/3_behav_eventseg.pdf}
+\includegraphics[width=1\textwidth]{figs/3_behav_quality.pdf}
+\caption{\label{fig:behav}
+}
+\end{figure}
+
+\subsubsection{Naturalistic extensions of classic memory analyses}
+In addition to the novel metrics we introduce above, our approach also allows us to extend classic memory analyses designed to characterize memory in list-learning experiments to more naturalistic settings.
+Just like in a `free-recall' list-learning experiment where participants verbally recall a series of unique items in some order, our video-recall matching approach allows to analyze memory in the same way.
+
+\begin{figure}[t!]
+\centering
+\includegraphics[width=1\textwidth]{figs/4_behav_eventseg.pdf}
 \caption{\label{fig:behav}Naturalistic extensions of classic memory analyses.

### 2018-05-23 main.tex
saving progress

@@
 To assess significance, we performed a permutation test where we circularly shifted the recall model (10000 times) and recomputed the RMSD.
-The recall model significantly matched the video model for nine of the participants (p<.05; participants: 3-4, 8-13, 17 and the p-value for the rest of the participants was less than .25).
-Furthermore, the RMSD values were significantly correlated to memory performance across participants (Pearson's r=-.57, p=.016).
+The recall model significantly matched the video model for nine of the participants [p<.05; participants: 3-4, 8-13, 17 and the p-value for the rest of the participants was less than .25].
+Furthermore, the RMSD values were significantly correlated to memory performance across participants [Pearson's r(16)=-.57, p=.016].
 Thus, a closer match between the video and recall event models was related to better recall performance.
+
+% \begin{figure}[t!]
+% \centering
+% \includegraphics[width=1\textwidth]{figs/3_behav_quality.pdf}
+% \caption{\label{fig:behav}
+% }
+% \end{figure}
 
@@
 We then averaged the correlations within participant.
-In line with our prediction, there was a strong correlation between memory performance and precision suggesting that participants who remembered more events also remembered them more veridically (Pearson's r=.74, p=.0006).
+In line with our prediction, there was a strong correlation between memory performance and precision suggesting that participants who remembered more events also remembered them more veridically [Pearson's r(16)=.74, p=.0006].
 Next, we considered the distinctiveness of each recall event.
@@
 Then, we averaged this measure over recall events within participant.
-We found that participants with higher memory performance also had higher distinctiveness scores (Pearson's r=.8, p=.0001).
+We found that participants with higher memory performance also had higher distinctiveness scores [Pearson's r(16)=.8, p=.0001].
 Lastly, we tested whether participants with better memory performance were also more likely to remember the events in order.
 For each participant, we computed the Spearman rank correlation between the order of events that the participant recalled and the actual order of events (filtering events that were actually recalled).
-We found that participants who recalled more events also recalled more of them in order (Pearson's r=.5, p=.04).
+We found that participants who recalled more events also recalled more of them in order [Pearson's r(16)=.5, p=.04].
 In summary, we found that better memory performance was associated with more precise and distinctive recall.
 
-\begin{figure}[t!]
-\centering
-\includegraphics[width=1\textwidth]{figs/3_behav_quality.pdf}
-\caption{\label{fig:behav}
-}
-\end{figure}
+\subsubsection{Naturalistic extensions of classic memory analyses}
+In addition to the novel metrics we introduce above, our approach also allows us to extend classic analyses designed to characterize memory in list-learning experiments to more naturalistic settings.
+Just like in a `free-recall' list-learning experiment where participants view a set of items (such as words) and then verbally recall them, our video-recall matching approach allows us to analyze memory in the same way (where the items are recall events).
+Since each recall event has a matching video event, we can consider characteristics of the sequence of recalls.
 
-\subsubsection{Naturalistic extensions of classic memory analyses}
-In addition to the novel metrics we introduce above, our approach also allows us to extend classic memory analyses designed to characterize memory in list-learning experiments to more naturalistic settings.
-Just like in a `free-recall' list-learning experiment where participants verbally recall a series of unique items in some order, our video-recall matching approach allows to analyze memory in the same way.
+First, we asked whether the estimated number of recall events (k) by participant was related to hand-annotated accuracy as published in Chen et al.
+(2017).
+We found a strong positive correlation where subjects with a greater number of recall events also had better memory performance (Fig~\ref{eventseg_behav}a; Pearson's $r$(16)=.67, $p$=.003).
+Thus, to the extent that they are correlated, k could be use in place of a measure such as overall recall accuracy.
+We considered two additional across-participant measures of recall that characterize memory organization: temporal clustering and semantic clustering.
+Temporal clustering (as described in REF) measures the extent to which participants tend to cluster recalls of events encoded nearby in time.
+For example, if a participant recalled in exact serial order, the score would be 1 whereas if they sequentially recalled randomly positioned items the score would be ~.5.
+We found that participants who clustered in time also recalled a greater number of events (Fig~\ref{eventseg_behav}b; Pearson's $r$(16)=.62, $p$=.007).
+Next, we assessed semantic clustering.
+Similar to temporal clustering, semantic clustering measures the extent to which participants cluster their responses by semantic similarity.
+We used the topic vector representations of each event as a proxy for semantic information contained in that event.
+For each transition, we computed the rank percentile of the of the correlation between the the current event and then next event.
+For example, if a participant sequentially recalled events where each successive recall was the event that was most semantically similar to the previous, the semantic clustering score would be 1.
+If the events were recalled in a random order with respect to semantic information, the clustering score would be ~.5.
+We found that the semantic clustering score was related to memory performance across participants (Fig~\ref{eventseg_behav}c; Pearson's $r$(16)=.55, $p$=.02).
+Thus, participants who organized their recalls with respect to the semantic information contained in the scene had better memory performance.
+
+Next, we considered initiating the recall sequence (known in the literature as the `probability of first recall' or `PFR').
+This metric quantifies the likelihood of initiating a recall sequence based on the item's serial position.
+We found that participants tended to initiate their recall sequences with the first few events, which is qualitatively very similar to previously published list learning experiments (REF).
+Next, we considered another well-studied memory measure in list-learning, the lag conditional response probability curve (or lag-CRP).
+Given the recall of a stimulus in study position $n$, the lag-CRP quantifies the probability that the next item recalled will be of lag $i$.
+The results suggest a strong bias to transition sequentially in the forward direction.
+This can be seen by the high probability values in the lag ~1-5 positions compared to the rest of the transition possibilties.
+Notably, participants were instructed to recall as much as they could in order, and the shape of this lag-CRP is qualitatively similar to list-learning studies of serial recall (REF), where participants are required to recall lists of words in their serial order.
+Finally, we assessed memory performance for each event in the video.
+This plot quantifies the proportion of participants that recalled each event in the video (Fig~\ref{eventseg_behav}f).
 
@@
 
-\section{Methods}
-\label{sec:methods}
+\subsubsection{Duration of recall events}
+
+% \section{Methods}
+% \label{sec:methods}
 

### 2018-06-12 boneyard.tex
checking in paper

@@
 To account for this, we resampled the matrices back to their original shape (1976 x 100).
+
+% \section{Methods}
+% \label{sec:methods}
+
+% \subsection{Participants and Experimental Design}
+% How much detail here? or just point to janice's paper?
+%
+% \subsubsection{Fitting a topic model from text descriptions of Sherlock}
+% To quantify the flow of information from scene to scene, we used a topic model.
+A topic model estimates the most likely mixture of topics in a sample of text.
+First, the video was manually segmented into 1000 scenes, and a collection of descriptive features were manually transcribed.
+For each scene, we considered the following features: scene details (i.e.
+a sentence or two describing what happened in that scene, space (indoor or outdoor), name of all the characters in the scene, name of the character in focus, name of the character speaking, location, camera angle, music presence, and words on the screen.
+We concatenated the text for all of these features within each segment, creating a 'bag of words' describing each scene.
+We then transformed the text descriptions into overlapping windows of 50 scene segments.
+For example, the first text sample comprised the text from the first 50 segments, the second comprised the text from n+1:n+51, and so on.
+We trained our model using these overlapping text samples using scikit-learn's `CountVectorizer' and `LatentDirichletAllocation' classes.
+First, the text was transformed into a vector of word counts (default scikit-learn parameters).
+This gave a word count vector for each scene in the video.
+Then, the word count vectors were used to fit a topic model (number of topics=100, method=batch).
+%
+% \subsubsection{Projecting the video and verbal recall into a common space}
+% We used the model described above to transform the video text descriptions and verbal recall transcripts into a common space.
+We created the video model by transforming exactly the same text (overlapping scene descriptions) with the topic model, resulting in a scene (1000) by topic (100) matrix that summarized the topics in each scene (Fig.
+\ref{fig:model}a).
+The scene descriptions often spanned multiple timepoints (i.e.
+TRs).
+To account for this, we expanded the video model by copying the rows of the model for as many timepoints that the scene description spanned.
+After this expansion, the shape of the model was the length of the duration of the video (1976 TRs).
+%
+% To create the recall models, for each participant we tokenized the recall transcript into a list of sentences and then mapped the list to overlapping windows of 10 sentences.
+We transformed the list of overlapping recall sentences using the model that was trained on the video text.
+The result of this was a matrix (\# of sentences by 100 topics) that represented the most likely mixture of topics for a given chunk of sentences.
+We resampled the recall model to be the same length as the video model (1976 samples).
+The result was 17 participant-specific recall models (1976 timepoints by 100 topics).
+Intuitively, if the recall transcript for a given participant correctly described each video scene in order, the video and recall models should match closely.
+However, if the scenes were recalled out of order, omitted, or described using language that was very different from the video scene descriptions, the video and recall models would look very different.
+Figure \ref{fig:model}b shows the group average recall model.
+Qualitatively, the two matrices appear to be similar.
+Our next set of analyses sought to quantify this relationship.
+%
+% To quantify the similarity between the movie and recall models, for each participant we correlated every moment of the video model with every moment of the recall models, resulting in a timepoints (1976) by timepoints (1976) correlation matrix for each participant.
+The individual matrices for each participant can be seen in Supp Fig.
+X and the group average is displayed in \ref{fig:model}c.
+%
+% \subsubsection{Estimating the number of recall events for each participant}
+% Our metric for choosing k was to select the value that maximized the ratio of the average `within-event' correlation (i.e.
+blocks of time the model identified as an event) and the average `across-event' correlation.
+%
+% \subsubsection{Characterizing memory performance}
+% We used a few different metrics to assess memory that were all designed to capture the relationship between the video and recall models.
+First, to get a general sense for the match between the video and recall matrices, we vectorized the the matrices and correlated them.
+This resulted in a single number representing how well a given participant recalled the video.
+To get a temporally dynamic measure of memory, for each participant we computed the pairwise correlation between matching video/recall timepoints.
+This allowed us to assess memory for individual moments of the video.
+Finally to get a more nuanced representation of memory for the video, we computed a video/recall model correlation matrix for each participant.
+These timepoint (1976) by timepoint (1976) matrices represent the correlation between every moment of the video model and every moment of the recall model.
+To provide some intuition, if a participant recalled every scene at the same rate and in exactly the same order as the video, we would expect high correlation values along the diagonal of this matrix.
+However, if a participant recalls the scenes out of order, or at different rates for different scenes, this will result in high values off the diagonal.
+
+The only additional constraint we imposed was that there was at least 2 points between each line segment.
+We searched for the optimal number of line segments by iteratively splitting the participants into two groups, fitting the model to the first half and testing the model on the remaining subjects.
+To compute fit to the model, for each recall event (a 1 by 100 topics vector) we computed the nearest line segment and then calculated the mean squared distance averaging over all events and all participants (in the sample).
+We repeated this 20 times using 1-10

### 2018-06-12 main.tex
checking in paper

@@
-\documentclass[a4paper,man,natbib,floatsintext]{apa6}
+\documentclass{article}
+\usepackage[utf8]{inputenc}
+\usepackage[font=small,labelfont=bf]{caption}
+\usepackage{geometry}
+\usepackage{natbib}
+\usepackage{pxfonts}
+\usepackage{graphicx}
+% \usepackage{amsmath}
+% \newcommand{\rpm}{\raisebox{.2ex}{$\scriptstyle\pm$}}
+% \DeclareMathOperator*{\argmax}{arg\,max}
 
-\usepackage[english]{babel}
-\usepackage[utf8x]{inputenc}
-\usepackage{amsmath}
-\usepackage{graphicx}
-\usepackage[colorinlistoftodos]{todonotes}
-\usepackage[font=small,labelfont=bf]{caption}
-\newcommand{\rpm}{\raisebox{.2ex}{$\scriptstyle\pm$}}
-\usepackage{amsmath}
-\DeclareMathOperator*{\argmax}{arg\,max}
-
-\title{Sherlock topic model paper}
-% A common space for dynamic experiences and memories
-% Geometric principles of episodic recall for naturalistic experiences
-% The geometry of episodic recall for naturalistic experiences
-% Recasting episodic memory as a weighted blend of prior experiences
-% Capturing the moment-by-moment flow of information in naturalistic stimuli
-% A continuous, content-general approach to characterizing memory for naturalistic events
-% A common model for naturalistic stimuli, memories, and brains
-% \title{A dynamic, content-general encoding signal to characterize memory for naturalistic stimuli}
-% Topic models as a bridge between naturalistic stimuli, memories, and brains
-% Automated analysis of memory for naturalistic stimuli using topic modeling
-% Topic modeling as a link between videos and memories
-% Topic models as a bridge between dynamic experiences and memories
-
-\shorttitle{Your APA6-Style Manuscript}
+% \title{Capturing the geometric structure of our experiences and how we remember them}
+\title{The fundamental shape of experiences are preserved in memory}
 \author{Andrew C. Heusser \& Jeremy R. Manning}
-\affiliation{Dartmouth College}
-
-\abstract{
-}
+% \affiliation{Dartmouth College}
 
@@
 
+\section{Abstract}
+{
+The human memory system is adept at cataloging the rich dynamics of ongoing experience.
+However, traditional trial-based memory experiments cannot capture these dynamics, and therefore cannot be used to study them.
+By constraining participants' experiences in an experiment to occur in temporally discrete trials (and often arranged in a randomized order) the temporal, contextual, and emotional structure of those in-lab experiences necessarily differ from the naturalistic experiences we encounter in everyday life.
+Here we investigate how people verbally recall continuous videos by characterizing and relating the thematic dynamics, or ``trajectories,'' of the stimulus and participants' recalls.
+Unlike trial-based studies of memory wherein participants attempt to recall the precise stimuli they encounter, naturalistic recall entails capturing the fundamental geometric components of the stimulus topic trajectory.
+The precise words participants use to describe the stimulus, and the level of detail and number of distinct events they recall, vary considerably across participants.
+Nevertheless, the majority of participants' recall narratives captured the fundamental ``shape'' of the original stimulus.
+These findings provide a window into which aspects of naturalistic experiences must be preserved, and which might be more flexible, in considering whether and how those experiences are remembered.
+
 \section{Introduction}
 
-- using list-learning / trial based experiments, we've learned a great deal about the human memory system.
+What does it mean to \textit{remember} something?
+In traditional episodic memory experiments~\citep[e.g., list-learning or trial-based experiments;][]{Murd62a, Kaha96}, remembering is often cast as a binary operation: either an item is recalled or it isn't.
+More nuanced studies might incorporate self-reported confidence measures as a proxy for memory strength, or ask participants to discriminate between ``recollecting'' an experience or a feeling of ``familiarity''~\citep{Yone02}.
+However, characterizing and evaluating memory in more realistic contexts (e.g., telling a story to a friend about a recent vacation) is a fundamentally different task.
+Real-world recall is continuous, rather than binary.
+The specific words used to describe an experience have very little bearing on whether the experience is considered to have been ``remembered.''  Further, one might remember the gist of an experience but forgot (or neglect to recount) particular details.
+Or different people who share an experience might recount the experience with a similar level of detail, but the specific details that were remembered might vary across people.
+Which aspects of those recollections should be considered fundamental, and which are extraneous to the main story?
 
-- however, its undeniable that many lab-based experiments are severely contrived as compared to real life experiences
+Another major difference between traditional trial-based memory paradigms and real-world memory concerns the subjective experience of the participant.
+For example, consider an emotionally salient event in your life (e.g.\ marriage, the birth of a child, death of a loved one, etc.), or even a movie that you were especially impacted by.
+No list-learning paradigm (or similar) can hope to capture the nuance and depth of such experiences.
+Our everyday experiences feel ``important'' to us, whereas the words we study on a random word list do not.
+One component of naturalistic experiences that enhances their impact concerns the temporal structure with which they unfold.
+For example, our experiences in the real world are necessarily autocorrelated in space and time on short timescales.
+Further, or experiences are often characterized by longer timescale correlations that reflect the impact of our past actions and observations.
+These temporal dynamics are not typically present in traditional memory studies, but are important if we wish to understand how our memory systems remember our everyday experiences.
 
-- for example, real life experiences are typically highly autocorrelated in space and time, a feature that is not typically present in traditional laboratory studies.
+% MAY NEED ANOTHER PARAGRAPH HERE MOTIVATING THE HYPOTHESIS THAT PEOPLE
+% REMEMBER THE GIST OF AN EXPERIENCE
 
-- nonetheless, we want to leverage the tools and knowledge gained over the past few decades
-
-- here, we present a methodological and theoretical advance in our understanding of memory for naturalistic experiences.
-
-- our approach is model the semantic information contained in a stimulus and project memory responses into this stimulus space, allowing for fine-grained analysis of the mnemonic reprsentations.
+To study the temporal and semantic aspects of memory for naturalistic experiences, we analyzed an open dataset in which participants view and verbally recall an episode of the BBC series \textit{Sherlock}~\citep{ChenEtal17}.
+We developed a novel computational approach which combines topic ~\cite{Blei03} and hidden Markov models to capture the temporal evolution of rich semantic structure present in naturalistic experiences.
+We then use this model to characterize the shape and contents of episodic memories for naturalistic experiences.
 
@@
 
-\subsubsection{A model to capture the moment-by-moment flow of information in naturalistic stimuli}
-We fit a topic model to overlapping windows of manually annotated text descriptions of scenes from an episode of the BBC series, Sherlock.
-The text description contained details of the scene such as the characters, location, and a short summary of the scene (see \ref{fig:schematic} for example text, see \ref{sec:methods} for analysis details).
-We then transformed the text descriptions with the (same) topic model, resulting in a scenes (1000) by topics (100) matrix where each row of the matrix represents a probabalistic mixture of topics discovered in that scene.
+\subsubsection{Capturing the geometric structure of naturalistic stimuli}
+We fit a topic model to overlapping windows of manually annotated text descriptions of scenes from the episode.
+The text descriptions contained details of the scene such as the characters, location, and a short summary of the scene (see \ref{fig:schematic} for example text, see \ref{sec:methods} for analysis details).
+We then transformed the text descriptions with the (same) topic model, resulting in a scenes (1000) by topics (100) matrix, where each row of the matrix represents a probabalistic mixture of topics discovered in that scene.
 We expanded this matrix from 1000 to 1976 timepoints by copying the vectors for scenes that spanned multiple TRs.
@@
 The sparsity was also expected since the topic modeling approach we used (Latent Dirichlet Allocation) assumes a sparse Dirichlet prior.
-By eye, there are clear transitions from one topic `state' to the next, likely indexing scene transitions in the stimulus.
+By eye, there are clear transitions from one topic `state' to the next, possibly indexing scene transitions in the stimulus.
 To get a better handle on this temporal structure, we computed the timepoint-by-timepoint correlation matrix of the video model (\ref{fig:model}b).
-This correlation matrix reveals that the model has a strong, blocky structure along the diagonal.
+This correlation matrix reveals that the model has a strong, block-diagonal structure.
 Another interesting feature is that there is very little correlation between events (i.e.
@@
 Note that the topics were derived solely from the text descriptions of the stimulus, and so the topic models estimated for recall are entirely dependent on the topics in the episode.
-In effect, this approach projects the participants' verbal recall into the video 'stimulus space', allowing us to quantify the dynamics of verbally reported memories as well as relate them to the experiences from which they were born.
+In effect, this approach projects the participants' verbal recall into the video 'stimulus space', allowing us to quantify the dynamics of verbally reported memories as well as relate them to their originating experiences.
 
@@
 For each participant, we computed a timepoint-by-timepoint correlation matrix from recall models.
-Like the video model, the recall correlation matrices exhibited blocky structure along the diagonal (Supp Fig X).
-To visualize the group average, we resampled all of the recall models to the duration of the video model (1976 timepoints), computed the timepoint-by-timepoint correlation matrices and then averaged across partcipants.
-Like the video correlation matrix, the average recall matrix was blocky along the diagonal, albeit noisier (\ref{fig:model}d).
-Presumably this noise stems from the fact that there was variability in the amount of time each participant spent describing each event.
-We will come back to this point later in the paper.
+Like the video model, each participant's recall correlation matrix exhibited a block-diagonal structure (Supp Fig X).
+To visualize the group average, we resampled all of the recall models to the duration of the video model (1976 timepoints), computed the timepoint-by-timepoint correlation matrices and then averaged across participants.
+The average recall matrix also had a block-diagonal structure, albeit smoother than the video model (\ref{fig:model}d).
+At least some of this smoothness stems from the fact that there was variability in the amount of time each participant spent describing each event, and thus the block sizes were variable.
 
@@
 The participants in this study were instructed to recall as much of the episode as they could in the order it happened.
-Thus, we expected that to the extent that participants followed these instructions and had reasonably good memory accuracy, the recall models should resemble the video model.
-In our first approach to test this hypothesis, we correlated each moment of the video model with each moment of each participants' resampled recall model.
+Thus, we expected that to the extent that participants followed these instructions (and had reasonably good memory accuracy), the recall models should resemble the video model.
+To test whether this was true, we correlated each moment of the video model with each moment of each participants' resampled recall model.
 We then averaged these matrices together to get a single group averaged matrix.
@@
 
-\begin{figure}[t!]
-\centering
-\includegraphics[width=1\textwidth]{figs/1_video_recall_models.pdf}
-\caption{\label{fig:model}Topic models for the video and verbal recall.
+% \begin{figure}[t!]
+% \centering
+% \includegraphics[width=1\textwidth]{figs/1_video_recall_models.pdf}
+% \caption{\label{fig:model}Topic models for the video and verbal recall.
 A.
@@
 }
-\end{figure}
+% \end{figure}
 
-\subsubsection{Segmenting the video and recall models into events}
-One prominent feature of the video and recall correlation matrices (see \ref{fig:model}) is the strong, blocky structure along the diagonal.
-We hypothesized that this structure arises from transient stability in the language used to describe each event of the video.
-If that were true, we reasoned that it would be possible to decode which particular event a participant is describing by comparing the average topic model for a particular recall `event' with the average topic vector for each video event.
-The video event that is most similar to the given recall event is the event the participant is most likely describing.
+\subsubsection{Segmenting the video and recall models into `events'}
+One prominent feature of the video and recall correlation matrices (see \ref{fig:model}) is a strong, block structure along the diagonal of the matrices.
+We hypothesized that this structure might arise from transient stability in the language used to describe each event of the video.
+If true, we reasoned that it would be possible to decode which particular event a participant is describing by comparing the average topic model for a particular recall `event' with the average topic vector for each video event.
+Following this logic, the video event that is most similar to the given recall event would be the event the participant is most likely describing.
 To test this idea it is first necessary to systematically parse the matrices into events.
-To do this, we leveraged the event segmentation approach developed by Baldassano et al 2017.
-Briefly, this algorithm implements a variant of a Hidden Markov Model to estimate k events given a (multivariate) time series and a k value (number of states).
-We automatically determined a k value for the video model and each participant's recall model using the following equation:
-
-% ADD EQUATION HERE
-
-The algorithm determined 34 events for the movie model and a range of values (range=8-27, mean= 15.41, SD=5.6) for the recall models.
-The events discovered for a representative participant can be seen in \ref{fig:eventseg}b.
-Importantly, the k values were highly correlated to hand annotated accuracy (r(16)=.67, p=.003) across participants.
-Thus, the blocky temporal structure in the recall matrices computed by our model is strongly related to the variability in memory performance across participants.
+To do this, we leveraged a hidden Markov model (~\citep{BaldEtal17}) to estimate k events given a (multivariate) time series and a $k$ value (number of states).
+The algorithm determined 34 events for the movie model and a range of values (range=8-27, mean= 15.41, SD=5.6) for the recall models (see ~\ref{sec:methods} for details on choosing $k$).
+The events discovered for a representative participant are highlighted in \ref{fig:eventseg}b.
+Importantly, the $k$ values were highly correlated to hand annotated accuracy (r(16)=.67, p=.003) across participants.
+Thus, the block-diagonal temporal structure in the recall matrices computed by our model is strongly related to the variability in memory performance across participants.
 
@@
 H.
-2D embedding of video and average recall event models.
-}
+2D embedding of video and average recall event models.}
 \end{figure}
 
-Next, we tested the hypothesis that the individual `blocks' along the diagonals of the recall matrices represent the recall of a particular video event.
+Next, we explored the idea that the individual `blocks' along the diagonals of the recall matrices represent the recall of a particular video event.
 To test this, first we created a video event model, which was done by averaging together neighboring topic vectors that the were classified to be in the same event (\ref{fig:eventseg}c), resulting in an events (34) by topics (100) matrix.
@@
 This is depicted in \ref{fig:eventseg}e as the cell highlighted with the black box for each column in the video-recall event correlation matrix.
-Notably, our algorithm suggests that the example participant recalled the events largely in order, occasionally skipping over an event.
+Notably, our algorithm suggests that the example participant recalled the events largely in order (occasionally skipping over an event).
 
-Next, we computed a group average recall event model and video-recall event correlation matrix (\ref{fig:eventseg}f).
-To do this, for each participant (and each recall event), we grouped the recall event vectors by the video event that they were most highly correlated to.
-We then averaged the recall event vectors across subjects.
-This gave an average recall event vector for all but one (of 34) events since no subjects remembered this events (according to our model).
+Next, we computed a group-average recall event model and video-recall event correlation matrix (\ref{fig:eventseg}f).
+To do this, for each participant (and each recall event), we grouped the recall event vectors (across all participants) by the video event that they were most highly correlated to.
+We then averaged the recall event vectors within event.
+This gave an average recall event vector for all but one (of 34) event since no participant remembered this event (according to our model).
 Lastly, we computed an average recall event (34) by video event (34) correlation matrix, and highlighted the highest correlation in the column with a black box (\ref{fig:eventseg}f).
 Notably, this matrix displayed high correlation values along the diagonal and low correlations in the off-diagonal cells.
+This suggests that on average, participants were able to recapitulate the events in the episode and our model was sensitive enough to capture this behavior.
 
@@
 
-\subsubsection{Measuring the quality of recall events}
-Representing the video and verbal recall as events in `topic space' affords us the ability to characterize the quality of recall in a more fine-grained and nuanced way than what is typically possible.
+\subsubsection{The fundamental shape of the stimulus is preserved in recall}
+To formalize the observation that participants' recall trajectories generally matched the shape of the video trajectory, we fit participants' recall data to a model comprised of $n$ line segments that were connected by the average recall trajectory coordinates.
+We fixed the endpoints of the model at the average first and last recall event, but fit the placement/length of rest of the segments to the data using the average recall events as `hinge-points'.
+Using a cross-validated model fitting procedure (see ~\ref{sec:methods} for details), we searched for the optimal number of line segments.
+The best fitting model ($n$=10) can be seen in Fig.~\ref{fig:linesegs}.
+This model represents the set of consecutive line segments that best describe participant's recall trajectories.
+Visualizing this model with the video model suggests that participants recall trajectories capture the fundamental shape of the stimulus.
+
+%% HOW CAN WE TEST THIS STATISTICALLY?
+
+To better understand the content
+
+\subsubsection{Measuring the quality of recall}
+Representing the video and verbal recall as events in `topic space' also affords us the ability to characterize the quality of recall in a more fine-grained and nuanced way than what is typically possible.
 To quantify the similarity between the video model and individual recall models, we considered a number of novel metrics.
@@
 Thus, a closer match between the video and recall event models was related to better recall performance.
-
-% \begin{figure}[t!]
-% \centering
-% \includegraphics[width=1\textwidth]{figs/3_behav_quality.pdf}
-% \caption{\label{fig:behav}
-% }
-% \end{figure}
 
@@
 
-\begin{figure}[t!]
+\begin{figure}[ht!]
 \centering
@@
 \end{figure}
-
-\subsubsection{Duration of recall events}
-
-% \section{Methods}
-% \label{sec:methods}
-
-% \subsection{Participants and Experimental Design}
-% How much detail here? or just point to janice's paper?
-%
-% \subsubsection{Fitting a topic model from text descriptions of Sherlock}
-% To quantify the flow of information from scene to scene, we used a topic model.
-A topic model estimates the most likely mixture of topics in a sample of text.
-First, the video was manually segmented into 1000 scenes, and a collection of descriptive features were manually transcribed.
-For each scene, we considered the following features: scene details (i.e.
-a sentence or two describing what happened in that scene, space (indoor or outdoor), name of all the characters in the scene, name of the character in focus, name of the character speaking, location, camera angle, music presence, and words on the screen.
-We concatenated the text for all of these features within each segment, creating a 'bag of words' describing each scene.
-We then transformed the text descriptions into overlapping windows of 50 scene segments.
-For example, the first text sample comprised the text from the first 50 segments, the second comprised the text from n+1:n+51, and so on.
-We trained our model using these overlapping text samples using scikit-learn's `CountVectorizer' and `LatentDirichletAllocation' classes.
-First, the text was transformed into a vector of word counts (default scikit-learn parameters).
-This gave a word count vector for each scene in the video.
-Then, the word count vectors were used to fit a topic model (number of topics=100, method=batch).
-%
-% \subsubsection{Projecting the video and verbal recall into a common space}
-% We used the model described above to transform the video text descriptions and verbal recall transcripts into a common space.
-We created the video model by transforming exactly the same text (overlapping scene descriptions) with the topic model, resulting in a scene (1000) by topic (100) matrix that summarized the topics in each scene (Fig.
-\ref{fig:model}a).
-The scene descriptions often spanned multiple timepoints (i.e.
-TRs).
-To account for this, we expanded the video model by copying the rows of the model for as many timepoints that the scene description spanned.
-After this expansion, the shape of the model was the length of the duration of the video (1976 TRs).
-%
-% To create the recall models, for each participant we tokenized the recall transcript into a list of sentences and then mapped the list to overlapping windows of 10 sentences.
-We transformed the list of overlapping recall sentences using the model that was trained on the video text.
-The result of this was a matrix (\# of sentences by 100 topics) that represented the most likely mixture of topics for a given chunk of sentences.
-We resampled the recall model to be the same length as the video model (1976 samples).
-The result was 17 participant-specific recall models (1976 timepoints by 100 topics).
-Intuitively, if the recall transcript for a given participant correctly described each video scene in order, the video and recall models should match closely.
-However, if the scenes were recalled out of order, omitted, or described using language that was very different from the video scene descriptions, the video and recall models would look very different.
-Figure \ref{fig:model}b shows the group average recall model.
-Qualitatively, the two matrices appear to be similar.
-Our next set of analyses sought to quantify this relationship.
-%
-% To quantify the similarity between the movie and recall models, for each participant we correlated every moment of the video model with every moment of the recall models, resulting in a timepoints (1976) by timepoints (1976) correlation matrix for each participant.
-The individual matrices for each participant can be seen in Supp Fig.
-X and the group average is displayed in \ref{fig:model}c.
-%
-% \subsubsection{Estimating the number of recall events for each participant}
-% Our metric for choosing k was to select the value that maximized the ratio of the average `within-event' correlation (i.e.
-blocks of time the model identified as an event) and the average `across-event' correlation.
-%
-% \subsubsection{Characterizing memory performance}
-% We used a few different metrics to assess memory that were all designed to capture the relationship between the video and recall models.
-First, to get a general sense for the match between the video and recall matrices, we vectorized the the matrices and correlated them.
-This resulted in a single number representing how well a given participant recalled the video.
-To get a temporally dynamic measure of memory, for each participant we computed the pairwise correlation between matching video/recall timepoints.
-This allowed us to assess memory for individual moments of the video.
-Finally to get a more nuanced representation of memory for the video, we computed a video/recall model correlation matrix for each participant.
-These timepoint (1976) by timepoint (1976) matrices represent the correlation between every moment of the video model and every moment of the recall model.
-To provide some intuition, if a participant recalled every scene at the same rate and in exactly the same order as the video, we would expect high correlation values along the diagonal of this matrix.
-However, if a participant recalls the scenes out of order, or at different rates for different scenes, this will result in high values off the diagonal.
 

### 2018-06-19 boneyard.tex
checking in progress

--- 2018-05-15 boneyard.tex
@@
 To account for this, we resampled the matrices back to their original shape (1976 x 100).
+
+\section{Methods}
+\label{sec:methods}
+
+\subsection{Participants and Experimental Design}
+How much detail here? or just point to janice's paper?
+
+\subsubsection{Fitting a topic model from text descriptions of Sherlock}
+To quantify the flow of information from scene to scene, we used a topic model.
+A topic model estimates the most likely mixture of topics in a sample of text.
+First, the video was manually segmented into 1000 scenes, and a collection of descriptive features were manually transcribed.
+For each scene, we considered the following features: scene details (i.e.
+a sentence or two describing what happened in that scene, space (indoor or outdoor), name of all the characters in the scene, name of the character in focus, name of the character speaking, location, camera angle, music presence, and words on the screen.
+We concatenated the text for all of these features within each segment, creating a 'bag of words' describing each scene.
+We then transformed the text descriptions into overlapping windows of 50 scene segments.
+For example, the first text sample comprised the text from the first 50 segments, the second comprised the text from n+1:n+51, and so on.
+We trained our model using these overlapping text samples using scikit-learn's `CountVectorizer' and `LatentDirichletAllocation' classes.
+First, the text was transformed into a vector of word counts (default scikit-learn parameters).
+This gave a word count vector for each scene in the video.
+Then, the word count vectors were used to fit a topic model (number of topics=100, method=batch).
+
+\subsubsection{Projecting the video and verbal recall into a common space}
+We used the model described above to transform the video text descriptions and verbal recall transcripts into a common space.
+We created the video model by transforming exactly the same text (overlapping scene descriptions) with the topic model, resulting in a scene (1000) by topic (100) matrix that summarized the topics in each scene (Fig.
+\ref{fig:model}a).
+The scene descriptions often spanned multiple timepoints (i.e.
+TRs).
+To account for this, we expanded the video model by copying the rows of the model for as many timepoints that the scene description spanned.
+After this expansion, the shape of the model was the length of the duration of the video (1976 TRs).
+
+To create the recall models, for each participant we tokenized the recall transcript into a list of sentences and then mapped the list to overlapping windows of 10 sentences.
+We transformed the list of overlapping recall sentences using the model that was trained on the video text.
+The result of this was a matrix (\# of sentences by 100 topics) that represented the most likely mixture of topics for a given chunk of sentences.
+We resampled the recall model to be the same length as the video model (1976 samples).
+The result was 17 participant-specific recall models (1976 timepoints by 100 topics).
+Intuitively, if the recall transcript for a given participant correctly described each video scene in order, the video and recall models should match closely.
+However, if the scenes were recalled out of order, omitted, or described using language that was very different from the video scene descriptions, the video and recall models would look very different.
+Figure \ref{fig:model}b shows the group average recall model.
+Qualitatively, the two matrices appear to be similar.
+Our next set of analyses sought to quantify this relationship.
+
+To quantify the similarity between the movie and recall models, for each participant we correlated every moment of the video model with every moment of the recall models, resulting in a timepoints (1976) by timepoints (1976) correlation matrix for each participant.
+The individual matrices for each participant can be seen in Supp Fig.
+X and the group average is displayed in \ref{fig:model}c.
+
+\subsubsection{Estimating the number of recall events for each participant}
+Our metric for choosing k was to select the value that maximized the ratio of the average `within-event' correlation (i.e.
+blocks of time the model identified as an event) and the average `across-event' correlation.
+
+\subsubsection{Characterizing memory performance}
+We used a few different metrics to assess memory that were all designed to capture the relationship between the video and recall models.
+First, to get a general sense for the match between the video and recall matrices, we vectorized the the matrices and correlated them.
+This resulted in a single number representing how well a given participant recalled the video.
+To get a temporally dynamic measure of memory, for each participant we computed the pairwise correlation between matching video/recall timepoints.
+This allowed us to assess memory for individual moments of the video.
+Finally to get a more nuanced representation of memory for the video, we computed a video/recall model correlation matrix for each participant.
+These timepoint (1976) by timepoint (1976) matrices represent the correlation between every moment of the video model and every moment of the recall model.
+To provide some intuition, if a participant recalled every scene at the same rate and in exactly the same order as the video, we would expect high correlation values along the diagonal of this matrix.
+However, if a participant recalls the scenes out of order, or at different rates for different scenes, this will result in high values off the diagonal.
+
+The only additional constraint we imposed was that there was at least 2 points between each line segment.
+We searched for the optimal number of line segments by iteratively splitting the participants into two groups, fitting the model to the first half and testing the model on the remaining subjects.
+To compute fit to the model, for each recall event (a 1 by 100 topics vector) we computed the nearest line segment and then calculated the mean squared distance averaging over all events and all participants (in the sample).
+We repeated this 20 times using 1-10

### 2018-06-19 main.tex
checking in progress

@@
 % \title{Capturing the geometric structure of our experiences and how we remember them}
-\title{The fundamental shape of experiences are preserved in memory}
+\title{The fundamental geometry of dynamic experiences is preserved in memory}
 \author{Andrew C. Heusser \& Jeremy R. Manning}
@@
 
-% MAY NEED ANOTHER PARAGRAPH HERE MOTIVATING THE HYPOTHESIS THAT PEOPLE
-% REMEMBER THE GIST OF AN EXPERIENCE
-
 To study the temporal and semantic aspects of memory for naturalistic experiences, we analyzed an open dataset in which participants view and verbally recall an episode of the BBC series \textit{Sherlock}~\citep{ChenEtal17}.
-We developed a novel computational approach which combines topic ~\cite{Blei03} and hidden Markov models to capture the temporal evolution of rich semantic structure present in naturalistic experiences.
+We developed a novel computational approach which combines topic models ~\cite{Blei03} and hidden Markov models to capture the temporal evolution of rich semantic structure present in naturalistic experiences.
 We then use this model to characterize the shape and contents of episodic memories for naturalistic experiences.
+We hypothesized that memory for naturalistic experiences is more about preserving the overall ``shape'' of an experience than any of the particular details.
 
@@
 
-\subsubsection{Capturing the geometric structure of naturalistic stimuli}
-We fit a topic model to overlapping windows of manually annotated text descriptions of scenes from the episode.
-The text descriptions contained details of the scene such as the characters, location, and a short summary of the scene (see \ref{fig:schematic} for example text, see \ref{sec:methods} for analysis details).
-We then transformed the text descriptions with the (same) topic model, resulting in a scenes (1000) by topics (100) matrix, where each row of the matrix represents a probabalistic mixture of topics discovered in that scene.
+\subsubsection{A model to capture the geometric structure of naturalistic stimuli}
+We fit a topic model ~\cite{Blei03} to manually annotated text descriptions of scenes from the episode.
+The text descriptions contained details of the scene such as the characters, location, and a short summary of the scene (see Fig.\ref{fig:schematic} for example text, see \ref{sec:methods} for analysis details).
+We then transformed the text descriptions using the (same) topic model, resulting in a scenes (1000) by topics (100) matrix, where each row of the matrix represents a probabalistic mixture of topics discovered in that scene (See Fig.\ref{fig:schematic} for example topic vectors).
 We expanded this matrix from 1000 to 1976 timepoints by copying the vectors for scenes that spanned multiple TRs.
 As depicted in \ref{fig:model}a, the topics are sparse and change slowly over time.
-This gradual change was anticipated, since we used overlapping windows of text (50 sentences) as input to the model.
-The sparsity was also expected since the topic modeling approach we used (Latent Dirichlet Allocation) assumes a sparse Dirichlet prior.
-By eye, there are clear transitions from one topic `state' to the next, possibly indexing scene transitions in the stimulus.
+Furthermore, there are clear transitions from one topic `state' to the next, possibly indexing scene transitions in the stimulus.
 To get a better handle on this temporal structure, we computed the timepoint-by-timepoint correlation matrix of the video model (\ref{fig:model}b).
 This correlation matrix reveals that the model has a strong, block-diagonal structure.
-Another interesting feature is that there is very little correlation between events (i.e.
+Another interesting feature is that there is very little correlation between blocks (i.e.
 the off-diagonal values are small).
-This is an important feature of the model because the `event' representations are unique and highly discriminable.
+This is an interesting feature of the model because to the extend that the blocks represent `events' in the video, the model representations of those events are unique and highly discriminable.
 
-\subsubsection{Projecting verbal recall into stimulus space}
-After watching the episode, participants verbally recalled (in order) as much of the episode as they could.
-We used the same topic model (fit with the text descriptions of the video) to transform participants' verbal recall transcripts (split by sentence in overlapping chunks of 10 sentences).
+\subsubsection{Modelling verbal free recall}
+After watching the episode, participants verbally recalled (in order) as much as they could.
+We used the same topic model (fit with the text descriptions of the video) to transform participants' verbal recall transcripts.
 The result was a sentences (range: X to X) by topics (100) matrix for each participant, where each row represented the estimated mixture of topics for a given window of sentences during recall.
 In order to average the recall models across participants, we resampled each model at the resolution of the video model (1976 timepoints).
-The individual models can be seen in Supp Fig X and the group average is plotted in \ref{fig:model}c.
-Note that the topics were derived solely from the text descriptions of the stimulus, and so the topic models estimated for recall are entirely dependent on the topics in the episode.
+The individual models can be seen in Supp Fig X and the group average is plotted in Fig.
+\ref{fig:model}c.
+Note that the topics were derived solely from the text descriptions of the video, and so the topic models estimated for recall are dependent on the topics in the episode.
 In effect, this approach projects the participants' verbal recall into the video 'stimulus space', allowing us to quantify the dynamics of verbally reported memories as well as relate them to their originating experiences.
@@
 The average recall matrix also had a block-diagonal structure, albeit smoother than the video model (\ref{fig:model}d).
-At least some of this smoothness stems from the fact that there was variability in the amount of time each participant spent describing each event, and thus the block sizes were variable.
 
-\subsubsection{Correlating the video and recall models}
+\subsubsection{Bridging between the stimulus and recall}
 The participants in this study were instructed to recall as much of the episode as they could in the order it happened.
-Thus, we expected that to the extent that participants followed these instructions (and had reasonably good memory accuracy), the recall models should resemble the video model.
+Thus, we hypothesized that the recall models should resemble the video model to the extent that participants followed these instructions and had reasonably good memory accuracy.
 To test whether this was true, we correlated each moment of the video model with each moment of each participants' resampled recall model.
@@
 Following this logic, the video event that is most similar to the given recall event would be the event the participant is most likely describing.
-To test this idea it is first necessary to systematically parse the matrices into events.
-To do this, we leveraged a hidden Markov model (~\citep{BaldEtal17}) to estimate k events given a (multivariate) time series and a $k$ value (number of states).
+To test this idea, it is first necessary to systematically parse the matrices into events.
+To do this, we leveraged a hidden Markov model (~\citep{BaldEtal17}) to estimate $k$ events from a (multivariate) time series.
 The algorithm determined 34 events for the movie model and a range of values (range=8-27, mean= 15.41, SD=5.6) for the recall models (see ~\ref{sec:methods} for details on choosing $k$).
 The events discovered for a representative participant are highlighted in \ref{fig:eventseg}b.
-Importantly, the $k$ values were highly correlated to hand annotated accuracy (r(16)=.67, p=.003) across participants.
-Thus, the block-diagonal temporal structure in the recall matrices computed by our model is strongly related to the variability in memory performance across participants.
 
@@
 
-Next, we computed a group-average recall event model and video-recall event correlation matrix (\ref{fig:eventseg}f).
+Next, we computed a group-averaged recall event model and video-recall event correlation matrix (\ref{fig:eventseg}f).
 To do this, for each participant (and each recall event), we grouped the recall event vectors (across all participants) by the video event that they were most highly correlated to.
-We then averaged the recall event vectors within event.
-This gave an average recall event vector for all but one (of 34) event since no participant remembered this event (according to our model).
+We then averaged the recall event vectors within group.
+This yielded an average recall event vector for all but one (of 34) event (since no participant remembered this event according to our model).
 Lastly, we computed an average recall event (34) by video event (34) correlation matrix, and highlighted the highest correlation in the column with a black box (\ref{fig:eventseg}f).
@@
 This suggests that on average, participants were able to recapitulate the events in the episode and our model was sensitive enough to capture this behavior.
+% NOTE: ^ Need a null model for the group analysis.
+I think it could be to get a result that looks like this even if we scrambled the text.
+My concern is that I'm grouping the recall events by the video event they were most similar to, and then averaging, which may give rise to a smooth looking plot without any real information there...
 
-To better visualize the relationship between the video and recall models, we embedded the video and average recall model into a 2D space (using the UMAP dimensionality reduction algorithm, for details see \ref{sec:methods}) where the points represent video/recall events and the distance between them represents their similarity in 'topic space' (\ref{fig:eventseg}g).
-We computed the group average transition probabilites from each event to each other event and plotted the values as lines where the tranparency is proportional to the probability of the transition.
-By eye, it is clear that the two models have a very similar geometric structure, and the transition probabilities tend to be strongest between events that occured sequentially (or nearby) in time.
+\subsubsection{Naturalistic extensions of classic memory analyses}
+Just like in a traditional `free-recall' list-learning experiment where participants view a list of words and then verbally recall them, our video-recall matching approach described above affords us the ability to analyze memory in the same way (where the recalled words are analogous to recalled events).
+In our first set of analyses, we sought to characterize memory performance/dynamics by extending classic analyses originally designed for list-learning experiments to more naturalistic settings.
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[width=1\textwidth]{figs/4_behav_eventseg.pdf}
+\caption{\label{fig:behav}Naturalistic extensions of classic memory analyses.
+A-C use the `smooth' approach and D-F use the `best' approach (see Methods for details).
+A/D.
+The probability of first recall as a function of the serial position the the event during encoding.
+B/E.
+Given recall of event i, the probability that the next recalled item will be from serial position i \rpm~lag.
+C/F.
+Proportion recalled as a function of serial position.
+All error bars are the standard error of the mean derived from a bootstrap resampling procedure.
+}
+\end{figure}
+
+First, we asked whether the estimated number of recall events (k) by participant was related to hand-annotated accuracy as published in Chen et al.
+(2017).
+We found a strong positive correlation where subjects with a greater number of recall events also had better memory performance (Fig~\ref{eventseg_behav}a; Pearson's $r$(16)=.67, $p$=.003).
+Thus, the block-diagonal temporal structure in the recall matrices computed by our model is strongly related to the variability in memory performance across participants.
+We considered two additional across-participant measures of recall that characterize memory organization: temporal clustering and semantic clustering.
+Temporal clustering (as described in REF) measures the extent to which participants tend to cluster recalls of events encoded nearby in time.
+For example, if a participant recalled in exact serial order, the score would be 1 whereas if they sequentially recalled randomly positioned items the score would be ~.5.
+We found that participants who clustered in time also recalled a greater number of events (Fig~\ref{eventseg_behav}b; Pearson's $r$(16)=.62, $p$=.007).
+Next, we assessed semantic clustering.
+Similar to temporal clustering, semantic clustering measures the extent to which participants cluster their responses by semantic similarity.
+We used the topic vector representations of each event as a proxy for semantic information contained in that event.
+For each transition, we computed the rank percentile of the of the correlation between the the current event and then next event.
+For example, if a participant sequentially recalled events where each successive recall was the event that was most semantically similar to the previous, the semantic clustering score would be 1.
+If the events were recalled in a random order with respect to semantic information, the clustering score would be ~.5.
+We found that the semantic clustering score was related to memory performance across participants (Fig~\ref{eventseg_behav}c; Pearson's $r$(16)=.55, $p$=.02).
+Thus, participants who organized their recalls with respect to the semantic information contained in the scene had better memory performance.
+
+Then, we considered initiating the recall sequence (known in the literature as the `probability of first recall' or `PFR').
+This metric quantifies the likelihood of initiating a sequence of recalls based on the item's serial position.
+We found that participants tended to initiate their recall sequences with the first few events, which is qualitatively very similar to previously published list learning experiments (REF).
+Next, we considered another well-studied memory measure in list-learning, the lag conditional response probability curve (or lag-CRP).
+Given the recall of a stimulus in study position $n$, the lag-CRP quantifies the probability that the next item recalled will be of lag $i$.
+The results suggest a strong bias to transition sequentially in the forward direction.
+This can be seen by the high probability values in the lag ~1-5 positions compared to the rest of the transition possibilties.
+Notably, participants were instructed to recall as much as they could in order, and the shape of this lag-CRP is qualitatively similar to list-learning studies of serial recall (REF), where participants are required to recall lists of words in their serial order.
+Finally, we assessed memory performance for each event in the video.
+This plot quantifies the proportion of participants that recalled each event in the video (Fig~\ref{eventseg_behav}f).
+We found that there was substantial variability in memory for the different events.
+% NOTE: whats the right stat for this?
+
+\subsubsection{The fundamental shape of an experience is preserved in recall}
+The previous set of analyses are useful in that they enable us to quantify memory dynamics for naturalistic stimuli in a way that is comparable to a vast literature on list-learning recall dynamics.
+However, these methods fail to capture the rich semantic and temporal structure present in naturalistic stimuli (and associated recall of those experiences).
+Thus, our next set of analyses test whether the `shape' of an experience is preserved in memory.
+We hypothesized that despite individual variability in the precision and amount of content recalled across subjects, the general shape of the episode would be recalled by everyone.
+
+To better visualize the relationship between the video and recall event models, we embedded the video and average recall model into a 2D space (using the UMAP dimensionality reduction algorithm, for details see \ref{sec:methods}) where the points represent video/recall events and the distance between them represents their similarity in 'topic space' (\ref{fig:eventseg}g).
+(Note that all analyses are performed in the original 100 dimensional space.) We computed the group average transition probabilities from each event to each other event and plotted the values as lines where the tranparency is proportional to the probability of the transition.
+Visual inspection reveals that the two models have a very similar geometric structure, and the transition probabilities tend to be strongest between events that occured sequentially (or nearby) in time.
 To explore individual variability (and consistency) in the recall event models, we embedded each participant's recall event model in the same 2D 'topics space' described above (\ref{fig:eventseg}h).
@@
 
-\subsubsection{The fundamental shape of the stimulus is preserved in recall}
-To formalize the observation that participants' recall trajectories generally matched the shape of the video trajectory, we fit participants' recall data to a model comprised of $n$ line segments that were connected by the average recall trajectory coordinates.
+To formalize the observation that participants' recall trajectories generally matched the shape of the video trajectory, we fit participants' recall data to a model comprised of $k$ line segments that were connected by the average recall event coordinates.
 We fixed the endpoints of the model at the average first and last recall event, but fit the placement/length of rest of the segments to the data using the average recall events as `hinge-points'.
 Using a cross-validated model fitting procedure (see ~\ref{sec:methods} for details), we searched for the optimal number of line segments.
-The best fitting model ($n$=10) can be seen in Fig.~\ref{fig:linesegs}.
+The best fitting model ($k$=11) can be seen in Fig.~\ref{fig:linesegs}.
 This model represents the set of consecutive line segments that best describe participant's recall trajectories.
-Visualizing this model with the video model suggests that participants recall trajectories capture the fundamental shape of the stimulus.
+Notably, the optimal model comprises a subset of the total recall events (~roughly 1/3).
 
-%% HOW CAN WE TEST THIS STATISTICALLY?
+We hypothesized that the `hinge-points' between line segments represent critical scenes of the video where the storyline changed direction.
+To get a sense of the semantic content of each hinge-point, we created wordles (left side of each wordle) where the size of the word is proportional to its frequency in the video text descriptions for that event (Fig.~\ref{fig:linesegs}).
+We performed the same analysis for the recall text (right side of each wordle).
+Notably, the text in the worldes is distinct across hinge-points, but but similar between video and recall within hinge-point.
 
-To better understand the content
+% NOTE: WILL ADD ANOTHER PARAGRAPH HERE IF THE 'TOPIC FLOW' ANALYSES WORK OUT
 
 \subsubsection{Measuring the quality of recall}
-Representing the video and verbal recall as events in `topic space' also affords us the ability to characterize the quality of recall in a more fine-grained and nuanced way than what is typically possible.
+Representing the video and verbal recall as events in `topic space' also affords us the ability to characterize the quality of recall in a more fine-grained and nuanced way than what was previously possible.
 To quantify the similarity between the video model and individual recall models, we considered a number of novel metrics.
@@
 We found that participants with higher memory performance also had higher distinctiveness scores [Pearson's r(16)=.8, p=.0001].
+
 Lastly, we tested whether participants with better memory performance were also more likely to remember the events in order.
@@
 In summary, we found that better memory performance was associated with more precise and distinctive recall.
-
-\subsubsection{Naturalistic extensions of classic memory analyses}
-In addition to the novel metrics we introduce above, our approach also allows us to extend classic analyses designed to characterize memory in list-learning experiments to more naturalistic settings.
-Just like in a `free-recall' list-learning experiment where participants view a set of items (such as words) and then verbally recall them, our video-recall matching approach allows us to analyze memory in the same way (where the items are recall events).
-Since each recall event has a matching video event, we can consider characteristics of the sequence of recalls.
-
-First, we asked whether the estimated number of recall events (k) by participant was related to hand-annotated accuracy as published in Chen et al.
-(2017).
-We found a strong positive correlation where subjects with a greater number of recall events also had better memory performance (Fig~\ref{eventseg_behav}a; Pearson's $r$(16)=.67, $p$=.003).
-Thus, to the extent that they are correlated, k could be use in place of a measure such as overall recall accuracy.
-We considered two additional across-participant measures of recall that characterize memory organization: temporal clustering and semantic clustering.
-Temporal clustering (as described in REF) measures the extent to which participants tend to cluster recalls of events encoded nearby in time.
-For example, if a participant recalled in exact serial order, the score would be 1 whereas if they sequentially recalled randomly positioned items the score would be ~.5.
-We found that participants who clustered in time also recalled a greater number of events (Fig~\ref{eventseg_behav}b; Pearson's $r$(16)=.62, $p$=.007).
-Next, we assessed semantic clustering.
-Similar to temporal clustering, semantic clustering measures the extent to which participants cluster their responses by semantic similarity.
-We used the topic vector representations of each event as a proxy for semantic information contained in that event.
-For each transition, we computed the rank percentile of the of the correlation between the the current event and then next event.
-For example, if a participant sequentially recalled events where each successive recall was the event that was most semantically similar to the previous, the semantic clustering score would be 1.
-If the events were recalled in a random order with respect to semantic information, the clustering score would be ~.5.
-We found that the semantic clustering score was related to memory performance across participants (Fig~\ref{eventseg_behav}c; Pearson's $r$(16)=.55, $p$=.02).
-Thus, participants who organized their recalls with respect to the semantic information contained in the scene had better memory performance.
-
-Next, we considered initiating the recall sequence (known in the literature as the `probability of first recall' or `PFR').
-This metric quantifies the likelihood of initiating a recall sequence based on the item's serial position.
-We found that participants tended to initiate their recall sequences with the first few events, which is qualitatively very similar to previously published list learning experiments (REF).
-Next, we considered another well-studied memory measure in list-learning, the lag conditional response probability curve (or lag-CRP).
-Given the recall of a stimulus in study position $n$, the lag-CRP quantifies the probability that the next item recalled will be of lag $i$.
-The results suggest a strong bias to transition sequentially in the forward direction.
-This can be seen by the high probability values in the lag ~1-5 positions compared to the rest of the transition possibilties.
-Notably, participants were instructed to recall as much as they could in order, and the shape of this lag-CRP is qualitatively similar to list-learning studies of serial recall (REF), where participants are required to recall lists of words in their serial order.
-Finally, we assessed memory performance for each event in the video.
-This plot quantifies the proportion of participants that recalled each event in the video (Fig~\ref{eventseg_behav}f).
-
-\begin{figure}[ht!]
-\centering
-\includegraphics[width=1\textwidth]{figs/4_behav_eventseg.pdf}
-\caption{\label{fig:behav}Naturalistic extensions of classic memory analyses.
-A-C use the `smooth' approach and D-F use the `best' approach (see Methods for details).
-A/D.
-The probability of first recall as a function of the serial position the the event during encoding.
-B/E.
-Given recall of event i, the probability that the next recalled item will be from serial position i \rpm~lag.
-C/F.
-Proportion recalled as a function of serial position.
-All error bars are the standard error of the mean derived from a bootstrap resampling procedure.
-}
-\end{figure}
 

### 2018-06-22 main.tex
checking in progress

@@
 
-% \begin{figure}[t!]
-% \centering
-% \includegraphics[width=1\textwidth]{figs/1_video_recall_models.pdf}
-% \caption{\label{fig:model}Topic models for the video and verbal recall.
-A.
-A timepoints (1976) by topics (100) matrix was created by fitting a topic model to overlapping segments of the moment-by-moment video text descriptions.
+\begin{figure}[ht!]
+\centering
+\includegraphics[width=\textwidth]{figs/2_eventseg_v4.pdf}
+\caption{\label{fig:eventseg} Event segmentation analysis of the video and recall models.
+For all plots, darker colors indicate greater values and the range of each plot is 0-1.
+A).
+A timepoints (1976) by topics (100) matrix representing the video stimulus.
 Each row represents the most likely mixture of topics for a given timepoint.
 Each columns represents a different topic.
-The darker the color, the higher the probability that the topic is contained in that timepoint.
-B.
-A timepoints (1976) by topics (100) matrix representing group average topic model of the recall transcripts.
-All participant's recall transcripts were transformed using the topic model fit to the video descriptions and then resampled to the same length (1976).
-C.
-A viewing-time (1976) by recall-time (1976) correlation matrix representing the correlation of each moment of the video model with every moment of the average recall model.
-The darker the color, the higher the correlation between the video and recall models at a given timepoint.
-D.
-A 3D embedding of the video and recall topic models reduced using spectral embedding.
-}
-% \end{figure}
+B).
+A timepoints (1976) by topics (100) matrix representing participant \#13's recall.
+C).
+A viewing-time (1976) by viewing-time (1976) correlation matrix representing the correlation of each moment of the video model with every other moment of the video model.
+The white boxes represent `events' recovered by a hidden Markov model.
+D).
+A recall-time (294 sentences) by recall-time (294) correlation matrix for participant \#13.
+E).
+An events (34) by topics (100) matrix where each row represents the average topic vector for each event in the video model.
+F).
+An events (27) by topics (100) matrix where each row represents the average topic vector for each event in participant \#13's recall model.
+G.
+A recall events (27) by video events (34) correlation matrix for participant \#13.
+The yellow squares identify the video event with the highest correlation to a given recall event.
+F.
+A group averaged recall events (34) by video events (34) correlation matrix.
+The yellow squares identify the video event with the highest correlation to a given average recall event.}
+\end{figure}
 
@@
 
-\begin{figure}[t!]
-\centering
-\includegraphics[width=.75\textwidth]{figs/2_eventseg.pdf}
-\caption{\label{fig:eventseg} Event segmentation analysis of the video and recall models.
-A.
-A recall-time (294) by topics (100) matrix representing a recall model for a single participant (participant \#13).
-B.
-A recall-time (294) by recall-time (294) correlation matrix for participant \#13.
-The white squares along the diagonal outline events, i.e.
-neighboring timepoints with a stable and similar topic vector.
-C.
-An events (34) by topics (100) matrix where each row represents the average topic vector for each event in the video model.
-D.
-An events (27) by topics (100) matrix where each row represents the average topic vector for each event in the recall model.
-E.
-A recall events (27) by video events (34) correlation matrix representing the `match' between each video and recall event.
-The black squares identify the video event with the highest correlation to a given recall event.
-F.
-A group averaged recall events (34) by video events (34) correlation matrix.
-The black squares identify the video event with the highest correlation to a given average recall event.
-G.
-2D embeddings (reduced with UMAP algorithm) of each participants' recall event model (example shown in D).
-Each dot represents a recall event and the connecting lines indicate the order of recall.
-Colors indicate the most likely video event that the participant was describing as determined by the video-recall matching model.
-H.
-2D embedding of video and average recall event models.}
-\end{figure}
-
-Next, we explored the idea that the individual `blocks' along the diagonals of the recall matrices represent the recall of a particular video event.
+Next, we hypothesized that the individual `blocks' along the diagonals of the recall matrices represent the recall of a particular video event.
 To test this, first we created a video event model, which was done by averaging together neighboring topic vectors that the were classified to be in the same event (\ref{fig:eventseg}c), resulting in an events (34) by topics (100) matrix.
@@
 
-\subsubsection{Naturalistic extensions of classic memory analyses}
-Just like in a traditional `free-recall' list-learning experiment where participants view a list of words and then verbally recall them, our video-recall matching approach described above affords us the ability to analyze memory in the same way (where the recalled words are analogous to recalled events).
-In our first set of analyses, we sought to characterize memory performance/dynamics by extending classic analyses originally designed for list-learning experiments to more naturalistic settings.
-
-\begin{figure}[ht!]
+\begin{figure}[t!]
 \centering
@@
 \end{figure}
+
+\subsubsection{Naturalistic extensions of classic memory analyses}
+Just like in a traditional `free-recall' list-learning experiment where participants view a list of words and then verbally recall them, our video-recall matching approach described above affords us the ability to analyze memory in the same way (where the recalled words are analogous to recalled events).
+In our first set of analyses, we sought to characterize memory performance/dynamics by extending classic analyses originally designed for list-learning experiments to more naturalistic settings.
 

### 2018-06-22 main.tex
saving progress

@@
 \usepackage[utf8]{inputenc}
+\usepackage[english]{babel}
 \usepackage[font=small,labelfont=bf]{caption}
@@
 % \title{Capturing the geometric structure of our experiences and how we remember them}
-\title{The fundamental geometry of dynamic experiences is preserved in memory}
+\title{The fundamental shape of dynamic experiences is preserved in episodic memory}
 \author{Andrew C. Heusser \& Jeremy R. Manning}
 % \affiliation{Dartmouth College}
+
+\bibliographystyle{apa}
 
@@
 What does it mean to \textit{remember} something?
-In traditional episodic memory experiments~\citep[e.g., list-learning or trial-based experiments;][]{Murd62a, Kaha96}, remembering is often cast as a binary operation: either an item is recalled or it isn't.
-More nuanced studies might incorporate self-reported confidence measures as a proxy for memory strength, or ask participants to discriminate between ``recollecting'' an experience or a feeling of ``familiarity''~\citep{Yone02}.
+In traditional episodic memory experiments \citep[e.g., list-learning or trial-based experiments;][]{Murd62a, Kaha96}, remembering is often cast as a binary operation: either an item is recalled or it isn't.
+More nuanced studies might incorporate self-reported confidence measures as a proxy for memory strength, or ask participants to discriminate between ``recollecting'' an experience or a feeling of ``familiarity'' \citep{Yone02}.
 However, characterizing and evaluating memory in more realistic contexts (e.g., telling a story to a friend about a recent vacation) is a fundamentally different task.
@@
 
-To study the temporal and semantic aspects of memory for naturalistic experiences, we analyzed an open dataset in which participants view and verbally recall an episode of the BBC series \textit{Sherlock}~\citep{ChenEtal17}.
-We developed a novel computational approach which combines topic models ~\cite{Blei03} and hidden Markov models to capture the temporal evolution of rich semantic structure present in naturalistic experiences.
+To study the temporal and semantic aspects of memory for naturalistic experiences, we analyzed an open dataset in which participants view and verbally recall an episode of the BBC series \textit{Sherlock}  \citep{ChenEtal17} .
+We developed a novel computational approach which combines topic models \citep{BleiEtal03} and hidden Markov models to capture the temporal evolution of rich semantic structure present in naturalistic experiences.
 We then use this model to characterize the shape and contents of episodic memories for naturalistic experiences.
@@
 \centering
-\includegraphics[width=1\textwidth]{figs/0_analysis_schematic.pdf}
-\caption{\label{fig:schematic}Schematic of the analysis approach.
-For each moment of the video, text descriptions were manually generated.
+\includegraphics[width=1\textwidth]{figs/1_analysis_schematic.pdf}
+\caption{\small \textbf{Schematic of the analysis approach.} For each moment of the video, text descriptions were manually generated.
 Three exemplary time points are displayed here.
@@
 The bar charts display the resulting topic model weights for the video (in blue) and recall (in orange) for three example topic dimensions.}
+\label{fig:schematic}
 \end{figure}
@@
 \subsubsection{A model to capture the geometric structure of naturalistic stimuli}
-We fit a topic model ~\cite{Blei03} to manually annotated text descriptions of scenes from the episode.
+We fit a topic model \citep{BleiEtal03} to manually annotated text descriptions of scenes from the episode.
 The text descriptions contained details of the scene such as the characters, location, and a short summary of the scene (see Fig.\ref{fig:schematic} for example text, see \ref{sec:methods} for analysis details).
@@
 We expanded this matrix from 1000 to 1976 timepoints by copying the vectors for scenes that spanned multiple TRs.
-As depicted in \ref{fig:model}a, the topics are sparse and change slowly over time.
+As depicted in Fig.~\ref{fig:model}a, the topics are sparse and change slowly over time.
 Furthermore, there are clear transitions from one topic `state' to the next, possibly indexing scene transitions in the stimulus.
-To get a better handle on this temporal structure, we computed the timepoint-by-timepoint correlation matrix of the video model (\ref{fig:model}b).
+To get a better handle on this temporal structure, we computed the timepoint-by-timepoint correlation matrix of the video model (Fig.~\ref{fig:model}b).
 This correlation matrix reveals that the model has a strong, block-diagonal structure.
@@
 In order to average the recall models across participants, we resampled each model at the resolution of the video model (1976 timepoints).
-The individual models can be seen in Supp Fig X and the group average is plotted in Fig.
-\ref{fig:model}c.
+The individual models can be seen in Supp Fig X and the group average is plotted in Fig.~\ref{fig:model}c.
 Note that the topics were derived solely from the text descriptions of the video, and so the topic models estimated for recall are dependent on the topics in the episode.
@@
 To visualize the group average, we resampled all of the recall models to the duration of the video model (1976 timepoints), computed the timepoint-by-timepoint correlation matrices and then averaged across participants.
-The average recall matrix also had a block-diagonal structure, albeit smoother than the video model (\ref{fig:model}d).
+The average recall matrix also had a block-diagonal structure, albeit smoother than the video model (Fig.~\ref{fig:model}d).
 
@@
 We then averaged these matrices together to get a single group averaged matrix.
-The result was a viewing time (1976) by recall time (1976) correlation matrix representing the average relationship between every moment of the movie and recall models (\ref{fig:model}e).
+The result was a viewing time (1976) by recall time (1976) correlation matrix representing the average relationship between every moment of the movie and recall models (Fig.~\ref{fig:model}e).
 Notably, we observe significant correlation values (p<.05, permutation test described in \ref{sec:methods}) primarily along the diagonal, suggesting that our model captures the fact that participants recalled the episode in order.
@@
 \includegraphics[width=\textwidth]{figs/2_eventseg_v4.pdf}
-\caption{\label{fig:eventseg} Event segmentation analysis of the video and recall models.
-For all plots, darker colors indicate greater values and the range of each plot is 0-1.
+\caption{\small \textbf{Modelling naturalistic stimuli and recall.} For all plots, darker colors indicate greater values and the range of each plot is 0-1.
 A).
@@
 The yellow squares identify the video event with the highest correlation to a given average recall event.}
+\label{fig:model}
 \end{figure}
@@
 \subsubsection{Segmenting the video and recall models into `events'}
-One prominent feature of the video and recall correlation matrices (see \ref{fig:model}) is a strong, block structure along the diagonal of the matrices.
+One prominent feature of the video and recall correlation matrices (see Fig.~\ref{fig:model}) is a strong, block structure along the diagonal of the matrices.
 We hypothesized that this structure might arise from transient stability in the language used to describe each event of the video.
@@
 The algorithm determined 34 events for the movie model and a range of values (range=8-27, mean= 15.41, SD=5.6) for the recall models (see ~\ref{sec:methods} for details on choosing $k$).
-The events discovered for a representative participant are highlighted in \ref{fig:eventseg}b.
+The events discovered for a representative participant are highlighted in \ref{fig:model}b.
 
 Next, we hypothesized that the individual `blocks' along the diagonals of the recall matrices represent the recall of a particular video event.
-To test this, first we created a video event model, which was done by averaging together neighboring topic vectors that the were classified to be in the same event (\ref{fig:eventseg}c), resulting in an events (34) by topics (100) matrix.
-We performed the same procedure for the recall matrices (see \ref{fig:eventseg}d for example).
-Then, we computed the correlation between these two event models, resulting in a video events (34) by recall events (8-27, depending on the participant) correlation matrix (see \ref{fig:eventseg}e).
+To test this, first we created a video event model, which was done by averaging together neighboring topic vectors that the were classified to be in the same event (Fig.~\ref{fig:model}c), resulting in an events (34) by topics (100) matrix.
+We performed the same procedure for the recall matrices (see Fig.~\ref{fig:model}d for example).
+Then, we computed the correlation between these two event models, resulting in a video events (34) by recall events (8-27, depending on the participant) correlation matrix (see Fig/~\ref{fig:model}e).
 These matrices represent the extent to which each recall event is similar to each video event (for each participant).
@@
 the argmax).
-This is depicted in \ref{fig:eventseg}e as the cell highlighted with the black box for each column in the video-recall event correlation matrix.
+This is depicted in Fig.~\ref{fig:model}e as the cell highlighted with the black box for each column in the video-recall event correlation matrix.
 Notably, our algorithm suggests that the example participant recalled the events largely in order (occasionally skipping over an event).
 
-Next, we computed a group-averaged recall event model and video-recall event correlation matrix (\ref{fig:eventseg}f).
+Next, we computed a group-averaged recall event model and video-recall event correlation matrix (Fig.~\ref{fig:model}f).
 To do this, for each participant (and each recall event), we grouped the recall event vectors (across all participants) by the video event that they were most highly correlated to.
@@
 This yielded an average recall event vector for all but one (of 34) event (since no participant remembered this event according to our model).
-Lastly, we computed an average recall event (34) by video event (34) correlation matrix, and highlighted the highest correlation in the column with a black box (\ref{fig:eventseg}f).
+Lastly, we computed an average recall event (34) by video event (34) correlation matrix, and highlighted the highest correlation in the column with a black box (Fig.~\ref{fig:model}f).
 Notably, this matrix displayed high correlation values along the diagonal and low correlations in the off-diagonal cells.
@@
 \centering
-\includegraphics[width=1\textwidth]{figs/4_behav_eventseg.pdf}
-\caption{\label{fig:behav}Naturalistic extensions of classic memory analyses.
-A-C use the `smooth' approach and D-F use the `best' approach (see Methods for details).
-A/D.
-The probability of first recall as a function of the serial position the the event during encoding.
-B/E.
-Given recall of event i, the probability that the next recalled item will be from serial position i \rpm~lag.
-C/F.
+\includegraphics[width=1\textwidth]{figs/3_list_learning.pdf}
+\caption{\small \textbf{Naturalistic extensions of classic memory analyses.} A).
+The probability of first recall as a function of the serial position of the event during encoding.
+B).
+Given recall of event i, the probability that the next recalled item will be from serial position i +/- lag.
+C).
 Proportion recalled as a function of serial position.
-All error bars are the standard error of the mean derived from a bootstrap resampling procedure.
-}
+All error bars are the standard error of the mean derived from a bootstrap resampling procedure.}
+\label{fig:list-learning}
 \end{figure}
@@
 
-First, we asked whether the estimated number of recall events (k) by participant was related to hand-annotated accuracy as published in Chen et al.
+First, we asked whether the estimated number of recall events ($k$) by participant was related to hand-annotated accuracy as published in Chen et al.
 (2017).
-We found a strong positive correlation where subjects with a greater number of recall events also had better memory performance (Fig~\ref{eventseg_behav}a; Pearson's $r$(16)=.67, $p$=.003).
+We found a strong positive correlation where subjects with a greater number of recall events also had better memory performance (Pearson's $r$(16)=.67, $p$=.003).
 Thus, the block-diagonal temporal structure in the recall matrices computed by our model is strongly related to the variability in memory performance across participants.
@@
 For example, if a participant recalled in exact serial order, the score would be 1 whereas if they sequentially recalled randomly positioned items the score would be ~.5.
-We found that participants who clustered in time also recalled a greater number of events (Fig~\ref{eventseg_behav}b; Pearson's $r$(16)=.62, $p$=.007).
+We found that participants who clustered in time also recalled a greater number of events (Pearson's $r$(16)=.62, $p$=.007).
 Next, we assessed semantic clustering.
@@
 If the events were recalled in a random order with respect to semantic information, the clustering score would be ~.5.
-We found that the semantic clustering score was related to memory performance across participants (Fig~\ref{eventseg_behav}c; Pearson's $r$(16)=.55, $p$=.02).
+We found that the semantic clustering score was related to memory performance across participants (Pearson's $r$(16)=.55, $p$=.02).
 Thus, participants who organized their recalls with respect to the semantic information contained in the scene had better memory performance.
@@
 This metric quantifies the likelihood of initiating a sequence of recalls based on the item's serial position.
-We found that participants tended to initiate their recall sequences with the first few events, which is qualitatively very similar to previously published list learning experiments (REF).
+We found that participants tended to initiate their recall sequences with the first few events (Fig.~\ref{fig:list-learning}a), which is qualitatively very similar to previously published list learning experiments (REF).
 Next, we considered another well-studied memory measure in list-learning, the lag conditional response probability curve (or lag-CRP).
 Given the recall of a stimulus in study position $n$, the lag-CRP quantifies the probability that the next item recalled will be of lag $i$.
-The results suggest a strong bias to transition sequentially in the forward direction.
+The results suggest a strong bias to transition sequentially in the forward direction Fig.~\ref{fig:list-learning}b.
 This can be seen by the high probability values in the lag ~1-5 positions compared to the rest of the transition possibilties.
@@
 Finally, we assessed memory performance for each event in the video.
-This plot quantifies the proportion of participants that recalled each event in the video (Fig~\ref{eventseg_behav}f).
+This plot quantifies the proportion of participants that recalled each event in the video (Fig.~\ref{fig:list-learning}c).
 We found that there was substantial variability in memory for the different events.
@@
 
-To better visualize the relationship between the video and recall event models, we embedded the video and average recall model into a 2D space (using the UMAP dimensionality reduction algorithm, for details see \ref{sec:methods}) where the points represent video/recall events and the distance between them represents their similarity in 'topic space' (\ref{fig:eventseg}g).
-(Note that all analyses are performed in the original 100 dimensional space.) We computed the group average transition probabilities from each event to each other event and plotted the values as lines where the tranparency is proportional to the probability of the transition.
+\begin{figure}[t!]
+\centering
+\includegraphics[width=1\textwidth]{figs/4_trajectory.pdf}
+\caption{\small \textbf{Video and recall trajectory plots.} A).
+2-dimensional embedding of recall events model.
+The arrows indicate the forward direction of the video events.
+B).
+2-dimensional embedding of the average recall events.
+The colors refer to the most similar video events.
+The lines connecting the points represent the average probability of transitioning from one event to the other.
+The weight of the line is proportional to the transition probability.}
+\label{fig:trajectory}
+\end{figure}
+
+To better visualize the relationship between the video and recall event models, we embedded the video and average recall model into a 2D space (using the UMAP dimensionality reduction algorithm, for details see \ref{sec:methods}) where the points represent video/recall events and the distance between them represents their similarity in 'topic space' (Fig.~\ref{fig:trajectory}a).
+(Note that all analyses are performed in the original 100 dimensional space.) We computed the group average transition probabilities from each event to each other event and plotted the values as lines where the tranparency is proportional to the probability of the transition (Fig.~\ref{fig:trajectory}b).
 Visual inspection reveals that the two models have a very similar geometric structure, and the transition probabilities tend to be strongest between events that occured sequentially (or nearby) in time.
-To explore individual variability (and consistency) in the recall event models, we embedded each participant's recall event model in the same 2D 'topics space' described above (\ref{fig:eventseg}h).
-Despite the variability in the number of events remembered, the overall shape of most of the participants' recall trajectories are similar to the video model (\ref{fig:eventseg}h), particularly the participants with a greater number of recalled events.
+
+% To explore individual variability (and consistency) in the recall event models, we embedded each participant's recall event model in the same 2D 'topics space' described above (\ref{fig:model}h).
+Despite the variability in the number of events remembered, the overall shape of most of the participants' recall trajectories are similar to the video model (\ref{fig:model}h), particularly the participants with a greater number of recalled events.
 
@@
 
-\subsection{References}
-
-LaTeX automatically generates a bibliography in the APA style from your .bib file.
-The citep command generates a formatted citation in parentheses \citep{Lamport1986}.
-The cite command generates one without parentheses.
-LaTeX was first discovered by \cite{Lamport1986}.
-
-% \subsection{Tables and Figures}
-
-% Use the table and tabular commands for basic tables --- see Table~\ref{tab:widgets}, for example.
-You can upload a figure (JPEG, PNG or PDF) using the files menu.
-To include it in your document, use the includegraphics command as in the code for Figure~\ref{fig:frog} below.
-
 \bibliography{memlab}
-
 \end{document}
-
-%
-% Please see the package documentation for more information
-% on the APA6 document class:
-%
-% http://www.ctan.org/pkg/apa6
-%

### 2018-06-25 boneyard.tex
saving progress

@@
 We repeated this 20 times using 1-10
+
+\subsubsection{Bridging between the stimulus and recall}
+The participants in this study were instructed to recall as much of the episode as they could in the order it happened.
+Thus, we hypothesized that the recall models should resemble the video model to the extent that participants followed these instructions and had reasonably good memory accuracy.
+To test whether this was true, we correlated each moment of the video model with each moment of each participants' resampled recall model.
+We then averaged these matrices together to get a single group averaged matrix.
+The result was a viewing time (1976) by recall time (1976) correlation matrix representing the average relationship between every moment of the movie and recall models (Fig.~\ref{fig:model}e).
+Notably, we observe significant correlation values (p<.05, permutation test described in \ref{sec:methods}) primarily along the diagonal, suggesting that our model captures the fact that participants recalled the episode in order.
+We also visualized this effect by projecting the matrices into a 3D space (reduced using Spectral Embedding [cite]) where the proximity of the trajectories at every timepoint represents how similar the topic vectors were.
+Visualizing the data in this way makes it clear that the overall shape and correlational structure of the video and average recall matrices is quite similar.

### 2018-06-25 main.tex
saving progress

@@
 
+%Another notable feature of human memory is that despite the fact that information flows continuously through our sensory systems, our memories are descretized and centered around particular events.
+
 Another major difference between traditional trial-based memory paradigms and real-world memory concerns the subjective experience of the participant.
@@
 
-To study the temporal and semantic aspects of memory for naturalistic experiences, we analyzed an open dataset in which participants view and verbally recall an episode of the BBC series \textit{Sherlock}  \citep{ChenEtal17} .
-We developed a novel computational approach which combines topic models \citep{BleiEtal03} and hidden Markov models to capture the temporal evolution of rich semantic structure present in naturalistic experiences.
-We then use this model to characterize the shape and contents of episodic memories for naturalistic experiences.
+To study the temporal and semantic aspects of memory for naturalistic experiences, we analyzed an open dataset in which participants view and verbally recall an episode of the BBC series \textit{Sherlock}  \citep{ChenEtal17}.
+We developed a novel computational approach which combines topic models \citep{BleiEtal03} and hidden Markov models \citep{Rabi89, BaldEtal17} to capture the temporal evolution of rich semantic structure present in naturalistic experiences.
+We then use this model to characterize the geometric structure and contents of episodic memories for naturalistic experiences.
 We hypothesized that memory for naturalistic experiences is more about preserving the overall ``shape'' of an experience than any of the particular details.
@@
 Furthermore, there are clear transitions from one topic `state' to the next, possibly indexing scene transitions in the stimulus.
-To get a better handle on this temporal structure, we computed the timepoint-by-timepoint correlation matrix of the video model (Fig.~\ref{fig:model}b).
+To get a better handle on this temporal structure, we computed the timepoint-by-timepoint correlation matrix of the video model (Fig.~\ref{fig:model}c).
 This correlation matrix reveals that the model has a strong, block-diagonal structure.
-Another interesting feature is that there is very little correlation between blocks (i.e.
-the off-diagonal values are small).
-This is an interesting feature of the model because to the extend that the blocks represent `events' in the video, the model representations of those events are unique and highly discriminable.
+Another noteworthy characteristic is that there is very little correlation between blocks (i.e.
+the off-diagonal values are small), suggesting the representations of each block are unique and highly descriminable.
 
-\subsubsection{Modelling verbal free recall}
-After watching the episode, participants verbally recalled (in order) as much as they could.
+\subsubsection{Modeling verbal free recall}
+After watching the episode, participants verbally recalled (in order) as much of the episode as they could.
 We used the same topic model (fit with the text descriptions of the video) to transform participants' verbal recall transcripts.
-The result was a sentences (range: X to X) by topics (100) matrix for each participant, where each row represented the estimated mixture of topics for a given window of sentences during recall.
-In order to average the recall models across participants, we resampled each model at the resolution of the video model (1976 timepoints).
-The individual models can be seen in Supp Fig X and the group average is plotted in Fig.~\ref{fig:model}c.
+The result is a sentences (range: 68 to 294, mean: 131.94) by topics (100) matrix for each participant, where each row represents the estimated mixture of topics for a given window of sentences during recall.
+An example participant's (#13) model is plotted in Fig.~\ref{fig:model}c.
 Note that the topics were derived solely from the text descriptions of the video, and so the topic models estimated for recall are dependent on the topics in the episode.
-In effect, this approach projects the participants' verbal recall into the video 'stimulus space', allowing us to quantify the dynamics of verbally reported memories as well as relate them to their originating experiences.
+This approach effectively projects the participants' verbal recall into the video ``stimulus space'', allowing us to quantify the dynamics of verbally reported memories as well as relate them to their originating experiences.
 
@@
 For each participant, we computed a timepoint-by-timepoint correlation matrix from recall models.
+An example participant's (\#13) correlation matrix is plotted in Fig.~\ref{fig:model}d).
 Like the video model, each participant's recall correlation matrix exhibited a block-diagonal structure (Supp Fig X).
-To visualize the group average, we resampled all of the recall models to the duration of the video model (1976 timepoints), computed the timepoint-by-timepoint correlation matrices and then averaged across participants.
-The average recall matrix also had a block-diagonal structure, albeit smoother than the video model (Fig.~\ref{fig:model}d).
 
-\subsubsection{Bridging between the stimulus and recall}
-The participants in this study were instructed to recall as much of the episode as they could in the order it happened.
-Thus, we hypothesized that the recall models should resemble the video model to the extent that participants followed these instructions and had reasonably good memory accuracy.
-To test whether this was true, we correlated each moment of the video model with each moment of each participants' resampled recall model.
-We then averaged these matrices together to get a single group averaged matrix.
-The result was a viewing time (1976) by recall time (1976) correlation matrix representing the average relationship between every moment of the movie and recall models (Fig.~\ref{fig:model}e).
-Notably, we observe significant correlation values (p<.05, permutation test described in \ref{sec:methods}) primarily along the diagonal, suggesting that our model captures the fact that participants recalled the episode in order.
-We also visualized this effect by projecting the matrices into a 3D space (reduced using Spectral Embedding [cite]) where the proximity of the trajectories at every timepoint represents how similar the topic vectors were.
-Visualizing the data in this way makes it clear that the overall shape and correlational structure of the video and average recall matrices is quite similar.
+\subsubsection{Segmenting the video and recall models into `events'}
+One striking feature of the video and recall correlation matrices (see Fig.~\ref{fig:model}) is a strong, block structure along the diagonal of the matrices.
+We hypothesized that this structure might arise from transient stability in the content of the video, and the subsequent language used to describe each event of the video.
+If true, we reasoned that it would be possible to infer the specific event a participant is describing by comparing the (average) topic model for a particular recall ``event'' with the (average) topic vector for each video event.
+In other words, the video event that is most similar to a given recall event is the event that the participant is most likely describing.
+To test this idea, it is first necessary to systematically parse the matrices into events.
+We leveraged a hidden Markov model (~\citep{BaldEtal17}) to estimate $k$ events (or states) from a (multivariate) time series.
+The algorithm determined 34 events for the movie model and a range of values (range: 8-27; mean: 15.41; SD: 5.6) for the recall models (see ~\ref{sec:methods} for details on choosing an optimal $k$ value).
+The events discovered for a representative participant (\#13) are highlighted as yellow rectangles outlining blocks along the diagonal of the participant's correlation matrix (Fig.~\ref{fig:model}d).
+Next, we created a video event model by averaging together neighboring topic vectors that the were classified to be in the same event, resulting in an events (34) by topics (100) matrix (Fig.~\ref{fig:model}e).
+We performed the same procedure for the recall matrices (see Fig.~\ref{fig:model}f for example).
+Then, we computed the correlation between these two event models, resulting in a video events (34) by recall events (8-27, depending on the participant) correlation matrix (see Fig/~\ref{fig:model}g).
+These matrices represent the similarity (correlation) between each video event and each recall event (for each participant).
+To determine which video events the recall events most likely referred to, for each recall event, we found the index of the video event with the highest correlation (i.e.
+the argmax).
+This is depicted in Fig.~\ref{fig:model}g as the cell highlighted with the yellow box for each column in the video-recall event correlation matrix.
+Notably, our algorithm suggests that the example participant recalled the events largely in order (occasionally skipping over an event).
+
+Next, we computed a group-averaged recall event model and video-recall event correlation matrix.
+To do this, for each participant (and each recall event), we grouped the recall event vectors (across all participants) by the video event that they were most highly correlated to.
+We then averaged the recall event vectors within group.
+This yielded an average recall event vector for all but one (of 34) event (since no participant remembered this event according to our model).
+Lastly, we computed an average recall event (34) by video event (34) correlation matrix, and highlighted the highest correlation in the column with a black box (Fig.~\ref{fig:model}h).
+Notably, this matrix displayed high correlation values along the diagonal and low correlations in the off-diagonal cells.
+This suggests that on average, participants were able to recapitulate the events in the episode and our approach captured this behavior.
+% NOTE: ^ possibly need a null model for the group analysis.
+I think it could be to get a result that looks like this even if we scrambled the text.
+My concern is that I'm grouping the recall events by the video event they were most similar to, and then averaging, which may give rise to a smooth looking plot without any real information there...
 
@@
 
-\subsubsection{Segmenting the video and recall models into `events'}
-One prominent feature of the video and recall correlation matrices (see Fig.~\ref{fig:model}) is a strong, block structure along the diagonal of the matrices.
-We hypothesized that this structure might arise from transient stability in the language used to describe each event of the video.
-If true, we reasoned that it would be possible to decode which particular event a participant is describing by comparing the average topic model for a particular recall `event' with the average topic vector for each video event.
-Following this logic, the video event that is most similar to the given recall event would be the event the participant is most likely describing.
-To test this idea, it is first necessary to systematically parse the matrices into events.
-To do this, we leveraged a hidden Markov model (~\citep{BaldEtal17}) to estimate $k$ events from a (multivariate) time series.
-The algorithm determined 34 events for the movie model and a range of values (range=8-27, mean= 15.41, SD=5.6) for the recall models (see ~\ref{sec:methods} for details on choosing $k$).
-The events discovered for a representative participant are highlighted in \ref{fig:model}b.
-
-Next, we hypothesized that the individual `blocks' along the diagonals of the recall matrices represent the recall of a particular video event.
-To test this, first we created a video event model, which was done by averaging together neighboring topic vectors that the were classified to be in the same event (Fig.~\ref{fig:model}c), resulting in an events (34) by topics (100) matrix.
-We performed the same procedure for the recall matrices (see Fig.~\ref{fig:model}d for example).
-Then, we computed the correlation between these two event models, resulting in a video events (34) by recall events (8-27, depending on the participant) correlation matrix (see Fig/~\ref{fig:model}e).
-These matrices represent the extent to which each recall event is similar to each video event (for each participant).
-To determine which video events the recall events most likely referred to, for each recall event, we found the index of the video event with the highest correlation (i.e.
-the argmax).
-This is depicted in Fig.~\ref{fig:model}e as the cell highlighted with the black box for each column in the video-recall event correlation matrix.
-Notably, our algorithm suggests that the example participant recalled the events largely in order (occasionally skipping over an event).
-
-Next, we computed a group-averaged recall event model and video-recall event correlation matrix (Fig.~\ref{fig:model}f).
-To do this, for each participant (and each recall event), we grouped the recall event vectors (across all participants) by the video event that they were most highly correlated to.
-We then averaged the recall event vectors within group.
-This yielded an average recall event vector for all but one (of 34) event (since no participant remembered this event according to our model).
-Lastly, we computed an average recall event (34) by video event (34) correlation matrix, and highlighted the highest correlation in the column with a black box (Fig.~\ref{fig:model}f).
-Notably, this matrix displayed high correlation values along the diagonal and low correlations in the off-diagonal cells.
-This suggests that on average, participants were able to recapitulate the events in the episode and our model was sensitive enough to capture this behavior.
-% NOTE: ^ Need a null model for the group analysis.
-I think it could be to get a result that looks like this even if we scrambled the text.
-My concern is that I'm grouping the recall events by the video event they were most similar to, and then averaging, which may give rise to a smooth looking plot without any real information there...
-
 \begin{figure}[t!]
@@
 
-First, we asked whether the estimated number of recall events ($k$) by participant was related to hand-annotated accuracy as published in Chen et al.
+First, we considered how participant's initiated the recall sequence (known in the literature as the `probability of first recall' or `PFR').
+This metric quantifies the likelihood of initiating a sequence of recalls based on the item's serial position.
+We found that participants tended to initiate their recall sequences with the first few events (Fig.~\ref{fig:list-learning}a), which is qualitatively very similar to previously published list learning experiments (REF).
+Next, we considered another well-studied memory measure in list-learning, the lag conditional response probability curve (or lag-CRP).
+Given the recall of a stimulus in study position $n$, the lag-CRP quantifies the probability that the next item recalled will be of lag $i$.
+The results suggest a strong bias to transition sequentially in the forward direction Fig.~\ref{fig:list-learning}b.
+This can be seen by the high probability values in the lag ~1-5 positions compared to the rest of the transition possibilties.
+Notably, participants were instructed to recall as much as they could in order, and the shape of this lag-CRP is qualitatively similar to list-learning studies of serial recall (REF), where participants are required to recall lists of words in their serial order.
+Finally, we assessed memory performance for each event in the video.
+This plot quantifies the proportion of participants that recalled each event in the video (Fig.~\ref{fig:list-learning}c).
+We found that there was substantial variability in memory for the different events.
+Furthermore, the shape of the curve is different than what is typically found in list learning experiments (we'll come back to this point in the dicussion).
+
+Next, we asked whether the estimated number of recall events ($k$) by participant was related to hand-annotated accuracy as published in Chen et al.
 (2017).
 We found a strong positive correlation where subjects with a greater number of recall events also had better memory performance (Pearson's $r$(16)=.67, $p$=.003).
-Thus, the block-diagonal temporal structure in the recall matrices computed by our model is strongly related to the variability in memory performance across participants.
 We considered two additional across-participant measures of recall that characterize memory organization: temporal clustering and semantic clustering.
-Temporal clustering (as described in REF) measures the extent to which participants tend to cluster recalls of events encoded nearby in time.
+Temporal clustering (REF) measures the extent to which participants tend to cluster recalls of events encoded nearby in time.
 For example, if a participant recalled in exact serial order, the score would be 1 whereas if they sequentially recalled randomly positioned items the score would be ~.5.
@@
 Thus, participants who organized their recalls with respect to the semantic information contained in the scene had better memory performance.
-
-Then, we considered initiating the recall sequence (known in the literature as the `probability of first recall' or `PFR').
-This metric quantifies the likelihood of initiating a sequence of recalls based on the item's serial position.
-We found that participants tended to initiate their recall sequences with the first few events (Fig.~\ref{fig:list-learning}a), which is qualitatively very similar to previously published list learning experiments (REF).
-Next, we considered another well-studied memory measure in list-learning, the lag conditional response probability curve (or lag-CRP).
-Given the recall of a stimulus in study position $n$, the lag-CRP quantifies the probability that the next item recalled will be of lag $i$.
-The results suggest a strong bias to transition sequentially in the forward direction Fig.~\ref{fig:list-learning}b.
-This can be seen by the high probability values in the lag ~1-5 positions compared to the rest of the transition possibilties.
-Notably, participants were instructed to recall as much as they could in order, and the shape of this lag-CRP is qualitatively similar to list-learning studies of serial recall (REF), where participants are required to recall lists of words in their serial order.
-Finally, we assessed memory performance for each event in the video.
-This plot quantifies the proportion of participants that recalled each event in the video (Fig.~\ref{fig:list-learning}c).
-We found that there was substantial variability in memory for the different events.
-% NOTE: whats the right stat for this?
 
@@
 
-To better visualize the relationship between the video and recall event models, we embedded the video and average recall model into a 2D space (using the UMAP dimensionality reduction algorithm, for details see \ref{sec:methods}) where the points represent video/recall events and the distance between them represents their similarity in 'topic space' (Fig.~\ref{fig:trajectory}a).
+To visualize the relationship between the video and recall event models, we embedded the video and average recall model into a 2D space (using the UMAP dimensionality reduction algorithm, for details see \ref{sec:methods}) where the points represent video/recall events and the distance between them represents their similarity in ``topic space'' (Fig.~\ref{fig:trajectory}a).
 (Note that all analyses are performed in the original 100 dimensional space.) We computed the group average transition probabilities from each event to each other event and plotted the values as lines where the tranparency is proportional to the probability of the transition (Fig.~\ref{fig:trajectory}b).
-Visual inspection reveals that the two models have a very similar geometric structure, and the transition probabilities tend to be strongest between events that occured sequentially (or nearby) in time.
+We observed that the two models have a very similar geometric structure, and the transition probabilities tend to be strongest between events that occured sequentially (or nearby) in time.
 
-% To explore individual variability (and consistency) in the recall event models, we embedded each participant's recall event model in the same 2D 'topics space' described above (\ref{fig:model}h).
-Despite the variability in the number of events remembered, the overall shape of most of the participants' recall trajectories are similar to the video model (\ref{fig:model}h), particularly the participants with a greater number of recalled events.
-
-To formalize the observation that participants' recall trajectories generally matched the shape of the video trajectory, we fit participants' recall data to a model comprised of $k$ line segments that were connected by the average recall event coordinates.
+To test the observation that participants' recall trajectories generally matched the shape of the video trajectory, we fit participants' recall data to a model comprised of $n$ line segments that were connected by the average recall event coordinates.
 We fixed the endpoints of the model at the average first and last recall event, but fit the placement/length of rest of the segments to the data using the average recall events as `hinge-points'.
 Using a cross-validated model fitting procedure (see ~\ref{sec:methods} for details), we searched for the optimal number of line segments.
-The best fitting model ($k$=11) can be seen in Fig.~\ref{fig:linesegs}.
+The best fitting model ($n$=11) can be seen in Fig.~\ref{fig:linesegs}.
 This model represents the set of consecutive line segments that best describe participant's recall trajectories.
 Notably, the optimal model comprises a subset of the total recall events (~roughly 1/3).
+% include a measure of the variance described by the model?
 
-We hypothesized that the `hinge-points' between line segments represent critical scenes of the video where the storyline changed direction.
-To get a sense of the semantic content of each hinge-point, we created wordles (left side of each wordle) where the size of the word is proportional to its frequency in the video text descriptions for that event (Fig.~\ref{fig:linesegs}).
-We performed the same analysis for the recall text (right side of each wordle).
-Notably, the text in the worldes is distinct across hinge-points, but but similar between video and recall within hinge-point.
-
-% NOTE: WILL ADD ANOTHER PARAGRAPH HERE IF THE 'TOPIC FLOW' ANALYSES WORK OUT
+We hypothesized that the points connecting the line segments (we'll refer to them as ``hinge-points'') represent critical scenes in the storyline.
+To visualize the semantic content of each hinge-point, we created wordles (left side, purple) from the topic vectors for each video event, where the size of the word is proportional to its relative ``activation'' in the video event (Fig.~\ref{fig:linesegs}, see ~\ref{sec:methods} for analysis details).
+We performed the same analysis for the average recall topic vectors (right side, orange).
+Notably, the text in the wordles is distinct across hinge-points, but but similar between video and recall within hinge-point.
 
@@
 To assess significance, we performed a permutation test where we circularly shifted the recall model (10000 times) and recomputed the RMSD.
-The recall model significantly matched the video model for nine of the participants [p<.05; participants: 3-4, 8-13, 17 and the p-value for the rest of the participants was less than .25].
-Furthermore, the RMSD values were significantly correlated to memory performance across participants [Pearson's r(16)=-.57, p=.016].
+The recall model significantly matched the video model for nine of the participants ($p$<.05; participants: 3-4, 8-13, 17 and the p-value for the rest of the participants was less than .25).
+Furthermore, the RMSD values were significantly correlated to memory performance across participants (Pearson's $r$(16)=-.57, $p$=.016).
 Thus, a closer match between the video and recall event models was related to better recall performance.
@@
 We then averaged the correlations within participant.
-In line with our prediction, there was a strong correlation between memory performance and precision suggesting that participants who remembered more events also remembered them more veridically [Pearson's r(16)=.74, p=.0006].
+In line with our prediction, there was a strong correlation between memory performance and precision suggesting that participants who remembered more events also remembered them more veridically (Pearson's $r$(16)=.74, p=.0006).
 Next, we considered the distinctiveness of each recall event.
@@
 Then, we averaged this measure over recall events within participant.
-We found that participants with higher memory performance also had higher distinctiveness scores [Pearson's r(16)=.8, p=.0001].
+We found that participants with higher memory performance also had higher distinctiveness scores (Pearson's $r$(16)=.8, p=.0001).
 
@@
 For each participant, we computed the Spearman rank correlation between the order of events that the participant recalled and the actual order of events (filtering events that were actually recalled).
-We found that participants who recalled more events also recalled more of them in order [Pearson's r(16)=.5, p=.04].
+We found that participants who recalled more events also recalled more of them in order (Pearson's $r$(16)=.5, p=.04).
 In summary, we found that better memory performance was associated with more precise and distinctive recall.

### 2018-06-25 main.tex
added in last main text figure

@@
 \centering
-\includegraphics[width=\textwidth]{figs/2_eventseg_v4.pdf}
+\includegraphics[width=\textwidth]{figs/2_eventseg.pdf}
 \caption{\small \textbf{Modelling naturalistic stimuli and recall.} For all plots, darker colors indicate greater values and the range of each plot is 0-1.
@@
 \caption{\small \textbf{Video and recall trajectory plots.} A).
-2-dimensional embedding of recall events model.
+2-dimensional embedding of video events model.
 The arrows indicate the forward direction of the video events.
@@
 The lines connecting the points represent the average probability of transitioning from one event to the other.
-The weight of the line is proportional to the transition probability.}
+The opacity of the line is proportional to the transition probability (0 to 1).
+Arrows indicate the transition with the highest probability for each event.}
 \label{fig:trajectory}
@@
 We observed that the two models have a very similar geometric structure, and the transition probabilities tend to be strongest between events that occured sequentially (or nearby) in time.
+
+\begin{figure}[th!]
+\centering
+\includegraphics[width=1\textwidth]{figs/5_linesegs.pdf}
+\caption{\small \textbf{Recall shape analysis and video/recall content.} A 2-dimensional embedding of the best fitting line segments model across all participant's recall event models.
+The points outlined in black represent the ``hinge-points'' of the best fitting model colored according to their matching video event.
+The points not outlined in black are individual participant recall events colored by the most similar video event.
+The kernel density plot represents the distribution across all points.
+The word clouds for each event (left: video; right: recall) were created by taking the top 100 words for the topics that were ``activated'' during a particular event.}
+\label{fig:linesegs}
+\end{figure}
 

### 2018-06-26 main.tex
added event segmentation paragraph

@@
 More nuanced studies might incorporate self-reported confidence measures as a proxy for memory strength, or ask participants to discriminate between ``recollecting'' an experience or a feeling of ``familiarity'' \citep{Yone02}.
-However, characterizing and evaluating memory in more realistic contexts (e.g., telling a story to a friend about a recent vacation) is a fundamentally different task.
+However, characterizing and evaluating memory in more realistic contexts (e.g., telling a story to a friend about a recent vacation) is much more nuanced.
 Real-world recall is continuous, rather than binary.
-The specific words used to describe an experience have very little bearing on whether the experience is considered to have been ``remembered.''  Further, one might remember the gist of an experience but forgot (or neglect to recount) particular details.
+The specific words used to describe an experience have very little bearing on whether the experience is considered to have been ``remembered.''  Further, one might remember the gist of an experience but forget (or neglect to recount) particular details.
 Or different people who share an experience might recount the experience with a similar level of detail, but the specific details that were remembered might vary across people.
 Which aspects of those recollections should be considered fundamental, and which are extraneous to the main story?
-
-%Another notable feature of human memory is that despite the fact that information flows continuously through our sensory systems, our memories are descretized and centered around particular events.
 
@@
 
+Despite the fact that information flows continuously through our sensory systems, prior research suggests that our memories are partitioned and centered around particular ``events'' \citep{Radv12, RadvZack11, BrunEtal18}.
+Short timescale autocorrelations in the contents of our experiences may cause information to become associatively linked in memory, while sharp contrasts (i.e.
+``event boundaries'') may segment continuous experiences into events \citep{HeusEtal18, BrunEtal18, Radv12}.
+There is compelling evidence that event boundaries can influence memory organization in trial-based recognition \citep{HeusEtal18}, navigation \citep{BrunEtal18}, and narrative comprehension \citep{ZwaaRadv98, EzzyDava11}.
+However, the extent to which people naturally (verbally) recount their experiences in segments centered around particular events has not been explored.
+
 To study the temporal and semantic aspects of memory for naturalistic experiences, we analyzed an open dataset in which participants view and verbally recall an episode of the BBC series \textit{Sherlock}  \citep{ChenEtal17}.
-We developed a novel computational approach which combines topic models \citep{BleiEtal03} and hidden Markov models \citep{Rabi89, BaldEtal17} to capture the temporal evolution of rich semantic structure present in naturalistic experiences.
-We then use this model to characterize the geometric structure and contents of episodic memories for naturalistic experiences.
-We hypothesized that memory for naturalistic experiences is more about preserving the overall ``shape'' of an experience than any of the particular details.
+We developed a novel computational approach based on topic modeling \citep{BleiEtal03} and hidden Markov models \citep{Rabi89, BaldEtal17} to capture the temporal evolution of rich semantic structure present in naturalistic experiences.
+We then use this model to characterize the shape and contents of episodic memories for naturalistic experiences.
+We hypothesized that memory for naturalistic experiences is less about recalling specific details and more about preserving the overall ``shape'' of an experience.
 

### 2018-06-26 main.tex
checking in

@@
 We developed a novel computational approach based on topic modeling \citep{BleiEtal03} and hidden Markov models \citep{Rabi89, BaldEtal17} to capture the temporal evolution of rich semantic structure present in naturalistic experiences.
-We then use this model to characterize the shape and contents of episodic memories for naturalistic experiences.
-We hypothesized that memory for naturalistic experiences is less about recalling specific details and more about preserving the overall ``shape'' of an experience.
+We then use this model to characterize verbally recalled episodic memories for naturalistic experiences.
+We hypothesized that memories for naturalistic experiences are 1) segmented and centered around particular events and 2) less about recalling specific details and more about preserving the overall ``shape'' of an experience.
 
@@
 \includegraphics[width=1\textwidth]{figs/1_analysis_schematic.pdf}
-\caption{\small \textbf{Schematic of the analysis approach.} For each moment of the video, text descriptions were manually generated.
+\caption{\small \textbf{Schematic of the analysis approach.} For each scene in the video, text descriptions were generated by hand.
 Three exemplary time points are displayed here.
 Below the video descriptions are text samples from an example participant's verbal recall transcript.
-We trained a topic model on the moment-by-moment video description text and transformed participant's recall transcripts using this same model.
+We fit a topic model to the moment-by-moment video text descriptions and transformed participant's verbal recall transcripts using this same model.
 The bar charts display the resulting topic model weights for the video (in blue) and recall (in orange) for three example topic dimensions.}
@@
 
-\subsubsection{A model to capture the geometric structure of naturalistic stimuli}
-We fit a topic model \citep{BleiEtal03} to manually annotated text descriptions of scenes from the episode.
+\subsubsection{A model to capture the temporal and semantic structure of naturalistic stimuli}
+We fit a topic model \citep{BleiEtal03} to (manually annotated) text descriptions of scenes from the video.
 The text descriptions contained details of the scene such as the characters, location, and a short summary of the scene (see Fig.\ref{fig:schematic} for example text, see \ref{sec:methods} for analysis details).
-We then transformed the text descriptions using the (same) topic model, resulting in a scenes (1000) by topics (100) matrix, where each row of the matrix represents a probabalistic mixture of topics discovered in that scene (See Fig.\ref{fig:schematic} for example topic vectors).
-We expanded this matrix from 1000 to 1976 timepoints by copying the vectors for scenes that spanned multiple TRs.
-As depicted in Fig.~\ref{fig:model}a, the topics are sparse and change slowly over time.
+We then transformed the text descriptions using the (same) topic model, resulting in a scenes (1976) by topics (100) matrix, where each row of the matrix represents a probabalistic mixture of topics discovered in that scene (See Fig.\ref{fig:schematic} for example topic vectors).
+As depicted in Fig.~\ref{fig:model}a, the topic vectors are sparse and change slowly over time.
 Furthermore, there are clear transitions from one topic `state' to the next, possibly indexing scene transitions in the stimulus.
-To get a better handle on this temporal structure, we computed the timepoint-by-timepoint correlation matrix of the video model (Fig.~\ref{fig:model}c).
+To get a better handle on this temporal structure, we computed a timepoint (1976) by timepoint (1976) correlation matrix of the video model (Fig.~\ref{fig:model}c).
 This correlation matrix reveals that the model has a strong, block-diagonal structure.
@@
 
-\subsubsection{Modeling verbal free recall}
-After watching the episode, participants verbally recalled (in order) as much of the episode as they could.
+\subsubsection{Modeling verbal recall}
+After watching the video, participants verbally recalled (in order) as much of the episode as they could.
 We used the same topic model (fit with the text descriptions of the video) to transform participants' verbal recall transcripts.
-The result is a sentences (range: 68 to 294, mean: 131.94) by topics (100) matrix for each participant, where each row represents the estimated mixture of topics for a given window of sentences during recall.
-An example participant's (#13) model is plotted in Fig.~\ref{fig:model}c.
-Note that the topics were derived solely from the text descriptions of the video, and so the topic models estimated for recall are dependent on the topics in the episode.
-This approach effectively projects the participants' verbal recall into the video ``stimulus space'', allowing us to quantify the dynamics of verbally reported memories as well as relate them to their originating experiences.
+The result was a sentences (range: 68 to 294, mean: 131.94) by topics (100) matrix for each participant, where each row represents a probabalistic mixture of topics for a given window of sentences during recall.
+An example participant's (#13) recall model is plotted in Fig.~\ref{fig:model}c.
+Like the video model, topic vectors were sparse and changed gradually.
+Note that the topics were derived solely from the text descriptions of the video, and so the topic models estimated for recall are dependent on the topics present in the video.
+This approach effectively projects the participants' verbal recall into the video's `topic space'', allowing us to directly compare them to the video model.
 
 Next, we investigated the temporal structure of the recall matrices.
-For each participant, we computed a timepoint-by-timepoint correlation matrix from recall models.
+For each participant, we computed a timepoint (68 to 294) by timepoint (68 to 294) correlation matrix from the recall models.
 An example participant's (\#13) correlation matrix is plotted in Fig.~\ref{fig:model}d).
-Like the video model, each participant's recall correlation matrix exhibited a block-diagonal structure (Supp Fig X).
+Like the video model, each participant's recall correlation matrix exhibited a strong block-diagonal structure (Supp Fig X).
+Notably, this suggests that participants recounted the video in discriminable segments, potentially indexing the recall of specific events from the video.
 
 \subsubsection{Segmenting the video and recall models into `events'}
-One striking feature of the video and recall correlation matrices (see Fig.~\ref{fig:model}) is a strong, block structure along the diagonal of the matrices.
-We hypothesized that this structure might arise from transient stability in the content of the video, and the subsequent language used to describe each event of the video.
-If true, we reasoned that it would be possible to infer the specific event a participant is describing by comparing the (average) topic model for a particular recall ``event'' with the (average) topic vector for each video event.
-In other words, the video event that is most similar to a given recall event is the event that the participant is most likely describing.
-To test this idea, it is first necessary to systematically parse the matrices into events.
-We leveraged a hidden Markov model (~\citep{BaldEtal17}) to estimate $k$ events (or states) from a (multivariate) time series.
-The algorithm determined 34 events for the movie model and a range of values (range: 8-27; mean: 15.41; SD: 5.6) for the recall models (see ~\ref{sec:methods} for details on choosing an optimal $k$ value).
-The events discovered for a representative participant (\#13) are highlighted as yellow rectangles outlining blocks along the diagonal of the participant's correlation matrix (Fig.~\ref{fig:model}d).
+As described above, a striking feature of the video and recall correlation matrices (see Fig.~\ref{fig:model}) is a strong, block structure along the diagonal of the matrices.
+We hypothesized that this structure might arise from transient stability in the contents of the video (i.e.
+``events''), as well as the subsequent language used to recount each event of the video.
+If true, we reasoned that it would be possible to identify the specific event a participant is describing by comparing the topic vector for a particular recall ``event'' with the topic vector for each video event.
+In other words, the video event that is most similar (i.e.
+correlated) to a particular recall event is the event that the participant is most likely describing.
+
+To test this idea, first we segmented the video and recall models in $k$ events (i.e.
+states) using a hidden Markov model (~\citep{BaldEtal17}).
+The algorithm determined 34 events for the video model and a range of values (range: 8-27; mean: 15.41; SD: 5.6) for the recall models (see ~\ref{sec:methods} for details on choosing an optimal $k$ value).
+The events discovered for the model and a representative participant (\#13) are highlighted as yellow rectangles outlining blocks along the diagonal of the correlation matrices (Fig.~\ref{fig:model}b,d).
+
 Next, we created a video event model by averaging together neighboring topic vectors that the were classified to be in the same event, resulting in an events (34) by topics (100) matrix (Fig.~\ref{fig:model}e).
 We performed the same procedure for the recall matrices (see Fig.~\ref{fig:model}f for example).
-Then, we computed the correlation between these two event models, resulting in a video events (34) by recall events (8-27, depending on the participant) correlation matrix (see Fig/~\ref{fig:model}g).
+Then, we computed the correlation between video and recall event models, resulting in a video events (34) by recall events (8-27, depending on the participant) correlation matrix (Fig/~\ref{fig:model}g).
 These matrices represent the similarity (correlation) between each video event and each recall event (for each participant).
-To determine which video events the recall events most likely referred to, for each recall event, we found the index of the video event with the highest correlation (i.e.
+To determine which video event a particular recall event was most likely describing, we computed the index of the video event with the highest correlation to the recall event (i.e.
 the argmax).
-This is depicted in Fig.~\ref{fig:model}g as the cell highlighted with the yellow box for each column in the video-recall event correlation matrix.
-Notably, our algorithm suggests that the example participant recalled the events largely in order (occasionally skipping over an event).
+This is depicted in Fig.~\ref{fig:model}g as the cells highlighted with a yellow border.
+Interestingly, our algorithm suggests that the example participant recalled the events largely in order, occasionally skipping a video event.
 
-Next, we computed a group-averaged recall event model and video-recall event correlation matrix.
-To do this, for each participant (and each recall event), we grouped the recall event vectors (across all participants) by the video event that they were most highly correlated to.
-We then averaged the recall event vectors within group.
-This yielded an average recall event vector for all but one (of 34) event (since no participant remembered this event according to our model).
-Lastly, we computed an average recall event (34) by video event (34) correlation matrix, and highlighted the highest correlation in the column with a black box (Fig.~\ref{fig:model}h).
+Then, we computed a group-averaged recall event model and video-recall event correlation matrix.
+For each participant (and each recall event), we sorted the recall event vectors (across all participants) according to the video event that they were most highly correlated to.
+We then averaged the recall event vectors within each group.
+This yielded an average recall event vector for all but one (of 34) video events, since no participant remembered one of the events according to our model.
+Lastly, we computed an average recall event (34) by video event (34) correlation matrix, and highlighted the cell with the highest correlation value with a yellow border (Fig.~\ref{fig:model}h).
 Notably, this matrix displayed high correlation values along the diagonal and low correlations in the off-diagonal cells.
-This suggests that on average, participants were able to recapitulate the events in the episode and our approach captured this behavior.
+This suggests that on average, participants were able to recapitulate the events in the episode in a specific, highly descriminable way.
 % NOTE: ^ possibly need a null model for the group analysis.
@@
 \includegraphics[width=\textwidth]{figs/2_eventseg.pdf}
-\caption{\small \textbf{Modelling naturalistic stimuli and recall.} For all plots, darker colors indicate greater values and the range of each plot is 0-1.
+\caption{\small \textbf{Modelling naturalistic stimuli and recall.} A depiction of our analysis pipeline.
+For all plots, darker colors indicate greater values and the range of each plot is 0-1.
 A).
 A timepoints (1976) by topics (100) matrix representing the video stimulus.
-Each row represents the most likely mixture of topics for a given timepoint.
-Each columns represents a different topic.
+Each row represents the most likely mixture of topics for a given timepoint (i.e.
+topic weights).
+Each column represents a different topic.
 B).
@@
 A recall events (27) by video events (34) correlation matrix for participant \#13.
-The yellow squares identify the video event with the highest correlation to a given recall event.
+The cells with a yellow border identify the video event with the highest correlation to a given recall event.
 F.
 A group averaged recall events (34) by video events (34) correlation matrix.
-The yellow squares identify the video event with the highest correlation to a given average recall event.}
+The cells with yellow borders are the video event with the highest correlation to a given average recall event.}
 \label{fig:model}
@@
 \includegraphics[width=1\textwidth]{figs/3_list_learning.pdf}
-\caption{\small \textbf{Naturalistic extensions of classic memory analyses.} A).
+\caption{\small \textbf{Naturalistic extensions of classic list-learning memory analyses.} A).
 The probability of first recall as a function of the serial position of the event during encoding.
 B).
+A lag-conditional response probability curve.
 Given recall of event i, the probability that the next recalled item will be from serial position i +/- lag.
 C).
-Proportion recalled as a function of serial position.
+Proportion of events recalled as a function of serial position.
 All error bars are the standard error of the mean derived from a bootstrap resampling procedure.}
@@
 
-\subsubsection{Naturalistic extensions of classic memory analyses}
-Just like in a traditional `free-recall' list-learning experiment where participants view a list of words and then verbally recall them, our video-recall matching approach described above affords us the ability to analyze memory in the same way (where the recalled words are analogous to recalled events).
+\subsubsection{Naturalistic extensions of classic list-learning memory analyses}
+Just like in a traditional `free-recall' list-learning experiment where participants view a list of words and then verbally recall them, our video-recall matching analysis approach affords us the ability to analyze memory in the same way.
+The recalled events can be treated as ``items'' analogous to words recalled in a list-learning study.
 In our first set of analyses, we sought to characterize memory performance/dynamics by extending classic analyses originally designed for list-learning experiments to more naturalistic settings.

### 2018-06-26 main.tex
cheching in

@@
 
-First, we considered how participant's initiated the recall sequence (known in the literature as the `probability of first recall' or `PFR').
-This metric quantifies the likelihood of initiating a sequence of recalls based on the item's serial position.
+First, we asked whether the estimated number of recall events ($k$) by participant was related to hand-annotated accuracy as published in Chen et al.
+(2017).
+We found a strong positive correlation where subjects with a greater number of recall events also had better overall memory performance (Pearson's $r$(16)=.67, $p$=.003).
+Then, we considered how participants initiated the recall sequence (known in the literature as the `probability of first recall' or `PFR').
+This metric quantifies the likelihood of initiating a sequence of recalls based on an item's serial position during encoding.
 We found that participants tended to initiate their recall sequences with the first few events (Fig.~\ref{fig:list-learning}a), which is qualitatively very similar to previously published list learning experiments (REF).
-Next, we considered another well-studied memory measure in list-learning, the lag conditional response probability curve (or lag-CRP).
+Next, we considered another well-studied memory measure in the list-learning literature, the lag conditional response probability curve (or lag-CRP) ~\citep{Kaha96}.
 Given the recall of a stimulus in study position $n$, the lag-CRP quantifies the probability that the next item recalled will be of lag $i$.
-The results suggest a strong bias to transition sequentially in the forward direction Fig.~\ref{fig:list-learning}b.
+The result suggests a strong bias to transition sequentially events in the forward direction Fig.~\ref{fig:list-learning}b.
 This can be seen by the high probability values in the lag ~1-5 positions compared to the rest of the transition possibilties.
 Notably, participants were instructed to recall as much as they could in order, and the shape of this lag-CRP is qualitatively similar to list-learning studies of serial recall (REF), where participants are required to recall lists of words in their serial order.
-Finally, we assessed memory performance for each event in the video.
-This plot quantifies the proportion of participants that recalled each event in the video (Fig.~\ref{fig:list-learning}c).
-We found that there was substantial variability in memory for the different events.
+Finally, we assessed memory performance for each event in the video as a function of its serial position during encoding (Fig.~\ref{fig:list-learning}c).
+We found that there was substantial variability in memory for the different events (STAT?).
 Furthermore, the shape of the curve is different than what is typically found in list learning experiments (we'll come back to this point in the dicussion).
 
-Next, we asked whether the estimated number of recall events ($k$) by participant was related to hand-annotated accuracy as published in Chen et al.
-(2017).
-We found a strong positive correlation where subjects with a greater number of recall events also had better memory performance (Pearson's $r$(16)=.67, $p$=.003).
-We considered two additional across-participant measures of recall that characterize memory organization: temporal clustering and semantic clustering.
-Temporal clustering (REF) measures the extent to which participants tend to cluster recalls of events encoded nearby in time.
+ We also considered two additional across-participant measures of recall that characterize memory organization: temporal clustering and semantic clustering.
+Temporal clustering (REF?) measures the extent to which participants tend to cluster recalls of events encoded nearby in time.
 For example, if a participant recalled in exact serial order, the score would be 1 whereas if they sequentially recalled randomly positioned items the score would be ~.5.
@@
 \subsubsection{The fundamental shape of an experience is preserved in recall}
-The previous set of analyses are useful in that they enable us to quantify memory dynamics for naturalistic stimuli in a way that is comparable to a vast literature on list-learning recall dynamics.
-However, these methods fail to capture the rich semantic and temporal structure present in naturalistic stimuli (and associated recall of those experiences).
+The analyses described in the previous section are useful in that they allow us to quantify memory dynamics for naturalistic stimuli in a way that is comparable to a vast literature on list-learning.
+However, these methods (and trial-based experiments more generally) fail to capture the rich semantic and temporal structure present in naturalistic stimuli and associated recall of those experiences.
 Thus, our next set of analyses test whether the `shape' of an experience is preserved in memory.
-We hypothesized that despite individual variability in the precision and amount of content recalled across subjects, the general shape of the episode would be recalled by everyone.
+We hypothesized that despite substantial individual variability in the precision and amount of content recalled across by participants, the overall shape of the episode would be recapitulated by all.
 
@@
 \caption{\small \textbf{Video and recall trajectory plots.} A).
-2-dimensional embedding of video events model.
+2-dimensional embedding of the video events model.
 The arrows indicate the forward direction of the video events.
 B).
-2-dimensional embedding of the average recall events.
+2-dimensional embedding of the average recall events model.
 The colors refer to the most similar video events.
@@
 
-To visualize the relationship between the video and recall event models, we embedded the video and average recall model into a 2D space (using the UMAP dimensionality reduction algorithm, for details see \ref{sec:methods}) where the points represent video/recall events and the distance between them represents their similarity in ``topic space'' (Fig.~\ref{fig:trajectory}a).
+To visualize the relationship between the video and recall event models, we embedded the video and average recall models into a 2D space (using the UMAP dimensionality reduction algorithm, for details see \ref{sec:methods}) where the points represent video/recall events and the distance between them represents their similarity in ``topic space'' (Fig.~\ref{fig:trajectory}a).
 (Note that all analyses are performed in the original 100 dimensional space.) We computed the group average transition probabilities from each event to each other event and plotted the values as lines where the tranparency is proportional to the probability of the transition (Fig.~\ref{fig:trajectory}b).
-We observed that the two models have a very similar geometric structure, and the transition probabilities tend to be strongest between events that occured sequentially (or nearby) in time.
+We observed that the two models have a very similar temporal evolution and geometric structure, and the transition probabilities tend to be strongest between events that occured sequentially (or nearby) in time.
 
@@
 \includegraphics[width=1\textwidth]{figs/5_linesegs.pdf}
-\caption{\small \textbf{Recall shape analysis and video/recall content.} A 2-dimensional embedding of the best fitting line segments model across all participant's recall event models.
-The points outlined in black represent the ``hinge-points'' of the best fitting model colored according to their matching video event.
-The points not outlined in black are individual participant recall events colored by the most similar video event.
+\caption{\small \textbf{Recall shape analysis and video/recall content.} A 2-dimensional embedding of the best fitting line segment model.
+The points outlined in black represent and connected by black line segments represent the critical recall events (or ``hinge-points'') of the best fitting model colored according to their matching video event.
+The points not outlined in black are individual participant recall event topic vectors colored by the most similar video event.
 The kernel density plot represents the distribution across all points.
-The word clouds for each event (left: video; right: recall) were created by taking the top 100 words for the topics that were ``activated'' during a particular event.}
+The word clouds for hinge-point (left: video; right: recall) were created by plotting the top 100 words from topic model that were ``activated'' during a particular event.}
 \label{fig:linesegs}
@@
 
-To test the observation that participants' recall trajectories generally matched the shape of the video trajectory, we fit participants' recall data to a model comprised of $n$ line segments that were connected by the average recall event coordinates.
-We fixed the endpoints of the model at the average first and last recall event, but fit the placement/length of rest of the segments to the data using the average recall events as `hinge-points'.
+To test the observation that participants' recall trajectories generally matched the shape of the video trajectory, we fit participants' recall data to a model comprised of $n$ line segments that were connected by a subset of the average recall event coordinates.
+We fixed the endpoints of the model at the average first and last recall event, but fit the placement/length of rest of the line segments to the data.
 Using a cross-validated model fitting procedure (see ~\ref{sec:methods} for details), we searched for the optimal number of line segments.
-The best fitting model ($n$=11) can be seen in Fig.~\ref{fig:linesegs}.
-This model represents the set of consecutive line segments that best describe participant's recall trajectories.
+The best fitting model (12 line segments) can be seen in Fig.~\ref{fig:linesegs}.
+This model represents the set of consecutive line segments that best describe all participants recall event models.
 Notably, the optimal model comprises a subset of the total recall events (~roughly 1/3).
@@
 
-We hypothesized that the points connecting the line segments (we'll refer to them as ``hinge-points'') represent critical scenes in the storyline.
-To visualize the semantic content of each hinge-point, we created wordles (left side, purple) from the topic vectors for each video event, where the size of the word is proportional to its relative ``activation'' in the video event (Fig.~\ref{fig:linesegs}, see ~\ref{sec:methods} for analysis details).
-We performed the same analysis for the average recall topic vectors (right side, orange).
-Notably, the text in the wordles is distinct across hinge-points, but but similar between video and recall within hinge-point.
+We hypothesized that the points connecting the line segments (referred to as ``hinge-points'') represent critical scenes in the storyline.
+To visualize the semantic content of each hinge-point, we created wordles from the average topic vectors for each video event (left side), where the size of the word is proportional to its ``activation'' in the video event relative to other video events (Fig.~\ref{fig:linesegs}, see ~\ref{sec:methods} for analysis details).
+We performed the same analysis for the average recall topic vectors (right side).
+Notably, the text in the wordles is distinct across the hinge-points, but but similar between video and recall within hinge-point.
 

### 2018-07-06 boneyard.tex
checking in intro changes

@@
 Visualizing the data in this way makes it clear that the overall shape and correlational structure of the video and average recall matrices is quite similar.
+
+Another major difference between traditional trial-based memory paradigms and real-world memory concerns the subjective experience of the participant.
+For example, consider an emotionally salient event in your life (e.g.\ marriage, the birth of a child, death of a loved one, etc.), or even a movie that you were especially impacted by.
+No list-learning paradigm (or similar) can hope to capture the nuance and depth of such experiences.
+Our everyday experiences feel ``important'' to us, whereas the words we study on a random word list do not.

### 2018-07-06 main.tex
checking in intro changes

@@
 
-Another major difference between traditional trial-based memory paradigms and real-world memory concerns the subjective experience of the participant.
-For example, consider an emotionally salient event in your life (e.g.\ marriage, the birth of a child, death of a loved one, etc.), or even a movie that you were especially impacted by.
-No list-learning paradigm (or similar) can hope to capture the nuance and depth of such experiences.
-Our everyday experiences feel ``important'' to us, whereas the words we study on a random word list do not.
-One component of naturalistic experiences that enhances their impact concerns the temporal structure with which they unfold.
-For example, our experiences in the real world are necessarily autocorrelated in space and time on short timescales.
+One hallmark feature of naturalistic experiences is the temporal structure with which they unfold.
+For example, our experiences in the real world are typically autocorrelated in space and time on short timescales.
+In other words, the contents of our experiences from moment to moment are similar, predictable and (often) change slowly over time.
 Further, or experiences are often characterized by longer timescale correlations that reflect the impact of our past actions and observations.
-These temporal dynamics are not typically present in traditional memory studies, but are important if we wish to understand how our memory systems remember our everyday experiences.
+For instance, distant memories can influence current perception and actions.
+These temporal dynamics are not typically present in traditional memory studies, but are likely important if we wish to understand how our memory systems remember our everyday experiences.
 
-Despite the fact that information flows continuously through our sensory systems, prior research suggests that our memories are partitioned and centered around particular ``events'' \citep{Radv12, RadvZack11, BrunEtal18}.
+Despite the continuous nature of naturalistic experiences, prior research suggests that our memories are segmented and centered around particular ``events'' \citep{Radv12, RadvZack11, BrunEtal18}.
 Short timescale autocorrelations in the contents of our experiences may cause information to become associatively linked in memory, while sharp contrasts (i.e.
 ``event boundaries'') may segment continuous experiences into events \citep{HeusEtal18, BrunEtal18, Radv12}.
-There is compelling evidence that event boundaries can influence memory organization in trial-based recognition \citep{HeusEtal18}, navigation \citep{BrunEtal18}, and narrative comprehension \citep{ZwaaRadv98, EzzyDava11}.
-However, the extent to which people naturally (verbally) recount their experiences in segments centered around particular events has not been explored.
+There is now compelling evidence that event boundaries can influence memory organization in trial-based recognition \citep{HeusEtal18}, navigation \citep{BrunEtal18}, and narrative comprehension \citep{ZwaaRadv98, EzzyDava11}.
+However, the extent to which people naturally recount their experiences as ``events'' has not been explored.
+
+ Here, we propose that naturalistic experiences have a unique geometric `shape' formed by correlational structure in perceptual/conceptual aspects of the stimulus.
+For instance, if a particular location is revisited more than once during a naturalistic experience (e.g.
+watching a movie), the perceptual features will be more similar during those timepoints as compared to other timepoints in distinct locations.
+Similarly, if two actors hold a conversation spanning multiple locations, conceptual espects of the stimulus will be more similar during those timepoints as compared to other timepoints.
+Together, both perceptual and conceptual features contribute to the overall shape of a naturalistic stimulus.
+As a consequence of this structure, we hypothesize that episodic memories for those same experiences should mirror this shape.
+While the specific details and words recalled may be different from person to person, we expect that the overall shape of the experience will be preserved.
 
@@
 We then use this model to characterize verbally recalled episodic memories for naturalistic experiences.
-We hypothesized that memories for naturalistic experiences are 1) segmented and centered around particular events and 2) less about recalling specific details and more about preserving the overall ``shape'' of an experience.
 

### 2018-07-09 main.tex
checking in intro...struggling on the framing

--- 2018-06-26 main.tex
@@
 
-Another major difference between traditional trial-based memory paradigms and real-world memory concerns the subjective experience of the participant.
-For example, consider an emotionally salient event in your life (e.g.\ marriage, the birth of a child, death of a loved one, etc.), or even a movie that you were especially impacted by.
-No list-learning paradigm (or similar) can hope to capture the nuance and depth of such experiences.
-Our everyday experiences feel ``important'' to us, whereas the words we study on a random word list do not.
-One component of naturalistic experiences that enhances their impact concerns the temporal structure with which they unfold.
-For example, our experiences in the real world are necessarily autocorrelated in space and time on short timescales.
-Further, or experiences are often characterized by longer timescale correlations that reflect the impact of our past actions and observations.
-These temporal dynamics are not typically present in traditional memory studies, but are important if we wish to understand how our memory systems remember our everyday experiences.
+A defining feature of naturalistic experiences is the temporal structure with which they unfold.
+Our experiences in the real world are typically autocorrelated in space and time on short timescales.
+In other words, the contents of an experience are often similar from moment to moment and change gradually.
+For example, many of us spend our mornings/evenings at home and much of our days at work (e.g.
+an office).
+While the specific happenings within these contexts differs, they are (usually) highly correlated and predictable over time.
+Furthermore, our experiences can also be characterized by longer timescale correlations.
+For example, consider returning to your office after taking a lunch break.
+The perceptual contexts before and after lunch are highly similar, but separated in time.
+However, these recurrent and gradually changing temporal dynamics are not typically present in traditional memory studies, but are likely important if we wish to understand how our memory systems remember our everyday experiences.
 
-Despite the fact that information flows continuously through our sensory systems, prior research suggests that our memories are partitioned and centered around particular ``events'' \citep{Radv12, RadvZack11, BrunEtal18}.
-Short timescale autocorrelations in the contents of our experiences may cause information to become associatively linked in memory, while sharp contrasts (i.e.
+Despite the continuous and (often) gradually changing nature of naturalistic experiences, prior research suggests that our memories for those same experiences may be more descrete and centered around particular ``events'' \citep{Radv12, RadvZack11, BrunEtal18}.
+Short timescale autocorrelations in the contents of an experience may cause information to become associatively linked in memory (and thus treated as a single event), while sharp changes (i.e.
 ``event boundaries'') may segment continuous experiences into events \citep{HeusEtal18, BrunEtal18, Radv12}.
-There is compelling evidence that event boundaries can influence memory organization in trial-based recognition \citep{HeusEtal18}, navigation \citep{BrunEtal18}, and narrative comprehension \citep{ZwaaRadv98, EzzyDava11}.
-However, the extent to which people naturally (verbally) recount their experiences in segments centered around particular events has not been explored.
+There is now compelling evidence that event boundaries can influence memory organization when learning sequences of items \citep{HeusEtal18, DuBrDava13}, during navigation \citep{BrunEtal18}, and narrative comprehension \citep{ZwaaRadv98, EzzyDava11}.
+Furthermore, brain activity while viewing naturalistic stimuli displays a block-diagonal structure, and the neurally-derived segments are correlated with judgements of event boundaries \citep{BaldEtal17}.
+However, whether people naturally recount their experiences in as events has not been explored.
 
-To study the temporal and semantic aspects of memory for naturalistic experiences, we analyzed an open dataset in which participants view and verbally recall an episode of the BBC series \textit{Sherlock}  \citep{ChenEtal17}.
-We developed a novel computational approach based on topic modeling \citep{BleiEtal03} and hidden Markov models \citep{Rabi89, BaldEtal17} to capture the temporal evolution of rich semantic structure present in naturalistic experiences.
-We then use this model to characterize verbally recalled episodic memories for naturalistic experiences.
-We hypothesized that memories for naturalistic experiences are 1) segmented and centered around particular events and 2) less about recalling specific details and more about preserving the overall ``shape'' of an experience.
+% We propose that variability in the contents of an experience over time define a ``stimulus-space''.
+In this space, timepoints where the contents of experience are more similar are represented as points that are closer together.
+Timepoints with relatively more distinct content are represented further apart.
+The moment-by-moment flow of content through this space can be represented as a ``stimulus trajectory''.
+%
+% As a consequence of this structure, we hypothesized that verbally recounted memories for those experiences would mirror this shape.
+
+To study the temporal and semantic aspects of memories for naturalistic experiences, we analyzed an open dataset in which participants view and then verbally recall an episode of the BBC series \textit{Sherlock}  \citep{ChenEtal17}.
+We Furthermore, we hypothesized that the stimulus To test these hypotheses, we developed a novel computational approach based on topic modeling \citep{BleiEtal03} and hidden Markov models \citep{Rabi89, BaldEtal17} to capture the temporal structure present in naturalistic experiences.
+We then use this model to characterize the shape of the stimulus as well as verbally recalled memories.
 

### 2018-07-09 main.tex
added methods up to list learning analyses

@@
 
+\section{Methods}
+\label{sec:methods}
+
+\subsection{Participants and Experimental Design}
+How much detail here? or just point to janice's paper?
+
+\subsubsection{Fitting the topic model to the video text and recall transcripts}
+A topic model was used to estimate the most likely mixture of topics for a given sample of text.
+First, the video was manually segmented into 1000 scenes, and a collection of descriptive features was manually transcribed.
+For each scene, we considered the following features: scene details (i.e.
+a sentence or two describing what happened in that scene, space (indoor or outdoor), name of all the characters in the scene, name of the character in focus, name of the character speaking, location, camera angle, music presence, and words on the screen.
+We concatenated the text for all of these features within each segment, creating a 'bag of words' describing each scene.
+We then transformed the text descriptions into overlapping windows of 50 scene segments.
+For example, the first text sample comprised the text from the first 50 segments, the second comprised the text from n+1:n+51, and so on.
+We trained our model using these overlapping text samples using scikit-learn's (version 0.19.1) `CountVectorizer' and `LatentDirichletAllocation' classes.
+First, the text was transformed into a vector of word counts (default parameters).
+This gave a word count vector for each scene in the video.
+Then, the word count vectors were used to fit a topic model (\# of topics=100, method=batch).
+We transformed the text descriptions using the model resulting in a scenes (1000) by topics (100) matrix.
+The scene descriptions often spanned multiple timepoints (i.e.
+TRs).
+To account for this, we expanded the video model by copying the rows of the model for as many timepoints that the scene description spanned.
+After this expansion, the shape of the model was the length of the duration of the video (1976 TRs).
+
+To create the recall models, for each participant we tokenized the recall transcript into a list of sentences and then mapped the list to overlapping windows of 10 sentences.
+We transformed the list of overlapping recall sentences using the model that was trained on the video text (as described in the paragraph above).
+The result of this was a sentences (range: 68-294) by topics (100) matrix for each participant that represented the most likely mixture of topics for a given chunk of sentences.
+
+\subsubsection{Extracting events using a hidden Markov model}
+The topic model timepoint-by-timepoint correlation matrices all exhibited a block-diagonal structure (with small off-diagonal values), suggesting that the models were comprised of a number of sequential `states' (or events).
+To capture this structure, we fit the video and each recall model using a hidden Markov model (HMM).
+Given a number of states or events ($k$), the HMM recovers a set of labels that segments consecutive timepoints into $k$ events (REF markov paper).
+To implement this analysis, we used the Brainiak toolbox \citep{BaldEtal17}.
+
+Our metric for choosing the `best fitting' HMM was to choose the model with the $k$ value that maximized the ratio of the average `within-event' correlation values (i.e.
+the correlation values for blocks of consecutive timepoints the model identified as one event) and the average `across-event' correlation (i.e.
+the rest of the correlation values).
+Additionally, we included a penalty parameter that was proportional to the smoothing of the model that preferred models with smaller $k$ values.
+We chose $k$ values separately for the video model and for each recall model.
+Then, using the best $k$ values, We fit a separate HMM for each topic model.
+Finally, we averaged over timepoints identified to be in the same event resulting in a $k$ events by 100 topics matrix for the video model and each of the recall models.
+%
+% \subsubsection{Matching recall events to video events}
+% To figure out which video event each recall event referred to, we correlated the video events model and each recall events model.
+This resulted in a video events (34) by recall events (8-27) correlation matrix (for each participant) which contains the similarity between each video event and each recall event.
+To find the most likely video event that a given recall event referred to, we computed the argmax over the columns of this matrix.
+The result was a list of video event indices for each participant.
+These indices are analogous to the values found in a ``recall matrix'' from a free recall list learning experiment, but represent the recall of particular events (instead of words, for example).
+%
+% \subsubsection{Characterizing memory performance}
+% We used a few different metrics to assess memory that were all designed to capture the relationship between the video and recall models.
+First, to get a general sense for the match between the video and recall matrices, we vectorized the the matrices and correlated them.
+This resulted in a single number representing how well a given participant recalled the video.
+To get a temporally dynamic measure of memory, for each participant we computed the pairwise correlation between matching video/recall timepoints.
+This allowed us to assess memory for individual moments of the video.
+Finally to get a more nuanced representation of memory for the video, we computed a video/recall model correlation matrix for each participant.
+These timepoint (1976) by timepoint (1976) matrices represent the correlation between every moment of the video model and every moment of the recall model.
+To provide some intuition, if a participant recalled every scene at the same rate and in exactly the same order as the video, we would expect high correlation values along the diagonal of this matrix.
+However, if a participant recalls the scenes out of order, or at different rates for different scenes, this will result in high values off the diagonal.
+%
+% The only additional constraint we imposed was that there was at least 2 points between each line segment.
+% We searched for the optimal number of line segments by iteratively splitting the participants into two groups, fitting the model to the first half and testing the model on the remaining subjects.
+To compute fit to the model, for each recall event (a 1 by 100 topics vector) we computed the nearest line segment and then calculated the mean squared distance averaging over all events and all participants (in the sample).
+We repeated this 20 times using 1-10
+%
+% \subsubsection{Bridging between the stimulus and recall}
+% The participants in this study were instructed to recall as much of the episode as they could in the order it happened.
+Thus, we hypothesized that the recall models should resemble the video model to the extent that participants followed these instructions and had reasonably good memory accuracy.
+To test whether this was true, we correlated each moment of the video model with each moment of each participants' resampled recall model.
+We then averaged these matrices together to get a single group averaged matrix.
+The result was a viewing time (1976) by recall time (1976) correlation matrix representing the average relationship between every moment of the movie and recall models (Fig.~\ref{fig:model}e).
+Notably, we observe significant correlation values (p<.05, permutation test described in \ref{sec:methods}) primarily along the diagonal, suggesting that our model captures the fact that participants recalled the episode in order.
+We also visualized this effect by projecting the matrices into a 3D space (reduced using Spectral Embedding [cite]) where the proximity of the trajectories at every timepoint represents how similar the topic vectors were.
+Visualizing the data in this way makes it clear that the overall shape and correlational structure of the video and average recall matrices is quite similar.
+
 \bibliography{memlab}

### 2018-07-09 main.tex
added methods up to list learning analyses

@@
 %
-% \subsubsection{Matching recall events to video events}
-% To figure out which video event each recall event referred to, we correlated the video events model and each recall events model.
+\subsubsection{Matching recall events to video events}
+To figure out which video event each recall event referred to, we correlated the video events model and each recall events model.
 This resulted in a video events (34) by recall events (8-27) correlation matrix (for each participant) which contains the similarity between each video event and each recall event.

### 2018-07-09 main.tex
finished methods for classic memory analyses

@@
 %
-% \subsubsection{Characterizing memory performance}
+\subsubsection{Characterizing memory performance using classic analyses.}
+
+\textbf{Overall Accuracy.}  To get an overall measure of the quantity of information recalled, we computed the proportion of sucessfully recalled events by counting the number of unique recall events identified by the HMM model and dividing by the total number of video events.
+We performed this analysis for each participant separately.
+
+\textbf{Probability of first recall (PFR).}  The (PFR) analysis represents the probability that an item will be recalled first as a function of its serial position during encoding.
+We initialized a \# of participants (17) by \# of video events (34) matrix.
+Then for each participant, we found the index of the video event that was recalled first and filled in that index in the matrix with a 1.
+Finally, we averaged over the rows of the matrix, resulting in a 1 by 34 array representing the proportion of subject that recalled an event as a function of serial position during encoding.
+
+\textbf{Lag conditional probability curve (lag-CRP).} The lag-CRP represents the probability that the next item recalled will be of lag $i$ from the just recalled item.
+For each recall transition, we computed the lag between the current recall event and the next recall event, normalizing by the total number of possible transitions.
+This resulted in a \# of participants (17) by lags (-33:+33) matrix.
+We averaged over the rows of this matrix to get a group-averaged lag-CRP.
+
+\textbf{Serial position curve (SPC).} The SPC represents the proportion of participants that remember an item as a function of its serial position during encoding.
+We initialized a \# of participants (17) by \# of video events (34) matrix.
+Then, for each recall event (and each participant), we found the index of the video event that was recalled and filled it in with a 1.
+This resulted in a matrix where 1s indicate the successful recall of an event in serial position $n$ and zeros indicate the lack of recall for that event.
+Lastly, we averaged over the rows of the matrix to get a 1 by 34 array representing the proportion of subjects that recalled an event as a function of its serial position.
 % We used a few different metrics to assess memory that were all designed to capture the relationship between the video and recall models.

### 2018-07-09 main.tex
checking in temporal and semantic clustering methods

@@
 \subsubsection{The fundamental shape of an experience is preserved in recall}
-The analyses described in the previous section are useful in that they allow us to quantify memory dynamics for naturalistic stimuli in a way that is comparable to a vast literature on list-learning.
-However, these methods (and trial-based experiments more generally) fail to capture the rich semantic and temporal structure present in naturalistic stimuli and associated recall of those experiences.
-Thus, our next set of analyses test whether the `shape' of an experience is preserved in memory.
-We hypothesized that despite substantial individual variability in the precision and amount of content recalled across by participants, the overall shape of the episode would be recapitulated by all.
+The analyses described in the previous section are useful in that they allow us to quantify memory dynamics for naturalistic stimuli in a way that is comparable to a vast literature on trial-based list-learning experiments.
+However, these methods fail to capture the rich temporal structure present in naturalistic stimuli and associated recall of those experiences.
+Thus, our next set of analyses test whether the ``shape'' of an experience is preserved in memory.
+We hypothesized that despite substantial individual variability in the precision and amount of content recalled across by participants, the overall shape of the episode would be recapitulated by the majority of participants.
 
@@
 Lastly, we averaged over the rows of the matrix to get a 1 by 34 array representing the proportion of subjects that recalled an event as a function of its serial position.
+
+\textbf{Temporal clustering.} Temporal clustering measures the extent to which participants group their recall responses according to encoding position.
+For instance, if the participant recalled each item in the presentation order, this would result in a score of 1.
+If the participant recalled randomly with respect to presentation order, this would result in a score of ~.5.
+For each event transition (and separately for each participant), we computed the rank similarity (euclidean distance) between the presentation position  of the current and next recall events.
+The scores were then averaged within participant to get a single number representing the extent of temporal clustering exhibited by a given participant.
+
+\textbf{Semantic clustering.} Similar to temporal clustering, semantic clustering measures the extent to which participants group their recall responses according to semantic similarity.
+Here, we are using the topic vectors for each event as a proxy for its semantic content.
+Thus, similarity between the semantic content for two events can be computed by correlating their respective topic vectors.
+For instance, if each consecutive recall was the next most similar event (in terms of its s), this would result in a score of ~1.
+If the participant recalled randomly with respect to semantic similarity, this would result in a score of ~.5.
+For each event transition (and separately for each participant), we computed the rank similarity (correlation distance) between the current recall event and the next recall event.
+The scores were then averaged within participant to get a single number representing the extent of semantic clustering exhibited by a given participant.
+
 % We used a few different metrics to assess memory that were all designed to capture the relationship between the video and recall models.

### 2018-07-12 main.tex
checking in vector field methods

@@
 
-\subsubsection{Naturalistic extensions of classic list-learning memory analyses}
+\subsubsection{Characterizing naturalistic memory with traditional list-learning analyses}
 Just like in a traditional `free-recall' list-learning experiment where participants view a list of words and then verbally recall them, our video-recall matching analysis approach affords us the ability to analyze memory in the same way.
@@
 
+ \subsubsection{Measuring the quality of naturalistic memories}
+ Representing the video and verbal recall as events in `topic space' also affords us the ability to characterize the quality of recall in a more fine-grained and nuanced way than what was previously possible.
+To quantify the similarity between the video model and individual recall models, we considered a number of novel metrics.
+First, we tested whether each participant's recall model matched the movie model in a general sense.
+To do this, for each participant we filtered the video model to only include the events that the participant remembered.
+Then, we computed the root mean squared difference (RMSD) between the video model and the recall model.
+As an example, if the participant remembered all the events in order (with perfect precision), the expected distance value would be 0.
+However, if they remembered a subset of events, events our of order or with low precision the expected distance would be greater than 0.
+To assess significance, we performed a permutation test where we circularly shifted the recall model (10000 times) and recomputed the RMSD.
+The recall model significantly matched the video model for nine of the participants ($p$<.05; participants: 3-4, 8-13, 17 and the p-value for the rest of the participants was less than .25).
+Furthermore, the RMSD values were significantly correlated to memory performance across participants (Pearson's $r$(16)=-.57, $p$=.016).
+Thus, a closer match between the video and recall event models was related to better recall performance.
+
+ Next, we tested whether participants who recalled more events were also more precise in their recollections.
+For each participant, we computed the correlation between each recall event and its matching video event (only for the events which they recalled).
+This resulted in a single number for each recalled event indexing how similar the recall event was to its matching movie event (i.e the `precision' of the recall).
+We then averaged the correlations within participant.
+In line with our prediction, there was a strong correlation between memory performance and precision suggesting that participants who remembered more events also remembered them more veridically (Pearson's $r$(16)=.74, p=.0006).
+Next, we considered the distinctiveness of each recall event.
+That is, how uniquely a recall event matched a given video event compared to all other video events.
+We hypothesized that participants with high memory performance might describe each event in a more distinctive way (relative to those with lower memory performance who might describe events in a more general way).
+To this end, we computed a `distinctiveness' score for each participant (i.e.
+1 - the correlation between a recall event and all non-matching video events).
+Then, we averaged this measure over recall events within participant.
+We found that participants with higher memory performance also had higher distinctiveness scores (Pearson's $r$(16)=.8, p=.0001).
+
+ Lastly, we tested whether participants with better memory performance were also more likely to remember the events in order.
+For each participant, we computed the Spearman rank correlation between the order of events that the participant recalled and the actual order of events (filtering events that were actually recalled).
+We found that participants who recalled more events also recalled more of them in order (Pearson's $r$(16)=.5, p=.04).
+In summary, we found that better memory performance was associated with more precise and distinctive recall.
+
 \subsubsection{The fundamental shape of an experience is preserved in recall}
-The analyses described in the previous section are useful in that they allow us to quantify memory dynamics for naturalistic stimuli in a way that is comparable to a vast literature on trial-based list-learning experiments.
+The analyses described in the previous sections are useful in that they allow us to quantify memory dynamics for naturalistic stimuli in a way that is comparable to a vast literature on trial-based list-learning experiments.
 However, these methods fail to capture the rich temporal structure present in naturalistic stimuli and associated recall of those experiences.
@@
 The colors refer to the most similar video events.
-The lines connecting the points represent the average probability of transitioning from one event to the other.
-The opacity of the line is proportional to the transition probability (0 to 1).
-Arrows indicate the transition with the highest probability for each event.}
+The directional lines connecting the points represent the true video event order.
+The arrows represent the average direction of all recall event transitions (i.e.
+a line segment connecting two consecutive recall event vectors) that intersected a box (width=.25) centered on the origin of the arrow.
 \label{fig:trajectory}
@@
 Notably, the text in the wordles is distinct across the hinge-points, but but similar between video and recall within hinge-point.
-
-\subsubsection{Measuring the quality of recall}
-Representing the video and verbal recall as events in `topic space' also affords us the ability to characterize the quality of recall in a more fine-grained and nuanced way than what was previously possible.
-To quantify the similarity between the video model and individual recall models, we considered a number of novel metrics.
-First, we tested whether each participant's recall model matched the movie model in a general sense.
-To do this, for each participant we filtered the video model to only include the events that the participant remembered.
-Then, we computed the root mean squared difference (RMSD) between the video model and the recall model.
-As an example, if the participant remembered all the events in order (with perfect precision), the expected distance value would be 0.
-However, if they remembered a subset of events, events our of order or with low precision the expected distance would be greater than 0.
-To assess significance, we performed a permutation test where we circularly shifted the recall model (10000 times) and recomputed the RMSD.
-The recall model significantly matched the video model for nine of the participants ($p$<.05; participants: 3-4, 8-13, 17 and the p-value for the rest of the participants was less than .25).
-Furthermore, the RMSD values were significantly correlated to memory performance across participants (Pearson's $r$(16)=-.57, $p$=.016).
-Thus, a closer match between the video and recall event models was related to better recall performance.
-
-Next, we tested whether participants who recalled more events were also more precise in their recollections.
-For each participant, we computed the correlation between each recall event and its matching video event (only for the events which they recalled).
-This resulted in a single number for each recalled event indexing how similar the recall event was to its matching movie event (i.e the `precision' of the recall).
-We then averaged the correlations within participant.
-In line with our prediction, there was a strong correlation between memory performance and precision suggesting that participants who remembered more events also remembered them more veridically (Pearson's $r$(16)=.74, p=.0006).
-Next, we considered the distinctiveness of each recall event.
-That is, how uniquely a recall event matched a given video event compared to all other video events.
-We hypothesized that participants with high memory performance might describe each event in a more distinctive way (relative to those with lower memory performance who might describe events in a more general way).
-To this end, we computed a `distinctiveness' score for each participant (i.e.
-1 - the correlation between a recall event and all non-matching video events).
-Then, we averaged this measure over recall events within participant.
-We found that participants with higher memory performance also had higher distinctiveness scores (Pearson's $r$(16)=.8, p=.0001).
-
-Lastly, we tested whether participants with better memory performance were also more likely to remember the events in order.
-For each participant, we computed the Spearman rank correlation between the order of events that the participant recalled and the actual order of events (filtering events that were actually recalled).
-We found that participants who recalled more events also recalled more of them in order (Pearson's $r$(16)=.5, p=.04).
-In summary, we found that better memory performance was associated with more precise and distinctive recall.
 
@@
 %
-\subsubsection{Characterizing memory performance using classic analyses.}
+\subsubsection{Characterizing memory performance using traditional approaches.}
 
@@
 
+\subsubsection{Visualizing the video and recall event models.}
+
+To better understand the temporal structure of the video event model (34 events by 100 topics) and the recall event models (8-27 events by 100 topics), we used a technique called UMAP to reduce the ``topic-space'' from 100 dimensions down to 2 dimensions (REF).
+UMAP is a nonlinear dimensionality reduction technique which models the manifold of the data with a fuzzy topological structure, and then searches for a (2D) projection of the data that has the closest equivalent fuzzy topological structure.
+We concatenated (vertically stacked) all event models (video, average recall, and individual recall), and then fit and transformed all of the models at once.
+This assured that the models were projected into the same space.
+
+\subsubsection{Vector field analysis.}
+To quantify (and visualize) the flow of recall from event to event, we performed a vector field analysis.
+We tiled the 2D topic space (x, y: -6 to 6 by .25) with an evenly spaced grid.
+For each grid point, we drew a square around the point (height/width=.5).
+Then, we tested whether any line segments (formed by event recall transitions) passed through this area of the topic space.
+For example, say that a participant transitioned from recalling event 2 to event 3.
+These 2 recall events correspond to 2 points in topic space, and connecting them forms a line segment.
+We collected all line segments that passed through a given section of topic space (collapsing across participants).
+To plot the average direction of the line segments (i.e.
+the arrows for each grid point in ~\ref{fig:trajectory}b), we converted each of them to unit vectors and then averaged.
+For grid points where the direction was consistent (across all participants contributing to that point), the length of the arrow approaches 1, whereas if the direction was random the length of the arrow approaches 0.
+Lastly, we converted each unit vector to an angle (in radians) by taking the inverse tangent of the x, y components of the vector.
+To test whether the distribution of angles was significantly non-uniform (i.e.
+displayed a preferred direction across participants), we performed a Rayleigh test on the angles (REF).
+Arrows where the Rayleigh test was significant are displayed in color while non-significant tests are displayed in gray with lower opacity.
+
 % We used a few different metrics to assess memory that were all designed to capture the relationship between the video and recall models.

### 2018-07-13 main.tex
added line segment analysis to methods

@@
 %
-\subsubsection{Characterizing memory performance using traditional approaches.}
+\subsubsection{Characterizing memory performance using traditional approaches}
 
@@
 
-\subsubsection{Visualizing the video and recall event models.}
+\subsubsection{Visualizing the video and recall event models}
 
@@
 
-\subsubsection{Vector field analysis.}
+\subsubsection{Vector field analysis}
 To quantify (and visualize) the flow of recall from event to event, we performed a vector field analysis.
@@
 Arrows where the Rayleigh test was significant are displayed in color while non-significant tests are displayed in gray with lower opacity.
+Note that it was not computationally tractible to perform this analysis in the original 100 dimensional space because the number of grid points grows factorially with the number of topic dimensions.
+
+%NOTE: Potentially more stringent test?
+One idea I had was for each grid point, find the number of line segments that passed through it, and then randomly sample that number from all line segments to build a null distribution for that point.
+Compute p value from this distribution.
+
+\subsubsection{Line segment analysis}
+This analysis tested whether recall dynamics across participants could be explained by a smaller number of consecutive line segments.
+To test this idea, we ran an analysis similar to a piecewise linear regression, with a few additional constraints.
+First, the endpoints of the line segments were constrained to the average recall event coordinates.
+Second, we did not consider solutions with neighboring events (i.e.
+there must be at least 1 event between line segments).
+This greatly reduced the search space, making the analysis computationally tractable.
+Third, we considered models with different numbers of line segments (2-15).
+To fit the model, we randomly split participants into 2 groups (i.e.
+training and test).
+For the training group, we (exhaustively) searched for $n$ consecutive line segments (from 2-15) that best explained the recall data.
+The cost function was given by the grand average euclidean distance of each participant's recall events to the closest line segment in the model.
+Then, the test group was also fit to this model.
+We repeated this procedure 100 times, randomly splitting the participants on each iteration.
+We chose $n$ (i.e.
+the number of line segments) by selecting the value with the lowest test error.
+Finally, we refit the model including all subjects to give the line segment model that best explained the data.
 

### 2018-07-13 main.tex
topic vector word clouds

@@
 
+\subsubsection{Topic vector word clouds}
+ We created word clouds to visualize the themes contained in the ``hinge-point'' recall events of the model.
+One component of the topic model comprises a words (???) by topics (100) matrix (R), where the rows represent the weighting of a given word on each topic.
+Each event (video and recall) was associated with a 1 by 100 topic vector (v) representing the mixture of topics contained in the event.
+To find words associated with a given event, we computed the dot product between R and v, which gave a 1 by # of words vector where the values represent the `activation' of each of in the event.
+We normalized these vectors by subtracting the average `activation' across all events.
+We performed this analysis for each of the line segment model `hinge-points' (i.e.
+the average recall events connecting the line segments).
+We also performed this analysis for the video events at the hinge-point locations.
+Finally, we created word clouds by extracting the top 100 words and plotting them where the size of the word is proportional to its `activation' in the event.
+
 % We used a few different metrics to assess memory that were all designed to capture the relationship between the video and recall models.

### 2018-07-13 main.tex
fixed some typos

@@
 The result was a sentences (range: 68 to 294, mean: 131.94) by topics (100) matrix for each participant, where each row represents a probabalistic mixture of topics for a given window of sentences during recall.
-An example participant's (#13) recall model is plotted in Fig.~\ref{fig:model}c.
+An example participant's (\#13) recall model is plotted in Fig.~\ref{fig:model}c.
 Like the video model, topic vectors were sparse and changed gradually.
@@
 The arrows represent the average direction of all recall event transitions (i.e.
-a line segment connecting two consecutive recall event vectors) that intersected a box (width=.25) centered on the origin of the arrow.
+a line segment connecting two consecutive recall event vectors) that intersected a box (width=.25) centered on the origin of the arrow.}
 \label{fig:trajectory}
@@
 Each event (video and recall) was associated with a 1 by 100 topic vector (v) representing the mixture of topics contained in the event.
-To find words associated with a given event, we computed the dot product between R and v, which gave a 1 by # of words vector where the values represent the `activation' of each of in the event.
+To find words associated with a given event, we computed the dot product between R and v, which gave a 1 by \# of words vector where the values represent the `activation' of each of in the event.
 We normalized these vectors by subtracting the average `activation' across all events.

### 2018-07-16 main.tex
added corrmats supp fig

@@
 An example participant's (\#13) correlation matrix is plotted in Fig.~\ref{fig:model}d).
-Like the video model, each participant's recall correlation matrix exhibited a strong block-diagonal structure (Supp Fig X).
+Like the video model, each participant's recall correlation matrix exhibited a strong block-diagonal structure (Supp Fig.~\ref{fig:corrmats}).
 Notably, this suggests that participants recounted the video in discriminable segments, potentially indexing the recall of specific events from the video.
@@
 \bibliography{memlab}
+
+% Supplemental materials
+
+\begin{figure}[t!]
+\centering
+\includegraphics[width=1\textwidth]{figs/supp1_corrmats.pdf}
+\caption{\small \textbf{Recall model correlation matrices and event segmentation fits.} Each participant's timepoint-by-timepoint recall correlation matrix.
+The yellow boxes represent ``events'' identified by a hidden Markov model.}
+\label{fig:corrmats}
+\end{figure}
+
 \end{document}

### 2018-07-16 main.tex
ind embeddings supp fig

@@
 To visualize the relationship between the video and recall event models, we embedded the video and average recall models into a 2D space (using the UMAP dimensionality reduction algorithm, for details see \ref{sec:methods}) where the points represent video/recall events and the distance between them represents their similarity in ``topic space'' (Fig.~\ref{fig:trajectory}a).
-(Note that all analyses are performed in the original 100 dimensional space.) We computed the group average transition probabilities from each event to each other event and plotted the values as lines where the tranparency is proportional to the probability of the transition (Fig.~\ref{fig:trajectory}b).
+(Note that all analyses are performed in the original 100 dimensional space.) We computed the group average transition probabilities from each event to each other event and plotted the values as lines where the tranparency is proportional to the probability of the transition (Fig.~\ref{fig:trajectory}b, see Supp Fig.~\ref{fig:ind_embeddings} for individual participant plots).
 We observed that the two models have a very similar temporal evolution and geometric structure, and the transition probabilities tend to be strongest between events that occured sequentially (or nearby) in time.
@@
 
+\begin{figure}[t!]
+\centering
+\includegraphics[width=1\textwidth]{figs/supp2_projs.pdf}
+\caption{\small \textbf{Individual participant recall event model embeddings.} Each participant's recall event model embedded into a 2D space using the UMAP algorithm.
+The arrows on the lines connecting the recall events represents the direction of the sequence of recalls.
+The color of the dots represent the most likely (i.e.
+most correlated) video event.
+The dark black line represents the best fitting line segment model (same for each participant).}
+\label{fig:ind_embeddings}
+\end{figure}
+
 \end{document}

### 2018-07-16 main.tex
added paragraph to experimental procedures

@@
 \subsection{Participants and Experimental Design}
-How much detail here? or just point to janice's paper?
+Participants ($n$=17) viewed \textit{A Study in Pink}, a 50 minute episode of the BBC series, \textit{Sherlock}.
+Immediately upon completion of the video, participants were instructed to (verbally) recount the events in the video in their original order and in as much detail as possible.
+During the entire experiment, participants were in an fMRI scanner.
+However, only the behavioral data (e.g.
+the recall transcripts) were used in this paper.
+For comprehensive details of the experimental procedures, please refer to \cite{ChenEtal17}.
 
@@
 
-% We used a few different metrics to assess memory that were all designed to capture the relationship between the video and recall models.
-First, to get a general sense for the match between the video and recall matrices, we vectorized the the matrices and correlated them.
-This resulted in a single number representing how well a given participant recalled the video.
-To get a temporally dynamic measure of memory, for each participant we computed the pairwise correlation between matching video/recall timepoints.
-This allowed us to assess memory for individual moments of the video.
-Finally to get a more nuanced representation of memory for the video, we computed a video/recall model correlation matrix for each participant.
-These timepoint (1976) by timepoint (1976) matrices represent the correlation between every moment of the video model and every moment of the recall model.
-To provide some intuition, if a participant recalled every scene at the same rate and in exactly the same order as the video, we would expect high correlation values along the diagonal of this matrix.
-However, if a participant recalls the scenes out of order, or at different rates for different scenes, this will result in high values off the diagonal.
-%
-% The only additional constraint we imposed was that there was at least 2 points between each line segment.
-% We searched for the optimal number of line segments by iteratively splitting the participants into two groups, fitting the model to the first half and testing the model on the remaining subjects.
-To compute fit to the model, for each recall event (a 1 by 100 topics vector) we computed the nearest line segment and then calculated the mean squared distance averaging over all events and all participants (in the sample).
-We repeated this 20 times using 1-10
-%
-% \subsubsection{Bridging between the stimulus and recall}
-% The participants in this study were instructed to recall as much of the episode as they could in the order it happened.
-Thus, we hypothesized that the recall models should resemble the video model to the extent that participants followed these instructions and had reasonably good memory accuracy.
-To test whether this was true, we correlated each moment of the video model with each moment of each participants' resampled recall model.
-We then averaged these matrices together to get a single group averaged matrix.
-The result was a viewing time (1976) by recall time (1976) correlation matrix representing the average relationship between every moment of the movie and recall models (Fig.~\ref{fig:model}e).
-Notably, we observe significant correlation values (p<.05, permutation test described in \ref{sec:methods}) primarily along the diagonal, suggesting that our model captures the fact that participants recalled the episode in order.
-We also visualized this effect by projecting the matrices into a 3D space (reduced using Spectral Embedding [cite]) where the proximity of the trajectories at every timepoint represents how similar the topic vectors were.
-Visualizing the data in this way makes it clear that the overall shape and correlational structure of the video and average recall matrices is quite similar.
-
 \bibliography{memlab}

### 2018-07-16 main.tex
more work on intro

@@
 % \title{Capturing the geometric structure of our experiences and how we remember them}
-\title{The fundamental shape of dynamic experiences is preserved in episodic memory}
+% \title{The fundamental shape of naturalistic experiences is preserved in episodic memory}
+\title{Memory dynamics for naturalistic experiences}
 \author{Andrew C. Heusser \& Jeremy R. Manning}
@@
 
-A defining feature of naturalistic experiences is the temporal structure with which they unfold.
-Our experiences in the real world are typically autocorrelated in space and time on short timescales.
-In other words, the contents of an experience are often similar from moment to moment and change gradually.
+Human memory studies typically assess memory for the individual contents of an experience, such as the people, places and things/items encountered.
+However, real life experiences can also be described in terms of their temporal structure (i.e.
+how the contents relate over time).
+Naturalistic experiences are typically autocorrelated in space and time on short timescales: the contents of an experience are often similar from moment to moment and change gradually.
 For example, many of us spend our mornings/evenings at home and much of our days at work (e.g.
 an office).
-While the specific happenings within these contexts differs, they are (usually) highly correlated and predictable over time.
+While the specific happenings within these contexts differ, they are often highly correlated (and thus predictable) over time.
 Furthermore, our experiences can also be characterized by longer timescale correlations.
 For example, consider returning to your office after taking a lunch break.
-The perceptual contexts before and after lunch are highly similar, but separated in time.
-However, these recurrent and gradually changing temporal dynamics are not typically present in traditional memory studies, but are likely important if we wish to understand how our memory systems remember our everyday experiences.
+The spatial contexts before and after lunch are highly similar, but separated in time.
+Thus, while evaluating the ability to recall specific contents of an experience is one way to assess memory, another important dimension to consider is the temporal structure of the remembered experience, and how the temporal structure of the memory relates to the original experience.
+However, these recurrent and gradually changing temporal dynamics are not typically present in traditional memory studies, but are likely critical if we wish to understand how our memory systems remember our life experiences.
 
-Despite the continuous and (often) gradually changing nature of naturalistic experiences, prior research suggests that our memories for those same experiences may be more descrete and centered around particular ``events'' \citep{Radv12, RadvZack11, BrunEtal18}.
-Short timescale autocorrelations in the contents of an experience may cause information to become associatively linked in memory (and thus treated as a single event), while sharp changes (i.e.
-``event boundaries'') may segment continuous experiences into events \citep{HeusEtal18, BrunEtal18, Radv12}.
+Despite the continuous and (often) gradually changing nature of naturalistic experiences, prior research suggests that our memories for those same experiences may be more descrete and organized around particular ``events'' \citep{Radv12, RadvZack11, BrunEtal18}.
+Short timescale autocorrelations in the contents of an experience are thought associatively link information in memory, while more drastic changes in perceptual or semantic aspects of an experience (i.e.
+``event boundaries'') may lead to discontinuous in memory \citep{HeusEtal18, BrunEtal18, Radv12}.
 There is now compelling evidence that event boundaries can influence memory organization when learning sequences of items \citep{HeusEtal18, DuBrDava13}, during navigation \citep{BrunEtal18}, and narrative comprehension \citep{ZwaaRadv98, EzzyDava11}.
-Furthermore, brain activity while viewing naturalistic stimuli displays a block-diagonal structure, and the neurally-derived segments are correlated with judgements of event boundaries \citep{BaldEtal17}.
-However, whether people naturally recount their experiences in as events has not been explored.
+However, whether people naturally recount their experiences in a way that is structured around events is not known.
 
-% We propose that variability in the contents of an experience over time define a ``stimulus-space''.
-In this space, timepoints where the contents of experience are more similar are represented as points that are closer together.
-Timepoints with relatively more distinct content are represented further apart.
-The moment-by-moment flow of content through this space can be represented as a ``stimulus trajectory''.
-%
-% As a consequence of this structure, we hypothesized that verbally recounted memories for those experiences would mirror this shape.
-
-To study the temporal and semantic aspects of memories for naturalistic experiences, we analyzed an open dataset in which participants view and then verbally recall an episode of the BBC series \textit{Sherlock}  \citep{ChenEtal17}.
-We Furthermore, we hypothesized that the stimulus To test these hypotheses, we developed a novel computational approach based on topic modeling \citep{BleiEtal03} and hidden Markov models \citep{Rabi89, BaldEtal17} to capture the temporal structure present in naturalistic experiences.
-We then use this model to characterize the shape of the stimulus as well as verbally recalled memories.
+In this study, we analyzed an open dataset in which participants view and then verbally recount an episode of the BBC series \textit{Sherlock} \citep{ChenEtal17}.
+To capture the temporal structure present in naturalistic experiences, we developed a novel computational approach based on topic modeling \citep{BleiEtal03} and hidden Markov models \citep{Rabi89, BaldEtal17}.
+We propose that the temporal structure of an experience gives it a unique geometric ``shape'' or ``trajectory'', defined by how the contents of the experience relate and change over time.
+We hypothesized that when recounting naturalistic experiences, the precise details that are recapitulated and language used may differ across people, but the trajectory of the stimulus is generally preserved.
 

### 2018-07-16 main.tex
new abstract

@@
 The human memory system is adept at cataloging the rich dynamics of ongoing experience.
+A hallmark feature of human experiences is that they unfold in a structured and predictable manner, governed by the laws of the physical systems that produce them.
+However, this temporal structure is typically absent (or severly impoverished) in traditional trial-based memory experiments.
+As a consequence, our understanding of how the inherent temporal structure of our life experiences influences memorability and memory organization is limited.
+Using a novel computational modelling approach, we investigate how people verbally recall continuous videos by characterizing and relating the thematic dynamics, or ``trajectories,'' of the stimulus and participants' recalls.
+We found that despite large differences in the quantity of information recalled across participants, the overall shape of the stimulus was recapitulated by most of the participants.
+These findings provide a window into which aspects of naturalistic experiences must be preserved, and which might be more flexible, in considering whether and how those experiences are remembered.
+
+% The human memory system is adept at cataloging the rich dynamics of ongoing experience.
 However, traditional trial-based memory experiments cannot capture these dynamics, and therefore cannot be used to study them.

### 2018-07-16 main.tex
removed old lineseg figure

@@
 
-% \title{Capturing the geometric structure of our experiences and how we remember them}
+\title{Capturing the geometric structure of our experiences and how we remember them}
 % \title{The fundamental shape of naturalistic experiences is preserved in episodic memory}
-\title{Memory dynamics for naturalistic experiences}
+% \title{Memory dynamics for naturalistic experiences}
 \author{Andrew C. Heusser \& Jeremy R. Manning}
@@
 
+% I realize this sticks out and needs to be better integrate into the narrative, but not sure how!
 Despite the continuous and (often) gradually changing nature of naturalistic experiences, prior research suggests that our memories for those same experiences may be more descrete and organized around particular ``events'' \citep{Radv12, RadvZack11, BrunEtal18}.
@@
 
+\section{Discussion}
+\label{sec:discussion}
+
++ novel way to quantify naturalistic experiences and memories
++ opens the door to studies of how various manipulations (or simply the passage of time) might lead to changes in the structure of naturalistic memories
++ other potential applications - quantifying learning from educational videos, memory assessment/diagnosis of memory disorders and other psychiatric disorders
+
 \section{Methods}

### 2018-07-23 boneyard.tex
checking in after brain figure

@@
 Our everyday experiences feel ``important'' to us, whereas the words we study on a random word list do not.
+
+To test the observation that participants' recall trajectories generally matched the shape of the video trajectory, we fit participants' recall data to a model comprised of $n$ line segments that were connected by a subset of the average recall event coordinates.
+We fixed the endpoints of the model at the average first and last recall event, but fit the placement/length of rest of the line segments to the data.
+Using a cross-validated model fitting procedure (see ~\ref{sec:methods} for details), we searched for the optimal number of line segments.
+The best fitting model (12 line segments) can be seen in Fig.~\ref{fig:linesegs}.
+This model represents the set of consecutive line segments that best describe all participants recall event models.
+Notably, the optimal model comprises a subset of the total recall events (~roughly 1/3).
+% include a measure of the variance described by the model?
+
+We hypothesized that the points connecting the line segments (referred to as ``hinge-points'') represent critical scenes in the storyline.
+To visualize the semantic content of each hinge-point, we created wordles from the average topic vectors for each video event (left side), where the size of the word is proportional to its ``activation'' in the video event relative to other video events (Fig.~\ref{fig:linesegs}, see ~\ref{sec:methods} for analysis details).
+We performed the same analysis for the average recall topic vectors (right side).
+Notably, the text in the wordles is distinct across the hinge-points, but but similar between video and recall within hinge-point.
+
+\subsubsection{Line segment analysis}
+This analysis tested whether recall dynamics across participants could be explained by a smaller number of consecutive line segments.
+To test this idea, we ran an analysis similar to a piecewise linear regression, with a few additional constraints.
+First, the endpoints of the line segments were constrained to the average recall event coordinates.
+Second, we did not consider solutions with neighboring events (i.e.
+there must be at least 1 event between line segments).
+This greatly reduced the search space, making the analysis computationally tractable.
+Third, we considered models with different numbers of line segments (2-15).
+To fit the model, we randomly split participants into 2 groups (i.e.
+training and test).
+For the training group, we (exhaustively) searched for $n$ consecutive line segments (from 2-15) that best explained the recall data.
+The cost function was given by the grand average euclidean distance of each participant's recall events to the closest line segment in the model.
+Then, the test group was also fit to this model.
+We repeated this procedure 100 times, randomly splitting the participants on each iteration.
+We chose $n$ (i.e.
+the number of line segments) by selecting the value with the lowest test error.
+Finally, we refit the model including all subjects to give the line segment model that best explained the data.
+
+\subsubsection{Univariate subsequent memory analysis}
+To characterize brain regions involved in memory encoding, we conducted an analysis inspired by prior studies investigating the  `subsequent memory effect' (Paller and Wagner).
+For each participant, we computed the correlation between topic vectors at each timepoint of the video model and recall model (they were temporally aligned with DTW and resampled to 1976 timesamples).
+The result was a 1 x 1976 vector of correlation values representing how similar each moment of the video model was to each moment of the recall model.
+Then, to compute the average correlation, we Fisher's z transformed the correlation vectors, averaged them together, and then inverse Fisher's z transformed them.
+Finally, we mean centered the vector.
+This 1 x 1976 vector represents memorable/unmemorable parts of the video, and be thought of as a `continuous' extension of a subsequent memory regressor.
+We convolved the timeseries with a double gamma function (PARAMS) to account for the hemodynamic response, and used it as a model for each voxel's activity timeseries (using FSL software).
+Finally, to aggregate across participants, we performed a mixed effects (ordinary least squares) analysis, thresholding at p<.001 and cluster correcting a p<.05.
+
+\begin{figure}[t!]
+\centering
+\includegraphics[width=1\textwidth]{figs/supp2_projs.pdf}
+\caption{\small \textbf{Individual participant recall event model embeddings.} Each participant's recall event model embedded into a 2D space using the UMAP algorithm.
+The arrows on the lines connecting the recall events represents the direction of the sequence of recalls.
+The color of the dots represent the most likely (i.e.
+most correlated) video event.
+The dark black line represents the best fitting line segment model (same for each participant).}
+\label{fig:ind_embeddings}
+\end{figure}

### 2018-07-23 main.tex
checking in after brain figure

@@
 
-\begin{figure}[t!]
+\begin{figure}[th!]
 \centering
@@
 
-\begin{figure}[th!]
+\begin{figure}[t!]
 \centering
-\includegraphics[width=1\textwidth]{figs/5_linesegs.pdf}
+\includegraphics[width=1\textwidth]{figs/5_topics.pdf}
 \caption{\small \textbf{Recall shape analysis and video/recall content.} A 2-dimensional embedding of the best fitting line segment model.
@@
 The word clouds for hinge-point (left: video; right: recall) were created by plotting the top 100 words from topic model that were ``activated'' during a particular event.}
-\label{fig:linesegs}
+\label{fig:topics}
 \end{figure}
 
-To test the observation that participants' recall trajectories generally matched the shape of the video trajectory, we fit participants' recall data to a model comprised of $n$ line segments that were connected by a subset of the average recall event coordinates.
-We fixed the endpoints of the model at the average first and last recall event, but fit the placement/length of rest of the line segments to the data.
-Using a cross-validated model fitting procedure (see ~\ref{sec:methods} for details), we searched for the optimal number of line segments.
-The best fitting model (12 line segments) can be seen in Fig.~\ref{fig:linesegs}.
-This model represents the set of consecutive line segments that best describe all participants recall event models.
-Notably, the optimal model comprises a subset of the total recall events (~roughly 1/3).
-% include a measure of the variance described by the model?
-
-We hypothesized that the points connecting the line segments (referred to as ``hinge-points'') represent critical scenes in the storyline.
-To visualize the semantic content of each hinge-point, we created wordles from the average topic vectors for each video event (left side), where the size of the word is proportional to its ``activation'' in the video event relative to other video events (Fig.~\ref{fig:linesegs}, see ~\ref{sec:methods} for analysis details).
-We performed the same analysis for the average recall topic vectors (right side).
-Notably, the text in the wordles is distinct across the hinge-points, but but similar between video and recall within hinge-point.
+\begin{figure}[]
+\centering
+\includegraphics[width=1\textwidth]{figs/6_brains.pdf}
+\caption{\small \textbf{Recall model searchlight analysis.} A 2-dimensional embedding of the best fitting line segment model.
+The points outlined in black represent and connected by black line segments represent the critical recall events (or ``hinge-points'') of the best fitting model colored according to their matching video event.
+The points not outlined in black are individual participant recall event topic vectors colored by the most similar video event.
+The kernel density plot represents the distribution across all points.
+The word clouds for hinge-point (left: video; right: recall) were created by plotting the top 100 words from topic model that were ``activated'' during a particular event.}
+\label{fig:topics}
+\end{figure}
 
@@
 
-\subsubsection{Line segment analysis}
-This analysis tested whether recall dynamics across participants could be explained by a smaller number of consecutive line segments.
-To test this idea, we ran an analysis similar to a piecewise linear regression, with a few additional constraints.
-First, the endpoints of the line segments were constrained to the average recall event coordinates.
-Second, we did not consider solutions with neighboring events (i.e.
-there must be at least 1 event between line segments).
-This greatly reduced the search space, making the analysis computationally tractable.
-Third, we considered models with different numbers of line segments (2-15).
-To fit the model, we randomly split participants into 2 groups (i.e.
-training and test).
-For the training group, we (exhaustively) searched for $n$ consecutive line segments (from 2-15) that best explained the recall data.
-The cost function was given by the grand average euclidean distance of each participant's recall events to the closest line segment in the model.
-Then, the test group was also fit to this model.
-We repeated this procedure 100 times, randomly splitting the participants on each iteration.
-We chose $n$ (i.e.
-the number of line segments) by selecting the value with the lowest test error.
-Finally, we refit the model including all subjects to give the line segment model that best explained the data.
+\subsubsection{Topic vector word clouds}
+ We created word clouds to visualize the themes contained in the recall events.
+One component of the topic model comprises a words (XX) by topics (100) matrix (R), where the rows represent the weight of a given word in each topic.
+To find words that were maximally associated with a particular event vector, we computed the dot product between R and v, which gave a 1 by \# of words vector where the values represent the `activation' of each of in the event.
+Then, we created word clouds by extracting the top $n$ words and plotting them where the size of the word is proportional to its `activation' in the event.
 
-\subsubsection{Topic vector word clouds}
- We created word clouds to visualize the themes contained in the ``hinge-point'' recall events of the model.
-One component of the topic model comprises a words (???) by topics (100) matrix (R), where the rows represent the weighting of a given word on each topic.
-Each event (video and recall) was associated with a 1 by 100 topic vector (v) representing the mixture of topics contained in the event.
-To find words associated with a given event, we computed the dot product between R and v, which gave a 1 by \# of words vector where the values represent the `activation' of each of in the event.
-We normalized these vectors by subtracting the average `activation' across all events.
-We performed this analysis for each of the line segment model `hinge-points' (i.e.
-the average recall events connecting the line segments).
-We also performed this analysis for the video events at the hinge-point locations.
-Finally, we created word clouds by extracting the top 100 words and plotting them where the size of the word is proportional to its `activation' in the event.
+In the first analysis (Fig.~\ref{fig:topics}a/b), we quantified the most and least remembered topics/words throughout the entire video by computing a weighted average over all recall events, where the weights were proportional to memory for each recall event.
+To measure memory for each event, for each participant we computed the correlation between the video event vector and the closest recall event vector.
+We then averaged these correlation values across participants.
+We then computed a weighted average of all video events using the correlation values as weights.
+Next, we computed the dot product between this weighted-average video event vector and the R matrix (described in the paragraph above) to get ``activations'' for each word.
+Finally, we plotted the top 200 words where the size of the word is proportional to its ``activation''.
+To get the least remembered topics/words, we performed the same analysis but inverted memory weights.
+
+In the second analysis (Fig.~\ref{fig:topics}c), we created wordles for the top/bottom 3 remembered video events indexed by the average correlation values (Fig.~\ref{fig:topics}a).
+To get the ``activations'' for words associated with the video events, we computed the dot product between the video event vector and the R matrix.
+The same procedure was used to get word activations for the recall events.
+We then plotted the top 200 words for the top/bottom 3 recalled events.
+
+ \subsection{fMRI analyses}
+ Seventeen participants watched the first 50 minutes of Episode 1 of BBC's Sherlock.
+The video was split into two parts of approximately equal length (946 and 1030 TRs).
+All data were preprocessed and transformed to 3mm MNI space as described in the paper.
+Data were zscored across time at every voxel.
+6mm smoothing was applied.
+ Files are cropped so that all video-viewing data are aligned across participants, and all recall data are aligned to the scene timestamps below.
+The cropping includes a constant 3-TR (4.5 sec) shift to correct for hemodynamic lag.
+
+ \subsubsection{Searchlight analysis}
+ Our multivariate analyses were designed to capture brain regions whose timepoint-by-timepoint correlational structure mirrors the correlational structure of the participant-specific recall topic models during video viewing.
+To correct for non-linearities between the viewing time and recall time, for each participant we used DTW to temporally align the matrices.
+The algorithm recovers a path of coordinates that would bring the video and recall model in maximal temporal alignment.
+We used this path to warp the fMRI data and the recall model into temporal alignment (separately for each participant).
+Then, we conducted a searchlight analysis (5x5x5 voxel cube) where for each cube, we correlated the model timepoint-by-timepoint correlation matrix with the neural correlation matrix.
+To aggregate across participants, we Fisher's z-transformed the correlations and then averaged.
+To assess significance, we recomputed this group analysis 100 times, but randomly phase shifted the model (by \# of timepoints - 1) by the same amount for each participant but different amounts for each permutation to build a null distribution of correlation values.
+Finally, we thresholded the group averaged correlation maps where the `real' correlation value for a given voxel exceeded the 95th percentile of the null distribution.
 
@@
 
-\begin{figure}[t!]
-\centering
-\includegraphics[width=1\textwidth]{figs/supp2_projs.pdf}
-\caption{\small \textbf{Individual participant recall event model embeddings.} Each participant's recall event model embedded into a 2D space using the UMAP algorithm.
-The arrows on the lines connecting the recall events represents the direction of the sequence of recalls.
-The color of the dots represent the most likely (i.e.
-most correlated) video event.
-The dark black line represents the best fitting line segment model (same for each participant).}
-\label{fig:ind_embeddings}
-\end{figure}
-
 \end{document}

### 2018-07-23 main.tex
brain plot figure legend

@@
 \includegraphics[width=1\textwidth]{figs/6_brains.pdf}
-\caption{\small \textbf{Recall model searchlight analysis.} A 2-dimensional embedding of the best fitting line segment model.
-The points outlined in black represent and connected by black line segments represent the critical recall events (or ``hinge-points'') of the best fitting model colored according to their matching video event.
-The points not outlined in black are individual participant recall event topic vectors colored by the most similar video event.
-The kernel density plot represents the distribution across all points.
-The word clouds for hinge-point (left: video; right: recall) were created by plotting the top 100 words from topic model that were ``activated'' during a particular event.}
+\caption{\small \textbf{Recall model searchlight analysis.} A).
+We used dynamic time warping to separately align each participant's recall model to the video model.
+The left matrix is S13's video-recall correlation matrix before warping.
+The yellow stars represent the path recovered by dynamic time warping.
+The right matrix is the result after warping.
+The same warping path was applied to the fMRI timeseries (separately for each participant).
+Below the matrices are toy examples representing a vectorized (aligned) recall correlation matrix and a vectorized (aligned) fMRI searchlight correlation matrix.
+These vectors were correlated for each searchlight sphere in the brain to assess brain regions whose temporal correlation structure mirrored the participant's recall model correlation structure.
+B) A surface plot of brain regions whose activity patterns mirrored the participant-specific recall correlation matrix.
+Significance threshold (p<.05) derived from a permutation procedure by phase shifting the video model and recomputing the z-scores.}
 \label{fig:topics}

### 2018-07-24 main.tex
added text to results

@@
 To visualize the relationship between the video and recall event models, we embedded the video and average recall models into a 2D space (using the UMAP dimensionality reduction algorithm, for details see \ref{sec:methods}) where the points represent video/recall events and the distance between them represents their similarity in ``topic space'' (Fig.~\ref{fig:trajectory}a).
-(Note that all analyses are performed in the original 100 dimensional space.) We computed the group average transition probabilities from each event to each other event and plotted the values as lines where the tranparency is proportional to the probability of the transition (Fig.~\ref{fig:trajectory}b, see Supp Fig.~\ref{fig:ind_embeddings} for individual participant plots).
-We observed that the two models have a very similar temporal evolution and geometric structure, and the transition probabilities tend to be strongest between events that occured sequentially (or nearby) in time.
+We observed that the two models have a very similar temporal evolution and geometric structure.
+To further quantify this correspondence and to characterize how participants navigated through the space during recall, we analyzed the angle between successive recall events.
+We created a grid of evenly spaced points (.25 units) in the 2D ``topic space''.
+For each point on the grid, we drew a circle (radius=.25) around the point and grouped together all recall transitions that intersected the circle (across subjects).
+To visualize the average angle, we converted each transition angle to a unit vector and then averaged the vectors together.
+To assess consistency in the direction of the recall transition across participants, we performed a Rayleigh test (p<.001, corrected at p<.05 using permutation procedure described in \ref{sec:methods}).
+We found that on average, participants' recalls flowed along the same path as the video model (Fig.~\ref{fig:trajectory}b).
+Each participant's recall path can be seen in Fig.~\ref{fig:trajectory}c.
+
+Notably, many of the participants' recall trajectories appear to recover the overall shape of the video stimulus.
+To quantify this similarity, we measured the average euclidean distance between each each segment of the video model (e.g.
+the line formed by successive video events) and the closest recall event for each participant.
+Inuitively, if the participant approximately remembered every video event, the measure would approach 0.
+The more missing recall events, the higher the value.
+We found that this shape measure was highly correlated to the number of events remembered across participants (Pearson's $r$(16)=-.87, p$<$.001).
+While these measures are highly correlated (as might be expected), there are cases where the measures dissociate.
+For example participant X and X recalled exactly the same number of events, but the shape measure is drastically different between them.
+Conversely, participant X and X had the same shape measure, but there was a large difference in the number of events recalled.
+Thus, measuring similarity in shape between the video and recall models provides unique information about participant's recall behavior that is not captured by classic measures of memory accuracy.
 
@@
 
+\subsubsection{Brain regions that mirror the correlational structure of memory}
+
 \begin{figure}[]
@@
 \includegraphics[width=1\textwidth]{figs/6_brains.pdf}
-\caption{\small \textbf{Recall model searchlight analysis.} A).
+\caption{\small \textbf{Recall model correlational structure searchlight analysis.} A).
 We used dynamic time warping to separately align each participant's recall model to the video model.
@@
 B) A surface plot of brain regions whose activity patterns mirrored the participant-specific recall correlation matrix.
-Significance threshold (p<.05) derived from a permutation procedure by phase shifting the video model and recomputing the z-scores.}
+Significance threshold (p$<$.05) derived from a permutation procedure by phase shifting the video model and recomputing the z-scores.}
 \label{fig:topics}

### 2018-07-24 main.tex
memorability by event and topics

@@
 
-To visualize the relationship between the video and recall event models, we embedded the video and average recall models into a 2D space (using the UMAP dimensionality reduction algorithm, for details see \ref{sec:methods}) where the points represent video/recall events and the distance between them represents their similarity in ``topic space'' (Fig.~\ref{fig:trajectory}a).
+To visualize the relationship between the video and recall event models, we embedded them into a 2D space (using the UMAP dimensionality reduction algorithm, for details see \ref{sec:methods}) where the points represent video/recall events and the distance between them represents their similarity in ``topic space'' (Fig.~\ref{fig:trajectory}a).
 We observed that the two models have a very similar temporal evolution and geometric structure.
@@
 
-\begin{figure}[t!]
+\subsubsection{Memorability by event and topics}
+Another advantage of representing naturalistic stimuli/memory using this approach is that the event models can be mapped back to the language used to fit the model(s).
+In this next analysis, we 1) quantified the memorability of each video event and 2) used memorability to plot the top words for the most and least memorable scenes, and across the entire video.
+
+To measure video event memorability, we computed the correlational distance between each video event and the closest recall event and then averaged those values within participant.
+We used this measure of memory to create a weighted average over all video events, where video events with better memory were weighted more heavily.
+Then, we extracted the top 200 words and created ``wordles'' from the most memorable scenes of the video (see Methods for details).
+The result reveal that scenes containing "Sherlock" and "John" are highly memorable, and also "medium", "street" and "baker" (Fig.~\ref{fig:topics}b).
+To find words related to the least memorable scenes, we inverted the "memorability" weights and extracted the top 200 words.
+Scenes containing "Mike" and "Molly" were least remembered, and also words like "conference", "hospital" and "psychotherapist" (Fig.~\ref{fig:topics}b).
+
+Then, we took a closer look at the themes contained in the top/bottom 3 events.
+We used the "memorability" weights described above to select the top/bottom events.
+We performed the same analysis as described above, but separately for the video event and average recall event vectors representing each of the top/bottom 3 remembered events.
+In Figure~\ref{fig:topics}c, the trajectory represents a low-dimensional embedding of the video model and the large colored dots represent the video events.
+Each of the smaller colored dots represents the distribution of individual recall events over participants, colored by the closest video event.
+
+\begin{figure}[t!h]
 \centering
 \includegraphics[width=1\textwidth]{figs/5_topics.pdf}
-\caption{\small \textbf{Recall shape analysis and video/recall content.} A 2-dimensional embedding of the best fitting line segment model.
+\caption{\small \textbf{Topic vector memorability.} A 2-dimensional embedding of the best fitting line segment model.
 The points outlined in black represent and connected by black line segments represent the critical recall events (or ``hinge-points'') of the best fitting model colored according to their matching video event.

### 2018-07-24 main.tex
checking in last topic model para

@@
 Then, we took a closer look at the themes contained in the top/bottom 3 events.
-We used the "memorability" weights described above to select the top/bottom events.
+We used the "memorability" weights to select the top/bottom events.
 We performed the same analysis as described above, but separately for the video event and average recall event vectors representing each of the top/bottom 3 remembered events.
 In Figure~\ref{fig:topics}c, the trajectory represents a low-dimensional embedding of the video model and the large colored dots represent the video events.
-Each of the smaller colored dots represents the distribution of individual recall events over participants, colored by the closest video event.
+The smaller colored dots represent the distribution of individual recall events across all participants, colored by the closest video event.
+We plotted wordles for the top 3 (circled in green) and bottom 3 (red) most/least remembered events, where the video is represented in the left half of the circle and the average recall is represented in the right half of the circle.
+Visual inspection reveals that the words contained in the memorability weighted worldles (Fig.~\ref{fig:topics}b) overlap with the individual top/bottom event wordles (Fig.~\ref{fig:topics}c).
+These analyses uncover the contents of naturalistic stimuli and accompanying memories, and highlight the flexibility in transforming between human and machine readable representations of the data afforded by our modeling approach.
 

### 2018-07-24 main.tex
topic figure legend

@@
 
-\begin{figure}[t!h]
+\begin{figure}[t!]
 \centering
 \includegraphics[width=1\textwidth]{figs/5_topics.pdf}
-\caption{\small \textbf{Topic vector memorability.} A 2-dimensional embedding of the best fitting line segment model.
-The points outlined in black represent and connected by black line segments represent the critical recall events (or ``hinge-points'') of the best fitting model colored according to their matching video event.
-The points not outlined in black are individual participant recall event topic vectors colored by the most similar video event.
-The kernel density plot represents the distribution across all points.
-The word clouds for hinge-point (left: video; right: recall) were created by plotting the top 100 words from topic model that were ``activated'' during a particular event.}
+\caption{\small \textbf{Analysis of topics by event memorability.} A).
+Group-averaged correlation between each video event and closest recall event (per subject).
+Error bars represent 95\% confidence intervals.
+B).
+Wordles (top 200 words) representing a weighted average of video event topic vectors weighted by event memorability (e.g.
+the correlation values in A).
+The top wordle (green) contains words from the most remembered events and the bottom (red) contains words from least memorable events.
+The word sizes are proportional to the word's ``activation''.
+C).
+Trajectory represents the video event model embedded in a 2D space using UMAP.
+The large colored dots are video events.
+The small colored dots are all individual recall events across all participants, where the colors refer to the closest video event.
+The circular wordles represent the top 3 most (green circles) and least (red) memorable video events.
+The left side of the wordle circles contain words associated with the video event vector and the right side contains words associated with the average recall event vector.}
 \label{fig:topics}
@@
 
-\begin{figure}[]
+\begin{figure}[t!]
 \centering
@@
 Significance threshold (p$<$.05) derived from a permutation procedure by phase shifting the video model and recomputing the z-scores.}
-\label{fig:topics}
+\label{fig:brainz}
 \end{figure}

### 2018-07-24 main.tex
checking in work

@@
 
-\subsubsection{Brain regions that mirror the correlational structure of memory}
+\subsubsection{Brain regions that mirror the correlational structure of naturalistic memories}.
+While each participant remembered roughly the same sequence of events, there were subtle idiosyncracies in the way each individual described the events.
+For example, the event by event similarity structure (e.g.
+the off-diagonal values of the recall correlation matrices) differed by individual (Supp.
+Fig.~\ref{fig:corrmats}).
+In the final analysis, we identified brain areas whose responses at the time of viewing exhibited the same (segmented) idiosyncratic dynamics that later appeared in that participants’ recalls.
+
+The amount of time/number of sentences used describing each scene differed drastically between participants and as compared to the original video \cite{ChenEtal17}.
+This makes it challenging to use the recall model directly to examine neural activity patterns during video viewing.
+To account for these temporal non-linearities between the video and recall, we used dynamic time warping to align each participant's recall model and the movie model (DTW ref).
+We used the resulting path warp each voxel's timeseries as well as the recall model timeseries.
+Then using a searchlight procedure (5mm), we computed the timepoint-by-timepoint correlation matrix over searchlight voxels.
+We vectorized the recall correlation and searchlight correlation.
 

### 2018-07-25 main.tex
finished brain results

@@
 The amount of time/number of sentences used describing each scene differed drastically between participants and as compared to the original video \cite{ChenEtal17}.
-This makes it challenging to use the recall model directly to examine neural activity patterns during video viewing.
 To account for these temporal non-linearities between the video and recall, we used dynamic time warping to align each participant's recall model and the movie model (DTW ref).
-We used the resulting path warp each voxel's timeseries as well as the recall model timeseries.
-Then using a searchlight procedure (5mm), we computed the timepoint-by-timepoint correlation matrix over searchlight voxels.
-We vectorized the recall correlation and searchlight correlation.
+We used the resulting alignment path to warp the fMRI timeseries (for each voxel) as well as the recall model timeseries.
+Then using a searchlight procedure (5mm), we computed the timepoint-by-timepoint neural correlation matrix within each searchlight.
+To measure the similarity between the neural and behavioral correlation matrices, we vectorized and then correlated them.
+The result was a correlation value for each voxel representing the extent to which the brain data mirrored the recall data.
+Finally, to test the significance of the correlation values, we phase shifted the recall models (100 permuations) and recomputed the correlation values.
+Significance was determined by ``real'' correlation values that exceeded the 95th percentile of this null distribution.
+The resulting map suggests that the correlational structure of a network of brain regions including the ventromedial prefrontal cortex, anterior cingulate, and right medial temporal lobe mirror the idiosyncratic structure of participants'' recalls.
 

### 2018-07-25 main.tex
intro and results edits

@@
 The human memory system is adept at cataloging the rich dynamics of ongoing experience.
-A hallmark feature of human experiences is that they unfold in a structured and predictable manner, governed by the laws of the physical systems that produce them.
+A defining feature of our experiences is that they unfold in a structured and predictable manner, governed by the laws of the physical systems that produce them.
 However, this temporal structure is typically absent (or severly impoverished) in traditional trial-based memory experiments.
@@
 
-Human memory studies typically assess memory for the individual contents of an experience, such as the people, places and things/items encountered.
+Human memory studies typically assess memory for the ``items'' within an experience, such as the people, places and things encountered.
 However, real life experiences can also be described in terms of their temporal structure (i.e.
-how the contents relate over time).
+how the contents relate/change over time).
 Naturalistic experiences are typically autocorrelated in space and time on short timescales: the contents of an experience are often similar from moment to moment and change gradually.
@@
 \subsubsection{A model to capture the temporal and semantic structure of naturalistic stimuli}
-We fit a topic model \citep{BleiEtal03} to (manually annotated) text descriptions of scenes from the video.
+We fit a topic model \citep{BleiEtal03} to hand-annotated text descriptions of scenes from the video.
 The text descriptions contained details of the scene such as the characters, location, and a short summary of the scene (see Fig.\ref{fig:schematic} for example text, see \ref{sec:methods} for analysis details).
-We then transformed the text descriptions using the (same) topic model, resulting in a scenes (1976) by topics (100) matrix, where each row of the matrix represents a probabalistic mixture of topics discovered in that scene (See Fig.\ref{fig:schematic} for example topic vectors).
+We then transformed the text descriptions using the (same) topic model, resulting in a scenes (1976) by topics (100) matrix, where each row of the matrix represents a probabalistic mixture of topics discovered in that scene (See Fig.~\ref{fig:schematic} for example topic vectors).
 As depicted in Fig.~\ref{fig:model}a, the topic vectors are sparse and change slowly over time.
 Furthermore, there are clear transitions from one topic `state' to the next, possibly indexing scene transitions in the stimulus.
-To get a better handle on this temporal structure, we computed a timepoint (1976) by timepoint (1976) correlation matrix of the video model (Fig.~\ref{fig:model}c).
+To get a better handle on this temporal structure, we computed a timepoints (1976) by timepoints (1976) correlation matrix of the video model (Fig.~\ref{fig:model}c).
 This correlation matrix reveals that the model has a strong, block-diagonal structure.
@@
 The result was a sentences (range: 68 to 294, mean: 131.94) by topics (100) matrix for each participant, where each row represents a probabalistic mixture of topics for a given window of sentences during recall.
-An example participant's (\#13) recall model is plotted in Fig.~\ref{fig:model}c.
+An example participant's (\#13) recall model is plotted in Fig.~\ref{fig:model}b.
 Like the video model, topic vectors were sparse and changed gradually.
 Note that the topics were derived solely from the text descriptions of the video, and so the topic models estimated for recall are dependent on the topics present in the video.
-This approach effectively projects the participants' verbal recall into the video's `topic space'', allowing us to directly compare them to the video model.
+This approach effectively projects the participants' verbal recall into the video's ``topic space'', allowing us to directly compare them to the video model.
 
 Next, we investigated the temporal structure of the recall matrices.
-For each participant, we computed a timepoint (68 to 294) by timepoint (68 to 294) correlation matrix from the recall models.
+For each participant, we computed a timepoint (68 to 294) by timepoints by timepoints (range: 68 to 294) correlation matrix from the recall models.
 An example participant's (\#13) correlation matrix is plotted in Fig.~\ref{fig:model}d).
-Like the video model, each participant's recall correlation matrix exhibited a strong block-diagonal structure (Supp Fig.~\ref{fig:corrmats}).
-Notably, this suggests that participants recounted the video in discriminable segments, potentially indexing the recall of specific events from the video.
+Like the video model, each participants' recall correlation matrix exhibited a strong block-diagonal structure (Supp Fig.
+1).
+Notably, this suggests that participants recounted the video in discriminable segments, potentially related to the recall of specific events (or scenes) from the video.
 
 \subsubsection{Segmenting the video and recall models into `events'}
-As described above, a striking feature of the video and recall correlation matrices (see Fig.~\ref{fig:model}) is a strong, block structure along the diagonal of the matrices.
+As described above, a striking feature of the video and recall correlation matrices is a strong, block structure along the diagonal of the matrices (see Fig.~\ref{fig:model}c,d).
 We hypothesized that this structure might arise from transient stability in the contents of the video (i.e.
@@
 To test this idea, first we segmented the video and recall models in $k$ events (i.e.
-states) using a hidden Markov model (~\citep{BaldEtal17}).
-The algorithm determined 34 events for the video model and a range of values (range: 8-27; mean: 15.41; SD: 5.6) for the recall models (see ~\ref{sec:methods} for details on choosing an optimal $k$ value).
+states) using a hidden Markov model ~\citep{BaldEtal17}.
+Our algorithm determined 34 events for the video model and a range of values (range: 8-27; mean: 15.41; SD: 5.6) for the recall models (see Methods for details on choosing an optimal $k$ value).
 The events discovered for the model and a representative participant (\#13) are highlighted as yellow rectangles outlining blocks along the diagonal of the correlation matrices (Fig.~\ref{fig:model}b,d).
 
-Next, we created a video event model by averaging together neighboring topic vectors that the were classified to be in the same event, resulting in an events (34) by topics (100) matrix (Fig.~\ref{fig:model}e).
+Next, we created a video ``event model by'' averaging together neighboring topic vectors that the were classified to be in the same event, resulting in an events (34) by topics (100) matrix (Fig.~\ref{fig:model}e).
 We performed the same procedure for the recall matrices (see Fig.~\ref{fig:model}f for example).
-Then, we computed the correlation between video and recall event models, resulting in a video events (34) by recall events (8-27, depending on the participant) correlation matrix (Fig/~\ref{fig:model}g).
+Then, we computed the correlation between video and recall event models, resulting in a video events (34) by recall events (8-27, depending on the participant) correlation matrix (Fig~\ref{fig:model}g).
 These matrices represent the similarity (correlation) between each video event and each recall event (for each participant).
@@
 This is depicted in Fig.~\ref{fig:model}g as the cells highlighted with a yellow border.
-Interestingly, our algorithm suggests that the example participant recalled the events largely in order, occasionally skipping a video event.
+Interestingly, our algorithm suggests that the example participant recalled most of the video events in order.
 
 Then, we computed a group-averaged recall event model and video-recall event correlation matrix.
-For each participant (and each recall event), we sorted the recall event vectors (across all participants) according to the video event that they were most highly correlated to.
+For each participant (and each recall event), we sorted the recall event vectors (across all participants) according to the video event with the highest correlation.
 We then averaged the recall event vectors within each group.
@@
 \subsubsection{Characterizing naturalistic memory with traditional list-learning analyses}
-Just like in a traditional `free-recall' list-learning experiment where participants view a list of words and then verbally recall them, our video-recall matching analysis approach affords us the ability to analyze memory in the same way.
+Just like in a traditional ``free-recall'' list-learning experiment where participants view a list of words and then verbally recall them, our video-recall matching analysis approach affords us the ability to analyze memory in the same way.
 The recalled events can be treated as ``items'' analogous to words recalled in a list-learning study.
@@
 This metric quantifies the likelihood of initiating a sequence of recalls based on an item's serial position during encoding.
-We found that participants tended to initiate their recall sequences with the first few events (Fig.~\ref{fig:list-learning}a), which is qualitatively very similar to previously published list learning experiments (REF).
+We found that participants tended to initiate their recall sequences with the first few events (Fig.~\ref{fig:list-learning}a), which is qualitatively very similar to previously published list learning experiments (REF?).
 Next, we considered another well-studied memory measure in the list-learning literature, the lag conditional response probability curve (or lag-CRP) ~\citep{Kaha96}.
 Given the recall of a stimulus in study position $n$, the lag-CRP quantifies the probability that the next item recalled will be of lag $i$.
-The result suggests a strong bias to transition sequentially events in the forward direction Fig.~\ref{fig:list-learning}b.
+The result suggests a strong bias to transition sequentially events in the forward direction (Fig.~\ref{fig:list-learning}b).
 This can be seen by the high probability values in the lag ~1-5 positions compared to the rest of the transition possibilties.
-Notably, participants were instructed to recall as much as they could in order, and the shape of this lag-CRP is qualitatively similar to list-learning studies of serial recall (REF), where participants are required to recall lists of words in their serial order.
+Notably, participants were instructed to recall as much as they could in order, and the shape of this lag-CRP is qualitatively similar to list-learning studies of serial recall (REF?), where participants are required to recall lists of words in their serial order.
 Finally, we assessed memory performance for each event in the video as a function of its serial position during encoding (Fig.~\ref{fig:list-learning}c).
-We found that there was substantial variability in memory for the different events (STAT?).
-Furthermore, the shape of the curve is different than what is typically found in list learning experiments (we'll come back to this point in the dicussion).
+We found that there was substantial variability in memory for the different events (STAT).
+Furthermore, the shape of the curve is different than what is typically found in list learning experiments.
 
@@
 Temporal clustering (REF?) measures the extent to which participants tend to cluster recalls of events encoded nearby in time.
-For example, if a participant recalled in exact serial order, the score would be 1 whereas if they sequentially recalled randomly positioned items the score would be ~.5.
+For example, if a participant recalled in exact serial order, the score would be 1 whereas if they sequentially recalled randomly positioned items the score would be \~.5.
 We found that participants who clustered in time also recalled a greater number of events (Pearson's $r$(16)=.62, $p$=.007).
@@
  \subsubsection{Measuring the quality of naturalistic memories}
- Representing the video and verbal recall as events in `topic space' also affords us the ability to characterize the quality of recall in a more fine-grained and nuanced way than what was previously possible.
+ Representing the video and verbal recall as events in ``topic space'' also affords us the ability to characterize the quality of recall in a more fine-grained and nuanced way than what was previously possible.
 To quantify the similarity between the video model and individual recall models, we considered a number of novel metrics.
@@
 The recall model significantly matched the video model for nine of the participants ($p$<.05; participants: 3-4, 8-13, 17 and the p-value for the rest of the participants was less than .25).
-Furthermore, the RMSD values were significantly correlated to memory performance across participants (Pearson's $r$(16)=-.57, $p$=.016).
+Furthermore, the RMSD values were significantly correlated to hand annotated memory performance across participants (Pearson's $r$(16)=-.57, $p$=.016).
 Thus, a closer match between the video and recall event models was related to better recall performance.
@@
 For each participant, we computed the correlation between each recall event and its matching video event (only for the events which they recalled).
-This resulted in a single number for each recalled event indexing how similar the recall event was to its matching movie event (i.e the `precision' of the recall).
+This resulted in a single number for each recalled event indexing how similar the recall event was to its matching movie event (i.e the ``precision'' of the recall).
 We then averaged the correlations within participant.
-In line with our prediction, there was a strong correlation between memory performance and precision suggesting that participants who remembered more events also remembered them more veridically (Pearson's $r$(16)=.74, p=.0006).
+In line with our prediction, there was a strong correlation between hand annotated memory performance and precision suggesting that participants who remembered more events also remembered them more veridically (Pearson's $r$(16)=.74, p=.0006).
 Next, we considered the distinctiveness of each recall event.
@@
 Then, we averaged this measure over recall events within participant.
-We found that participants with higher memory performance also had higher distinctiveness scores (Pearson's $r$(16)=.8, p=.0001).
+We found that participants with higher hand annotated memory performance also had higher distinctiveness scores (Pearson's $r$(16)=.8, p=.0001).
 
@@
 We found that participants who recalled more events also recalled more of them in order (Pearson's $r$(16)=.5, p=.04).
-In summary, we found that better memory performance was associated with more precise and distinctive recall.
+In summary, we found that better memory performance was associated with more precise, distinctive and ordered recalls.
 
-\subsubsection{The fundamental shape of an experience is preserved in recall}
+\subsubsection{The shape of a naturalistic experience is preserved in recall}
 The analyses described in the previous sections are useful in that they allow us to quantify memory dynamics for naturalistic stimuli in a way that is comparable to a vast literature on trial-based list-learning experiments.
+Furthermore, we introduce novel measures (precision and distinctiveness) which provide additional details regarding the veracity of naturalistic memories.
 However, these methods fail to capture the rich temporal structure present in naturalistic stimuli and associated recall of those experiences.
@@
 To visualize the average angle, we converted each transition angle to a unit vector and then averaged the vectors together.
-To assess consistency in the direction of the recall transition across participants, we performed a Rayleigh test (p<.001, corrected at p<.05 using permutation procedure described in \ref{sec:methods}).
-We found that on average, participants' recalls flowed along the same path as the video model (Fig.~\ref{fig:trajectory}b).
-Each participant's recall path can be seen in Fig.~\ref{fig:trajectory}c.
+To assess consistency in the direction of the recall transition across participants, we performed a Rayleigh test (p$<$.001, corrected at p$<$.05 using permutation procedure described in Methods).Thus participants' recalls followed the same path as the video model (Fig.~\ref{fig:trajectory}b), suggesting the shape of the stimulus was preserved despite idiosyncratic differences between participants in their recalls.
 
@@
 \subsubsection{Memorability by event and topics}
-Another advantage of representing naturalistic stimuli/memory using this approach is that the event models can be mapped back to the language used to fit the model(s).
-In this next analysis, we 1) quantified the memorability of each video event and 2) used memorability to plot the top words for the most and least memorable scenes, and across the entire video.
+A noteworthy advantage of representing naturalistic stimuli/memory using this approach is that the event models can be mapped back to the language used to fit the model(s).
+This allows for analysis and visualization of the language used when participant's recounted their experiences.
+In this next analysis, we 1) quantified the memorability of each video event and 2) used memorability to plot the top words for the most and least memorable scenes, and also aggregated across the entire video.
 
-To measure video event memorability, we computed the correlational distance between each video event and the closest recall event and then averaged those values within participant.
-We used this measure of memory to create a weighted average over all video events, where video events with better memory were weighted more heavily.
-Then, we extracted the top 200 words and created ``wordles'' from the most memorable scenes of the video (see Methods for details).
-The result reveal that scenes containing "Sherlock" and "John" are highly memorable, and also "medium", "street" and "baker" (Fig.~\ref{fig:topics}b).
-To find words related to the least memorable scenes, we inverted the "memorability" weights and extracted the top 200 words.
-Scenes containing "Mike" and "Molly" were least remembered, and also words like "conference", "hospital" and "psychotherapist" (Fig.~\ref{fig:topics}b).
+To measure video event memorability, we computed the correlation between each video event and the closest recall event and then averaged those values within participant (Fig.~\ref{fig:topics}a).
+We used event memorability to create a weighted average over all video event vectors, where video events with better memory were weighted more heavily.
+Then, we extracted the top 200 words and created ``wordles'' representing the most memorable themes in the video.
+The result reveal that scenes containing ``Sherlock'' and ``John'' were highly memorable, and also scenes containing words such as ``medium'', ``street'' and ``baker'' (Fig.~\ref{fig:topics}b).
+To find words related to the least memorable scenes, we inverted the memorability weights and again extracted the top 200 words.
+Scenes containing ``Mike'' and ``Molly'' were least remembered, and also words like ``conference'', ``hospital'' and ``psychotherapist'' (Fig.~\ref{fig:topics}b).
 
-Then, we took a closer look at the themes contained in the top/bottom 3 events.
-We used the "memorability" weights to select the top/bottom events.
-We performed the same analysis as described above, but separately for the video event and average recall event vectors representing each of the top/bottom 3 remembered events.
+Then, we took a closer look at the themes contained in the top/bottom 3 events, using the memorability weights to select the top/bottom events.
+We performed the same analysis as described above, but separately for the video and average recall event vectors representing each of the top/bottom 3 remembered events.
 In Figure~\ref{fig:topics}c, the trajectory represents a low-dimensional embedding of the video model and the large colored dots represent the video events.
@@
 Visual inspection reveals that the words contained in the memorability weighted worldles (Fig.~\ref{fig:topics}b) overlap with the individual top/bottom event wordles (Fig.~\ref{fig:topics}c).
-These analyses uncover the contents of naturalistic stimuli and accompanying memories, and highlight the flexibility in transforming between human and machine readable representations of the data afforded by our modeling approach.
+These analyses shed light on the contents of naturalistic stimuli and accompanying memories, and highlight the flexibility in transforming between human and machine readable representations of the data afforded by our modeling approach.
 
@@
 For example, the event by event similarity structure (e.g.
-the off-diagonal values of the recall correlation matrices) differed by individual (Supp.
+the off-diagonal values of the recall correlation matrices) differed across individuals (Supp.
 Fig.~\ref{fig:corrmats}).
-In the final analysis, we identified brain areas whose responses at the time of viewing exhibited the same (segmented) idiosyncratic dynamics that later appeared in that participants’ recalls.
+We hypothesized that idiosyncracies in the recall dynamics across subjects might be related to the temporal structure of brain networks are representing the events during video viewing.
+Thus in the last analysis, we identified brain areas whose responses at the time of viewing exhibited the same (segmented) idiosyncratic dynamics that later appeared in that participants’ recalls.
 
 The amount of time/number of sentences used describing each scene differed drastically between participants and as compared to the original video \cite{ChenEtal17}.
-To account for these temporal non-linearities between the video and recall, we used dynamic time warping to align each participant's recall model and the movie model (DTW ref).
+To account for these temporal non-linearities between the video and recall, we used dynamic time warping to align each participant's recall model and the movie model (DTW REF).
 We used the resulting alignment path to warp the fMRI timeseries (for each voxel) as well as the recall model timeseries.

### 2018-07-25 main.tex
methods edits

@@
 During the entire experiment, participants were in an fMRI scanner.
-However, only the behavioral data (e.g.
-the recall transcripts) were used in this paper.
 For comprehensive details of the experimental procedures, please refer to \cite{ChenEtal17}.
+%NOTE: is this sufficient or should i provide more detail?
 
@@
 This gave a word count vector for each scene in the video.
-Then, the word count vectors were used to fit a topic model (\# of topics=100, method=batch).
+Then, the word count vectors were used to fit a topic model (topics=100, method=batch).
 We transformed the text descriptions using the model resulting in a scenes (1000) by topics (100) matrix.
@@
 The result of this was a sentences (range: 68-294) by topics (100) matrix for each participant that represented the most likely mixture of topics for a given chunk of sentences.
+
+\subsubsection{Choosing topic model parameters}
+There were 3 critical parameters related to fitting the topic model: 1) the number of topics, 2) the window size of text descriptions of the video used to fit the model, and 3) the window size of recall sentences used to transform the recall data.
+To chose these parameter values, we performed a grid search where the range of possible parameter values was 1, 5, 10, 25, 50, 100, 200, and 500.
+Our optimization objective was defined as the correlation between the hand annotated memory performance and the root mean squared distance between the video model and the recall model before any further processing (e.g.
+hidden Markov modelling, averaging within event, etc).
+While many of the parameter combination elicited moderately high correlations, the best choice was 100 topics, 50 video segments and 10 recall sentences.
 
@@
 Then, using the best $k$ values, We fit a separate HMM for each topic model.
-Finally, we averaged over timepoints identified to be in the same event resulting in a $k$ events by 100 topics matrix for the video model and each of the recall models.
+Finally, we averaged over timepoints identified to be in the same event resulting in a events by topics matrix for the video model and each of the recall models.
 %
@@
 
-%NOTE: Potentially more stringent test?
-One idea I had was for each grid point, find the number of line segments that passed through it, and then randomly sample that number from all line segments to build a null distribution for that point.
-Compute p value from this distribution.
-
 \subsubsection{Topic vector word clouds}

### 2018-08-16 paper/main.tex
started discussion

--- 2018-07-25 main.tex
@@
 The human memory system is adept at cataloging the rich dynamics of ongoing experience.
-A defining feature of our experiences is that they unfold in a structured and predictable manner, governed by the laws of the physical systems that produce them.
+A defining feature of our everyday experiences is that they unfold in a structured and predictable manner, governed by the laws of the physical systems that produce them.
 However, this temporal structure is typically absent (or severly impoverished) in traditional trial-based memory experiments.
-As a consequence, our understanding of how the inherent temporal structure of our life experiences influences memorability and memory organization is limited.
-Using a novel computational modelling approach, we investigate how people verbally recall continuous videos by characterizing and relating the thematic dynamics, or ``trajectories,'' of the stimulus and participants' recalls.
-We found that despite large differences in the quantity of information recalled across participants, the overall shape of the stimulus was recapitulated by most of the participants.
+As a consequence, our understanding of how the inherent temporal structure of our experiences influences memorability and memory organization is limited.
+In this study, we investigate how people verbally recount a video by characterizing and relating the thematic dynamics, or ``trajectories,'' of the stimulus and participants' recalls.
+We found that despite large differences in the amount of information recalled across participants as well as the particular words used to describe the experience, the overall shape of the stimulus was recapitulated by most of the participants.
 These findings provide a window into which aspects of naturalistic experiences must be preserved, and which might be more flexible, in considering whether and how those experiences are remembered.
@@
 
+Studying episodic memory is commonly distilled down to a process of matching specific moments of a past experience with specific mnemonic outcomes.
+In traditional trial-based free recall and item recognition experiments, individual stimuli encountered during encoding are typically labeled as ``remembered'' or ``forgotten'' depending on whether the stimulus is recalled/recognized during a subsequent test.
+However, this approach does not translate well to naturalistic experiences.
+For one thing, the contents of our recall at any given moment might be reflected in many prior experiences/moments.
+Furthermore, the particular words used to describe the experience will inevitably vary across people and even across repeated recollections within an individual.
+Thus, there is not a ``one-to-one'' mapping between naturalistic experiences and their mnemonic counterparts.
+Our topic modeling approach, whereby we consider the broad ``theme'' present in different moments of participants' experiences and their memories for those experiences, allows us to flexibly and accurately characterize memory for naturalistic experiences.
+This allows us to quantify which moments from the past the current thoughts match, in terms of their thematic content and critically, our ability to perform this matching does not require participants to use any specific overlapping words.
+
+Historically, human memory reseachers have focussed on measuring the quantity of information recovered by an individual under different experimental conditions (i.e.
+the proportion correct).
+However, for real world experiences this is not a well-defined task.
+For example, remembering the patterns and colors of each person's shirt in a crowd might be considered as excellent recall in a standard memory task setup.
+But if the rememberer failed to note that the people in the crowd were gathered for their surprise birthday party, then they would have missed the "point" of the experience.
+Our work characterizes experience by comparing the overall ``shape'' of an experience and a memory.
+We assess the quality of memory for the movie participants viewed by measuring the match between the shapes of the movie's trajectory and each participant's recall trajectory.
+By contrast, the number of recalls could be captured by the "sampling frequency" along that trajectory-- but the number of recalls alone cannot tell us whether participants successfully recollected the meaning of the story by capturing the salient points of the narrative that define its main shape.
+
+Prior work on neural responses during naturalistic experience and recall (e.g.
+Hasson group) has largely focused on identifying brain regions whose responses are reliably similar across individuals.
+This allows one to identify which regions might be processing or representing the stimulus, or retrieving details of the experience during recall.
+Our approach is fundamentally different.
+We ask: which brain regions during movie viewing match how individual participants will recall the movie later (in terms of the temporal correlations of their recall topic trajectory)?
+This approach highlights regions such as the vmPFC that may respond in idiosyncratic ways across individuals, but that nonetheless play an important role in encoding experience into memory.
+
+More broadly, these findings have strong implications for how we assess memory in other naturalistic contexts, like the in the classroom or in a doctor's office.
+Whereas instructors often measure students' performance using metrics such as the proportion of correctly answered questions, our work suggests that this approach might miss the ``forrest for the trees''.
+True learning is about understanding the key concepts (i.e.
+understanding key themes in the learned content and how they relate) rather than about regurgitating the greatest number of facts.
+In addition to educational contexts, our approach may provide unique metrics that can be used to assist in the diagnosis of a memory disorder, and other psychiatric disorders that influence memory.
+For example, while the quantity of information recalled could be roughly matched between a healthy and patient population, other aspects of the memory (such as the shape, serial order, precision or distinctiveness) might be different.
+Thus, this work serves as a foundation for more nuanced approaches to memory assessment that consider the trajectory and specific contents of memory for a naturalistic experience.
+
+An important question for future work concerns the factors that drive an individual to sample their recall trajectory finely or coarsely.
+For example, given a short recall interval, would participants intuitively gravitate towards coarser samplings that still outline the basic shape of the movie's topic trajectory?
+Or if participants were told that their narrations would be played back to other participants (cite Hasson work), would that change the resolution or shape of their recalls?
+And over successive recountings of the same sequence of events, how do the shapes of the trajectories change?
+For example, loss of detail would result in a "smoothing our" of the trajectories with each new retelling.
+This could be quantified using our topic trajectory approach.
+
+In summary, using a novel content-based memory assessment approach,
+
 + novel way to quantify naturalistic experiences and memories

### 2018-08-16 paper/main.tex
trimmed list-learning section and moved the shape analyses up

@@
 Then, we considered how participants initiated the recall sequence (known in the literature as the `probability of first recall' or `PFR').
-This metric quantifies the likelihood of initiating a sequence of recalls based on an item's serial position during encoding.
 We found that participants tended to initiate their recall sequences with the first few events (Fig.~\ref{fig:list-learning}a), which is qualitatively very similar to previously published list learning experiments (REF?).
 Next, we considered another well-studied memory measure in the list-learning literature, the lag conditional response probability curve (or lag-CRP) ~\citep{Kaha96}.
-Given the recall of a stimulus in study position $n$, the lag-CRP quantifies the probability that the next item recalled will be of lag $i$.
 The result suggests a strong bias to transition sequentially events in the forward direction (Fig.~\ref{fig:list-learning}b).
-This can be seen by the high probability values in the lag ~1-5 positions compared to the rest of the transition possibilties.
-Notably, participants were instructed to recall as much as they could in order, and the shape of this lag-CRP is qualitatively similar to list-learning studies of serial recall (REF?), where participants are required to recall lists of words in their serial order.
 Finally, we assessed memory performance for each event in the video as a function of its serial position during encoding (Fig.~\ref{fig:list-learning}c).
 We found that there was substantial variability in memory for the different events (STAT).
-Furthermore, the shape of the curve is different than what is typically found in list learning experiments.
 
 We also considered two additional across-participant measures of recall that characterize memory organization: temporal clustering and semantic clustering.
-Temporal clustering (REF?) measures the extent to which participants tend to cluster recalls of events encoded nearby in time.
-For example, if a participant recalled in exact serial order, the score would be 1 whereas if they sequentially recalled randomly positioned items the score would be \~.5.
 We found that participants who clustered in time also recalled a greater number of events (Pearson's $r$(16)=.62, $p$=.007).
 Next, we assessed semantic clustering.
-Similar to temporal clustering, semantic clustering measures the extent to which participants cluster their responses by semantic similarity.
-We used the topic vector representations of each event as a proxy for semantic information contained in that event.
-For each transition, we computed the rank percentile of the of the correlation between the the current event and then next event.
-For example, if a participant sequentially recalled events where each successive recall was the event that was most semantically similar to the previous, the semantic clustering score would be 1.
-If the events were recalled in a random order with respect to semantic information, the clustering score would be ~.5.
 We found that the semantic clustering score was related to memory performance across participants (Pearson's $r$(16)=.55, $p$=.02).
 Thus, participants who organized their recalls with respect to the semantic information contained in the scene had better memory performance.
-
- \subsubsection{Measuring the quality of naturalistic memories}
- Representing the video and verbal recall as events in ``topic space'' also affords us the ability to characterize the quality of recall in a more fine-grained and nuanced way than what was previously possible.
-To quantify the similarity between the video model and individual recall models, we considered a number of novel metrics.
-First, we tested whether each participant's recall model matched the movie model in a general sense.
-To do this, for each participant we filtered the video model to only include the events that the participant remembered.
-Then, we computed the root mean squared difference (RMSD) between the video model and the recall model.
-As an example, if the participant remembered all the events in order (with perfect precision), the expected distance value would be 0.
-However, if they remembered a subset of events, events our of order or with low precision the expected distance would be greater than 0.
-To assess significance, we performed a permutation test where we circularly shifted the recall model (10000 times) and recomputed the RMSD.
-The recall model significantly matched the video model for nine of the participants ($p$<.05; participants: 3-4, 8-13, 17 and the p-value for the rest of the participants was less than .25).
-Furthermore, the RMSD values were significantly correlated to hand annotated memory performance across participants (Pearson's $r$(16)=-.57, $p$=.016).
-Thus, a closer match between the video and recall event models was related to better recall performance.
-
- Next, we tested whether participants who recalled more events were also more precise in their recollections.
-For each participant, we computed the correlation between each recall event and its matching video event (only for the events which they recalled).
-This resulted in a single number for each recalled event indexing how similar the recall event was to its matching movie event (i.e the ``precision'' of the recall).
-We then averaged the correlations within participant.
-In line with our prediction, there was a strong correlation between hand annotated memory performance and precision suggesting that participants who remembered more events also remembered them more veridically (Pearson's $r$(16)=.74, p=.0006).
-Next, we considered the distinctiveness of each recall event.
-That is, how uniquely a recall event matched a given video event compared to all other video events.
-We hypothesized that participants with high memory performance might describe each event in a more distinctive way (relative to those with lower memory performance who might describe events in a more general way).
-To this end, we computed a `distinctiveness' score for each participant (i.e.
-1 - the correlation between a recall event and all non-matching video events).
-Then, we averaged this measure over recall events within participant.
-We found that participants with higher hand annotated memory performance also had higher distinctiveness scores (Pearson's $r$(16)=.8, p=.0001).
-
- Lastly, we tested whether participants with better memory performance were also more likely to remember the events in order.
-For each participant, we computed the Spearman rank correlation between the order of events that the participant recalled and the actual order of events (filtering events that were actually recalled).
-We found that participants who recalled more events also recalled more of them in order (Pearson's $r$(16)=.5, p=.04).
-In summary, we found that better memory performance was associated with more precise, distinctive and ordered recalls.
 
@@
 Thus, measuring similarity in shape between the video and recall models provides unique information about participant's recall behavior that is not captured by classic measures of memory accuracy.
+
+\subsubsection{Measuring the quality of naturalistic memories}
+Representing the video and verbal recall as events in ``topic space'' also affords us the ability to characterize the quality of recall in a more fine-grained and nuanced way than what was previously possible.
+To quantify the similarity between the video model and individual recall models, we considered a number of novel metrics.
+First, we tested whether each participant's recall model matched the movie model in a general sense.
+To do this, for each participant we filtered the video model to only include the events that the participant remembered.
+Then, we computed the root mean squared difference (RMSD) between the video model and the recall model.
+As an example, if the participant remembered all the events in order (with perfect precision), the expected distance value would be 0.
+However, if they remembered a subset of events, events our of order or with low precision the expected distance would be greater than 0.
+To assess significance, we performed a permutation test where we circularly shifted the recall model (10000 times) and recomputed the RMSD.
+The recall model significantly matched the video model for nine of the participants ($p$<.05; participants: 3-4, 8-13, 17 and the p-value for the rest of the participants was less than .25).
+Furthermore, the RMSD values were significantly correlated to hand annotated memory performance across participants (Pearson's $r$(16)=-.57, $p$=.016).
+Thus, a closer match between the video and recall event models was related to better recall performance.
+
+Next, we tested whether participants who recalled more events were also more precise in their recollections.
+For each participant, we computed the correlation between each recall event and its matching video event (only for the events which they recalled).
+This resulted in a single number for each recalled event indexing how similar the recall event was to its matching movie event (i.e the ``precision'' of the recall).
+We then averaged the correlations within participant.
+In line with our prediction, there was a strong correlation between hand annotated memory performance and precision suggesting that participants who remembered more events also remembered them more veridically (Pearson's $r$(16)=.74, p=.0006).
+Next, we considered the distinctiveness of each recall event.
+That is, how uniquely a recall event matched a given video event compared to all other video events.
+We hypothesized that participants with high memory performance might describe each event in a more distinctive way (relative to those with lower memory performance who might describe events in a more general way).
+To this end, we computed a `distinctiveness' score for each participant (i.e.
+1 - the correlation between a recall event and all non-matching video events).
+Then, we averaged this measure over recall events within participant.
+We found that participants with higher hand annotated memory performance also had higher distinctiveness scores (Pearson's $r$(16)=.8, p=.0001).
+
+Lastly, we tested whether participants with better memory performance were also more likely to remember the events in order.
+For each participant, we computed the Spearman rank correlation between the order of events that the participant recalled and the actual order of events (filtering events that were actually recalled).
+We found that participants who recalled more events also recalled more of them in order (Pearson's $r$(16)=.5, p=.04).
+In summary, we found that better memory performance was associated with more precise, distinctive and ordered recalls.
 
@@
 In traditional trial-based free recall and item recognition experiments, individual stimuli encountered during encoding are typically labeled as ``remembered'' or ``forgotten'' depending on whether the stimulus is recalled/recognized during a subsequent test.
-However, this approach does not translate well to naturalistic experiences.
+While this approach has advanced our understanding of human memory immensely, it does not translate well to naturalistic experiences.
 For one thing, the contents of our recall at any given moment might be reflected in many prior experiences/moments.
@@
 Thus, there is not a ``one-to-one'' mapping between naturalistic experiences and their mnemonic counterparts.
-Our topic modeling approach, whereby we consider the broad ``theme'' present in different moments of participants' experiences and their memories for those experiences, allows us to flexibly and accurately characterize memory for naturalistic experiences.
-This allows us to quantify which moments from the past the current thoughts match, in terms of their thematic content and critically, our ability to perform this matching does not require participants to use any specific overlapping words.
+Our topic modeling approach, whereby we consider the broad ``theme'' present in different moments of participants' experiences and their memories for those experiences, affords us the ability to flexibly and accurately characterize memory for naturalistic experiences.
+This approach allows us to quantify which moments from the past and the current recounted experience match in terms of their thematic content and critically, our ability to perform this matching does not require participants to use any specific overlapping words.
 
-Historically, human memory reseachers have focussed on measuring the quantity of information recovered by an individual under different experimental conditions (i.e.
-the proportion correct).
+Historically, human memory reseachers have focussed on measuring the quantity of information recovered by an individual (i.e.
+the proportion correct) under different experimental conditions.
 However, for real world experiences this is not a well-defined task.
@@
 But if the rememberer failed to note that the people in the crowd were gathered for their surprise birthday party, then they would have missed the "point" of the experience.
-Our work characterizes experience by comparing the overall ``shape'' of an experience and a memory.
+Our work characterizes experience by comparing the overall ``shape'' of a dynamic stimulus and a memory.
 We assess the quality of memory for the movie participants viewed by measuring the match between the shapes of the movie's trajectory and each participant's recall trajectory.

### 2018-08-16 paper/main.tex
what if we shelved the fmri analysis

@@
 
-\subsubsection{Brain regions that mirror the correlational structure of naturalistic memories}.
-While each participant remembered roughly the same sequence of events, there were subtle idiosyncracies in the way each individual described the events.
+%NOTE: I'm not sure the brain stuff really fits in this paper.
+It's cool, but seems like a distraction from the main point.
+perhaps it needs it own paper with more motivation, and more extensive analyses (for example, what brain regions have temporal structure like the movie model?).
+I'm also having a hard time motivating it in the discussion, so maybe we should cut it.
+
+% \subsubsection{Brain regions that mirror the correlational structure of naturalistic memories}.
+% While each participant remembered roughly the same sequence of events, there were subtle idiosyncracies in the way each individual described the events.
 For example, the event by event similarity structure (e.g.
@@
 Thus in the last analysis, we identified brain areas whose responses at the time of viewing exhibited the same (segmented) idiosyncratic dynamics that later appeared in that participants’ recalls.
-
-The amount of time/number of sentences used describing each scene differed drastically between participants and as compared to the original video \cite{ChenEtal17}.
+%
+% The amount of time/number of sentences used describing each scene differed drastically between participants and as compared to the original video \cite{ChenEtal17}.
 To account for these temporal non-linearities between the video and recall, we used dynamic time warping to align each participant's recall model and the movie model (DTW REF).
@@
 The resulting map suggests that the correlational structure of a network of brain regions including the ventromedial prefrontal cortex, anterior cingulate, and right medial temporal lobe mirror the idiosyncratic structure of participants'' recalls.
-
-\begin{figure}[t!]
-\centering
-\includegraphics[width=1\textwidth]{figs/6_brains.pdf}
-\caption{\small \textbf{Recall model correlational structure searchlight analysis.} A).
+%
+% \begin{figure}[t!]
+% \centering
+% \includegraphics[width=1\textwidth]{figs/6_brains.pdf}
+% \caption{\small \textbf{Recall model correlational structure searchlight analysis.} A).
 We used dynamic time warping to separately align each participant's recall model to the video model.
@@
 Significance threshold (p$<$.05) derived from a permutation procedure by phase shifting the video model and recomputing the z-scores.}
-\label{fig:brainz}
-\end{figure}
+% \label{fig:brainz}
+% \end{figure}
 
@@
 
-Prior work on neural responses during naturalistic experience and recall (e.g.
+% Prior work on neural responses during naturalistic experience and recall (e.g.
 Hasson group) has largely focused on identifying brain regions whose responses are reliably similar across individuals.
@@
 This could be quantified using our topic trajectory approach.
-
-In summary, using a novel content-based memory assessment approach,
-
-+ novel way to quantify naturalistic experiences and memories
-+ opens the door to studies of how various manipulations (or simply the passage of time) might lead to changes in the structure of naturalistic memories
-+ other potential applications - quantifying learning from educational videos, memory assessment/diagnosis of memory disorders and other psychiatric disorders
 

### 2018-08-16 paper/main.tex
..
commenting out brain methods

@@
 
-\title{Capturing the geometric structure of our experiences and how we remember them}
+\title{Capturing the shape of our experiences and how we remember them}
 % \title{The fundamental shape of naturalistic experiences is preserved in episodic memory}
@@
 
- \subsection{fMRI analyses}
- Seventeen participants watched the first 50 minutes of Episode 1 of BBC's Sherlock.
+ % \subsection{fMRI analyses}
+ % Seventeen participants watched the first 50 minutes of Episode 1 of BBC's Sherlock.
 The video was split into two parts of approximately equal length (946 and 1030 TRs).
@@
 6mm smoothing was applied.
- Files are cropped so that all video-viewing data are aligned across participants, and all recall data are aligned to the scene timestamps below.
+ % Files are cropped so that all video-viewing data are aligned across participants, and all recall data are aligned to the scene timestamps below.
 The cropping includes a constant 3-TR (4.5 sec) shift to correct for hemodynamic lag.
-
- \subsubsection{Searchlight analysis}
- Our multivariate analyses were designed to capture brain regions whose timepoint-by-timepoint correlational structure mirrors the correlational structure of the participant-specific recall topic models during video viewing.
+ %
+ % \subsubsection{Searchlight analysis}
+ % Our multivariate analyses were designed to capture brain regions whose timepoint-by-timepoint correlational structure mirrors the correlational structure of the participant-specific recall topic models during video viewing.
 To correct for non-linearities between the viewing time and recall time, for each participant we used DTW to temporally align the matrices.

### 2018-08-16 paper/main.tex
moved figures to supp

@@
 % \DeclareMathOperator*{\argmax}{arg\,max}
+\usepackage{newfloat}
+\DeclareFloatingEnvironment[name={Supplementary Figure},fileext=lof]{suppfigure}
 
@@
 
-\begin{figure}[ht!]
-\centering
-\includegraphics[width=\textwidth]{figs/2_eventseg.pdf}
-\caption{\small \textbf{Modelling naturalistic stimuli and recall.} A depiction of our analysis pipeline.
-For all plots, darker colors indicate greater values and the range of each plot is 0-1.
-A).
-A timepoints (1976) by topics (100) matrix representing the video stimulus.
-Each row represents the most likely mixture of topics for a given timepoint (i.e.
-topic weights).
-Each column represents a different topic.
-B).
-A timepoints (1976) by topics (100) matrix representing participant \#13's recall.
-C).
-A viewing-time (1976) by viewing-time (1976) correlation matrix representing the correlation of each moment of the video model with every other moment of the video model.
-The white boxes represent `events' recovered by a hidden Markov model.
-D).
-A recall-time (294 sentences) by recall-time (294) correlation matrix for participant \#13.
-E).
-An events (34) by topics (100) matrix where each row represents the average topic vector for each event in the video model.
-F).
-An events (27) by topics (100) matrix where each row represents the average topic vector for each event in participant \#13's recall model.
-G.
-A recall events (27) by video events (34) correlation matrix for participant \#13.
-The cells with a yellow border identify the video event with the highest correlation to a given recall event.
-F.
-A group averaged recall events (34) by video events (34) correlation matrix.
-The cells with yellow borders are the video event with the highest correlation to a given average recall event.}
-\label{fig:model}
-\end{figure}
-
-\begin{figure}[t!]
-\centering
-\includegraphics[width=1\textwidth]{figs/3_list_learning.pdf}
-\caption{\small \textbf{Naturalistic extensions of classic list-learning memory analyses.} A).
-The probability of first recall as a function of the serial position of the event during encoding.
-B).
-A lag-conditional response probability curve.
-Given recall of event i, the probability that the next recalled item will be from serial position i +/- lag.
-C).
-Proportion of events recalled as a function of serial position.
-All error bars are the standard error of the mean derived from a bootstrap resampling procedure.}
-\label{fig:list-learning}
-\end{figure}
-
 \subsubsection{Characterizing naturalistic memory with traditional list-learning analyses}
@@
 
+\begin{figure}[t!]
+\centering
+\includegraphics[width=1\textwidth]{figs/5_topics.pdf}
+\caption{\small \textbf{Analysis of topics by event memorability.} A).
+Group-averaged correlation between each video event and closest recall event (per subject).
+Error bars represent 95\% confidence intervals.
+B).
+Wordles (top 200 words) representing a weighted average of video event topic vectors weighted by event memorability (e.g.
+the correlation values in A).
+The top wordle (green) contains words from the most remembered events and the bottom (red) contains words from least memorable events.
+The word sizes are proportional to the word's ``activation''.
+C).
+Trajectory represents the video event model embedded in a 2D space using UMAP.
+The large colored dots are video events.
+The small colored dots are all individual recall events across all participants, where the colors refer to the closest video event.
+The circular wordles represent the top 3 most (green circles) and least (red) memorable video events.
+The left side of the wordle circles contain words associated with the video event vector and the right side contains words associated with the average recall event vector.}
+\label{fig:topics}
+\end{figure}
+
 \subsubsection{Memorability by event and topics}
@@
 These analyses shed light on the contents of naturalistic stimuli and accompanying memories, and highlight the flexibility in transforming between human and machine readable representations of the data afforded by our modeling approach.
-
-\begin{figure}[t!]
-\centering
-\includegraphics[width=1\textwidth]{figs/5_topics.pdf}
-\caption{\small \textbf{Analysis of topics by event memorability.} A).
-Group-averaged correlation between each video event and closest recall event (per subject).
-Error bars represent 95\% confidence intervals.
-B).
-Wordles (top 200 words) representing a weighted average of video event topic vectors weighted by event memorability (e.g.
-the correlation values in A).
-The top wordle (green) contains words from the most remembered events and the bottom (red) contains words from least memorable events.
-The word sizes are proportional to the word's ``activation''.
-C).
-Trajectory represents the video event model embedded in a 2D space using UMAP.
-The large colored dots are video events.
-The small colored dots are all individual recall events across all participants, where the colors refer to the closest video event.
-The circular wordles represent the top 3 most (green circles) and least (red) memorable video events.
-The left side of the wordle circles contain words associated with the video event vector and the right side contains words associated with the average recall event vector.}
-\label{fig:topics}
-\end{figure}
 
@@
 This could be quantified using our topic trajectory approach.
+
+To conclude, let's revisit the question of what it means to remember something.
+We assert that episodic memories are not veridical snapshots from the past, and so we should stop treating (and modelling) them as such.
+Rather, episodic memories are better described as echoes of a prior experience that are shaped by other past experiences as well as the current context.
+Furthermore
 
@@
 
-\begin{figure}[t!]
+\begin{suppfigure}[ht!]
 \centering
-\includegraphics[width=1\textwidth]{figs/supp1_corrmats.pdf}
+\includegraphics[width=\textwidth]{figs/supp1_eventseg.pdf}
+\caption{\small \textbf{Modelling naturalistic stimuli and recall.} A depiction of our analysis pipeline.
+For all plots, darker colors indicate greater values and the range of each plot is 0-1.
+A).
+A timepoints (1976) by topics (100) matrix representing the video stimulus.
+Each row represents the most likely mixture of topics for a given timepoint (i.e.
+topic weights).
+Each column represents a different topic.
+B).
+A timepoints (1976) by topics (100) matrix representing participant \#13's recall.
+C).
+A viewing-time (1976) by viewing-time (1976) correlation matrix representing the correlation of each moment of the video model with every other moment of the video model.
+The white boxes represent `events' recovered by a hidden Markov model.
+D).
+A recall-time (294 sentences) by recall-time (294) correlation matrix for participant \#13.
+E).
+An events (34) by topics (100) matrix where each row represents the average topic vector for each event in the video model.
+F).
+An events (27) by topics (100) matrix where each row represents the average topic vector for each event in participant \#13's recall model.
+G.
+A recall events (27) by video events (34) correlation matrix for participant \#13.
+The cells with a yellow border identify the video event with the highest correlation to a given recall event.
+F.
+A group averaged recall events (34) by video events (34) correlation matrix.
+The cells with yellow borders are the video event with the highest correlation to a given average recall event.}
+\label{fig:model}
+\end{suppfigure}
+
+\begin{suppfigure}[t!]
+\centering
+\includegraphics[width=1\textwidth]{figs/supp2_corrmats.pdf}
 \caption{\small \textbf{Recall model correlation matrices and event segmentation fits.} Each participant's timepoint-by-timepoint recall correlation matrix.
@@
 \label{fig:corrmats}
-\end{figure}
+\end{suppfigure}
+
+\begin{suppfigure}[t!]
+\centering
+\includegraphics[width=1\textwidth]{figs/supp3_list_learning.pdf}
+\caption{\small \textbf{Naturalistic extensions of classic list-learning memory analyses.} A).
+The probability of first recall as a function of the serial position of the event during encoding.
+B).
+A lag-conditional response probability curve.
+Given recall of event i, the probability that the next recalled item will be from serial position i +/- lag.
+C).
+Proportion of events recalled as a function of serial position.
+All error bars are the standard error of the mean derived from a bootstrap resampling procedure.}
+\label{fig:list-learning}
+\end{suppfigure}
 

### 2018-08-17 paper/main.tex
saving progress
more paper reorganization

@@
 \title{Capturing the shape of our experiences and how we remember them}
-% \title{The fundamental shape of naturalistic experiences is preserved in episodic memory}
-% \title{Memory dynamics for naturalistic experiences}
 \author{Andrew C. Heusser \& Jeremy R. Manning}
@@
 However, this temporal structure is typically absent (or severly impoverished) in traditional trial-based memory experiments.
-As a consequence, our understanding of how the inherent temporal structure of our experiences influences memorability and memory organization is limited.
+As a consequence, our understanding of how the temporal structure (i.e.
+the shape) of our experiences influences memorability and memory organization is limited.
 In this study, we investigate how people verbally recount a video by characterizing and relating the thematic dynamics, or ``trajectories,'' of the stimulus and participants' recalls.
-We found that despite large differences in the amount of information recalled across participants as well as the particular words used to describe the experience, the overall shape of the stimulus was recapitulated by most of the participants.
-These findings provide a window into which aspects of naturalistic experiences must be preserved, and which might be more flexible, in considering whether and how those experiences are remembered.
-
-% The human memory system is adept at cataloging the rich dynamics of ongoing experience.
-However, traditional trial-based memory experiments cannot capture these dynamics, and therefore cannot be used to study them.
-By constraining participants' experiences in an experiment to occur in temporally discrete trials (and often arranged in a randomized order) the temporal, contextual, and emotional structure of those in-lab experiences necessarily differ from the naturalistic experiences we encounter in everyday life.
-Here we investigate how people verbally recall continuous videos by characterizing and relating the thematic dynamics, or ``trajectories,'' of the stimulus and participants' recalls.
-Unlike trial-based studies of memory wherein participants attempt to recall the precise stimuli they encounter, naturalistic recall entails capturing the fundamental geometric components of the stimulus topic trajectory.
-The precise words participants use to describe the stimulus, and the level of detail and number of distinct events they recall, vary considerably across participants.
-Nevertheless, the majority of participants' recall narratives captured the fundamental ``shape'' of the original stimulus.
+Using a novel approach based on topic modelling, we found that despite substantial variability in the quantity of information recalled across participants as well as the particular words used to describe the experience, the overall shape of the stimulus was recapitulated by most of the participants.
 These findings provide a window into which aspects of naturalistic experiences must be preserved, and which might be more flexible, in considering whether and how those experiences are remembered.
@@
 More nuanced studies might incorporate self-reported confidence measures as a proxy for memory strength, or ask participants to discriminate between ``recollecting'' an experience or a feeling of ``familiarity'' \citep{Yone02}.
-However, characterizing and evaluating memory in more realistic contexts (e.g., telling a story to a friend about a recent vacation) is much more nuanced.
+However, characterizing and evaluating memory in more realistic contexts (e.g., telling a story to a friend about a movie you recently saw) is much more nuanced.
 Real-world recall is continuous, rather than binary.
@@
 how the contents relate/change over time).
-Naturalistic experiences are typically autocorrelated in space and time on short timescales: the contents of an experience are often similar from moment to moment and change gradually.
+Naturalistic experiences are (typically) autocorrelated in space and time on short timescales: the contents of an experience are often similar from moment to moment and change gradually.
 For example, many of us spend our mornings/evenings at home and much of our days at work (e.g.
@@
 
-% I realize this sticks out and needs to be better integrate into the narrative, but not sure how!
 Despite the continuous and (often) gradually changing nature of naturalistic experiences, prior research suggests that our memories for those same experiences may be more descrete and organized around particular ``events'' \citep{Radv12, RadvZack11, BrunEtal18}.
 Short timescale autocorrelations in the contents of an experience are thought associatively link information in memory, while more drastic changes in perceptual or semantic aspects of an experience (i.e.
-``event boundaries'') may lead to discontinuous in memory \citep{HeusEtal18, BrunEtal18, Radv12}.
+``event boundaries'') may lead to discontinuities in memory \citep{HeusEtal18, BrunEtal18, Radv12}.
 There is now compelling evidence that event boundaries can influence memory organization when learning sequences of items \citep{HeusEtal18, DuBrDava13}, during navigation \citep{BrunEtal18}, and narrative comprehension \citep{ZwaaRadv98, EzzyDava11}.
@@
 In this study, we analyzed an open dataset in which participants view and then verbally recount an episode of the BBC series \textit{Sherlock} \citep{ChenEtal17}.
-To capture the temporal structure present in naturalistic experiences, we developed a novel computational approach based on topic modeling \citep{BleiEtal03} and hidden Markov models \citep{Rabi89, BaldEtal17}.
-We propose that the temporal structure of an experience gives it a unique geometric ``shape'' or ``trajectory'', defined by how the contents of the experience relate and change over time.
-We hypothesized that when recounting naturalistic experiences, the precise details that are recapitulated and language used may differ across people, but the trajectory of the stimulus is generally preserved.
+To capture the flow of the video's content (i.e.
+the storyline), we developed a novel computational approach based on topic modeling \citep{BleiEtal03} and hidden Markov models \citep{Rabi89, BaldEtal17}.
+We propose that the temporal evolution of an experience's content gives it a unique geometric ``shape'' or ``trajectory'', defined by how the contents of the experience relate and change over time.
+We hypothesized that when recounting naturalistic experiences, the precise details remembered and language used may differ across people, but the shape of the stimulus would be preserved.
 
@@
 The text descriptions contained details of the scene such as the characters, location, and a short summary of the scene (see Fig.\ref{fig:schematic} for example text, see \ref{sec:methods} for analysis details).
-We then transformed the text descriptions using the (same) topic model, resulting in a scenes (1976) by topics (100) matrix, where each row of the matrix represents a probabalistic mixture of topics discovered in that scene (See Fig.~\ref{fig:schematic} for example topic vectors).
 As depicted in Fig.~\ref{fig:model}a, the topic vectors are sparse and change slowly over time.
@@
 To get a better handle on this temporal structure, we computed a timepoints (1976) by timepoints (1976) correlation matrix of the video model (Fig.~\ref{fig:model}c).
-This correlation matrix reveals that the model has a strong, block-diagonal structure.
-Another noteworthy characteristic is that there is very little correlation between blocks (i.e.
-the off-diagonal values are small), suggesting the representations of each block are unique and highly descriminable.
+This correlation matrix reveals that the model has a strong, block-diagonal structure with very low off-diagonal correlation values, suggesting the representations of each block are unique and highly descriminable.
 
@@
 We used the same topic model (fit with the text descriptions of the video) to transform participants' verbal recall transcripts.
-The result was a sentences (range: 68 to 294, mean: 131.94) by topics (100) matrix for each participant, where each row represents a probabalistic mixture of topics for a given window of sentences during recall.
 An example participant's (\#13) recall model is plotted in Fig.~\ref{fig:model}b.
 Like the video model, topic vectors were sparse and changed gradually.
-Note that the topics were derived solely from the text descriptions of the video, and so the topic models estimated for recall are dependent on the topics present in the video.
-This approach effectively projects the participants' verbal recall into the video's ``topic space'', allowing us to directly compare them to the video model.
-
-Next, we investigated the temporal structure of the recall matrices.
-For each participant, we computed a timepoint (68 to 294) by timepoints by timepoints (range: 68 to 294) correlation matrix from the recall models.
+Then, we investigated the temporal structure of the recall matrices.
+From each participant's recall model, we computed a timepoint (68 to 294) by timepoints by timepoints (range: 68 to 294) correlation matrix.
 An example participant's (\#13) correlation matrix is plotted in Fig.~\ref{fig:model}d).
-Like the video model, each participants' recall correlation matrix exhibited a strong block-diagonal structure (Supp Fig.
-1).
+Like the video model, each participants' recall correlation matrix exhibited a strong block-diagonal structure (Supp.
+Fig.~\ref{fig:corrmats})).
 Notably, this suggests that participants recounted the video in discriminable segments, potentially related to the recall of specific events (or scenes) from the video.
 
+\begin{figure}[ht!]
+\centering
+\includegraphics[width=\textwidth]{figs/supp1_eventseg.pdf}
+\caption{\small \textbf{Modelling naturalistic stimuli and recall.} A depiction of our analysis pipeline.
+For all plots, darker colors indicate greater values and the range of each plot is 0-1.
+A).
+A timepoints (1976) by topics (100) matrix representing the video stimulus.
+Each row represents the most likely mixture of topics for a given timepoint (i.e.
+topic weights).
+Each column represents a different topic.
+B).
+A timepoints (1976) by topics (100) matrix representing participant \#13's recall.
+C).
+A viewing-time (1976) by viewing-time (1976) correlation matrix representing the correlation of each moment of the video model with every other moment of the video model.
+The white boxes represent `events' recovered by a hidden Markov model.
+D).
+A recall-time (294 sentences) by recall-time (294) correlation matrix for participant \#13.
+E).
+An events (34) by topics (100) matrix where each row represents the average topic vector for each event in the video model.
+F).
+An events (27) by topics (100) matrix where each row represents the average topic vector for each event in participant \#13's recall model.
+G.
+A recall events (27) by video events (34) correlation matrix for participant \#13.
+The cells with a yellow border identify the video event with the highest correlation to a given recall event.
+F.
+A group averaged recall events (34) by video events (34) correlation matrix.
+The cells with yellow borders are the video event with the highest correlation to a given average recall event.}
+\label{fig:model}
+\end{figure}
+
 \subsubsection{Segmenting the video and recall models into `events'}
-As described above, a striking feature of the video and recall correlation matrices is a strong, block structure along the diagonal of the matrices (see Fig.~\ref{fig:model}c,d).
-We hypothesized that this structure might arise from transient stability in the contents of the video (i.e.
-``events''), as well as the subsequent language used to recount each event of the video.
-If true, we reasoned that it would be possible to identify the specific event a participant is describing by comparing the topic vector for a particular recall ``event'' with the topic vector for each video event.
+As described above, a striking feature of both the video and recall correlation matrices is a strong, block structure along the diagonal of the matrices (see Fig.~\ref{fig:model}c,d).
+We hypothesized that this structure might arise from transient stability in "theme" of the video/recall (i.e.
+``events'').
+If true, we reasoned that specific events described by a participant could be ``matched'' to specific video events by computing the similarity between their topic vectors.
 In other words, the video event that is most similar (i.e.
 correlated) to a particular recall event is the event that the participant is most likely describing.
-
-To test this idea, first we segmented the video and recall models in $k$ events (i.e.
+To test this idea, we segmented the video and recall models in $k$ events (i.e.
 states) using a hidden Markov model ~\citep{BaldEtal17}.
@@
 
-Next, we created a video ``event model by'' averaging together neighboring topic vectors that the were classified to be in the same event, resulting in an events (34) by topics (100) matrix (Fig.~\ref{fig:model}e).
+Next, we created a video ``event model'' by averaging together neighboring topic vectors that the were classified to be in the same event, resulting in an events (34) by topics (100) matrix (Fig.~\ref{fig:model}e).
 We performed the same procedure for the recall matrices (see Fig.~\ref{fig:model}f for example).
@@
 
-\subsubsection{Characterizing naturalistic memory with traditional list-learning analyses}
-Just like in a traditional ``free-recall'' list-learning experiment where participants view a list of words and then verbally recall them, our video-recall matching analysis approach affords us the ability to analyze memory in the same way.
-The recalled events can be treated as ``items'' analogous to words recalled in a list-learning study.
-In our first set of analyses, we sought to characterize memory performance/dynamics by extending classic analyses originally designed for list-learning experiments to more naturalistic settings.
-
-First, we asked whether the estimated number of recall events ($k$) by participant was related to hand-annotated accuracy as published in Chen et al.
-(2017).
-We found a strong positive correlation where subjects with a greater number of recall events also had better overall memory performance (Pearson's $r$(16)=.67, $p$=.003).
-Then, we considered how participants initiated the recall sequence (known in the literature as the `probability of first recall' or `PFR').
-We found that participants tended to initiate their recall sequences with the first few events (Fig.~\ref{fig:list-learning}a), which is qualitatively very similar to previously published list learning experiments (REF?).
-Next, we considered another well-studied memory measure in the list-learning literature, the lag conditional response probability curve (or lag-CRP) ~\citep{Kaha96}.
-The result suggests a strong bias to transition sequentially events in the forward direction (Fig.~\ref{fig:list-learning}b).
-Finally, we assessed memory performance for each event in the video as a function of its serial position during encoding (Fig.~\ref{fig:list-learning}c).
-We found that there was substantial variability in memory for the different events (STAT).
-
-We also considered two additional across-participant measures of recall that characterize memory organization: temporal clustering and semantic clustering.
-We found that participants who clustered in time also recalled a greater number of events (Pearson's $r$(16)=.62, $p$=.007).
-Next, we assessed semantic clustering.
-We found that the semantic clustering score was related to memory performance across participants (Pearson's $r$(16)=.55, $p$=.02).
-Thus, participants who organized their recalls with respect to the semantic information contained in the scene had better memory performance.
-
 \subsubsection{The shape of a naturalistic experience is preserved in recall}
-The analyses described in the previous sections are useful in that they allow us to quantify memory dynamics for naturalistic stimuli in a way that is comparable to a vast literature on trial-based list-learning experiments.
-Furthermore, we introduce novel measures (precision and distinctiveness) which provide additional details regarding the veracity of naturalistic memories.
-However, these methods fail to capture the rich temporal structure present in naturalistic stimuli and associated recall of those experiences.
-Thus, our next set of analyses test whether the ``shape'' of an experience is preserved in memory.
-We hypothesized that despite substantial individual variability in the precision and amount of content recalled across by participants, the overall shape of the episode would be recapitulated by the majority of participants.
+Classic approaches to studying free recall in episodic memory (such as overall accuracy and serial position curve) focus on the quantity of information recalled.
+More recent metrics (such as lag-CRP, semantic and temporal clustering) go further to describe list-level memory organization.
+However, none of these approaches capture the rich autocorrelated structure inherent in naturalistic stimuli and associated recall of those experiences.
+Using our topic-based approach, in the next set of analyses we test the hypothesis that naturalistic recall entails recapitulating the trajectory of a stimulus.
 
@@
 To visualize the average angle, we converted each transition angle to a unit vector and then averaged the vectors together.
-To assess consistency in the direction of the recall transition across participants, we performed a Rayleigh test (p$<$.001, corrected at p$<$.05 using permutation procedure described in Methods).Thus participants' recalls followed the same path as the video model (Fig.~\ref{fig:trajectory}b), suggesting the shape of the stimulus was preserved despite idiosyncratic differences between participants in their recalls.
+To assess consistency in the direction of the recall transition across participants, we performed a Rayleigh test (p$<$.001, corrected at p$<$.05 using permutation procedure described in Methods).
+Thus participants' recalls followed the same path as the video model (Fig.~\ref{fig:trajectory}b), suggesting the shape of the stimulus was preserved despite idiosyncratic differences between participants in their recalls.
 
-Notably, many of the participants' recall trajectories appear to recover the overall shape of the video stimulus.
+% NOTE: Not sure if this part (below) is necessary, but if it is, then I think we need to come up with a null test to say that participants fits are better than chance
+
+% Notably, many of the participants' recall trajectories appear to recover the shape of the video stimulus.
 To quantify this similarity, we measured the average euclidean distance between each each segment of the video model (e.g.
@@
 Thus, measuring similarity in shape between the video and recall models provides unique information about participant's recall behavior that is not captured by classic measures of memory accuracy.
-
-\subsubsection{Measuring the quality of naturalistic memories}
-Representing the video and verbal recall as events in ``topic space'' also affords us the ability to characterize the quality of recall in a more fine-grained and nuanced way than what was previously possible.
-To quantify the similarity between the video model and individual recall models, we considered a number of novel metrics.
-First, we tested whether each participant's recall model matched the movie model in a general sense.
-To do this, for each participant we filtered the video model to only include the events that the participant remembered.
-Then, we computed the root mean squared difference (RMSD) between the video model and the recall model.
-As an example, if the participant remembered all the events in order (with perfect precision), the expected distance value would be 0.
-However, if they remembered a subset of events, events our of order or with low precision the expected distance would be greater than 0.
-To assess significance, we performed a permutation test where we circularly shifted the recall model (10000 times) and recomputed the RMSD.
-The recall model significantly matched the video model for nine of the participants ($p$<.05; participants: 3-4, 8-13, 17 and the p-value for the rest of the participants was less than .25).
-Furthermore, the RMSD values were significantly correlated to hand annotated memory performance across participants (Pearson's $r$(16)=-.57, $p$=.016).
-Thus, a closer match between the video and recall event models was related to better recall performance.
-
-Next, we tested whether participants who recalled more events were also more precise in their recollections.
-For each participant, we computed the correlation between each recall event and its matching video event (only for the events which they recalled).
-This resulted in a single number for each recalled event indexing how similar the recall event was to its matching movie event (i.e the ``precision'' of the recall).
-We then averaged the correlations within participant.
-In line with our prediction, there was a strong correlation between hand annotated memory performance and precision suggesting that participants who remembered more events also remembered them more veridically (Pearson's $r$(16)=.74, p=.0006).
-Next, we considered the distinctiveness of each recall event.
-That is, how uniquely a recall event matched a given video event compared to all other video events.
-We hypothesized that participants with high memory performance might describe each event in a more distinctive way (relative to those with lower memory performance who might describe events in a more general way).
-To this end, we computed a `distinctiveness' score for each participant (i.e.
-1 - the correlation between a recall event and all non-matching video events).
-Then, we averaged this measure over recall events within participant.
-We found that participants with higher hand annotated memory performance also had higher distinctiveness scores (Pearson's $r$(16)=.8, p=.0001).
-
-Lastly, we tested whether participants with better memory performance were also more likely to remember the events in order.
-For each participant, we computed the Spearman rank correlation between the order of events that the participant recalled and the actual order of events (filtering events that were actually recalled).
-We found that participants who recalled more events also recalled more of them in order (Pearson's $r$(16)=.5, p=.04).
-In summary, we found that better memory performance was associated with more precise, distinctive and ordered recalls.
 
@@
 These analyses shed light on the contents of naturalistic stimuli and accompanying memories, and highlight the flexibility in transforming between human and machine readable representations of the data afforded by our modeling approach.
+
+\subsubsection{Additional measures of naturalistic memory}
+Representing the video and verbal recall as events in ``topic space'' also affords us the ability to characterize the quality of recall in a more fine-grained and nuanced way than what was previously possible.
+To quantify the similarity between the video model and individual recall models, we considered a number of novel metrics.
+First, we tested whether each participant's recall model matched the movie model in a general sense.
+To do this, for each participant we filtered the video model to only include the events that the participant remembered.
+Then, we computed the root mean squared difference (RMSD) between the video model and the recall model.
+As an example, if the participant remembered all the events in order (with perfect precision), the expected distance value would be 0.
+However, if they remembered a subset of events, events our of order or with low precision the expected distance would be greater than 0.
+To assess significance, we performed a permutation test where we circularly shifted the recall model (10000 times) and recomputed the RMSD.
+The recall model significantly matched the video model for nine of the participants ($p$<.05; participants: 3-4, 8-13, 17 and the p-value for the rest of the participants was less than .25).
+Furthermore, the RMSD values were significantly correlated to hand annotated memory performance across participants (Pearson's $r$(16)=-.57, $p$=.016).
+Thus, a closer match between the video and recall event models was related to better recall performance.
+
+Next, we tested whether participants who recalled more events were also more precise in their recollections.
+For each participant, we computed the correlation between each recall event and its matching video event (only for the events which they recalled).
+This resulted in a single number for each recalled event indexing how similar the recall event was to its matching movie event (i.e the ``precision'' of the recall).
+We then averaged the correlations within participant.
+In line with our prediction, there was a strong correlation between hand annotated memory performance and precision suggesting that participants who remembered more events also remembered them more veridically (Pearson's $r$(16)=.74, p=.0006).
+Next, we considered the distinctiveness of each recall event.
+That is, how uniquely a recall event matched a given video event compared to all other video events.
+We hypothesized that participants with high memory performance might describe each event in a more distinctive way (relative to those with lower memory performance who might describe events in a more general way).
+To this end, we computed a `distinctiveness' score for each participant (i.e.
+1 - the correlation between a recall event and all non-matching video events).
+Then, we averaged this measure over recall events within participant.
+We found that participants with higher hand annotated memory performance also had higher distinctiveness scores (Pearson's $r$(16)=.8, $p$=.0001).
+
+Lastly, we tested whether participants with better memory performance were also more likely to remember the events in order.
+For each participant, we computed the Spearman rank correlation between the order of events that the participant recalled and the actual order of events (filtering events that were actually recalled).
+We found that participants who recalled more events also recalled more of them in order (Pearson's $r$(16)=.5, $p$=.04).
+In summary, we found that better memory performance was associated with more precise, distinctive and ordered recalls.
+
+Just like in a traditional ``free-recall'' list-learning experiment where participants view a list of words and then verbally recall them, our video-recall matching analysis approach affords us the ability to analyze memory in the same way.
+The recalled events can be treated as ``items'' analogous to words recalled in a list-learning study.
+In our first set of analyses, we sought to characterize memory performance/dynamics by extending classic analyses originally designed for list-learning experiments to more naturalistic settings.
+First, we asked whether the estimated number of recall events ($k$) by participant was related to hand-annotated accuracy as published in Chen et al.
+(2017).
+We found a strong positive correlation where subjects with a greater number of recall events also had better overall memory performance (Pearson's $r$(16)=.67, $p$=.003).
+Then, we considered how participants initiated the recall sequence (known in the literature as the `probability of first recall' or `PFR').
+We found that participants tended to initiate their recall sequences with the first few events (Supp.
+Fig.~\ref{fig:list-learning}a), which is qualitatively very similar to previously published list learning experiments (REF?).
+Next, we considered another well-studied memory measure in the list-learning literature, the lag conditional response probability curve (or lag-CRP) ~\citep{Kaha96}.
+The result suggests a strong bias to transition sequentially events in the forward direction (Supp.
+Fig.~\ref{fig:list-learning}b).
+Finally, we assessed memory performance for each event in the video as a function of its serial position during encoding (Supp.
+Fig.~\ref{fig:list-learning}c).
+We found that there was substantial variability in memory for the different events (STAT).
+We also considered two additional across-participant measures of recall that characterize memory organization: temporal clustering and semantic clustering.
+We found that participants who clustered in time also recalled a greater number of events (Pearson's $r$(16)=.62, $p$=.007).
+Next, we assessed semantic clustering.
+We found that the semantic clustering score was related to memory performance across participants (Pearson's $r$(16)=.55, $p$=.02).
+Thus, participants who organized their recalls with respect to the semantic information contained in the scene had better memory performance.
 
@@
 To conclude, let's revisit the question of what it means to remember something.
-We assert that episodic memories are not veridical snapshots from the past, and so we should stop treating (and modelling) them as such.
+We assert that episodic memories are not veridical snapshots of the past, and so we should stop treating (and modelling) them as such.
 Rather, episodic memories are better described as echoes of a prior experience that are shaped by other past experiences as well as the current context.
-Furthermore
 
@@
 % Supplemental materials
-
-\begin{suppfigure}[ht!]
-\centering
-\includegraphics[width=\textwidth]{figs/supp1_eventseg.pdf}
-\caption{\small \textbf{Modelling naturalistic stimuli and recall.} A depiction of our analysis pipeline.
-For all plots, darker colors indicate greater values and the range of each plot is 0-1.
-A).
-A timepoints (1976) by topics (100) matrix representing the video stimulus.
-Each row represents the most likely mixture of topics for a given timepoint (i.e.
-topic weights).
-Each column represents a different topic.
-B).
-A timepoints (1976) by topics (100) matrix representing participant \#13's recall.
-C).
-A viewing-time (1976) by viewing-time (1976) correlation matrix representing the correlation of each moment of the video model with every other moment of the video model.
-The white boxes represent `events' recovered by a hidden Markov model.
-D).
-A recall-time (294 sentences) by recall-time (294) correlation matrix for participant \#13.
-E).
-An events (34) by topics (100) matrix where each row represents the average topic vector for each event in the video model.
-F).
-An events (27) by topics (100) matrix where each row represents the average topic vector for each event in participant \#13's recall model.
-G.
-A recall events (27) by video events (34) correlation matrix for participant \#13.
-The cells with a yellow border identify the video event with the highest correlation to a given recall event.
-F.
-A group averaged recall events (34) by video events (34) correlation matrix.
-The cells with yellow borders are the video event with the highest correlation to a given average recall event.}
-\label{fig:model}
-\end{suppfigure}
-
 \begin{suppfigure}[t!]

### 2018-08-17 paper/main.tex
saving progress

@@
 The human memory system is adept at cataloging the rich dynamics of ongoing experience.
-A defining feature of our everyday experiences is that they unfold in a structured and predictable manner, governed by the laws of the physical systems that produce them.
-However, this temporal structure is typically absent (or severly impoverished) in traditional trial-based memory experiments.
+A defining feature of our everyday experiences is that they unfold in a structured and predictable manner.
+This temporal structure gives each of our experiences (and thus our memories for those experiences) a unique shape.
+However, temporal structure is typically absent (or severly impoverished) in traditional trial-based memory experiments.
 As a consequence, our understanding of how the temporal structure (i.e.
@@
 
-Human memory studies typically assess memory for the ``items'' within an experience, such as the people, places and things encountered.
+Human memory studies typically assess memory for the elements within an experience, such as the people, places and things encountered.
 However, real life experiences can also be described in terms of their temporal structure (i.e.
@@
 The spatial contexts before and after lunch are highly similar, but separated in time.
-Thus, while evaluating the ability to recall specific contents of an experience is one way to assess memory, another important dimension to consider is the temporal structure of the remembered experience, and how the temporal structure of the memory relates to the original experience.
+Thus, while evaluating the ability to recall specific contents of an experience has been a fruitful way to learn about human memory, another important dimension to consider is the temporal structure of the remembered experience, and how the temporal structure of the memory relates to the original experience.
 However, these recurrent and gradually changing temporal dynamics are not typically present in traditional memory studies, but are likely critical if we wish to understand how our memory systems remember our life experiences.
 
-Despite the continuous and (often) gradually changing nature of naturalistic experiences, prior research suggests that our memories for those same experiences may be more descrete and organized around particular ``events'' \citep{Radv12, RadvZack11, BrunEtal18}.
-Short timescale autocorrelations in the contents of an experience are thought associatively link information in memory, while more drastic changes in perceptual or semantic aspects of an experience (i.e.
-``event boundaries'') may lead to discontinuities in memory \citep{HeusEtal18, BrunEtal18, Radv12}.
+While our life experiences often change gradually, they can also change rapidly (e.g.
+walking through a doorway) \citep{Radv12}.
+Prior research suggests that these sharp transitions (coined in the literature as ``event boundaries'') during an experience may serve to descretize/organize our memories into ``events'' \citep{Radv12, RadvZack11, BrunEtal18, HeusEtal18, ClewDava18}.
+Short timescale autocorrelations in the contents of an experience are thought associatively link information in memory, while more drastic changes in perceptual or semantic aspects of an experience may lead to discontinuities in memory \citep{HeusEtal18, BrunEtal18, Radv12}.
 There is now compelling evidence that event boundaries can influence memory organization when learning sequences of items \citep{HeusEtal18, DuBrDava13}, during navigation \citep{BrunEtal18}, and narrative comprehension \citep{ZwaaRadv98, EzzyDava11}.
@@
 
-In this study, we analyzed an open dataset in which participants view and then verbally recount an episode of the BBC series \textit{Sherlock} \citep{ChenEtal17}.
+In this study, we analyzed an open dataset in which participants view and then verbally recall an episode of the BBC series \textit{Sherlock} \citep{ChenEtal17}.
 To capture the flow of the video's content (i.e.
 the storyline), we developed a novel computational approach based on topic modeling \citep{BleiEtal03} and hidden Markov models \citep{Rabi89, BaldEtal17}.
-We propose that the temporal evolution of an experience's content gives it a unique geometric ``shape'' or ``trajectory'', defined by how the contents of the experience relate and change over time.
-We hypothesized that when recounting naturalistic experiences, the precise details remembered and language used may differ across people, but the shape of the stimulus would be preserved.
+This model casts naturalistic stimuli as high-dimensional topic ``trajectories'', whereby the theme of each moment of the video is represented as a topic vector.
+Successful remembering entails verbally ``traversing'' the path formed by the stimulus topic trajectory as closely as possible.
+We hypothesized that successful memory for a naturalistic stimulus is given by a recall trajectory that 1) has temporal structure similar to the stimulus 2) closely follows the path of the stimulus trajectory and 3) covers the majority of the stimulus path.
 
@@
 
-\subsubsection{A model to capture the temporal and semantic structure of naturalistic stimuli}
+\subsubsection{Modeling the naturalistic stimulus and verbal recall}
 We fit a topic model \citep{BleiEtal03} to hand-annotated text descriptions of scenes from the video.
@@
 
-\subsubsection{Modeling verbal recall}
 After watching the video, participants verbally recalled (in order) as much of the episode as they could.
@@
 Fig.~\ref{fig:corrmats})).
-Notably, this suggests that participants recounted the video in discriminable segments, potentially related to the recall of specific events (or scenes) from the video.
+Notably, this suggests that participants recounted the video in discriminable segments, likely related to the recall of specific events from the video.
 
@@
 \centering
-\includegraphics[width=\textwidth]{figs/supp1_eventseg.pdf}
+\includegraphics[width=\textwidth]{figs/2_eventseg.pdf}
 \caption{\small \textbf{Modelling naturalistic stimuli and recall.} A depiction of our analysis pipeline.
@@
 ``events'').
-If true, we reasoned that specific events described by a participant could be ``matched'' to specific video events by computing the similarity between their topic vectors.
+We reasoned that specific events described by a participant could be ``matched'' to specific video events by computing the similarity between their topic vectors.
 In other words, the video event that is most similar (i.e.
@@
 This is depicted in Fig.~\ref{fig:model}g as the cells highlighted with a yellow border.
-Interestingly, our algorithm suggests that the example participant recalled most of the video events in order.
+Notably, our algorithm suggests that the example participant recalled most of the video events and did so in order.
 
@@
 However, none of these approaches capture the rich autocorrelated structure inherent in naturalistic stimuli and associated recall of those experiences.
-Using our topic-based approach, in the next set of analyses we test the hypothesis that naturalistic recall entails recapitulating the trajectory of a stimulus.
+In the next set of analyses, we test the hypothesis that successful recall of a naturalistic stimulus entails recovering the trajectory of a stimulus.
 
@@
 \centering
-\includegraphics[width=1\textwidth]{figs/4_trajectory.pdf}
+\includegraphics[width=1\textwidth]{figs/3_trajectory.pdf}
 \caption{\small \textbf{Video and recall trajectory plots.} A).
@@
 
-To visualize the relationship between the video and recall event models, we embedded them into a 2D space (using the UMAP dimensionality reduction algorithm, for details see \ref{sec:methods}) where the points represent video/recall events and the distance between them represents their similarity in ``topic space'' (Fig.~\ref{fig:trajectory}a).
-We observed that the two models have a very similar temporal evolution and geometric structure.
+To visualize the relationship between the video and recall event models, we embedded them into a 2D space (using the UMAP dimensionality reduction algorithm, for details see \ref{sec:methods}) where the points represent video/recall events and the distance between them represents their similarity/distance in ``topic space'' (Fig.~\ref{fig:trajectory}a).
+We observed that visually, it appears that the two models have a very similar temporal evolution and geometric structure.
 To further quantify this correspondence and to characterize how participants navigated through the space during recall, we analyzed the angle between successive recall events.
@@
 \centering
-\includegraphics[width=1\textwidth]{figs/5_topics.pdf}
+\includegraphics[width=1\textwidth]{figs/4_topics.pdf}
 \caption{\small \textbf{Analysis of topics by event memorability.} A).
@@
 
+%NOTE: could be useful to add a 'where this might break down' section
+
 To conclude, let's revisit the question of what it means to remember something.
@@
 \centering
-\includegraphics[width=1\textwidth]{figs/supp2_corrmats.pdf}
+\includegraphics[width=1\textwidth]{figs/supp1_corrmats.pdf}
 \caption{\small \textbf{Recall model correlation matrices and event segmentation fits.} Each participant's timepoint-by-timepoint recall correlation matrix.
@@
 \label{fig:corrmats}
+\end{suppfigure}
+
+\begin{suppfigure}[t!]
+\centering
+\includegraphics[width=1\textwidth]{figs/supp2_matchmats.pdf}
+\caption{\small \textbf{Video-recall event model correlation matrices.} Each participant's video event by recall event correlation matrix.
+The yellow boxes represent the maximum correlation in each column.}
+\label{fig:matchmats}
 \end{suppfigure}

### 2018-08-20 paper/main.tex
moved additional metrics and list learning to supplemental

@@
 This suggests that on average, participants were able to recapitulate the events in the episode in a specific, highly descriminable way.
-% NOTE: ^ possibly need a null model for the group analysis.
-I think it could be to get a result that looks like this even if we scrambled the text.
-My concern is that I'm grouping the recall events by the video event they were most similar to, and then averaging, which may give rise to a smooth looking plot without any real information there...
 
@@
 The directional lines connecting the points represent the true video event order.
-The arrows represent the average direction of all recall event transitions (i.e.
+The arrows represent the group-average direction of all recall event transitions (i.e.
 a line segment connecting two consecutive recall event vectors) that intersected a box (width=.25) centered on the origin of the arrow.}
@@
 
-% NOTE: Not sure if this part (below) is necessary, but if it is, then I think we need to come up with a null test to say that participants fits are better than chance
+\subsubsection{Additional measures of naturalistic recall}
+Representing the video and verbal recall as events in ``topic space'' also affords us the ability to characterize the quality of recall in a more fine-grained and nuanced way than what was previously possible.
+In addition to the shape analyses described above, we quantified the distance between each video event and its matching recall event (``precision''), the the distance between a video event and all non-matching recall events (``distinctiveness'') and the temporal order of the recall events (``order'').
+All three of these metrics were correlated to hand-annotated memory performance across participants ($p$<.05, see Supplemental Materials Section 1 for details).
 
-% Notably, many of the participants' recall trajectories appear to recover the shape of the video stimulus.
-To quantify this similarity, we measured the average euclidean distance between each each segment of the video model (e.g.
-the line formed by successive video events) and the closest recall event for each participant.
-Inuitively, if the participant approximately remembered every video event, the measure would approach 0.
-The more missing recall events, the higher the value.
-We found that this shape measure was highly correlated to the number of events remembered across participants (Pearson's $r$(16)=-.87, p$<$.001).
-While these measures are highly correlated (as might be expected), there are cases where the measures dissociate.
-For example participant X and X recalled exactly the same number of events, but the shape measure is drastically different between them.
-Conversely, participant X and X had the same shape measure, but there was a large difference in the number of events recalled.
-Thus, measuring similarity in shape between the video and recall models provides unique information about participant's recall behavior that is not captured by classic measures of memory accuracy.
+Just like in a traditional ``free-recall'' list-learning experiment where participants view a list of words and then verbally recall them, our video-recall matching analysis approach affords us the ability to analyze memory in the same way.
+We considered 6 classic list-learning analyses: overall accuracy, probability of first recall, lag-conditional response probability, serial position curve, temporal clustering and semantic clustering.
+Extending these classic list-learning analyses to naturalistic stimuli allows to directly compare trial- and naturalistic-based recall studies (see Supplemental Materials Section 2 for details).
 
@@
 \subsubsection{Memorability by event and topics}
-A noteworthy advantage of representing naturalistic stimuli/memory using this approach is that the event models can be mapped back to the language used to fit the model(s).
+A notable advantage of representing naturalistic stimuli/memory using this approach is that the event models can be mapped back to the language used to fit the model(s).
 This allows for analysis and visualization of the language used when participant's recounted their experiences.
@@
 
-\subsubsection{Additional measures of naturalistic memory}
-Representing the video and verbal recall as events in ``topic space'' also affords us the ability to characterize the quality of recall in a more fine-grained and nuanced way than what was previously possible.
-To quantify the similarity between the video model and individual recall models, we considered a number of novel metrics.
-First, we tested whether each participant's recall model matched the movie model in a general sense.
-To do this, for each participant we filtered the video model to only include the events that the participant remembered.
-Then, we computed the root mean squared difference (RMSD) between the video model and the recall model.
-As an example, if the participant remembered all the events in order (with perfect precision), the expected distance value would be 0.
-However, if they remembered a subset of events, events our of order or with low precision the expected distance would be greater than 0.
-To assess significance, we performed a permutation test where we circularly shifted the recall model (10000 times) and recomputed the RMSD.
-The recall model significantly matched the video model for nine of the participants ($p$<.05; participants: 3-4, 8-13, 17 and the p-value for the rest of the participants was less than .25).
-Furthermore, the RMSD values were significantly correlated to hand annotated memory performance across participants (Pearson's $r$(16)=-.57, $p$=.016).
-Thus, a closer match between the video and recall event models was related to better recall performance.
-
-Next, we tested whether participants who recalled more events were also more precise in their recollections.
-For each participant, we computed the correlation between each recall event and its matching video event (only for the events which they recalled).
-This resulted in a single number for each recalled event indexing how similar the recall event was to its matching movie event (i.e the ``precision'' of the recall).
-We then averaged the correlations within participant.
-In line with our prediction, there was a strong correlation between hand annotated memory performance and precision suggesting that participants who remembered more events also remembered them more veridically (Pearson's $r$(16)=.74, p=.0006).
-Next, we considered the distinctiveness of each recall event.
-That is, how uniquely a recall event matched a given video event compared to all other video events.
-We hypothesized that participants with high memory performance might describe each event in a more distinctive way (relative to those with lower memory performance who might describe events in a more general way).
-To this end, we computed a `distinctiveness' score for each participant (i.e.
-1 - the correlation between a recall event and all non-matching video events).
-Then, we averaged this measure over recall events within participant.
-We found that participants with higher hand annotated memory performance also had higher distinctiveness scores (Pearson's $r$(16)=.8, $p$=.0001).
-
-Lastly, we tested whether participants with better memory performance were also more likely to remember the events in order.
-For each participant, we computed the Spearman rank correlation between the order of events that the participant recalled and the actual order of events (filtering events that were actually recalled).
-We found that participants who recalled more events also recalled more of them in order (Pearson's $r$(16)=.5, $p$=.04).
-In summary, we found that better memory performance was associated with more precise, distinctive and ordered recalls.
-
-Just like in a traditional ``free-recall'' list-learning experiment where participants view a list of words and then verbally recall them, our video-recall matching analysis approach affords us the ability to analyze memory in the same way.
-The recalled events can be treated as ``items'' analogous to words recalled in a list-learning study.
-In our first set of analyses, we sought to characterize memory performance/dynamics by extending classic analyses originally designed for list-learning experiments to more naturalistic settings.
-First, we asked whether the estimated number of recall events ($k$) by participant was related to hand-annotated accuracy as published in Chen et al.
-(2017).
-We found a strong positive correlation where subjects with a greater number of recall events also had better overall memory performance (Pearson's $r$(16)=.67, $p$=.003).
-Then, we considered how participants initiated the recall sequence (known in the literature as the `probability of first recall' or `PFR').
-We found that participants tended to initiate their recall sequences with the first few events (Supp.
-Fig.~\ref{fig:list-learning}a), which is qualitatively very similar to previously published list learning experiments (REF?).
-Next, we considered another well-studied memory measure in the list-learning literature, the lag conditional response probability curve (or lag-CRP) ~\citep{Kaha96}.
-The result suggests a strong bias to transition sequentially events in the forward direction (Supp.
-Fig.~\ref{fig:list-learning}b).
-Finally, we assessed memory performance for each event in the video as a function of its serial position during encoding (Supp.
-Fig.~\ref{fig:list-learning}c).
-We found that there was substantial variability in memory for the different events (STAT).
-We also considered two additional across-participant measures of recall that characterize memory organization: temporal clustering and semantic clustering.
-We found that participants who clustered in time also recalled a greater number of events (Pearson's $r$(16)=.62, $p$=.007).
-Next, we assessed semantic clustering.
-We found that the semantic clustering score was related to memory performance across participants (Pearson's $r$(16)=.55, $p$=.02).
-Thus, participants who organized their recalls with respect to the semantic information contained in the scene had better memory performance.
-
-%NOTE: I'm not sure the brain stuff really fits in this paper.
-It's cool, but seems like a distraction from the main point.
-perhaps it needs it own paper with more motivation, and more extensive analyses (for example, what brain regions have temporal structure like the movie model?).
-I'm also having a hard time motivating it in the discussion, so maybe we should cut it.
-
-% \subsubsection{Brain regions that mirror the correlational structure of naturalistic memories}.
-% While each participant remembered roughly the same sequence of events, there were subtle idiosyncracies in the way each individual described the events.
-For example, the event by event similarity structure (e.g.
-the off-diagonal values of the recall correlation matrices) differed across individuals (Supp.
-Fig.~\ref{fig:corrmats}).
-We hypothesized that idiosyncracies in the recall dynamics across subjects might be related to the temporal structure of brain networks are representing the events during video viewing.
-Thus in the last analysis, we identified brain areas whose responses at the time of viewing exhibited the same (segmented) idiosyncratic dynamics that later appeared in that participants’ recalls.
-%
-% The amount of time/number of sentences used describing each scene differed drastically between participants and as compared to the original video \cite{ChenEtal17}.
-To account for these temporal non-linearities between the video and recall, we used dynamic time warping to align each participant's recall model and the movie model (DTW REF).
-We used the resulting alignment path to warp the fMRI timeseries (for each voxel) as well as the recall model timeseries.
-Then using a searchlight procedure (5mm), we computed the timepoint-by-timepoint neural correlation matrix within each searchlight.
-To measure the similarity between the neural and behavioral correlation matrices, we vectorized and then correlated them.
-The result was a correlation value for each voxel representing the extent to which the brain data mirrored the recall data.
-Finally, to test the significance of the correlation values, we phase shifted the recall models (100 permuations) and recomputed the correlation values.
-Significance was determined by ``real'' correlation values that exceeded the 95th percentile of this null distribution.
-The resulting map suggests that the correlational structure of a network of brain regions including the ventromedial prefrontal cortex, anterior cingulate, and right medial temporal lobe mirror the idiosyncratic structure of participants'' recalls.
-%
-% \begin{figure}[t!]
-% \centering
-% \includegraphics[width=1\textwidth]{figs/6_brains.pdf}
-% \caption{\small \textbf{Recall model correlational structure searchlight analysis.} A).
-We used dynamic time warping to separately align each participant's recall model to the video model.
-The left matrix is S13's video-recall correlation matrix before warping.
-The yellow stars represent the path recovered by dynamic time warping.
-The right matrix is the result after warping.
-The same warping path was applied to the fMRI timeseries (separately for each participant).
-Below the matrices are toy examples representing a vectorized (aligned) recall correlation matrix and a vectorized (aligned) fMRI searchlight correlation matrix.
-These vectors were correlated for each searchlight sphere in the brain to assess brain regions whose temporal correlation structure mirrored the participant's recall model correlation structure.
-B) A surface plot of brain regions whose activity patterns mirrored the participant-specific recall correlation matrix.
-Significance threshold (p$<$.05) derived from a permutation procedure by phase shifting the video model and recomputing the z-scores.}
-% \label{fig:brainz}
-% \end{figure}
-
 \section{Discussion}
 \label{sec:discussion}
-
 Studying episodic memory is commonly distilled down to a process of matching specific moments of a past experience with specific mnemonic outcomes.
@@
 By contrast, the number of recalls could be captured by the "sampling frequency" along that trajectory-- but the number of recalls alone cannot tell us whether participants successfully recollected the meaning of the story by capturing the salient points of the narrative that define its main shape.
-
-% Prior work on neural responses during naturalistic experience and recall (e.g.
-Hasson group) has largely focused on identifying brain regions whose responses are reliably similar across individuals.
-This allows one to identify which regions might be processing or representing the stimulus, or retrieving details of the experience during recall.
-Our approach is fundamentally different.
-We ask: which brain regions during movie viewing match how individual participants will recall the movie later (in terms of the temporal correlations of their recall topic trajectory)?
-This approach highlights regions such as the vmPFC that may respond in idiosyncratic ways across individuals, but that nonetheless play an important role in encoding experience into memory.
 
@@
 These indices are analogous to the values found in a ``recall matrix'' from a free recall list learning experiment, but represent the recall of particular events (instead of words, for example).
-%
-\subsubsection{Characterizing memory performance using traditional approaches}
-
-\textbf{Overall Accuracy.}  To get an overall measure of the quantity of information recalled, we computed the proportion of sucessfully recalled events by counting the number of unique recall events identified by the HMM model and dividing by the total number of video events.
-We performed this analysis for each participant separately.
-
-\textbf{Probability of first recall (PFR).}  The (PFR) analysis represents the probability that an item will be recalled first as a function of its serial position during encoding.
-We initialized a \# of participants (17) by \# of video events (34) matrix.
-Then for each participant, we found the index of the video event that was recalled first and filled in that index in the matrix with a 1.
-Finally, we averaged over the rows of the matrix, resulting in a 1 by 34 array representing the proportion of subject that recalled an event as a function of serial position during encoding.
-
-\textbf{Lag conditional probability curve (lag-CRP).} The lag-CRP represents the probability that the next item recalled will be of lag $i$ from the just recalled item.
-For each recall transition, we computed the lag between the current recall event and the next recall event, normalizing by the total number of possible transitions.
-This resulted in a \# of participants (17) by lags (-33:+33) matrix.
-We averaged over the rows of this matrix to get a group-averaged lag-CRP.
-
-\textbf{Serial position curve (SPC).} The SPC represents the proportion of participants that remember an item as a function of its serial position during encoding.
-We initialized a \# of participants (17) by \# of video events (34) matrix.
-Then, for each recall event (and each participant), we found the index of the video event that was recalled and filled it in with a 1.
-This resulted in a matrix where 1s indicate the successful recall of an event in serial position $n$ and zeros indicate the lack of recall for that event.
-Lastly, we averaged over the rows of the matrix to get a 1 by 34 array representing the proportion of subjects that recalled an event as a function of its serial position.
-
-\textbf{Temporal clustering.} Temporal clustering measures the extent to which participants group their recall responses according to encoding position.
-For instance, if the participant recalled each item in the presentation order, this would result in a score of 1.
-If the participant recalled randomly with respect to presentation order, this would result in a score of ~.5.
-For each event transition (and separately for each participant), we computed the rank similarity (euclidean distance) between the presentation position  of the current and next recall events.
-The scores were then averaged within participant to get a single number representing the extent of temporal clustering exhibited by a given participant.
-
-\textbf{Semantic clustering.} Similar to temporal clustering, semantic clustering measures the extent to which participants group their recall responses according to semantic similarity.
-Here, we are using the topic vectors for each event as a proxy for its semantic content.
-Thus, similarity between the semantic content for two events can be computed by correlating their respective topic vectors.
-For instance, if each consecutive recall was the next most similar event (in terms of its s), this would result in a score of ~1.
-If the participant recalled randomly with respect to semantic similarity, this would result in a score of ~.5.
-For each event transition (and separately for each participant), we computed the rank similarity (correlation distance) between the current recall event and the next recall event.
-The scores were then averaged within participant to get a single number representing the extent of semantic clustering exhibited by a given participant.
 
 \subsubsection{Visualizing the video and recall event models}
-
 To better understand the temporal structure of the video event model (34 events by 100 topics) and the recall event models (8-27 events by 100 topics), we used a technique called UMAP to reduce the ``topic-space'' from 100 dimensions down to 2 dimensions (REF).
@@
 
- % \subsection{fMRI analyses}
- % Seventeen participants watched the first 50 minutes of Episode 1 of BBC's Sherlock.
-The video was split into two parts of approximately equal length (946 and 1030 TRs).
-All data were preprocessed and transformed to 3mm MNI space as described in the paper.
-Data were zscored across time at every voxel.
-6mm smoothing was applied.
- % Files are cropped so that all video-viewing data are aligned across participants, and all recall data are aligned to the scene timestamps below.
-The cropping includes a constant 3-TR (4.5 sec) shift to correct for hemodynamic lag.
- %
- % \subsubsection{Searchlight analysis}
- % Our multivariate analyses were designed to capture brain regions whose timepoint-by-timepoint correlational structure mirrors the correlational structure of the participant-specific recall topic models during video viewing.
-To correct for non-linearities between the viewing time and recall time, for each participant we used DTW to temporally align the matrices.
-The algorithm recovers a path of coordinates that would bring the video and recall model in maximal temporal alignment.
-We used this path to warp the fMRI data and the recall model into temporal alignment (separately for each participant).
-Then, we conducted a searchlight analysis (5x5x5 voxel cube) where for each cube, we correlated the model timepoint-by-timepoint correlation matrix with the neural correlation matrix.
-To aggregate across participants, we Fisher's z-transformed the correlations and then averaged.
-To assess significance, we recomputed this group analysis 100 times, but randomly phase shifted the model (by \# of timepoints - 1) by the same amount for each participant but different amounts for each permutation to build a null distribution of correlation values.
-Finally, we thresholded the group averaged correlation maps where the `real' correlation value for a given voxel exceeded the 95th percentile of the null distribution.
+\bibliography{memlab}
 
-\bibliography{memlab}
+% SUPPLEMENTAL MATERIALS
+
+\pagebreak
+\begin{center}
+\textbf{\large Supplemental Materials: Capturing the shape of naturalistic experiences and how we remember them}
+\end{center}
+\setcounter{equation}{0}
+\setcounter{figure}{0}
+\setcounter{table}{0}
+\setcounter{page}{1}
+\setcounter{section}{0}
+\makeatletter
+\renewcommand{\theequation}{S\arabic{equation}}
+\renewcommand{\thefigure}{S\arabic{figure}}
+\renewcommand{\bibnumfmt}[1]{[S#1]}
+\renewcommand{\citenumfont}[1]{S#1}
 
@@
 
+\section{Additional measures of naturalistic memory}
+To quantify the similarity between the video model and individual recall models, we considered a number of novel metrics.
+First, we tested whether each participant's recall model matched the movie model in a general sense.
+To do this, for each participant we filtered the video model to only include the events that the participant remembered and computed the root mean squared difference (RMSD) between the video model and the recall model.
+As an example, if the participant remembered all the events in order (with perfect precision), the expected distance value would be 0.
+However, if they remembered a subset of events, events our of order or with low precision the expected distance would be greater than 0.
+To assess significance, we performed a permutation test where we circularly shifted the recall model (10000 times) and recomputed the RMSD.
+The recall model significantly matched the video model for nine of the participants ($p$<.05, permutation test, see Methods for details; participants: 3-4, 8-13, 17 and the p-value for the rest of the participants was less than .25).
+Furthermore, the RMSD values were significantly correlated to hand annotated memory performance across participants (Pearson's $r$(16)=-.57, $p$=.016).
+Thus, a closer match between the video and recall event models was related to better recall performance.
+
+Next, we tested whether participants who recalled more events were also more precise in their recollections.
+For each participant, we computed the correlation between each recall event and its matching video event (only for the events which they recalled).
+This resulted in a single number for each recalled event indexing how similar the recall event was to its matching movie event (i.e the ``precision'' of the recall).
+We then averaged the correlations within participant.
+In line with our prediction, there was a strong correlation between hand annotated memory performance and precision suggesting that participants who remembered more events also remembered them more veridically (Pearson's $r$(16)=.74, $p$=.0006).
+Then, we considered the distinctiveness of each recall event.
+That is, how uniquely a recall event matched a given video event compared to all other video events.
+We hypothesized that participants with high memory performance might describe each event in a more distinctive way (relative to those with lower memory performance who might describe events in a more general way).
+To this end, we computed a `distinctiveness' score for each participant (i.e.
+1 - the correlation between a recall event and all non-matching video events).
+Then, we averaged this measure over recall events within participant.
+We found that participants with higher hand annotated memory performance also had higher distinctiveness scores (Pearson's $r$(16)=.8, $p$=.0001).
+
+Lastly, we tested whether participants with better memory performance were also more likely to remember the events in order.
+For each participant, we computed the Spearman rank correlation between the order of events that the participant recalled and the actual order of events (filtering events that were actually recalled).
+We found that participants who recalled more events also recalled more of them in order (Pearson's $r$(16)=.5, $p$=.04).
+In summary, we found that better memory performance was associated with more precise, distinctive and ordered recalls.
+
+\section{Naturalistic extensions of classic list-learning analyses}
+Just like in a traditional ``free-recall'' list-learning experiment where participants view a list of words and then verbally recall them, our video-recall matching analysis approach affords us the ability to analyze memory in the same way.
+The recalled events can be treated as ``items'' analogous to words recalled in a list-learning study.
+In our first set of analyses, we sought to characterize memory performance/dynamics by extending classic analyses originally designed for list-learning experiments to more naturalistic settings.
+First, we asked whether the estimated number of recall events ($k$) by participant was related to hand-annotated accuracy as published in Chen et al.
+(2017).
+We found a strong positive correlation where subjects with a greater number of recall events also had better overall memory performance (Pearson's $r$(16)=.67, $p$=.003).
+Then, we considered how participants initiated the recall sequence (known in the literature as the `probability of first recall' or `PFR').
+We found that participants tended to initiate their recall sequences with the first few events (Supp.
+Fig.~\ref{fig:list-learning}a), which is qualitatively very similar to previously published list learning experiments (REF?).
+Next, we considered another well-studied memory measure in the list-learning literature, the lag conditional response probability curve (or lag-CRP) ~\citep{Kaha96}.
+The result suggests a strong bias to transition sequentially events in the forward direction (Supp.
+Fig.~\ref{fig:list-learning}b).
+Finally, we assessed memory performance for each event in the video as a function of its serial position during encoding (Supp.
+Fig.~\ref{fig:list-learning}c).
+We found that there was substantial variability in memory for the different events (STAT).
+We also considered two additional across-participant measures of recall that characterize memory organization: temporal clustering and semantic clustering.
+We found that participants who clustered in time also recalled a greater number of events (Pearson's $r$(16)=.62, $p$=.007).
+Next, we assessed semantic clustering.
+We found that the semantic clustering score was related to memory performance across participants (Pearson's $r$(16)=.55, $p$=.02).
+Thus, participants who organized their recalls with respect to the semantic information contained in the scene had better memory performance.
+
 \begin{suppfigure}[t!]
@@
 
+\section{Supplemental Methods}
+
+\subsection{Characterizing memory performance using traditional approaches}
+\textbf{Overall Accuracy.}  To get an overall measure of the quantity of information recalled, we computed the proportion of sucessfully recalled events by counting the number of unique recall events identified by the HMM model and dividing by the total number of video events.
+We performed this analysis for each participant separately.
+
+\textbf{Probability of first recall (PFR).}  The (PFR) analysis represents the probability that an item will be recalled first as a function of its serial position during encoding.
+We initialized a \# of participants (17) by \# of video events (34) matrix.
+Then for each participant, we found the index of the video event that was recalled first and filled in that index in the matrix with a 1.
+Finally, we averaged over the rows of the matrix, resulting in a 1 by 34 array representing the proportion of subject that recalled an event as a function of serial position during encoding.
+
+\textbf{Lag conditional probability curve (lag-CRP).} The lag-CRP represents the probability that the next item recalled will be of lag $i$ from the just recalled item.
+For each recall transition, we computed the lag between the current recall event and the next recall event, normalizing by the total number of possible transitions.
+This resulted in a \# of participants (17) by lags (-33:+33) matrix.
+We averaged over the rows of this matrix to get a group-averaged lag-CRP.
+
+\textbf{Serial position curve (SPC).} The SPC represents the proportion of participants that remember an item as a function of its serial position during encoding.
+We initialized a \# of participants (17) by \# of video events (34) matrix.
+Then, for each recall event (and each participant), we found the index of the video event that was recalled and filled it in with a 1.
+This resulted in a matrix where 1s indicate the successful recall of an event in serial position $n$ and zeros indicate the lack of recall for that event.
+Lastly, we averaged over the rows of the matrix to get a 1 by 34 array representing the proportion of subjects that recalled an event as a function of its serial position.
+
+\textbf{Temporal clustering.} Temporal clustering measures the extent to which participants group their recall responses according to encoding position.
+For instance, if the participant recalled each item in the presentation order, this would result in a score of 1.
+If the participant recalled randomly with respect to presentation order, this would result in a score of ~.5.
+For each event transition (and separately for each participant), we computed the rank similarity (euclidean distance) between the presentation position  of the current and next recall events.
+The scores were then averaged within participant to get a single number representing the extent of temporal clustering exhibited by a given participant.
+
+\textbf{Semantic clustering.} Similar to temporal clustering, semantic clustering measures the extent to which participants group their recall responses according to semantic similarity.
+Here, we are using the topic vectors for each event as a proxy for its semantic content.
+Thus, similarity between the semantic content for two events can be computed by correlating their respective topic vectors.
+For instance, if each consecutive recall was the next most similar event (in terms of its s), this would result in a score of ~1.
+If the participant recalled randomly with respect to semantic similarity, this would result in a score of ~.5.
+For each event transition (and separately for each participant), we computed the rank similarity (correlation distance) between the current recall event and the next recall event.
+The scores were then averaged within participant to get a single number representing the extent of semantic clustering exhibited by a given participant.
+
 \end{document}

### 2018-08-20 paper/main.tex
checking in edits

@@
 how the contents relate/change over time).
-Naturalistic experiences are (typically) autocorrelated in space and time on short timescales: the contents of an experience are often similar from moment to moment and change gradually.
+Naturalistic experiences are autocorrelated in space and time on short timescales: the contents of an experience are often similar from moment to moment and change gradually.
 For example, many of us spend our mornings/evenings at home and much of our days at work (e.g.
@@
 walking through a doorway) \citep{Radv12}.
-Prior research suggests that these sharp transitions (coined in the literature as ``event boundaries'') during an experience may serve to descretize/organize our memories into ``events'' \citep{Radv12, RadvZack11, BrunEtal18, HeusEtal18, ClewDava18}.
+Prior research suggests that these sharp transitions (coined in the literature as ``event boundaries'') during an experience may serve to descretize our memories into ``events'' \citep{Radv12, RadvZack11, BrunEtal18, HeusEtal18, ClewDava18}.
 Short timescale autocorrelations in the contents of an experience are thought associatively link information in memory, while more drastic changes in perceptual or semantic aspects of an experience may lead to discontinuities in memory \citep{HeusEtal18, BrunEtal18, Radv12}.
@@
 In this study, we analyzed an open dataset in which participants view and then verbally recall an episode of the BBC series \textit{Sherlock} \citep{ChenEtal17}.
-To capture the flow of the video's content (i.e.
-the storyline), we developed a novel computational approach based on topic modeling \citep{BleiEtal03} and hidden Markov models \citep{Rabi89, BaldEtal17}.
+To capture the temporal structure of the video, we developed a novel computational approach based on topic modeling \citep{BleiEtal03} and hidden Markov models \citep{Rabi89, BaldEtal17}.
 This model casts naturalistic stimuli as high-dimensional topic ``trajectories'', whereby the theme of each moment of the video is represented as a topic vector.
 Successful remembering entails verbally ``traversing'' the path formed by the stimulus topic trajectory as closely as possible.
-We hypothesized that successful memory for a naturalistic stimulus is given by a recall trajectory that 1) has temporal structure similar to the stimulus 2) closely follows the path of the stimulus trajectory and 3) covers the majority of the stimulus path.
+We hypothesized that successful memory for a naturalistic stimulus is given by a recall trajectory that closely follows the path (and covers the entirety) of the stimulus trajectory.
 
@@
 We fit a topic model \citep{BleiEtal03} to hand-annotated text descriptions of scenes from the video.
-The text descriptions contained details of the scene such as the characters, location, and a short summary of the scene (see Fig.\ref{fig:schematic} for example text, see \ref{sec:methods} for analysis details).
+The text descriptions contained details of the scene such as the characters, location, and a short summary of the scene (see Fig.~\ref{fig:schematic} for example text, see Methods for analysis details).
 As depicted in Fig.~\ref{fig:model}a, the topic vectors are sparse and change slowly over time.
-Furthermore, there are clear transitions from one topic `state' to the next, possibly indexing scene transitions in the stimulus.
+Furthermore, there are clear transitions from one topic ``state'' to the next (possibly indexing scene transitions in the stimulus).
 To get a better handle on this temporal structure, we computed a timepoints (1976) by timepoints (1976) correlation matrix of the video model (Fig.~\ref{fig:model}c).
@@
 From each participant's recall model, we computed a timepoint (68 to 294) by timepoints by timepoints (range: 68 to 294) correlation matrix.
-An example participant's (\#13) correlation matrix is plotted in Fig.~\ref{fig:model}d).
-Like the video model, each participants' recall correlation matrix exhibited a strong block-diagonal structure (Supp.
+An example participant's (\#13) correlation matrix is plotted in Fig.~\ref{fig:model}d.
+Like the video model, each participant's recall correlation matrix exhibited a strong block-diagonal structure (Supp.
 Fig.~\ref{fig:corrmats})).
@@
 As described above, a striking feature of both the video and recall correlation matrices is a strong, block structure along the diagonal of the matrices (see Fig.~\ref{fig:model}c,d).
-We hypothesized that this structure might arise from transient stability in "theme" of the video/recall (i.e.
-``events'').
+We hypothesized that this structure might arise from transient stability in the "theme" of the video/recall.
 We reasoned that specific events described by a participant could be ``matched'' to specific video events by computing the similarity between their topic vectors.
@@
 Our algorithm determined 34 events for the video model and a range of values (range: 8-27; mean: 15.41; SD: 5.6) for the recall models (see Methods for details on choosing an optimal $k$ value).
-The events discovered for the model and a representative participant (\#13) are highlighted as yellow rectangles outlining blocks along the diagonal of the correlation matrices (Fig.~\ref{fig:model}b,d).
+The events discovered for the video model and a representative participant's recall model are highlighted as yellow rectangles outlining blocks along the diagonal of the correlation matrices (Fig.~\ref{fig:model}b,d).
 
 Next, we created a video ``event model'' by averaging together neighboring topic vectors that the were classified to be in the same event, resulting in an events (34) by topics (100) matrix (Fig.~\ref{fig:model}e).
-We performed the same procedure for the recall matrices (see Fig.~\ref{fig:model}f for example).
+We performed the same procedure for the recall matrices (Fig.~\ref{fig:model}f).
 Then, we computed the correlation between video and recall event models, resulting in a video events (34) by recall events (8-27, depending on the participant) correlation matrix (Fig~\ref{fig:model}g).
@@
 \subsubsection{The shape of a naturalistic experience is preserved in recall}
-Classic approaches to studying free recall in episodic memory (such as overall accuracy and serial position curve) focus on the quantity of information recalled.
-More recent metrics (such as lag-CRP, semantic and temporal clustering) go further to describe list-level memory organization.
+Classic approaches to studying free recall in episodic memory (such as overall accuracy and serial position curve) focus on the quantity of information recalled \citep{Murd62a}.
+More recent metrics (such as lag-CRP, semantic and temporal clustering) go further to describe list-level memory organization \citep{Kaha96, }.
 However, none of these approaches capture the rich autocorrelated structure inherent in naturalistic stimuli and associated recall of those experiences.
@@
 
-To visualize the relationship between the video and recall event models, we embedded them into a 2D space (using the UMAP dimensionality reduction algorithm, for details see \ref{sec:methods}) where the points represent video/recall events and the distance between them represents their similarity/distance in ``topic space'' (Fig.~\ref{fig:trajectory}a).
+To visualize the relationship between the video and recall event models, we embedded them into a 2D space (using the UMAP dimensionality reduction algorithm, for details see Methods) where the points represent video/recall events and the distance between them represents their similarity/distance in ``topic space'' (Fig.~\ref{fig:trajectory}a).
 We observed that visually, it appears that the two models have a very similar temporal evolution and geometric structure.
@@
 Thus participants' recalls followed the same path as the video model (Fig.~\ref{fig:trajectory}b), suggesting the shape of the stimulus was preserved despite idiosyncratic differences between participants in their recalls.
-
-\subsubsection{Additional measures of naturalistic recall}
-Representing the video and verbal recall as events in ``topic space'' also affords us the ability to characterize the quality of recall in a more fine-grained and nuanced way than what was previously possible.
-In addition to the shape analyses described above, we quantified the distance between each video event and its matching recall event (``precision''), the the distance between a video event and all non-matching recall events (``distinctiveness'') and the temporal order of the recall events (``order'').
-All three of these metrics were correlated to hand-annotated memory performance across participants ($p$<.05, see Supplemental Materials Section 1 for details).
-
-Just like in a traditional ``free-recall'' list-learning experiment where participants view a list of words and then verbally recall them, our video-recall matching analysis approach affords us the ability to analyze memory in the same way.
-We considered 6 classic list-learning analyses: overall accuracy, probability of first recall, lag-conditional response probability, serial position curve, temporal clustering and semantic clustering.
-Extending these classic list-learning analyses to naturalistic stimuli allows to directly compare trial- and naturalistic-based recall studies (see Supplemental Materials Section 2 for details).
 
@@
 A notable advantage of representing naturalistic stimuli/memory using this approach is that the event models can be mapped back to the language used to fit the model(s).
-This allows for analysis and visualization of the language used when participant's recounted their experiences.
-In this next analysis, we 1) quantified the memorability of each video event and 2) used memorability to plot the top words for the most and least memorable scenes, and also aggregated across the entire video.
+This allows for analysis (and visualization) of the language used when participants' recounted their experiences.
+In this next analysis, we 1) quantified the memorability of each video event and 2) used memorability to plot the top words for the most and least memorable scenes.
 
@@
 Then, we extracted the top 200 words and created ``wordles'' representing the most memorable themes in the video.
-The result reveal that scenes containing ``Sherlock'' and ``John'' were highly memorable, and also scenes containing words such as ``medium'', ``street'' and ``baker'' (Fig.~\ref{fig:topics}b).
+The results reveal that scenes containing ``Sherlock'' and ``John'' were highly memorable, and also scenes containing words such as ``medium'', ``street'' and ``baker'' (Fig.~\ref{fig:topics}b).
 To find words related to the least memorable scenes, we inverted the memorability weights and again extracted the top 200 words.
@@
 These analyses shed light on the contents of naturalistic stimuli and accompanying memories, and highlight the flexibility in transforming between human and machine readable representations of the data afforded by our modeling approach.
+
+\subsubsection{Additional measures of naturalistic recall}
+Representing the video and verbal recall as events in ``topic space'' also affords us the ability to characterize the quality of recall in a more fine-grained and nuanced way than what was previously possible.
+We quantified the distance between each video event and its matching recall event (``precision''), the the distance between a video event and all non-matching recall events (``distinctiveness'') and the temporal order of the recall events (``order'').
+All three of these metrics were correlated to hand-annotated memory performance across participants (p$<$.05, see Supplemental Materials Section 1 for details).
+
+Just like in a traditional ``free-recall'' list-learning experiment where participants view a list of words and then verbally recall them, our video-recall matching analysis approach affords us the ability to analyze memory in the same way.
+We considered 6 classic list-learning analyses: overall accuracy, probability of first recall \citep{Hoga75, HowaKaha99; Lami99}, lag-conditional response probability \citep{Kaha96, HowaKaha99}, serial position curve \citep{Murd62a}, temporal clustering and semantic clustering \citep{HowaKaha02, PolyEtal09}.
+Extending these classic list-learning analyses to naturalistic stimuli allows to directly compare trial- and naturalistic-based recall studies (see Supplemental Materials Section 2 for details).
 
@@
 
-Historically, human memory reseachers have focussed on measuring the quantity of information recovered by an individual (i.e.
-the proportion correct) under different experimental conditions.
+Here, we find that participants Historically, human memory reseachers have focussed on measuring the quantity of information recovered by an individual (e.g.
+the ``proportion correct'') under different experimental conditions.
 However, for real world experiences this is not a well-defined task.
@@
 
-\textbf{Temporal clustering.} Temporal clustering measures the extent to which participants group their recall responses according to encoding position.
+\textbf{Temporal clustering.} Temporal clustering measures the extent to which participants group their recall responses according to encoding position ~\citep{PolyEtal09}.
 For instance, if the participant recalled each item in the presentation order, this would result in a score of 1.
@@
 
-\textbf{Semantic clustering.} Similar to temporal clustering, semantic clustering measures the extent to which participants group their recall responses according to semantic similarity.
+\textbf{Semantic clustering.} Similar to temporal clustering, semantic clustering measures the extent to which participants group their recall responses according to semantic similarity ~\citep{PolyEtal09}.
 Here, we are using the topic vectors for each event as a proxy for its semantic content.

### 2018-08-20 paper/main.tex
saving progress

@@
 While our life experiences often change gradually, they can also change rapidly (e.g.
-walking through a doorway) \citep{Radv12}.
-Prior research suggests that these sharp transitions (coined in the literature as ``event boundaries'') during an experience may serve to descretize our memories into ``events'' \citep{Radv12, RadvZack11, BrunEtal18, HeusEtal18, ClewDava18}.
-Short timescale autocorrelations in the contents of an experience are thought associatively link information in memory, while more drastic changes in perceptual or semantic aspects of an experience may lead to discontinuities in memory \citep{HeusEtal18, BrunEtal18, Radv12}.
+walking through a doorway) \citep{RadvZack17}.
+Prior research suggests that these sharp transitions (coined in the literature as ``event boundaries'') during an experience may serve to descretize our memories into ``events'' \citep{RadvZack17, BrunEtal18, HeusEtal18, ClewDava17}.
+Short timescale autocorrelations in the contents of an experience are thought associatively link information in memory, while more drastic changes in perceptual or semantic aspects of an experience may lead to discontinuities in memory \citep{HeusEtal18, BrunEtal18}.
 There is now compelling evidence that event boundaries can influence memory organization when learning sequences of items \citep{HeusEtal18, DuBrDava13}, during navigation \citep{BrunEtal18}, and narrative comprehension \citep{ZwaaRadv98, EzzyDava11}.
@@
 Classic approaches to studying free recall in episodic memory (such as overall accuracy and serial position curve) focus on the quantity of information recalled \citep{Murd62a}.
-More recent metrics (such as lag-CRP, semantic and temporal clustering) go further to describe list-level memory organization \citep{Kaha96, }.
-However, none of these approaches capture the rich autocorrelated structure inherent in naturalistic stimuli and associated recall of those experiences.
+More recent metrics (such as lag-CRP, semantic and temporal clustering) go further to describe list-level memory organization \citep{Kaha96, PolyEtal09}.
+However, these approaches do not capture the rich temporal structure inherent in naturalistic stimuli and associated recall of those experiences.
 In the next set of analyses, we test the hypothesis that successful recall of a naturalistic stimulus entails recovering the trajectory of a stimulus.
@@
 
-To visualize the relationship between the video and recall event models, we embedded them into a 2D space (using the UMAP dimensionality reduction algorithm, for details see Methods) where the points represent video/recall events and the distance between them represents their similarity/distance in ``topic space'' (Fig.~\ref{fig:trajectory}a).
+To visualize the relationship between the video and recall event models, we embedded them into a 2D space using the UMAP dimensionality reduction algorithm ~\citep{McInHeal18}, where the points represent video/recall events and the distance between them represents their similarity/distance in ``topic space'' (Fig.~\ref{fig:trajectory}a).
 We observed that visually, it appears that the two models have a very similar temporal evolution and geometric structure.
@@
 Just like in a traditional ``free-recall'' list-learning experiment where participants view a list of words and then verbally recall them, our video-recall matching analysis approach affords us the ability to analyze memory in the same way.
-We considered 6 classic list-learning analyses: overall accuracy, probability of first recall \citep{Hoga75, HowaKaha99; Lami99}, lag-conditional response probability \citep{Kaha96, HowaKaha99}, serial position curve \citep{Murd62a}, temporal clustering and semantic clustering \citep{HowaKaha02, PolyEtal09}.
+We considered 6 classic list-learning analyses: overall accuracy, probability of first recall \citep{Hoga75, HowaKaha99, Lami99}, lag-conditional response probability \citep{Kaha96, HowaKaha99}, serial position curve \citep{Murd62a}, temporal clustering and semantic clustering \citep{HowaKaha02, PolyEtal09}.
 Extending these classic list-learning analyses to naturalistic stimuli allows to directly compare trial- and naturalistic-based recall studies (see Supplemental Materials Section 2 for details).
@@
 hidden Markov modelling, averaging within event, etc).
-While many of the parameter combination elicited moderately high correlations, the best choice was 100 topics, 50 video segments and 10 recall sentences.
+While many of the parameter combination elicited moderately high correlations, the optimal choice was 100 topics, 50 video segments and 10 recall sentences.
 
@@
 To capture this structure, we fit the video and each recall model using a hidden Markov model (HMM).
-Given a number of states or events ($k$), the HMM recovers a set of labels that segments consecutive timepoints into $k$ events (REF markov paper).
+Given a number of states or events ($k$), the HMM recovers a set of labels that segments consecutive timepoints into $k$ events ~\citep{Rabi89, BaldEtal17}.
 To implement this analysis, we used the Brainiak toolbox \citep{BaldEtal17}.
@@
 \subsubsection{Visualizing the video and recall event models}
-To better understand the temporal structure of the video event model (34 events by 100 topics) and the recall event models (8-27 events by 100 topics), we used a technique called UMAP to reduce the ``topic-space'' from 100 dimensions down to 2 dimensions (REF).
+To better understand the temporal structure of the video event model (34 events by 100 topics) and the recall event models (8-27 events by 100 topics), we used a technique called UMAP ~\citep{McInHeal18} to reduce the ``topic-space'' from 100 dimensions down to 2 dimensions.
 UMAP is a nonlinear dimensionality reduction technique which models the manifold of the data with a fuzzy topological structure, and then searches for a (2D) projection of the data that has the closest equivalent fuzzy topological structure.
@@
 To test whether the distribution of angles was significantly non-uniform (i.e.
-displayed a preferred direction across participants), we performed a Rayleigh test on the angles (REF).
+displayed a preferred direction across participants), we performed a Rayleigh test on the angles.
 Arrows where the Rayleigh test was significant are displayed in color while non-significant tests are displayed in gray with lower opacity.
-Note that it was not computationally tractible to perform this analysis in the original 100 dimensional space because the number of grid points grows factorially with the number of topic dimensions.
 
@@
  We created word clouds to visualize the themes contained in the recall events.
-One component of the topic model comprises a words (XX) by topics (100) matrix (R), where the rows represent the weight of a given word in each topic.
+One component of the topic model comprises a words (2117) by topics (100) matrix (R), where the rows represent the weight of a given word in each topic.
 To find words that were maximally associated with a particular event vector, we computed the dot product between R and v, which gave a 1 by \# of words vector where the values represent the `activation' of each of in the event.

### 2018-08-20 paper/main.tex
intro edits

@@
 how the contents relate/change over time).
-Naturalistic experiences are autocorrelated in space and time on short timescales: the contents of an experience are often similar from moment to moment and change gradually.
-For example, many of us spend our mornings/evenings at home and much of our days at work (e.g.
+For instance, naturalistic experiences are autocorrelated in space and time on short timescales.
+In other words, the contents of an experience are often similar from moment to moment and change gradually.
+As an example, many of us spend our mornings/evenings at home and much of our days at work (e.g.
 an office).
@@
 The spatial contexts before and after lunch are highly similar, but separated in time.
-Thus, while evaluating the ability to recall specific contents of an experience has been a fruitful way to learn about human memory, another important dimension to consider is the temporal structure of the remembered experience, and how the temporal structure of the memory relates to the original experience.
+Thus, while evaluating the ability to recall the isolated elements of an experience has been a fruitful way to learn about human memory, another important dimension to consider is the temporal structure of the remembered experience, and how the temporal structure of the memory relates to the original experience.
 However, these recurrent and gradually changing temporal dynamics are not typically present in traditional memory studies, but are likely critical if we wish to understand how our memory systems remember our life experiences.
 
-While our life experiences often change gradually, they can also change rapidly (e.g.
+While our experiences often change gradually, they can also change rapidly (e.g.
 walking through a doorway) \citep{RadvZack17}.
@@
 Short timescale autocorrelations in the contents of an experience are thought associatively link information in memory, while more drastic changes in perceptual or semantic aspects of an experience may lead to discontinuities in memory \citep{HeusEtal18, BrunEtal18}.
+In other words, the interplay between stable and transient temporal dynamics may impose structure on memories for those experiences.
 There is now compelling evidence that event boundaries can influence memory organization when learning sequences of items \citep{HeusEtal18, DuBrDava13}, during navigation \citep{BrunEtal18}, and narrative comprehension \citep{ZwaaRadv98, EzzyDava11}.
-However, whether people naturally recount their experiences in a way that is structured around events is not known.
+However, whether people verbally recount their experiences in a way that is structured around events has not been established.
 
@@
 This model casts naturalistic stimuli as high-dimensional topic ``trajectories'', whereby the theme of each moment of the video is represented as a topic vector.
-Successful remembering entails verbally ``traversing'' the path formed by the stimulus topic trajectory as closely as possible.
+In this framework, successful remembering entails verbally ``traversing'' the path formed by the stimulus topic trajectory as closely as possible.
 We hypothesized that successful memory for a naturalistic stimulus is given by a recall trajectory that closely follows the path (and covers the entirety) of the stimulus trajectory.

### 2018-08-20 paper/main.tex
results edits

@@
 As depicted in Fig.~\ref{fig:model}a, the topic vectors are sparse and change slowly over time.
-Furthermore, there are clear transitions from one topic ``state'' to the next (possibly indexing scene transitions in the stimulus).
+Furthermore, there are clear transitions from one topic ``state'' to the next, possibly indexing scene transitions in the stimulus.
 To get a better handle on this temporal structure, we computed a timepoints (1976) by timepoints (1976) correlation matrix of the video model (Fig.~\ref{fig:model}c).
@@
 Like the video model, each participant's recall correlation matrix exhibited a strong block-diagonal structure (Supp.
-Fig.~\ref{fig:corrmats})).
+Fig.~\ref{fig:corrmats}).
 Notably, this suggests that participants recounted the video in discriminable segments, likely related to the recall of specific events from the video.
@@
 
-\subsubsection{Segmenting the video and recall models into `events'}
+\subsubsection{Segmenting the video and recall models into ``events''}
 As described above, a striking feature of both the video and recall correlation matrices is a strong, block structure along the diagonal of the matrices (see Fig.~\ref{fig:model}c,d).
-We hypothesized that this structure might arise from transient stability in the "theme" of the video/recall.
-We reasoned that specific events described by a participant could be ``matched'' to specific video events by computing the similarity between their topic vectors.
-In other words, the video event that is most similar (i.e.
-correlated) to a particular recall event is the event that the participant is most likely describing.
+We hypothesized that this structure might arise from transient stability in the "theme" of both the video and of participants' memory for the video.
+We hypothesized that specific events described by a participant could be ``matched'' to specific video events by computing the similarity (i.e.
+correlation) between their topic vectors.
+In other words, the video event that is most similar to a particular recall event is the event that the participant is most likely describing.
 To test this idea, we segmented the video and recall models in $k$ events (i.e.
@@
 Notably, this matrix displayed high correlation values along the diagonal and low correlations in the off-diagonal cells.
-This suggests that on average, participants were able to recapitulate the events in the episode in a specific, highly descriminable way.
+This suggests that on average, participants were able to recapitulate the events in the episode in a specific and highly descriminable way.
 
@@
 More recent metrics (such as lag-CRP, semantic and temporal clustering) go further to describe list-level memory organization \citep{Kaha96, PolyEtal09}.
-However, these approaches do not capture the rich temporal structure inherent in naturalistic stimuli and associated recall of those experiences.
+However, these approaches cannot (and were not designed to) capture the rich temporal dynamics inherent in naturalistic stimuli and associated recall of those experiences.
 In the next set of analyses, we test the hypothesis that successful recall of a naturalistic stimulus entails recovering the trajectory of a stimulus.
@@
 \caption{\small \textbf{Video and recall trajectory plots.} A).
-2-dimensional embedding of the video events model.
+2-dimensional embedding of the video events model (reduced with UMAP algorithm).
 The arrows indicate the forward direction of the video events.
@@
 To assess consistency in the direction of the recall transition across participants, we performed a Rayleigh test (p$<$.001, corrected at p$<$.05 using permutation procedure described in Methods).
-Thus participants' recalls followed the same path as the video model (Fig.~\ref{fig:trajectory}b), suggesting the shape of the stimulus was preserved despite idiosyncratic differences between participants in their recalls.
+Notably, all video events fell within the path formed by the video events.
+Thus, participants' recalls followed the same path as the video model (Fig.~\ref{fig:trajectory}b), suggesting the shape of the stimulus was preserved despite idiosyncratic differences between participants in their recalls.
+
+%NOTE: it feels like we need some more supporting evidence that the shape of the video and the recall trajectories are related.
+one possibility would be to add the analysis where i compute the distance between each recall event and the line formed by each video transition per subject.
+the result is that hand annotated memory correlates to this distance, suggesting that subjects who better capture the shape also have better memory on average.
 

### 2018-08-20 paper/main.tex
discussion edits

@@
 \label{sec:discussion}
-Studying episodic memory is commonly distilled down to a process of matching specific moments of a past experience with specific mnemonic outcomes.
-In traditional trial-based free recall and item recognition experiments, individual stimuli encountered during encoding are typically labeled as ``remembered'' or ``forgotten'' depending on whether the stimulus is recalled/recognized during a subsequent test.
+Studying human memory is commonly distilled down to a process of matching specific moments of a past experience with specific mnemonic outcomes.
+In traditional trial-based free recall experiments, individual stimuli encountered during encoding are typically labeled as ``remembered'' or ``forgotten'' depending on whether the stimulus is recalled/recognized during a subsequent test.
 While this approach has advanced our understanding of human memory immensely, it does not translate well to naturalistic experiences.
@@
 Thus, there is not a ``one-to-one'' mapping between naturalistic experiences and their mnemonic counterparts.
+For example, remembering the patterns and colors of each person's shirt in a crowd might be considered as excellent recall in a standard memory task setup.
+But if the rememberer failed to note that the people in the crowd were gathered for their surprise birthday party, then they would have missed the "point" of the experience.
+
 Our topic modeling approach, whereby we consider the broad ``theme'' present in different moments of participants' experiences and their memories for those experiences, affords us the ability to flexibly and accurately characterize memory for naturalistic experiences.
 This approach allows us to quantify which moments from the past and the current recounted experience match in terms of their thematic content and critically, our ability to perform this matching does not require participants to use any specific overlapping words.
-
-Here, we find that participants Historically, human memory reseachers have focussed on measuring the quantity of information recovered by an individual (e.g.
-the ``proportion correct'') under different experimental conditions.
-However, for real world experiences this is not a well-defined task.
-For example, remembering the patterns and colors of each person's shirt in a crowd might be considered as excellent recall in a standard memory task setup.
-But if the rememberer failed to note that the people in the crowd were gathered for their surprise birthday party, then they would have missed the "point" of the experience.
 Our work characterizes experience by comparing the overall ``shape'' of a dynamic stimulus and a memory.
@@
 
-More broadly, these findings have strong implications for how we assess memory in other naturalistic contexts, like the in the classroom or in a doctor's office.
-Whereas instructors often measure students' performance using metrics such as the proportion of correctly answered questions, our work suggests that this approach might miss the ``forrest for the trees''.
-True learning is about understanding the key concepts (i.e.
+In addition to providing a way to capture the shape of an experience, this method affords the ability to quantify the particular contents of memory.
+Whereas traditional approaches abstract over the content (e.g.
+percent correct), Our approach allows one to quantify which aspects of an experience are memorable and which fail to stick.
+This aspect of our approach opens the door for a much richer characterization of memory that considers not just how much information was recalled, but the particular details of that information as well.
+
+More broadly, these findings have strong implications for how we assess memory in other naturalistic contexts, such as the classroom or in a doctor's office.
+Whereas tests often measure students' performance using metrics such as the proportion of correctly answered questions, our work suggests that this approach might miss the ``forrest for the trees''.
+We view ``true learning'' as understanding the key concepts (i.e.
 understanding key themes in the learned content and how they relate) rather than about regurgitating the greatest number of facts.
@@
 For example, given a short recall interval, would participants intuitively gravitate towards coarser samplings that still outline the basic shape of the movie's topic trajectory?
-Or if participants were told that their narrations would be played back to other participants (cite Hasson work), would that change the resolution or shape of their recalls?
-And over successive recountings of the same sequence of events, how do the shapes of the trajectories change?
-For example, loss of detail would result in a "smoothing our" of the trajectories with each new retelling.
-This could be quantified using our topic trajectory approach.
+Or if participants were told that their narrations would be played back to other participants ~\citep{ZadbEtal16}, would that change the resolution or shape of their recalls?
+And over successive recountings of the same sequence of events or with more elapsed time between encoding and recall, how do the shapes of the trajectories change?
+For example, loss of detail would result in a "smoothing out" of the trajectories with each new retelling.
 
-%NOTE: could be useful to add a 'where this might break down' section
+While we view this work as a major advance in characterizing and understanding human memory, as with any approach there are limitations.
+First, the approach relies on having a ``good'' model of the stimulus (e.g.
+one that describes the video in the same way as participant's recall it), which is currently only achievable by a human hand-annotating each moment of the video.
+To increase the scalability of this approach, future work could explore automated methods for extracting meaning from videos ~\citep{YuEtal16}.
+Another potential limitation is that by its nature, the model extracts the ``gist'' of scenes from the video.
+This provides desirable flexibility (e.g.
+participants can use different combinations of words to describe the scenes), but this comes at the expense of capturing specific details.
+Thus, a future direction of this work will be to increase sensitivity to details (while maintaining flexibility).
 
-To conclude, let's revisit the question of what it means to remember something.
-We assert that episodic memories are not veridical snapshots of the past, and so we should stop treating (and modelling) them as such.
-Rather, episodic memories are better described as echoes of a prior experience that are shaped by other past experiences as well as the current context.
+To conclude, we'll revisit the question of what it means to remember something.
+Our view is that ``successful remembering'' is about recovering the ``trajectory'' of an experience, rather than the ability to recognize/recall any of its particular isolated details.
+Decades of research suggest that episodic memories are not veridical and context-free snapshots of the past, and so treating (and modelling) them as such is overly simplistic at best (and counterproductive at worst).
+While its undeniable that these models have been immensely useful in advancing our understanding of the fundamental principles that govern human memory, they are severely limited in their ability to explain memory for naturalistic experiences.
+Real-life experiences are highly structured in time, and so our experiments and models of memory should account for this fact.
 

### 2018-08-20 paper/main.tex
small change to discussion

@@
 Decades of research suggest that episodic memories are not veridical and context-free snapshots of the past, and so treating (and modelling) them as such is overly simplistic at best (and counterproductive at worst).
-While its undeniable that these models have been immensely useful in advancing our understanding of the fundamental principles that govern human memory, they are severely limited in their ability to explain memory for naturalistic experiences.
-Real-life experiences are highly structured in time, and so our experiments and models of memory should account for this fact.
+While its undeniable that these models have been useful in advancing our understanding of human memory, they are severely limited in their ability to explain memory for naturalistic experiences.
+Real-life experiences are highly structured in time, and so to have a complete understanding of the human memory system, our experiments and models of memory should not ignore this fact.
+This work provides a methodological and theoretic advance in our understanding of what it means to remember.
 

### 2018-08-20 paper/main.tex
a few more edits to results

@@
 We performed the same procedure for the recall matrices (Fig.~\ref{fig:model}f).
-Then, we computed the correlation between video and recall event models, resulting in a video events (34) by recall events (8-27, depending on the participant) correlation matrix (Fig~\ref{fig:model}g).
+Then, we computed the correlation between video and recall event models, resulting in a video events (34) by recall events (8-27, depending on the participant) correlation matrix (Fig~\ref{fig:model}g for example, Supp.
+Fig~\ref{fig:matchmats} for all participants).
 These matrices represent the similarity (correlation) between each video event and each recall event (for each participant).
@@
 Real-life experiences are highly structured in time, and so to have a complete understanding of the human memory system, our experiments and models of memory should not ignore this fact.
-This work provides a methodological and theoretic advance in our understanding of what it means to remember.
+This work provides a methodological and theoretical advance in our understanding of what it means to remember.
 

### 2018-08-20 paper/main.tex
edits to results

@@
 For each scene, we considered the following features: scene details (i.e.
-a sentence or two describing what happened in that scene, space (indoor or outdoor), name of all the characters in the scene, name of the character in focus, name of the character speaking, location, camera angle, music presence, and words on the screen.
-We concatenated the text for all of these features within each segment, creating a 'bag of words' describing each scene.
+a sentence or two describing what happened in that scene), space (indoor or outdoor), name of all the characters in the scene, name of the character in focus, name of the character speaking, location, camera angle, music presence, and words on the screen.
+We concatenated the text for all of these features within each segment, creating a ``bag of words'' describing each scene.
 We then transformed the text descriptions into overlapping windows of 50 scene segments.
@@
 We trained our model using these overlapping text samples using scikit-learn's (version 0.19.1) `CountVectorizer' and `LatentDirichletAllocation' classes.
-First, the text was transformed into a vector of word counts (default parameters).
+First, the text was transformed into a vector of word counts (after removing English stopwords).
 This gave a word count vector for each scene in the video.
-Then, the word count vectors were used to fit a topic model (topics=100, method=batch).
+Then, the word count vectors were used to fit a topic model (topics=100, method=`batch').
 We transformed the text descriptions using the model resulting in a scenes (1000) by topics (100) matrix.
@@
 While many of the parameter combination elicited moderately high correlations, the optimal choice was 100 topics, 50 video segments and 10 recall sentences.
+%NOTE: I did run this analysis, but before that i arbitrarily selected some parameters that ended up being very close to the best.
+The reason I bring this up is that the correlations between some of the memory metrics (k, precision, distinctiveness) and hand annotated accuracy could be biased because we searched for the optimal parameters.
+Its not `the same' measure, but they are related to each other, so we'll have to be extra careful not to over interpret the correlations in this study.
 
 \subsubsection{Extracting events using a hidden Markov model}
-The topic model timepoint-by-timepoint correlation matrices all exhibited a block-diagonal structure (with small off-diagonal values), suggesting that the models were comprised of a number of sequential `states' (or events).
+The topic model timepoint-by-timepoint correlation matrices all exhibited a block-diagonal structure (with small off-diagonal values), suggesting that the models were comprised of a number of sequential `states' (or events, e.g.
+Supp.
+Fig.~\ref{fig:corrmats}).
 To capture this structure, we fit the video and each recall model using a hidden Markov model (HMM).
@@
 
-Our metric for choosing the `best fitting' HMM was to choose the model with the $k$ value that maximized the ratio of the average `within-event' correlation values (i.e.
+Our metric for choosing the ``best fitting'' HMM was to choose the model with the $k$ value that maximized the ratio of the average `within-event' correlation values (i.e.
 the correlation values for blocks of consecutive timepoints the model identified as one event) and the average `across-event' correlation (i.e.
@@
 We chose $k$ values separately for the video model and for each recall model.
-Then, using the best $k$ values, We fit a separate HMM for each topic model.
+Then, using the best $k$ values, We fit a separate HMM for the video and each recall model.
 Finally, we averaged over timepoints identified to be in the same event resulting in a events by topics matrix for the video model and each of the recall models.
-%
+
 \subsubsection{Matching recall events to video events}
-To figure out which video event each recall event referred to, we correlated the video events model and each recall events model.
+To estimate which video event each recall event referred to, we correlated the video events model and each recall events model.
 This resulted in a video events (34) by recall events (8-27) correlation matrix (for each participant) which contains the similarity between each video event and each recall event.
@@
 \subsubsection{Visualizing the video and recall event models}
-To better understand the temporal structure of the video event model (34 events by 100 topics) and the recall event models (8-27 events by 100 topics), we used a technique called UMAP ~\citep{McInHeal18} to reduce the ``topic-space'' from 100 dimensions down to 2 dimensions.
+To visualize the temporal structure of the video event model (34 events by 100 topics) and the recall event models (8-27 events by 100 topics), we used a technique called UMAP ~\citep{McInHeal18} to reduce the ``topic-space'' from 100 dimensions down to 2 dimensions.
 UMAP is a nonlinear dimensionality reduction technique which models the manifold of the data with a fuzzy topological structure, and then searches for a (2D) projection of the data that has the closest equivalent fuzzy topological structure.
@@
 \subsubsection{Vector field analysis}
-To quantify (and visualize) the flow of recall from event to event, we performed a vector field analysis.
+To quantify the flow of recall from event to event, we performed a vector field analysis.
 We tiled the 2D topic space (x, y: -6 to 6 by .25) with an evenly spaced grid.
-For each grid point, we drew a square around the point (height/width=.5).
+For each grid point, we drew a circle around the point (radius=.5).
 Then, we tested whether any line segments (formed by event recall transitions) passed through this area of the topic space.
@@
 To test whether the distribution of angles was significantly non-uniform (i.e.
-displayed a preferred direction across participants), we performed a Rayleigh test on the angles.
+displayed a preferred direction across participants), we performed a Rayleigh test on the angles (p$<$.001, FDR-corrected at p$<$.05 using Benjamani-Hochberg procedure).
 Arrows where the Rayleigh test was significant are displayed in color while non-significant tests are displayed in gray with lower opacity.

### 2018-08-20 paper/main.tex
added some software references

@@
 For example, the first text sample comprised the text from the first 50 segments, the second comprised the text from n+1:n+51, and so on.
-We trained our model using these overlapping text samples using scikit-learn's (version 0.19.1) `CountVectorizer' and `LatentDirichletAllocation' classes.
+We trained our model using these overlapping text samples with scikit-learn's (version 0.19.1) `CountVectorizer' and `LatentDirichletAllocation' classes \citep{PedrEtal11} implemented using our high-dimensional visualization/analysis software, Hypertools \citep{HeusEtal18}.
 First, the text was transformed into a vector of word counts (after removing English stopwords).
@@
 Given a number of states or events ($k$), the HMM recovers a set of labels that segments consecutive timepoints into $k$ events ~\citep{Rabi89, BaldEtal17}.
-To implement this analysis, we used the Brainiak toolbox \citep{BaldEtal17}.
+To implement this analysis, we used the Brainiak toolbox \citep{BaldEtal17, Brainiak}.
 

### 2018-08-20 paper/main.tex
supplemental edits

@@
 For example, the first text sample comprised the text from the first 50 segments, the second comprised the text from n+1:n+51, and so on.
-We trained our model using these overlapping text samples with scikit-learn's (version 0.19.1) `CountVectorizer' and `LatentDirichletAllocation' classes \citep{PedrEtal11} implemented using our high-dimensional visualization/analysis software, Hypertools \citep{HeusEtal18}.
+We trained our model using these overlapping text samples with scikit-learn's (version 0.19.1) `CountVectorizer' and `LatentDirichletAllocation' classes \citep{PedrEtal11} implemented using our high-dimensional visualization/analysis software, Hypertools \citep{HeusEtal17a}.
 First, the text was transformed into a vector of word counts (after removing English stopwords).
@@
 Fig.~\ref{fig:list-learning}c).
-We found that there was substantial variability in memory for the different events (STAT).
 We also considered two additional across-participant measures of recall that characterize memory organization: temporal clustering and semantic clustering.

### 2018-08-21 paper/main.tex
blur figure 1, edits to supp materials

@@
 \centering
-\includegraphics[width=1\textwidth]{figs/1_analysis_schematic.pdf}
+\includegraphics[width=1\textwidth]{figs/1_analysis_schematic_blur.pdf}
 \caption{\small \textbf{Schematic of the analysis approach.} For each scene in the video, text descriptions were generated by hand.
@@
 For example, given a short recall interval, would participants intuitively gravitate towards coarser samplings that still outline the basic shape of the movie's topic trajectory?
-Or if participants were told that their narrations would be played back to other participants ~\citep{ZadbEtal16}, would that change the resolution or shape of their recalls?
+Or if participants were told that their narrations would be played back to other participants ~\citep{ZadbEtal17}, would that change the resolution or shape of their recalls?
 And over successive recountings of the same sequence of events or with more elapsed time between encoding and recall, how do the shapes of the trajectories change?
@@
 
+\section{Naturalistic extensions of classic list-learning analyses}
+Just like in a traditional ``free-recall'' list-learning experiment where participants view a list of words and then verbally recall them, our video-recall matching analysis approach affords us the ability to analyze memory in the same way.
+The recalled events can be treated as ``items'' analogous to words recalled in a list-learning study.
+Here, we sought to characterize memory performance/dynamics by extending classic analyses originally designed for list-learning experiments to more naturalistic settings.
+First, we asked whether the estimated number of recall events ($k$) by participant was related to hand-annotated accuracy as published in Chen et al.
+(2017).
+We found a strong positive correlation where subjects with a greater number of recall events also had better overall memory performance (Pearson's $r$(16)=.67, $p$=.003).
+Then, we considered how participants initiated the recall sequence (known in the literature as the `probability of first recall' or `PFR').
+We found that participants tended to initiate their recall sequences with the first few events (Supp.
+Fig.~\ref{fig:list-learning}a), which is qualitatively very similar to previously published list learning experiments ~\citep{HowaKaha99}.
+Next, we considered another well-studied memory measure in the list-learning literature, the lag conditional response probability curve (or lag-CRP) ~\citep{Kaha96}.
+The result suggests a strong bias to transition sequentially events in the forward direction (Supp.
+Fig.~\ref{fig:list-learning}b).
+Finally, we assessed memory performance for each event in the video as a function of its serial position during encoding (Supp.
+Fig.~\ref{fig:list-learning}c).
+We did not observe the classic ``primacy'' and ``recency'' pattern which is prevalent in the literature ~\citep{Murd62a}.
+We also considered two additional across-participant measures of recall that characterize memory organization: temporal clustering and semantic clustering.
+We found that participants who clustered in time also recalled a greater number of events (Pearson's $r$(16)=.62, $p$=.007).
+Next, we assessed semantic clustering.
+We found that the semantic clustering score was related to memory performance across participants (Pearson's $r$(16)=.55, $p$=.02).
+Thus, participants who organized their recalls with respect to the semantic information contained in the scene had better memory performance.
+
 \section{Additional measures of naturalistic memory}
@@
 To assess significance, we performed a permutation test where we circularly shifted the recall model (10000 times) and recomputed the RMSD.
-The recall model significantly matched the video model for nine of the participants ($p$<.05, permutation test, see Methods for details; participants: 3-4, 8-13, 17 and the p-value for the rest of the participants was less than .25).
+The recall model significantly matched the video model for nine of the participants ($p$<.05, participants: 3-4, 8-13, 17 and the p-value for the rest of the participants was less than .25).
 Furthermore, the RMSD values were significantly correlated to hand annotated memory performance across participants (Pearson's $r$(16)=-.57, $p$=.016).
@@
 In line with our prediction, there was a strong correlation between hand annotated memory performance and precision suggesting that participants who remembered more events also remembered them more veridically (Pearson's $r$(16)=.74, $p$=.0006).
+
 Then, we considered the distinctiveness of each recall event.
@@
 In summary, we found that better memory performance was associated with more precise, distinctive and ordered recalls.
-
-\section{Naturalistic extensions of classic list-learning analyses}
-Just like in a traditional ``free-recall'' list-learning experiment where participants view a list of words and then verbally recall them, our video-recall matching analysis approach affords us the ability to analyze memory in the same way.
-The recalled events can be treated as ``items'' analogous to words recalled in a list-learning study.
-In our first set of analyses, we sought to characterize memory performance/dynamics by extending classic analyses originally designed for list-learning experiments to more naturalistic settings.
-First, we asked whether the estimated number of recall events ($k$) by participant was related to hand-annotated accuracy as published in Chen et al.
-(2017).
-We found a strong positive correlation where subjects with a greater number of recall events also had better overall memory performance (Pearson's $r$(16)=.67, $p$=.003).
-Then, we considered how participants initiated the recall sequence (known in the literature as the `probability of first recall' or `PFR').
-We found that participants tended to initiate their recall sequences with the first few events (Supp.
-Fig.~\ref{fig:list-learning}a), which is qualitatively very similar to previously published list learning experiments (REF?).
-Next, we considered another well-studied memory measure in the list-learning literature, the lag conditional response probability curve (or lag-CRP) ~\citep{Kaha96}.
-The result suggests a strong bias to transition sequentially events in the forward direction (Supp.
-Fig.~\ref{fig:list-learning}b).
-Finally, we assessed memory performance for each event in the video as a function of its serial position during encoding (Supp.
-Fig.~\ref{fig:list-learning}c).
-We also considered two additional across-participant measures of recall that characterize memory organization: temporal clustering and semantic clustering.
-We found that participants who clustered in time also recalled a greater number of events (Pearson's $r$(16)=.62, $p$=.007).
-Next, we assessed semantic clustering.
-We found that the semantic clustering score was related to memory performance across participants (Pearson's $r$(16)=.55, $p$=.02).
-Thus, participants who organized their recalls with respect to the semantic information contained in the scene had better memory performance.
 
@@
 \section{Supplemental Methods}
-
-\subsection{Characterizing memory performance using traditional approaches}
+\subsection{List-learning analyses}
 \textbf{Overall Accuracy.}  To get an overall measure of the quantity of information recalled, we computed the proportion of sucessfully recalled events by counting the number of unique recall events identified by the HMM model and dividing by the total number of video events.
@@
 
+\subsection{Additional measures of naturalistic memory}
+\textbf{Precision.} This measure gives us an indication of the specific match between a video event and recall event, where values approaching 1 are highly precise and lower values are inprecise.
+We defined ``precision'' as the correlation between a recall event and its matching (i.e.
+argmax) video event.
+
+\textbf{Distinctiveness.} Distinctiveness quantifies how similar a recall event is to all non-matching video events.
+It provides a metric of how uniquely a particular recall event describes a particular video event.
+To compute it, a given recall event is correlated to all video events, the argmax is removed and the rest of the values are averaged.
+The resulting value is subtracted from 1 such that larger values indicate a more distinctive recall event.
+
 \end{document}

### 2018-08-21 paper/main.tex
added a few more references

@@
 walking through a doorway) \citep{RadvZack17}.
-Prior research suggests that these sharp transitions (coined in the literature as ``event boundaries'') during an experience may serve to descretize our memories into ``events'' \citep{RadvZack17, BrunEtal18, HeusEtal18, ClewDava17}.
-Short timescale autocorrelations in the contents of an experience are thought associatively link information in memory, while more drastic changes in perceptual or semantic aspects of an experience may lead to discontinuities in memory \citep{HeusEtal18, BrunEtal18}.
+Prior research suggests that these sharp transitions (coined in the literature as ``event boundaries'') during an experience may serve to descretize our memories into ``events'' \citep{RadvZack17, BrunEtal18, HeusEtal18, ClewDava17, EzzyDava11, DuBrDava13}.
+Short timescale autocorrelations in the contents of an experience are thought associatively link information in memory, while more drastic changes in perceptual or semantic aspects of an experience may lead to discontinuities in memory \citep{HeusEtal18, BrunEtal18, EzzyDava11, DuBrDava13}.
 In other words, the interplay between stable and transient temporal dynamics may impose structure on memories for those experiences.

### 2018-08-21 paper/main.tex
edit fig 1 legend
updated model figure, edit to trjectory fig legend

@@
 We fit a topic model to the moment-by-moment video text descriptions and transformed participant's verbal recall transcripts using this same model.
-The bar charts display the resulting topic model weights for the video (in blue) and recall (in orange) for three example topic dimensions.}
+The bar charts display the resulting topic model weights for the video (in blue) and recall (in green) for three example topic dimensions.}
 \label{fig:schematic}
@@
 The arrows represent the group-average direction of all recall event transitions (i.e.
-a line segment connecting two consecutive recall event vectors) that intersected a box (width=.25) centered on the origin of the arrow.}
+a line segment connecting two consecutive recall event vectors) that intersected a circle (radius=.5) centered on the origin of the arrow.}
 \label{fig:trajectory}

### 2018-08-21 paper/main.tex
formatted stats

@@
 We created a grid of evenly spaced points (.25 units) in the 2D ``topic space''.
-For each point on the grid, we drew a circle (radius=.25) around the point and grouped together all recall transitions that intersected the circle (across subjects).
+For each point on the grid, we drew a circle (radius=.5) around the point and grouped together all recall transitions that intersected the circle (across subjects).
 To visualize the average angle, we converted each transition angle to a unit vector and then averaged the vectors together.
-To assess consistency in the direction of the recall transition across participants, we performed a Rayleigh test (p$<$.001, corrected at p$<$.05 using permutation procedure described in Methods).
+To assess consistency in the direction of the recall transition across participants, we performed a Rayleigh test ($p<.001$, corrected at $p<.05$ using permutation procedure described in Methods).
 Notably, all video events fell within the path formed by the video events.
@@
 We quantified the distance between each video event and its matching recall event (``precision''), the the distance between a video event and all non-matching recall events (``distinctiveness'') and the temporal order of the recall events (``order'').
-All three of these metrics were correlated to hand-annotated memory performance across participants (p$<$.05, see Supplemental Materials Section 1 for details).
+All three of these metrics were correlated to hand-annotated memory performance across participants ($p<.05$, see Supplemental Materials Section 1 for details).
 
@@
 \subsection{Participants and Experimental Design}
-Participants ($n$=17) viewed \textit{A Study in Pink}, a 50 minute episode of the BBC series, \textit{Sherlock}.
+Participants ($n=17$) viewed \textit{A Study in Pink}, a 50 minute episode of the BBC series, \textit{Sherlock}.
 Immediately upon completion of the video, participants were instructed to (verbally) recount the events in the video in their original order and in as much detail as possible.
@@
 To test whether the distribution of angles was significantly non-uniform (i.e.
-displayed a preferred direction across participants), we performed a Rayleigh test on the angles (p$<$.001, FDR-corrected at p$<$.05 using Benjamani-Hochberg procedure).
+displayed a preferred direction across participants), we performed a Rayleigh test on the angles ($p<.001$, FDR-corrected at $p<.05$ using Benjamani-Hochberg procedure).
 Arrows where the Rayleigh test was significant are displayed in color while non-significant tests are displayed in gray with lower opacity.
@@
 (2017).
-We found a strong positive correlation where subjects with a greater number of recall events also had better overall memory performance (Pearson's $r$(16)=.67, $p$=.003).
+We found a strong positive correlation where subjects with a greater number of recall events also had better overall memory performance (Pearson's $r(16)=.67, p=.003$).
 Then, we considered how participants initiated the recall sequence (known in the literature as the `probability of first recall' or `PFR').
@@
 We also considered two additional across-participant measures of recall that characterize memory organization: temporal clustering and semantic clustering.
-We found that participants who clustered in time also recalled a greater number of events (Pearson's $r$(16)=.62, $p$=.007).
+We found that participants who clustered in time also recalled a greater number of events (Pearson's $r(16)=.62, p=.007$).
 Next, we assessed semantic clustering.
-We found that the semantic clustering score was related to memory performance across participants (Pearson's $r$(16)=.55, $p$=.02).
+We found that the semantic clustering score was related to memory performance across participants (Pearson's $r(16)=.55, p=.02$).
 Thus, participants who organized their recalls with respect to the semantic information contained in the scene had better memory performance.
@@
 To assess significance, we performed a permutation test where we circularly shifted the recall model (10000 times) and recomputed the RMSD.
-The recall model significantly matched the video model for nine of the participants ($p$<.05, participants: 3-4, 8-13, 17 and the p-value for the rest of the participants was less than .25).
-Furthermore, the RMSD values were significantly correlated to hand annotated memory performance across participants (Pearson's $r$(16)=-.57, $p$=.016).
+The recall model significantly matched the video model for nine of the participants ($p<.05$, participants: 3-4, 8-13, 17 and the p-value for the rest of the participants was less than .25).
+Furthermore, the RMSD values were significantly correlated to hand annotated memory performance across participants (Pearson's $r(16)=-.57, p=.016$).
 Thus, a closer match between the video and recall event models was related to better recall performance.
@@
 We then averaged the correlations within participant.
-In line with our prediction, there was a strong correlation between hand annotated memory performance and precision suggesting that participants who remembered more events also remembered them more veridically (Pearson's $r$(16)=.74, $p$=.0006).
+In line with our prediction, there was a strong correlation between hand annotated memory performance and precision suggesting that participants who remembered more events also remembered them more veridically (Pearson's $r(16)=.74, p=.0006$).
 
@@
 Then, we averaged this measure over recall events within participant.
-We found that participants with higher hand annotated memory performance also had higher distinctiveness scores (Pearson's $r$(16)=.8, $p$=.0001).
+We found that participants with higher hand annotated memory performance also had higher distinctiveness scores (Pearson's $r(16)=.8, p=.0001$).
 
@@
 For each participant, we computed the Spearman rank correlation between the order of events that the participant recalled and the actual order of events (filtering events that were actually recalled).
-We found that participants who recalled more events also recalled more of them in order (Pearson's $r$(16)=.5, $p$=.04).
+We found that participants who recalled more events also recalled more of them in order (Pearson's $r(16)=.5, p=.04$).
 In summary, we found that better memory performance was associated with more precise, distinctive and ordered recalls.

### 2018-08-23 paper/main.tex
supp mat formatting
moved refs above methods
JRM abstract edits

@@
 \usepackage{graphicx}
-% \usepackage{amsmath}
-% \newcommand{\rpm}{\raisebox{.2ex}{$\scriptstyle\pm$}}
-% \DeclareMathOperator*{\argmax}{arg\,max}
 \usepackage{newfloat}
@@
 
-\title{Capturing the shape of our experiences and how we remember them}
-\author{Andrew C. Heusser \& Jeremy R. Manning}
-% \affiliation{Dartmouth College}
+\title{How is experience transformed into memory?}
+\author{Andrew C. Heusser and Jeremy R. Manning\\Department of Psychological and Brain Sciences, Dartmouth College, Hanover, NH 03755, USA\\Corresponding author: jeremy.r.manning@dartmouth.edu}
 
@@
 
-\section{Abstract}
-{
+\begin{abstract}
 The human memory system is adept at cataloging the rich dynamics of ongoing experience.
-A defining feature of our everyday experiences is that they unfold in a structured and predictable manner.
-This temporal structure gives each of our experiences (and thus our memories for those experiences) a unique shape.
-However, temporal structure is typically absent (or severly impoverished) in traditional trial-based memory experiments.
-As a consequence, our understanding of how the temporal structure (i.e.
-the shape) of our experiences influences memorability and memory organization is limited.
-In this study, we investigate how people verbally recount a video by characterizing and relating the thematic dynamics, or ``trajectories,'' of the stimulus and participants' recalls.
-Using a novel approach based on topic modelling, we found that despite substantial variability in the quantity of information recalled across participants as well as the particular words used to describe the experience, the overall shape of the stimulus was recapitulated by most of the participants.
+A defining feature of our everyday experiences is that, despite the rich complexities of real-world experiences, they unfold in a structured and often predictable manner.
+This structure gives each of our experiences (and thus our memories for those experiences) a unique `shape' with respect to how it unfolds in the relevant representational space.
+However, temporal structure is typically absent (or severely impoverished) in traditional trial-based  experiments.
+As a consequence, our understanding of how the temporal structure (i.e., the shape) of our experiences influences memorability and memory organization is limited.
+In this study, we investigate how people verbally recount a video by characterizing and relating the thematic dynamics, or ``trajectories,'' of the video to participants' later recounting of the narrative.
+Using a novel approach that leverages topic modeling and Hidden Markov Models, we found that, despite substantial variability in the quantity of information recalled across participants as well as the particular words used to describe the experience, the overall shape of the stimulus was recapitulated by nearly every participant.
 These findings provide a window into which aspects of naturalistic experiences must be preserved, and which might be more flexible, in considering whether and how those experiences are remembered.
+\end{abstract}
 
-\section{Introduction}
+\section*{Introduction}
 
@@
 Human memory studies typically assess memory for the elements within an experience, such as the people, places and things encountered.
-However, real life experiences can also be described in terms of their temporal structure (i.e.
-how the contents relate/change over time).
+However, real life experiences can also be described in terms of their temporal structure (i.e., how the contents relate/change over time).
 For instance, naturalistic experiences are autocorrelated in space and time on short timescales.
 In other words, the contents of an experience are often similar from moment to moment and change gradually.
-As an example, many of us spend our mornings/evenings at home and much of our days at work (e.g.
-an office).
+As an example, many of us spend our mornings/evenings at home and much of our days at work (e.g.\ an office).
 While the specific happenings within these contexts differ, they are often highly correlated (and thus predictable) over time.
@@
 
-While our experiences often change gradually, they can also change rapidly (e.g.
-walking through a doorway) \citep{RadvZack17}.
+While our experiences often change gradually, they can also change rapidly (e.g.\ walking through a doorway) \citep{RadvZack17}.
 Prior research suggests that these sharp transitions (coined in the literature as ``event boundaries'') during an experience may serve to descretize our memories into ``events'' \citep{RadvZack17, BrunEtal18, HeusEtal18, ClewDava17, EzzyDava11, DuBrDava13}.
@@
 A timepoints (1976) by topics (100) matrix representing the video stimulus.
-Each row represents the most likely mixture of topics for a given timepoint (i.e.
-topic weights).
+Each row represents the most likely mixture of topics for a given timepoint (i.e., topic weights).
 Each column represents a different topic.
@@
 We hypothesized that this structure might arise from transient stability in the "theme" of both the video and of participants' memory for the video.
-We hypothesized that specific events described by a participant could be ``matched'' to specific video events by computing the similarity (i.e.
-correlation) between their topic vectors.
+We hypothesized that specific events described by a participant could be ``matched'' to specific video events by computing the similarity (i.e., correlation) between their topic vectors.
 In other words, the video event that is most similar to a particular recall event is the event that the participant is most likely describing.
-To test this idea, we segmented the video and recall models in $k$ events (i.e.
-states) using a hidden Markov model ~\citep{BaldEtal17}.
+To test this idea, we segmented the video and recall models in $k$ events (i.e., states) using a hidden Markov model ~\citep{BaldEtal17}.
 Our algorithm determined 34 events for the video model and a range of values (range: 8-27; mean: 15.41; SD: 5.6) for the recall models (see Methods for details on choosing an optimal $k$ value).
@@
 These matrices represent the similarity (correlation) between each video event and each recall event (for each participant).
-To determine which video event a particular recall event was most likely describing, we computed the index of the video event with the highest correlation to the recall event (i.e.
-the argmax).
+To determine which video event a particular recall event was most likely describing, we computed the index of the video event with the highest correlation to the recall event (i.e., the argmax).
 This is depicted in Fig.~\ref{fig:model}g as the cells highlighted with a yellow border.
@@
 The directional lines connecting the points represent the true video event order.
-The arrows represent the group-average direction of all recall event transitions (i.e.
-a line segment connecting two consecutive recall event vectors) that intersected a circle (radius=.5) centered on the origin of the arrow.}
+The arrows represent the group-average direction of all recall event transitions (i.e., a line segment connecting two consecutive recall event vectors) that intersected a circle (radius=.5) centered on the origin of the arrow.}
 \label{fig:trajectory}
@@
 B).
-Wordles (top 200 words) representing a weighted average of video event topic vectors weighted by event memorability (e.g.
-the correlation values in A).
+Wordles (top 200 words) representing a weighted average of video event topic vectors weighted by event memorability (e.g.\ the correlation values in A).
 The top wordle (green) contains words from the most remembered events and the bottom (red) contains words from least memorable events.
@@
 
-\section{Discussion}
+\section*{Discussion}
 \label{sec:discussion}
@@
 In addition to providing a way to capture the shape of an experience, this method affords the ability to quantify the particular contents of memory.
-Whereas traditional approaches abstract over the content (e.g.
-percent correct), Our approach allows one to quantify which aspects of an experience are memorable and which fail to stick.
+Whereas traditional approaches abstract over the content (e.g.\ percent correct), Our approach allows one to quantify which aspects of an experience are memorable and which fail to stick.
 This aspect of our approach opens the door for a much richer characterization of memory that considers not just how much information was recalled, but the particular details of that information as well.
@@
 Whereas tests often measure students' performance using metrics such as the proportion of correctly answered questions, our work suggests that this approach might miss the ``forrest for the trees''.
-We view ``true learning'' as understanding the key concepts (i.e.
-understanding key themes in the learned content and how they relate) rather than about regurgitating the greatest number of facts.
+We view ``true learning'' as understanding the key concepts (i.e., understanding key themes in the learned content and how they relate) rather than about regurgitating the greatest number of facts.
 In addition to educational contexts, our approach may provide unique metrics that can be used to assist in the diagnosis of a memory disorder, and other psychiatric disorders that influence memory.
@@
 While we view this work as a major advance in characterizing and understanding human memory, as with any approach there are limitations.
-First, the approach relies on having a ``good'' model of the stimulus (e.g.
-one that describes the video in the same way as participant's recall it), which is currently only achievable by a human hand-annotating each moment of the video.
+First, the approach relies on having a ``good'' model of the stimulus (e.g.\ one that describes the video in the same way as participant's recall it), which is currently only achievable by a human hand-annotating each moment of the video.
 To increase the scalability of this approach, future work could explore automated methods for extracting meaning from videos ~\citep{YuEtal16}.
 Another potential limitation is that by its nature, the model extracts the ``gist'' of scenes from the video.
-This provides desirable flexibility (e.g.
-participants can use different combinations of words to describe the scenes), but this comes at the expense of capturing specific details.
+This provides desirable flexibility (e.g.\ participants can use different combinations of words to describe the scenes), but this comes at the expense of capturing specific details.
 Thus, a future direction of this work will be to increase sensitivity to details (while maintaining flexibility).
@@
 
-\section{Methods}
+\pagebreak
+\bibliography{memlab}
+
+\pagebreak
+\section*{Methods}
 \label{sec:methods}
@@
 First, the video was manually segmented into 1000 scenes, and a collection of descriptive features was manually transcribed.
-For each scene, we considered the following features: scene details (i.e.
-a sentence or two describing what happened in that scene), space (indoor or outdoor), name of all the characters in the scene, name of the character in focus, name of the character speaking, location, camera angle, music presence, and words on the screen.
+For each scene, we considered the following features: scene details (i.e., a sentence or two describing what happened in that scene), space (indoor or outdoor), name of all the characters in the scene, name of the character in focus, name of the character speaking, location, camera angle, music presence, and words on the screen.
 We concatenated the text for all of these features within each segment, creating a ``bag of words'' describing each scene.
@@
 We transformed the text descriptions using the model resulting in a scenes (1000) by topics (100) matrix.
-The scene descriptions often spanned multiple timepoints (i.e.
-TRs).
+The scene descriptions often spanned multiple timepoints (i.e., TRs).
 To account for this, we expanded the video model by copying the rows of the model for as many timepoints that the scene description spanned.
@@
 To chose these parameter values, we performed a grid search where the range of possible parameter values was 1, 5, 10, 25, 50, 100, 200, and 500.
-Our optimization objective was defined as the correlation between the hand annotated memory performance and the root mean squared distance between the video model and the recall model before any further processing (e.g.
-hidden Markov modelling, averaging within event, etc).
+Our optimization objective was defined as the correlation between the hand annotated memory performance and the root mean squared distance between the video model and the recall model before any further processing (e.g.\ hidden Markov modelling, averaging within event, etc).
 While many of the parameter combination elicited moderately high correlations, the optimal choice was 100 topics, 50 video segments and 10 recall sentences.
@@
 \subsubsection{Extracting events using a hidden Markov model}
-The topic model timepoint-by-timepoint correlation matrices all exhibited a block-diagonal structure (with small off-diagonal values), suggesting that the models were comprised of a number of sequential `states' (or events, e.g.
-Supp.
+The topic model timepoint-by-timepoint correlation matrices all exhibited a block-diagonal structure (with small off-diagonal values), suggesting that the models were comprised of a number of sequential `states' (or events, e.g.\ Supp.
 Fig.~\ref{fig:corrmats}).
@@
 
-Our metric for choosing the ``best fitting'' HMM was to choose the model with the $k$ value that maximized the ratio of the average `within-event' correlation values (i.e.
-the correlation values for blocks of consecutive timepoints the model identified as one event) and the average `across-event' correlation (i.e.
-the rest of the correlation values).
+Our metric for choosing the ``best fitting'' HMM was to choose the model with the $k$ value that maximized the ratio of the average `within-event' correlation values (i.e., the correlation values for blocks of consecutive timepoints the model identified as one event) and the average `across-event' correlation (i.e., the rest of the correlation values).
 Additionally, we included a penalty parameter that was proportional to the smoothing of the model that preferred models with smaller $k$ values.
@@
 We collected all line segments that passed through a given section of topic space (collapsing across participants).
-To plot the average direction of the line segments (i.e.
-the arrows for each grid point in ~\ref{fig:trajectory}b), we converted each of them to unit vectors and then averaged.
+To plot the average direction of the line segments (i.e., the arrows for each grid point in ~\ref{fig:trajectory}b), we converted each of them to unit vectors and then averaged.
 For grid points where the direction was consistent (across all participants contributing to that point), the length of the arrow approaches 1, whereas if the direction was random the length of the arrow approaches 0.
 Lastly, we converted each unit vector to an angle (in radians) by taking the inverse tangent of the x, y components of the vector.
-To test whether the distribution of angles was significantly non-uniform (i.e.
-displayed a preferred direction across participants), we performed a Rayleigh test on the angles ($p<.001$, FDR-corrected at $p<.05$ using Benjamani-Hochberg procedure).
+To test whether the distribution of angles was significantly non-uniform (i.e., displayed a preferred direction across participants), we performed a Rayleigh test on the angles ($p<.001$, FDR-corrected at $p<.05$ using Benjamani-Hochberg procedure).
 Arrows where the Rayleigh test was significant are displayed in color while non-significant tests are displayed in gray with lower opacity.
@@
 We then plotted the top 200 words for the top/bottom 3 recalled events.
-
-\bibliography{memlab}
 
@@
 
-\section{Naturalistic extensions of classic list-learning analyses}
+\section*{Naturalistic extensions of classic list-learning analyses}
 Just like in a traditional ``free-recall'' list-learning experiment where participants view a list of words and then verbally recall them, our video-recall matching analysis approach affords us the ability to analyze memory in the same way.
@@
 Here, we sought to characterize memory performance/dynamics by extending classic analyses originally designed for list-learning experiments to more naturalistic settings.
+
 First, we asked whether the estimated number of recall events ($k$) by participant was related to hand-annotated accuracy as published in Chen et al.
@@
 
-\section{Additional measures of naturalistic memory}
+\section*{Additional measures of naturalistic memory}
 To quantify the similarity between the video model and individual recall models, we considered a number of novel metrics.
@@
 We hypothesized that participants with high memory performance might describe each event in a more distinctive way (relative to those with lower memory performance who might describe events in a more general way).
-To this end, we computed a `distinctiveness' score for each participant (i.e.
-1 - the correlation between a recall event and all non-matching video events).
+To this end, we computed a `distinctiveness' score for each participant (i.e., 1 - the correlation between a recall event and all non-matching video events).
 Then, we averaged this measure over recall events within participant.
@@
 
-\section{Supplemental Methods}
+\section*{Supplemental Methods}
 \subsection{List-learning analyses}
@@
 \textbf{Precision.} This measure gives us an indication of the specific match between a video event and recall event, where values approaching 1 are highly precise and lower values are inprecise.
-We defined ``precision'' as the correlation between a recall event and its matching (i.e.
-argmax) video event.
+We defined ``precision'' as the correlation between a recall event and its matching (i.e., argmax) video event.
 

### 2018-08-23 paper/main.tex
working on intro

@@
 Using a novel approach that leverages topic modeling and Hidden Markov Models, we found that, despite substantial variability in the quantity of information recalled across participants as well as the particular words used to describe the experience, the overall shape of the stimulus was recapitulated by nearly every participant.
+Our findings suggest that assessing the degree of match between the shape of an experience and the subsequent retelling of that experience provides a much more nuanced view (compared with traditional methods, such as comparing the proportion of remembered details) into what it means to remember.
 These findings provide a window into which aspects of naturalistic experiences must be preserved, and which might be more flexible, in considering whether and how those experiences are remembered.
@@
 What does it mean to \textit{remember} something?
-In traditional episodic memory experiments \citep[e.g., list-learning or trial-based experiments;][]{Murd62a, Kaha96}, remembering is often cast as a binary operation: either an item is recalled or it isn't.
-More nuanced studies might incorporate self-reported confidence measures as a proxy for memory strength, or ask participants to discriminate between ``recollecting'' an experience or a feeling of ``familiarity'' \citep{Yone02}.
-However, characterizing and evaluating memory in more realistic contexts (e.g., telling a story to a friend about a movie you recently saw) is much more nuanced.
-Real-world recall is continuous, rather than binary.
-The specific words used to describe an experience have very little bearing on whether the experience is considered to have been ``remembered.''  Further, one might remember the gist of an experience but forget (or neglect to recount) particular details.
+In traditional episodic memory experiments \citep[e.g., list-learning or trial-based experiments;][]{Murd62a, Kaha96}, remembering is often cast as a binary operation: either a studied item is recalled or it isn't.
+More nuanced studies might incorporate self-reported confidence measures as a proxy for memory strength, or ask participants to discriminate between ``recollecting'' an experience or a general feeling of ``familiarity'' \citep{Yone02}.
+However, characterizing and evaluating memory in more realistic contexts (e.g., recounting a recent experience to a friend) concerns a much different set of criteria.
+First, eal-world recall is continuous, rather than binary.
+Second, the specific words used to describe an experience have very little bearing on whether the experience is considered to have been ``remembered.''  Third, one might remember the gist of an experience but forget (or neglect to recount) particular details.
 Or different people who share an experience might recount the experience with a similar level of detail, but the specific details that were remembered might vary across people.
-Which aspects of those recollections should be considered fundamental, and which are extraneous to the main story?
+Which aspects of those recollections should be considered fundamental to determining whether or how reliably an experience has been remembered?
+
+%JRM STOPPED INPUTTING EDITS HERE
 

### 2018-08-27 paper/main.tex
added back brain analyses and added paxtons control analyses and text

@@
 \title{How is experience transformed into memory?}
-\author{Andrew C. Heusser and Jeremy R. Manning\\Department of Psychological and Brain Sciences, Dartmouth College, Hanover, NH 03755, USA\\Corresponding author: jeremy.r.manning@dartmouth.edu}
+% \title{Capturing the transformation of experience into memory}
+\author{Andrew C. Heusser and Jeremy R. Manning\\Department of Psychological and Brain Sciences\\Dartmouth College, Hanover, NH 03755, USA\\Corresponding author: jeremy.r.manning@dartmouth.edu}
 
@@
 \centering
-\includegraphics[width=1\textwidth]{figs/1_analysis_schematic_blur.pdf}
+\includegraphics[width=1\textwidth]{figs/1_analysis_schematic_bw.pdf}
 \caption{\small \textbf{Schematic of the analysis approach.} For each scene in the video, text descriptions were generated by hand.
@@
 We fit a topic model \citep{BleiEtal03} to hand-annotated text descriptions of scenes from the video.
-The text descriptions contained details of the scene such as the characters, location, and a short summary of the scene (see Fig.~\ref{fig:schematic} for example text, see Methods for analysis details).
+The text descriptions contained details of the scene such as the characters, location, and a short summary of the scene (see Fig.~\ref{fig:schematic} for example text).
 As depicted in Fig.~\ref{fig:model}a, the topic vectors are sparse and change slowly over time.
@@
 This correlation matrix reveals that the model has a strong, block-diagonal structure with very low off-diagonal correlation values, suggesting the representations of each block are unique and highly descriminable.
+We found that the ``narrative details'' (e.g.
+a few sentences summarizing the specific happenings of the scene) of the video were the most important feature driving this model structure (see Supp.
+Fig.~\ref{fig:feature-importance}a).
 
@@
 An example participant's (\#13) recall model is plotted in Fig.~\ref{fig:model}b.
+Notably, participant \#13's recall model appears visually similar to the video model.
+Similar to the video model analysis (Supp.
+Fig.~\ref{fig:feature-importance}a), We found that the ``narrative details'' feature was most important for driving the video/recall relationship (Supp.
+Fig.~\ref{fig:feature-importance}b).
 Like the video model, topic vectors were sparse and changed gradually.
@@
 
-\begin{figure}[ht!]
+\begin{figure}[t!]
 \centering
@@
 
+\subsubsection{Brain regions that mirror the correlational structure of naturalistic stimuli and memories}.
 \begin{figure}[t!]
 \centering
-\includegraphics[width=1\textwidth]{figs/4_topics.pdf}
+\includegraphics[width=1\textwidth]{figs/4_brains_panels.pdf}
+\caption{\small \textbf{Video and recall model correlational structure searchlight analysis.} A) The correlation matrix representing the temporal structure of the video model.
+Below it is a surface plot of brain regions whose activity patterns mirrored the correlational structure of video model during viewing.
+B) The left matrix is S13's video-recall correlation matrix before warping.
+The yellow stars represent the path recovered by dynamic time warping.
+The right matrix is the result after warping.
+The same warping path was applied to the fMRI timeseries (separately for each participant).
+A surface plot of brain regions whose activity patterns mirrored the participant-specific recall correlation matrix.
+Significance threshold (p$<$.05) for both video and recall analyses derived from a permutation procedure by phase shifting the video model and recomputing the z-scores.}
+\label{fig:brainz}
+\end{figure}
+
+Previous work suggests that the brain may represent our experiences as ``events'' with different time scales in a nested hierarchy ~\citep{LernEtal11, ChenEtal17, BaldEtal17}.
+In this next analysis we asked: what brain regions mirror the event-like correlational structure of our topic-based video model during viewing?
+We used a searchlight procedure (see Methods for details) to identify regions whose timepoint-by-timepoint correlational structure matched the correlational structure of our model.
+This analysis revealed a network of regions including bilateral frontal and cingulate cortex (Fig.
+~\ref{fig:brainz}).
+Thus, these regions may play a role in maintaining information relevant to the narrative trajectory of the video.
+
+While each participant remembered roughly the same sequence of events, there were subtle idiosyncracies in the way each individual described the events.
+For example, the event by event similarity structure (e.g.
+the off-diagonal values of the recall correlation matrices) differed across individuals (Supp.
+Fig.~\ref{fig:corrmats}).
+We hypothesized that idiosyncracies in the recall dynamics across subjects might be related to the temporal structure of brain networks are representing the events during video viewing.
+In this analysis, we identified brain areas whose responses at the time of viewing exhibited the same (segmented) idiosyncratic dynamics that later appeared in that participants’ recalls.
+Using a procedure similar to the approach above (see Methods for details), we searched for regions whose correlational structure during viewing was related to the idiosyncratic structure of the participant's recall model.
+The resulting map suggests that the correlational structure of a network of brain regions including the ventromedial prefrontal cortex, anterior cingulate, and right medial temporal lobe mirror the idiosyncratic structure of participants'' recalls (Fig.
+~\ref{fig:brainz}).
+
+\begin{figure}[t!]
+\centering
+\includegraphics[width=1\textwidth]{figs/5_topics.pdf}
 \caption{\small \textbf{Analysis of topics by event memorability.} A).
-Group-averaged correlation between each video event and closest recall event (per subject).
+Group-averaged correlation between each video event and closest recall event.
 Error bars represent 95\% confidence intervals.
-B).
+Stars indicate top (green) and bottom (red) 3 remembered events across participants B).
 Wordles (top 200 words) representing a weighted average of video event topic vectors weighted by event memorability (e.g.\ the correlation values in A).
@@
 By contrast, the number of recalls could be captured by the "sampling frequency" along that trajectory-- but the number of recalls alone cannot tell us whether participants successfully recollected the meaning of the story by capturing the salient points of the narrative that define its main shape.
-
 In addition to providing a way to capture the shape of an experience, this method affords the ability to quantify the particular contents of memory.
@@
 This aspect of our approach opens the door for a much richer characterization of memory that considers not just how much information was recalled, but the particular details of that information as well.
+
+Prior work on neural responses during naturalistic experiences and recall has largely focused on identifying brain regions whose responses are reliably similar across individuals ~\citep{LernEtal11, SimoEtal16, ChenEtal17, BaldEtal17, ZadbEtal17}.
+This allows one to identify which regions might be processing or representing the stimulus, or retrieving details of the experience during recall.
+Our approach is fundamentally different.
+We ask: which brain regions during movie viewing match the movie structure and how individual participants will recall the movie later (in terms of the temporal correlations of their recall topic trajectory)?
+This latter approach highlights regions such as the medial prefrontal cortex (mPFC) and medial temporal lobes (MTL) that may respond in idiosyncratic ways across individuals, but that nonetheless play an important role in encoding experience into memory.
+In other work, the mPFC has been suggested to play a role in the representation of a ``schema'', or a network prior knowledge that is consistent with the current task ~\citep{KestEtal12}.
+One interpretation for mPFC's involvement in our work is that mPFC represents participant-specific relationships with the content of the video, and its representation during scene viewing is related to how a participant later describes the scene.
+MTL activity patterns also matched participant's recall, which is consistent with a large body of literature highlighting the role of the MTL in episodic memory encoding ~\citep{PallWagn02, DavaEtAl03, RangEtal04, Dava06}.
 
@@
 Real-life experiences are highly structured in time, and so to have a complete understanding of the human memory system, our experiments and models of memory should not ignore this fact.
-This work provides a methodological and theoretical advance in our understanding of what it means to remember.
+Our work provides a theoretical advance in our understanding of what it means to remember as well as a novel methodological tool to study it.
 
@@
 
+\subsection{fMRI analyses}
+Seventeen participants watched the first 50 minutes of Episode 1 of BBC's Sherlock.
+The video was split into two parts of approximately equal length (946 and 1030 TRs).
+All data were preprocessed and transformed to 3mm MNI space as described in ~\citep{ChenEtal17}.
+Data were z-scored across time at every voxel.
+6mm smoothing was applied.
+Files are cropped so that all video-viewing data are aligned across participants, and all recall data are aligned to the scene timestamps below.
+The cropping includes a constant 3-TR (4.5 sec) shift to correct for hemodynamic lag.
+
+\subsubsection{Searchlight analysis}
+Our multivariate analyses were designed to capture brain regions whose timepoint-by-timepoint correlational structure mirrors the correlational structure of the video model as well as participant-specific recall topic models during video viewing.
+We conducted a searchlight analysis (5x5x5 voxel cube) where for each cube, we correlated the model timepoint-by-timepoint correlation matrix with the neural correlation matrix.
+To aggregate across participants, we Fisher's z-transformed the correlations and then averaged.
+To assess significance, we recomputed this group analysis 100 times, but randomly phase shifted the model (by \# of timepoints - 1) by the same amount for each participant but different amounts for each permutation to build a null distribution of correlation values.
+Finally, we thresholded the group averaged correlation maps where the `real' correlation value for a given voxel exceeded the 95th percentile of the null distribution.
+To correct for non-linearities between the viewing time and recall time, for each participant we used dynamic time warping to temporally align the matrices.
+The algorithm recovers a path of coordinates that would bring the video and recall model in maximal temporal alignment.
+We used this path to warp the fMRI data and the recall model into temporal alignment (separately for each participant).
+
 \subsubsection{Topic vector word clouds}
@@
 \label{fig:matchmats}
+\end{suppfigure}
+
+\begin{suppfigure}[t!]
+\centering
+\includegraphics[width=1\textwidth]{figs/supp4_feature_value.pdf}
+\caption{\small \textbf{Impact of individual features on topic modeling analysis.} Contribution of each feature to model structure.
+Bars represent the correlation of a video model trained in the absence of a given feature to the model trained on all features.
+B).Contribution of each feature to video model/recall model relationship.
+The leftmost bar represents the across-subjects mean correlation between the video model and recall models trained on all features.
+Subsequent bars represent the same relationship between video and recall models trained in the absence of a given feature.
+Error bars are the standard error of the mean across subjects.}
+\label{fig:feature-importance}
 \end{suppfigure}
@@
 \section*{Supplemental Methods}
+\subsection{Quantifying the importance of features}
+To determine the contribution of each feature to the structure of the video model, we examined the similarity between the temporal structure of models trained in the absence of a single feature and that of our original (i.e.
+full) model.
+First, we iteratively removed one transcribed feature from the scene descriptions and constructed a timepoints (1976) by topis (100) matrix using a topic model fit to the remaining features.
+We then represented the original model as well as the new model’s temporal structure as a timepoints (1976) by timepoints (1976) correlation matrix.
+Finally, we vectorized these correlation matrices and correlated them to each other resulting in a single number (for each feature removed from the model) representing the similarity of the ``feature-removed'' models to the full model.
+
+In order to ascertain which features were important in relating the recall models to the video model, we similarly compared to the temporal structures of video and recall models deprived of a single feature at a time.
+For each feature removed, we transformed each subject’s recall transcript using a model trained on the feature-deprived video text windows (of 50 scene segments), and resampled the recall timeseries to match the shape of the movie model (1976 timepoints).
+We then represented the temporal structures of each subject’s recall model as timepoints (1976) by timepoints (1976) correlation matrices and computed the average correlation with the temporal structure of the video model (across subjects).
+
 \subsection{List-learning analyses}

### 2018-08-27 paper/main.tex
updated code and added one more ref

@@
 This latter approach highlights regions such as the medial prefrontal cortex (mPFC) and medial temporal lobes (MTL) that may respond in idiosyncratic ways across individuals, but that nonetheless play an important role in encoding experience into memory.
-In other work, the mPFC has been suggested to play a role in the representation of a ``schema'', or a network prior knowledge that is consistent with the current task ~\citep{KestEtal12}.
+In other work, the mPFC has been suggested to play a role in the representation of a ``schema'', or a network prior knowledge that is consistent with the current task ~\citep{KestEtal12, GilbMarl17}.
 One interpretation for mPFC's involvement in our work is that mPFC represents participant-specific relationships with the content of the video, and its representation during scene viewing is related to how a participant later describes the scene.

### 2018-08-28 paper/main.tex
added paxton to readme and paper
saving abstract and intro edits

@@
 \title{How is experience transformed into memory?}
-% \title{Capturing the transformation of experience into memory}
-\author{Andrew C. Heusser and Jeremy R. Manning\\Department of Psychological and Brain Sciences\\Dartmouth College, Hanover, NH 03755, USA\\Corresponding author: jeremy.r.manning@dartmouth.edu}
+% \title{Observing the transformation of dynamic experiences into memory}
+\author{Andrew C.
+Heusser, Paxton C.
+Fitzpatrick \& Jeremy R.
+Manning\\Department of Psychological and Brain Sciences\\Dartmouth College, Hanover, NH 03755, USA\\Corresponding author: jeremy.r.manning@dartmouth.edu}
 
@@
 The human memory system is adept at cataloging the rich dynamics of ongoing experience.
-A defining feature of our everyday experiences is that, despite the rich complexities of real-world experiences, they unfold in a structured and often predictable manner.
+A defining feature of our everyday experiences is that, despite the complexities of real-world experiences, they unfold in a structured and often predictable manner.
 This structure gives each of our experiences (and thus our memories for those experiences) a unique `shape' with respect to how it unfolds in the relevant representational space.
@@
 As a consequence, our understanding of how the temporal structure (i.e., the shape) of our experiences influences memorability and memory organization is limited.
-In this study, we investigate how people verbally recount a video by characterizing and relating the thematic dynamics, or ``trajectories,'' of the video to participants' later recounting of the narrative.
+In this study, we investigate how people verbally recount a video by characterizing and relating the thematic dynamics, or ``trajectories,'' of the video to participants' later recountings of the narrative.
 Using a novel approach that leverages topic modeling and Hidden Markov Models, we found that, despite substantial variability in the quantity of information recalled across participants as well as the particular words used to describe the experience, the overall shape of the stimulus was recapitulated by nearly every participant.
-Our findings suggest that assessing the degree of match between the shape of an experience and the subsequent retelling of that experience provides a much more nuanced view (compared with traditional methods, such as comparing the proportion of remembered details) into what it means to remember.
+Our findings suggest that assessing the degree of match between the shape of an experience and the subsequent retelling of that experience provides a much more nuanced view (compared with traditional methods such as comparing the proportion of remembered details) into what it means to remember.
 These findings provide a window into which aspects of naturalistic experiences must be preserved, and which might be more flexible, in considering whether and how those experiences are remembered.
@@
 However, characterizing and evaluating memory in more realistic contexts (e.g., recounting a recent experience to a friend) concerns a much different set of criteria.
-First, eal-world recall is continuous, rather than binary.
-Second, the specific words used to describe an experience have very little bearing on whether the experience is considered to have been ``remembered.''  Third, one might remember the gist of an experience but forget (or neglect to recount) particular details.
+First, real-world recall is continuous, rather than binary.
+Second, the specific words used to describe an experience have very little bearing on whether the experience is considered to have been ``remembered.''  Third, one might remember the gist or essence of an experience but forget (or neglect to recount) particular details.
 Or different people who share an experience might recount the experience with a similar level of detail, but the specific details that were remembered might vary across people.
-Which aspects of those recollections should be considered fundamental to determining whether or how reliably an experience has been remembered?
+Which aspects of those recollections should be considered fundamental to determining to whast extent or how reliably an experience has been remembered?
 
@@
 For instance, naturalistic experiences are autocorrelated in space and time on short timescales.
-In other words, the contents of an experience are often similar from moment to moment and change gradually.
-As an example, many of us spend our mornings/evenings at home and much of our days at work (e.g.\ an office).
-While the specific happenings within these contexts differ, they are often highly correlated (and thus predictable) over time.
+In other words, the contents of an experience often change gradually and are therefore similar from moment to moment.
+As an example, many of us spend our mornings/evenings at home and much of our days at work (e.g.\ in an office).
+While the specific happenings within these contexts differ, they are often highly correlated (and thus predictable) within an experience.
 Furthermore, our experiences can also be characterized by longer timescale correlations.
@@
 Thus, while evaluating the ability to recall the isolated elements of an experience has been a fruitful way to learn about human memory, another important dimension to consider is the temporal structure of the remembered experience, and how the temporal structure of the memory relates to the original experience.
-However, these recurrent and gradually changing temporal dynamics are not typically present in traditional memory studies, but are likely critical if we wish to understand how our memory systems remember our life experiences.
+These recurrent and gradually changing temporal dynamics are not typically present in traditional memory studies, but are likely critical to understanding how our memory systems encode, store and retrieve our life experiences.
 
-While our experiences often change gradually, they can also change rapidly (e.g.\ walking through a doorway) \citep{RadvZack17}.
+While our experiences often change gradually, they can also sometimes change suddenly (e.g.\ walking through a doorway) \citep{RadvZack17}.
 Prior research suggests that these sharp transitions (coined in the literature as ``event boundaries'') during an experience may serve to descretize our memories into ``events'' \citep{RadvZack17, BrunEtal18, HeusEtal18, ClewDava17, EzzyDava11, DuBrDava13}.
-Short timescale autocorrelations in the contents of an experience are thought associatively link information in memory, while more drastic changes in perceptual or semantic aspects of an experience may lead to discontinuities in memory \citep{HeusEtal18, BrunEtal18, EzzyDava11, DuBrDava13}.
+Short-timescale autocorrelations in the contents of an experience are thought to associatively link information in memory, while more drastic changes in perceptual or semantic aspects of an experience may lead to discontinuities in memory \citep{HeusEtal18, BrunEtal18, EzzyDava11, DuBrDava13}.
 In other words, the interplay between stable and transient temporal dynamics may impose structure on memories for those experiences.
@@
 To capture the temporal structure of the video, we developed a novel computational approach based on topic modeling \citep{BleiEtal03} and hidden Markov models \citep{Rabi89, BaldEtal17}.
-This model casts naturalistic stimuli as high-dimensional topic ``trajectories'', whereby the theme of each moment of the video is represented as a topic vector.
+This technique casts naturalistic stimuli as high-dimensional topic ``trajectories'', whereby the theme of each moment of the video is represented as a topic vector.
 In this framework, successful remembering entails verbally ``traversing'' the path formed by the stimulus topic trajectory as closely as possible.

### 2018-08-28 paper/main.tex
edits to results and figure captions

@@
 Below the video descriptions are text samples from an example participant's verbal recall transcript.
-We fit a topic model to the moment-by-moment video text descriptions and transformed participant's verbal recall transcripts using this same model.
+We fit a topic model to the moment-by-moment video text descriptions and transformed participants' verbal recall transcripts using this same model.
 The bar charts display the resulting topic model weights for the video (in blue) and recall (in green) for three example topic dimensions.}
@@
 We fit a topic model \citep{BleiEtal03} to hand-annotated text descriptions of scenes from the video.
-The text descriptions contained details of the scene such as the characters, location, and a short summary of the scene (see Fig.~\ref{fig:schematic} for example text).
-As depicted in Fig.~\ref{fig:model}a, the topic vectors are sparse and change slowly over time.
+The text descriptions contained details of the scene such as the characters present, location, and a short summary of the scene (see Fig.~\ref{fig:schematic} for example text).
+As depicted in Fig.~\ref{fig:model}A, the topic vectors are sparse and change slowly over time.
 Furthermore, there are clear transitions from one topic ``state'' to the next, possibly indexing scene transitions in the stimulus.
-To get a better handle on this temporal structure, we computed a timepoints (1976) by timepoints (1976) correlation matrix of the video model (Fig.~\ref{fig:model}c).
+To get a better handle on this temporal structure, we computed a timepoints (1976) by timepoints (1976) correlation matrix of the video model (Fig.~\ref{fig:model}C).
 This correlation matrix reveals that the model has a strong, block-diagonal structure with very low off-diagonal correlation values, suggesting the representations of each block are unique and highly descriminable.
-We found that the ``narrative details'' (e.g.
-a few sentences summarizing the specific happenings of the scene) of the video were the most important feature driving this model structure (see Supp.
-Fig.~\ref{fig:feature-importance}a).
+We found that the ``narrative details'' (a few sentences summarizing the dialogue and specific happenings of the scene) of the video were the most important feature driving this model structure (see Supp.
+Fig.~\ref{fig:feature-importance}A).
 
@@
 We used the same topic model (fit with the text descriptions of the video) to transform participants' verbal recall transcripts.
-An example participant's (\#13) recall model is plotted in Fig.~\ref{fig:model}b.
+An example participant's (\#13) recall model is plotted in Fig.~\ref{fig:model}B.
 Notably, participant \#13's recall model appears visually similar to the video model.
 Similar to the video model analysis (Supp.
-Fig.~\ref{fig:feature-importance}a), We found that the ``narrative details'' feature was most important for driving the video/recall relationship (Supp.
-Fig.~\ref{fig:feature-importance}b).
+Fig.~\ref{fig:feature-importance}A), we found that the ``narrative details'' feature was most important for driving the video/recall relationship (Supp.
+Fig.~\ref{fig:feature-importance}B).
 Like the video model, topic vectors were sparse and changed gradually.
 Then, we investigated the temporal structure of the recall matrices.
-From each participant's recall model, we computed a timepoint (68 to 294) by timepoints by timepoints (range: 68 to 294) correlation matrix.
-An example participant's (\#13) correlation matrix is plotted in Fig.~\ref{fig:model}d.
+From each participant's recall model, we computed a sentences (68 to 294) by sentences (68 to 294) correlation matrix (Fig.~\ref{fig:model}D).
 Like the video model, each participant's recall correlation matrix exhibited a strong block-diagonal structure (Supp.
@@
 For all plots, darker colors indicate greater values and the range of each plot is 0-1.
-A).
-A timepoints (1976) by topics (100) matrix representing the video stimulus.
+\textbf{A.} A timepoints (1976) by topics (100) matrix representing the video stimulus.
 Each row represents the most likely mixture of topics for a given timepoint (i.e., topic weights).
 Each column represents a different topic.
-B).
-A timepoints (1976) by topics (100) matrix representing participant \#13's recall.
-C).
-A viewing-time (1976) by viewing-time (1976) correlation matrix representing the correlation of each moment of the video model with every other moment of the video model.
-The white boxes represent `events' recovered by a hidden Markov model.
-D).
-A recall-time (294 sentences) by recall-time (294) correlation matrix for participant \#13.
-E).
-An events (34) by topics (100) matrix where each row represents the average topic vector for each event in the video model.
-F).
-An events (27) by topics (100) matrix where each row represents the average topic vector for each event in participant \#13's recall model.
-G.
-A recall events (27) by video events (34) correlation matrix for participant \#13.
+\textbf{B.} A sentences (294) by topics (100) matrix representing participant \#13's recall.
+\textbf{C.} A viewing-time (1976) by viewing-time (1976) correlation matrix representing the correlation of each moment of the video model with every other moment of the video model.
+The yellow boxes represent `events' recovered by a hidden Markov model.
+\textbf{D.} A recall-time (294 sentences) by recall-time (294) correlation matrix for participant \#13.
+\textbf{E.} An events (34) by topics (100) matrix where each row represents the average topic vector for each event in the video model.
+\textbf{F.} An events (27) by topics (100) matrix where each row represents the average topic vector for each event in participant \#13's recall model.
+\textbf{G.} A recall events (27) by video events (34) correlation matrix for participant \#13.
 The cells with a yellow border identify the video event with the highest correlation to a given recall event.
-F.
-A group averaged recall events (34) by video events (34) correlation matrix.
+\textbf{H.} A group averaged recall events (34) by video events (34) correlation matrix.
 The cells with yellow borders are the video event with the highest correlation to a given average recall event.}
@@
 \subsubsection{Segmenting the video and recall models into ``events''}
-As described above, a striking feature of both the video and recall correlation matrices is a strong, block structure along the diagonal of the matrices (see Fig.~\ref{fig:model}c,d).
+As described above, a striking feature of both the video and recall correlation matrices is a strong, block structure along the diagonal of the matrices (see Fig.~\ref{fig:model}C,D).
 We hypothesized that this structure might arise from transient stability in the "theme" of both the video and of participants' memory for the video.
 We hypothesized that specific events described by a participant could be ``matched'' to specific video events by computing the similarity (i.e., correlation) between their topic vectors.
-In other words, the video event that is most similar to a particular recall event is the event that the participant is most likely describing.
+In other words, the video event that is most thematically similar to a particular recall event is the event that the participant is most likely describing.
 To test this idea, we segmented the video and recall models in $k$ events (i.e., states) using a hidden Markov model ~\citep{BaldEtal17}.
 Our algorithm determined 34 events for the video model and a range of values (range: 8-27; mean: 15.41; SD: 5.6) for the recall models (see Methods for details on choosing an optimal $k$ value).
-The events discovered for the video model and a representative participant's recall model are highlighted as yellow rectangles outlining blocks along the diagonal of the correlation matrices (Fig.~\ref{fig:model}b,d).
+The events discovered for the video model and a representative participant's recall model are highlighted as yellow rectangles outlining blocks along the diagonal of the correlation matrices (Fig.~\ref{fig:model}C,D).
 
-Next, we created a video ``event model'' by averaging together neighboring topic vectors that the were classified to be in the same event, resulting in an events (34) by topics (100) matrix (Fig.~\ref{fig:model}e).
-We performed the same procedure for the recall matrices (Fig.~\ref{fig:model}f).
-Then, we computed the correlation between video and recall event models, resulting in a video events (34) by recall events (8-27, depending on the participant) correlation matrix (Fig~\ref{fig:model}g for example, Supp.
+Next, we created a video ``event model'' by averaging together neighboring topic vectors that the were classified to be in the same event, resulting in an events (34) by topics (100) matrix (Fig.~\ref{fig:model}E).
+We performed the same procedure for the recall matrices (Fig.~\ref{fig:model}F).
+Then, we computed the correlation between video and recall event models, resulting in a video events (34) by recall events (8-27, depending on the participant) correlation matrix (Fig~\ref{fig:model}G for example, Supp.
 Fig~\ref{fig:matchmats} for all participants).
 These matrices represent the similarity (correlation) between each video event and each recall event (for each participant).
-To determine which video event a particular recall event was most likely describing, we computed the index of the video event with the highest correlation to the recall event (i.e., the argmax).
-This is depicted in Fig.~\ref{fig:model}g as the cells highlighted with a yellow border.
+To determine which video event a particular recall event was most likely describing, we found the index of the video event with the highest correlation to the recall event (i.e., the argmax).
+This is depicted in Fig.~\ref{fig:model}G as the cells highlighted with a yellow border.
 Notably, our algorithm suggests that the example participant recalled most of the video events and did so in order.
@@
 This yielded an average recall event vector for all but one (of 34) video events, since no participant remembered one of the events according to our model.
-Lastly, we computed an average recall event (34) by video event (34) correlation matrix, and highlighted the cell with the highest correlation value with a yellow border (Fig.~\ref{fig:model}h).
+Lastly, we computed an average recall event (34) by video event (34) correlation matrix, and highlighted the cell with the highest correlation value with a yellow border (Fig.~\ref{fig:model}H).
 Notably, this matrix displayed high correlation values along the diagonal and low correlations in the off-diagonal cells.
-This suggests that on average, participants were able to recapitulate the events in the episode in a specific and highly descriminable way.
+This suggests that on average, participants were able to recapitulate the events in the episode in a specific, sequential and highly descriminable way.
 
-\subsubsection{The shape of a naturalistic experience is preserved in recall}
+\subsubsection{The trajectory of a naturalistic experience is preserved in recall}
 Classic approaches to studying free recall in episodic memory (such as overall accuracy and serial position curve) focus on the quantity of information recalled \citep{Murd62a}.
@@
 \includegraphics[width=1\textwidth]{figs/3_trajectory.pdf}
-\caption{\small \textbf{Video and recall trajectory plots.} A).
-2-dimensional embedding of the video events model (reduced with UMAP algorithm).
+\caption{\small \textbf{Video and recall trajectory plots.} \textbf{A.} 2-dimensional embedding of the video events model (reduced with UMAP algorithm).
 The arrows indicate the forward direction of the video events.
-B).
-2-dimensional embedding of the average recall events model.
+\textbf{B.} 2-dimensional embedding of the average recall events model.
 The colors refer to the most similar video events.
 The directional lines connecting the points represent the true video event order.
-The arrows represent the group-average direction of all recall event transitions (i.e., a line segment connecting two consecutive recall event vectors) that intersected a circle (radius=.5) centered on the origin of the arrow.}
+The arrows represent the group-average direction of all recall event transitions (i.e., a line segment connecting two consecutive recall event vectors) that intersected a circle (radius=.5) centered on the origin of the arrow.
+\textbf{C.} Individual trajectory plots for each participant overlayed with the video model (black).
+The direction of the recall sequence is indicated by the direction of arrows connecting each recall event.
+The colors refer to the most likely video event.}
 \label{fig:trajectory}
@@
 
-To visualize the relationship between the video and recall event models, we embedded them into a 2D space using the UMAP dimensionality reduction algorithm ~\citep{McInHeal18}, where the points represent video/recall events and the distance between them represents their similarity/distance in ``topic space'' (Fig.~\ref{fig:trajectory}a).
+To visualize the relationship between the video and recall event models, we embedded them into a 2D space using the UMAP dimensionality reduction algorithm ~\citep{McInHeal18}, where the points represent video/recall events and the distance between them represents their similarity/distance in ``topic space'' (Fig.~\ref{fig:trajectory}A).
 We observed that visually, it appears that the two models have a very similar temporal evolution and geometric structure.
 To further quantify this correspondence and to characterize how participants navigated through the space during recall, we analyzed the angle between successive recall events.
-We created a grid of evenly spaced points (.25 units) in the 2D ``topic space''.
-For each point on the grid, we drew a circle (radius=.5) around the point and grouped together all recall transitions that intersected the circle (across subjects).
+We created a grid of evenly spaced points (.25 units) in the 2D ``topic space.'' For each point on the grid, we drew a circle (radius=.5) around the point and grouped together all recall transitions that intersected the circle (across subjects).
 To visualize the average angle, we converted each transition angle to a unit vector and then averaged the vectors together.
-To assess consistency in the direction of the recall transition across participants, we performed a Rayleigh test ($p<.001$, corrected at $p<.05$ using permutation procedure described in Methods).
-Notably, all video events fell within the path formed by the video events.
-Thus, participants' recalls followed the same path as the video model (Fig.~\ref{fig:trajectory}b), suggesting the shape of the stimulus was preserved despite idiosyncratic differences between participants in their recalls.
+To assess consistency in the direction of the recall transition across participants, we performed a Rayleigh test ($p<.001$, corrected at $p<.05$ using the permutation procedure described in Methods).
+Notably, the video events fell within the path formed by the recall events.
+Thus, participants' recalls followed the same path as the video model (Fig.~\ref{fig:trajectory}B), suggesting the shape of the stimulus was preserved despite idiosyncratic differences between participants in their recalls.
 
@@
 \includegraphics[width=1\textwidth]{figs/4_brains_panels.pdf}
-\caption{\small \textbf{Video and recall model correlational structure searchlight analysis.} A) The correlation matrix representing the temporal structure of the video model.
+\caption{\small \textbf{Video and recall model correlational structure searchlight analysis.} \textbf{A.} The correlation matrix representing the temporal structure of the video model.
 Below it is a surface plot of brain regions whose activity patterns mirrored the correlational structure of video model during viewing.
-B) The left matrix is S13's video-recall correlation matrix before warping.
+\textbf{B.} The left matrix is S13's video-recall correlation matrix before warping.
 The yellow stars represent the path recovered by dynamic time warping.
@@
 This analysis revealed a network of regions including bilateral frontal and cingulate cortex (Fig.
-~\ref{fig:brainz}).
-Thus, these regions may play a role in maintaining information relevant to the narrative trajectory of the video.
+~\ref{fig:brainz}), suggesting that these regions may play a role in maintaining information relevant to the narrative trajectory of the video.
 
 While each participant remembered roughly the same sequence of events, there were subtle idiosyncracies in the way each individual described the events.
-For example, the event by event similarity structure (e.g.
+For example, the event-by-event similarity structure (i.e.
 the off-diagonal values of the recall correlation matrices) differed across individuals (Supp.
 Fig.~\ref{fig:corrmats}).
-We hypothesized that idiosyncracies in the recall dynamics across subjects might be related to the temporal structure of brain networks are representing the events during video viewing.
+We hypothesized that idiosyncracies in the recall dynamics across subjects might be related to the temporal structure of brain networks representing the events during video viewing.
 In this analysis, we identified brain areas whose responses at the time of viewing exhibited the same (segmented) idiosyncratic dynamics that later appeared in that participants’ recalls.
 Using a procedure similar to the approach above (see Methods for details), we searched for regions whose correlational structure during viewing was related to the idiosyncratic structure of the participant's recall model.
-The resulting map suggests that the correlational structure of a network of brain regions including the ventromedial prefrontal cortex, anterior cingulate, and right medial temporal lobe mirror the idiosyncratic structure of participants'' recalls (Fig.
+The resulting map suggests that the correlational structure of a network of brain regions including the ventromedial prefrontal cortex, anterior cingulate, and right medial temporal lobe mirror the idiosyncratic structure of participants' recalls (Fig.
 ~\ref{fig:brainz}).
@@
 \includegraphics[width=1\textwidth]{figs/5_topics.pdf}
-\caption{\small \textbf{Analysis of topics by event memorability.} A).
-Group-averaged correlation between each video event and closest recall event.
+\caption{\small \textbf{Analysis of topics by event memorability.} \textbf{A.} Group-averaged correlation between each video event and closest recall event.
 Error bars represent 95\% confidence intervals.
-Stars indicate top (green) and bottom (red) 3 remembered events across participants B).
-Wordles (top 200 words) representing a weighted average of video event topic vectors weighted by event memorability (e.g.\ the correlation values in A).
+Stars indicate top (green) and bottom (red) 3 remembered events across participants \textbf{B.} Wordles (top 200 words) representing a weighted average of video event topic vectors weighted by event memorability (e.g.\ the correlation values in A).
 The top wordle (green) contains words from the most remembered events and the bottom (red) contains words from least memorable events.
 The word sizes are proportional to the word's ``activation''.
-C).
-Trajectory represents the video event model embedded in a 2D space using UMAP.
+\textbf{C.} Trajectory represents the video event model embedded in a 2D space using UMAP.
 The large colored dots are video events.
-The small colored dots are all individual recall events across all participants, where the colors refer to the closest video event.
+The small colored dots are individual recall events across all participants, where the colors correspond to the closest video event.
 The circular wordles represent the top 3 most (green circles) and least (red) memorable video events.
@@
 \subsubsection{Memorability by event and topics}
-A notable advantage of representing naturalistic stimuli/memory using this approach is that the event models can be mapped back to the language used to fit the model(s).
-This allows for analysis (and visualization) of the language used when participants' recounted their experiences.
-In this next analysis, we 1) quantified the memorability of each video event and 2) used memorability to plot the top words for the most and least memorable scenes.
+A notable advantage of representing naturalistic stimuli and memory using this approach is that the event models can be mapped back to the language used to fit the model(s).
+This allows for analysis (and visualization) of the language used when participants recounted their experiences.
+In this next analysis, we 1) quantified the memorability of each video event and 2) used memorability to plot the ``top'' words for the most and least memorable scenes.
 
-To measure video event memorability, we computed the correlation between each video event and the closest recall event and then averaged those values within participant (Fig.~\ref{fig:topics}a).
+To measure video event memorability, we computed the correlation between each video event and the closest recall event and then averaged those values within participants (Fig.~\ref{fig:topics}A).
 We used event memorability to create a weighted average over all video event vectors, where video events with better memory were weighted more heavily.
 Then, we extracted the top 200 words and created ``wordles'' representing the most memorable themes in the video.
-The results reveal that scenes containing ``Sherlock'' and ``John'' were highly memorable, and also scenes containing words such as ``medium'', ``street'' and ``baker'' (Fig.~\ref{fig:topics}b).
+The results reveal that scenes containing ``Sherlock'' and ``John'' were highly memorable, as were scenes containing words such as ``medium'', ``street'' and ``baker'' (Fig.~\ref{fig:topics}B).
 To find words related to the least memorable scenes, we inverted the memorability weights and again extracted the top 200 words.
-Scenes containing ``Mike'' and ``Molly'' were least remembered, and also words like ``conference'', ``hospital'' and ``psychotherapist'' (Fig.~\ref{fig:topics}b).
+Scenes containing ``Mike'' and ``Molly'' were least remembered, and also words like ``conference'', ``hospital'' and ``psychotherapist'' (Fig.~\ref{fig:topics}B).
 
@@
 We performed the same analysis as described above, but separately for the video and average recall event vectors representing each of the top/bottom 3 remembered events.
-In Figure~\ref{fig:topics}c, the trajectory represents a low-dimensional embedding of the video model and the large colored dots represent the video events.
+In Figure~\ref{fig:topics}C, the trajectory represents a low-dimensional embedding of the video model and the large colored dots represent the video events.
 The smaller colored dots represent the distribution of individual recall events across all participants, colored by the closest video event.
 We plotted wordles for the top 3 (circled in green) and bottom 3 (red) most/least remembered events, where the video is represented in the left half of the circle and the average recall is represented in the right half of the circle.
-Visual inspection reveals that the words contained in the memorability weighted worldles (Fig.~\ref{fig:topics}b) overlap with the individual top/bottom event wordles (Fig.~\ref{fig:topics}c).
+Visual inspection reveals that the words contained in the memorability weighted worldles (Fig.~\ref{fig:topics}B) overlap with the individual top/bottom event wordles (Fig.~\ref{fig:topics}C).
 These analyses shed light on the contents of naturalistic stimuli and accompanying memories, and highlight the flexibility in transforming between human and machine readable representations of the data afforded by our modeling approach.
@@
 \subsubsection{Additional measures of naturalistic recall}
-Representing the video and verbal recall as events in ``topic space'' also affords us the ability to characterize the quality of recall in a more fine-grained and nuanced way than what was previously possible.
+Representing the video and verbal recall as events in ``topic space'' also affords us the ability to characterize the quality of recall in a more fine-grained and nuanced way than was previously possible.
 We quantified the distance between each video event and its matching recall event (``precision''), the the distance between a video event and all non-matching recall events (``distinctiveness'') and the temporal order of the recall events (``order'').
@@
 
-Just like in a traditional ``free-recall'' list-learning experiment where participants view a list of words and then verbally recall them, our video-recall matching analysis approach affords us the ability to analyze memory in the same way.
-We considered 6 classic list-learning analyses: overall accuracy, probability of first recall \citep{Hoga75, HowaKaha99, Lami99}, lag-conditional response probability \citep{Kaha96, HowaKaha99}, serial position curve \citep{Murd62a}, temporal clustering and semantic clustering \citep{HowaKaha02, PolyEtal09}.
+Just like in a traditional free recall list-learning experiment where participants view a list of words and then verbally recall them, our video-recall matching analysis approach affords us the ability to analyze memory in the same way.
+We considered 6 classic list-learning analyses: overall accuracy, probability of first recall \citep{Hoga75, HowaKaha99, Lami99}, lag-conditional response probability \citep{Kaha96, HowaKaha99}, serial position curve \citep{Murd62a}, temporal clustering, and semantic clustering \citep{HowaKaha02, PolyEtal09}.
 Extending these classic list-learning analyses to naturalistic stimuli allows to directly compare trial- and naturalistic-based recall studies (see Supplemental Materials Section 2 for details).
@@
 We collected all line segments that passed through a given section of topic space (collapsing across participants).
-To plot the average direction of the line segments (i.e., the arrows for each grid point in ~\ref{fig:trajectory}b), we converted each of them to unit vectors and then averaged.
+To plot the average direction of the line segments (i.e., the arrows for each grid point in ~\ref{fig:trajectory}B), we converted each of them to unit vectors and then averaged.
 For grid points where the direction was consistent (across all participants contributing to that point), the length of the arrow approaches 1, whereas if the direction was random the length of the arrow approaches 0.
@@
 
-In the first analysis (Fig.~\ref{fig:topics}a/b), we quantified the most and least remembered topics/words throughout the entire video by computing a weighted average over all recall events, where the weights were proportional to memory for each recall event.
+In the first analysis (Fig.~\ref{fig:topics}A,B), we quantified the most and least remembered topics/words throughout the entire video by computing a weighted average over all recall events, where the weights were proportional to memory for each recall event.
 To measure memory for each event, for each participant we computed the correlation between the video event vector and the closest recall event vector.
@@
 
-In the second analysis (Fig.~\ref{fig:topics}c), we created wordles for the top/bottom 3 remembered video events indexed by the average correlation values (Fig.~\ref{fig:topics}a).
+In the second analysis (Fig.~\ref{fig:topics}C), we created wordles for the top/bottom 3 remembered video events indexed by the average correlation values (Fig.~\ref{fig:topics}A).
 To get the ``activations'' for words associated with the video events, we computed the dot product between the video event vector and the R matrix.
@@
 We found that participants tended to initiate their recall sequences with the first few events (Supp.
-Fig.~\ref{fig:list-learning}a), which is qualitatively very similar to previously published list learning experiments ~\citep{HowaKaha99}.
+Fig.~\ref{fig:list-learning}A), which is qualitatively very similar to previously published list learning experiments ~\citep{HowaKaha99}.
 Next, we considered another well-studied memory measure in the list-learning literature, the lag conditional response probability curve (or lag-CRP) ~\citep{Kaha96}.
 The result suggests a strong bias to transition sequentially events in the forward direction (Supp.
-Fig.~\ref{fig:list-learning}b).
+Fig.~\ref{fig:list-learning}B).
 Finally, we assessed memory performance for each event in the video as a function of its serial position during encoding (Supp.
-Fig.~\ref{fig:list-learning}c).
+Fig.~\ref{fig:list-learning}C).
 We did not observe the classic ``primacy'' and ``recency'' pattern which is prevalent in the literature ~\citep{Murd62a}.

### 2018-08-28 paper/main.tex
discussion edits

@@
 This approach allows us to quantify which moments from the past and the current recounted experience match in terms of their thematic content and critically, our ability to perform this matching does not require participants to use any specific overlapping words.
-Our work characterizes experience by comparing the overall ``shape'' of a dynamic stimulus and a memory.
-We assess the quality of memory for the movie participants viewed by measuring the match between the shapes of the movie's trajectory and each participant's recall trajectory.
-By contrast, the number of recalls could be captured by the "sampling frequency" along that trajectory-- but the number of recalls alone cannot tell us whether participants successfully recollected the meaning of the story by capturing the salient points of the narrative that define its main shape.
+Our work characterizes recollection of an experience by comparing the overall ``shape'' of a dynamic stimulus and a memory.
+We assess the quality of memory for the video participants viewed by measuring the match between the shapes of the video's trajectory and each participant's recall trajectory.
+By contrast, the number of recalls could be captured by the "sampling frequency" along that trajectory -- but the number of recalls alone cannot tell us whether participants successfully recollected the meaning of the story by capturing the salient points of the narrative that define its main shape.
 In addition to providing a way to capture the shape of an experience, this method affords the ability to quantify the particular contents of memory.
@@
 Our approach is fundamentally different.
-We ask: which brain regions during movie viewing match the movie structure and how individual participants will recall the movie later (in terms of the temporal correlations of their recall topic trajectory)?
+We ask: which brain regions during video viewing match the video structure and how individual participants will recall the video later (in terms of the temporal correlations of their recall topic trajectory)?
 This latter approach highlights regions such as the medial prefrontal cortex (mPFC) and medial temporal lobes (MTL) that may respond in idiosyncratic ways across individuals, but that nonetheless play an important role in encoding experience into memory.
-In other work, the mPFC has been suggested to play a role in the representation of a ``schema'', or a network prior knowledge that is consistent with the current task ~\citep{KestEtal12, GilbMarl17}.
+In other work, the mPFC has been suggested to play a role in the representation of a ``schema'', or a network of prior knowledge that is consistent with the current task ~\citep{KestEtal12, GilbMarl17}.
 One interpretation for mPFC's involvement in our work is that mPFC represents participant-specific relationships with the content of the video, and its representation during scene viewing is related to how a participant later describes the scene.
@@
 More broadly, these findings have strong implications for how we assess memory in other naturalistic contexts, such as the classroom or in a doctor's office.
-Whereas tests often measure students' performance using metrics such as the proportion of correctly answered questions, our work suggests that this approach might miss the ``forrest for the trees''.
-We view ``true learning'' as understanding the key concepts (i.e., understanding key themes in the learned content and how they relate) rather than about regurgitating the greatest number of facts.
-In addition to educational contexts, our approach may provide unique metrics that can be used to assist in the diagnosis of a memory disorder, and other psychiatric disorders that influence memory.
-For example, while the quantity of information recalled could be roughly matched between a healthy and patient population, other aspects of the memory (such as the shape, serial order, precision or distinctiveness) might be different.
+Whereas academic tests often measure students' performance using metrics such as the proportion of correctly answered questions, our work suggests that this approach might ``miss the forrest for the trees''.
+We view ``true learning'' as understanding key concepts (i.e., understanding central themes in the learned content and how they relate) rather than regurgitating the greatest number of facts.
+In addition to educational contexts, our approach may provide unique metrics that can be used to assist in the diagnosis of memory disorders, and other psychiatric disorders that influence memory.
+For example, while the quantity of information recalled could be roughly matched between a healthy and patient population, and other aspects of the memory (such as the shape, serial order, precision or distinctiveness) might be different.
 Thus, this work serves as a foundation for more nuanced approaches to memory assessment that consider the trajectory and specific contents of memory for a naturalistic experience.
@@
 An important question for future work concerns the factors that drive an individual to sample their recall trajectory finely or coarsely.
-For example, given a short recall interval, would participants intuitively gravitate towards coarser samplings that still outline the basic shape of the movie's topic trajectory?
+For example, given a short recall interval, would participants intuitively gravitate towards coarser samplings that still outline the basic shape of the video's topic trajectory?
 Or if participants were told that their narrations would be played back to other participants ~\citep{ZadbEtal17}, would that change the resolution or shape of their recalls?
@@
 While we view this work as a major advance in characterizing and understanding human memory, as with any approach there are limitations.
-First, the approach relies on having a ``good'' model of the stimulus (e.g.\ one that describes the video in the same way as participant's recall it), which is currently only achievable by a human hand-annotating each moment of the video.
+First, the approach relies on having a ``good'' model of the stimulus (e.g.\ one that describes the video in the same way as participants recall it), which is currently only achievable by a human hand-annotating each moment of the video.
 To increase the scalability of this approach, future work could explore automated methods for extracting meaning from videos ~\citep{YuEtal16}.
@@
 This provides desirable flexibility (e.g.\ participants can use different combinations of words to describe the scenes), but this comes at the expense of capturing specific details.
-Thus, a future direction of this work will be to increase sensitivity to details (while maintaining flexibility).
+Thus, a future direction of this work will be to increase sensitivity to such details while maintaining flexibility.
 
@@
 Decades of research suggest that episodic memories are not veridical and context-free snapshots of the past, and so treating (and modelling) them as such is overly simplistic at best (and counterproductive at worst).
-While its undeniable that these models have been useful in advancing our understanding of human memory, they are severely limited in their ability to explain memory for naturalistic experiences.
-Real-life experiences are highly structured in time, and so to have a complete understanding of the human memory system, our experiments and models of memory should not ignore this fact.
+While it's undeniable that these models have been useful in advancing our understanding of human memory, they are severely limited in their ability to explain memory for real-life experiences.
+Real-life experiences are highly structured in time, and so to have a complete understanding of the human memory system, our experiments and models of memory must not ignore this fact.
 Our work provides a theoretical advance in our understanding of what it means to remember as well as a novel methodological tool to study it.
@@
 To quantify the similarity between the video model and individual recall models, we considered a number of novel metrics.
-First, we tested whether each participant's recall model matched the movie model in a general sense.
+First, we tested whether each participant's recall model matched the video model in a general sense.
 To do this, for each participant we filtered the video model to only include the events that the participant remembered and computed the root mean squared difference (RMSD) between the video model and the recall model.
@@
 For each participant, we computed the correlation between each recall event and its matching video event (only for the events which they recalled).
-This resulted in a single number for each recalled event indexing how similar the recall event was to its matching movie event (i.e the ``precision'' of the recall).
+This resulted in a single number for each recalled event indexing how similar the recall event was to its matching video event (i.e the ``precision'' of the recall).
 We then averaged the correlations within participant.
@@
 In order to ascertain which features were important in relating the recall models to the video model, we similarly compared to the temporal structures of video and recall models deprived of a single feature at a time.
-For each feature removed, we transformed each subject’s recall transcript using a model trained on the feature-deprived video text windows (of 50 scene segments), and resampled the recall timeseries to match the shape of the movie model (1976 timepoints).
+For each feature removed, we transformed each subject’s recall transcript using a model trained on the feature-deprived video text windows (of 50 scene segments), and resampled the recall timeseries to match the shape of the video model (1976 timepoints).
 We then represented the temporal structures of each subject’s recall model as timepoints (1976) by timepoints (1976) correlation matrices and computed the average correlation with the temporal structure of the video model (across subjects).

### 2018-08-28 paper/main.tex
methods edits

@@
 \subsection{Participants and Experimental Design}
-Participants ($n=17$) viewed \textit{A Study in Pink}, a 50 minute episode of the BBC series, \textit{Sherlock}.
-Immediately upon completion of the video, participants were instructed to (verbally) recount the events in the video in their original order and in as much detail as possible.
+Participants ($n=17$) viewed the first 50 minutes of ``A Study in Pink'', an episode of the BBC series, \textit{Sherlock}.
+Immediately upon completion of the video, participants were instructed to (verbally) recount the events in the \textit{Sherlock} episode in their original order and in as much detail as possible.
 During the entire experiment, participants were in an fMRI scanner.
@@
 First, the video was manually segmented into 1000 scenes, and a collection of descriptive features was manually transcribed.
-For each scene, we considered the following features: scene details (i.e., a sentence or two describing what happened in that scene), space (indoor or outdoor), name of all the characters in the scene, name of the character in focus, name of the character speaking, location, camera angle, music presence, and words on the screen.
+For each scene, we considered the following features: narrative details (a sentence or two describing what happened in that scene), whether the scene was indoor or outdoor, name of all the characters in the scene, name of the character in focus, name of the character speaking, location, camera angle, music presence, and text on the screen.
 We concatenated the text for all of these features within each segment, creating a ``bag of words'' describing each scene.
 We then transformed the text descriptions into overlapping windows of 50 scene segments.
-For example, the first text sample comprised the text from the first 50 segments, the second comprised the text from n+1:n+51, and so on.
+For example, the first text sample comprised the text from the first 50 segments, the 2nd comprised the text from n+1:n+51, and so on.
 We trained our model using these overlapping text samples with scikit-learn's (version 0.19.1) `CountVectorizer' and `LatentDirichletAllocation' classes \citep{PedrEtal11} implemented using our high-dimensional visualization/analysis software, Hypertools \citep{HeusEtal17a}.
@@
 \subsubsection{Extracting events using a hidden Markov model}
-The topic model timepoint-by-timepoint correlation matrices all exhibited a block-diagonal structure (with small off-diagonal values), suggesting that the models were comprised of a number of sequential `states' (or events, e.g.\ Supp.
+The topic model timepoint-by-timepoint correlation matrices all exhibited a block-diagonal structure (with small off-diagonal values), suggesting that the models were comprised of a number of sequential `states' (or events, see Supp.
 Fig.~\ref{fig:corrmats}).
@@
 To estimate which video event each recall event referred to, we correlated the video events model and each recall events model.
-This resulted in a video events (34) by recall events (8-27) correlation matrix (for each participant) which contains the similarity between each video event and each recall event.
+This resulted in a video events (34) by recall events (8-27) correlation matrix (for each participant) which contains the similarity between each video event and each recall event (see Supp.
+Fig.~\ref{matchmats}).
 To find the most likely video event that a given recall event referred to, we computed the argmax over the columns of this matrix.
@@
 To test whether the distribution of angles was significantly non-uniform (i.e., displayed a preferred direction across participants), we performed a Rayleigh test on the angles ($p<.001$, FDR-corrected at $p<.05$ using Benjamani-Hochberg procedure).
-Arrows where the Rayleigh test was significant are displayed in color while non-significant tests are displayed in gray with lower opacity.
+Arrows where the Rayleigh test was significant are displayed in color (the darker the blue the more significant) while non-significant tests are displayed in gray with lower opacity.
 
 \subsection{fMRI analyses}
-Seventeen participants watched the first 50 minutes of Episode 1 of BBC's Sherlock.
-The video was split into two parts of approximately equal length (946 and 1030 TRs).
+Participants viewed and recalled the video stimulus inside an fMRI scanner.
+The video was split into two parts of approximately equal length (946 and 1030 TRs, $TR=1.5 seconds$).
 All data were preprocessed and transformed to 3mm MNI space as described in ~\citep{ChenEtal17}.
@@
 To aggregate across participants, we Fisher's z-transformed the correlations and then averaged.
-To assess significance, we recomputed this group analysis 100 times, but randomly phase shifted the model (by \# of timepoints - 1) by the same amount for each participant but different amounts for each permutation to build a null distribution of correlation values.
+To assess significance, we recomputed this group analysis 100 times, but randomly phase shifted the model by the same amount for each participant but different amounts for each permutation to build a null distribution of correlation values.
 Finally, we thresholded the group averaged correlation maps where the `real' correlation value for a given voxel exceeded the 95th percentile of the null distribution.
@@
 One component of the topic model comprises a words (2117) by topics (100) matrix (R), where the rows represent the weight of a given word in each topic.
-To find words that were maximally associated with a particular event vector, we computed the dot product between R and v, which gave a 1 by \# of words vector where the values represent the `activation' of each of in the event.
-Then, we created word clouds by extracting the top $n$ words and plotting them where the size of the word is proportional to its `activation' in the event.
+To find words that were maximally associated with a particular event vector, we computed the dot product between R and v, which gave a 1 by \# of words vector where the values represent the ``activation'' of each of in the event.
+Activation is defined as the weight of a particular word in a particular event.
+Then, we created word clouds by extracting the top $n$ words and plotting them where the size of the word is proportional to its activation in the event.
 
@@
 We then computed a weighted average of all video events using the correlation values as weights.
-Next, we computed the dot product between this weighted-average video event vector and the R matrix (described in the paragraph above) to get ``activations'' for each word.
-Finally, we plotted the top 200 words where the size of the word is proportional to its ``activation''.
+Next, we computed the dot product between this weighted-average video event vector and the R matrix (described in the paragraph above) to get activations for each word.
+Finally, we plotted the top 200 words where the size of the word is proportional to its activation.
 To get the least remembered topics/words, we performed the same analysis but inverted memory weights.

### 2018-08-28 paper/main.tex
supp materials edits

@@
 \includegraphics[width=1\textwidth]{figs/supp4_feature_value.pdf}
-\caption{\small \textbf{Impact of individual features on topic modeling analysis.} Contribution of each feature to model structure.
+\caption{\small \textbf{Impact of individual features on topic modeling analysis.} \textbf{A.} Contribution of each feature to model structure.
 Bars represent the correlation of a video model trained in the absence of a given feature to the model trained on all features.
-B).Contribution of each feature to video model/recall model relationship.
+\textbf{B.} Contribution of each feature to video model/recall model relationship.
 The leftmost bar represents the across-subjects mean correlation between the video model and recall models trained on all features.
@@
 \section*{Naturalistic extensions of classic list-learning analyses}
-Just like in a traditional ``free-recall'' list-learning experiment where participants view a list of words and then verbally recall them, our video-recall matching analysis approach affords us the ability to analyze memory in the same way.
+Just like in a traditional free recall list-learning experiment where participants view a list of words and then verbally recall them, our video-recall matching analysis approach affords us the ability to analyze memory in the same way.
 The recalled events can be treated as ``items'' analogous to words recalled in a list-learning study.
@@
 As an example, if the participant remembered all the events in order (with perfect precision), the expected distance value would be 0.
-However, if they remembered a subset of events, events our of order or with low precision the expected distance would be greater than 0.
+However, if they remembered a subset of events, events out of order, or with low precision, the expected distance would be greater than 0.
 To assess significance, we performed a permutation test where we circularly shifted the recall model (10000 times) and recomputed the RMSD.
@@
 To determine the contribution of each feature to the structure of the video model, we examined the similarity between the temporal structure of models trained in the absence of a single feature and that of our original (i.e.
-full) model.
+full) model (Supp.
+Fig.~\ref{fig:feature-importance}A).
 First, we iteratively removed one transcribed feature from the scene descriptions and constructed a timepoints (1976) by topis (100) matrix using a topic model fit to the remaining features.
-We then represented the original model as well as the new model’s temporal structure as a timepoints (1976) by timepoints (1976) correlation matrix.
+We then represented the original model as well as the new model’s temporal structure as a timepoints-by-timepoints correlation matrix.
 Finally, we vectorized these correlation matrices and correlated them to each other resulting in a single number (for each feature removed from the model) representing the similarity of the ``feature-removed'' models to the full model.
 
-In order to ascertain which features were important in relating the recall models to the video model, we similarly compared to the temporal structures of video and recall models deprived of a single feature at a time.
+In order to ascertain which features were important in relating the recall models to the video model, we similarly compared to the temporal structures of video and recall models deprived of a single feature at a time (Supp.
+Fig.~\ref{fig:feature-importance}B).
 For each feature removed, we transformed each subject’s recall transcript using a model trained on the feature-deprived video text windows (of 50 scene segments), and resampled the recall timeseries to match the shape of the video model (1976 timepoints).
-We then represented the temporal structures of each subject’s recall model as timepoints (1976) by timepoints (1976) correlation matrices and computed the average correlation with the temporal structure of the video model (across subjects).
+We then represented the temporal structures of each subject’s recall model as timepoints-by -timepoints correlation matrices and computed the average correlation with the temporal structure of the video model (across subjects).
 

### 2018-08-28 paper/main.tex
few minor edits and updated pdf

@@
 We used a searchlight procedure (see Methods for details) to identify regions whose timepoint-by-timepoint correlational structure matched the correlational structure of our model.
-This analysis revealed a network of regions including bilateral frontal and cingulate cortex (Fig.
-~\ref{fig:brainz}), suggesting that these regions may play a role in maintaining information relevant to the narrative trajectory of the video.
+This analysis revealed a network of regions including bilateral frontal and cingulate cortex (Fig.~\ref{fig:brainz}), suggesting that these regions may play a role in maintaining information relevant to the narrative trajectory of the video.
 
@@
 Using a procedure similar to the approach above (see Methods for details), we searched for regions whose correlational structure during viewing was related to the idiosyncratic structure of the participant's recall model.
-The resulting map suggests that the correlational structure of a network of brain regions including the ventromedial prefrontal cortex, anterior cingulate, and right medial temporal lobe mirror the idiosyncratic structure of participants' recalls (Fig.
-~\ref{fig:brainz}).
+The resulting map suggests that the correlational structure of a network of brain regions including the ventromedial prefrontal cortex, anterior cingulate, and right medial temporal lobe mirror the idiosyncratic structure of participants' recalls (Fig.~\ref{fig:brainz}).
 
@@
 We collected all line segments that passed through a given section of topic space (collapsing across participants).
-To plot the average direction of the line segments (i.e., the arrows for each grid point in ~\ref{fig:trajectory}B), we converted each of them to unit vectors and then averaged.
+To plot the average direction of the line segments (i.e., the arrows for each grid point in Fig.~\ref{fig:trajectory}B), we converted each of them to unit vectors and then averaged.
 For grid points where the direction was consistent (across all participants contributing to that point), the length of the arrow approaches 1, whereas if the direction was random the length of the arrow approaches 0.
@@
 \begin{center}
-\textbf{\large Supplemental Materials: Capturing the shape of naturalistic experiences and how we remember them}
+\textbf{\large Supplemental Materials: How is experience transformed into memory?}
 \end{center}

### 2018-08-28 paper/main.tex

@@
+% !TEX TS-program = pdflatex
 \documentclass{article}
@@
 \title{How is experience transformed into memory?}
-% \title{Observing the transformation of dynamic experiences into memory}
 \author{Andrew C.
 Heusser, Paxton C.
-Fitzpatrick \& Jeremy R.
+Fitzpatrick, and Jeremy R.
 Manning\\Department of Psychological and Brain Sciences\\Dartmouth College, Hanover, NH 03755, USA\\Corresponding author: jeremy.r.manning@dartmouth.edu}
@@
 \begin{abstract}
-The human memory system is adept at cataloging the rich dynamics of ongoing experience.
-A defining feature of our everyday experiences is that, despite the complexities of real-world experiences, they unfold in a structured and often predictable manner.
-This structure gives each of our experiences (and thus our memories for those experiences) a unique `shape' with respect to how it unfolds in the relevant representational space.
-However, temporal structure is typically absent (or severely impoverished) in traditional trial-based  experiments.
-As a consequence, our understanding of how the temporal structure (i.e., the shape) of our experiences influences memorability and memory organization is limited.
-In this study, we investigate how people verbally recount a video by characterizing and relating the thematic dynamics, or ``trajectories,'' of the video to participants' later recountings of the narrative.
-Using a novel approach that leverages topic modeling and Hidden Markov Models, we found that, despite substantial variability in the quantity of information recalled across participants as well as the particular words used to describe the experience, the overall shape of the stimulus was recapitulated by nearly every participant.
-Our findings suggest that assessing the degree of match between the shape of an experience and the subsequent retelling of that experience provides a much more nuanced view (compared with traditional methods such as comparing the proportion of remembered details) into what it means to remember.
-These findings provide a window into which aspects of naturalistic experiences must be preserved, and which might be more flexible, in considering whether and how those experiences are remembered.
+  How our experiences unfold over time define unique \textit{thought
+    trajectories} through the relevant representational spaces.
+  Within this geometric framework, one can compare the shape of the
+  trajectory formed by an experience to that defined by our later
+  remembering of that experience.  We propose a framework for mapping
+  naturalistic experiences onto geometric spaces that characterize how
+  they unfold over time.  New insights emerge when we apply this
+  approach to a naturalistic memory experiment which had participants
+  view and recount a video.  We found that the shapes of the
+  trajectories formed by participants' recountings were all highly
+  similar to that of the original video, but participants differed in
+  the level of detail they remembered.  We also identified a network
+  of brain structures that are sensitive to the ``shapes'' of our
+  ongoing experiences, and an overlapping network that is sensitive to
+  how we will later remember those experiences.
 \end{abstract}
@@
 
-What does it mean to \textit{remember} something?
-In traditional episodic memory experiments \citep[e.g., list-learning or trial-based experiments;][]{Murd62a, Kaha96}, remembering is often cast as a binary operation: either a studied item is recalled or it isn't.
-More nuanced studies might incorporate self-reported confidence measures as a proxy for memory strength, or ask participants to discriminate between ``recollecting'' an experience or a general feeling of ``familiarity'' \citep{Yone02}.
-However, characterizing and evaluating memory in more realistic contexts (e.g., recounting a recent experience to a friend) concerns a much different set of criteria.
-First, real-world recall is continuous, rather than binary.
-Second, the specific words used to describe an experience have very little bearing on whether the experience is considered to have been ``remembered.''  Third, one might remember the gist or essence of an experience but forget (or neglect to recount) particular details.
-Or different people who share an experience might recount the experience with a similar level of detail, but the specific details that were remembered might vary across people.
-Which aspects of those recollections should be considered fundamental to determining to whast extent or how reliably an experience has been remembered?
+What does it mean to \textit{remember} something? In traditional
+episodic memory experiments \citep[e.g., list-learning or trial-based
+experiments;][]{Murd62a, Kaha96}, remembering is often cast as a
+discrete and binary operation: each studied item may be separated from
+the rest of one's experiences, and that item may be labeled as having
+been recalled versus forgotten. More nuanced studies might incorporate
+self-reported confidence measures as a proxy for memory strength, or
+ask participants to discriminate between ``recollecting'' the
+(contextual) details of an experience or having a general feeling of
+``familiarity'' \citep{Yone02}. However, characterizing and evaluating
+memory in more realistic contexts (e.g., recounting a recent
+experience to a friend) is fundamentally different.  First, real-world
+recall is continuous, rather than discrete.  Removing an event from
+the context in which it occurrs often subtantially changes its
+meaning.  Second, the specific words used to describe an experience
+have very little bearing on whether the experience is considered to
+have been ``remembered.''  Asking whether the rememberer has precisely
+reproduced a specific set of words to describe a given experience is
+nearly orthogonal to whether they were actually able to remember it.
+Third, one might remember the gist or essence of an experience but
+forget (or neglect to recount) particular details.  Capturing the gist
+of what happened is typically the ``point'' of recounting a memory to
+a listener but, depending on the circumstances, accurate recall of any
+specific detail may be irrelevant.
 
-%JRM STOPPED INPUTTING EDITS HERE
+% JRM REWRITES STOPPED HERE
 
-Human memory studies typically assess memory for the elements within an experience, such as the people, places and things encountered.
-However, real life experiences can also be described in terms of their temporal structure (i.e., how the contents relate/change over time).
-For instance, naturalistic experiences are autocorrelated in space and time on short timescales.
-In other words, the contents of an experience often change gradually and are therefore similar from moment to moment.
-As an example, many of us spend our mornings/evenings at home and much of our days at work (e.g.\ in an office).
-While the specific happenings within these contexts differ, they are often highly correlated (and thus predictable) within an experience.
-Furthermore, our experiences can also be characterized by longer timescale correlations.
-For example, consider returning to your office after taking a lunch break.
-The spatial contexts before and after lunch are highly similar, but separated in time.
-Thus, while evaluating the ability to recall the isolated elements of an experience has been a fruitful way to learn about human memory, another important dimension to consider is the temporal structure of the remembered experience, and how the temporal structure of the memory relates to the original experience.
-These recurrent and gradually changing temporal dynamics are not typically present in traditional memory studies, but are likely critical to understanding how our memory systems encode, store and retrieve our life experiences.
+%(JRM: started on the next paragraph...)
+Human memory studies typically assess memory for the elements within
+an experience, such as the people, places and things
+encountered. However, real life experiences can also be described in
+terms of their temporal structure (i.e., how the contents
+relate/change over time).  For instance, naturalistic experiences are
+autocorrelated in space and time on short timescales. In other words,
+the contents of an experience often change gradually and are therefore
+similar from moment to moment. As an example, many of us spend our
+mornings/evenings at home and much of our days at work (e.g., in an
+office). While the specific happenings within these contexts differ,
+they are often highly correlated (and thus predictable) within an
+experience. Furthermore, our experiences can also be characterized by
+longer timescale correlations. For example, consider returning to your
+office after taking a lunch break. The spatial contexts before and
+after lunch are highly similar, but separated in time. Thus, while
+evaluating the ability to recall the isolated elements of an
+experience has been a fruitful way to learn about human memory,
+another important dimension to consider is the temporal structure of
+the remembered experience, and how the temporal structure of the
+memory relates to the original experience. These recurrent and
+gradually changing temporal dynamics are not typically present in
+traditional memory studies, but are likely critical to understanding
+how our memory systems encode, store and retrieve our life
+experiences.
 
-While our experiences often change gradually, they can also sometimes change suddenly (e.g.\ walking through a doorway) \citep{RadvZack17}.
+While our experiences often change gradually, they can also sometimes change suddenly (e.g., walking through a doorway) \citep{RadvZack17}.
 Prior research suggests that these sharp transitions (coined in the literature as ``event boundaries'') during an experience may serve to descretize our memories into ``events'' \citep{RadvZack17, BrunEtal18, HeusEtal18, ClewDava17, EzzyDava11, DuBrDava13}.
@@
 
-\subsection{Results}
+\subsection*{Results}
 
@@
 
-\subsubsection{Modeling the naturalistic stimulus and verbal recall}
+\subsubsection*{Modeling the naturalistic stimulus and verbal recall}
 We fit a topic model \citep{BleiEtal03} to hand-annotated text descriptions of scenes from the video.
@@
 
-\subsubsection{Segmenting the video and recall models into ``events''}
+\subsubsection*{Segmenting the video and recall models into ``events''}
 As described above, a striking feature of both the video and recall correlation matrices is a strong, block structure along the diagonal of the matrices (see Fig.~\ref{fig:model}C,D).
@@
 
-\subsubsection{The trajectory of a naturalistic experience is preserved in recall}
+\subsubsection*{The trajectory of a naturalistic experience is preserved in recall}
 Classic approaches to studying free recall in episodic memory (such as overall accuracy and serial position curve) focus on the quantity of information recalled \citep{Murd62a}.
@@
 To further quantify this correspondence and to characterize how participants navigated through the space during recall, we analyzed the angle between successive recall events.
-We created a grid of evenly spaced points (.25 units) in the 2D ``topic space.'' For each point on the grid, we drew a circle (radius=.5) around the point and grouped together all recall transitions that intersected the circle (across subjects).
+We created a grid of evenly spaced points (.25 units) in the 2D ``topic space.'' For each point on the grid, we drew a circle (radius=.5) around the point and grouped together all recall transitions that intersected the circle (across participants).
 To visualize the average angle, we converted each transition angle to a unit vector and then averaged the vectors together.
@@
 %NOTE: it feels like we need some more supporting evidence that the shape of the video and the recall trajectories are related.
-one possibility would be to add the analysis where i compute the distance between each recall event and the line formed by each video transition per subject.
-the result is that hand annotated memory correlates to this distance, suggesting that subjects who better capture the shape also have better memory on average.
+one possibility would be to add the analysis where i compute the distance between each recall event and the line formed by each video transition per participant.
+the result is that hand annotated memory correlates to this distance, suggesting that participants who better capture the shape also have better memory on average.
 
-\subsubsection{Brain regions that mirror the correlational structure of naturalistic stimuli and memories}.
+\subsubsection*{Brain regions that mirror the correlational structure of naturalistic stimuli and memories}.
 \begin{figure}[t!]
@@
 While each participant remembered roughly the same sequence of events, there were subtle idiosyncracies in the way each individual described the events.
-For example, the event-by-event similarity structure (i.e.
-the off-diagonal values of the recall correlation matrices) differed across individuals (Supp.
+For example, the event-by-event similarity structure (i.e., the off-diagonal values of the recall correlation matrices) differed across individuals (Supp.
 Fig.~\ref{fig:corrmats}).
-We hypothesized that idiosyncracies in the recall dynamics across subjects might be related to the temporal structure of brain networks representing the events during video viewing.
+We hypothesized that idiosyncracies in the recall dynamics across participants might be related to the temporal structure of brain networks representing the events during video viewing.
 In this analysis, we identified brain areas whose responses at the time of viewing exhibited the same (segmented) idiosyncratic dynamics that later appeared in that participants’ recalls.
@@
 Error bars represent 95\% confidence intervals.
-Stars indicate top (green) and bottom (red) 3 remembered events across participants \textbf{B.} Wordles (top 200 words) representing a weighted average of video event topic vectors weighted by event memorability (e.g.\ the correlation values in A).
+Stars indicate top (green) and bottom (red) 3 remembered events across participants \textbf{B.} Wordles (top 200 words) representing a weighted average of video event topic vectors weighted by event memorability (e.g., the correlation values in A).
 The top wordle (green) contains words from the most remembered events and the bottom (red) contains words from least memorable events.
@@
 
-\subsubsection{Memorability by event and topics}
+\subsubsection*{Memorability by event and topics}
 A notable advantage of representing naturalistic stimuli and memory using this approach is that the event models can be mapped back to the language used to fit the model(s).
@@
 
-\subsubsection{Additional measures of naturalistic recall}
+\subsubsection*{Additional measures of naturalistic recall}
 Representing the video and verbal recall as events in ``topic space'' also affords us the ability to characterize the quality of recall in a more fine-grained and nuanced way than was previously possible.
@@
 In addition to providing a way to capture the shape of an experience, this method affords the ability to quantify the particular contents of memory.
-Whereas traditional approaches abstract over the content (e.g.\ percent correct), Our approach allows one to quantify which aspects of an experience are memorable and which fail to stick.
+Whereas traditional approaches abstract over the content (e.g., percent correct), Our approach allows one to quantify which aspects of an experience are memorable and which fail to stick.
 This aspect of our approach opens the door for a much richer characterization of memory that considers not just how much information was recalled, but the particular details of that information as well.
@@
 While we view this work as a major advance in characterizing and understanding human memory, as with any approach there are limitations.
-First, the approach relies on having a ``good'' model of the stimulus (e.g.\ one that describes the video in the same way as participants recall it), which is currently only achievable by a human hand-annotating each moment of the video.
+First, the approach relies on having a ``good'' model of the stimulus (e.g., one that describes the video in the same way as participants recall it), which is currently only achievable by a human hand-annotating each moment of the video.
 To increase the scalability of this approach, future work could explore automated methods for extracting meaning from videos ~\citep{YuEtal16}.
 Another potential limitation is that by its nature, the model extracts the ``gist'' of scenes from the video.
-This provides desirable flexibility (e.g.\ participants can use different combinations of words to describe the scenes), but this comes at the expense of capturing specific details.
+This provides desirable flexibility (e.g., participants can use different combinations of words to describe the scenes), but this comes at the expense of capturing specific details.
 Thus, a future direction of this work will be to increase sensitivity to such details while maintaining flexibility.
@@
 
-\subsection{Participants and Experimental Design}
+\subsection*{Participants and Experimental Design}
 Participants ($n=17$) viewed the first 50 minutes of ``A Study in Pink'', an episode of the BBC series, \textit{Sherlock}.
@@
 
-\subsubsection{Fitting the topic model to the video text and recall transcripts}
+\subsubsection*{Fitting the topic model to the video text and recall transcripts}
 A topic model was used to estimate the most likely mixture of topics for a given sample of text.
@@
 For example, the first text sample comprised the text from the first 50 segments, the 2nd comprised the text from n+1:n+51, and so on.
-We trained our model using these overlapping text samples with scikit-learn's (version 0.19.1) `CountVectorizer' and `LatentDirichletAllocation' classes \citep{PedrEtal11} implemented using our high-dimensional visualization/analysis software, Hypertools \citep{HeusEtal17a}.
+We trained our model using these overlapping text samples with scikit-learn's (version 0.19.1) `CountVectorizer' and `LatentDirichletAllocation' classes \citep{PedrEtal11} implemented using our high-dimensional visualization/analysis software, Hypertools \citep{HeusEtal18}.
 First, the text was transformed into a vector of word counts (after removing English stopwords).
@@
 
-\subsubsection{Choosing topic model parameters}
+\subsubsection*{Choosing topic model parameters}
 There were 3 critical parameters related to fitting the topic model: 1) the number of topics, 2) the window size of text descriptions of the video used to fit the model, and 3) the window size of recall sentences used to transform the recall data.
 To chose these parameter values, we performed a grid search where the range of possible parameter values was 1, 5, 10, 25, 50, 100, 200, and 500.
-Our optimization objective was defined as the correlation between the hand annotated memory performance and the root mean squared distance between the video model and the recall model before any further processing (e.g.\ hidden Markov modelling, averaging within event, etc).
+Our optimization objective was defined as the correlation between the hand annotated memory performance and the root mean squared distance between the video model and the recall model before any further processing (e.g., hidden Markov modelling, averaging within event, etc).
 While many of the parameter combination elicited moderately high correlations, the optimal choice was 100 topics, 50 video segments and 10 recall sentences.
@@
 
-\subsubsection{Extracting events using a hidden Markov model}
+\subsubsection*{Extracting events using a hidden Markov model}
 The topic model timepoint-by-timepoint correlation matrices all exhibited a block-diagonal structure (with small off-diagonal values), suggesting that the models were comprised of a number of sequential `states' (or events, see Supp.
@@
 
-\subsubsection{Matching recall events to video events}
+\subsubsection*{Matching recall events to video events}
 To estimate which video event each recall event referred to, we correlated the video events model and each recall events model.
@@
 
-\subsubsection{Visualizing the video and recall event models}
+\subsubsection*{Visualizing the video and recall event models}
 To visualize the temporal structure of the video event model (34 events by 100 topics) and the recall event models (8-27 events by 100 topics), we used a technique called UMAP ~\citep{McInHeal18} to reduce the ``topic-space'' from 100 dimensions down to 2 dimensions.
@@
 
-\subsubsection{Vector field analysis}
+\subsubsection*{Vector field analysis}
 To quantify the flow of recall from event to event, we performed a vector field analysis.
@@
 
-\subsection{fMRI analyses}
+\subsection*{fMRI analyses}
 Participants viewed and recalled the video stimulus inside an fMRI scanner.
@@
 
-\subsubsection{Searchlight analysis}
+\subsubsection*{Searchlight analysis}
 Our multivariate analyses were designed to capture brain regions whose timepoint-by-timepoint correlational structure mirrors the correlational structure of the video model as well as participant-specific recall topic models during video viewing.
@@
 
-\subsubsection{Topic vector word clouds}
+\subsubsection*{Topic vector word clouds}
 We created word clouds to visualize the themes contained in the recall events.
@@
 \textbf{B.} Contribution of each feature to video model/recall model relationship.
-The leftmost bar represents the across-subjects mean correlation between the video model and recall models trained on all features.
+The leftmost bar represents the across-participants mean correlation between the video model and recall models trained on all features.
 Subsequent bars represent the same relationship between video and recall models trained in the absence of a given feature.
-Error bars are the standard error of the mean across subjects.}
+Error bars are the standard error of the mean across participants.}
 \label{fig:feature-importance}
@@
 (2017).
-We found a strong positive correlation where subjects with a greater number of recall events also had better overall memory performance (Pearson's $r(16)=.67, p=.003$).
+We found a strong positive correlation where participants with a greater number of recall events also had better overall memory performance (Pearson's $r(16)=.67, p=.003$).
 Then, we considered how participants initiated the recall sequence (known in the literature as the `probability of first recall' or `PFR').
@@
 \section*{Supplemental Methods}
-\subsection{Quantifying the importance of features}
-To determine the contribution of each feature to the structure of the video model, we examined the similarity between the temporal structure of models trained in the absence of a single feature and that of our original (i.e.
-full) model (Supp.
+\subsection*{Quantifying the importance of features}
+To determine the contribution of each feature to the structure of the video model, we examined the similarity between the temporal structure of models trained in the absence of a single feature and that of our original (i.e., full) model (Supp.
 Fig.~\ref{fig:feature-importance}A).
@@
 Fig.~\ref{fig:feature-importance}B).
-For each feature removed, we transformed each subject’s recall transcript using a model trained on the feature-deprived video text windows (of 50 scene segments), and resampled the recall timeseries to match the shape of the video model (1976 timepoints).
-We then represented the temporal structures of each subject’s recall model as timepoints-by -timepoints correlation matrices and computed the average correlation with the temporal structure of the video model (across subjects).
+For each feature removed, we transformed each participant’s recall transcript using a model trained on the feature-deprived video text windows (of 50 scene segments), and resampled the recall timeseries to match the shape of the video model (1976 timepoints).
+We then represented the temporal structures of each participant’s recall model as timepoints-by -timepoints correlation matrices and computed the average correlation with the temporal structure of the video model (across participants).
 
-\subsection{List-learning analyses}
+\subsection*{List-learning analyses}
 \textbf{Overall Accuracy.}  To get an overall measure of the quantity of information recalled, we computed the proportion of sucessfully recalled events by counting the number of unique recall events identified by the HMM model and dividing by the total number of video events.
@@
 Then for each participant, we found the index of the video event that was recalled first and filled in that index in the matrix with a 1.
-Finally, we averaged over the rows of the matrix, resulting in a 1 by 34 array representing the proportion of subject that recalled an event as a function of serial position during encoding.
+Finally, we averaged over the rows of the matrix, resulting in a 1 by 34 array representing the proportion of participant that recalled an event as a function of serial position during encoding.
 
@@
 This resulted in a matrix where 1s indicate the successful recall of an event in serial position $n$ and zeros indicate the lack of recall for that event.
-Lastly, we averaged over the rows of the matrix to get a 1 by 34 array representing the proportion of subjects that recalled an event as a function of its serial position.
+Lastly, we averaged over the rows of the matrix to get a 1 by 34 array representing the proportion of participants that recalled an event as a function of its serial position.
 
@@
 
-\subsection{Additional measures of naturalistic memory}
+\subsection*{Additional measures of naturalistic memory}
 \textbf{Precision.} This measure gives us an indication of the specific match between a video event and recall event, where values approaching 1 are highly precise and lower values are inprecise.

### 2018-08-28 paper/main.tex
checking in interim changes to intro [WIP]

@@
 
-What does it mean to \textit{remember} something? In traditional
-episodic memory experiments \citep[e.g., list-learning or trial-based
-experiments;][]{Murd62a, Kaha96}, remembering is often cast as a
-discrete and binary operation: each studied item may be separated from
-the rest of one's experiences, and that item may be labeled as having
-been recalled versus forgotten. More nuanced studies might incorporate
-self-reported confidence measures as a proxy for memory strength, or
-ask participants to discriminate between ``recollecting'' the
-(contextual) details of an experience or having a general feeling of
-``familiarity'' \citep{Yone02}. However, characterizing and evaluating
-memory in more realistic contexts (e.g., recounting a recent
-experience to a friend) is fundamentally different.  First, real-world
-recall is continuous, rather than discrete.  Removing an event from
-the context in which it occurrs often subtantially changes its
-meaning.  Second, the specific words used to describe an experience
-have very little bearing on whether the experience is considered to
-have been ``remembered.''  Asking whether the rememberer has precisely
-reproduced a specific set of words to describe a given experience is
-nearly orthogonal to whether they were actually able to remember it.
-Third, one might remember the gist or essence of an experience but
-forget (or neglect to recount) particular details.  Capturing the gist
-of what happened is typically the ``point'' of recounting a memory to
-a listener but, depending on the circumstances, accurate recall of any
-specific detail may be irrelevant.
+What does it mean to \textit{remember} something?
+In traditional episodic memory experiments \citep[e.g., list-learning or trial-based experiments;][]{Murd62a, Kaha96}, remembering is often cast as a discrete and binary operation: each studied item may be separated from the rest of one's experiences, and that item may be labeled as having been recalled versus forgotten.
+More nuanced studies might incorporate self-reported confidence measures as a proxy for memory strength, or ask participants to discriminate between ``recollecting'' the (contextual) details of an experience or having a general feeling of ``familiarity'' \citep{Yone02}.
+However, characterizing and evaluating memory in more realistic contexts (e.g., recounting a recent experience to a friend) is fundamentally different in at least three ways~\citep[also see][for a review]{KoriGold94}.
+First, real world recall is continuous, rather than discrete.
+Removing an event from the context in which it occurrs often subtantially changes its meaning.
+Second, the specific words used to describe an experience have very little bearing on whether the experience is considered to have been ``remembered.''  Asking whether the rememberer has precisely reproduced a specific set of words to describe a given experience is nearly orthogonal to whether they were actually able to remember it.
+Third, one might remember the gist or essence of an experience but forget (or neglect to recount) particular details.
+Capturing the gist of what happened is typically the main ``point'' of recounting a memory to a listener whereas, depending on the circumstances, accurate recall of any specific detail may be irrelevant.
 
-% JRM REWRITES STOPPED HERE
+How might one go about formally characterizing the ``gist'' of an experience?
+Real world experiences unfold over extended time intervals.
+Any given moment of an experience might derive meaning from surrounding moments, as well as from longer-range temporal associations~\citep[e.g.\ ][]{LernEtal11}.
+This interplay between our subjective experiences at different timescales defines a \textit{context} for each new moment, and plays an important role in how we interpret that moment and remember it later~\citep[for review see][]{MannEtal15}.
+Further, our memory systems can leverage these associations to form predictions that help guide our behaviors~\citep{RangRitc12}.
+For example, as we navigate the world, the features of our subjective experiences tend to change gradually (e.g.\ the room or situation we are in is strongly temporally autocorrelated).
+This allows us to form stable estimates of our current situation and thereby behave accordingly~\citep{ZackEtal07, ZwaaRadv98}.
+%%%JRM STOPPED HERE
+Although our experiences often change gradually, they occasionaly change suddenly~\citep[e.g., walking through a doorway][]{RadvZack17}.
 
-%(JRM: started on the next paragraph...)
-Human memory studies typically assess memory for the elements within
-an experience, such as the people, places and things
-encountered. However, real life experiences can also be described in
-terms of their temporal structure (i.e., how the contents
-relate/change over time).  For instance, naturalistic experiences are
-autocorrelated in space and time on short timescales. In other words,
-the contents of an experience often change gradually and are therefore
-similar from moment to moment. As an example, many of us spend our
-mornings/evenings at home and much of our days at work (e.g., in an
-office). While the specific happenings within these contexts differ,
-they are often highly correlated (and thus predictable) within an
-experience. Furthermore, our experiences can also be characterized by
-longer timescale correlations. For example, consider returning to your
-office after taking a lunch break. The spatial contexts before and
-after lunch are highly similar, but separated in time. Thus, while
-evaluating the ability to recall the isolated elements of an
-experience has been a fruitful way to learn about human memory,
-another important dimension to consider is the temporal structure of
-the remembered experience, and how the temporal structure of the
-memory relates to the original experience. These recurrent and
-gradually changing temporal dynamics are not typically present in
-traditional memory studies, but are likely critical to understanding
-how our memory systems encode, store and retrieve our life
-experiences.
-
-While our experiences often change gradually, they can also sometimes change suddenly (e.g., walking through a doorway) \citep{RadvZack17}.
 Prior research suggests that these sharp transitions (coined in the literature as ``event boundaries'') during an experience may serve to descretize our memories into ``events'' \citep{RadvZack17, BrunEtal18, HeusEtal18, ClewDava17, EzzyDava11, DuBrDava13}.
@@
 Decades of research suggest that episodic memories are not veridical and context-free snapshots of the past, and so treating (and modelling) them as such is overly simplistic at best (and counterproductive at worst).
-While it's undeniable that these models have been useful in advancing our understanding of human memory, they are severely limited in their ability to explain memory for real-life experiences.
-Real-life experiences are highly structured in time, and so to have a complete understanding of the human memory system, our experiments and models of memory must not ignore this fact.
+While it's undeniable that these models have been useful in advancing our understanding of human memory, they are severely limited in their ability to explain memory for real life experiences.
+Real life experiences are highly structured in time, and so to have a complete understanding of the human memory system, our experiments and models of memory must not ignore this fact.
 Our work provides a theoretical advance in our understanding of what it means to remember as well as a novel methodological tool to study it.

### 2018-08-28 paper/main.tex
legend

--- 2018-08-28 paper/main.tex
@@
 recall is continuous, rather than discrete.  Removing an event from
-the context in which it occurrs often subtantially changes its
+the context in which it occurs often substantially changes its
 meaning.  Second, the specific words used to describe an experience
@@
 While our experiences often change gradually, they can also sometimes change suddenly (e.g., walking through a doorway) \citep{RadvZack17}.
-Prior research suggests that these sharp transitions (coined in the literature as ``event boundaries'') during an experience may serve to descretize our memories into ``events'' \citep{RadvZack17, BrunEtal18, HeusEtal18, ClewDava17, EzzyDava11, DuBrDava13}.
+Prior research suggests that these sharp transitions (coined in the literature as ``event boundaries'') during an experience may serve to discretize our memories into ``events'' \citep{RadvZack17, BrunEtal18, HeusEtal18, ClewDava17, EzzyDava11, DuBrDava13}.
 Short-timescale autocorrelations in the contents of an experience are thought to associatively link information in memory, while more drastic changes in perceptual or semantic aspects of an experience may lead to discontinuities in memory \citep{HeusEtal18, BrunEtal18, EzzyDava11, DuBrDava13}.
@@
 To get a better handle on this temporal structure, we computed a timepoints (1976) by timepoints (1976) correlation matrix of the video model (Fig.~\ref{fig:model}C).
-This correlation matrix reveals that the model has a strong, block-diagonal structure with very low off-diagonal correlation values, suggesting the representations of each block are unique and highly descriminable.
+This correlation matrix reveals that the model has a strong, block-diagonal structure with very low off-diagonal correlation values, suggesting the representations of each block are unique and highly discriminable.
 We found that the ``narrative details'' (a few sentences summarizing the dialogue and specific happenings of the scene) of the video were the most important feature driving this model structure (see Supp.
@@
 To chose these parameter values, we performed a grid search where the range of possible parameter values was 1, 5, 10, 25, 50, 100, 200, and 500.
-Our optimization objective was defined as the correlation between the hand annotated memory performance and the root mean squared distance between the video model and the recall model before any further processing (e.g., hidden Markov modelling, averaging within event, etc).
+Our optimization objective was defined as the correlation between the hand annotated memory performance and the root mean squared distance between the video model and the recall model before any further processing (e.g., hidden Markov modeling, averaging within event, etc).
 While many of the parameter combination elicited moderately high correlations, the optimal choice was 100 topics, 50 video segments and 10 recall sentences.
@@
 Subsequent bars represent the same relationship between video and recall models trained in the absence of a given feature.
-Error bars are the standard error of the mean across participants.}
+Error bars are the standard error of the mean across participants.
+\textbf{C.}  Individual feature trajectory similarity matrix.
+The first row/column is the topic trajectory the full video model.
+Each subsequent row/column is that of a single feature.
+Shading corresponds to the value of the correlation coefficient (Pearson's $r$) .}
 \label{fig:feature-importance}

### 2018-08-29 paper/main.tex
JRM finished pass through intro

--- 2018-08-28 paper/main.tex
@@
 \begin{abstract}
-  How our experiences unfold over time define unique \textit{thought
-    trajectories} through the relevant representational spaces.
-  Within this geometric framework, one can compare the shape of the
-  trajectory formed by an experience to that defined by our later
-  remembering of that experience.  We propose a framework for mapping
-  naturalistic experiences onto geometric spaces that characterize how
-  they unfold over time.  New insights emerge when we apply this
-  approach to a naturalistic memory experiment which had participants
-  view and recount a video.  We found that the shapes of the
-  trajectories formed by participants' recountings were all highly
-  similar to that of the original video, but participants differed in
-  the level of detail they remembered.  We also identified a network
-  of brain structures that are sensitive to the ``shapes'' of our
-  ongoing experiences, and an overlapping network that is sensitive to
-  how we will later remember those experiences.
+How our experiences unfold over time define unique \textit{trajectories} through the relevant representational spaces.
+Within this geometric framework, one can compare the shape of the trajectory formed by an experience to that defined by our later remembering of that experience.
+We propose a framework for mapping naturalistic experiences onto geometric spaces that characterize how they unfold over time.
+New insights emerge when we apply this approach to a naturalistic memory experiment which had participants view and recount a video.
+We found that the shapes of the trajectories formed by participants' recountings were all highly similar to that of the original video, but participants differed in the level of detail they remembered.
+We also identified a network of brain structures that are sensitive to the ``shapes'' of our ongoing experiences, and an overlapping network that is sensitive to how we will later remember those experiences.
 \end{abstract}
@@
 First, real world recall is continuous, rather than discrete.
-Removing an event from the context in which it occurrs often subtantially changes its meaning.
-Second, the specific words used to describe an experience have very little bearing on whether the experience is considered to have been ``remembered.''  Asking whether the rememberer has precisely reproduced a specific set of words to describe a given experience is nearly orthogonal to whether they were actually able to remember it.
+Unlike in trial-based experiments, removing a (naturalistic) event from the context in which it occurs can substantially change its meaning.
+Second, the specific words used to describe an experience have little bearing on whether the experience should be considered to have been ``remembered.''  Asking whether the rememberer has precisely reproduced a specific set of words to describe a given experience is nearly orthogonal to whether they were actually able to remember it.
+In classic (e.g., list-learning) memory studies, precise recall is often a primary metric of assessing the quality of participants' memories.
 Third, one might remember the gist or essence of an experience but forget (or neglect to recount) particular details.
 Capturing the gist of what happened is typically the main ``point'' of recounting a memory to a listener whereas, depending on the circumstances, accurate recall of any specific detail may be irrelevant.
+There is no analog of the ``gist'' of an experience in most traditional memory experiments; rather we tend to assess participants' abilities to recover specific details (e.g., the precise stimuli they encountered earlier in the experiment).
 
 How might one go about formally characterizing the ``gist'' of an experience?
-Real world experiences unfold over extended time intervals.
 Any given moment of an experience might derive meaning from surrounding moments, as well as from longer-range temporal associations~\citep[e.g.\ ][]{LernEtal11}.
-This interplay between our subjective experiences at different timescales defines a \textit{context} for each new moment, and plays an important role in how we interpret that moment and remember it later~\citep[for review see][]{MannEtal15}.
-Further, our memory systems can leverage these associations to form predictions that help guide our behaviors~\citep{RangRitc12}.
-For example, as we navigate the world, the features of our subjective experiences tend to change gradually (e.g.\ the room or situation we are in is strongly temporally autocorrelated).
-This allows us to form stable estimates of our current situation and thereby behave accordingly~\citep{ZackEtal07, ZwaaRadv98}.
-%%%JRM STOPPED HERE
-Although our experiences often change gradually, they occasionaly change suddenly~\citep[e.g., walking through a doorway][]{RadvZack17}.
+Therefore perhaps the timecourse of how an event unfolds might be critical to its overall meaning.
+Further, this hierarchy formed by our subjective experiences at different timescales defines a \textit{context} for each new moment~\citep[e.g., ][]{HowaKaha02, HowaEtal14}, and plays an important role in how we interpret that moment and remember it later~\citep[for review see][]{MannEtal15}.
+Our memory systems can then leverage these associations to form predictions that help guide our behaviors~\citep{RangRitc12}.
+For example, as we navigate the world, the features of our subjective experiences tend to change gradually (e.g.\ the room or situation we are in is strongly temporally autocorrelated), allowing us to form stable estimates of our current situation and behave accordingly~\citep{ZackEtal07, ZwaaRadv98}.
+Although our experiences typically change gradually, they also occasionally change suddenly~\citep[e.g., walking through a doorway; ][]{RadvZack17}.
+Prior research suggests that these sharp transitions (termed \textit{event boundaries}) during an experience help to discretize our experiences into \textit{events}~\citep{RadvZack17, BrunEtal18, HeusEtal18, ClewDava17, EzzyDava11, DuBrDava13}.
+The interplay between the stable (within event) and transient (across event) temporal dynamics of an experience also provides a potential framework for transforming experiences into compressed memories.
+For example, prior work has shown that event boundaries can influence how we learn sequences of items~\citep{HeusEtal18, DuBrDava13}, navigate~\citep{BrunEtal18}, and remember and understand narratives~\citep{ZwaaRadv98, EzzyDava11}.
 
-Prior research suggests that these sharp transitions (coined in the literature as ``event boundaries'') during an experience may serve to descretize our memories into ``events'' \citep{RadvZack17, BrunEtal18, HeusEtal18, ClewDava17, EzzyDava11, DuBrDava13}.
-Short-timescale autocorrelations in the contents of an experience are thought to associatively link information in memory, while more drastic changes in perceptual or semantic aspects of an experience may lead to discontinuities in memory \citep{HeusEtal18, BrunEtal18, EzzyDava11, DuBrDava13}.
-In other words, the interplay between stable and transient temporal dynamics may impose structure on memories for those experiences.
-There is now compelling evidence that event boundaries can influence memory organization when learning sequences of items \citep{HeusEtal18, DuBrDava13}, during navigation \citep{BrunEtal18}, and narrative comprehension \citep{ZwaaRadv98, EzzyDava11}.
-However, whether people verbally recount their experiences in a way that is structured around events has not been established.
+Here we sought to examine how temporal dynamics of a ``naturalistic'' experience was reflected in participants' later memories of that experience.
+We analyzed an open dataset which comprised behavioral and functional Magnetic Resonance Imaging (fMRI) data collected as participants viewed and then verbally recalled an episode of the BBC television series \textit{Sherlock}~\citep{ChenEtal17}.
+We developed a computational framework for characterizing the temporal dynamics of the moment-by-moment content of the episode (and of participants' verbal recalls).
+Specifically, we use topic modeling~\citep{BleiEtal03} to characterize the thematic conceptual (semantic) content present in each moment of the episode and recalls, and we use Hidden Markov Models~\citep{Rabi89, BaldEtal17} to discretize the evolving semantic content into events.
+In this way, we cast naturalistic experiences (and recalls of those experiences) as \textit{topic trajectories} that describe how the experiences evolve over time.
+In other words, the episode's topic trajectory is a formalization of its gist.
+Under this framework, successful remembering entails verbally ``traversing'' the topic trajectory of the original episode, thereby reproducing the gist of the original episode.
+In addition, comparing the shapes of the topic trajectories of the original episode and of participants' retelling of the episode reveals which aspects of the episode were preserved (or lost) in the translation into memory.
+We also identified a network of brain structures whose responses (as participants watched the episode) reflected the gist of the episode, and a second network whose responses reflected how participants would later recount the episode.
 
-In this study, we analyzed an open dataset in which participants view and then verbally recall an episode of the BBC series \textit{Sherlock} \citep{ChenEtal17}.
-To capture the temporal structure of the video, we developed a novel computational approach based on topic modeling \citep{BleiEtal03} and hidden Markov models \citep{Rabi89, BaldEtal17}.
-This technique casts naturalistic stimuli as high-dimensional topic ``trajectories'', whereby the theme of each moment of the video is represented as a topic vector.
-In this framework, successful remembering entails verbally ``traversing'' the path formed by the stimulus topic trajectory as closely as possible.
-We hypothesized that successful memory for a naturalistic stimulus is given by a recall trajectory that closely follows the path (and covers the entirety) of the stimulus trajectory.
+%JRM STOPPED HERE
 
@@
 
-\begin{figure}[th!]
+\begin{figure}[t]
 \centering
@@
 
-\begin{figure}[t!]
+\begin{figure}[t]
 \centering
@@
 \subsubsection*{Brain regions that mirror the correlational structure of naturalistic stimuli and memories}.
-\begin{figure}[t!]
+\begin{figure}[t]
 \centering
@@
 % Supplemental materials
-\begin{suppfigure}[t!]
+\begin{suppfigure}[t]
 \centering
@@
 
-\begin{suppfigure}[t!]
+\begin{suppfigure}[t]
 \centering

### 2018-08-29 paper/main.tex
minor typo fixes to intro

@@
 How might one go about formally characterizing the ``gist'' of an experience?
-Any given moment of an experience might derive meaning from surrounding moments, as well as from longer-range temporal associations~\citep[e.g.\ ][]{LernEtal11}.
-Therefore perhaps the timecourse of how an event unfolds might be critical to its overall meaning.
+Any given moment of an experience derives meaning from surrounding moments, as well as from longer-range temporal associations~\citep[e.g., ][]{LernEtal11}.
+Therefore the timecourse of how an event unfolds is fundamental to its overall meaning.
 Further, this hierarchy formed by our subjective experiences at different timescales defines a \textit{context} for each new moment~\citep[e.g., ][]{HowaKaha02, HowaEtal14}, and plays an important role in how we interpret that moment and remember it later~\citep[for review see][]{MannEtal15}.
@@
 For example, as we navigate the world, the features of our subjective experiences tend to change gradually (e.g.\ the room or situation we are in is strongly temporally autocorrelated), allowing us to form stable estimates of our current situation and behave accordingly~\citep{ZackEtal07, ZwaaRadv98}.
-Although our experiences typically change gradually, they also occasionally change suddenly~\citep[e.g., walking through a doorway; ][]{RadvZack17}.
+Although our experiences typically change gradually, they also occasionally change suddenly~\citep[e.g., when we walk through a doorway; ][]{RadvZack17}.
 Prior research suggests that these sharp transitions (termed \textit{event boundaries}) during an experience help to discretize our experiences into \textit{events}~\citep{RadvZack17, BrunEtal18, HeusEtal18, ClewDava17, EzzyDava11, DuBrDava13}.
@@
 
-Here we sought to examine how temporal dynamics of a ``naturalistic'' experience was reflected in participants' later memories of that experience.
+Here we sought to examine how the temporal dynamics of a ``naturalistic'' experience were reflected in participants' later memories of that experience.
 We analyzed an open dataset which comprised behavioral and functional Magnetic Resonance Imaging (fMRI) data collected as participants viewed and then verbally recalled an episode of the BBC television series \textit{Sherlock}~\citep{ChenEtal17}.
@@
 Under this framework, successful remembering entails verbally ``traversing'' the topic trajectory of the original episode, thereby reproducing the gist of the original episode.
-In addition, comparing the shapes of the topic trajectories of the original episode and of participants' retelling of the episode reveals which aspects of the episode were preserved (or lost) in the translation into memory.
+In addition, comparing the shapes of the topic trajectories of the original episode and of participants' retellings of the episode reveals which aspects of the episode were preserved (or lost) in the translation into memory.
 We also identified a network of brain structures whose responses (as participants watched the episode) reflected the gist of the episode, and a second network whose responses reflected how participants would later recount the episode.

### 2018-08-29 paper/main.tex
updated figure, updated legend, new supp methods section

--- 2018-08-28 paper/main.tex
@@
 For each feature removed, we transformed each participant’s recall transcript using a model trained on the feature-deprived video text windows (of 50 scene segments), and resampled the recall timeseries to match the shape of the video model (1976 timepoints).
-We then represented the temporal structures of each participant’s recall model as timepoints-by -timepoints correlation matrices and computed the average correlation with the temporal structure of the video model (across participants).
+We then represented the temporal structures of each participant’s recall model as timepoints-by-timepoints correlation matrices and computed the average correlation with the temporal structure of the video model (across participants).
+
+The two prior analyses examine information (about either the video model structure or the video/recall model relationship) lost in the absence of each feature.
+However, they do not consider redundancy in the information each feature contributes (e.g., how much unique information does "Character speaking" provide that "Character in focus" does not?).
+As a measure of information overlap between features, we computed the similarity between the topic trajectories of each individual annotated feature in addition to the full feature set.
+First, we singularly transformed the text of each feature using a model trained on the collection of all features.
+We then represented the single feature's model's temporal structure as a timepoints-by-timepoints correlation matrix, and compared the temporal structures pairwise by constructing a features-by-features correlation matrix ((Supp.
+Fig.~\ref{fig:feature-importance}C).
+We additionally computed the correlation between the individual features' temporal structures and that of the full video model as a measure of the proportion of information discernible from that feature alone.
 

### 2018-08-29 paper/main.tex
formatting edits

--- 2018-08-29 paper/main.tex
@@
 
-%JRM STOPPED HERE
-
-\subsection*{Results}
+\section*{Results}
 
@@
 
-\subsubsection*{Modeling the naturalistic stimulus and verbal recall}
+\subsection*{Modeling the naturalistic stimulus and verbal recall}
 We fit a topic model \citep{BleiEtal03} to hand-annotated text descriptions of scenes from the video.
@@
 
-\subsubsection*{Segmenting the video and recall models into ``events''}
+\subsection*{Segmenting the video and recall models into ``events''}
 As described above, a striking feature of both the video and recall correlation matrices is a strong, block structure along the diagonal of the matrices (see Fig.~\ref{fig:model}C,D).
@@
 
-\subsubsection*{The trajectory of a naturalistic experience is preserved in recall}
+\subsection*{The trajectory of a naturalistic experience is preserved in recall}
 Classic approaches to studying free recall in episodic memory (such as overall accuracy and serial position curve) focus on the quantity of information recalled \citep{Murd62a}.
@@
 
-\subsubsection*{Brain regions that mirror the correlational structure of naturalistic stimuli and memories}.
+\subsection*{Brain regions that mirror the correlational structure of naturalistic stimuli and memories}.
 \begin{figure}[t]
@@
 
-\subsubsection*{Memorability by event and topics}
+\subsection*{Memorability by event and topics}
 A notable advantage of representing naturalistic stimuli and memory using this approach is that the event models can be mapped back to the language used to fit the model(s).
@@
 
-\subsubsection*{Additional measures of naturalistic recall}
+\subsection*{Additional measures of naturalistic recall}
 Representing the video and verbal recall as events in ``topic space'' also affords us the ability to characterize the quality of recall in a more fine-grained and nuanced way than was previously possible.
@@
 
-\pagebreak
 \bibliography{memlab}
 
-\pagebreak
 \section*{Methods}
@@
 
-\subsubsection*{Fitting the topic model to the video text and recall transcripts}
+\subsection*{Fitting the topic model to the video text and recall transcripts}
 A topic model was used to estimate the most likely mixture of topics for a given sample of text.

### 2018-08-29 paper/boneyard.tex

--- 2018-07-23 boneyard.tex
@@
+These features of real world memory provide a stark contrast with classic list-learning memory tasks that ask participants to reproduce from memory a set of studied items (e.g.
+words)-- whereby each word's meaning is distinct from surrounding words, and successful memory for a given word entails reproducing it exactly during recall.
+So how might one go about assessing the quality of real world memory?
+Which analysis methods and findings from the list-learning literature apply to real world learning?
+And how might one go about formally characterizing whether (or how well) the ``gist'' of a memory has been accurately remembered?
+
+A defining characteristic of
+
+One approach to studying memory for naturalistic experiences and real life events in the laboratory has been to quantify the participant's ability to recall specific aspects of the experience, such as the people, places, and things encountered~\citep[e.g.\ for review see][]{KoriGold94}.
+This essentially
+
+Human memory studies typically assess memory for the elements within an experience, such as the people, places and things encountered.
+However, real life experiences can also be described in terms of their temporal structure (i.e., how the contents relate/change over time).
+For instance, naturalistic experiences are autocorrelated in space and time on short timescales.
+In other words, the contents of an experience often change gradually and are therefore similar from moment to moment.
+As an example, many of us spend our mornings/evenings at home and much of our days at work (e.g., in an office).
+While the specific happenings within these contexts differ, they are often highly correlated (and thus predictable) within an experience.
+Furthermore, our experiences can also be characterized by longer timescale correlations.
+For example, consider returning to your office after taking a lunch break.
+The spatial contexts before and after lunch are highly similar, but separated in time.
+Thus, while evaluating the ability to recall the isolated elements of an experience has been a fruitful way to learn about human memory, another important dimension to consider is the temporal structure of the remembered experience, and how the temporal structure of the memory relates to the original experience.
+These recurrent and gradually changing temporal dynamics are not typically present in traditional memory studies, but are likely critical to understanding how our memory systems encode, store and retrieve our life experiences.
+
 Another interesting feature of the recall matrices is the off-diagonal structure, which represents the use of language that generalizes to more than one event.

### 2018-08-29 paper/main.tex
working on results section (backing up progress) [WIP]

@@
 In classic (e.g., list-learning) memory studies, precise recall is often a primary metric of assessing the quality of participants' memories.
-Third, one might remember the gist or essence of an experience but forget (or neglect to recount) particular details.
+Third, one might remember the \textit{gist} or essence of an experience but forget (or neglect to recount) particular details.
 Capturing the gist of what happened is typically the main ``point'' of recounting a memory to a listener whereas, depending on the circumstances, accurate recall of any specific detail may be irrelevant.
-There is no analog of the ``gist'' of an experience in most traditional memory experiments; rather we tend to assess participants' abilities to recover specific details (e.g., the precise stimuli they encountered earlier in the experiment).
+There is no analog of the gist of an experience in most traditional memory experiments; rather we tend to assess participants' abilities to recover specific details (e.g., the precise stimuli they encountered earlier in the experiment).
 
-How might one go about formally characterizing the ``gist'' of an experience?
+How might one go about formally characterizing the gist of an experience?
 Any given moment of an experience derives meaning from surrounding moments, as well as from longer-range temporal associations~\citep[e.g., ][]{LernEtal11}.
@@
 For example, as we navigate the world, the features of our subjective experiences tend to change gradually (e.g.\ the room or situation we are in is strongly temporally autocorrelated), allowing us to form stable estimates of our current situation and behave accordingly~\citep{ZackEtal07, ZwaaRadv98}.
-Although our experiences typically change gradually, they also occasionally change suddenly~\citep[e.g., when we walk through a doorway; ][]{RadvZack17}.
+Although our experiences most often change gradually, they also occasionally change suddenly~\citep[e.g., when we walk through a doorway; ][]{RadvZack17}.
 Prior research suggests that these sharp transitions (termed \textit{event boundaries}) during an experience help to discretize our experiences into \textit{events}~\citep{RadvZack17, BrunEtal18, HeusEtal18, ClewDava17, EzzyDava11, DuBrDava13}.
-The interplay between the stable (within event) and transient (across event) temporal dynamics of an experience also provides a potential framework for transforming experiences into compressed memories.
+The interplay between the stable (within event) and transient (across event) temporal dynamics of an experience also provides a potential framework for transforming experiences into memories that distill those experiences down to their essence-- i.e., their gists.
 For example, prior work has shown that event boundaries can influence how we learn sequences of items~\citep{HeusEtal18, DuBrDava13}, navigate~\citep{BrunEtal18}, and remember and understand narratives~\citep{ZwaaRadv98, EzzyDava11}.
@@
 \section*{Results}
+We sought to formalize the gists of a naturalistic stimulus (an episode of the \textit{Sherlock} television show) and participants' recountings of that stimulus.
+% JRM STOPPED HERE
+% - add a general overview
+% - some of this seems like it belongs in methods...
+% - possible section title change to "Narrative?" -- see author guidelines and prior nature submissions
 
@@
 The directional lines connecting the points represent the true video event order.
-The arrows represent the group-average direction of all recall event transitions (i.e., a line segment connecting two consecutive recall event vectors) that intersected a circle (radius=.5) centered on the origin of the arrow.
+The arrows represent the group-average direction of all recall event transitions (i.e., a line segment connecting two consecutive recall event vectors) that intersected a circle (radius = 0.5) centered on the origin of the arrow.
 \textbf{C.} Individual trajectory plots for each participant overlayed with the video model (black).
@@
 To further quantify this correspondence and to characterize how participants navigated through the space during recall, we analyzed the angle between successive recall events.
-We created a grid of evenly spaced points (.25 units) in the 2D ``topic space.'' For each point on the grid, we drew a circle (radius=.5) around the point and grouped together all recall transitions that intersected the circle (across participants).
+We created a grid of evenly spaced points (.25 units) in the 2D ``topic space.'' For each point on the grid, we drew a circle (radius= 0.5) around the point and grouped together all recall transitions that intersected the circle (across participants).
 To visualize the average angle, we converted each transition angle to a unit vector and then averaged the vectors together.
-To assess consistency in the direction of the recall transition across participants, we performed a Rayleigh test ($p<.001$, corrected at $p<.05$ using the permutation procedure described in Methods).
+To assess consistency in the direction of the recall transition across participants, we performed a Rayleigh test ($p < 0.001$, corrected at $p < 0.05$ using the permutation procedure described in Methods).
 Notably, the video events fell within the path formed by the recall events.
@@
 We quantified the distance between each video event and its matching recall event (``precision''), the the distance between a video event and all non-matching recall events (``distinctiveness'') and the temporal order of the recall events (``order'').
-All three of these metrics were correlated to hand-annotated memory performance across participants ($p<.05$, see Supplemental Materials Section 1 for details).
+All three of these metrics were correlated to hand-annotated memory performance across participants ($p < 0.05$, see Supplemental Materials Section 1 for details).
 
@@
 We tiled the 2D topic space (x, y: -6 to 6 by .25) with an evenly spaced grid.
-For each grid point, we drew a circle around the point (radius=.5).
+For each grid point, we drew a circle around the point (radius= 0.5).
 Then, we tested whether any line segments (formed by event recall transitions) passed through this area of the topic space.
@@
 Lastly, we converted each unit vector to an angle (in radians) by taking the inverse tangent of the x, y components of the vector.
-To test whether the distribution of angles was significantly non-uniform (i.e., displayed a preferred direction across participants), we performed a Rayleigh test on the angles ($p<.001$, FDR-corrected at $p<.05$ using Benjamani-Hochberg procedure).
+To test whether the distribution of angles was significantly non-uniform (i.e., displayed a preferred direction across participants), we performed a Rayleigh test on the angles ($p < 0.001$, FDR-corrected at $p < 0.05$ using Benjamani-Hochberg procedure).
 Arrows where the Rayleigh test was significant are displayed in color (the darker the blue the more significant) while non-significant tests are displayed in gray with lower opacity.
@@
 (2017).
-We found a strong positive correlation where participants with a greater number of recall events also had better overall memory performance (Pearson's $r(16)=.67, p=.003$).
+We found a strong positive correlation where participants with a greater number of recall events also had better overall memory performance (Pearson's $r(16) = 0.67, p = 0.003$).
 Then, we considered how participants initiated the recall sequence (known in the literature as the `probability of first recall' or `PFR').
@@
 We also considered two additional across-participant measures of recall that characterize memory organization: temporal clustering and semantic clustering.
-We found that participants who clustered in time also recalled a greater number of events (Pearson's $r(16)=.62, p=.007$).
+We found that participants who clustered in time also recalled a greater number of events (Pearson's $r(16) = 0.62, p = 0.007$).
 Next, we assessed semantic clustering.
-We found that the semantic clustering score was related to memory performance across participants (Pearson's $r(16)=.55, p=.02$).
+We found that the semantic clustering score was related to memory performance across participants (Pearson's $r(16) = 0.55, p = 0.02$).
 Thus, participants who organized their recalls with respect to the semantic information contained in the scene had better memory performance.
@@
 To assess significance, we performed a permutation test where we circularly shifted the recall model (10000 times) and recomputed the RMSD.
-The recall model significantly matched the video model for nine of the participants ($p<.05$, participants: 3-4, 8-13, 17 and the p-value for the rest of the participants was less than .25).
-Furthermore, the RMSD values were significantly correlated to hand annotated memory performance across participants (Pearson's $r(16)=-.57, p=.016$).
+The recall model significantly matched the video model for nine of the participants ($p < 0.05$, participants: 3-4, 8-13, 17 and the p-value for the rest of the participants was less than .25).
+Furthermore, the RMSD values were significantly correlated to hand annotated memory performance across participants (Pearson's $r(16) =-.57, p = 0.016$).
 Thus, a closer match between the video and recall event models was related to better recall performance.
@@
 We then averaged the correlations within participant.
-In line with our prediction, there was a strong correlation between hand annotated memory performance and precision suggesting that participants who remembered more events also remembered them more veridically (Pearson's $r(16)=.74, p=.0006$).
+In line with our prediction, there was a strong correlation between hand annotated memory performance and precision suggesting that participants who remembered more events also remembered them more veridically (Pearson's $r(16) = 0.74, p = 0.0006$).
 
@@
 Then, we averaged this measure over recall events within participant.
-We found that participants with higher hand annotated memory performance also had higher distinctiveness scores (Pearson's $r(16)=.8, p=.0001$).
+We found that participants with higher hand annotated memory performance also had higher distinctiveness scores (Pearson's $r(16) = 0.8, p = 0.0001$).
 
@@
 For each participant, we computed the Spearman rank correlation between the order of events that the participant recalled and the actual order of events (filtering events that were actually recalled).
-We found that participants who recalled more events also recalled more of them in order (Pearson's $r(16)=.5, p=.04$).
+We found that participants who recalled more events also recalled more of them in order (Pearson's $r(16) = 0.5, p = 0.04$).
 In summary, we found that better memory performance was associated with more precise, distinctive and ordered recalls.

### 2018-08-29 paper/main.tex
(still) working on results [WIP]

@@
-% !TEX TS-program = pdflatex
 \documentclass{article}
@@
 \usepackage{newfloat}
+\usepackage{setspace}
 \DeclareFloatingEnvironment[name={Supplementary Figure},fileext=lof]{suppfigure}
+\doublespacing
 
@@
 \section*{Results}
+
 We sought to formalize the gists of a naturalistic stimulus (an episode of the \textit{Sherlock} television show) and participants' recountings of that stimulus.
@@
 
-\bibliography{memlab}
-
 \section*{Methods}
@@
 We then plotted the top 200 words for the top/bottom 3 recalled events.
+
+\bibliography{memlab}
 

### 2018-08-30 paper/main.tex
substantial reorganization

@@
 \usepackage{setspace}
-\DeclareFloatingEnvironment[name={Supplementary Figure},fileext=lof]{suppfigure}
-\doublespacing
+%\doublespacing
 
@@
 
-\begin{figure}[t]
+\begin{figure}[tp]
 \centering
@@
 This correlation matrix reveals that the model has a strong, block-diagonal structure with very low off-diagonal correlation values, suggesting the representations of each block are unique and highly discriminable.
-We found that the ``narrative details'' (a few sentences summarizing the dialogue and specific happenings of the scene) of the video were the most important feature driving this model structure (see Supp.
-Fig.~\ref{fig:feature-importance}A).
+We found that the ``narrative details'' (a few sentences summarizing the dialogue and specific happenings of the scene) of the video were the most important feature driving this model structure (see Fig.~S3A).
 
@@
 Notably, participant \#13's recall model appears visually similar to the video model.
-Similar to the video model analysis (Supp.
-Fig.~\ref{fig:feature-importance}A), we found that the ``narrative details'' feature was most important for driving the video/recall relationship (Supp.
-Fig.~\ref{fig:feature-importance}B).
+Similar to the video model analysis (Fig.~S3A), we found that the ``narrative details'' feature was most important for driving the video/recall relationship (Fig.~S3B).
 Like the video model, topic vectors were sparse and changed gradually.
@@
 From each participant's recall model, we computed a sentences (68 to 294) by sentences (68 to 294) correlation matrix (Fig.~\ref{fig:model}D).
-Like the video model, each participant's recall correlation matrix exhibited a strong block-diagonal structure (Supp.
-Fig.~\ref{fig:corrmats}).
+Like the video model, each participant's recall correlation matrix exhibited a strong block-diagonal structure (Fig.~S1).
 Notably, this suggests that participants recounted the video in discriminable segments, likely related to the recall of specific events from the video.
 
-\begin{figure}[t]
+\begin{figure}[tp]
 \centering
@@
 We performed the same procedure for the recall matrices (Fig.~\ref{fig:model}F).
-Then, we computed the correlation between video and recall event models, resulting in a video events (34) by recall events (8-27, depending on the participant) correlation matrix (Fig~\ref{fig:model}G for example, Supp.
-Fig~\ref{fig:matchmats} for all participants).
+Then, we computed the correlation between video and recall event models, resulting in a video events (34) by recall events (8-27, depending on the participant) correlation matrix (Fig~\ref{fig:model}G for example, Fig.~S2 for all participants).
 These matrices represent the similarity (correlation) between each video event and each recall event (for each participant).
@@
 \subsection*{Brain regions that mirror the correlational structure of naturalistic stimuli and memories}.
-\begin{figure}[t]
+\begin{figure}[tp]
 \centering
@@
 While each participant remembered roughly the same sequence of events, there were subtle idiosyncracies in the way each individual described the events.
-For example, the event-by-event similarity structure (i.e., the off-diagonal values of the recall correlation matrices) differed across individuals (Supp.
-Fig.~\ref{fig:corrmats}).
+For example, the event-by-event similarity structure (i.e., the off-diagonal values of the recall correlation matrices) differed across individuals (Fig.~S1).
 We hypothesized that idiosyncracies in the recall dynamics across participants might be related to the temporal structure of brain networks representing the events during video viewing.
@@
 \subsubsection*{Extracting events using a hidden Markov model}
-The topic model timepoint-by-timepoint correlation matrices all exhibited a block-diagonal structure (with small off-diagonal values), suggesting that the models were comprised of a number of sequential `states' (or events, see Supp.
-Fig.~\ref{fig:corrmats}).
+The topic model timepoint-by-timepoint correlation matrices all exhibited a block-diagonal structure (with small off-diagonal values), suggesting that the models were comprised of a number of sequential `states' (or events, see Fig.~S1).
 To capture this structure, we fit the video and each recall model using a hidden Markov model (HMM).
@@
 To estimate which video event each recall event referred to, we correlated the video events model and each recall events model.
-This resulted in a video events (34) by recall events (8-27) correlation matrix (for each participant) which contains the similarity between each video event and each recall event (see Supp.
-Fig.~\ref{matchmats}).
+This resulted in a video events (34) by recall events (8-27) correlation matrix (for each participant) which contains the similarity between each video event and each recall event (see Fig.~S2).
 To find the most likely video event that a given recall event referred to, we computed the argmax over the columns of this matrix.
@@
 
-% SUPPLEMENTAL MATERIALS
-
-\pagebreak
-\begin{center}
-\textbf{\large Supplemental Materials: How is experience transformed into memory?}
-\end{center}
-\setcounter{equation}{0}
-\setcounter{figure}{0}
-\setcounter{table}{0}
-\setcounter{page}{1}
-\setcounter{section}{0}
-\makeatletter
-\renewcommand{\theequation}{S\arabic{equation}}
-\renewcommand{\thefigure}{S\arabic{figure}}
-\renewcommand{\bibnumfmt}[1]{[S#1]}
-\renewcommand{\citenumfont}[1]{S#1}
-
-% Supplemental materials
-\begin{suppfigure}[t]
-\centering
-\includegraphics[width=1\textwidth]{figs/supp1_corrmats.pdf}
-\caption{\small \textbf{Recall model correlation matrices and event segmentation fits.} Each participant's timepoint-by-timepoint recall correlation matrix.
-The yellow boxes represent ``events'' identified by a hidden Markov model.}
-\label{fig:corrmats}
-\end{suppfigure}
-
-\begin{suppfigure}[t]
-\centering
-\includegraphics[width=1\textwidth]{figs/supp2_matchmats.pdf}
-\caption{\small \textbf{Video-recall event model correlation matrices.} Each participant's video event by recall event correlation matrix.
-The yellow boxes represent the maximum correlation in each column.}
-\label{fig:matchmats}
-\end{suppfigure}
-
-\begin{suppfigure}[t]
-\centering
-\includegraphics[width=1\textwidth]{figs/supp4_feature_value.pdf}
-\caption{\small \textbf{Impact of individual features on topic modeling analysis.} \textbf{A.} Contribution of each feature to model structure.
-Bars represent the correlation of a video model trained in the absence of a given feature to the model trained on all features.
-\textbf{B.} Contribution of each feature to video model/recall model relationship.
-The leftmost bar represents the across-participants mean correlation between the video model and recall models trained on all features.
-Subsequent bars represent the same relationship between video and recall models trained in the absence of a given feature.
-Error bars are the standard error of the mean across participants.
-\textbf{C.}  Individual feature trajectory similarity matrix.
-The first row/column is the topic trajectory the full video model.
-Each subsequent row/column is that of a single feature.
-Shading corresponds to the value of the correlation coefficient (Pearson's $r$) .}
-\label{fig:feature-importance}
-\end{suppfigure}
-
-\section*{Naturalistic extensions of classic list-learning analyses}
-Just like in a traditional free recall list-learning experiment where participants view a list of words and then verbally recall them, our video-recall matching analysis approach affords us the ability to analyze memory in the same way.
-The recalled events can be treated as ``items'' analogous to words recalled in a list-learning study.
-Here, we sought to characterize memory performance/dynamics by extending classic analyses originally designed for list-learning experiments to more naturalistic settings.
-
-First, we asked whether the estimated number of recall events ($k$) by participant was related to hand-annotated accuracy as published in Chen et al.
-(2017).
-We found a strong positive correlation where participants with a greater number of recall events also had better overall memory performance (Pearson's $r(16) = 0.67, p = 0.003$).
-Then, we considered how participants initiated the recall sequence (known in the literature as the `probability of first recall' or `PFR').
-We found that participants tended to initiate their recall sequences with the first few events (Supp.
-Fig.~\ref{fig:list-learning}A), which is qualitatively very similar to previously published list learning experiments ~\citep{HowaKaha99}.
-Next, we considered another well-studied memory measure in the list-learning literature, the lag conditional response probability curve (or lag-CRP) ~\citep{Kaha96}.
-The result suggests a strong bias to transition sequentially events in the forward direction (Supp.
-Fig.~\ref{fig:list-learning}B).
-Finally, we assessed memory performance for each event in the video as a function of its serial position during encoding (Supp.
-Fig.~\ref{fig:list-learning}C).
-We did not observe the classic ``primacy'' and ``recency'' pattern which is prevalent in the literature ~\citep{Murd62a}.
-We also considered two additional across-participant measures of recall that characterize memory organization: temporal clustering and semantic clustering.
-We found that participants who clustered in time also recalled a greater number of events (Pearson's $r(16) = 0.62, p = 0.007$).
-Next, we assessed semantic clustering.
-We found that the semantic clustering score was related to memory performance across participants (Pearson's $r(16) = 0.55, p = 0.02$).
-Thus, participants who organized their recalls with respect to the semantic information contained in the scene had better memory performance.
-
-\section*{Additional measures of naturalistic memory}
-To quantify the similarity between the video model and individual recall models, we considered a number of novel metrics.
-First, we tested whether each participant's recall model matched the video model in a general sense.
-To do this, for each participant we filtered the video model to only include the events that the participant remembered and computed the root mean squared difference (RMSD) between the video model and the recall model.
-As an example, if the participant remembered all the events in order (with perfect precision), the expected distance value would be 0.
-However, if they remembered a subset of events, events out of order, or with low precision, the expected distance would be greater than 0.
-To assess significance, we performed a permutation test where we circularly shifted the recall model (10000 times) and recomputed the RMSD.
-The recall model significantly matched the video model for nine of the participants ($p < 0.05$, participants: 3-4, 8-13, 17 and the p-value for the rest of the participants was less than .25).
-Furthermore, the RMSD values were significantly correlated to hand annotated memory performance across participants (Pearson's $r(16) =-.57, p = 0.016$).
-Thus, a closer match between the video and recall event models was related to better recall performance.
-
-Next, we tested whether participants who recalled more events were also more precise in their recollections.
-For each participant, we computed the correlation between each recall event and its matching video event (only for the events which they recalled).
-This resulted in a single number for each recalled event indexing how similar the recall event was to its matching video event (i.e the ``precision'' of the recall).
-We then averaged the correlations within participant.
-In line with our prediction, there was a strong correlation between hand annotated memory performance and precision suggesting that participants who remembered more events also remembered them more veridically (Pearson's $r(16) = 0.74, p = 0.0006$).
-
-Then, we considered the distinctiveness of each recall event.
-That is, how uniquely a recall event matched a given video event compared to all other video events.
-We hypothesized that participants with high memory performance might describe each event in a more distinctive way (relative to those with lower memory performance who might describe events in a more general way).
-To this end, we computed a `distinctiveness' score for each participant (i.e., 1 - the correlation between a recall event and all non-matching video events).
-Then, we averaged this measure over recall events within participant.
-We found that participants with higher hand annotated memory performance also had higher distinctiveness scores (Pearson's $r(16) = 0.8, p = 0.0001$).
-
-Lastly, we tested whether participants with better memory performance were also more likely to remember the events in order.
-For each participant, we computed the Spearman rank correlation between the order of events that the participant recalled and the actual order of events (filtering events that were actually recalled).
-We found that participants who recalled more events also recalled more of them in order (Pearson's $r(16) = 0.5, p = 0.04$).
-In summary, we found that better memory performance was associated with more precise, distinctive and ordered recalls.
-
-\begin{suppfigure}[t]
-\centering
-\includegraphics[width=1\textwidth]{figs/supp3_list_learning.pdf}
-\caption{\small \textbf{Naturalistic extensions of classic list-learning memory analyses.} A).
-The probability of first recall as a function of the serial position of the event during encoding.
-B).
-A lag-conditional response probability curve.
-Given recall of event i, the probability that the next recalled item will be from serial position i +/- lag.
-C).
-Proportion of events recalled as a function of serial position.
-All error bars are the standard error of the mean derived from a bootstrap resampling procedure.}
-\label{fig:list-learning}
-\end{suppfigure}
-
-\section*{Supplemental Methods}
-\subsection*{Quantifying the importance of features}
-To determine the contribution of each feature to the structure of the video model, we examined the similarity between the temporal structure of models trained in the absence of a single feature and that of our original (i.e., full) model (Supp.
-Fig.~\ref{fig:feature-importance}A).
-First, we iteratively removed one transcribed feature from the scene descriptions and constructed a timepoints (1976) by topis (100) matrix using a topic model fit to the remaining features.
-We then represented the original model as well as the new model’s temporal structure as a timepoints-by-timepoints correlation matrix.
-Finally, we vectorized these correlation matrices and correlated them to each other resulting in a single number (for each feature removed from the model) representing the similarity of the ``feature-removed'' models to the full model.
-
-In order to ascertain which features were important in relating the recall models to the video model, we similarly compared to the temporal structures of video and recall models deprived of a single feature at a time (Supp.
-Fig.~\ref{fig:feature-importance}B).
-For each feature removed, we transformed each participant’s recall transcript using a model trained on the feature-deprived video text windows (of 50 scene segments), and resampled the recall timeseries to match the shape of the video model (1976 timepoints).
-We then represented the temporal structures of each participant’s recall model as timepoints-by-timepoints correlation matrices and computed the average correlation with the temporal structure of the video model (across participants).
-
-The two prior analyses examine information (about either the video model structure or the video/recall model relationship) lost in the absence of each feature.
-However, they do not consider redundancy in the information each feature contributes (e.g., how much unique information does "Character speaking" provide that "Character in focus" does not?).
-As a measure of information overlap between features, we computed the similarity between the topic trajectories of each individual annotated feature in addition to the full feature set.
-First, we singularly transformed the text of each feature using a model trained on the collection of all features.
-We then represented the single feature's model's temporal structure as a timepoints-by-timepoints correlation matrix, and compared the temporal structures pairwise by constructing a features-by-features correlation matrix ((Supp.
-Fig.~\ref{fig:feature-importance}C).
-We additionally computed the correlation between the individual features' temporal structures and that of the full video model as a measure of the proportion of information discernible from that feature alone.
-
-\subsection*{List-learning analyses}
-\textbf{Overall Accuracy.}  To get an overall measure of the quantity of information recalled, we computed the proportion of sucessfully recalled events by counting the number of unique recall events identified by the HMM model and dividing by the total number of video events.
-We performed this analysis for each participant separately.
-
-\textbf{Probability of first recall (PFR).}  The (PFR) analysis represents the probability that an item will be recalled first as a function of its serial position during encoding.
-We initialized a \# of participants (17) by \# of video events (34) matrix.
-Then for each participant, we found the index of the video event that was recalled first and filled in that index in the matrix with a 1.
-Finally, we averaged over the rows of the matrix, resulting in a 1 by 34 array representing the proportion of participant that recalled an event as a function of serial position during encoding.
-
-\textbf{Lag conditional probability curve (lag-CRP).} The lag-CRP represents the probability that the next item recalled will be of lag $i$ from the just recalled item.
-For each recall transition, we computed the lag between the current recall event and the next recall event, normalizing by the total number of possible transitions.
-This resulted in a \# of participants (17) by lags (-33:+33) matrix.
-We averaged over the rows of this matrix to get a group-averaged lag-CRP.
-
-\textbf{Serial position curve (SPC).} The SPC represents the proportion of participants that remember an item as a function of its serial position during encoding.
-We initialized a \# of participants (17) by \# of video events (34) matrix.
-Then, for each recall event (and each participant), we found the index of the video event that was recalled and filled it in with a 1.
-This resulted in a matrix where 1s indicate the successful recall of an event in serial position $n$ and zeros indicate the lack of recall for that event.
-Lastly, we averaged over the rows of the matrix to get a 1 by 34 array representing the proportion of participants that recalled an event as a function of its serial position.
-
-\textbf{Temporal clustering.} Temporal clustering measures the extent to which participants group their recall responses according to encoding position ~\citep{PolyEtal09}.
-For instance, if the participant recalled each item in the presentation order, this would result in a score of 1.
-If the participant recalled randomly with respect to presentation order, this would result in a score of ~.5.
-For each event transition (and separately for each participant), we computed the rank similarity (euclidean distance) between the presentation position  of the current and next recall events.
-The scores were then averaged within participant to get a single number representing the extent of temporal clustering exhibited by a given participant.
-
-\textbf{Semantic clustering.} Similar to temporal clustering, semantic clustering measures the extent to which participants group their recall responses according to semantic similarity ~\citep{PolyEtal09}.
-Here, we are using the topic vectors for each event as a proxy for its semantic content.
-Thus, similarity between the semantic content for two events can be computed by correlating their respective topic vectors.
-For instance, if each consecutive recall was the next most similar event (in terms of its s), this would result in a score of ~1.
-If the participant recalled randomly with respect to semantic similarity, this would result in a score of ~.5.
-For each event transition (and separately for each participant), we computed the rank similarity (correlation distance) between the current recall event and the next recall event.
-The scores were then averaged within participant to get a single number representing the extent of semantic clustering exhibited by a given participant.
-
-\subsection*{Additional measures of naturalistic memory}
-\textbf{Precision.} This measure gives us an indication of the specific match between a video event and recall event, where values approaching 1 are highly precise and lower values are inprecise.
-We defined ``precision'' as the correlation between a recall event and its matching (i.e., argmax) video event.
-
-\textbf{Distinctiveness.} Distinctiveness quantifies how similar a recall event is to all non-matching video events.
-It provides a metric of how uniquely a particular recall event describes a particular video event.
-To compute it, a given recall event is correlated to all video events, the argmax is removed and the rest of the values are averaged.
-The resulting value is subtracted from 1 such that larger values indicate a more distinctive recall event.
-
 \end{document}

### 2018-08-30 paper/supplemental_materials.tex
substantial reorganization

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage{geometry}
\usepackage{natbib}
\usepackage{pxfonts}
\usepackage{graphicx}
\usepackage{newfloat}
\usepackage{setspace}
%\doublespacing

\title{\textit{Supplemental materials for}: How is experience transformed into memory?}
\author{Andrew C. Heusser, Paxton C. Fitzpatrick, and Jeremy R. Manning\\Department of Psychological and Brain Sciences\\Dartmouth College, Hanover, NH 03755, USA\\Corresponding author: jeremy.r.manning@dartmouth.edu}

\bibliographystyle{apa}

\begin{document}
\maketitle

\setcounter{equation}{0}
\setcounter{figure}{0}
\setcounter{table}{0}
\setcounter{page}{1}
\setcounter{section}{0}
\makeatletter
\renewcommand{\theequation}{S\arabic{equation}}
\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\bibnumfmt}[1]{[S#1]}
\renewcommand{\citenumfont}[1]{S#1}

% Supplemental materials
\begin{figure}[tp]
\centering
\includegraphics[width=1\textwidth]{figs/supp1_corrmats.pdf}
\caption{\small \textbf{Recall model correlation matrices and event segmentation fits.} Each participant's timepoint-by-timepoint recall correlation matrix.  The yellow boxes represent ``events'' identified by a hidden Markov model.}
\label{fig:corrmats}
\end{figure}

\begin{figure}[tp]
\centering
\includegraphics[width=1\textwidth]{figs/supp2_matchmats.pdf}
\caption{\small \textbf{Video-recall event model correlation matrices.} Each participant's video event by recall event correlation matrix.  The yellow boxes represent the maximum correlation in each column.}
\label{fig:matchmats}
\end{figure}

\begin{figure}[tb]
\centering
\includegraphics[width=1\textwidth]{figs/supp4_feature_value.pdf}
\caption{\small \textbf{Impact of individual features on topic modeling analysis.} \textbf{A.} Contribution of each feature to model structure. Bars represent the correlation of a video model trained in the absence of a given feature to the model trained on all features. \textbf{B.} Contribution of each feature to video model/recall model relationship. The leftmost bar represents the across-participants mean correlation between the video model and recall models trained on all features. Subsequent bars represent the same relationship between video and recall models trained in the absence of a given feature. Error bars are the standard error of the mean across participants. \textbf{C.}  Individual feature trajectory similarity matrix. The first row/column is the topic trajectory the full video model. Each subsequent row/column is that of a single feature. Shading corresponds to the value of the correlation coefficient (Pearson's $r$) .}
\label{fig:feature-importance}
\end{figure}

\section*{Naturalistic extensions of classic list-learning analyses}
Just like in a traditional free recall list-learning experiment where participants view a list of words and then verbally recall them, our video-recall matching analysis approach affords us the ability to analyze memory in the same way. The recalled events can be treated as ``items'' analogous to words recalled in a list-learning study. Here, we sought to characterize memory performance/dynamics by extending classic analyses originally designed for list-learning experiments to more naturalistic settings.

First, we asked whether the estimated number of recall events ($k$) by participant was related to hand-annotated accuracy as published in Chen et al. (2017).  We found a strong positive correlation where participants with a greater number of recall events also had better overall memory performance (Pearson's $r(16) = 0.67, p = 0.003$). Then, we considered how participants initiated the recall sequence (known in the literature as the `probability of first recall' or `PFR'). We found that participants tended to initiate their recall sequences with the first few events (Supp. Fig.~\ref{fig:list-learning}A), which is qualitatively very similar to previously published list learning experiments ~\citep{HowaKaha99}. Next, we considered another well-studied memory measure in the list-learning literature, the lag conditional response probability curve (or lag-CRP) ~\citep{Kaha96}. The result suggests a strong bias to transition sequentially events in the forward direction (Supp. Fig.~\ref{fig:list-learning}B). Finally, we assessed memory performance for each event in the video as a function of its serial position during encoding (Supp. Fig.~\ref{fig:list-learning}C). We did not observe the classic ``primacy'' and ``recency'' pattern which is prevalent in the literature ~\citep{Murd62a}. We also considered two additional across-participant measures of recall that characterize memory organization: temporal clustering and semantic clustering. We found that participants who clustered in time also recalled a greater number of events (Pearson's $r(16) = 0.62, p = 0.007$). Next, we assessed semantic clustering. We found that the semantic clustering score was related to memory performance across participants (Pearson's $r(16) = 0.55, p = 0.02$).  Thus, participants who organized their recalls with respect to the semantic information contained in the scene had better memory performance.

\section*{Additional measures of naturalistic memory}
To quantify the similarity between the video model and individual recall models, we considered a number of novel metrics.  First, we tested whether each participant's recall model matched the video model in a general sense. To do this, for each participant we filtered the video model to only include the events that the participant remembered and computed the root mean squared difference (RMSD) between the video model and the recall model. As an example, if the participant remembered all the events in order (with perfect precision), the expected distance value would be 0. However, if they remembered a subset of events, events out of order, or with low precision, the expected distance would be greater than 0. To assess significance, we performed a permutation test where we circularly shifted the recall model (10000 times) and recomputed the RMSD. The recall model significantly matched the video model for nine of the participants ($p < 0.05$, participants: 3-4, 8-13, 17 and the p-value for the rest of the participants was less than .25). Furthermore, the RMSD values were significantly correlated to hand annotated memory performance across participants (Pearson's $r(16) =-.57, p = 0.016$). Thus, a closer match between the video and recall event models was related to better recall performance.

Next, we tested whether participants who recalled more events were also more precise in their recollections. For each participant, we computed the correlation between each recall event and its matching video event (only for the events which they recalled). This resulted in a single number for each recalled event indexing how similar the recall event was to its matching video event (i.e the ``precision'' of the recall). We then averaged the correlations within participant. In line with our prediction, there was a strong correlation between hand annotated memory performance and precision suggesting that participants who remembered more events also remembered them more veridically (Pearson's $r(16) = 0.74, p = 0.0006$).

Then, we considered the distinctiveness of each recall event. That is, how uniquely a recall event matched a given video event compared to all other video events. We hypothesized that participants with high memory performance might describe each event in a more distinctive way (relative to those with lower memory performance who might describe events in a more general way). To this end, we computed a `distinctiveness' score for each participant (i.e., 1 - the correlation between a recall event and all non-matching video events).  Then, we averaged this measure over recall events within participant.  We found that participants with higher hand annotated memory performance also had higher distinctiveness scores (Pearson's $r(16) = 0.8, p = 0.0001$).

Lastly, we tested whether participants with better memory performance were also more likely to remember the events in order.  For each participant, we computed the Spearman rank correlation between the order of events that the participant recalled and the actual order of events (filtering events that were actually recalled).  We found that participants who recalled more events also recalled more of them in order (Pearson's $r(16) = 0.5, p = 0.04$). In summary, we found that better memory performance was associated with more precise, distinctive and ordered recalls.

\begin{figure}[tb]
\centering
\includegraphics[width=1\textwidth]{figs/supp3_list_learning.pdf}
\caption{\small \textbf{Naturalistic extensions of classic list-learning memory analyses.} A). The probability of first recall as a function of the serial position of the event during encoding. B). A lag-conditional response probability curve. Given recall of event i, the probability that the next recalled item will be from serial position i +/- lag. C). Proportion of events recalled as a function of serial position. All error bars are the standard error of the mean derived from a bootstrap resampling procedure.}
\label{fig:list-learning}
\end{figure}

\section*{Supplemental Methods}
\subsection*{Quantifying the importance of features}
To determine the contribution of each feature to the structure of the video model, we examined the similarity between the temporal structure of models trained in the absence of a single feature and that of our original (i.e., full) model (Supp. Fig.~\ref{fig:feature-importance}A). First, we iteratively removed one transcribed feature from the scene descriptions and constructed a timepoints (1976) by topis (100) matrix using a topic model fit to the remaining features. We then represented the original model as well as the new model’s temporal structure as a timepoints-by-timepoints correlation matrix. Finally, we vectorized these correlation matrices and correlated them to each other resulting in a single number (for each feature removed from the model) representing the similarity of the ``feature-removed'' models to the full model.

In order to ascertain which features were important in relating the recall models to the video model, we similarly compared to the temporal structures of video and recall models deprived of a single feature at a time (Supp. Fig.~\ref{fig:feature-importance}B). For each feature removed, we transformed each participant’s recall transcript using a model trained on the feature-deprived video text windows (of 50 scene segments), and resampled the recall timeseries to match the shape of the video model (1976 timepoints). We then represented the temporal structures of each participant’s recall model as timepoints-by-timepoints correlation matrices and computed the average correlation with the temporal structure of the video model (across participants).

The two prior analyses examine information (about either the video model structure or the video/recall model relationship) lost in the absence of each feature. However, they do not consider redundancy in the information each feature contributes (e.g., how much unique information does "Character speaking" provide that "Character in focus" does not?). As a measure of information overlap between features, we computed the similarity between the topic trajectories of each individual annotated feature in addition to the full feature set. First, we singularly transformed the text of each feature using a model trained on the collection of all features. We then represented the single feature's model's temporal structure as a timepoints-by-timepoints correlation matrix, and compared the temporal structures pairwise by constructing a features-by-features correlation matrix ((Supp. Fig.~\ref{fig:feature-importance}C). We additionally computed the correlation between the individual features' temporal structures and that of the full video model as a measure of the proportion of information discernible from that feature alone.

\subsection*{List-learning analyses}
\textbf{Overall Accuracy.}  To get an overall measure of the quantity of information recalled, we computed the proportion of sucessfully recalled events by counting the number of unique recall events identified by the HMM model and dividing by the total number of video events.  We performed this analysis for each participant separately.

\textbf{Probability of first recall (PFR).}  The (PFR) analysis represents the probability that an item will be recalled first as a function of its serial position during encoding. We initialized a \# of participants (17) by \# of video events (34) matrix. Then for each participant, we found the index of the video event that was recalled first and filled in that index in the matrix with a 1.  Finally, we averaged over the rows of the matrix, resulting in a 1 by 34 array representing the proportion of participant that recalled an event as a function of serial position during encoding.

\textbf{Lag conditional probability curve (lag-CRP).} The lag-CRP represents the probability that the next item recalled will be of lag $i$ from the just recalled item. For each recall transition, we computed the lag between the current recall event and the next recall event, normalizing by the total number of possible transitions.  This resulted in a \# of participants (17) by lags (-33:+33) matrix. We averaged over the rows of this matrix to get a group-averaged lag-CRP.

\textbf{Serial position curve (SPC).} The SPC represents the proportion of participants that remember an item as a function of its serial position during encoding. We initialized a \# of participants (17) by \# of video events (34) matrix. Then, for each recall event (and each participant), we found the index of the video event that was recalled and filled it in with a 1. This resulted in a matrix where 1s indicate the successful recall of an event in serial position $n$ and zeros indicate the lack of recall for that event.  Lastly, we averaged over the rows of the matrix to get a 1 by 34 array representing the proportion of participants that recalled an event as a function of its serial position.

\textbf{Temporal clustering.} Temporal clustering measures the extent to which participants group their recall responses according to encoding position ~\citep{PolyEtal09}. For instance, if the participant recalled each item in the presentation order, this would result in a score of 1. If the participant recalled randomly with respect to presentation order, this would result in a score of ~.5.  For each event transition (and separately for each participant), we computed the rank similarity (euclidean distance) between the presentation position  of the current and next recall events. The scores were then averaged within participant to get a single number representing the extent of temporal clustering exhibited by a given participant.

\textbf{Semantic clustering.} Similar to temporal clustering, semantic clustering measures the extent to which participants group their recall responses according to semantic similarity ~\citep{PolyEtal09}. Here, we are using the topic vectors for each event as a proxy for its semantic content. Thus, similarity between the semantic content for two events can be computed by correlating their respective topic vectors.  For instance, if each consecutive recall was the next most similar event (in terms of its s), this would result in a score of ~1. If the participant recalled randomly with respect to semantic similarity, this would result in a score of ~.5.  For each event transition (and separately for each participant), we computed the rank similarity (correlation distance) between the current recall event and the next recall event. The scores were then averaged within participant to get a single number representing the extent of semantic clustering exhibited by a given participant.

\subsection*{Additional measures of naturalistic memory}
\textbf{Precision.} This measure gives us an indication of the specific match between a video event and recall event, where values approaching 1 are highly precise and lower values are inprecise.  We defined ``precision'' as the correlation between a recall event and its matching (i.e., argmax) video event.

\textbf{Distinctiveness.} Distinctiveness quantifies how similar a recall event is to all non-matching video events.  It provides a metric of how uniquely a particular recall event describes a particular video event.  To compute it, a given recall event is correlated to all video events, the argmax is removed and the rest of the values are averaged. The resulting value is subtracted from 1 such that larger values indicate a more distinctive recall event.

%\newpage
\renewcommand{\refname}{Supplemental references}
\bibliography{memlab}

\end{document}

### 2018-08-31 paper/main.tex
added outline of results overhaul
backing up progress on results

@@
 \section*{Results}
+To characterize the gists of the \textit{Sherlock} episode participants watched and their subsequent recountings of the episode, we used a topic model~\cite{BleiEtal03} to discover the latent thematic content.
+\cite{ChenEtal17} collected hand-annotated information about each of 1000 (manually identified) scenes spanning the roughly 45 minute video.
+This information included: a brief narrative description of what was happening; whether the scene took place indoors vs.
+outdoors; names of any characters on the screen; names of any characters who were in focus in the camera show; names of characters who were speaking; the location where the scene took place; the camera angle (close up, medium, long, etc.); whether or not background music was present; and other similar details (for a full list of annoted features see \textit{Methods}).
+We took from these annotations the union of all unique words (excluding stop words, such as ``and,'' ``or,'' ``but,'' etc.) across all features and scenes as the ``vocabulary'' for the topic model.
+We then concatenated the sets of words across all features contained in overlapping 50-scene sliding windows, and treated each 50-scene sequence as a single ``document'' for the purposes of fitting the topic model.
+Next, we fit a topic model with (up to) $K = 100$ topics to this collection of documents.
+We found that 28 topics were sufficient to describe the time-varying content of the movie (see \textit{Methods}).
+Note that our approach is similar in some respects
+
+% characterize gist of movie and recalls
+% 1. movie: fit topic models (add note on dynamic topic models).  fig 1: what do the topics reflect (top words from each topic), example with a few scenes.
+% 2. notice block diagonal structure, rather than smooth transitions; motivates HMM approach.  Note about selecting K
+% 3.
+question: do recalls exhibit same structure?
+apply topic model to recalls.
+note that by projecting everything into a common topic space, the thematic content of each moment of movie/recall can be compared, even though the mix of words used to describe any given event or moment may not be consistent across people (or across annotations/recall)
+% 4. recalls exhibit blocky structure, but at different scales.  motivates fitting K separately by person
+% 5. match up events (correlations)
+% 6.
+now we can use classic memory analyses to examine structure of recall.
+motivate and reference PFR, lag-CRP, and SPC.
+but this does not tell us about structure in the *content* of what people remembered, or whether people's recalls are capturing the hierarchical temporal structure of the original movie.
+% 7.
+topic trajectories as a new way of characterizing recall.
+assess agreement using rayleigh test.
+also examine shapes of each subject's trajectory to show match.
+key insight: everyone captures the general shape, but at different "sampling resolutions"
+% 8. we can also project back onto the original (word) features to understand more about what any particular part of the trajectory reflects (wordle fig)
+% 9.
+the above analyses tell us about how the trajectory of thematic content in the episode is both preserved and transformed in participants' memories.
+we next carried out analyses to understand the neural bases of these phenomena.
+analysis 1: which structures are sensitive (during viewing) to the original episode's topic trajectory?
+answer: default mode.
+anlaysis 2: which structure are sensitive (during viewing) to how the participants will later recall the episode?
+answer: vmPFC, default mode.
+(potential role of vmPFC in reflecting participant-specific memory transformations and processing)
 

### 2018-08-31 paper/main.tex
backing up work on results [WIP]

@@
 Next, we fit a topic model with (up to) $K = 100$ topics to this collection of documents.
-We found that 28 topics were sufficient to describe the time-varying content of the movie (see \textit{Methods}).
-Note that our approach is similar in some respects
+We found that 28 unique topics were sufficient to describe the time-varying content of the movie (see \textit{Methods}).
+Note that our approach is similar in some respects to Dynamic Topic Models~\citep{BleiLaff06}, in that we sought to characterize how the thematic content of the data evolved over time.
+%JRM STOPPED HERE
 

### 2018-09-01 paper/main.tex
added new figure, still working on results

@@
 Note that our approach is similar in some respects to Dynamic Topic Models~\citep{BleiLaff06}, in that we sought to characterize how the thematic content of the data evolved over time.
+
+\begin{figure}[tp]
+\centering
+\includegraphics[width=0.5\textwidth]{figs/0_topics.pdf}
+\caption{\small \textbf{Topics discovered in \textit{Sherlock}.} We applied a topic model to hand-annotated information about 1000 scenes spanning the 45 minute episode.
+We identified 28 unique topics with non-zero weights (we used $K=100$ topics to fit the model).
+Each topic comprises a distribution of weights over all words in the vocabulary.
+For each topic, we show the words with the 10 largest weights, along with a suggested description of the topic.}
+\label{fig:topics}
+\end{figure}
+
+The topics we found appeared heavily character-focused (e.g.
+the top-weighted word in each topic was nearly always a character) and could be roughly divided into themes related to primarily Sherlock-focused; primarily (John) Watson-focused (Watson is Sherlock's close confidant and assistant); and themes that involved Sherlock and Watson interacting (Fig.~\ref{fig:topics}).
+Several of the topics also appeared highly similar, which we hypothesized might allow us to distinguish between subtle narrative differences (e.g., if the distinctions between those overlapping topics were meaningful), but could also impair characterization of the narrative (e.g., if the distinctions between topics were not meaningful).
+
 %JRM STOPPED HERE

### 2018-09-01 paper/main.tex
updated figure names to allow for reordering

--- 2018-08-31 paper/main.tex
@@
 %\doublespacing
+
+\newcommand{\topics}{S1}
+\newcommand{\corrmats}{S2}
+\newcommand{\matchmats}{S3}
+\newcommand{\featureimportance}{S4}
+\newcommand{\listlearning}{S5}
 
@@
 Next, we fit a topic model with (up to) $K = 100$ topics to this collection of documents.
-We found that 28 unique topics were sufficient to describe the time-varying content of the movie (see \textit{Methods}).
+We found that 28 unique topics were sufficient to describe the time-varying content of the movie (see \textit{Methods}; Fig.~\ref{fig:schematic}).
 Note that our approach is similar in some respects to Dynamic Topic Models~\citep{BleiLaff06}, in that we sought to characterize how the thematic content of the data evolved over time.
+
+\begin{figure}[tp]
+\centering
+\includegraphics[width=1\textwidth]{figs/analysis_schematic_bw}
+\caption{\small \textbf{Schematic of the analysis approach.} For each scene in the video, text descriptions were generated by hand.
+Three exemplary time points are displayed here.
+Below the video descriptions are text samples from an example participant's verbal recall transcript.
+We fit a topic model to the moment-by-moment video text descriptions and transformed participants' verbal recall transcripts using this same model.
+The bar charts display the resulting topic model weights for the video (in blue) and recall (in green) for three example topic dimensions.}
+\label{fig:schematic}
+\end{figure}
+
+The topics we found appeared heavily character-focused (e.g., the top-weighted word in each topic was nearly always a character) and could be roughly divided into themes related to primarily Sherlock-focused; primarily (John) Watson-focused (Watson is Sherlock's close confidant and assistant); and themes that involved Sherlock and Watson interacting (Fig.~\topics).
+Several of the topics also appeared highly similar, which we hypothesized might allow us to distinguish between subtle narrative differences (e.g., if the distinctions between those overlapping topics were meaningful), but could also impair characterization of the narrative (e.g., if the distinctions between topics were not meaningful).
+
 %JRM STOPPED HERE
@@
 
-We sought to formalize the gists of a naturalistic stimulus (an episode of the \textit{Sherlock} television show) and participants' recountings of that stimulus.
-% JRM STOPPED HERE
-% - add a general overview
-% - some of this seems like it belongs in methods...
-% - possible section title change to "Narrative?" -- see author guidelines and prior nature submissions
-
-\begin{figure}[tp]
-\centering
-\includegraphics[width=1\textwidth]{figs/1_analysis_schematic_bw.pdf}
-\caption{\small \textbf{Schematic of the analysis approach.} For each scene in the video, text descriptions were generated by hand.
-Three exemplary time points are displayed here.
-Below the video descriptions are text samples from an example participant's verbal recall transcript.
-We fit a topic model to the moment-by-moment video text descriptions and transformed participants' verbal recall transcripts using this same model.
-The bar charts display the resulting topic model weights for the video (in blue) and recall (in green) for three example topic dimensions.}
-\label{fig:schematic}
-\end{figure}
-
 \subsection*{Modeling the naturalistic stimulus and verbal recall}
@@
 This correlation matrix reveals that the model has a strong, block-diagonal structure with very low off-diagonal correlation values, suggesting the representations of each block are unique and highly discriminable.
-We found that the ``narrative details'' (a few sentences summarizing the dialogue and specific happenings of the scene) of the video were the most important feature driving this model structure (see Fig.~S3A).
+We found that the ``narrative details'' (a few sentences summarizing the dialogue and specific happenings of the scene) of the video were the most important feature driving this model structure (see Fig.~\featureimportance A).
 
@@
 Notably, participant \#13's recall model appears visually similar to the video model.
-Similar to the video model analysis (Fig.~S3A), we found that the ``narrative details'' feature was most important for driving the video/recall relationship (Fig.~S3B).
+Similar to the video model analysis (Fig.~\featureimportance A), we found that the ``narrative details'' feature was most important for driving the video/recall relationship (Fig.~\featureimportance B).
 Like the video model, topic vectors were sparse and changed gradually.
@@
 From each participant's recall model, we computed a sentences (68 to 294) by sentences (68 to 294) correlation matrix (Fig.~\ref{fig:model}D).
-Like the video model, each participant's recall correlation matrix exhibited a strong block-diagonal structure (Fig.~S1).
+Like the video model, each participant's recall correlation matrix exhibited a strong block-diagonal structure (Fig.~\corrmats).
 Notably, this suggests that participants recounted the video in discriminable segments, likely related to the recall of specific events from the video.
@@
 \centering
-\includegraphics[width=\textwidth]{figs/2_eventseg.pdf}
+\includegraphics[width=\textwidth]{figs/eventseg}
 \caption{\small \textbf{Modelling naturalistic stimuli and recall.} A depiction of our analysis pipeline.
@@
 We performed the same procedure for the recall matrices (Fig.~\ref{fig:model}F).
-Then, we computed the correlation between video and recall event models, resulting in a video events (34) by recall events (8-27, depending on the participant) correlation matrix (Fig~\ref{fig:model}G for example, Fig.~S2 for all participants).
+Then, we computed the correlation between video and recall event models, resulting in a video events (34) by recall events (8-27, depending on the participant) correlation matrix (Fig~\ref{fig:model}G for example, Fig.~\matchmats for all participants).
 These matrices represent the similarity (correlation) between each video event and each recall event (for each participant).
@@
 \centering
-\includegraphics[width=1\textwidth]{figs/3_trajectory.pdf}
+\includegraphics[width=1\textwidth]{figs/trajectory}
 \caption{\small \textbf{Video and recall trajectory plots.} \textbf{A.} 2-dimensional embedding of the video events model (reduced with UMAP algorithm).
@@
 \centering
-\includegraphics[width=1\textwidth]{figs/4_brains_panels.pdf}
+\includegraphics[width=1\textwidth]{figs/brains_panels}
 \caption{\small \textbf{Video and recall model correlational structure searchlight analysis.} \textbf{A.} The correlation matrix representing the temporal structure of the video model.
@@
 While each participant remembered roughly the same sequence of events, there were subtle idiosyncracies in the way each individual described the events.
-For example, the event-by-event similarity structure (i.e., the off-diagonal values of the recall correlation matrices) differed across individuals (Fig.~S1).
+For example, the event-by-event similarity structure (i.e., the off-diagonal values of the recall correlation matrices) differed across individuals (Fig.~\corrmats).
 We hypothesized that idiosyncracies in the recall dynamics across participants might be related to the temporal structure of brain networks representing the events during video viewing.
@@
 \centering
-\includegraphics[width=1\textwidth]{figs/5_topics.pdf}
+\includegraphics[width=1\textwidth]{figs/topics}
 \caption{\small \textbf{Analysis of topics by event memorability.} \textbf{A.} Group-averaged correlation between each video event and closest recall event.
@@
 \subsubsection*{Extracting events using a hidden Markov model}
-The topic model timepoint-by-timepoint correlation matrices all exhibited a block-diagonal structure (with small off-diagonal values), suggesting that the models were comprised of a number of sequential `states' (or events, see Fig.~S1).
+The topic model timepoint-by-timepoint correlation matrices all exhibited a block-diagonal structure (with small off-diagonal values), suggesting that the models were comprised of a number of sequential `states' (or events, see Fig.~\corrmats).
 To capture this structure, we fit the video and each recall model using a hidden Markov model (HMM).
@@
 To estimate which video event each recall event referred to, we correlated the video events model and each recall events model.
-This resulted in a video events (34) by recall events (8-27) correlation matrix (for each participant) which contains the similarity between each video event and each recall event (see Fig.~S2).
+This resulted in a video events (34) by recall events (8-27) correlation matrix (for each participant) which contains the similarity between each video event and each recall event (see Fig.~\matchmats).
 To find the most likely video event that a given recall event referred to, we computed the argmax over the columns of this matrix.

### 2018-09-01 paper/supplemental_materials.tex
updated figure names to allow for reordering

@@
 \centering
-\includegraphics[width=1\textwidth]{figs/supp1_corrmats.pdf}
+\includegraphics[width=0.75\textwidth]{figs/topic_words}
+\caption{\small \textbf{Topics discovered in \textit{Sherlock}.} We applied a topic model to hand-annotated information about 1000 scenes spanning the 45 minute episode.
+We identified 28 unique topics with non-zero weights (we used $K=100$ topics to fit the model).
+Each topic comprises a distribution of weights over all words in the vocabulary.
+For each topic, we show the words with the 10 largest weights, along with a suggested description of the topic.}
+\label{fig:topics}
+\end{figure}
+
+\begin{figure}[tp]
+\centering
+\includegraphics[width=1\textwidth]{figs/corrmats}
 \caption{\small \textbf{Recall model correlation matrices and event segmentation fits.} Each participant's timepoint-by-timepoint recall correlation matrix.
@@
 \centering
-\includegraphics[width=1\textwidth]{figs/supp2_matchmats.pdf}
+\includegraphics[width=1\textwidth]{figs/matchmats}
 \caption{\small \textbf{Video-recall event model correlation matrices.} Each participant's video event by recall event correlation matrix.
@@
 \centering
-\includegraphics[width=1\textwidth]{figs/supp4_feature_value.pdf}
+\includegraphics[width=1\textwidth]{figs/feature_value}
 \caption{\small \textbf{Impact of individual features on topic modeling analysis.} \textbf{A.} Contribution of each feature to model structure.
@@
 \centering
-\includegraphics[width=1\textwidth]{figs/supp3_list_learning.pdf}
+\includegraphics[width=1\textwidth]{figs/list_learning}
 \caption{\small \textbf{Naturalistic extensions of classic list-learning memory analyses.} A).

### 2018-09-01 paper/main.tex
edits to event seg figure, backing up work

@@
 Next, we fit a topic model with (up to) $K = 100$ topics to this collection of documents.
-We found that 28 unique topics were sufficient to describe the time-varying content of the movie (see \textit{Methods}; Fig.~\ref{fig:schematic}).
-Note that our approach is similar in some respects to Dynamic Topic Models~\citep{BleiLaff06}, in that we sought to characterize how the thematic content of the data evolved over time.
+We found that 28 unique topics (with non-zero weights) were sufficient to describe the time-varying content of the movie (see \textit{Methods}; Figs.~\ref{fig:schematic}, \topics).
+Note that our approach is similar in some respects to Dynamic Topic Models~\citep{BleiLaff06}, in that we sought to characterize how the thematic content of the episode evolved over time.
+However, whereas Dynamic Topic Models are designed to characterize the how the properties of collections of documents change over time, our approach allows us to examine the topic dynamics within a single episode.
+Specifically, our approach yielded a single \textit{topic vector} for each timepoint of the episode (we set timepoints to match the acquisition times of the 1976 fMRI volumes collected as participants viewed the episode).
 
@@
 \includegraphics[width=1\textwidth]{figs/analysis_schematic_bw}
-\caption{\small \textbf{Schematic of the analysis approach.} For each scene in the video, text descriptions were generated by hand.
-Three exemplary time points are displayed here.
-Below the video descriptions are text samples from an example participant's verbal recall transcript.
-We fit a topic model to the moment-by-moment video text descriptions and transformed participants' verbal recall transcripts using this same model.
-The bar charts display the resulting topic model weights for the video (in blue) and recall (in green) for three example topic dimensions.}
+\caption{\small \textbf{Methods overview.} We used hand-annotated descriptions of each moment of video to fit a topic model.
+Three example video frames, and their associated descriptions are displayed (top two rows).
+Participants later recalled the video (in the third row, we show example recalls of the same three scenes from one participant).
+We used the topic model (fit to the annotations) to estimate topic vectors for each moment of video and each sentence the participants recalled.
+Example topic vectors are displayed in the bottom row (green: video annotations; blue: example participant's recalls).
+Three topic dimensions are shown (the highest-weighted topics for each of the three example scenes, respectively).
+We also show the 5 highest-weighted words for each topic.
+Figure~\topics~provides a full list of the top 10 words from each of the discovered topics.}
 \label{fig:schematic}
@@
 
-The topics we found appeared heavily character-focused (e.g., the top-weighted word in each topic was nearly always a character) and could be roughly divided into themes related to primarily Sherlock-focused; primarily (John) Watson-focused (Watson is Sherlock's close confidant and assistant); and themes that involved Sherlock and Watson interacting (Fig.~\topics).
-Several of the topics also appeared highly similar, which we hypothesized might allow us to distinguish between subtle narrative differences (e.g., if the distinctions between those overlapping topics were meaningful), but could also impair characterization of the narrative (e.g., if the distinctions between topics were not meaningful).
+The topics we found were heavily character-focused (e.g., the top-weighted word in each topic was nearly always a character) and could be roughly divided into themes related to primarily Sherlock-focused; primarily (John) Watson-focused (Watson is Sherlock's close confidant and assistant); and themes that involved Sherlock and Watson interacting (Fig.~\topics).
+Several of the topics also appeared highly similar, which we hypothesized might allow us to distinguish between subtle narrative differences (if the distinctions between those overlapping topics were meaningful).
+The topic vectors for each timepoint were \textit{sparse}, in that only a small number (usually one or two) topics tended to be ``active'' in any given timepoint (Fig.~\ref{fig:model}A).
+Further, the dynamics of the topic activations appeared to exhibit \textit{persistance} (i.e., given that a topic was active in one timepoint, it was likely to be active in the following timepoint) along with \textit{occasional rapid changes} (i.e., occasionally topics would appear to spring into or out of existence).
+These two properties of the topic dynamics may be seen in the block diagonal structure of the timepoint-by-timepoint correlation matrix (Fig.~\ref{fig:model}B).
+Following \cite{BaldEtal17}, used a Hidden Markov Model (HMM) to identify the \textit{event boundaries} where the topic activations changed rapidly (i.e., at the boundaries of the blocks in the correlation matrix; event boundaries identified by the HMM are outlined in yellow).
+Part of our model fitting procedure required selecting an appropriate number of ``events'' to segment the timeseries into.
+We used an optimization procedure to identify the number of events that maximized within-event stability while also minimizing across-event correlations (see \textit{Methods} for additional detail).
+To create a stable ``summary'' of the episode, we computed the avereage topic vector within each event (Fig.~\ref{fig:model}C).
+
+\begin{figure}[tp]
+\centering
+\includegraphics[width=\textwidth]{figs/eventseg}
+\caption{\small \textbf{Modelling naturalistic stimuli and recalls.} All panels: darker colors indicate greater values; range: [0, 1].
+\textbf{A.} Topic vectors ($K = 100$) for each of the 1976 video timepoints.
+\textbf{B.} Timepoint-by-timepoint correlation matrix of the topic vectors displayed in Panel A.
+Event boundaries detected by the HMM are denoted in yellow (34 events detected).
+\textbf{C.} Average topic vectors for each of the 34 video events.
+\textbf{D.} Topic vectors for each of 294 sentences spoken by an example participant while recalling the video.
+\textbf{E.} Timepoint-by-timepoint correlation matrix of the topic vectors displayed in Panel D.
+Event boundaries detected by the HMM are denoted in yellow (27 events detected).
+\textbf{F.} Average topic vectors for each of the 27 recalled events from the example participant.
+\textbf{G.} Correlations between the topic vectors for every pair of video events (Panel C) and recalled events (from the example participant; Panel F).
+\textbf{H.} Average correlations between each pair of video events and recalled events (across all 17 participants).
+To create the figure, each recalled event was assigned to the video event with the most correlated topic vector.}
+\label{fig:model}
+\end{figure}
 
@@
 % characterize gist of movie and recalls
-% 1. movie: fit topic models (add note on dynamic topic models).  fig 1: what do the topics reflect (top words from each topic), example with a few scenes.
-% 2. notice block diagonal structure, rather than smooth transitions; motivates HMM approach.  Note about selecting K
+% x1. movie: fit topic models (add note on dynamic topic models).  fig 1: what do the topics reflect (top words from each topic), example with a few scenes.
+% x2. notice block diagonal structure, rather than smooth transitions; motivates HMM approach.  Note about selecting K
 % 3.
@@
 Notably, this suggests that participants recounted the video in discriminable segments, likely related to the recall of specific events from the video.
-
-\begin{figure}[tp]
-\centering
-\includegraphics[width=\textwidth]{figs/eventseg}
-\caption{\small \textbf{Modelling naturalistic stimuli and recall.} A depiction of our analysis pipeline.
-For all plots, darker colors indicate greater values and the range of each plot is 0-1.
-\textbf{A.} A timepoints (1976) by topics (100) matrix representing the video stimulus.
-Each row represents the most likely mixture of topics for a given timepoint (i.e., topic weights).
-Each column represents a different topic.
-\textbf{B.} A sentences (294) by topics (100) matrix representing participant \#13's recall.
-\textbf{C.} A viewing-time (1976) by viewing-time (1976) correlation matrix representing the correlation of each moment of the video model with every other moment of the video model.
-The yellow boxes represent `events' recovered by a hidden Markov model.
-\textbf{D.} A recall-time (294 sentences) by recall-time (294) correlation matrix for participant \#13.
-\textbf{E.} An events (34) by topics (100) matrix where each row represents the average topic vector for each event in the video model.
-\textbf{F.} An events (27) by topics (100) matrix where each row represents the average topic vector for each event in participant \#13's recall model.
-\textbf{G.} A recall events (27) by video events (34) correlation matrix for participant \#13.
-The cells with a yellow border identify the video event with the highest correlation to a given recall event.
-\textbf{H.} A group averaged recall events (34) by video events (34) correlation matrix.
-The cells with yellow borders are the video event with the highest correlation to a given average recall event.}
-\label{fig:model}
-\end{figure}
 

### 2018-09-01 paper/main.tex
WIP (results)

@@
 \section*{Results}
-To characterize the gists of the \textit{Sherlock} episode participants watched and their subsequent recountings of the episode, we used a topic model~\cite{BleiEtal03} to discover the latent thematic content.
+To characterize the gists of the \textit{Sherlock} episode participants watched and their subsequent recountings of the episode, we used a topic model~\cite{BleiEtal03} to discover the latent thematic content in the video.
+Topic models take as inputs a vocabulary of words to consider and a collection of text documents; they return as output two matrices.
+The first output is a \textit{topics matrix} whose rows are topics (latent themes) and whose columns correspond to words in the vocabulary.
+The entries of the topics matrix define how each word in the vocabulary is weighted by each discovered topic.
+For example, a detective-themed topic might weight heavily on words like ``crime,'' and ``search.''  The second output is a \textit{topic proportions matrix}, with one row per document and one column per topic.
+The topic proportions matrix describes which mix topics is reflected in each document.
+
 \cite{ChenEtal17} collected hand-annotated information about each of 1000 (manually identified) scenes spanning the roughly 45 minute video.
@@
 However, whereas Dynamic Topic Models are designed to characterize the how the properties of collections of documents change over time, our approach allows us to examine the topic dynamics within a single episode.
-Specifically, our approach yielded a single \textit{topic vector} for each timepoint of the episode (we set timepoints to match the acquisition times of the 1976 fMRI volumes collected as participants viewed the episode).
+Specifically, our approach yielded (via the topic proportions matrix) a single \textit{topic vector} for each timepoint of the episode (we set timepoints to match the acquisition times of the 1976 fMRI volumes collected as participants viewed the episode).
 
@@
 Part of our model fitting procedure required selecting an appropriate number of ``events'' to segment the timeseries into.
-We used an optimization procedure to identify the number of events that maximized within-event stability while also minimizing across-event correlations (see \textit{Methods} for additional detail).
-To create a stable ``summary'' of the episode, we computed the avereage topic vector within each event (Fig.~\ref{fig:model}C).
+We used an optimization procedure to identify the number of events that maximized within-event stability while also minimizing across-event correlations (see \textit{Methods} for additional details).
+To create a stable ``summary'' of the video, we computed the avereage topic vector within each event (Fig.~\ref{fig:model}C).
 
@@
 \end{figure}
+
+Given that the time-varying content of the video could be segmented cleanly into discrete events, we wondered whether participants' recalls of the video also displayed a similar structure.
+We applied the same topic model (already trained on the video annotations) to each participant's recalls.
+Analogous to how we analyzed the time-varying content of the video, to obtain similar estimates for participants recalls we treated each (overlapping) 10 sentence ``window'' of their transcript as a ``document'' and then computed the most probable mix of topics reflected in each timepoint's sentences.
+This yielded, for each participant, a number-of-sentences by number-of-topics topic proportions matrix that characterized how the topics identified in the original video were reflected in the participant's recalls.
+Note that an important feature of our approach is that it allows us to compare participant's recalls to events from the original video, despite that different participants may have used different language to describe the same event, and that those descriptions may not match the original annotations.
+This is a consequence of projecting the video and recalls into a common ``topic'' space.
+An example matrix from one participant is shown in Figure~\ref{fig:model}D.
+
+To
 

### 2018-09-01 paper/main.tex
backing up edits to results

@@
 \section*{Results}
-To characterize the gists of the \textit{Sherlock} episode participants watched and their subsequent recountings of the episode, we used a topic model~\cite{BleiEtal03} to discover the latent thematic content in the video.
+To characterize the gists of the \textit{Sherlock} episode participants watched and their subsequent recountings of the episode, we used a topic model~\citep{BleiEtal03} to discover the latent thematic content in the video.
 Topic models take as inputs a vocabulary of words to consider and a collection of text documents; they return as output two matrices.
@@
 This information included: a brief narrative description of what was happening; whether the scene took place indoors vs.
-outdoors; names of any characters on the screen; names of any characters who were in focus in the camera show; names of characters who were speaking; the location where the scene took place; the camera angle (close up, medium, long, etc.); whether or not background music was present; and other similar details (for a full list of annoted features see \textit{Methods}).
+outdoors; names of any characters on the screen; names of any characters who were in focus in the camera; names of characters who were speaking; the location where the scene took place; the camera angle (close up, medium, long, etc.); whether or not background music was present; and other similar details (for a full list of annoted features see \textit{Methods}).
 We took from these annotations the union of all unique words (excluding stop words, such as ``and,'' ``or,'' ``but,'' etc.) across all features and scenes as the ``vocabulary'' for the topic model.
@@
 Note that our approach is similar in some respects to Dynamic Topic Models~\citep{BleiLaff06}, in that we sought to characterize how the thematic content of the episode evolved over time.
-However, whereas Dynamic Topic Models are designed to characterize the how the properties of collections of documents change over time, our approach allows us to examine the topic dynamics within a single episode.
+However, whereas Dynamic Topic Models are designed to characterize the how the properties of collections of documents change over time, our approach allows us to examine the topic dynamics within a single video.
 Specifically, our approach yielded (via the topic proportions matrix) a single \textit{topic vector} for each timepoint of the episode (we set timepoints to match the acquisition times of the 1976 fMRI volumes collected as participants viewed the episode).
@@
 
-The topics we found were heavily character-focused (e.g., the top-weighted word in each topic was nearly always a character) and could be roughly divided into themes related to primarily Sherlock-focused; primarily (John) Watson-focused (Watson is Sherlock's close confidant and assistant); and themes that involved Sherlock and Watson interacting (Fig.~\topics).
-Several of the topics also appeared highly similar, which we hypothesized might allow us to distinguish between subtle narrative differences (if the distinctions between those overlapping topics were meaningful).
+The topics we found were heavily character-focused (e.g., the top-weighted word in each topic was nearly always a character) and could be roughly divided into themes that were primarily Sherlock-focused; primarily (John) Watson-focused (Watson is Sherlock's close confidant and assistant); or that involved Sherlock and Watson interacting (Fig.~\topics).
+Several of the topics were highly similar, which we hypothesized might allow us to distinguish between subtle narrative differences (if the distinctions between those overlapping topics were meaningful).
 The topic vectors for each timepoint were \textit{sparse}, in that only a small number (usually one or two) topics tended to be ``active'' in any given timepoint (Fig.~\ref{fig:model}A).
@@
 These two properties of the topic dynamics may be seen in the block diagonal structure of the timepoint-by-timepoint correlation matrix (Fig.~\ref{fig:model}B).
-Following \cite{BaldEtal17}, used a Hidden Markov Model (HMM) to identify the \textit{event boundaries} where the topic activations changed rapidly (i.e., at the boundaries of the blocks in the correlation matrix; event boundaries identified by the HMM are outlined in yellow).
+Following \cite{BaldEtal17}, we used a Hidden Markov Model (HMM) to identify the \textit{event boundaries} where the topic activations changed rapidly (i.e., at the boundaries of the blocks in the correlation matrix; event boundaries identified by the HMM are outlined in yellow).
 Part of our model fitting procedure required selecting an appropriate number of ``events'' to segment the timeseries into.
@@
 We applied the same topic model (already trained on the video annotations) to each participant's recalls.
-Analogous to how we analyzed the time-varying content of the video, to obtain similar estimates for participants recalls we treated each (overlapping) 10 sentence ``window'' of their transcript as a ``document'' and then computed the most probable mix of topics reflected in each timepoint's sentences.
+Analogous to how we analyzed the time-varying content of the video, to obtain similar estimates for participants' recalls we treated each (overlapping) 10 sentence ``window'' of their transcript as a ``document'' and then computed the most probable mix of topics reflected in each timepoint's sentences.
 This yielded, for each participant, a number-of-sentences by number-of-topics topic proportions matrix that characterized how the topics identified in the original video were reflected in the participant's recalls.
 Note that an important feature of our approach is that it allows us to compare participant's recalls to events from the original video, despite that different participants may have used different language to describe the same event, and that those descriptions may not match the original annotations.
-This is a consequence of projecting the video and recalls into a common ``topic'' space.
-An example matrix from one participant is shown in Figure~\ref{fig:model}D.
+This is a huge benefit of projecting the video and recalls into a common ``topic'' space.
+An example topic proportions matrix from one participant's recalls is shown in Figure~\ref{fig:model}D.
 
-To
+Although the example participant's recall topic proportions matrix has some visual similarity to the video topic proportions matrix, the time-varying topic proportions for the example participant's recalls are not as sparse as for the video (e.g., compare Figs.~\ref{fig:model}A and D).
+Similarly, although there do appear to be periods of stability in the recall topic dynamics (e.g., most topics are active or inactive over contiguous blocks of time), the overall timecourses are not as cleanly delineated as the video topics are.
+To examine these patterns in detail, we computed the timepoint-by-timepoint correlation matrix for the example participant's recall topic proportions (Fig.~\ref{fig:model}E).
+As in the video correlation matrix (Fig.~\ref{fig:model}B), the example partipant's recall correlation matrix has a strong block diagonal structure, indicating that their recalls are discretized into separated events.
+As for the video correlation matrix, we can use an HMM, along with the aformentioned event number optimization procedure (also see \textit{Methods}) to determine how many events are reflected in the participant's recalls and where specifically the event boundaries fall (outlined in yellow).
+We carried out a similar analysis on all 17 participants' recall topic proportions matrices (Fig.~\corrmats).
 
-%JRM STOPPED HERE
+Two clear patterns emerged from this set of analyses.
+First, although every individual participant's recalls could be segmented into discrete events (e.g.\ every individual participant's recall correlation matrix exhibited clear block diagonal structure; Fig.~\corrmats), each participant appeared to have a unique \textit{recall resolution}, reflected in the sizes of those blocks.
+For example, some participants' recall topic proportions segmented into just a few events (e.g.\ Participants 1, 4, and 15), while others' recalls segmented into many shorter duration events (e.g.\ Participants 12, 13, and 17).
+This suggests that different participants may be recalling the video with different levels of detail-- e.g.
+some might touch on just the major plot points, whereas others might attempt to recall every minor scene.
+The second clear pattern present in every individual participant's recall correlation matrix is that, unlike in the video correlation matrix, there are substantial off-diagonal correlations in participant's recalls.
+Whereas each event in the original video (was largely) separable from the others (Fig.~\ref{fig:model}B), in transforming those separable events into memory participants appear to be integrating \textit{across} different events, blending elements of previously recalled and not-yet-recalled events into each newly recalled event (Figs.~\ref{fig:model}D, \corrmats).
+
+\textbf{JRM STOPPED HERE}
 
@@
 % x2. notice block diagonal structure, rather than smooth transitions; motivates HMM approach.  Note about selecting K
-% 3.
+% x3.
 question: do recalls exhibit same structure?
@@
 note that by projecting everything into a common topic space, the thematic content of each moment of movie/recall can be compared, even though the mix of words used to describe any given event or moment may not be consistent across people (or across annotations/recall)
-% 4. recalls exhibit blocky structure, but at different scales.  motivates fitting K separately by person
+% x4. recalls exhibit blocky structure, but at different scales.  motivates fitting K separately by person
 % 5. match up events (correlations)

### 2018-09-02 paper/boneyard.tex
backing up progress (results)

@@
+\subsection*{Modeling the naturalistic stimulus and verbal recall}
+We fit a topic model \citep{BleiEtal03} to hand-annotated text descriptions of scenes from the video.
+The text descriptions contained details of the scene such as the characters present, location, and a short summary of the scene (see Fig.~\ref{fig:schematic} for example text).
+As depicted in Fig.~\ref{fig:model}A, the topic vectors are sparse and change slowly over time.
+Furthermore, there are clear transitions from one topic ``state'' to the next, possibly indexing scene transitions in the stimulus.
+To get a better handle on this temporal structure, we computed a timepoints (1976) by timepoints (1976) correlation matrix of the video model (Fig.~\ref{fig:model}C).
+This correlation matrix reveals that the model has a strong, block-diagonal structure with very low off-diagonal correlation values, suggesting the representations of each block are unique and highly discriminable.
+We found that the ``narrative details'' (a few sentences summarizing the dialogue and specific happenings of the scene) of the video were the most important feature driving this model structure (see Fig.~\featureimportance A).
+
+After watching the video, participants verbally recalled (in order) as much of the episode as they could.
+We used the same topic model (fit with the text descriptions of the video) to transform participants' verbal recall transcripts.
+An example participant's (\#13) recall model is plotted in Fig.~\ref{fig:model}B.
+Notably, participant \#13's recall model appears visually similar to the video model.
+Similar to the video model analysis (Fig.~\featureimportance A), we found that the ``narrative details'' feature was most important for driving the video/recall relationship (Fig.~\featureimportance B).
+Like the video model, topic vectors were sparse and changed gradually.
+Then, we investigated the temporal structure of the recall matrices.
+From each participant's recall model, we computed a sentences (68 to 294) by sentences (68 to 294) correlation matrix (Fig.~\ref{fig:model}D).
+Like the video model, each participant's recall correlation matrix exhibited a strong block-diagonal structure (Fig.~\corrmats).
+Notably, this suggests that participants recounted the video in discriminable segments, likely related to the recall of specific events from the video.
+
+\subsection*{Segmenting the video and recall models into ``events''}
+As described above, a striking feature of both the video and recall correlation matrices is a strong, block structure along the diagonal of the matrices (see Fig.~\ref{fig:model}C,D).
+We hypothesized that this structure might arise from transient stability in the "theme" of both the video and of participants' memory for the video.
+We hypothesized that specific events described by a participant could be ``matched'' to specific video events by computing the similarity (i.e., correlation) between their topic vectors.
+In other words, the video event that is most thematically similar to a particular recall event is the event that the participant is most likely describing.
+To test this idea, we segmented the video and recall models in $k$ events (i.e., states) using a hidden Markov model ~\citep{BaldEtal17}.
+Our algorithm determined 34 events for the video model and a range of values (range: 8-27; mean: 15.41; SD: 5.6) for the recall models (see Methods for details on choosing an optimal $k$ value).
+The events discovered for the video model and a representative participant's recall model are highlighted as yellow rectangles outlining blocks along the diagonal of the correlation matrices (Fig.~\ref{fig:model}C,D).
+
+Next, we created a video ``event model'' by averaging together neighboring topic vectors that the were classified to be in the same event, resulting in an events (34) by topics (100) matrix (Fig.~\ref{fig:model}E).
+We performed the same procedure for the recall matrices (Fig.~\ref{fig:model}F).
+Then, we computed the correlation between video and recall event models, resulting in a video events (34) by recall events (8-27, depending on the participant) correlation matrix (Fig~\ref{fig:model}G for example, Fig.~\matchmats for all participants).
+These matrices represent the similarity (correlation) between each video event and each recall event (for each participant).
+To determine which video event a particular recall event was most likely describing, we found the index of the video event with the highest correlation to the recall event (i.e., the argmax).
+This is depicted in Fig.~\ref{fig:model}G as the cells highlighted with a yellow border.
+Notably, our algorithm suggests that the example participant recalled most of the video events and did so in order.
+
+Then, we computed a group-averaged recall event model and video-recall event correlation matrix.
+For each participant (and each recall event), we sorted the recall event vectors (across all participants) according to the video event with the highest correlation.
+We then averaged the recall event vectors within each group.
+This yielded an average recall event vector for all but one (of 34) video events, since no participant remembered one of the events according to our model.
+Lastly, we computed an average recall event (34) by video event (34) correlation matrix, and highlighted the cell with the highest correlation value with a yellow border (Fig.~\ref{fig:model}H).
+Notably, this matrix displayed high correlation values along the diagonal and low correlations in the off-diagonal cells.
+This suggests that on average, participants were able to recapitulate the events in the episode in a specific, sequential and highly descriminable way.
+
+\subsection*{The trajectory of a naturalistic experience is preserved in recall}
+Classic approaches to studying free recall in episodic memory (such as overall accuracy and serial position curve) focus on the quantity of information recalled \citep{Murd62a}.
+More recent metrics (such as lag-CRP, semantic and temporal clustering) go further to describe list-level memory organization \citep{Kaha96, PolyEtal09}.
+However, these approaches cannot (and were not designed to) capture the rich temporal dynamics inherent in naturalistic stimuli and associated recall of those experiences.
+In the next set of analyses, we test the hypothesis that successful recall of a naturalistic stimulus entails recovering the trajectory of a stimulus.
+
+%%%%
+
 These features of real world memory provide a stark contrast with classic list-learning memory tasks that ask participants to reproduce from memory a set of studied items (e.g.

### 2018-09-02 paper/main.tex
backing up progress (results)

@@
 The second clear pattern present in every individual participant's recall correlation matrix is that, unlike in the video correlation matrix, there are substantial off-diagonal correlations in participant's recalls.
-Whereas each event in the original video (was largely) separable from the others (Fig.~\ref{fig:model}B), in transforming those separable events into memory participants appear to be integrating \textit{across} different events, blending elements of previously recalled and not-yet-recalled events into each newly recalled event (Figs.~\ref{fig:model}D, \corrmats).
+Whereas each event in the original video (was largely) separable from the others (Fig.~\ref{fig:model}B), in transforming those separable events into memory participants appear to be integrating \textit{across} different events, blending elements of previously recalled and not-yet-recalled events into each newly recalled event~\citep[Figs.~\ref{fig:model}D, \corrmats; also see][]{MannEtal11, HowaEtal12}.
+
+The above results indicate that both the structure of the original video and participants' recalls of the video exhibit event boundaries that can be identified automatically by characterizing the dynamic content using a common topic model and segmenting the content into events using HMMs.
+Next we asked whether some correspondence might be made between the specific content of the events the participants experienced in the video, and the events they later recalled.
+One approach to linking the experienced (video) and recalled events is to label each recalled event as matching the video event with the most similar (i.e., most highly correlated) topic vector.
+This yields a sequence of ``presented'' events from the original movie, and a sequence of (potentially differently ordered) ``recalled'' events for each participant.
+Analogous to classic list-learning studies, we can then examine participants' recall sequences by asking which events they tended to recall first~\citep[e.g., probability of first recall; Fig.~\listlearning A); ][]{WelcBurn24, PostPhil65, AtkiShif68}; how participants most often transition between recalls of the events as a function of the temporal distance between them~\citep[e.g., lag-conditional response probability; Fig.~\listlearning B; ][]{Kaha96}; and which events they were likely to remember overall~\citep[e.g., serial position recall analyses; Fig.~\listlearning C; ][]{Murd62a}.
+In list-learning studies, this set of analyses may be used to gain a nearly complete view into the sequences of recalls participants made~\citep[e.g., ][]{Kaha12}.
+However, in naturalistic recall the analyses provide a wholely incomplete picture: it leaves out any attempt to quantify participants' abilities to capture the \textit{content} of what occurred in the video (i.e., their only experimental instruction!).
+
+The dynamic content of the video and participants' recalls is quantified in the corresponding topic proportion matrices.
+However, it is difficult to gain deep insights into that content by directly examining the topic proportion matrices (e.g., Figs.~\ref{fig:model}A, D) or the corresponding correlation matrices (Figs.~\ref{fig:model}B, E, \corrmats).
+To visualize the time-varying high-dimensional content in a more intuitive way~\citep{HeusEtal18} we projected the topic proportion matrices onto a 2-dimensional space using Uniform Manifold Approximation and Projection~\citep[UMAP; ][]{McInHeal18}.
+In this lower-dimensional space, each point represents a single video or recall event, and the distances between the points reflects the distances between their associated topic vectors (Fig.~\ref{fig:trajectory}A, B).
+
+\begin{figure}[tp]
+\centering
+\includegraphics[width=1\textwidth]{figs/trajectory}
+\caption{\small \textbf{Trajectories through topic space capture the dynamic content of the video and recalls.}  All panels: the topic proportion matrices have been projected onto a common two-dimensional space using UMAP.
+\textbf{A.} The two-dimensional topic trajectory taken by the episode of \textit{Sherlock}.
+Each dot indicates an event identified using the HMM (see \textit{Methods}); the dot colors denote the order of the events (early events are in red; later events are in blue), and the connecting lines indicate the transitions between successive events.
+\textbf{B.} The average two-dimensional trajectory captured by participants' recall sequences, with the same format and coloring as the trajectory in Panel A.
+To compute the event positions, we matched each recalled event with an event from the original video (see text), and then we averaged the positions of all events with the same label.
+The arrows reflect the average transition direction through topic space taken by any participants whose trajectories crossed that part of topic space; blue denotes reliable agreement across participants via a Rayleigh test ($p < 0.05$, corrected).
+\textbf{C.} The recall topic trajectories taken by each individual participant (1--17).
+The video's trajectory is shown in black for reference.
+(Same format and coloring as Panel A.)}
+\label{fig:trajectory}
+\end{figure}
 
@@
 % x4. recalls exhibit blocky structure, but at different scales.  motivates fitting K separately by person
-% 5. match up events (correlations)
-% 6.
+% x5. match up events (correlations)
+% x6.
 now we can use classic memory analyses to examine structure of recall.
@@
 (potential role of vmPFC in reflecting participant-specific memory transformations and processing)
-
-\subsection*{Modeling the naturalistic stimulus and verbal recall}
-We fit a topic model \citep{BleiEtal03} to hand-annotated text descriptions of scenes from the video.
-The text descriptions contained details of the scene such as the characters present, location, and a short summary of the scene (see Fig.~\ref{fig:schematic} for example text).
-As depicted in Fig.~\ref{fig:model}A, the topic vectors are sparse and change slowly over time.
-Furthermore, there are clear transitions from one topic ``state'' to the next, possibly indexing scene transitions in the stimulus.
-To get a better handle on this temporal structure, we computed a timepoints (1976) by timepoints (1976) correlation matrix of the video model (Fig.~\ref{fig:model}C).
-This correlation matrix reveals that the model has a strong, block-diagonal structure with very low off-diagonal correlation values, suggesting the representations of each block are unique and highly discriminable.
-We found that the ``narrative details'' (a few sentences summarizing the dialogue and specific happenings of the scene) of the video were the most important feature driving this model structure (see Fig.~\featureimportance A).
-
-After watching the video, participants verbally recalled (in order) as much of the episode as they could.
-We used the same topic model (fit with the text descriptions of the video) to transform participants' verbal recall transcripts.
-An example participant's (\#13) recall model is plotted in Fig.~\ref{fig:model}B.
-Notably, participant \#13's recall model appears visually similar to the video model.
-Similar to the video model analysis (Fig.~\featureimportance A), we found that the ``narrative details'' feature was most important for driving the video/recall relationship (Fig.~\featureimportance B).
-Like the video model, topic vectors were sparse and changed gradually.
-Then, we investigated the temporal structure of the recall matrices.
-From each participant's recall model, we computed a sentences (68 to 294) by sentences (68 to 294) correlation matrix (Fig.~\ref{fig:model}D).
-Like the video model, each participant's recall correlation matrix exhibited a strong block-diagonal structure (Fig.~\corrmats).
-Notably, this suggests that participants recounted the video in discriminable segments, likely related to the recall of specific events from the video.
-
-\subsection*{Segmenting the video and recall models into ``events''}
-As described above, a striking feature of both the video and recall correlation matrices is a strong, block structure along the diagonal of the matrices (see Fig.~\ref{fig:model}C,D).
-We hypothesized that this structure might arise from transient stability in the "theme" of both the video and of participants' memory for the video.
-We hypothesized that specific events described by a participant could be ``matched'' to specific video events by computing the similarity (i.e., correlation) between their topic vectors.
-In other words, the video event that is most thematically similar to a particular recall event is the event that the participant is most likely describing.
-To test this idea, we segmented the video and recall models in $k$ events (i.e., states) using a hidden Markov model ~\citep{BaldEtal17}.
-Our algorithm determined 34 events for the video model and a range of values (range: 8-27; mean: 15.41; SD: 5.6) for the recall models (see Methods for details on choosing an optimal $k$ value).
-The events discovered for the video model and a representative participant's recall model are highlighted as yellow rectangles outlining blocks along the diagonal of the correlation matrices (Fig.~\ref{fig:model}C,D).
-
-Next, we created a video ``event model'' by averaging together neighboring topic vectors that the were classified to be in the same event, resulting in an events (34) by topics (100) matrix (Fig.~\ref{fig:model}E).
-We performed the same procedure for the recall matrices (Fig.~\ref{fig:model}F).
-Then, we computed the correlation between video and recall event models, resulting in a video events (34) by recall events (8-27, depending on the participant) correlation matrix (Fig~\ref{fig:model}G for example, Fig.~\matchmats for all participants).
-These matrices represent the similarity (correlation) between each video event and each recall event (for each participant).
-To determine which video event a particular recall event was most likely describing, we found the index of the video event with the highest correlation to the recall event (i.e., the argmax).
-This is depicted in Fig.~\ref{fig:model}G as the cells highlighted with a yellow border.
-Notably, our algorithm suggests that the example participant recalled most of the video events and did so in order.
-
-Then, we computed a group-averaged recall event model and video-recall event correlation matrix.
-For each participant (and each recall event), we sorted the recall event vectors (across all participants) according to the video event with the highest correlation.
-We then averaged the recall event vectors within each group.
-This yielded an average recall event vector for all but one (of 34) video events, since no participant remembered one of the events according to our model.
-Lastly, we computed an average recall event (34) by video event (34) correlation matrix, and highlighted the cell with the highest correlation value with a yellow border (Fig.~\ref{fig:model}H).
-Notably, this matrix displayed high correlation values along the diagonal and low correlations in the off-diagonal cells.
-This suggests that on average, participants were able to recapitulate the events in the episode in a specific, sequential and highly descriminable way.
-
-\subsection*{The trajectory of a naturalistic experience is preserved in recall}
-Classic approaches to studying free recall in episodic memory (such as overall accuracy and serial position curve) focus on the quantity of information recalled \citep{Murd62a}.
-More recent metrics (such as lag-CRP, semantic and temporal clustering) go further to describe list-level memory organization \citep{Kaha96, PolyEtal09}.
-However, these approaches cannot (and were not designed to) capture the rich temporal dynamics inherent in naturalistic stimuli and associated recall of those experiences.
-In the next set of analyses, we test the hypothesis that successful recall of a naturalistic stimulus entails recovering the trajectory of a stimulus.
-
-\begin{figure}[tp]
-\centering
-\includegraphics[width=1\textwidth]{figs/trajectory}
-\caption{\small \textbf{Video and recall trajectory plots.} \textbf{A.} 2-dimensional embedding of the video events model (reduced with UMAP algorithm).
-The arrows indicate the forward direction of the video events.
-\textbf{B.} 2-dimensional embedding of the average recall events model.
-The colors refer to the most similar video events.
-The directional lines connecting the points represent the true video event order.
-The arrows represent the group-average direction of all recall event transitions (i.e., a line segment connecting two consecutive recall event vectors) that intersected a circle (radius = 0.5) centered on the origin of the arrow.
-\textbf{C.} Individual trajectory plots for each participant overlayed with the video model (black).
-The direction of the recall sequence is indicated by the direction of arrows connecting each recall event.
-The colors refer to the most likely video event.}
-\label{fig:trajectory}
-\end{figure}
 

### 2018-09-02 paper/boneyard.tex
finished draft of results

@@
+\textbf{JRM STOPPED HERE}
+
+% characterize gist of movie and recalls
+% x1. movie: fit topic models (add note on dynamic topic models).  fig 1: what do the topics reflect (top words from each topic), example with a few scenes.
+% x2. notice block diagonal structure, rather than smooth transitions; motivates HMM approach.  Note about selecting K
+% x3.
+question: do recalls exhibit same structure?
+apply topic model to recalls.
+note that by projecting everything into a common topic space, the thematic content of each moment of movie/recall can be compared, even though the mix of words used to describe any given event or moment may not be consistent across people (or across annotations/recall)
+% x4. recalls exhibit blocky structure, but at different scales.  motivates fitting K separately by person
+% x5. match up events (correlations)
+% x6.
+now we can use classic memory analyses to examine structure of recall.
+motivate and reference PFR, lag-CRP, and SPC.
+but this does not tell us about structure in the *content* of what people remembered, or whether people's recalls are capturing the hierarchical temporal structure of the original movie.
+% x7.
+topic trajectories as a new way of characterizing recall.
+assess agreement using rayleigh test.
+also examine shapes of each subject's trajectory to show match.
+key insight: everyone captures the general shape, but at different "sampling resolutions"
+% x8. we can also project back onto the original (word) features to understand more about what any particular part of the trajectory reflects (wordle fig)
+% x9.
+the above analyses tell us about how the trajectory of thematic content in the episode is both preserved and transformed in participants' memories.
+we next carried out analyses to understand the neural bases of these phenomena.
+analysis 1: which structures are sensitive (during viewing) to the original episode's topic trajectory?
+answer: default mode.
+anlaysis 2: which structure are sensitive (during viewing) to how the participants will later recall the episode?
+answer: vmPFC, default mode.
+(potential role of vmPFC in reflecting participant-specific memory transformations and processing)
+
+\subsection*{Brain regions that mirror the correlational structure of naturalistic stimuli and memories}.
+
+Previous work suggests that the brain may represent our experiences as ``events'' with different time scales in a nested hierarchy ~\citep{LernEtal11, ChenEtal17, BaldEtal17}.
+In this next analysis we asked: what brain regions mirror the event-like correlational structure of our topic-based video model during viewing?
+We used a searchlight procedure (see Methods for details) to identify regions whose timepoint-by-timepoint correlational structure matched the correlational structure of our model.
+This analysis revealed a network of regions including bilateral frontal and cingulate cortex (Fig.~\ref{fig:brainz}), suggesting that these regions may play a role in maintaining information relevant to the narrative trajectory of the video.
+
+While each participant remembered roughly the same sequence of events, there were subtle idiosyncracies in the way each individual described the events.
+For example, the event-by-event similarity structure (i.e., the off-diagonal values of the recall correlation matrices) differed across individuals (Fig.~\corrmats).
+We hypothesized that idiosyncracies in the recall dynamics across participants might be related to the temporal structure of brain networks representing the events during video viewing.
+In this analysis, we identified brain areas whose responses at the time of viewing exhibited the same (segmented) idiosyncratic dynamics that later appeared in that participants’ recalls.
+Using a procedure similar to the approach above (see Methods for details), we searched for regions whose correlational structure during viewing was related to the idiosyncratic structure of the participant's recall model.
+The resulting map suggests that the correlational structure of a network of brain regions including the ventromedial prefrontal cortex, anterior cingulate, and right medial temporal lobe mirror the idiosyncratic structure of participants' recalls (Fig.~\ref{fig:brainz}).
+
+%%%
+
+\subsection*{Additional measures of naturalistic recall}
+Representing the video and verbal recall as events in ``topic space'' also affords us the ability to characterize the quality of recall in a more fine-grained and nuanced way than was previously possible.
+We quantified the distance between each video event and its matching recall event (``precision''), the the distance between a video event and all non-matching recall events (``distinctiveness'') and the temporal order of the recall events (``order'').
+All three of these metrics were correlated to hand-annotated memory performance across participants ($p < 0.05$, see Supplemental Materials Section 1 for details).
+
+Just like in a traditional free recall list-learning experiment where participants view a list of words and then verbally recall them, our video-recall matching analysis approach affords us the ability to analyze memory in the same way.
+We considered 6 classic list-learning analyses: overall accuracy, probability of first recall \citep{Hoga75, HowaKaha99, Lami99}, lag-conditional response probability \citep{Kaha96, HowaKaha99}, serial position curve \citep{Murd62a}, temporal clustering, and semantic clustering \citep{HowaKaha02, PolyEtal09}.
+Extending these classic list-learning analyses to naturalistic stimuli allows to directly compare trial- and naturalistic-based recall studies (see Supplemental Materials Section 2 for details).
+
+%%%%
+
+\subsection*{Memorability by event and topics}
+A notable advantage of representing naturalistic stimuli and memory using this approach is that the event models can be mapped back to the language used to fit the model(s).
+This allows for analysis (and visualization) of the language used when participants recounted their experiences.
+In this next analysis, we 1) quantified the memorability of each video event and 2) used memorability to plot the ``top'' words for the most and least memorable scenes.
+
+To measure video event memorability, we computed the correlation between each video event and the closest recall event and then averaged those values within participants (Fig.~\ref{fig:topics}A).
+We used event memorability to create a weighted average over all video event vectors, where video events with better memory were weighted more heavily.
+Then, we extracted the top 200 words and created ``wordles'' representing the most memorable themes in the video.
+The results reveal that scenes containing ``Sherlock'' and ``John'' were highly memorable, as were scenes containing words such as ``medium'', ``street'' and ``baker'' (Fig.~\ref{fig:topics}B).
+To find words related to the least memorable scenes, we inverted the memorability weights and again extracted the top 200 words.
+Scenes containing ``Mike'' and ``Molly'' were least remembered, and also words like ``conference'', ``hospital'' and ``psychotherapist'' (Fig.~\ref{fig:topics}B).
+
+Then, we took a closer look at the themes contained in the top/bottom 3 events, using the memorability weights to select the top/bottom events.
+We performed the same analysis as described above, but separately for the video and average recall event vectors representing each of the top/bottom 3 remembered events.
+In Figure~\ref{fig:topics}C, the trajectory represents a low-dimensional embedding of the video model and the large colored dots represent the video events.
+The smaller colored dots represent the distribution of individual recall events across all participants, colored by the closest video event.
+We plotted wordles for the top 3 (circled in green) and bottom 3 (red) most/least remembered events, where the video is represented in the left half of the circle and the average recall is represented in the right half of the circle.
+Visual inspection reveals that the words contained in the memorability weighted worldles (Fig.~\ref{fig:topics}B) overlap with the individual top/bottom event wordles (Fig.~\ref{fig:topics}C).
+These analyses shed light on the contents of naturalistic stimuli and accompanying memories, and highlight the flexibility in transforming between human and machine readable representations of the data afforded by our modeling approach.
+
+%%%%
+
+To visualize the relationship between the video and recall event models, we embedded them into a 2D space using the UMAP dimensionality reduction algorithm ~\citep{McInHeal18}, where the points represent video/recall events and the distance between them represents their similarity/distance in ``topic space'' (Fig.~\ref{fig:trajectory}A).
+We observed that visually, it appears that the two models have a very similar temporal evolution and geometric structure.
+To further quantify this correspondence and to characterize how participants navigated through the space during recall, we analyzed the angle between successive recall events.
+We created a grid of evenly spaced points (.25 units) in the 2D ``topic space.'' For each point on the grid, we drew a circle (radius= 0.5) around the point and grouped together all recall transitions that intersected the circle (across participants).
+To visualize the average angle, we converted each transition angle to a unit vector and then averaged the vectors together.
+To assess consistency in the direction of the recall transition across participants, we performed a Rayleigh test ($p < 0.001$, corrected at $p < 0.05$ using the permutation procedure described in Methods).
+Notably, the video events fell within the path formed by the recall events.
+Thus, participants' recalls followed the same path as the video model (Fig.~\ref{fig:trajectory}B), suggesting the shape of the stimulus was preserved despite idiosyncratic differences between participants in their recalls.
+
+%NOTE: it feels like we need some more supporting evidence that the shape of the video and the recall trajectories are related.
+one possibility would be to add the analysis where i compute the distance between each recall event and the line formed by each video transition per participant.
+the result is that hand annotated memory correlates to this distance, suggesting that participants who better capture the shape also have better memory on average.
+
+%%%
+
 \subsection*{Modeling the naturalistic stimulus and verbal recall}

### 2018-09-02 paper/main.tex
finished draft of results

@@
 
-\cite{ChenEtal17} collected hand-annotated information about each of 1000 (manually identified) scenes spanning the roughly 45 minute video.
+\cite{ChenEtal17} collected hand-annotated information about each of 1000 (manually identified) scenes spanning the roughly 45 minute video used in their experiment.
 This information included: a brief narrative description of what was happening; whether the scene took place indoors vs.
-outdoors; names of any characters on the screen; names of any characters who were in focus in the camera; names of characters who were speaking; the location where the scene took place; the camera angle (close up, medium, long, etc.); whether or not background music was present; and other similar details (for a full list of annoted features see \textit{Methods}).
+outdoors; names of any characters on the screen; names of any characters who were in focus in the camera; names of characters who were speaking; the location where the scene took place; the camera angle (close up, medium, long, etc.); whether or not background music was present; and other similar details (for a full list of annotated features see \textit{Methods}).
 We took from these annotations the union of all unique words (excluding stop words, such as ``and,'' ``or,'' ``but,'' etc.) across all features and scenes as the ``vocabulary'' for the topic model.
@@
 
-The topics we found were heavily character-focused (e.g., the top-weighted word in each topic was nearly always a character) and could be roughly divided into themes that were primarily Sherlock-focused; primarily (John) Watson-focused (Watson is Sherlock's close confidant and assistant); or that involved Sherlock and Watson interacting (Fig.~\topics).
+The topics we found were heavily character-focused (e.g., the top-weighted word in each topic was nearly always a character) and could be roughly divided into themes that were primarily Sherlock-focused; primarily John-focused (John is Sherlock's close confidant and assistant); or that involved Sherlock and John interacting (Fig.~\topics).
 Several of the topics were highly similar, which we hypothesized might allow us to distinguish between subtle narrative differences (if the distinctions between those overlapping topics were meaningful).
@@
 We used an optimization procedure to identify the number of events that maximized within-event stability while also minimizing across-event correlations (see \textit{Methods} for additional details).
-To create a stable ``summary'' of the video, we computed the avereage topic vector within each event (Fig.~\ref{fig:model}C).
+To create a stable ``summary'' of the video, we computed the average topic vector within each event (Fig.~\ref{fig:model}C).
 
@@
 \textbf{G.} Correlations between the topic vectors for every pair of video events (Panel C) and recalled events (from the example participant; Panel F).
+For similar plots for all participants see Figure~\matchmats.
 \textbf{H.} Average correlations between each pair of video events and recalled events (across all 17 participants).
@@
 As in the video correlation matrix (Fig.~\ref{fig:model}B), the example partipant's recall correlation matrix has a strong block diagonal structure, indicating that their recalls are discretized into separated events.
-As for the video correlation matrix, we can use an HMM, along with the aformentioned event number optimization procedure (also see \textit{Methods}) to determine how many events are reflected in the participant's recalls and where specifically the event boundaries fall (outlined in yellow).
+As for the video correlation matrix, we can use an HMM, along with the aforementioned event number optimization procedure (also see \textit{Methods}) to determine how many events are reflected in the participant's recalls and where specifically the event boundaries fall (outlined in yellow).
 We carried out a similar analysis on all 17 participants' recall topic proportions matrices (Fig.~\corrmats).
@@
 
-The above results indicate that both the structure of the original video and participants' recalls of the video exhibit event boundaries that can be identified automatically by characterizing the dynamic content using a common topic model and segmenting the content into events using HMMs.
+The above results indicate that both the structure of the original video and participants' recalls of the video exhibit event boundaries that can be identified automatically by characterizing the dynamic content using a common (shared) topic model and segmenting the content into events using HMMs.
 Next we asked whether some correspondence might be made between the specific content of the events the participants experienced in the video, and the events they later recalled.
-One approach to linking the experienced (video) and recalled events is to label each recalled event as matching the video event with the most similar (i.e., most highly correlated) topic vector.
+One approach to linking the experienced (video) and recalled events is to label each recalled event as matching the video event with the most similar (i.e., most highly correlated) topic vector (Figs.~\ref{fig:model}G, \matchmats).
 This yields a sequence of ``presented'' events from the original movie, and a sequence of (potentially differently ordered) ``recalled'' events for each participant.
-Analogous to classic list-learning studies, we can then examine participants' recall sequences by asking which events they tended to recall first~\citep[e.g., probability of first recall; Fig.~\listlearning A); ][]{WelcBurn24, PostPhil65, AtkiShif68}; how participants most often transition between recalls of the events as a function of the temporal distance between them~\citep[e.g., lag-conditional response probability; Fig.~\listlearning B; ][]{Kaha96}; and which events they were likely to remember overall~\citep[e.g., serial position recall analyses; Fig.~\listlearning C; ][]{Murd62a}.
-In list-learning studies, this set of analyses may be used to gain a nearly complete view into the sequences of recalls participants made~\citep[e.g., ][]{Kaha12}.
-However, in naturalistic recall the analyses provide a wholely incomplete picture: it leaves out any attempt to quantify participants' abilities to capture the \textit{content} of what occurred in the video (i.e., their only experimental instruction!).
+Analogous to classic list-learning studies, we can then examine participants' recall sequences by asking which events they tended to recall first~\citep[e.g., probability of first recall; Fig.~\listlearning A; ][]{WelcBurn24, PostPhil65, AtkiShif68}; how participants most often transition between recalls of the events as a function of the temporal distance between them~\citep[e.g., lag-conditional response probability; Fig.~\listlearning B; ][]{Kaha96}; and which events they were likely to remember overall~\citep[e.g., serial position recall analyses; Fig.~\listlearning C; ][]{Murd62a}.
+In list-learning studies, this set of three analyses may be used to gain a nearly complete view into the sequences of recalls participants made~\citep[e.g., ][]{Kaha12}.
+However, in naturalistic recall the analyses provide a wholly incomplete picture: they leave out any attempt to quantify participants' abilities to capture the \textit{content} of what occurred in the video (i.e., their only experimental instruction!).
 
@@
 However, it is difficult to gain deep insights into that content by directly examining the topic proportion matrices (e.g., Figs.~\ref{fig:model}A, D) or the corresponding correlation matrices (Figs.~\ref{fig:model}B, E, \corrmats).
-To visualize the time-varying high-dimensional content in a more intuitive way~\citep{HeusEtal18} we projected the topic proportion matrices onto a 2-dimensional space using Uniform Manifold Approximation and Projection~\citep[UMAP; ][]{McInHeal18}.
-In this lower-dimensional space, each point represents a single video or recall event, and the distances between the points reflects the distances between their associated topic vectors (Fig.~\ref{fig:trajectory}A, B).
+To visualize the time-varying high-dimensional content in a more intuitive way~\citep{HeusEtal18} we projected the topic proportion matrices onto a two-dimensional space using Uniform Manifold Approximation and Projection~\citep[UMAP; ][]{McInHeal18}.
+In this lower-dimensional space, each point represents a single video or recall event, and the distances between the points reflect the distances between the events' associated topic vectors (Fig.~\ref{fig:trajectory}).
 
@@
 
-\textbf{JRM STOPPED HERE}
+Visual inspection of the video and recall topic trajectories reveals a striking pattern.
+First, the topic trajectory of the video (which reflects its dynamic content; Fig.~\ref{fig:trajectory}A) is captured nearly perfectly by the averaged topic trajectories of participants' recalls (Fig.~\ref{fig:trajectory}B).
+To assess the consistency of these recall trajectories across participants, we asked: given that a participant's recall trajectory had entered a particular location in topic space, could the position of their \textit{next} recalled event be predicted reliably?
+For each location in topic space, we computed the set of line segments connecting successively recalled events (across all participants) that intersected that location (see \textit{Methods} for additional details).
+We then computed (for each location) the distribution of angles formed by the lines defined by those line segments and a fixed reference line (the $x$-axis).
+Rayleigh tests revealed the set of locations in topic space at which these across-participant distributions exhibited reliable peaks (blue arrows in Fig.~\ref{fig:trajectory}B).
+We observed that the locations traversed by nearly the entire the video trajectory exhibited such peaks.
+In other words, participants exhibited similar trajectories that also matched the trajectory of the original video (Fig.~\ref{fig:trajectory}C).
+This is especially notable when considering the fact that the number of events participants recalled (dots in Fig.~\ref{fig:trajectory}C) varied considerably across people, and that every participant used different words to describe what they had remembered happening in the video.
 
-% characterize gist of movie and recalls
-% x1. movie: fit topic models (add note on dynamic topic models).  fig 1: what do the topics reflect (top words from each topic), example with a few scenes.
-% x2. notice block diagonal structure, rather than smooth transitions; motivates HMM approach.  Note about selecting K
-% x3.
-question: do recalls exhibit same structure?
-apply topic model to recalls.
-note that by projecting everything into a common topic space, the thematic content of each moment of movie/recall can be compared, even though the mix of words used to describe any given event or moment may not be consistent across people (or across annotations/recall)
-% x4. recalls exhibit blocky structure, but at different scales.  motivates fitting K separately by person
-% x5. match up events (correlations)
-% x6.
-now we can use classic memory analyses to examine structure of recall.
-motivate and reference PFR, lag-CRP, and SPC.
-but this does not tell us about structure in the *content* of what people remembered, or whether people's recalls are capturing the hierarchical temporal structure of the original movie.
-% 7.
-topic trajectories as a new way of characterizing recall.
-assess agreement using rayleigh test.
-also examine shapes of each subject's trajectory to show match.
-key insight: everyone captures the general shape, but at different "sampling resolutions"
-% 8. we can also project back onto the original (word) features to understand more about what any particular part of the trajectory reflects (wordle fig)
-% 9.
-the above analyses tell us about how the trajectory of thematic content in the episode is both preserved and transformed in participants' memories.
-we next carried out analyses to understand the neural bases of these phenomena.
-analysis 1: which structures are sensitive (during viewing) to the original episode's topic trajectory?
-answer: default mode.
-anlaysis 2: which structure are sensitive (during viewing) to how the participants will later recall the episode?
-answer: vmPFC, default mode.
-(potential role of vmPFC in reflecting participant-specific memory transformations and processing)
+Because our analysis framework projects the dynamic video content and participants' recalls onto a common topic space, and because the dimensions of that space are known (i.e., each topic dimension is a set of weights over words in the vocabulary; Fig.~\topics), we can examine the topic trajectories to understand which specific content was remembered well (or poorly).
+For each video event, we can ask: for all participants who recalled that event, what was the average correlation (across participants) between the video event's topic vector and the recall event topic vectors from each participant?
+This yields a single correlation coefficient for each video event, describing how closely participants' recalls of the event tended to reliably capture its content (Fig.~\ref{fig:topics}A).
+(We also examined how different comparisons between each video event's topic vector and the corresponding recall event topic vectors related to hand-annotated characterizations of memory performance; see \textit{Supplemental Materials}).
+Given this summary of which events were recalled reliably (or not), we next asked whether the better-remembered or worse-remembered events tended to reflect particular topics.
+We computed a weighted average of the topic vectors for each video event, where the weights reflected how reliably each event was recalled.
+To visualize the result, we created a ``wordle'' image~\citep{MuelEtal18} where words weighted more heavily by better-remembered topics appear in a larger font (Fig.~\ref{fig:topics}B, green box).
+Events that reflected topics weighting heavily on characters like ``Sherlock'' and ``John'' (i.e., the main characters) and locations like ``221b Baker Street'' (i.e., a major recurring location; the address of the flat that Sherlock and John share) were best remembered.
+An analogous analysis revealed which themes were poorly remembered; here in computing the weighted average over events' topic vectors we weighted each event in \textit{inverse} proportion to how well it was remembered (Fig.~\ref{fig:topics}B, red box).
+This revealed that events with relatively minor characters such as ``Mike,'' ``Jeffrey,'' and ``Molly,'' as well as less-integral plot locations (e.g., ``hospital'' and ``office'') were least well-remembered.
+This suggests that what is retained in memory are the major plot elements (i.e., the overall ``gist'' of what happened), whereas the more minor details are prone to pruning.
 
-To visualize the relationship between the video and recall event models, we embedded them into a 2D space using the UMAP dimensionality reduction algorithm ~\citep{McInHeal18}, where the points represent video/recall events and the distance between them represents their similarity/distance in ``topic space'' (Fig.~\ref{fig:trajectory}A).
-We observed that visually, it appears that the two models have a very similar temporal evolution and geometric structure.
-To further quantify this correspondence and to characterize how participants navigated through the space during recall, we analyzed the angle between successive recall events.
-We created a grid of evenly spaced points (.25 units) in the 2D ``topic space.'' For each point on the grid, we drew a circle (radius= 0.5) around the point and grouped together all recall transitions that intersected the circle (across participants).
-To visualize the average angle, we converted each transition angle to a unit vector and then averaged the vectors together.
-To assess consistency in the direction of the recall transition across participants, we performed a Rayleigh test ($p < 0.001$, corrected at $p < 0.05$ using the permutation procedure described in Methods).
-Notably, the video events fell within the path formed by the recall events.
-Thus, participants' recalls followed the same path as the video model (Fig.~\ref{fig:trajectory}B), suggesting the shape of the stimulus was preserved despite idiosyncratic differences between participants in their recalls.
-
-%NOTE: it feels like we need some more supporting evidence that the shape of the video and the recall trajectories are related.
-one possibility would be to add the analysis where i compute the distance between each recall event and the line formed by each video transition per participant.
-the result is that hand annotated memory correlates to this distance, suggesting that participants who better capture the shape also have better memory on average.
-
-\subsection*{Brain regions that mirror the correlational structure of naturalistic stimuli and memories}.
-\begin{figure}[tp]
-\centering
-\includegraphics[width=1\textwidth]{figs/brains_panels}
-\caption{\small \textbf{Video and recall model correlational structure searchlight analysis.} \textbf{A.} The correlation matrix representing the temporal structure of the video model.
-Below it is a surface plot of brain regions whose activity patterns mirrored the correlational structure of video model during viewing.
-\textbf{B.} The left matrix is S13's video-recall correlation matrix before warping.
-The yellow stars represent the path recovered by dynamic time warping.
-The right matrix is the result after warping.
-The same warping path was applied to the fMRI timeseries (separately for each participant).
-A surface plot of brain regions whose activity patterns mirrored the participant-specific recall correlation matrix.
-Significance threshold (p$<$.05) for both video and recall analyses derived from a permutation procedure by phase shifting the video model and recomputing the z-scores.}
-\label{fig:brainz}
-\end{figure}
-
-Previous work suggests that the brain may represent our experiences as ``events'' with different time scales in a nested hierarchy ~\citep{LernEtal11, ChenEtal17, BaldEtal17}.
-In this next analysis we asked: what brain regions mirror the event-like correlational structure of our topic-based video model during viewing?
-We used a searchlight procedure (see Methods for details) to identify regions whose timepoint-by-timepoint correlational structure matched the correlational structure of our model.
-This analysis revealed a network of regions including bilateral frontal and cingulate cortex (Fig.~\ref{fig:brainz}), suggesting that these regions may play a role in maintaining information relevant to the narrative trajectory of the video.
-
-While each participant remembered roughly the same sequence of events, there were subtle idiosyncracies in the way each individual described the events.
-For example, the event-by-event similarity structure (i.e., the off-diagonal values of the recall correlation matrices) differed across individuals (Fig.~\corrmats).
-We hypothesized that idiosyncracies in the recall dynamics across participants might be related to the temporal structure of brain networks representing the events during video viewing.
-In this analysis, we identified brain areas whose responses at the time of viewing exhibited the same (segmented) idiosyncratic dynamics that later appeared in that participants’ recalls.
-Using a procedure similar to the approach above (see Methods for details), we searched for regions whose correlational structure during viewing was related to the idiosyncratic structure of the participant's recall model.
-The resulting map suggests that the correlational structure of a network of brain regions including the ventromedial prefrontal cortex, anterior cingulate, and right medial temporal lobe mirror the idiosyncratic structure of participants' recalls (Fig.~\ref{fig:brainz}).
+In addition to constructing overall summaries, assessing the video and recall topic vectors from individual recalls can provide further insights.
+Specifically, for any given event we can construct a wordle from that event's topic vector, and we can construct a similar wordle from the average topic vectors produced by all participants who recalled that event.
+We can then examine those wordles visually to gain an intuition for which aspects of the video event were recapitulated in participants' recalls of that event.
+Several example wordles are displayed in Figure~\ref{fig:topics}C (wordles from the three best-remembered events are circled in green; wordles from the three worst-remembered events are circled in red).
+\textbf{[JRM NOTE: NEED SOME SORT OF ``POINT'' OR TAKE-AWAY FROM THIS ANALYSIS]}
 
@@
 \includegraphics[width=1\textwidth]{figs/topics}
-\caption{\small \textbf{Analysis of topics by event memorability.} \textbf{A.} Group-averaged correlation between each video event and closest recall event.
-Error bars represent 95\% confidence intervals.
-Stars indicate top (green) and bottom (red) 3 remembered events across participants \textbf{B.} Wordles (top 200 words) representing a weighted average of video event topic vectors weighted by event memorability (e.g., the correlation values in A).
-The top wordle (green) contains words from the most remembered events and the bottom (red) contains words from least memorable events.
-The word sizes are proportional to the word's ``activation''.
-\textbf{C.} Trajectory represents the video event model embedded in a 2D space using UMAP.
-The large colored dots are video events.
-The small colored dots are individual recall events across all participants, where the colors correspond to the closest video event.
-The circular wordles represent the top 3 most (green circles) and least (red) memorable video events.
-The left side of the wordle circles contain words associated with the video event vector and the right side contains words associated with the average recall event vector.}
+\caption{\small \textbf{Transforming experience into memory.} \textbf{A.} Average correlations (across participants) between the topic vectors from each video event and the closest-matching recall events.
+Error bars denote bootstrap-derived across-participant 95\% confidence intervals.
+The stars denote the three best-remembered events (green) and worst-remembered events (red).
+\textbf{B.} Wordles comprising the top 200 highest-weighted words reflected in the weighted-average topic vector across video events.
+Green: video events were weighted by how well the topic vectors derived from recalls of those events matched the video events' topic vectors (Panel A).
+Red: video events were weighted by the inverse of how well their topic vectors matched the recalled topic vectors.
+\textbf{C.}  The set of all video and recall events is projected onto the two-dimensional space derived in Figure~\ref{fig:trajectory}.
+The large dots denote video events and the smaller dots denote recalled events (same color scheme as Fig.~\ref{fig:trajectory}A).
+Wordles for several example events are displayed (green: three best-remembered events; red: three worst-remembered events).
+Within each circular wordle, the left side displays words associated with the topic vector for the video event, and the right side displays words associated with the (average) recall event topic vector, across all recall events matched to the given video event.}
 \label{fig:topics}
@@
 
-\subsection*{Memorability by event and topics}
-A notable advantage of representing naturalistic stimuli and memory using this approach is that the event models can be mapped back to the language used to fit the model(s).
-This allows for analysis (and visualization) of the language used when participants recounted their experiences.
-In this next analysis, we 1) quantified the memorability of each video event and 2) used memorability to plot the ``top'' words for the most and least memorable scenes.
+The results thus far tell us about which aspects of the dynamic content in the episode participants watched were preserved or altered in participants' memories of the episode.
+We next carried out a series of analyses aimed at understanding which brain structures might implement these processes.
+In one analysis we sought to identify which brain structures were sensitive to the video's dynamic content, as characterized by its topic trajectory.
+Specifically, we used a searchlight procedure to identify the extent to which each cluster of voxels exhibited a timecourse (as the participants watched the video) whose temporal correlation matrix matched the temporal correlation matrix of the original video's topic proportion matrix (Fig.~\ref{fig:model}B).
+As shown in Figure~\ref{fig:brainz}A, the analysis revealed a network of regions including bilateral frontal and cingulate cortex, suggesting that these regions may play a role in maintaining information relevant to the narrative structure of the video.
+In a second analysis, we sought to identify which brain structures' responses (while viewing the video) reflected how each participant would later \textit{recall} the video.
+Specifically, we used an analogous searchlight procedure to identify clusters of voxels whose temporal correlation matrices reflected the temporal correlation matrix of the topic proportions for each individual's recalls (Figs.~\corrmats).
+As shown in Figure~\ref{fig:brainz}B, the analysis revealed a network of regions including the ventromedial prefrontal cortex, anterior cingulate, and right medial temporal lobe, suggesting that these regions may play a role in transforming each individual's experience into memory.
 
-To measure video event memorability, we computed the correlation between each video event and the closest recall event and then averaged those values within participants (Fig.~\ref{fig:topics}A).
-We used event memorability to create a weighted average over all video event vectors, where video events with better memory were weighted more heavily.
-Then, we extracted the top 200 words and created ``wordles'' representing the most memorable themes in the video.
-The results reveal that scenes containing ``Sherlock'' and ``John'' were highly memorable, as were scenes containing words such as ``medium'', ``street'' and ``baker'' (Fig.~\ref{fig:topics}B).
-To find words related to the least memorable scenes, we inverted the memorability weights and again extracted the top 200 words.
-Scenes containing ``Mike'' and ``Molly'' were least remembered, and also words like ``conference'', ``hospital'' and ``psychotherapist'' (Fig.~\ref{fig:topics}B).
-
-Then, we took a closer look at the themes contained in the top/bottom 3 events, using the memorability weights to select the top/bottom events.
-We performed the same analysis as described above, but separately for the video and average recall event vectors representing each of the top/bottom 3 remembered events.
-In Figure~\ref{fig:topics}C, the trajectory represents a low-dimensional embedding of the video model and the large colored dots represent the video events.
-The smaller colored dots represent the distribution of individual recall events across all participants, colored by the closest video event.
-We plotted wordles for the top 3 (circled in green) and bottom 3 (red) most/least remembered events, where the video is represented in the left half of the circle and the average recall is represented in the right half of the circle.
-Visual inspection reveals that the words contained in the memorability weighted worldles (Fig.~\ref{fig:topics}B) overlap with the individual top/bottom event wordles (Fig.~\ref{fig:topics}C).
-These analyses shed light on the contents of naturalistic stimuli and accompanying memories, and highlight the flexibility in transforming between human and machine readable representations of the data afforded by our modeling approach.
-
-\subsection*{Additional measures of naturalistic recall}
-Representing the video and verbal recall as events in ``topic space'' also affords us the ability to characterize the quality of recall in a more fine-grained and nuanced way than was previously possible.
-We quantified the distance between each video event and its matching recall event (``precision''), the the distance between a video event and all non-matching recall events (``distinctiveness'') and the temporal order of the recall events (``order'').
-All three of these metrics were correlated to hand-annotated memory performance across participants ($p < 0.05$, see Supplemental Materials Section 1 for details).
-
-Just like in a traditional free recall list-learning experiment where participants view a list of words and then verbally recall them, our video-recall matching analysis approach affords us the ability to analyze memory in the same way.
-We considered 6 classic list-learning analyses: overall accuracy, probability of first recall \citep{Hoga75, HowaKaha99, Lami99}, lag-conditional response probability \citep{Kaha96, HowaKaha99}, serial position curve \citep{Murd62a}, temporal clustering, and semantic clustering \citep{HowaKaha02, PolyEtal09}.
-Extending these classic list-learning analyses to naturalistic stimuli allows to directly compare trial- and naturalistic-based recall studies (see Supplemental Materials Section 2 for details).
+\begin{figure}[tp]
+\centering
+\includegraphics[width=1\textwidth]{figs/brains_panels}
+\caption{\small \textbf{Brain structures that underlie the transformation of experience into memory.} \textbf{A.} We searched for regions whose responses (as participants watched the video) matched the temporal correlation matrix of the video topic proportions.
+These regions are sensitive to the narrative structure of the video.
+\textbf{B.} We searched for regions whose responses (as participants watched the video) matched the temporal correlation matrix of the topic proportions derived from each individual's later recall of video.
+These regions are sensitive to how the narrative structure of the video is transformed into a memory of the video.
+Both panels: the maps are thresholded at $p < 0.05$, corrected.}
+\label{fig:brainz}
+\end{figure}
 
@@
 Given a number of states or events ($k$), the HMM recovers a set of labels that segments consecutive timepoints into $k$ events ~\citep{Rabi89, BaldEtal17}.
-To implement this analysis, we used the Brainiak toolbox \citep{BaldEtal17, Brainiak}.
+To implement this analysis, we used the BrainIAK toolbox \citep{BaldEtal17, Brainiak}.
 

### 2018-09-02 paper/main.tex
minor polishing

@@
 Second, the specific words used to describe an experience have little bearing on whether the experience should be considered to have been ``remembered.''  Asking whether the rememberer has precisely reproduced a specific set of words to describe a given experience is nearly orthogonal to whether they were actually able to remember it.
-In classic (e.g., list-learning) memory studies, precise recall is often a primary metric of assessing the quality of participants' memories.
+In classic (e.g., list-learning) memory studies, counting the number or proportion of precise recalls is often a primary metric of assessing the quality of participants' memories.
 Third, one might remember the \textit{gist} or essence of an experience but forget (or neglect to recount) particular details.
 Capturing the gist of what happened is typically the main ``point'' of recounting a memory to a listener whereas, depending on the circumstances, accurate recall of any specific detail may be irrelevant.
-There is no analog of the gist of an experience in most traditional memory experiments; rather we tend to assess participants' abilities to recover specific details (e.g., the precise stimuli they encountered earlier in the experiment).
+There is no analog of the gist of an experience in most traditional memory experiments; rather we tend to assess participants' abilities to recover specific details (e.g., computing the proportion of specific stimuli they remember, which presentation positions the remembered stimuli came from, etc.).
 
-How might one go about formally characterizing the gist of an experience?
+How might one go about formally characterizing the gist of an experience, or whether that gist has been recovered by the rememberer?
 Any given moment of an experience derives meaning from surrounding moments, as well as from longer-range temporal associations~\citep[e.g., ][]{LernEtal11}.
@@
 Note that an important feature of our approach is that it allows us to compare participant's recalls to events from the original video, despite that different participants may have used different language to describe the same event, and that those descriptions may not match the original annotations.
-This is a huge benefit of projecting the video and recalls into a common ``topic'' space.
+This is a huge benefit of projecting the video and recalls into a shared ``topic'' space.
 An example topic proportions matrix from one participant's recalls is shown in Figure~\ref{fig:model}D.
@@
 As in the video correlation matrix (Fig.~\ref{fig:model}B), the example partipant's recall correlation matrix has a strong block diagonal structure, indicating that their recalls are discretized into separated events.
-As for the video correlation matrix, we can use an HMM, along with the aforementioned event number optimization procedure (also see \textit{Methods}) to determine how many events are reflected in the participant's recalls and where specifically the event boundaries fall (outlined in yellow).
+As for the video correlation matrix, we can use an HMM, along with the aforementioned number-of-events optimization procedure (also see \textit{Methods}) to determine how many events are reflected in the participant's recalls and where specifically the event boundaries fall (outlined in yellow).
 We carried out a similar analysis on all 17 participants' recall topic proportions matrices (Fig.~\corrmats).
@@
 
-The above results indicate that both the structure of the original video and participants' recalls of the video exhibit event boundaries that can be identified automatically by characterizing the dynamic content using a common (shared) topic model and segmenting the content into events using HMMs.
+The above results indicate that both the structure of the original video and participants' recalls of the video exhibit event boundaries that can be identified automatically by characterizing the dynamic content using a shared topic model and segmenting the content into events using HMMs.
 Next we asked whether some correspondence might be made between the specific content of the events the participants experienced in the video, and the events they later recalled.
@@
 \includegraphics[width=1\textwidth]{figs/trajectory}
-\caption{\small \textbf{Trajectories through topic space capture the dynamic content of the video and recalls.}  All panels: the topic proportion matrices have been projected onto a common two-dimensional space using UMAP.
+\caption{\small \textbf{Trajectories through topic space capture the dynamic content of the video and recalls.}  All panels: the topic proportion matrices have been projected onto a shared two-dimensional space using UMAP.
 \textbf{A.} The two-dimensional topic trajectory taken by the episode of \textit{Sherlock}.
@@
 
-Because our analysis framework projects the dynamic video content and participants' recalls onto a common topic space, and because the dimensions of that space are known (i.e., each topic dimension is a set of weights over words in the vocabulary; Fig.~\topics), we can examine the topic trajectories to understand which specific content was remembered well (or poorly).
+Because our analysis framework projects the dynamic video content and participants' recalls onto a shared topic space, and because the dimensions of that space are known (i.e., each topic dimension is a set of weights over words in the vocabulary; Fig.~\topics), we can examine the topic trajectories to understand which specific content was remembered well (or poorly).
 For each video event, we can ask: for all participants who recalled that event, what was the average correlation (across participants) between the video event's topic vector and the recall event topic vectors from each participant?

### 2018-09-02 paper/main.tex
additional edits to results, got down some discussion thoughts in comments

@@
 This is especially notable when considering the fact that the number of events participants recalled (dots in Fig.~\ref{fig:trajectory}C) varied considerably across people, and that every participant used different words to describe what they had remembered happening in the video.
+Differences in the numbers of remembered events appear in participants' trajectories as differences in the sampling resolution along the trajectory.
+We note that this framework also provides a means of detangling classic ``proportion recalled'' measures (i.e., the proportion of video events referenced in participants' recalls) from participants' abilities to recaputulate the full gist of the original video (i.e., the similarity in the shape of the original video trajectory and that defined by each participant's reocounting of the video).
 
@@
 \label{sec:discussion}
+% JRM THOUGHTS ON DISCUSSION:
+% - Nature says "2-3 paragraphs" -- needs to be much shorter.
+% - I think we can get rid of anything we mention in the intro or results
+% - Things not easily presented elsewhere are the background on the brain results and applications to education metrics.
+I think we can focus on those two parts, add an "overview" and "conclusion" (potentially), and cut the rest.
 Studying human memory is commonly distilled down to a process of matching specific moments of a past experience with specific mnemonic outcomes.

### 2018-09-02 paper/boneyard.tex
working on discussion [WIP]

@@
-\textbf{JRM STOPPED HERE}
+% DISCUSSION
+Prior work on neural responses during naturalistic experiences and recall has largely focused on identifying brain regions whose responses are reliably similar across individuals ~\citep{LernEtal11, SimoEtal16, ChenEtal17, BaldEtal17, ZadbEtal17}.
+This allows one to identify which regions might be processing or representing the stimulus, or retrieving details of the experience during recall.
+Our approach is fundamentally different.
+We ask: which brain regions during video viewing match the video structure and how individual participants will recall the video later (in terms of the temporal correlations of their recall topic trajectory)?
+This latter approach highlights regions such as the medial prefrontal cortex (mPFC) and medial temporal lobes (MTL) that may respond in idiosyncratic ways across individuals, but that nonetheless play an important role in encoding experience into memory.
+In other work, the mPFC has been suggested to play a role in the representation of a ``schema'', or a network of prior knowledge that is consistent with the current task ~\citep{KestEtal12, GilbMarl17}.
+One interpretation for mPFC's involvement in our work is that mPFC represents participant-specific relationships with the content of the video, and its representation during scene viewing is related to how a participant later describes the scene.
+MTL activity patterns also matched participant's recall, which is consistent with a large body of literature highlighting the role of the MTL in episodic memory encoding ~\citep{PallWagn02, DavaEtAl03, RangEtal04, Dava06}.
+
+%%%%
+
+More broadly, these findings have strong implications for how we assess memory in other naturalistic contexts, such as the classroom or in a doctor's office.
+Whereas academic tests often measure students' performance using metrics such as the proportion of correctly answered questions, our work suggests that this approach might ``miss the forrest for the trees''.
+We view ``true learning'' as understanding key concepts (i.e., understanding central themes in the learned content and how they relate) rather than regurgitating the greatest number of facts.
+In addition to educational contexts, our approach may provide unique metrics that can be used to assist in the diagnosis of memory disorders, and other psychiatric disorders that influence memory.
+For example, while the quantity of information recalled could be roughly matched between a healthy and patient population, and other aspects of the memory (such as the shape, serial order, precision or distinctiveness) might be different.
+Thus, this work serves as a foundation for more nuanced approaches to memory assessment that consider the trajectory and specific contents of memory for a naturalistic experience.
+
+%%%%
+
+Studying human memory is commonly distilled down to a process of matching specific moments of a past experience with specific mnemonic outcomes.
+In traditional trial-based free recall experiments, individual stimuli encountered during encoding are typically labeled as ``remembered'' or ``forgotten'' depending on whether the stimulus is recalled/recognized during a subsequent test.
+While this approach has advanced our understanding of human memory immensely, it does not translate well to naturalistic experiences.
+For one thing, the contents of our recall at any given moment might be reflected in many prior experiences/moments.
+Furthermore, the particular words used to describe the experience will inevitably vary across people and even across repeated recollections within an individual.
+Thus, there is not a ``one-to-one'' mapping between naturalistic experiences and their mnemonic counterparts.
+For example, remembering the patterns and colors of each person's shirt in a crowd might be considered as excellent recall in a standard memory task setup.
+But if the rememberer failed to note that the people in the crowd were gathered for their surprise birthday party, then they would have missed the "point" of the experience.
+
+Our topic modeling approach, whereby we consider the broad ``theme'' present in different moments of participants' experiences and their memories for those experiences, affords us the ability to flexibly and accurately characterize memory for naturalistic experiences.
+This approach allows us to quantify which moments from the past and the current recounted experience match in terms of their thematic content and critically, our ability to perform this matching does not require participants to use any specific overlapping words.
+Our work characterizes recollection of an experience by comparing the overall ``shape'' of a dynamic stimulus and a memory.
+We assess the quality of memory for the video participants viewed by measuring the match between the shapes of the video's trajectory and each participant's recall trajectory.
+By contrast, the number of recalls could be captured by the "sampling frequency" along that trajectory -- but the number of recalls alone cannot tell us whether participants successfully recollected the meaning of the story by capturing the salient points of the narrative that define its main shape.
+In addition to providing a way to capture the shape of an experience, this method affords the ability to quantify the particular contents of memory.
+Whereas traditional approaches abstract over the content (e.g., percent correct), Our approach allows one to quantify which aspects of an experience are memorable and which fail to stick.
+This aspect of our approach opens the door for a much richer characterization of memory that considers not just how much information was recalled, but the particular details of that information as well.
+
+An important question for future work concerns the factors that drive an individual to sample their recall trajectory finely or coarsely.
+For example, given a short recall interval, would participants intuitively gravitate towards coarser samplings that still outline the basic shape of the video's topic trajectory?
+Or if participants were told that their narrations would be played back to other participants ~\citep{ZadbEtal17}, would that change the resolution or shape of their recalls?
+And over successive recountings of the same sequence of events or with more elapsed time between encoding and recall, how do the shapes of the trajectories change?
+For example, loss of detail would result in a "smoothing out" of the trajectories with each new retelling.
+
+While we view this work as a major advance in characterizing and understanding human memory, as with any approach there are limitations.
+First, the approach relies on having a ``good'' model of the stimulus (e.g., one that describes the video in the same way as participants recall it), which is currently only achievable by a human hand-annotating each moment of the video.
+To increase the scalability of this approach, future work could explore automated methods for extracting meaning from videos ~\citep{YuEtal16}.
+Another potential limitation is that by its nature, the model extracts the ``gist'' of scenes from the video.
+This provides desirable flexibility (e.g., participants can use different combinations of words to describe the scenes), but this comes at the expense of capturing specific details.
+Thus, a future direction of this work will be to increase sensitivity to such details while maintaining flexibility.
+
+To conclude, we'll revisit the question of what it means to remember something.
+Our view is that ``successful remembering'' is about recovering the ``trajectory'' of an experience, rather than the ability to recognize/recall any of its particular isolated details.
+Decades of research suggest that episodic memories are not veridical and context-free snapshots of the past, and so treating (and modelling) them as such is overly simplistic at best (and counterproductive at worst).
+While it's undeniable that these models have been useful in advancing our understanding of human memory, they are severely limited in their ability to explain memory for real life experiences.
+Real life experiences are highly structured in time, and so to have a complete understanding of the human memory system, our experiments and models of memory must not ignore this fact.
+Our work provides a theoretical advance in our understanding of what it means to remember as well as a novel methodological tool to study it.
+
+%RESULTS
 

### 2018-09-02 paper/main.tex
revised commented thoughts
working on discussion [WIP]

@@
 Specifically, we used an analogous searchlight procedure to identify clusters of voxels whose temporal correlation matrices reflected the temporal correlation matrix of the topic proportions for each individual's recalls (Figs.~\corrmats).
-As shown in Figure~\ref{fig:brainz}B, the analysis revealed a network of regions including the ventromedial prefrontal cortex, anterior cingulate, and right medial temporal lobe, suggesting that these regions may play a role in transforming each individual's experience into memory.
+As shown in Figure~\ref{fig:brainz}B, the analysis revealed a network of regions including the ventromedial prefrontal cortex (vmPFC), anterior cingulate, and right medial temporal lobe (rMTL), suggesting that these regions may play a role in transforming each individual's experience into memory.
 
@@
 \label{sec:discussion}
+
+One approach to identifying neural responses to naturalistic stimuli (including experiences) entails building a model of the stimulus and searching for brain regions whose responses are consistent with the model.
+In prior work, a series of studies from Uri Hasson's group~\citep{LernEtal11, SimoEtal16, ChenEtal17, BaldEtal17, ZadbEtal17} have extended this approach with a clever twist.
+Rather than building an explicit stimulus model, these studies instead search for brain responses (while experiencing the stimulus) that are reliably similar across individuals.
+So called \textit{inter-subject correlation} (ISC) and \textit{inter-subject functional connectivity} (ISFC) analyses effectively treat other people's brain responses to the stimulus as a ``model'' of how its features change over time.
+By contrast, in our present work we used topic models and HMMs to construct an explicit stimulus model (i.e., the topic trajectory of the movie).
+When we searched for brain structures whose responses are consistent with the video's topic trajectory, we identified a network of structures that overlaped strongly with the ``long temporal receptive window'' network reported by the Hasson group~\citep[e.g., compare our Fig.~\ref{fig:brainz}A with the map of long temporal receptive window voxels in ][]{LernEtal11}.
+This provides support for the notion that part of the long temporal receptive window network may be maintaining an explicit model of the stimulus dynamics.
+When we performed a similar analysis after swapping out the video's topic trajectory with the recall topic trajectories of each individual participant, this allowed us to identify brain regions whose responses (as the participants viewed the video) reflected how the video trajectory would be transformed in memory (as reflected by the recall topic trajectory).
+The analysis revealed that the rMTL and vmPFC may play a role in this person-specific transformation from experience into memory.
+The role of the MTL in episodic memory encoding has been well-reported~\citep[e.g., ][]{PallWagn02, DavaEtAl03, RangEtal04, Dava06}.
+Prior work has also implicated the medial prefrontal cortex in representing ``schema'' knowledge~\citep[i.e., general knowledge about the format of an ongoing experience given prior similar experiencs; ][]{KestEtal12, GilbMarl17}.
+Integrating across our study and this prior work, one interpretation is that the person-specific transformations mediated (or represented) by the rMTL and vmPFC may reflect schema knowledge being leveraged, formed, or updated, incorporating ongoing experience into previously acquired knowledge.
+
+Our work has broad implications for how we characterize and assess memory in real-world settings such as the classroom or physician's office.
+For example, the most commonly used classroom evaluation tools involve computing the proportion of correctly answered exam questions.
+Our work indicates that this approach is only loosly related to what educators might really want to measure: how well did the students understand the key ideas presented in the course?
+One could apply the computational framework we developed to construct topic trajectories for the video and participants' recalls to build explicit content models of the course material and exam questions.
+This approach would provide a more nuanced and specific view into which aspects of the material students had learned well (or poorly).
+Similarly, memory evaluations that incorporate explicit content models might provide more direct measures of the qualitiy of patients' memories.
+
 % JRM THOUGHTS ON DISCUSSION:
-% - Nature says "2-3 paragraphs" -- needs to be much shorter.
+% - Nature says "1-2 short paragraphs" -- needs to be much shorter.
 % - I think we can get rid of anything we mention in the intro or results
@@
 I think we can focus on those two parts, add an "overview" and "conclusion" (potentially), and cut the rest.
-Studying human memory is commonly distilled down to a process of matching specific moments of a past experience with specific mnemonic outcomes.
-In traditional trial-based free recall experiments, individual stimuli encountered during encoding are typically labeled as ``remembered'' or ``forgotten'' depending on whether the stimulus is recalled/recognized during a subsequent test.
-While this approach has advanced our understanding of human memory immensely, it does not translate well to naturalistic experiences.
-For one thing, the contents of our recall at any given moment might be reflected in many prior experiences/moments.
-Furthermore, the particular words used to describe the experience will inevitably vary across people and even across repeated recollections within an individual.
-Thus, there is not a ``one-to-one'' mapping between naturalistic experiences and their mnemonic counterparts.
-For example, remembering the patterns and colors of each person's shirt in a crowd might be considered as excellent recall in a standard memory task setup.
-But if the rememberer failed to note that the people in the crowd were gathered for their surprise birthday party, then they would have missed the "point" of the experience.
-
-Our topic modeling approach, whereby we consider the broad ``theme'' present in different moments of participants' experiences and their memories for those experiences, affords us the ability to flexibly and accurately characterize memory for naturalistic experiences.
-This approach allows us to quantify which moments from the past and the current recounted experience match in terms of their thematic content and critically, our ability to perform this matching does not require participants to use any specific overlapping words.
-Our work characterizes recollection of an experience by comparing the overall ``shape'' of a dynamic stimulus and a memory.
-We assess the quality of memory for the video participants viewed by measuring the match between the shapes of the video's trajectory and each participant's recall trajectory.
-By contrast, the number of recalls could be captured by the "sampling frequency" along that trajectory -- but the number of recalls alone cannot tell us whether participants successfully recollected the meaning of the story by capturing the salient points of the narrative that define its main shape.
-In addition to providing a way to capture the shape of an experience, this method affords the ability to quantify the particular contents of memory.
-Whereas traditional approaches abstract over the content (e.g., percent correct), Our approach allows one to quantify which aspects of an experience are memorable and which fail to stick.
-This aspect of our approach opens the door for a much richer characterization of memory that considers not just how much information was recalled, but the particular details of that information as well.
-
-Prior work on neural responses during naturalistic experiences and recall has largely focused on identifying brain regions whose responses are reliably similar across individuals ~\citep{LernEtal11, SimoEtal16, ChenEtal17, BaldEtal17, ZadbEtal17}.
-This allows one to identify which regions might be processing or representing the stimulus, or retrieving details of the experience during recall.
-Our approach is fundamentally different.
-We ask: which brain regions during video viewing match the video structure and how individual participants will recall the video later (in terms of the temporal correlations of their recall topic trajectory)?
-This latter approach highlights regions such as the medial prefrontal cortex (mPFC) and medial temporal lobes (MTL) that may respond in idiosyncratic ways across individuals, but that nonetheless play an important role in encoding experience into memory.
-In other work, the mPFC has been suggested to play a role in the representation of a ``schema'', or a network of prior knowledge that is consistent with the current task ~\citep{KestEtal12, GilbMarl17}.
-One interpretation for mPFC's involvement in our work is that mPFC represents participant-specific relationships with the content of the video, and its representation during scene viewing is related to how a participant later describes the scene.
-MTL activity patterns also matched participant's recall, which is consistent with a large body of literature highlighting the role of the MTL in episodic memory encoding ~\citep{PallWagn02, DavaEtAl03, RangEtal04, Dava06}.
-
-More broadly, these findings have strong implications for how we assess memory in other naturalistic contexts, such as the classroom or in a doctor's office.
-Whereas academic tests often measure students' performance using metrics such as the proportion of correctly answered questions, our work suggests that this approach might ``miss the forrest for the trees''.
-We view ``true learning'' as understanding key concepts (i.e., understanding central themes in the learned content and how they relate) rather than regurgitating the greatest number of facts.
-In addition to educational contexts, our approach may provide unique metrics that can be used to assist in the diagnosis of memory disorders, and other psychiatric disorders that influence memory.
-For example, while the quantity of information recalled could be roughly matched between a healthy and patient population, and other aspects of the memory (such as the shape, serial order, precision or distinctiveness) might be different.
-Thus, this work serves as a foundation for more nuanced approaches to memory assessment that consider the trajectory and specific contents of memory for a naturalistic experience.
-
-An important question for future work concerns the factors that drive an individual to sample their recall trajectory finely or coarsely.
-For example, given a short recall interval, would participants intuitively gravitate towards coarser samplings that still outline the basic shape of the video's topic trajectory?
-Or if participants were told that their narrations would be played back to other participants ~\citep{ZadbEtal17}, would that change the resolution or shape of their recalls?
-And over successive recountings of the same sequence of events or with more elapsed time between encoding and recall, how do the shapes of the trajectories change?
-For example, loss of detail would result in a "smoothing out" of the trajectories with each new retelling.
-
-While we view this work as a major advance in characterizing and understanding human memory, as with any approach there are limitations.
-First, the approach relies on having a ``good'' model of the stimulus (e.g., one that describes the video in the same way as participants recall it), which is currently only achievable by a human hand-annotating each moment of the video.
-To increase the scalability of this approach, future work could explore automated methods for extracting meaning from videos ~\citep{YuEtal16}.
-Another potential limitation is that by its nature, the model extracts the ``gist'' of scenes from the video.
-This provides desirable flexibility (e.g., participants can use different combinations of words to describe the scenes), but this comes at the expense of capturing specific details.
-Thus, a future direction of this work will be to increase sensitivity to such details while maintaining flexibility.
-
-To conclude, we'll revisit the question of what it means to remember something.
-Our view is that ``successful remembering'' is about recovering the ``trajectory'' of an experience, rather than the ability to recognize/recall any of its particular isolated details.
-Decades of research suggest that episodic memories are not veridical and context-free snapshots of the past, and so treating (and modelling) them as such is overly simplistic at best (and counterproductive at worst).
-While it's undeniable that these models have been useful in advancing our understanding of human memory, they are severely limited in their ability to explain memory for real life experiences.
-Real life experiences are highly structured in time, and so to have a complete understanding of the human memory system, our experiments and models of memory must not ignore this fact.
-Our work provides a theoretical advance in our understanding of what it means to remember as well as a novel methodological tool to study it.
 

### 2018-09-02 paper/main.tex
draft of discussion complete
working on general cleanup

@@
 The topics we found were heavily character-focused (e.g., the top-weighted word in each topic was nearly always a character) and could be roughly divided into themes that were primarily Sherlock-focused; primarily John-focused (John is Sherlock's close confidant and assistant); or that involved Sherlock and John interacting (Fig.~\topics).
-Several of the topics were highly similar, which we hypothesized might allow us to distinguish between subtle narrative differences (if the distinctions between those overlapping topics were meaningful).
+Several of the topics were highly similar, which we hypothesized might allow us to distinguish between subtle narrative differences (if the distinctions between those overlapping topics were meaningful; also see Fig.~\featureimportance).
 The topic vectors for each timepoint were \textit{sparse}, in that only a small number (usually one or two) topics tended to be ``active'' in any given timepoint (Fig.~\ref{fig:model}A).
@@
 By contrast, in our present work we used topic models and HMMs to construct an explicit stimulus model (i.e., the topic trajectory of the movie).
-When we searched for brain structures whose responses are consistent with the video's topic trajectory, we identified a network of structures that overlaped strongly with the ``long temporal receptive window'' network reported by the Hasson group~\citep[e.g., compare our Fig.~\ref{fig:brainz}A with the map of long temporal receptive window voxels in ][]{LernEtal11}.
+When we searched for brain structures whose responses are consistent with the video's topic trajectory, we identified a network of structures that overlaped strongly with the ``long temporal receptive window'' network reported by the Hasson group~\citep[e.g., compare our Fig.~\ref{fig:brainz}A with the map of long temporal receptive window voxels in][]{LernEtal11}.
 This provides support for the notion that part of the long temporal receptive window network may be maintaining an explicit model of the stimulus dynamics.
@@
 This approach would provide a more nuanced and specific view into which aspects of the material students had learned well (or poorly).
-Similarly, memory evaluations that incorporate explicit content models might provide more direct measures of the qualitiy of patients' memories.
-
-% JRM THOUGHTS ON DISCUSSION:
-% - Nature says "1-2 short paragraphs" -- needs to be much shorter.
-% - I think we can get rid of anything we mention in the intro or results
-% - Things not easily presented elsewhere are the background on the brain results and applications to education metrics.
-I think we can focus on those two parts, add an "overview" and "conclusion" (potentially), and cut the rest.
+In clinical settings, memory measures that incorporate such explicit content models might also provide more direct evaluations patients' memories.
 

### 2018-09-02 paper/main.tex

@@
 \subsection*{Participants and Experimental Design}
-Participants ($n=17$) viewed the first 50 minutes of ``A Study in Pink'', an episode of the BBC series, \textit{Sherlock}.
-Immediately upon completion of the video, participants were instructed to (verbally) recount the events in the \textit{Sherlock} episode in their original order and in as much detail as possible.
-During the entire experiment, participants were in an fMRI scanner.
-For comprehensive details of the experimental procedures, please refer to \cite{ChenEtal17}.
-%NOTE: is this sufficient or should i provide more detail?
+Data were collected by \cite{ChenEtal17}.
+In brief, participants ($n=17$) viewed the first 48 minutes of ``A Study in Pink'', the first episode of the BBC television series \textit{Sherlock}, while fMRI volumes were collected (TR = 1500~ms).
+The stimulus was divided into a 23 minute and a 25 minute segment to facilitate technical issues related to the scanner.
+After finishing the clip, participants were instructed to \citep[quoting from][]{ChenEtal17} ``describe what they recalled of the movie in as much detail as they could, to try to recount events in the original order they were viewed in, and to speak for at least 10 minutes if possible but that longer was better.
+They were told that completeness and detail were more important than temporal order, and that if at any point they realized they had missed something, to return to it.
+Participants were then allowed to speak for as long as they wished, and verbally indicated when they were finished (e.g., `I’m done').''  For additional details about the experimental procedure and scanning parameters see \cite{ChenEtal17}.
 
-\subsection*{Fitting the topic model to the video text and recall transcripts}
-A topic model was used to estimate the most likely mixture of topics for a given sample of text.
-First, the video was manually segmented into 1000 scenes, and a collection of descriptive features was manually transcribed.
-For each scene, we considered the following features: narrative details (a sentence or two describing what happened in that scene), whether the scene was indoor or outdoor, name of all the characters in the scene, name of the character in focus, name of the character speaking, location, camera angle, music presence, and text on the screen.
+\subsection*{Modeling the dynamic content of the video and recall transcripts}
+\subsubsection*{Topic modeling}
+The input to the topic model we trained to characterize the dynamic content of the video comprised hand-generated annotations of each of 1000 scenes spanning the video clip~\citep[generated by][]{ChenEtal17}.
+The features included: narrative details (a sentence or two describing what happened in that scene); whether the scene took place indoors or outdoors; names of any characters that appeared in the scene; name(s) of characters in camera focus; name(s) of characters who were speaking in the scene; the location (in the story) that the scene took place; camera angle (close up, medium, long, top, tracking, over the shoulder, etc.); whether music was playing in the scene or not; and a transcription of any on-screen text.
 We concatenated the text for all of these features within each segment, creating a ``bag of words'' describing each scene.
-We then transformed the text descriptions into overlapping windows of 50 scene segments.
-For example, the first text sample comprised the text from the first 50 segments, the 2nd comprised the text from n+1:n+51, and so on.
-We trained our model using these overlapping text samples with scikit-learn's (version 0.19.1) `CountVectorizer' and `LatentDirichletAllocation' classes \citep{PedrEtal11} implemented using our high-dimensional visualization/analysis software, Hypertools \citep{HeusEtal18}.
-First, the text was transformed into a vector of word counts (after removing English stopwords).
-This gave a word count vector for each scene in the video.
-Then, the word count vectors were used to fit a topic model (topics=100, method=`batch').
-We transformed the text descriptions using the model resulting in a scenes (1000) by topics (100) matrix.
-The scene descriptions often spanned multiple timepoints (i.e., TRs).
-To account for this, we expanded the video model by copying the rows of the model for as many timepoints that the scene description spanned.
-After this expansion, the shape of the model was the length of the duration of the video (1976 TRs).
+We then re-organized the text descriptions into overlapping sliding windows spanning 50 scenes each.
+In other words, the first text sample comprised the combined text from the first 50 scenes (i.e., 1--50), the second comprised the text from scenes 2--51, and so on.
+We trained our model using these overlapping text samples with \texttt{scikit-learn}~\citep[version 0.19.1; ][]{PedrEtal11}, called from our high-dimensional visualization and text analysis software, \texttt{HyperTools}~\citep{HeusEtal18}.
+Specifically, we use the \texttt{CountVectorizor} class to transform the text from each scene into a vector of word counts (using the union of all words across all scenes as the ``vocabulary,'' excluding English stop words); this yields a number-of-scenes by number-of-words \textit{word count} matrix.
+We then use the \texttt{LatentDirichletAllocatin} class (topics=100, method=`batch') to fit a topic model~\citep{BleiEtal03} to the word count matrix, yielding a number-of-scenes (1000) by number-of-topics (100) \textit{topic proportions} matrix.
+The topic proportions matrix describes which mix of topics (latent themes) is present in each scene.
+Next, we transformed the topic proportions matrix to match the 1976 fMRI volume acquisition times.
+For each fMRI volume, we took the topic proportions from whatever scene was displayed for most of that volume's 1500~ms acquisition time.
+This yielded a new number-of-TRs (1976) by number-of-topics (100) topic proportions matrix.
 
-To create the recall models, for each participant we tokenized the recall transcript into a list of sentences and then mapped the list to overlapping windows of 10 sentences.
-We transformed the list of overlapping recall sentences using the model that was trained on the video text (as described in the paragraph above).
-The result of this was a sentences (range: 68-294) by topics (100) matrix for each participant that represented the most likely mixture of topics for a given chunk of sentences.
+We created similar topic proportion matrices using hand-annotated transcripts of each participant's recall of the video~\citep[annotated by ][]{ChenEtal17}.
+We tokenized the transcript into a list of sentences, and then re-organized the list into overlapping sliding windows spanning 10 sentences each; we in turn transformed each window's sentences into a word count vector (using the same vocabulary as for the video model).
+We then used the topic model already trained on the video scenes to compute the most probable topic proportions for each sliding window.
+This yielded a number-of-sentences (range: 68--294) by number-of-topics (100) topic proportions matrix, for each participant.
+These reflected the dynamic content of each participant's recalls.
 
-\subsubsection*{Choosing topic model parameters}
+\paragraph*{Choosing topic model parameters}
+\textbf{JRM NOTE: NEED TO DISCUSS THIS SECTION.  ALSO, I HAVE NOT EDITING THE WORDING.}
 There were 3 critical parameters related to fitting the topic model: 1) the number of topics, 2) the window size of text descriptions of the video used to fit the model, and 3) the window size of recall sentences used to transform the recall data.
@@
 While many of the parameter combination elicited moderately high correlations, the optimal choice was 100 topics, 50 video segments and 10 recall sentences.
-%NOTE: I did run this analysis, but before that i arbitrarily selected some parameters that ended up being very close to the best.
+%ACH NOTE: I did run this analysis, but before that i arbitrarily selected some parameters that ended up being very close to the best.
 The reason I bring this up is that the correlations between some of the memory metrics (k, precision, distinctiveness) and hand annotated accuracy could be biased because we searched for the optimal parameters.
 Its not `the same' measure, but they are related to each other, so we'll have to be extra careful not to over interpret the correlations in this study.
+
+\textbf{JRM STOPPED HERE}
 
@@
 
-\subsection*{fMRI analyses}
-Participants viewed and recalled the video stimulus inside an fMRI scanner.
-The video was split into two parts of approximately equal length (946 and 1030 TRs, $TR=1.5 seconds$).
-All data were preprocessed and transformed to 3mm MNI space as described in ~\citep{ChenEtal17}.
-Data were z-scored across time at every voxel.
-6mm smoothing was applied.
-Files are cropped so that all video-viewing data are aligned across participants, and all recall data are aligned to the scene timestamps below.
-The cropping includes a constant 3-TR (4.5 sec) shift to correct for hemodynamic lag.
-
-\subsubsection*{Searchlight analysis}
-Our multivariate analyses were designed to capture brain regions whose timepoint-by-timepoint correlational structure mirrors the correlational structure of the video model as well as participant-specific recall topic models during video viewing.
-We conducted a searchlight analysis (5x5x5 voxel cube) where for each cube, we correlated the model timepoint-by-timepoint correlation matrix with the neural correlation matrix.
-To aggregate across participants, we Fisher's z-transformed the correlations and then averaged.
-To assess significance, we recomputed this group analysis 100 times, but randomly phase shifted the model by the same amount for each participant but different amounts for each permutation to build a null distribution of correlation values.
-Finally, we thresholded the group averaged correlation maps where the `real' correlation value for a given voxel exceeded the 95th percentile of the null distribution.
-To correct for non-linearities between the viewing time and recall time, for each participant we used dynamic time warping to temporally align the matrices.
-The algorithm recovers a path of coordinates that would bring the video and recall model in maximal temporal alignment.
-We used this path to warp the fMRI data and the recall model into temporal alignment (separately for each participant).
-
 \subsubsection*{Topic vector word clouds}
@@
 
+\subsection*{fMRI analyses}
+Participants viewed and recalled the video stimulus inside an fMRI scanner.
+The video was split into two parts of approximately equal length (946 and 1030 TRs, $TR=1.5 seconds$).
+All data were preprocessed and transformed to 3mm MNI space as described in ~\citep{ChenEtal17}.
+Data were z-scored across time at every voxel.
+6mm smoothing was applied.
+Files are cropped so that all video-viewing data are aligned across participants, and all recall data are aligned to the scene timestamps below.
+The cropping includes a constant 3-TR (4.5 sec) shift to correct for hemodynamic lag.
+
+\subsubsection*{Searchlight analysis}
+Our multivariate analyses were designed to capture brain regions whose timepoint-by-timepoint correlational structure mirrors the correlational structure of the video model as well as participant-specific recall topic models during video viewing.
+We conducted a searchlight analysis (5x5x5 voxel cube) where for each cube, we correlated the model timepoint-by-timepoint correlation matrix with the neural correlation matrix.
+To aggregate across participants, we Fisher's z-transformed the correlations and then averaged.
+To assess significance, we recomputed this group analysis 100 times, but randomly phase shifted the model by the same amount for each participant but different amounts for each permutation to build a null distribution of correlation values.
+Finally, we thresholded the group averaged correlation maps where the `real' correlation value for a given voxel exceeded the 95th percentile of the null distribution.
+To correct for non-linearities between the viewing time and recall time, for each participant we used dynamic time warping to temporally align the matrices.
+The algorithm recovers a path of coordinates that would bring the video and recall model in maximal temporal alignment.
+We used this path to warp the fMRI data and the recall model into temporal alignment (separately for each participant).
+
 \bibliography{memlab}

### 2018-09-03 paper/main.tex
checking in changes after edits to wordles figure and associated text

@@
 Because our analysis framework projects the dynamic video content and participants' recalls onto a shared topic space, and because the dimensions of that space are known (i.e., each topic dimension is a set of weights over words in the vocabulary; Fig.~\topics), we can examine the topic trajectories to understand which specific content was remembered well (or poorly).
-For each video event, we can ask: for all participants who recalled that event, what was the average correlation (across participants) between the video event's topic vector and the recall event topic vectors from each participant?
+For each video event, we can ask: what was the average correlation (across participants) between the video event's topic vector and the closest matching recall event topic vectors from each participant?
 This yields a single correlation coefficient for each video event, describing how closely participants' recalls of the event tended to reliably capture its content (Fig.~\ref{fig:topics}A).
@@
 Several example wordles are displayed in Figure~\ref{fig:topics}C (wordles from the three best-remembered events are circled in green; wordles from the three worst-remembered events are circled in red).
-\textbf{[JRM NOTE: NEED SOME SORT OF ``POINT'' OR TAKE-AWAY FROM THIS ANALYSIS]}
+Using wordles to visually compare the topical content of each video event and the (average) corresponding recall event reveals the specific content from the specific events that is reliably retained in the transformation into memory (green events) or not (red events).
 
@@
 \textbf{C.}  The set of all video and recall events is projected onto the two-dimensional space derived in Figure~\ref{fig:trajectory}.
-The large dots denote video events and the smaller dots denote recalled events (same color scheme as Fig.~\ref{fig:trajectory}A).
+The dots outlined in black denote video events (dot size reflects the average correlation between the video event's topic vector and the topic vectors from the closest matching recalled events from each participant; bigger dots denote stronger correlations).
+The dots without black outlines denote recalled events.
+All dots are colored using the same scheme as Figure~\ref{fig:trajectory}A.
 Wordles for several example events are displayed (green: three best-remembered events; red: three worst-remembered events).

### 2018-09-03 paper/main.tex
backup up progress (working on Methods, minor edits to results, added Quail reference).  all JRM NOTE issues have now been addressed, modulo existing github issues related to figure images

@@
 \newcommand{\listlearning}{S5}
+\newcommand{\topicopt}{S6}
 
@@
 In list-learning studies, this set of three analyses may be used to gain a nearly complete view into the sequences of recalls participants made~\citep[e.g., ][]{Kaha12}.
-However, in naturalistic recall the analyses provide a wholly incomplete picture: they leave out any attempt to quantify participants' abilities to capture the \textit{content} of what occurred in the video (i.e., their only experimental instruction!).
+Extending these analyses to apply to naturalistic stimuli and recall~\citep{HeusEtal17b} highlights that, in naturalistic recall, these analyses provide a wholly incomplete picture: they leave out any attempt to quantify participants' abilities to capture the \textit{content} of what occurred in the video (i.e., their only experimental instruction!).
 
@@
 These reflected the dynamic content of each participant's recalls.
-
-\paragraph*{Choosing topic model parameters}
-\textbf{JRM NOTE: NEED TO DISCUSS THIS SECTION.  ALSO, I HAVE NOT EDITING THE WORDING.}
-There were 3 critical parameters related to fitting the topic model: 1) the number of topics, 2) the window size of text descriptions of the video used to fit the model, and 3) the window size of recall sentences used to transform the recall data.
-To chose these parameter values, we performed a grid search where the range of possible parameter values was 1, 5, 10, 25, 50, 100, 200, and 500.
-Our optimization objective was defined as the correlation between the hand annotated memory performance and the root mean squared distance between the video model and the recall model before any further processing (e.g., hidden Markov modeling, averaging within event, etc).
-While many of the parameter combination elicited moderately high correlations, the optimal choice was 100 topics, 50 video segments and 10 recall sentences.
-%ACH NOTE: I did run this analysis, but before that i arbitrarily selected some parameters that ended up being very close to the best.
-The reason I bring this up is that the correlations between some of the memory metrics (k, precision, distinctiveness) and hand annotated accuracy could be biased because we searched for the optimal parameters.
-Its not `the same' measure, but they are related to each other, so we'll have to be extra careful not to over interpret the correlations in this study.
+Note: for details on how we selected the video and recall window lengths and number of topics, see \textit{Supplemental Materials} and Figure~\topicopt.
 

### 2018-09-03 paper/main.tex
working on methods [WIP]

@@
 
-\textbf{JRM STOPPED HERE}
+\subsubsection*{Parsing topic trajectories into events using Hidden Markov Models}
 
-\subsubsection*{Extracting events using a hidden Markov model}
+\textbf{JRM STOPPED HERE...MISSING INFO}
+% don't need background or "logic"
+% what was the actual optimization metric used?  e.g. what was the penalty parameter?  we should write out the optimization as an "argmax" equation...but need info from ACH about the penalty term
+
 The topic model timepoint-by-timepoint correlation matrices all exhibited a block-diagonal structure (with small off-diagonal values), suggesting that the models were comprised of a number of sequential `states' (or events, see Fig.~\corrmats).

### 2018-09-03 paper/main.tex
backing up work for the night (methods, WIP)
updated schematic figure with new version from andy
updated figs, still working on methods

@@
 \centering
-\includegraphics[width=1\textwidth]{figs/analysis_schematic_bw}
+\includegraphics[width=1\textwidth]{figs/schematic}
 \caption{\small \textbf{Methods overview.} We used hand-annotated descriptions of each moment of video to fit a topic model.
 Three example video frames, and their associated descriptions are displayed (top two rows).
-Participants later recalled the video (in the third row, we show example recalls of the same three scenes from one participant).
+Participants later recalled the video (in the third row, we show example recalls of the same three scenes from participant 13).
 We used the topic model (fit to the annotations) to estimate topic vectors for each moment of video and each sentence the participants recalled.
@@
 Three topic dimensions are shown (the highest-weighted topics for each of the three example scenes, respectively).
-We also show the 5 highest-weighted words for each topic.
+We also show the ten highest-weighted words for each topic.
 Figure~\topics~provides a full list of the top 10 words from each of the discovered topics.}
@@
 
-The topics we found were heavily character-focused (e.g., the top-weighted word in each topic was nearly always a character) and could be roughly divided into themes that were primarily Sherlock-focused; primarily John-focused (John is Sherlock's close confidant and assistant); or that involved Sherlock and John interacting (Fig.~\topics).
+The topics we found were heavily character-focused (e.g., the top-weighted word in each topic was nearly always a character) and could be roughly divided into themes that were primarily Sherlock Holmes-focused (Sherlock is the titular character); primarily John Watson-focused (John is Sherlock's close confidant and assistant); or that involved Sherlock and John interacting (Fig.~\topics).
 Several of the topics were highly similar, which we hypothesized might allow us to distinguish between subtle narrative differences (if the distinctions between those overlapping topics were meaningful; also see Fig.~\featureimportance).
@@
 % what was the actual optimization metric used?  e.g. what was the penalty parameter?  we should write out the optimization as an "argmax" equation...but need info from ACH about the penalty term
+% from slack: "for the video model its 250 and for the recall models its 50, and atm i cant recall why we chose those particular numbers."  also "well, for both numbers its 5x the window size"
 

### 2018-09-03 paper/boneyard.tex
added paxton's changes to schematic, backing up methods progress

@@
+%METHODS
+
+\subsubsection*{Matching recall events to video events}
+
+To estimate which video event each recall event referred to, we correlated the video events model and each recall events model.
+This resulted in a video events (34) by recall events (8-27) correlation matrix (for each participant) which contains the similarity between each video event and each recall event (see Fig.~\matchmats).
+To find the most likely video event that a given recall event referred to, we computed the argmax over the columns of this matrix.
+The result was a list of video event indices for each participant.
+These indices are analogous to the values found in a ``recall matrix'' from a free recall list learning experiment, but represent the recall of particular events (instead of words, for example).
+
+%%%%%
+
 % DISCUSSION
+
+% JRM THOUGHTS ON DISCUSSION:
+% - Nature says "1-2 short paragraphs" -- needs to be much shorter.
+% - I think we can get rid of anything we mention in the intro or results
+% - Things not easily presented elsewhere are the background on the brain results and applications to education metrics.
+I think we can focus on those two parts, add an "overview" and "conclusion" (potentially), and cut the rest.
+
 Prior work on neural responses during naturalistic experiences and recall has largely focused on identifying brain regions whose responses are reliably similar across individuals ~\citep{LernEtal11, SimoEtal16, ChenEtal17, BaldEtal17, ZadbEtal17}.

### 2018-09-03 paper/main.tex
added paxton's changes to schematic, backing up methods progress

@@
 \usepackage{setspace}
-%\doublespacing
+
+\newcommand{\argmax}{\mathop{\mathrm{argmax}}\limits}
 
@@
 \newcommand{\topicopt}{S6}
+
+%\doublespacing
 
@@
 \subsubsection*{Parsing topic trajectories into events using Hidden Markov Models}
+We parsed the topic trajectories of the video and participants' recalls into events using Hidden Markov Models~\citep{Rabi89}.
+Given the topic portions matrix (describing the mix of topics at each timepoint) and a number of states, $K$, an HMM recovers the set of state transitions that segments the timeseries into $K$ discrete states.
+Following \cite{BaldEtal17}, we imposed an additional set of constraints on the discovered state transitions that ensured that each state was encountered exactly once (i.e., never repeated).
+We used the BrainIAK toolbox~\citep{Brainiak} to implement this segmentation.
 
-\textbf{JRM STOPPED HERE...MISSING INFO}
-% don't need background or "logic"
-% what was the actual optimization metric used?  e.g. what was the penalty parameter?  we should write out the optimization as an "argmax" equation...but need info from ACH about the penalty term
-% from slack: "for the video model its 250 and for the recall models its 50, and atm i cant recall why we chose those particular numbers."  also "well, for both numbers its 5x the window size"
+We used an optimization procedure to select the appropriate $K$ for each topic proportions matrix.  Specifically, we computed (for each matrix)
+\[
+  \argmax_K \left[\frac{a}{b} - \frac{K}{\alpha}\right],
+\]
+where $a$ was the average correlation between the topic vectors of timepoints within the same state; $b$ was the average correlation between the topic vectors of timepoints within \textit{different} states; and $\alpha$ was a regularization parameter that we set to 5 times the windowlength (i.e., 250 scenes for the video topic trajectory and 50 sentences for the recall topic trajectories).
+Figure~\ref{fig:model}B displays the event boundaries returned for the video, and Figure~\corrmats displays the event boundaries returned for each participant's recalls.
+After obtaining these event boundaries, we created stable estimates of each topic proportions matrix by averaging the topic vectors within each event.
+This yielded a number-of-events by number-of-topics matrix for the video and recalls from each participant.
 
-The topic model timepoint-by-timepoint correlation matrices all exhibited a block-diagonal structure (with small off-diagonal values), suggesting that the models were comprised of a number of sequential `states' (or events, see Fig.~\corrmats).
-To capture this structure, we fit the video and each recall model using a hidden Markov model (HMM).
-Given a number of states or events ($k$), the HMM recovers a set of labels that segments consecutive timepoints into $k$ events ~\citep{Rabi89, BaldEtal17}.
-To implement this analysis, we used the BrainIAK toolbox \citep{BaldEtal17, Brainiak}.
+\subsubsection*{Visualizing the video and recall topic trajectories}
+We used the UMAP algorithm~\citep{McInHeal18} to project the 100-dimensional topic space onto a two-dimensional space for visualization (Figs.~\ref{fig:trajectory}, \ref{fig:topics}).
+To ensure that all of the trajectories were projected onto the \textit{same} lower dimensional space, we computed the low-dimensional embedding on a ``stacked'' matrix created by vertically concatenating the events-by-topics topic proportions matrices for the video and all 17 participants' recalls.
+We then divided the rows of the result (a total-number-of-events by two matrix) back into separate matrices for the video topic trajectory and the trajectories for each participant's recalls (Fig.~\ref{fig:trajectory}).
+This general approach for discovering a shared low-dimensional embedding for a collections of high-dimensional observations follows \cite{HeusEtal18}.
 
-Our metric for choosing the ``best fitting'' HMM was to choose the model with the $k$ value that maximized the ratio of the average `within-event' correlation values (i.e., the correlation values for blocks of consecutive timepoints the model identified as one event) and the average `across-event' correlation (i.e., the rest of the correlation values).
-Additionally, we included a penalty parameter that was proportional to the smoothing of the model that preferred models with smaller $k$ values.
-We chose $k$ values separately for the video model and for each recall model.
-Then, using the best $k$ values, We fit a separate HMM for the video and each recall model.
-Finally, we averaged over timepoints identified to be in the same event resulting in a events by topics matrix for the video model and each of the recall models.
+\subsubsection*{Estimating the consistency of flow through topic space across participants}
+In Figure~\ref{fig:trajectory}B, we present an analysis aimed at characterizing locations in topic space for which we can predict that
 
-\subsubsection*{Matching recall events to video events}
-To estimate which video event each recall event referred to, we correlated the video events model and each recall events model.
-This resulted in a video events (34) by recall events (8-27) correlation matrix (for each participant) which contains the similarity between each video event and each recall event (see Fig.~\matchmats).
-To find the most likely video event that a given recall event referred to, we computed the argmax over the columns of this matrix.
-The result was a list of video event indices for each participant.
-These indices are analogous to the values found in a ``recall matrix'' from a free recall list learning experiment, but represent the recall of particular events (instead of words, for example).
-
-\subsubsection*{Visualizing the video and recall event models}
-To visualize the temporal structure of the video event model (34 events by 100 topics) and the recall event models (8-27 events by 100 topics), we used a technique called UMAP ~\citep{McInHeal18} to reduce the ``topic-space'' from 100 dimensions down to 2 dimensions.
-UMAP is a nonlinear dimensionality reduction technique which models the manifold of the data with a fuzzy topological structure, and then searches for a (2D) projection of the data that has the closest equivalent fuzzy topological structure.
-We concatenated (vertically stacked) all event models (video, average recall, and individual recall), and then fit and transformed all of the models at once.
-This assured that the models were projected into the same space.
-
-\subsubsection*{Vector field analysis}
 To quantify the flow of recall from event to event, we performed a vector field analysis.

### 2018-09-03 paper/main.tex
paxton noticed more stuff, thereby solidifying his position as real-world sherlock holmes

@@
 \subsubsection*{Estimating the consistency of flow through topic space across participants}
-In Figure~\ref{fig:trajectory}B, we present an analysis aimed at characterizing locations in topic space for which we can predict that
+In Figure~\ref{fig:trajectory}B, we present an analysis aimed at characterizing locations in topic space that different participants move through in a consistent way (via their recall topic trajectories).
+The two-dimensional topic space used in our visualizations (Fig.~\ref{fig:trajectory}) ranged from -6 to 6 (arbitrary) units, in both the $x$ and $y$ dimensions.
+We divided this space into a grid of vertices spaced 0.25~units apart.
+For each square, we examined the set of line segments formed by connecting each pair successively recalled events, across all participants, that passed within 0.5 units of its center.
 

### 2018-09-03 paper/boneyard.tex
done with full draft!  now need to proofread...

@@
 
+%Already say these in text:
 \subsubsection*{Matching recall events to video events}
@@
 These indices are analogous to the values found in a ``recall matrix'' from a free recall list learning experiment, but represent the recall of particular events (instead of words, for example).
+
+\subsubsection*{Topic vector word clouds}
+We created word clouds to visualize the themes contained in the recall events.
+One component of the topic model comprises a words (2117) by topics (100) matrix (R), where the rows represent the weight of a given word in each topic.
+To find words that were maximally associated with a particular event vector, we computed the dot product between R and v, which gave a 1 by \# of words vector where the values represent the ``activation'' of each of in the event.
+Activation is defined as the weight of a particular word in a particular event.
+Then, we created word clouds by extracting the top $n$ words and plotting them where the size of the word is proportional to its activation in the event.
+
+In the first analysis (Fig.~\ref{fig:topics}A,B), we quantified the most and least remembered topics/words throughout the entire video by computing a weighted average over all recall events, where the weights were proportional to memory for each recall event.
+To measure memory for each event, for each participant we computed the correlation between the video event vector and the closest recall event vector.
+We then averaged these correlation values across participants.
+We then computed a weighted average of all video events using the correlation values as weights.
+Next, we computed the dot product between this weighted-average video event vector and the R matrix (described in the paragraph above) to get activations for each word.
+Finally, we plotted the top 200 words where the size of the word is proportional to its activation.
+To get the least remembered topics/words, we performed the same analysis but inverted memory weights.
+
+In the second analysis (Fig.~\ref{fig:topics}C), we created wordles for the top/bottom 3 remembered video events indexed by the average correlation values (Fig.~\ref{fig:topics}A).
+To get the ``activations'' for words associated with the video events, we computed the dot product between the video event vector and the R matrix.
+The same procedure was used to get word activations for the recall events.
+We then plotted the top 200 words for the top/bottom 3 recalled events.
 

### 2018-09-03 paper/main.tex
done with full draft!  now need to proofread...

@@
 Differences in the numbers of remembered events appear in participants' trajectories as differences in the sampling resolution along the trajectory.
-We note that this framework also provides a means of detangling classic ``proportion recalled'' measures (i.e., the proportion of video events referenced in participants' recalls) from participants' abilities to recaputulate the full gist of the original video (i.e., the similarity in the shape of the original video trajectory and that defined by each participant's reocounting of the video).
+We note that this framework also provides a means of detangling classic ``proportion recalled'' measures (i.e., the proportion of video events referenced in participants' recalls) from participants' abilities to recapitulate the full gist of the original video (i.e., the similarity in the shape of the original video trajectory and that defined by each participant's recounting of the video).
 
@@
 By contrast, in our present work we used topic models and HMMs to construct an explicit stimulus model (i.e., the topic trajectory of the movie).
-When we searched for brain structures whose responses are consistent with the video's topic trajectory, we identified a network of structures that overlaped strongly with the ``long temporal receptive window'' network reported by the Hasson group~\citep[e.g., compare our Fig.~\ref{fig:brainz}A with the map of long temporal receptive window voxels in][]{LernEtal11}.
+When we searched for brain structures whose responses are consistent with the video's topic trajectory, we identified a network of structures that overlapped strongly with the ``long temporal receptive window'' network reported by the Hasson group~\citep[e.g., compare our Fig.~\ref{fig:brainz}A with the map of long temporal receptive window voxels in][]{LernEtal11}.
 This provides support for the notion that part of the long temporal receptive window network may be maintaining an explicit model of the stimulus dynamics.
@@
 The role of the MTL in episodic memory encoding has been well-reported~\citep[e.g., ][]{PallWagn02, DavaEtAl03, RangEtal04, Dava06}.
-Prior work has also implicated the medial prefrontal cortex in representing ``schema'' knowledge~\citep[i.e., general knowledge about the format of an ongoing experience given prior similar experiencs; ][]{KestEtal12, GilbMarl17}.
+Prior work has also implicated the medial prefrontal cortex in representing ``schema'' knowledge~\citep[i.e., general knowledge about the format of an ongoing experience given prior similar experiences; ][]{KestEtal12, GilbMarl17}.
 Integrating across our study and this prior work, one interpretation is that the person-specific transformations mediated (or represented) by the rMTL and vmPFC may reflect schema knowledge being leveraged, formed, or updated, incorporating ongoing experience into previously acquired knowledge.
@@
 For example, the most commonly used classroom evaluation tools involve computing the proportion of correctly answered exam questions.
-Our work indicates that this approach is only loosly related to what educators might really want to measure: how well did the students understand the key ideas presented in the course?
+Our work indicates that this approach is only loosely related to what educators might really want to measure: how well did the students understand the key ideas presented in the course?
 One could apply the computational framework we developed to construct topic trajectories for the video and participants' recalls to build explicit content models of the course material and exam questions.
@@
 
-\subsection*{Participants and Experimental Design}
+\subsection*{Experimental design and data collection}
 Data were collected by \cite{ChenEtal17}.
 In brief, participants ($n=17$) viewed the first 48 minutes of ``A Study in Pink'', the first episode of the BBC television series \textit{Sherlock}, while fMRI volumes were collected (TR = 1500~ms).
-The stimulus was divided into a 23 minute and a 25 minute segment to facilitate technical issues related to the scanner.
+The stimulus was divided into a 23 minute (946~TR) and a 25~min (1030~TR) segment to facilitate technical issues related to the scanner.
 After finishing the clip, participants were instructed to \citep[quoting from][]{ChenEtal17} ``describe what they recalled of the movie in as much detail as they could, to try to recount events in the original order they were viewed in, and to speak for at least 10 minutes if possible but that longer was better.
@@
 Participants were then allowed to speak for as long as they wished, and verbally indicated when they were finished (e.g., `I’m done').''  For additional details about the experimental procedure and scanning parameters see \cite{ChenEtal17}.
+
+After preprocessing the fMRI data and warping the images into a standard (3~mm$^3$ MNI) space, the voxel activations were $z$-scored (within voxel) and spatially smoothed using a 6~mm (full width at half maximum) Gaussian kernel.
+The fMRI data were also cropped so that all video-viewing data were aligned across partipants.
+This included a constant 3 TR (4.5~s) shift to account for the lag in the hemodynamic response.
+\citep[All of these preprocessing steps followed][where additional details may be found.]{ChenEtal17}
 
@@
 We trained our model using these overlapping text samples with \texttt{scikit-learn}~\citep[version 0.19.1; ][]{PedrEtal11}, called from our high-dimensional visualization and text analysis software, \texttt{HyperTools}~\citep{HeusEtal18}.
-Specifically, we use the \texttt{CountVectorizor} class to transform the text from each scene into a vector of word counts (using the union of all words across all scenes as the ``vocabulary,'' excluding English stop words); this yields a number-of-scenes by number-of-words \textit{word count} matrix.
-We then use the \texttt{LatentDirichletAllocatin} class (topics=100, method=`batch') to fit a topic model~\citep{BleiEtal03} to the word count matrix, yielding a number-of-scenes (1000) by number-of-topics (100) \textit{topic proportions} matrix.
+Specifically, we use the \texttt{CountVectorizer} class to transform the text from each scene into a vector of word counts (using the union of all words across all scenes as the ``vocabulary,'' excluding English stop words); this yields a number-of-scenes by number-of-words \textit{word count} matrix.
+We then use the \texttt{LatentDirichletAllocation} class (topics=100, method=`batch') to fit a topic model~\citep{BleiEtal03} to the word count matrix, yielding a number-of-scenes (1000) by number-of-topics (100) \textit{topic proportions} matrix.
 The topic proportions matrix describes which mix of topics (latent themes) is present in each scene.
@@
 \]
-where $a$ was the average correlation between the topic vectors of timepoints within the same state; $b$ was the average correlation between the topic vectors of timepoints within \textit{different} states; and $\alpha$ was a regularization parameter that we set to 5 times the windowlength (i.e., 250 scenes for the video topic trajectory and 50 sentences for the recall topic trajectories).
+where $a$ was the average correlation between the topic vectors of timepoints within the same state; $b$ was the average correlation between the topic vectors of timepoints within \textit{different} states; and $\alpha$ was a regularization parameter that we set to 5 times the window length (i.e., 250 scenes for the video topic trajectory and 50 sentences for the recall topic trajectories).
 Figure~\ref{fig:model}B displays the event boundaries returned for the video, and Figure~\corrmats displays the event boundaries returned for each participant's recalls.
@@
 We divided this space into a grid of vertices spaced 0.25~units apart.
-For each square, we examined the set of line segments formed by connecting each pair successively recalled events, across all participants, that passed within 0.5 units of its center.
+For each vertex, we examined the set of line segments formed by connecting each pair successively recalled events, across all participants, that passed within 0.5 units.
+We computed the distribution of angles formed by those segments and the $x$-axis, and used a Rayleigh test to determine whether the distribution of angles was reliably ``peaked'' (i.e.
+consistent across all transitions that passed through that local portion of topic space).
+To create Figure~\ref{fig:trajectory}B we drew an arrow originating from each grid vertex, pointing in the direction of the average angle formed by line segments that passed within 0.5 units.
+We set the arrow lengths proportional to the $p$-values of the Rayleigh tests at each vertex.
+We also indicated any significant results ($p < 0.05$, corrected using the Benjamani-Hochberg procedure) by coloring the arrows in blue (darker blue denotes a lower $p$-value); all tests with $p \geq 0.05$ are displayed in gray and given a lower opacity value.
 
-To quantify the flow of recall from event to event, we performed a vector field analysis.
-We tiled the 2D topic space (x, y: -6 to 6 by .25) with an evenly spaced grid.
-For each grid point, we drew a circle around the point (radius= 0.5).
-Then, we tested whether any line segments (formed by event recall transitions) passed through this area of the topic space.
-For example, say that a participant transitioned from recalling event 2 to event 3.
-These 2 recall events correspond to 2 points in topic space, and connecting them forms a line segment.
-We collected all line segments that passed through a given section of topic space (collapsing across participants).
-To plot the average direction of the line segments (i.e., the arrows for each grid point in Fig.~\ref{fig:trajectory}B), we converted each of them to unit vectors and then averaged.
-For grid points where the direction was consistent (across all participants contributing to that point), the length of the arrow approaches 1, whereas if the direction was random the length of the arrow approaches 0.
-Lastly, we converted each unit vector to an angle (in radians) by taking the inverse tangent of the x, y components of the vector.
-To test whether the distribution of angles was significantly non-uniform (i.e., displayed a preferred direction across participants), we performed a Rayleigh test on the angles ($p < 0.001$, FDR-corrected at $p < 0.05$ using Benjamani-Hochberg procedure).
-Arrows where the Rayleigh test was significant are displayed in color (the darker the blue the more significant) while non-significant tests are displayed in gray with lower opacity.
+\subsection*{Searchlight fMRI analyses}
+In Figure~\ref{fig:brainz}, we present two analyses aimed at identifying brain structures whose responses (as participants viewed the video) exhibited particular temporal correlations.
+We developed a searchlight analysis whereby we constructed a 5~mm$^3$ cube centered on each voxel.
+For each of these cubes, we computed the temporal correlation matrix of the voxel responses during movie viewing.
+Specifically, for each of the 1976 volumes collected during movie viewing, we correlated the activity patterns in the given cube with the activity patterns (in the same cube) collected during every other timepoint.
+This yielded a 1976 by 1976 correlation matrix for each cube.
 
-\subsubsection*{Topic vector word clouds}
-We created word clouds to visualize the themes contained in the recall events.
-One component of the topic model comprises a words (2117) by topics (100) matrix (R), where the rows represent the weight of a given word in each topic.
-To find words that were maximally associated with a particular event vector, we computed the dot product between R and v, which gave a 1 by \# of words vector where the values represent the ``activation'' of each of in the event.
-Activation is defined as the weight of a particular word in a particular event.
-Then, we created word clouds by extracting the top $n$ words and plotting them where the size of the word is proportional to its activation in the event.
+Next, we constructed two sets of ``template'' matrices; one reflected the video's topic trajectory and the other reflected each participant's recall topic trajectory.
+To construct the video template, we computed the correlations between the topic proportions estimated for every pair of TRs (prior to segmenting the trajectory into discrete events; i.e., the correlation matrix shown in Figs.~\ref{fig:model}B and \ref{fig:brainz}A).
+We constructed similar temporal correlation matrices for each participant's recall topic trajectory (Figs.~\ref{fig:model}D, \corrmats).
+However, to correct for length differences and non-linear transformation between viewing time and recall time, we first used dynamic time warping~\citep{BernClif94} to temporally align participants' recall topic trajectories with the video topic trajectory (an example correlation matrix before and after warping is shown in Fig.~\ref{fig:brainz}B).
+This yielded a 1976 by 1976 correlation matrix for the video template and for each participant's recall template.
 
-In the first analysis (Fig.~\ref{fig:topics}A,B), we quantified the most and least remembered topics/words throughout the entire video by computing a weighted average over all recall events, where the weights were proportional to memory for each recall event.
-To measure memory for each event, for each participant we computed the correlation between the video event vector and the closest recall event vector.
-We then averaged these correlation values across participants.
-We then computed a weighted average of all video events using the correlation values as weights.
-Next, we computed the dot product between this weighted-average video event vector and the R matrix (described in the paragraph above) to get activations for each word.
-Finally, we plotted the top 200 words where the size of the word is proportional to its activation.
-To get the least remembered topics/words, we performed the same analysis but inverted memory weights.
+To determine which (cubes of) voxel responses reliably matched the video template, we correlated the upper triangle of the voxel correlation matrix for each cube with the upper triangle of the video template matrix~\citep{KrieEtal08b}.
+This yielded, for each participant, a single correlation value.
+We computed the average (Fisher $z$-transformed) correlation coefficient across participants.
+We used a permutation-based procedure to assess significance, whereby we re-computed the average correlations for each of 100 ``null'' video templates (constructed by circularly shifting the template by a random number of timepoints).
+(For each permutation, the same shift was used for all participants.)  We then estimated a $p$-value by computing the proportion of shifted correlations that were larger than the observed (unshifted) correlation.
+To create the map in Figure~\ref{fig:brainz}A we thresholded out any voxels whose correlation values fell below the 95\textsuperscript{th} percentile of the permutation-derived null distribution.
 
-In the second analysis (Fig.~\ref{fig:topics}C), we created wordles for the top/bottom 3 remembered video events indexed by the average correlation values (Fig.~\ref{fig:topics}A).
-To get the ``activations'' for words associated with the video events, we computed the dot product between the video event vector and the R matrix.
-The same procedure was used to get word activations for the recall events.
-We then plotted the top 200 words for the top/bottom 3 recalled events.
-
-\subsection*{fMRI analyses}
-Participants viewed and recalled the video stimulus inside an fMRI scanner.
-The video was split into two parts of approximately equal length (946 and 1030 TRs, $TR=1.5 seconds$).
-All data were preprocessed and transformed to 3mm MNI space as described in ~\citep{ChenEtal17}.
-Data were z-scored across time at every voxel.
-6mm smoothing was applied.
-Files are cropped so that all video-viewing data are aligned across participants, and all recall data are aligned to the scene timestamps below.
-The cropping includes a constant 3-TR (4.5 sec) shift to correct for hemodynamic lag.
-
-\subsubsection*{Searchlight analysis}
-Our multivariate analyses were designed to capture brain regions whose timepoint-by-timepoint correlational structure mirrors the correlational structure of the video model as well as participant-specific recall topic models during video viewing.
-We conducted a searchlight analysis (5x5x5 voxel cube) where for each cube, we correlated the model timepoint-by-timepoint correlation matrix with the neural correlation matrix.
-To aggregate across participants, we Fisher's z-transformed the correlations and then averaged.
-To assess significance, we recomputed this group analysis 100 times, but randomly phase shifted the model by the same amount for each participant but different amounts for each permutation to build a null distribution of correlation values.
-Finally, we thresholded the group averaged correlation maps where the `real' correlation value for a given voxel exceeded the 95th percentile of the null distribution.
-To correct for non-linearities between the viewing time and recall time, for each participant we used dynamic time warping to temporally align the matrices.
-The algorithm recovers a path of coordinates that would bring the video and recall model in maximal temporal alignment.
-We used this path to warp the fMRI data and the recall model into temporal alignment (separately for each participant).
+We used a similar procedure to identify which voxels' responses reflected the recall templates.
+For each participant, we correlated the upper triangle of the correlation matrix for each cube of voxels with their (time warped) recall correlation matrix.
+As in the video template analysis this yielded, a single correlation coefficient for each participant.
+However, whereas the video analysis compared every participant's responses to the same template, here the recall templates were unique for each participant.
+We computed the average $z$-transformed correlation coefficient across participants, and used the same permutation procedure we developed for the video responses to assess significant correlations.
+To create the map in Figure~\ref{fig:brainz}B we thresholded out any voxels whose correlation values fell below the 95\textsuperscript{th} percentile of the permutation-derived null distribution.
 

### 2018-09-03 paper/main.tex
minor typo corrections, updated brainz fig

@@
 Our memory systems can then leverage these associations to form predictions that help guide our behaviors~\citep{RangRitc12}.
-For example, as we navigate the world, the features of our subjective experiences tend to change gradually (e.g.\ the room or situation we are in is strongly temporally autocorrelated), allowing us to form stable estimates of our current situation and behave accordingly~\citep{ZackEtal07, ZwaaRadv98}.
+For example, as we navigate the world, the features of our subjective experiences tend to change gradually (e.g., the room or situation we are in is strongly temporally autocorrelated), allowing us to form stable estimates of our current situation and behave accordingly~\citep{ZackEtal07, ZwaaRadv98}.
 Although our experiences most often change gradually, they also occasionally change suddenly~\citep[e.g., when we walk through a doorway; ][]{RadvZack17}.
@@
 We used the topic model (fit to the annotations) to estimate topic vectors for each moment of video and each sentence the participants recalled.
-Example topic vectors are displayed in the bottom row (green: video annotations; blue: example participant's recalls).
+Example topic vectors are displayed in the bottom row (blue: video annotations; green: example participant's recalls).
 Three topic dimensions are shown (the highest-weighted topics for each of the three example scenes, respectively).
@@
 Several of the topics were highly similar, which we hypothesized might allow us to distinguish between subtle narrative differences (if the distinctions between those overlapping topics were meaningful; also see Fig.~\featureimportance).
-The topic vectors for each timepoint were \textit{sparse}, in that only a small number (usually one or two) topics tended to be ``active'' in any given timepoint (Fig.~\ref{fig:model}A).
+The topic vectors for each timepoint were \textit{sparse}, in that only a small number (usually one or two) of topics tended to be ``active'' in any given timepoint (Fig.~\ref{fig:model}A).
 Further, the dynamics of the topic activations appeared to exhibit \textit{persistance} (i.e., given that a topic was active in one timepoint, it was likely to be active in the following timepoint) along with \textit{occasional rapid changes} (i.e., occasionally topics would appear to spring into or out of existence).
@@
 \textbf{H.} Average correlations between each pair of video events and recalled events (across all 17 participants).
-To create the figure, each recalled event was assigned to the video event with the most correlated topic vector.}
+To create the figure, each recalled event was assigned to the video event with the most correlated topic vector (yellow boxes in panels G and H).}
 \label{fig:model}
@@
 Two clear patterns emerged from this set of analyses.
-First, although every individual participant's recalls could be segmented into discrete events (e.g.\ every individual participant's recall correlation matrix exhibited clear block diagonal structure; Fig.~\corrmats), each participant appeared to have a unique \textit{recall resolution}, reflected in the sizes of those blocks.
-For example, some participants' recall topic proportions segmented into just a few events (e.g.\ Participants 1, 4, and 15), while others' recalls segmented into many shorter duration events (e.g.\ Participants 12, 13, and 17).
-This suggests that different participants may be recalling the video with different levels of detail-- e.g.
-some might touch on just the major plot points, whereas others might attempt to recall every minor scene.
+First, although every individual participant's recalls could be segmented into discrete events (e.g., every individual participant's recall correlation matrix exhibited clear block diagonal structure; Fig.~\corrmats), each participant appeared to have a unique \textit{recall resolution}, reflected in the sizes of those blocks.
+For example, some participants' recall topic proportions segmented into just a few events (e.g., Participants 1, 4, and 15), while others' recalls segmented into many shorter duration events (e.g., Participants 12, 13, and 17).
+This suggests that different participants may be recalling the video with different levels of detail-- e.g., some might touch on just the major plot points, whereas others might attempt to recall every minor scene.
 The second clear pattern present in every individual participant's recall correlation matrix is that, unlike in the video correlation matrix, there are substantial off-diagonal correlations in participant's recalls.
@@
 The dynamic content of the video and participants' recalls is quantified in the corresponding topic proportion matrices.
-However, it is difficult to gain deep insights into that content by directly examining the topic proportion matrices (e.g., Figs.~\ref{fig:model}A, D) or the corresponding correlation matrices (Figs.~\ref{fig:model}B, E, \corrmats).
+However, it is difficult to gain deep insights into that content solely by examining the topic proportion matrices (e.g., Figs.~\ref{fig:model}A, D) or the corresponding correlation matrices (Figs.~\ref{fig:model}B, E, \corrmats).
 To visualize the time-varying high-dimensional content in a more intuitive way~\citep{HeusEtal18} we projected the topic proportion matrices onto a two-dimensional space using Uniform Manifold Approximation and Projection~\citep[UMAP; ][]{McInHeal18}.
@@
 In addition to constructing overall summaries, assessing the video and recall topic vectors from individual recalls can provide further insights.
-Specifically, for any given event we can construct a wordle from that event's topic vector, and we can construct a similar wordle from the average topic vectors produced by all participants who recalled that event.
+Specifically, for any given event we can construct a wordle from that event's topic vector, and we can construct a similar wordle from the average topic vectors produced by all participants' recalls of that event.
 We can then examine those wordles visually to gain an intuition for which aspects of the video event were recapitulated in participants' recalls of that event.
@@
 In a second analysis, we sought to identify which brain structures' responses (while viewing the video) reflected how each participant would later \textit{recall} the video.
-Specifically, we used an analogous searchlight procedure to identify clusters of voxels whose temporal correlation matrices reflected the temporal correlation matrix of the topic proportions for each individual's recalls (Figs.~\corrmats).
+In particular, we used an analogous searchlight procedure to identify clusters of voxels whose temporal correlation matrices reflected the temporal correlation matrix of the topic proportions for each individual's recalls (Figs.~\ref{fig:model}D, \corrmats).
 As shown in Figure~\ref{fig:brainz}B, the analysis revealed a network of regions including the ventromedial prefrontal cortex (vmPFC), anterior cingulate, and right medial temporal lobe (rMTL), suggesting that these regions may play a role in transforming each individual's experience into memory.
@@
 This provides support for the notion that part of the long temporal receptive window network may be maintaining an explicit model of the stimulus dynamics.
-When we performed a similar analysis after swapping out the video's topic trajectory with the recall topic trajectories of each individual participant, this allowed us to identify brain regions whose responses (as the participants viewed the video) reflected how the video trajectory would be transformed in memory (as reflected by the recall topic trajectory).
+When we performed a similar analysis after swapping out the video's topic trajectory with the recall topic trajectories of each individual participant, this allowed us to identify brain regions whose responses (as the participants viewed the video) reflected how the video trajectory would be transformed in memory (as reflected by the recall topic trajectories).
 The analysis revealed that the rMTL and vmPFC may play a role in this person-specific transformation from experience into memory.
@@
 This approach would provide a more nuanced and specific view into which aspects of the material students had learned well (or poorly).
-In clinical settings, memory measures that incorporate such explicit content models might also provide more direct evaluations patients' memories.
+In clinical settings, memory measures that incorporate such explicit content models might also provide more direct evaluations of patients' memories.
 
@@
 where $a$ was the average correlation between the topic vectors of timepoints within the same state; $b$ was the average correlation between the topic vectors of timepoints within \textit{different} states; and $\alpha$ was a regularization parameter that we set to 5 times the window length (i.e., 250 scenes for the video topic trajectory and 50 sentences for the recall topic trajectories).
-Figure~\ref{fig:model}B displays the event boundaries returned for the video, and Figure~\corrmats displays the event boundaries returned for each participant's recalls.
+Figure~\ref{fig:model}B displays the event boundaries returned for the video, and Figure~\corrmats~displays the event boundaries returned for each participant's recalls.
 After obtaining these event boundaries, we created stable estimates of each topic proportions matrix by averaging the topic vectors within each event.
@@
 We constructed similar temporal correlation matrices for each participant's recall topic trajectory (Figs.~\ref{fig:model}D, \corrmats).
-However, to correct for length differences and non-linear transformation between viewing time and recall time, we first used dynamic time warping~\citep{BernClif94} to temporally align participants' recall topic trajectories with the video topic trajectory (an example correlation matrix before and after warping is shown in Fig.~\ref{fig:brainz}B).
+However, to correct for length differences and potential non-linear transformations between viewing time and recall time, we first used dynamic time warping~\citep{BernClif94} to temporally align participants' recall topic trajectories with the video topic trajectory (an example correlation matrix before and after warping is shown in Fig.~\ref{fig:brainz}B).
 This yielded a 1976 by 1976 correlation matrix for the video template and for each participant's recall template.
@@
 For each participant, we correlated the upper triangle of the correlation matrix for each cube of voxels with their (time warped) recall correlation matrix.
-As in the video template analysis this yielded, a single correlation coefficient for each participant.
+As in the video template analysis this yielded a single correlation coefficient for each participant.
 However, whereas the video analysis compared every participant's responses to the same template, here the recall templates were unique for each participant.

### 2018-09-03 paper/main.tex
corrected HeusEtal18 references

@@
 Although our experiences most often change gradually, they also occasionally change suddenly~\citep[e.g., when we walk through a doorway; ][]{RadvZack17}.
-Prior research suggests that these sharp transitions (termed \textit{event boundaries}) during an experience help to discretize our experiences into \textit{events}~\citep{RadvZack17, BrunEtal18, HeusEtal18, ClewDava17, EzzyDava11, DuBrDava13}.
+Prior research suggests that these sharp transitions (termed \textit{event boundaries}) during an experience help to discretize our experiences into \textit{events}~\citep{RadvZack17, BrunEtal18, HeusEtal18b, ClewDava17, EzzyDava11, DuBrDava13}.
 The interplay between the stable (within event) and transient (across event) temporal dynamics of an experience also provides a potential framework for transforming experiences into memories that distill those experiences down to their essence-- i.e., their gists.
-For example, prior work has shown that event boundaries can influence how we learn sequences of items~\citep{HeusEtal18, DuBrDava13}, navigate~\citep{BrunEtal18}, and remember and understand narratives~\citep{ZwaaRadv98, EzzyDava11}.
+For example, prior work has shown that event boundaries can influence how we learn sequences of items~\citep{HeusEtal18b, DuBrDava13}, navigate~\citep{BrunEtal18}, and remember and understand narratives~\citep{ZwaaRadv98, EzzyDava11}.
 
@@
 However, it is difficult to gain deep insights into that content solely by examining the topic proportion matrices (e.g., Figs.~\ref{fig:model}A, D) or the corresponding correlation matrices (Figs.~\ref{fig:model}B, E, \corrmats).
-To visualize the time-varying high-dimensional content in a more intuitive way~\citep{HeusEtal18} we projected the topic proportion matrices onto a two-dimensional space using Uniform Manifold Approximation and Projection~\citep[UMAP; ][]{McInHeal18}.
+To visualize the time-varying high-dimensional content in a more intuitive way~\citep{HeusEtal18a} we projected the topic proportion matrices onto a two-dimensional space using Uniform Manifold Approximation and Projection~\citep[UMAP; ][]{McInHeal18}.
 In this lower-dimensional space, each point represents a single video or recall event, and the distances between the points reflect the distances between the events' associated topic vectors (Fig.~\ref{fig:trajectory}).
@@
 In other words, the first text sample comprised the combined text from the first 50 scenes (i.e., 1--50), the second comprised the text from scenes 2--51, and so on.
-We trained our model using these overlapping text samples with \texttt{scikit-learn}~\citep[version 0.19.1; ][]{PedrEtal11}, called from our high-dimensional visualization and text analysis software, \texttt{HyperTools}~\citep{HeusEtal18}.
+We trained our model using these overlapping text samples with \texttt{scikit-learn}~\citep[version 0.19.1; ][]{PedrEtal11}, called from our high-dimensional visualization and text analysis software, \texttt{HyperTools}~\citep{HeusEtal18a}.
 Specifically, we use the \texttt{CountVectorizer} class to transform the text from each scene into a vector of word counts (using the union of all words across all scenes as the ``vocabulary,'' excluding English stop words); this yields a number-of-scenes by number-of-words \textit{word count} matrix.
@@
 We then divided the rows of the result (a total-number-of-events by two matrix) back into separate matrices for the video topic trajectory and the trajectories for each participant's recalls (Fig.~\ref{fig:trajectory}).
-This general approach for discovering a shared low-dimensional embedding for a collections of high-dimensional observations follows \cite{HeusEtal18}.
+This general approach for discovering a shared low-dimensional embedding for a collections of high-dimensional observations follows \cite{HeusEtal18a}.
 

### 2018-09-03 paper/boneyard.tex
working on supplemental materials-- currently a complete mess but vaguely organized in what seems like a reasonable order [WIP]

@@
+% Supplemental materials
+
+trajectories obtained in the absence of a single feature and that of our original (i.e., full) model (Supp.
+Fig.~\ref{fig:feature-importance}A).
+First, we iteratively removed one transcribed feature from the scene descriptions and constructed a timepoints (1976) by topis (100) matrix using a topic model fit to the remaining features.
+We then represented the original model as well as the new model’s temporal structure as a timepoints-by-timepoints correlation matrix.
+Finally, we vectorized these correlation matrices and correlated them to each other resulting in a single number (for each feature removed from the model) representing the similarity of the ``feature-removed'' models to the full model.
+
+In order to ascertain which features were important in relating the recall models to the video model, we similarly compared to the temporal structures of video and recall models deprived of a single feature at a time (Supp.
+Fig.~\ref{fig:feature-importance}B).
+For each feature removed, we transformed each participant’s recall transcript using a model trained on the feature-deprived video text windows (of 50 scene segments), and resampled the recall timeseries to match the shape of the video model (1976 timepoints).
+We then represented the temporal structures of each participant’s recall model as timepoints-by-timepoints correlation matrices and computed the average correlation with the temporal structure of the video model (across participants).
+
 %METHODS

### 2018-09-03 paper/supplemental_materials.tex
figre legend
working on supplemental materials-- currently a complete mess but vaguely organized in what seems like a reasonable order [WIP]

@@
 
-% Supplemental materials
+\section*{Overview}
+This document provides additional details about the methods we used in the main text.  We also include some additional figures referenced in the main text.
+
+\section*{Additional details about topic modeling methods and results}
+\subsection*{Optimizing topic model parameters}
+In order to create accurate video and recall models, we used an optimization method that was driven by our ability to explain hand-annotated memory performance metrics collected by \cite{ChenEtal17}.
+Specifically, we \textbf{JRM STOPPED HERE}
+% argmax \omega (movie window size), \rho (recall window size), and K (number of topics)
+
+\begin{figure}[tp]
+\centering
+\includegraphics[width=1\textwidth]{figs/parameter_search}
+\caption{\small \textbf{Optimizing video model parameters.} Matrices representing the correlation value between hand-annotated memory performance and mean squared error between video model and recall model.
+Best fitting model was 100 topics, 50 video window size and 10 recall window size}
+\label{fig:paramsearch}
+\end{figure}
+
+The optimized model converged on 28 unique topics that were assigned non-zero weights over the course of the video.
+We provide a list of the top ten highest-weighted words from each topic in Figure~\ref{fig:topics}.
+
 \begin{figure}[tp]
@@
 
-\begin{figure}[tp]
-\centering
-\includegraphics[width=1\textwidth]{figs/corrmats}
-\caption{\small \textbf{Recall model correlation matrices and event segmentation fits.} Each participant's timepoint-by-timepoint recall correlation matrix.
-The yellow boxes represent ``events'' identified by a hidden Markov model.}
-\label{fig:corrmats}
-\end{figure}
-
-\begin{figure}[tp]
-\centering
-\includegraphics[width=1\textwidth]{figs/matchmats}
-\caption{\small \textbf{Video-recall event model correlation matrices.} Each participant's video event by recall event correlation matrix.
-The yellow boxes represent the maximum correlation in each column.}
-\label{fig:matchmats}
-\end{figure}
+\subsection*{Feature importance}
+To determine the contribution of each feature to the structure of the video topic proportions, we conducted a ``leave one out'' anlaysis.
+Specifically, we compared the original video topic trajectory (created using all hand-annotated features from the 1000 hand-annotated scenes spanning the \textit{Sherlock episode}; see \textit{Methods} for a full list of features) with video trajectories created using all but one type of feature.
+We created temporal correlation matrices for each trajectory (using the topic proportions matrices) and correlated the upper triangles of each impoverished trajectory with the original feature-complete trajectory.
+Observing a lower correlation between an impoverished trajectory (holding out a particular feature) and the feature-complete trajectory would suggest that the given feature played a more prominent role in shaping the structue of the feature-complete trajectory.
+We found that hand-annotated narrative details provided the most structure to the feature-complete trajectory, whereas transcriptions of onscreen text provided the least structure (Fig.~\ref{fig:feature-importance}A).
 
@@
 \end{figure}
+
+We also carried out an analysis of which annotated features tended to shape aspects of the video topic trajectory that were preserved in participants' recalls.
+Specifically, we computed the timepoint-by-timepoint correlation matrix of the video topic trajectory, and correlated its upper triangle with the timepoint-by-timepoint correlation matrices of each participant's recall topic trajectory (resampled using linear interpolation to have the same number of timepoints as the video trajectory).
+This yielded a single correlation coefficient for each participant.
+We then carried out a series of analyses whereby we repeated the analysis with each annotated feature held out in turn.
+Observing a lower correlation between the video and recall trajectories (when a given feature was held out) would indicate that the feature tends to be preserved in participants' recalls.
+We found that hand-annotated narrative details were the most preserved type of feature, whereas information about the camera angle tended not to feature in participants' recalls (Fig.~\ref{fig:feature-importance}B).
+
+Next, we wondered how the different types of features might relate.
+For example, knowing which characters are on screen during a given scene may also provide information about which characters are speaking.
+We computed video topic trajectories for each feature in turn, and then compared the temporal correlation matrices of all pairs of features.
+This provided additional confirmation that the full model (including all types of features) was largely driven by narrative details.
+We also found that character-driven features (characters on screen, characters speaking, and characters in focus) were strongly correlated.
+Other details, such as the presense or absense of music, led to very different topic trajectories (Fig.~\ref{fig:feature-importance}C).
+
+\section*{Additional analyses of memory performance}
 
@@
 
-\begin{figure}[tb]
-\centering
-\includegraphics[width=1\textwidth]{figs/list_learning}
-\caption{\small \textbf{Naturalistic extensions of classic list-learning memory analyses.} A).
-The probability of first recall as a function of the serial position of the event during encoding.
-B).
-A lag-conditional response probability curve.
-Given recall of event i, the probability that the next recalled item will be from serial position i +/- lag.
-C).
-Proportion of events recalled as a function of serial position.
-All error bars are the standard error of the mean derived from a bootstrap resampling procedure.}
-\label{fig:list-learning}
-\end{figure}
-
-\section*{Supplemental Methods}
-\subsection*{Quantifying the importance of features}
-To determine the contribution of each feature to the structure of the video model, we examined the similarity between the temporal structure of models trained in the absence of a single feature and that of our original (i.e., full) model (Supp.
-Fig.~\ref{fig:feature-importance}A).
-First, we iteratively removed one transcribed feature from the scene descriptions and constructed a timepoints (1976) by topis (100) matrix using a topic model fit to the remaining features.
-We then represented the original model as well as the new model’s temporal structure as a timepoints-by-timepoints correlation matrix.
-Finally, we vectorized these correlation matrices and correlated them to each other resulting in a single number (for each feature removed from the model) representing the similarity of the ``feature-removed'' models to the full model.
-
-In order to ascertain which features were important in relating the recall models to the video model, we similarly compared to the temporal structures of video and recall models deprived of a single feature at a time (Supp.
-Fig.~\ref{fig:feature-importance}B).
-For each feature removed, we transformed each participant’s recall transcript using a model trained on the feature-deprived video text windows (of 50 scene segments), and resampled the recall timeseries to match the shape of the video model (1976 timepoints).
-We then represented the temporal structures of each participant’s recall model as timepoints-by-timepoints correlation matrices and computed the average correlation with the temporal structure of the video model (across participants).
-
-The two prior analyses examine information (about either the video model structure or the video/recall model relationship) lost in the absence of each feature.
-However, they do not consider redundancy in the information each feature contributes (e.g., how much unique information does "Character speaking" provide that "Character in focus" does not?).
-As a measure of information overlap between features, we computed the similarity between the topic trajectories of each individual annotated feature in addition to the full feature set.
-First, we singularly transformed the text of each feature using a model trained on the collection of all features.
-We then represented the single feature's model's temporal structure as a timepoints-by-timepoints correlation matrix, and compared the temporal structures pairwise by constructing a features-by-features correlation matrix ((Supp.
-Fig.~\ref{fig:feature-importance}C).
-We additionally computed the correlation between the individual features' temporal structures and that of the full video model as a measure of the proportion of information discernible from that feature alone.
-
 \subsection*{List-learning analyses}
@@
 
+\begin{figure}[tb]
+\centering
+\includegraphics[width=1\textwidth]{figs/list_learning}
+\caption{\small \textbf{Naturalistic extensions of classic list-learning memory analyses.} A).
+The probability of first recall as a function of the serial position of the event during encoding.
+B).
+A lag-conditional response probability curve.
+Given recall of event i, the probability that the next recalled item will be from serial position i +/- lag.
+C).
+Proportion of events recalled as a function of serial position.
+All error bars are the standard error of the mean derived from a bootstrap resampling procedure.}
+\label{fig:list-learning}
+\end{figure}
+
+\section*{Participant-level results referenced in the main text}
+
+% Supplemental materials
+
+\begin{figure}[tp]
+\centering
+\includegraphics[width=1\textwidth]{figs/corrmats}
+\caption{\small \textbf{Recall model correlation matrices and event segmentation fits.} Each participant's timepoint-by-timepoint recall correlation matrix.
+The yellow boxes represent ``events'' identified by a hidden Markov model.}
+\label{fig:corrmats}
+\end{figure}
+
+\begin{figure}[tp]
+\centering
+\includegraphics[width=1\textwidth]{figs/matchmats}
+\caption{\small \textbf{Video-recall event model correlation matrices.} Each participant's video event by recall event correlation matrix.
+The yellow boxes represent the maximum correlation in each column.}
+\label{fig:matchmats}
+\end{figure}
+
 %\newpage

### 2018-09-03 paper/supplemental_materials.tex
supp mats, in progress

@@
 %\doublespacing
+
+\newcommand{\argmax}{\mathop{\mathrm{argmax}}\limits}
 
@@
 In order to create accurate video and recall models, we used an optimization method that was driven by our ability to explain hand-annotated memory performance metrics collected by \cite{ChenEtal17}.
-Specifically, we \textbf{JRM STOPPED HERE}
-% argmax \omega (movie window size), \rho (recall window size), and K (number of topics)
+Specifically, we used a grid search to compute the $\omega$ (movie sliding window duration, in scenes), $\rho$ (recall sliding window duration, in sentences), and $K$ (number of topics) that satisfied
+\[
+\argmax_{\omega, \rho, K} \mathrm{corr}\left(\mathrm{corr}\left(\mu\left(\omega, \rho, K\right), \nu\left(\omega, \rho, K\right)\right), \theta\right),
+\]
+where $\mathrm{corr}(\mu, \nu)$ is the per-participant correlation between the upper triangles of the temporal correlation matrices of the video ($\mu$) and recall ($\nu$) trajectory, and $\theta$ is the per-participant hand-annotated memory performance.
+We searched over a grid of pre-specified values for each of these parameters; the resulting correlations are displayed in Figure~\ref{fig:paramsearch}.
+The optimal parameters were $\omega = 250$, $\rho = 50$, and $K = 100$.
 
@@
 
-\subsection*{Feature importance}
+\subsection*{Feature importance analyses}
 To determine the contribution of each feature to the structure of the video topic proportions, we conducted a ``leave one out'' anlaysis.
@@
 Other details, such as the presense or absense of music, led to very different topic trajectories (Fig.~\ref{fig:feature-importance}C).
+
+\textbf{JRM STOPPED HERE.  NOTE: STILL NEED TO LOOK AT FIG CAPTIONS TOO...}
 

### 2018-09-04 paper/supplemental_materials.tex
updated supp mat fig captions related to topic models

@@
 \includegraphics[width=1\textwidth]{figs/parameter_search}
-\caption{\small \textbf{Optimizing video model parameters.} Matrices representing the correlation value between hand-annotated memory performance and mean squared error between video model and recall model.
-Best fitting model was 100 topics, 50 video window size and 10 recall window size}
+\caption{\small \textbf{Optimizing topic model parameters.}  We performed a grid search over movie sliding window length ($\omega \in \{5, 10, 25, 50, 100 \}$), recall sliding window length ($\rho \in \{5, 10, 25, 50, 100 \}$, and number of topics ($K \in \{5, 10, 25, 50, 100 \}$.
+The reported correlations are between per-subject video-recall trajectory correlations and per-subject hand-annotated memory performance ratings.}
 \label{fig:paramsearch}
@@
 \includegraphics[width=1\textwidth]{figs/feature_value}
-\caption{\small \textbf{Impact of individual features on topic modeling analysis.} \textbf{A.} Contribution of each feature to model structure.
-Bars represent the correlation of a video model trained in the absence of a given feature to the model trained on all features.
-\textbf{B.} Contribution of each feature to video model/recall model relationship.
-The leftmost bar represents the across-participants mean correlation between the video model and recall models trained on all features.
-Subsequent bars represent the same relationship between video and recall models trained in the absence of a given feature.
-Error bars are the standard error of the mean across participants.
-\textbf{C.}  Individual feature trajectory similarity matrix.
-The first row/column is the topic trajectory the full video model.
-Each subsequent row/column is that of a single feature.
-Shading corresponds to the value of the correlation coefficient (Pearson's $r$) .}
+\caption{\small \textbf{Feature importance analysis.} \textbf{A.} Contributions of each feature type to the structure of the video trajectory.
+The bar heights reflect the correlation between the video trajectory computed using all features with a video trajectory computed using all features except the indicated feature.
+(Lower bars reflect features that contribute more substantially to the video trajectory's shape.) \textbf{B.} Which features are preserved during recall?
+The bar heights reflect the (average) across-participant correlations between the video and recall trajectories.
+Error bars denote 95\% confidence intervals.
+\textbf{C.} Feature correlation matrix.
+Each entry displays the correlation between video topic trajectories created using only the indicated (row/column) features.}
 \label{fig:feature-importance}
@@
 
-\textbf{JRM STOPPED HERE.  NOTE: STILL NEED TO LOOK AT FIG CAPTIONS TOO...}
+\textbf{JRM STOPPED HERE.}
 

### 2018-09-04 paper/supplemental_materials.tex
backing up edits to supplemental materials [WIP]

@@
 \[
-\argmax_{\omega, \rho, K} \mathrm{corr}\left(\mathrm{corr}\left(\mu\left(\omega, \rho, K\right), \nu\left(\omega, \rho, K\right)\right), \theta\right),
+\argmax_{\omega, \rho, K} \left[\mathrm{corr}\left(\mathrm{corr}\left(\mu\left(\omega, \rho, K\right), \nu\left(\omega, \rho, K\right)\right), \theta\right)\right],
 \]
@@
 The bar heights reflect the (average) across-participant correlations between the video and recall trajectories.
-Error bars denote 95\% confidence intervals.
+Error bars denote bootstrap-estimated standard error of the mean.
 \textbf{C.} Feature correlation matrix.
@@
 
-\textbf{JRM STOPPED HERE.}
-
 \section*{Additional analyses of memory performance}
 
-\section*{Naturalistic extensions of classic list-learning analyses}
-Just like in a traditional free recall list-learning experiment where participants view a list of words and then verbally recall them, our video-recall matching analysis approach affords us the ability to analyze memory in the same way.
-The recalled events can be treated as ``items'' analogous to words recalled in a list-learning study.
-Here, we sought to characterize memory performance/dynamics by extending classic analyses originally designed for list-learning experiments to more naturalistic settings.
+\subsection*{Naturalistic extensions of classic list-learning analyses}
+In traditional list-learning experiments, participants view a list of items (e.g., words) and then recall the items later.
+Our video-recall event matching approach affords us the ability to analyze memory in a similar way.
+The video and recall events can be treated analogously to studied and recalled ``items'' in a list-learning study.
+We can then extend classic analyses of memory performance and dynamics (originally designed for list-learning experiments) to the more naturalistic video recall task used in our study.
 
-First, we asked whether the estimated number of recall events ($k$) by participant was related to hand-annotated accuracy as published in Chen et al.
-(2017).
-We found a strong positive correlation where participants with a greater number of recall events also had better overall memory performance (Pearson's $r(16) = 0.67, p = 0.003$).
-Then, we considered how participants initiated the recall sequence (known in the literature as the `probability of first recall' or `PFR').
-We found that participants tended to initiate their recall sequences with the first few events (Supp.
-Fig.~\ref{fig:list-learning}A), which is qualitatively very similar to previously published list learning experiments ~\citep{HowaKaha99}.
-Next, we considered another well-studied memory measure in the list-learning literature, the lag conditional response probability curve (or lag-CRP) ~\citep{Kaha96}.
-The result suggests a strong bias to transition sequentially events in the forward direction (Supp.
-Fig.~\ref{fig:list-learning}B).
-Finally, we assessed memory performance for each event in the video as a function of its serial position during encoding (Supp.
-Fig.~\ref{fig:list-learning}C).
-We did not observe the classic ``primacy'' and ``recency'' pattern which is prevalent in the literature ~\citep{Murd62a}.
-We also considered two additional across-participant measures of recall that characterize memory organization: temporal clustering and semantic clustering.
-We found that participants who clustered in time also recalled a greater number of events (Pearson's $r(16) = 0.62, p = 0.007$).
-Next, we assessed semantic clustering.
-We found that the semantic clustering score was related to memory performance across participants (Pearson's $r(16) = 0.55, p = 0.02$).
-Thus, participants who organized their recalls with respect to the semantic information contained in the scene had better memory performance.
+Perhaps the simplest and most widely used measure of memory performance is \textit{accuracy}-- i.e., the proportion of studied (experienced) items (in this case, the 34 video events) that the participant later remembered.
+\cite{ChenEtal17} developed a human rating system whereby the quality of each participant's memory was evaluated by an independent rater.
+We found a strong across-participants correlation between these independant ratings and the overall number of events that our HMM approach identified in participants' recalls ($r = 0.67, p = 0.003$).
 
-\section*{Additional measures of naturalistic memory}
+As described below, we next considered three more naunced measures of the memory performance and dynamics that are typically associated with list-learning studies.
+We also provide a software package, \texttt{Quail}, for carrying out these analyses~\citep{HeusEtal17b}.
+
+\begin{figure}[tb]
+\centering
+\includegraphics[width=1\textwidth]{figs/list_learning}
+\caption{\small \textbf{Naturalistic extensions of classic list-learning memory analyses.} \textbf{A.} The probability of first recall as a function of the serial position of the event in the video.
+\textbf{B}.
+The probability of recalling each event, conditioned on having just recalled the event \textit{lag} events away in the video.
+\textbf{C.} The proportion of participants who recalled each event, as a function of the serial position of the events in the video.
+All panels: error bars denote bootstrap-estimated standard error of the mean.}
+\label{fig:list-learning}
+\end{figure}
+
+\paragraph{Probability of first recall (PFR).}  PFR curves~\citep{WelcBurn24, PostPhil65, AtkiShif68} reflect the probability that an item will be recalled first as a function of its serial position during encoding.
+To carry out this analysis, we initialized a number-of-participants (17) by number-of-video-events (34) matrix.
+Then for each participant, we found the index of the video event that was recalled first (i.e., the video event whose topic vector was most strongly correlated with that of the first recall event) and filled in that index in the matrix with a 1.
+Finally, we averaged over the rows of the matrix, resulting in a 1 by 34 array representing the proportion of participant that recalled an event as a function of serial position during encoding (Fig.~\ref{fig:list-learning}A).
+
+\paragraph{Lag conditional probability curve (lag-CRP).} The lag-CRP curve~\citep{Kaha96} reflects the probability of recalling a given event after the just-recalled event, as a function of their relative positions (or \textit{lag}).
+In other words, a lag of 1 indicates that a recalled event came immediately after the previously recalled event in the video, and a lag of -3 indicates that a recalled event came 3 items before the previously recalled event.
+For each recall transition (following the first recall), we computed the lag between the current recall event and the next recall event, normalizing by the total number of possible transitions.
+This yielded a number-of-participants (17) by number-of-lags (-33 to +33; 67 lags total) matrix.
+We averaged over the rows of this matrix to obtain a group-averaged lag-CRP curve (Fig.~\ref{fig:list-learning}B).
+
+\paragraph{Serial position curve (SPC).} SPCs~\citep{Murd62a} reflect the proportion of participants that remember each item as a function of their serial position during encoding.
+We initialized a number-of-participants (17) by number-of-video-events (34) matrix of zeros.
+Then, for each recalled event (and each participant), we found the index of the video event that the recalled event most closely matched (via the correlation between the events' topic vectors) and entered a 1 into that position in the matrix (i.e., for the given participant and event).
+This resulted in a matrix whose entries indicated whether or not each event was recalled by each participant (depending on whether the corresponding entires were set to one or zero.
+Finally, we averaged over the rows of the matrix to yield a 1 by 34 array representing the proportion of participants that recalled each event as a function of its serial position (Fig.~\ref{fig:list-learning}C).
+
+\paragraph{Temporal clustering scores.} Temporal clustering refers to the extent to which participants group their recall responses according to encoding position~\citep{PolyEtal09}.
+For instance, if the participant recalled the video events in the exact order they occurred, this would yield a score of 1.
+If the participant recalled the video events in reverse order, this would yield a score of 0.
+Similarly, if the participant recalled the events in random order, this yield yield an expected score of 0.5.
+For each recall event transition (and separately for each participant), we sorted all not-yet-recalled events according to their absolute lag (i.e., distance away in the video).
+We then computed the percentile rank of the next event the participant recalled.
+We averaged these percentile ranks across all of the participant's recalls to obtain a single temporal clustering score for the participant.
+Overall, we found that participants with higher temporal clustering scores also tended to recall more events ($r = 0.62, p = 0.007$).
+
+\paragraph{Semantic clustering scores.} Semantic clustering measures the extent to which participants grouped their recall responses according to semantic similarity~\citep{PolyEtal09}.
+Here, we used the topic vectors for each event as a proxy for its semantic content.
+Thus, the similarity between the semantic content for two events can be computed by correlating their respective topic vectors.
+For each recall event transition, we sorted all not-yet-recalled events according to how correlated the topic vector \textit{of the closest-matching video event} was to the topic vector of the closest-matching video event to the just-recalled event.
+We then computed the percentile rank of the observed next recall.
+We averaged these percentile ranks across all of the participant's recalls to obtain a single semantic clustering score for the participant.
+We found that participants who exhibited stronger semantic clustering scores overall remembered more video events ($r = 0.55, p = 0.02$).
+
+\textbf{JRM STOPPED HERE}
+
+\subsection*{Additional measures of naturalistic memory}
 To quantify the similarity between the video model and individual recall models, we considered a number of novel metrics.
@@
 
-\subsection*{List-learning analyses}
-\textbf{Overall Accuracy.}  To get an overall measure of the quantity of information recalled, we computed the proportion of sucessfully recalled events by counting the number of unique recall events identified by the HMM model and dividing by the total number of video events.
-We performed this analysis for each participant separately.
-
-\textbf{Probability of first recall (PFR).}  The (PFR) analysis represents the probability that an item will be recalled first as a function of its serial position during encoding.
-We initialized a \# of participants (17) by \# of video events (34) matrix.
-Then for each participant, we found the index of the video event that was recalled first and filled in that index in the matrix with a 1.
-Finally, we averaged over the rows of the matrix, resulting in a 1 by 34 array representing the proportion of participant that recalled an event as a function of serial position during encoding.
-
-\textbf{Lag conditional probability curve (lag-CRP).} The lag-CRP represents the probability that the next item recalled will be of lag $i$ from the just recalled item.
-For each recall transition, we computed the lag between the current recall event and the next recall event, normalizing by the total number of possible transitions.
-This resulted in a \# of participants (17) by lags (-33:+33) matrix.
-We averaged over the rows of this matrix to get a group-averaged lag-CRP.
-
-\textbf{Serial position curve (SPC).} The SPC represents the proportion of participants that remember an item as a function of its serial position during encoding.
-We initialized a \# of participants (17) by \# of video events (34) matrix.
-Then, for each recall event (and each participant), we found the index of the video event that was recalled and filled it in with a 1.
-This resulted in a matrix where 1s indicate the successful recall of an event in serial position $n$ and zeros indicate the lack of recall for that event.
-Lastly, we averaged over the rows of the matrix to get a 1 by 34 array representing the proportion of participants that recalled an event as a function of its serial position.
-
-\textbf{Temporal clustering.} Temporal clustering measures the extent to which participants group their recall responses according to encoding position ~\citep{PolyEtal09}.
-For instance, if the participant recalled each item in the presentation order, this would result in a score of 1.
-If the participant recalled randomly with respect to presentation order, this would result in a score of ~.5.
-For each event transition (and separately for each participant), we computed the rank similarity (euclidean distance) between the presentation position  of the current and next recall events.
-The scores were then averaged within participant to get a single number representing the extent of temporal clustering exhibited by a given participant.
-
-\textbf{Semantic clustering.} Similar to temporal clustering, semantic clustering measures the extent to which participants group their recall responses according to semantic similarity ~\citep{PolyEtal09}.
-Here, we are using the topic vectors for each event as a proxy for its semantic content.
-Thus, similarity between the semantic content for two events can be computed by correlating their respective topic vectors.
-For instance, if each consecutive recall was the next most similar event (in terms of its s), this would result in a score of ~1.
-If the participant recalled randomly with respect to semantic similarity, this would result in a score of ~.5.
-For each event transition (and separately for each participant), we computed the rank similarity (correlation distance) between the current recall event and the next recall event.
-The scores were then averaged within participant to get a single number representing the extent of semantic clustering exhibited by a given participant.
-
 \subsection*{Additional measures of naturalistic memory}
@@
 The resulting value is subtracted from 1 such that larger values indicate a more distinctive recall event.
-
-\begin{figure}[tb]
-\centering
-\includegraphics[width=1\textwidth]{figs/list_learning}
-\caption{\small \textbf{Naturalistic extensions of classic list-learning memory analyses.} A).
-The probability of first recall as a function of the serial position of the event during encoding.
-B).
-A lag-conditional response probability curve.
-Given recall of event i, the probability that the next recalled item will be from serial position i +/- lag.
-C).
-Proportion of events recalled as a function of serial position.
-All error bars are the standard error of the mean derived from a bootstrap resampling procedure.}
-\label{fig:list-learning}
-\end{figure}
 

### 2018-09-04 paper/supplemental_materials.tex
backing up progress on supp mats [WIP]

@@
 We then computed the percentile rank of the next event the participant recalled.
-We averaged these percentile ranks across all of the participant's recalls to obtain a single temporal clustering score for the participant.
+We averaged these percentile ranks across all of the participant's recalls to obtain a single temporal clustering score for the participant (mean: 0.808, SEM: 0.022).
 Overall, we found that participants with higher temporal clustering scores also tended to recall more events ($r = 0.62, p = 0.007$).
@@
 We then computed the percentile rank of the observed next recall.
-We averaged these percentile ranks across all of the participant's recalls to obtain a single semantic clustering score for the participant.
+We averaged these percentile ranks across all of the participant's recalls to obtain a single semantic clustering score for the participant (mean: 0.813, SEM: 0.022).
 We found that participants who exhibited stronger semantic clustering scores overall remembered more video events ($r = 0.55, p = 0.02$).
+
+\subsection*{Additional measures of naturalistic memory}
+To quantify the similarity between the video topic trajectory and individual recall topic trajectories, we considered several novel metrics.
+First, we tested whether each participant's recall trajectory matched the video trajectory in a general sense.
+For each participant we filtered the video trajectory to only include the events that the participant remembered.
+We then computed the root mean squared difference (RMSD) between the remaining video events and the (closest-matching) recalled events.
+For example, if the topic vectors for a participant's recall event topic vectors matched the corresponding video event topic vectors exactly (and in order), the expected RMSD for those events would be 0.
+However, if the participant's recall events did not perfectly match the video events, or if they were out of order, then the RMSD would be greater than 0.
+To assess the significance of the match between the video and recall trajectories, we carried out a permutation procedure whereby, for each of 10000 repetitions, we circularly shifted the recall trajectories (in time) by a random amount and then re-computed the RMSD each time.
+This yielded a distribution of ``null'' RMSD values for each participant.
+The observed RMSD values reached significance (i.e., $p < 0.05$, reflecting that more than 95\% of the null RMSD values were greater than the observed RMSD value) for nine of the participants (3, 4, 8--13, and 17).
+(For the remaining participants this test yielded $p$s$ < 0.25$.)  The observed RMSD values were also reliably correlated with hand-annotated memory performance across participants ($r = -0.57, p = 0.016$).
+In other words, a closer match between the video and recall topic trajectories was related to better overall recall performance.
+
+\paragraph*{Precision.}
+We tested whether participants who recalled more events were also more \textit{precise} in their recollections.
+For each participant, we computed the correlation between the topic vectors for each recall event and that of its matching video event (only for the events which they recalled).
+This resulted in a single number for each recalled event,  indexing how similar the recall event was to its matching video event.
+We defined the precision as the average video-recall correlation across all of the events a participant recalled.
+We found a strong correlation between hand-annotated memory performance and precision, suggesting that participants who remembered more events also remembered them more veridically ($r= 0.74, p = 0.0006$).
 
@@
 
-\subsection*{Additional measures of naturalistic memory}
-To quantify the similarity between the video model and individual recall models, we considered a number of novel metrics.
-First, we tested whether each participant's recall model matched the video model in a general sense.
-To do this, for each participant we filtered the video model to only include the events that the participant remembered and computed the root mean squared difference (RMSD) between the video model and the recall model.
-As an example, if the participant remembered all the events in order (with perfect precision), the expected distance value would be 0.
-However, if they remembered a subset of events, events out of order, or with low precision, the expected distance would be greater than 0.
-To assess significance, we performed a permutation test where we circularly shifted the recall model (10000 times) and recomputed the RMSD.
-The recall model significantly matched the video model for nine of the participants ($p < 0.05$, participants: 3-4, 8-13, 17 and the p-value for the rest of the participants was less than .25).
-Furthermore, the RMSD values were significantly correlated to hand annotated memory performance across participants (Pearson's $r(16) =-.57, p = 0.016$).
-Thus, a closer match between the video and recall event models was related to better recall performance.
-
-Next, we tested whether participants who recalled more events were also more precise in their recollections.
-For each participant, we computed the correlation between each recall event and its matching video event (only for the events which they recalled).
-This resulted in a single number for each recalled event indexing how similar the recall event was to its matching video event (i.e the ``precision'' of the recall).
-We then averaged the correlations within participant.
-In line with our prediction, there was a strong correlation between hand annotated memory performance and precision suggesting that participants who remembered more events also remembered them more veridically (Pearson's $r(16) = 0.74, p = 0.0006$).
-
-Then, we considered the distinctiveness of each recall event.
+\paragraph*{Distinctiveness.}
+We also considered the distinctiveness of each recall event.
 That is, how uniquely a recall event matched a given video event compared to all other video events.

### 2018-09-04 paper/supplemental_materials.tex
backing up progress

@@
 
+\paragraph*{Distinctiveness.}
+We also considered the \textit{distinctiveness} of each recalled event.
+That is, how uniquely a recalled event's topic vector matched a given video event topic vector, versus the topic vectors for the other video events.
 \textbf{JRM STOPPED HERE}
-
-\paragraph*{Distinctiveness.}
-We also considered the distinctiveness of each recall event.
-That is, how uniquely a recall event matched a given video event compared to all other video events.
 We hypothesized that participants with high memory performance might describe each event in a more distinctive way (relative to those with lower memory performance who might describe events in a more general way).

### 2018-09-04 paper/supplemental_materials.tex
finished draft of supplemental materials

@@
 \subsection*{Feature importance analyses}
-To determine the contribution of each feature to the structure of the video topic proportions, we conducted a ``leave one out'' anlaysis.
-Specifically, we compared the original video topic trajectory (created using all hand-annotated features from the 1000 hand-annotated scenes spanning the \textit{Sherlock episode}; see \textit{Methods} for a full list of features) with video trajectories created using all but one type of feature.
+To determine the contribution of each feature to the structure of the video topic proportions, we conducted a ``leave one out'' analysis.
+Specifically, we compared the original video topic trajectory (created using all hand-annotated features from the 1000 hand-annotated scenes spanning the \textit{Sherlock} episode; see \textit{Methods} for a full list of features) with video trajectories created using all but one type of feature.
 We created temporal correlation matrices for each trajectory (using the topic proportions matrices) and correlated the upper triangles of each impoverished trajectory with the original feature-complete trajectory.
-Observing a lower correlation between an impoverished trajectory (holding out a particular feature) and the feature-complete trajectory would suggest that the given feature played a more prominent role in shaping the structue of the feature-complete trajectory.
+Observing a lower correlation between an impoverished trajectory (holding out a particular feature) and the feature-complete trajectory would suggest that the given feature played a more prominent role in shaping the structure of the feature-complete trajectory.
 We found that hand-annotated narrative details provided the most structure to the feature-complete trajectory, whereas transcriptions of onscreen text provided the least structure (Fig.~\ref{fig:feature-importance}A).
@@
 
-As described below, we next considered three more naunced measures of the memory performance and dynamics that are typically associated with list-learning studies.
+As described below, we next considered three more nuanced measures of the memory performance and dynamics that are typically associated with list-learning studies.
 We also provide a software package, \texttt{Quail}, for carrying out these analyses~\citep{HeusEtal17b}.
@@
 \paragraph{Probability of first recall (PFR).}  PFR curves~\citep{WelcBurn24, PostPhil65, AtkiShif68} reflect the probability that an item will be recalled first as a function of its serial position during encoding.
-To carry out this analysis, we initialized a number-of-participants (17) by number-of-video-events (34) matrix.
+To carry out this analysis, we initialized a number-of-participants (17) by number-of-video-events (34) matrix of zeros.
 Then for each participant, we found the index of the video event that was recalled first (i.e., the video event whose topic vector was most strongly correlated with that of the first recall event) and filled in that index in the matrix with a 1.
-Finally, we averaged over the rows of the matrix, resulting in a 1 by 34 array representing the proportion of participant that recalled an event as a function of serial position during encoding (Fig.~\ref{fig:list-learning}A).
+Finally, we averaged over the rows of the matrix, resulting in a 1 by 34 array representing the proportion of participant that recalled an event first, as a function of the order of the event's appearance in the video (Fig.~\ref{fig:list-learning}A).
 
@@
 Then, for each recalled event (and each participant), we found the index of the video event that the recalled event most closely matched (via the correlation between the events' topic vectors) and entered a 1 into that position in the matrix (i.e., for the given participant and event).
-This resulted in a matrix whose entries indicated whether or not each event was recalled by each participant (depending on whether the corresponding entires were set to one or zero.
-Finally, we averaged over the rows of the matrix to yield a 1 by 34 array representing the proportion of participants that recalled each event as a function of its serial position (Fig.~\ref{fig:list-learning}C).
+This resulted in a matrix whose entries indicated whether or not each event was recalled by each participant (depending on whether the corresponding entires were set to one or zero).
+Finally, we averaged over the rows of the matrix to yield a 1 by 34 array representing the proportion of participants that recalled each event as a function of the order of the event's appearance in the video (Fig.~\ref{fig:list-learning}C).
 
 \paragraph{Temporal clustering scores.} Temporal clustering refers to the extent to which participants group their recall responses according to encoding position~\citep{PolyEtal09}.
-For instance, if the participant recalled the video events in the exact order they occurred, this would yield a score of 1.
-If the participant recalled the video events in reverse order, this would yield a score of 0.
-Similarly, if the participant recalled the events in random order, this yield yield an expected score of 0.5.
+For instance, if a participant recalled the video events in the exact order they occurred, this would yield a score of 1.
+If a participant recalled the video events in reverse order, this would yield a score of 0.
+Similarly, if a participant recalled the events in random order, this yield yield an expected score of 0.5.
 For each recall event transition (and separately for each participant), we sorted all not-yet-recalled events according to their absolute lag (i.e., distance away in the video).
@@
 
-\paragraph{Semantic clustering scores.} Semantic clustering measures the extent to which participants grouped their recall responses according to semantic similarity~\citep{PolyEtal09}.
+\paragraph{Semantic clustering scores.} Semantic clustering measures the extent to which participants clustered their recall responses according to semantic similarity~\citep{PolyEtal09}.
 Here, we used the topic vectors for each event as a proxy for its semantic content.
@@
 The observed RMSD values reached significance (i.e., $p < 0.05$, reflecting that more than 95\% of the null RMSD values were greater than the observed RMSD value) for nine of the participants (3, 4, 8--13, and 17).
-(For the remaining participants this test yielded $p$s$ < 0.25$.)  The observed RMSD values were also reliably correlated with hand-annotated memory performance across participants ($r = -0.57, p = 0.016$).
+(For the remaining participants this test yielded $0.05 \leq p < 0.25$.)  The observed RMSD values were also reliably correlated with hand-annotated memory performance across participants ($r = -0.57, p = 0.016$).
 In other words, a closer match between the video and recall topic trajectories was related to better overall recall performance.
@@
 We tested whether participants who recalled more events were also more \textit{precise} in their recollections.
-For each participant, we computed the correlation between the topic vectors for each recall event and that of its matching video event (only for the events which they recalled).
-This resulted in a single number for each recalled event,  indexing how similar the recall event was to its matching video event.
+For each participant, we computed the correlation between the topic vectors for each recall event and that of its closest-matching video event (only for the events which they recalled).
 We defined the precision as the average video-recall correlation across all of the events a participant recalled.
-We found a strong correlation between hand-annotated memory performance and precision, suggesting that participants who remembered more events also remembered them more veridically ($r= 0.74, p = 0.0006$).
+We found a strong correlation between hand-annotated memory performance and precision, suggesting that participants who remembered more events also remembered them more veridically ($r = 0.74, p = 0.0006$).
 
@@
 That is, how uniquely a recalled event's topic vector matched a given video event topic vector, versus the topic vectors for the other video events.
-\textbf{JRM STOPPED HERE}
 We hypothesized that participants with high memory performance might describe each event in a more distinctive way (relative to those with lower memory performance who might describe events in a more general way).
-To this end, we computed a `distinctiveness' score for each participant (i.e., 1 - the correlation between a recall event and all non-matching video events).
-Then, we averaged this measure over recall events within participant.
-We found that participants with higher hand annotated memory performance also had higher distinctiveness scores (Pearson's $r(16) = 0.8, p = 0.0001$).
+To test this hypothesis we define a distinctiveness score for each recalled event as
+\[
+  d(\mathrm{event}) = 1 - \bar{c}(\mathrm{event}),
+\]
+where $\bar{c}(\mathrm{event})$ is the average correlation between the given recalled event's topic vector and the topic vectors from all video events \textit{except} the best-matching video event.
+We then averaged these distinctiveness scores across all of the events recalled by the given participant.
+We found that participants with higher average distinctiveness scores tended to also have better hand-annotated memory performance ($r = 0.8, p = 0.0001$).
 
-Lastly, we tested whether participants with better memory performance were also more likely to remember the events in order.
-For each participant, we computed the Spearman rank correlation between the order of events that the participant recalled and the actual order of events (filtering events that were actually recalled).
-We found that participants who recalled more events also recalled more of them in order (Pearson's $r(16) = 0.5, p = 0.04$).
-In summary, we found that better memory performance was associated with more precise, distinctive and ordered recalls.
+\paragraph*{Other order effects.}
+We tested whether participants with better memory performance were also more likely to remember the events in order.
+For each participant, we computed the Spearman rank correlation between the order of events that the participant recalled and the order the events actually occurred in the video (considering in the analysis only the events that the participant recalled).
+Participants who recalled more events also recalled more of them in order ($r = 0.5, p = 0.04$).
+In summary, we found that better memory performance was associated with more precise, distinctive, and ordered recalls.
 
-\subsection*{Additional measures of naturalistic memory}
-\textbf{Precision.} This measure gives us an indication of the specific match between a video event and recall event, where values approaching 1 are highly precise and lower values are inprecise.
-We defined ``precision'' as the correlation between a recall event and its matching (i.e., argmax) video event.
-
-\textbf{Distinctiveness.} Distinctiveness quantifies how similar a recall event is to all non-matching video events.
-It provides a metric of how uniquely a particular recall event describes a particular video event.
-To compute it, a given recall event is correlated to all video events, the argmax is removed and the rest of the values are averaged.
-The resulting value is subtracted from 1 such that larger values indicate a more distinctive recall event.
-
-\section*{Participant-level results referenced in the main text}
+\section*{Participant-level figures referenced in the main text}
 
@@
 
-\begin{figure}[tp]
+\begin{figure}[htp]
 \centering
-\includegraphics[width=1\textwidth]{figs/corrmats}
-\caption{\small \textbf{Recall model correlation matrices and event segmentation fits.} Each participant's timepoint-by-timepoint recall correlation matrix.
-The yellow boxes represent ``events'' identified by a hidden Markov model.}
+\includegraphics[width=\textwidth]{figs/corrmats}
+\caption{\small \textbf{Recall trajectory temporal correlation matrices and event segmentation fits.} Each panel is in the same format as Figure~2E in the main text.
+The yellow boxes indicate HMM-identified event boundaries.}
 \label{fig:corrmats}
@@
 
-\begin{figure}[tp]
+\begin{figure}[htp]
 \centering
-\includegraphics[width=1\textwidth]{figs/matchmats}
-\caption{\small \textbf{Video-recall event model correlation matrices.} Each participant's video event by recall event correlation matrix.
-The yellow boxes represent the maximum correlation in each column.}
+\includegraphics[width=\textwidth]{figs/matchmats}
+\caption{\small \textbf{Video-recall event correlation matrices.}  Each panel is in the same format as Figure~2G in the main text.  The yellow boxes mark the maximum correlation in each column.}
 \label{fig:matchmats}
@@
 
-%\newpage
+\newpage
 \renewcommand{\refname}{Supplemental references}

### 2018-09-05 code/scripts/searchlight_movie.py
updated and checked all notebooks and code

@@ -1,0 +1,31 @@
+import sys
+import numpy as np
+from nilearn.image import load_img
+from brainiak.searchlight.searchlight import Searchlight
+
+subid = sys.argv[1]
+data = load_img('/idata/cdl/data/fMRI/andy/sherlock/data/sherlock_movie_s%s_10000.nii.gz' % str(subid)).get_data()
+
+mask = data[:,:,:,0]!=10000
+model = np.load('/idata/cdl/data/fMRI/andy/sherlock/data/movie_corrmat.npy')
+params = dict(sl_rad=5)
+
+# Create searchlight object
+sl = Searchlight(**params)
+
+# Distribute data to processes
+sl.distribute([data], mask)
+sl.broadcast(model)
+
+# Define voxel function
+def sfn(l, msk, myrad, bcast_var):
+    from scipy.spatial.distance import cdist
+    from scipy.stats import pearsonr
+    b = l[0][msk,:].T
+    c = 1 - cdist(b, b, 'correlation').ravel()
+    return pearsonr(c, bcast_var.ravel())[0]
+
+# Run searchlight
+result = sl.run_searchlight(sfn)
+
+np.save('/idata/cdl/data/fMRI/andy/sherlock/analyses/searchlight_movie/s%s' % str(subid), result)

### 2018-09-05 code/scripts/searchlight_movie_perms.py

@@ -1,0 +1,53 @@
+import sys
+import numpy as np
+from nilearn.image import load_img
+from brainiak.searchlight.searchlight import Searchlight
+import pandas as pd
+
+subid = int(sys.argv[1])
+perm = int(sys.argv[2])
+
+np.random.seed(perm)
+
+# load fmri data
+data = load_img('/idata/cdl/data/fMRI/andy/sherlock/data/sherlock_movie_s%s_10000.nii.gz' % str(subid)).get_data()
+
+# load dtw warp path and extract the movie path
+#path = np.load('/idata/cdl/data/fMRI/andy/sherlock/data/s%s_dtw_path.npy' % str(subid))
+#movie_path = np.array(list(map(lambda x: x[0], path)))
+
+# reindex the fmri data with the movie path
+#data = data[:,:,:, movie_path]
+
+# create the mask
+mask = data[:,:,:,0]!=10000
+
+# load video model
+model = np.load('/idata/cdl/data/fMRI/andy/sherlock/data/movie_corrmat.npy')
+
+# shift the video model
+shift = np.random.randint(1, model.shape[0]-1)
+shifted = np.roll(model, shift=shift, axis=0)
+
+# recompute shifted correlation matrix
+model = pd.DataFrame(shifted).T.corr().values
+
+# Create searchlight object
+params = dict(sl_rad=5)
+sl = Searchlight(**params)
+
+# Distribute data to processes
+sl.distribute([data], mask)
+sl.broadcast(model)
+
+# Define voxel function
+def sfn(l, msk, myrad, bcast_var):
+    from scipy.spatial.distance import cdist
+    from scipy.stats import pearsonr
+    b = l[0][msk,:].T
+    c = 1 - cdist(b, b, 'correlation').ravel()
+    return pearsonr(c, bcast_var.ravel())[0]
+
+# Run searchlight
+result = sl.run_searchlight(sfn)
+np.save('/idata/cdl/data/fMRI/andy/sherlock/analyses/searchlight_movie/perms/s%s_perm%s_shift%s' % (str(subid), str(perm), str(shift)), result)

### 2018-09-05 code/scripts/searchlight_recall.py

@@ -1,0 +1,43 @@
+import sys
+import numpy as np
+from nilearn.image import load_img
+from brainiak.searchlight.searchlight import Searchlight
+
+subid = sys.argv[1]
+
+# load fmri data
+data = load_img('/idata/cdl/data/fMRI/andy/sherlock/data/sherlock_movie_s%s_10000.nii.gz' % str(subid)).get_data()
+
+# load dtw warp path and extract the movie path
+path = np.load('/idata/cdl/data/fMRI/andy/sherlock/data/s%s_dtw_path.npy' % str(subid))
+movie_path = np.array(list(map(lambda x: x[0], path)))
+
+# reindex the fmri data with the movie path
+data = data[:,:,:, movie_path]
+
+# create the mask
+mask = data[:,:,:,0]!=10000
+
+# load the recall model
+model = np.load('/idata/cdl/data/fMRI/andy/sherlock/data/s%s_recall_corrmat_dtw.npy' % str(subid))
+
+# Create searchlight object
+params = dict(sl_rad=5)
+sl = Searchlight(**params)
+
+# Distribute data to processes
+sl.distribute([data], mask)
+sl.broadcast(model)
+
+# Define voxel function
+def sfn(l, msk, myrad, bcast_var):
+    from scipy.spatial.distance import cdist
+    from scipy.stats import pearsonr
+    b = l[0][msk,:].T
+    c = 1 - cdist(b, b, 'correlation').ravel()
+    return pearsonr(c, bcast_var.ravel())[0]
+
+# Run searchlight
+result = sl.run_searchlight(sfn)
+
+np.save('/idata/cdl/data/fMRI/andy/sherlock/analyses/searchlight_recall/s%s' % str(subid), result)

### 2018-09-05 code/scripts/searchlight_recall_perms.py

@@ -1,0 +1,53 @@
+import sys
+import numpy as np
+from nilearn.image import load_img
+from brainiak.searchlight.searchlight import Searchlight
+import pandas as pd
+
+subid = int(sys.argv[1])
+perm = int(sys.argv[2])
+
+np.random.seed(perm)
+
+# load fmri data
+data = load_img('/idata/cdl/data/fMRI/andy/sherlock/data/sherlock_movie_s%s_10000.nii.gz' % str(subid)).get_data()
+
+# load dtw warp path and extract the movie path
+path = np.load('/idata/cdl/data/fMRI/andy/sherlock/data/s%s_dtw_path.npy' % str(subid))
+movie_path = np.array(list(map(lambda x: x[0], path)))
+
+# reindex the fmri data with the movie path
+data = data[:,:,:, movie_path]
+
+# create the mask
+mask = data[:,:,:,0]!=10000
+
+# load the recall model
+model = np.load('/idata/cdl/data/fMRI/andy/sherlock/data/s%s_recall_model_dtw.npy' % str(subid))
+
+# shift the recall model
+shift = np.random.randint(1, model.shape[0]-1)
+shifted = np.roll(model, shift=shift, axis=0)
+
+# recompute shifted correlation matrix
+model = pd.DataFrame(shifted).T.corr().values
+
+# Create searchlight object
+params = dict(sl_rad=5)
+sl = Searchlight(**params)
+
+# Distribute data to processes
+sl.distribute([data], mask)
+sl.broadcast(model)
+
+# Define voxel function
+def sfn(l, msk, myrad, bcast_var):
+    from scipy.spatial.distance import cdist
+    from scipy.stats import pearsonr
+    b = l[0][msk,:].T
+    c = 1 - cdist(b, b, 'correlation').ravel()
+    return pearsonr(c, bcast_var.ravel())[0]
+
+# Run searchlight
+result = sl.run_searchlight(sfn)
+np.save('/idata/cdl/data/fMRI/andy/sherlock/analyses/searchlight_recall/perms/s%s_perm%s_shift%s' % (str(subid), str(perm), str(shift)), result)

### 2018-09-05 paper/main.tex
backing up edits to supplemental materials [WIP]
renamed supplemental materials supporting information

@@
 
-\newcommand{\topics}{S1}
-\newcommand{\corrmats}{S2}
-\newcommand{\matchmats}{S3}
-\newcommand{\featureimportance}{S4}
-\newcommand{\listlearning}{S5}
-\newcommand{\topicopt}{S6}
+\newcommand{\topicopt}{S1}
+\newcommand{\topics}{S2}
+\newcommand{\featureimportance}{S3}
+\newcommand{\listlearning}{S4}
+\newcommand{\corrmats}{S5}
+\newcommand{\matchmats}{S6}
 
@@
 This yields a single correlation coefficient for each video event, describing how closely participants' recalls of the event tended to reliably capture its content (Fig.~\ref{fig:topics}A).
-(We also examined how different comparisons between each video event's topic vector and the corresponding recall event topic vectors related to hand-annotated characterizations of memory performance; see \textit{Supplemental Materials}).
+(We also examined how different comparisons between each video event's topic vector and the corresponding recall event topic vectors related to hand-annotated characterizations of memory performance; see \textit{Supporting information}).
 Given this summary of which events were recalled reliably (or not), we next asked whether the better-remembered or worse-remembered events tended to reflect particular topics.
@@
 These reflected the dynamic content of each participant's recalls.
-Note: for details on how we selected the video and recall window lengths and number of topics, see \textit{Supplemental Materials} and Figure~\topicopt.
+Note: for details on how we selected the video and recall window lengths and number of topics, see \textit{Supporting information} and Figure~\topicopt.
 

### 2018-09-05 paper/main.tex
inputted paxton edits

@@
 Any given moment of an experience derives meaning from surrounding moments, as well as from longer-range temporal associations~\citep[e.g., ][]{LernEtal11}.
-Therefore the timecourse of how an event unfolds is fundamental to its overall meaning.
+Therefore the timecourse describing how an event unfolds is fundamental to its overall meaning.
 Further, this hierarchy formed by our subjective experiences at different timescales defines a \textit{context} for each new moment~\citep[e.g., ][]{HowaKaha02, HowaEtal14}, and plays an important role in how we interpret that moment and remember it later~\citep[for review see][]{MannEtal15}.
@@
 Here we sought to examine how the temporal dynamics of a ``naturalistic'' experience were reflected in participants' later memories of that experience.
-We analyzed an open dataset which comprised behavioral and functional Magnetic Resonance Imaging (fMRI) data collected as participants viewed and then verbally recalled an episode of the BBC television series \textit{Sherlock}~\citep{ChenEtal17}.
-We developed a computational framework for characterizing the temporal dynamics of the moment-by-moment content of the episode (and of participants' verbal recalls).
+We analyzed an open dataset that comprised behavioral and functional Magnetic Resonance Imaging (fMRI) data collected as participants viewed and then verbally recalled an episode of the BBC television series \textit{Sherlock}~\citep{ChenEtal17}.
+We developed a computational framework for characterizing the temporal dynamics of the moment-by-moment content of the episode and of participants' verbal recalls.
 Specifically, we use topic modeling~\citep{BleiEtal03} to characterize the thematic conceptual (semantic) content present in each moment of the episode and recalls, and we use Hidden Markov Models~\citep{Rabi89, BaldEtal17} to discretize the evolving semantic content into events.
@@
 In other words, the episode's topic trajectory is a formalization of its gist.
-Under this framework, successful remembering entails verbally ``traversing'' the topic trajectory of the original episode, thereby reproducing the gist of the original episode.
+Under this framework, successful remembering entails verbally ``traversing'' the topic trajectory of the original episode, thereby reproducing the original episode's gist.
 In addition, comparing the shapes of the topic trajectories of the original episode and of participants' retellings of the episode reveals which aspects of the episode were preserved (or lost) in the translation into memory.
@@
 This information included: a brief narrative description of what was happening; whether the scene took place indoors vs.
-outdoors; names of any characters on the screen; names of any characters who were in focus in the camera; names of characters who were speaking; the location where the scene took place; the camera angle (close up, medium, long, etc.); whether or not background music was present; and other similar details (for a full list of annotated features see \textit{Methods}).
+outdoors; names of any characters on the screen; names of any characters who were in focus in the camera shot; names of characters who were speaking; the location where the scene took place; the camera angle (close up, medium, long, etc.); whether or not background music was present; and other similar details (for a full list of annotated features see \textit{Methods}).
 We took from these annotations the union of all unique words (excluding stop words, such as ``and,'' ``or,'' ``but,'' etc.) across all features and scenes as the ``vocabulary'' for the topic model.
@@
 Note that our approach is similar in some respects to Dynamic Topic Models~\citep{BleiLaff06}, in that we sought to characterize how the thematic content of the episode evolved over time.
-However, whereas Dynamic Topic Models are designed to characterize the how the properties of collections of documents change over time, our approach allows us to examine the topic dynamics within a single video.
+However, whereas Dynamic Topic Models are designed to characterize how the properties of \textit{collections} of documents change over time, our sliding window approach allows us to examine the topic dynamics within a single document (or video).
 Specifically, our approach yielded (via the topic proportions matrix) a single \textit{topic vector} for each timepoint of the episode (we set timepoints to match the acquisition times of the 1976 fMRI volumes collected as participants viewed the episode).
@@
 \caption{\small \textbf{Methods overview.} We used hand-annotated descriptions of each moment of video to fit a topic model.
-Three example video frames, and their associated descriptions are displayed (top two rows).
+Three example video frames and their associated descriptions are displayed (top two rows).
 Participants later recalled the video (in the third row, we show example recalls of the same three scenes from participant 13).
@@
 We applied the same topic model (already trained on the video annotations) to each participant's recalls.
-Analogous to how we analyzed the time-varying content of the video, to obtain similar estimates for participants' recalls we treated each (overlapping) 10 sentence ``window'' of their transcript as a ``document'' and then computed the most probable mix of topics reflected in each timepoint's sentences.
+Analogous to how we analyzed the time-varying content of the video, to obtain similar estimates for participants' recalls, we treated each (overlapping) 10 sentence ``window'' of their transcript as a ``document'' and then computed the most probable mix of topics reflected in each timepoint's sentences.
 This yielded, for each participant, a number-of-sentences by number-of-topics topic proportions matrix that characterized how the topics identified in the original video were reflected in the participant's recalls.
@@
 Two clear patterns emerged from this set of analyses.
-First, although every individual participant's recalls could be segmented into discrete events (e.g., every individual participant's recall correlation matrix exhibited clear block diagonal structure; Fig.~\corrmats), each participant appeared to have a unique \textit{recall resolution}, reflected in the sizes of those blocks.
+First, although every individual participant's recalls could be segmented into discrete events (i.e., every individual participant's recall correlation matrix exhibited clear block diagonal structure; Fig.~\corrmats), each participant appeared to have a unique \textit{recall resolution}, reflected in the sizes of those blocks.
 For example, some participants' recall topic proportions segmented into just a few events (e.g., Participants 1, 4, and 15), while others' recalls segmented into many shorter duration events (e.g., Participants 12, 13, and 17).
@@
 This yields a sequence of ``presented'' events from the original movie, and a sequence of (potentially differently ordered) ``recalled'' events for each participant.
-Analogous to classic list-learning studies, we can then examine participants' recall sequences by asking which events they tended to recall first~\citep[e.g., probability of first recall; Fig.~\listlearning A; ][]{WelcBurn24, PostPhil65, AtkiShif68}; how participants most often transition between recalls of the events as a function of the temporal distance between them~\citep[e.g., lag-conditional response probability; Fig.~\listlearning B; ][]{Kaha96}; and which events they were likely to remember overall~\citep[e.g., serial position recall analyses; Fig.~\listlearning C; ][]{Murd62a}.
+Analogous to classic list-learning studies, we can then examine participants' recall sequences by asking which events they tended to recall first~\citep[probability of first recall; Fig.~\listlearning A;][]{WelcBurn24, PostPhil65, AtkiShif68}; how participants most often transition between recalls of the events as a function of the temporal distance between them~\citep[lag-conditional response probability; Fig.~\listlearning B;][]{Kaha96}; and which events they were likely to remember overall~\citep[serial position recall analyses; Fig.~\listlearning C;][]{Murd62a}.
 In list-learning studies, this set of three analyses may be used to gain a nearly complete view into the sequences of recalls participants made~\citep[e.g., ][]{Kaha12}.
-Extending these analyses to apply to naturalistic stimuli and recall~\citep{HeusEtal17b} highlights that, in naturalistic recall, these analyses provide a wholly incomplete picture: they leave out any attempt to quantify participants' abilities to capture the \textit{content} of what occurred in the video (i.e., their only experimental instruction!).
+Extending these analyses to apply to naturalistic stimuli and recall~\citep{HeusEtal17b} highlights that, in naturalistic recall, these analyses provide a wholly incomplete picture: they leave out any attempt to quantify participants' abilities to capture the \textit{content} of what occurred in the video-- their only experimental instruction!
 
@@
 However, it is difficult to gain deep insights into that content solely by examining the topic proportion matrices (e.g., Figs.~\ref{fig:model}A, D) or the corresponding correlation matrices (Figs.~\ref{fig:model}B, E, \corrmats).
-To visualize the time-varying high-dimensional content in a more intuitive way~\citep{HeusEtal18a} we projected the topic proportion matrices onto a two-dimensional space using Uniform Manifold Approximation and Projection~\citep[UMAP; ][]{McInHeal18}.
+To visualize the time-varying high-dimensional content in a more intuitive way~\citep{HeusEtal18a} we projected the topic proportions matrices onto a two-dimensional space using Uniform Manifold Approximation and Projection~\citep[UMAP; ][]{McInHeal18}.
 In this lower-dimensional space, each point represents a single video or recall event, and the distances between the points reflect the distances between the events' associated topic vectors (Fig.~\ref{fig:trajectory}).
@@
 The arrows reflect the average transition direction through topic space taken by any participants whose trajectories crossed that part of topic space; blue denotes reliable agreement across participants via a Rayleigh test ($p < 0.05$, corrected).
-\textbf{C.} The recall topic trajectories taken by each individual participant (1--17).
+\textbf{C.} The recall topic trajectories (gray) taken by each individual participant (P1--P17).
 The video's trajectory is shown in black for reference.
@@
 Rayleigh tests revealed the set of locations in topic space at which these across-participant distributions exhibited reliable peaks (blue arrows in Fig.~\ref{fig:trajectory}B).
-We observed that the locations traversed by nearly the entire the video trajectory exhibited such peaks.
+We observed that the locations traversed by nearly the entire video trajectory exhibited such peaks.
 In other words, participants exhibited similar trajectories that also matched the trajectory of the original video (Fig.~\ref{fig:trajectory}C).
@@
 To visualize the result, we created a ``wordle'' image~\citep{MuelEtal18} where words weighted more heavily by better-remembered topics appear in a larger font (Fig.~\ref{fig:topics}B, green box).
-Events that reflected topics weighting heavily on characters like ``Sherlock'' and ``John'' (i.e., the main characters) and locations like ``221b Baker Street'' (i.e., a major recurring location; the address of the flat that Sherlock and John share) were best remembered.
-An analogous analysis revealed which themes were poorly remembered; here in computing the weighted average over events' topic vectors we weighted each event in \textit{inverse} proportion to how well it was remembered (Fig.~\ref{fig:topics}B, red box).
+Events that reflected topics weighting heavily on characters like ``Sherlock'' and ``John'' (i.e., the main characters) and locations like ``221b Baker Street'' (i.e., a major recurring location and the address of the flat that Sherlock and John share) were best remembered.
+An analogous analysis revealed which themes were poorly remembered.
+Here in computing the weighted average over events' topic vectors we weighted each event in \textit{inverse} proportion to how well it was remembered (Fig.~\ref{fig:topics}B, red box).
 This revealed that events with relatively minor characters such as ``Mike,'' ``Jeffrey,'' and ``Molly,'' as well as less-integral plot locations (e.g., ``hospital'' and ``office'') were least well-remembered.
@@
 In addition to constructing overall summaries, assessing the video and recall topic vectors from individual recalls can provide further insights.
-Specifically, for any given event we can construct a wordle from that event's topic vector, and we can construct a similar wordle from the average topic vectors produced by all participants' recalls of that event.
+Specifically, for any given event we can construct two wordles: one from the original video event's topic vector, and a second from the average topic vectors produced by all participants' recalls of that event.
 We can then examine those wordles visually to gain an intuition for which aspects of the video event were recapitulated in participants' recalls of that event.
@@
 
-The results thus far tell us about which aspects of the dynamic content in the episode participants watched were preserved or altered in participants' memories of the episode.
+The results thus far inform us about which aspects of the dynamic content in the episode participants watched were preserved or altered in participants' memories of the episode.
 We next carried out a series of analyses aimed at understanding which brain structures might implement these processes.
@@
 Specifically, we used a searchlight procedure to identify the extent to which each cluster of voxels exhibited a timecourse (as the participants watched the video) whose temporal correlation matrix matched the temporal correlation matrix of the original video's topic proportion matrix (Fig.~\ref{fig:model}B).
-As shown in Figure~\ref{fig:brainz}A, the analysis revealed a network of regions including bilateral frontal and cingulate cortex, suggesting that these regions may play a role in maintaining information relevant to the narrative structure of the video.
+As shown in Figure~\ref{fig:brainz}A, the analysis revealed a network of regions including bilateral frontal cortex and cingulate cortex, suggesting that these regions may play a role in maintaining information relevant to the narrative structure of the video.
 In a second analysis, we sought to identify which brain structures' responses (while viewing the video) reflected how each participant would later \textit{recall} the video.
-In particular, we used an analogous searchlight procedure to identify clusters of voxels whose temporal correlation matrices reflected the temporal correlation matrix of the topic proportions for each individual's recalls (Figs.~\ref{fig:model}D, \corrmats).
-As shown in Figure~\ref{fig:brainz}B, the analysis revealed a network of regions including the ventromedial prefrontal cortex (vmPFC), anterior cingulate, and right medial temporal lobe (rMTL), suggesting that these regions may play a role in transforming each individual's experience into memory.
+We used an analogous searchlight procedure to identify clusters of voxels whose temporal correlation matrices reflected the temporal correlation matrix of the topic proportions for each individual's recalls (Figs.~\ref{fig:model}D, \corrmats).
+As shown in Figure~\ref{fig:brainz}B, the analysis revealed a network of regions including the ventromedial prefrontal cortex (vmPFC), anterior cingulate cortex, and right medial temporal lobe (rMTL), suggesting that these regions may play a role in transforming each individual's experience into memory.
 
@@
 In brief, participants ($n=17$) viewed the first 48 minutes of ``A Study in Pink'', the first episode of the BBC television series \textit{Sherlock}, while fMRI volumes were collected (TR = 1500~ms).
-The stimulus was divided into a 23 minute (946~TR) and a 25~min (1030~TR) segment to facilitate technical issues related to the scanner.
+The stimulus was divided into a 23~min (946~TR) and a 25~min (1030~TR) segment to mitigate technical issues related to the scanner.
 After finishing the clip, participants were instructed to \citep[quoting from][]{ChenEtal17} ``describe what they recalled of the movie in as much detail as they could, to try to recount events in the original order they were viewed in, and to speak for at least 10 minutes if possible but that longer was better.
@@
 
-We created similar topic proportion matrices using hand-annotated transcripts of each participant's recall of the video~\citep[annotated by ][]{ChenEtal17}.
-We tokenized the transcript into a list of sentences, and then re-organized the list into overlapping sliding windows spanning 10 sentences each; we in turn transformed each window's sentences into a word count vector (using the same vocabulary as for the video model).
+We created similar topic proportions matrices using hand-annotated transcripts of each participant's recall of the video~\citep[annotated by ][]{ChenEtal17}.
+We tokenized the transcript into a list of sentences, and then re-organized the list into overlapping sliding windows spanning 10 sentences each; in turn we transformed each window's sentences into a word count vector (using the same vocabulary as for the video model).
 We then used the topic model already trained on the video scenes to compute the most probable topic proportions for each sliding window.
@@
 
-Next, we constructed two sets of ``template'' matrices; one reflected the video's topic trajectory and the other reflected each participant's recall topic trajectory.
+Next, we constructed two sets of ``template'' matrices: one reflected the video's topic trajectory and the other reflected each participant's recall topic trajectory.
 To construct the video template, we computed the correlations between the topic proportions estimated for every pair of TRs (prior to segmenting the trajectory into discrete events; i.e., the correlation matrix shown in Figs.~\ref{fig:model}B and \ref{fig:brainz}A).

### 2018-09-05 paper/main.tex
inputted andy's comments on main text

@@
 We propose a framework for mapping naturalistic experiences onto geometric spaces that characterize how they unfold over time.
-New insights emerge when we apply this approach to a naturalistic memory experiment which had participants view and recount a video.
+We apply this approach to a naturalistic memory experiment which had participants view and recount a video.
 We found that the shapes of the trajectories formed by participants' recountings were all highly similar to that of the original video, but participants differed in the level of detail they remembered.
@@
 More nuanced studies might incorporate self-reported confidence measures as a proxy for memory strength, or ask participants to discriminate between ``recollecting'' the (contextual) details of an experience or having a general feeling of ``familiarity'' \citep{Yone02}.
-However, characterizing and evaluating memory in more realistic contexts (e.g., recounting a recent experience to a friend) is fundamentally different in at least three ways~\citep[also see][for a review]{KoriGold94}.
+However, characterizing and evaluating memory in more realistic contexts (e.g., recounting a recent experience to a friend) is fundamentally different in at least three ways~\citep[for review also see][]{KoriGold94, HukEtal18}.
 First, real world recall is continuous, rather than discrete.
@@
 Second, the specific words used to describe an experience have little bearing on whether the experience should be considered to have been ``remembered.''  Asking whether the rememberer has precisely reproduced a specific set of words to describe a given experience is nearly orthogonal to whether they were actually able to remember it.
-In classic (e.g., list-learning) memory studies, counting the number or proportion of precise recalls is often a primary metric of assessing the quality of participants' memories.
+In classic (e.g., list-learning) memory studies, by contrast, counting the number or proportion of precise recalls is often a primary metric of assessing the quality of participants' memories.
 Third, one might remember the \textit{gist} or essence of an experience but forget (or neglect to recount) particular details.
@@
 Next, we fit a topic model with (up to) $K = 100$ topics to this collection of documents.
-We found that 28 unique topics (with non-zero weights) were sufficient to describe the time-varying content of the movie (see \textit{Methods}; Figs.~\ref{fig:schematic}, \topics).
+We found that 27 unique topics (with non-zero weights) were sufficient to describe the time-varying content of the video (see \textit{Methods}; Figs.~\ref{fig:schematic}, \topics).
 Note that our approach is similar in some respects to Dynamic Topic Models~\citep{BleiLaff06}, in that we sought to characterize how the thematic content of the episode evolved over time.
@@
 \textbf{H.} Average correlations between each pair of video events and recalled events (across all 17 participants).
-To create the figure, each recalled event was assigned to the video event with the most correlated topic vector (yellow boxes in panels G and H).}
+To create the figure, each recalled event was assigned to the video event with the most correlated topic vector (yellow boxes in panels G and H).
+The heat maps in each panel were created using \texttt{Seaborn}~\citep{WaskEtal16}.}
 \label{fig:model}
@@
 To examine these patterns in detail, we computed the timepoint-by-timepoint correlation matrix for the example participant's recall topic proportions (Fig.~\ref{fig:model}E).
-As in the video correlation matrix (Fig.~\ref{fig:model}B), the example partipant's recall correlation matrix has a strong block diagonal structure, indicating that their recalls are discretized into separated events.
+As in the video correlation matrix (Fig.~\ref{fig:model}B), the example participant's recall correlation matrix has a strong block diagonal structure, indicating that their recalls are discretized into separated events.
 As for the video correlation matrix, we can use an HMM, along with the aforementioned number-of-events optimization procedure (also see \textit{Methods}) to determine how many events are reflected in the participant's recalls and where specifically the event boundaries fall (outlined in yellow).
@@
 One approach to linking the experienced (video) and recalled events is to label each recalled event as matching the video event with the most similar (i.e., most highly correlated) topic vector (Figs.~\ref{fig:model}G, \matchmats).
-This yields a sequence of ``presented'' events from the original movie, and a sequence of (potentially differently ordered) ``recalled'' events for each participant.
+This yields a sequence of ``presented'' events from the original video, and a sequence of (potentially differently ordered) ``recalled'' events for each participant.
 Analogous to classic list-learning studies, we can then examine participants' recall sequences by asking which events they tended to recall first~\citep[probability of first recall; Fig.~\listlearning A;][]{WelcBurn24, PostPhil65, AtkiShif68}; how participants most often transition between recalls of the events as a function of the temporal distance between them~\citep[lag-conditional response probability; Fig.~\listlearning B;][]{Kaha96}; and which events they were likely to remember overall~\citep[serial position recall analyses; Fig.~\listlearning C;][]{Murd62a}.
@@
 \textbf{B.} The average two-dimensional trajectory captured by participants' recall sequences, with the same format and coloring as the trajectory in Panel A.
-To compute the event positions, we matched each recalled event with an event from the original video (see text), and then we averaged the positions of all events with the same label.
+To compute the event positions, we matched each recalled event with an event from the original video (see \textit{Results}), and then we averaged the positions of all events with the same label.
 The arrows reflect the average transition direction through topic space taken by any participants whose trajectories crossed that part of topic space; blue denotes reliable agreement across participants via a Rayleigh test ($p < 0.05$, corrected).
@@
 We then computed (for each location) the distribution of angles formed by the lines defined by those line segments and a fixed reference line (the $x$-axis).
-Rayleigh tests revealed the set of locations in topic space at which these across-participant distributions exhibited reliable peaks (blue arrows in Fig.~\ref{fig:trajectory}B).
+Rayleigh tests revealed the set of locations in topic space at which these across-participant distributions exhibited reliable peaks (blue arrows in Fig.~\ref{fig:trajectory}B reflect significant peaks at $p < 0.05$, corrected).
 We observed that the locations traversed by nearly the entire video trajectory exhibited such peaks.
@@
 This yields a single correlation coefficient for each video event, describing how closely participants' recalls of the event tended to reliably capture its content (Fig.~\ref{fig:topics}A).
-(We also examined how different comparisons between each video event's topic vector and the corresponding recall event topic vectors related to hand-annotated characterizations of memory performance; see \textit{Supporting information}).
+(We also examined how different comparisons between each video event's topic vector and the corresponding recall event topic vectors related to hand-annotated characterizations of memory performance; see \textit{Supporting Information}).
 Given this summary of which events were recalled reliably (or not), we next asked whether the better-remembered or worse-remembered events tended to reflect particular topics.
@@
 As shown in Figure~\ref{fig:brainz}B, the analysis revealed a network of regions including the ventromedial prefrontal cortex (vmPFC), anterior cingulate cortex, and right medial temporal lobe (rMTL), suggesting that these regions may play a role in transforming each individual's experience into memory.
+In identifying regions whose responses to ongoing experiences reflect how those experiences will be remembered later, this latter analysis extends classic \textit{subsequent memory analyses}~\citep[e.g.,][]{PallWagn02} to domain of naturalistic stimuli.
 
@@
 
+Our work casts remembering as reproducing (behaviorally and neurally) the topic trajectory, or ``gist,'' of the original experience.
+This view draws inspiration from prior work aimed at elucidating the neural and behavioral underpinnings of how we process dynamic naturalistic experiences and remember them later.
 One approach to identifying neural responses to naturalistic stimuli (including experiences) entails building a model of the stimulus and searching for brain regions whose responses are consistent with the model.
@@
 So called \textit{inter-subject correlation} (ISC) and \textit{inter-subject functional connectivity} (ISFC) analyses effectively treat other people's brain responses to the stimulus as a ``model'' of how its features change over time.
-By contrast, in our present work we used topic models and HMMs to construct an explicit stimulus model (i.e., the topic trajectory of the movie).
+By contrast, in our present work we used topic models and HMMs to construct an explicit stimulus model (i.e., the topic trajectory of the video).
 When we searched for brain structures whose responses are consistent with the video's topic trajectory, we identified a network of structures that overlapped strongly with the ``long temporal receptive window'' network reported by the Hasson group~\citep[e.g., compare our Fig.~\ref{fig:brainz}A with the map of long temporal receptive window voxels in][]{LernEtal11}.
@@
 The role of the MTL in episodic memory encoding has been well-reported~\citep[e.g., ][]{PallWagn02, DavaEtAl03, RangEtal04, Dava06}.
-Prior work has also implicated the medial prefrontal cortex in representing ``schema'' knowledge~\citep[i.e., general knowledge about the format of an ongoing experience given prior similar experiences; ][]{KestEtal12, GilbMarl17}.
+Prior work has also implicated the medial prefrontal cortex in representing ``schema'' knowledge~\citep[i.e., general knowledge about the format of an ongoing experience given prior similar experiences; ][]{KestEtal12, SchlPres15, GilbMarl17, SpalEtal18}.
 Integrating across our study and this prior work, one interpretation is that the person-specific transformations mediated (or represented) by the rMTL and vmPFC may reflect schema knowledge being leveraged, formed, or updated, incorporating ongoing experience into previously acquired knowledge.
@@
 The stimulus was divided into a 23~min (946~TR) and a 25~min (1030~TR) segment to mitigate technical issues related to the scanner.
-After finishing the clip, participants were instructed to \citep[quoting from][]{ChenEtal17} ``describe what they recalled of the movie in as much detail as they could, to try to recount events in the original order they were viewed in, and to speak for at least 10 minutes if possible but that longer was better.
+After finishing the clip, participants were instructed to \citep[quoting from][]{ChenEtal17} ``describe what they recalled of the [episode] in as much detail as they could, to try to recount events in the original order they were viewed in, and to speak for at least 10 minutes if possible but that longer was better.
 They were told that completeness and detail were more important than temporal order, and that if at any point they realized they had missed something, to return to it.
@@
 After preprocessing the fMRI data and warping the images into a standard (3~mm$^3$ MNI) space, the voxel activations were $z$-scored (within voxel) and spatially smoothed using a 6~mm (full width at half maximum) Gaussian kernel.
-The fMRI data were also cropped so that all video-viewing data were aligned across partipants.
+The fMRI data were also cropped so that all video-viewing data were aligned across participants.
 This included a constant 3 TR (4.5~s) shift to account for the lag in the hemodynamic response.
@@
 These reflected the dynamic content of each participant's recalls.
-Note: for details on how we selected the video and recall window lengths and number of topics, see \textit{Supporting information} and Figure~\topicopt.
+Note: for details on how we selected the video and recall window lengths and number of topics, see \textit{Supporting Information} and Figure~\topicopt.
 
@@
 We parsed the topic trajectories of the video and participants' recalls into events using Hidden Markov Models~\citep{Rabi89}.
-Given the topic portions matrix (describing the mix of topics at each timepoint) and a number of states, $K$, an HMM recovers the set of state transitions that segments the timeseries into $K$ discrete states.
+Given the topic proportions matrix (describing the mix of topics at each timepoint) and a number of states, $K$, an HMM recovers the set of state transitions that segments the timeseries into $K$ discrete states.
 Following \cite{BaldEtal17}, we imposed an additional set of constraints on the discovered state transitions that ensured that each state was encountered exactly once (i.e., never repeated).
@@
 In Figure~\ref{fig:trajectory}B, we present an analysis aimed at characterizing locations in topic space that different participants move through in a consistent way (via their recall topic trajectories).
-The two-dimensional topic space used in our visualizations (Fig.~\ref{fig:trajectory}) ranged from -6 to 6 (arbitrary) units, in both the $x$ and $y$ dimensions.
+The two-dimensional topic space used in our visualizations (Fig.~\ref{fig:trajectory}) ranged from -5 to 5 (arbitrary) units in the $x$ dimension and from -6.5 to 2 units in the $y$ dimension.
 We divided this space into a grid of vertices spaced 0.25~units apart.
@@
 To create Figure~\ref{fig:trajectory}B we drew an arrow originating from each grid vertex, pointing in the direction of the average angle formed by line segments that passed within 0.5 units.
-We set the arrow lengths proportional to the $p$-values of the Rayleigh tests at each vertex.
-We also indicated any significant results ($p < 0.05$, corrected using the Benjamani-Hochberg procedure) by coloring the arrows in blue (darker blue denotes a lower $p$-value); all tests with $p \geq 0.05$ are displayed in gray and given a lower opacity value.
+We set the arrow lengths to be inversely proportional to the $p$-values of the Rayleigh tests at each vertex.
+Specifically, for each vertex we converted all of the angles of segments that passed within 0.5 units to unit vectors, and we set the arrow lengths at each vertex proportional to the length of the (circular) mean vector.
+We also indicated any significant results ($p < 0.05$, corrected using the Benjamani-Hochberg procedure) by coloring the arrows in blue (darker blue denotes a lower $p$-value, i.e., a longer mean vector); all tests with $p \geq 0.05$ are displayed in gray and given a lower opacity value.
 
@@
 We developed a searchlight analysis whereby we constructed a 5~mm$^3$ cube centered on each voxel.
-For each of these cubes, we computed the temporal correlation matrix of the voxel responses during movie viewing.
-Specifically, for each of the 1976 volumes collected during movie viewing, we correlated the activity patterns in the given cube with the activity patterns (in the same cube) collected during every other timepoint.
+For each of these cubes, we computed the temporal correlation matrix of the voxel responses during video viewing.
+Specifically, for each of the 1976 volumes collected during video viewing, we correlated the activity patterns in the given cube with the activity patterns (in the same cube) collected during every other timepoint.
 This yielded a 1976 by 1976 correlation matrix for each cube.

### 2018-09-05 paper/supporting_information.tex
renamed supplemental materials supporting information
inputted andy's comments on main text

--- 2018-09-04 paper/supplemental_materials.tex
@@
 
-\title{\textit{Supplemental materials for}: How is experience transformed into memory?}
+\title{\textit{Supporting information for}: How is experience transformed into memory?}
 \author{Andrew C.
@@
 
-The optimized model converged on 28 unique topics that were assigned non-zero weights over the course of the video.
+The optimized model converged on 27 unique topics that were assigned non-zero weights over the course of the video.
 We provide a list of the top ten highest-weighted words from each topic in Figure~\ref{fig:topics}.
@@
 \caption{\small \textbf{Topics discovered in \textit{Sherlock}.} We applied a topic model to hand-annotated information about 1000 scenes spanning the 45 minute episode.
-We identified 28 unique topics with non-zero weights (we used $K=100$ topics to fit the model).
+We identified 27 unique topics with non-zero weights (we used $K=100$ topics to fit the model).
 Each topic comprises a distribution of weights over all words in the vocabulary.
@@
 
-% Supplemental materials
+% Supporting information
 

### 2018-09-05 paper/supporting_information.tex
paxton's and andy's edits to main text and supplement have been inputted

@@
 
-\title{\textit{Supporting information for}: How is experience transformed into memory?}
+\title{\textit{Supporting Information for}: How is experience transformed into memory?}
 \author{Andrew C.
@@
 \section*{Overview}
-This document provides additional details about the methods we used in the main text.  We also include some additional figures referenced in the main text.
+This document provides additional details about the methods we used in the main text.  We also include some additional analyses and figures referenced in the main text.
 
@@
 In order to create accurate video and recall models, we used an optimization method that was driven by our ability to explain hand-annotated memory performance metrics collected by \cite{ChenEtal17}.
-Specifically, we used a grid search to compute the $\omega$ (movie sliding window duration, in scenes), $\rho$ (recall sliding window duration, in sentences), and $K$ (number of topics) that satisfied
+Specifically, we used a grid search to compute the $\omega$ (video sliding window duration, in scenes), $\rho$ (recall sliding window duration, in sentences), and $K$ (number of topics) that satisfied
 \[
@@
 We searched over a grid of pre-specified values for each of these parameters; the resulting correlations are displayed in Figure~\ref{fig:paramsearch}.
-The optimal parameters were $\omega = 250$, $\rho = 50$, and $K = 100$.
+The optimal parameters were $\omega = 50$, $\rho = 10$, and $K = 100$.
 
@@
 \includegraphics[width=1\textwidth]{figs/parameter_search}
-\caption{\small \textbf{Optimizing topic model parameters.}  We performed a grid search over movie sliding window length ($\omega \in \{5, 10, 25, 50, 100 \}$), recall sliding window length ($\rho \in \{5, 10, 25, 50, 100 \}$, and number of topics ($K \in \{5, 10, 25, 50, 100 \}$.
+\caption{\small \textbf{Optimizing topic model parameters.}  We performed a grid search over video sliding window length ($\omega \in \{5, 10, 25, 50, 100 \}$), recall sliding window length ($\rho \in \{5, 10, 25, 50, 100 \}$, and number of topics ($K \in \{5, 10, 25, 50, 100 \}$.
 The reported correlations are between per-subject video-recall trajectory correlations and per-subject hand-annotated memory performance ratings.}
@@
 We also carried out an analysis of which annotated features tended to shape aspects of the video topic trajectory that were preserved in participants' recalls.
-Specifically, we computed the timepoint-by-timepoint correlation matrix of the video topic trajectory, and correlated its upper triangle with the timepoint-by-timepoint correlation matrices of each participant's recall topic trajectory (resampled using linear interpolation to have the same number of timepoints as the video trajectory).
+Specifically, we computed the timepoint-by-timepoint correlation matrix of the video topic trajectory, and correlated its upper triangle with that of the timepoint-by-timepoint correlation matrices of each participant's recall topic trajectory (resampled using linear interpolation to have the same number of timepoints as the video trajectory).
 This yielded a single correlation coefficient for each participant.
-We then carried out a series of analyses whereby we repeated the analysis with each annotated feature held out in turn.
+We then repeated this analysis with each annotated feature held out in turn.
 Observing a lower correlation between the video and recall trajectories (when a given feature was held out) would indicate that the feature tends to be preserved in participants' recalls.
-We found that hand-annotated narrative details were the most preserved type of feature, whereas information about the camera angle tended not to feature in participants' recalls (Fig.~\ref{fig:feature-importance}B).
+We found that hand-annotated narrative details were the most preserved type of feature, whereas information about the camera angle tended not to influence participants' recalls (Fig.~\ref{fig:feature-importance}B).
 
@@
 We computed video topic trajectories for each feature in turn, and then compared the temporal correlation matrices of all pairs of features.
-This provided additional confirmation that the full model (including all types of features) was largely driven by narrative details.
+This provided additional confirmation that the shape of the full trajectory (including all types of features) was largely driven by narrative details.
 We also found that character-driven features (characters on screen, characters speaking, and characters in focus) were strongly correlated.
-Other details, such as the presense or absense of music, led to very different topic trajectories (Fig.~\ref{fig:feature-importance}C).
+Other details, such as the presence or absence of music, led to very different topic trajectories (Fig.~\ref{fig:feature-importance}C).
 
@@
 \textbf{B}.
-The probability of recalling each event, conditioned on having just recalled the event \textit{lag} events away in the video.
+The probability of recalling each event, conditioned on having most recently recalled the event \textit{lag} events away in the video.
 \textbf{C.} The proportion of participants who recalled each event, as a function of the serial position of the events in the video.
@@
 Then for each participant, we found the index of the video event that was recalled first (i.e., the video event whose topic vector was most strongly correlated with that of the first recall event) and filled in that index in the matrix with a 1.
-Finally, we averaged over the rows of the matrix, resulting in a 1 by 34 array representing the proportion of participant that recalled an event first, as a function of the order of the event's appearance in the video (Fig.~\ref{fig:list-learning}A).
+Finally, we averaged over the rows of the matrix, resulting in a 1 by 34 array representing the proportion of participants that recalled an event first, as a function of the order of the event's appearance in the video (Fig.~\ref{fig:list-learning}A).
 
 \paragraph{Lag conditional probability curve (lag-CRP).} The lag-CRP curve~\citep{Kaha96} reflects the probability of recalling a given event after the just-recalled event, as a function of their relative positions (or \textit{lag}).
-In other words, a lag of 1 indicates that a recalled event came immediately after the previously recalled event in the video, and a lag of -3 indicates that a recalled event came 3 items before the previously recalled event.
+In other words, a lag of 1 indicates that a recalled event came immediately after the previously recalled event in the video, and a lag of -3 indicates that a recalled event came 3 events before the previously recalled event.
 For each recall transition (following the first recall), we computed the lag between the current recall event and the next recall event, normalizing by the total number of possible transitions.
@@
 We initialized a number-of-participants (17) by number-of-video-events (34) matrix of zeros.
-Then, for each recalled event (and each participant), we found the index of the video event that the recalled event most closely matched (via the correlation between the events' topic vectors) and entered a 1 into that position in the matrix (i.e., for the given participant and event).
+Then, for each recalled event, for each participant, we found the index of the video event that the recalled event most closely matched (via the correlation between the events' topic vectors) and entered a 1 into that position in the matrix (i.e., for the given participant and event).
 This resulted in a matrix whose entries indicated whether or not each event was recalled by each participant (depending on whether the corresponding entires were set to one or zero).
@@
 \paragraph{Temporal clustering scores.} Temporal clustering refers to the extent to which participants group their recall responses according to encoding position~\citep{PolyEtal09}.
-For instance, if a participant recalled the video events in the exact order they occurred, this would yield a score of 1.
-If a participant recalled the video events in reverse order, this would yield a score of 0.
-Similarly, if a participant recalled the events in random order, this yield yield an expected score of 0.5.
+For instance, if a participant recalled the video events in the exact order they occurred (or in exact reverse order), this would yield a score of 1.
+If a participant recalled the events in random order, this would yield an expected score of 0.5.
 For each recall event transition (and separately for each participant), we sorted all not-yet-recalled events according to their absolute lag (i.e., distance away in the video).
@@
 \paragraph*{Precision.}
-We tested whether participants who recalled more events were also more \textit{precise} in their recollections.
+We next tested whether participants who recalled more events were also more \textit{precise} in their recollections.
 For each participant, we computed the correlation between the topic vectors for each recall event and that of its closest-matching video event (only for the events which they recalled).

### 2018-09-05 paper/main.tex
paxton's and andy's edits to main text and supplement have been inputted
addressed a bunch of minor issues to satisfy the nature administrators

@@
 \usepackage{setspace}
+\usepackage{hyperref}
 
@@
 
+\subsection*{Data availability}
+The behavioral and fMRI data we analyzed are available online \href{http://dataspace.princeton.edu/jspui/handle/88435/dsp01nz8062179}{\underline{here}}.
+
+\subsection*{Statistics}
+All statistical tests we performed were two-sided.
+
 \subsection*{Modeling the dynamic content of the video and recall transcripts}
@@
 For each vertex, we examined the set of line segments formed by connecting each pair successively recalled events, across all participants, that passed within 0.5 units.
-We computed the distribution of angles formed by those segments and the $x$-axis, and used a Rayleigh test to determine whether the distribution of angles was reliably ``peaked'' (i.e.
-consistent across all transitions that passed through that local portion of topic space).
+We computed the distribution of angles formed by those segments and the $x$-axis, and used a Rayleigh test to determine whether the distribution of angles was reliably ``peaked'' (i.e., consistent across all transitions that passed through that local portion of topic space).
 To create Figure~\ref{fig:trajectory}B we drew an arrow originating from each grid vertex, pointing in the direction of the average angle formed by line segments that passed within 0.5 units.
@@
 In Figure~\ref{fig:brainz}, we present two analyses aimed at identifying brain structures whose responses (as participants viewed the video) exhibited particular temporal correlations.
-We developed a searchlight analysis whereby we constructed a 5~mm$^3$ cube centered on each voxel.
+We developed a searchlight analysis whereby we constructed a cube centered on each voxel (radius: 5~voxels).
 For each of these cubes, we computed the temporal correlation matrix of the voxel responses during video viewing.
@@
 
+\section*{Supporting information}
+Supporting information is available in the online version of the paper.
+
+\section*{Acknowledgements}
+We thank Luke Chang, Janice Chen, Chris Honey, Lucy Owen, Emily Whitaker, and Kirsten Ziman for feedback and scientific discussions.
+We also thank Janice Chen, Yuan Chang Leong, Kenneth Norman, and Uri Hasson for sharing the data used in our study.
+Our work was supported in part by NSF EPSCoR Award Number 1632738.
+The content is solely the responsibility of the authors and does not necessarily represent the official views of our supporting organizations.
+
+\section*{Author contributions}
+Conceptualization: A.C.H.
+and J.R.M.; Methodology: A.C.H.
+and J.R.M.; Software: A.C.H., P.C.F.
+and J.R.M.; Analysis: A.C.H., P.C.F.
+and J.R.M.; Writing, Reviewing, and Editing: A.C.H., P.C.F.
+and J.R.M.; Supervision: J.R.M.
+
+\section*{Author information}
+The authors declare no competing financial interests.  Correspondence and requests for materials should be addressed to J.R.M. (jeremy.r.manning@dartmouth.edu).
+
 \end{document}

### 2018-09-05 paper/supporting_information.tex
addressed a bunch of minor issues to satisfy the nature administrators

@@
 \cite{ChenEtal17} developed a human rating system whereby the quality of each participant's memory was evaluated by an independent rater.
-We found a strong across-participants correlation between these independant ratings and the overall number of events that our HMM approach identified in participants' recalls ($r = 0.67, p = 0.003$).
+We found a strong across-participants correlation between these independant ratings and the overall number of events that our HMM approach identified in participants' recalls (Pearson's $r(15) = 0.67, p = 0.003$).
 
@@
 We averaged these percentile ranks across all of the participant's recalls to obtain a single temporal clustering score for the participant (mean: 0.808, SEM: 0.022).
-Overall, we found that participants with higher temporal clustering scores also tended to recall more events ($r = 0.62, p = 0.007$).
+Overall, we found that participants with higher temporal clustering scores also tended to recall more events (Pearson's $r(15) = 0.62, p = 0.007$).
 
@@
 We averaged these percentile ranks across all of the participant's recalls to obtain a single semantic clustering score for the participant (mean: 0.813, SEM: 0.022).
-We found that participants who exhibited stronger semantic clustering scores overall remembered more video events ($r = 0.55, p = 0.02$).
+We found that participants who exhibited stronger semantic clustering scores overall remembered more video events (Pearson's $r(15) = 0.55, p = 0.02$).
 
@@
 The observed RMSD values reached significance (i.e., $p < 0.05$, reflecting that more than 95\% of the null RMSD values were greater than the observed RMSD value) for nine of the participants (3, 4, 8--13, and 17).
-(For the remaining participants this test yielded $0.05 \leq p < 0.25$.)  The observed RMSD values were also reliably correlated with hand-annotated memory performance across participants ($r = -0.57, p = 0.016$).
+(For the remaining participants this test yielded $0.05 \leq p < 0.25$.)  The observed RMSD values were also reliably correlated with hand-annotated memory performance across participants (Pearson's $r(15) = -0.57, p = 0.016$).
 In other words, a closer match between the video and recall topic trajectories was related to better overall recall performance.
@@
 We defined the precision as the average video-recall correlation across all of the events a participant recalled.
-We found a strong correlation between hand-annotated memory performance and precision, suggesting that participants who remembered more events also remembered them more veridically ($r = 0.74, p = 0.0006$).
+We found a strong correlation between hand-annotated memory performance and precision, suggesting that participants who remembered more events also remembered them more veridically (Pearson's $r(15) = 0.74, p = 0.0006$).
 
@@
 We then averaged these distinctiveness scores across all of the events recalled by the given participant.
-We found that participants with higher average distinctiveness scores tended to also have better hand-annotated memory performance ($r = 0.8, p = 0.0001$).
+We found that participants with higher average distinctiveness scores tended to also have better hand-annotated memory performance (Pearson's $r(15) = 0.8, p = 0.0001$).
 
@@
 For each participant, we computed the Spearman rank correlation between the order of events that the participant recalled and the order the events actually occurred in the video (considering in the analysis only the events that the participant recalled).
-Participants who recalled more events also recalled more of them in order ($r = 0.5, p = 0.04$).
+Participants who recalled more events also recalled more of them in order (Pearson's $r(15) = 0.5, p = 0.04$).
 In summary, we found that better memory performance was associated with more precise, distinctive, and ordered recalls.

### 2018-09-06 paper/main.tex
added P in front of participant codes in one more place in the text

@@
 First, although every individual participant's recalls could be segmented into discrete events (i.e., every individual participant's recall correlation matrix exhibited clear block diagonal structure; Fig.~\corrmats), each participant appeared to have a unique \textit{recall resolution}, reflected in the sizes of those blocks.
-For example, some participants' recall topic proportions segmented into just a few events (e.g., Participants 1, 4, and 15), while others' recalls segmented into many shorter duration events (e.g., Participants 12, 13, and 17).
+For example, some participants' recall topic proportions segmented into just a few events (e.g., Participants P1, P4, and P15), while others' recalls segmented into many shorter duration events (e.g., Participants P12, P13, and P17).
 This suggests that different participants may be recalling the video with different levels of detail-- e.g., some might touch on just the major plot points, whereas others might attempt to recall every minor scene.

### 2018-09-27 paper/main.tex
minor edits needed for nature submission
minor figure cleanup in illustrator

@@
 \usepackage{hyperref}
+\usepackage{lineno}
 
@@
 
-%\doublespacing
+\doublespacing
+\linenumbers
 
@@
 \begin{abstract}
-How our experiences unfold over time define unique \textit{trajectories} through the relevant representational spaces.
+The ways our experiences unfold over time define unique \textit{trajectories} through the relevant representational spaces.
 Within this geometric framework, one can compare the shape of the trajectory formed by an experience to that defined by our later remembering of that experience.
@@
 Participants were then allowed to speak for as long as they wished, and verbally indicated when they were finished (e.g., `I’m done').''  For additional details about the experimental procedure and scanning parameters see \cite{ChenEtal17}.
+The experimental protocol was approved by Princeton University's Institutional Review Board.
 
@@
 
-\subsection*{Data availability}
-The behavioral and fMRI data we analyzed are available online \href{http://dataspace.princeton.edu/jspui/handle/88435/dsp01nz8062179}{\underline{here}}.
+\subsection*{Data and code availability}
+The fMRI data we analyzed are available online \href{http://dataspace.princeton.edu/jspui/handle/88435/dsp01nz8062179}{\underline{here}}.
+The behavioral data and all of our analysis code may be downloaded \href{https://github.com/ContextLab/sherlock-topic-model-paper}{\underline{here}}.
 

### 2019-04-17 paper/main.tex
added wasserstein figure and text, did not compile the pdfs bc i dont have latex on this computer

@@
 \newcommand{\matchmats}{S6}
+\newcommand{\wasserstein}{S7}
 
@@
 
+We also evaluated a parameter-free procedure for choosing $K$, which finds the $K$ value that maximizes the Wasserstein distance (a.k.a.
+"Earth mover's" distance) between the within and across event distributions of correlation values.
+This alternative procedure largely replicated the pattern of results found with the parameterized method described above, but recovered substantially fewer events on average (Fig.\wasserstein).
+While both approaches seem to underestimate the number of video/recall events relative to the "true" number (as determined by human raters), the parameterized approach was closer to the true number.
+
 \subsubsection*{Visualizing the video and recall topic trajectories}

### 2019-04-17 paper/supporting_information.tex
minor edits needed for nature submission
added wasserstein figure and text, did not compile the pdfs bc i dont have latex on this computer

@@
 \section*{Overview}
-This document provides additional details about the methods we used in the main text.  We also include some additional analyses and figures referenced in the main text.
+This document provides additional details about the methods we used in the main text.  We also include some additional analyses referenced in the main text.
 
@@
 
-\begin{figure}[tp]
+\begin{figure}[p!]
 \centering
@@
 
-\begin{figure}[tb]
+\begin{figure}[p!]
 \centering
@@
 
-\section*{Participant-level figures referenced in the main text}
+%\section*{Participant-level figures referenced in the main text}
 
@@
 
-\begin{figure}[htp]
+\begin{figure}[p!]
 \centering
@@
 \label{fig:matchmats}
+\end{figure}
+
+\begin{figure}[p!]
+  \centering
+  \includegraphics[width=\textwidth]{figs/trajectory_wasserstein}
+  \caption{\small \textbf{Trajectories using Wasserstein distance for choosing $K$.}  We replicated the trajectory analysis using Wasserstein distance, a parameter-free procedure for choosing $K$.
+Overall, the pattern of findings is quite similar to our main approach, but resulted in a smaller number of events.}
+  \label{fig:trajectory_wasserstein}
   \end{figure}

### 2019-06-13 paper/main.tex
saving progress on revision paper edits

@@
 
-\title{How is experience transformed into memory?}
+%\title{How is experience transformed into memory?}
+%\title{A content-based framework for capturing stimulus and memory dynamics reveals event-like structure in naturalistic episodic recall}
+%\title{A content-based model characterizing/describing/representing how experiences and memories unfold over time reveals event-like structure in naturalistic episodic recall}
+%\title{A content-based framework describing the temporal dynamics of experiences and memories reveals event-like structure in naturalistic episodic recall}
+\title{A content-based model of how experiences and memories unfold over time reveals event-like structure in naturalistic episodic recall}
+
 \author{Andrew C.
@@
 We found that the shapes of the trajectories formed by participants' recountings were all highly similar to that of the original video, but participants differed in the level of detail they remembered.
-We also identified a network of brain structures that are sensitive to the ``shapes'' of our ongoing experiences, and an overlapping network that is sensitive to how we will later remember those experiences.
+Further, we identified a network of brain structures that are sensitive to the ``shapes'' of our ongoing experiences, and an overlapping network that is sensitive to how we will later remember those experiences.
 \end{abstract}
@@
 More nuanced studies might incorporate self-reported confidence measures as a proxy for memory strength, or ask participants to discriminate between ``recollecting'' the (contextual) details of an experience or having a general feeling of ``familiarity'' \citep{Yone02}.
-However, characterizing and evaluating memory in more realistic contexts (e.g., recounting a recent experience to a friend) is fundamentally different in at least three ways~\citep[for review also see][]{KoriGold94, HukEtal18}.
-First, real world recall is continuous, rather than discrete.
-Unlike in trial-based experiments, removing a (naturalistic) event from the context in which it occurs can substantially change its meaning.
+Using well-controlled, trial-based experimental designs, the field has amassed a wealth of valuable information regarding human episodic memory.
+However, there are fundamental properties of our memories that trial-based experiments are not well suited to capture~\citep[for review also see][]{KoriGold94, HukEtal18}.
+First, our memories are continuous, rather than discrete: removing a (naturalistic) event from the context in which it occurs can substantially change its meaning.
 Second, the specific words used to describe an experience have little bearing on whether the experience should be considered to have been ``remembered.''  Asking whether the rememberer has precisely reproduced a specific set of words to describe a given experience is nearly orthogonal to whether they were actually able to remember it.
 In classic (e.g., list-learning) memory studies, by contrast, counting the number or proportion of precise recalls is often a primary metric of assessing the quality of participants' memories.
-Third, one might remember the \textit{gist} or essence of an experience but forget (or neglect to recount) particular details.
-Capturing the gist of what happened is typically the main ``point'' of recounting a memory to a listener whereas, depending on the circumstances, accurate recall of any specific detail may be irrelevant.
-There is no analog of the gist of an experience in most traditional memory experiments; rather we tend to assess participants' abilities to recover specific details (e.g., computing the proportion of specific stimuli they remember, which presentation positions the remembered stimuli came from, etc.).
+Third, one might remember the essence of an experience but forget (or neglect to recount) particular details.
+Capturing the essence (or the \textit{shape}) of what happened is typically the main ``point'' of recounting a memory to a listener.
 
-How might one go about formally characterizing the gist of an experience, or whether that gist has been recovered by the rememberer?
+How might one go about formally characterizing the shape of an experience, or whether that shape has been recovered by the rememberer?
 Any given moment of an experience derives meaning from surrounding moments, as well as from longer-range temporal associations~\citep[e.g., ][]{LernEtal11}.
@@
 Prior research suggests that these sharp transitions (termed \textit{event boundaries}) during an experience help to discretize our experiences into \textit{events}~\citep{RadvZack17, BrunEtal18, HeusEtal18b, ClewDava17, EzzyDava11, DuBrDava13}.
-The interplay between the stable (within event) and transient (across event) temporal dynamics of an experience also provides a potential framework for transforming experiences into memories that distill those experiences down to their essence-- i.e., their gists.
+The interplay between the stable (within event) and transient (across event) temporal dynamics of an experience also provides a potential framework for transforming experiences into memories that distill those experiences down to their essence.
 For example, prior work has shown that event boundaries can influence how we learn sequences of items~\citep{HeusEtal18b, DuBrDava13}, navigate~\citep{BrunEtal18}, and remember and understand narratives~\citep{ZwaaRadv98, EzzyDava11}.
+Prior studies have implicated the hippocampus and the medial prefrontal cortex as playing a critical role in this process [CITE].
 
@@
 In this way, we cast naturalistic experiences (and recalls of those experiences) as \textit{topic trajectories} that describe how the experiences evolve over time.
-In other words, the episode's topic trajectory is a formalization of its gist.
-Under this framework, successful remembering entails verbally ``traversing'' the topic trajectory of the original episode, thereby reproducing the original episode's gist.
+In other words, the episode's topic trajectory is a formalization of its shape.
+Under this framework, successful remembering entails verbally ``traversing'' the topic trajectory of the original episode, thereby reproducing the original episode's shape.
 In addition, comparing the shapes of the topic trajectories of the original episode and of participants' retellings of the episode reveals which aspects of the episode were preserved (or lost) in the translation into memory.
-We also identified a network of brain structures whose responses (as participants watched the episode) reflected the gist of the episode, and a second network whose responses reflected how participants would later recount the episode.
+Further, we identified a network of brain structures whose responses (as participants watched the episode) reflected the shape of the episode, and a second network whose responses reflected how participants would later recount the episode.
 
 \section*{Results}
-To characterize the gists of the \textit{Sherlock} episode participants watched and their subsequent recountings of the episode, we used a topic model~\citep{BleiEtal03} to discover the latent thematic content in the video.
+To characterize the shape of the \textit{Sherlock} episode participants watched and their subsequent recountings of the episode, we used a topic model~\citep{BleiEtal03} to discover the latent thematic content in the video.
 Topic models take as inputs a vocabulary of words to consider and a collection of text documents; they return as output two matrices.
@@
 This yields a sequence of ``presented'' events from the original video, and a sequence of (potentially differently ordered) ``recalled'' events for each participant.
-Analogous to classic list-learning studies, we can then examine participants' recall sequences by asking which events they tended to recall first~\citep[probability of first recall; Fig.~\listlearning A;][]{WelcBurn24, PostPhil65, AtkiShif68}; how participants most often transition between recalls of the events as a function of the temporal distance between them~\citep[lag-conditional response probability; Fig.~\listlearning B;][]{Kaha96}; and which events they were likely to remember overall~\citep[serial position recall analyses; Fig.~\listlearning C;][]{Murd62a}.
-In list-learning studies, this set of three analyses may be used to gain a nearly complete view into the sequences of recalls participants made~\citep[e.g., ][]{Kaha12}.
+Analogous to classic list-learning studies, we can then examine participants' recall sequences by asking which events they tended to recall first~\citep[probability of first recall; Fig.~\ref{fig:list-learning}A;][]{WelcBurn24, PostPhil65, AtkiShif68}; how participants most often transition between recalls of the events as a function of the temporal distance between them~\citep[lag-conditional response probability; Fig.~\ref{fig:list-learning}B;][]{Kaha96}; and which events they were likely to remember overall~\citep[serial position recall analyses; Fig.~\ref{fig:list-learning}C;][]{Murd62a}.
+Interestingly, for 2 of the analyses (probability of first recall and lag-conditional response probability curves) we observe patterns comparable to classic effects from the list-learning literature.
+Namely, a higher probability of initiating recall with the first event in the sequence (Fig.~\ref{fig:list-learning}A) and a higher probability of transitioning to neighboring events with a forward assymetric bias (Fig.~\ref{fig:list-learning}C).
+In contrast, we do not observe a pattern comparable to the serial position effect (Fig.~\ref{fig:list-learning}C), but rather we see higher memory for specific events distributed somewhat evenly throughout the video.
+
+% NOTE: Pruning out to tone down the list-learning slander
+%In list-learning studies, this set of three analyses may be used to gain a nearly complete view into the sequences of recalls participants made~\citep[e.g., ][]{Kaha12}.
 Extending these analyses to apply to naturalistic stimuli and recall~\citep{HeusEtal17b} highlights that, in naturalistic recall, these analyses provide a wholly incomplete picture: they leave out any attempt to quantify participants' abilities to capture the \textit{content} of what occurred in the video-- their only experimental instruction!
+
+\begin{figure}[tp]
+  \centering
+  \includegraphics[width=1\textwidth]{figs/list_learning}
+  \caption{\small \textbf{Naturalistic extensions of classic list-learning memory analyses.} \textbf{A.} The probability of first recall as a function of the serial position of the event in the video.
+\textbf{B}.
+The probability of recalling each event, conditioned on having most recently recalled the event \textit{lag} events away in the video.
+\textbf{C.} The proportion of participants who recalled each event, as a function of the serial position of the events in the video.
+All panels: error bars denote bootstrap-estimated standard error of the mean.}
+  \label{fig:list-learning}
+\end{figure}
+
+Statistical models of memory studies often treat memory recalls as "all-or nothing" and independent events.
+However, our approach produces a content-based model of individual stimulus events and recall events, allowing for direct quantitative comparison between all stimulus and recall events, as well as between the recall events themselves.
+Leveraging this affordance, we introduce 2 novel metrics for quantifying memory representations: precision and distinctiveness.
+We define precision as the average correlation between each recall event and the maximally correlated video event [INSERT FIGURE REF].
+Participants whose recall events are more veridical descriptions of what happened in the video event will have higher precision scores.
+We find that across participants, a higher precision score is correlated to both hand annotated memory performance as well as the number of recall events (per participant) estimated by our model [INSERT STATS, INSERT FIGURE REF].
+A second novel metric we introduce here is the distinctiveness, or the uniqueness of each recall event relative to other recall events.
+Distinctiveness is defined as 1 minus the average of the upper triangle of the recall-by-recall correlation matrix.
+Similar to precision, we find that the more distinct participants recalls are (on average), the more they remembered (for both hand-annotated and model derived memory performance) [INSERT STATS AND FIGURE REF].
+In summary, using two novel metrics afforded by our approach, we find that participants whose recalls are both more precise and distinct remember more content.
+
+\begin{figure}[tp]
+  \centering
+  \includegraphics[width=1\textwidth]{figs/precision_distinctiveness}
+  \caption{\small \textbf{Novel content-based metrics of naturalistic memory: precision and distinctiveness.} \textbf{A.} Blah-bahdy Blah}
+  \label{fig:precision-distinctiveness}
+\end{figure}
 
@@
 Differences in the numbers of remembered events appear in participants' trajectories as differences in the sampling resolution along the trajectory.
-We note that this framework also provides a means of detangling classic ``proportion recalled'' measures (i.e., the proportion of video events referenced in participants' recalls) from participants' abilities to recapitulate the full gist of the original video (i.e., the similarity in the shape of the original video trajectory and that defined by each participant's recounting of the video).
+We note that this framework also provides a means of detangling classic ``proportion recalled'' measures (i.e., the proportion of video events referenced in participants' recalls) from participants' abilities to recapitulate the full shape of the original video (i.e., the similarity in the shape of the original video trajectory and that defined by each participant's recounting of the video).
 
@@
 This revealed that events with relatively minor characters such as ``Mike,'' ``Jeffrey,'' and ``Molly,'' as well as less-integral plot locations (e.g., ``hospital'' and ``office'') were least well-remembered.
-This suggests that what is retained in memory are the major plot elements (i.e., the overall ``gist'' of what happened), whereas the more minor details are prone to pruning.
+This suggests that what is retained in memory are the major plot elements (i.e., the overall shape of what happened), whereas the more minor details are prone to pruning.
 
@@
 
-Our work casts remembering as reproducing (behaviorally and neurally) the topic trajectory, or ``gist,'' of the original experience.
+Our work casts remembering as reproducing (behaviorally and neurally) the topic trajectory, or shape, of the original experience.
 This view draws inspiration from prior work aimed at elucidating the neural and behavioral underpinnings of how we process dynamic naturalistic experiences and remember them later.
@@
 Integrating across our study and this prior work, one interpretation is that the person-specific transformations mediated (or represented) by the rMTL and vmPFC may reflect schema knowledge being leveraged, formed, or updated, incorporating ongoing experience into previously acquired knowledge.
+
+In this work, we used topic models to capure the contents of verbal recall.  While a large number of language models exist (e.g. WAS, LSA, word2vec), we
 
@@
 
+\subsection*{Naturalistic extensions of classic list-learning analyses}
+In traditional list-learning experiments, participants view a list of items (e.g., words) and then recall the items later.
+Our video-recall event matching approach affords us the ability to analyze memory in a similar way.
+The video and recall events can be treated analogously to studied and recalled ``items'' in a list-learning study.
+We can then extend classic analyses of memory performance and dynamics (originally designed for list-learning experiments) to the more naturalistic video recall task used in our study.
+
+Perhaps the simplest and most widely used measure of memory performance is \textit{accuracy}-- i.e., the proportion of studied (experienced) items (in this case, the 34 video events) that the participant later remembered.
+\cite{ChenEtal17} developed a human rating system whereby the quality of each participant's memory was evaluated by an independent rater.
+We found a strong across-participants correlation between these independant ratings and the overall number of events that our HMM approach identified in participants' recalls (Pearson's $r(15) = 0.67, p = 0.003$).
+
+As described below, we next considered a number of memory performance measures that are typically associated with list-learning studies.
+We also provide a software package, \texttt{Quail}, for carrying out these analyses~\citep{HeusEtal17b}.
+
+\paragraph{Probability of first recall (PFR).}  PFR curves~\citep{WelcBurn24, PostPhil65, AtkiShif68} reflect the probability that an item will be recalled first as a function of its serial position during encoding.
+To carry out this analysis, we initialized a number-of-participants (17) by number-of-video-events (34) matrix of zeros.
+Then for each participant, we found the index of the video event that was recalled first (i.e., the video event whose topic vector was most strongly correlated with that of the first recall event) and filled in that index in the matrix with a 1.
+Finally, we averaged over the rows of the matrix, resulting in a 1 by 34 array representing the proportion of participants that recalled an event first, as a function of the order of the event's appearance in the video (Fig.~\ref{fig:list-learning}A).
+
+\paragraph{Lag conditional probability curve (lag-CRP).} The lag-CRP curve~\citep{Kaha96} reflects the probability of recalling a given event after the just-recalled event, as a function of their relative positions (or \textit{lag}).
+In other words, a lag of 1 indicates that a recalled event came immediately after the previously recalled event in the video, and a lag of -3 indicates that a recalled event came 3 events before the previously recalled event.
+For each recall transition (following the first recall), we computed the lag between the current recall event and the next recall event, normalizing by the total number of possible transitions.
+This yielded a number-of-participants (17) by number-of-lags (-33 to +33; 67 lags total) matrix.
+We averaged over the rows of this matrix to obtain a group-averaged lag-CRP curve (Fig.~\ref{fig:list-learning}B).
+
+\paragraph{Serial position curve (SPC).} SPCs~\citep{Murd62a} reflect the proportion of participants that remember each item as a function of their serial position during encoding.
+We initialized a number-of-participants (17) by number-of-video-events (34) matrix of zeros.
+Then, for each recalled event, for each participant, we found the index of the video event that the recalled event most closely matched (via the correlation between the events' topic vectors) and entered a 1 into that position in the matrix (i.e., for the given participant and event).
+This resulted in a matrix whose entries indicated whether or not each event was recalled by each participant (depending on whether the corresponding entires were set to one or zero).
+Finally, we averaged over the rows of the matrix to yield a 1 by 34 array representing the proportion of participants that recalled each event as a function of the order of the event's appearance in the video (Fig.~\ref{fig:list-learning}C).
+
+\paragraph{Temporal clustering scores.} Temporal clustering refers to the extent to which participants group their recall responses according to encoding position~\citep{PolyEtal09}.
+For instance, if a participant recalled the video events in the exact order they occurred (or in exact reverse order), this would yield a score of 1.
+If a participant recalled the events in random order, this would yield an expected score of 0.5.
+For each recall event transition (and separately for each participant), we sorted all not-yet-recalled events according to their absolute lag (i.e., distance away in the video).
+We then computed the percentile rank of the next event the participant recalled.
+We averaged these percentile ranks across all of the participant's recalls to obtain a single temporal clustering score for the participant (mean: 0.808, SEM: 0.022).
+Overall, we found that participants with higher temporal clustering scores also tended to recall more events (Pearson's $r(15) = 0.62, p = 0.007$).
+
+\paragraph{Semantic clustering scores.} Semantic clustering measures the extent to which participants clustered their recall responses according to semantic similarity~\citep{PolyEtal09}.
+Here, we used the topic vectors for each event as a proxy for its semantic content.
+Thus, the similarity between the semantic content for two events can be computed by correlating their respective topic vectors.
+For each recall event transition, we sorted all not-yet-recalled events according to how correlated the topic vector \textit{of the closest-matching video event} was to the topic vector of the closest-matching video event to the just-recalled event.
+We then computed the percentile rank of the observed next recall.
+We averaged these percentile ranks across all of the participant's recalls to obtain a single semantic clustering score for the participant (mean: 0.813, SEM: 0.022).
+We found that participants who exhibited stronger semantic clustering scores overall remembered more video events (Pearson's $r(15) = 0.55, p = 0.02$).
+
+% NOTE: Thinking about removing this analysis? More of a sanity check than something novel and cool, and takes up space. Happy to be convinced otherwise
+
+% To quantify the similarity between the video topic trajectory and individual recall topic trajectories, we considered several novel metrics.
+First, we tested whether each participant's recall trajectory matched the video trajectory in a general sense.
+For each participant we filtered the video trajectory to only include the events that the participant remembered.
+We then computed the root mean squared difference (RMSD) between the remaining video events and the (closest-matching) recalled events.
+For example, if the topic vectors for a participant's recall event topic vectors matched the corresponding video event topic vectors exactly (and in order), the expected RMSD for those events would be 0.
+However, if the participant's recall events did not perfectly match the video events, or if they were out of order, then the RMSD would be greater than 0.
+To assess the significance of the match between the video and recall trajectories, we carried out a permutation procedure whereby, for each of 10000 repetitions, we circularly shifted the recall trajectories (in time) by a random amount and then re-computed the RMSD each time.
+This yielded a distribution of ``null'' RMSD values for each participant.
+The observed RMSD values reached significance (i.e., $p < 0.05$, reflecting that more than 95\% of the null RMSD values were greater than the observed RMSD value) for nine of the participants (3, 4, 8--13, and 17).
+(For the remaining participants this test yielded $0.05 \leq p < 0.25$.)  The observed RMSD values were also reliably correlated with hand-annotated memory performance across participants (Pearson's $r(15) = -0.57, p = 0.016$).
+In other words, a closer match between the video and recall topic trajectories was related to better overall recall performance.
+
+Statistical models of memory studies often treat memory recalls as binary and distinct events.
+However, our approach produces a formal model of individual stimulus events and recall events, allowing for direct quantitative comparison between all stimulus and recall events, as well as between the recall events themselves.
+Leveraging this fact, we introduce 2 novel metrics for quantifying memory representations: precision and distinctiveness.
+
+\paragraph*{Precision.}
+We next tested whether participants who recalled more events were also more \textit{precise} in their recollections.
+For each participant, we computed the correlation between the topic vectors for each recall event and that of its closest-matching video event (only for the events which they recalled).
+We defined the precision as the average video-recall correlation across all of the events a participant recalled.
+We found a strong correlation between hand-annotated memory performance and precision, suggesting that participants who remembered more events also remembered them more veridically (Pearson's $r(15) = 0.74, p = 0.0006$).
+
+\paragraph*{Distinctiveness.}
+We also considered the \textit{distinctiveness} of each recalled event.
+That is, how uniquely a recalled event's topic vector matched a given video event topic vector, versus the topic vectors for the other video events.
+We hypothesized that participants with high memory performance might describe each event in a more distinctive way (relative to those with lower memory performance who might describe events in a more general way).
+To test this hypothesis we define a distinctiveness score for each recalled event as
+\[
+  d(\mathrm{event}) = 1 - \bar{c}(\mathrm{event}),
+\]
+where $\bar{c}(\mathrm{event})$ is the average correlation between the given recalled event's topic vector and the topic vectors from all video events \textit{except} the best-matching video event.
+We then averaged these distinctiveness scores across all of the events recalled by the given participant.
+We found that participants with higher average distinctiveness scores tended to also have better hand-annotated memory performance (Pearson's $r(15) = 0.8, p = 0.0001$).
+
 \subsection*{Searchlight fMRI analyses}

### 2019-06-13 paper/supporting_information.tex
saving progress on revision paper edits

@@
 
-\section*{Additional analyses of memory performance}
+% \section*{Additional analyses of memory performance}
 
-\subsection*{Naturalistic extensions of classic list-learning analyses}
-In traditional list-learning experiments, participants view a list of items (e.g., words) and then recall the items later.
+% \subsection*{Naturalistic extensions of classic list-learning analyses}
+% In traditional list-learning experiments, participants view a list of items (e.g., words) and then recall the items later.
 Our video-recall event matching approach affords us the ability to analyze memory in a similar way.
@@
 
-Perhaps the simplest and most widely used measure of memory performance is \textit{accuracy}-- i.e., the proportion of studied (experienced) items (in this case, the 34 video events) that the participant later remembered.
+% Perhaps the simplest and most widely used measure of memory performance is \textit{accuracy}-- i.e., the proportion of studied (experienced) items (in this case, the 34 video events) that the participant later remembered.
 \cite{ChenEtal17} developed a human rating system whereby the quality of each participant's memory was evaluated by an independent rater.
@@
 
-As described below, we next considered three more nuanced measures of the memory performance and dynamics that are typically associated with list-learning studies.
+% As described below, we next considered three more nuanced measures of the memory performance and dynamics that are typically associated with list-learning studies.
 We also provide a software package, \texttt{Quail}, for carrying out these analyses~\citep{HeusEtal17b}.
 
-\begin{figure}[p!]
-\centering
-\includegraphics[width=1\textwidth]{figs/list_learning}
-\caption{\small \textbf{Naturalistic extensions of classic list-learning memory analyses.} \textbf{A.} The probability of first recall as a function of the serial position of the event in the video.
+% \begin{figure}[p!]
+% \centering
+% \includegraphics[width=1\textwidth]{figs/list_learning}
+% \caption{\small \textbf{Naturalistic extensions of classic list-learning memory analyses.} \textbf{A.} The probability of first recall as a function of the serial position of the event in the video.
 \textbf{B}.
@@
 All panels: error bars denote bootstrap-estimated standard error of the mean.}
-\label{fig:list-learning}
-\end{figure}
+% \label{fig:list-learning}
+% \end{figure}
 
-\paragraph{Probability of first recall (PFR).}  PFR curves~\citep{WelcBurn24, PostPhil65, AtkiShif68} reflect the probability that an item will be recalled first as a function of its serial position during encoding.
+% \paragraph{Probability of first recall (PFR).}  PFR curves~\citep{WelcBurn24, PostPhil65, AtkiShif68} reflect the probability that an item will be recalled first as a function of its serial position during encoding.
 To carry out this analysis, we initialized a number-of-participants (17) by number-of-video-events (34) matrix of zeros.
@@
 
-\paragraph{Lag conditional probability curve (lag-CRP).} The lag-CRP curve~\citep{Kaha96} reflects the probability of recalling a given event after the just-recalled event, as a function of their relative positions (or \textit{lag}).
+% \paragraph{Lag conditional probability curve (lag-CRP).} The lag-CRP curve~\citep{Kaha96} reflects the probability of recalling a given event after the just-recalled event, as a function of their relative positions (or \textit{lag}).
 In other words, a lag of 1 indicates that a recalled event came immediately after the previously recalled event in the video, and a lag of -3 indicates that a recalled event came 3 events before the previously recalled event.
@@
 
-\paragraph{Serial position curve (SPC).} SPCs~\citep{Murd62a} reflect the proportion of participants that remember each item as a function of their serial position during encoding.
+% \paragraph{Serial position curve (SPC).} SPCs~\citep{Murd62a} reflect the proportion of participants that remember each item as a function of their serial position during encoding.
 We initialized a number-of-participants (17) by number-of-video-events (34) matrix of zeros.
@@
 
-\paragraph{Temporal clustering scores.} Temporal clustering refers to the extent to which participants group their recall responses according to encoding position~\citep{PolyEtal09}.
+% \paragraph{Temporal clustering scores.} Temporal clustering refers to the extent to which participants group their recall responses according to encoding position~\citep{PolyEtal09}.
 For instance, if a participant recalled the video events in the exact order they occurred (or in exact reverse order), this would yield a score of 1.
@@
 
-\paragraph{Semantic clustering scores.} Semantic clustering measures the extent to which participants clustered their recall responses according to semantic similarity~\citep{PolyEtal09}.
+% \paragraph{Semantic clustering scores.} Semantic clustering measures the extent to which participants clustered their recall responses according to semantic similarity~\citep{PolyEtal09}.
 Here, we used the topic vectors for each event as a proxy for its semantic content.
@@
 
-\subsection*{Additional measures of naturalistic memory}
-To quantify the similarity between the video topic trajectory and individual recall topic trajectories, we considered several novel metrics.
+% \subsection*{Novel memory measures afforded by our framework}
+% To quantify the similarity between the video topic trajectory and individual recall topic trajectories, we considered several novel metrics.
 First, we tested whether each participant's recall trajectory matched the video trajectory in a general sense.
@@
 
-\paragraph*{Precision.}
-We next tested whether participants who recalled more events were also more \textit{precise} in their recollections.
+% \paragraph*{Precision.}
+% We next tested whether participants who recalled more events were also more \textit{precise} in their recollections.
 For each participant, we computed the correlation between the topic vectors for each recall event and that of its closest-matching video event (only for the events which they recalled).
@@
 
-\paragraph*{Distinctiveness.}
-We also considered the \textit{distinctiveness} of each recalled event.
+% \paragraph*{Distinctiveness.}
+% We also considered the \textit{distinctiveness} of each recalled event.
 That is, how uniquely a recalled event's topic vector matched a given video event topic vector, versus the topic vectors for the other video events.
@@
 To test this hypothesis we define a distinctiveness score for each recalled event as
-\[
-  d(\mathrm{event}) = 1 - \bar{c}(\mathrm{event}),
-\]
-where $\bar{c}(\mathrm{event})$ is the average correlation between the given recalled event's topic vector and the topic vectors from all video events \textit{except} the best-matching video event.
+% \[
+%   d(\mathrm{event}) = 1 - \bar{c}(\mathrm{event}),
+% \]
+% where $\bar{c}(\mathrm{event})$ is the average correlation between the given recalled event's topic vector and the topic vectors from all video events \textit{except} the best-matching video event.
 We then averaged these distinctiveness scores across all of the events recalled by the given participant.
@@
 
-\paragraph*{Other order effects.}
-We tested whether participants with better memory performance were also more likely to remember the events in order.
+% NOTE: REMOVE THIS?
+% \paragraph*{Other order effects.}
+% We tested whether participants with better memory performance were also more likely to remember the events in order.
 For each participant, we computed the Spearman rank correlation between the order of events that the participant recalled and the order the events actually occurred in the video (considering in the analysis only the events that the participant recalled).

### 2019-06-18 paper/main.tex
saving progress on discussion

@@
 \newcommand{\featureimportance}{S3}
-\newcommand{\listlearning}{S4}
-\newcommand{\corrmats}{S5}
-\newcommand{\matchmats}{S6}
-\newcommand{\wasserstein}{S7}
+% \newcommand{\listlearning}{S4}
+\newcommand{\corrmats}{S4}
+\newcommand{\matchmats}{S5}
+\newcommand{\wasserstein}{S6}
 
@@
 
-Statistical models of memory studies often treat memory recalls as "all-or nothing" and independent events.
+Statistical models of memory studies often treat memory recalls as binary (e.g.
+the item was recalled or not) and independent events.
 However, our approach produces a content-based model of individual stimulus events and recall events, allowing for direct quantitative comparison between all stimulus and recall events, as well as between the recall events themselves.
 Leveraging this affordance, we introduce 2 novel metrics for quantifying memory representations: precision and distinctiveness.
-We define precision as the average correlation between each recall event and the maximally correlated video event [INSERT FIGURE REF].
-Participants whose recall events are more veridical descriptions of what happened in the video event will have higher precision scores.
-We find that across participants, a higher precision score is correlated to both hand annotated memory performance as well as the number of recall events (per participant) estimated by our model [INSERT STATS, INSERT FIGURE REF].
+We define precision as the average correlation between each recall event and the maximally correlated video event (Fig.~\ref{fig:precision-distinctiveness}).
+Participants whose recall events are more veridical descriptions of what happened in the video event will presumably have higher precision scores.
+We find that across participants, a higher precision score is correlated to both hand annotated memory performance (Pearson's $r(15) = 0.6, p = 0.011$) as well as the number of recall events (per participant) estimated by our model (Pearson's $r(15) = 0.64, p = 0.005$).
 A second novel metric we introduce here is the distinctiveness, or the uniqueness of each recall event relative to other recall events.
 Distinctiveness is defined as 1 minus the average of the upper triangle of the recall-by-recall correlation matrix.
-Similar to precision, we find that the more distinct participants recalls are (on average), the more they remembered (for both hand-annotated and model derived memory performance) [INSERT STATS AND FIGURE REF].
+Similar to precision, we find that the more distinct participants recalls are (on average), the more they remembered (hand-annotated memory: Pearson's $r(15) = 0.83, p < 0.001$ and model derived memory: Pearson's $r(15) = 0.71, p = 0.001$).
 In summary, using two novel metrics afforded by our approach, we find that participants whose recalls are both more precise and distinct remember more content.
@@
   \includegraphics[width=1\textwidth]{figs/precision_distinctiveness}
-  \caption{\small \textbf{Novel content-based metrics of naturalistic memory: precision and distinctiveness.} \textbf{A.} Blah-bahdy Blah}
+  \caption{\small \textbf{Novel content-based metrics of naturalistic memory: precision and distinctiveness.} \textbf{A.} A video-recall correlation matrix for a representative participant (17).
+The yellow boxes highlight the maximum correlation in each column.
+Precision was computed as the average of the maximum correlation in each column.
+On the other hand, distinctiveness was defined as the average of everything except for the maximum correlation in each column.
+\textbf{B.} The (Pearson's) correlation between precision and hand-annotated memory performance.
+\textbf{C.} The correlation between precision and the number of events recovered by the model ($k$).
+\textbf{D.} The correlation between distinctiveness and hand-annotated memory performance.
+\textbf{E.} The correlation between distinctiveness and the number of events recovered by the model ($k$).}
   \label{fig:precision-distinctiveness}
@@
 
-In this work, we used topic models to capure the contents of verbal recall.  While a large number of language models exist (e.g. WAS, LSA, word2vec), we
+Many statistical models of memory treat recall as binary and unrelated events.
+Our novel framework allows one to measure the \textit{precision} of each recall event (by considering the correlation to the highest video event) as well as how \textit{distinctive} each recall event is from other recall events.
+These new metrics afforded by our method allow for much more nuanced analysis of recall dynamics than were previously possible.
+Using them, we find that both precision and distinctiveness are correlated to the amount of information participants recall.
+Thus, the manner in which a person recounts a \textit{particular} event is related to their ability to recall \textit{many} events.
+
+While a large number of language models exist (e.g.
+WAS, LSA, word2vec, universal sentence encoder), here we use topic models for a few reasons.
+First, topic models capture the \textit{essence} of a text passage devoid of the specific set and order of words used.
+This was an important feature of our model since different people may accurately recall a scene using very different language.
+Secondly, words can mean different things in different contexts (e.g.
+baseball bat vs.
+the animal bat), and topic models are robust to this since words can be part of multiple topics.
+Lastly, topic models provide a straight forward to recover the weights for the particular words comprising a topic, allowing for easy interpretation of an event's contents (e.g.
+Fig.~\ref{fig:topics}).
+Other models such as Google's universal sentence encoder offer a context-sensitive encoding of text passages, but the encoding space is complex and non-linear and thus, recovering the original words used to fit the model is not straight forward.
+
+However, it's worth pointing out that our framework is divorced from the particular choice of language model.
+Moreover, many of the aspects of our framework could be swapped out for other choices.
+For example, the language model, the timeseries segmentation model and the video-recall matching function could all be customized for the particular problem.
+Indeed for some problems, recovery of the particular recall words may not be necessary, and thus other text-modeling approaches (such as universal sentence encoder) may be preferable.
+Future work will explore the influence of particular model choices on the framework's accuracy.
 

### 2019-06-19 paper/main.tex
finished edits to text, a few references left

@@
 %\title{A content-based framework describing the temporal dynamics of experiences and memories reveals event-like structure in naturalistic episodic recall}
-\title{A content-based model of how experiences and memories unfold over time reveals event-like structure in naturalistic episodic recall}
+%\title{A content-based model of how experiences and memories unfold over time reveals event-like structure in naturalistic episodic recall}
+\title{A framework for linking dynamic experiences to memories reveals event-like structure in naturalistic episodic recall}
 
@@
 \begin{abstract}
-The ways our experiences unfold over time define unique \textit{trajectories} through the relevant representational spaces.
+Our life experiences unfold over time and the temporal dynamics of their contents form unique \textit{experience trajectories}.
 Within this geometric framework, one can compare the shape of the trajectory formed by an experience to that defined by our later remembering of that experience.
@@
 We apply this approach to a naturalistic memory experiment which had participants view and recount a video.
-We found that the shapes of the trajectories formed by participants' recountings were all highly similar to that of the original video, but participants differed in the level of detail they remembered.
-Further, we identified a network of brain structures that are sensitive to the ``shapes'' of our ongoing experiences, and an overlapping network that is sensitive to how we will later remember those experiences.
+We find that the video and subsequent recall share an event-like structure, and that the shapes of the trajectories formed by participants' recountings were all highly similar to that of the original video.
+Further, the level of precision that participants' recount the events as well as how distinct their recountings are from other recall events both predict overall subsequent memory performance.
+Lastly, we identified a network of brain structures that are sensitive to the ``shapes'' of our ongoing experiences, and an overlapping network that is sensitive to how we will later remember those experiences.
+These result highlight that our dynamic experiences are structured into events in memory, and introduce a novel framework for mapping between dynamic life experiences and their mnemonic counterparts.
 \end{abstract}
@@
 More nuanced studies might incorporate self-reported confidence measures as a proxy for memory strength, or ask participants to discriminate between ``recollecting'' the (contextual) details of an experience or having a general feeling of ``familiarity'' \citep{Yone02}.
-Using well-controlled, trial-based experimental designs, the field has amassed a wealth of valuable information regarding human episodic memory.
+Undoubtedly, using well-controlled trial-based experimental designs, the field has amassed a wealth of valuable information regarding human episodic memory.
 However, there are fundamental properties of our memories that trial-based experiments are not well suited to capture~\citep[for review also see][]{KoriGold94, HukEtal18}.
 First, our memories are continuous, rather than discrete: removing a (naturalistic) event from the context in which it occurs can substantially change its meaning.
-Second, the specific words used to describe an experience have little bearing on whether the experience should be considered to have been ``remembered.''  Asking whether the rememberer has precisely reproduced a specific set of words to describe a given experience is nearly orthogonal to whether they were actually able to remember it.
+Second, the specific language used to describe an experience have little bearing on whether the experience should be considered to have been ``remembered.''  Asking whether the rememberer has precisely reproduced a specific set of words to describe a given experience is nearly orthogonal to whether they were actually able to remember it.
 In classic (e.g., list-learning) memory studies, by contrast, counting the number or proportion of precise recalls is often a primary metric of assessing the quality of participants' memories.
-Third, one might remember the essence of an experience but forget (or neglect to recount) particular details.
-Capturing the essence (or the \textit{shape}) of what happened is typically the main ``point'' of recounting a memory to a listener.
+Third, one might remember the \textit{essence} (or shape) of an experience but forget (or neglect to recount) particular details.
+Capturing the essence of what happened is typically the main ``point'' of recounting a memory to a listener.
 
@@
 Any given moment of an experience derives meaning from surrounding moments, as well as from longer-range temporal associations~\citep[e.g., ][]{LernEtal11}.
-Therefore the timecourse describing how an event unfolds is fundamental to its overall meaning.
+Therefore, the timecourse describing how an event unfolds is fundamental to its overall meaning.
 Further, this hierarchy formed by our subjective experiences at different timescales defines a \textit{context} for each new moment~\citep[e.g., ][]{HowaKaha02, HowaEtal14}, and plays an important role in how we interpret that moment and remember it later~\citep[for review see][]{MannEtal15}.
@@
 For example, as we navigate the world, the features of our subjective experiences tend to change gradually (e.g., the room or situation we are in is strongly temporally autocorrelated), allowing us to form stable estimates of our current situation and behave accordingly~\citep{ZackEtal07, ZwaaRadv98}.
+
 Although our experiences most often change gradually, they also occasionally change suddenly~\citep[e.g., when we walk through a doorway; ][]{RadvZack17}.
@@
 For example, prior work has shown that event boundaries can influence how we learn sequences of items~\citep{HeusEtal18b, DuBrDava13}, navigate~\citep{BrunEtal18}, and remember and understand narratives~\citep{ZwaaRadv98, EzzyDava11}.
-Prior studies have implicated the hippocampus and the medial prefrontal cortex as playing a critical role in this process [CITE].
+Prior research has implicated the hippocampus and the medial prefrontal cortex as playing a critical role in transforming experiences into stuctured and consolidated memories ~\citep{TompDava17}.
 
@@
 Specifically, we use topic modeling~\citep{BleiEtal03} to characterize the thematic conceptual (semantic) content present in each moment of the episode and recalls, and we use Hidden Markov Models~\citep{Rabi89, BaldEtal17} to discretize the evolving semantic content into events.
-In this way, we cast naturalistic experiences (and recalls of those experiences) as \textit{topic trajectories} that describe how the experiences evolve over time.
-In other words, the episode's topic trajectory is a formalization of its shape.
-Under this framework, successful remembering entails verbally ``traversing'' the topic trajectory of the original episode, thereby reproducing the original episode's shape.
-In addition, comparing the shapes of the topic trajectories of the original episode and of participants' retellings of the episode reveals which aspects of the episode were preserved (or lost) in the translation into memory.
-Further, we identified a network of brain structures whose responses (as participants watched the episode) reflected the shape of the episode, and a second network whose responses reflected how participants would later recount the episode.
+In this way, we cast naturalistic experiences (and recalls of those experiences) as \textit{trajectories} that describe how the experiences evolve over time.
+Under this framework, successful remembering entails verbally ``traversing'' the topic trajectory of the original episode, thereby reproducing the shape of the original experience.
+Comparing the shapes of the topic trajectories of the original episode and of participants' retellings of the episode reveals which aspects of the episode were preserved (or lost) in the translation into memory.
+
+% NOTE: Can we remove this part? its captured in the abstract
+% Using a series of novel memory metrics (introduced here and afforded by our computational framework), we find that the successful memory performance is related to 1) the \textit{precision} with which the participant recounts each event and 2) how \textit{distinctive} each recall event is (relative to the other recalled events).
+Finally, we identified a network of brain structures whose responses (as participants watched the episode) reflected the shape of the episode, and a second network whose responses reflected how participants would later recount the episode.
 
@@
 the item was recalled or not) and independent events.
-However, our approach produces a content-based model of individual stimulus events and recall events, allowing for direct quantitative comparison between all stimulus and recall events, as well as between the recall events themselves.
-Leveraging this affordance, we introduce 2 novel metrics for quantifying memory representations: precision and distinctiveness.
+However, our framework produces a content-based model of individual stimulus events and recall events, allowing for direct quantitative comparison between all stimulus and recall events, as well as between the recall events themselves.
+Leveraging this affordance, we introduce 2 novel metrics for quantifying naturalistic memory representations: precision and distinctiveness.
 We define precision as the average correlation between each recall event and the maximally correlated video event (Fig.~\ref{fig:precision-distinctiveness}).
@@
 A second novel metric we introduce here is the distinctiveness, or the uniqueness of each recall event relative to other recall events.
-Distinctiveness is defined as 1 minus the average of the upper triangle of the recall-by-recall correlation matrix.
+We define distinctiveness as 1 minus the average of all non-matching recall events from the video-recall correlation matrix.
+We hypothesized that participants who recounted events in a more distinctive way would display better overall memory.
 Similar to precision, we find that the more distinct participants recalls are (on average), the more they remembered (hand-annotated memory: Pearson's $r(15) = 0.83, p < 0.001$ and model derived memory: Pearson's $r(15) = 0.71, p = 0.001$).
@@
 
-Many statistical models of memory treat recall as binary and unrelated events.
-Our novel framework allows one to measure the \textit{precision} of each recall event (by considering the correlation to the highest video event) as well as how \textit{distinctive} each recall event is from other recall events.
-These new metrics afforded by our method allow for much more nuanced analysis of recall dynamics than were previously possible.
-Using them, we find that both precision and distinctiveness are correlated to the amount of information participants recall.
-Thus, the manner in which a person recounts a \textit{particular} event is related to their ability to recall \textit{many} events.
+When modeling memory experiments, often times events (or items) and their later memories are treated as binary (or categorical in the case of confidence ratings) and independent events.
+Our novel framework allows one to assess memory performance in a more continuous way, as well as analyze the correlational structure of each encoding event to each memory event.
+Further and importantly, it allows for consideration of the actual content of the experience/memories, which is not typically modeled.
+Leveraging this, using 2 novel memory metrics we find that the successful memory performance is related to 1) the \textit{precision} with which the participant recounts each event and 2) how \textit{distinctive} each recall event is (relative to the other recalled events).
+The first finding suggests to us that the accuracy of recall for \textit{any individual event} may predict the overall amount of information recovered by the participant.
+The second finding suggests that remembering/describing events in a unique way (relative to other recalled events) is also related to the quantity of content recovered.
+Intriguingly, prior studies show that pattern separation, or the ability to discriminate between similar experiences, is impaired in many cognitive disorders as well as natural aging [Craig Stark and friends].
+Future work might explore how/whether these metrics compare between cognitively impoverished groups and healthy controls.
 
 While a large number of language models exist (e.g.
-WAS, LSA, word2vec, universal sentence encoder), here we use topic models for a few reasons.
+WAS, LSA, word2vec, universal sentence encoder), here we use topic models for a few reasons [CITE THESE].
 First, topic models capture the \textit{essence} of a text passage devoid of the specific set and order of words used.
@@
 
-Statistical models of memory studies often treat memory recalls as binary and distinct events.
-However, our approach produces a formal model of individual stimulus events and recall events, allowing for direct quantitative comparison between all stimulus and recall events, as well as between the recall events themselves.
-Leveraging this fact, we introduce 2 novel metrics for quantifying memory representations: precision and distinctiveness.
-
 \paragraph*{Precision.}
-We next tested whether participants who recalled more events were also more \textit{precise} in their recollections.
+We tested whether participants who recalled more events were also more \textit{precise} in their recollections.
 For each participant, we computed the correlation between the topic vectors for each recall event and that of its closest-matching video event (only for the events which they recalled).
-We defined the precision as the average video-recall correlation across all of the events a participant recalled.
-We found a strong correlation between hand-annotated memory performance and precision, suggesting that participants who remembered more events also remembered them more veridically (Pearson's $r(15) = 0.74, p = 0.0006$).
+We Fisher's z-transformed the correlations, computed the average and then inverse Fisher's z-transformed the resulting value.
+This gave a single value per participant representing the average precision across all recalled events.
+We then correlated this value with hand-annotated as well as model derived (e.g.
+$k$ or the number of events recovered by the HMM) memory performance.
 
@@
 To test this hypothesis we define a distinctiveness score for each recalled event as
+
+%NOTE: Need to check on this equation!
 \[
@@
 We then averaged these distinctiveness scores across all of the events recalled by the given participant.
-We found that participants with higher average distinctiveness scores tended to also have better hand-annotated memory performance (Pearson's $r(15) = 0.8, p = 0.0001$).
+As above, we used Fisher's z (transform and inverse-transform) before/after averaging correlation values.
+Finally, we correlated these values with hand-annotated and model derived memory performance scores across-subjects.
 

### 2019-06-19 paper/main.tex
updated out-of-date bibtex keys, recompiled pdf

@@
 Therefore, the timecourse describing how an event unfolds is fundamental to its overall meaning.
-Further, this hierarchy formed by our subjective experiences at different timescales defines a \textit{context} for each new moment~\citep[e.g., ][]{HowaKaha02, HowaEtal14}, and plays an important role in how we interpret that moment and remember it later~\citep[for review see][]{MannEtal15}.
+Further, this hierarchy formed by our subjective experiences at different timescales defines a \textit{context} for each new moment~\citep[e.g., ][]{HowaKaha02a, HowaEtal14}, and plays an important role in how we interpret that moment and remember it later~\citep[for review see][]{MannEtal15}.
 Our memory systems can then leverage these associations to form predictions that help guide our behaviors~\citep{RangRitc12}.
@@
 The analysis revealed that the rMTL and vmPFC may play a role in this person-specific transformation from experience into memory.
-The role of the MTL in episodic memory encoding has been well-reported~\citep[e.g., ][]{PallWagn02, DavaEtAl03, RangEtal04, Dava06}.
+The role of the MTL in episodic memory encoding has been well-reported~\citep[e.g., ][]{PallWagn02, DavaEtAl03, RangEtal04a, Dava06}.
 Prior work has also implicated the medial prefrontal cortex in representing ``schema'' knowledge~\citep[i.e., general knowledge about the format of an ongoing experience given prior similar experiences; ][]{KestEtal12, SchlPres15, GilbMarl17, SpalEtal18}.

### 2019-07-18 paper/main.tex

@@
 %\title{A content-based model of how experiences and memories unfold over time reveals event-like structure in naturalistic episodic recall}
-\title{A framework for linking dynamic experiences to memories reveals event-like structure in naturalistic episodic recall}
+\title{A novel framework for linking dynamic experiences to memories reveals event-like structure in naturalistic episodic recall}
+%\title{Recalling naturalistic experiences exhibits event-like structure}
 
@@
 We apply this approach to a naturalistic memory experiment which had participants view and recount a video.
-We find that the video and subsequent recall share an event-like structure, and that the shapes of the trajectories formed by participants' recountings were all highly similar to that of the original video.
-Further, the level of precision that participants' recount the events as well as how distinct their recountings are from other recall events both predict overall subsequent memory performance.
-Lastly, we identified a network of brain structures that are sensitive to the ``shapes'' of our ongoing experiences, and an overlapping network that is sensitive to how we will later remember those experiences.
-These result highlight that our dynamic experiences are structured into events in memory, and introduce a novel framework for mapping between dynamic life experiences and their mnemonic counterparts.
+We find that the video and subsequent recall share an event-like structure, and that the ``shapes'' of the trajectories formed by participants' recountings were all highly similar to that of the original video.
+Further, participants' that recounted the events with a high level of precision and in a distinctive way had better subsequent memory performance.
+Lastly, we identified a network of brain structures that are sensitive to the shapes of our ongoing experiences, and an overlapping network that is sensitive to how we will later remember those experiences.
+These results highlight the rich event-like structure of memories for our life experiences, and introduce a novel framework for mapping between dynamic life experiences and their mnemonic counterparts.
 \end{abstract}
@@
 More nuanced studies might incorporate self-reported confidence measures as a proxy for memory strength, or ask participants to discriminate between ``recollecting'' the (contextual) details of an experience or having a general feeling of ``familiarity'' \citep{Yone02}.
-Undoubtedly, using well-controlled trial-based experimental designs, the field has amassed a wealth of valuable information regarding human episodic memory.
+Using well-controlled trial-based experimental designs, the field has amassed a wealth of valuable information regarding human episodic memory.
 However, there are fundamental properties of our memories that trial-based experiments are not well suited to capture~\citep[for review also see][]{KoriGold94, HukEtal18}.
@@
 
-% NOTE: Can we remove this part? its captured in the abstract
-% Using a series of novel memory metrics (introduced here and afforded by our computational framework), we find that the successful memory performance is related to 1) the \textit{precision} with which the participant recounts each event and 2) how \textit{distinctive} each recall event is (relative to the other recalled events).
-Finally, we identified a network of brain structures whose responses (as participants watched the episode) reflected the shape of the episode, and a second network whose responses reflected how participants would later recount the episode.
+Here, we introduce a novel content-based framework for linking dynamic experiences to memories.
+We hypothesized that the ``shape'' and the event-like structure of an experience would be preserved in memory.
+Further, we tested  1) whether the \textit{precision} with which the participant recounts each event and 2) how \textit{distinctive} each recall event is (relative to the other recalled events) relates to overall memory performance.
+Last, we identify networks of  brain structures whose responses (as participants watched the episode) reflected the shape of the episode, and how participants would later recount the episode.
 
@@
 For example, a detective-themed topic might weight heavily on words like ``crime,'' and ``search.''  The second output is a \textit{topic proportions matrix}, with one row per document and one column per topic.
-The topic proportions matrix describes which mix topics is reflected in each document.
+The topic proportions matrix describes which mixture of topics is reflected in each document.
 
@@
 the item was recalled or not) and independent events.
-However, our framework produces a content-based model of individual stimulus events and recall events, allowing for direct quantitative comparison between all stimulus and recall events, as well as between the recall events themselves.
-Leveraging this affordance, we introduce 2 novel metrics for quantifying naturalistic memory representations: precision and distinctiveness.
+However, our framework produces a content-based model of individual stimulus and recall events, allowing for direct quantitative comparison between all stimulus and recall events, as well as between the recall events themselves.
+Leveraging these content-based models of the stimulus/recall events, we developed 2 novel metrics for quantifying naturalistic memory representations: precision and distinctiveness.
 We define precision as the average correlation between each recall event and the maximally correlated video event (Fig.~\ref{fig:precision-distinctiveness}).
 Participants whose recall events are more veridical descriptions of what happened in the video event will presumably have higher precision scores.
-We find that across participants, a higher precision score is correlated to both hand annotated memory performance (Pearson's $r(15) = 0.6, p = 0.011$) as well as the number of recall events (per participant) estimated by our model (Pearson's $r(15) = 0.64, p = 0.005$).
-A second novel metric we introduce here is the distinctiveness, or the uniqueness of each recall event relative to other recall events.
+We find that across participants, a higher precision score is correlated to both hand annotated memory performance (Pearson's $r(15) = 0.6, p = 0.011$) as well as the number of recall events estimated by our model (Pearson's $r(15) = 0.64, p = 0.005$).
+A second novel metric we introduce here is distinctiveness, or how unique the recall description was to each video event.
 We define distinctiveness as 1 minus the average of all non-matching recall events from the video-recall correlation matrix.
@@
 
-The dynamic content of the video and participants' recalls is quantified in the corresponding topic proportion matrices.
+The prior analyses leverage the correspondence between the 100-dimensional topic proportion matrices for the video and participants' recalls to characterize recall.
 However, it is difficult to gain deep insights into that content solely by examining the topic proportion matrices (e.g., Figs.~\ref{fig:model}A, D) or the corresponding correlation matrices (Figs.~\ref{fig:model}B, E, \corrmats).
@@
 In this lower-dimensional space, each point represents a single video or recall event, and the distances between the points reflect the distances between the events' associated topic vectors (Fig.~\ref{fig:trajectory}).
+In other words, events that are near to each other in this space are more semantically similar.
 
@@
 When modeling memory experiments, often times events (or items) and their later memories are treated as binary (or categorical in the case of confidence ratings) and independent events.
-Our novel framework allows one to assess memory performance in a more continuous way, as well as analyze the correlational structure of each encoding event to each memory event.
+Our novel framework allows one to assess memory performance in a more continuous way (e.g.
+precision), as well as analyze the correlational structure of each encoding event to each memory event (e.g.
+distinctiveness).
 Further and importantly, it allows for consideration of the actual content of the experience/memories, which is not typically modeled.
@@
 The second finding suggests that remembering/describing events in a unique way (relative to other recalled events) is also related to the quantity of content recovered.
-Intriguingly, prior studies show that pattern separation, or the ability to discriminate between similar experiences, is impaired in many cognitive disorders as well as natural aging [Craig Stark and friends].
-Future work might explore how/whether these metrics compare between cognitively impoverished groups and healthy controls.
+Intriguingly, prior studies show that pattern separation, or the ability to discriminate between similar experiences, is impaired in many cognitive disorders as well as natural aging \citep{StarEtal10, YassEtal11c, YassStar11b}.
+Future work might explore how/whether the novel metrics introduce here compare between cognitively impoverished groups and healthy controls.
 
+% NOTE: do you know of a good reference for WAS and word2vec ?
 While a large number of language models exist (e.g.
-WAS, LSA, word2vec, universal sentence encoder), here we use topic models for a few reasons [CITE THESE].
+WAS, LSA, word2vec, universal sentence encoder) \citep{LandEtal98, CerEtal18}, here we use topic models for a few reasons.
 First, topic models capture the \textit{essence} of a text passage devoid of the specific set and order of words used.
@@
 Other models such as Google's universal sentence encoder offer a context-sensitive encoding of text passages, but the encoding space is complex and non-linear and thus, recovering the original words used to fit the model is not straight forward.
-
 However, it's worth pointing out that our framework is divorced from the particular choice of language model.
@@
 
-\subsubsection*{Visualizing the video and recall topic trajectories}
-We used the UMAP algorithm~\citep{McInHeal18} to project the 100-dimensional topic space onto a two-dimensional space for visualization (Figs.~\ref{fig:trajectory}, \ref{fig:topics}).
-To ensure that all of the trajectories were projected onto the \textit{same} lower dimensional space, we computed the low-dimensional embedding on a ``stacked'' matrix created by vertically concatenating the events-by-topics topic proportions matrices for the video and all 17 participants' recalls.
-We then divided the rows of the result (a total-number-of-events by two matrix) back into separate matrices for the video topic trajectory and the trajectories for each participant's recalls (Fig.~\ref{fig:trajectory}).
-This general approach for discovering a shared low-dimensional embedding for a collections of high-dimensional observations follows \cite{HeusEtal18a}.
-
-\subsubsection*{Estimating the consistency of flow through topic space across participants}
-In Figure~\ref{fig:trajectory}B, we present an analysis aimed at characterizing locations in topic space that different participants move through in a consistent way (via their recall topic trajectories).
-The two-dimensional topic space used in our visualizations (Fig.~\ref{fig:trajectory}) ranged from -5 to 5 (arbitrary) units in the $x$ dimension and from -6.5 to 2 units in the $y$ dimension.
-We divided this space into a grid of vertices spaced 0.25~units apart.
-For each vertex, we examined the set of line segments formed by connecting each pair successively recalled events, across all participants, that passed within 0.5 units.
-We computed the distribution of angles formed by those segments and the $x$-axis, and used a Rayleigh test to determine whether the distribution of angles was reliably ``peaked'' (i.e., consistent across all transitions that passed through that local portion of topic space).
-To create Figure~\ref{fig:trajectory}B we drew an arrow originating from each grid vertex, pointing in the direction of the average angle formed by line segments that passed within 0.5 units.
-We set the arrow lengths to be inversely proportional to the $p$-values of the Rayleigh tests at each vertex.
-Specifically, for each vertex we converted all of the angles of segments that passed within 0.5 units to unit vectors, and we set the arrow lengths at each vertex proportional to the length of the (circular) mean vector.
-We also indicated any significant results ($p < 0.05$, corrected using the Benjamani-Hochberg procedure) by coloring the arrows in blue (darker blue denotes a lower $p$-value, i.e., a longer mean vector); all tests with $p \geq 0.05$ are displayed in gray and given a lower opacity value.
-
-\subsection*{Naturalistic extensions of classic list-learning analyses}
+\subsubsection*{Naturalistic extensions of classic list-learning analyses}
 In traditional list-learning experiments, participants view a list of items (e.g., words) and then recall the items later.
@@
 
+\subsubsection*{Novel naturalistic memory metrics}
+
 \paragraph*{Precision.}
@@
 Finally, we correlated these values with hand-annotated and model derived memory performance scores across-subjects.
+
+\subsubsection*{Visualizing the video and recall topic trajectories}
+We used the UMAP algorithm~\citep{McInHeal18} to project the 100-dimensional topic space onto a two-dimensional space for visualization (Figs.~\ref{fig:trajectory}, \ref{fig:topics}).
+To ensure that all of the trajectories were projected onto the \textit{same} lower dimensional space, we computed the low-dimensional embedding on a ``stacked'' matrix created by vertically concatenating the events-by-topics topic proportions matrices for the video and all 17 participants' recalls.
+We then divided the rows of the result (a total-number-of-events by two matrix) back into separate matrices for the video topic trajectory and the trajectories for each participant's recalls (Fig.~\ref{fig:trajectory}).
+This general approach for discovering a shared low-dimensional embedding for a collections of high-dimensional observations follows \cite{HeusEtal18a}.
+
+\subsubsection*{Estimating the consistency of flow through topic space across participants}
+In Figure~\ref{fig:trajectory}B, we present an analysis aimed at characterizing locations in topic space that different participants move through in a consistent way (via their recall topic trajectories).
+The two-dimensional topic space used in our visualizations (Fig.~\ref{fig:trajectory}) ranged from -5 to 5 (arbitrary) units in the $x$ dimension and from -6.5 to 2 units in the $y$ dimension.
+We divided this space into a grid of vertices spaced 0.25~units apart.
+For each vertex, we examined the set of line segments formed by connecting each pair successively recalled events, across all participants, that passed within 0.5 units.
+We computed the distribution of angles formed by those segments and the $x$-axis, and used a Rayleigh test to determine whether the distribution of angles was reliably ``peaked'' (i.e., consistent across all transitions that passed through that local portion of topic space).
+To create Figure~\ref{fig:trajectory}B we drew an arrow originating from each grid vertex, pointing in the direction of the average angle formed by line segments that passed within 0.5 units.
+We set the arrow lengths to be inversely proportional to the $p$-values of the Rayleigh tests at each vertex.
+Specifically, for each vertex we converted all of the angles of segments that passed within 0.5 units to unit vectors, and we set the arrow lengths at each vertex proportional to the length of the (circular) mean vector.
+We also indicated any significant results ($p < 0.05$, corrected using the Benjamani-Hochberg procedure) by coloring the arrows in blue (darker blue denotes a lower $p$-value, i.e., a longer mean vector); all tests with $p \geq 0.05$ are displayed in gray and given a lower opacity value.
 

### 2019-07-21 paper/main.tex
saving progress

@@
 \begin{abstract}
-Our life experiences unfold over time and the temporal dynamics of their contents form unique \textit{experience trajectories}.
+Our life experiences unfold over time in highly complex manner, with the evolving presence and absence of numerous intricate features describing our journey between each circumstance or event we encounter.
+Here, we propose a framework for mapping dynamic naturalistic experiences onto geometric spaces as \textit{trajectories} that capture the temporal dynamics of real-world content.
+Within this geometric framework, one may compare the shape of the trajectory formed by an experience to that defined by one's later recollection to characterize our memories' recovery and distortion of the external world.
+Here, we apply this approach to a naturalistic memory experiment in which participants viewed and verbally recounted a video, and find that the video and subsequent recalls share both an experience-specific shape and a discernible event-like structure.
+However, the level of \textit{precision} with which individuals recounted various events and the \textit{distinctiveness} of recall for those events were varied and predictive of overall memory performance.
+Finally, we identify a network of brain structures that is sensitive to the ``shapes" of our ongoing experiences, and an overlapping network sensitive to how we will later remember them.
+These results highlight the rich event-like structure of the external world and our memories, and offer novel, content-sensitive alternatives to classical ``proportion recalled" measures for assessing episodic memory
+%Our life experiences unfold over time and the temporal dynamics of their contents form unique \textit{experience trajectories}.
 Within this geometric framework, one can compare the shape of the trajectory formed by an experience to that defined by our later remembering of that experience.
@@
 More nuanced studies might incorporate self-reported confidence measures as a proxy for memory strength, or ask participants to discriminate between ``recollecting'' the (contextual) details of an experience or having a general feeling of ``familiarity'' \citep{Yone02}.
-Using well-controlled trial-based experimental designs, the field has amassed a wealth of valuable information regarding human episodic memory.
-However, there are fundamental properties of our memories that trial-based experiments are not well suited to capture~\citep[for review also see][]{KoriGold94, HukEtal18}.
-First, our memories are continuous, rather than discrete: removing a (naturalistic) event from the context in which it occurs can substantially change its meaning.
-Second, the specific language used to describe an experience have little bearing on whether the experience should be considered to have been ``remembered.''  Asking whether the rememberer has precisely reproduced a specific set of words to describe a given experience is nearly orthogonal to whether they were actually able to remember it.
-In classic (e.g., list-learning) memory studies, by contrast, counting the number or proportion of precise recalls is often a primary metric of assessing the quality of participants' memories.
-Third, one might remember the \textit{essence} (or shape) of an experience but forget (or neglect to recount) particular details.
-Capturing the essence of what happened is typically the main ``point'' of recounting a memory to a listener.
+Using well-controlled, trial-based experimental designs, the field has amassed a wealth of valuable information regarding human episodic memory.
+However, there are fundamental properties of the external world and our memories that trial-based experiments are not well suited to capture~\citep[for review also see][]{KoriGold94, HukEtal18}.
+First, our experiences and memories are continuous, rather than discrete---removing a (naturalistic) event from the context in which it occurs can substantially change its meaning.
+Second, the specific language used to describe an experience has little bearing on whether the experience should be considered to have been ``remembered.''  Asking whether the rememberer has precisely reproduced a specific set of words to describe a given experience is nearly orthogonal to whether they were actually able to remember it.
+In classic (e.g., list-learning) memory studies, by contrast, the number or proportion of precise recalls is often a primary metric for assessing the quality of participants' memories.
+Third, one might remember the \textit{essence} (or a general summary) of an experience but forget (or neglect to recount) particular details.
+Capturing the essence of what happened is typically the main ``point'' of recounting a memory to a listener, while the addition of highly specific details may add comparatively little to successful conveyance of an experience.
 
-How might one go about formally characterizing the shape of an experience, or whether that shape has been recovered by the rememberer?
-Any given moment of an experience derives meaning from surrounding moments, as well as from longer-range temporal associations~\citep[e.g., ][]{LernEtal11}.
+How might one go about formally characterizing the essence of an experience, or whether it has been recovered by the rememberer?
+Any given moment of an experience derives meaning from surrounding moments, as well as from longer-range temporal associations~\citep[e.g., ][]{LernEtal11, Mann19}.
 Therefore, the timecourse describing how an event unfolds is fundamental to its overall meaning.
 Further, this hierarchy formed by our subjective experiences at different timescales defines a \textit{context} for each new moment~\citep[e.g., ][]{HowaKaha02a, HowaEtal14}, and plays an important role in how we interpret that moment and remember it later~\citep[for review see][]{MannEtal15}.
-Our memory systems can then leverage these associations to form predictions that help guide our behaviors~\citep{RangRitc12}.
-For example, as we navigate the world, the features of our subjective experiences tend to change gradually (e.g., the room or situation we are in is strongly temporally autocorrelated), allowing us to form stable estimates of our current situation and behave accordingly~\citep{ZackEtal07, ZwaaRadv98}.
+Our memory systems can leverage these associations to form predictions that help guide our behaviors~\citep{RangRitc12}.
+For example, as we navigate the world, the features of our subjective experiences tend to change gradually (e.g., the room or situation we are in at any given moment is strongly temporally autocorrelated), allowing us to form stable estimates of our current situation and behave accordingly~\citep{ZackEtal07, ZwaaRadv98}.
 
 Although our experiences most often change gradually, they also occasionally change suddenly~\citep[e.g., when we walk through a doorway; ][]{RadvZack17}.
-Prior research suggests that these sharp transitions (termed \textit{event boundaries}) during an experience help to discretize our experiences into \textit{events}~\citep{RadvZack17, BrunEtal18, HeusEtal18b, ClewDava17, EzzyDava11, DuBrDava13}.
+Prior research suggests that these sharp transitions (termed \textit{event boundaries}) during an experience help to discretize our experiences (and their mental representations) into \textit{events}~\citep{RadvZack17, BrunEtal18, HeusEtal18b, ClewDava17, EzzyDava11, DuBrDava13}.
 The interplay between the stable (within event) and transient (across event) temporal dynamics of an experience also provides a potential framework for transforming experiences into memories that distill those experiences down to their essence.
@@
 
-Here we sought to examine how the temporal dynamics of a ``naturalistic'' experience were reflected in participants' later memories of that experience.
-We analyzed an open dataset that comprised behavioral and functional Magnetic Resonance Imaging (fMRI) data collected as participants viewed and then verbally recalled an episode of the BBC television series \textit{Sherlock}~\citep{ChenEtal17}.
+Here we sought to examine how the temporal dynamics of a ``naturalistic'' experience were later reflected in participants' memories.
+We analyzed an open dataset that comprised behavioral and functional Magnetic Resonance Imaging (fMRI) data collected as participants viewed and then verbally recounted an episode of the BBC television series \textit{Sherlock}~\citep{ChenEtal17}.
 We developed a computational framework for characterizing the temporal dynamics of the moment-by-moment content of the episode and of participants' verbal recalls.
-Specifically, we use topic modeling~\citep{BleiEtal03} to characterize the thematic conceptual (semantic) content present in each moment of the episode and recalls, and we use Hidden Markov Models~\citep{Rabi89, BaldEtal17} to discretize the evolving semantic content into events.
+Specifically, we use topic modeling~\citep{BleiEtal03} to characterize the thematic conceptual (semantic) content present in each moment of the episode and recalls, and Hidden Markov Models~\citep{Rabi89, BaldEtal17} to discretize the evolving semantic content into events.
 In this way, we cast naturalistic experiences (and recalls of those experiences) as \textit{trajectories} that describe how the experiences evolve over time.
-Under this framework, successful remembering entails verbally ``traversing'' the topic trajectory of the original episode, thereby reproducing the shape of the original experience.
-Comparing the shapes of the topic trajectories of the original episode and of participants' retellings of the episode reveals which aspects of the episode were preserved (or lost) in the translation into memory.
-
-Here, we introduce a novel content-based framework for linking dynamic experiences to memories.
-We hypothesized that the ``shape'' and the event-like structure of an experience would be preserved in memory.
-Further, we tested  1) whether the \textit{precision} with which the participant recounts each event and 2) how \textit{distinctive} each recall event is (relative to the other recalled events) relates to overall memory performance.
+Under this framework, successful remembering entails verbally ``traversing'' the content trajectory of the episode, thereby reproducing the shape (or essence) of the original experience.
+Comparing the shapes of the topic trajectories of the episode and of participants' retellings of the episode then reveals which aspects of the episode were preserved (or lost) in the translation into memory.
+We further examine whether 1) the \textit{precision} with which a participant recounts each event and 2) the \textit{distinctiveness} each recall event is (relative to the other recalled events) relates to their overall memory performance.
 Last, we identify networks of  brain structures whose responses (as participants watched the episode) reflected the shape of the episode, and how participants would later recount the episode.
@@
 \section*{Results}
-To characterize the shape of the \textit{Sherlock} episode participants watched and their subsequent recountings of the episode, we used a topic model~\citep{BleiEtal03} to discover the latent thematic content in the video.
+To characterize the shape of the \textit{Sherlock} episode and participants' subsequent recountings of its unfolding, we used a topic model~\citep{BleiEtal03} to discover the latent themes in the episode's dynamic content.
 Topic models take as inputs a vocabulary of words to consider and a collection of text documents; they return as output two matrices.
@@
 
-\cite{ChenEtal17} collected hand-annotated information about each of 1000 (manually identified) scenes spanning the roughly 45 minute video used in their experiment.
+\cite{ChenEtal17} collected hand-annotated information about each of 1000 (manually identified) scenes spanning the roughly 50 minute video used in their experiment.
 This information included: a brief narrative description of what was happening; whether the scene took place indoors vs.
@@
 We took from these annotations the union of all unique words (excluding stop words, such as ``and,'' ``or,'' ``but,'' etc.) across all features and scenes as the ``vocabulary'' for the topic model.
-We then concatenated the sets of words across all features contained in overlapping 50-scene sliding windows, and treated each 50-scene sequence as a single ``document'' for the purposes of fitting the topic model.
+We then concatenated the sets of words across all features contained in overlapping, 50-scene sliding windows, and treated each 50-scene sequence as a single ``document'' for the purpose of fitting the topic model.
 Next, we fit a topic model with (up to) $K = 100$ topics to this collection of documents.
@@
 Further, the dynamics of the topic activations appeared to exhibit \textit{persistance} (i.e., given that a topic was active in one timepoint, it was likely to be active in the following timepoint) along with \textit{occasional rapid changes} (i.e., occasionally topics would appear to spring into or out of existence).
-These two properties of the topic dynamics may be seen in the block diagonal structure of the timepoint-by-timepoint correlation matrix (Fig.~\ref{fig:model}B).
-Following \cite{BaldEtal17}, we used a Hidden Markov Model (HMM) to identify the \textit{event boundaries} where the topic activations changed rapidly (i.e., at the boundaries of the blocks in the correlation matrix; event boundaries identified by the HMM are outlined in yellow).
+These two properties of the topic dynamics may be seen in the block diagonal structure of the timepoint-by-timepoint correlation matrix (Fig.~\ref{fig:model}B) and reflect the gradual drift and sudden shifts fundamental to the contextual dynamics of real-world experiences.
+Given this observation, we adapted an approach devised by \cite{BaldEtal17}, and used a Hidden Markov Model (HMM) to identify the \textit{event boundaries} where the topic activations changed rapidly (i.e., at the boundaries of the blocks in the correlation matrix; event boundaries identified by the HMM are outlined in yellow).
 Part of our model fitting procedure required selecting an appropriate number of ``events'' to segment the timeseries into.

### 2019-07-22 paper/main.tex
saving revision progress

@@
 Note that an important feature of our approach is that it allows us to compare participant's recalls to events from the original video, despite that different participants may have used different language to describe the same event, and that those descriptions may not match the original annotations.
-This is a huge benefit of projecting the video and recalls into a shared ``topic'' space.
+This is a substantial benefit of projecting the video and recalls into a shared ``topic'' space.
 An example topic proportions matrix from one participant's recalls is shown in Figure~\ref{fig:model}D.
@@
 For example, some participants' recall topic proportions segmented into just a few events (e.g., Participants P1, P4, and P15), while others' recalls segmented into many shorter duration events (e.g., Participants P12, P13, and P17).
-This suggests that different participants may be recalling the video with different levels of detail-- e.g., some might touch on just the major plot points, whereas others might attempt to recall every minor scene.
+This suggests that different participants may be recalling the video with different levels of detail-- e.g., some might touch on just the major plot points, whereas others might attempt to recall every minor scene or action.
 The second clear pattern present in every individual participant's recall correlation matrix is that, unlike in the video correlation matrix, there are substantial off-diagonal correlations in participant's recalls.
-Whereas each event in the original video (was largely) separable from the others (Fig.~\ref{fig:model}B), in transforming those separable events into memory participants appear to be integrating \textit{across} different events, blending elements of previously recalled and not-yet-recalled events into each newly recalled event~\citep[Figs.~\ref{fig:model}D, \corrmats; also see][]{MannEtal11, HowaEtal12}.
+Whereas each event in the original video was (largely) separable from the others (Fig.~\ref{fig:model}B), in transforming those separable events into memory participants appear to be integrating \textit{across} different events, blending elements of previously recalled and not-yet-recalled events into each newly recalled event~\citep[Figs.~\ref{fig:model}D, \corrmats; also see][]{MannEtal11, HowaEtal12}.
 
 The above results indicate that both the structure of the original video and participants' recalls of the video exhibit event boundaries that can be identified automatically by characterizing the dynamic content using a shared topic model and segmenting the content into events using HMMs.
-Next we asked whether some correspondence might be made between the specific content of the events the participants experienced in the video, and the events they later recalled.
+Next, we asked whether some correspondence might be made between the specific content of the events the participants experienced in the video, and the events they later recalled.
 One approach to linking the experienced (video) and recalled events is to label each recalled event as matching the video event with the most similar (i.e., most highly correlated) topic vector (Figs.~\ref{fig:model}G, \matchmats).
@@
 Analogous to classic list-learning studies, we can then examine participants' recall sequences by asking which events they tended to recall first~\citep[probability of first recall; Fig.~\ref{fig:list-learning}A;][]{WelcBurn24, PostPhil65, AtkiShif68}; how participants most often transition between recalls of the events as a function of the temporal distance between them~\citep[lag-conditional response probability; Fig.~\ref{fig:list-learning}B;][]{Kaha96}; and which events they were likely to remember overall~\citep[serial position recall analyses; Fig.~\ref{fig:list-learning}C;][]{Murd62a}.
-Interestingly, for 2 of the analyses (probability of first recall and lag-conditional response probability curves) we observe patterns comparable to classic effects from the list-learning literature.
-Namely, a higher probability of initiating recall with the first event in the sequence (Fig.~\ref{fig:list-learning}A) and a higher probability of transitioning to neighboring events with a forward assymetric bias (Fig.~\ref{fig:list-learning}C).
+Interestingly, for 2 of these analyses (probability of first recall and lag-conditional response probability curves) we observe patterns comparable to classic effects from the list-learning literature: namely, a higher probability of initiating recall with the first event in the sequence (Fig.~\ref{fig:list-learning}A) and a higher probability of transitioning to neighboring events with an asymmetric forward bias (Fig.~\ref{fig:list-learning}C).
 In contrast, we do not observe a pattern comparable to the serial position effect (Fig.~\ref{fig:list-learning}C), but rather we see higher memory for specific events distributed somewhat evenly throughout the video.
+
+% One may reasonably hypothesize that the diminished effect of presentation order on recall likelihood stems from 1) differences between the presence of certain features of episodic experiences that are absent in the simple, discretized stimuli of classic list-learning experiments.
+Random word lists most often employ simple, common words While they are well-suited to the random word-list paradigm, these analyses address only the temporal order of stimuli, neglecting to consider their content (or, for example, that content's potential interrelatedness).
+This difference serves to highlight the need for alternative approaches to quantifying memory success that account for such contextual features and the way they may impact memory organization and retrieval dynamics.
 
@@
 However, our framework produces a content-based model of individual stimulus and recall events, allowing for direct quantitative comparison between all stimulus and recall events, as well as between the recall events themselves.
-Leveraging these content-based models of the stimulus/recall events, we developed 2 novel metrics for quantifying naturalistic memory representations: precision and distinctiveness.
-We define precision as the average correlation between each recall event and the maximally correlated video event (Fig.~\ref{fig:precision-distinctiveness}).
+Leveraging these content-based models of the stimulus/recall events, we developed two novel metrics for quantifying naturalistic memory representations:~\textit{precision} and \textit{distinctiveness}.
+We define precision as the average correlation between the topic proportions of each recall event and the maximally correlated video event (Fig.~\ref{fig:precision-distinctiveness}).
 Participants whose recall events are more veridical descriptions of what happened in the video event will presumably have higher precision scores.
-We find that across participants, a higher precision score is correlated to both hand annotated memory performance (Pearson's $r(15) = 0.6, p = 0.011$) as well as the number of recall events estimated by our model (Pearson's $r(15) = 0.64, p = 0.005$).
+We find that across participants, a higher precision score is correlated to both hand annotated memory performance (Pearson's $r(15) = 0.6, p = 0.011$) and the number of recall events estimated by our model (Pearson's $r(15) = 0.64, p = 0.005$).
 A second novel metric we introduce here is distinctiveness, or how unique the recall description was to each video event.
@@
 We hypothesized that participants who recounted events in a more distinctive way would display better overall memory.
-Similar to precision, we find that the more distinct participants recalls are (on average), the more they remembered (hand-annotated memory: Pearson's $r(15) = 0.83, p < 0.001$ and model derived memory: Pearson's $r(15) = 0.71, p = 0.001$).
+Similarly to precision, we find that the more distinct participants recalls are (on average), the more they remembered (hand-annotated memory: Pearson's $r(15) = 0.83, p < 0.001$; model-derived memory: Pearson's $r(15) = 0.71, p = 0.001$).
 In summary, using two novel metrics afforded by our approach, we find that participants whose recalls are both more precise and distinct remember more content.
@@
 An analogous analysis revealed which themes were poorly remembered.
-Here in computing the weighted average over events' topic vectors we weighted each event in \textit{inverse} proportion to how well it was remembered (Fig.~\ref{fig:topics}B, red box).
+Here in computing the weighted average over events' topic vectors, we weighted each event in \textit{inverse} proportion to how well it was remembered (Fig.~\ref{fig:topics}B, red box).
 This revealed that events with relatively minor characters such as ``Mike,'' ``Jeffrey,'' and ``Molly,'' as well as less-integral plot locations (e.g., ``hospital'' and ``office'') were least well-remembered.
@@
 
-In addition to constructing overall summaries, assessing the video and recall topic vectors from individual recalls can provide further insights.
+In addition to constructing overall summaries, assessing the video and recall topic vectors from individual events can provide further insights.
 Specifically, for any given event we can construct two wordles: one from the original video event's topic vector, and a second from the average topic vectors produced by all participants' recalls of that event.
-We can then examine those wordles visually to gain an intuition for which aspects of the video event were recapitulated in participants' recalls of that event.
+We can then examine those wordles visually to gain an intuition for which aspects of the video event were recapitulated in participants' recalls.
 Several example wordles are displayed in Figure~\ref{fig:topics}C (wordles from the three best-remembered events are circled in green; wordles from the three worst-remembered events are circled in red).
@@
 In one analysis we sought to identify which brain structures were sensitive to the video's dynamic content, as characterized by its topic trajectory.
-Specifically, we used a searchlight procedure to identify the extent to which each cluster of voxels exhibited a timecourse (as the participants watched the video) whose temporal correlation matrix matched the temporal correlation matrix of the original video's topic proportion matrix (Fig.~\ref{fig:model}B).
-As shown in Figure~\ref{fig:brainz}A, the analysis revealed a network of regions including bilateral frontal cortex and cingulate cortex, suggesting that these regions may play a role in maintaining information relevant to the narrative structure of the video.
+Specifically, we used a searchlight procedure to identify the extent to which each cluster of voxels exhibited a timecourse of activity (as the participants watched the video) whose temporal correlation matrix matched the temporal correlation matrix of the original video's topic proportions (Fig.~\ref{fig:model}B).
+As shown in Figure~\ref{fig:brainz}A, the analysis revealed a network of regions including bilateral frontal cortex and cingulate cortex, suggesting that these regions may play a role in processing information relevant to the narrative structure of the video.
 In a second analysis, we sought to identify which brain structures' responses (while viewing the video) reflected how each participant would later \textit{recall} the video.
 We used an analogous searchlight procedure to identify clusters of voxels whose temporal correlation matrices reflected the temporal correlation matrix of the topic proportions for each individual's recalls (Figs.~\ref{fig:model}D, \corrmats).
-As shown in Figure~\ref{fig:brainz}B, the analysis revealed a network of regions including the ventromedial prefrontal cortex (vmPFC), anterior cingulate cortex, and right medial temporal lobe (rMTL), suggesting that these regions may play a role in transforming each individual's experience into memory.
+As shown in Figure~\ref{fig:brainz}B, the analysis revealed a network of regions including the ventromedial prefrontal cortex (vmPFC), anterior cingulate cortex (ACC), and right medial temporal lobe (rMTL), suggesting that these regions may play a role in transforming each individual's experience into memory.
 In identifying regions whose responses to ongoing experiences reflect how those experiences will be remembered later, this latter analysis extends classic \textit{subsequent memory analyses}~\citep[e.g.,][]{PallWagn02} to domain of naturalistic stimuli.

### 2019-07-22 paper/main.tex
saving progress on list learning discussion section

@@
 Analogous to classic list-learning studies, we can then examine participants' recall sequences by asking which events they tended to recall first~\citep[probability of first recall; Fig.~\ref{fig:list-learning}A;][]{WelcBurn24, PostPhil65, AtkiShif68}; how participants most often transition between recalls of the events as a function of the temporal distance between them~\citep[lag-conditional response probability; Fig.~\ref{fig:list-learning}B;][]{Kaha96}; and which events they were likely to remember overall~\citep[serial position recall analyses; Fig.~\ref{fig:list-learning}C;][]{Murd62a}.
-Interestingly, for 2 of these analyses (probability of first recall and lag-conditional response probability curves) we observe patterns comparable to classic effects from the list-learning literature: namely, a higher probability of initiating recall with the first event in the sequence (Fig.~\ref{fig:list-learning}A) and a higher probability of transitioning to neighboring events with an asymmetric forward bias (Fig.~\ref{fig:list-learning}C).
+Interestingly, for two of these analyses (probability of first recall and lag-conditional response probability curves) we observe patterns comparable to classic effects from the list-learning literature: namely, a higher probability of initiating recall with the first event in the sequence (Fig.~\ref{fig:list-learning}A) and a higher probability of transitioning to neighboring events with an asymmetric forward bias (Fig.~\ref{fig:list-learning}C).
 In contrast, we do not observe a pattern comparable to the serial position effect (Fig.~\ref{fig:list-learning}C), but rather we see higher memory for specific events distributed somewhat evenly throughout the video.
-
-% One may reasonably hypothesize that the diminished effect of presentation order on recall likelihood stems from 1) differences between the presence of certain features of episodic experiences that are absent in the simple, discretized stimuli of classic list-learning experiments.
-Random word lists most often employ simple, common words While they are well-suited to the random word-list paradigm, these analyses address only the temporal order of stimuli, neglecting to consider their content (or, for example, that content's potential interrelatedness).
-This difference serves to highlight the need for alternative approaches to quantifying memory success that account for such contextual features and the way they may impact memory organization and retrieval dynamics.
 
@@
 
-Our work casts remembering as reproducing (behaviorally and neurally) the topic trajectory, or shape, of the original experience.
+Our work casts remembering as reproducing (behaviorally and neurally) the topic trajectory, or shape, of an experience.
 This view draws inspiration from prior work aimed at elucidating the neural and behavioral underpinnings of how we process dynamic naturalistic experiences and remember them later.
 One approach to identifying neural responses to naturalistic stimuli (including experiences) entails building a model of the stimulus and searching for brain regions whose responses are consistent with the model.
-In prior work, a series of studies from Uri Hasson's group~\citep{LernEtal11, SimoEtal16, ChenEtal17, BaldEtal17, ZadbEtal17} have extended this approach with a clever twist.
-Rather than building an explicit stimulus model, these studies instead search for brain responses (while experiencing the stimulus) that are reliably similar across individuals.
+In prior work, a series of studies from Uri Hasson's group~\citep{LernEtal11, SimoEtal16, ChenEtal17, BaldEtal17, ZadbEtal17} have extended this approach with a clever twist: rather than building an explicit stimulus model, these studies instead search for brain responses (while experiencing the stimulus) that are reliably similar across individuals.
 So called \textit{inter-subject correlation} (ISC) and \textit{inter-subject functional connectivity} (ISFC) analyses effectively treat other people's brain responses to the stimulus as a ``model'' of how its features change over time.
@@
 The analysis revealed that the rMTL and vmPFC may play a role in this person-specific transformation from experience into memory.
-The role of the MTL in episodic memory encoding has been well-reported~\citep[e.g., ][]{PallWagn02, DavaEtAl03, RangEtal04a, Dava06}.
-Prior work has also implicated the medial prefrontal cortex in representing ``schema'' knowledge~\citep[i.e., general knowledge about the format of an ongoing experience given prior similar experiences; ][]{KestEtal12, SchlPres15, GilbMarl17, SpalEtal18}.
+The role of the MTL in episodic memory encoding has been well-reported~\citep[e.g., ][]{PallWagn02, DavaEtAl03, RangEtal04a, Dava06, WiltSilv07, DianEtal07, KestEtal13}.
+Prior work has also implicated the medial prefrontal cortex in representing ``schema'' knowledge~\citep[i.e., general knowledge about the format of an ongoing experience given prior similar experiences; ][]{KestEtal12, KestEtal13, SchlPres15, GilbMarl17, SpalEtal18}.
 Integrating across our study and this prior work, one interpretation is that the person-specific transformations mediated (or represented) by the rMTL and vmPFC may reflect schema knowledge being leveraged, formed, or updated, incorporating ongoing experience into previously acquired knowledge.
+% Here's a bunch of citations to possibly add to this last sentence, though not sure if we should because the sentence is framed as a "new idea" to come out of this study:
+% Takashima et al., 2007 -- vmPFC involved in stabilizing/reorganizing retrieval networks
+% Tse et al., 2007; Zeithamova and Preston, 2010; Tse et al., 2011 -- vmPFC involved in integrating featurally similar experiences
+% Nieuwenhuis and Takashima, 2011 -- vmPFC activity linked to evaluating memories' relevance to current situation
+% Kuhl et al., 2007; Wimber et al., 2008, 2009, 2011, 2015 -- vmPFC and vlPFC inhibit contextually irrelevant memories during retrieval
+% -Paxton
+
+In extending classical free recall analyses to our naturalistic memory framework, we recovered two patterns of recall dynamics similar to those central to list-learning studies: a high probability of initiating recall with the first video event (Fig.~\ref{fig:list-learning}A) and a strong bias toward transitioning from recalling a given event to recalling the event immediately following it (Fig.~\ref{fig:list-learning}B).
+However, equally noteworthy are the typical free recall results not recovered in these analyses, as each highlights a fundamental difference between list-learning studies and naturalistic memory paradigms like that employed in the present study.
+The most noticeable departure from hallmark free recall dynamics in these findings is the apparent lack of a serial position effect in Figure \ref{fig:list-learning}C, which instead shows greater and lesser recall probabilities for events distributed across the video.
+Free recall experiments' stimuli most often comprise lists of simple, common words, presented to participants in a random order.
+\citep[In fact, numerous word pools have been developed for precisely this purpose; e.g.,][]{FrieEtal82}.
+These stimulus qualities enable two assumptions that are central to word list analyses, but frequently do not hold for real-world experiences.
+First, researchers conducting free recall studies may assume that the content at each presentation index is essentially equal, and does not bear qualities that would affect participants' abilities to remember it above that of others.
+Such is rarely the case with real-world experiences or experiments meant to approximate them, and the effects of both intrinsic and observer-dependent factors on memorability are well-established \citep[for review see][]{ChunTurk07, ByliEtal15, TyngEtal17}.
+Second, the random ordering of list items ensures that (across participants, on average) there is no relationship between the thematic similarity of stimuli and their presentation positions---in other words, two semantically related words are no more likely to be presented next to each other than at opposite ends of the list.
+In most cases, the exact opposite is true of real-world episodes.
+Our internal thoughts, our actions, and the physical state of the world around us all tend to follow a direct, causal progression.
+And as a result, each moment of our experience tends to be inherently more similar to surrounding moments than to those in the distant past or future.
+Memory literature has termed this strong temporal autocorrelation ``context," and in various media that depict real-world events (e.g., movies and written stories), we recognize it as a \textit{narrative structure}.
+While random word lists (by definition) have no such structure, the logical progression between ideas and actions in a naturalistic scenario prompts the rememberer to recount presented events in order, from the beginning.
+This pattern is reflected in our findings' second departure from typical free recall dynamics: a lack of increased probability of first recall for end-of-sequence events (Fig.~\ref{fig:list-learning}A).
+
+% One may reasonably hypothesize that the diminished effect of presentation order on recall likelihood stems from 1) differences between the presence of certain features of episodic experiences that are absent in the simple, discretized stimuli of classic list-learning experiments.
+Random word lists most often employ simple, common words While they are well-suited to the random word-list paradigm, these analyses address only the temporal order of stimuli, neglecting to consider their content (or, for example, that content's potential interrelatedness).
+This difference serves to highlight the need for alternative approaches to quantifying memory success that account for such contextual features and the way they may impact memory organization and retrieval dynamics.
 
@@
 Further and importantly, it allows for consideration of the actual content of the experience/memories, which is not typically modeled.
-Leveraging this, using 2 novel memory metrics we find that the successful memory performance is related to 1) the \textit{precision} with which the participant recounts each event and 2) how \textit{distinctive} each recall event is (relative to the other recalled events).
-The first finding suggests to us that the accuracy of recall for \textit{any individual event} may predict the overall amount of information recovered by the participant.
-The second finding suggests that remembering/describing events in a unique way (relative to other recalled events) is also related to the quantity of content recovered.
+Leveraging this, using two novel memory metrics we find that the successful memory performance is related to 1) the \textit{precision} with which the participant recounts each event and 2) the \textit{distinctiveness} of each recall event (relative to the other recalled events).
+The first finding suggests that the information retained for \textit{any individual event} may predict the overall amount of information retained by the participant.
+The second finding suggests that the ability to distinguish between temporally or semantically similar content is also related to the quantity of content recovered.
 Intriguingly, prior studies show that pattern separation, or the ability to discriminate between similar experiences, is impaired in many cognitive disorders as well as natural aging \citep{StarEtal10, YassEtal11c, YassStar11b}.
@@
 % NOTE: do you know of a good reference for WAS and word2vec ?
-While a large number of language models exist (e.g.
-WAS, LSA, word2vec, universal sentence encoder) \citep{LandEtal98, CerEtal18}, here we use topic models for a few reasons.
+% SteyEtal04 = WAS; MikoEtal13 = word2vec
+% -Paxton
+While a large number of language models exist \citep[e.g., WAS, LSA, word2vec, universal sentence encoder;][]{SteyEtal04, LandEtal98, MikoEtal13, CerEtal18}, here we use latent dirichlet allocation (LDA)-based topic models for a few reasons.
 First, topic models capture the \textit{essence} of a text passage devoid of the specific set and order of words used.
 This was an important feature of our model since different people may accurately recall a scene using very different language.
-Secondly, words can mean different things in different contexts (e.g.
-baseball bat vs.
-the animal bat), and topic models are robust to this since words can be part of multiple topics.
-Lastly, topic models provide a straight forward to recover the weights for the particular words comprising a topic, allowing for easy interpretation of an event's contents (e.g.
+Second, words can mean different things in different contexts (e.g.
+``bat" as the act of hitting a baseball, the object used for that action, or a flying mammal).
+Topic models are robust to this, allowing words to exist as part of multiple topics.
+Last, topic models provide a straightforward means to recover the weights for the particular words comprising a topic, enabling easy interpretation of an event's contents (e.g.
 Fig.~\ref{fig:topics}).
-Other models such as Google's universal sentence encoder offer a context-sensitive encoding of text passages, but the encoding space is complex and non-linear and thus, recovering the original words used to fit the model is not straight forward.
+Other models such as Google's universal sentence encoder offer a context-sensitive encoding of text passages, but the encoding space is complex and non-linear, and thus recovering the original words used to fit the model is not straightforward.
 However, it's worth pointing out that our framework is divorced from the particular choice of language model.
@@
 
-Our work has broad implications for how we characterize and assess memory in real-world settings such as the classroom or physician's office.
-For example, the most commonly used classroom evaluation tools involve computing the proportion of correctly answered exam questions.
+Our work has broad implications for how we characterize and assess memory in real-world settings, such as the classroom or physician's office.
+For example, the most commonly used classroom evaluation tools involve simply computing the proportion of correctly answered exam questions.
 Our work indicates that this approach is only loosely related to what educators might really want to measure: how well did the students understand the key ideas presented in the course?
-One could apply the computational framework we developed to construct topic trajectories for the video and participants' recalls to build explicit content models of the course material and exam questions.
+Under this typical framework of assessment, the same exam score of 50\% could be ascribed to two very different students: one who attended the full course but struggled to learn more than a broad overview of the material, and one who attended only half of the course but understood the material perfectly.
+Instead, one could apply our computational framework to build explicit content models of the course material and exam questions.
 This approach would provide a more nuanced and specific view into which aspects of the material students had learned well (or poorly).

### 2019-07-23 paper/main.tex
finished first pass at list learning discussion

@@
 
-In extending classical free recall analyses to our naturalistic memory framework, we recovered two patterns of recall dynamics similar to those central to list-learning studies: a high probability of initiating recall with the first video event (Fig.~\ref{fig:list-learning}A) and a strong bias toward transitioning from recalling a given event to recalling the event immediately following it (Fig.~\ref{fig:list-learning}B).
+In extending classical free recall analyses to our naturalistic memory framework, we recovered two patterns of recall dynamics central to list-learning studies: a high probability of initiating recall with the first video event (Fig.~\ref{fig:list-learning}A) and a strong bias toward transitioning from recalling a given event to recalling the event immediately following it (Fig.~\ref{fig:list-learning}B).
 However, equally noteworthy are the typical free recall results not recovered in these analyses, as each highlights a fundamental difference between list-learning studies and naturalistic memory paradigms like that employed in the present study.
@@
 Free recall experiments' stimuli most often comprise lists of simple, common words, presented to participants in a random order.
-\citep[In fact, numerous word pools have been developed for precisely this purpose; e.g.,][]{FrieEtal82}.
+\citep[In fact, numerous word pools have been developed based on these criteria; e.g.,][]{FrieEtal82}.
 These stimulus qualities enable two assumptions that are central to word list analyses, but frequently do not hold for real-world experiences.
 First, researchers conducting free recall studies may assume that the content at each presentation index is essentially equal, and does not bear qualities that would affect participants' abilities to remember it above that of others.
-Such is rarely the case with real-world experiences or experiments meant to approximate them, and the effects of both intrinsic and observer-dependent factors on memorability are well-established \citep[for review see][]{ChunTurk07, ByliEtal15, TyngEtal17}.
+Such is rarely the case with real-world experiences or experiments meant to approximate them, and the effects of both intrinsic and observer-dependent factors on stimulus memorability are well-established \citep[for review see][]{ChunTurk07, ByliEtal15, TyngEtal17}.
 Second, the random ordering of list items ensures that (across participants, on average) there is no relationship between the thematic similarity of stimuli and their presentation positions---in other words, two semantically related words are no more likely to be presented next to each other than at opposite ends of the list.
@@
 Our internal thoughts, our actions, and the physical state of the world around us all tend to follow a direct, causal progression.
-And as a result, each moment of our experience tends to be inherently more similar to surrounding moments than to those in the distant past or future.
+As a result, each moment of our experience tends to be inherently more similar to surrounding moments than to those in the distant past or future.
 Memory literature has termed this strong temporal autocorrelation ``context," and in various media that depict real-world events (e.g., movies and written stories), we recognize it as a \textit{narrative structure}.
-While random word lists (by definition) have no such structure, the logical progression between ideas and actions in a naturalistic scenario prompts the rememberer to recount presented events in order, from the beginning.
-This pattern is reflected in our findings' second departure from typical free recall dynamics: a lack of increased probability of first recall for end-of-sequence events (Fig.~\ref{fig:list-learning}A).
+While a random word list (by definition) has no such structure, the logical progression between ideas and actions in a naturalistic stimulus prompts the rememberer to recount presented events in order, from the beginning.
+This tendency is reflected in our findings' second departure from typical free recall dynamics: a lack of increased probability of first recall for end-of-sequence events (Fig.~\ref{fig:list-learning}A).
 
@@
 
-When modeling memory experiments, often times events (or items) and their later memories are treated as binary (or categorical in the case of confidence ratings) and independent events.
-Our novel framework allows one to assess memory performance in a more continuous way (e.g.
-precision), as well as analyze the correlational structure of each encoding event to each memory event (e.g.
-distinctiveness).
-Further and importantly, it allows for consideration of the actual content of the experience/memories, which is not typically modeled.
-Leveraging this, using two novel memory metrics we find that the successful memory performance is related to 1) the \textit{precision} with which the participant recounts each event and 2) the \textit{distinctiveness} of each recall event (relative to the other recalled events).
+Thus, analyses such as those in Figure \ref{fig:list-learning} that address only the temporal dynamics of free recall paint an incomplete picture of memory for naturalistic episodes.
+While useful for studying presentation order-dependent recall dynamics, they neglect to consider the stimuli's content (or, for example, that content's potential interrelatedness).
+However, sensitivity to stimulus and recall content introduces a new challenge: distinguishing between levels of recall quality for a stimulus (i.e., an event) that is considered to have been ``remembered."  When modeling memory experiments, often times events (or items) and their later memories are treated as binary and independent events (e.g., a given list item was simply either remembered or not remembered).
+Various models of memory (e.g., \citealp{Yone02}) attempt to improve upon this by including confidence ratings, rendering the binary judgement instead categorical.
+Our novel framework allows one to assess memory performance in a more continuous way (\textit{precision}), as well as analyze the correlational structure of each encoding event to each memory event (\textit{distinctiveness}).
+Further and importantly, these two novel metrics we introduce here arise from comparisons of the actual content of the experience/memories, which is not typically modeled.
+Leveraging this, we find that the successful memory performance is related to 1) the precision with which the participant recounts each event and 2) the distinctiveness of each recall event (relative to the other recalled events).
 The first finding suggests that the information retained for \textit{any individual event} may predict the overall amount of information retained by the participant.
@@
 Intriguingly, prior studies show that pattern separation, or the ability to discriminate between similar experiences, is impaired in many cognitive disorders as well as natural aging \citep{StarEtal10, YassEtal11c, YassStar11b}.
-Future work might explore how/whether the novel metrics introduce here compare between cognitively impoverished groups and healthy controls.
+Future work might explore whether and how these metrics compare between cognitively impoverished groups and healthy controls.
 
@@
 They were told that completeness and detail were more important than temporal order, and that if at any point they realized they had missed something, to return to it.
-Participants were then allowed to speak for as long as they wished, and verbally indicated when they were finished (e.g., `I’m done').''  For additional details about the experimental procedure and scanning parameters see \cite{ChenEtal17}.
+Participants were then allowed to speak for as long as they wished, and verbally indicated when they were finished (e.g., `I’m done').''  For additional details about the experimental procedure and scanning parameters, see \cite{ChenEtal17}.
 The experimental protocol was approved by Princeton University's Institutional Review Board.
@@
 The input to the topic model we trained to characterize the dynamic content of the video comprised hand-generated annotations of each of 1000 scenes spanning the video clip~\citep[generated by][]{ChenEtal17}.
-The features included: narrative details (a sentence or two describing what happened in that scene); whether the scene took place indoors or outdoors; names of any characters that appeared in the scene; name(s) of characters in camera focus; name(s) of characters who were speaking in the scene; the location (in the story) that the scene took place; camera angle (close up, medium, long, top, tracking, over the shoulder, etc.); whether music was playing in the scene or not; and a transcription of any on-screen text.
+The features annotated included: narrative details (a sentence or two describing what happened in that scene); whether the scene took place indoors or outdoors; names of any characters that appeared in the scene; name(s) of characters in camera focus; name(s) of characters who were speaking in the scene; the location (in the story) that the scene took place; camera angle (close up, medium, long, top, tracking, over the shoulder, etc.); whether music was playing in the scene or not; and a transcription of any on-screen text.
 We concatenated the text for all of these features within each segment, creating a ``bag of words'' describing each scene.
@@
 We trained our model using these overlapping text samples with \texttt{scikit-learn}~\citep[version 0.19.1; ][]{PedrEtal11}, called from our high-dimensional visualization and text analysis software, \texttt{HyperTools}~\citep{HeusEtal18a}.
-Specifically, we use the \texttt{CountVectorizer} class to transform the text from each scene into a vector of word counts (using the union of all words across all scenes as the ``vocabulary,'' excluding English stop words); this yields a number-of-scenes by number-of-words \textit{word count} matrix.
-We then use the \texttt{LatentDirichletAllocation} class (topics=100, method=`batch') to fit a topic model~\citep{BleiEtal03} to the word count matrix, yielding a number-of-scenes (1000) by number-of-topics (100) \textit{topic proportions} matrix.
+Specifically, we used the \texttt{CountVectorizer} class to transform the text from each scene into a vector of word counts (using the union of all words across all scenes as the ``vocabulary,'' excluding English stop words); this yielded a number-of-scenes by number-of-words \textit{word count} matrix.
+We then used the \texttt{LatentDirichletAllocation} class (topics=100, method=`batch') to fit a topic model~\citep{BleiEtal03} to the word count matrix, yielding a number-of-scenes (1000) by number-of-topics (100) \textit{topic proportions} matrix.
 The topic proportions matrix describes which mix of topics (latent themes) is present in each scene.
@@
 We also evaluated a parameter-free procedure for choosing $K$, which finds the $K$ value that maximizes the Wasserstein distance (a.k.a.
-"Earth mover's" distance) between the within and across event distributions of correlation values.
+``Earth mover's" distance) between the within and across event distributions of correlation values.
 This alternative procedure largely replicated the pattern of results found with the parameterized method described above, but recovered substantially fewer events on average (Fig.\wasserstein).
-While both approaches seem to underestimate the number of video/recall events relative to the "true" number (as determined by human raters), the parameterized approach was closer to the true number.
+While both approaches seem to underestimate the number of video/recall events relative to the ``true" number (as determined by human raters), the parameterized approach was closer to the true number.
 
@@
 The video and recall events can be treated analogously to studied and recalled ``items'' in a list-learning study.
-We can then extend classic analyses of memory performance and dynamics (originally designed for list-learning experiments) to the more naturalistic video recall task used in our study.
+We can then extend classic analyses of memory performance and dynamics (originally designed for list-learning experiments) to the more naturalistic video recall task used in this study.
 
-Perhaps the simplest and most widely used measure of memory performance is \textit{accuracy}-- i.e., the proportion of studied (experienced) items (in this case, the 34 video events) that the participant later remembered.
+Perhaps the simplest and most widely used measure of memory performance is \textit{accuracy}---i.e., the proportion of studied (experienced) items (in this case, the 34 video events) that the participant later remembered.
 \cite{ChenEtal17} developed a human rating system whereby the quality of each participant's memory was evaluated by an independent rater.
@@
 
-\paragraph{Serial position curve (SPC).} SPCs~\citep{Murd62a} reflect the proportion of participants that remember each item as a function of their serial position during encoding.
+\paragraph{Serial position curve (SPC).} SPCs~\citep{Murd62a} reflect the proportion of participants that remember each item as a function of the items' serial position during encoding.
 We initialized a number-of-participants (17) by number-of-video-events (34) matrix of zeros.

### 2019-07-23 paper/main.tex
finished first pass through revision

@@
 
+We can also apply two analyses native to list-learning studies that describe how participants group items in their recall sequences: temporal clustering and semantic clustering \citep[][see \textit{Methods} for details]{PolyEtal09}.
+Temporal clustering refers to the extent to which participants group their recall responses according to encoding position.
+Overall, we found that sequentially viewed video events were clustered heavily in participants' recall event sequences (mean: 0.808, SEM: 0.022) and that participants with higher temporal clustering scores also tended to recall more events (Pearson's $r(15) = 0.62, p = 0.007$).
+Semantic clustering measures the extent to which participants cluster their recall responses according to semantic similarity.
+We found that participants tended to recall semantically similar video events together (mean: 0.813, SEM: 0.022) and participants who exhibited stronger semantic clustering scores overall remembered more video events (Pearson's $r(15) = 0.55, p = 0.02$).
+
 % NOTE: Pruning out to tone down the list-learning slander
@@
 
-% One may reasonably hypothesize that the diminished effect of presentation order on recall likelihood stems from 1) differences between the presence of certain features of episodic experiences that are absent in the simple, discretized stimuli of classic list-learning experiments.
-Random word lists most often employ simple, common words While they are well-suited to the random word-list paradigm, these analyses address only the temporal order of stimuli, neglecting to consider their content (or, for example, that content's potential interrelatedness).
-This difference serves to highlight the need for alternative approaches to quantifying memory success that account for such contextual features and the way they may impact memory organization and retrieval dynamics.
+% NOTE: for the "nearby moments of real life/naturalistic stimuli tend to be semantically similar" argument, is it worth adding something to the effect of:
+% 1. we observed high temporal clustering scores
+% 2. we also observed high semantic clustering scores
+% 3. ergo, for both to be true, temporally proximal video events must be semantically similar
+% - Paxton
 
@@
 
-\paragraph{Temporal clustering scores.} Temporal clustering refers to the extent to which participants group their recall responses according to encoding position~\citep{PolyEtal09}.
+\paragraph{Temporal clustering scores.} Temporal clustering describes participants' tendency to organize their recall sequences by the learned items' encoding positions.
 For instance, if a participant recalled the video events in the exact order they occurred (or in exact reverse order), this would yield a score of 1.
@@
 We then computed the percentile rank of the next event the participant recalled.
-We averaged these percentile ranks across all of the participant's recalls to obtain a single temporal clustering score for the participant (mean: 0.808, SEM: 0.022).
-Overall, we found that participants with higher temporal clustering scores also tended to recall more events (Pearson's $r(15) = 0.62, p = 0.007$).
+We averaged these percentile ranks across all of the participant's recalls to obtain a single temporal clustering score for the participant.
 
-\paragraph{Semantic clustering scores.} Semantic clustering measures the extent to which participants clustered their recall responses according to semantic similarity~\citep{PolyEtal09}.
+\paragraph{Semantic clustering scores.} Semantic clustering describes participants' tendency to recall semantically similar presented items together in their recall sequences.
 Here, we used the topic vectors for each event as a proxy for its semantic content.
@@
 We then computed the percentile rank of the observed next recall.
-We averaged these percentile ranks across all of the participant's recalls to obtain a single semantic clustering score for the participant (mean: 0.813, SEM: 0.022).
-We found that participants who exhibited stronger semantic clustering scores overall remembered more video events (Pearson's $r(15) = 0.55, p = 0.02$).
+We averaged these percentile ranks across all of the participant's recalls to obtain a single semantic clustering score for the participant.
+
+% I moved the actual results from the two paragraphs to the results section as an afterthought to the list-learning analyses.
+We could also possibly just take them out, though we should keep them if you think it's worth referencing as support for our argument (see my note in discussion section)
+% -Paxton
 
 % NOTE: Thinking about removing this analysis? More of a sanity check than something novel and cool, and takes up space. Happy to be convinced otherwise
+% leaving this one to Jeremy's judgement
+% -Paxton
 
@@
 First, we tested whether each participant's recall trajectory matched the video trajectory in a general sense.
-For each participant we filtered the video trajectory to only include the events that the participant remembered.
+For each participant, we filtered the video trajectory to only include the events that the participant remembered.
 We then computed the root mean squared difference (RMSD) between the remaining video events and the (closest-matching) recalled events.
@@
 For each participant, we computed the correlation between the topic vectors for each recall event and that of its closest-matching video event (only for the events which they recalled).
-We Fisher's z-transformed the correlations, computed the average and then inverse Fisher's z-transformed the resulting value.
+We Fisher's $z$-transformed the correlations, computed the average and then inverse Fisher's z-transformed the resulting value.
 This gave a single value per participant representing the average precision across all recalled events.
@@
 We then averaged these distinctiveness scores across all of the events recalled by the given participant.
-As above, we used Fisher's z (transform and inverse-transform) before/after averaging correlation values.
+As above, we used Fisher's $z$-transform (and inverse-transform) before/after averaging correlation values.
 Finally, we correlated these values with hand-annotated and model derived memory performance scores across-subjects.
@@
 
-Next, we constructed two sets of ``template'' matrices: one reflected the video's topic trajectory and the other reflected each participant's recall topic trajectory.
+Next, we constructed two sets of ``template'' matrices: one reflecting the video's topic trajectory and the other reflecting each participant's recall topic trajectory.
 To construct the video template, we computed the correlations between the topic proportions estimated for every pair of TRs (prior to segmenting the trajectory into discrete events; i.e., the correlation matrix shown in Figs.~\ref{fig:model}B and \ref{fig:brainz}A).

### 2019-07-24 paper/main.tex
finished revision

@@
 %\title{A content-based model of how experiences and memories unfold over time reveals event-like structure in naturalistic episodic recall}
-\title{A novel framework for linking dynamic experiences to memories reveals event-like structure in naturalistic episodic recall}
 %\title{Recalling naturalistic experiences exhibits event-like structure}
+%\title{A novel framework for linking dynamic experiences to memories reveals event-like structure in naturalistic episodic recall}
+\title{A content-sensitive framework for modeling episodic memory reveals event-like structure in naturalistic experience, recall, and neural processing}
 
@@
 \begin{abstract}
-Our life experiences unfold over time in highly complex manner, with the evolving presence and absence of numerous intricate features describing our journey between each circumstance or event we encounter.
-Here, we propose a framework for mapping dynamic naturalistic experiences onto geometric spaces as \textit{trajectories} that capture the temporal dynamics of real-world content.
+Our life experiences unfold over time in highly complex manner, with the evolving presence of numerous intricate features describing our journey between each event we encounter.
+Here, we propose a framework for mapping dynamic naturalistic episodes onto geometric spaces as \textit{experience trajectories} that capture the temporal dynamics of real-world content.
 Within this geometric framework, one may compare the shape of the trajectory formed by an experience to that defined by one's later recollection to characterize our memories' recovery and distortion of the external world.
 Here, we apply this approach to a naturalistic memory experiment in which participants viewed and verbally recounted a video, and find that the video and subsequent recalls share both an experience-specific shape and a discernible event-like structure.
-However, the level of \textit{precision} with which individuals recounted various events and the \textit{distinctiveness} of recall for those events were varied and predictive of overall memory performance.
+Despite this apparent similarity, we find that the level of \textit{precision} with which individuals recounted various events and the \textit{distinctiveness} of recall for those events were varied and predictive of overall memory performance.
 Finally, we identify a network of brain structures that is sensitive to the ``shapes" of our ongoing experiences, and an overlapping network sensitive to how we will later remember them.
-These results highlight the rich event-like structure of the external world and our memories, and offer novel, content-sensitive alternatives to classical ``proportion recalled" measures for assessing episodic memory
+Our framework and findings underscore the rich event-like structure of the external world and our memories, and offer novel, content-sensitive measures for assessing episodic memory
 %Our life experiences unfold over time and the temporal dynamics of their contents form unique \textit{experience trajectories}.
@@
 What does it mean to \textit{remember} something?
-In traditional episodic memory experiments \citep[e.g., list-learning or trial-based experiments;][]{Murd62a, Kaha96}, remembering is often cast as a discrete and binary operation: each studied item may be separated from the rest of one's experiences, and that item may be labeled as having been recalled versus forgotten.
+In traditional episodic memory experiments \citep[e.g., list-learning or trial-based experiments;][]{Murd62a, Kaha96}, remembering is often cast as a discrete and binary operation: each studied item may be separated from all others, and labeled as having been recalled or forgotten.
 More nuanced studies might incorporate self-reported confidence measures as a proxy for memory strength, or ask participants to discriminate between ``recollecting'' the (contextual) details of an experience or having a general feeling of ``familiarity'' \citep{Yone02}.
@@
 
-How might one go about formally characterizing the essence of an experience, or whether it has been recovered by the rememberer?
-Any given moment of an experience derives meaning from surrounding moments, as well as from longer-range temporal associations~\citep[e.g., ][]{LernEtal11, Mann19}.
+How might one go about formally characterizing the ``essence" of an experience, or whether it has been recovered by the rememberer?
+Any given moment of an experience derives meaning from surrounding moments, as well as from longer-range temporal associations~\citep{LernEtal11, Mann19}.
 Therefore, the timecourse describing how an event unfolds is fundamental to its overall meaning.
@@
 We developed a computational framework for characterizing the temporal dynamics of the moment-by-moment content of the episode and of participants' verbal recalls.
-Specifically, we use topic modeling~\citep{BleiEtal03} to characterize the thematic conceptual (semantic) content present in each moment of the episode and recalls, and Hidden Markov Models~\citep{Rabi89, BaldEtal17} to discretize the evolving semantic content into events.
+Specifically, we use topic modeling~\citep{BleiEtal03} to characterize the thematic conceptual (semantic) content present in each moment of the episode and recalls, and Hidden Markov Models~\citep{Rabi89, BaldEtal17} to discretize this evolving semantic content into events.
 In this way, we cast naturalistic experiences (and recalls of those experiences) as \textit{trajectories} that describe how the experiences evolve over time.
@@
 We further examine whether 1) the \textit{precision} with which a participant recounts each event and 2) the \textit{distinctiveness} each recall event is (relative to the other recalled events) relates to their overall memory performance.
-Last, we identify networks of  brain structures whose responses (as participants watched the episode) reflected the shape of the episode, and how participants would later recount the episode.
+Last, we identify networks of  brain structures whose responses (as participants watched the episode) reflected the temporal dynamics of the episode, and how participants would later recount the episode.
 
@@
 To characterize the shape of the \textit{Sherlock} episode and participants' subsequent recountings of its unfolding, we used a topic model~\citep{BleiEtal03} to discover the latent themes in the episode's dynamic content.
-Topic models take as inputs a vocabulary of words to consider and a collection of text documents; they return as output two matrices.
-The first output is a \textit{topics matrix} whose rows are topics (latent themes) and whose columns correspond to words in the vocabulary.
+Topic models take as inputs a vocabulary of words to consider and a collection of text documents, and return two output matrices.
+The first of these is a \textit{topics matrix} whose rows are topics (latent themes) and whose columns correspond to words in the vocabulary.
 The entries of the topics matrix define how each word in the vocabulary is weighted by each discovered topic.
 For example, a detective-themed topic might weight heavily on words like ``crime,'' and ``search.''  The second output is a \textit{topic proportions matrix}, with one row per document and one column per topic.
-The topic proportions matrix describes which mixture of topics is reflected in each document.
+The topic proportions matrix describes what mixture of discovered topics is reflected in each document.
 
 \cite{ChenEtal17} collected hand-annotated information about each of 1000 (manually identified) scenes spanning the roughly 50 minute video used in their experiment.
-This information included: a brief narrative description of what was happening; whether the scene took place indoors vs.
-outdoors; names of any characters on the screen; names of any characters who were in focus in the camera shot; names of characters who were speaking; the location where the scene took place; the camera angle (close up, medium, long, etc.); whether or not background music was present; and other similar details (for a full list of annotated features see \textit{Methods}).
+This information included: a brief narrative description of what was happening; whether the scene took place indoors or outdoors; the names of any characters on the screen; the names of any characters who were in focus in the camera shot; the names of characters who were speaking; the location where the scene took place; the camera angle (close up, medium, long, etc.); whether or not background music was present; and other similar details (for a full list of annotated features see \textit{Methods}).
 We took from these annotations the union of all unique words (excluding stop words, such as ``and,'' ``or,'' ``but,'' etc.) across all features and scenes as the ``vocabulary'' for the topic model.
@@
 We found that 27 unique topics (with non-zero weights) were sufficient to describe the time-varying content of the video (see \textit{Methods}; Figs.~\ref{fig:schematic}, \topics).
-Note that our approach is similar in some respects to Dynamic Topic Models~\citep{BleiLaff06}, in that we sought to characterize how the thematic content of the episode evolved over time.
+Note that our approach is similar in some respects to Dynamic Topic Models~\citep{BleiLaff06} in that we sought to characterize how the thematic content of the episode evolved over time.
 However, whereas Dynamic Topic Models are designed to characterize how the properties of \textit{collections} of documents change over time, our sliding window approach allows us to examine the topic dynamics within a single document (or video).
@@
 
-The topics we found were heavily character-focused (e.g., the top-weighted word in each topic was nearly always a character) and could be roughly divided into themes that were primarily Sherlock Holmes-focused (Sherlock is the titular character); primarily John Watson-focused (John is Sherlock's close confidant and assistant); or that involved Sherlock and John interacting (Fig.~\topics).
+The topics we found were heavily character-focused (e.g., the top-weighted word in each topic was nearly always a character) and could be roughly divided into themes that were primarily Sherlock Holmes-focused (Sherlock is the titular character), primarily John Watson-focused (John is Sherlock's close confidant and assistant), or focused on Sherlock and John interacting (Fig.~\topics).
 Several of the topics were highly similar, which we hypothesized might allow us to distinguish between subtle narrative differences (if the distinctions between those overlapping topics were meaningful; also see Fig.~\featureimportance).
@@
 We applied the same topic model (already trained on the video annotations) to each participant's recalls.
-Analogous to how we analyzed the time-varying content of the video, to obtain similar estimates for participants' recalls, we treated each (overlapping) 10 sentence ``window'' of their transcript as a ``document'' and then computed the most probable mix of topics reflected in each timepoint's sentences.
+Analogous to how we analyzed the time-varying content of the video, to obtain similar estimates for participants' recalls, we treated each (overlapping) 10-sentence ``window'' of their transcript as a ``document'' and then computed the most probable mix of topics reflected in each timepoint's sentences.
 This yielded, for each participant, a number-of-sentences by number-of-topics topic proportions matrix that characterized how the topics identified in the original video were reflected in the participant's recalls.
@@
 This suggests that different participants may be recalling the video with different levels of detail-- e.g., some might touch on just the major plot points, whereas others might attempt to recall every minor scene or action.
-The second clear pattern present in every individual participant's recall correlation matrix is that, unlike in the video correlation matrix, there are substantial off-diagonal correlations in participant's recalls.
-Whereas each event in the original video was (largely) separable from the others (Fig.~\ref{fig:model}B), in transforming those separable events into memory participants appear to be integrating \textit{across} different events, blending elements of previously recalled and not-yet-recalled events into each newly recalled event~\citep[Figs.~\ref{fig:model}D, \corrmats; also see][]{MannEtal11, HowaEtal12}.
+The second clear pattern present in every individual participant's recall correlation matrix is that, unlike in the video correlation matrix, there are substantial off-diagonal correlations.
+Whereas each event in the original video was (largely) separable from the others (Fig.~\ref{fig:model}B), in transforming those separable events into memory, participants appear to be integrating across mutliple events, blending elements of previously recalled and not-yet-recalled events into each newly recalled event~\citep[Figs.~\ref{fig:model}D, \corrmats; also see][]{MannEtal11, HowaEtal12}.
 
@@
 One approach to linking the experienced (video) and recalled events is to label each recalled event as matching the video event with the most similar (i.e., most highly correlated) topic vector (Figs.~\ref{fig:model}G, \matchmats).
-This yields a sequence of ``presented'' events from the original video, and a sequence of (potentially differently ordered) ``recalled'' events for each participant.
+This yields a sequence of ``presented'' events from the original video, and a (potentially differently ordered) sequence of ``recalled'' events for each participant.
 Analogous to classic list-learning studies, we can then examine participants' recall sequences by asking which events they tended to recall first~\citep[probability of first recall; Fig.~\ref{fig:list-learning}A;][]{WelcBurn24, PostPhil65, AtkiShif68}; how participants most often transition between recalls of the events as a function of the temporal distance between them~\citep[lag-conditional response probability; Fig.~\ref{fig:list-learning}B;][]{Kaha96}; and which events they were likely to remember overall~\citep[serial position recall analyses; Fig.~\ref{fig:list-learning}C;][]{Murd62a}.
@@
 
-We can also apply two analyses native to list-learning studies that describe how participants group items in their recall sequences: temporal clustering and semantic clustering \citep[][see \textit{Methods} for details]{PolyEtal09}.
+We can also apply two list-learning-native analyses that describe how participants group items in their recall sequences: temporal clustering and semantic clustering \citep[][see \textit{Methods} for details]{PolyEtal09}.
 Temporal clustering refers to the extent to which participants group their recall responses according to encoding position.
@@
 Semantic clustering measures the extent to which participants cluster their recall responses according to semantic similarity.
-We found that participants tended to recall semantically similar video events together (mean: 0.813, SEM: 0.022) and participants who exhibited stronger semantic clustering scores overall remembered more video events (Pearson's $r(15) = 0.55, p = 0.02$).
+We found that participants tended to recall semantically similar video events together (mean: 0.813, SEM: 0.022) and participants who exhibited stronger semantic clustering remembered more video events overall (Pearson's $r(15) = 0.55, p = 0.02$).
 
@@
 Participants whose recall events are more veridical descriptions of what happened in the video event will presumably have higher precision scores.
-We find that across participants, a higher precision score is correlated to both hand annotated memory performance (Pearson's $r(15) = 0.6, p = 0.011$) and the number of recall events estimated by our model (Pearson's $r(15) = 0.64, p = 0.005$).
+We find that, across participants, a higher precision score is correlated to both hand-annotated memory performance (Pearson's $r(15) = 0.6, p = 0.011$) and the number of recall events estimated by our model (Pearson's $r(15) = 0.64, p = 0.005$).
 A second novel metric we introduce here is distinctiveness, or how unique the recall description was to each video event.
@@
 In extending classical free recall analyses to our naturalistic memory framework, we recovered two patterns of recall dynamics central to list-learning studies: a high probability of initiating recall with the first video event (Fig.~\ref{fig:list-learning}A) and a strong bias toward transitioning from recalling a given event to recalling the event immediately following it (Fig.~\ref{fig:list-learning}B).
-However, equally noteworthy are the typical free recall results not recovered in these analyses, as each highlights a fundamental difference between list-learning studies and naturalistic memory paradigms like that employed in the present study.
-The most noticeable departure from hallmark free recall dynamics in these findings is the apparent lack of a serial position effect in Figure \ref{fig:list-learning}C, which instead shows greater and lesser recall probabilities for events distributed across the video.
-Free recall experiments' stimuli most often comprise lists of simple, common words, presented to participants in a random order.
+However, equally noteworthy are the typical free recall results not recovered in these analyses, as each highlights a fundamental difference between list-learning studies and naturalistic memory paradigms like the one employed in the present study.
+The most noticeable departure from hallmark free recall dynamics in these findings is the apparent lack of a serial position effect in Figure \ref{fig:list-learning}C, which instead shows greater and lesser recall probabilities for events distributed across the video stimulus.
+Stimuli in free recall experiments most often comprise lists of simple, common words, presented to participants in a random order.
 \citep[In fact, numerous word pools have been developed based on these criteria; e.g.,][]{FrieEtal82}.
 These stimulus qualities enable two assumptions that are central to word list analyses, but frequently do not hold for real-world experiences.
-First, researchers conducting free recall studies may assume that the content at each presentation index is essentially equal, and does not bear qualities that would affect participants' abilities to remember it above that of others.
-Such is rarely the case with real-world experiences or experiments meant to approximate them, and the effects of both intrinsic and observer-dependent factors on stimulus memorability are well-established \citep[for review see][]{ChunTurk07, ByliEtal15, TyngEtal17}.
-Second, the random ordering of list items ensures that (across participants, on average) there is no relationship between the thematic similarity of stimuli and their presentation positions---in other words, two semantically related words are no more likely to be presented next to each other than at opposite ends of the list.
+First, researchers conducting free recall studies may assume that the content at each presentation index is essentially equal, and does not bear qualities that would cause participants to remember it more or less successfully than others.
+Such is rarely the case with real-world experiences or experiments meant to approximate them, and the effects of both intrinsic and observer-dependent factors on stimulus memorability are well established \citep[for review see][]{ChunTurk07, ByliEtal15, TyngEtal17}.
+Second, the random ordering of list items ensures that (across participants, on average) there is no relationship between the thematic similarity of individual stimuli and their presentation positions---in other words, two semantically related words are no more likely to be presented next to each other than at opposite ends of the list.
 In most cases, the exact opposite is true of real-world episodes.
@@
 Memory literature has termed this strong temporal autocorrelation ``context," and in various media that depict real-world events (e.g., movies and written stories), we recognize it as a \textit{narrative structure}.
-While a random word list (by definition) has no such structure, the logical progression between ideas and actions in a naturalistic stimulus prompts the rememberer to recount presented events in order, from the beginning.
+While a random word list (by definition) has no such structure, the logical progression between ideas and actions in a naturalistic stimulus prompts the rememberer to recount presented events in order, starting with the beginning.
 This tendency is reflected in our findings' second departure from typical free recall dynamics: a lack of increased probability of first recall for end-of-sequence events (Fig.~\ref{fig:list-learning}A).
@@
 However, sensitivity to stimulus and recall content introduces a new challenge: distinguishing between levels of recall quality for a stimulus (i.e., an event) that is considered to have been ``remembered."  When modeling memory experiments, often times events (or items) and their later memories are treated as binary and independent events (e.g., a given list item was simply either remembered or not remembered).
-Various models of memory (e.g., \citealp{Yone02}) attempt to improve upon this by including confidence ratings, rendering the binary judgement instead categorical.
+Various models of memory (e.g., \citealp{Yone02}) attempt to improve upon this by including confidence ratings, rendering this binary judgement instead categorical.
 Our novel framework allows one to assess memory performance in a more continuous way (\textit{precision}), as well as analyze the correlational structure of each encoding event to each memory event (\textit{distinctiveness}).
@@
 Second, words can mean different things in different contexts (e.g.
-``bat" as the act of hitting a baseball, the object used for that action, or a flying mammal).
+``bat" as the act of hitting a baseball, the object used for that action, or as a flying mammal).
 Topic models are robust to this, allowing words to exist as part of multiple topics.

### 2019-08-25 paper/main.tex
recompiled docs with fixes

@@
 \textbf{B.} Timepoint-by-timepoint correlation matrix of the topic vectors displayed in Panel A.
-Event boundaries detected by the HMM are denoted in yellow (34 events detected).
-\textbf{C.} Average topic vectors for each of the 34 video events.
+Event boundaries detected by the HMM are denoted in yellow (36 events detected).
+\textbf{C.} Average topic vectors for each of the 36 video events.
 \textbf{D.} Topic vectors for each of 294 sentences spoken by an example participant while recalling the video.
 \textbf{E.} Timepoint-by-timepoint correlation matrix of the topic vectors displayed in Panel D.
-Event boundaries detected by the HMM are denoted in yellow (27 events detected).
-\textbf{F.} Average topic vectors for each of the 27 recalled events from the example participant.
+Event boundaries detected by the HMM are denoted in yellow (37 events detected).
+\textbf{F.} Average topic vectors for each of the 37 recalled events from the example participant.
 \textbf{G.} Correlations between the topic vectors for every pair of video events (Panel C) and recalled events (from the example participant; Panel F).

### 2019-08-26 paper/main.tex
first few text edits

@@
 First, although every individual participant's recalls could be segmented into discrete events (i.e., every individual participant's recall correlation matrix exhibited clear block diagonal structure; Fig.~\corrmats), each participant appeared to have a unique \textit{recall resolution}, reflected in the sizes of those blocks.
-For example, some participants' recall topic proportions segmented into just a few events (e.g., Participants P1, P4, and P15), while others' recalls segmented into many shorter duration events (e.g., Participants P12, P13, and P17).
+For example, some participants' recall topic proportions segmented into just a few events (e.g., Participants P2, P6, and P14), while others' recalls segmented into many shorter duration events (e.g., Participants P12, P13, and P17).
 This suggests that different participants may be recalling the video with different levels of detail-- e.g., some might touch on just the major plot points, whereas others might attempt to recall every minor scene or action.
@@
 Temporal clustering refers to the extent to which participants group their recall responses according to encoding position.
-Overall, we found that sequentially viewed video events were clustered heavily in participants' recall event sequences (mean: 0.808, SEM: 0.022) and that participants with higher temporal clustering scores also tended to recall more events (Pearson's $r(15) = 0.62, p = 0.007$).
-Semantic clustering measures the extent to which participants cluster their recall responses according to semantic similarity.
-We found that participants tended to recall semantically similar video events together (mean: 0.813, SEM: 0.022) and participants who exhibited stronger semantic clustering remembered more video events overall (Pearson's $r(15) = 0.55, p = 0.02$).
+Overall, we found that sequentially viewed video events were clustered heavily in participants' recall event sequences (mean: 0.860, SEM: 0.016) and that participants with higher temporal clustering scores also tended to recall more events (Pearson's $r(15) = 0.50, p = 0.042$).
+
+% ------ NOTE: ------
+% Semantic clustering correlation with number of events no longer significant.  Andy referenced possible bug in code in slack message a while ago, need to make sure this is using his fixed version
+% - Paxton
+%Semantic clustering measures the extent to which participants cluster their recall responses according to semantic similarity.
+We found that participants tended to recall semantically similar video events together (mean: 0.888, SEM: 0.014) and participants who exhibited stronger semantic clustering remembered more video events overall (Pearson's $r(15) = 0.55, p = 0.02$).
 
@@
 Participants whose recall events are more veridical descriptions of what happened in the video event will presumably have higher precision scores.
-We find that, across participants, a higher precision score is correlated to both hand-annotated memory performance (Pearson's $r(15) = 0.6, p = 0.011$) and the number of recall events estimated by our model (Pearson's $r(15) = 0.64, p = 0.005$).
+We find that, across participants, a higher precision score is correlated to both hand-annotated memory performance (Pearson's $r(15) = 0.62, p = 0.08$) and the number of recall events estimated by our model (Pearson's $r(15) = 0.64, p = 0.006$).
 A second novel metric we introduce here is distinctiveness, or how unique the recall description was to each video event.
@@
 In summary, using two novel metrics afforded by our approach, we find that participants whose recalls are both more precise and distinct remember more content.
+% ------ NOTE: ------
+% Correlations between precision/distinctiveness and number of events need to be updated once analysis is re-run
+% - Paxton
 
@@
 \end{figure}
+% ------ NOTE: ------
+% Figure and caption need to be updated once analysis is re-run
+% - Paxton
 
@@
 In identifying regions whose responses to ongoing experiences reflect how those experiences will be remembered later, this latter analysis extends classic \textit{subsequent memory analyses}~\citep[e.g.,][]{PallWagn02} to domain of naturalistic stimuli.
+% ------ NOTE: ------
+% Searchlight results and figure need to be updated once analysis is re-run
+% - Paxton
 

### 2019-08-29 paper/main.tex
updated stats in text, moved topics fig

@@
 \textbf{C.} Average topic vectors for each of the 36 video events.
-\textbf{D.} Topic vectors for each of 294 sentences spoken by an example participant while recalling the video.
+\textbf{D.} Topic vectors for each of 294 sentences spoken by an example participant while recalling the video, resampled to match the timseries of the video.
 \textbf{E.} Timepoint-by-timepoint correlation matrix of the topic vectors displayed in Panel D.
@@
 Temporal clustering refers to the extent to which participants group their recall responses according to encoding position.
-Overall, we found that sequentially viewed video events were clustered heavily in participants' recall event sequences (mean: 0.860, SEM: 0.016) and that participants with higher temporal clustering scores also tended to recall more events (Pearson's $r(15) = 0.50, p = 0.042$).
+Semantic clustering measures the extent to which participants cluster their recall responses according to semantic similarity.
+Overall, we found that participants heavily clustered video events in their recalls by both temporal proximity (mean: 0.860, SEM: 0.016) and semantic content (mean: 0.888, SEM: 0.014).
+
+% Overall, we found that sequentially viewed video events were clustered heavily in participants' recall event sequences (mean: 0.860, SEM: 0.016) and that participants with higher temporal clustering scores also tended to recall more events (Pearson's $r(15) = 0.50, p = 0.042$).
+Semantic clustering measures the extent to which participants cluster their recall responses according to semantic similarity.
+We found that participants tended to recall semantically similar video events together (mean: 0.888, SEM: 0.014) and participants who exhibited stronger semantic clustering remembered more video events overall (Pearson's $r(15) = 0.55, p = 0.02$).
 
 % ------ NOTE: ------
-% Semantic clustering correlation with number of events no longer significant.  Andy referenced possible bug in code in slack message a while ago, need to make sure this is using his fixed version
+% Temporal & semantic clustering scores' correlations with number of events & model-estimated memory are no longer significant.  Worth mentioning at all then?
+% temporal x hand-annotated: r=.5, p=0.042
+% temporal x model-estimated: r=.36, p=.16
+% temporal x n events: r=.29, p=.26
+% semantic x hand-annotated: r=.32, p=.21
+% semantic x model-estimated: r=.33, p=.20
+% semantic x n events: r=.48, p=.053
 % - Paxton
-%Semantic clustering measures the extent to which participants cluster their recall responses according to semantic similarity.
-We found that participants tended to recall semantically similar video events together (mean: 0.888, SEM: 0.014) and participants who exhibited stronger semantic clustering remembered more video events overall (Pearson's $r(15) = 0.55, p = 0.02$).
 
@@
 Participants whose recall events are more veridical descriptions of what happened in the video event will presumably have higher precision scores.
-We find that, across participants, a higher precision score is correlated to both hand-annotated memory performance (Pearson's $r(15) = 0.62, p = 0.08$) and the number of recall events estimated by our model (Pearson's $r(15) = 0.64, p = 0.006$).
+We find that, across participants, a higher precision score is correlated to both hand-annotated memory performance (Pearson's $r(15) = 0.55, p = 0.021$) and the number of recall events estimated by our model (Pearson's $r(15) = 0.66, p = 0.004$).
 A second novel metric we introduce here is distinctiveness, or how unique the recall description was to each video event.
@@
 We hypothesized that participants who recounted events in a more distinctive way would display better overall memory.
-Similarly to precision, we find that the more distinct participants recalls are (on average), the more they remembered (hand-annotated memory: Pearson's $r(15) = 0.83, p < 0.001$; model-derived memory: Pearson's $r(15) = 0.71, p = 0.001$).
+Similarly to precision, we find that the more distinct participants recalls are (on average), the more they remembered (hand-annotated memory: Pearson's $r(15) = 0.62, p = 0.007$; number of events: Pearson's $r(15) = 0.78, p < 0.001$).
 In summary, using two novel metrics afforded by our approach, we find that participants whose recalls are both more precise and distinct remember more content.
@@
 
-In addition to constructing overall summaries, assessing the video and recall topic vectors from individual events can provide further insights.
-Specifically, for any given event we can construct two wordles: one from the original video event's topic vector, and a second from the average topic vectors produced by all participants' recalls of that event.
-We can then examine those wordles visually to gain an intuition for which aspects of the video event were recapitulated in participants' recalls.
-Several example wordles are displayed in Figure~\ref{fig:topics}C (wordles from the three best-remembered events are circled in green; wordles from the three worst-remembered events are circled in red).
-Using wordles to visually compare the topical content of each video event and the (average) corresponding recall event reveals the specific content from the specific events that is reliably retained in the transformation into memory (green events) or not (red events).
-
 \begin{figure}[tp]
@@
 \end{figure}
+
+In addition to constructing overall summaries, assessing the video and recall topic vectors from individual events can provide further insights.
+Specifically, for any given event we can construct two wordles: one from the original video event's topic vector, and a second from the average topic vectors produced by all participants' recalls of that event.
+We can then examine those wordles visually to gain an intuition for which aspects of the video event were recapitulated in participants' recalls.
+Several example wordles are displayed in Figure~\ref{fig:topics}C (wordles from the three best-remembered events are circled in green; wordles from the three worst-remembered events are circled in red).
+Using wordles to visually compare the topical content of each video event and the (average) corresponding recall event reveals the specific content from the specific events that is reliably retained in the transformation into memory (green events) or not (red events).
 
@@
 
-\bibliography{memlab}
+%\bibliography{memlab}
+\bibliography{/Users/paxtonfitzpatrick/Documents/Dartmouth/CDL/CDL-bibliography/memlab.bib}
 

### 2019-08-29 paper/main.tex
added resampling step to methods

@@
 To visualize the result, we created a ``wordle'' image~\citep{MuelEtal18} where words weighted more heavily by better-remembered topics appear in a larger font (Fig.~\ref{fig:topics}B, green box).
-Events that reflected topics weighting heavily on characters like ``Sherlock'' and ``John'' (i.e., the main characters) and locations like ``221b Baker Street'' (i.e., a major recurring location and the address of the flat that Sherlock and John share) were best remembered.
+Events that reflected topics weighting heavily on characters like ``Sherlock'' and ``John'' (the main characters) and locations like ``221b Baker Street'' (a major recurring location and the address of the flat that Sherlock and John share) were best remembered.
 An analogous analysis revealed which themes were poorly remembered.
@@
 These reflected the dynamic content of each participant's recalls.
+Finally, we resampled each recall model to match the timecourse of the video model.
 Note: for details on how we selected the video and recall window lengths and number of topics, see \textit{Supporting Information} and Figure~\topicopt.

### 2019-08-29 paper/main.tex
updated fig 6 text

@@
 To visualize the result, we created a ``wordle'' image~\citep{MuelEtal18} where words weighted more heavily by better-remembered topics appear in a larger font (Fig.~\ref{fig:topics}B, green box).
-Events that reflected topics weighting heavily on characters like ``Sherlock'' and ``John'' (the main characters) and locations like ``221b Baker Street'' (a major recurring location and the address of the flat that Sherlock and John share) were best remembered.
+Across the full video, content that reflected topics necessary to convey the central focus of the video (e.g., the names of the two main characters, ``Sherlock" and ``John", and the address of a major recurring location, ``221b Baker Street") were best remembered.
 An analogous analysis revealed which themes were poorly remembered.
 Here in computing the weighted average over events' topic vectors, we weighted each event in \textit{inverse} proportion to how well it was remembered (Fig.~\ref{fig:topics}B, red box).
-This revealed that events with relatively minor characters such as ``Mike,'' ``Jeffrey,'' and ``Molly,'' as well as less-integral plot locations (e.g., ``hospital'' and ``office'') were least well-remembered.
-This suggests that what is retained in memory are the major plot elements (i.e., the overall shape of what happened), whereas the more minor details are prone to pruning.
+The least well-remembered video content reflected information not necessary to conveying the video's ``gist," such as the names of relatively minor characters (e.g., ``Mike," ``Jeffrey," ``Molly," and ``Jimmy") and locations (e.g., ``St.
+Bartholomew's Hospital").
 
@@
 
-In addition to constructing overall summaries, assessing the video and recall topic vectors from individual events can provide further insights.
+A similar result emerged from assessing the topic vectors for individual video and recall events (Fig.~\ref{fig:topics}C).
+Here, for each of the three best- and worst-remembered video events, we have constructed two wordles: one from the original video event's topic vector (left) and a second from the average recall topic vector for that event (right).
+The three best-remembered events (circled in green) correspond to scenes important to the central plot-line (Sherlock and John meeting, Sherlock and John chasing the killer, and the killer calling spying on John in a phone booth).
+Meanwhile, the three worst-remembered events (circled in red) reflect various side-stories (John talking to his therapist about the war, a soon-to-be-victim's affair with his assistant, and another soon-to-be-victim leaving a party with his friend) that are not essentially to summarizing the video's narrative.
+
+%Events that reflected topics weighting heavily on characters like ``Sherlock'' and ``John'' (the main characters) and locations like ``221b Baker Street'' (a major recurring location and the address of the flat that Sherlock and John share) were best remembered.
+An analogous analysis revealed which themes were poorly remembered.
+Here in computing the weighted average over events' topic vectors, we weighted each event in \textit{inverse} proportion to how well it was remembered (Fig.~\ref{fig:topics}B, red box).
+This revealed that events with relatively minor characters such as ``Mike,'' ``Jeffrey,'' and ``Molly,'' as well as less-integral plot locations (e.g., ``hospital'' and ``office'') were least well-remembered.
+This suggests that what is retained in memory are the major plot elements (i.e., the overall shape of what happened), whereas the more minor details are prone to pruning.
+
+% In addition to constructing overall summaries, assessing the video and recall topic vectors from individual events can provide further insights.
 Specifically, for any given event we can construct two wordles: one from the original video event's topic vector, and a second from the average topic vectors produced by all participants' recalls of that event.
@@
 \cite{ChenEtal17} developed a human rating system whereby the quality of each participant's memory was evaluated by an independent rater.
-We found a strong across-participants correlation between these independant ratings and the overall number of events that our HMM approach identified in participants' recalls (Pearson's $r(15) = 0.67, p = 0.003$).
+We found a strong across-participants correlation between these independant ratings and the overall number of events that our HMM approach identified in participants' recalls (Pearson's $r(15) = 0.64, p = 0.006$).
 
@@
 We tested whether participants who recalled more events were also more \textit{precise} in their recollections.
-For each participant, we computed the correlation between the topic vectors for each recall event and that of its closest-matching video event (only for the events which they recalled).
-We Fisher's $z$-transformed the correlations, computed the average and then inverse Fisher's z-transformed the resulting value.
+For each participant, we computed the average correlation between the topic vectors for each recall event and those of its closest-matching video event.
 This gave a single value per participant representing the average precision across all recalled events.
-We then correlated this value with hand-annotated as well as model derived (e.g.
-$k$ or the number of events recovered by the HMM) memory performance.
+We then Fisher's $z$-transformed these values and correlated them with both hand-annotated and model-derived (i.e., $k$ or the number of events recovered by the HMM) memory performance.
 
@@
 We hypothesized that participants with high memory performance might describe each event in a more distinctive way (relative to those with lower memory performance who might describe events in a more general way).
-To test this hypothesis we define a distinctiveness score for each recalled event as
+To test this hypothesis we define a distinctiveness score for each recall event as
 
-%NOTE: Need to check on this equation!
 \[
@@
 We then averaged these distinctiveness scores across all of the events recalled by the given participant.
-As above, we used Fisher's $z$-transform (and inverse-transform) before/after averaging correlation values.
-Finally, we correlated these values with hand-annotated and model derived memory performance scores across-subjects.
+As above, we used Fisher's $z$-transformation before correlating these values with hand-annotated and model derived memory performance scores across-subjects.
 
@@
 In Figure~\ref{fig:trajectory}B, we present an analysis aimed at characterizing locations in topic space that different participants move through in a consistent way (via their recall topic trajectories).
-The two-dimensional topic space used in our visualizations (Fig.~\ref{fig:trajectory}) ranged from -5 to 5 (arbitrary) units in the $x$ dimension and from -6.5 to 2 units in the $y$ dimension.
+The two-dimensional topic space used in our visualizations (Fig.~\ref{fig:trajectory}) comprised a 9x9 (arbitrary units) square.
 We divided this space into a grid of vertices spaced 0.25~units apart.

### 2019-08-29 paper/main.tex
added ref to new supplemental figures

@@
 \newcommand{\wasserstein}{S6}
+\newcommand{\kcorrs}{S7}
+\newcommand{\kopt}{S8}
 
@@
 \textbf{C.} Average topic vectors for each of the 36 video events.
-\textbf{D.} Topic vectors for each of 294 sentences spoken by an example participant while recalling the video, resampled to match the timseries of the video.
+\textbf{D.} Topic vectors for each of 252 sentences spoken by an example participant while recalling the video, resampled to match the timseries of the video.
 \textbf{E.} Timepoint-by-timepoint correlation matrix of the topic vectors displayed in Panel D.
-Event boundaries detected by the HMM are denoted in yellow (37 events detected).
-\textbf{F.} Average topic vectors for each of the 37 recalled events from the example participant.
+Event boundaries detected by the HMM are denoted in yellow (29 events detected).
+\textbf{F.} Average topic vectors for each of the 29 recalled events from the example participant.
 \textbf{G.} Correlations between the topic vectors for every pair of video events (Panel C) and recalled events (from the example participant; Panel F).
@@
 where $a$ was the average correlation between the topic vectors of timepoints within the same state; $b$ was the average correlation between the topic vectors of timepoints within \textit{different} states; and $\alpha$ was a regularization parameter that we set to 5 times the window length (i.e., 250 scenes for the video topic trajectory and 50 sentences for the recall topic trajectories).
-Figure~\ref{fig:model}B displays the event boundaries returned for the video, and Figure~\corrmats~displays the event boundaries returned for each participant's recalls.
+Figure~\ref{fig:model}B displays the event boundaries returned for the video, and Figure~\corrmats~displays the event boundaries returned for each participant's recalls (see Figs.~\kcorrs, \kopt~for the optimization functions for the video and recalls).
 After obtaining these event boundaries, we created stable estimates of each topic proportions matrix by averaging the topic vectors within each event.

### 2019-08-30 paper/main.tex
reordered supplemental figs
updated k-optimization formula

@@
 \newcommand{\matchmats}{S5}
-\newcommand{\wasserstein}{S6}
-\newcommand{\kcorrs}{S7}
-\newcommand{\kopt}{S8}
+\newcommand{\kcorrs}{S6}
+\newcommand{\kopt}{S7}
+\newcommand{\wasserstein}{S8}
 
@@
 \[
-  \argmax_K \left[\frac{a}{b} - \frac{K}{\alpha}\right],
+  \argmax_K \left[POM(\frac{a}{b+J}) - \frac{K}{\alpha}\right],
 \]
-where $a$ was the average correlation between the topic vectors of timepoints within the same state; $b$ was the average correlation between the topic vectors of timepoints within \textit{different} states; and $\alpha$ was a regularization parameter that we set to 5 times the window length (i.e., 250 scenes for the video topic trajectory and 50 sentences for the recall topic trajectories).
-Figure~\ref{fig:model}B displays the event boundaries returned for the video, and Figure~\corrmats~displays the event boundaries returned for each participant's recalls (see Figs.~\kcorrs, \kopt~for the optimization functions for the video and recalls).
+where $a$ was the average correlation between the topic vectors of timepoints within the same state; $b$ was the average correlation between the topic vectors of timepoints within \textit{different} states; \textit{J} was an arbitrary constant used to ensure a positive denominator, set equal to 100; and $\alpha$ was a regularization parameter that we set to 5 times the window length (i.e., 250 scenes for the video topic trajectory and 50 sentences for the recall topic trajectories).
+Before subtracting the regularization term, we scaled the ratio of correlations to be a proportion of the maximum ratio across all $K$'s.
+Figure~\ref{fig:model}B displays the event boundaries returned for the video, and Figure~\corrmats~displays the event boundaries returned for each participant's recalls (See Fig.~\kcorrs~for the values of \textit{a} and \textit{b} for each $K$, Fig.~\kopt~for the optimization functions for the video and recalls).
 After obtaining these event boundaries, we created stable estimates of each topic proportions matrix by averaging the topic vectors within each event.

### 2019-08-30 paper/supporting_information.tex
finished edits on paper
added new fig to supporting information

@@
 \centering
+\includegraphics[width=\textwidth]{figs/k_corrs}
+\caption{\small \textbf{Within- and across-event correlations as a function of $K$.}  As part of the event-segmentation procedure, we searched over a range of possible $K$-values [2,50] (i.e., number of events) for the video and each recall topic trajectory, separately.
+For each $K$, we used an HMM to segment the trajectory into $K$-events.
+We then computed the average correlation between topic vectors at timepoints within the same event, and the average correlation between topic vectors at timepoints across different events.}
+\label{fig:k_corrs}
+\end{figure}
+
+%\begin{figure}[p!]
+%\centering
+%\includegraphics[width=\textwidth]{figs/k_optimization}
+%\caption{\small \textbf{Video and recall trajectory $K$-optimization functions.}  We selected the optimal $K$-value for the video and each recall trajectory, using the formula described in \textit{Methods}.
+This computation resulted in a curve for each trajectory, describing the regularized ratio of the average within-event topic vector correlation to the average across-event topic vector correlation, as a function of $K$.}
+%\label{fig:k_optimization}
+%\end{figure}
+
+\begin{figure}[p!]
+\centering
 \includegraphics[width=\textwidth]{figs/trajectory_wasserstein}
@@
 
+\
+
 \newpage

### 2019-08-30 paper/supporting_information.tex
added k_optimization fig to supporting information

@@
 
-%\begin{figure}[p!]
-%\centering
-%\includegraphics[width=\textwidth]{figs/k_optimization}
-%\caption{\small \textbf{Video and recall trajectory $K$-optimization functions.}  We selected the optimal $K$-value for the video and each recall trajectory, using the formula described in \textit{Methods}.
+\begin{figure}[p!]
+\centering
+\includegraphics[width=\textwidth]{figs/k_optimization}
+\caption{\small \textbf{Video and recall trajectory $K$-optimization functions.}  We selected the optimal $K$-value for the video and each recall trajectory, using the formula described in \textit{Methods}.
 This computation resulted in a curve for each trajectory, describing the regularized ratio of the average within-event topic vector correlation to the average across-event topic vector correlation, as a function of $K$.}
-%\label{fig:k_optimization}
-%\end{figure}
+\label{fig:k_optimization}
+\end{figure}
 

### 2019-08-30 paper/main.tex
udpated k-optimization term

@@
 \[
-  \argmax_K \left[POM(\frac{a}{b+J}) - \frac{K}{\alpha}\right],
+  \argmax_K \left[POM(\frac{a}{b-J}) - \frac{K}{\alpha}\right],
 \]
-where $a$ was the average correlation between the topic vectors of timepoints within the same state; $b$ was the average correlation between the topic vectors of timepoints within \textit{different} states; \textit{J} was an arbitrary constant used to ensure a positive denominator, set equal to 100; and $\alpha$ was a regularization parameter that we set to 5 times the window length (i.e., 250 scenes for the video topic trajectory and 50 sentences for the recall topic trajectories).
+where $a$ was the average correlation between the topic vectors of timepoints within the same state; $b$ was the average correlation between the topic vectors of timepoints within \textit{different} states; \textit{J} was a constant used to ensure a positive denominator, set equal to $\min_K\left[{\frac{a}{b}}\right]$; and $\alpha$ was a regularization parameter that we set to 5 times the window length (i.e., 250 scenes for the video topic trajectory and 50 sentences for the recall topic trajectories).
 Before subtracting the regularization term, we scaled the ratio of correlations to be a proportion of the maximum ratio across all $K$'s.

### 2019-09-13 paper/main.tex
Added placeholder precision distinctiveness example figure
updated abstract

@@
 
-%\title{How is experience transformed into memory?}
-%\title{A content-based framework for capturing stimulus and memory dynamics reveals event-like structure in naturalistic episodic recall}
-%\title{A content-based model characterizing/describing/representing how experiences and memories unfold over time reveals event-like structure in naturalistic episodic recall}
-%\title{A content-based framework describing the temporal dynamics of experiences and memories reveals event-like structure in naturalistic episodic recall}
-%\title{A content-based model of how experiences and memories unfold over time reveals event-like structure in naturalistic episodic recall}
-%\title{Recalling naturalistic experiences exhibits event-like structure}
-%\title{A novel framework for linking dynamic experiences to memories reveals event-like structure in naturalistic episodic recall}
-\title{A content-sensitive framework for modeling episodic memory reveals event-like structure in naturalistic experience, recall, and neural processing}
+\title{Memory for television episodes preserves event content while introducing new across-event similarities}
 
 \author{Andrew C.
-Heusser, Paxton C.
-Fitzpatrick, and Jeremy R.
-Manning\\Department of Psychological and Brain Sciences\\Dartmouth College, Hanover, NH 03755, USA\\Corresponding author: jeremy.r.manning@dartmouth.edu}
+Heusser\textsuperscript{1, 2}, Paxton C.
+Fitzpatrick\textsuperscript{1}, and Jeremy R.
+Manning\textsuperscript{1, *}\\\textsuperscript{1}Department of Psychological and Brain Sciences\\Dartmouth College, Hanover, NH 03755, USA\\\textsuperscript{2}Akili Interactive\\Boston, MA 02110\\\textsuperscript{*}Corresponding author: jeremy.r.manning@dartmouth.edu}
 
@@
 \begin{abstract}
-Our life experiences unfold over time in highly complex manner, with the evolving presence of numerous intricate features describing our journey between each event we encounter.
-Here, we propose a framework for mapping dynamic naturalistic episodes onto geometric spaces as \textit{experience trajectories} that capture the temporal dynamics of real-world content.
-Within this geometric framework, one may compare the shape of the trajectory formed by an experience to that defined by one's later recollection to characterize our memories' recovery and distortion of the external world.
-Here, we apply this approach to a naturalistic memory experiment in which participants viewed and verbally recounted a video, and find that the video and subsequent recalls share both an experience-specific shape and a discernible event-like structure.
-Despite this apparent similarity, we find that the level of \textit{precision} with which individuals recounted various events and the \textit{distinctiveness} of recall for those events were varied and predictive of overall memory performance.
-Finally, we identify a network of brain structures that is sensitive to the ``shapes" of our ongoing experiences, and an overlapping network sensitive to how we will later remember them.
-Our framework and findings underscore the rich event-like structure of the external world and our memories, and offer novel, content-sensitive measures for assessing episodic memory
-%Our life experiences unfold over time and the temporal dynamics of their contents form unique \textit{experience trajectories}.
+The ways our experiences unfold over time define unique \textit{trajectories} through the relevant representational spaces.
 Within this geometric framework, one can compare the shape of the trajectory formed by an experience to that defined by our later remembering of that experience.
-We propose a framework for mapping naturalistic experiences onto geometric spaces that characterize how they unfold over time.
-We apply this approach to a naturalistic memory experiment which had participants view and recount a video.
-We find that the video and subsequent recall share an event-like structure, and that the ``shapes'' of the trajectories formed by participants' recountings were all highly similar to that of the original video.
-Further, participants' that recounted the events with a high level of precision and in a distinctive way had better subsequent memory performance.
-Lastly, we identified a network of brain structures that are sensitive to the shapes of our ongoing experiences, and an overlapping network that is sensitive to how we will later remember those experiences.
-These results highlight the rich event-like structure of memories for our life experiences, and introduce a novel framework for mapping between dynamic life experiences and their mnemonic counterparts.
+We propose a framework for mapping naturalistic experiences onto geometric spaces that characterize how experiences are segmented into discrete events, and how the contents of a event sequences evolve over time.
+We apply this approach to a naturalistic memory experiment which had participants view and recount a television episode.
+The content of participants' recountings of events from the original episode closely matched the original episode's content.
+However, the similarity patterns \textit{across} events was much different in the original episode as compared with participants' recountings.
+We also identified a network of brain structures that are sensitive to the ``shapes'' of ongoing experiences, and an overlapping network that is sensitive (at the time of encoding) to how people later remembered those experiences in relation to other experiences.
+In this way, modeling the content of richly structured experiences can reveal how (geometrically and conceptually) those experiences are segmented into events and integrated into our memories of other experiences.
 \end{abstract}
@@
 % - Paxton
+
+\begin{figure}[tp]
+\centering
+\includegraphics[width=\textwidth]{figs/precision_distinctiveness_example}
+\caption{\small \textbf{Precision and Distinctiveness Example.}}
+\label{fig:precision-distinctiveness-example}
+\end{figure}
 
@@
 %\bibliography{memlab}
-\bibliography{/Users/paxtonfitzpatrick/Documents/Dartmouth/CDL/CDL-bibliography/memlab.bib}
+\bibliography{CDL-bibliography/memlabr}
 

### 2019-12-08 code/scripts/searchlights/searchlight_permute_recall.py
fixed filepath

@@ -17,7 +17,7 @@ def sfn(l, msk, sl_rad, bcast_var):
 subid, perm = int(sys.argv[1]), int(sys.argv[2])
 
 input_dir = opj(config['datadir'], 'inputs')
-traj_path = opj(input_dir, 'warped', f'{subid}_dtw.npy')
+traj_path = opj(input_dir, 'warped', f'sub{subid}_dtw.npy')
 scan_path = opj(input_dir, 'fMRI', f'sherlock_movie_s{subid}_10000.nii.gz')
 results_dir = opj(config['datadir'], 'outputs', 'searchlight_recall')
 

### 2019-12-08 code/scripts/searchlights/searchlight_config.py
upped ppn to 4

@@ -17,8 +17,8 @@ config['lockdir'] = os.path.join(config['workingdir'], 'locks')
 config['jobname'] = "searchlight"  # default job name
 config['q'] = "largeq"  # options: default, test, largeq
 config['nnodes'] = 1  # how many nodes to use for this one job
-config['ppn'] = 1  # how many processors to use for this one job (assume 4GB of RAM per processor)
-config['walltime'] = '12:00:00'  # maximum runtime, in h:MM:SS
+config['ppn'] = 4  # how many processors to use for this one job (assume 4GB of RAM per processor)
+config['walltime'] = '10:00:00'  # maximum runtime, in h:MM:SS
 config['cmd_wrapper'] = "python"  # replace with actual command wrapper (e.g. matlab, python, etc.)
 
 # ====== MODIFY ONLY THE CODE BETWEEN THESE LINES ======

### 2019-12-10 code/scripts/searchlights/searchlight_config.py
upped ppn to 8

@@ -17,7 +17,7 @@ config['lockdir'] = os.path.join(config['workingdir'], 'locks')
 config['jobname'] = "searchlight"  # default job name
 config['q'] = "largeq"  # options: default, test, largeq
 config['nnodes'] = 1  # how many nodes to use for this one job
-config['ppn'] = 4  # how many processors to use for this one job (assume 4GB of RAM per processor)
+config['ppn'] = 8  # how many processors to use for this one job (assume 4GB of RAM per processor)
 config['walltime'] = '10:00:00'  # maximum runtime, in h:MM:SS
 config['cmd_wrapper'] = "python"  # replace with actual command wrapper (e.g. matlab, python, etc.)
 

### 2019-12-10 code/scripts/searchlights/searchlight_permute_recall.py
fixed searchlight function to compare upper triangles only

@@ -10,8 +10,9 @@ from searchlight_config import config
 # voxel function for searchlight
 def sfn(l, msk, sl_rad, bcast_var):
     b = l[0][msk, :].T
-    c = np.corrcoef(b).ravel()
-    return pearsonr(c, bcast_var.ravel())[0]
+    cm = np.corrcoef(b)
+    triu_brain = cm[np.triu_indices_from(cm, k=1)]
+    return pearsonr(triu_brain, bcast_var)[0]
 
 
 subid, perm = int(sys.argv[1]), int(sys.argv[2])
@@ -42,12 +43,15 @@ except ValueError:
 shifted = np.roll(recall_model, shift=shift, axis=0)
 shifted_corrmat = np.corrcoef(shifted)
 
+# isolate upper right triangle
+shifted_corrmat_triu = shifted_corrmat[np.triu_indices_from(shifted_corrmat, k=1)]
+
 # create Searchlight object
 sl = Searchlight(sl_rad=5)
 
 # distribute data to processes
 sl.distribute([scan_data], mask)
-sl.broadcast(shifted_corrmat)
+sl.broadcast(shifted_corrmat_triu)
 
 # run searchlight, save data
 result = sl.run_searchlight(sfn)

### 2019-12-10 code/scripts/searchlights/searchlight_permute_video.py

@@ -10,8 +10,9 @@ from searchlight_config import config
 # voxel function for searchlight
 def sfn(l, msk, sl_rad, bcast_var):
     b = l[0][msk, :].T
-    c = np.corrcoef(b).ravel()
-    return pearsonr(c, bcast_var.ravel())[0]
+    cm = np.corrcoef(b)
+    triu_brain = cm[np.triu_indices_from(cm, k=1)]
+    return pearsonr(triu_brain, bcast_var)[0]
 
 
 subid, perm = int(sys.argv[1]), int(sys.argv[2])
@@ -42,12 +43,15 @@ except ValueError:
 shifted = np.roll(video_model, shift=shift, axis=0)
 shifted_corrmat = np.corrcoef(shifted)
 
+# isolate upper right triangle
+shifted_corrmat_triu = shifted_corrmat[np.triu_indices_from(shifted_corrmat, k=1)]
+
 # create Searchlight object
 sl = Searchlight(sl_rad=5)
 
 # distribute data to processes
 sl.distribute([scan_data], mask)
-sl.broadcast(shifted_corrmat)
+sl.broadcast(shifted_corrmat_triu)
 
 # run searchlight, save data
 result = sl.run_searchlight(sfn)

### 2019-12-10 code/scripts/searchlights/searchlight_collector.py
writing collector script

@@ -1,0 +1,42 @@
+import os
+import glob
+import numpy as np
+from os.path import join as opj
+from shutil import copy2
+from nilearn.image import load_img, new_img_like
+from searchlight_config import config
+
+video_dir_old = opj(config['datadir'], 'outputs', 'searchlight_video')
+recall_dir_old = opj(config['datadir'], 'outputs', 'searchlight_recall')
+finished_dir = opj(config['datadir'], 'finished')
+video_dir_new = opj(finished_dir, 'searchlight_video')
+recall_dir_new = opj(finished_dir, 'searchlight_recall')
+
+
+N_SUBJECTS = 17
+N_PERMS = 100
+
+
+# make sure all permutations have finished
+assert len(os.listdir(opj(video_dir_old, 'perms'))) == N_SUBJECTS * N_PERMS, 'Some video permutations not finished yet'
+assert len(os.listdir(opj(recall_dir_old, 'perms'))) == N_SUBJECTS * N_PERMS, 'Some recall permutations not finished yet'
+
+try:
+    os.stat(finished_dir)
+# create directory structure
+except FileNotFoundError:
+    print('Creating directory structure...')
+    for d_old, d_new in zip([video_dir_old, recall_dir_old],
+                            [video_dir_new, recall_dir_new]):
+        os.makedirs(opj(d_new, 'perms'), exist_ok=True)
+        # copy non-permuted data
+        for sub in range(1, 18):
+            old_path = opj(d_old, f'sub{sub}.npy')
+            new_path = opj(d_new, f'sub{sub}.npy')
+            copy2(old_path, new_path)
+
+# collect permutations
+ref_img = load_img(opj('????????'))
+
+for perm in range(100):
+    print(f'collecting permutation {perm}...')

### 2019-12-10 code/scripts/searchlights/searchlight_collector.py
finished searchlight collector script

@@ -1,42 +1,63 @@
 import os
-import glob
 import numpy as np
+from glob import glob
 from os.path import join as opj
 from shutil import copy2
-from nilearn.image import load_img, new_img_like
+from nilearn.image import concat_imgs, load_img, new_img_like
+from scipy.stats import ttest_1samp as ttest
 from searchlight_config import config
 
-video_dir_old = opj(config['datadir'], 'outputs', 'searchlight_video')
-recall_dir_old = opj(config['datadir'], 'outputs', 'searchlight_recall')
+output_dir = opj(config['datadir'], 'outputs')
 finished_dir = opj(config['datadir'], 'finished')
-video_dir_new = opj(finished_dir, 'searchlight_video')
-recall_dir_new = opj(finished_dir, 'searchlight_recall')
-
+ref_img_path = opj(config['datadir'], 'inputs', 'fMRI', 'ref_img.nii.gz')
 
 N_SUBJECTS = 17
 N_PERMS = 100
 
 
+def r2z(r):
+    # computes the Fisher z-transformation
+    with np.errstate(invalid='ignore', divide='ignore'):
+        return 0.5 * (np.log(1 + r) - np.log(1 - r))
+
+
 # make sure all permutations have finished
-assert len(os.listdir(opj(video_dir_old, 'perms'))) == N_SUBJECTS * N_PERMS, 'Some video permutations not finished yet'
-assert len(os.listdir(opj(recall_dir_old, 'perms'))) == N_SUBJECTS * N_PERMS, 'Some recall permutations not finished yet'
+assert len(os.listdir(opj(output_dir, 'searchlight_video', 'perms'))) == N_SUBJECTS * N_PERMS, \
+    'Some video permutations not finished yet'
+assert len(os.listdir(opj(output_dir, 'searchlight_recall', 'perms'))) == N_SUBJECTS * N_PERMS, \
+    'Some recall permutations not finished yet'
 
 try:
     os.stat(finished_dir)
 # create directory structure
 except FileNotFoundError:
     print('Creating directory structure...')
-    for d_old, d_new in zip([video_dir_old, recall_dir_old],
-                            [video_dir_new, recall_dir_new]):
-        os.makedirs(opj(d_new, 'perms'), exist_ok=True)
-        # copy non-permuted data
+    for analysis in ['video', 'recall']:
+        dir_old = opj(output_dir, f'searchlight_{analysis}')
[…]

### 2019-12-11 code/scripts/searchlights/searchlight_submit.py
update to searchlight submit script

@@ -19,6 +19,8 @@ from scipy.spatial.distance import correlation
 input_dir = opj(config['datadir'], 'inputs')
 traj_path = opj(input_dir, 'models_t100_v50_r10.npy')
 warped_dir = opj(input_dir, 'warped')
+vid_perms_dir = opj(config['datadir'], 'outputs', 'searchlight_video', 'perms')
+rec_perms_dir = opj(config['datadir'], 'outputs', 'searchlight_recall', 'perms')
 video_jobscript = opj(dirname(realpath(__file__)), 'searchlight_permute_video.py')
 recall_jobscript = opj(dirname(realpath(__file__)), 'searchlight_permute_recall.py')
 
@@ -40,6 +42,7 @@ for sub, rec_traj in enumerate(recall_trajs):
 # create jobs for submission
 job_commands = list()
 job_names = list()
+
 for perm in perms:
     for subid in range(1, 18):
         job_names.append(f'searchlight_video_{subid}_{perm}')
@@ -47,7 +50,6 @@ for perm in perms:
 
         job_names.append(f'searchlight_recall_{subid}_{perm}')
         job_commands.append(f'{recall_jobscript} {subid} {perm}')
-
 
 # ====== MODIFY ONLY THE CODE BETWEEN THESE LINES ======
 

### 2019-12-11 code/scripts/searchlights/searchlight_collector.py
made nifti dataobjects float64 precision

@@ -52,12 +52,12 @@ for perm in range(100):
         for sub in range(1, 18):
             img_path = glob(opj(finished_dir, f'searchlight_{analysis}', 'perms', f'sub{sub}_perm{perm}_*'))[0]
             sub_data = np.load(img_path, allow_pickle=True)
-            img = new_img_like(ref_img, sub_data.astype(np.float))
+            img = new_img_like(ref_img, sub_data.astype(np.float64))
             imgs.append(img)
 
         imgs = concat_imgs(imgs)
-        imgs_z = r2z(imgs.get_data())
+        imgs_z = r2z(imgs.get_data().astype(np.float64))
         statmap = ttest(np.moveaxis(imgs_z, -1, 0), 0).statistic
-        stat_img = new_img_like(ref_img, statmap.astype(np.float))
+        stat_img = new_img_like(ref_img, statmap.astype(np.float64))
         result_path = opj(finished_dir, f'searchlight_{analysis}', 'perms', f'perm{perm}.nii.gz')
         stat_img.to_filename(result_path)

### 2019-12-11 code/scripts/searchlight_movie.py
deleted old searchlight scripts

@@ -1,31 +1,0 @@
-import sys
-import numpy as np
-from nilearn.image import load_img
-from brainiak.searchlight.searchlight import Searchlight
-
-subid = sys.argv[1]
-data = load_img('/idata/cdl/data/fMRI/andy/sherlock/data/sherlock_movie_s%s_10000.nii.gz' % str(subid)).get_data()
-
-mask = data[:,:,:,0]!=10000
-model = np.load('/idata/cdl/data/fMRI/andy/sherlock/data/movie_corrmat.npy')
-params = dict(sl_rad=5)
-
-# Create searchlight object
-sl = Searchlight(**params)
-
-# Distribute data to processes
-sl.distribute([data], mask)
-sl.broadcast(model)
-
-# Define voxel function
-def sfn(l, msk, myrad, bcast_var):
-    from scipy.spatial.distance import cdist
-    from scipy.stats import pearsonr
-    b = l[0][msk,:].T
-    c = 1 - cdist(b, b, 'correlation').ravel()
-    return pearsonr(c, bcast_var.ravel())[0]
-
-# Run searchlight
-result = sl.run_searchlight(sfn)
-
-np.save('/idata/cdl/data/fMRI/andy/sherlock/analyses/searchlight_movie/s%s' % str(subid), result)

### 2019-12-11 code/scripts/searchlight_movie_perms.py

@@ -1,53 +1,0 @@
-import sys
-import numpy as np
-from nilearn.image import load_img
-from brainiak.searchlight.searchlight import Searchlight
-import pandas as pd
-
-subid = int(sys.argv[1])
-perm = int(sys.argv[2])
-
-np.random.seed(perm)
-
-# load fmri data
-data = load_img('/idata/cdl/data/fMRI/andy/sherlock/data/sherlock_movie_s%s_10000.nii.gz' % str(subid)).get_data()
-
-# load dtw warp path and extract the movie path
-#path = np.load('/idata/cdl/data/fMRI/andy/sherlock/data/s%s_dtw_path.npy' % str(subid))
-#movie_path = np.array(list(map(lambda x: x[0], path)))
-
-# reindex the fmri data with the movie path
-#data = data[:,:,:, movie_path]
-
-# create the mask
-mask = data[:,:,:,0]!=10000
-
-# load video model
-model = np.load('/idata/cdl/data/fMRI/andy/sherlock/data/movie_corrmat.npy')
-
-# shift the video model
-shift = np.random.randint(1, model.shape[0]-1)
-shifted = np.roll(model, shift=shift, axis=0)
-
-# recompute shifted correlation matrix
-model = pd.DataFrame(shifted).T.corr().values
-
-# Create searchlight object
-params = dict(sl_rad=5)
-sl = Searchlight(**params)
-
-# Distribute data to processes
-sl.distribute([data], mask)
-sl.broadcast(model)
-
-# Define voxel function
-def sfn(l, msk, myrad, bcast_var):
-    from scipy.spatial.distance import cdist
-    from scipy.stats import pearsonr
-    b = l[0][msk,:].T
-    c = 1 - cdist(b, b, 'correlation').ravel()
-    return pearsonr(c, bcast_var.ravel())[0]
-
-# Run searchlight
-result = sl.run_searchlight(sfn)
-np.save('/idata/cdl/data/fMRI/andy/sherlock/analyses/searchlight_movie/perms/s%s_perm%s_shift%s' % (str(subid), str(perm), str(shift)), result)

### 2019-12-11 code/scripts/searchlight_recall.py

@@ -1,43 +1,0 @@
-import sys
-import numpy as np
-from nilearn.image import load_img
-from brainiak.searchlight.searchlight import Searchlight
-
-subid = sys.argv[1]
-
-# load fmri data
-data = load_img('/idata/cdl/data/fMRI/andy/sherlock/data/sherlock_movie_s%s_10000.nii.gz' % str(subid)).get_data()
-
-# load dtw warp path and extract the movie path
-path = np.load('/idata/cdl/data/fMRI/andy/sherlock/data/s%s_dtw_path.npy' % str(subid))
-movie_path = np.array(list(map(lambda x: x[0], path)))
-
-# reindex the fmri data with the movie path
-data = data[:,:,:, movie_path]
-
-# create the mask
-mask = data[:,:,:,0]!=10000
-
-# load the recall model
-model = np.load('/idata/cdl/data/fMRI/andy/sherlock/data/s%s_recall_corrmat_dtw.npy' % str(subid))
-
-# Create searchlight object
-params = dict(sl_rad=5)
-sl = Searchlight(**params)
-
-# Distribute data to processes
-sl.distribute([data], mask)
-sl.broadcast(model)
-
-# Define voxel function
-def sfn(l, msk, myrad, bcast_var):
-    from scipy.spatial.distance import cdist
-    from scipy.stats import pearsonr
-    b = l[0][msk,:].T
-    c = 1 - cdist(b, b, 'correlation').ravel()
-    return pearsonr(c, bcast_var.ravel())[0]
-
-# Run searchlight
-result = sl.run_searchlight(sfn)
-
-np.save('/idata/cdl/data/fMRI/andy/sherlock/analyses/searchlight_recall/s%s' % str(subid), result)

### 2019-12-11 code/scripts/embedding/embedding_config.py
added embedding cluster scripts

@@ -1,0 +1,31 @@
+import socket
+import os
+
+config = dict()
+
+# ====== MODIFY ONLY THE CODE BETWEEN THESE LINES ======
+# job creation options
+
+#add additional checks for your local machine here...
+# ******** check kiewit hostname from eduroam ********
+
+config['startdir'] = '/dartfs/rc/lab/D/DBIC/CDL/f0028ph/sherlock-embedding'
+config['workingdir'] = os.path.join(config['startdir'], 'scripts')
+config['datadir'] = os.path.join(config['startdir'], 'data')
+config['figdir'] = os.path.join(config['startdir'], 'figures')
+config['template'] = os.path.join(os.path.dirname(os.path.realpath(__file__)), 'run_job_cluster.sh')
+config['scriptdir'] = os.path.join(config['workingdir'], 'scripts')
+config['lockdir'] = os.path.join(config['workingdir'], 'locks')
+
+
+# runtime options
+config['jobname'] = "embedding"  # default job name
+config['q'] = "largeq"  # options: default, test, largeq
+config['nnodes'] = 1  # how many nodes to use for this one job
+config['ppn'] = 1  # how many processors to use for this one job (assume 4GB of RAM per processor)
+config['walltime'] = '2:00:00'  # maximum runtime, in h:MM:SS
+config['cmd_wrapper'] = "python"  # replace with actual command wrapper (e.g. matlab, python, etc.)
+
+#extra options
+
+# ====== MODIFY ONLY THE CODE BETWEEN THESE LINES ======

### 2019-12-11 code/scripts/embedding/embedding_submit.py

@@ -1,0 +1,159 @@
+#!/usr/bin/python
+
+# create a bunch of job scripts
+from embedding_config import config
+from subprocess import call
+import os
+import socket
+import getpass
+import datetime as dt
+from os.path import join as opj
+
+
+# ====== MODIFY ONLY THE CODE BETWEEN THESE LINES ======
+import numpy as np
+job_script = opj(os.path.dirname(os.path.realpath(__file__)), 'embedding_cruncher.py')
+
+embeddings_dir = opj(config['datadir'], 'embeddings')
+fig_dir = config['figdir']
+
+job_commands = list()
+job_names = list()
+
+min_seed = 0
+max_seed = 10000
+
+# order 1: recalls, video, avg recall
+# order 2: recalls, avg recall, video
+# order 3: video, avg recall, recalls
+# order 4: video, recalls, avg recall
+# order 5: avg recall, recalls, video
+# order 6: avg recalls, video, recalls
+
+for order in range(1, 7):
+    if not os.path.isdir(opj(embeddings_dir, f'order{order}')):
+        os.mkdir(opj(embeddings_dir, f'order{order}'))
+    if not os.path.isdir(opj(fig_dir, f'order{order}')):
+        os.mkdir(opj(fig_dir, f'order{order}'))
+    for division in range(10):
+        job_commands.append(f'{job_script} {order} {min_seed} {max_seed} {division}')
+        job_names.append(f'optimize_embedding_order{order}_{min_seed}_{max_seed}_{division}')
+
+    # done = [int(os.path.splitext(file)[0][4:]) for file in os.listdir(opj(embeddings_dir, f'order{order}'))]
+    # seeds_todo = [s for s in seeds if s not in done]
+
+    # for seed in seeds_todo:
+    #     job_commands.append(f'{job_script} {order} {seed}')
+    #     job_names.append(f'optimize_embedding_order{order}_seed{seed}')
+
+
+
+# ====== MODIFY ONLY THE CODE BETWEEN THESE LINES ======
+
+assert(len(job_commands) == len(job_names))
+
+
+# job_command is referenced in the run_job.sh script
+# noinspection PyBroadException,PyUnusedLocal
+def create_job(name, job_command):
+    # noinspection PyUnusedLocal,PyShadowingNames
+    def create_helper(s, job_command):
+        x = [i for i, char in enumerate(s) if char == '<']
+        y = [i for i, char in enumerate(s) if char == '>']
+        if len(x) == 0:
+            return s
+
+        q = ''
+        index = 0
[…]

### 2019-12-11 paper/main.tex
started updating text

@@
 Next, we fit a topic model with (up to) $K = 100$ topics to this collection of documents.
-We found that 27 unique topics (with non-zero weights) were sufficient to describe the time-varying content of the video (see \textit{Methods}; Figs.~\ref{fig:schematic}, \topics).
+We found that 32 unique topics (with non-zero weights) were sufficient to describe the time-varying content of the video (see \textit{Methods}; Figs.~\ref{fig:schematic}, \topics).
 Note that our approach is similar in some respects to Dynamic Topic Models~\citep{BleiLaff06} in that we sought to characterize how the thematic content of the episode evolved over time.
@@
 \textbf{B.} Timepoint-by-timepoint correlation matrix of the topic vectors displayed in Panel A.
-Event boundaries detected by the HMM are denoted in yellow (36 events detected).
-\textbf{C.} Average topic vectors for each of the 36 video events.
-\textbf{D.} Topic vectors for each of 252 sentences spoken by an example participant while recalling the video, resampled to match the timseries of the video.
+Event boundaries detected by the HMM are denoted in yellow (30 events detected).
+\textbf{C.} Average topic vectors for each of the 30 video events.
+\textbf{D.} Topic vectors for each of 265 sliding windows of sentences spoken by an example participant while recalling the video.
 \textbf{E.} Timepoint-by-timepoint correlation matrix of the topic vectors displayed in Panel D.
-Event boundaries detected by the HMM are denoted in yellow (29 events detected).
-\textbf{F.} Average topic vectors for each of the 29 recalled events from the example participant.
+Event boundaries detected by the HMM are denoted in yellow (22 events detected).
+\textbf{F.} Average topic vectors for each of the 22 recalled events from the example participant.
 \textbf{G.} Correlations between the topic vectors for every pair of video events (Panel C) and recalled events (from the example participant; Panel F).
@@
 Analogous to how we analyzed the time-varying content of the video, to obtain similar estimates for participants' recalls, we treated each (overlapping) 10-sentence ``window'' of their transcript as a ``document'' and then computed the most probable mix of topics reflected in each timepoint's sentences.
-This yielded, for each participant, a number-of-sentences by number-of-topics topic proportions matrix that characterized how the topics identified in the original video were reflected in the participant's recalls.
+This yielded, for each participant, a number-of-windows by number-of-topics topic proportions matrix that characterized how the topics identified in the original video were reflected in the participant's recalls.
 Note that an important feature of our approach is that it allows us to compare participant's recalls to events from the original video, despite that different participants may have used different language to describe the same event, and that those descriptions may not match the original annotations.
@@
 First, although every individual participant's recalls could be segmented into discrete events (i.e., every individual participant's recall correlation matrix exhibited clear block diagonal structure; Fig.~\corrmats), each participant appeared to have a unique \textit{recall resolution}, reflected in the sizes of those blocks.
-For example, some participants' recall topic proportions segmented into just a few events (e.g., Participants P2, P6, and P14), while others' recalls segmented into many shorter duration events (e.g., Participants P12, P13, and P17).
+For example, some participants' recall topic proportions segmented into just a few events (e.g., Participants P4, P5, and P7), while others' recalls segmented into many shorter duration events (e.g., Participants P12, P13, and P17).
 This suggests that different participants may be recalling the video with different levels of detail-- e.g., some might touch on just the major plot points, whereas others might attempt to recall every minor scene or action.
@@
 Temporal clustering refers to the extent to which participants group their recall responses according to encoding position.
+Overall, we found that sequentially viewed video events were clustered heavily in participants' recall event sequences (mean: 0.767, SEM: 0.029), and that participants with higher temporal clustering scores also tended to perform better according to both \cite{ChenEtal17}'s hand-annotated memory scores (Pearson's $r(15) = 0.62, p = 0.008$) and our model's estimate (Pearson's $r(15) = 0.54, p = 0.024$).
 Semantic clustering measures the extent to which participants cluster their recall responses according to semantic similarity.
-Overall, we found that participants heavily clustered video events in their recalls by both temporal proximity (mean: 0.860, SEM: 0.016) and semantic content (mean: 0.888, SEM: 0.014).
+We found that participants tended to recall semantically similar video events together (mean: 0.787, SEM: 0.018), and participants who exhibited stronger semantic clustering remembered more video events overall (Pearson's $r(15) = 0.55, p = 0.02$).
 
-% Overall, we found that sequentially viewed video events were clustered heavily in participants' recall event sequences (mean: 0.860, SEM: 0.016) and that participants with higher temporal clustering scores also tended to recall more events (Pearson's $r(15) = 0.50, p = 0.042$).
-Semantic clustering measures the extent to which participants cluster their recall responses according to semantic similarity.
-We found that participants tended to recall semantically similar video events together (mean: 0.888, SEM: 0.014) and participants who exhibited stronger semantic clustering remembered more video events overall (Pearson's $r(15) = 0.55, p = 0.02$).
+% Overall, we found that participants heavily clustered video events in their recalls by both temporal proximity (mean: 0.860, SEM: 0.016) and semantic content (mean: 0.888, SEM: 0.014).
+
+% Semantic clustering measures the extent to which participants cluster their recall responses according to semantic similarity.
 

### 2019-12-11 paper/main.tex
updated text stats, removed placeholder fig

@@
 Temporal clustering refers to the extent to which participants group their recall responses according to encoding position.
-Overall, we found that sequentially viewed video events were clustered heavily in participants' recall event sequences (mean: 0.767, SEM: 0.029), and that participants with higher temporal clustering scores also tended to perform better according to both \cite{ChenEtal17}'s hand-annotated memory scores (Pearson's $r(15) = 0.62, p = 0.008$) and our model's estimate (Pearson's $r(15) = 0.54, p = 0.024$).
+Overall, we found that sequentially viewed video events were clustered heavily in participants' recall event sequences (mean: 0.767, SEM: 0.029), and that participants with higher temporal clustering scores tended to perform better according to both \cite{ChenEtal17}'s hand-annotated memory scores (Pearson's $r(15) = 0.62,~p = 0.008$) and our model's estimate (Pearson's $r(15) = 0.54,~p = 0.024$).
 Semantic clustering measures the extent to which participants cluster their recall responses according to semantic similarity.
-We found that participants tended to recall semantically similar video events together (mean: 0.787, SEM: 0.018), and participants who exhibited stronger semantic clustering remembered more video events overall (Pearson's $r(15) = 0.55, p = 0.02$).
+We found that participants tended to recall semantically similar video events together (mean: 0.787, SEM: 0.018), and that semantic clustering score was also related to both hand-annotated  (Pearson's $r(15) = 0.65,~p = 0.004$) and model-derived (Pearson's $r(15) = 0.63,~p = 0.007$) memory performance.
 
-% Overall, we found that participants heavily clustered video events in their recalls by both temporal proximity (mean: 0.860, SEM: 0.016) and semantic content (mean: 0.888, SEM: 0.014).
-
-% Semantic clustering measures the extent to which participants cluster their recall responses according to semantic similarity.
-
-% ------ NOTE: ------
-% Temporal & semantic clustering scores' correlations with number of events & model-estimated memory are no longer significant.  Worth mentioning at all then?
-% temporal x hand-annotated: r=.5, p=0.042
-% temporal x model-estimated: r=.36, p=.16
-% temporal x n events: r=.29, p=.26
-% semantic x hand-annotated: r=.32, p=.21
-% semantic x model-estimated: r=.33, p=.20
-% semantic x n events: r=.48, p=.053
+% NOTE: 
+% Semantic and temporal clustering are both positively correlated with n_events -- r=0.49; p=0.046 and r=0.61; p=0.009, respectively.  
 % - Paxton
@@
 Participants whose recall events are more veridical descriptions of what happened in the video event will presumably have higher precision scores.
-We find that, across participants, a higher precision score is correlated to both hand-annotated memory performance (Pearson's $r(15) = 0.55, p = 0.021$) and the number of recall events estimated by our model (Pearson's $r(15) = 0.66, p = 0.004$).
+We find that, across participants, a higher precision score is correlated to both hand-annotated memory performance (Pearson's $r(15) = 0.56, p = 0.021$) and the number of recall events estimated by our model (Pearson's $r(15) = 0.85, p < 0.001$).
 A second novel metric we introduce here is distinctiveness, or how unique the recall description was to each video event.
@@
 We hypothesized that participants who recounted events in a more distinctive way would display better overall memory.
-Similarly to precision, we find that the more distinct participants recalls are (on average), the more they remembered (hand-annotated memory: Pearson's $r(15) = 0.62, p = 0.007$; number of events: Pearson's $r(15) = 0.78, p < 0.001$).
+We find that this distinctiveness score is related to our model's estimated number of recalled events (Pearson's $r(15) = 0.49, p = 0.046$) but not to the analogous hand-annotated metric (Pearson's $r(15) = 0.31, p = 0.23$).
 In summary, using two novel metrics afforded by our approach, we find that participants whose recalls are both more precise and distinct remember more content.
 % ------ NOTE: ------
-% Correlations between precision/distinctiveness and number of events need to be updated once analysis is re-run
+% rephrase/reframe distinctiveness?
 % - Paxton
@@
   \label{fig:precision-distinctiveness}
-\end{figure}
-% ------ NOTE: ------
-% Figure and caption need to be updated once analysis is re-run
-% - Paxton
-
-\begin{figure}[tp]
-\centering
-\includegraphics[width=\textwidth]{figs/precision_distinctiveness_example}
-\caption{\small \textbf{Precision and Distinctiveness Example.}}
-\label{fig:precision-distinctiveness-example}
 \end{figure}
@@
 \end{figure}
+% ------ NOTE: ------
+% will update trajectory fig when new version is finished
+% - Paxton
 

### 2019-12-11 paper/main.tex
updated topic modeling methods

@@
 \end{figure}
+% ------ NOTE: ------
+% will also update this fig when new version is finished
+% - Paxton
 
@@
 
-% NOTE: for the "nearby moments of real life/naturalistic stimuli tend to be semantically similar" argument, is it worth adding something to the effect of:
-% 1. we observed high temporal clustering scores
-% 2. we also observed high semantic clustering scores
-% 3. ergo, for both to be true, temporally proximal video events must be semantically similar
-% - Paxton
-
 Thus, analyses such as those in Figure \ref{fig:list-learning} that address only the temporal dynamics of free recall paint an incomplete picture of memory for naturalistic episodes.
@@
 Future work might explore whether and how these metrics compare between cognitively impoverished groups and healthy controls.
+% ------ NOTE: ------
+% need to update text here to reflect new distinctivness stats in precision/distinctiveness fig
+% - Paxton
 
@@
 \subsubsection*{Topic modeling}
-The input to the topic model we trained to characterize the dynamic content of the video comprised hand-generated annotations of each of 1000 scenes spanning the video clip~\citep[generated by][]{ChenEtal17}.
+The input to the topic model we trained to characterize the dynamic content of the video comprised 998 hand-generated annotations of short (mean: 2.96s) scenes spanning the video clip~(\citealp{ChenEtal17} generated 1000 annotations total; we removed two referring to the break between the first and second scan sessions, during which no fMRI data was collected).
 The features annotated included: narrative details (a sentence or two describing what happened in that scene); whether the scene took place indoors or outdoors; names of any characters that appeared in the scene; name(s) of characters in camera focus; name(s) of characters who were speaking in the scene; the location (in the story) that the scene took place; camera angle (close up, medium, long, top, tracking, over the shoulder, etc.); whether music was playing in the scene or not; and a transcription of any on-screen text.
 We concatenated the text for all of these features within each segment, creating a ``bag of words'' describing each scene.
-We then re-organized the text descriptions into overlapping sliding windows spanning 50 scenes each.
-In other words, the first text sample comprised the combined text from the first 50 scenes (i.e., 1--50), the second comprised the text from scenes 2--51, and so on.
+We then re-organized the text descriptions into overlapping sliding windows of 50 scenes each.
+In other words, we created a ``context" for each scene comprising the text descriptions of the preceding 25 scenes, the present scene, and the following 24 scenes.
+To model the ``context" at the beginning and end of the video (i.e., within 50 scenes of the beginning or end), we created overlapping sliding windows that grew in size from one scene to the full length, then similarly tapered their length at the end.
+This bore the additional benefit of representing each scene's description in the text corpus an equal number of times.
+
 We trained our model using these overlapping text samples with \texttt{scikit-learn}~\citep[version 0.19.1; ][]{PedrEtal11}, called from our high-dimensional visualization and text analysis software, \texttt{HyperTools}~\citep{HeusEtal18a}.
-Specifically, we used the \texttt{CountVectorizer} class to transform the text from each scene into a vector of word counts (using the union of all words across all scenes as the ``vocabulary,'' excluding English stop words); this yielded a number-of-scenes by number-of-words \textit{word count} matrix.
-We then used the \texttt{LatentDirichletAllocation} class (topics=100, method=`batch') to fit a topic model~\citep{BleiEtal03} to the word count matrix, yielding a number-of-scenes (1000) by number-of-topics (100) \textit{topic proportions} matrix.
-The topic proportions matrix describes which mix of topics (latent themes) is present in each scene.
+Specifically, we used the \texttt{CountVectorizer} class to transform the text from each window into a vector of word counts (using the union of all words across all scenes as the ``vocabulary,'' excluding English stop words); this yielded a number-of-windows by number-of-words \textit{word count} matrix.
+We then used the \texttt{LatentDirichletAllocation} class (topics=100, method=`batch') to fit a topic model~\citep{BleiEtal03} to the word count matrix, yielding a number-of-windows (1047) by number-of-topics (100) \textit{topic proportions} matrix.
+The topic proportions matrix describes which mix of topics (latent themes) is present in and around each scene.
 Next, we transformed the topic proportions matrix to match the 1976 fMRI volume acquisition times.
-For each fMRI volume, we took the topic proportions from whatever scene was displayed for most of that volume's 1500~ms acquisition time.
-This yielded a new number-of-TRs (1976) by number-of-topics (100) topic proportions matrix.
+We assigned each topic vector to the timepoint midway between the beginning of the first scene and the end of the last scene in its corresponding sliding text window.
+We then transformed these timepoints to units of TRs and interpolated the dynamic topic proportions matrix to obtain number-of-TRs (1976) by number-of-topics (100) matrix.
 
 We created similar topic proportions matrices using hand-annotated transcripts of each participant's recall of the video~\citep[annotated by ][]{ChenEtal17}.
-We tokenized the transcript into a list of sentences, and then re-organized the list into overlapping sliding windows spanning 10 sentences each; in turn we transformed each window's sentences into a word count vector (using the same vocabulary as for the video model).
+We tokenized the transcript into a list of sentences, and then re-organized the list into overlapping sliding windows spanning 10 sentences each (and analogously tapered the lengths of the first and last 10 sliding windows).
+In turn, we transformed each window's sentences into a word count vector (using the same vocabulary as for the video model).
 We then used the topic model already trained on the video scenes to compute the most probable topic proportions for each sliding window.
-This yielded a number-of-sentences (range: 68--294) by number-of-topics (100) topic proportions matrix, for each participant.
+This yielded a number-of-windows (range: 83--312) by number-of-topics (100) topic proportions matrix for each participant.
 These reflected the dynamic content of each participant's recalls.
-Finally, we resampled each recall model to match the timecourse of the video model.
 Note: for details on how we selected the video and recall window lengths and number of topics, see \textit{Supporting Information} and Figure~\topicopt.
@@
 
-%\bibliography{memlab}
-\bibliography{CDL-bibliography/memlabr}
+\bibliography{../../CDL-bibliography/memlab}
+%\bibliography{CDL-bibliography/memlab}
 

### 2019-12-11 paper/main.tex
updated brain methods

@@
 In other words, we created a ``context" for each scene comprising the text descriptions of the preceding 25 scenes, the present scene, and the following 24 scenes.
-To model the ``context" at the beginning and end of the video (i.e., within 50 scenes of the beginning or end), we created overlapping sliding windows that grew in size from one scene to the full length, then similarly tapered their length at the end.
+To model the ``context" at the beginning and end of the video (i.e., within 25 scenes of the beginning or end), we created overlapping sliding windows that grew in size from one scene to the full length, then similarly tapered their length at the end.
 This bore the additional benefit of representing each scene's description in the text corpus an equal number of times.
+% ------ NOTE: ------
+% need to refine explanation here a little bit
+% - Paxton
 
@@
 
-We used an optimization procedure to select the appropriate $K$ for each topic proportions matrix.  Specifically, we computed (for each matrix)
+We used an optimization procedure to select the appropriate $K$ for each topic proportions matrix.
+Prior studies on narrative structure and processing have shown that we both perceive and internally represent the world around us at multiple, hierarchical timescales (e.g., \citealp{HassEtal08, LernEtal11, HassEtal15, ChenEtal17, BaldEtal17, BaldEtal18}).
+However, for the purposes of our framework, we sought to identify the single timescale of event-representations that is emphasized \textit{most heavily} in the temporal structure of the video and each participant's recalls.
+We quantified this as the set of $K$ event boundaries that yielded the maximal distinctiveness between the content (i.e., topics) within each event and that in all other events.
+Specifically, we computed (for each matrix)
 \[
-  \argmax_K \left[POM(\frac{a}{b-J}) - \frac{K}{\alpha}\right],
+  \argmax_K \left[W_{1}(a, b)\right],
 \]
-where $a$ was the average correlation between the topic vectors of timepoints within the same state; $b$ was the average correlation between the topic vectors of timepoints within \textit{different} states; \textit{J} was a constant used to ensure a positive denominator, set equal to $\min_K\left[{\frac{a}{b}}\right]$; and $\alpha$ was a regularization parameter that we set to 5 times the window length (i.e., 250 scenes for the video topic trajectory and 50 sentences for the recall topic trajectories).
-Before subtracting the regularization term, we scaled the ratio of correlations to be a proportion of the maximum ratio across all $K$'s.
-Figure~\ref{fig:model}B displays the event boundaries returned for the video, and Figure~\corrmats~displays the event boundaries returned for each participant's recalls (See Fig.~\kcorrs~for the values of \textit{a} and \textit{b} for each $K$, Fig.~\kopt~for the optimization functions for the video and recalls).
+where $a$ was the distribution of correlations between the topic vectors of timepoints within the same state and $b$ was the average correlation between the topic vectors of timepoints within \textit{different} states.
+For each possible $K$, we computed the first Wasserstein distance ($W_{1}$; also known as ``earth mover's distance"; \citealp{Dobr70, RamdEtal17}) between these distributions, and chose the $K$-value that yielded the greatest difference.
+Figure~\ref{fig:model}B displays the event boundaries returned for the video, and Figure~\corrmats~displays the event boundaries returned for each participant's recalls (See Fig.~\kopt~for the optimization functions for the video and recalls).
 After obtaining these event boundaries, we created stable estimates of each topic proportions matrix by averaging the topic vectors within each event.
 This yielded a number-of-events by number-of-topics matrix for the video and recalls from each participant.
-
-We also evaluated a parameter-free procedure for choosing $K$, which finds the $K$ value that maximizes the Wasserstein distance (a.k.a.
-``Earth mover's" distance) between the within and across event distributions of correlation values.
-This alternative procedure largely replicated the pattern of results found with the parameterized method described above, but recovered substantially fewer events on average (Fig.\wasserstein).
-While both approaches seem to underestimate the number of video/recall events relative to the ``true" number (as determined by human raters), the parameterized approach was closer to the true number.
 
@@
 
-Perhaps the simplest and most widely used measure of memory performance is \textit{accuracy}---i.e., the proportion of studied (experienced) items (in this case, the 34 video events) that the participant later remembered.
+Perhaps the simplest and most widely used measure of memory performance is \textit{accuracy}---i.e., the proportion of studied (experienced) items (in this case, the 30 video events) that the participant later remembered.
 \cite{ChenEtal17} developed a human rating system whereby the quality of each participant's memory was evaluated by an independent rater.
-We found a strong across-participants correlation between these independant ratings and the overall number of events that our HMM approach identified in participants' recalls (Pearson's $r(15) = 0.64, p = 0.006$).
+We found a strong across-participants correlation between these independant ratings and the overall number of events that our HMM approach identified in participants' recalls (Pearson's $r(15) = 0.65, p = 0.004$).
 
@@
 \paragraph{Probability of first recall (PFR).}  PFR curves~\citep{WelcBurn24, PostPhil65, AtkiShif68} reflect the probability that an item will be recalled first as a function of its serial position during encoding.
-To carry out this analysis, we initialized a number-of-participants (17) by number-of-video-events (34) matrix of zeros.
+To carry out this analysis, we initialized a number-of-participants (17) by number-of-video-events (30) matrix of zeros.
 Then for each participant, we found the index of the video event that was recalled first (i.e., the video event whose topic vector was most strongly correlated with that of the first recall event) and filled in that index in the matrix with a 1.
-Finally, we averaged over the rows of the matrix, resulting in a 1 by 34 array representing the proportion of participants that recalled an event first, as a function of the order of the event's appearance in the video (Fig.~\ref{fig:list-learning}A).
+Finally, we averaged over the rows of the matrix, resulting in a 1 by 30 array representing the proportion of participants that recalled an event first, as a function of the order of the event's appearance in the video (Fig.~\ref{fig:list-learning}A).
 
@@
 For each recall transition (following the first recall), we computed the lag between the current recall event and the next recall event, normalizing by the total number of possible transitions.
-This yielded a number-of-participants (17) by number-of-lags (-33 to +33; 67 lags total) matrix.
+This yielded a number-of-participants (17) by number-of-lags (-29 to +29; 61 lags total) matrix.
 We averaged over the rows of this matrix to obtain a group-averaged lag-CRP curve (Fig.~\ref{fig:list-learning}B).
@@
 \paragraph{Serial position curve (SPC).} SPCs~\citep{Murd62a} reflect the proportion of participants that remember each item as a function of the items' serial position during encoding.
-We initialized a number-of-participants (17) by number-of-video-events (34) matrix of zeros.
+We initialized a number-of-participants (17) by number-of-video-events (30) matrix of zeros.
 Then, for each recalled event, for each participant, we found the index of the video event that the recalled event most closely matched (via the correlation between the events' topic vectors) and entered a 1 into that position in the matrix (i.e., for the given participant and event).
 This resulted in a matrix whose entries indicated whether or not each event was recalled by each participant (depending on whether the corresponding entires were set to one or zero).
-Finally, we averaged over the rows of the matrix to yield a 1 by 34 array representing the proportion of participants that recalled each event as a function of the order of the event's appearance in the video (Fig.~\ref{fig:list-learning}C).
+Finally, we averaged over the rows of the matrix to yield a 1 by 30 array representing the proportion of participants that recalled each event as a function of the order of the event's appearance in the video (Fig.~\ref{fig:list-learning}C).
 
@@
 
-% NOTE: Thinking about removing this analysis? More of a sanity check than something novel and cool, and takes up space. Happy to be convinced otherwise
+% NOTE: Thinking about removing this analysis? More of a sanity check than something novel and cool, and takes up space. Happy to be convinced otherwise - andy
 % leaving this one to Jeremy's judgement
@@
 This general approach for discovering a shared low-dimensional embedding for a collections of high-dimensional observations follows \cite{HeusEtal18a}.
+% ------ NOTE: ------
+% need to add info about embedding optimization
+% - Paxton
 
@@
 \subsection*{Searchlight fMRI analyses}
-In Figure~\ref{fig:brainz}, we present two analyses aimed at identifying brain structures whose responses (as participants viewed the video) exhibited particular temporal correlations.
-We developed a searchlight analysis whereby we constructed a cube centered on each voxel (radius: 5~voxels).
-For each of these cubes, we computed the temporal correlation matrix of the voxel responses during video viewing.
+In Figure~\ref{fig:brainz}, we present two analyses aimed at identifying brain regions whose responses (as participants viewed the video) exhibited a particular temporal structure.
+We developed a searchlight analysis wherein we constructed a cube centered on each voxel (radius: 5~voxels) and for each of these cubes, computed the temporal correlation matrix of the voxel responses during video viewing.
 Specifically, for each of the 1976 volumes collected during video viewing, we correlated the activity patterns in the given cube with the activity patterns (in the same cube) collected during every other timepoint.
@@
 
-Next, we constructed two sets of ``template'' matrices: one reflecting the video's topic trajectory and the other reflecting each participant's recall topic trajectory.
+Next, we constructed a series of ``template'' matrices: the first reflecting the timecourse of video's topic trajectory, and the others reflecting that of each participant's recall topic trajectory.
 To construct the video template, we computed the correlations between the topic proportions estimated for every pair of TRs (prior to segmenting the trajectory into discrete events; i.e., the correlation matrix shown in Figs.~\ref{fig:model}B and \ref{fig:brainz}A).
 We constructed similar temporal correlation matrices for each participant's recall topic trajectory (Figs.~\ref{fig:model}D, \corrmats).
-However, to correct for length differences and potential non-linear transformations between viewing time and recall time, we first used dynamic time warping~\citep{BernClif94} to temporally align participants' recall topic trajectories with the video topic trajectory (an example correlation matrix before and after warping is shown in Fig.~\ref{fig:brainz}B).
+However, to correct for length differences and potential non-linear transformations between viewing time and recall time, we first used dynamic time warping~\citep{BernClif94} to temporally align participants' recall topic trajectories with the video topic trajectory.
+An example correlation matrix before and after warping is shown in Fig.~\ref{fig:brainz}B.
 This yielded a 1976 by 1976 correlation matrix for the video template and for each participant's recall template.
 
-To determine which (cubes of) voxel responses reliably matched the video template, we correlated the upper triangle of the voxel correlation matrix for each cube with the upper triangle of the video template matrix~\citep{KrieEtal08b}.
-This yielded, for each participant, a single correlation value.
-We computed the average (Fisher $z$-transformed) correlation coefficient across participants.
-We used a permutation-based procedure to assess significance, whereby we re-computed the average correlations for each of 100 ``null'' video templates (constructed by circularly shifting the template by a random number of timepoints).
-(For each permutation, the same shift was used for all participants.)  We then estimated a $p$-value by computing the proportion of shifted correlations that were larger than the observed (unshifted) correlation.
-To create the map in Figure~\ref{fig:brainz}A we thresholded out any voxels whose correlation values fell below the 95\textsuperscript{th} percentile of the permutation-derived null distribution.
+To determine which (cubes of) voxel responses matched the video template, we correlated the upper triangle of the voxel correlation matrix for each cube with the upper triangle of the video template matrix~\citep{KrieEtal08b}.
+This yielded, for each participant, a voxelwise map of correlation values.
+We then performed a one-sample $t$-test on the distribution of (Fisher $z$-transformed) correlations at each voxel, across participants.
+This resulted in a value for each voxel (cube), describing how reliably its timecourse mirrored that of the video.
 
-We used a similar procedure to identify which voxels' responses reflected the recall templates.
+We further sought to ensure that our analysis identified regions where the activations’ temporal structure specifically reflected that of the video, rather than regions whose activity was simply autocorrelated at a width similar to the video template’s diagonal.
+To achieve this, we used a phase shift-based permutation procedure, wherein we circularly shifted the video’s topic trajectory by a random number of timepoints, computed the resulting ``null” video template, and re-ran the searchlight analysis, in full.
+(For each of the 100 permutations, the same random shift was used for all participants).
+We $z$-scored the observed (unshifted) result at each voxel against the distribution of permutation-derived ``null” results, and estimated a $p$-value by computing the proportion of shifted results that yielded larger values.
+To create the map in Figure~\ref{fig:brainz}A, we thresholded out any voxels whose similarity to the unshifted video’s structure fell below the 95\textsuperscript{th} percentile of the permutation-derived similarity results.
+
+We used an analogous procedure to identify which voxels' responses reflected the recall templates.
 For each participant, we correlated the upper triangle of the correlation matrix for each cube of voxels with their (time warped) recall correlation matrix.
-As in the video template analysis this yielded a single correlation coefficient for each participant.
+As in the video template analysis this yielded a voxelwise map of correlation coefficients per participant.
 However, whereas the video analysis compared every participant's responses to the same template, here the recall templates were unique for each participant.
-We computed the average $z$-transformed correlation coefficient across participants, and used the same permutation procedure we developed for the video responses to assess significant correlations.
-To create the map in Figure~\ref{fig:brainz}B we thresholded out any voxels whose correlation values fell below the 95\textsuperscript{th} percentile of the permutation-derived null distribution.
+As in the analysis described above, we $t$-scored the (Fisher $z$-transformed) voxelwise correlations, and used the same permutation procedure we developed for the video responses to ensure specificity to the recall timeseries and assign significance values.
+To create the map in Figure~\ref{fig:brainz}B we again thresholded out any voxels whose correspondence values fell below the 95\textsuperscript{th} percentile of the permutation-derived null distribution.
 

### 2020-01-03 code/scripts/embedding/embedding_submit.py
updated embedding scripts

@@ -11,17 +11,13 @@ from os.path import join as opj
 
 
 # ====== MODIFY ONLY THE CODE BETWEEN THESE LINES ======
-import numpy as np
 job_script = opj(os.path.dirname(os.path.realpath(__file__)), 'embedding_cruncher.py')
-
 embeddings_dir = opj(config['datadir'], 'embeddings')
-fig_dir = config['figdir']
+min_seed = 0
+max_seed = 100
 
 job_commands = list()
 job_names = list()
-
-min_seed = 0
-max_seed = 10000
 
 # order 1: recalls, video, avg recall
 # order 2: recalls, avg recall, video
@@ -31,22 +27,11 @@ max_seed = 10000
 # order 6: avg recalls, video, recalls
 
 for order in range(1, 7):
-    if not os.path.isdir(opj(embeddings_dir, f'order{order}')):
-        os.mkdir(opj(embeddings_dir, f'order{order}'))
-    if not os.path.isdir(opj(fig_dir, f'order{order}')):
-        os.mkdir(opj(fig_dir, f'order{order}'))
-    for division in range(10):
-        job_commands.append(f'{job_script} {order} {min_seed} {max_seed} {division}')
-        job_names.append(f'optimize_embedding_order{order}_{min_seed}_{max_seed}_{division}')
+    os.mkdir(opj(embeddings_dir, f'order{order}'))
 
-    # done = [int(os.path.splitext(file)[0][4:]) for file in os.listdir(opj(embeddings_dir, f'order{order}'))]
-    # seeds_todo = [s for s in seeds if s not in done]
-
-    # for seed in seeds_todo:
-    #     job_commands.append(f'{job_script} {order} {seed}')
-    #     job_names.append(f'optimize_embedding_order{order}_seed{seed}')
-
-
+    for seed in range(min_seed, max_seed + 1):
+        job_commands.append(f'{job_script} {order} {seed}')
+        job_names.append(f'optimize_embedding_order{order}_{seed}')
 
 # ====== MODIFY ONLY THE CODE BETWEEN THESE LINES ======
 

### 2020-01-03 code/scripts/embedding/embedding_collector_submit.py
wrote submission and job scripts for collector

@@ -1,0 +1,137 @@
+#!/usr/bin/python
+
+# create a bunch of job scripts
+from embedding_config import config
+from subprocess import call
+import os
+import socket
+import getpass
+import datetime as dt
+from os.path import join as opj
+
+
+# ====== MODIFY ONLY THE CODE BETWEEN THESE LINES ======
+job_script = opj(os.path.dirname(os.path.realpath(__file__)), 'embedding_collector.py')
+results_dir = opj(config['datadir'], 'results')
+if not os.path.isdir(results_dir):
+    os.mkdir(results_dir)
+
+min_seed = 0
+max_seed = 100
+
+job_commands = list()
+job_names = list()
+
+for order in range(1, 7):
+    job_commands.append(f'{job_script} {order}')
+    job_names.append(f'collect_embeddings_{order}')
+
+# ====== MODIFY ONLY THE CODE BETWEEN THESE LINES ======
+
+assert(len(job_commands) == len(job_names))
+
+
+# job_command is referenced in the run_job.sh script
+# noinspection PyBroadException,PyUnusedLocal
+def create_job(name, job_command):
+    # noinspection PyUnusedLocal,PyShadowingNames
+    def create_helper(s, job_command):
+        x = [i for i, char in enumerate(s) if char == '<']
+        y = [i for i, char in enumerate(s) if char == '>']
+        if len(x) == 0:
+            return s
+
+        q = ''
+        index = 0
+        for i in range(len(x)):
+            q += s[index:x[i]]
+            unpacked = eval(s[x[i]+1:y[i]])
+            q += str(unpacked)
+            index = y[i]+1
+        return q
+
+    # create script directory if it doesn't already exist
+    try:
+        os.stat(config['scriptdir'])
+    except:
+        os.makedirs(config['scriptdir'])
+
+    template_fd = open(config['template'], 'r')
+    job_fname = opj(config['scriptdir'], name)
+    new_fd = open(job_fname, 'w+')
+
+    while True:
+        next_line = template_fd.readline()
+        if len(next_line) == 0:
+            break
+        new_fd.writelines(create_helper(next_line, job_command))
+    template_fd.close()
+    new_fd.close()
+    return job_fname
+
+
+# noinspection PyBroadException
+def lock(lockfile):
+    try:
+        os.stat(lockfile)
+        return False
+    except:
+        fd = open(lockfile, 'w')
[…]

### 2020-01-06 code/scripts/load_cluster_output.py
wrote quick script for copying data from cluster

@@ -1,0 +1,40 @@
+import os
+import sys
+import spurplus
+from os.path import join as opj
+
+hostname, username, password = sys.argv[1:]
+
+datadir_local = '../../data/processed/'
+emb_path_remote = '/dartfs/rc/lab/D/DBIC/CDL/f0028ph/sherlock-embedding/data/optimized/embeddings.npy'
+emb_path_local = opj(datadir_local, 'embeddings.npy')
+
+sl_dir_remote = '/dartfs/rc/lab/D/DBIC/CDL/f0028ph/searchlight-sherlock/data/finished/'
+sl_vdir_local = opj(datadir_local, 'searchlight_video')
+sl_rdir_local = opj(datadir_local, 'searchlight_recall')
+
+if not os.path.isdir(sl_vdir_local):
+    os.mkdir(sl_vdir_local)
+if not os.path.isdir(sl_rdir_local):
+    os.mkdir(sl_rdir_local)
+
+with spurplus.connect_with_retries(hostname=hostname,
+                                   username=username,
+                                   password=password) as remote:
+                               # copy over embeddings
+                               remote.get(emb_path_remote, emb_path_local)
+                               # copy over searchlights
+                               for analysis in ['video', 'recall']:
+                                   src_dir = opj(sl_dir_remote, f'searchlight_{analysis}')
+                                   dest_dir = opj(datadir_local, f'searchlight_{analysis}')
+                                   perm_dir = opj(src_dir, 'perms')
+                                   for sub in range(1, 18):
+                                       # unshifted data
+                                       src_path = opj(src_dir, f'sub{sub}.npy')
+                                       dest_path = opj(dest_dir, f'sub{sub}.npy')
+                                       remote.get(src_path, dest_path)
+                                   # permuted data
+                                   for perm in range(100):
+                                       perm_src_path = opj(perm_dir, f'perm{perm}.nii.gz')
+                                       perm_dest_path = opj(dest_dir, f'perm{perm}.nii.gz')
+                                       remote.get(perm_src_path, perm_dest_path)

### 2020-01-06 paper/main.tex
fixed memlab.bib path
updated wordle figure text

@@
 This yields a single correlation coefficient for each video event, describing how closely participants' recalls of the event tended to reliably capture its content (Fig.~\ref{fig:topics}A).
-(We also examined how different comparisons between each video event's topic vector and the corresponding recall event topic vectors related to hand-annotated characterizations of memory performance; see \textit{Supporting Information}).
 Given this summary of which events were recalled reliably (or not), we next asked whether the better-remembered or worse-remembered events tended to reflect particular topics.
@@
 To visualize the result, we created a ``wordle'' image~\citep{MuelEtal18} where words weighted more heavily by better-remembered topics appear in a larger font (Fig.~\ref{fig:topics}B, green box).
-Across the full video, content that reflected topics necessary to convey the central focus of the video (e.g., the names of the two main characters, ``Sherlock" and ``John", and the address of a major recurring location, ``221b Baker Street") were best remembered.
+Across the full video, content that reflected topics necessary to convey the central focus of the video (e.g., the names of the two main characters, ``Sherlock" and ``John", and the address of a major recurring location, ``221B Baker Street") were best remembered.
 An analogous analysis revealed which themes were poorly remembered.
 Here in computing the weighted average over events' topic vectors, we weighted each event in \textit{inverse} proportion to how well it was remembered (Fig.~\ref{fig:topics}B, red box).
-The least well-remembered video content reflected information not necessary to conveying the video's ``gist," such as the names of relatively minor characters (e.g., ``Mike," ``Jeffrey," ``Molly," and ``Jimmy") and locations (e.g., ``St.
-Bartholomew's Hospital").
+The least well-remembered video content reflected information not necessary to conveying the video's ``gist," such as the proper names of relatively minor characters (e.g., ``Mike," ``Molly," and ``Lestrade") and locations (e.g., ``St.
+Bartholomew's Hospital"), as well as the brief, animated clip participants viewed at the beginning of each of the two scan session (involving ``singing" ``cartoon" characters).
 
@@
 Here, for each of the three best- and worst-remembered video events, we have constructed two wordles: one from the original video event's topic vector (left) and a second from the average recall topic vector for that event (right).
-The three best-remembered events (circled in green) correspond to scenes important to the central plot-line (Sherlock and John meeting, Sherlock and John chasing the killer, and the killer calling spying on John in a phone booth).
-Meanwhile, the three worst-remembered events (circled in red) reflect various side-stories (John talking to his therapist about the war, a soon-to-be-victim's affair with his assistant, and another soon-to-be-victim leaving a party with his friend) that are not essentially to summarizing the video's narrative.
-
-%Events that reflected topics weighting heavily on characters like ``Sherlock'' and ``John'' (the main characters) and locations like ``221b Baker Street'' (a major recurring location and the address of the flat that Sherlock and John share) were best remembered.
-An analogous analysis revealed which themes were poorly remembered.
-Here in computing the weighted average over events' topic vectors, we weighted each event in \textit{inverse} proportion to how well it was remembered (Fig.~\ref{fig:topics}B, red box).
-This revealed that events with relatively minor characters such as ``Mike,'' ``Jeffrey,'' and ``Molly,'' as well as less-integral plot locations (e.g., ``hospital'' and ``office'') were least well-remembered.
-This suggests that what is retained in memory are the major plot elements (i.e., the overall shape of what happened), whereas the more minor details are prone to pruning.
-
-% In addition to constructing overall summaries, assessing the video and recall topic vectors from individual events can provide further insights.
-Specifically, for any given event we can construct two wordles: one from the original video event's topic vector, and a second from the average topic vectors produced by all participants' recalls of that event.
-We can then examine those wordles visually to gain an intuition for which aspects of the video event were recapitulated in participants' recalls.
-Several example wordles are displayed in Figure~\ref{fig:topics}C (wordles from the three best-remembered events are circled in green; wordles from the three worst-remembered events are circled in red).
-Using wordles to visually compare the topical content of each video event and the (average) corresponding recall event reveals the specific content from the specific events that is reliably retained in the transformation into memory (green events) or not (red events).
+The three best-remembered events (circled in green) correspond to scenes important to the central plot-line: a mysterious figure spying on John in a phone booth; John and Sherlock discussing the murders in their apartment; and Sherlock laying a trap to catch the murderer.
+Meanwhile, the three worst-remembered events (circled in red) reflect scenes that are non-essential to summarizing the narrative's structure: the two appearances of singing cartoon characters; Molly watching as Sherlock beats a corpse in the morgue; and Sherlock noticing evidence of Anderson's and Donovan's affair.
 
@@
 This general approach for discovering a shared low-dimensional embedding for a collections of high-dimensional observations follows \cite{HeusEtal18a}.
+Note: for further details on how we created this low-dimensional embedding space, see \textit{Supporting Information}.
 % ------ NOTE: ------
@@
 \bibliography{../../CDL-bibliography/memlab}
-%\bibliography{CDL-bibliography/memlab}
+% \bibliography{CDL-bibliography/memlab}
 

### 2020-01-06 paper/main.tex
updated embedding section

@@
 In Figure~\ref{fig:trajectory}B, we present an analysis aimed at characterizing locations in topic space that different participants move through in a consistent way (via their recall topic trajectories).
-The two-dimensional topic space used in our visualizations (Fig.~\ref{fig:trajectory}) comprised a 9x9 (arbitrary units) square.
-We divided this space into a grid of vertices spaced 0.25~units apart.
-For each vertex, we examined the set of line segments formed by connecting each pair successively recalled events, across all participants, that passed within 0.5 units.
+The two-dimensional topic space used in our visualizations (Fig.~\ref{fig:trajectory}) comprised a 60 x 60 (arbitrary units) square.
+We tiled this space with a 50 x 50 grid of evenly spaced vertices, and defined a circular area centered on each vertex whose radius was two times the distance between adjacent vertices (i.e., 2.4 units).
+For each vertex, we examined the set of line segments formed by connecting each pair successively recalled events, across all participants, that passed through this circle.
 We computed the distribution of angles formed by those segments and the $x$-axis, and used a Rayleigh test to determine whether the distribution of angles was reliably ``peaked'' (i.e., consistent across all transitions that passed through that local portion of topic space).
-To create Figure~\ref{fig:trajectory}B we drew an arrow originating from each grid vertex, pointing in the direction of the average angle formed by line segments that passed within 0.5 units.
+To create Figure~\ref{fig:trajectory}B we drew an arrow originating from each grid vertex, pointing in the direction of the average angle formed by line segments that passed within its circular radius.
 We set the arrow lengths to be inversely proportional to the $p$-values of the Rayleigh tests at each vertex.
-Specifically, for each vertex we converted all of the angles of segments that passed within 0.5 units to unit vectors, and we set the arrow lengths at each vertex proportional to the length of the (circular) mean vector.
+Specifically, for each vertex we converted all of the angles of segments that passed within 2.4 units to unit vectors, and we set the arrow lengths at each vertex proportional to the length of the (circular) mean vector.
 We also indicated any significant results ($p < 0.05$, corrected using the Benjamani-Hochberg procedure) by coloring the arrows in blue (darker blue denotes a lower $p$-value, i.e., a longer mean vector); all tests with $p \geq 0.05$ are displayed in gray and given a lower opacity value.

### 2020-01-06 paper/supporting_information.tex
resized figs to avoid covering page numbers
updated title and author info to match updates in main

--- 2019-06-13 paper/supporting_information.tex
@@
 
-\title{\textit{Supporting Information for}: How is experience transformed into memory?}
+\title{\textit{Supporting Information for}: Memory for television episodes preserves event content while introducing new across-event similarities}
 \author{Andrew C.
-Heusser, Paxton C.
-Fitzpatrick, and Jeremy R.
-Manning\\Department of Psychological and Brain Sciences\\Dartmouth College, Hanover, NH 03755, USA\\Corresponding author: jeremy.r.manning@dartmouth.edu}
+Heusser\textsuperscript{1, 2}, Paxton C.
+Fitzpatrick\textsuperscript{1}, and Jeremy R.
+Manning\textsuperscript{1, *}\\\textsuperscript{1}Department of Psychological and Brain Sciences\\Dartmouth College, Hanover, NH 03755, USA\\\textsuperscript{2}Akili Interactive\\Boston, MA 02110\\\textsuperscript{*}Corresponding author: jeremy.r.manning@dartmouth.edu}
 
@@
 \centering
-  \includegraphics[width=\textwidth]{figs/trajectory_wasserstein}
-  \caption{\small \textbf{Trajectories using Wasserstein distance for choosing $K$.}  We replicated the trajectory analysis using Wasserstein distance, a parameter-free procedure for choosing $K$.
-Overall, the pattern of findings is quite similar to our main approach, but resulted in a smaller number of events.}
-  \label{fig:trajectory_wasserstein}
+\includegraphics[width=.9\textwidth]{figs/k_optimization}
+\caption{\small \textbf{Video and recall trajectory $K$-optimization functions.}  We selected the optimal $K$-value for the video and each recall trajectory, using the formula described in \textit{Methods}.
+This computation resulted in a curve for each trajectory, describing the regularized ratio of the average within-event topic vector correlation to the average across-event topic vector correlation, as a function of $K$.}
+\label{fig:k_optimization}
 \end{figure}
+
+\
 

### 2020-01-06 paper/supporting_information.tex
updated feature importance text

@@
 
-The optimized model converged on 27 unique topics that were assigned non-zero weights over the course of the video.
+The optimized model converged on 32 unique topics that were assigned non-zero weights over the course of the video.
 We provide a list of the top ten highest-weighted words from each topic in Figure~\ref{fig:topics}.
@@
 We created temporal correlation matrices for each trajectory (using the topic proportions matrices) and correlated the upper triangles of each impoverished trajectory with the original feature-complete trajectory.
-Observing a lower correlation between an impoverished trajectory (holding out a particular feature) and the feature-complete trajectory would suggest that the given feature played a more prominent role in shaping the structure of the feature-complete trajectory.
-We found that hand-annotated narrative details provided the most structure to the feature-complete trajectory, whereas transcriptions of onscreen text provided the least structure (Fig.~\ref{fig:feature-importance}A).
+Observing a lower correlation between an impoverished trajectory (holding out a particular feature) and the feature-complete trajectory would suggest that the given feature played a more prominent role in shaping the temporal structure of the feature-complete trajectory.
+We found that hand-annotated scene locations provided the most structure to the feature-complete trajectory, whereas the name of the character(s) in focus for each shot provided the least structure (Fig.~\ref{fig:feature-importance}A).
 
@@
 
-We also carried out an analysis of which annotated features tended to shape aspects of the video topic trajectory that were preserved in participants' recalls.
+We also carried out an analysis of which annotated features tended to shape aspects of the video topic trajectory's structure that were preserved in participants' recalls.
 Specifically, we computed the timepoint-by-timepoint correlation matrix of the video topic trajectory, and correlated its upper triangle with that of the timepoint-by-timepoint correlation matrices of each participant's recall topic trajectory (resampled using linear interpolation to have the same number of timepoints as the video trajectory).
@@
 We then repeated this analysis with each annotated feature held out in turn.
-Observing a lower correlation between the video and recall trajectories (when a given feature was held out) would indicate that the feature tends to be preserved in participants' recalls.
-We found that hand-annotated narrative details were the most preserved type of feature, whereas information about the camera angle tended not to influence participants' recalls (Fig.~\ref{fig:feature-importance}B).
+Observing a lower correlation between the video and recall trajectories (when a given feature was held out) would indicate that participants utilize changes in that feature's content to discriminate between sections of the video when organizing their recalls.
+We found that hand-annotated narrative details were the most heavily utilized type of feature, whereas changes in which character was speaking tended not to impact participants' recall structures (Fig.~\ref{fig:feature-importance}B).
 
 Next, we wondered how the different types of features might relate.
-For example, knowing which characters are on screen during a given scene may also provide information about which characters are speaking.
-We computed video topic trajectories for each feature in turn, and then compared the temporal correlation matrices of all pairs of features.
+For example, knowing which character is in focus during a given scene may also provide information about which character is speaking.
+We computed video topic trajectories for each feature in turn, and then compared the upper triangles of the temporal correlation matrices of all pairs of features.
 This provided additional confirmation that the shape of the full trajectory (including all types of features) was largely driven by narrative details.
@@
 
-% \section*{Additional analyses of memory performance}
-
-% \subsection*{Naturalistic extensions of classic list-learning analyses}
-% In traditional list-learning experiments, participants view a list of items (e.g., words) and then recall the items later.
-Our video-recall event matching approach affords us the ability to analyze memory in a similar way.
-The video and recall events can be treated analogously to studied and recalled ``items'' in a list-learning study.
-We can then extend classic analyses of memory performance and dynamics (originally designed for list-learning experiments) to the more naturalistic video recall task used in our study.
-
-% Perhaps the simplest and most widely used measure of memory performance is \textit{accuracy}-- i.e., the proportion of studied (experienced) items (in this case, the 34 video events) that the participant later remembered.
-\cite{ChenEtal17} developed a human rating system whereby the quality of each participant's memory was evaluated by an independent rater.
-We found a strong across-participants correlation between these independant ratings and the overall number of events that our HMM approach identified in participants' recalls (Pearson's $r(15) = 0.67, p = 0.003$).
-
-% As described below, we next considered three more nuanced measures of the memory performance and dynamics that are typically associated with list-learning studies.
-We also provide a software package, \texttt{Quail}, for carrying out these analyses~\citep{HeusEtal17b}.
-
-% \begin{figure}[p!]
-% \centering
-% \includegraphics[width=1\textwidth]{figs/list_learning}
-% \caption{\small \textbf{Naturalistic extensions of classic list-learning memory analyses.} \textbf{A.} The probability of first recall as a function of the serial position of the event in the video.
-\textbf{B}.
-The probability of recalling each event, conditioned on having most recently recalled the event \textit{lag} events away in the video.
-\textbf{C.} The proportion of participants who recalled each event, as a function of the serial position of the events in the video.
-All panels: error bars denote bootstrap-estimated standard error of the mean.}
-% \label{fig:list-learning}
-% \end{figure}
-
-% \paragraph{Probability of first recall (PFR).}  PFR curves~\citep{WelcBurn24, PostPhil65, AtkiShif68} reflect the probability that an item will be recalled first as a function of its serial position during encoding.
-To carry out this analysis, we initialized a number-of-participants (17) by number-of-video-events (34) matrix of zeros.
-Then for each participant, we found the index of the video event that was recalled first (i.e., the video event whose topic vector was most strongly correlated with that of the first recall event) and filled in that index in the matrix with a 1.
-Finally, we averaged over the rows of the matrix, resulting in a 1 by 34 array representing the proportion of participants that recalled an event first, as a function of the order of the event's appearance in the video (Fig.~\ref{fig:list-learning}A).
-
-% \paragraph{Lag conditional probability curve (lag-CRP).} The lag-CRP curve~\citep{Kaha96} reflects the probability of recalling a given event after the just-recalled event, as a function of their relative positions (or \textit{lag}).
-In other words, a lag of 1 indicates that a recalled event came immediately after the previously recalled event in the video, and a lag of -3 indicates that a recalled event came 3 events before the previously recalled event.
-For each recall transition (following the first recall), we computed the lag between the current recall event and the next recall event, normalizing by the total number of possible transitions.
-This yielded a number-of-participants (17) by number-of-lags (-33 to +33; 67 lags total) matrix.
-We averaged over the rows of this matrix to obtain a group-averaged lag-CRP curve (Fig.~\ref{fig:list-learning}B).
-
-% \paragraph{Serial position curve (SPC).} SPCs~\citep{Murd62a} reflect the proportion of participants that remember each item as a function of their serial position during encoding.
-We initialized a number-of-participants (17) by number-of-video-events (34) matrix of zeros.
-Then, for each recalled event, for each participant, we found the index of the video event that the recalled event most closely matched (via the correlation between the events' topic vectors) and entered a 1 into that position in the matrix (i.e., for the given participant and event).
-This resulted in a matrix whose entries indicated whether or not each event was recalled by each participant (depending on whether the corresponding entires were set to one or zero).
-Finally, we averaged over the rows of the matrix to yield a 1 by 34 array representing the proportion of participants that recalled each event as a function of the order of the event's appearance in the video (Fig.~\ref{fig:list-learning}C).
-
-% \paragraph{Temporal clustering scores.} Temporal clustering refers to the extent to which participants group their recall responses according to encoding position~\citep{PolyEtal09}.
-For instance, if a participant recalled the video events in the exact order they occurred (or in exact reverse order), this would yield a score of 1.
-If a participant recalled the events in random order, this would yield an expected score of 0.5.
-For each recall event transition (and separately for each participant), we sorted all not-yet-recalled events according to their absolute lag (i.e., distance away in the video).
-We then computed the percentile rank of the next event the participant recalled.
-We averaged these percentile ranks across all of the participant's recalls to obtain a single temporal clustering score for the participant (mean: 0.808, SEM: 0.022).
-Overall, we found that participants with higher temporal clustering scores also tended to recall more events (Pearson's $r(15) = 0.62, p = 0.007$).
-
-% \paragraph{Semantic clustering scores.} Semantic clustering measures the extent to which participants clustered their recall responses according to semantic similarity~\citep{PolyEtal09}.
-Here, we used the topic vectors for each event as a proxy for its semantic content.
-Thus, the similarity between the semantic content for two events can be computed by correlating their respective topic vectors.
-For each recall event transition, we sorted all not-yet-recalled events according to how correlated the topic vector \textit{of the closest-matching video event} was to the topic vector of the closest-matching video event to the just-recalled event.
-We then computed the percentile rank of the observed next recall.
-We averaged these percentile ranks across all of the participant's recalls to obtain a single semantic clustering score for the participant (mean: 0.813, SEM: 0.022).
-We found that participants who exhibited stronger semantic clustering scores overall remembered more video events (Pearson's $r(15) = 0.55, p = 0.02$).
-
-% \subsection*{Novel memory measures afforded by our framework}
-% To quantify the similarity between the video topic trajectory and individual recall topic trajectories, we considered several novel metrics.
-First, we tested whether each participant's recall trajectory matched the video trajectory in a general sense.
-For each participant we filtered the video trajectory to only include the events that the participant remembered.
-We then computed the root mean squared difference (RMSD) between the remaining video events and the (closest-matching) recalled events.
-For example, if the topic vectors for a participant's recall event topic vectors matched the corresponding video event topic vectors exactly (and in order), the expected RMSD for those events would be 0.
-However, if the participant's recall events did not perfectly match the video events, or if they were out of order, then the RMSD would be greater than 0.
-To assess the significance of the match between the video and recall trajectories, we carried out a permutation procedure whereby, for each of 10000 repetitions, we circularly shifted the recall trajectories (in time) by a random amount and then re-computed the RMSD each time.
-This yielded a distribution of ``null'' RMSD values for each participant.
-The observed RMSD values reached significance (i.e., $p < 0.05$, reflecting that more than 95\% of the null RMSD values were greater than the observed RMSD value) for nine of the participants (3, 4, 8--13, and 17).
-(For the remaining participants this test yielded $0.05 \leq p < 0.25$.)  The observed RMSD values were also reliably correlated with hand-annotated memory performance across participants (Pearson's $r(15) = -0.57, p = 0.016$).
-In other words, a closer match between the video and recall topic trajectories was related to better overall recall performance.
-
-% \paragraph*{Precision.}
-% We next tested whether participants who recalled more events were also more \textit{precise} in their recollections.
-For each participant, we computed the correlation between the topic vectors for each recall event and that of its closest-matching video event (only for the events which they recalled).
-We defined the precision as the average video-recall correlation across all of the events a participant recalled.
-We found a strong correlation between hand-annotated memory performance and precision, suggesting that participants who remembered more events also remembered them more veridically (Pearson's $r(15) = 0.74, p = 0.0006$).
-
-% \paragraph*{Distinctiveness.}
-% We also considered the \textit{distinctiveness} of each recalled event.
-That is, how uniquely a recalled event's topic vector matched a given video event topic vector, versus the topic vectors for the other video events.
-We hypothesized that participants with high memory performance might describe each event in a more distinctive way (relative to those with lower memory performance who might describe events in a more general way).
-To test this hypothesis we define a distinctiveness score for each recalled event as
-% \[
-%   d(\mathrm{event}) = 1 - \bar{c}(\mathrm{event}),
-% \]
-% where $\bar{c}(\mathrm{event})$ is the average correlation between the given recalled event's topic vector and the topic vectors from all video events \textit{except} the best-matching video event.
-We then averaged these distinctiveness scores across all of the events recalled by the given participant.
-We found that participants with higher average distinctiveness scores tended to also have better hand-annotated memory performance (Pearson's $r(15) = 0.8, p = 0.0001$).
-
-% NOTE: REMOVE THIS?
-% \paragraph*{Other order effects.}
-% We tested whether participants with better memory performance were also more likely to remember the events in order.
-For each participant, we computed the Spearman rank correlation between the order of events that the participant recalled and the order the events actually occurred in the video (considering in the analysis only the events that the participant recalled).
-Participants who recalled more events also recalled more of them in order (Pearson's $r(15) = 0.5, p = 0.04$).
-In summary, we found that better memory performance was associated with more precise, distinctive, and ordered recalls.
-
-%\section*{Participant-level figures referenced in the main text}
-
-% Supporting information
+\section*{Participant-level figures referenced in the main text}
 
@@
 \includegraphics[width=.9\textwidth]{figs/k_optimization}
-\caption{\small \textbf{Video and recall trajectory $K$-optimization functions.}  We selected the optimal $K$-value for the video and each recall trajectory, using the formula described in \textit{Methods}.
-This computation resulted in a curve for each trajectory, describing the regularized ratio of the average within-event topic vector correlation to the average across-event topic vector correlation, as a function of $K$.}
+\caption{\small \textbf{Video and recall trajectory \textit{K}-optimization functions.}  We selected the optimal $K$-value for the video and each recall trajectory, using the formula described in \textit{Methods}.
+This computation resulted in a curve for each trajectory, describing the Wasserstein distance between the distributions of within-event and across-event topic vector correlations, as a function of $K$.}
 \label{fig:k_optimization}
@@
 \renewcommand{\refname}{Supplemental references}
-\bibliography{memlab}
+\bibliography{../../CDL-bibliography/memlab}
 

### 2020-01-07 paper/main.tex
removed refs to old supplemental figs
updated methods section on embedding

@@
 \newcommand{\featureimportance}{S3}
-% \newcommand{\listlearning}{S4}
 \newcommand{\corrmats}{S4}
 \newcommand{\matchmats}{S5}
-\newcommand{\kcorrs}{S6}
-\newcommand{\kopt}{S7}
-\newcommand{\wasserstein}{S8}
+\newcommand{\kopt}{S6}
 
@@
 However, it is difficult to gain deep insights into that content solely by examining the topic proportion matrices (e.g., Figs.~\ref{fig:model}A, D) or the corresponding correlation matrices (Figs.~\ref{fig:model}B, E, \corrmats).
-To visualize the time-varying high-dimensional content in a more intuitive way~\citep{HeusEtal18a} we projected the topic proportions matrices onto a two-dimensional space using Uniform Manifold Approximation and Projection~\citep[UMAP; ][]{McInHeal18}.
+To visualize the time-varying high-dimensional content in a more intuitive way~\citep{HeusEtal18a} we projected the topic proportions matrices onto a two-dimensional space using Uniform Manifold Approximation and Projection~\citep[UMAP; ][]{McInEtal18}.
 In this lower-dimensional space, each point represents a single video or recall event, and the distances between the points reflect the distances between the events' associated topic vectors (Fig.~\ref{fig:trajectory}).
@@
 \subsubsection*{Visualizing the video and recall topic trajectories}
-We used the UMAP algorithm~\citep{McInHeal18} to project the 100-dimensional topic space onto a two-dimensional space for visualization (Figs.~\ref{fig:trajectory}, \ref{fig:topics}).
-To ensure that all of the trajectories were projected onto the \textit{same} lower dimensional space, we computed the low-dimensional embedding on a ``stacked'' matrix created by vertically concatenating the events-by-topics topic proportions matrices for the video and all 17 participants' recalls.
+We used the UMAP algorithm~\citep{McInEtal18} to project the 100-dimensional topic space onto a two-dimensional space for visualization (Figs.~\ref{fig:trajectory}, \ref{fig:topics}).
+Importantly, to ensure that all of the trajectories were projected onto the \textit{same} lower dimensional space, we computed the low-dimensional embedding on a ``stacked'' matrix created by vertically concatenating the events-by-topics topic proportions matrices for the video, across-participants average recalls and all 17 individual participants' recalls.
 We then divided the rows of the result (a total-number-of-events by two matrix) back into separate matrices for the video topic trajectory and the trajectories for each participant's recalls (Fig.~\ref{fig:trajectory}).
@@
 Conceptualization: A.C.H.
-and J.R.M.; Methodology: A.C.H.
+and J.R.M.; Methodology: A.C.H., P.C.F.
 and J.R.M.; Software: A.C.H., P.C.F.

### 2020-01-07 paper/supporting_information.tex
WIP embedding optimization section

@@
 \usepackage{setspace}
+\usepackage{placeins}
 %\doublespacing
@@
 \centering
-\includegraphics[width=0.75\textwidth]{figs/topic_words}
+\includegraphics[width=0.65\textwidth]{figs/topic_words}
 \caption{\small \textbf{Topics discovered in \textit{Sherlock}.} We applied a topic model to hand-annotated information about 1000 scenes spanning the 45 minute episode.
@@
 \end{figure}
+\FloatBarrier
 
@@
 
-\begin{figure}[p!]
+\begin{figure}[t]
 \centering
@@
 Other details, such as the presence or absence of music, led to very different topic trajectories (Fig.~\ref{fig:feature-importance}C).
+\FloatBarrier
+
+\subsection*{Creating a low-dimensional embedding space}
+Figures~5 and 6C in the main text display two-dimensional projections of the 100-dimensional topic trajectories for the video (5A, 6C), average recall (5B), and each individual's recall (5C, 6C).
+We created these embeddings using the Uniform Manifold Approximation and Projection algorithm \citep[UMAP;][]{McInEtal18} called from our high-dimensional visualization and text analysis software, \texttt{HyperTools}~\citep{HeusEtal18a}.
+An advantage of the UMAP algorithm over comparable manifold learning techniques (such as $t$-SNE) is that UMAP explicitly attempts to preserve the global structure of the data \citep{McInEtal18,BechEtal19} by constructing a space where distance on the manifold is standard Euclidean distance, with respect to the global coordinate system.
+This was important in our use case, as we wanted to visualize both the evolving structure of the video and the spatial relationships between presented and recalled content.
+
+UMAP achieves a balance between representing local and global structure via a subset of its hyper-parameters: \texttt{n\_neighbors} , \texttt{spread}, and \texttt{min\_dist}.
+The \texttt{n\_neighbors} hyper-parameter ($K$) denotes the number of nearest neighbors to consider in constructing the high-dimensional fuzzy simplicial set for each datapoint.
+\texttt{Spread} ($\gamma$) and \texttt{min\_dist} ($\delta$) function together to create the differentiable decay curve used to approximate the injective function used to map between high- and low-dimensional fuzzy simplicial sets.
+In essence, \texttt{min\_dist} determines the degree to which nearby points are clustered or expanded, relative to to the overall \texttt{spread}.
+
+To optimize the manifold space shown in Figures~5 and 6C, we performed a grid search over pre-specified values of these hyper-parameters, as well as a pre-specified set of random states ($\tau$).
+Additionally, as described in \textit{Methods}, we ensured the video and recall events were projected onto the \textit{same} low-dimensional manifold by fitting the embedding model to a stacked matrix of
 

### 2020-01-08 paper/supporting_information.tex
wrote equations for embeddings grid search

@@
 \newcommand{\argmax}{\mathop{\mathrm{argmax}}\limits}
+\newcommand{\argmin}{\mathop{\mathrm{argmin}}\limits}
 
@@
 \includegraphics[width=1\textwidth]{figs/parameter_search}
-\caption{\small \textbf{Optimizing topic model parameters.}  We performed a grid search over video sliding window length ($\omega \in \{5, 10, 25, 50, 100 \}$), recall sliding window length ($\rho \in \{5, 10, 25, 50, 100 \}$, and number of topics ($K \in \{5, 10, 25, 50, 100 \}$.
+\caption{\small \textbf{Optimizing topic model parameters.}  We performed a grid search over video sliding window length ($\omega \in \{5, 10, 25, 50, 100 \}$), recall sliding window length ($\rho \in \{5, 10, 25, 50, 100 \}$), and number of topics ($K \in \{5, 10, 25, 50, 100 \}$).
 The reported correlations are between per-subject video-recall trajectory correlations and per-subject hand-annotated memory performance ratings.}
@@
 
-To optimize the manifold space shown in Figures~5 and 6C, we performed a grid search over pre-specified values of these hyper-parameters, as well as a pre-specified set of random states ($\tau$).
-Additionally, as described in \textit{Methods}, we ensured the video and recall events were projected onto the \textit{same} low-dimensional manifold by fitting the embedding model to a stacked matrix of
+Two other parameters ultimately affect this balance between preserving local and global structure: the seed ($\tau$) for the (pseudo-)random number generator, and the order of the observations (i.e., trajectories) to be embedded ($\phi$).
+As described in \textit{Methods}, we ensured the video and recall events were projected onto the \textit{same} low-dimensional manifold by fitting the embedding model to a stacked matrix of all video, average recall, and individuals' recall events.
+After initializing the low-dimensional simplicial set (by default, using a spectral embedding of the high-dimensional simplicial set's fuzzy 1-skeleton), UMAP optimizes the embedding using stochastic gradient descent with cross-entropy as a cost function.
+During optimization, indices of the data are sampled at random, and thus local minimum reached by the optimization is dependent on both the state of the RNG and the sequence of observations.
+
+We performed a grid search over pre-specified values of these hyper-parameters, and optimized the manifold space for visualization based on two criteria: First, that the 2D embedding of the video trajectory should reflect its original 100-dimensional structure as faithfully as possible.
+Second, that the path traversed by the video trajectory should intersect itself as few times as possible.
+The first criteria helps promote the ability to gain (albeit fuzzy) intuitions about similarities and differences between sections of video content based on their locations in the embedding space.
+The second criteria was motivated by the low off-diagonal values in the video trajectory's temporal correlation matrix (suggesting that the same topic-space coordinates should not be revisited; see Figure~2A in the main text) and the inability to accurately describe the consistency of participants' transitions through topic space at locations where those transitions were consistent, but occurred in multiple, orthogonal directions (see \textit{Methods} for analysis details).
+We formalized this optimization as the combination of values that satisfied
+\[
+\argmax_{\left\{K, \gamma, \delta, \tau, \varphi~\in~E~\mathrm{|}~\Phi\left(K, \gamma, \delta, \tau, \varphi \right) \right\}} \left[\mathrm{corr}\left(\Upsilon\left(\xi_{K, \gamma, \delta, \tau, \varphi}\right),~\Upsilon\left(\chi\right)\right)\right],~\mathrm{where}
+\]
+\[
+\Phi\left(K, \gamma, \delta, \tau, \varphi \right) = \argmin_{K, \gamma, \delta, \tau, \varphi} \left[\Gamma\left(\xi_{K, \gamma, \delta, \tau, \varphi}\right)\right],
+\]
+$\xi$ is the video's trajectory through the manifold space; $\chi$ is the original, 100-dimensional video trajectory; $\Upsilon$ is a condensed matrix of pairwise distances between event vectors (computed using correlation distance in the original topic space and Euclidean distance in the manifold space); $\mathrm{corr}\left(\Upsilon\left(\xi\right), \Upsilon\left(\chi\right)\right)$ is the correlation between the sets of pairwise distances, and $\Gamma$ is the number of instances in which lines drawn between consecutive video event embeddings intersect.
+We searched over the hyper-parameter values
+\[
+K \in \{
 

### 2020-01-08 paper/supporting_information.tex
finished embedding supporting info section

@@
 
-\begin{figure}[p!]
+\begin{figure}[]
 \centering
@@
 \end{figure}
-\FloatBarrier
+%\FloatBarrier
 
@@
 To determine the contribution of each feature to the structure of the video topic proportions, we conducted a ``leave one out'' analysis.
-Specifically, we compared the original video topic trajectory (created using all hand-annotated features from the 1000 hand-annotated scenes spanning the \textit{Sherlock} episode; see \textit{Methods} for a full list of features) with video trajectories created using all but one type of feature.
+Specifically, we compared the original video topic trajectory (created using all hand-annotated features from the 998 hand-annotated scenes spanning the \textit{Sherlock} episode; see \textit{Methods} for a full list of features) with video trajectories created using all but one type of feature.
 We created temporal correlation matrices for each trajectory (using the topic proportions matrices) and correlated the upper triangles of each impoverished trajectory with the original feature-complete trajectory.
@@
 
-\begin{figure}[t]
+\begin{figure}[]
 \centering
@@
 Other details, such as the presence or absence of music, led to very different topic trajectories (Fig.~\ref{fig:feature-importance}C).
-\FloatBarrier
+%\FloatBarrier
 
@@
 After initializing the low-dimensional simplicial set (by default, using a spectral embedding of the high-dimensional simplicial set's fuzzy 1-skeleton), UMAP optimizes the embedding using stochastic gradient descent with cross-entropy as a cost function.
-During optimization, indices of the data are sampled at random, and thus local minimum reached by the optimization is dependent on both the state of the RNG and the sequence of observations.
+During optimization, indices of the data are sampled at random, and thus local minimum reached by the optimization is dependent on both the state of the RNG and the sequence in which observations are concatenated.
 
@@
 $\xi$ is the video's trajectory through the manifold space; $\chi$ is the original, 100-dimensional video trajectory; $\Upsilon$ is a condensed matrix of pairwise distances between event vectors (computed using correlation distance in the original topic space and Euclidean distance in the manifold space); $\mathrm{corr}\left(\Upsilon\left(\xi\right), \Upsilon\left(\chi\right)\right)$ is the correlation between the sets of pairwise distances, and $\Gamma$ is the number of instances in which lines drawn between consecutive video event embeddings intersect.
-We searched over the hyper-parameter values
-\[
-K \in \{
+The sets of hyper-parameter values we searched over comprised: $K \in \{10x \in \mathbb{Z}~|~10 < x <  22\} \cup \{161\}$ (a range roughly centered on half the total number of events, 161, in order to balance representations of local and global structure); $\gamma \in \{1, 3, 5, 7, 9\}$; $\delta \in \{0.1, 0.3, 0.5, 0.7\}$; $\tau \in \{x \in \mathbb{Z}~|~0 < x < 101\}$; and $\phi \in {S\choose3},~\mathrm{where}~S=\{\mathrm{video~events,~average~recall~events, individual~recall~events}\}$.
+The optimal parameters (that yielded $\Phi=0$) were $K=170$, $\gamma=7$, $\delta=0.7$, $\tau=41$, and $\varphi$ as a the sequences of average recall events, video events, and individuals' recall events, vertically concatenated.
 
+\FloatBarrier
 \section*{Participant-level figures referenced in the main text}
@@
 
-\
+\FloatBarrier
 

### 2020-01-08 paper/supporting_information.tex
minor updates

@@
 We performed a grid search over pre-specified values of these hyper-parameters, and optimized the manifold space for visualization based on two criteria: First, that the 2D embedding of the video trajectory should reflect its original 100-dimensional structure as faithfully as possible.
-Second, that the path traversed by the video trajectory should intersect itself as few times as possible.
-The first criteria helps promote the ability to gain (albeit fuzzy) intuitions about similarities and differences between sections of video content based on their locations in the embedding space.
-The second criteria was motivated by the low off-diagonal values in the video trajectory's temporal correlation matrix (suggesting that the same topic-space coordinates should not be revisited; see Figure~2A in the main text) and the inability to accurately describe the consistency of participants' transitions through topic space at locations where those transitions were consistent, but occurred in multiple, orthogonal directions (see \textit{Methods} for analysis details).
-We formalized this optimization as the combination of values that satisfied
+Second, that the path traversed by the embedded video trajectory should intersect itself a minimal number of times.
+The first criteria helps bolster the validity of visual intuitions about relationships between sections of video content, based on their locations in the embedding space.
+The second criteria was motivated by the observed low off-diagonal values in the video trajectory's temporal correlation matrix (suggesting that the same topic-space coordinates should not be revisited; see Figure~2A in the main text) and the inability to accurately describe the consistency of participants' transitions through topic space at locations where those transitions frequently occurred in multiple, orthogonal directions (see \textit{Methods} for analysis details).
+We formalized this optimization as the combination of hyper-parameter values that satisfied
 \[
@@
 \]
-$\xi$ is the video's trajectory through the manifold space; $\chi$ is the original, 100-dimensional video trajectory; $\Upsilon$ is a condensed matrix of pairwise distances between event vectors (computed using correlation distance in the original topic space and Euclidean distance in the manifold space); $\mathrm{corr}\left(\Upsilon\left(\xi\right), \Upsilon\left(\chi\right)\right)$ is the correlation between the sets of pairwise distances, and $\Gamma$ is the number of instances in which lines drawn between consecutive video event embeddings intersect.
+$\xi$ is the video's trajectory through the manifold space; $\chi$ is the original, 100-dimensional video trajectory; $\Upsilon$ is a condensed matrix of pairwise distances between event vectors (computed using correlation distance in the original topic space and Euclidean distance in the manifold space); $\mathrm{corr}\left(\Upsilon\left(\xi\right), \Upsilon\left(\chi\right)\right)$ is the correlation between the sets of pairwise distances, and $\Gamma$ is the number of instances in which lines drawn between consecutive video event embeddings intersected each other.
 The sets of hyper-parameter values we searched over comprised: $K \in \{10x \in \mathbb{Z}~|~10 < x <  22\} \cup \{161\}$ (a range roughly centered on half the total number of events, 161, in order to balance representations of local and global structure); $\gamma \in \{1, 3, 5, 7, 9\}$; $\delta \in \{0.1, 0.3, 0.5, 0.7\}$; $\tau \in \{x \in \mathbb{Z}~|~0 < x < 101\}$; and $\phi \in {S\choose3},~\mathrm{where}~S=\{\mathrm{video~events,~average~recall~events, individual~recall~events}\}$.

### 2020-01-08 code/scripts/embedding/embedding_cruncher.py
fixed accidental shortening of range

@@ -27,7 +27,7 @@ else:
     to_reduce = [avg_recall_events] + [video_events] + list(recall_events)
 
 for n_neighbors in list(range(100, 220, 10)) + [161]:
-    for min_dist in np.arange(.1, .9, .2):
+    for min_dist in np.arange(.1, 1, .2):
         for spread in range(1, 11, 2):
             params = {
                 'metric': 'correlation',

### 2020-01-10 code/scripts/searchlights/searchlight_collector.py
fixed a bug with globbing

@@ -50,7 +50,7 @@ for perm in range(100):
     for analysis in ['video', 'recall']:
         imgs = []
         for sub in range(1, 18):
-            img_path = glob(opj(finished_dir, f'searchlight_{analysis}', 'perms', f'sub{sub}_perm{perm}_*'))[0]
+            img_path = glob(opj(output_dir, f'searchlight_{analysis}', 'perms', f'sub{sub}_perm{perm}_*'))[0]
             sub_data = np.load(img_path, allow_pickle=True)
             img = new_img_like(ref_img, sub_data.astype(np.float64))
             imgs.append(img)

### 2020-01-26 code/scripts/load_cluster_output.py
updated script for loading cluster output

@@ -6,10 +6,11 @@ from os.path import join as opj
 hostname, username, password = sys.argv[1:]
 
 datadir_local = '../../data/processed/'
-emb_path_remote = '/dartfs/rc/lab/D/DBIC/CDL/f0028ph/sherlock-embedding/data/optimized/embeddings.npy'
+emb_path_remote = f'/dartfs/rc/lab/D/DBIC/CDL/{username}/sherlock-embedding/data/optimized/embeddings.npy'
 emb_path_local = opj(datadir_local, 'embeddings.npy')
 
-sl_dir_remote = '/dartfs/rc/lab/D/DBIC/CDL/f0028ph/searchlight-sherlock/data/finished/'
+sl_dir_remote = f'/dartfs/rc/lab/D/DBIC/CDL/{username}/searchlights/data/'
+sl_output_dr = opj(sl_dir_remote, 'finished')
 sl_vdir_local = opj(datadir_local, 'searchlight_video')
 sl_rdir_local = opj(datadir_local, 'searchlight_recall')
 
@@ -23,9 +24,10 @@ with spurplus.connect_with_retries(hostname=hostname,
                                    password=password) as remote:
                                # copy over embeddings
                                remote.get(emb_path_remote, emb_path_local)
+
                                # copy over searchlights
                                for analysis in ['video', 'recall']:
-                                   src_dir = opj(sl_dir_remote, f'searchlight_{analysis}')
+                                   src_dir = opj(sl_output_dr, f'searchlight_{analysis}')
                                    dest_dir = opj(datadir_local, f'searchlight_{analysis}')
                                    perm_dir = opj(src_dir, 'perms')
                                    for sub in range(1, 18):
@@ -38,3 +40,7 @@ with spurplus.connect_with_retries(hostname=hostname,
                                        perm_src_path = opj(perm_dir, f'perm{perm}.nii.gz')
                                        perm_dest_path = opj(dest_dir, f'perm{perm}.nii.gz')
                                        remote.get(perm_src_path, perm_dest_path)
+
+                                # copy over reference image
+                                src_path = opj(sl_dir_remote, 'inputs', 'fMRI', 'ref_img.nii.gz')
+                                dest_path = opj(sl_vdir_local, 'ref_img.nii.gz')

### 2020-01-28 code/scripts/download_neural_data.sh
bash script to download and format scan data

@@ -1,0 +1,24 @@
+#!/bin/bash
+
+# This script downloads the fMRI data used in some analyses.
+# Data was collected by Chen et al. (2017) and is available on the Princeton
+# Neuroscience Institute's website, here:
+# http://arks.princeton.edu/ark:/88435/dsp01nz8062179
+# The link used below is the direct download link, though you can verify this
+# yourself by copying the download link next to "SherlockMovies_published.tgz"
+# on the page linked above.
+
+# the destination for the files
+DEST=/mnt/data/processed/fMRI
+
+# create the new directory
+mkdir -p $DEST
+
+# download compressed file
+FILE=wget -c https://dataspace.princeton.edu/jspui/bitstream/88435/dsp01nz8062179/7/SherlockMovies_published.tgz -O -
+
+# extract contents to fMRI directory
+tar $FILE -xz -C $DEST
+
+# gzip each .nii file to save space
+gzip $DEST/*

### 2020-01-28 code/helpers/download_neural_data.sh
moved helper scripts, added note about nifti dir size

@@ -8,6 +8,8 @@
 # yourself by copying the download link next to "SherlockMovies_published.tgz"
 # on the page linked above.
 
+# NOTE: THIS TAKES QUITE A WHILE TO COMPLETE (>1 hour)
+
 # the destination for the files
 DEST=/mnt/data/processed/fMRI
 

### 2020-01-28 code/helpers/download_neural_data.sh
remove copy

@@ -8,7 +8,8 @@
 # yourself by copying the download link next to "SherlockMovies_published.tgz"
 # on the page linked above.
 
-# NOTE: THIS TAKES QUITE A WHILE TO COMPLETE (>1 hour)
+# NOTE: this takes quite a while to complete (>1 hour)
+# ALSO NOTE: the scan data will take up ~11.44 GB of space on your computer
 
 # the destination for the files
 DEST=/mnt/data/processed/fMRI
@@ -22,5 +23,5 @@ FILE=wget -c https://dataspace.princeton.edu/jspui/bitstream/88435/dsp01nz806217
 # extract contents to fMRI directory
 tar $FILE -xz -C $DEST
 
-# gzip each .nii file to save space
+# gzip each .nii file to save some space
 gzip $DEST/*

### 2020-01-28 code/helpers/download_neural_data.sh
pipe contents instead of storing

@@ -17,11 +17,9 @@ DEST=/mnt/data/processed/fMRI
 # create the new directory
 mkdir -p $DEST
 
-# download compressed file
-FILE=wget -c https://dataspace.princeton.edu/jspui/bitstream/88435/dsp01nz8062179/7/SherlockMovies_published.tgz -O -
-
-# extract contents to fMRI directory
-tar $FILE -xz -C $DEST
+# download compressed file, extract contents to fMRI directory
+wget -c https://dataspace.princeton.edu/jspui/bitstream/88435/dsp01nz8062179/7/SherlockMovies_published.tgz -O - \
+tar -xz -C $DEST
 
 # gzip each .nii file to save some space
 gzip $DEST/*

### 2020-01-29 code/helpers/analysis_helpers.py
file for helper functions used in multiple notebooks

@@ -1,0 +1,84 @@
+# This file contains variables and functions used across multiple analysis
+# notebooks (in /code/notebooks/) in a centralized location.  Both variables
+# and functions are grouped according to their use
+
+import re
+import numpy as np
+import pandas as pd
+from IPython.display import display, Markdown
+
+# provide link to this file on GitHub for reference
+github_link = "https://github.com/contextlab/sherlock-topic-model-paper/blob/master/code/helpers/analysis_helpers.py"
+info_msg = Markdown(f"Functions and variables used across multiple notebooks can be found [here]({github_link})")
+display(info_msg)
+
+
+#####################################
+#          RE-USED VARIABLES        #
+#####################################
+
+# Topic modeling parameters
+N_TOPICS = 100
+VIDEO_WSIZE = 50
+RECALL_WSIZE = 10
+VECTORIZER_PARAMS = {
+    'model' : 'CountVectorizer',
+    'params' : {
+        'stop_words' : 'english'
+    }
+}
+SEMANTIC_PARAMS = {
+    'model' : 'LatentDirichletAllocation',
+    'params' : {
+        'n_components' : N_TOPICS,
+        'learning_method' : 'batch',
+        'random_state' : 0
+    }
+}
+
+
+
+
+#####################################
+#          RE-USED FUNCTIONS        #
+#####################################
+
+# text preprocessing
+def format_text(text):
+    if isinstance(text, pd.Series):
+        text = ' '.join(list(text.dropna()))
+        pattern = "[^\w\s]+"
+    else:
+        pattern = "[^.\w\s]+"
+
+    no_possessive = text.lower().replace("'s", '')
+    punc_stripped = re.sub(pattern, '', no_possessive)
+    spaced = ' '.join(punc_stripped.split())
+    return punc_stripped
+
+
+def parse_windows(textlist, wsize):
+    windows = []
+    w_lengths = []
+    for ix in range(1, wsize):
+        start, end = 0, ix
+        w_lengths.append((start, end))
+        windows.append(' '.join(textlist[start : end]))
+
+    for ix in range(len(textlist)):
+        start = ix
+        end = ix + wsize if ix + wsize <= len(textlist) else len(textlist)
+        w_lengths.append((start, end))
+        windows.append(' '.join(textlist[start : end]))
+
+    return windows, w_lengths
+
+
+def get_video_timepoints(window_spans, annotations):
+    timepoints = []
+    for first, last in window_spans:
[…]

### 2020-01-29 code/helpers/analysis_helpers.py
added funcs for dtw, diag masking. added hand_rec and n_rec_events

@@ -5,7 +5,9 @@
 import re
 import numpy as np
 import pandas as pd
+from fastdtw import fastdtw
 from IPython.display import display, Markdown
+from scipy.spatial.distance import correlation
 
 # provide link to this file on GitHub for reference
 github_link = "https://github.com/contextlab/sherlock-topic-model-paper/blob/master/code/helpers/analysis_helpers.py"
@@ -17,7 +19,7 @@ display(info_msg)
 #          RE-USED VARIABLES        #
 #####################################
 
-# Topic modeling parameters
+# topic modeling parameters
 N_TOPICS = 100
 VIDEO_WSIZE = 50
 RECALL_WSIZE = 10
@@ -36,6 +38,11 @@ SEMANTIC_PARAMS = {
     }
 }
 
+# hand-annotated memory performance
+HAND_REC = np.array([27, 24, 32, 33, 32, 39, 30, 39, 28, 40, 34, 38, 47, 38, 27, 37, 39])
+
+# number of recall events per participant
+N_REC_EVENTS = np.array([11, 16, 12, 10, 10, 12, 11, 16, 14, 15, 15, 23, 29, 16, 13, 17, 22])
 
 
 
@@ -82,3 +89,38 @@ def get_video_timepoints(window_spans, annotations):
         timepoints.append((window_onset + window_offset) / 2)
 
     return np.array(timepoints)
+
+
+# dynamic time-warping recall trajectories
+def warp_recall(recall_traj, video_traj, return_paths=False):
+    dist, path = fastdtw(video_traj, recall_traj, dist=correlation)
+    recall_path = [i[1] for i in path]
+    warped_recall = recall_traj[recall_path]
+    if return_paths:
+        video_path = [i[0] for i in path]
+        return warped_recall, video_path, recall_path
+    else:
+        return warped_recall
+
+
+# masking long-timescale temporal correlations
+def kth_diag_indices(arr, k):
+    row_ix, col_ix = np.diag_indices_from(arr)
+    return row_ix[:-k], col_ix[k:]
+
+
+def find_diag_limit(corrmat):
+    for k in range(corrmat.shape[0]):
+        d = np.diag(corrmat, k=k)
+        if ~(d > 0).any():
+            return k
+
+
+def create_diag_mask(corrmat, diag_limit=None):
+    diag_mask = np.zeros_like(corrmat, dtype=bool)
+    if diag_limit is None:
+        diag_limit = find_diag_limit(corrmat)
[…]

### 2020-01-29 code/helpers/analysis_helpers.py
fisher z-transform

@@ -124,3 +124,9 @@ def create_diag_mask(corrmat, diag_limit=None):
         ix = kth_diag_indices(diag_mask, k)
         diag_mask[ix] = True
     return diag_mask
+
+
+# Fisher Z-transformation & inverse transformation
+def r2z(r):
+    with np.errstate(invalid='ignore', divide='ignore'):
+        return 0.5 * (np.log(1 + r) - np.log(1 - r))

### 2020-01-29 code/helpers/analysis_helpers.py
added draw_bounds

@@ -1,6 +1,7 @@
 # This file contains variables and functions used across multiple analysis
 # notebooks (in /code/notebooks/) in a centralized location.  Both variables
-# and functions are grouped according to their use
+# and functions are grouped according to their use, and tagged with the notebooks
+# in which they're imported for easy searching
 
 import re
 import numpy as np
@@ -8,6 +9,8 @@ import pandas as pd
 from fastdtw import fastdtw
 from IPython.display import display, Markdown
 from scipy.spatial.distance import correlation
+
+import matplotlib.patches as patches
 
 # provide link to this file on GitHub for reference
 github_link = "https://github.com/contextlab/sherlock-topic-model-paper/blob/master/code/helpers/analysis_helpers.py"
@@ -20,6 +23,7 @@ display(info_msg)
 #####################################
 
 # topic modeling parameters
+# topic_model_analysis.ipynb, feature_contribution.ipynb
 N_TOPICS = 100
 VIDEO_WSIZE = 50
 RECALL_WSIZE = 10
@@ -39,6 +43,7 @@ SEMANTIC_PARAMS = {
 }
 
 # hand-annotated memory performance
+# list-learning_analysis.ipynb, precision_distinctiveness_fig.ipynb
 HAND_REC = np.array([27, 24, 32, 33, 32, 39, 30, 39, 28, 40, 34, 38, 47, 38, 27, 37, 39])
 
 # number of recall events per participant
@@ -130,3 +135,16 @@ def create_diag_mask(corrmat, diag_limit=None):
 def r2z(r):
     with np.errstate(invalid='ignore', divide='ignore'):
         return 0.5 * (np.log(1 + r) - np.log(1 - r))
+
+
+# plotting temporal correlation matrices
+#eventseg_fig.ipynb
+def draw_bounds(ax, model):
+    bounds = np.where(np.diff(np.argmax(model.segments_[0], axis=1)))[0]
+    bounds_aug = np.concatenate(([0],bounds,[model.segments_[0].shape[0]]))
+    for i in range(len(bounds_aug)-1):
+        rect = patches.Rectangle((bounds_aug[i], bounds_aug[i]), bounds_aug[i+1]-bounds_aug[i],
+                                 bounds_aug[i+1]-bounds_aug[i], linewidth=1, edgecolor='#FFF9AE',
+                                 facecolor='none')
+        ax.add_patch(rect)
+    return ax

### 2020-01-29 code/helpers/analysis_helpers.py
eventseg_analysis helpers

@@ -43,10 +43,11 @@ SEMANTIC_PARAMS = {
 }
 
 # hand-annotated memory performance
-# list-learning_analysis.ipynb, precision_distinctiveness_fig.ipynb
+# eventseg_analysis.ipynb, list-learning_analysis.ipynb, precision_distinctiveness_fig.ipynb
 HAND_REC = np.array([27, 24, 32, 33, 32, 39, 30, 39, 28, 40, 34, 38, 47, 38, 27, 37, 39])
 
 # number of recall events per participant
+# list-learning_analysis.ipynb, precision_distinctiveness_fig.ipynb
 N_REC_EVENTS = np.array([11, 16, 12, 10, 10, 12, 11, 16, 14, 15, 15, 23, 29, 16, 13, 17, 22])
 
 
@@ -56,6 +57,7 @@ N_REC_EVENTS = np.array([11, 16, 12, 10, 10, 12, 11, 16, 14, 15, 15, 23, 29, 16,
 #####################################
 
 # text preprocessing
+# topic_model_analysis.ipynb, feature_contribution.ipynb
 def format_text(text):
     if isinstance(text, pd.Series):
         text = ' '.join(list(text.dropna()))
@@ -69,6 +71,7 @@ def format_text(text):
     return punc_stripped
 
 
+# topic_model_analysis.ipynb, feature_contribution.ipynb
 def parse_windows(textlist, wsize):
     windows = []
     w_lengths = []
@@ -86,6 +89,7 @@ def parse_windows(textlist, wsize):
     return windows, w_lengths
 
 
+# topic_model_analysis.ipynb, feature_contribution.ipynb
 def get_video_timepoints(window_spans, annotations):
     timepoints = []
     for first, last in window_spans:
@@ -97,6 +101,7 @@ def get_video_timepoints(window_spans, annotations):
 
 
 # dynamic time-warping recall trajectories
+# feature_contribution.ipynb, searchlight_fig.ipynb
 def warp_recall(recall_traj, video_traj, return_paths=False):
     dist, path = fastdtw(video_traj, recall_traj, dist=correlation)
     recall_path = [i[1] for i in path]
@@ -109,11 +114,13 @@ def warp_recall(recall_traj, video_traj, return_paths=False):
 
 
 # masking long-timescale temporal correlations
+# feature_contribution.ipynb, searchlight_fig.ipynb
 def kth_diag_indices(arr, k):
[…]

### 2020-01-29 code/helpers/analysis_helpers.py
helpers for searchlight notebooks

@@ -42,11 +42,9 @@ SEMANTIC_PARAMS = {
     }
 }
 
-# hand-annotated memory performance
+# hand-annotated memory performance & number of HMM-identified recall events
 # eventseg_analysis.ipynb, list-learning_analysis.ipynb, precision_distinctiveness_fig.ipynb
 HAND_REC = np.array([27, 24, 32, 33, 32, 39, 30, 39, 28, 40, 34, 38, 47, 38, 27, 37, 39])
-
-# number of recall events per participant
 # list-learning_analysis.ipynb, precision_distinctiveness_fig.ipynb
 N_REC_EVENTS = np.array([11, 16, 12, 10, 10, 12, 11, 16, 14, 15, 15, 23, 29, 16, 13, 17, 22])
 
@@ -140,14 +138,14 @@ def create_diag_mask(corrmat, diag_limit=None):
 
 
 # Fisher Z-transformation & inverse transformation
-# precision_distinctiveness_fig.ipynb,
+# precision_distinctiveness_fig.ipynb, searchlight_analyses.ipynb
 def r2z(r):
     with np.errstate(invalid='ignore', divide='ignore'):
         return 0.5 * (np.log(1 + r) - np.log(1 - r))
 
 
 # plotting temporal correlation matrices
-#eventseg_fig.ipynb
+# eventseg_fig.ipynb
 def draw_bounds(ax, model):
     bounds = np.where(np.diff(np.argmax(model.segments_[0], axis=1)))[0]
     bounds_aug = np.concatenate(([0],bounds,[model.segments_[0].shape[0]]))

### 2020-01-29 code/helpers/analysis_helpers.py
helpers for feature value notebooks

@@ -23,7 +23,7 @@ display(info_msg)
 #####################################
 
 # topic modeling parameters
-# topic_model_analysis.ipynb, feature_contribution.ipynb
+# topic_model_analysis.ipynb, feature_contribution.ipynb, feature_similarity.ipynb
 N_TOPICS = 100
 VIDEO_WSIZE = 50
 RECALL_WSIZE = 10
@@ -55,7 +55,7 @@ N_REC_EVENTS = np.array([11, 16, 12, 10, 10, 12, 11, 16, 14, 15, 15, 23, 29, 16,
 #####################################
 
 # text preprocessing
-# topic_model_analysis.ipynb, feature_contribution.ipynb
+# topic_model_analysis.ipynb, feature_contribution.ipynb, feature_similarity.ipynb
 def format_text(text):
     if isinstance(text, pd.Series):
         text = ' '.join(list(text.dropna()))
@@ -69,7 +69,7 @@ def format_text(text):
     return punc_stripped
 
 
-# topic_model_analysis.ipynb, feature_contribution.ipynb
+# topic_model_analysis.ipynb, feature_contribution.ipynb, feature_similarity.ipynb
 def parse_windows(textlist, wsize):
     windows = []
     w_lengths = []
@@ -87,7 +87,7 @@ def parse_windows(textlist, wsize):
     return windows, w_lengths
 
 
-# topic_model_analysis.ipynb, feature_contribution.ipynb
+# topic_model_analysis.ipynb, feature_contribution.ipynb, feature_similarity.ipynb
 def get_video_timepoints(window_spans, annotations):
     timepoints = []
     for first, last in window_spans:
@@ -99,7 +99,7 @@ def get_video_timepoints(window_spans, annotations):
 
 
 # dynamic time-warping recall trajectories
-# feature_contribution.ipynb, searchlight_fig.ipynb
+# searchlight_fig.ipynb, feature_contribution.ipynb
 def warp_recall(recall_traj, video_traj, return_paths=False):
     dist, path = fastdtw(video_traj, recall_traj, dist=correlation)
     recall_path = [i[1] for i in path]
@@ -112,13 +112,13 @@ def warp_recall(recall_traj, video_traj, return_paths=False):
 
 
 # masking long-timescale temporal correlations
-# feature_contribution.ipynb, searchlight_fig.ipynb
[…]

### 2020-01-29 code/helpers/analysis_helpers.py
helpers for trajectory plotting, wordles

@@ -42,12 +42,15 @@ SEMANTIC_PARAMS = {
     }
 }
 
+# scale for embedding-space trajectory figures
+# trajectory_analysis_and_fig.ipynb, wordle_analysis_and_fig.ipynb
+SCALE = 30
+
 # hand-annotated memory performance & number of HMM-identified recall events
 # eventseg_analysis.ipynb, list-learning_analysis.ipynb, precision_distinctiveness_fig.ipynb
 HAND_REC = np.array([27, 24, 32, 33, 32, 39, 30, 39, 28, 40, 34, 38, 47, 38, 27, 37, 39])
 # list-learning_analysis.ipynb, precision_distinctiveness_fig.ipynb
 N_REC_EVENTS = np.array([11, 16, 12, 10, 10, 12, 11, 16, 14, 15, 15, 23, 29, 16, 13, 17, 22])
-
 
 
 #####################################
@@ -138,10 +141,21 @@ def create_diag_mask(corrmat, diag_limit=None):
 
 
 # Fisher Z-transformation & inverse transformation
-# precision_distinctiveness_fig.ipynb, searchlight_analyses.ipynb
+# precision_distinctiveness_fig.ipynb, searchlight_analyses.ipynb, wordle_analysis_and_fig.ipynb
 def r2z(r):
     with np.errstate(invalid='ignore', divide='ignore'):
         return 0.5 * (np.log(1 + r) - np.log(1 - r))
+
+
+# wordle_analysis_and_fig.ipynb
+def z2r(z):
+    with np.errstate(invalid='ignore', divide='ignore'):
+        return (np.exp(2 * z) - 1) / (np.exp(2 * z) + 1)
+
+
+# wordle_analysis_and_fig.ipynb
+def corr_mean(rs, axis=0):
+    return z2r(np.nanmean([r2z(r) for r in rs], axis=axis))
 
 
 # plotting temporal correlation matrices
@@ -155,3 +169,47 @@ def draw_bounds(ax, model):
                                  facecolor='none')
         ax.add_patch(rect)
     return ax
+
+
+# adding arrows to trajectory embedding plots
+# trajectory_analysis_and_fig.ipynb, wordle_analysis_and_fig.ipynb
+def add_arrows(axes, x, y, **kwargs):
+    # spacing of arrows
+    aspace = .05
+    aspace *= SCALE
+    # r is the distance spanned between pairs of points
+    r = [0]
[…]

### 2020-01-29 code/helpers/analysis_helpers.py
helpers for precision_detail code

@@ -47,9 +47,9 @@ SEMANTIC_PARAMS = {
 SCALE = 30
 
 # hand-annotated memory performance & number of HMM-identified recall events
-# eventseg_analysis.ipynb, list-learning_analysis.ipynb, precision_distinctiveness_fig.ipynb
+# eventseg_analysis.ipynb, list-learning_analysis.ipynb, precision_distinctiveness_fig.ipynb, precision_detail.ipynb
 HAND_REC = np.array([27, 24, 32, 33, 32, 39, 30, 39, 28, 40, 34, 38, 47, 38, 27, 37, 39])
-# list-learning_analysis.ipynb, precision_distinctiveness_fig.ipynb
+# list-learning_analysis.ipynb, precision_distinctiveness_fig.ipynb, precision_detail.ipynb
 N_REC_EVENTS = np.array([11, 16, 12, 10, 10, 12, 11, 16, 14, 15, 15, 23, 29, 16, 13, 17, 22])
 
 

### 2020-02-01 code/helpers/analysis_helpers.py
removed dead line

@@ -68,7 +68,6 @@ def format_text(text):
 
     no_possessive = text.lower().replace("'s", '')
     punc_stripped = re.sub(pattern, '', no_possessive)
-    spaced = ' '.join(punc_stripped.split())
     return punc_stripped
 
 

### 2020-02-01 code/helpers/analysis_helpers.py
updated notebook tags

@@ -23,7 +23,7 @@ display(info_msg)
 #####################################
 
 # topic modeling parameters
-# topic_model_analysis.ipynb, feature_contribution.ipynb, feature_similarity.ipynb
+# topic_model_analysis.ipynb, feature_contribution.ipynb, feature_similarity.ipynb, precision_detail.ipynb
 N_TOPICS = 100
 VIDEO_WSIZE = 50
 RECALL_WSIZE = 10
@@ -47,9 +47,9 @@ SEMANTIC_PARAMS = {
 SCALE = 30
 
 # hand-annotated memory performance & number of HMM-identified recall events
-# eventseg_analysis.ipynb, list-learning_analysis.ipynb, precision_distinctiveness_fig.ipynb, precision_detail.ipynb
+# eventseg_analysis.ipynb, list-learning_analysis.ipynb, precision_distinctiveness_fig.ipynb
 HAND_REC = np.array([27, 24, 32, 33, 32, 39, 30, 39, 28, 40, 34, 38, 47, 38, 27, 37, 39])
-# list-learning_analysis.ipynb, precision_distinctiveness_fig.ipynb, precision_detail.ipynb
+# list-learning_analysis.ipynb, precision_distinctiveness_fig.ipynb
 N_REC_EVENTS = np.array([11, 16, 12, 10, 10, 12, 11, 16, 14, 15, 15, 23, 29, 16, 13, 17, 22])
 
 

### 2020-02-01 paper/main.tex
updated brain fig, added neurosynth fig, added placeins package for floatbarrier command
recompiled paper, started new figure caption

@@
 \usepackage{lineno}
+\usepackage{placeins}
 
@@
 
+\begin{figure}[tp]
+  \centering
+  \includegraphics[width=1\textwidth]{figs/precision_detail}
+  \caption{\small \textbf{Precision metric reflects quality and specificity of recall.} \textbf{A.} Recall precision distributions over participants, for each video event.
+Grey violin plots display kernel density estimates for the distribution of recall precision scores for a single video event.
+Colored dots within the violin plots represent each participant's recall precision for that event.
+Video events are ordered along the $x$-axis by the average precision with which they were remembered.
+\textbf{B.} The set of text annotatations (generated by \citealp{ChenEtal17}) comprising
+   \textbf{C.} }
+  \label{fig:precision-detail}
+\end{figure}
+
 The prior analyses leverage the correspondence between the 100-dimensional topic proportion matrices for the video and participants' recalls to characterize recall.
@@
 
-\begin{figure}[tp]
+\begin{figure}[t]
 \centering
-\includegraphics[width=1\textwidth]{figs/brains_panels}
+\includegraphics[width=1\textwidth]{figs/searchlights}
 \caption{\small \textbf{Brain structures that underlie the transformation of experience into memory.} \textbf{A.} We searched for regions whose responses (as participants watched the video) matched the temporal correlation matrix of the video topic proportions.
@@
 \end{figure}
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=1\textwidth]{figs/neurosynth_decoding}
+\caption{\small \textbf{INSERT CAPTION HERE}}
+\label{fig:brainz}
+\end{figure}
+\FloatBarrier
 

### 2020-02-01 paper/supporting_information.tex

@@
 The \texttt{n\_neighbors} hyper-parameter ($K$) denotes the number of nearest neighbors to consider in constructing the high-dimensional fuzzy simplicial set for each datapoint.
-\texttt{Spread} ($\gamma$) and \texttt{min\_dist} ($\delta$) function together to create the differentiable decay curve used to approximate the injective function used to map between high- and low-dimensional fuzzy simplicial sets.
+\texttt{Spread} ($\gamma$) and \texttt{min\_dist} ($\delta$) function together to create the differentiable decay curve used to approximate the injective function for mapping between high- and low-dimensional fuzzy simplicial sets.
 In essence, \texttt{min\_dist} determines the degree to which nearby points are clustered or expanded, relative to to the overall \texttt{spread}.
@@
 After initializing the low-dimensional simplicial set (by default, using a spectral embedding of the high-dimensional simplicial set's fuzzy 1-skeleton), UMAP optimizes the embedding using stochastic gradient descent with cross-entropy as a cost function.
-During optimization, indices of the data are sampled at random, and thus local minimum reached by the optimization is dependent on both the state of the RNG and the sequence in which observations are concatenated.
+During optimization, indices of the data are sampled at random, and thus the local minimum achieved by the optimization is dependent on both the state of the RNG and the sequence in which observations are concatenated.
 
@@
 $\xi$ is the video's trajectory through the manifold space; $\chi$ is the original, 100-dimensional video trajectory; $\Upsilon$ is a condensed matrix of pairwise distances between event vectors (computed using correlation distance in the original topic space and Euclidean distance in the manifold space); $\mathrm{corr}\left(\Upsilon\left(\xi\right), \Upsilon\left(\chi\right)\right)$ is the correlation between the sets of pairwise distances, and $\Gamma$ is the number of instances in which lines drawn between consecutive video event embeddings intersected each other.
-The sets of hyper-parameter values we searched over comprised: $K \in \{10x \in \mathbb{Z}~|~10 < x <  22\} \cup \{161\}$ (a range roughly centered on half the total number of events, 161, in order to balance representations of local and global structure); $\gamma \in \{1, 3, 5, 7, 9\}$; $\delta \in \{0.1, 0.3, 0.5, 0.7\}$; $\tau \in \{x \in \mathbb{Z}~|~0 < x < 101\}$; and $\phi \in {S\choose3},~\mathrm{where}~S=\{\mathrm{video~events,~average~recall~events, individual~recall~events}\}$.
-The optimal parameters (that yielded $\Phi=0$) were $K=170$, $\gamma=7$, $\delta=0.7$, $\tau=41$, and $\varphi$ as a the sequences of average recall events, video events, and individuals' recall events, vertically concatenated.
+The sets of hyper-parameter values we searched over comprised: $K \in \{10x \in \mathbb{Z}~|~10 < x <  22\} \cup \{161\}$ (a range roughly centered on half the total number of events, 161, in order to balance representations of local and global structure); $\gamma \in \{1, 3, 5, 7, 9\}$; $\delta \in \{0.1, 0.3, 0.5, 0.7, 0.9\}$; $\tau \in \{x \in \mathbb{Z}~|~0 < x < 101\}$; and $\phi \in {S\choose3},~\mathrm{where}~S=\{\mathrm{video~events,~average~recall~events, individual~recall~events}\}$.
+The optimal parameters (that yielded $\Phi=0$) were $K=170$, $\gamma=7$, $\delta=0.7$, $\tau=41$, with the order of sequence $\varphi$ as the average recall events, video events, and individuals' recall events, vertically concatenated, in order.
 

### 2020-02-03 paper/main.tex
recompiled with updated figs

@@
   \includegraphics[width=1\textwidth]{figs/precision_detail}
-  \caption{\small \textbf{Precision metric reflects quality and specificity of recall.} \textbf{A.} Recall precision distributions over participants, for each video event.
+  \caption{\small \textbf{Precision metric reflects completeness of recall.} \textbf{A.} Recall precision distributions over participants, for each video event.
 Grey violin plots display kernel density estimates for the distribution of recall precision scores for a single video event.
-Colored dots within the violin plots represent each participant's recall precision for that event.
+Colored dots within the violin plots represent individual participants' recall precision for that event.
 Video events are ordered along the $x$-axis by the average precision with which they were remembered.
-\textbf{B.} The set of text annotatations (generated by \citealp{ChenEtal17}) comprising
-   \textbf{C.} }
+\textbf{B.} The set of ``Narrative details" video annotations (generated by \citealp{ChenEtal17}) for scenes comprising an example video event (22) identified by the HMM.
+Each action or feature is highlighted in a different color.
+\textbf{C.} A subset of the sentences comprising the most precise (P17) and least precise (P6) participants' recalls of video event 22.
+Descriptions of specific actions or features reflecting those highlighted in panel B are highlighted in the corresponding color.}
   \label{fig:precision-detail}
+\end{figure}
+
+\begin{figure}[tp]
+  \centering
+  \includegraphics[width=1\textwidth]{figs/distinctiveness_detail}
+  \caption{\small \textbf{Distinctiveness metric reflects specificity of recall.} \textbf{A.} Recall precision distributions over participants, for each video event.
+Grey violin plots display kernel density estimates for the distribution of recall precision scores for a single video event.
+Colored dots within the violin plots represent individual participants' recall precision for that event.
+Video events are ordered along the $x$-axis by the average precision with which they were remembered.
+\textbf{B.} The set of ``Narrative details" video annotations (generated by \citealp{ChenEtal17}) for scenes comprising an example video event (22) identified by the HMM.
+Each action or feature is highlighted in a different color.
+\textbf{C.} A subset of the sentences comprising the most precise (P17) and least precise (P6) participants' recalls of video event 22.
+Descriptions of specific actions or features reflecting those highlighted in panel B are highlighted in the corresponding color.}
+  \label{fig:distinctiveness-detail}
 \end{figure}

### 2020-02-03 code/helpers/analysis_helpers.py
update helper notebook tags

@@ -23,7 +23,8 @@ display(info_msg)
 #####################################
 
 # topic modeling parameters
-# topic_model_analysis.ipynb, feature_contribution.ipynb, feature_similarity.ipynb, precision_detail.ipynb
+# topic_model_analysis.ipynb, feature_contribution.ipynb, feature_similarity.ipynb,
+# precision_detail_fig.ipynb, distinctiveness_detail_fig.ipynb
 N_TOPICS = 100
 VIDEO_WSIZE = 50
 RECALL_WSIZE = 10
@@ -152,7 +153,7 @@ def z2r(z):
         return (np.exp(2 * z) - 1) / (np.exp(2 * z) + 1)
 
 
-# wordle_analysis_and_fig.ipynb
+# wordle_analysis_and_fig.ipynb, , distinctiveness_detail_fig.ipynb
 def corr_mean(rs, axis=0):
     return z2r(np.nanmean([r2z(r) for r in rs], axis=axis))
 

### 2020-02-03 paper/main.tex
working on intro

@@
 
-Although our experiences most often change gradually, they also occasionally change suddenly~\citep[e.g., when we walk through a doorway; ][]{RadvZack17}.
-Prior research suggests that these sharp transitions (termed \textit{event boundaries}) during an experience help to discretize our experiences (and their mental representations) into \textit{events}~\citep{RadvZack17, BrunEtal18, HeusEtal18b, ClewDava17, EzzyDava11, DuBrDava13}.
-The interplay between the stable (within event) and transient (across event) temporal dynamics of an experience also provides a potential framework for transforming experiences into memories that distill those experiences down to their essence.
+Occasionally, this gradual ``drift" of our ongoing experience is punctuated by sudden changes, or ``shifts"~\citep[e.g., when we walk through a doorway; ][]{RadvZack17}.
+Prior research suggests that these sharp transitions (termed \textit{event boundaries}) help to discretize our experiences (and their mental representations) into \textit{events}~\citep{RadvZack17, BrunEtal18, HeusEtal18b, ClewDava17, EzzyDava11, DuBrDava13}.
+The interplay between the stable (within-event) and transient (across-event) temporal dynamics of an experience also provides a potential framework for transforming experiences into memories that distill those experiences down to their essence.
 For example, prior work has shown that event boundaries can influence how we learn sequences of items~\citep{HeusEtal18b, DuBrDava13}, navigate~\citep{BrunEtal18}, and remember and understand narratives~\citep{ZwaaRadv98, EzzyDava11}.
@@
 We analyzed an open dataset that comprised behavioral and functional Magnetic Resonance Imaging (fMRI) data collected as participants viewed and then verbally recounted an episode of the BBC television series \textit{Sherlock}~\citep{ChenEtal17}.
-We developed a computational framework for characterizing the temporal dynamics of the moment-by-moment content of the episode and of participants' verbal recalls.
+We developed a computational framework for characterizing the temporal dynamics of the moment-by-moment content of the episode, and of participants' verbal recalls.
 Specifically, we use topic modeling~\citep{BleiEtal03} to characterize the thematic conceptual (semantic) content present in each moment of the episode and recalls, and Hidden Markov Models~\citep{Rabi89, BaldEtal17} to discretize this evolving semantic content into events.
-In this way, we cast naturalistic experiences (and recalls of those experiences) as \textit{trajectories} that describe how the experiences evolve over time.
+In this way, we cast naturalistic experiences (and recalls of those experiences) as geometric \textit{trajectories} that describe how the experiences evolve over time.
 Under this framework, successful remembering entails verbally ``traversing'' the content trajectory of the episode, thereby reproducing the shape (or essence) of the original experience.
 Comparing the shapes of the topic trajectories of the episode and of participants' retellings of the episode then reveals which aspects of the episode were preserved (or lost) in the translation into memory.
-We further examine whether 1) the \textit{precision} with which a participant recounts each event and 2) the \textit{distinctiveness} each recall event is (relative to the other recalled events) relates to their overall memory performance.
-Last, we identify networks of  brain structures whose responses (as participants watched the episode) reflected the temporal dynamics of the episode, and how participants would later recount the episode.
+We further introduce two novel metrics for assessing memory quality: the \textit{precision} with which a participant recounts each event and 2) the \textit{distinctiveness} of each recall event (relative to other recalled events).
+We examine how these metrics relate to participants' overall memory performance, and discuss the ways in which they improve upon classic ``proportion-recalled" measures for analyzing naturalistic memory.
+Last, we utilize our framework to identify networks of brain structures whose responses (as participants watched the episode) reflected the temporal dynamics of the episode, and how participants would later recount it.
 
 \section*{Results}
-To characterize the shape of the \textit{Sherlock} episode and participants' subsequent recountings of its unfolding, we used a topic model~\citep{BleiEtal03} to discover the latent themes in the episode's dynamic content.
+To characterize the ``essence" of the \textit{Sherlock} episode and participants' subsequent recountings of its unfolding, we used a topic model~\citep{BleiEtal03} to discover the latent themes in the episode's dynamic content.
 Topic models take as inputs a vocabulary of words to consider and a collection of text documents, and return two output matrices.
@@
 \cite{ChenEtal17} collected hand-annotated information about each of 1000 (manually identified) scenes spanning the roughly 50 minute video used in their experiment.
-This information included: a brief narrative description of what was happening; whether the scene took place indoors or outdoors; the names of any characters on the screen; the names of any characters who were in focus in the camera shot; the names of characters who were speaking; the location where the scene took place; the camera angle (close up, medium, long, etc.); whether or not background music was present; and other similar details (for a full list of annotated features see \textit{Methods}).
-We took from these annotations the union of all unique words (excluding stop words, such as ``and,'' ``or,'' ``but,'' etc.) across all features and scenes as the ``vocabulary'' for the topic model.
+This information included: a brief narrative description of what was happening; the location where the scene took place; the names of any characters on the screen; and other similar details (for a full list of annotated features, see \textit{Methods}).
+We took from these annotations the union of all unique words (excluding stop words, such as ``and," ``or," ``but," etc.) across all features and scenes as the ``vocabulary" for the topic model.
 We then concatenated the sets of words across all features contained in overlapping, 50-scene sliding windows, and treated each 50-scene sequence as a single ``document'' for the purpose of fitting the topic model.
@@
 Video events are ordered along the $x$-axis by the average precision with which they were remembered.
-\textbf{B.} The set of ``Narrative details" video annotations (generated by \citealp{ChenEtal17}) for scenes comprising an example video event (22) identified by the HMM.
+\textbf{B.} The set of ``Narrative Details" video annotations (generated by \citealp{ChenEtal17}) for scenes comprising an example video event (22) identified by the HMM.
 Each action or feature is highlighted in a different color.
@@
   \includegraphics[width=1\textwidth]{figs/distinctiveness_detail}
-  \caption{\small \textbf{Distinctiveness metric reflects specificity of recall.} \textbf{A.} Recall precision distributions over participants, for each video event.
-Grey violin plots display kernel density estimates for the distribution of recall precision scores for a single video event.
-Colored dots within the violin plots represent individual participants' recall precision for that event.
-Video events are ordered along the $x$-axis by the average precision with which they were remembered.
-\textbf{B.} The set of ``Narrative details" video annotations (generated by \citealp{ChenEtal17}) for scenes comprising an example video event (22) identified by the HMM.
-Each action or feature is highlighted in a different color.
-\textbf{C.} A subset of the sentences comprising the most precise (P17) and least precise (P6) participants' recalls of video event 22.
-Descriptions of specific actions or features reflecting those highlighted in panel B are highlighted in the corresponding color.}
+  \caption{\small \textbf{Distinctiveness metric reflects specificity of recall.} \textbf{A.} Recall distinctiveness distributions over participants, for each video event.
+Kernel density estimates for each video event's distribution of recall distinctiveness scores, analogous to Fig.~\ref{fig:precision-detail}A.
+\textbf{B.} The set of ``Narrative Details" video annotations (generated by \citealp{ChenEtal17}) for scenes comprising an example video event (19) identified by the HMM.
+\textbf{C.} The sentences comprising the most distinctive (P13) and least distinctive (P11) participants' recalls of video event 19.
+Descriptions of recalled content specific to video event 19 (as opposed to that combining surrounding events) are highlighted.}
   \label{fig:distinctiveness-detail}

### 2020-02-03 paper/main.tex
first pass through eventseg fig

@@
 We took from these annotations the union of all unique words (excluding stop words, such as ``and," ``or," ``but," etc.) across all features and scenes as the ``vocabulary" for the topic model.
-We then concatenated the sets of words across all features contained in overlapping, 50-scene sliding windows, and treated each 50-scene sequence as a single ``document'' for the purpose of fitting the topic model.
+We then concatenated the sets of words across all features contained in overlapping, sliding windows of (up to) 50 scenes, and treated each window as a single ``document" for the purpose of fitting the topic model.
 Next, we fit a topic model with (up to) $K = 100$ topics to this collection of documents.
@@
 However, whereas Dynamic Topic Models are designed to characterize how the properties of \textit{collections} of documents change over time, our sliding window approach allows us to examine the topic dynamics within a single document (or video).
-Specifically, our approach yielded (via the topic proportions matrix) a single \textit{topic vector} for each timepoint of the episode (we set timepoints to match the acquisition times of the 1976 fMRI volumes collected as participants viewed the episode).
+Specifically, our approach yielded (via the topic proportions matrix) a single \textit{topic vector} for each sliding window of annotations transformed by the topic model.
+We then stretched the resulting windows-by-topics matrix to match the time series of the 1976 fMRI volumes collected as participants viewed the episode.
 
@@
 \end{figure}
+% Odd name for figure in "Results" section rather than "methods" section -PF
 
-The topics we found were heavily character-focused (e.g., the top-weighted word in each topic was nearly always a character) and could be roughly divided into themes that were primarily Sherlock Holmes-focused (Sherlock is the titular character), primarily John Watson-focused (John is Sherlock's close confidant and assistant), or focused on Sherlock and John interacting (Fig.~\topics).
-Several of the topics were highly similar, which we hypothesized might allow us to distinguish between subtle narrative differences (if the distinctions between those overlapping topics were meaningful; also see Fig.~\featureimportance).
-The topic vectors for each timepoint were \textit{sparse}, in that only a small number (usually one or two) of topics tended to be ``active'' in any given timepoint (Fig.~\ref{fig:model}A).
-Further, the dynamics of the topic activations appeared to exhibit \textit{persistance} (i.e., given that a topic was active in one timepoint, it was likely to be active in the following timepoint) along with \textit{occasional rapid changes} (i.e., occasionally topics would appear to spring into or out of existence).
-These two properties of the topic dynamics may be seen in the block diagonal structure of the timepoint-by-timepoint correlation matrix (Fig.~\ref{fig:model}B) and reflect the gradual drift and sudden shifts fundamental to the contextual dynamics of real-world experiences.
-Given this observation, we adapted an approach devised by \cite{BaldEtal17}, and used a Hidden Markov Model (HMM) to identify the \textit{event boundaries} where the topic activations changed rapidly (i.e., at the boundaries of the blocks in the correlation matrix; event boundaries identified by the HMM are outlined in yellow).
-Part of our model fitting procedure required selecting an appropriate number of ``events'' to segment the timeseries into.
-We used an optimization procedure to identify the number of events that maximized within-event stability while also minimizing across-event correlations (see \textit{Methods} for additional details).
-To create a stable ``summary'' of the video, we computed the average topic vector within each event (Fig.~\ref{fig:model}C).
+The 32 topics we found were heavily character-focused (i.e., the top-weighted word in each topic was nearly always a character) and could be roughly divided into themes centered around Sherlock Holmes (the titular character), John Watson (Sherlock's close confidant and assistant), supporting characters (e.g., Inspector Lestrade, Sergeant Donovan, or Sherlock's brother Mycroft), or the interactions between various pairs of these characters (see Fig.~\topics).
+Several of the identified topics were highly similar, which we hypothesized might allow us to distinguish between subtle narrative differences if the distinctions between those overlapping topics were meaningful.
+The topic vectors for each timepoint were \textit{sparse}, in that only a small number (usually one or two) of topics tended to be ``active" in any given timepoint (Fig.~\ref{fig:model}A).
+Further, the dynamics of the topic activations appeared to exhibit \textit{persistence} (i.e., given that a topic was active in one timepoint, it was likely to be active in the following timepoint) along with \textit{occasional rapid changes} (i.e., occasionally topics would appear to spring into or out of existence).
+These two properties of the topic dynamics may be seen in the block diagonal structure of the timepoint-by-timepoint correlation matrix (Fig.~\ref{fig:model}B) and reflect the gradual drift and sudden shifts fundamental to the temporal dynamics of real-world experiences.
+Given this observation, we adapted an approach devised by \cite{BaldEtal17}, and used a Hidden Markov Model (HMM) to identify the \textit{event boundaries} where the topic activations changed rapidly (i.e., at the boundaries of the blocks in the correlation matrix; event boundaries identified by the HMM are outlined in yellow in Fig.~\ref{fig:model}B).
+Part of our model fitting procedure required selecting an appropriate number of ``events" into which the topic trajectory should be segmented.
+To accomplish this, we used an optimization procedure that maximized the difference between the topic weights for timepoints within an event and across multiple events (see \textit{Methods} for additional details).
+We then created a stable ``summary'' of the content within each video event by averaging across the topic vectors each event comprised (Fig.~\ref{fig:model}C).
 
@@
 \textbf{B.} Timepoint-by-timepoint correlation matrix of the topic vectors displayed in Panel A.
-Event boundaries detected by the HMM are denoted in yellow (30 events detected).
+Event boundaries discovered by the HMM are denoted in yellow (30 events detected).
 \textbf{C.} Average topic vectors for each of the 30 video events.
@@
 Event boundaries detected by the HMM are denoted in yellow (22 events detected).
+For similar plots for all participants see Figure~\corrmats.
 \textbf{F.} Average topic vectors for each of the 22 recalled events from the example participant.
 \textbf{G.} Correlations between the topic vectors for every pair of video events (Panel C) and recalled events (from the example participant; Panel F).
-For similar plots for all participants see Figure~\matchmats.
+For similar plots for all participants, see Figure~\matchmats.
 \textbf{H.} Average correlations between each pair of video events and recalled events (across all 17 participants).
@@
 \end{figure}
+% I'm all for citing software packages, but where what's the distinction between packages we do cite (seaborn, brainiak, sklearn, hypertools, quail, umap, etc.) and don't cite (wordcloud, nilearn, fastdtw, etc.)?
 
@@
 We applied the same topic model (already trained on the video annotations) to each participant's recalls.
-Analogous to how we analyzed the time-varying content of the video, to obtain similar estimates for participants' recalls, we treated each (overlapping) 10-sentence ``window'' of their transcript as a ``document'' and then computed the most probable mix of topics reflected in each timepoint's sentences.
+Analogous to how we parsed the time-varying content of the video, to obtain similar estimates for each participant's recall, we treated each overlapping  ``window" (of up to 10 sentences) from their transcript as a ``document" and then computed the most probable mix of topics reflected in each timepoint's sentences.
 This yielded, for each participant, a number-of-windows by number-of-topics topic proportions matrix that characterized how the topics identified in the original video were reflected in the participant's recalls.
 Note that an important feature of our approach is that it allows us to compare participant's recalls to events from the original video, despite that different participants may have used different language to describe the same event, and that those descriptions may not match the original annotations.
-This is a substantial benefit of projecting the video and recalls into a shared ``topic'' space.
+This is a substantial benefit of projecting the video and recalls into a shared ``topic" space.
 An example topic proportions matrix from one participant's recalls is shown in Figure~\ref{fig:model}D.

### 2020-02-03 paper/main.tex
new distinctiveness fig, working on results section

@@
 To accomplish this, we used an optimization procedure that maximized the difference between the topic weights for timepoints within an event and across multiple events (see \textit{Methods} for additional details).
-We then created a stable ``summary'' of the content within each video event by averaging across the topic vectors each event comprised (Fig.~\ref{fig:model}C).
+We then created a stable ``summary'' of the content within each video event by averaging the topic vectors across timepoints each event spanned (Fig.~\ref{fig:model}C).
 
@@
 We applied the same topic model (already trained on the video annotations) to each participant's recalls.
-Analogous to how we parsed the time-varying content of the video, to obtain similar estimates for each participant's recall, we treated each overlapping  ``window" (of up to 10 sentences) from their transcript as a ``document" and then computed the most probable mix of topics reflected in each timepoint's sentences.
+Analogous to how we parsed the time-varying content of the video, to obtain similar estimates for each participant's recall, we treated each overlapping  ``window" of (up to 10) sentences from their transcript as a ``document," and computed the most probable mix of topics reflected in each timepoint's sentences.
 This yielded, for each participant, a number-of-windows by number-of-topics topic proportions matrix that characterized how the topics identified in the original video were reflected in the participant's recalls.
-Note that an important feature of our approach is that it allows us to compare participant's recalls to events from the original video, despite that different participants may have used different language to describe the same event, and that those descriptions may not match the original annotations.
+Note that an important feature of our approach is that it allows us to compare participants' recalls to events from the original video, despite different participants using widely varying language to describe the same event, and that those descriptions may not match the original annotations.
 This is a substantial benefit of projecting the video and recalls into a shared ``topic" space.
@@
 
-Although the example participant's recall topic proportions matrix has some visual similarity to the video topic proportions matrix, the time-varying topic proportions for the example participant's recalls are not as sparse as for the video (e.g., compare Figs.~\ref{fig:model}A and D).
-Similarly, although there do appear to be periods of stability in the recall topic dynamics (e.g., most topics are active or inactive over contiguous blocks of time), the overall timecourses are not as cleanly delineated as the video topics are.
-To examine these patterns in detail, we computed the timepoint-by-timepoint correlation matrix for the example participant's recall topic proportions (Fig.~\ref{fig:model}E).
+Although the example participant's recall topic proportions matrix has some visual similarity to the video topic proportions matrix, the time-varying topic proportions for the example participant's recalls are not as sparse as those for the video (compare Figs.~\ref{fig:model}A and D).
+Similarly, although there do appear to be periods of stability in the recall topic dynamics (i.e., most topics are active or inactive over contiguous blocks of time), the individual topics' overall timecourses are not as cleanly delineated as the video topics'.
+To examine these patterns in detail, we computed the timepoint-by-timepoint correlation matrix for the example participant's recall topic trajectory (Fig.~\ref{fig:model}E).
 As in the video correlation matrix (Fig.~\ref{fig:model}B), the example participant's recall correlation matrix has a strong block diagonal structure, indicating that their recalls are discretized into separated events.
@@
 First, although every individual participant's recalls could be segmented into discrete events (i.e., every individual participant's recall correlation matrix exhibited clear block diagonal structure; Fig.~\corrmats), each participant appeared to have a unique \textit{recall resolution}, reflected in the sizes of those blocks.
-For example, some participants' recall topic proportions segmented into just a few events (e.g., Participants P4, P5, and P7), while others' recalls segmented into many shorter duration events (e.g., Participants P12, P13, and P17).
+While, some participants' recall topic proportions segmented into just a few events (e.g., Participants P4, P5, and P7), others' segmented into many shorter duration events (e.g., Participants P12, P13, and P17).
 This suggests that different participants may be recalling the video with different levels of detail-- e.g., some might touch on just the major plot points, whereas others might attempt to recall every minor scene or action.
 The second clear pattern present in every individual participant's recall correlation matrix is that, unlike in the video correlation matrix, there are substantial off-diagonal correlations.
-Whereas each event in the original video was (largely) separable from the others (Fig.~\ref{fig:model}B), in transforming those separable events into memory, participants appear to be integrating across mutliple events, blending elements of previously recalled and not-yet-recalled events into each newly recalled event~\citep[Figs.~\ref{fig:model}D, \corrmats; also see][]{MannEtal11, HowaEtal12}.
+Whereas each event in the original video was (largely) separable from the others (Fig.~\ref{fig:model}B), in transforming those separable events into memory, participants appear to be integrating across multiple events, blending elements of previously recalled and not-yet-recalled content into each newly recalled event~\citep[Figs.~\ref{fig:model}D, \corrmats; also see][]{MannEtal11, HowaEtal12}.
 
-The above results indicate that both the structure of the original video and participants' recalls of the video exhibit event boundaries that can be identified automatically by characterizing the dynamic content using a shared topic model and segmenting the content into events using HMMs.
+The above results indicate that both the structure of the original video and participants' recalls of the video exhibit event boundaries that can be identified automatically by characterizing the dynamic content using a shared topic model and segmenting the content into events via HMMs.
 Next, we asked whether some correspondence might be made between the specific content of the events the participants experienced in the video, and the events they later recalled.
 One approach to linking the experienced (video) and recalled events is to label each recalled event as matching the video event with the most similar (i.e., most highly correlated) topic vector (Figs.~\ref{fig:model}G, \matchmats).
-This yields a sequence of ``presented'' events from the original video, and a (potentially differently ordered) sequence of ``recalled'' events for each participant.
-Analogous to classic list-learning studies, we can then examine participants' recall sequences by asking which events they tended to recall first~\citep[probability of first recall; Fig.~\ref{fig:list-learning}A;][]{WelcBurn24, PostPhil65, AtkiShif68}; how participants most often transition between recalls of the events as a function of the temporal distance between them~\citep[lag-conditional response probability; Fig.~\ref{fig:list-learning}B;][]{Kaha96}; and which events they were likely to remember overall~\citep[serial position recall analyses; Fig.~\ref{fig:list-learning}C;][]{Murd62a}.
+This yields a sequence of ``presented" events from the original video, and a (potentially differently ordered) sequence of ``recalled" events for each participant.
+Analogous to classic list-learning studies, we can then examine participants' recall sequences by asking which events they tended to recall first~\citep[probability of first recall; Fig.~\ref{fig:list-learning}A;][]{AtkiShif68, PostPhil65, WelcBurn24}; how participants most often transition between recalls of the events as a function of the temporal distance between them~\citep[lag-conditional response probability; Fig.~\ref{fig:list-learning}B;][]{Kaha96}; and which events they were likely to remember overall~\citep[serial position recall analyses; Fig.~\ref{fig:list-learning}C;][]{Murd62a}.
 Interestingly, for two of these analyses (probability of first recall and lag-conditional response probability curves) we observe patterns comparable to classic effects from the list-learning literature: namely, a higher probability of initiating recall with the first event in the sequence (Fig.~\ref{fig:list-learning}A) and a higher probability of transitioning to neighboring events with an asymmetric forward bias (Fig.~\ref{fig:list-learning}C).

### 2020-02-03 paper/main.tex
writing results sections for new figs

@@
 \end{figure}
-% Odd name for figure in "Results" section rather than "methods" section -PF
+% Odd name for figure in "Results" section rather than "methods" section 
+% - Paxton
 
@@
 % I'm all for citing software packages, but where what's the distinction between packages we do cite (seaborn, brainiak, sklearn, hypertools, quail, umap, etc.) and don't cite (wordcloud, nilearn, fastdtw, etc.)?
+% - Paxton
 
@@
 We found that participants tended to recall semantically similar video events together (mean: 0.787, SEM: 0.018), and that semantic clustering score was also related to both hand-annotated  (Pearson's $r(15) = 0.65,~p = 0.004$) and model-derived (Pearson's $r(15) = 0.63,~p = 0.007$) memory performance.
-
 % NOTE: 
@@
 
-Statistical models of memory studies often treat memory recalls as binary (e.g.
-the item was recalled or not) and independent events.
-However, our framework produces a content-based model of individual stimulus and recall events, allowing for direct quantitative comparison between all stimulus and recall events, as well as between the recall events themselves.
-Leveraging these content-based models of the stimulus/recall events, we developed two novel metrics for quantifying naturalistic memory representations:~\textit{precision} and \textit{distinctiveness}.
-We define precision as the average correlation between the topic proportions of each recall event and the maximally correlated video event (Fig.~\ref{fig:precision-distinctiveness}).
+Statistical models of memory studies often treat recall success as binary (i.e., an item either was or was not recalled), or occasionally categorical \citep[e.g., to distinguish familiarity from recollection][]{YoneEtal02}.
+Such approaches are tenable in classical list-learning or recognition memory paradigms, as the presented stimuli tend to be very simple (e.g., a sequence of individual words or items).
+However, the feature-rich content of a naturalistic experiences may later be described with many, highly variable levels of success.
+Our framework produces a content-based model of individual stimulus and recall events, allowing for direct quantitative comparison between all stimulus and recall events, as well as between the recall events themselves.
+Leveraging these content-based models of the stimulus/recall events, we developed two novel, \textit{continuous} metrics for quantifying naturalistic memory representations:~\textit{precision} and \textit{distinctiveness}.
+We define precision as the ``completeness" of recall-- i.e., how fully the presented content was recapitulated in memory.
+Under our framework, we quantify this for a given recall event as the correlation between the topic proportions of the recall event and the maximally correlated video event (Fig.~\ref{fig:precision-distinctiveness}).
+A second novel metric we introduce here is \textit{distinctiveness}, which we define as the ``specificity" of recall-- i.e., how unique the description of a given section of content was, compared to descriptions for other sections of content.
+We quantify this for each recall event as 1 minus the average correlation between the given recall event and all other recall events not matched to the same video event.
+In addition to individual events, one may also use these metrics to describe each participant's overall performance.
 Participants whose recall events are more veridical descriptions of what happened in the video event will presumably have higher precision scores.
 We find that, across participants, a higher precision score is correlated to both hand-annotated memory performance (Pearson's $r(15) = 0.56, p = 0.021$) and the number of recall events estimated by our model (Pearson's $r(15) = 0.85, p < 0.001$).
-A second novel metric we introduce here is distinctiveness, or how unique the recall description was to each video event.
-We define distinctiveness as 1 minus the average of all non-matching recall events from the video-recall correlation matrix.
-We hypothesized that participants who recounted events in a more distinctive way would display better overall memory.
-We find that this distinctiveness score is related to our model's estimated number of recalled events (Pearson's $r(15) = 0.49, p = 0.046$) but not to the analogous hand-annotated metric (Pearson's $r(15) = 0.31, p = 0.23$).
-In summary, using two novel metrics afforded by our approach, we find that participants whose recalls are both more precise and distinct remember more content.
-% ------ NOTE: ------
-% rephrase/reframe distinctiveness?
-% - Paxton
+We also hypothesized that participants who recounted events in a more distinctive way would display better overall memory.
+We find that this distinctiveness score is related to our model's estimated number of recalled events (Pearson's $r(15) = 0.53, p = 0.028$).
+While we do not find distinctiveness to be related to hand-annotated memory performance (Pearson's $r(15) = 0.28, p = 0.275$), this is not entirely surprising given how the hand-annotated memory scores were computed (see \textit{Methods}).
 
@@
   \includegraphics[width=1\textwidth]{figs/precision_distinctiveness}
-  \caption{\small \textbf{Novel content-based metrics of naturalistic memory: precision and distinctiveness.} \textbf{A.} A video-recall correlation matrix for a representative participant (17).
+  \caption{\small \textbf{Novel content-based metrics of naturalistic memory: precision and distinctiveness.} \textbf{A.} The video-recall correlation matrix for a representative participant (17).
 The yellow boxes highlight the maximum correlation in each column.
-Precision was computed as the average of the maximum correlation in each column.
-On the other hand, distinctiveness was defined as the average of everything except for the maximum correlation in each column.
+The example participant's overall precision score was computed as the average across correlation values in the yellow boxes.
+Their distinctiveness score was computed as the the average (over recall events) of 1 minus the average correlation between each recall event and all other recall events that do not display a box in the same row.
 \textbf{B.} The (Pearson's) correlation between precision and hand-annotated memory performance.
-\textbf{C.} The correlation between precision and the number of events recovered by the model ($k$).
-\textbf{D.} The correlation between distinctiveness and hand-annotated memory performance.
+\textbf{C.} The correlation between distinctiveness and hand-annotated memory performance.
+\textbf{D.} The correlation between precision and the number of events recovered by the model ($k$).
 \textbf{E.} The correlation between distinctiveness and the number of events recovered by the model ($k$).}
@@
 \end{figure}
+
+Further intuition for the behaviors captured by these two metrics may be gained by directly examining the content of the video and recalls our framework models.
+In Figure \ref{fig:precision-detail}, we contrast two participants' recall descriptions of the same video event: one with a high precision score, the other with a low precision score.
+From the HMM-identified event boundaries, we recovered the set of annotations describing the content of an example video event (panel B), and divided them into different color-coded sections for each action or feature described.
+We then similarly recovered the set of sentences comprising the corresponding recall event for each of the two example participants.
+Because the recall sliding windows overlap heavily, and each recall event spans multiple recall timepoints (i.e., windows), we have stripped any sentences from the beginning and end that describe earlier or later video events.
+In other words, the sentences displayed in Fig.~\ref{fig:precision-detail}C are a subset of the full recall event text, spanning sentences between the first and last descriptions of content from the example video event.
+We then colored all descriptions of the video event's content by the
 

### 2020-02-04 paper/main.tex
some updates to results section

@@
 
-\cite{ChenEtal17} collected hand-annotated information about each of 1000 (manually identified) scenes spanning the roughly 50 minute video used in their experiment.
-This information included: a brief narrative description of what was happening; the location where the scene took place; the names of any characters on the screen; and other similar details (for a full list of annotated features, see \textit{Methods}).
+\cite{ChenEtal17} collected hand-annotated information about each of 1000 (manually identified) time segments spanning the roughly 50 minute video used in their experiment.
+This information included: a brief narrative description of what was happening, the location where the scene took place, the names of any characters on the screen, and other similar details (for a full list of annotated features, see \textit{Methods}).
 We took from these annotations the union of all unique words (excluding stop words, such as ``and," ``or," ``but," etc.) across all features and scenes as the ``vocabulary" for the topic model.
@@
 
-Statistical models of memory studies often treat recall success as binary (i.e., an item either was or was not recalled), or occasionally categorical \citep[e.g., to distinguish familiarity from recollection][]{YoneEtal02}.
+Statistical models of memory studies often treat recall success as binary (i.e., an item either was or was not recalled), or occasionally categorical \citep[e.g., to distinguish familiarity from recollection;][]{YoneEtal02}.
 Such approaches are tenable in classical list-learning or recognition memory paradigms, as the presented stimuli tend to be very simple (e.g., a sequence of individual words or items).
@@
 Leveraging these content-based models of the stimulus/recall events, we developed two novel, \textit{continuous} metrics for quantifying naturalistic memory representations:~\textit{precision} and \textit{distinctiveness}.
-We define precision as the ``completeness" of recall-- i.e., how fully the presented content was recapitulated in memory.
+We define precision as the ``completeness" of recall, or how fully the presented content was recapitulated in memory.
 Under our framework, we quantify this for a given recall event as the correlation between the topic proportions of the recall event and the maximally correlated video event (Fig.~\ref{fig:precision-distinctiveness}).
-A second novel metric we introduce here is \textit{distinctiveness}, which we define as the ``specificity" of recall-- i.e., how unique the description of a given section of content was, compared to descriptions for other sections of content.
+A second novel metric we introduce here is \textit{distinctiveness}, which we define as the ``specificity" of recall, or how unique the description of a given section of content was, compared to descriptions for other sections of content.
 We quantify this for each recall event as 1 minus the average correlation between the given recall event and all other recall events not matched to the same video event.
-In addition to individual events, one may also use these metrics to describe each participant's overall performance.
+In addition to individual events, one may also use these metrics to describe each participant's overall performance (i.e., by averaging across a participant's event-wise precision or distinctiveness scores).
 Participants whose recall events are more veridical descriptions of what happened in the video event will presumably have higher precision scores.
@@
 We also hypothesized that participants who recounted events in a more distinctive way would display better overall memory.
-We find that this distinctiveness score is related to our model's estimated number of recalled events (Pearson's $r(15) = 0.53, p = 0.028$).
-While we do not find distinctiveness to be related to hand-annotated memory performance (Pearson's $r(15) = 0.28, p = 0.275$), this is not entirely surprising given how the hand-annotated memory scores were computed (see \textit{Methods}).
+We find that this distinctiveness score is related to our model's estimated number of recalled events (Pearson's $r(15) = 0.53, p = 0.028$), and while we do not find distinctiveness to be related to hand-annotated memory performance (Pearson's $r(15) = 0.28, p = 0.275$), this is not entirely surprising given how the hand-annotated memory scores were computed (see \textit{Methods}).
 
@@
 Further intuition for the behaviors captured by these two metrics may be gained by directly examining the content of the video and recalls our framework models.
-In Figure \ref{fig:precision-detail}, we contrast two participants' recall descriptions of the same video event: one with a high precision score, the other with a low precision score.
-From the HMM-identified event boundaries, we recovered the set of annotations describing the content of an example video event (panel B), and divided them into different color-coded sections for each action or feature described.
+In Figure \ref{fig:precision-detail}, we contrast recalls for the same video event from two participants: one with a high precision score (P17), the other with a low precision score (P6).
+From the HMM-identified event boundaries, we recovered the set of annotations describing the content of an example video event (event 22; Fig.~\ref{fig:precision-detail}B), and divided them into different color-coded sections for each action or feature described.
 We then similarly recovered the set of sentences comprising the corresponding recall event for each of the two example participants.
-Because the recall sliding windows overlap heavily, and each recall event spans multiple recall timepoints (i.e., windows), we have stripped any sentences from the beginning and end that describe earlier or later video events.
-In other words, the sentences displayed in Fig.~\ref{fig:precision-detail}C are a subset of the full recall event text, spanning sentences between the first and last descriptions of content from the example video event.
-We then colored all descriptions of the video event's content by the
+Because the recall sliding windows overlap heavily, and each recall event spans multiple recall timepoints (i.e., windows), we have stripped any sentences from the beginning and end that describe earlier or later video events for the sake of readability.
+In other words, Fig.~\ref{fig:precision-detail}C shows a subset of the full recall event text, comprising sentences between the first and last descriptions of content from the example video event.
+We then colored all words describing actions and features coded in panel B by their corresponding color.
+Visual comparison of the transcripts reveals that the most precise participant's recall captures a greater amount of the video event's content, and with far more detail.
+
+Figure \ref{fig:distinctiveness-detail} similarly contrasts two participants' recall for an example video event (event 19) to illustrate the tangible differences between high and low distinctiveness scores.
+Here, we have extracted the full text from the most
 
@@
 Data were collected by \cite{ChenEtal17}.
-In brief, participants ($n=17$) viewed the first 48 minutes of ``A Study in Pink'', the first episode of the BBC television series \textit{Sherlock}, while fMRI volumes were collected (TR = 1500~ms).
+In brief, participants ($n=22$) viewed the first 48 minutes of ``A Study in Pink'', the first episode of the BBC television series \textit{Sherlock}, while fMRI volumes were collected (TR = 1500~ms).
+Participants were pre-screened to ensure they had never seen any episode of the show before.
 The stimulus was divided into a 23~min (946~TR) and a 25~min (1030~TR) segment to mitigate technical issues related to the scanner.
@@
 They were told that completeness and detail were more important than temporal order, and that if at any point they realized they had missed something, to return to it.
-Participants were then allowed to speak for as long as they wished, and verbally indicated when they were finished (e.g., `I’m done').''  For additional details about the experimental procedure and scanning parameters, see \cite{ChenEtal17}.
+Participants were then allowed to speak for as long as they wished, and verbally indicated when they were finished (e.g., `I’m done').''  Five participants were dropped from the original dataset due to excessive head motion (2 participants), insufficient recall length (2 participants), or falling asleep during stimulus viewing (1 participant), resulting in a final sample size of $n=17$.
+For additional details about the experimental procedure and scanning parameters, see \cite{ChenEtal17}.
 The experimental protocol was approved by Princeton University's Institutional Review Board.
@@
 
+The video stimulus was divided into 1,000 fine-grained ``scenes" and annotated by an independent coder.
+For each of these 1,000 scenes, the following information was recorded: a brief narrative description of what was happening, the location where the scene took place, whether that location was indoors or outdoors, the names of all characters on-screen, the name(s) of the character(s) in focus in the shot, the name(s) of the character(s) currently speaking, the camera angle of the shot, a transcription of any text appearing on-screen, and whether or not there was music present in the background.
+Each scene was also tagged with its onset and offset time, in both seconds and TRs.
+
+The video was also divided by an independent coder into 50 more broad ``scenes" ``following major shifts in the narrative (e.g., location, topic, and/or time)" \citep{ChenEtal17}.
+The hand-annotated memory scores for each participant we reference in our present study were generated by considering a scene to have been recalled (in a binary fashion) ``if the participant described any part of the scene."
+
 \subsection*{Data and code availability}
@@
 \subsection*{Statistics}
-All statistical tests we performed were two-sided.
+All statistical tests performed in the behavioral analyses were two-sided.
+All statistical tests performed in the neural data analyses were two-sided, except for the permutation-based thresholding, which was one-sided.
+In this case, we were specifically interested in identifying voxels whose activation time series reflected the temporal structure of the video and recall trajectories to a \textit{greater} extent than that of the phase-shifted trajectories.
+% ------ NOTE: ------
+% from the Nature Human Behavior submission requirements: "Specify whether tests were one- or two-tailed, and justify the use of one-tailed tests."
+% - Paxton
 

### 2020-02-04 paper/main.tex
updates to methods, results sections for new precision and distinctiveness figs

@@
 
-\begin{figure}[tp]
+\begin{figure}[t]
   \centering
@@
   \label{fig:list-learning}
+\end{figure}
+
+\begin{figure}[t]
+  \centering
+  \includegraphics[width=1\textwidth]{figs/precision_distinctiveness}
+  \caption{\small \textbf{Novel content-based metrics of naturalistic memory: precision and distinctiveness.} \textbf{A.} The video-recall correlation matrix for a representative participant (17).
+The yellow boxes highlight the maximum correlation in each column.
+The example participant's overall precision score was computed as the average across correlation values in the yellow boxes.
+Their distinctiveness score was computed as the the average (over recall events) of 1 minus the average correlation between each recall event and all other recall events that do not display a box in the same row.
+\textbf{B.} The (Pearson's) correlation between precision and hand-annotated memory performance.
+\textbf{C.} The correlation between distinctiveness and hand-annotated memory performance.
+\textbf{D.} The correlation between precision and the number of events recovered by the model ($k$).
+\textbf{E.} The correlation between distinctiveness and the number of events recovered by the model ($k$).}
+  \label{fig:precision-distinctiveness}
 \end{figure}
@@
 
-\begin{figure}[tp]
-  \centering
-  \includegraphics[width=1\textwidth]{figs/precision_distinctiveness}
-  \caption{\small \textbf{Novel content-based metrics of naturalistic memory: precision and distinctiveness.} \textbf{A.} The video-recall correlation matrix for a representative participant (17).
-The yellow boxes highlight the maximum correlation in each column.
-The example participant's overall precision score was computed as the average across correlation values in the yellow boxes.
-Their distinctiveness score was computed as the the average (over recall events) of 1 minus the average correlation between each recall event and all other recall events that do not display a box in the same row.
-\textbf{B.} The (Pearson's) correlation between precision and hand-annotated memory performance.
-\textbf{C.} The correlation between distinctiveness and hand-annotated memory performance.
-\textbf{D.} The correlation between precision and the number of events recovered by the model ($k$).
-\textbf{E.} The correlation between distinctiveness and the number of events recovered by the model ($k$).}
-  \label{fig:precision-distinctiveness}
-\end{figure}
-
-\begin{figure}[tp]
+\begin{figure}[t]
   \centering
@@
 Further intuition for the behaviors captured by these two metrics may be gained by directly examining the content of the video and recalls our framework models.
-In Figure \ref{fig:precision-detail}, we contrast recalls for the same video event from two participants: one with a high precision score (P17), the other with a low precision score (P6).
-From the HMM-identified event boundaries, we recovered the set of annotations describing the content of an example video event (event 22; Fig.~\ref{fig:precision-detail}B), and divided them into different color-coded sections for each action or feature described.
+In Figure \ref{fig:precision-detail}, we contrast recalls for the same video event (event 22) from two participants: one with a high precision score (P17), the other with a low precision score (P6).
+From the HMM-identified event boundaries, we recovered the set of annotations describing the content of an example video event (Fig.~\ref{fig:precision-detail}B), and divided them into different color-coded sections for each action or feature described.
 We then similarly recovered the set of sentences comprising the corresponding recall event for each of the two example participants.
@@
 We then colored all words describing actions and features coded in panel B by their corresponding color.
-Visual comparison of the transcripts reveals that the most precise participant's recall captures a greater amount of the video event's content, and with far more detail.
+Visual comparison of the transcripts reveals that the most precise participant's recall both captures more of the video event's content, and does so with far more detail.
 
-Figure \ref{fig:distinctiveness-detail} similarly contrasts two participants' recall for an example video event (event 19) to illustrate the tangible differences between high and low distinctiveness scores.
-Here, we have extracted the full text from the most
+Figure \ref{fig:distinctiveness-detail} similarly contrasts two example participants' recalls for a common video event (event 19) to illustrate the tangible differences between high and low distinctiveness scores.
+Here, we have extracted the full set of sentences comprising the most distinctive recall event (P13) and least distinctive recall event (P11) recall event matched to the example video event (Fig.~\ref{fig:distinctiveness-detail}C).
+We also extracted the annotations for the example video event, as well as those from each other video event whose content the example participants' single recall events described (Fig.~\ref{fig:distinctiveness-detail}B).
+We then shaded the annotation text for each video event with a different color, and shaded each word of the example participants' recall text by the color of the video event it describes.
+The majority of the most distinctive recall event text describes video event 19's content, with the first five and last one sentence describing the video events immediately preceding and succeeding the current one, respectively.
+Meanwhile, the least precise participant's recall for video event 19 blends the content from five separate video events, does not transition between them in order, and often combines descriptions of two video events' content in the same sentence
 

### 2020-02-05 paper/main.tex

@@
 However, the feature-rich content of a naturalistic experiences may later be described with many, highly variable levels of success.
-Our framework produces a content-based model of individual stimulus and recall events, allowing for direct quantitative comparison between all stimulus and recall events, as well as between the recall events themselves.
-Leveraging these content-based models of the stimulus/recall events, we developed two novel, \textit{continuous} metrics for quantifying naturalistic memory representations:~\textit{precision} and \textit{distinctiveness}.
+Our framework produces a content-based model of individual stimulus and recall events by projecting the dynamic content of the video and participants' recalls into a shared topic space.
+This allows for direct, quantitative comparison between all stimulus and recall events, as well as between the recall events themselves.
+Leveraging these content-based models of the stimulus/recall events, we developed two novel, \textit{continuous} metrics for analyzing naturalistic memory:~\textit{precision} and \textit{distinctiveness}.
 We define precision as the ``completeness" of recall, or how fully the presented content was recapitulated in memory.
@@
   \includegraphics[width=1\textwidth]{figs/precision_detail}
-  \caption{\small \textbf{Precision metric reflects completeness of recall.} \textbf{A.} Recall precision distributions over participants, for each video event.
+  \caption{\small \textbf{Precision metric reflects completeness of recall.} \textbf{A.} Recall precision by video event.
 Grey violin plots display kernel density estimates for the distribution of recall precision scores for a single video event.
-Colored dots within the violin plots represent individual participants' recall precision for that event.
+Colored dots within each violin plot represent individual participants' recall precision for the given event.
 Video events are ordered along the $x$-axis by the average precision with which they were remembered.
@@
   \includegraphics[width=1\textwidth]{figs/distinctiveness_detail}
-  \caption{\small \textbf{Distinctiveness metric reflects specificity of recall.} \textbf{A.} Recall distinctiveness distributions over participants, for each video event.
+  \caption{\small \textbf{Distinctiveness metric reflects specificity of recall.} \textbf{A.} Recall distinctiveness by video event.
 Kernel density estimates for each video event's distribution of recall distinctiveness scores, analogous to Fig.~\ref{fig:precision-detail}A.
-\textbf{B.} The set of ``Narrative Details" video annotations (generated by \citealp{ChenEtal17}) for scenes comprising an example video event (19) identified by the HMM.
+\textbf{B.} The sets of ``Narrative Details" video annotations (generated by \citealp{ChenEtal17}) for scenes comprising video events described by the example participants in panel C.
+Each event's text is highlighted in a different color.
 \textbf{C.} The sentences comprising the most distinctive (P13) and least distinctive (P11) participants' recalls of video event 19.
-Descriptions of recalled content specific to video event 19 (as opposed to that combining surrounding events) are highlighted.}
+Sections of recall describing each each video event in panel B are highlighted with the corresponding color.}
   \label{fig:distinctiveness-detail}
@@
 The prior analyses leverage the correspondence between the 100-dimensional topic proportion matrices for the video and participants' recalls to characterize recall.
-However, it is difficult to gain deep insights into that content solely by examining the topic proportion matrices (e.g., Figs.~\ref{fig:model}A, D) or the corresponding correlation matrices (Figs.~\ref{fig:model}B, E, \corrmats).
+However, it is difficult to gain deep insights into the content of (or relationships between) experiences and memories solely by examining these topic proportions (e.g., Figs.~\ref{fig:model}A, D) or the corresponding correlation matrices (Figs.~\ref{fig:model}B, E, \corrmats).
+And while we can directly examine the original text underlying these topic vectors (e.g., Figs.~\ref{fig:precision-detail},~\ref{fig:distinctiveness-detail}) to show how relationships between them reflect real-world behavior, this comparison becomes prohibitively cumbersome at larger timescales.
 To visualize the time-varying high-dimensional content in a more intuitive way~\citep{HeusEtal18a} we projected the topic proportions matrices onto a two-dimensional space using Uniform Manifold Approximation and Projection~\citep[UMAP; ][]{McInEtal18}.
 In this lower-dimensional space, each point represents a single video or recall event, and the distances between the points reflect the distances between the events' associated topic vectors (Fig.~\ref{fig:trajectory}).
-In other words, events that are near to each other in this space are more semantically similar.
+In other words, events that are nearer to each other in this space are more semantically similar, and those that are farther apart are less so.
 
@@
 The video's trajectory is shown in black for reference.
-(Same format and coloring as Panel A.)}
+Here, events (dots) are colored by their matched video event (Panel A).}
 \label{fig:trajectory}
 \end{figure}
-% ------ NOTE: ------
-% will update trajectory fig when new version is finished
-% - Paxton
 
@@
 Differences in the numbers of remembered events appear in participants' trajectories as differences in the sampling resolution along the trajectory.
-We note that this framework also provides a means of detangling classic ``proportion recalled'' measures (i.e., the proportion of video events referenced in participants' recalls) from participants' abilities to recapitulate the full shape of the original video (i.e., the similarity in the shape of the original video trajectory and that defined by each participant's recounting of the video).
+We note that this framework also provides a means of disentangling classic ``proportion recalled'' measures (i.e., the proportion of video events described in participants' recalls) from participants' abilities to recapitulate the overall unfolding of the original video's content (i.e., the similarity between the shapes of the original video trajectory and that defined by each participant's recounting of the video).
+% ------ NOTE: ------
+% not sure it's accurate to use "topic space" in paragraph above.  These analyses were all conducted in the 2D manifold space
+% - Paxton
 
-Because our analysis framework projects the dynamic video content and participants' recalls onto a shared topic space, and because the dimensions of that space are known (i.e., each topic dimension is a set of weights over words in the vocabulary; Fig.~\topics), we can examine the topic trajectories to understand which specific content was remembered well (or poorly).
-For each video event, we can ask: what was the average correlation (across participants) between the video event's topic vector and the closest matching recall event topic vectors from each participant?
-This yields a single correlation coefficient for each video event, describing how closely participants' recalls of the event tended to reliably capture its content (Fig.~\ref{fig:topics}A).
-Given this summary of which events were recalled reliably (or not), we next asked whether the better-remembered or worse-remembered events tended to reflect particular topics.
-We computed a weighted average of the topic vectors for each video event, where the weights reflected how reliably each event was recalled.
+The results displayed in Figures \ref{fig:list-learning}C and \ref{fig:precision-detail}A suggest that certain events were remembered better than others.
+Given this, we next asked asked whether the events were generally remembered well or poorly tended to reflect particular content.
+Because our analysis framework projects the dynamic video content and participants' recalls into a shared space, and because the dimensions of that space represent topics (which are, in turn, sets of weights over words in the vocabulary), we are able to recover the weighted combination of words that make up any point (i.e., topic vector) in this space.
+We first computed the average precision with which participants recalled each of the 30 video events (Fig.~\ref{fig:topics}A; note that this result is analogous to a serial position curve created from our continuous recall quality metric).
+We then computed a weighted average of the topic vectors for each video event, where the weights reflected how reliably each event was recalled.
 To visualize the result, we created a ``wordle'' image~\citep{MuelEtal18} where words weighted more heavily by better-remembered topics appear in a larger font (Fig.~\ref{fig:topics}B, green box).
@@
 Here in computing the weighted average over events' topic vectors, we weighted each event in \textit{inverse} proportion to how well it was remembered (Fig.~\ref{fig:topics}B, red box).
-The least well-remembered video content reflected information not necessary to conveying the video's ``gist," such as the proper names of relatively minor characters (e.g., ``Mike," ``Molly," and ``Lestrade") and locations (e.g., ``St.
-Bartholomew's Hospital"), as well as the brief, animated clip participants viewed at the beginning of each of the two scan session (involving ``singing" ``cartoon" characters).
+The least well-remembered video content reflected information not necessary to later convey a general summary of the video, such as the proper names of relatively minor characters (e.g., ``Mike," ``Molly," and ``Lestrade") and locations (e.g., ``St.
+Bartholomew's Hospital").
+%, as well as the brief, animated clip participants viewed at the beginning of each of the two scan session (involving ``singing" ``cartoon" characters).
 
@@
 \includegraphics[width=1\textwidth]{figs/topics}
-\caption{\small \textbf{Transforming experience into memory.} \textbf{A.} Average correlations (across participants) between the topic vectors from each video event and the closest-matching recall events.
+\caption{\small \textbf{Transforming experience into memory.} \textbf{A.} Average precision (video event-recall event topic vector correlation) across participants for each video event.
 Error bars denote bootstrap-derived across-participant 95\% confidence intervals.
@@
 \end{figure}
-% ------ NOTE: ------
-% will also update this fig when new version is finished
-% - Paxton
 
@@
 Here, for each of the three best- and worst-remembered video events, we have constructed two wordles: one from the original video event's topic vector (left) and a second from the average recall topic vector for that event (right).
-The three best-remembered events (circled in green) correspond to scenes important to the central plot-line: a mysterious figure spying on John in a phone booth; John and Sherlock discussing the murders in their apartment; and Sherlock laying a trap to catch the murderer.
-Meanwhile, the three worst-remembered events (circled in red) reflect scenes that are non-essential to summarizing the narrative's structure: the two appearances of singing cartoon characters; Molly watching as Sherlock beats a corpse in the morgue; and Sherlock noticing evidence of Anderson's and Donovan's affair.
+The three best-remembered events (circled in green) correspond to scenes important to the central plot-line: a mysterious figure spying on John in a phone booth; John meeting Sherlock at Baker St.
+to discuss the murders; and Sherlock laying a trap to catch the killer.
+Meanwhile, the three worst-remembered events (circled in red) reflect scenes that are non-essential to summarizing the narrative's structure: the video of singing cartoon characters participants viewed prior to the main episode; John asking Molly about Sherlock's habit of over-analyzing people; and Sherlock noticing evidence of Anderson's and Donovan's affair.
 
 The results thus far inform us about which aspects of the dynamic content in the episode participants watched were preserved or altered in participants' memories of the episode.
-We next carried out a series of analyses aimed at understanding which brain structures might implement these processes.
-In one analysis we sought to identify which brain structures were sensitive to the video's dynamic content, as characterized by its topic trajectory.
-Specifically, we used a searchlight procedure to identify the extent to which each cluster of voxels exhibited a timecourse of activity (as the participants watched the video) whose temporal correlation matrix matched the temporal correlation matrix of the original video's topic proportions (Fig.~\ref{fig:model}B).
-As shown in Figure~\ref{fig:brainz}A, the analysis revealed a network of regions including bilateral frontal cortex and cingulate cortex, suggesting that these regions may play a role in processing information relevant to the narrative structure of the video.
-In a second analysis, we sought to identify which brain structures' responses (while viewing the video) reflected how each participant would later \textit{recall} the video.
-We used an analogous searchlight procedure to identify clusters of voxels whose temporal correlation matrices reflected the temporal correlation matrix of the topic proportions for each individual's recalls (Figs.~\ref{fig:model}D, \corrmats).
-As shown in Figure~\ref{fig:brainz}B, the analysis revealed a network of regions including the ventromedial prefrontal cortex (vmPFC), anterior cingulate cortex (ACC), and right medial temporal lobe (rMTL), suggesting that these regions may play a role in transforming each individual's experience into memory.
+We next carried out a series of analyses aimed at understanding which brain structures might facilitate these preservations and alterations as the explicit content of the video was transformed into participants' memories.
+In one analysis we sought to identify brain structures that were sensitive to the dynamic unfolding of the video's content, as characterized by its topic trajectory.
+Specifically, we used a searchlight procedure to identify clusters of voxels whose proximal temporal correlation matrix of activity (as participants watched the video) matched the proximal temporal correlation matrix of original video's topic proportions (Fig.~\ref{fig:brainz}A; see \textit{Methods} for additional details).
+We then performed a phase shift-based permutation correction to ensure our searchlight procedure identified regions specifically sensitive to the temporal structure of the video (i.e., rather than those with an autocorrelation length similar to the video; see \textit{Methods}).
+We $z$-scored the searchlight results at each voxel against the null distribution of (100) permuted searchlight results, thresholding at $p=0.05$.
+As shown in Figure~\ref{fig:brainz}C, the analysis revealed a distributed network of regions including \textbf{\textit{????}}, suggesting that these regions may play a role in processing information relevant to the narrative structure of the video.
+In a second analysis, we sought to identify which brain structures' responses (while viewing the video) reflected how each participant would later structure their \textit{recall} of the video.
+We used an analogous searchlight procedure and permutation correction to identify clusters of voxels whose proximal temporal correlation matrices reflected the proximal temporal correlation matrix of the topic proportions for each individual's recall (Figs.~\ref{fig:brainz}B; see \textit{Methods} for additional details).
+As shown in Figure~\ref{fig:brainz}D, the analysis revealed a network of regions including \textbf{\textit{????}}, suggesting that these regions may play a role in transforming each individual's experience into memory.
 In identifying regions whose responses to ongoing experiences reflect how those experiences will be remembered later, this latter analysis extends classic \textit{subsequent memory analyses}~\citep[e.g.,][]{PallWagn02} to domain of naturalistic stimuli.
 % ------ NOTE: ------
-% Searchlight results and figure need to be updated once analysis is re-run
+% Potentially need to fill in ????s with names of structures? But maybe not; better to leave without inference because of neurosynth analysis?
 % - Paxton
@@
 \includegraphics[width=1\textwidth]{figs/searchlights}
-\caption{\small \textbf{Brain structures that underlie the transformation of experience into memory.} \textbf{A.} We searched for regions whose responses (as participants watched the video) matched the temporal correlation matrix of the video topic proportions.
-These regions are sensitive to the narrative structure of the video.
-\textbf{B.} We searched for regions whose responses (as participants watched the video) matched the temporal correlation matrix of the topic proportions derived from each individual's later recall of video.
-These regions are sensitive to how the narrative structure of the video is transformed into a memory of the video.
-Both panels: the maps are thresholded at $p < 0.05$, corrected.}
+\caption{\small \textbf{Brain structures that underlie the transformation of experience into memory.} \textbf{A.} We isolated the proximal diagonals from the upper triangle of the video correlation matrix, and applied this same diagonal mask to the voxel response correlation matrix for each cube of voxels in the brain.
+We then searched for brain regions whose activation timeseries consistently exhibited a similar proximal correlational structure to the video model, across participants.
+\textbf{B.} We used dynamic time warping \citep{BernClif94} to align each participant's recall timeseries to the TR timeseries of the video.
+We then applied the same diagonal mask used in Panel A to isolate the proximal temporal correlations and searched for brain regions whose activation timeseries for an individual consistently exhibited a similar proximal correlational structure to each individual's recall.
+\textbf{C.} We identified a network of regions sensitive to the narrative structure of participants' ongoing experience.
+The map shown is thresholded at at $p < 0.05$, corrected.
+\textbf{D}.
+We also identified a network or regions sensitive to how individuals would later structure the video's content in their recalls.
+The map shown is thresholded at at $p < 0.05$, corrected.}
 \label{fig:brainz}
 \end{figure}
+
+The set of searchlight analyses described above yielded two distributed networks of brain regions, whose activity timecourses mirrored to the temporal structure of the video (Fig.~\ref{fig:brainz}C) or participants' eventual recalls (Fig.~\ref{fig:brainz}D).
+As an exploratory analysis, we sought to identify structures comprised these networks and what functions are shared among them.
+To accomplish this in a blind, unbiased manner (i.e., without reverse inference via visual observation) we used \texttt{Neurosynth} \citep{YarkEtal11}.
+\texttt{Neurosynth} parses a massive online database of over 14,000 neuroimaging studies and constructs meta-analysis images for over 13,000 psychology- and neuroscience-related terms based on NIfTI images accompanying studies where those terms appear at a high frequency.
+Given a novel image tagged with its value type (e.g., $t$-, $F$- or $p$-statistics), \texttt{Neurosynth} can then \textit{decode} the list of terms whose meta-analysis images are most similar.
+We constructed brain maps of voxelwise $p$-values derived from our permutation correction (masking voxels with a corresponding permutation-derived $z$-score at or below zero).
+These maps describe the extent to which each voxel specifically reflected the temporal structure of the video or individuals' recalls (i.e., for each voxel, the percentage of phase-shifted topic vector correlation matrices to which the voxel activity correlation matrix was less similar).
+These $p$-value maps for the video- and recall-driven searchlight analyses are displayed in Figure \ref{fig:neurosynth}, along with the top ten terms decoded from each using \texttt{Neurosynth}.
 
@@
 \includegraphics[width=1\textwidth]{figs/neurosynth_decoding}
-\caption{\small \textbf{INSERT CAPTION HERE}}
-\label{fig:brainz}
+\caption{\small \textbf{Decoding distributed statistical maps via Neurosynth meta-analyses.} \textbf{A.} Video-searchlight $p$-map and top 10 decoded terms.
+We constructed a map of the permutation-derived $p$-values for the video-driven searchlight analysis (Fig.~\ref{fig:brainz}A, C) for all voxels with a positive permutation-derived $z$-score.
+The top 10 terms decoded from this $p$-map are shown in red.
+\textbf{B.} Recall-searchlight $p$-map and top 10 decoded terms.
+We constructed a map of the permutation-derived $p$-values for the recall-driven searchlight analysis (Fig.~\ref{fig:brainz}B, D) for all voxels with a positive permutation-derived $z$-score.
+The top 10 terms decoded from this $p$-map are shown in blue.}
+\label{fig:neurosynth}
 \end{figure}

### 2020-02-05 paper/main.tex
WIP discussion updates

@@
 
-The results thus far inform us about which aspects of the dynamic content in the episode participants watched were preserved or altered in participants' memories of the episode.
-We next carried out a series of analyses aimed at understanding which brain structures might facilitate these preservations and alterations as the explicit content of the video was transformed into participants' memories.
-In one analysis we sought to identify brain structures that were sensitive to the dynamic unfolding of the video's content, as characterized by its topic trajectory.
-Specifically, we used a searchlight procedure to identify clusters of voxels whose proximal temporal correlation matrix of activity (as participants watched the video) matched the proximal temporal correlation matrix of original video's topic proportions (Fig.~\ref{fig:brainz}A; see \textit{Methods} for additional details).
-We then performed a phase shift-based permutation correction to ensure our searchlight procedure identified regions specifically sensitive to the temporal structure of the video (i.e., rather than those with an autocorrelation length similar to the video; see \textit{Methods}).
-We $z$-scored the searchlight results at each voxel against the null distribution of (100) permuted searchlight results, thresholding at $p=0.05$.
-As shown in Figure~\ref{fig:brainz}C, the analysis revealed a distributed network of regions including \textbf{\textit{????}}, suggesting that these regions may play a role in processing information relevant to the narrative structure of the video.
-In a second analysis, we sought to identify which brain structures' responses (while viewing the video) reflected how each participant would later structure their \textit{recall} of the video.
-We used an analogous searchlight procedure and permutation correction to identify clusters of voxels whose proximal temporal correlation matrices reflected the proximal temporal correlation matrix of the topic proportions for each individual's recall (Figs.~\ref{fig:brainz}B; see \textit{Methods} for additional details).
-As shown in Figure~\ref{fig:brainz}D, the analysis revealed a network of regions including \textbf{\textit{????}}, suggesting that these regions may play a role in transforming each individual's experience into memory.
+The results thus far inform us about which aspects of the dynamic content in the episode participants watched were preserved or altered in participants' memories.
+We next carried out a series of analyses aimed at understanding which brain structures might facilitate these preservations and transformations between the external world and memory.
+In one analysis, we sought to identify brain structures that were sensitive to the dynamic unfolding of the video's content, as characterized by its topic trajectory.
+We used a searchlight procedure to identify clusters of voxels whose activity patterns displayed a proximal temporal correlation structure (as participants watched the video) matching that of the original video's topic proportions (Fig.~\ref{fig:brainz}A; see \textit{Methods} for additional details).
+In a second analysis, we sought to identify brain structures whose responses (during video viewing) reflected how each participant would later structure their \textit{recalls} of the video.
+We used an analogous searchlight procedure to identify clusters of voxels whose proximal temporal correlation matrices matched that of the topic proportions for each individual's recall (Figs.~\ref{fig:brainz}B; see \textit{Methods} for additional details).
+To ensure our searchlight procedure identified regions \textit{specifically} sensitive to the temporal structure of the video or recalls (i.e., rather than those with a temporal autocorrelation length similar to that of the video/recalls), we performed a phase shift-based permutation correction (see \textit{Methods} for additional details).
+Specifically, we circularly shifted the timeseries of the topic trajectory by a random number of timepoints, recomputed the shifted trajectory's correlation matrix, and again performed our searchlight analysis on this permuted data.
+We then $z$-scored the ``real" searchlight results at each voxel against the null distribution of (100) permuted results.
+In Figure~\ref{fig:brainz}, only voxels whose activity pattern reflected the ``real" video/recall timeseries more closely than 95\% of the permuted results are shown.
+As shown in Figure~\ref{fig:brainz}C, the video-driven searchlight analysis revealed a distributed network of regions including \textbf{\textit{????}}, suggesting that these regions may play a role in processing information relevant to the narrative structure of the video.
+As shown in Figure~\ref{fig:brainz}D, the analysis revealed a network of regions including \textbf{\textit{????}}, suggesting that these regions facilitate a person-specific transformation of one's experience into memory.
 In identifying regions whose responses to ongoing experiences reflect how those experiences will be remembered later, this latter analysis extends classic \textit{subsequent memory analyses}~\citep[e.g.,][]{PallWagn02} to domain of naturalistic stimuli.
@@
 
-The set of searchlight analyses described above yielded two distributed networks of brain regions, whose activity timecourses mirrored to the temporal structure of the video (Fig.~\ref{fig:brainz}C) or participants' eventual recalls (Fig.~\ref{fig:brainz}D).
-As an exploratory analysis, we sought to identify structures comprised these networks and what functions are shared among them.
-To accomplish this in a blind, unbiased manner (i.e., without reverse inference via visual observation) we used \texttt{Neurosynth} \citep{YarkEtal11}.
-\texttt{Neurosynth} parses a massive online database of over 14,000 neuroimaging studies and constructs meta-analysis images for over 13,000 psychology- and neuroscience-related terms based on NIfTI images accompanying studies where those terms appear at a high frequency.
-Given a novel image tagged with its value type (e.g., $t$-, $F$- or $p$-statistics), \texttt{Neurosynth} can then \textit{decode} the list of terms whose meta-analysis images are most similar.
-We constructed brain maps of voxelwise $p$-values derived from our permutation correction (masking voxels with a corresponding permutation-derived $z$-score at or below zero).
-These maps describe the extent to which each voxel specifically reflected the temporal structure of the video or individuals' recalls (i.e., for each voxel, the percentage of phase-shifted topic vector correlation matrices to which the voxel activity correlation matrix was less similar).
-These $p$-value maps for the video- and recall-driven searchlight analyses are displayed in Figure \ref{fig:neurosynth}, along with the top ten terms decoded from each using \texttt{Neurosynth}.
+The searchlight analyses described above yielded two distributed networks of brain regions, whose activity timecourses mirrored to the temporal structure of the video (Fig.~\ref{fig:brainz}C) or participants' eventual recalls (Fig.~\ref{fig:brainz}D).
+We next sought to gain greater insight into the structures and functional networks our results reflected.
+To accomplish this in a blind, unbiased manner (i.e., without reverse inference via visual observation) we performed an additional, exploratory analysis using \texttt{Neurosynth} \citep{YarkEtal11}.
+\texttt{Neurosynth} parses a massive online database of over 14,000 neuroimaging studies and constructs meta-analysis images for over 13,000 psychology- and neuroscience-related terms, based on NIfTI images accompanying studies where those terms appear at a high frequency.
+Then, given a novel image (tagged with its value type; e.g., $t$-, $F$- or $p$-statistics), \texttt{Neurosynth} returns a list of terms whose meta-analysis images are most similar to this new data.
+Our permutation procedure (described above) yielded, for each of the two searchlight analyses, a voxelwise map of significance ($p$-statistic) values.
+These maps describe the extent to which each voxel \textit{specifically} reflected the temporal structure of the video or individuals' recalls (i.e., for each voxel, the proportion of phase-shifted topic vector correlation matrices less similar to the voxel activity correlation matrix than the unshifted video's correlation matrix).
+These significance maps for the video- and recall-driven searchlight analyses, along with the 10 terms with maximally similar meta-analysis images identified by \texttt{Neurosynth} are shown in Figure \ref{fig:neurosynth}.
 
@@
 \includegraphics[width=1\textwidth]{figs/neurosynth_decoding}
-\caption{\small \textbf{Decoding distributed statistical maps via Neurosynth meta-analyses.} \textbf{A.} Video-searchlight $p$-map and top 10 decoded terms.
-We constructed a map of the permutation-derived $p$-values for the video-driven searchlight analysis (Fig.~\ref{fig:brainz}A, C) for all voxels with a positive permutation-derived $z$-score.
-The top 10 terms decoded from this $p$-map are shown in red.
-\textbf{B.} Recall-searchlight $p$-map and top 10 decoded terms.
-We constructed a map of the permutation-derived $p$-values for the recall-driven searchlight analysis (Fig.~\ref{fig:brainz}B, D) for all voxels with a positive permutation-derived $z$-score.
-The top 10 terms decoded from this $p$-map are shown in blue.}
+\caption{\small \textbf{Decoding distributed statistical maps via Neurosynth meta-analyses.} \textbf{A.} Video-searchlight significance and top 10 decoded terms.
+We constructed a map of the permutation-derived $p$-values for the video-driven searchlight analysis (Fig.~\ref{fig:brainz}A, C) at each voxel with a positive permutation-derived $z$-score.
+The top 10 terms decoded from this significance map are shown in red.
+\textbf{B.} Recall-searchlight significance and top 10 decoded terms.
+We constructed a map of the permutation-derived $p$-values for the recall-driven searchlight analysis (Fig.~\ref{fig:brainz}A, C) at each voxel with a positive permutation-derived $z$-score.
+The top 10 terms decoded from this significance map are shown in blue.}
 \label{fig:neurosynth}
@@
 So called \textit{inter-subject correlation} (ISC) and \textit{inter-subject functional connectivity} (ISFC) analyses effectively treat other people's brain responses to the stimulus as a ``model'' of how its features change over time.
-By contrast, in our present work we used topic models and HMMs to construct an explicit stimulus model (i.e., the topic trajectory of the video).
-When we searched for brain structures whose responses are consistent with the video's topic trajectory, we identified a network of structures that overlapped strongly with the ``long temporal receptive window'' network reported by the Hasson group~\citep[e.g., compare our Fig.~\ref{fig:brainz}A with the map of long temporal receptive window voxels in][]{LernEtal11}.
-This provides support for the notion that part of the long temporal receptive window network may be maintaining an explicit model of the stimulus dynamics.
-When we performed a similar analysis after swapping out the video's topic trajectory with the recall topic trajectories of each individual participant, this allowed us to identify brain regions whose responses (as the participants viewed the video) reflected how the video trajectory would be transformed in memory (as reflected by the recall topic trajectories).
-The analysis revealed that the rMTL and vmPFC may play a role in this person-specific transformation from experience into memory.
-The role of the MTL in episodic memory encoding has been well-reported~\citep[e.g., ][]{PallWagn02, DavaEtAl03, RangEtal04a, Dava06, WiltSilv07, DianEtal07, KestEtal13}.
-Prior work has also implicated the medial prefrontal cortex in representing ``schema'' knowledge~\citep[i.e., general knowledge about the format of an ongoing experience given prior similar experiences; ][]{KestEtal12, KestEtal13, SchlPres15, GilbMarl17, SpalEtal18}.
-Integrating across our study and this prior work, one interpretation is that the person-specific transformations mediated (or represented) by the rMTL and vmPFC may reflect schema knowledge being leveraged, formed, or updated, incorporating ongoing experience into previously acquired knowledge.
+By contrast, in our present work we used topic models to construct an explicit content model directly from the stimulus (i.e., the topic trajectory of the video).
+Projecting each participant's recall into a space shared by both the stimulus and other participants then allows us to compare recalls both directly to the stimulus and to each other.
+Similarly, prior work introducing the use of HMMs to discover latent event structure in naturalistic stimuli and recall \citep{BaldEtal17} used a between-subjects cross-validation approach to identify event boundaries shared across participants, and between stimulus and recall.
+Our framework allows us to break from the restriction of a common, shared event-timeseries and identify the unique \textit{resolution} of each participant's recall event structure, and how that may differ from the video and each other.
+% @JEREMY @ANDY PLEASE CHECK THIS TO MAKE SURE I'M NOT MISCHARACTERIZING BALDETAL17
+
+In extending classical free recall analyses to our naturalistic memory framework, we recovered two patterns of recall dynamics central to list-learning studies: a heightened probability of initiating recall with the first presented ``item" (in our case, video events; Fig.~\ref{fig:list-learning}A) and a strong bias toward transitioning from recalling a given event to recalling the one immediately following it (Fig.~\ref{fig:list-learning}B).
+However, equally noteworthy are the typical free recall results \textit{not} recovered in these analyses, as each highlights a fundamental difference between the list-learning paradigm and naturalistic memory paradigms like the one employed in the present study.
+The most noticeable departure from hallmark free recall dynamics in these findings is the apparent lack of a serial position effect in Figure \ref{fig:list-learning}C, which instead shows greater and lesser recall probabilities for events distributed across the video.
+Stimuli in free recall experiments most often comprise lists of simple, common words, presented to participants in a random order.
+\citep[In fact, numerous word pools have been developed based on these criteria; e.g.,][]{FrieEtal82}.
+These stimulus qualities enable two assumptions that are central to word list analyses, but frequently do not hold for real-world experiences.
+First, researchers conducting free recall studies may assume that the content at each presentation index is essentially equal, and does not possess attributes that would render it, on average, more or less memorable than others.
+Such is rarely the case with real-world experiences or experiments meant to approximate them, and the effects of both intrinsic and observer-dependent factors on stimulus memorability are well established \citep[for review see][]{ChunTurk07, ByliEtal15, TyngEtal17}.
+Second, the random ordering of list items ensures that (across participants, on average) there is no relationship between the thematic similarity of individual stimuli and their presentation positions---in other words, two successively presented items are no more likely to be highly semantically similar than they are to be high dissimilar.
+In most cases, the exact opposite is true of real-world episodes.
+Our internal thoughts, our actions, and the physical state of the world around us all tend to follow a direct, causal progression.
+As a result, each moment of our experience tends to be inherently more similar to surrounding moments than to those in the distant past or future.
+Memory literature has termed this strong temporal autocorrelation ``context," and in various media that depict real-world events (e.g., movies or written stories), we recognize it as a \textit{narrative structure}.
+While a random word list (by definition) has no such structure, the logical progression between ideas and actions in a naturalistic stimulus prompts the rememberer to recount presented events in order, starting with the beginning.
+This tendency is reflected in our findings' second departure from typical free recall dynamics: a lack of increased probability of first recall for end-of-sequence events (Fig.~\ref{fig:list-learning}A).
+
+Because they disregard presentation order-dependent variability in the stimulus content, analyses such as those in Figure \ref{fig:list-learning} enable a more sensitive analysis of presentation order-dependent temporal dynamics in free recall.
+Yet by the same token, they paint a wholly incomplete picture of memory for naturalistic episodes.
+In an attempt to address this shortcoming, we have developed a framework in the present study that characterizes the explicit semantic content of the stimulus and subsequent recalls.
+However, sensitivity to stimulus and recall content introduces a new challenge: distinguishing between levels of recall quality for a stimulus (e.g., an event) that is considered to have been ``remembered."  When modeling memory in an experimental setting, recall quality for individual events is often cast as binary (e.g., a given list item was simply either remembered or not remembered).
+Various models of memory (e.g., \citealp{Yone02}) attempt to improve upon this by including confidence ratings, rendering this binary judgement instead categorical.
+To better evaluate naturalistic memory quality, we introduce a continuous metric (\textit{precision}), which reflects the level of completeness of a participant's recall for a feature-rich experience.
+Additionally, recall quality for a single event is typically assessed independently from that for all other events (e.g., it is difficult to ``compare" a participant's binary recall success for list item 1 to that of list item 10).
+The second novel metric we introduce (\textit{distinctiveness}) is based on analyzing of the correlational structure of an individual's full set of recall events, and reflects the specificity of their memory for a single experienced event.
+We find that the successful memory performance is related to 1) the precision with which the participant recounts each event and 2) the distinctiveness of each recall event (relative to the other recalled events).
+The first finding suggests that the information retained for \textit{any individual event} may predict the overall amount of information retained by the participant.
+The second finding suggests that the ability to distinguish between temporally or semantically similar content is also related to the quantity of content recovered.
+Intriguingly, prior studies show that pattern separation, or the ability to discriminate between similar experiences, is impaired in many cognitive disorders as well as natural aging \citep{StarEtal10, YassEtal11c, YassStar11b}.
+Future work might explore whether and how these metrics compare between cognitively impoverished groups and healthy controls.
+
+While a large number of language models exist \citep[e.g., WAS, LSA, word2vec, universal sentence encoder;][]{SteyEtal04, LandEtal98, MikoEtal13, CerEtal18}, here we use latent dirichlet allocation (LDA)-based topic models for a few reasons.
+First, topic models capture the \textit{essence} of a text passage devoid of the specific set and order of words used.
+This was an important feature of our model since different people may accurately recall a scene using very different language.
+Second, words can mean different things in different contexts (e.g.
+``bat" may be the act of hitting a baseball, the object used for that action, or as a flying mammal).
+Topic models are robust to this, allowing words to exist as part of multiple topics.
+Last, topic models provide a straightforward means to recover the weights for the particular words comprising a topic, enabling easy interpretation of an event's contents (e.g.
+Fig.~\ref{fig:topics}).
+Other models such as Google's Universal Sentence Encoder offer a context-sensitive encoding of text passages, but the encoding space is complex and non-linear, and thus recovering the original words used to fit the model is not straightforward.
+However, it's worth pointing out that our framework is divorced from the particular choice of language model.
+Moreover, many of the aspects of our framework could be swapped out for other choices.
+For example, the language model, the timeseries segmentation model and the video-recall matching function could all be customized for the particular problem.
+Indeed for some problems, recovery of the particular recall words may not be necessary, and thus other text-modeling approaches (such as universal sentence encoder) may be preferable.
+Future work will explore the influence of particular model choices on the framework's efficacy.
+
+When we searched for brain structures whose responses are consistent with the video and recall topic trajectories, we identified two diffuse networks of regions \textbf{\textit{INSERT SOME BETTER COMMENTARY HERE}} (Fig.~\ref{fig:brainz}C,D).
+Decoding the significance maps (Fig.~\ref{fig:neurosynth}) revealed two interesting results.
+The significant
+
 % Here's a bunch of citations to possibly add to this last sentence, though not sure if we should because the sentence is framed as a "new idea" to come out of this study:
@@
 % -Paxton
-
-In extending classical free recall analyses to our naturalistic memory framework, we recovered two patterns of recall dynamics central to list-learning studies: a high probability of initiating recall with the first video event (Fig.~\ref{fig:list-learning}A) and a strong bias toward transitioning from recalling a given event to recalling the event immediately following it (Fig.~\ref{fig:list-learning}B).
-However, equally noteworthy are the typical free recall results not recovered in these analyses, as each highlights a fundamental difference between list-learning studies and naturalistic memory paradigms like the one employed in the present study.
-The most noticeable departure from hallmark free recall dynamics in these findings is the apparent lack of a serial position effect in Figure \ref{fig:list-learning}C, which instead shows greater and lesser recall probabilities for events distributed across the video stimulus.
-Stimuli in free recall experiments most often comprise lists of simple, common words, presented to participants in a random order.
-\citep[In fact, numerous word pools have been developed based on these criteria; e.g.,][]{FrieEtal82}.
-These stimulus qualities enable two assumptions that are central to word list analyses, but frequently do not hold for real-world experiences.
-First, researchers conducting free recall studies may assume that the content at each presentation index is essentially equal, and does not bear qualities that would cause participants to remember it more or less successfully than others.
-Such is rarely the case with real-world experiences or experiments meant to approximate them, and the effects of both intrinsic and observer-dependent factors on stimulus memorability are well established \citep[for review see][]{ChunTurk07, ByliEtal15, TyngEtal17}.
-Second, the random ordering of list items ensures that (across participants, on average) there is no relationship between the thematic similarity of individual stimuli and their presentation positions---in other words, two semantically related words are no more likely to be presented next to each other than at opposite ends of the list.
-In most cases, the exact opposite is true of real-world episodes.
-Our internal thoughts, our actions, and the physical state of the world around us all tend to follow a direct, causal progression.
-As a result, each moment of our experience tends to be inherently more similar to surrounding moments than to those in the distant past or future.
-Memory literature has termed this strong temporal autocorrelation ``context," and in various media that depict real-world events (e.g., movies and written stories), we recognize it as a \textit{narrative structure}.
-While a random word list (by definition) has no such structure, the logical progression between ideas and actions in a naturalistic stimulus prompts the rememberer to recount presented events in order, starting with the beginning.
-This tendency is reflected in our findings' second departure from typical free recall dynamics: a lack of increased probability of first recall for end-of-sequence events (Fig.~\ref{fig:list-learning}A).
-
-Thus, analyses such as those in Figure \ref{fig:list-learning} that address only the temporal dynamics of free recall paint an incomplete picture of memory for naturalistic episodes.
-While useful for studying presentation order-dependent recall dynamics, they neglect to consider the stimuli's content (or, for example, that content's potential interrelatedness).
-However, sensitivity to stimulus and recall content introduces a new challenge: distinguishing between levels of recall quality for a stimulus (i.e., an event) that is considered to have been ``remembered."  When modeling memory experiments, often times events (or items) and their later memories are treated as binary and independent events (e.g., a given list item was simply either remembered or not remembered).
-Various models of memory (e.g., \citealp{Yone02}) attempt to improve upon this by including confidence ratings, rendering this binary judgement instead categorical.
-Our novel framework allows one to assess memory performance in a more continuous way (\textit{precision}), as well as analyze the correlational structure of each encoding event to each memory event (\textit{distinctiveness}).
-Further and importantly, these two novel metrics we introduce here arise from comparisons of the actual content of the experience/memories, which is not typically modeled.
-Leveraging this, we find that the successful memory performance is related to 1) the precision with which the participant recounts each event and 2) the distinctiveness of each recall event (relative to the other recalled events).
-The first finding suggests that the information retained for \textit{any individual event} may predict the overall amount of information retained by the participant.
-The second finding suggests that the ability to distinguish between temporally or semantically similar content is also related to the quantity of content recovered.
-Intriguingly, prior studies show that pattern separation, or the ability to discriminate between similar experiences, is impaired in many cognitive disorders as well as natural aging \citep{StarEtal10, YassEtal11c, YassStar11b}.
-Future work might explore whether and how these metrics compare between cognitively impoverished groups and healthy controls.
-% ------ NOTE: ------
-% need to update text here to reflect new distinctivness stats in precision/distinctiveness fig
-% - Paxton
-
-% NOTE: do you know of a good reference for WAS and word2vec ?
-% SteyEtal04 = WAS; MikoEtal13 = word2vec
-% -Paxton
-While a large number of language models exist \citep[e.g., WAS, LSA, word2vec, universal sentence encoder;][]{SteyEtal04, LandEtal98, MikoEtal13, CerEtal18}, here we use latent dirichlet allocation (LDA)-based topic models for a few reasons.
-First, topic models capture the \textit{essence} of a text passage devoid of the specific set and order of words used.
-This was an important feature of our model since different people may accurately recall a scene using very different language.
-Second, words can mean different things in different contexts (e.g.
-``bat" as the act of hitting a baseball, the object used for that action, or as a flying mammal).
-Topic models are robust to this, allowing words to exist as part of multiple topics.
-Last, topic models provide a straightforward means to recover the weights for the particular words comprising a topic, enabling easy interpretation of an event's contents (e.g.
-Fig.~\ref{fig:topics}).
-Other models such as Google's universal sentence encoder offer a context-sensitive encoding of text passages, but the encoding space is complex and non-linear, and thus recovering the original words used to fit the model is not straightforward.
-However, it's worth pointing out that our framework is divorced from the particular choice of language model.
-Moreover, many of the aspects of our framework could be swapped out for other choices.
-For example, the language model, the timeseries segmentation model and the video-recall matching function could all be customized for the particular problem.
-Indeed for some problems, recovery of the particular recall words may not be necessary, and thus other text-modeling approaches (such as universal sentence encoder) may be preferable.
-Future work will explore the influence of particular model choices on the framework's accuracy.
 

### 2020-02-06 paper/main.tex
finished discussion revision

@@
 Three topic dimensions are shown (the highest-weighted topics for each of the three example scenes, respectively).
-We also show the ten highest-weighted words for each topic.
+We also show the 10 highest-weighted words for each topic.
 Figure~\topics~provides a full list of the top 10 words from each of the discovered topics.}
@@
 \textbf{C.} The correlation between distinctiveness and hand-annotated memory performance.
-\textbf{D.} The correlation between precision and the number of events recovered by the model ($k$).
-\textbf{E.} The correlation between distinctiveness and the number of events recovered by the model ($k$).}
+\textbf{D.} The correlation between precision and the number of video events successfully recalled, as determined by our model.
+\textbf{E.} The correlation between distinctiveness and the number of video events successfully recalled, as determined by our model.}
   \label{fig:precision-distinctiveness}
@@
 Participants whose recall events are more veridical descriptions of what happened in the video event will presumably have higher precision scores.
-We find that, across participants, a higher precision score is correlated to both hand-annotated memory performance (Pearson's $r(15) = 0.56, p = 0.021$) and the number of recall events estimated by our model (Pearson's $r(15) = 0.85, p < 0.001$).
+We find that, across participants, a higher precision score is correlated to both hand-annotated memory performance (Pearson's $r(15) = 0.56, p = 0.021$) and the number of video events successfully remembered, as determined by our model (Pearson's $r(15) = 0.88, p < 0.001$).
 We also hypothesized that participants who recounted events in a more distinctive way would display better overall memory.
-We find that this distinctiveness score is related to our model's estimated number of recalled events (Pearson's $r(15) = 0.53, p = 0.028$), and while we do not find distinctiveness to be related to hand-annotated memory performance (Pearson's $r(15) = 0.28, p = 0.275$), this is not entirely surprising given how the hand-annotated memory scores were computed (see \textit{Methods}).
+We find that this distinctiveness score is related to our model's estimated number of recalled events (Pearson's $r(15) = 0.55, p = 0.021$), and while we do not find distinctiveness to be related to hand-annotated memory performance (Pearson's $r(15) = 0.28, p = 0.275$), this is not entirely surprising given how the hand-annotated memory scores were computed (see \textit{Methods}).
 
@@
 The second novel metric we introduce (\textit{distinctiveness}) is based on analyzing of the correlational structure of an individual's full set of recall events, and reflects the specificity of their memory for a single experienced event.
-We find that the successful memory performance is related to 1) the precision with which the participant recounts each event and 2) the distinctiveness of each recall event (relative to the other recalled events).
-The first finding suggests that the information retained for \textit{any individual event} may predict the overall amount of information retained by the participant.
-The second finding suggests that the ability to distinguish between temporally or semantically similar content is also related to the quantity of content recovered.
-Intriguingly, prior studies show that pattern separation, or the ability to discriminate between similar experiences, is impaired in many cognitive disorders as well as natural aging \citep{StarEtal10, YassEtal11c, YassStar11b}.
+We find that both of these metrics relate to the overall number of video events participants successfully recalled, and that our precision metric additionally relates to \cite{ChenEtal17}'s hand-annotated memory memory scores.
+Though we do not find participants' average recall distinctiveness related to the hand-annotated memory scores, this is not entirely surprising given the divergence of behavior they capture.
+In hand-scoring each participant's verbal recall for each of 50 (manually-deliniated) scenes, ``[a] scene was counted as recalled if the participant described any part of the scene" \citep{ChenEtal17}.
+In other words, both an extensive description of a scene's content and a brief mention of some subset of its content were (binarily) considered equally successful recalls.
+By contrast, we identify the event structure in participants' recalls in an unsupervised manner, independent of the video event-timeseries, prior to mapping between video and recall content.
+Our HMM-based event-segmentation produces boundaries between timepoints where the topic proportions shift in a substantial way, and because a small handful of words is unlikely to contribute significantly to the topic proportions for any sliding window, such brief scene descriptions will most often not begat a sufficiently large shift in the resulting topic proportions for the HMM to identify an event boundary.
+Instead, they will be grouped with a neighboring event, consequently lowering that event's distinctiveness score and by extension, the participant's overall distinctiveness score.
+This is in essence the qualitative difference between distinctive and indistinctive recall, and reflects the comparison shown in Figure \ref{fig:distinctiveness-detail}C.
+Intriguingly, prior studies show that pattern separation, or the ability to cleanly discriminate between similar experiences, is impaired in many cognitive disorders as well as natural aging \citep{StarEtal10, YassEtal11c, YassStar11b}.
 Future work might explore whether and how these metrics compare between cognitively impoverished groups and healthy controls.
@@
 
-When we searched for brain structures whose responses are consistent with the video and recall topic trajectories, we identified two diffuse networks of regions \textbf{\textit{INSERT SOME BETTER COMMENTARY HERE}} (Fig.~\ref{fig:brainz}C,D).
-Decoding the significance maps (Fig.~\ref{fig:neurosynth}) revealed two interesting results.
-The significant
+In the analyses outlined in Figure \ref{fig:brainz}, we identified two diffuse networks of brain structures whose responses were consistent with the video and recall topic trajectories, respectively.
+Decoding the associated significance maps with \texttt{Neurosynth} revealed two intriguing results.
+First, the top 10 terms returned for the video-driven searchlight significance map were centered around themes of language and semantic meaning (Fig.~\ref{fig:neurosynth}A).
+In other words, the voxels identified as more reflective of the video's temporal structure (i.e., voxels with lower permutation correction-derived $p$-values), as defined by our model, were most likely to be reported as active in studies focusd on the the neural underpinnings of semantic processing.
+This finding is interesting, as our model specifically captures the temporal structure of the video's \textit{semantic} content (e.g., as opposed to that of the visual, auditory, or affective content).
+This suggests that the network of structures displayed in Figure \ref{fig:brainz}C may play a roll in processing the evolving semantic structure of ongoing experiences.
 
-% Here's a bunch of citations to possibly add to this last sentence, though not sure if we should because the sentence is framed as a "new idea" to come out of this study:
-% Takashima et al., 2007 -- vmPFC involved in stabilizing/reorganizing retrieval networks
-% Tse et al., 2007; Zeithamova and Preston, 2010; Tse et al., 2011 -- vmPFC involved in integrating featurally similar experiences
-% Nieuwenhuis and Takashima, 2011 -- vmPFC activity linked to evaluating memories' relevance to current situation
-% Kuhl et al., 2007; Wimber et al., 2008, 2009, 2011, 2015 -- vmPFC and vlPFC inhibit contextually irrelevant memories during retrieval
-% -Paxton
+Our second searchlight analysis identified a largely separate network of regions (Fig.~\ref{fig:brainz}D) whose patterns of activity as participants viewed the video reflected the idiosyncratic structure of each individual's later recall.
+Decoding the associated significance map yielded a set of terms that primarily reflected names of specific structural regions (such as ``thalamus," ``anterior insula," ``anterior cingulate" and ``inferior frontal"; Fig.~\ref{fig:neurosynth}B).
+Interestingly, these regions share membership in a common, large-scale functional network (termed the ``salience network") involved in detecting and processing affective cues.
+In particular, the latter three regions have been implicated in functions relevant to assigning personal meaning to an experience, including: ascribing subjective value to raw, sensory input \citep{MedfCrit10}; modulating semantic and phonological processing in response to personally salient stimuli \citep{KellEtal07b}; and directing and reallocating attention and working memory resources towards the most relevant stimuli \citep{MenoUddi10}.
+This suggests that the network of structures displayed in Figure \ref{fig:brainz}D may be play a roll in transforming and restructuring ongoing experiences through the lens of one's own personal values as they are encoded in memory.
 
@@
 Each scene was also tagged with its onset and offset time, in both seconds and TRs.
-
-The video was also divided by an independent coder into 50 more broad ``scenes" ``following major shifts in the narrative (e.g., location, topic, and/or time)" \citep{ChenEtal17}.
-The hand-annotated memory scores for each participant we reference in our present study were generated by considering a scene to have been recalled (in a binary fashion) ``if the participant described any part of the scene."
 

### 2020-02-06 paper/main.tex
working on methods

@@
 In Figure~\ref{fig:brainz}, only voxels whose activity pattern reflected the ``real" video/recall timeseries more closely than 95\% of the permuted results are shown.
-As shown in Figure~\ref{fig:brainz}C, the video-driven searchlight analysis revealed a distributed network of regions including \textbf{\textit{????}}, suggesting that these regions may play a role in processing information relevant to the narrative structure of the video.
-As shown in Figure~\ref{fig:brainz}D, the analysis revealed a network of regions including \textbf{\textit{????}}, suggesting that these regions facilitate a person-specific transformation of one's experience into memory.
+As shown in Figure~\ref{fig:brainz}C, the video-driven searchlight analysis revealed a distributed network of regions that may play a role in processing information relevant to the narrative structure of the video.
+Similarly, the recall-driven searchlight analysis revealed a second diffuse network of regions (Fig.~\ref{fig:brainz}D) that may facilitate a person-specific transformation of one's experience into memory.
 In identifying regions whose responses to ongoing experiences reflect how those experiences will be remembered later, this latter analysis extends classic \textit{subsequent memory analyses}~\citep[e.g.,][]{PallWagn02} to domain of naturalistic stimuli.
-% ------ NOTE: ------
-% Potentially need to fill in ????s with names of structures? But maybe not; better to leave without inference because of neurosynth analysis?
-% - Paxton
 
@@
 So called \textit{inter-subject correlation} (ISC) and \textit{inter-subject functional connectivity} (ISFC) analyses effectively treat other people's brain responses to the stimulus as a ``model'' of how its features change over time.
-By contrast, in our present work we used topic models to construct an explicit content model directly from the stimulus (i.e., the topic trajectory of the video).
+By contrast, in our present work, we use topic models to construct an explicit content model directly from the stimulus (i.e., the topic trajectory of the video).
 Projecting each participant's recall into a space shared by both the stimulus and other participants then allows us to compare recalls both directly to the stimulus and to each other.
-Similarly, prior work introducing the use of HMMs to discover latent event structure in naturalistic stimuli and recall \citep{BaldEtal17} used a between-subjects cross-validation approach to identify event boundaries shared across participants, and between stimulus and recall.
-Our framework allows us to break from the restriction of a common, shared event-timeseries and identify the unique \textit{resolution} of each participant's recall event structure, and how that may differ from the video and each other.
+Similarly, prior work introducing the use of HMMs to discover latent event structure in naturalistic stimuli and recall \citep{BaldEtal17} used between-subjects cross-validation to identify event boundaries shared across participants, and between stimulus and recall.
+Our framework allows us to break from the restriction of a common, shared event-timeseries and identify the unique \textit{resolution} of each participant's recall event structure, and how that may differ from the video and that of other participants.
 % @JEREMY @ANDY PLEASE CHECK THIS TO MAKE SURE I'M NOT MISCHARACTERIZING BALDETAL17
+
+While a large number of language models exist \citep[e.g., WAS, LSA, word2vec, universal sentence encoder;][]{SteyEtal04, LandEtal98, MikoEtal13, CerEtal18}, here we use latent dirichlet allocation (LDA)-based topic models for a few reasons.
+First, topic models capture the \textit{essence} of a text passage devoid of the specific set and order of words used.
+This was an important feature of our model since different people may accurately recall a scene using very different language.
+Second, words can mean different things in different contexts (e.g.
+``bat" may be the act of hitting a baseball, the object used for that action, or as a flying mammal).
+Topic models are robust to this, allowing words to exist as part of multiple topics.
+Last, topic models provide a straightforward means to recover the weights for the particular words comprising a topic, enabling easy interpretation of an event's contents (e.g.
+Fig.~\ref{fig:topics}).
+Other models such as Google's Universal Sentence Encoder offer a context-sensitive encoding of text passages, but the encoding space is complex and non-linear, and thus recovering the original words used to fit the model is not straightforward.
+However, it's worth pointing out that our framework is divorced from the particular choice of language model.
+Moreover, many of the aspects of our framework could be swapped out for other choices.
+For example, the language model, the timeseries segmentation model and the video-recall matching function could all be customized for the particular problem.
+Indeed for some problems, recovery of the particular recall words may not be necessary, and thus other text-modeling approaches (such as universal sentence encoder) may be preferable.
+Future work will explore the influence of particular model choices on the framework's efficacy.
 
@@
 Future work might explore whether and how these metrics compare between cognitively impoverished groups and healthy controls.
-
-While a large number of language models exist \citep[e.g., WAS, LSA, word2vec, universal sentence encoder;][]{SteyEtal04, LandEtal98, MikoEtal13, CerEtal18}, here we use latent dirichlet allocation (LDA)-based topic models for a few reasons.
-First, topic models capture the \textit{essence} of a text passage devoid of the specific set and order of words used.
-This was an important feature of our model since different people may accurately recall a scene using very different language.
-Second, words can mean different things in different contexts (e.g.
-``bat" may be the act of hitting a baseball, the object used for that action, or as a flying mammal).
-Topic models are robust to this, allowing words to exist as part of multiple topics.
-Last, topic models provide a straightforward means to recover the weights for the particular words comprising a topic, enabling easy interpretation of an event's contents (e.g.
-Fig.~\ref{fig:topics}).
-Other models such as Google's Universal Sentence Encoder offer a context-sensitive encoding of text passages, but the encoding space is complex and non-linear, and thus recovering the original words used to fit the model is not straightforward.
-However, it's worth pointing out that our framework is divorced from the particular choice of language model.
-Moreover, many of the aspects of our framework could be swapped out for other choices.
-For example, the language model, the timeseries segmentation model and the video-recall matching function could all be customized for the particular problem.
-Indeed for some problems, recovery of the particular recall words may not be necessary, and thus other text-modeling approaches (such as universal sentence encoder) may be preferable.
-Future work will explore the influence of particular model choices on the framework's efficacy.
 
@@
 The input to the topic model we trained to characterize the dynamic content of the video comprised 998 hand-generated annotations of short (mean: 2.96s) scenes spanning the video clip~(\citealp{ChenEtal17} generated 1000 annotations total; we removed two referring to the break between the first and second scan sessions, during which no fMRI data was collected).
-The features annotated included: narrative details (a sentence or two describing what happened in that scene); whether the scene took place indoors or outdoors; names of any characters that appeared in the scene; name(s) of characters in camera focus; name(s) of characters who were speaking in the scene; the location (in the story) that the scene took place; camera angle (close up, medium, long, top, tracking, over the shoulder, etc.); whether music was playing in the scene or not; and a transcription of any on-screen text.
-We concatenated the text for all of these features within each segment, creating a ``bag of words'' describing each scene.
-We then re-organized the text descriptions into overlapping sliding windows of 50 scenes each.
+We concatenated the text for all of the annotated features within each segment, creating a ``bag of words'' describing each scene and performed some minor preprocessing (e.g., stemming possessive nouns and removing punctuation).
+We then re-organized the text descriptions into overlapping sliding windows spanning (up to) 50 scenes each.
 In other words, we created a ``context" for each scene comprising the text descriptions of the preceding 25 scenes, the present scene, and the following 24 scenes.
-To model the ``context" at the beginning and end of the video (i.e., within 25 scenes of the beginning or end), we created overlapping sliding windows that grew in size from one scene to the full length, then similarly tapered their length at the end.
-This bore the additional benefit of representing each scene's description in the text corpus an equal number of times.
+To model the ``context" for scenes near the beginning and end of the video (i.e., within 25 scenes of the beginning or end), we created overlapping sliding windows that grew in size from one scene to the full length, then similarly tapered their length at the end.
+This additionally ensured that each scene's content was represented in the text corpus an equal number of times.
+% In other words, one sample contained the text from scenes 1-50, the next contained the text from scenes 2-51, and so on.  In order to ensure each scene's content was represented in these 
 % ------ NOTE: ------
@@
 We then used the \texttt{LatentDirichletAllocation} class (topics=100, method=`batch') to fit a topic model~\citep{BleiEtal03} to the word count matrix, yielding a number-of-windows (1047) by number-of-topics (100) \textit{topic proportions} matrix.
-The topic proportions matrix describes which mix of topics (latent themes) is present in and around each scene.
+The topic proportions matrix describes the gradually evolving mix of topics (latent themes) present in each scene.
 Next, we transformed the topic proportions matrix to match the 1976 fMRI volume acquisition times.
-We assigned each topic vector to the timepoint midway between the beginning of the first scene and the end of the last scene in its corresponding sliding text window.
-We then transformed these timepoints to units of TRs and interpolated the dynamic topic proportions matrix to obtain number-of-TRs (1976) by number-of-topics (100) matrix.
+We assigned each topic vector to the timepoint (in seconds) midway between the beginning of the first scene and the end of the last scene in its corresponding sliding text window.
+By doing so, we warped the linear temporal distance between consecutive topic vectors to align with the inconsistent temporal distance between consecutive annotations (whose durations varied greatly).
+We then rescaled these timepoints to 1.5s TR units, and used linear interpolation to estimate a topic vector for each TR.
+This resulted in a number-of-TRs (1976) by number-of-topics (100) matrix.
 
 We created similar topic proportions matrices using hand-annotated transcripts of each participant's recall of the video~\citep[annotated by ][]{ChenEtal17}.
-We tokenized the transcript into a list of sentences, and then re-organized the list into overlapping sliding windows spanning 10 sentences each (and analogously tapered the lengths of the first and last 10 sliding windows).
-In turn, we transformed each window's sentences into a word count vector (using the same vocabulary as for the video model).
-We then used the topic model already trained on the video scenes to compute the most probable topic proportions for each sliding window.
+We tokenized the transcript into a list of sentences, and then re-organized the list into overlapping sliding windows spanning (up to) 10 sentences each, analogously to how we parsed the video annotations.
+In turn, we transformed each window's sentences into a word count vector (using the same vocabulary as for the video model), then used the topic model already trained on the video scenes to compute the most probable topic proportions for each sliding window.
 This yielded a number-of-windows (range: 83--312) by number-of-topics (100) topic proportions matrix for each participant.
@@
 Prior studies on narrative structure and processing have shown that we both perceive and internally represent the world around us at multiple, hierarchical timescales (e.g., \citealp{HassEtal08, LernEtal11, HassEtal15, ChenEtal17, BaldEtal17, BaldEtal18}).
-However, for the purposes of our framework, we sought to identify the single timescale of event-representations that is emphasized \textit{most heavily} in the temporal structure of the video and each participant's recalls.
-We quantified this as the set of $K$ event boundaries that yielded the maximal distinctiveness between the content (i.e., topics) within each event and that in all other events.
+However, for the purposes of our framework, we sought to identify the single timeseries of event-representations that is emphasized \textit{most heavily} in the temporal structure of the video and of each participant's recall.
+We quantified this as the set of $K$ states that maximized the similarity between topic vectors for timepoints comprising each state, while minimizing the similarity between topic vectors for timepoints across different states.
 Specifically, we computed (for each matrix)
@@
 \]
-where $a$ was the distribution of correlations between the topic vectors of timepoints within the same state and $b$ was the average correlation between the topic vectors of timepoints within \textit{different} states.
-For each possible $K$, we computed the first Wasserstein distance ($W_{1}$; also known as ``earth mover's distance"; \citealp{Dobr70, RamdEtal17}) between these distributions, and chose the $K$-value that yielded the greatest difference.
+where $a$ was the distribution of within-state topic vector correlations, and $b$ was the distribution of across-state topic vector correlations .
+We computed the first Wasserstein distance ($W_{1}$; also known as ``earth mover's distance"; \citealp{Dobr70, RamdEtal17}) between these distributions for a large range of possible $K$-values (range [2,50]), and selected the $K$ that yielded the greatest difference.
 Figure~\ref{fig:model}B displays the event boundaries returned for the video, and Figure~\corrmats~displays the event boundaries returned for each participant's recalls (See Fig.~\kopt~for the optimization functions for the video and recalls).

### 2020-02-07 paper/main.tex
progress on methods

@@
 This additionally ensured that each scene's content was represented in the text corpus an equal number of times.
-% In other words, one sample contained the text from scenes 1-50, the next contained the text from scenes 2-51, and so on.  In order to ensure each scene's content was represented in these 
 % ------ NOTE: ------
@@
 where $a$ was the distribution of within-state topic vector correlations, and $b$ was the distribution of across-state topic vector correlations .
-We computed the first Wasserstein distance ($W_{1}$; also known as ``earth mover's distance"; \citealp{Dobr70, RamdEtal17}) between these distributions for a large range of possible $K$-values (range [2,50]), and selected the $K$ that yielded the greatest difference.
-Figure~\ref{fig:model}B displays the event boundaries returned for the video, and Figure~\corrmats~displays the event boundaries returned for each participant's recalls (See Fig.~\kopt~for the optimization functions for the video and recalls).
-After obtaining these event boundaries, we created stable estimates of each topic proportions matrix by averaging the topic vectors within each event.
+We computed the first Wasserstein distance ($W_{1}$; also known as ``earth mover's distance"; \citealp{Dobr70, RamdEtal17}) between these distributions for a large range of possible $K$-values (range [2,50]), and selected the $K$ that yielded the maximum value.
+Figure~\ref{fig:model}B displays the event boundaries returned for the video, and Figure~\corrmats~displays the event boundaries returned for each participant's recalls.
+See Figure \kopt~for the optimization functions for the video and recalls.
+After obtaining these event boundaries, we created stable estimates of the content represented in each event by averaging the topic vectors across timepoints between each pair of event boundaries.
 This yielded a number-of-events by number-of-topics matrix for the video and recalls from each participant.
@@
 
-Perhaps the simplest and most widely used measure of memory performance is \textit{accuracy}---i.e., the proportion of studied (experienced) items (in this case, the 30 video events) that the participant later remembered.
-\cite{ChenEtal17} developed a human rating system whereby the quality of each participant's memory was evaluated by an independent rater.
-We found a strong across-participants correlation between these independant ratings and the overall number of events that our HMM approach identified in participants' recalls (Pearson's $r(15) = 0.65, p = 0.004$).
-
-As described below, we next considered a number of memory performance measures that are typically associated with list-learning studies.
+Perhaps the simplest and most widely used measure of memory performance is \textit{accuracy}---i.e., the proportion of studied (experienced) items (in this case, video events) that the participant later remembered.
+\cite{ChenEtal17} used this method to rate each participant's memory quality by computing the proportion of (50, manually identified) scenes mentioned in their recall.
+We found a strong across-participants correlation between these independent ratings and the proportion of (30, HMM-identified) video events matched to participants' recalls (Pearson's $r(15) = 0.71, p = 0.002$).
+We further considered a number of more nuanced memory performance measures that are typically associated with list-learning studies.
 We also provide a software package, \texttt{Quail}, for carrying out these analyses~\citep{HeusEtal17b}.
@@
 Finally, we averaged over the rows of the matrix, resulting in a 1 by 30 array representing the proportion of participants that recalled an event first, as a function of the order of the event's appearance in the video (Fig.~\ref{fig:list-learning}A).
+% ------ NOTE: ------
+% reiterate meaning of error ribbons in list-learning figure? (already noted in figure caption)
+% - Paxton
 
-\paragraph{Lag conditional probability curve (lag-CRP).} The lag-CRP curve~\citep{Kaha96} reflects the probability of recalling a given event after the just-recalled event, as a function of their relative positions (or \textit{lag}).
-In other words, a lag of 1 indicates that a recalled event came immediately after the previously recalled event in the video, and a lag of -3 indicates that a recalled event came 3 events before the previously recalled event.
+\paragraph{Lag conditional probability curve (lag-CRP).} The lag-CRP curve~\citep{Kaha96} reflects the probability of recalling a given item after the just-recalled item, as a function of their relative encoding positions (or \textit{lag}).
+In other words, a lag of 1 indicates that a recalled item was presented immediately after the previously recalled item, and a lag of -3 indicates that a recalled item came 3 items before the previously recalled item.
 For each recall transition (following the first recall), we computed the lag between the current recall event and the next recall event, normalizing by the total number of possible transitions.
@@
 
-\paragraph{Serial position curve (SPC).} SPCs~\citep{Murd62a} reflect the proportion of participants that remember each item as a function of the items' serial position during encoding.
+\paragraph{Serial position curve (SPC).} SPCs~\citep{Murd62a} reflect the proportion of participants that remember each item as a function of the items' serial positions during encoding.
 We initialized a number-of-participants (17) by number-of-video-events (30) matrix of zeros.
-Then, for each recalled event, for each participant, we found the index of the video event that the recalled event most closely matched (via the correlation between the events' topic vectors) and entered a 1 into that position in the matrix (i.e., for the given participant and event).
+Then, for each recalled event, for each participant, we found the index of the video event that the recalled event most closely matched (via the correlation between the events' topic vectors) and entered a 1 into that position in the matrix.
 This resulted in a matrix whose entries indicated whether or not each event was recalled by each participant (depending on whether the corresponding entires were set to one or zero).
-Finally, we averaged over the rows of the matrix to yield a 1 by 30 array representing the proportion of participants that recalled each event as a function of the order of the event's appearance in the video (Fig.~\ref{fig:list-learning}C).
+Finally, we averaged over the rows of the matrix to yield a 1 by 30 array representing the proportion of participants that recalled each event as a function of the events' order appearance in the video (Fig.~\ref{fig:list-learning}C).
 
-\paragraph{Temporal clustering scores.} Temporal clustering describes participants' tendency to organize their recall sequences by the learned items' encoding positions.
+\paragraph{Temporal clustering scores.} Temporal clustering describes a participant's tendency to organize their recall sequences by the learned items' encoding positions.
 For instance, if a participant recalled the video events in the exact order they occurred (or in exact reverse order), this would yield a score of 1.
@@
 
-\paragraph{Semantic clustering scores.} Semantic clustering describes participants' tendency to recall semantically similar presented items together in their recall sequences.
+\paragraph{Semantic clustering scores.} Semantic clustering describes a participant's tendency to recall semantically similar presented items together in their recall sequences.
 Here, we used the topic vectors for each event as a proxy for its semantic content.
@@
 We averaged these percentile ranks across all of the participant's recalls to obtain a single semantic clustering score for the participant.
-
-% I moved the actual results from the two paragraphs to the results section as an afterthought to the list-learning analyses.
-We could also possibly just take them out, though we should keep them if you think it's worth referencing as support for our argument (see my note in discussion section)
-% -Paxton
-
-% NOTE: Thinking about removing this analysis? More of a sanity check than something novel and cool, and takes up space. Happy to be convinced otherwise - andy
-% leaving this one to Jeremy's judgement
-% -Paxton
 
@@
 In other words, a closer match between the video and recall topic trajectories was related to better overall recall performance.
+% ------ NOTE: ------
+% Andy was thinking about including this in the revision early on.  It wasn't in the preprint version, and with how much else we have in here, I don't think it's worth including anymore.
+% - Paxton
 
@@
 This gave a single value per participant representing the average precision across all recalled events.
-We then Fisher's $z$-transformed these values and correlated them with both hand-annotated and model-derived (i.e., $k$ or the number of events recovered by the HMM) memory performance.
+We then correlated these values with both hand-annotated and model-derived (i.e., the number of unique video events matched by a participant's recall events) memory performance.
 
@@
 We also considered the \textit{distinctiveness} of each recalled event.
-That is, how uniquely a recalled event's topic vector matched a given video event topic vector, versus the topic vectors for the other video events.
+That is, how unique a participant's description of a video event was, versus their descriptions of other video events.
 We hypothesized that participants with high memory performance might describe each event in a more distinctive way (relative to those with lower memory performance who might describe events in a more general way).
@@
 \[
-  d(\mathrm{event}) = 1 - \bar{c}(\mathrm{event}),
+  d(\mathrm{event}) = 1 - \bar{c}(\mathrm{\mathbb{P} \setminus \{event\}}),
 \]
-where $\bar{c}(\mathrm{event})$ is the average correlation between the given recalled event's topic vector and the topic vectors from all video events \textit{except} the best-matching video event.
-We then averaged these distinctiveness scores across all of the events recalled by the given participant.
-As above, we used Fisher's $z$-transformation before correlating these values with hand-annotated and model derived memory performance scores across-subjects.
+where $\bar{c}(\mathrm{\mathbb{P} \setminus \{event\}})$ is the average correlation between the given recall event's topic vector and the topic vectors from all other recall events not matched to the same video event (for a single participant).
+We then averaged these distinctiveness scores across all of the events recalled by the given participant and correlated resulting values with hand-annotated and model derived memory performance scores across-subjects, as above.
+
+\noindent Note: in all instances where we performed statistical tests involving precision or distinctiveness scores, we used Fisher's $z$-transformation \citep{Fish25} to stabilize the variance across the distribution of correlation values prior to performing the test.
+Similarly, when averaging precision or distinctiveness scores, we $z$-transformed the scores prior to computing the mean, and inverse $z$-transformed the result.
 

### 2020-02-07 paper/main.tex
finished initial revision of paper

@@
 We used the UMAP algorithm~\citep{McInEtal18} to project the 100-dimensional topic space onto a two-dimensional space for visualization (Figs.~\ref{fig:trajectory}, \ref{fig:topics}).
-Importantly, to ensure that all of the trajectories were projected onto the \textit{same} lower dimensional space, we computed the low-dimensional embedding on a ``stacked'' matrix created by vertically concatenating the events-by-topics topic proportions matrices for the video, across-participants average recalls and all 17 individual participants' recalls.
+Importantly, to ensure that all of the trajectories were projected onto the \textit{same} lower dimensional space, we computed the low-dimensional embedding on a ``stacked" matrix created by vertically concatenating the events-by-topics topic proportions matrices for the video, across-participants average recall and all 17 individual participants' recalls.
 We then divided the rows of the result (a total-number-of-events by two matrix) back into separate matrices for the video topic trajectory and the trajectories for each participant's recalls (Fig.~\ref{fig:trajectory}).
@@
 We computed the distribution of angles formed by those segments and the $x$-axis, and used a Rayleigh test to determine whether the distribution of angles was reliably ``peaked'' (i.e., consistent across all transitions that passed through that local portion of topic space).
-To create Figure~\ref{fig:trajectory}B we drew an arrow originating from each grid vertex, pointing in the direction of the average angle formed by line segments that passed within its circular radius.
+To create Figure~\ref{fig:trajectory}B we drew an arrow originating from each grid vertex, pointing in the direction of the average angle formed by the line segments that passed within its circular radius.
 We set the arrow lengths to be inversely proportional to the $p$-values of the Rayleigh tests at each vertex.
@@
 In Figure~\ref{fig:brainz}, we present two analyses aimed at identifying brain regions whose responses (as participants viewed the video) exhibited a particular temporal structure.
-We developed a searchlight analysis wherein we constructed a cube centered on each voxel (radius: 5~voxels) and for each of these cubes, computed the temporal correlation matrix of the voxel responses during video viewing.
+We developed a searchlight analysis wherein we constructed a 5 x 5 x 5 cube of voxels (following \citealp{ChenEtal17}) centered on each voxel in the brain, and for each of these cubes, computed the temporal correlation matrix of the voxel responses during video viewing.
 Specifically, for each of the 1976 volumes collected during video viewing, we correlated the activity patterns in the given cube with the activity patterns (in the same cube) collected during every other timepoint.
 This yielded a 1976 by 1976 correlation matrix for each cube.
+Note: participant 5's scan ended 75s early, and in \citealp{ChenEtal17}'s publicly released dataset, their scan data was padded to match the length of the other participants'.
+For our searchlight analyses, we removed this padded data (i.e., the last 50 TRs), resulting in a 1925 by 1925 correlation matrix for each cube in participant 5's brain.
 
-Next, we constructed a series of ``template'' matrices: the first reflecting the timecourse of video's topic trajectory, and the others reflecting that of each participant's recall topic trajectory.
+Next, we constructed a series of ``template" matrices: the first reflecting the timecourse of video's topic trajectory, and the others reflecting that of each participant's recall topic trajectory.
 To construct the video template, we computed the correlations between the topic proportions estimated for every pair of TRs (prior to segmenting the trajectory into discrete events; i.e., the correlation matrix shown in Figs.~\ref{fig:model}B and \ref{fig:brainz}A).
@@
 
-To determine which (cubes of) voxel responses matched the video template, we correlated the upper triangle of the voxel correlation matrix for each cube with the upper triangle of the video template matrix~\citep{KrieEtal08b}.
+The temporal structure of the video's content (as described by our model) is captured in the block-diagonal structure of the video's temporal correlation matrix (e.g., Figs.~\ref{fig:model}B, \ref{fig:brainz}A), with time periods of thematic stability represented as dark blocks of varying sizes.
+Inspecting the video correlation matrix suggests that the video's semantic content is highly temporally specific (i.e., the correlations between topic vectors from distant timepoints are almost entirely near-zero).
+By contrast, the activity patterns of individual (cubes of) voxels can encode relatively limited information on their own, and their activity frequently contributes to multiple separate functions \citep{FreeEtal01, SigmDeha08, CharKoec10, RishEtal13}.
+By nature, these two attributes give rise to similarities in activity across large timescales that may not necessarily reflect a single task.
+To enable a more sensitive analysis of brain regions whose shifts in activity patterns mirrored shifts in the semantic content of the video or recalls, we restricted the temporal correlations we considered to timescale of semantic information captured by our model.
+Specifically, we isolated the upper triangle of the video correlation matrix and created a ``proximal correlation mask" that included only diagonals from the upper triangle of the video correlation matrix up to the first that contained no positive correlations.
+Applying this mask to the full video correlation matrix was analogous to excluding diagonals beyond the corner of the largest diagonal block.
+In other words, the timescale of temporal correlations we considered corresponded to the longest period of thematic stability in the video, and by extension the longest expected period of thematic stability in participants' recalls and the longest period of stability we might expect to see in voxel activity arising from processing or encoding video content.
+Figure \ref{fig:brainz} shows this proximal correlation mask applied to the temporal correlation matrices for the video, an example participant's (warped) recall, and an example cube of voxels from our searchlight analyses.
+
+To determine which (cubes of) voxel responses matched the video template, we correlated the proximal diagonals from the upper triangle of the voxel correlation matrix for each cube with the proximal diagonals from video template matrix~\citep{KrieEtal08b}.
 This yielded, for each participant, a voxelwise map of correlation values.
@@
 We $z$-scored the observed (unshifted) result at each voxel against the distribution of permutation-derived ``null” results, and estimated a $p$-value by computing the proportion of shifted results that yielded larger values.
-To create the map in Figure~\ref{fig:brainz}A, we thresholded out any voxels whose similarity to the unshifted video’s structure fell below the 95\textsuperscript{th} percentile of the permutation-derived similarity results.
+To create the map in Figure~\ref{fig:brainz}C, we thresholded out any voxels whose similarity to the unshifted video’s structure fell below the 95\textsuperscript{th} percentile of the permutation-derived similarity results.
 
 We used an analogous procedure to identify which voxels' responses reflected the recall templates.
-For each participant, we correlated the upper triangle of the correlation matrix for each cube of voxels with their (time warped) recall correlation matrix.
-As in the video template analysis this yielded a voxelwise map of correlation coefficients per participant.
+For each participant, we correlated the proximal diagonals from the upper triangle of the correlation matrix for each cube of voxels with the proximal diagonals from the upper triangle of their (time-warped) recall correlation matrix.
+As in the video template analysis, this yielded a voxelwise map of correlation coefficients per participant.
 However, whereas the video analysis compared every participant's responses to the same template, here the recall templates were unique for each participant.
 As in the analysis described above, we $t$-scored the (Fisher $z$-transformed) voxelwise correlations, and used the same permutation procedure we developed for the video responses to ensure specificity to the recall timeseries and assign significance values.
-To create the map in Figure~\ref{fig:brainz}B we again thresholded out any voxels whose correspondence values fell below the 95\textsuperscript{th} percentile of the permutation-derived null distribution.
+To create the map in Figure~\ref{fig:brainz}D we again thresholded out any voxels whose correspondence values fell below the 95\textsuperscript{th} percentile of the permutation-derived null distribution.
 
-\bibliography{../../CDL-bibliography/memlab}
-% \bibliography{CDL-bibliography/memlab}
+%\subsection*{Neurosynth decoding analyses}
+%To gain further insights into the results from our video searchlight analysis, we constructed a voxelwise map of $p$-values by assigning each voxel the proportion of phase-shifted video trajectories to which its corresponding cube's timeseries was more highly correlated than the timeseries of the ``real" video.
+This $p$-maps described the sensitivity of each voxel (cube) to the specific temporal structure of the video.
+We then passed this $p$-map to \texttt{Neurosynth}.
+Neurosynth does cool stuff.
+
+% \bibliography{../../CDL-bibliography/memlab}
+\bibliography{CDL-bibliography/memlab}
 

### 2020-02-07 paper/main.tex

@@
 \author{Andrew C.
-Heusser\textsuperscript{1, 2}, Paxton C.
-Fitzpatrick\textsuperscript{1}, and Jeremy R.
-Manning\textsuperscript{1, *}\\\textsuperscript{1}Department of Psychological and Brain Sciences\\Dartmouth College, Hanover, NH 03755, USA\\\textsuperscript{2}Akili Interactive\\Boston, MA 02110\\\textsuperscript{*}Corresponding author: jeremy.r.manning@dartmouth.edu}
+Heusser\textsuperscript{1, 2, \textdagger}, Paxton C.
+Fitzpatrick\textsuperscript{1, \textdagger}, and Jeremy R.
+Manning\textsuperscript{1, *}\\\textsuperscript{1}Department of Psychological and Brain Sciences\\Dartmouth College, Hanover, NH 03755, USA\\\textsuperscript{2}Akili Interactive\\Boston, MA 02110\\\textsuperscript{\textdagger}Denotes equal contribution\\\textsuperscript{*}Corresponding author: jeremy.r.manning@dartmouth.edu}
 
@@
 \section*{Introduction}
-
 What does it mean to \textit{remember} something?

### 2020-02-07 paper/supporting_information.tex

@@
 \]
-where $\mathrm{corr}(\mu, \nu)$ is the per-participant correlation between the upper triangles of the temporal correlation matrices of the video ($\mu$) and recall ($\nu$) trajectory, and $\theta$ is the per-participant hand-annotated memory performance.
+where $\mathrm{corr}(\mu, \nu)$ is the per-participant correlation between the temporal correlation matrices of the video ($\mu$) and recall ($\nu$) trajectory, and $\theta$ is the per-participant hand-annotated memory performance.
 We searched over a grid of pre-specified values for each of these parameters; the resulting correlations are displayed in Figure~\ref{fig:paramsearch}.
 The optimal parameters were $\omega = 50$, $\rho = 10$, and $K = 100$.
+In subsequent refinements of our topic modeling approach, we made various improvements to how we parse the video and recall text and construct the trajectories' timeseries, but maintained these optimized parameters throughout.
 
@@
 Specifically, we compared the original video topic trajectory (created using all hand-annotated features from the 998 hand-annotated scenes spanning the \textit{Sherlock} episode; see \textit{Methods} for a full list of features) with video trajectories created using all but one type of feature.
-We created temporal correlation matrices for each trajectory (using the topic proportions matrices) and correlated the upper triangles of each impoverished trajectory with the original feature-complete trajectory.
+We created temporal correlation matrices for each trajectory (using the topic proportions matrices) and correlated the proximal diagonals from the upper triangles of each impoverished trajectory with the original feature-complete trajectory (see \textit{Methods} for details on how we isolated proximal temporal correlations).
 Observing a lower correlation between an impoverished trajectory (holding out a particular feature) and the feature-complete trajectory would suggest that the given feature played a more prominent role in shaping the temporal structure of the feature-complete trajectory.
-We found that hand-annotated scene locations provided the most structure to the feature-complete trajectory, whereas the name of the character(s) in focus for each shot provided the least structure (Fig.~\ref{fig:feature-importance}A).
+We found that hand-annotated narrative details provided the most structure to the feature-complete trajectory, whereas the name of the character(s) in focus for each shot provided the least structure (Fig.~\ref{fig:feature-importance}A).
 
@@
 We also carried out an analysis of which annotated features tended to shape aspects of the video topic trajectory's structure that were preserved in participants' recalls.
-Specifically, we computed the timepoint-by-timepoint correlation matrix of the video topic trajectory, and correlated its upper triangle with that of the timepoint-by-timepoint correlation matrices of each participant's recall topic trajectory (resampled using linear interpolation to have the same number of timepoints as the video trajectory).
+Specifically, we computed the timepoint-by-timepoint correlation matrix of the video topic trajectory, and correlated the proximal diagonals from its upper triangle with those of the timepoint-by-timepoint correlation matrices for each participant's recall topic trajectory (resampled using linear interpolation to have the same number of timepoints as the video trajectory).
 This yielded a single correlation coefficient for each participant.
@@
 Observing a lower correlation between the video and recall trajectories (when a given feature was held out) would indicate that participants utilize changes in that feature's content to discriminate between sections of the video when organizing their recalls.
-We found that hand-annotated narrative details were the most heavily utilized type of feature, whereas changes in which character was speaking tended not to impact participants' recall structures (Fig.~\ref{fig:feature-importance}B).
+We found that hand-annotated narrative details were the most heavily utilized type of feature, whereas changes in the text present on-screen, the indoor/outdoor distinction between scenes, the camera angle, the names of the various characters on screen, and which character was speaking tended not to impact participants' recall structures (i.e., removing those features resulted in a \textit{greater} video-recall topic vector correlation than including them; Fig.~\ref{fig:feature-importance}B).
 
@@
 For example, knowing which character is in focus during a given scene may also provide information about which character is speaking.
-We computed video topic trajectories for each feature in turn, and then compared the upper triangles of the temporal correlation matrices of all pairs of features.
+We computed video topic trajectories from annotations of each individual feature, in turn, and then compared the proximal diagonals from the upper triangles of the temporal correlation matrices of all pairs of features.
 This provided additional confirmation that the shape of the full trajectory (including all types of features) was largely driven by narrative details.
@@
 $\xi$ is the video's trajectory through the manifold space; $\chi$ is the original, 100-dimensional video trajectory; $\Upsilon$ is a condensed matrix of pairwise distances between event vectors (computed using correlation distance in the original topic space and Euclidean distance in the manifold space); $\mathrm{corr}\left(\Upsilon\left(\xi\right), \Upsilon\left(\chi\right)\right)$ is the correlation between the sets of pairwise distances, and $\Gamma$ is the number of instances in which lines drawn between consecutive video event embeddings intersected each other.
-The sets of hyper-parameter values we searched over comprised: $K \in \{10x \in \mathbb{Z}~|~10 < x <  22\} \cup \{161\}$ (a range roughly centered on half the total number of events, 161, in order to balance representations of local and global structure); $\gamma \in \{1, 3, 5, 7, 9\}$; $\delta \in \{0.1, 0.3, 0.5, 0.7, 0.9\}$; $\tau \in \{x \in \mathbb{Z}~|~0 < x < 101\}$; and $\phi \in {S\choose3},~\mathrm{where}~S=\{\mathrm{video~events,~average~recall~events, individual~recall~events}\}$.
+The sets of hyper-parameter values we searched over comprised: $K \in \{10x \in \mathbb{Z}~|~10 < x <  22\} \cup \{161\}$ (a range roughly centered on half the total number of events, 161, in order to balance representations of local and global structure); $\gamma \in \{1, 3, 5, 7, 9\}$; $\delta \in \{0.1, 0.3, 0.5, 0.7, 0.9\}$; $\tau \in \{x \in \mathbb{Z}~|~0 < x < 101\}$; and $\varphi \in {S\choose3},~\mathrm{where}~S=\{\mathrm{video~events,~average~recall~events, individual~recall~events}\}$.
 The optimal parameters (that yielded $\Phi=0$) were $K=170$, $\gamma=7$, $\delta=0.7$, $\tau=41$, with the order of sequence $\varphi$ as the average recall events, video events, and individuals' recall events, vertically concatenated, in order.
@@
 \includegraphics[width=\textwidth]{figs/matchmats}
-\caption{\small \textbf{Video-recall event correlation matrices.}  Each panel is in the same format as Figure~2G in the main text.  The yellow boxes mark the maximum correlation in each column.}
+\caption{\small \textbf{Video-recall event correlation matrices.}  Each panel is in the same format as Figure~2G in the main text.
+The yellow boxes mark the matched video event for each recall event (i.e., the maximum correlation in each column).}
 \label{fig:matchmats}
@@
 \renewcommand{\refname}{Supplemental references}
-\bibliography{../../CDL-bibliography/memlab}
+% \bibliography{../../CDL-bibliography/memlab}
+\bibliography{CDL-bibliography/memlab}
 

### 2020-02-13 paper/main.tex
corrected stats in text, fixed reference to discussion section, other minor wording changes

@@
 % NOTE: 
-% Semantic and temporal clustering are both positively correlated with n_events -- r=0.49; p=0.046 and r=0.61; p=0.009, respectively.  
+% Temporal and semantic clustering are both positively correlated with n_events -- r=0.49; p=0.046 and r=0.61; p=0.009, respectively.  
 % - Paxton
@@
 Participants whose recall events are more veridical descriptions of what happened in the video event will presumably have higher precision scores.
-We find that, across participants, a higher precision score is correlated to both hand-annotated memory performance (Pearson's $r(15) = 0.56, p = 0.021$) and the number of video events successfully remembered, as determined by our model (Pearson's $r(15) = 0.88, p < 0.001$).
+We find that, across participants, a higher precision score is correlated to both hand-annotated memory performance (Pearson's $r(15) = 0.60, p = 0.010$) and the number of video events successfully remembered, as determined by our model (Pearson's $r(15) = 0.90, p < 0.001$).
 We also hypothesized that participants who recounted events in a more distinctive way would display better overall memory.
-We find that this distinctiveness score is related to our model's estimated number of recalled events (Pearson's $r(15) = 0.55, p = 0.021$), and while we do not find distinctiveness to be related to hand-annotated memory performance (Pearson's $r(15) = 0.28, p = 0.275$), this is not entirely surprising given how the hand-annotated memory scores were computed (see \textit{Methods}).
+We find that this distinctiveness score is related to our model's estimated number of recalled events (Pearson's $r(15) = 0.55, p = 0.021$), and while we do not find distinctiveness to be related to hand-annotated memory performance (Pearson's $r(15) = 0.28, p = 0.275$), this is not entirely surprising given how the hand-annotated memory scores were computed (see \textit{Discussion}).
 
@@
 These stimulus qualities enable two assumptions that are central to word list analyses, but frequently do not hold for real-world experiences.
-First, researchers conducting free recall studies may assume that the content at each presentation index is essentially equal, and does not possess attributes that would render it, on average, more or less memorable than others.
+First, researchers conducting list-learning experiments may assume that the content at each presentation index is essentially equal, and does not possess attributes that would render it, on average, more or less memorable than others.
 Such is rarely the case with real-world experiences or experiments meant to approximate them, and the effects of both intrinsic and observer-dependent factors on stimulus memorability are well established \citep[for review see][]{ChunTurk07, ByliEtal15, TyngEtal17}.
@@
 
-% \bibliography{../../CDL-bibliography/memlab}
-\bibliography{CDL-bibliography/memlab}
+\bibliography{../../CDL-bibliography/memlab}
+% \bibliography{CDL-bibliography/memlab}
 

### 2020-02-14 code/helpers/download_neural_data.sh
added missing pipe

@@ -18,8 +18,7 @@ DEST=/mnt/data/processed/fMRI
 mkdir -p $DEST
 
 # download compressed file, extract contents to fMRI directory
-wget -c https://dataspace.princeton.edu/jspui/bitstream/88435/dsp01nz8062179/7/SherlockMovies_published.tgz -O - \
-tar -xz -C $DEST
+wget -c https://dataspace.princeton.edu/jspui/bitstream/88435/dsp01nz8062179/7/SherlockMovies_published.tgz -O - | tar -xz -C $DEST
 
 # gzip each .nii file to save some space
 gzip $DEST/*

### 2020-02-14 code/helpers/download_neural_data.sh
fixed tar extraction, finished test run on alt computer

@@ -8,8 +8,11 @@
 # yourself by copying the download link next to "SherlockMovies_published.tgz"
 # on the page linked above.
 
-# NOTE: this takes quite a while to complete (>1 hour)
+# NOTE: this takes quite a while to complete (~1 hour)
 # ALSO NOTE: the scan data will take up ~11.44 GB of space on your computer
+
+# the file to download and decompress
+SRC=https://dataspace.princeton.edu/jspui/bitstream/88435/dsp01nz8062179/7/SherlockMovies_published.tgz
 
 # the destination for the files
 DEST=/mnt/data/processed/fMRI
@@ -18,7 +21,7 @@ DEST=/mnt/data/processed/fMRI
 mkdir -p $DEST
 
 # download compressed file, extract contents to fMRI directory
-wget -c https://dataspace.princeton.edu/jspui/bitstream/88435/dsp01nz8062179/7/SherlockMovies_published.tgz -O - | tar -xz -C $DEST
+wget -c $SRC -O - | tar -xz -C $DEST --strip-components=1
 
 # gzip each .nii file to save some space
 gzip $DEST/*

### 2020-02-17 paper/supporting_information.tex
supporting info edits

@@
 The optimal parameters were $\omega = 50$, $\rho = 10$, and $K = 100$.
-In subsequent refinements of our topic modeling approach, we made various improvements to how we parse the video and recall text and construct the trajectories' timeseries, but maintained these optimized parameters throughout.
 
@@
 \caption{\small \textbf{Topics discovered in \textit{Sherlock}.} We applied a topic model to hand-annotated information about 1000 scenes spanning the 45 minute episode.
-We identified 27 unique topics with non-zero weights (we used $K=100$ topics to fit the model).
+We identified 32 unique topics with non-zero weights (we used $K=100$ topics to fit the model).
 Each topic comprises a distribution of weights over all words in the vocabulary.
@@
 \subsection*{Creating a low-dimensional embedding space}
-Figures~5 and 6C in the main text display two-dimensional projections of the 100-dimensional topic trajectories for the video (5A, 6C), average recall (5B), and each individual's recall (5C, 6C).
+Figures~7 and 8C in the main text display two-dimensional projections of the 100-dimensional topic trajectories for the video (7A, 8C), average recall (7B), and each individual's recall (7C, 8C).
 We created these embeddings using the Uniform Manifold Approximation and Projection algorithm \citep[UMAP;][]{McInEtal18} called from our high-dimensional visualization and text analysis software, \texttt{HyperTools}~\citep{HeusEtal18a}.
@@
 \]
-$\xi$ is the video's trajectory through the manifold space; $\chi$ is the original, 100-dimensional video trajectory; $\Upsilon$ is a condensed matrix of pairwise distances between event vectors (computed using correlation distance in the original topic space and Euclidean distance in the manifold space); $\mathrm{corr}\left(\Upsilon\left(\xi\right), \Upsilon\left(\chi\right)\right)$ is the correlation between the sets of pairwise distances, and $\Gamma$ is the number of instances in which lines drawn between consecutive video event embeddings intersected each other.
+$\xi$ is the video's trajectory through the manifold space; $\chi$ is the original, 100-dimensional video trajectory; $\Upsilon$ is a function that computes a condensed matrix of pairwise distances between event vectors (computed using correlation distance in the original topic space and Euclidean distance in the manifold space); $\mathrm{corr}\left(\Upsilon\left(\xi\right), \Upsilon\left(\chi\right)\right)$ is the correlation between the sets of pairwise distances, and $\Gamma$ is the number of instances in which lines drawn between consecutive video event embeddings intersected each other.
 The sets of hyper-parameter values we searched over comprised: $K \in \{10x \in \mathbb{Z}~|~10 < x <  22\} \cup \{161\}$ (a range roughly centered on half the total number of events, 161, in order to balance representations of local and global structure); $\gamma \in \{1, 3, 5, 7, 9\}$; $\delta \in \{0.1, 0.3, 0.5, 0.7, 0.9\}$; $\tau \in \{x \in \mathbb{Z}~|~0 < x < 101\}$; and $\varphi \in {S\choose3},~\mathrm{where}~S=\{\mathrm{video~events,~average~recall~events, individual~recall~events}\}$.

### 2020-02-18 paper/main.tex
fixed another typo

@@
 \title{Memory for television episodes preserves event content while introducing new across-event similarities}
+% I think this title still needs work. In this version of the paper, we don’t really focus on the across-event similarities. Let's revisit this once the edits are complete - AH
+
+% Constructing mnemonic events from meaningfully structured experiences
+% Transforming meaningfully structured experiences into mnemonic events
 
@@
 \begin{abstract}
-The ways our experiences unfold over time define unique \textit{trajectories} through the relevant representational spaces.
-Within this geometric framework, one can compare the shape of the trajectory formed by an experience to that defined by our later remembering of that experience.
-We propose a framework for mapping naturalistic experiences onto geometric spaces that characterize how experiences are segmented into discrete events, and how the contents of a event sequences evolve over time.
+Our experiences unfold over time defining unique \textit{trajectories} through the relevant representational spaces.
+By casting our life events as temporally evolving trajectories, one can compare the shape of the trajectory formed by an experience to that defined by our later remembering of that experience.
+We propose a framework for mapping naturalistic experiences onto geometric spaces that characterize how experiences are segmented into discrete events, and how the contents of event sequences evolve over time.
 We apply this approach to a naturalistic memory experiment which had participants view and recount a television episode.
 The content of participants' recountings of events from the original episode closely matched the original episode's content.
-However, the similarity patterns \textit{across} events was much different in the original episode as compared with participants' recountings.
-We also identified a network of brain structures that are sensitive to the ``shapes'' of ongoing experiences, and an overlapping network that is sensitive (at the time of encoding) to how people later remembered those experiences in relation to other experiences.
+Further, we introduce two novel metrics for assessing memory quality (precision and distinctiveness), both of which relate to participants' ability to recapitulate the experience.
+Lastly, we identified a network of brain structures that are sensitive to the ``shapes'' of ongoing experiences, and an overlapping network that is sensitive (at the time of encoding) to how people later remembered those experiences in relation to other experiences.
 In this way, modeling the content of richly structured experiences can reveal how (geometrically and conceptually) those experiences are segmented into events and integrated into our memories of other experiences.
@@
 For example, prior work has shown that event boundaries can influence how we learn sequences of items~\citep{HeusEtal18b, DuBrDava13}, navigate~\citep{BrunEtal18}, and remember and understand narratives~\citep{ZwaaRadv98, EzzyDava11}.
-Prior research has implicated the hippocampus and the medial prefrontal cortex as playing a critical role in transforming experiences into stuctured and consolidated memories ~\citep{TompDava17}.
+Prior research has implicated a network of brain regions (including the hippocampus and the medial prefrontal cortex) as playing a critical role in transforming experiences into structured and consolidated memories ~\citep{TompDava17}.
 
@@
 \section*{Results}
-To characterize the ``essence" of the \textit{Sherlock} episode and participants' subsequent recountings of its unfolding, we used a topic model~\citep{BleiEtal03} to discover the latent themes in the episode's dynamic content.
+To characterize the temporally dynamic contents of the \textit{Sherlock} episode and participants' subsequent recountings, we used a topic model~\citep{BleiEtal03} to discover the latent themes.
 Topic models take as inputs a vocabulary of words to consider and a collection of text documents, and return two output matrices.
@@
 Specifically, our approach yielded (via the topic proportions matrix) a single \textit{topic vector} for each sliding window of annotations transformed by the topic model.
-We then stretched the resulting windows-by-topics matrix to match the time series of the 1976 fMRI volumes collected as participants viewed the episode.
+We then stretched (interpolated) the resulting windows-by-topics matrix to match the time series of the 1976 fMRI volumes collected as participants viewed the episode.
 
@@
 Three example video frames and their associated descriptions are displayed (top two rows).
-Participants later recalled the video (in the third row, we show example recalls of the same three scenes from participant 13).
+Participants later recalled the video (in the third row, we show example recalls of the same three scenes from participant 17).
 We used the topic model (fit to the annotations) to estimate topic vectors for each moment of video and each sentence the participants recalled.
@@
 % - Paxton
+% The 10 top words in this figure seem to be out of order or incorrect. Paxton, can you look into this? - Andy
 
@@
 \textbf{H.} Average correlations between each pair of video events and recalled events (across all 17 participants).
-To create the figure, each recalled event was assigned to the video event with the most correlated topic vector (yellow boxes in panels G and H).
-The heat maps in each panel were created using \texttt{Seaborn}~\citep{WaskEtal16}.}
+To create the figure, each recalled event was assigned to the video event with the most correlated topic vector (yellow boxes in panels G and H).}
 \label{fig:model}
@@
 % - Paxton
+% I also flagged the seaborn reference for removal here. Def not critical to understanding the figure - Andy
 
@@
 As in the video correlation matrix (Fig.~\ref{fig:model}B), the example participant's recall correlation matrix has a strong block diagonal structure, indicating that their recalls are discretized into separated events.
-As for the video correlation matrix, we can use an HMM, along with the aforementioned number-of-events optimization procedure (also see \textit{Methods}) to determine how many events are reflected in the participant's recalls and where specifically the event boundaries fall (outlined in yellow).
+As for the video correlation matrix, we leveraged an HMM-based optimization procedure (see \textit{Methods}) to determine how many events are reflected in the participant's recalls and where specifically the event boundaries fall (outlined in yellow).
 We carried out a similar analysis on all 17 participants' recall topic proportions matrices (Fig.~\corrmats).
@@
 The second clear pattern present in every individual participant's recall correlation matrix is that, unlike in the video correlation matrix, there are substantial off-diagonal correlations.
-Whereas each event in the original video was (largely) separable from the others (Fig.~\ref{fig:model}B), in transforming those separable events into memory, participants appear to be integrating across multiple events, blending elements of previously recalled and not-yet-recalled content into each newly recalled event~\citep[Figs.~\ref{fig:model}D, \corrmats; also see][]{MannEtal11, HowaEtal12}.
+Whereas each event in the original video was (largely) separable from the others (Fig.~\ref{fig:model}B), in transforming those separable events into memory, participants appear to be integrating across multiple events, blending elements of previously recalled and not-yet-recalled content into each newly recalled event~\citep[Figs.~\ref{fig:model}E, \corrmats; also see][]{MannEtal11, HowaEtal12}.
 
@@
 Analogous to classic list-learning studies, we can then examine participants' recall sequences by asking which events they tended to recall first~\citep[probability of first recall; Fig.~\ref{fig:list-learning}A;][]{AtkiShif68, PostPhil65, WelcBurn24}; how participants most often transition between recalls of the events as a function of the temporal distance between them~\citep[lag-conditional response probability; Fig.~\ref{fig:list-learning}B;][]{Kaha96}; and which events they were likely to remember overall~\citep[serial position recall analyses; Fig.~\ref{fig:list-learning}C;][]{Murd62a}.
-Interestingly, for two of these analyses (probability of first recall and lag-conditional response probability curves) we observe patterns comparable to classic effects from the list-learning literature: namely, a higher probability of initiating recall with the first event in the sequence (Fig.~\ref{fig:list-learning}A) and a higher probability of transitioning to neighboring events with an asymmetric forward bias (Fig.~\ref{fig:list-learning}C).
+Interestingly, for two of these analyses (probability of first recall and lag-conditional response probability curves) we observe patterns comparable to classic effects from the list-learning literature: namely, a higher probability of initiating recall with the first event in the sequence (Fig.~\ref{fig:list-learning}A) and a higher probability of transitioning to neighboring events with an asymmetric forward bias (Fig.~\ref{fig:list-learning}B).
 In contrast, we do not observe a pattern comparable to the serial position effect (Fig.~\ref{fig:list-learning}C), but rather we see higher memory for specific events distributed somewhat evenly throughout the video.
@@
 Temporal clustering refers to the extent to which participants group their recall responses according to encoding position.
-Overall, we found that sequentially viewed video events were clustered heavily in participants' recall event sequences (mean: 0.767, SEM: 0.029), and that participants with higher temporal clustering scores tended to perform better according to both \cite{ChenEtal17}'s hand-annotated memory scores (Pearson's $r(15) = 0.62,~p = 0.008$) and our model's estimate (Pearson's $r(15) = 0.54,~p = 0.024$).
+Overall, we found that sequentially viewed video events were clustered heavily in participants' recall event sequences (mean clustering score: 0.767, SEM: 0.029), and that participants with higher temporal clustering scores tended to perform better according to both \cite{ChenEtal17}'s hand-annotated memory scores (Pearson's $r(15) = 0.62,~p = 0.008$) and our model's estimate (Pearson's $r(15) = 0.54,~p = 0.024$).
 Semantic clustering measures the extent to which participants cluster their recall responses according to semantic similarity.
-We found that participants tended to recall semantically similar video events together (mean: 0.787, SEM: 0.018), and that semantic clustering score was also related to both hand-annotated  (Pearson's $r(15) = 0.65,~p = 0.004$) and model-derived (Pearson's $r(15) = 0.63,~p = 0.007$) memory performance.
+We found that participants tended to recall semantically similar video events together (mean clustering score: 0.787, SEM: 0.018), and that semantic clustering score was also related to both hand-annotated  (Pearson's $r(15) = 0.65,~p = 0.004$) and model-derived (Pearson's $r(15) = 0.63,~p = 0.007$) memory performance.
 % NOTE:
-% Temporal and semantic clustering are both positively correlated with n_events -- r=0.49; p=0.046 and r=0.61; p=0.009, respectively.  
+% Semantic and temporal clustering are both positively correlated with n_events -- r=0.49; p=0.046 and r=0.61; p=0.009, respectively.
 % - Paxton
-
-% NOTE: Pruning out to tone down the list-learning slander
-%In list-learning studies, this set of three analyses may be used to gain a nearly complete view into the sequences of recalls participants made~\citep[e.g., ][]{Kaha12}.
-Extending these analyses to apply to naturalistic stimuli and recall~\citep{HeusEtal17b} highlights that, in naturalistic recall, these analyses provide a wholly incomplete picture: they leave out any attempt to quantify participants' abilities to capture the \textit{content} of what occurred in the video-- their only experimental instruction!
 
@@
 The example participant's overall precision score was computed as the average across correlation values in the yellow boxes.
-Their distinctiveness score was computed as the the average (over recall events) of 1 minus the average correlation between each recall event and all other recall events that do not display a box in the same row.
+Their distinctiveness score was computed as the average (over recall events) of 1 minus the average correlation between each recall event and all other recall events that do not display a box in the same row.
 \textbf{B.} The (Pearson's) correlation between precision and hand-annotated memory performance.
@@
 \end{figure}
+% Need to reconcile the description of distinctiveness with how we computed it... - Andy
 
@@
 We also hypothesized that participants who recounted events in a more distinctive way would display better overall memory.
-We find that this distinctiveness score is related to our model's estimated number of recalled events (Pearson's $r(15) = 0.55, p = 0.021$), and while we do not find distinctiveness to be related to hand-annotated memory performance (Pearson's $r(15) = 0.28, p = 0.275$), this is not entirely surprising given how the hand-annotated memory scores were computed (see \textit{Discussion}).
+We find that this distinctiveness score is related to our model's estimated number of recalled events (Pearson's $r(15) = 0.55, p = 0.021$), and while we do not find distinctiveness to be related to hand-annotated memory performance (Pearson's $r(15) = 0.28, p = 0.275$), this is not entirely surprising given how the hand-annotated memory scores were computed (see \textit{Methods} and \textit{Discussion} for details).
 
@@
 Figure \ref{fig:distinctiveness-detail} similarly contrasts two example participants' recalls for a common video event (event 19) to illustrate the tangible differences between high and low distinctiveness scores.
-Here, we have extracted the full set of sentences comprising the most distinctive recall event (P13) and least distinctive recall event (P11) recall event matched to the example video event (Fig.~\ref{fig:distinctiveness-detail}C).
+Here, we have extracted the full set of sentences comprising the most distinctive recall event (P13) and least distinctive recall event (P11) matched to the example video event (Fig.~\ref{fig:distinctiveness-detail}C).
 We also extracted the annotations for the example video event, as well as those from each other video event whose content the example participants' single recall events described (Fig.~\ref{fig:distinctiveness-detail}B).
@@
 The majority of the most distinctive recall event text describes video event 19's content, with the first five and last one sentence describing the video events immediately preceding and succeeding the current one, respectively.
-Meanwhile, the least precise participant's recall for video event 19 blends the content from five separate video events, does not transition between them in order, and often combines descriptions of two video events' content in the same sentence
+In contrast, the least precise participant's recall for video event 19 blends the content from five separate video events, does not transition between them in order, and often combines descriptions of two video events' content in the same sentence.
 
@@
 And while we can directly examine the original text underlying these topic vectors (e.g., Figs.~\ref{fig:precision-detail},~\ref{fig:distinctiveness-detail}) to show how relationships between them reflect real-world behavior, this comparison becomes prohibitively cumbersome at larger timescales.
-To visualize the time-varying high-dimensional content in a more intuitive way~\citep{HeusEtal18a} we projected the topic proportions matrices onto a two-dimensional space using Uniform Manifold Approximation and Projection~\citep[UMAP; ][]{McInEtal18}.
+To visualize the time-varying high-dimensional content in a more intuitive way~\citep{HeusEtal18a}, we projected the topic proportions matrices onto a two-dimensional space using Uniform Manifold Approximation and Projection~\citep[UMAP; ][]{McInEtal18}.
 In this lower-dimensional space, each point represents a single video or recall event, and the distances between the points reflect the distances between the events' associated topic vectors (Fig.~\ref{fig:trajectory}).
@@
 First, the topic trajectory of the video (which reflects its dynamic content; Fig.~\ref{fig:trajectory}A) is captured nearly perfectly by the averaged topic trajectories of participants' recalls (Fig.~\ref{fig:trajectory}B).
-To assess the consistency of these recall trajectories across participants, we asked: given that a participant's recall trajectory had entered a particular location in topic space, could the position of their \textit{next} recalled event be predicted reliably?
-For each location in topic space, we computed the set of line segments connecting successively recalled events (across all participants) that intersected that location (see \textit{Methods} for additional details).
+To assess the consistency of these recall trajectories across participants, we asked: given that a participant's recall trajectory had entered a particular location in the reduced topic space, could the position of their \textit{next} recalled event be predicted reliably?
+For each location in the the reduced topic space, we computed the set of line segments connecting successively recalled events (across all participants) that intersected that location (see \textit{Methods} for additional details).
 We then computed (for each location) the distribution of angles formed by the lines defined by those line segments and a fixed reference line (the $x$-axis).
@@
 % - Paxton
+% I added "reduced" before the first reference and second reference to topic space to make it clear the analyses were performed on the 2D space. - Andy
 
+In addition to the more ``holistic'' measure of memory described in the previous section, our framework also affords the ability to drill down to individual words and quantify how each word relates to the  memorability of each event.
 The results displayed in Figures \ref{fig:list-learning}C and \ref{fig:precision-detail}A suggest that certain events were remembered better than others.
@@
 \includegraphics[width=1\textwidth]{figs/topics}
-\caption{\small \textbf{Transforming experience into memory.} \textbf{A.} Average precision (video event-recall event topic vector correlation) across participants for each video event.
+\caption{\small \textbf{Language used in the most and least memorable events.} \textbf{A.} Average precision (video event-recall event topic vector correlation) across participants for each video event.
 Error bars denote bootstrap-derived across-participant 95\% confidence intervals.
@@
 We next carried out a series of analyses aimed at understanding which brain structures might facilitate these preservations and transformations between the external world and memory.
-In one analysis, we sought to identify brain structures that were sensitive to the dynamic unfolding of the video's content, as characterized by its topic trajectory.
+In the first analysis, we sought to identify brain structures that were sensitive to the dynamic unfolding of the video's content, as characterized by its topic trajectory.
 We used a searchlight procedure to identify clusters of voxels whose activity patterns displayed a proximal temporal correlation structure (as participants watched the video) matching that of the original video's topic proportions (Fig.~\ref{fig:brainz}A; see \textit{Methods} for additional details).
-In a second analysis, we sought to identify brain structures whose responses (during video viewing) reflected how each participant would later structure their \textit{recalls} of the video.
+In a second analysis, we sought to identify brain structures whose responses (during video viewing) reflected how each participant would later structure their recounting of the video.
 We used an analogous searchlight procedure to identify clusters of voxels whose proximal temporal correlation matrices matched that of the topic proportions for each individual's recall (Figs.~\ref{fig:brainz}B; see \textit{Methods} for additional details).
 To ensure our searchlight procedure identified regions \textit{specifically} sensitive to the temporal structure of the video or recalls (i.e., rather than those with a temporal autocorrelation length similar to that of the video/recalls), we performed a phase shift-based permutation correction (see \textit{Methods} for additional details).
-Specifically, we circularly shifted the timeseries of the topic trajectory by a random number of timepoints, recomputed the shifted trajectory's correlation matrix, and again performed our searchlight analysis on this permuted data.
-We then $z$-scored the ``real" searchlight results at each voxel against the null distribution of (100) permuted results.
-In Figure~\ref{fig:brainz}, only voxels whose activity pattern reflected the ``real" video/recall timeseries more closely than 95\% of the permuted results are shown.
 As shown in Figure~\ref{fig:brainz}C, the video-driven searchlight analysis revealed a distributed network of regions that may play a role in processing information relevant to the narrative structure of the video.
-Similarly, the recall-driven searchlight analysis revealed a second diffuse network of regions (Fig.~\ref{fig:brainz}D) that may facilitate a person-specific transformation of one's experience into memory.
+Similarly, the recall-driven searchlight analysis revealed a second network of regions (Fig.~\ref{fig:brainz}D) that may facilitate a person-specific transformation of one's experience into memory.
 In identifying regions whose responses to ongoing experiences reflect how those experiences will be remembered later, this latter analysis extends classic \textit{subsequent memory analyses}~\citep[e.g.,][]{PallWagn02} to domain of naturalistic stimuli.
@@
 We next sought to gain greater insight into the structures and functional networks our results reflected.
-To accomplish this in a blind, unbiased manner (i.e., without reverse inference via visual observation) we performed an additional, exploratory analysis using \texttt{Neurosynth} \citep{YarkEtal11}.
-\texttt{Neurosynth} parses a massive online database of over 14,000 neuroimaging studies and constructs meta-analysis images for over 13,000 psychology- and neuroscience-related terms, based on NIfTI images accompanying studies where those terms appear at a high frequency.
-Then, given a novel image (tagged with its value type; e.g., $t$-, $F$- or $p$-statistics), \texttt{Neurosynth} returns a list of terms whose meta-analysis images are most similar to this new data.
-Our permutation procedure (described above) yielded, for each of the two searchlight analyses, a voxelwise map of significance ($p$-statistic) values.
-These maps describe the extent to which each voxel \textit{specifically} reflected the temporal structure of the video or individuals' recalls (i.e., for each voxel, the proportion of phase-shifted topic vector correlation matrices less similar to the voxel activity correlation matrix than the unshifted video's correlation matrix).
-These significance maps for the video- and recall-driven searchlight analyses, along with the 10 terms with maximally similar meta-analysis images identified by \texttt{Neurosynth} are shown in Figure \ref{fig:neurosynth}.
+To accomplish this, we performed an additional, exploratory analysis using \texttt{Neurosynth} \citep{YarkEtal11}.
+Given an arbitrary statistical map as input, \texttt{Neurosynth} performs a massive automated meta-analysis, returning a ranked list of terms reported in papers with similar significance maps.
+We ran \texttt{Neurosynth} on the significance maps for the video- and recall-driven searchlight analyses.
+These maps, along with the 10 terms with maximally similar meta-analysis images identified by \texttt{Neurosynth} are shown in Figure \ref{fig:neurosynth}.
 
@@
 These stimulus qualities enable two assumptions that are central to word list analyses, but frequently do not hold for real-world experiences.
-First, researchers conducting list-learning experiments may assume that the content at each presentation index is essentially equal, and does not possess attributes that would render it, on average, more or less memorable than others.
+First, researchers conducting list-learning studies may assume that the content at each presentation index is essentially equal, and does not possess attributes that would render it, on average, more or less memorable than others.
 Such is rarely the case with real-world experiences or experiments meant to approximate them, and the effects of both intrinsic and observer-dependent factors on stimulus memorability are well established \citep[for review see][]{ChunTurk07, ByliEtal15, TyngEtal17}.
-Second, the random ordering of list items ensures that (across participants, on average) there is no relationship between the thematic similarity of individual stimuli and their presentation positions---in other words, two successively presented items are no more likely to be highly semantically similar than they are to be high dissimilar.
+Second, the random ordering of list items ensures that (across participants, on average) there is no relationship between the thematic similarity of individual stimuli and their presentation positions---in other words, two successively presented items are no more likely to be highly semantically similar than they are to be highly dissimilar.
 In most cases, the exact opposite is true of real-world episodes.
@@
 
-In the analyses outlined in Figure \ref{fig:brainz}, we identified two diffuse networks of brain structures whose responses were consistent with the video and recall topic trajectories, respectively.
+In the analyses outlined in Figure \ref{fig:brainz}, we identified two networks of brain regions whose responses during video viewing were consistent with the temporal structure of the video and recall topic trajectories, respectively.
+The network identified by the video trajectory analysis included the ventromedial prefrontal cortex, left anterior temporal lobe, superior parietal and dorsal anterior cingulate cortex.
+The network from the video-recall trajectory analysis also included the ventromedial prefrontal and superior parietal cortices, in addition to the posterior medial cortex (PMC) and the inferior temporal regions.
+Notably, \cite{ChenEtal17} also observed the PMC in a number of analyses including one that searched for regions whose activity patterns during encoding were reinstated during free recall.
+The PMC has been consistently identified in studies involving stimuli with meaningfully structured events \cite{CohnRang17}.
+Further, the PMC is part of the "posterior medial" system, a network of brain regions thought to represent situation models ~\cite{ZackEtal07} in support of memory, spatial navigation and social cognition ~\citep{RangRitc12}.
+Given that we constructed our video-recall searchlight model to capture temporal structure in the episode's semantic content (and how one's later recall aligns with that structure), we speculate that the PMC may play a role in constructing mnemonic events from meaningfully structured experiences.
+
 Decoding the associated significance maps with \texttt{Neurosynth} revealed two intriguing results.
 First, the top 10 terms returned for the video-driven searchlight significance map were centered around themes of language and semantic meaning (Fig.~\ref{fig:neurosynth}A).
-In other words, the voxels identified as more reflective of the video's temporal structure (i.e., voxels with lower permutation correction-derived $p$-values), as defined by our model, were most likely to be reported as active in studies focusd on the the neural underpinnings of semantic processing.
+In other words, the voxels identified as more reflective of the video's temporal structure (i.e., voxels with lower permutation correction-derived $p$-values), as defined by our model, were most likely to be reported as active in studies focused on the the neural underpinnings of semantic processing.
 This finding is interesting, as our model specifically captures the temporal structure of the video's \textit{semantic} content (e.g., as opposed to that of the visual, auditory, or affective content).
@@
 % - Paxton
+% I agree that we can take it out. -AH
 
@@
 Importantly, to ensure that all of the trajectories were projected onto the \textit{same} lower dimensional space, we computed the low-dimensional embedding on a ``stacked" matrix created by vertically concatenating the events-by-topics topic proportions matrices for the video, across-participants average recall and all 17 individual participants' recalls.
-We then divided the rows of the result (a total-number-of-events by two matrix) back into separate matrices for the video topic trajectory and the trajectories for each participant's recalls (Fig.~\ref{fig:trajectory}).
+We then divided the rows of the result (a total-number-of-events by two matrix) back into separate matrices for the video topic trajectory, across-participant average recall trajectory and the trajectories for each individual participant's recalls (Fig.~\ref{fig:trajectory}).
 This general approach for discovering a shared low-dimensional embedding for a collections of high-dimensional observations follows \cite{HeusEtal18a}.
-Note: for further details on how we created this low-dimensional embedding space, see \textit{Supporting Information}.
-% ------ NOTE: ------
-% need to add info about embedding optimization
-% - Paxton
+
+We optimized the manifold space for visualization based on two criteria: First, that the 2D embedding of the video trajectory should reflect its original 100-dimensional structure as faithfully as possible.
+Second, that the path traversed by the embedded video trajectory should intersect itself a minimal number of times.
+The first criteria helps bolster the validity of visual intuitions about relationships between sections of video content, based on their locations in the embedding space.
+The second criteria was motivated by the observed low off-diagonal values in the video trajectory's temporal correlation matrix (suggesting that the same topic-space coordinates should not be revisited; see Figure~2A in the main text).
+For further details on how we created this low-dimensional embedding space, see \textit{Supporting Information}.
 
@@
 
-%\subsection*{Neurosynth decoding analyses}
-%To gain further insights into the results from our video searchlight analysis, we constructed a voxelwise map of $p$-values by assigning each voxel the proportion of phase-shifted video trajectories to which its corresponding cube's timeseries was more highly correlated than the timeseries of the ``real" video.
-This $p$-maps described the sensitivity of each voxel (cube) to the specific temporal structure of the video.
-We then passed this $p$-map to \texttt{Neurosynth}.
-Neurosynth does cool stuff.
+\subsection*{Neurosynth decoding analyses}
+\texttt{Neurosynth} parses a massive online database of over 14,000 neuroimaging studies and constructs meta-analysis images for over 13,000 psychology- and neuroscience-related terms, based on NIfTI images accompanying studies where those terms appear at a high frequency.
+Then, given a novel image (tagged with its value type; e.g., $t$-, $F$- or $p$-statistics), \texttt{Neurosynth} returns a list of terms whose meta-analysis images are most similar to this new data.
+Our permutation procedure yielded, for each of the two searchlight analyses, a voxelwise map of significance ($p$-statistic) values.
+These maps describe the extent to which each voxel \textit{specifically} reflected the temporal structure of the video or individuals' recalls (i.e., for each voxel, the proportion of phase-shifted topic vector correlation matrices less similar to the voxel activity correlation matrix than the unshifted video's correlation matrix).
+We input the two statistical maps described above to \texttt{Neurosynth} to create a list of the 10 most representative terms for each map.
 
-\bibliography{../../CDL-bibliography/memlab}
-% \bibliography{CDL-bibliography/memlab}
+% \bibliography{../../CDL-bibliography/memlab}
+\bibliography{CDL-bibliography/memlab}
 

### 2020-02-18 paper/supporting_information.tex

@@
 
-Two other parameters ultimately affect this balance between preserving local and global structure: the seed ($\tau$) for the (pseudo-)random number generator, and the order of the observations (i.e., trajectories) to be embedded ($\phi$).
+Two other parameters ultimately affect this balance between preserving local and global structure: the seed ($\tau$) for the (pseudo-)random number generator, and the order of the observations (i.e., trajectories) to be embedded ($\varphi$).
 As described in \textit{Methods}, we ensured the video and recall events were projected onto the \textit{same} low-dimensional manifold by fitting the embedding model to a stacked matrix of all video, average recall, and individuals' recall events.

### 2020-08-12 paper/main.tex
started inputting changes to paper [WIP]

@@
 
-\title{Memory for television episodes preserves event content while introducing new across-event similarities}
-% I think this title still needs work. In this version of the paper, we don’t really focus on the across-event similarities. Let's revisit this once the edits are complete - AH
-
-% Constructing mnemonic events from meaningfully structured experiences
-% Transforming meaningfully structured experiences into mnemonic events
+\title{Geometric models reveal behavioral and neural signatures of how naturalistic experiences are transformed into episodic memories}
 
@@
 \begin{abstract}
-Our experiences unfold over time defining unique \textit{trajectories} through the relevant representational spaces.
-By casting our life events as temporally evolving trajectories, one can compare the shape of the trajectory formed by an experience to that defined by our later remembering of that experience.
-We propose a framework for mapping naturalistic experiences onto geometric spaces that characterize how experiences are segmented into discrete events, and how the contents of event sequences evolve over time.
-We apply this approach to a naturalistic memory experiment which had participants view and recount a television episode.
-The content of participants' recountings of events from the original episode closely matched the original episode's content.
-Further, we introduce two novel metrics for assessing memory quality (precision and distinctiveness), both of which relate to participants' ability to recapitulate the experience.
-Lastly, we identified a network of brain structures that are sensitive to the ``shapes'' of ongoing experiences, and an overlapping network that is sensitive (at the time of encoding) to how people later remembered those experiences in relation to other experiences.
-In this way, modeling the content of richly structured experiences can reveal how (geometrically and conceptually) those experiences are segmented into events and integrated into our memories of other experiences.
+The ways our experiences unfold over time may be characterized by unique \textit{trajectories} through geometric representational spaces.
+In word embedding spaces, for example, each coordinate reflects a concept and nearby coordinates (in Euclidean distance) reflect semantically related concepts.
+We propose a framework for projecting naturalistic experiences into word embedding spaces, such that the conceptual content of each moment of an experience, and how different moments of the experience relate, are reflected by the \textit{shape} of the experience's trajectory.
+By projecting memories of those experiences into the same spaces, one may then geometrically compare the shape of the original experience's trajectory to the shape of how it is remembered later.
+According to this view, encoding an experience into memory entails geometrically distorting or transforming the original experience's trajectory.
+This translates qualitative questions about how we remember naturalistic experiences into quantitative geometric comparisons.
+We applied our framework to data collected as participants watched, and later verbally recounted, a television episode while undergoing functional neuroimaging.
+We found that all participants' remembered trajectories reflected the high-level \textit{essence} (i.e., large-scale narrative features) of the episode's trajectory, but participants differred markedly in their memories for low-level details (i.e, small-scale details of the trajectory).
+We also identified a network of brain structures that were sensitive to the shape of the episode's trajectory through word embedding space, and an overlapping network that predicted, at the time of encoding, how people would distort (transform) the episode's trajectory when they recounted the episode later.
+Our work provides insights into how our brains transform our ongoing experiences when we encode them into episodic memories, and provides a formal geometric framework for characterizing the complex dynamic content of naturalistic experiences.
 \end{abstract}
@@
 What does it mean to \textit{remember} something?
-In traditional episodic memory experiments \citep[e.g., list-learning or trial-based experiments;][]{Murd62a, Kaha96}, remembering is often cast as a discrete and binary operation: each studied item may be separated from all others, and labeled as having been recalled or forgotten.
+In traditional episodic memory experiments \citep[e.g., list-learning or trial-based experiments;][]{Murd62a, Kaha96}, remembering is often cast as a discrete and binary operation: each studied item may be separated from the rest of one's experiences and labeled as having been recalled or forgotten.
 More nuanced studies might incorporate self-reported confidence measures as a proxy for memory strength, or ask participants to discriminate between ``recollecting'' the (contextual) details of an experience or having a general feeling of ``familiarity'' \citep{Yone02}.
@@
 However, there are fundamental properties of the external world and our memories that trial-based experiments are not well suited to capture~\citep[for review also see][]{KoriGold94, HukEtal18}.
-First, our experiences and memories are continuous, rather than discrete---removing a (naturalistic) event from the context in which it occurs can substantially change its meaning.
+First, our experiences and memories are continuous, rather than discrete---isolating a (naturalistic) event from the context in which it occurs can substantially change its meaning.
 Second, the specific language used to describe an experience has little bearing on whether the experience should be considered to have been ``remembered.''  Asking whether the rememberer has precisely reproduced a specific set of words to describe a given experience is nearly orthogonal to whether they were actually able to remember it.
@@
 
-How might one go about formally characterizing the ``essence" of an experience, or whether it has been recovered by the rememberer?
-Any given moment of an experience derives meaning from surrounding moments, as well as from longer-range temporal associations~\citep{LernEtal11, Mann19}.
+How might one go about formally characterizing the \textit{essence} of an experience, or whether it has been recovered by the rememberer?
+Any given moment of an experience derives meaning from surrounding moments, as well as from longer-range temporal associations~\citep{LernEtal11, Mann19, Mann20}.
 Therefore, the timecourse describing how an event unfolds is fundamental to its overall meaning.
-Further, this hierarchy formed by our subjective experiences at different timescales defines a \textit{context} for each new moment~\citep[e.g., ][]{HowaKaha02a, HowaEtal14}, and plays an important role in how we interpret that moment and remember it later~\citep[for review see][]{MannEtal15}.
+Further, this hierarchy formed by our subjective experiences at different timescales defines a \textit{context} for each new moment~\citep[e.g., ][]{HowaKaha02a, HowaEtal14}, and plays an important role in how we interpret that moment and remember it later~\citep[for review see][]{MannEtal15, Mann20}.
 Our memory systems can leverage these associations to form predictions that help guide our behaviors~\citep{RangRitc12}.
@@
 Comparing the shapes of the topic trajectories of the episode and of participants' retellings of the episode then reveals which aspects of the episode were preserved (or lost) in the translation into memory.
-We further introduce two novel metrics for assessing memory quality: the \textit{precision} with which a participant recounts each event and 2) the \textit{distinctiveness} of each recall event (relative to other recalled events).
-We examine how these metrics relate to participants' overall memory performance, and discuss the ways in which they improve upon classic ``proportion-recalled" measures for analyzing naturalistic memory.
-Last, we utilize our framework to identify networks of brain structures whose responses (as participants watched the episode) reflected the temporal dynamics of the episode, and how participants would later recount it.
+We further introduce two novel metrics for assessing memory quality: (1) the \textit{precision} with which a participant recounts each event and (2) the \textit{distinctiveness} of each recall event (relative to other recalled events).
+We examine how these metrics relate to overall memory performance, and discuss the ways in which they improve upon classic ``proportion-recalled'' measures for analyzing naturalistic memory.
+Last, we utilize our framework to identify networks of brain structures whose responses (as participants watched the episode) reflected the temporal dynamics of the episode, and how participants recount it.
 
 \section*{Results}
-To characterize the temporally dynamic contents of the \textit{Sherlock} episode and participants' subsequent recountings, we used a topic model~\citep{BleiEtal03} to discover the latent themes.
+To characterize the dynamic content of the \textit{Sherlock} episode and participants' subsequent recountings, we used a topic model~\citep{BleiEtal03} to discover the latent themes.
 Topic models take as inputs a vocabulary of words to consider and a collection of text documents, and return two output matrices.
-The first of these is a \textit{topics matrix} whose rows are topics (latent themes) and whose columns correspond to words in the vocabulary.
+The first of these is a \textit{topics matrix} whose rows are \textit{topics} (latent themes) and whose columns correspond to words in the vocabulary.
 The entries of the topics matrix define how each word in the vocabulary is weighted by each discovered topic.
@@
 This information included: a brief narrative description of what was happening, the location where the scene took place, the names of any characters on the screen, and other similar details (for a full list of annotated features, see \textit{Methods}).
-We took from these annotations the union of all unique words (excluding stop words, such as ``and," ``or," ``but," etc.) across all features and scenes as the ``vocabulary" for the topic model.
+We took from these annotations the union of all unique words (excluding stop words, such as ``and,'' ``or,'' ``but,'' etc.) across all features and scenes as the ``vocabulary'' for the topic model.
 We then concatenated the sets of words across all features contained in overlapping, sliding windows of (up to) 50 scenes, and treated each window as a single ``document" for the purpose of fitting the topic model.
@@
 
-The 32 topics we found were heavily character-focused (i.e., the top-weighted word in each topic was nearly always a character) and could be roughly divided into themes centered around Sherlock Holmes (the titular character), John Watson (Sherlock's close confidant and assistant), supporting characters (e.g., Inspector Lestrade, Sergeant Donovan, or Sherlock's brother Mycroft), or the interactions between various pairs of these characters (see Fig.~\topics).
+The 32 topics we found were heavily character-focused (i.e., the top-weighted word in each topic was nearly always a character) and could be roughly divided into themes centered around Sherlock Holmes (the titular character), John Watson (Sherlock's close confidant and assistant), supporting characters (e.g., Inspector Lestrade, Sergeant Donovan, or Sherlock's brother Mycroft), or the interactions between various groupings of these characters (see Fig.~\topics).
 Several of the identified topics were highly similar, which we hypothesized might allow us to distinguish between subtle narrative differences if the distinctions between those overlapping topics were meaningful.
@@
 Part of our model fitting procedure required selecting an appropriate number of ``events" into which the topic trajectory should be segmented.
-To accomplish this, we used an optimization procedure that maximized the difference between the topic weights for timepoints within an event and across multiple events (see \textit{Methods} for additional details).
-We then created a stable ``summary'' of the content within each video event by averaging the topic vectors across timepoints each event spanned (Fig.~\ref{fig:model}C).
+To accomplish this, we used an optimization procedure that maximized the difference between the topic weights for timepoints within an event versus across multiple events (see \textit{Methods} for additional details).
+We then created a stable ``summary'' of the content within each video event by averaging the topic vectors across the timepoints spanned by each event (Fig.~\ref{fig:model}C).
 
@@
 Event boundaries detected by the HMM are denoted in yellow (22 events detected).
-For similar plots for all participants see Figure~\corrmats.
+For similar plots for all participants, see Figure~\corrmats.
 \textbf{F.} Average topic vectors for each of the 22 recalled events from the example participant.
@@
 This yielded, for each participant, a number-of-windows by number-of-topics topic proportions matrix that characterized how the topics identified in the original video were reflected in the participant's recalls.
-Note that an important feature of our approach is that it allows us to compare participants' recalls to events from the original video, despite different participants using widely varying language to describe the same event, and that those descriptions may not match the original annotations.
-This is a substantial benefit of projecting the video and recalls into a shared ``topic" space.
+Note that an important feature of our approach is that it allows us to compare participants' recalls to events from the original video, despite different participants using widely varying language to describe the events, and that those descriptions often diverged in content and quality from the video annotations.
+This is a substantial benefit of projecting the video and recalls into a shared ``topic'' space.
 An example topic proportions matrix from one participant's recalls is shown in Figure~\ref{fig:model}D.
+
+% JRM STOPPED HERE...
 

### 2020-08-13 code/sherlock_helpers/sherlock_helpers/__init__.py
reorganized helpers, added install files

@@ -1,0 +1,24 @@
+from pathlib import Path
+
+from IPython.display import display, Markdown
+
+
+version_info = (0, 0, 1)
+__version__ = '.'.join(map(str, version_info))
+
+github_url = "https://github.com/ContextLab/sherlock-topic-model-paper/tree/master/code/sherlock_helpers"
+pkg_dir = Path(__file__).resolve().parent
+message = Markdown(
+    "Helper functions and variables used across multiple notebooks can be "
+    f"found in `{pkg_dir}`, or on GitHub, [here]({github_url}).<br />You can "
+    "also view source code directly from the notebook with:<br /><pre>    "
+    "from sherlock_helpers.functions import show_source<br />    show_source(foo)"
+    "</pre>"
+)
+
+try:
+    # check whether package was imported from a notebook
+    get_ipython()
+    display(message)
+except NameError:
+    pass

### 2020-08-13 code/sherlock_helpers/sherlock_helpers/load_cluster_output.py

@@ -1,0 +1,48 @@
+import os
+import sys
+import spurplus
+from os.path import join as opj
+
+
+def load_cluster_output(hostname, username, password):
+    datadir_local = '../../data/processed/'
+    emb_path_remote = f'/dartfs/rc/lab/D/DBIC/CDL/{username}/sherlock-embedding/data/optimized/embeddings.npy'
+    emb_path_local = opj(datadir_local, 'embeddings.npy')
+
+    sl_dir_remote = f'/dartfs/rc/lab/D/DBIC/CDL/{username}/searchlights/data/'
+    sl_output_dr = opj(sl_dir_remote, 'finished')
+    sl_vdir_local = opj(datadir_local, 'searchlight_video')
+    sl_rdir_local = opj(datadir_local, 'searchlight_recall')
+
+    if not os.path.isdir(sl_vdir_local):
+        os.mkdir(sl_vdir_local)
+    if not os.path.isdir(sl_rdir_local):
+        os.mkdir(sl_rdir_local)
+
+    with spurplus.connect_with_retries(hostname=hostname,
+                                       username=username,
+                                       password=password) as remote:
+                                   # copy over embeddings
+                                   remote.get(emb_path_remote, emb_path_local)
+
+                                   # copy over searchlights
+                                   for analysis in ['video', 'recall']:
+                                       src_dir = opj(sl_output_dr, f'searchlight_{analysis}')
+                                       dest_dir = opj(datadir_local, f'searchlight_{analysis}')
+                                       perm_dir = opj(src_dir, 'perms')
+                                       for sub in range(1, 18):
+                                           # unshifted data
+                                           src_path = opj(src_dir, f'sub{sub}.npy')
+                                           dest_path = opj(dest_dir, f'sub{sub}.npy')
+                                           remote.get(src_path, dest_path)
+                                       # permuted data
+                                       for perm in range(100):
+                                           perm_src_path = opj(perm_dir, f'perm{perm}.nii.gz')
+                                           perm_dest_path = opj(dest_dir, f'perm{perm}.nii.gz')
+                                           remote.get(perm_src_path, perm_dest_path)
+
+                                    # copy over reference image
+                                    src_path = opj(sl_dir_remote, 'inputs', 'fMRI', 'ref_img.nii.gz')
+                                    dest_path = opj(sl_vdir_local, 'ref_img.nii.gz')
+                                   remote.get(src_path, dest_path)
+

### 2020-08-13 code/sherlock_helpers/sherlock_helpers/constants.py
reorganizing helpers

@@ -1,0 +1,44 @@
+"""
+This module contains variables and constant values used across multiple
+analysis notebooks in a centralized location.
+"""
+from pathlib import Path
+import numpy as np
+
+# paths for loading data and saving figures
+RAW_DIR = Path('/mnt/data/raw')
+DATA_DIR = RAW_DIR.parent.joinpath('processed')
+FIG_DIR = Path('/mnt/paper/figs')
+
+
+# video sliding window length (in annotations)
+VIDEO_WSIZE = 50
+# recall sliding window length (in sentences)
+RECALL_WSIZE = 10
+# text vectorizer parameters
+VECTORIZER_PARAMS = {
+    'model': 'CountVectorizer',
+    'params': {
+        'stop_words': 'english'
+    }
+}
+# topic model parameters
+SEMANTIC_PARAMS = {
+    'model': 'LatentDirichletAllocation',
+    'params': {
+        'n_components': 100,
+        'learning_method': 'batch',
+        'random_state': 0
+    }
+}
+
+
+# hand-annotated memory performance for each participant (from Chen et al., 2017)
+HAND_REC = np.array([27, 24, 32, 33, 32, 39, 30, 39,
+                     28, 40, 34, 38, 47, 38, 27, 37, 39])
+# number of HMM-identified recall events for each participant
+N_REC_EVENTS = np.array([11, 16, 12, 10, 10, 12, 11, 16,
+                         14, 15, 15, 23, 29, 16, 13, 17, 22])
+
+# min and max x- and y-bound for embedding space grid
+SCALE = 30

### 2020-08-13 code/sherlock_helpers/sherlock_helpers/functions.py

@@ -1,0 +1,192 @@
+"""
+This module contains analysis functions used across multiple notebooks,
+as well as some functions to view them from the notebooks
+"""
+
+import re
+from inspect import getsource
+
+import matplotlib.patches as patches
+import numpy as np
+import pandas as pd
+from fastdtw import fastdtw
+from IPython.display import display, HTML
+from IPython.core.oinspect import pylight
+from scipy.spatial.distance import correlation
+
+from .constants import SCALE
+
+
+########################################
+#     TEXT PREPROCESSING & MODELING    #
+########################################
+
+def format_text(text):
+    if isinstance(text, pd.Series):
+        text = ' '.join(list(text.dropna()))
+        pattern = "[^\w\s]+"
+    else:
+        pattern = "[^.\w\s]+"
+
+    no_possessive = text.lower().replace("'s", '')
+    return re.sub(pattern, '', no_possessive)
+
+
+def get_video_timepoints(window_spans, annotations):
+    timepoints = []
+    for first, last in window_spans:
+        window_onset = annotations.loc[first, 'Start Time (s) ']
+        window_offset = annotations.loc[last - 1, 'End Time (s) ']
+        timepoints.append((window_onset + window_offset) / 2)
+
+    return np.array(timepoints)
+
+
+def parse_windows(textlist, wsize):
+    windows = []
+    window_bounds = []
+    for ix in range(1, wsize):
+        start, end = 0, ix
+        window_bounds.append((start, end))
+        windows.append(' '.join(textlist[start:end]))
+
+    for ix in range(len(textlist)):
+        start = ix
+        end = ix + wsize if ix + wsize <= len(textlist) else len(textlist)
+        window_bounds.append((start, end))
+        windows.append(' '.join(textlist[start:end]))
+
+    return windows, window_bounds
+
+
+########################################
+#         STATS/MATH FUNCTIONS         #
+########################################
+
+def corr_mean(rs, axis=0):
+    return z2r(np.nanmean([r2z(r) for r in rs], axis=axis))
+
+
+def r2z(r):
+    with np.errstate(invalid='ignore', divide='ignore'):
+        return 0.5 * (np.log(1 + r) - np.log(1 - r))
+
+
+def z2r(z):
+    with np.errstate(invalid='ignore', divide='ignore'):
+        return (np.exp(2 * z) - 1) / (np.exp(2 * z) + 1)
+
+
[…]

### 2020-08-13 code/sherlock_helpers/sherlock_helpers/constants.py
add multicol display function and some constants

@@ -10,11 +10,12 @@ RAW_DIR = Path('/mnt/data/raw')
 DATA_DIR = RAW_DIR.parent.joinpath('processed')
 FIG_DIR = Path('/mnt/paper/figs')
 
-
 # video sliding window length (in annotations)
 VIDEO_WSIZE = 50
+
 # recall sliding window length (in sentences)
 RECALL_WSIZE = 10
+
 # text vectorizer parameters
 VECTORIZER_PARAMS = {
     'model': 'CountVectorizer',
@@ -22,6 +23,7 @@ VECTORIZER_PARAMS = {
         'stop_words': 'english'
     }
 }
+
 # topic model parameters
 SEMANTIC_PARAMS = {
     'model': 'LatentDirichletAllocation',
@@ -32,13 +34,12 @@ SEMANTIC_PARAMS = {
     }
 }
 
-
 # hand-annotated memory performance for each participant (from Chen et al., 2017)
 HAND_REC = np.array([27, 24, 32, 33, 32, 39, 30, 39,
                      28, 40, 34, 38, 47, 38, 27, 37, 39])
-# number of HMM-identified recall events for each participant
-N_REC_EVENTS = np.array([11, 16, 12, 10, 10, 12, 11, 16,
-                         14, 15, 15, 23, 29, 16, 13, 17, 22])
+
+# edge color for yellow boxes in corrmat and matchmat figures
+EDGECOLOR = '#FFF9AE'
 
 # min and max x- and y-bound for embedding space grid
-SCALE = 30
+GRID_SCALE = 30

### 2020-08-13 code/sherlock_helpers/sherlock_helpers/functions.py

@@ -5,6 +5,7 @@ as well as some functions to view them from the notebooks
 
 import re
 from inspect import getsource
+from typing import Iterator
 
 import matplotlib.patches as patches
 import numpy as np
@@ -14,7 +15,7 @@ from IPython.display import display, HTML
 from IPython.core.oinspect import pylight
 from scipy.spatial.distance import correlation
 
-from .constants import SCALE
+from .constants import EDGECOLOR, GRID_SCALE
 
 
 ########################################
@@ -83,13 +84,14 @@ def z2r(z):
 
 def add_arrows(axes, x, y, **kwargs):
     # spacing of arrows
-    aspace = .05 * SCALE
+    aspace = .05 * GRID_SCALE
     # distance spanned between pairs of points
     r = [0]
     for i in range(1, len(x)):
         dx = x[i] - x[i - 1]
         dy = y[i] - y[i - 1]
         r.append(np.sqrt(dx * dx + dy * dy))
+
     r = np.array(r)
     # cumulative sum of r, used to save time
     rtot = []
@@ -131,12 +133,13 @@ def draw_bounds(ax, model):
     bounds_aug = np.concatenate(([0], bounds, [model.segments_[0].shape[0]]))
     for i in range(len(bounds_aug) - 1):
         rect = patches.Rectangle((bounds_aug[i], bounds_aug[i]),
-                                 bounds_aug[i + 1]-bounds_aug[i],
-                                 bounds_aug[i + 1]-bounds_aug[i],
+                                 bounds_aug[i + 1] - bounds_aug[i],
+                                 bounds_aug[i + 1] - bounds_aug[i],
                                  linewidth=1,
-                                 edgecolor='#FFF9AE',
+                                 edgecolor=EDGECOLOR,
                                  facecolor='none')
         ax.add_patch(rect)
+
     return ax
 
 ########################################
@@ -148,9 +151,11 @@ def create_diag_mask(corrmat, diag_limit=None):
     diag_mask = np.zeros_like(corrmat, dtype=bool)
     if diag_limit is None:
         diag_limit = find_diag_limit(corrmat)
+
     for k in range(1, diag_limit):
         ix = kth_diag_indices(diag_mask, k)
         diag_mask[ix] = True
+
     return diag_mask
 
 
@@ -180,6 +185,109 @@ def warp_recall(recall_traj, video_traj, return_paths=False):
 ########################################
 #          NOTEBOOK DISPLAYS           #
 ########################################
+
[…]

### 2020-08-14 code/sherlock_helpers/sherlock_helpers/functions.py
added event text parsing functions

@@ -15,7 +15,7 @@ from IPython.display import display, HTML
 from IPython.core.oinspect import pylight
 from scipy.spatial.distance import correlation
 
-from .constants import EDGECOLOR, GRID_SCALE
+from .constants import EDGECOLOR, GRID_SCALE, RAW_DIR, RECALL_WSIZE
 
 
 ########################################
@@ -31,6 +31,44 @@ def format_text(text):
 
     no_possessive = text.lower().replace("'s", '')
     return re.sub(pattern, '', no_possessive)
+
+
+def get_recall_event_text(event_boundaries, subid):
+    onset, offset = event_boundaries
+    transcript_path = RAW_DIR.joinpath(f'NN{subid} transcript.txt')
+    with transcript_path.open(encoding='cp1252') as f:
+        transcript = f.read().replace(b'\x92'.decode('cp1252'), "'").strip()
+
+    textlist = transcript.split('.')
+    windows = []
+    window_n = 0
+    for w_ix in range(1, RECALL_WSIZE):
+        if onset <= window_n <= offset:
+            start, end = 0, w_ix
+            windows.append('.'.join(textlist[start:end]))
+
+        window_n += 1
+
+    for w_ix in range(len(textlist)):
+        if onset <= window_n <= offset:
+            start = w_ix
+            end = w_ix + RECALL_WSIZE if w_ix + RECALL_WSIZE <= len(textlist) else len(textlist)
+            windows.append('.'.join(textlist[start:end]))
+
+        window_n += 1
+
+    full_reclist = '.'.join(windows).split('.')
+    recall_text_slice = pd.unique(full_reclist)
+    return '.'.join(recall_text_slice).strip() + '.'
+
+
+def get_video_event_text(event_boundaries):
+    onset, offset = event_boundaries
+    video_text = pd.read_excel(RAW_DIR.joinpath('Sherlock_Segments_1000_NN_2017.xlsx'))
+    text_slice = video_text.loc[(video_text['Start Time (TRs, 1.5s)'] >= onset)
+                                & (video_text['End Time (TRs, 1.5s)'] < offset),
+                                'Scene Details - A Level ']
+    return ' '.join(text_slice)
 
 
 def get_video_timepoints(window_spans, annotations):
@@ -272,11 +310,11 @@ def multicol_display(*outputs,
     cell_style = ";".join(f"{prop}:{val}" for prop, val in cell_css.items())
 
     # string templates for individual elements
[…]

### 2020-08-17 code/sherlock_helpers/sherlock_helpers/functions.py
added get_topic_words func

@@ -33,44 +33,6 @@ def format_text(text):
     return re.sub(pattern, '', no_possessive)
 
 
-def get_recall_event_text(event_boundaries, subid):
-    onset, offset = event_boundaries
-    transcript_path = RAW_DIR.joinpath(f'NN{subid} transcript.txt')
-    with transcript_path.open(encoding='cp1252') as f:
-        transcript = f.read().replace(b'\x92'.decode('cp1252'), "'").strip()
-
-    textlist = transcript.split('.')
-    windows = []
-    window_n = 0
-    for w_ix in range(1, RECALL_WSIZE):
-        if onset <= window_n <= offset:
-            start, end = 0, w_ix
-            windows.append('.'.join(textlist[start:end]))
-
-        window_n += 1
-
-    for w_ix in range(len(textlist)):
-        if onset <= window_n <= offset:
-            start = w_ix
-            end = w_ix + RECALL_WSIZE if w_ix + RECALL_WSIZE <= len(textlist) else len(textlist)
-            windows.append('.'.join(textlist[start:end]))
-
-        window_n += 1
-
-    full_reclist = '.'.join(windows).split('.')
-    recall_text_slice = pd.unique(full_reclist)
-    return '.'.join(recall_text_slice).strip() + '.'
-
-
-def get_video_event_text(event_boundaries):
-    onset, offset = event_boundaries
-    video_text = pd.read_excel(RAW_DIR.joinpath('Sherlock_Segments_1000_NN_2017.xlsx'))
-    text_slice = video_text.loc[(video_text['Start Time (TRs, 1.5s)'] >= onset)
-                                & (video_text['End Time (TRs, 1.5s)'] < offset),
-                                'Scene Details - A Level ']
-    return ' '.join(text_slice)
-
-
 def get_video_timepoints(window_spans, annotations):
     timepoints = []
     for first, last in window_spans:
@@ -99,7 +61,63 @@ def parse_windows(textlist, wsize):
 
 
 ########################################
-#         STATS/MATH FUNCTIONS         #
+#             TEXT RECOVERY            #
+########################################
+
+def get_recall_text(onset, offset, subid):
+    transcript_path = RAW_DIR.joinpath(f'NN{subid} transcript.txt')
+    with transcript_path.open(encoding='cp1252') as f:
+        transcript = f.read().replace(b'\x92'.decode('cp1252'), "'").strip()
+
+    textlist = transcript.split('.')
+    windows = []
+    window_n = 0
[…]

### 2020-08-17 code/sherlock_helpers/sherlock_helpers/load_cluster_output.py
final code cleanup

@@ -1,48 +1,0 @@
-import os
-import sys
-import spurplus
-from os.path import join as opj
-
-
-def load_cluster_output(hostname, username, password):
-    datadir_local = '../../data/processed/'
-    emb_path_remote = f'/dartfs/rc/lab/D/DBIC/CDL/{username}/sherlock-embedding/data/optimized/embeddings.npy'
-    emb_path_local = opj(datadir_local, 'embeddings.npy')
-
-    sl_dir_remote = f'/dartfs/rc/lab/D/DBIC/CDL/{username}/searchlights/data/'
-    sl_output_dr = opj(sl_dir_remote, 'finished')
-    sl_vdir_local = opj(datadir_local, 'searchlight_video')
-    sl_rdir_local = opj(datadir_local, 'searchlight_recall')
-
-    if not os.path.isdir(sl_vdir_local):
-        os.mkdir(sl_vdir_local)
-    if not os.path.isdir(sl_rdir_local):
-        os.mkdir(sl_rdir_local)
-
-    with spurplus.connect_with_retries(hostname=hostname,
-                                       username=username,
-                                       password=password) as remote:
-                                   # copy over embeddings
-                                   remote.get(emb_path_remote, emb_path_local)
-
-                                   # copy over searchlights
-                                   for analysis in ['video', 'recall']:
-                                       src_dir = opj(sl_output_dr, f'searchlight_{analysis}')
-                                       dest_dir = opj(datadir_local, f'searchlight_{analysis}')
-                                       perm_dir = opj(src_dir, 'perms')
-                                       for sub in range(1, 18):
-                                           # unshifted data
-                                           src_path = opj(src_dir, f'sub{sub}.npy')
-                                           dest_path = opj(dest_dir, f'sub{sub}.npy')
-                                           remote.get(src_path, dest_path)
-                                       # permuted data
-                                       for perm in range(100):
-                                           perm_src_path = opj(perm_dir, f'perm{perm}.nii.gz')
-                                           perm_dest_path = opj(dest_dir, f'perm{perm}.nii.gz')
-                                           remote.get(perm_src_path, perm_dest_path)
-
-                                    # copy over reference image
-                                    src_path = opj(sl_dir_remote, 'inputs', 'fMRI', 'ref_img.nii.gz')
-                                    dest_path = opj(sl_vdir_local, 'ref_img.nii.gz')
-                                   remote.get(src_path, dest_path)
-

### 2020-08-17 code/sherlock_helpers/sherlock_helpers/functions.py
minor cleanup

@@ -199,32 +199,35 @@ def draw_bounds(ax, model):
     return ax
 
 ########################################
-#            BRAIN ANALYSES            #
+#          ARRAY MANIPULATION          #
 ########################################
 
 
-def create_diag_mask(corrmat, diag_limit=None):
-    diag_mask = np.zeros_like(corrmat, dtype=bool)
+def create_diag_mask(arr, diag_start=0, diag_limit=None):
+    diag_mask = np.zeros_like(arr, dtype=bool)
     if diag_limit is None:
-        diag_limit = find_diag_limit(corrmat)
+        diag_limit = find_diag_limit(arr)
 
-    for k in range(1, diag_limit):
+    for k in range(diag_start, diag_limit):
         ix = kth_diag_indices(diag_mask, k)
         diag_mask[ix] = True
 
     return diag_mask
 
 
-def find_diag_limit(corrmat):
-    for k in range(corrmat.shape[0]):
-        d = np.diag(corrmat, k=k)
+def find_diag_limit(arr):
+    for k in range(arr.shape[0]):
+        d = np.diag(arr, k=k)
         if ~(d > 0).any():
             return k
 
 
 def kth_diag_indices(arr, k):
     row_ix, col_ix = np.diag_indices_from(arr)
-    return row_ix[:-k], col_ix[k:]
+    if k == 0:
+        return row_ix, col_ix
+    else:
+        return row_ix[:-k], col_ix[k:]
 
 
 def warp_recall(recall_traj, video_traj, return_paths=False):
@@ -255,7 +258,7 @@ def multicol_display(*outputs,
         # formats some common Python objects for display
         if isinstance(obj, str):
             return obj.replace('\n', '<br>')
-        elif isinstance(obj, (int, float)):
+        elif isinstance(obj, (int, float, np.integer, np.floating)):
             return str(obj)
         elif (isinstance(obj, (list, tuple, set, Iterator))
               or type(obj).__module__ == 'numpy'):

### 2020-08-17 paper/main.tex

@@
 
-% JRM STOPPED HERE...
-
 Although the example participant's recall topic proportions matrix has some visual similarity to the video topic proportions matrix, the time-varying topic proportions for the example participant's recalls are not as sparse as those for the video (compare Figs.~\ref{fig:model}A and D).
-Similarly, although there do appear to be periods of stability in the recall topic dynamics (i.e., most topics are active or inactive over contiguous blocks of time), the individual topics' overall timecourses are not as cleanly delineated as the video topics'.
-To examine these patterns in detail, we computed the timepoint-by-timepoint correlation matrix for the example participant's recall topic trajectory (Fig.~\ref{fig:model}E).
+Similarly, although there do appear to be periods of stability in the recall topic dynamics (i.e., most topics are active or inactive over contiguous blocks of time), the changes in topic activations that define event boundaries appear less clearly delineated in participants' recalls than in the episode's annotations.
+To examine these patterns in detail, we computed the timepoint-by-timepoint correlation matrix for the example participant's recall trajectory (Fig.~\ref{fig:model}E).
 As in the video correlation matrix (Fig.~\ref{fig:model}B), the example participant's recall correlation matrix has a strong block diagonal structure, indicating that their recalls are discretized into separated events.
@@
 First, although every individual participant's recalls could be segmented into discrete events (i.e., every individual participant's recall correlation matrix exhibited clear block diagonal structure; Fig.~\corrmats), each participant appeared to have a unique \textit{recall resolution}, reflected in the sizes of those blocks.
-While, some participants' recall topic proportions segmented into just a few events (e.g., Participants P4, P5, and P7), others' segmented into many shorter duration events (e.g., Participants P12, P13, and P17).
+While some participants' recall topic proportions segmented into just a few events (e.g., Participants P4, P5, and P7), others' segmented into many shorter duration events (e.g., Participants P12, P13, and P17).
 This suggests that different participants may be recalling the video with different levels of detail-- e.g., some might touch on just the major plot points, whereas others might attempt to recall every minor scene or action.
 The second clear pattern present in every individual participant's recall correlation matrix is that, unlike in the video correlation matrix, there are substantial off-diagonal correlations.
-Whereas each event in the original video was (largely) separable from the others (Fig.~\ref{fig:model}B), in transforming those separable events into memory, participants appear to be integrating across multiple events, blending elements of previously recalled and not-yet-recalled content into each newly recalled event~\citep[Figs.~\ref{fig:model}E, \corrmats; also see][]{MannEtal11, HowaEtal12}.
+Whereas each event in the original video was (largely) separable from the others (Fig.~\ref{fig:model}B), in transforming those separable events into memory, participants appear to be integrating across multiple events, blending elements of previously recalled and not-yet-recalled content into each newly recalled event~\citep[Figs.~\ref{fig:model}E, \corrmats; also see][]{MannEtal11, HowaEtal12, Mann19}.
 
@@
 Interestingly, for two of these analyses (probability of first recall and lag-conditional response probability curves) we observe patterns comparable to classic effects from the list-learning literature: namely, a higher probability of initiating recall with the first event in the sequence (Fig.~\ref{fig:list-learning}A) and a higher probability of transitioning to neighboring events with an asymmetric forward bias (Fig.~\ref{fig:list-learning}B).
-In contrast, we do not observe a pattern comparable to the serial position effect (Fig.~\ref{fig:list-learning}C), but rather we see higher memory for specific events distributed somewhat evenly throughout the video.
+In contrast, we do not observe a pattern comparable to the serial position effect (Fig.~\ref{fig:list-learning}C), but rather we see higher memory for specific events distributed approximately evenly throughout the video.
 
@@
 \textbf{C.} The proportion of participants who recalled each event, as a function of the serial position of the events in the video.
-All panels: error bars denote bootstrap-estimated standard error of the mean.}
+All panels: error ribbons denote bootstrap-estimated standard error of the mean.}
   \label{fig:list-learning}
@@
 Such approaches are tenable in classical list-learning or recognition memory paradigms, as the presented stimuli tend to be very simple (e.g., a sequence of individual words or items).
-However, the feature-rich content of a naturalistic experiences may later be described with many, highly variable levels of success.
-Our framework produces a content-based model of individual stimulus and recall events by projecting the dynamic content of the video and participants' recalls into a shared topic space.
-This allows for direct, quantitative comparison between all stimulus and recall events, as well as between the recall events themselves.
+However, memory for naturalistic experiences is much more nuanced.
+For example, certain aspects of an experience might be correctly remembered at varying levels of detail, distorted, or forgotten.
+Further, each remembering is itself a richly structured phenomenon.
+Our framework produces a content-based model of individual video and recall events by projecting the dynamic content of the video and participants' recalls into a shared topic space.
+This allows for direct, quantitative comparisons between all stimulus and recall events, as well as between the recall events themselves.
 Leveraging these content-based models of the stimulus/recall events, we developed two novel, \textit{continuous} metrics for analyzing naturalistic memory:~\textit{precision} and \textit{distinctiveness}.
-We define precision as the ``completeness" of recall, or how fully the presented content was recapitulated in memory.
-Under our framework, we quantify this for a given recall event as the correlation between the topic proportions of the recall event and the maximally correlated video event (Fig.~\ref{fig:precision-distinctiveness}).
-A second novel metric we introduce here is \textit{distinctiveness}, which we define as the ``specificity" of recall, or how unique the description of a given section of content was, compared to descriptions for other sections of content.
-We quantify this for each recall event as 1 minus the average correlation between the given recall event and all other recall events not matched to the same video event.
+Precision is intended to capture the ``completeness'' of recall, or how fully the presented content was recapitulated in memory.
+We define a recall event's precision as the maximum correlation between the topic proportions of that recall event and any video event (Fig.~\ref{fig:precision-distinctiveness}).
+A second novel metric we introduce here is \textit{distinctiveness}, which is intended to capture the ``specificity'' of recall.
+In other words, distinctiveness quantifies how much the transcript of a given recalled event references that event in particular, as opposed to other video events.
+To compute a recall event's distinctiveness, we first identify the video event that it's topic vector is most strongly correlated with.
+We then define distinctiveness as 1 minus the average correlation between the given recall event and all \textit{other} video events.
 In addition to individual events, one may also use these metrics to describe each participant's overall performance (i.e., by averaging across a participant's event-wise precision or distinctiveness scores).
 Participants whose recall events are more veridical descriptions of what happened in the video event will presumably have higher precision scores.
-We find that, across participants, a higher precision score is correlated to both hand-annotated memory performance (Pearson's $r(15) = 0.60, p = 0.010$) and the number of video events successfully remembered, as determined by our model (Pearson's $r(15) = 0.90, p < 0.001$).
+We find that, across participants, higher precision scores are positively correlated with both hand-annotated memory performance (Pearson's $r(15) = 0.60, p = 0.010$) and the number of video events successfully remembered, as determined by our model (Pearson's $r(15) = 0.90, p < 0.001$).
 We also hypothesized that participants who recounted events in a more distinctive way would display better overall memory.
-We find that this distinctiveness score is related to our model's estimated number of recalled events (Pearson's $r(15) = 0.55, p = 0.021$), and while we do not find distinctiveness to be related to hand-annotated memory performance (Pearson's $r(15) = 0.28, p = 0.275$), this is not entirely surprising given how the hand-annotated memory scores were computed (see \textit{Methods} and \textit{Discussion} for details).
+We find that participants' distinctiveness scores were
+correlated with our model's estimated number of recall events (Pearson's $r(15) = 0.55, p = 0.021$).
+However, we found no evidence that distinctiveness scores were correlated with hand-annotated memory performance (Pearson's $r(15) = 0.28, p = 0.275$).
+We elaborate on this potential discrepency in the \textit{Discussion} section.
+
+%% JRM STOPPED HERE
 

### 2020-08-17 paper/old.tex

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage{geometry}
\usepackage{natbib}
\usepackage{pxfonts}
\usepackage{graphicx}
\usepackage{newfloat}
\usepackage{setspace}
\usepackage{hyperref}
\usepackage{lineno}

\newcommand{\argmax}{\mathop{\mathrm{argmax}}\limits}

\newcommand{\topicopt}{S1}
\newcommand{\topics}{S2}
\newcommand{\featureimportance}{S3}
\newcommand{\listlearning}{S4}
\newcommand{\corrmats}{S5}
\newcommand{\matchmats}{S6}

\doublespacing
\linenumbers

\title{How is experience transformed into memory?}
\author{Andrew C. Heusser, Paxton C. Fitzpatrick, and Jeremy R. Manning\\Department of Psychological and Brain Sciences\\Dartmouth College, Hanover, NH 03755, USA\\Corresponding author: jeremy.r.manning@dartmouth.edu}

\bibliographystyle{apa}

\begin{document}
\maketitle

\begin{abstract}
The ways our experiences unfold over time define unique \textit{trajectories} through the relevant representational spaces.  Within this geometric framework, one can compare the shape of the trajectory formed by an experience to that defined by our later remembering of that experience.  We propose a framework for mapping naturalistic experiences onto geometric spaces that characterize how they unfold over time.  We apply this approach to a naturalistic memory experiment which had participants view and recount a video.  We found that the shapes of the trajectories formed by participants' recountings were all highly similar to that of the original video, but participants differed in the level of detail they remembered.  We also identified a network of brain structures that are sensitive to the ``shapes'' of our ongoing experiences, and an overlapping network that is sensitive to how we will later remember those experiences.
\end{abstract}

\section*{Introduction}

What does it mean to \textit{remember} something? In traditional episodic memory experiments \citep[e.g., list-learning or trial-based experiments;][]{Murd62a, Kaha96}, remembering is often cast as a discrete and binary operation: each studied item may be separated from the rest of one's experiences, and that item may be labeled as having been recalled versus forgotten. More nuanced studies might incorporate self-reported confidence measures as a proxy for memory strength, or ask participants to discriminate between ``recollecting'' the (contextual) details of an experience or having a general feeling of ``familiarity'' \citep{Yone02}. However, characterizing and evaluating memory in more realistic contexts (e.g., recounting a recent experience to a friend) is fundamentally different in at least three ways~\citep[for review also see][]{KoriGold94, HukEtal18}.  First, real world recall is continuous, rather than discrete.  Unlike in trial-based experiments, removing a (naturalistic) event from the context in which it occurs can substantially change its meaning.  Second, the specific words used to describe an experience have little bearing on whether the experience should be considered to have been ``remembered.''  Asking whether the rememberer has precisely reproduced a specific set of words to describe a given experience is nearly orthogonal to whether they were actually able to remember it.  In classic (e.g., list-learning) memory studies, by contrast, counting the number or proportion of precise recalls is often a primary metric of assessing the quality of participants' memories.  Third, one might remember the \textit{gist} or essence of an experience but forget (or neglect to recount) particular details.  Capturing the gist of what happened is typically the main ``point'' of recounting a memory to a listener whereas, depending on the circumstances, accurate recall of any specific detail may be irrelevant.  There is no analog of the gist of an experience in most traditional memory experiments; rather we tend to assess participants' abilities to recover specific details (e.g., computing the proportion of specific stimuli they remember, which presentation positions the remembered stimuli came from, etc.).

How might one go about formally characterizing the gist of an experience, or whether that gist has been recovered by the rememberer?  Any given moment of an experience derives meaning from surrounding moments, as well as from longer-range temporal associations~\citep[e.g., ][]{LernEtal11}.  Therefore the timecourse describing how an event unfolds is fundamental to its overall meaning.  Further, this hierarchy formed by our subjective experiences at different timescales defines a \textit{context} for each new moment~\citep[e.g., ][]{HowaKaha02, HowaEtal14}, and plays an important role in how we interpret that moment and remember it later~\citep[for review see][]{MannEtal15}.  Our memory systems can then leverage these associations to form predictions that help guide our behaviors~\citep{RangRitc12}.  For example, as we navigate the world, the features of our subjective experiences tend to change gradually (e.g., the room or situation we are in is strongly temporally autocorrelated), allowing us to form stable estimates of our current situation and behave accordingly~\citep{ZackEtal07, ZwaaRadv98}.  Although our experiences most often change gradually, they also occasionally change suddenly~\citep[e.g., when we walk through a doorway; ][]{RadvZack17}.  Prior research suggests that these sharp transitions (termed \textit{event boundaries}) during an experience help to discretize our experiences into \textit{events}~\citep{RadvZack17, BrunEtal18, HeusEtal18b, ClewDava17, EzzyDava11, DuBrDava13}.  The interplay between the stable (within event) and transient (across event) temporal dynamics of an experience also provides a potential framework for transforming experiences into memories that distill those experiences down to their essence-- i.e., their gists.  For example, prior work has shown that event boundaries can influence how we learn sequences of items~\citep{HeusEtal18b, DuBrDava13}, navigate~\citep{BrunEtal18}, and remember and understand narratives~\citep{ZwaaRadv98, EzzyDava11}.

Here we sought to examine how the temporal dynamics of a ``naturalistic'' experience were reflected in participants' later memories of that experience.  We analyzed an open dataset that comprised behavioral and functional Magnetic Resonance Imaging (fMRI) data collected as participants viewed and then verbally recalled an episode of the BBC television series \textit{Sherlock}~\citep{ChenEtal17}.  We developed a computational framework for characterizing the temporal dynamics of the moment-by-moment content of the episode and of participants' verbal recalls.  Specifically, we use topic modeling~\citep{BleiEtal03} to characterize the thematic conceptual (semantic) content present in each moment of the episode and recalls, and we use Hidden Markov Models~\citep{Rabi89, BaldEtal17} to discretize the evolving semantic content into events.  In this way, we cast naturalistic experiences (and recalls of those experiences) as \textit{topic trajectories} that describe how the experiences evolve over time.  In other words, the episode's topic trajectory is a formalization of its gist.  Under this framework, successful remembering entails verbally ``traversing'' the topic trajectory of the original episode, thereby reproducing the original episode's gist.  In addition, comparing the shapes of the topic trajectories of the original episode and of participants' retellings of the episode reveals which aspects of the episode were preserved (or lost) in the translation into memory.  We also identified a network of brain structures whose responses (as participants watched the episode) reflected the gist of the episode, and a second network whose responses reflected how participants would later recount the episode.

\section*{Results}
To characterize the gists of the \textit{Sherlock} episode participants watched and their subsequent recountings of the episode, we used a topic model~\citep{BleiEtal03} to discover the latent thematic content in the video.  Topic models take as inputs a vocabulary of words to consider and a collection of text documents; they return as output two matrices.  The first output is a \textit{topics matrix} whose rows are topics (latent themes) and whose columns correspond to words in the vocabulary. The entries of the topics matrix define how each word in the vocabulary is weighted by each discovered topic.  For example, a detective-themed topic might weight heavily on words like ``crime,'' and ``search.''  The second output is a \textit{topic proportions matrix}, with one row per document and one column per topic.  The topic proportions matrix describes which mix topics is reflected in each document.

\cite{ChenEtal17} collected hand-annotated information about each of 1000 (manually identified) scenes spanning the roughly 45 minute video used in their experiment.  This information included: a brief narrative description of what was happening; whether the scene took place indoors vs. outdoors; names of any characters on the screen; names of any characters who were in focus in the camera shot; names of characters who were speaking; the location where the scene took place; the camera angle (close up, medium, long, etc.); whether or not background music was present; and other similar details (for a full list of annotated features see \textit{Methods}).  We took from these annotations the union of all unique words (excluding stop words, such as ``and,'' ``or,'' ``but,'' etc.) across all features and scenes as the ``vocabulary'' for the topic model.  We then concatenated the sets of words across all features contained in overlapping 50-scene sliding windows, and treated each 50-scene sequence as a single ``document'' for the purposes of fitting the topic model.  Next, we fit a topic model with (up to) $K = 100$ topics to this collection of documents.  We found that 27 unique topics (with non-zero weights) were sufficient to describe the time-varying content of the video (see \textit{Methods}; Figs.~\ref{fig:schematic}, \topics).  Note that our approach is similar in some respects to Dynamic Topic Models~\citep{BleiLaff06}, in that we sought to characterize how the thematic content of the episode evolved over time.  However, whereas Dynamic Topic Models are designed to characterize how the properties of \textit{collections} of documents change over time, our sliding window approach allows us to examine the topic dynamics within a single document (or video).  Specifically, our approach yielded (via the topic proportions matrix) a single \textit{topic vector} for each timepoint of the episode (we set timepoints to match the acquisition times of the 1976 fMRI volumes collected as participants viewed the episode).

\begin{figure}[tp]
\centering
\includegraphics[width=1\textwidth]{figs/schematic}
\caption{\small \textbf{Methods overview.} We used hand-annotated descriptions of each moment of video to fit a topic model.  Three example video frames and their associated descriptions are displayed (top two rows).  Participants later recalled the video (in the third row, we show example recalls of the same three scenes from participant 13).  We used the topic model (fit to the annotations) to estimate topic vectors for each moment of video and each sentence the participants recalled.  Example topic vectors are displayed in the bottom row (blue: video annotations; green: example participant's recalls).  Three topic dimensions are shown (the highest-weighted topics for each of the three example scenes, respectively).  We also show the ten highest-weighted words for each topic.  Figure~\topics~provides a full list of the top 10 words from each of the discovered topics.}
\label{fig:schematic}
\end{figure}

The topics we found were heavily character-focused (e.g., the top-weighted word in each topic was nearly always a character) and could be roughly divided into themes that were primarily Sherlock Holmes-focused (Sherlock is the titular character); primarily John Watson-focused (John is Sherlock's close confidant and assistant); or that involved Sherlock and John interacting (Fig.~\topics).  Several of the topics were highly similar, which we hypothesized might allow us to distinguish between subtle narrative differences (if the distinctions between those overlapping topics were meaningful; also see Fig.~\featureimportance).  The topic vectors for each timepoint were \textit{sparse}, in that only a small number (usually one or two) of topics tended to be ``active'' in any given timepoint (Fig.~\ref{fig:model}A).  Further, the dynamics of the topic activations appeared to exhibit \textit{persistance} (i.e., given that a topic was active in one timepoint, it was likely to be active in the following timepoint) along with \textit{occasional rapid changes} (i.e., occasionally topics would appear to spring into or out of existence).  These two properties of the topic dynamics may be seen in the block diagonal structure of the timepoint-by-timepoint correlation matrix (Fig.~\ref{fig:model}B).  Following \cite{BaldEtal17}, we used a Hidden Markov Model (HMM) to identify the \textit{event boundaries} where the topic activations changed rapidly (i.e., at the boundaries of the blocks in the correlation matrix; event boundaries identified by the HMM are outlined in yellow).  Part of our model fitting procedure required selecting an appropriate number of ``events'' to segment the timeseries into.  We used an optimization procedure to identify the number of events that maximized within-event stability while also minimizing across-event correlations (see \textit{Methods} for additional details).  To create a stable ``summary'' of the video, we computed the average topic vector within each event (Fig.~\ref{fig:model}C).

\begin{figure}[tp]
\centering
\includegraphics[width=\textwidth]{figs/eventseg}
\caption{\small \textbf{Modelling naturalistic stimuli and recalls.} All panels: darker colors indicate greater values; range: [0, 1].  \textbf{A.} Topic vectors ($K = 100$) for each of the 1976 video timepoints.  \textbf{B.} Timepoint-by-timepoint correlation matrix of the topic vectors displayed in Panel A.  Event boundaries detected by the HMM are denoted in yellow (34 events detected).  \textbf{C.} Average topic vectors for each of the 34 video events. \textbf{D.} Topic vectors for each of 294 sentences spoken by an example participant while recalling the video.  \textbf{E.} Timepoint-by-timepoint correlation matrix of the topic vectors displayed in Panel D. Event boundaries detected by the HMM are denoted in yellow (27 events detected).  \textbf{F.} Average topic vectors for each of the 27 recalled events from the example participant.  \textbf{G.} Correlations between the topic vectors for every pair of video events (Panel C) and recalled events (from the example participant; Panel F).  For similar plots for all participants see Figure~\matchmats.  \textbf{H.} Average correlations between each pair of video events and recalled events (across all 17 participants).  To create the figure, each recalled event was assigned to the video event with the most correlated topic vector (yellow boxes in panels G and H).  The heat maps in each panel were created using \texttt{Seaborn}~\citep{WaskEtal16}.}
\label{fig:model}
\end{figure}

Given that the time-varying content of the video could be segmented cleanly into discrete events, we wondered whether participants' recalls of the video also displayed a similar structure.  We applied the same topic model (already trained on the video annotations) to each participant's recalls.  Analogous to how we analyzed the time-varying content of the video, to obtain similar estimates for participants' recalls, we treated each (overlapping) 10 sentence ``window'' of their transcript as a ``document'' and then computed the most probable mix of topics reflected in each timepoint's sentences.  This yielded, for each participant, a number-of-sentences by number-of-topics topic proportions matrix that characterized how the topics identified in the original video were reflected in the participant's recalls.  Note that an important feature of our approach is that it allows us to compare participant's recalls to events from the original video, despite that different participants may have used different language to describe the same event, and that those descriptions may not match the original annotations.  This is a huge benefit of projecting the video and recalls into a shared ``topic'' space.  An example topic proportions matrix from one participant's recalls is shown in Figure~\ref{fig:model}D.

Although the example participant's recall topic proportions matrix has some visual similarity to the video topic proportions matrix, the time-varying topic proportions for the example participant's recalls are not as sparse as for the video (e.g., compare Figs.~\ref{fig:model}A and D).  Similarly, although there do appear to be periods of stability in the recall topic dynamics (e.g., most topics are active or inactive over contiguous blocks of time), the overall timecourses are not as cleanly delineated as the video topics are.  To examine these patterns in detail, we computed the timepoint-by-timepoint correlation matrix for the example participant's recall topic proportions (Fig.~\ref{fig:model}E).  As in the video correlation matrix (Fig.~\ref{fig:model}B), the example participant's recall correlation matrix has a strong block diagonal structure, indicating that their recalls are discretized into separated events.  As for the video correlation matrix, we can use an HMM, along with the aforementioned number-of-events optimization procedure (also see \textit{Methods}) to determine how many events are reflected in the participant's recalls and where specifically the event boundaries fall (outlined in yellow).  We carried out a similar analysis on all 17 participants' recall topic proportions matrices (Fig.~\corrmats).

Two clear patterns emerged from this set of analyses.  First, although every individual participant's recalls could be segmented into discrete events (i.e., every individual participant's recall correlation matrix exhibited clear block diagonal structure; Fig.~\corrmats), each participant appeared to have a unique \textit{recall resolution}, reflected in the sizes of those blocks.  For example, some participants' recall topic proportions segmented into just a few events (e.g., Participants P1, P4, and P15), while others' recalls segmented into many shorter duration events (e.g., Participants P12, P13, and P17).  This suggests that different participants may be recalling the video with different levels of detail-- e.g., some might touch on just the major plot points, whereas others might attempt to recall every minor scene.  The second clear pattern present in every individual participant's recall correlation matrix is that, unlike in the video correlation matrix, there are substantial off-diagonal correlations in participant's recalls.  Whereas each event in the original video (was largely) separable from the others (Fig.~\ref{fig:model}B), in transforming those separable events into memory participants appear to be integrating \textit{across} different events, blending elements of previously recalled and not-yet-recalled events into each newly recalled event~\citep[Figs.~\ref{fig:model}D, \corrmats; also see][]{MannEtal11, HowaEtal12}.

The above results indicate that both the structure of the original video and participants' recalls of the video exhibit event boundaries that can be identified automatically by characterizing the dynamic content using a shared topic model and segmenting the content into events using HMMs.  Next we asked whether some correspondence might be made between the specific content of the events the participants experienced in the video, and the events they later recalled.  One approach to linking the experienced (video) and recalled events is to label each recalled event as matching the video event with the most similar (i.e., most highly correlated) topic vector (Figs.~\ref{fig:model}G, \matchmats).  This yields a sequence of ``presented'' events from the original video, and a sequence of (potentially differently ordered) ``recalled'' events for each participant.  Analogous to classic list-learning studies, we can then examine participants' recall sequences by asking which events they tended to recall first~\citep[probability of first recall; Fig.~\listlearning A;][]{WelcBurn24, PostPhil65, AtkiShif68}; how participants most often transition between recalls of the events as a function of the temporal distance between them~\citep[lag-conditional response probability; Fig.~\listlearning B;][]{Kaha96}; and which events they were likely to remember overall~\citep[serial position recall analyses; Fig.~\listlearning C;][]{Murd62a}.  In list-learning studies, this set of three analyses may be used to gain a nearly complete view into the sequences of recalls participants made~\citep[e.g., ][]{Kaha12}.  Extending these analyses to apply to naturalistic stimuli and recall~\citep{HeusEtal17b} highlights that, in naturalistic recall, these analyses provide a wholly incomplete picture: they leave out any attempt to quantify participants' abilities to capture the \textit{content} of what occurred in the video-- their only experimental instruction!

The dynamic content of the video and participants' recalls is quantified in the corresponding topic proportion matrices.  However, it is difficult to gain deep insights into that content solely by examining the topic proportion matrices (e.g., Figs.~\ref{fig:model}A, D) or the corresponding correlation matrices (Figs.~\ref{fig:model}B, E, \corrmats).  To visualize the time-varying high-dimensional content in a more intuitive way~\citep{HeusEtal18a} we projected the topic proportions matrices onto a two-dimensional space using Uniform Manifold Approximation and Projection~\citep[UMAP; ][]{McInHeal18}.  In this lower-dimensional space, each point represents a single video or recall event, and the distances between the points reflect the distances between the events' associated topic vectors (Fig.~\ref{fig:trajectory}).

\begin{figure}[tp]
\centering
\includegraphics[width=1\textwidth]{figs/trajectory}
\caption{\small \textbf{Trajectories through topic space capture the dynamic content of the video and recalls.}  All panels: the topic proportion matrices have been projected onto a shared two-dimensional space using UMAP.  \textbf{A.} The two-dimensional topic trajectory taken by the episode of \textit{Sherlock}.  Each dot indicates an event identified using the HMM (see \textit{Methods}); the dot colors denote the order of the events (early events are in red; later events are in blue), and the connecting lines indicate the transitions between successive events.  \textbf{B.} The average two-dimensional trajectory captured by participants' recall sequences, with the same format and coloring as the trajectory in Panel A.  To compute the event positions, we matched each recalled event with an event from the original video (see \textit{Results}), and then we averaged the positions of all events with the same label.  The arrows reflect the average transition direction through topic space taken by any participants whose trajectories crossed that part of topic space; blue denotes reliable agreement across participants via a Rayleigh test ($p < 0.05$, corrected).  \textbf{C.} The recall topic trajectories (gray) taken by each individual participant (P1--P17).  The video's trajectory is shown in black for reference.  (Same format and coloring as Panel A.)}
\label{fig:trajectory}
\end{figure}

Visual inspection of the video and recall topic trajectories reveals a striking pattern.  First, the topic trajectory of the video (which reflects its dynamic content; Fig.~\ref{fig:trajectory}A) is captured nearly perfectly by the averaged topic trajectories of participants' recalls (Fig.~\ref{fig:trajectory}B).  To assess the consistency of these recall trajectories across participants, we asked: given that a participant's recall trajectory had entered a particular location in topic space, could the position of their \textit{next} recalled event be predicted reliably?  For each location in topic space, we computed the set of line segments connecting successively recalled events (across all participants) that intersected that location (see \textit{Methods} for additional details).  We then computed (for each location) the distribution of angles formed by the lines defined by those line segments and a fixed reference line (the $x$-axis).  Rayleigh tests revealed the set of locations in topic space at which these across-participant distributions exhibited reliable peaks (blue arrows in Fig.~\ref{fig:trajectory}B reflect significant peaks at $p < 0.05$, corrected).  We observed that the locations traversed by nearly the entire video trajectory exhibited such peaks.  In other words, participants exhibited similar trajectories that also matched the trajectory of the original video (Fig.~\ref{fig:trajectory}C).  This is especially notable when considering the fact that the number of events participants recalled (dots in Fig.~\ref{fig:trajectory}C) varied considerably across people, and that every participant used different words to describe what they had remembered happening in the video.  Differences in the numbers of remembered events appear in participants' trajectories as differences in the sampling resolution along the trajectory.  We note that this framework also provides a means of detangling classic ``proportion recalled'' measures (i.e., the proportion of video events referenced in participants' recalls) from participants' abilities to recapitulate the full gist of the original video (i.e., the similarity in the shape of the original video trajectory and that defined by each participant's recounting of the video).

Because our analysis framework projects the dynamic video content and participants' recalls onto a shared topic space, and because the dimensions of that space are known (i.e., each topic dimension is a set of weights over words in the vocabulary; Fig.~\topics), we can examine the topic trajectories to understand which specific content was remembered well (or poorly).  For each video event, we can ask: what was the average correlation (across participants) between the video event's topic vector and the closest matching recall event topic vectors from each participant? This yields a single correlation coefficient for each video event, describing how closely participants' recalls of the event tended to reliably capture its content (Fig.~\ref{fig:topics}A).  (We also examined how different comparisons between each video event's topic vector and the corresponding recall event topic vectors related to hand-annotated characterizations of memory performance; see \textit{Supporting Information}).  Given this summary of which events were recalled reliably (or not), we next asked whether the better-remembered or worse-remembered events tended to reflect particular topics.  We computed a weighted average of the topic vectors for each video event, where the weights reflected how reliably each event was recalled.  To visualize the result, we created a ``wordle'' image~\citep{MuelEtal18} where words weighted more heavily by better-remembered topics appear in a larger font (Fig.~\ref{fig:topics}B, green box).  Events that reflected topics weighting heavily on characters like ``Sherlock'' and ``John'' (i.e., the main characters) and locations like ``221b Baker Street'' (i.e., a major recurring location and the address of the flat that Sherlock and John share) were best remembered.  An analogous analysis revealed which themes were poorly remembered.  Here in computing the weighted average over events' topic vectors we weighted each event in \textit{inverse} proportion to how well it was remembered (Fig.~\ref{fig:topics}B, red box).  This revealed that events with relatively minor characters such as ``Mike,'' ``Jeffrey,'' and ``Molly,'' as well as less-integral plot locations (e.g., ``hospital'' and ``office'') were least well-remembered.  This suggests that what is retained in memory are the major plot elements (i.e., the overall ``gist'' of what happened), whereas the more minor details are prone to pruning.

In addition to constructing overall summaries, assessing the video and recall topic vectors from individual recalls can provide further insights.  Specifically, for any given event we can construct two wordles: one from the original video event's topic vector, and a second from the average topic vectors produced by all participants' recalls of that event.  We can then examine those wordles visually to gain an intuition for which aspects of the video event were recapitulated in participants' recalls of that event.  Several example wordles are displayed in Figure~\ref{fig:topics}C (wordles from the three best-remembered events are circled in green; wordles from the three worst-remembered events are circled in red).  Using wordles to visually compare the topical content of each video event and the (average) corresponding recall event reveals the specific content from the specific events that is reliably retained in the transformation into memory (green events) or not (red events).

\begin{figure}[tp]
\centering
\includegraphics[width=1\textwidth]{figs/topics}
\caption{\small \textbf{Transforming experience into memory.} \textbf{A.} Average correlations (across participants) between the topic vectors from each video event and the closest-matching recall events.  Error bars denote bootstrap-derived across-participant 95\% confidence intervals.  The stars denote the three best-remembered events (green) and worst-remembered events (red).  \textbf{B.} Wordles comprising the top 200 highest-weighted words reflected in the weighted-average topic vector across video events.  Green: video events were weighted by how well the topic vectors derived from recalls of those events matched the video events' topic vectors (Panel A).  Red: video events were weighted by the inverse of how well their topic vectors matched the recalled topic vectors.  \textbf{C.}  The set of all video and recall events is projected onto the two-dimensional space derived in Figure~\ref{fig:trajectory}.  The dots outlined in black denote video events (dot size reflects the average correlation between the video event's topic vector and the topic vectors from the closest matching recalled events from each participant; bigger dots denote stronger correlations).  The dots without black outlines denote recalled events.  All dots are colored using the same scheme as Figure~\ref{fig:trajectory}A.  Wordles for several example events are displayed (green: three best-remembered events; red: three worst-remembered events).  Within each circular wordle, the left side displays words associated with the topic vector for the video event, and the right side displays words associated with the (average) recall event topic vector, across all recall events matched to the given video event.}
\label{fig:topics}
\end{figure}

The results thus far inform us about which aspects of the dynamic content in the episode participants watched were preserved or altered in participants' memories of the episode.  We next carried out a series of analyses aimed at understanding which brain structures might implement these processes.  In one analysis we sought to identify which brain structures were sensitive to the video's dynamic content, as characterized by its topic trajectory.  Specifically, we used a searchlight procedure to identify the extent to which each cluster of voxels exhibited a timecourse (as the participants watched the video) whose temporal correlation matrix matched the temporal correlation matrix of the original video's topic proportion matrix (Fig.~\ref{fig:model}B).  As shown in Figure~\ref{fig:brainz}A, the analysis revealed a network of regions including bilateral frontal cortex and cingulate cortex, suggesting that these regions may play a role in maintaining information relevant to the narrative structure of the video.  In a second analysis, we sought to identify which brain structures' responses (while viewing the video) reflected how each participant would later \textit{recall} the video.  We used an analogous searchlight procedure to identify clusters of voxels whose temporal correlation matrices reflected the temporal correlation matrix of the topic proportions for each individual's recalls (Figs.~\ref{fig:model}D, \corrmats).  As shown in Figure~\ref{fig:brainz}B, the analysis revealed a network of regions including the ventromedial prefrontal cortex (vmPFC), anterior cingulate cortex, and right medial temporal lobe (rMTL), suggesting that these regions may play a role in transforming each individual's experience into memory.  In identifying regions whose responses to ongoing experiences reflect how those experiences will be remembered later, this latter analysis extends classic \textit{subsequent memory analyses}~\citep[e.g.,][]{PallWagn02} to domain of naturalistic stimuli.

\begin{figure}[tp]
\centering
\includegraphics[width=1\textwidth]{figs/searchlights}
\caption{\small \textbf{Brain structures that underlie the transformation of experience into memory.} \textbf{A.} We searched for regions whose responses (as participants watched the video) matched the temporal correlation matrix of the video topic proportions.  These regions are sensitive to the narrative structure of the video.  \textbf{B.} We searched for regions whose responses (as participants watched the video) matched the temporal correlation matrix of the topic proportions derived from each individual's later recall of video.  These regions are sensitive to how the narrative structure of the video is transformed into a memory of the video.  Both panels: the maps are thresholded at $p < 0.05$, corrected.}
\label{fig:brainz}
\end{figure}

\section*{Discussion}
\label{sec:discussion}

Our work casts remembering as reproducing (behaviorally and neurally) the topic trajectory, or ``gist,'' of the original experience.  This view draws inspiration from prior work aimed at elucidating the neural and behavioral underpinnings of how we process dynamic naturalistic experiences and remember them later.  One approach to identifying neural responses to naturalistic stimuli (including experiences) entails building a model of the stimulus and searching for brain regions whose responses are consistent with the model.  In prior work, a series of studies from Uri Hasson's group~\citep{LernEtal11, SimoEtal16, ChenEtal17, BaldEtal17, ZadbEtal17} have extended this approach with a clever twist.  Rather than building an explicit stimulus model, these studies instead search for brain responses (while experiencing the stimulus) that are reliably similar across individuals.  So called \textit{inter-subject correlation} (ISC) and \textit{inter-subject functional connectivity} (ISFC) analyses effectively treat other people's brain responses to the stimulus as a ``model'' of how its features change over time.  By contrast, in our present work we used topic models and HMMs to construct an explicit stimulus model (i.e., the topic trajectory of the video).  When we searched for brain structures whose responses are consistent with the video's topic trajectory, we identified a network of structures that overlapped strongly with the ``long temporal receptive window'' network reported by the Hasson group~\citep[e.g., compare our Fig.~\ref{fig:brainz}A with the map of long temporal receptive window voxels in][]{LernEtal11}.  This provides support for the notion that part of the long temporal receptive window network may be maintaining an explicit model of the stimulus dynamics.  When we performed a similar analysis after swapping out the video's topic trajectory with the recall topic trajectories of each individual participant, this allowed us to identify brain regions whose responses (as the participants viewed the video) reflected how the video trajectory would be transformed in memory (as reflected by the recall topic trajectories).  The analysis revealed that the rMTL and vmPFC may play a role in this person-specific transformation from experience into memory.  The role of the MTL in episodic memory encoding has been well-reported~\citep[e.g., ][]{PallWagn02, DavaEtAl03, RangEtal04, Dava06}.  Prior work has also implicated the medial prefrontal cortex in representing ``schema'' knowledge~\citep[i.e., general knowledge about the format of an ongoing experience given prior similar experiences; ][]{KestEtal12, SchlPres15, GilbMarl17, SpalEtal18}.  Integrating across our study and this prior work, one interpretation is that the person-specific transformations mediated (or represented) by the rMTL and vmPFC may reflect schema knowledge being leveraged, formed, or updated, incorporating ongoing experience into previously acquired knowledge.

Our work has broad implications for how we characterize and assess memory in real-world settings such as the classroom or physician's office.  For example, the most commonly used classroom evaluation tools involve computing the proportion of correctly answered exam questions.  Our work indicates that this approach is only loosely related to what educators might really want to measure: how well did the students understand the key ideas presented in the course?  One could apply the computational framework we developed to construct topic trajectories for the video and participants' recalls to build explicit content models of the course material and exam questions.  This approach would provide a more nuanced and specific view into which aspects of the material students had learned well (or poorly).  In clinical settings, memory measures that incorporate such explicit content models might also provide more direct evaluations of patients' memories.

\section*{Methods}
\label{sec:methods}

\subsection*{Experimental design and data collection}
Data were collected by \cite{ChenEtal17}.  In brief, participants ($n=17$) viewed the first 48 minutes of ``A Study in Pink'', the first episode of the BBC television series \textit{Sherlock}, while fMRI volumes were collected (TR = 1500~ms).  The stimulus was divided into a 23~min (946~TR) and a 25~min (1030~TR) segment to mitigate technical issues related to the scanner.  After finishing the clip, participants were instructed to \citep[quoting from][]{ChenEtal17} ``describe what they recalled of the [episode] in as much detail as they could, to try to recount events in the original order they were viewed in, and to speak for at least 10 minutes if possible but that longer was better. They were told that completeness and detail were more important than temporal order, and that if at any point they realized they had missed something, to return to it. Participants were then allowed to speak for as long as they wished, and verbally indicated when they were finished (e.g., `I’m done').''  For additional details about the experimental procedure and scanning parameters see \cite{ChenEtal17}.  The experimental protocol was approved by Princeton University's Institutional Review Board.

After preprocessing the fMRI data and warping the images into a standard (3~mm$^3$ MNI) space, the voxel activations were $z$-scored (within voxel) and spatially smoothed using a 6~mm (full width at half maximum) Gaussian kernel.  The fMRI data were also cropped so that all video-viewing data were aligned across participants.  This included a constant 3 TR (4.5~s) shift to account for the lag in the hemodynamic response.  \citep[All of these preprocessing steps followed][where additional details may be found.]{ChenEtal17}

\subsection*{Data and code availability}
The fMRI data we analyzed are available online \href{http://dataspace.princeton.edu/jspui/handle/88435/dsp01nz8062179}{\underline{here}}.  The behavioral data and all of our analysis code may be downloaded \href{https://github.com/ContextLab/sherlock-topic-model-paper}{\underline{here}}.

\subsection*{Statistics}
All statistical tests we performed were two-sided.

\subsection*{Modeling the dynamic content of the video and recall transcripts}
\subsubsection*{Topic modeling}
The input to the topic model we trained to characterize the dynamic content of the video comprised hand-generated annotations of each of 1000 scenes spanning the video clip~\citep[generated by][]{ChenEtal17}.  The features included: narrative details (a sentence or two describing what happened in that scene); whether the scene took place indoors or outdoors; names of any characters that appeared in the scene; name(s) of characters in camera focus; name(s) of characters who were speaking in the scene; the location (in the story) that the scene took place; camera angle (close up, medium, long, top, tracking, over the shoulder, etc.); whether music was playing in the scene or not; and a transcription of any on-screen text.  We concatenated the text for all of these features within each segment, creating a ``bag of words'' describing each scene.  We then re-organized the text descriptions into overlapping sliding windows spanning 50 scenes each. In other words, the first text sample comprised the combined text from the first 50 scenes (i.e., 1--50), the second comprised the text from scenes 2--51, and so on.  We trained our model using these overlapping text samples with \texttt{scikit-learn}~\citep[version 0.19.1; ][]{PedrEtal11}, called from our high-dimensional visualization and text analysis software, \texttt{HyperTools}~\citep{HeusEtal18a}.  Specifically, we use the \texttt{CountVectorizer} class to transform the text from each scene into a vector of word counts (using the union of all words across all scenes as the ``vocabulary,'' excluding English stop words); this yields a number-of-scenes by number-of-words \textit{word count} matrix.  We then use the \texttt{LatentDirichletAllocation} class (topics=100, method=`batch') to fit a topic model~\citep{BleiEtal03} to the word count matrix, yielding a number-of-scenes (1000) by number-of-topics (100) \textit{topic proportions} matrix.  The topic proportions matrix describes which mix of topics (latent themes) is present in each scene.  Next, we transformed the topic proportions matrix to match the 1976 fMRI volume acquisition times.  For each fMRI volume, we took the topic proportions from whatever scene was displayed for most of that volume's 1500~ms acquisition time.  This yielded a new number-of-TRs (1976) by number-of-topics (100) topic proportions matrix.

We created similar topic proportions matrices using hand-annotated transcripts of each participant's recall of the video~\citep[annotated by ][]{ChenEtal17}.  We tokenized the transcript into a list of sentences, and then re-organized the list into overlapping sliding windows spanning 10 sentences each; in turn we transformed each window's sentences into a word count vector (using the same vocabulary as for the video model).  We then used the topic model already trained on the video scenes to compute the most probable topic proportions for each sliding window.  This yielded a number-of-sentences (range: 68--294) by number-of-topics (100) topic proportions matrix, for each participant.  These reflected the dynamic content of each participant's recalls.  Note: for details on how we selected the video and recall window lengths and number of topics, see \textit{Supporting Information} and Figure~\topicopt.

\subsubsection*{Parsing topic trajectories into events using Hidden Markov Models}
We parsed the topic trajectories of the video and participants' recalls into events using Hidden Markov Models~\citep{Rabi89}.  Given the topic proportions matrix (describing the mix of topics at each timepoint) and a number of states, $K$, an HMM recovers the set of state transitions that segments the timeseries into $K$ discrete states.  Following \cite{BaldEtal17}, we imposed an additional set of constraints on the discovered state transitions that ensured that each state was encountered exactly once (i.e., never repeated).  We used the BrainIAK toolbox~\citep{Brainiak} to implement this segmentation.

We used an optimization procedure to select the appropriate $K$ for each topic proportions matrix.  Specifically, we computed (for each matrix)
\[
  \argmax_K \left[\frac{a}{b} - \frac{K}{\alpha}\right],
\]
where $a$ was the average correlation between the topic vectors of timepoints within the same state; $b$ was the average correlation between the topic vectors of timepoints within \textit{different} states; and $\alpha$ was a regularization parameter that we set to 5 times the window length (i.e., 250 scenes for the video topic trajectory and 50 sentences for the recall topic trajectories).  Figure~\ref{fig:model}B displays the event boundaries returned for the video, and Figure~\corrmats~displays the event boundaries returned for each participant's recalls.  After obtaining these event boundaries, we created stable estimates of each topic proportions matrix by averaging the topic vectors within each event.  This yielded a number-of-events by number-of-topics matrix for the video and recalls from each participant.

\subsubsection*{Visualizing the video and recall topic trajectories}
We used the UMAP algorithm~\citep{McInHeal18} to project the 100-dimensional topic space onto a two-dimensional space for visualization (Figs.~\ref{fig:trajectory}, \ref{fig:topics}).  To ensure that all of the trajectories were projected onto the \textit{same} lower dimensional space, we computed the low-dimensional embedding on a ``stacked'' matrix created by vertically concatenating the events-by-topics topic proportions matrices for the video and all 17 participants' recalls.  We then divided the rows of the result (a total-number-of-events by two matrix) back into separate matrices for the video topic trajectory and the trajectories for each participant's recalls (Fig.~\ref{fig:trajectory}).  This general approach for discovering a shared low-dimensional embedding for a collections of high-dimensional observations follows \cite{HeusEtal18a}.

\subsubsection*{Estimating the consistency of flow through topic space across participants}
In Figure~\ref{fig:trajectory}B, we present an analysis aimed at characterizing locations in topic space that different participants move through in a consistent way (via their recall topic trajectories).  The two-dimensional topic space used in our visualizations (Fig.~\ref{fig:trajectory}) ranged from -5 to 5 (arbitrary) units in the $x$ dimension and from -6.5 to 2 units in the $y$ dimension.  We divided this space into a grid of vertices spaced 0.25~units apart.  For each vertex, we examined the set of line segments formed by connecting each pair successively recalled events, across all participants, that passed within 0.5 units.  We computed the distribution of angles formed by those segments and the $x$-axis, and used a Rayleigh test to determine whether the distribution of angles was reliably ``peaked'' (i.e., consistent across all transitions that passed through that local portion of topic space).  To create Figure~\ref{fig:trajectory}B we drew an arrow originating from each grid vertex, pointing in the direction of the average angle formed by line segments that passed within 0.5 units.  We set the arrow lengths to be inversely proportional to the $p$-values of the Rayleigh tests at each vertex.  Specifically, for each vertex we converted all of the angles of segments that passed within 0.5 units to unit vectors, and we set the arrow lengths at each vertex proportional to the length of the (circular) mean vector.  We also indicated any significant results ($p < 0.05$, corrected using the Benjamani-Hochberg procedure) by coloring the arrows in blue (darker blue denotes a lower $p$-value, i.e., a longer mean vector); all tests with $p \geq 0.05$ are displayed in gray and given a lower opacity value.

\subsection*{Searchlight fMRI analyses}
In Figure~\ref{fig:brainz}, we present two analyses aimed at identifying brain structures whose responses (as participants viewed the video) exhibited particular temporal correlations.  We developed a searchlight analysis whereby we constructed a cube centered on each voxel (radius: 5~voxels).  For each of these cubes, we computed the temporal correlation matrix of the voxel responses during video viewing.  Specifically, for each of the 1976 volumes collected during video viewing, we correlated the activity patterns in the given cube with the activity patterns (in the same cube) collected during every other timepoint.  This yielded a 1976 by 1976 correlation matrix for each cube.

Next, we constructed two sets of ``template'' matrices: one reflected the video's topic trajectory and the other reflected each participant's recall topic trajectory.  To construct the video template, we computed the correlations between the topic proportions estimated for every pair of TRs (prior to segmenting the trajectory into discrete events; i.e., the correlation matrix shown in Figs.~\ref{fig:model}B and \ref{fig:brainz}A).  We constructed similar temporal correlation matrices for each participant's recall topic trajectory (Figs.~\ref{fig:model}D, \corrmats).  However, to correct for length differences and potential non-linear transformations between viewing time and recall time, we first used dynamic time warping~\citep{BernClif94} to temporally align participants' recall topic trajectories with the video topic trajectory (an example correlation matrix before and after warping is shown in Fig.~\ref{fig:brainz}B).  This yielded a 1976 by 1976 correlation matrix for the video template and for each participant's recall template.

To determine which (cubes of) voxel responses reliably matched the video template, we correlated the upper triangle of the voxel correlation matrix for each cube with the upper triangle of the video template matrix~\citep{KrieEtal08b}.  This yielded, for each participant, a single correlation value.  We computed the average (Fisher $z$-transformed) correlation coefficient across participants.  We used a permutation-based procedure to assess significance, whereby we re-computed the average correlations for each of 100 ``null'' video templates (constructed by circularly shifting the template by a random number of timepoints).  (For each permutation, the same shift was used for all participants.)  We then estimated a $p$-value by computing the proportion of shifted correlations that were larger than the observed (unshifted) correlation.  To create the map in Figure~\ref{fig:brainz}A we thresholded out any voxels whose correlation values fell below the 95\textsuperscript{th} percentile of the permutation-derived null distribution.

We used a similar procedure to identify which voxels' responses reflected the recall templates.  For each participant, we correlated the upper triangle of the correlation matrix for each cube of voxels with their (time warped) recall correlation matrix.  As in the video template analysis this yielded a single correlation coefficient for each participant.  However, whereas the video analysis compared every participant's responses to the same template, here the recall templates were unique for each participant.  We computed the average $z$-transformed correlation coefficient across participants, and used the same permutation procedure we developed for the video responses to assess significant correlations.  To create the map in Figure~\ref{fig:brainz}B we thresholded out any voxels whose correlation values fell below the 95\textsuperscript{th} percentile of the permutation-derived null distribution.

\bibliography{memlab}

\section*{Supporting information}
Supporting information is available in the online version of the paper.

\section*{Acknowledgements}
We thank Luke Chang, Janice Chen, Chris Honey, Lucy Owen, Emily Whitaker, and Kirsten Ziman for feedback and scientific discussions. We also thank Janice Chen, Yuan Chang Leong, Kenneth Norman, and Uri Hasson for sharing the data used in our study.  Our work was supported in part by NSF EPSCoR Award Number 1632738. The content is solely the responsibility of the authors and does not necessarily represent the official views of our supporting organizations.

\section*{Author contributions}
Conceptualization: A.C.H. and J.R.M.; Methodology: A.C.H. and J.R.M.; Software: A.C.H., P.C.F. and J.R.M.; Analysis: A.C.H., P.C.F. and J.R.M.; Writing, Reviewing, and Editing: A.C.H., P.C.F. and J.R.M.; Supervision: J.R.M.

\section*{Author information}
The authors declare no competing financial interests.  Correspondence and requests for materials should be addressed to J.R.M. (jeremy.r.manning@dartmouth.edu).

\end{document}

### 2020-08-18 paper/supporting_information.tex
re-added sentence about improvements to topic modeling
updated title, fig S2

@@
 
-\title{\textit{Supporting Information for}: Memory for television episodes preserves event content while introducing new across-event similarities}
+\title{\textit{Supporting Information for}: Geometric models reveal behavioral and neural signatures of how naturalistic experiences are transformed into episodic memories}
 \author{Andrew C.
@@
 The optimal parameters were $\omega = 50$, $\rho = 10$, and $K = 100$.
+In subsequent refinements of our topic modeling approach, we made various improvements to how we parse the video and recall text and construct the trajectories' timeseries, but maintained these optimized parameters throughout.
 

### 2020-08-18 paper/main.tex
edits through p 13

@@
 Fitzpatrick\textsuperscript{1, \textdagger}, and Jeremy R.
-Manning\textsuperscript{1, *}\\\textsuperscript{1}Department of Psychological and Brain Sciences\\Dartmouth College, Hanover, NH 03755, USA\\\textsuperscript{2}Akili Interactive\\Boston, MA 02110\\\textsuperscript{\textdagger}Denotes equal contribution\\\textsuperscript{*}Corresponding author: jeremy.r.manning@dartmouth.edu}
+Manning\textsuperscript{1, *}\\\textsuperscript{1}Department of Psychological and Brain Sciences\\Dartmouth College, Hanover, NH 03755, USA\\\textsuperscript{2}Akili Interactive\\Boston, MA 02110\\\textsuperscript{\textdagger}Denotes equal contribution\\\textsuperscript{*}Corresponding author: Jeremy.R.Manning@dartmouth.edu}
 
@@
 \begin{abstract}
-The ways our experiences unfold over time may be characterized by unique \textit{trajectories} through geometric representational spaces.
-In word embedding spaces, for example, each coordinate reflects a concept and nearby coordinates (in Euclidean distance) reflect semantically related concepts.
+The ways in which our experiences unfold over time are, by nature, incalculably complex.
+One effective approach to making sense of this complexity is to characterize experiencess as unique \textit{trajectories} through a certain geometric representational space.
+In word embedding spaces, for example, each dimension reflects a concept, such that a given coordinate reflects a weighted mixture of those concepts.
 We propose a framework for projecting naturalistic experiences into word embedding spaces, such that the conceptual content of each moment of an experience, and how different moments of the experience relate, are reflected by the \textit{shape} of the experience's trajectory.
@@
 This translates qualitative questions about how we remember naturalistic experiences into quantitative geometric comparisons.
-We applied our framework to data collected as participants watched, and later verbally recounted, a television episode while undergoing functional neuroimaging.
-We found that all participants' remembered trajectories reflected the high-level \textit{essence} (i.e., large-scale narrative features) of the episode's trajectory, but participants differred markedly in their memories for low-level details (i.e, small-scale details of the trajectory).
+We applied our framework to data collected as participants watched and verbally recounted a television episode while undergoing functional neuroimaging.
+We found that the trajectory of each participant's recall reflected the high-level \textit{essence} (i.e., large-scale narrative summaries) of the episode's trajectory, but participants differed markedly in their memories for low-level features (i.e, small-scale details).
 We also identified a network of brain structures that were sensitive to the shape of the episode's trajectory through word embedding space, and an overlapping network that predicted, at the time of encoding, how people would distort (transform) the episode's trajectory when they recounted the episode later.
-Our work provides insights into how our brains transform our ongoing experiences when we encode them into episodic memories, and provides a formal geometric framework for characterizing the complex dynamic content of naturalistic experiences.
+Our work provides insights into how our brains transform ongoing experiences when we encode them into episodic memories, and provides a formal geometric framework for characterizing the complex dynamic content of naturalistic experiences.
 \end{abstract}
@@
 What does it mean to \textit{remember} something?
-In traditional episodic memory experiments \citep[e.g., list-learning or trial-based experiments;][]{Murd62a, Kaha96}, remembering is often cast as a discrete and binary operation: each studied item may be separated from the rest of one's experiences and labeled as having been recalled or forgotten.
+In traditional episodic memory experiments \citep[e.g., list-learning or trial-based experiments;][]{Murd62a, Kaha96}, remembering is often cast as a discrete and binary operation: each studied item may be separated from the rest of one's experience and singularly labeled as having been recalled or forgotten.
 More nuanced studies might incorporate self-reported confidence measures as a proxy for memory strength, or ask participants to discriminate between ``recollecting'' the (contextual) details of an experience or having a general feeling of ``familiarity'' \citep{Yone02}.
-Using well-controlled, trial-based experimental designs, the field has amassed a wealth of valuable information regarding human episodic memory.
-However, there are fundamental properties of the external world and our memories that trial-based experiments are not well suited to capture~\citep[for review also see][]{KoriGold94, HukEtal18}.
+Using well controlled, trial-based experimental designs, the field has amassed a wealth of valuable information regarding human episodic memory.
+However, there are fundamental properties of the external world and our memories that trial-based experiments are not well suited to capture~\citep[for review, also see][]{KoriGold94, HukEtal18}.
 First, our experiences and memories are continuous, rather than discrete---isolating a (naturalistic) event from the context in which it occurs can substantially change its meaning.
-Second, the specific language used to describe an experience has little bearing on whether the experience should be considered to have been ``remembered.''  Asking whether the rememberer has precisely reproduced a specific set of words to describe a given experience is nearly orthogonal to whether they were actually able to remember it.
-In classic (e.g., list-learning) memory studies, by contrast, the number or proportion of precise recalls is often a primary metric for assessing the quality of participants' memories.
+Second, the specific language used to describe an experience has little bearing on whether the experience should be considered to have been ``remembered.''  Asking whether the rememberer has precisely reproduced a specific set of words to describe a given experience is nearly orthogonal to whether or not they were actually able to remember it.
+In classic (e.g., list-learning) memory studies, by contrast, the number or proportion of exact recalls is often a primary metric for assessing the quality of participants' memories.
 Third, one might remember the \textit{essence} (or a general summary) of an experience but forget (or neglect to recount) particular details.
@@
 
-How might one go about formally characterizing the \textit{essence} of an experience, or whether it has been recovered by the rememberer?
+How might one go about formally characterizing the \textit{essence} of an experience, and whether it has been recovered by the rememberer?
 Any given moment of an experience derives meaning from surrounding moments, as well as from longer-range temporal associations~\citep{LernEtal11, Mann19, Mann20}.
@@
 Prior research suggests that these sharp transitions (termed \textit{event boundaries}) help to discretize our experiences (and their mental representations) into \textit{events}~\citep{RadvZack17, BrunEtal18, HeusEtal18b, ClewDava17, EzzyDava11, DuBrDava13}.
-The interplay between the stable (within-event) and transient (across-event) temporal dynamics of an experience also provides a potential framework for transforming experiences into memories that distill those experiences down to their essence.
+The interplay between the stable (within-event) and transient (across-event) temporal dynamics of an experience also provides a potential framework for transforming experiences into memories that distills those experiences down to their essence.
 For example, prior work has shown that event boundaries can influence how we learn sequences of items~\citep{HeusEtal18b, DuBrDava13}, navigate~\citep{BrunEtal18}, and remember and understand narratives~\citep{ZwaaRadv98, EzzyDava11}.
@@
 
-Here we sought to examine how the temporal dynamics of a ``naturalistic'' experience were later reflected in participants' memories.
+Here, we sought to examine how the temporal dynamics of a ``naturalistic'' experience were later reflected in participants' memories.
 We analyzed an open dataset that comprised behavioral and functional Magnetic Resonance Imaging (fMRI) data collected as participants viewed and then verbally recounted an episode of the BBC television series \textit{Sherlock}~\citep{ChenEtal17}.
 We developed a computational framework for characterizing the temporal dynamics of the moment-by-moment content of the episode, and of participants' verbal recalls.
-Specifically, we use topic modeling~\citep{BleiEtal03} to characterize the thematic conceptual (semantic) content present in each moment of the episode and recalls, and Hidden Markov Models~\citep{Rabi89, BaldEtal17} to discretize this evolving semantic content into events.
-In this way, we cast naturalistic experiences (and recalls of those experiences) as geometric \textit{trajectories} that describe how the experiences evolve over time.
+Specifically, we use topic modeling~\citep{BleiEtal03} to characterize the thematic conceptual (semantic) content present in each moment of the episode and recalls, and hidden Markov models~\citep{Rabi89, BaldEtal17} to discretize this evolving semantic content into events.
+In this way, we cast naturalistic experiences (and memories of those experiences) as geometric \textit{trajectories} that describe how the experiences evolve over time.
 Under this framework, successful remembering entails verbally ``traversing'' the content trajectory of the episode, thereby reproducing the shape (or essence) of the original experience.
-Comparing the shapes of the topic trajectories of the episode and of participants' retellings of the episode then reveals which aspects of the episode were preserved (or lost) in the translation into memory.
-We further introduce two novel metrics for assessing memory quality: (1) the \textit{precision} with which a participant recounts each event and (2) the \textit{distinctiveness} of each recall event (relative to other recalled events).
+Comparing the shapes of the topic trajectories of the episode and of participants' retellings of the episode then reveals which aspects of the episode were preserved (or discarded) in the translation into memory.
+We further introduce two novel metrics for assessing memory quality: \textbf{1}) the \textit{precision} with which a participant recounts each event, and \textbf{2}) the \textit{distinctiveness} of each recall event (relative to other recalled events).
 We examine how these metrics relate to overall memory performance, and discuss the ways in which they improve upon classic ``proportion-recalled'' measures for analyzing naturalistic memory.
-Last, we utilize our framework to identify networks of brain structures whose responses (as participants watched the episode) reflected the temporal dynamics of the episode, and how participants recount it.
+Last, we utilize our framework to identify networks of brain structures whose responses (as participants watched the episode) reflected the temporal dynamics of either the episode or how participants would later recount it.
 
 \section*{Results}
-To characterize the dynamic content of the \textit{Sherlock} episode and participants' subsequent recountings, we used a topic model~\citep{BleiEtal03} to discover the latent themes.
+To characterize the dynamic content of the \textit{Sherlock} episode and participants' subsequent recountings, we used a topic model~\citep{BleiEtal03} to discover the episode's latent themes.
 Topic models take as inputs a vocabulary of words to consider and a collection of text documents, and return two output matrices.
 The first of these is a \textit{topics matrix} whose rows are \textit{topics} (latent themes) and whose columns correspond to words in the vocabulary.
-The entries of the topics matrix define how each word in the vocabulary is weighted by each discovered topic.
+The entries of the topics matrix reflect how each word in the vocabulary is weighted by each discovered topic.
 For example, a detective-themed topic might weight heavily on words like ``crime,'' and ``search.''  The second output is a \textit{topic proportions matrix}, with one row per document and one column per topic.
@@
 
-\cite{ChenEtal17} collected hand-annotated information about each of 1000 (manually identified) time segments spanning the roughly 50 minute video used in their experiment.
+\cite{ChenEtal17} collected hand-annotated information about each of 1000 (manually identified) scenes spanning the roughly 50 minute video used in their experiment.
 This information included: a brief narrative description of what was happening, the location where the scene took place, the names of any characters on the screen, and other similar details (for a full list of annotated features, see \textit{Methods}).
@@
 Several of the identified topics were highly similar, which we hypothesized might allow us to distinguish between subtle narrative differences if the distinctions between those overlapping topics were meaningful.
-The topic vectors for each timepoint were \textit{sparse}, in that only a small number (usually one or two) of topics tended to be ``active" in any given timepoint (Fig.~\ref{fig:model}A).
+The topic vectors for each timepoint were also \textit{sparse}, in that only a small number (usually one or two) of topics tended to be ``active" in any given timepoint (Fig.~\ref{fig:model}A).
 Further, the dynamics of the topic activations appeared to exhibit \textit{persistence} (i.e., given that a topic was active in one timepoint, it was likely to be active in the following timepoint) along with \textit{occasional rapid changes} (i.e., occasionally topics would appear to spring into or out of existence).
 These two properties of the topic dynamics may be seen in the block diagonal structure of the timepoint-by-timepoint correlation matrix (Fig.~\ref{fig:model}B) and reflect the gradual drift and sudden shifts fundamental to the temporal dynamics of real-world experiences.
-Given this observation, we adapted an approach devised by \cite{BaldEtal17}, and used a Hidden Markov Model (HMM) to identify the \textit{event boundaries} where the topic activations changed rapidly (i.e., at the boundaries of the blocks in the correlation matrix; event boundaries identified by the HMM are outlined in yellow in Fig.~\ref{fig:model}B).
+Given this observation, we adapted an approach devised by \cite{BaldEtal17}, and used a hidden Markov model (HMM) to identify the \textit{event boundaries} where the topic activations changed rapidly (i.e., the boundaries of the blocks in the temporal correlation matrix; event boundaries identified by the HMM are outlined in yellow in Fig.~\ref{fig:model}B).
 Part of our model fitting procedure required selecting an appropriate number of ``events" into which the topic trajectory should be segmented.
-To accomplish this, we used an optimization procedure that maximized the difference between the topic weights for timepoints within an event versus across multiple events (see \textit{Methods} for additional details).
+To accomplish this, we used an optimization procedure that maximized the difference between the topic weights for timepoints within an event versus timepoints across multiple events (see \textit{Methods} for additional details).
 We then created a stable ``summary'' of the content within each video event by averaging the topic vectors across the timepoints spanned by each event (Fig.~\ref{fig:model}C).
@@
 We applied the same topic model (already trained on the video annotations) to each participant's recalls.
-Analogous to how we parsed the time-varying content of the video, to obtain similar estimates for each participant's recall, we treated each overlapping  ``window" of (up to 10) sentences from their transcript as a ``document," and computed the most probable mix of topics reflected in each timepoint's sentences.
+Analogously to how we parsed the time-varying content of the video, to obtain similar estimates for each participant's recall, we treated each overlapping  window of (up to 10) sentences from their transcript as a ``document," and computed the most probable mix of topics reflected in each timepoint's sentences.
 This yielded, for each participant, a number-of-windows by number-of-topics topic proportions matrix that characterized how the topics identified in the original video were reflected in the participant's recalls.
@@
 While some participants' recall topic proportions segmented into just a few events (e.g., Participants P4, P5, and P7), others' segmented into many shorter duration events (e.g., Participants P12, P13, and P17).
-This suggests that different participants may be recalling the video with different levels of detail-- e.g., some might touch on just the major plot points, whereas others might attempt to recall every minor scene or action.
-The second clear pattern present in every individual participant's recall correlation matrix is that, unlike in the video correlation matrix, there are substantial off-diagonal correlations.
-Whereas each event in the original video was (largely) separable from the others (Fig.~\ref{fig:model}B), in transforming those separable events into memory, participants appear to be integrating across multiple events, blending elements of previously recalled and not-yet-recalled content into each newly recalled event~\citep[Figs.~\ref{fig:model}E, \corrmats; also see][]{MannEtal11, HowaEtal12, Mann19}.
+This suggests that different participants may be recalling the video with different levels of detail---i.e., some might touch on just the major plot points, whereas others might attempt to recall every minor scene or action.
+The second clear pattern present in every individual participant's recall correlation matrix was that, unlike in the video correlation matrix, there were substantial off-diagonal correlations.
+Whereas each event in the original video was (largely) separable from the others (Fig.~\ref{fig:model}B), in transforming those separable events into memory, participants appeared to be integrating across multiple events, blending elements of previously recalled and not-yet-recalled content into each newly recalled event~\citep[Figs.~\ref{fig:model}E, \corrmats; also see][]{MannEtal11, HowaEtal12, Mann19}.
 
@@
 Analogous to classic list-learning studies, we can then examine participants' recall sequences by asking which events they tended to recall first~\citep[probability of first recall; Fig.~\ref{fig:list-learning}A;][]{AtkiShif68, PostPhil65, WelcBurn24}; how participants most often transition between recalls of the events as a function of the temporal distance between them~\citep[lag-conditional response probability; Fig.~\ref{fig:list-learning}B;][]{Kaha96}; and which events they were likely to remember overall~\citep[serial position recall analyses; Fig.~\ref{fig:list-learning}C;][]{Murd62a}.
-Interestingly, for two of these analyses (probability of first recall and lag-conditional response probability curves) we observe patterns comparable to classic effects from the list-learning literature: namely, a higher probability of initiating recall with the first event in the sequence (Fig.~\ref{fig:list-learning}A) and a higher probability of transitioning to neighboring events with an asymmetric forward bias (Fig.~\ref{fig:list-learning}B).
-In contrast, we do not observe a pattern comparable to the serial position effect (Fig.~\ref{fig:list-learning}C), but rather we see higher memory for specific events distributed approximately evenly throughout the video.
+Interestingly, for two of these analyses (probability of first recall and lag-conditional response probability curves) we observed patterns comparable to classic effects from list-learning literature: namely, a higher probability of initiating recall with the first event in the sequence (Fig.~\ref{fig:list-learning}A) and a higher probability of transitioning to neighboring events with an asymmetric forward bias (Fig.~\ref{fig:list-learning}B).
+In contrast, we did not observe a pattern comparable to the serial position effect (Fig.~\ref{fig:list-learning}C), but rather greater memory for specific events distributed approximately evenly throughout the video.
 
-We can also apply two list-learning-native analyses that describe how participants group items in their recall sequences: temporal clustering and semantic clustering \citep[][see \textit{Methods} for details]{PolyEtal09}.
-Temporal clustering refers to the extent to which participants group their recall responses according to encoding position.
+We can also apply two list-learning-native analyses that describe how participants group items in their recall sequences: temporal clustering and semantic clustering \citep[][see \textit{Methods} for details]{PolyEtal09}.~Temporal clustering refers to the extent to which participants group their recall responses according to encoding position.
 Overall, we found that sequentially viewed video events were clustered heavily in participants' recall event sequences (mean clustering score: 0.767, SEM: 0.029), and that participants with higher temporal clustering scores tended to perform better according to both \cite{ChenEtal17}'s hand-annotated memory scores (Pearson's $r(15) = 0.62,~p = 0.008$) and our model's estimate (Pearson's $r(15) = 0.54,~p = 0.024$).
@@
 
-Statistical models of memory studies often treat recall success as binary (i.e., an item either was or was not recalled), or occasionally categorical \citep[e.g., to distinguish familiarity from recollection;][]{YoneEtal02}.
+Statistical models of memory studies often treat recall success as binary (in other words, an item either was or was not recalled), or occasionally categorical \citep[e.g., to distinguish familiarity from recollection;][]{YoneEtal02}.
 Such approaches are tenable in classical list-learning or recognition memory paradigms, as the presented stimuli tend to be very simple (e.g., a sequence of individual words or items).
 However, memory for naturalistic experiences is much more nuanced.
-For example, certain aspects of an experience might be correctly remembered at varying levels of detail, distorted, or forgotten.
+For example, certain aspects of an experience might be correctly remembered at varying levels of detail, or distorted, or forgotten entirely.
 Further, each remembering is itself a richly structured phenomenon.
@@
 A second novel metric we introduce here is \textit{distinctiveness}, which is intended to capture the ``specificity'' of recall.
-In other words, distinctiveness quantifies how much the transcript of a given recalled event references that event in particular, as opposed to other video events.
-To compute a recall event's distinctiveness, we first identify the video event that it's topic vector is most strongly correlated with.
-We then define distinctiveness as 1 minus the average correlation between the given recall event and all \textit{other} video events.
-In addition to individual events, one may also use these metrics to describe each participant's overall performance (i.e., by averaging across a participant's event-wise precision or distinctiveness scores).
+In other words, distinctiveness quantifies the extent to which a given recalled event reflects the most similar presented event moreso than it does other presented events.
+To compute a recall event's distinctiveness, we first identify the video event to which its topic vector is most strongly correlated.
+We then define distinctiveness as one minus the average correlation between the given recall event and all \textit{other} video events.
+In addition to individual events, one may also use these metrics to describe each participant's overall performance by averaging across a participant's event-wise precision or distinctiveness scores.
 Participants whose recall events are more veridical descriptions of what happened in the video event will presumably have higher precision scores.
-We find that, across participants, higher precision scores are positively correlated with both hand-annotated memory performance (Pearson's $r(15) = 0.60, p = 0.010$) and the number of video events successfully remembered, as determined by our model (Pearson's $r(15) = 0.90, p < 0.001$).
+We find that, across participants, higher precision scores are positively correlated with both hand-annotated memory performance (as collected by Chen et al., 2017; Pearson's $r(15) = 0.60, p = 0.010$) and the number of video events successfully remembered, as determined by our model (Pearson's $r(15) = 0.90, p < 0.001$).
 We also hypothesized that participants who recounted events in a more distinctive way would display better overall memory.

### 2020-08-18 paper/main.tex
minor abstract updates

@@
 The ways in which our experiences unfold over time are, by nature, incalculably complex.
-One effective approach to making sense of this complexity is to characterize experiencess as unique \textit{trajectories} through a certain geometric representational space.
-In word embedding spaces, for example, each dimension reflects a concept, such that a given coordinate reflects a weighted mixture of those concepts.
-We propose a framework for projecting naturalistic experiences into word embedding spaces, such that the conceptual content of each moment of an experience, and how different moments of the experience relate, are reflected by the \textit{shape} of the experience's trajectory.
+One popular approach to making sense of this complexity entails characterizing experiences as unique \textit{trajectories} through a particular geometric representational space whose dimensions are features of our experiences.
+In word embedding spaces, for example, each dimension reflects a concept.
+And by extension, any given coordinate reflects a weighted mixture of those concepts.
+We propose a framework for projecting naturalistic experiences into word embedding spaces, such that the conceptual content of each moment of an experience, and how different moments of the experience relate, are captured by the \textit{shape} of the experience's trajectory.
 By projecting memories of those experiences into the same spaces, one may then geometrically compare the shape of the original experience's trajectory to the shape of how it is remembered later.
@@
 For each recall transition (following the first recall), we computed the lag between the current recall event and the next recall event, normalizing by the total number of possible transitions.
-This yielded a number-of-participants (17) by number-of-lags (-29 to +29; 61 lags total) matrix.
+This yielded a number-of-participants (17) by number-of-lags (-29 to +29; 59 lags total) matrix.
 We averaged over the rows of this matrix to obtain a group-averaged lag-CRP curve (Fig.~\ref{fig:list-learning}B).

### 2020-08-19 paper/main.tex
JRM inputted handwritten edits

--- 2020-08-18 paper/main.tex
@@
 \begin{abstract}
-The ways in which our experiences unfold over time are, by nature, incalculably complex.
-One effective approach to making sense of this complexity is to characterize experiencess as unique \textit{trajectories} through a certain geometric representational space.
-In word embedding spaces, for example, each dimension reflects a concept, such that a given coordinate reflects a weighted mixture of those concepts.
-We propose a framework for projecting naturalistic experiences into word embedding spaces, such that the conceptual content of each moment of an experience, and how different moments of the experience relate, are reflected by the \textit{shape} of the experience's trajectory.
-By projecting memories of those experiences into the same spaces, one may then geometrically compare the shape of the original experience's trajectory to the shape of how it is remembered later.
+Our moment-by-moment subject experience reflects external sensory information from each moment, along with additional information from our past that we carry with us into that moment.
+The blend of memories, knowledge, emotions, goals, and other internal perceptual and mental states that color our subjective experience provides a \textit{context} for interpreting new information and conceptually linking what is happening now with our prior experiences.
+Because this contextual information is often person-specific, the subjective experience that each person encodes into their memory is often idiosyncratic, even for shared experiences and sensory perspectives.
+We sought to study which aspects of a shared naturalistic experience were preserved or distorted, and how those distortions compared across individuals.
+To this end, we developed a geometric framework for mathematically characterizing the subjective conceptual content of dynamic naturalistic experiences.
+We model experiences as \textit{trajectories} through word embedding spaces whose coordinates reflect the universe of thoughts under consideration.
+We also demonstrate how \textit{memories} may also be modeled as trajectories through the same spaces.
 According to this view, encoding an experience into memory entails geometrically distorting or transforming the original experience's trajectory.
-This translates qualitative questions about how we remember naturalistic experiences into quantitative geometric comparisons.
+This translates qualitative neuropsychological questions about how we remember naturalistic experiences into quantitive geometric questions about the spatial configurations of trajectory shapes.
 We applied our framework to data collected as participants watched and verbally recounted a television episode while undergoing functional neuroimaging.
-We found that the trajectory of each participant's recall reflected the high-level \textit{essence} (i.e., large-scale narrative summaries) of the episode's trajectory, but participants differed markedly in their memories for low-level features (i.e, small-scale details).
+We found that the trajectories of participants' recountings of the episode nearly all captured the coarse spatial properties of the original episode's trajectory (i.e., the essential plot points), but participants differed in their memory for fine details.
 We also identified a network of brain structures that were sensitive to the shape of the episode's trajectory through word embedding space, and an overlapping network that predicted, at the time of encoding, how people would distort (transform) the episode's trajectory when they recounted the episode later.
-Our work provides insights into how our brains transform ongoing experiences when we encode them into episodic memories, and provides a formal geometric framework for characterizing the complex dynamic content of naturalistic experiences.
+Our work provides insights into how our brains distort and transform our ongoing experiences when we encode them into episodic memories.
 \end{abstract}
@@
 We also hypothesized that participants who recounted events in a more distinctive way would display better overall memory.
-We find that participants' distinctiveness scores were
+We find that participants' distinctiveness scores were positively
 correlated with our model's estimated number of recall events (Pearson's $r(15) = 0.55, p = 0.021$).
@@
 We elaborate on this potential discrepency in the \textit{Discussion} section.
-
-%% JRM STOPPED HERE
 
@@
 We then colored all words describing actions and features coded in panel B by their corresponding color.
-Visual comparison of the transcripts reveals that the most precise participant's recall both captures more of the video event's content, and does so with far more detail.
+Visual comparison of these example transcripts reveals that the more precise recall captures more of the video event's content, and with more detail.
 
@@
 The majority of the most distinctive recall event text describes video event 19's content, with the first five and last one sentence describing the video events immediately preceding and succeeding the current one, respectively.
-In contrast, the least precise participant's recall for video event 19 blends the content from five separate video events, does not transition between them in order, and often combines descriptions of two video events' content in the same sentence.
+In contrast, the least distinctive recall of video event 19 blends the content from five separate video events, does not transition between them in order, and often combines descriptions of two video events' content in the same sentence.
 
@@
 Given this, we next asked asked whether the events were generally remembered well or poorly tended to reflect particular content.
-Because our analysis framework projects the dynamic video content and participants' recalls into a shared space, and because the dimensions of that space represent topics (which are, in turn, sets of weights over words in the vocabulary), we are able to recover the weighted combination of words that make up any point (i.e., topic vector) in this space.
+Because our analysis framework projects the dynamic video content and participants' recalls into a shared space, and because the dimensions of that space represent topics (which are, in turn, sets of weights over known words in the vocabulary), we are able to recover the weighted combination of words that make up any point (i.e., topic vector) in this space.
 We first computed the average precision with which participants recalled each of the 30 video events (Fig.~\ref{fig:topics}A; note that this result is analogous to a serial position curve created from our continuous recall quality metric).
@@
 To visualize the result, we created a ``wordle'' image~\citep{MuelEtal18} where words weighted more heavily by better-remembered topics appear in a larger font (Fig.~\ref{fig:topics}B, green box).
-Across the full video, content that reflected topics necessary to convey the central focus of the video (e.g., the names of the two main characters, ``Sherlock" and ``John", and the address of a major recurring location, ``221B Baker Street") were best remembered.
+Across the full video, content that reflected topics necessary to convey the central focus of the video (e.g., the names of the two main characters, ``Sherlock'' and ``John,'' and the address of a major recurring location, ``221B Baker Street") were best remembered.
 An analogous analysis revealed which themes were poorly remembered.
@@
 Here, for each of the three best- and worst-remembered video events, we have constructed two wordles: one from the original video event's topic vector (left) and a second from the average recall topic vector for that event (right).
-The three best-remembered events (circled in green) correspond to scenes important to the central plot-line: a mysterious figure spying on John in a phone booth; John meeting Sherlock at Baker St.
+The three best-remembered events (circled in green) correspond to scenes integral to the central plot-line: a mysterious figure spying on John in a phone booth; John meeting Sherlock at Baker St.
 to discuss the murders; and Sherlock laying a trap to catch the killer.
-Meanwhile, the three worst-remembered events (circled in red) reflect scenes that are non-essential to summarizing the narrative's structure: the video of singing cartoon characters participants viewed prior to the main episode; John asking Molly about Sherlock's habit of over-analyzing people; and Sherlock noticing evidence of Anderson's and Donovan's affair.
+Meanwhile, the three worst-remembered events (circled in red) reflect scenes that are non-essential to summarizing the narrative's structure: the video of singing cartoon characters participants viewed in an introductory clip prior to the main episode; John asking Molly about Sherlock's habit of over-analyzing people; and Sherlock noticing evidence of Anderson's and Donovan's affair.
 
@@
 
-While a large number of language models exist \citep[e.g., WAS, LSA, word2vec, universal sentence encoder;][]{SteyEtal04, LandEtal98, MikoEtal13, CerEtal18}, here we use latent dirichlet allocation (LDA)-based topic models for a few reasons.
+Word embedding models are a rapidly growing area of machine learning research.  Early approaches including latent
+  semantic analysis~\citep{LandDuma97} use word co-occurrence statistics (i.e., how often pairs of words occur in the same documents contained in the corpus) to derive a unique feature vector for each word.
+The feature vectors are constructed so that words that co-occur more frequently have feature vectors that are closer (in Euclidean distance).
+Related approaches, such as latent dirichlet
+  allocation~\citep{BleiEtal03} attempt to explicitly model the underlying causes of word co-occurrences by automatically identifying the set of themes or topics reflected across the documents in the corpus.
+More recent work on these types of semantic models, including word2vec~\citep{MikoEtal13}, the Universal Sentence Encoder~\citep{CerEtal18}, GPT-2~\citep{RadfEtal19}, and GTP-3~\citep{BrowEtal20} use deep neural networks to attempt to identify the deeper conceptual representations underlying each word.
+Despite the growing popularity of more sophisticated deep learning-based embedding models, here we leverage latent dirichlet allocation (i.e., topic modelling) to embed video and recall text.
+This decision was motivated by several factors.
 First, topic models capture the \textit{essence} of a text passage devoid of the specific set and order of words used.
@@
 Second, words can mean different things in different contexts (e.g.
-``bat" may be the act of hitting a baseball, the object used for that action, or as a flying mammal).
+``bat'' may be the act of hitting a baseball, the object used for that action, or as a flying mammal).
 Topic models are robust to this, allowing words to exist as part of multiple topics.
-Last, topic models provide a straightforward means to recover the weights for the particular words comprising a topic, enabling easy interpretation of an event's contents (e.g.
+Last, topic models provide a straightforward means of recovering the weights for the particular words comprising a topic, enabling straightforward interpretation of an event's contents (e.g.
 Fig.~\ref{fig:topics}).
-Other models such as Google's Universal Sentence Encoder offer a context-sensitive encoding of text passages, but the encoding space is complex and non-linear, and thus recovering the original words used to fit the model is not straightforward.
-However, it's worth pointing out that our framework is divorced from the particular choice of language model.
+Other models such as the Universal Sentence Encoder, GPT-2, and GPT-3 offer context-sensitive encoding of text passages, but the encoding space is complex and non-linear, and thus recovering the original words used to fit the model is not straightforward.
+However, it is worth pointing out that our general framework is divorced from the particular choice of language model.
 Moreover, many of the aspects of our framework could be swapped out for other choices.
-For example, the language model, the timeseries segmentation model and the video-recall matching function could all be customized for the particular problem.
-Indeed for some problems, recovery of the particular recall words may not be necessary, and thus other text-modeling approaches (such as universal sentence encoder) may be preferable.
+For example, the language model, the timeseries segmentation model and the video-recall matching function could all be customized to suit a particular question space or application.
+Indeed for some questions, recovery of the particular words used to describe a memory may not be necessary, and thus other text-modeling approaches (including the deep learning-based embedding models described above) may be preferable.
 Future work will explore the influence of particular model choices on the framework's efficacy.
@@
 In most cases, the exact opposite is true of real-world episodes.
-Our internal thoughts, our actions, and the physical state of the world around us all tend to follow a direct, causal progression.
+Our internal thoughts, our actions, and the physical state of the world around us all tend to follow a direct (often causal) progression.
 As a result, each moment of our experience tends to be inherently more similar to surrounding moments than to those in the distant past or future.
@@
 We find that both of these metrics relate to the overall number of video events participants successfully recalled, and that our precision metric additionally relates to \cite{ChenEtal17}'s hand-annotated memory memory scores.
-Though we do not find participants' average recall distinctiveness related to the hand-annotated memory scores, this is not entirely surprising given the divergence of behavior they capture.
-In hand-scoring each participant's verbal recall for each of 50 (manually-deliniated) scenes, ``[a] scene was counted as recalled if the participant described any part of the scene" \citep{ChenEtal17}.
+
+We did not find evidence that participants' average recall distinctiveness was related to their hand-annotated memory scores computed by~\cite{ChenEtal17}.
+One possible explanation is that, in hand-scoring each participant's verbal recall for each of 50 (manually-deliniated) scenes, ``[a] scene was counted as recalled if the participant described any part of the scene''~\citep{ChenEtal17}.
 In other words, both an extensive description of a scene's content and a brief mention of some subset of its content were (binarily) considered equally successful recalls.
 By contrast, we identify the event structure in participants' recalls in an unsupervised manner, independent of the video event-timeseries, prior to mapping between video and recall content.
-Our HMM-based event-segmentation produces boundaries between timepoints where the topic proportions shift in a substantial way, and because a small handful of words is unlikely to contribute significantly to the topic proportions for any sliding window, such brief scene descriptions will most often not begat a sufficiently large shift in the resulting topic proportions for the HMM to identify an event boundary.
+Our HMM-based event-segmentation produces boundaries between timepoints where the topic proportions shift in a substantial way, and because a small handful of words is unlikely to contribute significantly to the topic proportions for any sliding window, such brief scene descriptions will most often not result in a sufficiently large shift in the resulting topic proportions for the HMM to identify an event boundary.
 Instead, they will be grouped with a neighboring event, consequently lowering that event's distinctiveness score and by extension, the participant's overall distinctiveness score.
@@
 Notably, \cite{ChenEtal17} also observed the PMC in a number of analyses including one that searched for regions whose activity patterns during encoding were reinstated during free recall.
-The PMC has been consistently identified in studies involving stimuli with meaningfully structured events \cite{CohnRang17}.
-Further, the PMC is part of the "posterior medial" system, a network of brain regions thought to represent situation models ~\cite{ZackEtal07} in support of memory, spatial navigation and social cognition ~\citep{RangRitc12}.
+The PMC has been consistently identified in studies involving stimuli with meaningfully structured events~\citep{CohnRang17}.
+Further, the PMC is part of the "posterior medial" system, a network of brain regions thought to represent situation models~\citep{ZackEtal07} in support of memory, spatial navigation and social cognition~\citep{RangRitc12}.
 Given that we constructed our video-recall searchlight model to capture temporal structure in the episode's semantic content (and how one's later recall aligns with that structure), we speculate that the PMC may play a role in constructing mnemonic events from meaningfully structured experiences.
@@
 First, the top 10 terms returned for the video-driven searchlight significance map were centered around themes of language and semantic meaning (Fig.~\ref{fig:neurosynth}A).
-In other words, the voxels identified as more reflective of the video's temporal structure (i.e., voxels with lower permutation correction-derived $p$-values), as defined by our model, were most likely to be reported as active in studies focused on the the neural underpinnings of semantic processing.
+In other words, the voxels identified as more reflective of the video content's temporal structure (i.e., voxels with lower permutation correction-derived $p$-values), as defined by our model, were most likely to be reported as active in studies focused on the the neural underpinnings of semantic processing.
 This finding is interesting, as our model specifically captures the temporal structure of the video's \textit{semantic} content (e.g., as opposed to that of the visual, auditory, or affective content).
-This suggests that the network of structures displayed in Figure \ref{fig:brainz}C may play a roll in processing the evolving semantic structure of ongoing experiences.
+This suggests that the network of structures displayed in Figure \ref{fig:brainz}C may play a roll in processing the evolving semantic content of ongoing experiences.
 
-Our second searchlight analysis identified a largely separate network of regions (Fig.~\ref{fig:brainz}D) whose patterns of activity as participants viewed the video reflected the idiosyncratic structure of each individual's later recall.
-Decoding the associated significance map yielded a set of terms that primarily reflected names of specific structural regions (such as ``thalamus," ``anterior insula," ``anterior cingulate" and ``inferior frontal"; Fig.~\ref{fig:neurosynth}B).
+Our second searchlight analysis identified a partially overlapping network of regions (Fig.~\ref{fig:brainz}D) whose patterns of activity as participants viewed the video reflected the idiosyncratic structure of each individual's later recalls.
+The associated significance map yielded a set of \texttt{Neurosynth} terms that primarily reflected names of specific structural regions (such as ``thalamus," ``anterior insula," ``anterior cingulate" and ``inferior frontal"; Fig.~\ref{fig:neurosynth}B).
 Interestingly, these regions share membership in a common, large-scale functional network (termed the ``salience network") involved in detecting and processing affective cues.
 In particular, the latter three regions have been implicated in functions relevant to assigning personal meaning to an experience, including: ascribing subjective value to raw, sensory input \citep{MedfCrit10}; modulating semantic and phonological processing in response to personally salient stimuli \citep{KellEtal07b}; and directing and reallocating attention and working memory resources towards the most relevant stimuli \citep{MenoUddi10}.
-This suggests that the network of structures displayed in Figure \ref{fig:brainz}D may be play a roll in transforming and restructuring ongoing experiences through the lens of one's own personal values as they are encoded in memory.
+This suggests that the network of structures displayed in Figure \ref{fig:brainz}D may be play a roll in transforming and restructuring ongoing experiences through the lens of one's prior experience and subjective emotions as they are encoded in memory.
 
@@
 \subsubsection*{Topic modeling}
-The input to the topic model we trained to characterize the dynamic content of the video comprised 998 hand-generated annotations of short (mean: 2.96s) scenes spanning the video clip~(\citealp{ChenEtal17} generated 1000 annotations total; we removed two referring to the break between the first and second scan sessions, during which no fMRI data was collected).
+The input to the topic model we trained to characterize the dynamic content of the video comprised 998 hand-generated annotations of short (mean: 2.96s) scenes spanning the video clip~(\citealp{ChenEtal17} generated 1000 annotations total; we removed two annotations referring to a break between the first and second scan sessions, during which no fMRI data was collected).
 We concatenated the text for all of the annotated features within each segment, creating a ``bag of words'' describing each scene and performed some minor preprocessing (e.g., stemming possessive nouns and removing punctuation).
 We then re-organized the text descriptions into overlapping sliding windows spanning (up to) 50 scenes each.
-In other words, we created a ``context" for each scene comprising the text descriptions of the preceding 25 scenes, the present scene, and the following 24 scenes.
-To model the ``context" for scenes near the beginning and end of the video (i.e., within 25 scenes of the beginning or end), we created overlapping sliding windows that grew in size from one scene to the full length, then similarly tapered their length at the end.
-This additionally ensured that each scene's content was represented in the text corpus an equal number of times.
+In other words, we estimated the ``context'' for each scene using the text descriptions of the preceding 25 scenes, the present scene, and the following 24 scenes.
+To model the context for scenes near the beginning of the video (i.e., within 25 scenes of the beginning or end), we created overlapping sliding windows that grew in size from one scene to the full length.
+We also tapered the sliding window lengths at the end of the video, whereby scenes within fewer than 24 scenes of the end of the video were assigned sliding windows that extended to the end of the video.
+This procedure ensured that each scene's content was represented in the text corpus an equal number of times.
 % ------ NOTE: ------
@@
 
-We created similar topic proportions matrices using hand-annotated transcripts of each participant's recall of the video~\citep[annotated by ][]{ChenEtal17}.
+We created similar topic proportions matrices using hand-annotated transcripts of each participant's verbal recall of the video~\citep[annotated by][]{ChenEtal17}.
 We tokenized the transcript into a list of sentences, and then re-organized the list into overlapping sliding windows spanning (up to) 10 sentences each, analogously to how we parsed the video annotations.
-In turn, we transformed each window's sentences into a word count vector (using the same vocabulary as for the video model), then used the topic model already trained on the video scenes to compute the most probable topic proportions for each sliding window.
+In turn, we transformed each window's sentences into a word count vector (using the same vocabulary as for the video model), and then we used the topic model already trained on the video scenes to compute the most probable topic proportions for each sliding window.
 This yielded a number-of-windows (range: 83--312) by number-of-topics (100) topic proportions matrix for each participant.
@@
 \subsubsection*{Parsing topic trajectories into events using Hidden Markov Models}
-We parsed the topic trajectories of the video and participants' recalls into events using Hidden Markov Models~\citep{Rabi89}.
+We parsed the topic trajectories of the video and participants' recalls into events using Hidden Markov Models~\citep[HMMs;][]{Rabi89}.
 Given the topic proportions matrix (describing the mix of topics at each timepoint) and a number of states, $K$, an HMM recovers the set of state transitions that segments the timeseries into $K$ discrete states.
@@
 We used an optimization procedure to select the appropriate $K$ for each topic proportions matrix.
-Prior studies on narrative structure and processing have shown that we both perceive and internally represent the world around us at multiple, hierarchical timescales (e.g., \citealp{HassEtal08, LernEtal11, HassEtal15, ChenEtal17, BaldEtal17, BaldEtal18}).
+Prior studies on narrative structure and processing have shown that we both perceive and internally represent the world around us at multiple, hierarchical timescales \citep[e.g.,][]{HassEtal08, LernEtal11, HassEtal15, ChenEtal17, BaldEtal17, BaldEtal18}.
 However, for the purposes of our framework, we sought to identify the single timeseries of event-representations that is emphasized \textit{most heavily} in the temporal structure of the video and of each participant's recall.
@@
 where $a$ was the distribution of within-state topic vector correlations, and $b$ was the distribution of across-state topic vector correlations .
-We computed the first Wasserstein distance ($W_{1}$; also known as ``earth mover's distance"; \citealp{Dobr70, RamdEtal17}) between these distributions for a large range of possible $K$-values (range [2,50]), and selected the $K$ that yielded the maximum value.
+We computed the first Wasserstein distance ($W_{1}$; also known as \textit{Earth mover's distance}; \citealp{Dobr70, RamdEtal17}) between these distributions for a large range of possible $K$-values (range [2, 50]), and selected the $K$ that yielded the maximum value.
 Figure~\ref{fig:model}B displays the event boundaries returned for the video, and Figure~\corrmats~displays the event boundaries returned for each participant's recalls.
@@
 \cite{ChenEtal17} used this method to rate each participant's memory quality by computing the proportion of (50, manually identified) scenes mentioned in their recall.
-We found a strong across-participants correlation between these independent ratings and the proportion of (30, HMM-identified) video events matched to participants' recalls (Pearson's $r(15) = 0.71, p = 0.002$).
+We found a strong across-participants correlation between these independent ratings and the proportion of 30 HMM-identified video events matched to participants' recalls (Pearson's $r(15) = 0.71, p = 0.002$).
 We further considered a number of more nuanced memory performance measures that are typically associated with list-learning studies.
@@
 For each recall transition (following the first recall), we computed the lag between the current recall event and the next recall event, normalizing by the total number of possible transitions.
-This yielded a number-of-participants (17) by number-of-lags (-29 to +29; 61 lags total) matrix.
+This yielded a number-of-participants (17) by number-of-lags (-29 to +29; 58 lags total excluding lags of 0) matrix.
 We averaged over the rows of this matrix to obtain a group-averaged lag-CRP curve (Fig.~\ref{fig:list-learning}B).
@@
 We hypothesized that participants with high memory performance might describe each event in a more distinctive way (relative to those with lower memory performance who might describe events in a more general way).
-To test this hypothesis we define a distinctiveness score for each recall event as
+To test this hypothesis we define a distinctiveness score for each recall event $i$ as
 
 \[
-  d(\mathrm{event}) = 1 - \bar{c}(\mathrm{\mathbb{P} \setminus \{event\}}),
+  d(i) = 1 - \frac{1}{N - 1} \sum_{j = \\i}\mathrm{corr}\left(\mathrm{event}_i, \mathrm{event}_j\right) 
 \]
-where $\bar{c}(\mathrm{\mathbb{P} \setminus \{event\}})$ is the average correlation between the given recall event's topic vector and the topic vectors from all other recall events not matched to the same video event (for a single participant).
-We then averaged these distinctiveness scores across all of the events recalled by the given participant and correlated resulting values with hand-annotated and model derived memory performance scores across-subjects, as above.
+where the average is taken over the correlation between the recall event $i$'s topic vector and the topic vectors from all other recall events from that participant.
+We averaged these distinctiveness scores across all of the events recalled by the given participant to get the participant's distinctiveness score.
+We correlated these distinctiveness scores with hand-annotated and model-derived memory performance scores across-subjects, as above.
 
-\noindent Note: in all instances where we performed statistical tests involving precision or distinctiveness scores, we used Fisher's $z$-transformation \citep{Fish25} to stabilize the variance across the distribution of correlation values prior to performing the test.
+\paragraph*{Averaging correlations}
+In all instances where we performed statistical tests involving precision or distinctiveness scores, we used the Fisher $z$-transformation~\citep{Fish25} to stabilize the variance across the distribution of correlation values prior to performing the test.
 Similarly, when averaging precision or distinctiveness scores, we $z$-transformed the scores prior to computing the mean, and inverse $z$-transformed the result.
@@
 We used the UMAP algorithm~\citep{McInEtal18} to project the 100-dimensional topic space onto a two-dimensional space for visualization (Figs.~\ref{fig:trajectory}, \ref{fig:topics}).
-Importantly, to ensure that all of the trajectories were projected onto the \textit{same} lower dimensional space, we computed the low-dimensional embedding on a ``stacked" matrix created by vertically concatenating the events-by-topics topic proportions matrices for the video, across-participants average recall and all 17 individual participants' recalls.
-We then divided the rows of the result (a total-number-of-events by two matrix) back into separate matrices for the video topic trajectory, across-participant average recall trajectory and the trajectories for each individual participant's recalls (Fig.~\ref{fig:trajectory}).
+To ensure that all of the trajectories were projected onto the \textit{same} lower dimensional space, we computed the low-dimensional embedding on a ``stacked'' matrix created by vertically concatenating the events-by-topics topic proportions matrices for the video, across-participants average recall and all 17 individual participants' recalls.
+We then separated the rows of the result (a total-number-of-events by two matrix) back into individual matrices for the video topic trajectory, across-participant average recall trajectory and the trajectories for each individual participant's recalls (Fig.~\ref{fig:trajectory}).
 This general approach for discovering a shared low-dimensional embedding for a collections of high-dimensional observations follows \cite{HeusEtal18a}.
@@
 We computed the distribution of angles formed by those segments and the $x$-axis, and used a Rayleigh test to determine whether the distribution of angles was reliably ``peaked'' (i.e., consistent across all transitions that passed through that local portion of topic space).
-To create Figure~\ref{fig:trajectory}B we drew an arrow originating from each grid vertex, pointing in the direction of the average angle formed by the line segments that passed within its circular radius.
+To create Figure~\ref{fig:trajectory}B we drew an arrow originating from each grid vertex, pointing in the direction of the average angle formed by the line segments that passed within 2.4 units.
 We set the arrow lengths to be inversely proportional to the $p$-values of the Rayleigh tests at each vertex.
@@
 
-Next, we constructed a series of ``template" matrices: the first reflecting the timecourse of video's topic trajectory, and the others reflecting that of each participant's recall topic trajectory.
+Next, we constructed a series of ``template'' matrices.
+The first template reflected the timecourse of the video's topic trajectory, and the others reflected the timecourse of each participant's recall trajectory.
 To construct the video template, we computed the correlations between the topic proportions estimated for every pair of TRs (prior to segmenting the trajectory into discrete events; i.e., the correlation matrix shown in Figs.~\ref{fig:model}B and \ref{fig:brainz}A).
@@
 The temporal structure of the video's content (as described by our model) is captured in the block-diagonal structure of the video's temporal correlation matrix (e.g., Figs.~\ref{fig:model}B, \ref{fig:brainz}A), with time periods of thematic stability represented as dark blocks of varying sizes.
-Inspecting the video correlation matrix suggests that the video's semantic content is highly temporally specific (i.e., the correlations between topic vectors from distant timepoints are almost entirely near-zero).
+Inspecting the video correlation matrix suggests that the video's semantic content is highly temporally specific (i.e., the correlations between topic vectors from distant timepoints are almost all near zero).
 By contrast, the activity patterns of individual (cubes of) voxels can encode relatively limited information on their own, and their activity frequently contributes to multiple separate functions \citep{FreeEtal01, SigmDeha08, CharKoec10, RishEtal13}.
 By nature, these two attributes give rise to similarities in activity across large timescales that may not necessarily reflect a single task.
-To enable a more sensitive analysis of brain regions whose shifts in activity patterns mirrored shifts in the semantic content of the video or recalls, we restricted the temporal correlations we considered to timescale of semantic information captured by our model.
-Specifically, we isolated the upper triangle of the video correlation matrix and created a ``proximal correlation mask" that included only diagonals from the upper triangle of the video correlation matrix up to the first that contained no positive correlations.
+To enable a more sensitive analysis of brain regions whose shifts in activity patterns mirrored shifts in the semantic content of the video or recalls, we restricted the temporal correlations we considered to the timescale of semantic information captured by our model.
+Specifically, we isolated the upper triangle of the video correlation matrix and created a ``proximal correlation mask'' that included only diagonals from the upper triangle of the video correlation matrix up to the first diagonal that contained no positive correlations.
 Applying this mask to the full video correlation matrix was analogous to excluding diagonals beyond the corner of the largest diagonal block.
@@
 We then performed a one-sample $t$-test on the distribution of (Fisher $z$-transformed) correlations at each voxel, across participants.
-This resulted in a value for each voxel (cube), describing how reliably its timecourse mirrored that of the video.
+This resulted in a value for each voxel (cube), describing how reliably its timecourse followed that of the video.
 
 We further sought to ensure that our analysis identified regions where the activations’ temporal structure specifically reflected that of the video, rather than regions whose activity was simply autocorrelated at a width similar to the video template’s diagonal.
-To achieve this, we used a phase shift-based permutation procedure, wherein we circularly shifted the video’s topic trajectory by a random number of timepoints, computed the resulting ``null” video template, and re-ran the searchlight analysis, in full.
+To achieve this, we used a phase shift-based permutation procedure, whereby we circularly shifted the video’s topic trajectory by a random number of timepoints, computed the resulting ``null” video template, and re-ran the searchlight analysis, in full.
 (For each of the 100 permutations, the same random shift was used for all participants).
@@
 As in the analysis described above, we $t$-scored the (Fisher $z$-transformed) voxelwise correlations, and used the same permutation procedure we developed for the video responses to ensure specificity to the recall timeseries and assign significance values.
-To create the map in Figure~\ref{fig:brainz}D we again thresholded out any voxels whose correspondence values fell below the 95\textsuperscript{th} percentile of the permutation-derived null distribution.
+To create the map in Figure~\ref{fig:brainz}D we again thresholded out any voxels whose scores were below the 95\textsuperscript{th} percentile of the permutation-derived null distribution.
 
@@
 \texttt{Neurosynth} parses a massive online database of over 14,000 neuroimaging studies and constructs meta-analysis images for over 13,000 psychology- and neuroscience-related terms, based on NIfTI images accompanying studies where those terms appear at a high frequency.
-Then, given a novel image (tagged with its value type; e.g., $t$-, $F$- or $p$-statistics), \texttt{Neurosynth} returns a list of terms whose meta-analysis images are most similar to this new data.
+Given a novel image (tagged with its value type; e.g., $t$-, $F$- or $p$-statistics), \texttt{Neurosynth} returns a list of terms whose meta-analysis images are most similar.
 Our permutation procedure yielded, for each of the two searchlight analyses, a voxelwise map of significance ($p$-statistic) values.
 These maps describe the extent to which each voxel \textit{specifically} reflected the temporal structure of the video or individuals' recalls (i.e., for each voxel, the proportion of phase-shifted topic vector correlation matrices less similar to the voxel activity correlation matrix than the unshifted video's correlation matrix).
-We input the two statistical maps described above to \texttt{Neurosynth} to create a list of the 10 most representative terms for each map.
+We inputted the two statistical maps described above to \texttt{Neurosynth} to create a list of the 10 most representative terms for each map.
 

### 2020-08-20 paper/main.tex
JRM edits to intro

@@
 \begin{abstract}
-Our moment-by-moment subject experience reflects external sensory information from each moment, along with additional information from our past that we carry with us into that moment.
+Our ongoing subjective experience reflects external sensory information from each moment, along with additional information from our past that we carry with us into that moment.
 The blend of memories, knowledge, emotions, goals, and other internal perceptual and mental states that color our subjective experience provides a \textit{context} for interpreting new information and conceptually linking what is happening now with our prior experiences.
@@
 More nuanced studies might incorporate self-reported confidence measures as a proxy for memory strength, or ask participants to discriminate between ``recollecting'' the (contextual) details of an experience or having a general feeling of ``familiarity'' \citep{Yone02}.
-Using well controlled, trial-based experimental designs, the field has amassed a wealth of valuable information regarding human episodic memory.
-However, there are fundamental properties of the external world and our memories that trial-based experiments are not well suited to capture~\citep[for review, also see][]{KoriGold94, HukEtal18}.
+Using well-controlled, trial-based experimental designs, the field has amassed a wealth of information regarding human episodic memory.
+However, there are fundamental properties of the external world and our memories that trial-based experiments are not well-suited to capture~\citep[for review, also see][]{KoriGold94, HukEtal18}.
 First, our experiences and memories are continuous, rather than discrete---isolating a (naturalistic) event from the context in which it occurs can substantially change its meaning.
-Second, the specific language used to describe an experience has little bearing on whether the experience should be considered to have been ``remembered.''  Asking whether the rememberer has precisely reproduced a specific set of words to describe a given experience is nearly orthogonal to whether or not they were actually able to remember it.
-In classic (e.g., list-learning) memory studies, by contrast, the number or proportion of exact recalls is often a primary metric for assessing the quality of participants' memories.
+Second, asking whether the rememberer has precisely reproduced a specific set of words to describe a given experience is nearly orthogonal to how well they were actually able to remember it.
+In classic (e.g., list-learning) memory studies, by contrast, the number or proportion of (exact) recalls is often considered to be a primary metric for assessing the quality of participants' memories.
 Third, one might remember the \textit{essence} (or a general summary) of an experience but forget (or neglect to recount) particular details.
-Capturing the essence of what happened is typically the main ``point'' of recounting a memory to a listener, while the addition of highly specific details may add comparatively little to successful conveyance of an experience.
+Capturing the essence of what happened is often a main goal of recounting an episodic memory to a listener, whereas the inclusion of specific low-level details is often less pertinent.
 
-How might one go about formally characterizing the \textit{essence} of an experience, and whether it has been recovered by the rememberer?
-Any given moment of an experience derives meaning from surrounding moments, as well as from longer-range temporal associations~\citep{LernEtal11, Mann19, Mann20}.
+How might we formally characterize the \textit{essence} of an experience, and whether it has been recovered by the rememberer?
+And how might we distinguish an experience's overarching essence from its low-level details?
+One approach is to start by considering some fundamental properties of the dynamics of our experiences.
+Any given moment of an experience tends to derive meaning from surrounding moments, as well as from longer-range temporal associations~\citep{LernEtal11, Mann19, Mann20}.
 Therefore, the timecourse describing how an event unfolds is fundamental to its overall meaning.
@@
 For example, prior work has shown that event boundaries can influence how we learn sequences of items~\citep{HeusEtal18b, DuBrDava13}, navigate~\citep{BrunEtal18}, and remember and understand narratives~\citep{ZwaaRadv98, EzzyDava11}.
-Prior research has implicated a network of brain regions (including the hippocampus and the medial prefrontal cortex) as playing a critical role in transforming experiences into structured and consolidated memories ~\citep{TompDava17}.
+This work also suggests a means of distinguishing the essence of an experience from its low-level details.
+The event-level properties reflect how the high-level experience unfolds (i.e., its essence), whereas subtler within-event changes reflect low-level details.
+Prior research has also implicated a network of brain regions (including the hippocampus and the medial prefrontal cortex) as playing a critical role in transforming experiences into structured and consolidated memories ~\citep{TompDava17}.
 
 Here, we sought to examine how the temporal dynamics of a ``naturalistic'' experience were later reflected in participants' memories.
+We also sought to leverage the above conceptual insights into the distinctions between an experience's essence versus its low-level details to build models that explicitly quantified these distinctions.
 We analyzed an open dataset that comprised behavioral and functional Magnetic Resonance Imaging (fMRI) data collected as participants viewed and then verbally recounted an episode of the BBC television series \textit{Sherlock}~\citep{ChenEtal17}.
@@
 Under this framework, successful remembering entails verbally ``traversing'' the content trajectory of the episode, thereby reproducing the shape (or essence) of the original experience.
-Comparing the shapes of the topic trajectories of the episode and of participants' retellings of the episode then reveals which aspects of the episode were preserved (or discarded) in the translation into memory.
-We further introduce two novel metrics for assessing memory quality: \textbf{1}) the \textit{precision} with which a participant recounts each event, and \textbf{2}) the \textit{distinctiveness} of each recall event (relative to other recalled events).
-We examine how these metrics relate to overall memory performance, and discuss the ways in which they improve upon classic ``proportion-recalled'' measures for analyzing naturalistic memory.
-Last, we utilize our framework to identify networks of brain structures whose responses (as participants watched the episode) reflected the temporal dynamics of either the episode or how participants would later recount it.
+The essence of the episode is captured by the sequence of geometric coordinates of its events, and the episode's low-level details are captured by examining its within-event geometric properties.
+
+Comparing the overall shapes of the topic trajectories of the episode and of participants' retellings of the episode reveals which aspects of the episode's essence were preserved (or discarded) in the translation into memory.
+We also develop two metrics for assessing participants' memories for low-level details: (1) the \textit{precision} with which a participant recounts details about each event, and (2) the \textit{distinctiveness} of each recall event (relative to other recalled events).
+We examine how these metrics relate to overall memory performance as judged by third-party human annotators.
+We also compare and contrast our general approach to studying memory for naturalistic experiences with standard metrics for assessing performance on more traditional memory tasks, such as list learning.
+Last, we leverage our framework to identify networks of brain structures whose responses (as participants watched the episode) reflected the temporal dynamics of either the episode or how participants would later recount it.
 

### 2020-08-20 paper/main.tex
input edits to abstract and intro

@@
 Fitzpatrick\textsuperscript{1, \textdagger}, and Jeremy R.
-Manning\textsuperscript{1, *}\\\textsuperscript{1}Department of Psychological and Brain Sciences\\Dartmouth College, Hanover, NH 03755, USA\\\textsuperscript{2}Akili Interactive\\Boston, MA 02110\\\textsuperscript{\textdagger}Denotes equal contribution\\\textsuperscript{*}Corresponding author: Jeremy.R.Manning@dartmouth.edu}
+Manning\textsuperscript{1, *}\\\textsuperscript{1}Department of Psychological and Brain Sciences\\Dartmouth College, Hanover, NH 03755, USA\\\textsuperscript{2}Akili Interactive\\Boston, MA 02110\\\textsuperscript{\textdagger}Denotes equal contribution\\\textsuperscript{*}Corresponding author: Jeremy.R.Manning@Dartmouth.edu}
 
@@
 We also demonstrate how \textit{memories} may also be modeled as trajectories through the same spaces.
-According to this view, encoding an experience into memory entails geometrically distorting or transforming the original experience's trajectory.
-This translates qualitative neuropsychological questions about how we remember naturalistic experiences into quantitive geometric questions about the spatial configurations of trajectory shapes.
+According to this view, encoding an experience into memory entails geometrically distorting or transforming the \textit{shape} of the original experience's trajectory.
+This translates qualitative, neuropsychological questions about how we remember naturalistic experiences into quantitive, geometric questions about the spatial configurations of trajectory shapes.
 We applied our framework to data collected as participants watched and verbally recounted a television episode while undergoing functional neuroimaging.
@@
 Using well-controlled, trial-based experimental designs, the field has amassed a wealth of information regarding human episodic memory.
-However, there are fundamental properties of the external world and our memories that trial-based experiments are not well-suited to capture~\citep[for review, also see][]{KoriGold94, HukEtal18}.
+However, there are fundamental properties of the external world and our memories that trial-based experiments are not well suited to capture~\citep[for review, also see][]{KoriGold94, HukEtal18}.
 First, our experiences and memories are continuous, rather than discrete---isolating a (naturalistic) event from the context in which it occurs can substantially change its meaning.
-Second, asking whether the rememberer has precisely reproduced a specific set of words to describe a given experience is nearly orthogonal to how well they were actually able to remember it.
-In classic (e.g., list-learning) memory studies, by contrast, the number or proportion of (exact) recalls is often considered to be a primary metric for assessing the quality of participants' memories.
+Second, whether or not the rememberer has precisely reproduced a specific set of words in describing a given experience is nearly orthogonal to how well they were actually able to remember it.
+In classic (e.g., list-learning) memory studies, by contrast, the number or proportion of \textit{exact} recalls is often considered to be a primary metric for assessing the quality of participants' memories.
 Third, one might remember the \textit{essence} (or a general summary) of an experience but forget (or neglect to recount) particular details.
-Capturing the essence of what happened is often a main goal of recounting an episodic memory to a listener, whereas the inclusion of specific low-level details is often less pertinent.
+Capturing the essence of what happened is often a main goal of recounting an episodic memory to a listener, whereas the inclusion of specific, low-level details is often less pertinent.
 
@@
 One approach is to start by considering some fundamental properties of the dynamics of our experiences.
-Any given moment of an experience tends to derive meaning from surrounding moments, as well as from longer-range temporal associations~\citep{LernEtal11, Mann19, Mann20}.
+Each given moment of an experience tends to derive meaning from surrounding moments, as well as from longer-range temporal associations~\citep{LernEtal11, Mann19, Mann20}.
 Therefore, the timecourse describing how an event unfolds is fundamental to its overall meaning.
-Further, this hierarchy formed by our subjective experiences at different timescales defines a \textit{context} for each new moment~\citep[e.g., ][]{HowaKaha02a, HowaEtal14}, and plays an important role in how we interpret that moment and remember it later~\citep[for review see][]{MannEtal15, Mann20}.
+Further, this hierarchy formed by our subjective experiences at different timescales defines a \textit{context} for each new moment~\citep[e.g.,][]{HowaKaha02a, HowaEtal14}, and plays an important role in how we interpret that moment and remember it later~\citep[for review see][]{MannEtal15, Mann20}.
 Our memory systems can leverage these associations to form predictions that help guide our behaviors~\citep{RangRitc12}.
-For example, as we navigate the world, the features of our subjective experiences tend to change gradually (e.g., the room or situation we are in at any given moment is strongly temporally autocorrelated), allowing us to form stable estimates of our current situation and behave accordingly~\citep{ZackEtal07, ZwaaRadv98}.
+For example, as we navigate the world, the features of our subjective experiences tend to change gradually (e.g., the room or situation we find ourselves in at any given moment is strongly temporally autocorrelated), allowing us to form stable estimates of our current situation and behave accordingly~\citep{ZackEtal07, ZwaaRadv98}.
 
@@
 This work also suggests a means of distinguishing the essence of an experience from its low-level details.
-The event-level properties reflect how the high-level experience unfolds (i.e., its essence), whereas subtler within-event changes reflect low-level details.
-Prior research has also implicated a network of brain regions (including the hippocampus and the medial prefrontal cortex) as playing a critical role in transforming experiences into structured and consolidated memories ~\citep{TompDava17}.
+The overall structure of events and event transitions reflects how the high-level experience unfolds (i.e., its essence), while subtler event-level properties reflect low-level details.
+Prior research has also implicated a network of brain regions (including the hippocampus and the medial prefrontal cortex) in playing a critical role in transforming experiences into structured and consolidated memories ~\citep{TompDava17}.
 
 Here, we sought to examine how the temporal dynamics of a ``naturalistic'' experience were later reflected in participants' memories.
-We also sought to leverage the above conceptual insights into the distinctions between an experience's essence versus its low-level details to build models that explicitly quantified these distinctions.
+We also sought to leverage the above conceptual insights into the distinctions between an experience's essence and low-level details to build models that explicitly quantified these distinctions.
 We analyzed an open dataset that comprised behavioral and functional Magnetic Resonance Imaging (fMRI) data collected as participants viewed and then verbally recounted an episode of the BBC television series \textit{Sherlock}~\citep{ChenEtal17}.
@@
 Specifically, we use topic modeling~\citep{BleiEtal03} to characterize the thematic conceptual (semantic) content present in each moment of the episode and recalls, and hidden Markov models~\citep{Rabi89, BaldEtal17} to discretize this evolving semantic content into events.
-In this way, we cast naturalistic experiences (and memories of those experiences) as geometric \textit{trajectories} that describe how the experiences evolve over time.
-Under this framework, successful remembering entails verbally ``traversing'' the content trajectory of the episode, thereby reproducing the shape (or essence) of the original experience.
-The essence of the episode is captured by the sequence of geometric coordinates of its events, and the episode's low-level details are captured by examining its within-event geometric properties.
+In this way, we cast both naturalistic experiences and memories of those experiences as geometric \textit{trajectories} that describe how they evolve over time.
+Under this framework, successful remembering entails verbally ``traversing'' the content trajectory of the episode, thereby reproducing the shape (essence) of the original experience.
+Our framework captures the episode's essence in the sequence of geometric coordinates for its events, and its low-level details by examining its within-event geometric properties.
 
-Comparing the overall shapes of the topic trajectories of the episode and of participants' retellings of the episode reveals which aspects of the episode's essence were preserved (or discarded) in the translation into memory.
-We also develop two metrics for assessing participants' memories for low-level details: (1) the \textit{precision} with which a participant recounts details about each event, and (2) the \textit{distinctiveness} of each recall event (relative to other recalled events).
+Comparing the overall shapes of the topic trajectories for the episode and participants' recalls reveals which aspects of the episode's essence were preserved (or discarded) in the translation into memory.
+We also develop two metrics for assessing participants' memories for low-level details: (1) the \textit{precision} with which a participant recounts details about each event, and (2) the \textit{distinctiveness} of each recall event, relative to other recalled events.
 We examine how these metrics relate to overall memory performance as judged by third-party human annotators.
-We also compare and contrast our general approach to studying memory for naturalistic experiences with standard metrics for assessing performance on more traditional memory tasks, such as list learning.
+We also compare and contrast our general approach to studying memory for naturalistic experiences with standard metrics for assessing performance on more traditional memory tasks, such as list-learning.
 Last, we leverage our framework to identify networks of brain structures whose responses (as participants watched the episode) reflected the temporal dynamics of either the episode or how participants would later recount it.

### 2020-08-20 paper/main.tex
WIP results section edits

@@
 Topic models take as inputs a vocabulary of words to consider and a collection of text documents, and return two output matrices.
-The first of these is a \textit{topics matrix} whose rows are \textit{topics} (latent themes) and whose columns correspond to words in the vocabulary.
-The entries of the topics matrix reflect how each word in the vocabulary is weighted by each discovered topic.
+The first of these is a \textit{topics matrix} whose rows are \textit{topics} (or latent themes) and whose columns correspond to words in the vocabulary.
+The entries in the topics matrix reflect how each word in the vocabulary is weighted by each discovered topic.
 For example, a detective-themed topic might weight heavily on words like ``crime,'' and ``search.''  The second output is a \textit{topic proportions matrix}, with one row per document and one column per topic.
-The topic proportions matrix describes what mixture of discovered topics is reflected in each document.
+The topic proportions matrix describes the mixture of discovered topics reflected in each document.
 
-\cite{ChenEtal17} collected hand-annotated information about each of 1000 (manually identified) scenes spanning the roughly 50 minute video used in their experiment.
+\cite{ChenEtal17} collected hand-annotated information about each of 1,000 (manually identified) scenes spanning the roughly 50 minute video used in their experiment.
 This information included: a brief narrative description of what was happening, the location where the scene took place, the names of any characters on the screen, and other similar details (for a full list of annotated features, see \textit{Methods}).
 We took from these annotations the union of all unique words (excluding stop words, such as ``and,'' ``or,'' ``but,'' etc.) across all features and scenes as the ``vocabulary'' for the topic model.
-We then concatenated the sets of words across all features contained in overlapping, sliding windows of (up to) 50 scenes, and treated each window as a single ``document" for the purpose of fitting the topic model.
+We then concatenated the sets of words across all features contained in overlapping sliding windows of (up to) 50 scenes, and treated each window as a single ``document" for the purpose of fitting the topic model.
 Next, we fit a topic model with (up to) $K = 100$ topics to this collection of documents.
 We found that 32 unique topics (with non-zero weights) were sufficient to describe the time-varying content of the video (see \textit{Methods}; Figs.~\ref{fig:schematic}, \topics).
-Note that our approach is similar in some respects to Dynamic Topic Models~\citep{BleiLaff06} in that we sought to characterize how the thematic content of the episode evolved over time.
+Note that our approach is similar in some respects to Dynamic Topic Models~\citep{BleiLaff06}, in that we sought to characterize how the thematic content of the episode evolved over time.
 However, whereas Dynamic Topic Models are designed to characterize how the properties of \textit{collections} of documents change over time, our sliding window approach allows us to examine the topic dynamics within a single document (or video).
 Specifically, our approach yielded (via the topic proportions matrix) a single \textit{topic vector} for each sliding window of annotations transformed by the topic model.
-We then stretched (interpolated) the resulting windows-by-topics matrix to match the time series of the 1976 fMRI volumes collected as participants viewed the episode.
+We then stretched (interpolated) the resulting windows-by-topics matrix to match the time series of the 1,976 fMRI volumes collected as participants viewed the episode.
 
@@
 \includegraphics[width=1\textwidth]{figs/schematic}
-\caption{\small \textbf{Methods overview.} We used hand-annotated descriptions of each moment of video to fit a topic model.
+\caption{\small \textbf{Topic weights in episode and recall content.} We used hand-annotated descriptions of each moment of video to fit a topic model.
 Three example video frames and their associated descriptions are displayed (top two rows).
@@
 \end{figure}
-% Odd name for figure in "Results" section rather than "methods" section
-% - Paxton
-% The 10 top words in this figure seem to be out of order or incorrect. Paxton, can you look into this? - Andy
+% add an x-label under the "
 
@@
 Several of the identified topics were highly similar, which we hypothesized might allow us to distinguish between subtle narrative differences if the distinctions between those overlapping topics were meaningful.
-The topic vectors for each timepoint were also \textit{sparse}, in that only a small number (usually one or two) of topics tended to be ``active" in any given timepoint (Fig.~\ref{fig:model}A).
+The topic vectors for each timepoint were also \textit{sparse}, in that only a small number (typically one or two) of topics tended to be ``active" in any given timepoint (see Fig.~\ref{fig:model}A).
 Further, the dynamics of the topic activations appeared to exhibit \textit{persistence} (i.e., given that a topic was active in one timepoint, it was likely to be active in the following timepoint) along with \textit{occasional rapid changes} (i.e., occasionally topics would appear to spring into or out of existence).
@@
 \includegraphics[width=\textwidth]{figs/eventseg}
-\caption{\small \textbf{Modelling naturalistic stimuli and recalls.} All panels: darker colors indicate greater values; range: [0, 1].
+\caption{\small \textbf{Modeling naturalistic stimuli and recalls.} All panels: darker colors indicate greater values; range: [0, 1].
 \textbf{A.} Topic vectors ($K = 100$) for each of the 1976 video timepoints.

### 2020-08-20 paper/main.tex
rename video to episode

@@
 Next, we fit a topic model with (up to) $K = 100$ topics to this collection of documents.
-We found that 32 unique topics (with non-zero weights) were sufficient to describe the time-varying content of the video (see \textit{Methods}; Figs.~\ref{fig:schematic}, \topics).
+We found that 32 unique topics (with non-zero weights) were sufficient to describe the time-varying content of the episode (see \textit{Methods}; Figs.~\ref{fig:schematic}, \topics).
 Note that our approach is similar in some respects to Dynamic Topic Models~\citep{BleiLaff06}, in that we sought to characterize how the thematic content of the episode evolved over time.
@@
 \includegraphics[width=1\textwidth]{figs/schematic}
-\caption{\small \textbf{Topic weights in episode and recall content.} We used hand-annotated descriptions of each moment of video to fit a topic model.
-Three example video frames and their associated descriptions are displayed (top two rows).
-Participants later recalled the video (in the third row, we show example recalls of the same three scenes from participant 17).
-We used the topic model (fit to the annotations) to estimate topic vectors for each moment of video and each sentence the participants recalled.
-Example topic vectors are displayed in the bottom row (blue: video annotations; green: example participant's recalls).
-Three topic dimensions are shown (the highest-weighted topics for each of the three example scenes, respectively).
-We also show the 10 highest-weighted words for each topic.
+\caption{\small \textbf{Topic weights in episode and recall content.} We used hand-annotated descriptions of each manually identified scene from the episode to fit a topic model.
+Three example video frames (first row) and their associated descriptions (second row) are displayed.
+The third row shows an example participant's later recalls of the same three scenes.
+We used the topic model (fit to the episode annotations) to estimate topic vectors for each moment of the episode and each sentence of participants' recalls.
+Example topic vectors are displayed in the bottom row (blue: episode annotations; green: example participant's recalls).
+Three topic dimensions are shown (the highest-weighted topics for each of the three example scenes, respectively), along with the 10 highest-weighted words for each topic.
 Figure~\topics~provides a full list of the top 10 words from each of the discovered topics.}
@@
 To accomplish this, we used an optimization procedure that maximized the difference between the topic weights for timepoints within an event versus timepoints across multiple events (see \textit{Methods} for additional details).
-We then created a stable ``summary'' of the content within each video event by averaging the topic vectors across the timepoints spanned by each event (Fig.~\ref{fig:model}C).
+We then created a stable ``summary'' of the content within each episode event by averaging the topic vectors across the timepoints spanned by each event (Fig.~\ref{fig:model}C).
 
@@
 \caption{\small \textbf{Modeling naturalistic stimuli and recalls.} All panels: darker colors indicate greater values; range: [0, 1].
-\textbf{A.} Topic vectors ($K = 100$) for each of the 1976 video timepoints.
+\textbf{A.} Topic vectors ($K = 100$) for each of the 1976 episode timepoints.
 \textbf{B.} Timepoint-by-timepoint correlation matrix of the topic vectors displayed in Panel A.
 Event boundaries discovered by the HMM are denoted in yellow (30 events detected).
-\textbf{C.} Average topic vectors for each of the 30 video events.
-\textbf{D.} Topic vectors for each of 265 sliding windows of sentences spoken by an example participant while recalling the video.
+\textbf{C.} Average topic vectors for each of the 30 episode events.
+\textbf{D.} Topic vectors for each of 265 sliding windows of sentences spoken by an example participant while recalling the episode.
 \textbf{E.} Timepoint-by-timepoint correlation matrix of the topic vectors displayed in Panel D.
@@
 For similar plots for all participants, see Figure~\corrmats.
-\textbf{F.} Average topic vectors for each of the 22 recalled events from the example participant.
-\textbf{G.} Correlations between the topic vectors for every pair of video events (Panel C) and recalled events (from the example participant; Panel F).
+\textbf{F.} Average topic vectors for each of the 22 recall events from the example participant.
+\textbf{G.} Correlations between the topic vectors for every pair of episode events (Panel C) and recall events (from the example participant; Panel F).
 For similar plots for all participants, see Figure~\matchmats.
-\textbf{H.} Average correlations between each pair of video events and recalled events (across all 17 participants).
-To create the figure, each recalled event was assigned to the video event with the most correlated topic vector (yellow boxes in panels G and H).}
+\textbf{H.} Average correlations between each pair of episode events and recall events (across all 17 participants).
+To create the figure, each recalled event was assigned to the episode event with the most correlated topic vector (yellow boxes in panels G and H).}
 \label{fig:model}
@@
 
-Given that the time-varying content of the video could be segmented cleanly into discrete events, we wondered whether participants' recalls of the video also displayed a similar structure.
-We applied the same topic model (already trained on the video annotations) to each participant's recalls.
-Analogously to how we parsed the time-varying content of the video, to obtain similar estimates for each participant's recall, we treated each overlapping  window of (up to 10) sentences from their transcript as a ``document," and computed the most probable mix of topics reflected in each timepoint's sentences.
-This yielded, for each participant, a number-of-windows by number-of-topics topic proportions matrix that characterized how the topics identified in the original video were reflected in the participant's recalls.
-Note that an important feature of our approach is that it allows us to compare participants' recalls to events from the original video, despite different participants using widely varying language to describe the events, and that those descriptions often diverged in content and quality from the video annotations.
-This is a substantial benefit of projecting the video and recalls into a shared ``topic'' space.
+Given that the time-varying content of the episode could be segmented cleanly into discrete events, we wondered whether participants' recalls of the episode also displayed a similar structure.
+We applied the same topic model (already trained on the episode annotations) to each participant's recalls.
+Analogously to how we parsed the time-varying content of the episode, to obtain similar estimates for each participant's recall, we treated each overlapping  window of (up to 10) sentences from their transcript as a ``document," and computed the most probable mix of topics reflected in each timepoint's sentences.
+This yielded, for each participant, a number-of-windows by number-of-topics topic proportions matrix that characterized how the topics identified in the original episode were reflected in the participant's recalls.
+Note that an important feature of our approach is that it allows us to compare participants' recalls to events from the original episode, despite different participants using widely varying language to describe the events, and that those descriptions often diverged in content and quality from the episode annotations.
+This is a substantial benefit of projecting the episode and recalls into a shared ``topic'' space.
 An example topic proportions matrix from one participant's recalls is shown in Figure~\ref{fig:model}D.
 
-Although the example participant's recall topic proportions matrix has some visual similarity to the video topic proportions matrix, the time-varying topic proportions for the example participant's recalls are not as sparse as those for the video (compare Figs.~\ref{fig:model}A and D).
+Although the example participant's recall topic proportions matrix has some visual similarity to the episode topic proportions matrix, the time-varying topic proportions for the example participant's recalls are not as sparse as those for the episode (compare Figs.~\ref{fig:model}A and D).
 Similarly, although there do appear to be periods of stability in the recall topic dynamics (i.e., most topics are active or inactive over contiguous blocks of time), the changes in topic activations that define event boundaries appear less clearly delineated in participants' recalls than in the episode's annotations.
 To examine these patterns in detail, we computed the timepoint-by-timepoint correlation matrix for the example participant's recall trajectory (Fig.~\ref{fig:model}E).
-As in the video correlation matrix (Fig.~\ref{fig:model}B), the example participant's recall correlation matrix has a strong block diagonal structure, indicating that their recalls are discretized into separated events.
-As for the video correlation matrix, we leveraged an HMM-based optimization procedure (see \textit{Methods}) to determine how many events are reflected in the participant's recalls and where specifically the event boundaries fall (outlined in yellow).
+As in the episode correlation matrix (Fig.~\ref{fig:model}B), the example participant's recall correlation matrix has a strong block diagonal structure, indicating that their recalls are discretized into separated events.
+As for the episode correlation matrix, we leveraged an HMM-based optimization procedure (see \textit{Methods}) to determine how many events are reflected in the participant's recalls and where specifically the event boundaries fall (outlined in yellow).
 We carried out a similar analysis on all 17 participants' recall topic proportions matrices (Fig.~\corrmats).
@@
 While some participants' recall topic proportions segmented into just a few events (e.g., Participants P4, P5, and P7), others' segmented into many shorter duration events (e.g., Participants P12, P13, and P17).
-This suggests that different participants may be recalling the video with different levels of detail---i.e., some might touch on just the major plot points, whereas others might attempt to recall every minor scene or action.
-The second clear pattern present in every individual participant's recall correlation matrix was that, unlike in the video correlation matrix, there were substantial off-diagonal correlations.
-Whereas each event in the original video was (largely) separable from the others (Fig.~\ref{fig:model}B), in transforming those separable events into memory, participants appeared to be integrating across multiple events, blending elements of previously recalled and not-yet-recalled content into each newly recalled event~\citep[Figs.~\ref{fig:model}E, \corrmats; also see][]{MannEtal11, HowaEtal12, Mann19}.
+This suggests that different participants may be recalling the episode with different levels of detail---i.e., some might touch on just the major plot points, whereas others might attempt to recall every minor scene or action.
+The second clear pattern present in every individual participant's recall correlation matrix was that, unlike in the episode correlation matrix, there were substantial off-diagonal correlations.
+Whereas each event in the original episode was (largely) separable from the others (Fig.~\ref{fig:model}B), in transforming those separable events into memory, participants appeared to be integrating across multiple events, blending elements of previously recalled and not-yet-recalled content into each newly recalled event~\citep[Figs.~\ref{fig:model}E, \corrmats; also see][]{MannEtal11, HowaEtal12, Mann19}.
 
-The above results indicate that both the structure of the original video and participants' recalls of the video exhibit event boundaries that can be identified automatically by characterizing the dynamic content using a shared topic model and segmenting the content into events via HMMs.
-Next, we asked whether some correspondence might be made between the specific content of the events the participants experienced in the video, and the events they later recalled.
-One approach to linking the experienced (video) and recalled events is to label each recalled event as matching the video event with the most similar (i.e., most highly correlated) topic vector (Figs.~\ref{fig:model}G, \matchmats).
-This yields a sequence of ``presented" events from the original video, and a (potentially differently ordered) sequence of ``recalled" events for each participant.
+The above results indicate that both the structure of the original episode and participants' recalls of the episode exhibit event boundaries that can be identified automatically by characterizing the dynamic content using a shared topic model and segmenting the content into events via HMMs.
+Next, we asked whether some correspondence might be made between the specific content of the events the participants experienced in the episode, and the events they later recalled.
+One approach to linking the experienced (episode) and recalled events is to label each recalled event as matching the episode event with the most similar (i.e., most highly correlated) topic vector (Figs.~\ref{fig:model}G, \matchmats).
+This yields a sequence of ``presented" events from the original episode, and a (potentially differently ordered) sequence of ``recalled" events for each participant.
 Analogous to classic list-learning studies, we can then examine participants' recall sequences by asking which events they tended to recall first~\citep[probability of first recall; Fig.~\ref{fig:list-learning}A;][]{AtkiShif68, PostPhil65, WelcBurn24}; how participants most often transition between recalls of the events as a function of the temporal distance between them~\citep[lag-conditional response probability; Fig.~\ref{fig:list-learning}B;][]{Kaha96}; and which events they were likely to remember overall~\citep[serial position recall analyses; Fig.~\ref{fig:list-learning}C;][]{Murd62a}.
 Interestingly, for two of these analyses (probability of first recall and lag-conditional response probability curves) we observed patterns comparable to classic effects from list-learning literature: namely, a higher probability of initiating recall with the first event in the sequence (Fig.~\ref{fig:list-learning}A) and a higher probability of transitioning to neighboring events with an asymmetric forward bias (Fig.~\ref{fig:list-learning}B).
-In contrast, we did not observe a pattern comparable to the serial position effect (Fig.~\ref{fig:list-learning}C), but rather greater memory for specific events distributed approximately evenly throughout the video.
+In contrast, we did not observe a pattern comparable to the serial position effect (Fig.~\ref{fig:list-learning}C), but rather greater memory for specific events distributed approximately evenly throughout the episode.
 
 We can also apply two list-learning-native analyses that describe how participants group items in their recall sequences: temporal clustering and semantic clustering \citep[][see \textit{Methods} for details]{PolyEtal09}.~Temporal clustering refers to the extent to which participants group their recall responses according to encoding position.
-Overall, we found that sequentially viewed video events were clustered heavily in participants' recall event sequences (mean clustering score: 0.767, SEM: 0.029), and that participants with higher temporal clustering scores tended to perform better according to both \cite{ChenEtal17}'s hand-annotated memory scores (Pearson's $r(15) = 0.62,~p = 0.008$) and our model's estimate (Pearson's $r(15) = 0.54,~p = 0.024$).
+Overall, we found that sequentially viewed episode events were clustered heavily in participants' recall event sequences (mean clustering score: 0.767, SEM: 0.029), and that participants with higher temporal clustering scores tended to perform better according to both \cite{ChenEtal17}'s hand-annotated memory scores (Pearson's $r(15) = 0.62,~p = 0.008$) and our model's estimate (Pearson's $r(15) = 0.54,~p = 0.024$).
 Semantic clustering measures the extent to which participants cluster their recall responses according to semantic similarity.
-We found that participants tended to recall semantically similar video events together (mean clustering score: 0.787, SEM: 0.018), and that semantic clustering score was also related to both hand-annotated  (Pearson's $r(15) = 0.65,~p = 0.004$) and model-derived (Pearson's $r(15) = 0.63,~p = 0.007$) memory performance.
+We found that participants tended to recall semantically similar episode events together (mean clustering score: 0.787, SEM: 0.018), and that semantic clustering score was also related to both hand-annotated  (Pearson's $r(15) = 0.65,~p = 0.004$) and model-derived (Pearson's $r(15) = 0.63,~p = 0.007$) memory performance.
 % NOTE:
@@
   \includegraphics[width=1\textwidth]{figs/list_learning}
-  \caption{\small \textbf{Naturalistic extensions of classic list-learning memory analyses.} \textbf{A.} The probability of first recall as a function of the serial position of the event in the video.
+  \caption{\small \textbf{Naturalistic extensions of classic list-learning memory analyses.} \textbf{A.} The probability of first recall as a function of the serial position of the event in the episode.
 \textbf{B}.
-The probability of recalling each event, conditioned on having most recently recalled the event \textit{lag} events away in the video.
-\textbf{C.} The proportion of participants who recalled each event, as a function of the serial position of the events in the video.
+The probability of recalling each event, conditioned on having most recently recalled the event \textit{lag} events away in the episode.
+\textbf{C.} The proportion of participants who recalled each event, as a function of the serial position of the events in the episode.
 All panels: error ribbons denote bootstrap-estimated standard error of the mean.}
@@
   \includegraphics[width=1\textwidth]{figs/precision_distinctiveness}
-  \caption{\small \textbf{Novel content-based metrics of naturalistic memory: precision and distinctiveness.} \textbf{A.} The video-recall correlation matrix for a representative participant (17).
+  \caption{\small \textbf{Novel content-based metrics of naturalistic memory: precision and distinctiveness.} \textbf{A.} The episode-recall correlation matrix for a representative participant (17).
 The yellow boxes highlight the maximum correlation in each column.
@@
 \textbf{C.} The correlation between distinctiveness and hand-annotated memory performance.
-\textbf{D.} The correlation between precision and the number of video events successfully recalled, as determined by our model.
-\textbf{E.} The correlation between distinctiveness and the number of video events successfully recalled, as determined by our model.}
+\textbf{D.} The correlation between precision and the number of episode events successfully recalled, as determined by our model.
+\textbf{E.} The correlation between distinctiveness and the number of episode events successfully recalled, as determined by our model.}
   \label{fig:precision-distinctiveness}
@@
 Further, each remembering is itself a richly structured phenomenon.
-Our framework produces a content-based model of individual video and recall events by projecting the dynamic content of the video and participants' recalls into a shared topic space.
+Our framework produces a content-based model of individual episode and recall events by projecting the dynamic content of the episode and participants' recalls into a shared topic space.
 This allows for direct, quantitative comparisons between all stimulus and recall events, as well as between the recall events themselves.
@@
 Precision is intended to capture the ``completeness'' of recall, or how fully the presented content was recapitulated in memory.
-We define a recall event's precision as the maximum correlation between the topic proportions of that recall event and any video event (Fig.~\ref{fig:precision-distinctiveness}).
+We define a recall event's precision as the maximum correlation between the topic proportions of that recall event and any episode event (Fig.~\ref{fig:precision-distinctiveness}).
 A second novel metric we introduce here is \textit{distinctiveness}, which is intended to capture the ``specificity'' of recall.
 In other words, distinctiveness quantifies the extent to which a given recalled event reflects the most similar presented event moreso than it does other presented events.
-To compute a recall event's distinctiveness, we first identify the video event to which its topic vector is most strongly correlated.
-We then define distinctiveness as one minus the average correlation between the given recall event and all \textit{other} video events.
+To compute a recall event's distinctiveness, we first identify the episode event to which its topic vector is most strongly correlated.
+We then define distinctiveness as one minus the average correlation between the given recall event and all \textit{other} episode events.
 In addition to individual events, one may also use these metrics to describe each participant's overall performance by averaging across a participant's event-wise precision or distinctiveness scores.
-Participants whose recall events are more veridical descriptions of what happened in the video event will presumably have higher precision scores.
-We find that, across participants, higher precision scores are positively correlated with both hand-annotated memory performance (as collected by Chen et al., 2017; Pearson's $r(15) = 0.60, p = 0.010$) and the number of video events successfully remembered, as determined by our model (Pearson's $r(15) = 0.90, p < 0.001$).
+Participants whose recall events are more veridical descriptions of what happened in the episode event will presumably have higher precision scores.
+We find that, across participants, higher precision scores are positively correlated with both hand-annotated memory performance (as collected by Chen et al., 2017; Pearson's $r(15) = 0.60, p = 0.010$) and the number of episode events successfully remembered, as determined by our model (Pearson's $r(15) = 0.90, p < 0.001$).
 We also hypothesized that participants who recounted events in a more distinctive way would display better overall memory.
@@
   \includegraphics[width=1\textwidth]{figs/precision_detail}
-  \caption{\small \textbf{Precision metric reflects completeness of recall.} \textbf{A.} Recall precision by video event.
-Grey violin plots display kernel density estimates for the distribution of recall precision scores for a single video event.
+  \caption{\small \textbf{Precision metric reflects completeness of recall.} \textbf{A.} Recall precision by episode event.
+Grey violin plots display kernel density estimates for the distribution of recall precision scores for a single episode event.
 Colored dots within each violin plot represent individual participants' recall precision for the given event.
-Video events are ordered along the $x$-axis by the average precision with which they were remembered.
-\textbf{B.} The set of ``Narrative Details" video annotations (generated by \citealp{ChenEtal17}) for scenes comprising an example video event (22) identified by the HMM.
+episode events are ordered along the $x$-axis by the average precision with which they were remembered.
+\textbf{B.} The set of ``Narrative Details" episode annotations (generated by \citealp{ChenEtal17}) for scenes comprising an example episode event (22) identified by the HMM.
 Each action or feature is highlighted in a different color.
-\textbf{C.} A subset of the sentences comprising the most precise (P17) and least precise (P6) participants' recalls of video event 22.
+\textbf{C.} A subset of the sentences comprising the most precise (P17) and least precise (P6) participants' recalls of episode event 22.
 Descriptions of specific actions or features reflecting those highlighted in panel B are highlighted in the corresponding color.}
@@
   \includegraphics[width=1\textwidth]{figs/distinctiveness_detail}
-  \caption{\small \textbf{Distinctiveness metric reflects specificity of recall.} \textbf{A.} Recall distinctiveness by video event.
-Kernel density estimates for each video event's distribution of recall distinctiveness scores, analogous to Fig.~\ref{fig:precision-detail}A.
-\textbf{B.} The sets of ``Narrative Details" video annotations (generated by \citealp{ChenEtal17}) for scenes comprising video events described by the example participants in panel C.
+  \caption{\small \textbf{Distinctiveness metric reflects specificity of recall.} \textbf{A.} Recall distinctiveness by episode event.
+Kernel density estimates for each episode event's distribution of recall distinctiveness scores, analogous to Fig.~\ref{fig:precision-detail}A.
+\textbf{B.} The sets of ``Narrative Details" episode annotations (generated by \citealp{ChenEtal17}) for scenes comprising episode events described by the example participants in panel C.
 Each event's text is highlighted in a different color.
-\textbf{C.} The sentences comprising the most distinctive (P13) and least distinctive (P11) participants' recalls of video event 19.
-Sections of recall describing each each video event in panel B are highlighted with the corresponding color.}
+\textbf{C.} The sentences comprising the most distinctive (P13) and least distinctive (P11) participants' recalls of episode event 19.
+Sections of recall describing each each episode event in panel B are highlighted with the corresponding color.}
   \label{fig:distinctiveness-detail}
@@
 
-Further intuition for the behaviors captured by these two metrics may be gained by directly examining the content of the video and recalls our framework models.
-In Figure \ref{fig:precision-detail}, we contrast recalls for the same video event (event 22) from two participants: one with a high precision score (P17), the other with a low precision score (P6).
-From the HMM-identified event boundaries, we recovered the set of annotations describing the content of an example video event (Fig.~\ref{fig:precision-detail}B), and divided them into different color-coded sections for each action or feature described.
+Further intuition for the behaviors captured by these two metrics may be gained by directly examining the content of the episode and recalls our framework models.
+In Figure \ref{fig:precision-detail}, we contrast recalls for the same episode event (event 22) from two participants: one with a high precision score (P17), the other with a low precision score (P6).
+From the HMM-identified event boundaries, we recovered the set of annotations describing the content of an example episode event (Fig.~\ref{fig:precision-detail}B), and divided them into different color-coded sections for each action or feature described.
 We then similarly recovered the set of sentences comprising the corresponding recall event for each of the two example participants.
-Because the recall sliding windows overlap heavily, and each recall event spans multiple recall timepoints (i.e., windows), we have stripped any sentences from the beginning and end that describe earlier or later video events for the sake of readability.
-In other words, Fig.~\ref{fig:precision-detail}C shows a subset of the full recall event text, comprising sentences between the first and last descriptions of content from the example video event.
+Because the recall sliding windows overlap heavily, and each recall event spans multiple recall timepoints (i.e., windows), we have stripped any sentences from the beginning and end that describe earlier or later episode events for the sake of readability.
+In other words, Fig.~\ref{fig:precision-detail}C shows a subset of the full recall event text, comprising sentences between the first and last descriptions of content from the example episode event.
 We then colored all words describing actions and features coded in panel B by their corresponding color.
-Visual comparison of these example transcripts reveals that the more precise recall captures more of the video event's content, and with more detail.
+Visual comparison of these example transcripts reveals that the more precise recall captures more of the episode event's content, and with more detail.
 
-Figure \ref{fig:distinctiveness-detail} similarly contrasts two example participants' recalls for a common video event (event 19) to illustrate the tangible differences between high and low distinctiveness scores.
-Here, we have extracted the full set of sentences comprising the most distinctive recall event (P13) and least distinctive recall event (P11) matched to the example video event (Fig.~\ref{fig:distinctiveness-detail}C).
-We also extracted the annotations for the example video event, as well as those from each other video event whose content the example participants' single recall events described (Fig.~\ref{fig:distinctiveness-detail}B).
-We then shaded the annotation text for each video event with a different color, and shaded each word of the example participants' recall text by the color of the video event it describes.
-The majority of the most distinctive recall event text describes video event 19's content, with the first five and last one sentence describing the video events immediately preceding and succeeding the current one, respectively.
-In contrast, the least distinctive recall of video event 19 blends the content from five separate video events, does not transition between them in order, and often combines descriptions of two video events' content in the same sentence.
+Figure \ref{fig:distinctiveness-detail} similarly contrasts two example participants' recalls for a common episode event (event 19) to illustrate the tangible differences between high and low distinctiveness scores.
+Here, we have extracted the full set of sentences comprising the most distinctive recall event (P13) and least distinctive recall event (P11) matched to the example episode event (Fig.~\ref{fig:distinctiveness-detail}C).
+We also extracted the annotations for the example episode event, as well as those from each other episode event whose content the example participants' single recall events described (Fig.~\ref{fig:distinctiveness-detail}B).
+We then shaded the annotation text for each episode event with a different color, and shaded each word of the example participants' recall text by the color of the episode event it describes.
+The majority of the most distinctive recall event text describes episode event 19's content, with the first five and last one sentence describing the episode events immediately preceding and succeeding the current one, respectively.
+In contrast, the least distinctive recall of episode event 19 blends the content from five separate episode events, does not transition between them in order, and often combines descriptions of two episode events' content in the same sentence.
 
-The prior analyses leverage the correspondence between the 100-dimensional topic proportion matrices for the video and participants' recalls to characterize recall.
+The prior analyses leverage the correspondence between the 100-dimensional topic proportion matrices for the episode and participants' recalls to characterize recall.
 However, it is difficult to gain deep insights into the content of (or relationships between) experiences and memories solely by examining these topic proportions (e.g., Figs.~\ref{fig:model}A, D) or the corresponding correlation matrices (Figs.~\ref{fig:model}B, E, \corrmats).
@@
 To visualize the time-varying high-dimensional content in a more intuitive way~\citep{HeusEtal18a}, we projected the topic proportions matrices onto a two-dimensional space using Uniform Manifold Approximation and Projection~\citep[UMAP; ][]{McInEtal18}.
-In this lower-dimensional space, each point represents a single video or recall event, and the distances between the points reflect the distances between the events' associated topic vectors (Fig.~\ref{fig:trajectory}).
+In this lower-dimensional space, each point represents a single episode or recall event, and the distances between the points reflect the distances between the events' associated topic vectors (Fig.~\ref{fig:trajectory}).
 In other words, events that are nearer to each other in this space are more semantically similar, and those that are farther apart are less so.
@@
 \includegraphics[width=1\textwidth]{figs/trajectory}
-\caption{\small \textbf{Trajectories through topic space capture the dynamic content of the video and recalls.}  All panels: the topic proportion matrices have been projected onto a shared two-dimensional space using UMAP.
+\caption{\small \textbf{Trajectories through topic space capture the dynamic content of the episode and recalls.}  All panels: the topic proportion matrices have been projected onto a shared two-dimensional space using UMAP.
 \textbf{A.} The two-dimensional topic trajectory taken by the episode of \textit{Sherlock}.
@@
 \textbf{B.} The average two-dimensional trajectory captured by participants' recall sequences, with the same format and coloring as the trajectory in Panel A.
-To compute the event positions, we matched each recalled event with an event from the original video (see \textit{Results}), and then we averaged the positions of all events with the same label.
+To compute the event positions, we matched each recalled event with an event from the original episode (see \textit{Results}), and then we averaged the positions of all events with the same label.
 The arrows reflect the average transition direction through topic space taken by any participants whose trajectories crossed that part of topic space; blue denotes reliable agreement across participants via a Rayleigh test ($p < 0.05$, corrected).
 \textbf{C.} The recall topic trajectories (gray) taken by each individual participant (P1--P17).
-The video's trajectory is shown in black for reference.
-Here, events (dots) are colored by their matched video event (Panel A).}
+The episode's trajectory is shown in black for reference.
+Here, events (dots) are colored by their matched episode event (Panel A).}
 \label{fig:trajectory}
@@
 
-Visual inspection of the video and recall topic trajectories reveals a striking pattern.
-First, the topic trajectory of the video (which reflects its dynamic content; Fig.~\ref{fig:trajectory}A) is captured nearly perfectly by the averaged topic trajectories of participants' recalls (Fig.~\ref{fig:trajectory}B).
+Visual inspection of the episode and recall topic trajectories reveals a striking pattern.
+First, the topic trajectory of the episode (which reflects its dynamic content; Fig.~\ref{fig:trajectory}A) is captured nearly perfectly by the averaged topic trajectories of participants' recalls (Fig.~\ref{fig:trajectory}B).
 To assess the consistency of these recall trajectories across participants, we asked: given that a participant's recall trajectory had entered a particular location in the reduced topic space, could the position of their \textit{next} recalled event be predicted reliably?
@@
 Rayleigh tests revealed the set of locations in topic space at which these across-participant distributions exhibited reliable peaks (blue arrows in Fig.~\ref{fig:trajectory}B reflect significant peaks at $p < 0.05$, corrected).
-We observed that the locations traversed by nearly the entire video trajectory exhibited such peaks.
-In other words, participants exhibited similar trajectories that also matched the trajectory of the original video (Fig.~\ref{fig:trajectory}C).
-This is especially notable when considering the fact that the number of events participants recalled (dots in Fig.~\ref{fig:trajectory}C) varied considerably across people, and that every participant used different words to describe what they had remembered happening in the video.
+We observed that the locations traversed by nearly the entire episode trajectory exhibited such peaks.
+In other words, participants exhibited similar trajectories that also matched the trajectory of the original episode (Fig.~\ref{fig:trajectory}C).
+This is especially notable when considering the fact that the number of events participants recalled (dots in Fig.~\ref{fig:trajectory}C) varied considerably across people, and that every participant used different words to describe what they had remembered happening in the episode.
 Differences in the numbers of remembered events appear in participants' trajectories as differences in the sampling resolution along the trajectory.
-We note that this framework also provides a means of disentangling classic ``proportion recalled'' measures (i.e., the proportion of video events described in participants' recalls) from participants' abilities to recapitulate the overall unfolding of the original video's content (i.e., the similarity between the shapes of the original video trajectory and that defined by each participant's recounting of the video).
+We note that this framework also provides a means of disentangling classic ``proportion recalled'' measures (i.e., the proportion of episode events described in participants' recalls) from participants' abilities to recapitulate the overall unfolding of the original episode's content (i.e., the similarity between the shapes of the original episode trajectory and that defined by each participant's recounting of the episode).
 % ------ NOTE: ------
@@
 Given this, we next asked asked whether the events were generally remembered well or poorly tended to reflect particular content.
-Because our analysis framework projects the dynamic video content and participants' recalls into a shared space, and because the dimensions of that space represent topics (which are, in turn, sets of weights over known words in the vocabulary), we are able to recover the weighted combination of words that make up any point (i.e., topic vector) in this space.
-We first computed the average precision with which participants recalled each of the 30 video events (Fig.~\ref{fig:topics}A; note that this result is analogous to a serial position curve created from our continuous recall quality metric).
-We then computed a weighted average of the topic vectors for each video event, where the weights reflected how reliably each event was recalled.
+Because our analysis framework projects the dynamic episode content and participants' recalls into a shared space, and because the dimensions of that space represent topics (which are, in turn, sets of weights over known words in the vocabulary), we are able to recover the weighted combination of words that make up any point (i.e., topic vector) in this space.
+We first computed the average precision with which participants recalled each of the 30 episode events (Fig.~\ref{fig:topics}A; note that this result is analogous to a serial position curve created from our continuous recall quality metric).
+We then computed a weighted average of the topic vectors for each episode event, where the weights reflected how reliably each event was recalled.
 To visualize the result, we created a ``wordle'' image~\citep{MuelEtal18} where words weighted more heavily by better-remembered topics appear in a larger font (Fig.~\ref{fig:topics}B, green box).
-Across the full video, content that reflected topics necessary to convey the central focus of the video (e.g., the names of the two main characters, ``Sherlock'' and ``John,'' and the address of a major recurring location, ``221B Baker Street") were best remembered.
+Across the full episode, content that reflected topics necessary to convey the central focus of the episode (e.g., the names of the two main characters, ``Sherlock'' and ``John,'' and the address of a major recurring location, ``221B Baker Street") were best remembered.
 An analogous analysis revealed which themes were poorly remembered.
 Here in computing the weighted average over events' topic vectors, we weighted each event in \textit{inverse} proportion to how well it was remembered (Fig.~\ref{fig:topics}B, red box).
-The least well-remembered video content reflected information not necessary to later convey a general summary of the video, such as the proper names of relatively minor characters (e.g., ``Mike," ``Molly," and ``Lestrade") and locations (e.g., ``St.
+The least well-remembered episode content reflected information not necessary to later convey a general summary of the episode, such as the proper names of relatively minor characters (e.g., ``Mike," ``Molly," and ``Lestrade") and locations (e.g., ``St.
 Bartholomew's Hospital").
@@
 \includegraphics[width=1\textwidth]{figs/topics}
-\caption{\small \textbf{Language used in the most and least memorable events.} \textbf{A.} Average precision (video event-recall event topic vector correlation) across participants for each video event.
+\caption{\small \textbf{Language used in the most and least memorable events.} \textbf{A.} Average precision (episode event-recall event topic vector correlation) across participants for each episode event.
 Error bars denote bootstrap-derived across-participant 95\% confidence intervals.
 The stars denote the three best-remembered events (green) and worst-remembered events (red).
-\textbf{B.} Wordles comprising the top 200 highest-weighted words reflected in the weighted-average topic vector across video events.
-Green: video events were weighted by how well the topic vectors derived from recalls of those events matched the video events' topic vectors (Panel A).
-Red: video events were weighted by the inverse of how well their topic vectors matched the recalled topic vectors.
-\textbf{C.}  The set of all video and recall events is projected onto the two-dimensional space derived in Figure~\ref{fig:trajectory}.
-The dots outlined in black denote video events (dot size reflects the average correlation between the video event's topic vector and the topic vectors from the closest matching recalled events from each participant; bigger dots denote stronger correlations).
+\textbf{B.} Wordles comprising the top 200 highest-weighted words reflected in the weighted-average topic vector across episode events.
+Green: episode events were weighted by how well the topic vectors derived from recalls of those events matched the episode events' topic vectors (Panel A).
+Red: episode events were weighted by the inverse of how well their topic vectors matched the recalled topic vectors.
+\textbf{C.}  The set of all episode and recall events is projected onto the two-dimensional space derived in Figure~\ref{fig:trajectory}.
+The dots outlined in black denote episode events (dot size reflects the average correlation between the episode event's topic vector and the topic vectors from the closest matching recalled events from each participant; bigger dots denote stronger correlations).
 The dots without black outlines denote recalled events.
@@
 Wordles for several example events are displayed (green: three best-remembered events; red: three worst-remembered events).
-Within each circular wordle, the left side displays words associated with the topic vector for the video event, and the right side displays words associated with the (average) recall event topic vector, across all recall events matched to the given video event.}
+Within each circular wordle, the left side displays words associated with the topic vector for the episode event, and the right side displays words associated with the (average) recall event topic vector, across all recall events matched to the given episode event.}
 \label{fig:topics}
@@
 
-A similar result emerged from assessing the topic vectors for individual video and recall events (Fig.~\ref{fig:topics}C).
-Here, for each of the three best- and worst-remembered video events, we have constructed two wordles: one from the original video event's topic vector (left) and a second from the average recall topic vector for that event (right).
+A similar result emerged from assessing the topic vectors for individual episode and recall events (Fig.~\ref{fig:topics}C).
+Here, for each of the three best- and worst-remembered episode events, we have constructed two wordles: one from the original episode event's topic vector (left) and a second from the average recall topic vector for that event (right).
 The three best-remembered events (circled in green) correspond to scenes integral to the central plot-line: a mysterious figure spying on John in a phone booth; John meeting Sherlock at Baker St.
@@
 We next carried out a series of analyses aimed at understanding which brain structures might facilitate these preservations and transformations between the external world and memory.
-In the first analysis, we sought to identify brain structures that were sensitive to the dynamic unfolding of the video's content, as characterized by its topic trajectory.
-We used a searchlight procedure to identify clusters of voxels whose activity patterns displayed a proximal temporal correlation structure (as participants watched the video) matching that of the original video's topic proportions (Fig.~\ref{fig:brainz}A; see \textit{Methods} for additional details).
-In a second analysis, we sought to identify brain structures whose responses (during video viewing) reflected how each participant would later structure their recounting of the video.
+In the first analysis, we sought to identify brain structures that were sensitive to the dynamic unfolding of the episode's content, as characterized by its topic trajectory.
+We used a searchlight procedure to identify clusters of voxels whose activity patterns displayed a proximal temporal correlation structure (as participants watched the episode) matching that of the original episode's topic proportions (Fig.~\ref{fig:brainz}A; see \textit{Methods} for additional details).
+In a second analysis, we sought to identify brain structures whose responses (during episode viewing) reflected how each participant would later structure their recounting of the episode.
 We used an analogous searchlight procedure to identify clusters of voxels whose proximal temporal correlation matrices matched that of the topic proportions for each individual's recall (Figs.~\ref{fig:brainz}B; see \textit{Methods} for additional details).
-To ensure our searchlight procedure identified regions \textit{specifically} sensitive to the temporal structure of the video or recalls (i.e., rather than those with a temporal autocorrelation length similar to that of the video/recalls), we performed a phase shift-based permutation correction (see \textit{Methods} for additional details).
-As shown in Figure~\ref{fig:brainz}C, the video-driven searchlight analysis revealed a distributed network of regions that may play a role in processing information relevant to the narrative structure of the video.
+To ensure our searchlight procedure identified regions \textit{specifically} sensitive to the temporal structure of the episode or recalls (i.e., rather than those with a temporal autocorrelation length similar to that of the episode/recalls), we performed a phase shift-based permutation correction (see \textit{Methods} for additional details).
+As shown in Figure~\ref{fig:brainz}C, the episode-driven searchlight analysis revealed a distributed network of regions that may play a role in processing information relevant to the narrative structure of the episode.
 Similarly, the recall-driven searchlight analysis revealed a second network of regions (Fig.~\ref{fig:brainz}D) that may facilitate a person-specific transformation of one's experience into memory.
@@
 \includegraphics[width=1\textwidth]{figs/searchlights}
-\caption{\small \textbf{Brain structures that underlie the transformation of experience into memory.} \textbf{A.} We isolated the proximal diagonals from the upper triangle of the video correlation matrix, and applied this same diagonal mask to the voxel response correlation matrix for each cube of voxels in the brain.
-We then searched for brain regions whose activation timeseries consistently exhibited a similar proximal correlational structure to the video model, across participants.
-\textbf{B.} We used dynamic time warping \citep{BernClif94} to align each participant's recall timeseries to the TR timeseries of the video.
+\caption{\small \textbf{Brain structures that underlie the transformation of experience into memory.} \textbf{A.} We isolated the proximal diagonals from the upper triangle of the episode correlation matrix, and applied this same diagonal mask to the voxel response correlation matrix for each cube of voxels in the brain.
+We then searched for brain regions whose activation timeseries consistently exhibited a similar proximal correlational structure to the episode model, across participants.
+\textbf{B.} We used dynamic time warping \citep{BernClif94} to align each participant's recall timeseries to the TR timeseries of the episode.
 We then applied the same diagonal mask used in Panel A to isolate the proximal temporal correlations and searched for brain regions whose activation timeseries for an individual consistently exhibited a similar proximal correlational structure to each individual's recall.
@@
 \textbf{D}.
-We also identified a network or regions sensitive to how individuals would later structure the video's content in their recalls.
+We also identified a network or regions sensitive to how individuals would later structure the episode's content in their recalls.
 The map shown is thresholded at at $p < 0.05$, corrected.}
@@
 
-The searchlight analyses described above yielded two distributed networks of brain regions, whose activity timecourses mirrored to the temporal structure of the video (Fig.~\ref{fig:brainz}C) or participants' eventual recalls (Fig.~\ref{fig:brainz}D).
+The searchlight analyses described above yielded two distributed networks of brain regions, whose activity timecourses mirrored to the temporal structure of the episode (Fig.~\ref{fig:brainz}C) or participants' eventual recalls (Fig.~\ref{fig:brainz}D).
 We next sought to gain greater insight into the structures and functional networks our results reflected.
@@
 Given an arbitrary statistical map as input, \texttt{Neurosynth} performs a massive automated meta-analysis, returning a ranked list of terms reported in papers with similar significance maps.
-We ran \texttt{Neurosynth} on the significance maps for the video- and recall-driven searchlight analyses.
+We ran \texttt{Neurosynth} on the significance maps for the episode- and recall-driven searchlight analyses.
 These maps, along with the 10 terms with maximally similar meta-analysis images identified by \texttt{Neurosynth} are shown in Figure \ref{fig:neurosynth}.
@@
 \includegraphics[width=1\textwidth]{figs/neurosynth_decoding}
-\caption{\small \textbf{Decoding distributed statistical maps via Neurosynth meta-analyses.} \textbf{A.} Video-searchlight significance and top 10 decoded terms.
-We constructed a map of the permutation-derived $p$-values for the video-driven searchlight analysis (Fig.~\ref{fig:brainz}A, C) at each voxel with a positive permutation-derived $z$-score.
+\caption{\small \textbf{Decoding distributed statistical maps via Neurosynth meta-analyses.} \textbf{A.} episode-searchlight significance and top 10 decoded terms.
+We constructed a map of the permutation-derived $p$-values for the episode-driven searchlight analysis (Fig.~\ref{fig:brainz}A, C) at each voxel with a positive permutation-derived $z$-score.
 The top 10 terms decoded from this significance map are shown in red.
@@
 So called \textit{inter-subject correlation} (ISC) and \textit{inter-subject functional connectivity} (ISFC) analyses effectively treat other people's brain responses to the stimulus as a ``model'' of how its features change over time.
-By contrast, in our present work, we use topic models to construct an explicit content model directly from the stimulus (i.e., the topic trajectory of the video).
+By contrast, in our present work, we use topic models to construct an explicit content model directly from the stimulus (i.e., the topic trajectory of the episode).
 Projecting each participant's recall into a space shared by both the stimulus and other participants then allows us to compare recalls both directly to the stimulus and to each other.
 Similarly, prior work introducing the use of HMMs to discover latent event structure in naturalistic stimuli and recall \citep{BaldEtal17} used between-subjects cross-validation to identify event boundaries shared across participants, and between stimulus and recall.
-Our framework allows us to break from the restriction of a common, shared event-timeseries and identify the unique \textit{resolution} of each participant's recall event structure, and how that may differ from the video and that of other participants.
+Our framework allows us to break from the restriction of a common, shared event-timeseries and identify the unique \textit{resolution} of each participant's recall event structure, and how that may differ from the episode and that of other participants.
 % @JEREMY @ANDY PLEASE CHECK THIS TO MAKE SURE I'M NOT MISCHARACTERIZING BALDETAL17
@@
 More recent work on these types of semantic models, including word2vec~\citep{MikoEtal13}, the Universal Sentence Encoder~\citep{CerEtal18}, GPT-2~\citep{RadfEtal19}, and GTP-3~\citep{BrowEtal20} use deep neural networks to attempt to identify the deeper conceptual representations underlying each word.
-Despite the growing popularity of more sophisticated deep learning-based embedding models, here we leverage latent dirichlet allocation (i.e., topic modelling) to embed video and recall text.
+Despite the growing popularity of more sophisticated deep learning-based embedding models, here we leverage latent dirichlet allocation (i.e., topic modeling) to embed episode and recall text.
 This decision was motivated by several factors.
@@
 Moreover, many of the aspects of our framework could be swapped out for other choices.
-For example, the language model, the timeseries segmentation model and the video-recall matching function could all be customized to suit a particular question space or application.
+For example, the language model, the timeseries segmentation model and the episode-recall matching function could all be customized to suit a particular question space or application.
 Indeed for some questions, recovery of the particular words used to describe a memory may not be necessary, and thus other text-modeling approaches (including the deep learning-based embedding models described above) may be preferable.
@@
 
-In extending classical free recall analyses to our naturalistic memory framework, we recovered two patterns of recall dynamics central to list-learning studies: a heightened probability of initiating recall with the first presented ``item" (in our case, video events; Fig.~\ref{fig:list-learning}A) and a strong bias toward transitioning from recalling a given event to recalling the one immediately following it (Fig.~\ref{fig:list-learning}B).
+In extending classical free recall analyses to our naturalistic memory framework, we recovered two patterns of recall dynamics central to list-learning studies: a heightened probability of initiating recall with the first presented ``item" (in our case, episode events; Fig.~\ref{fig:list-learning}A) and a strong bias toward transitioning from recalling a given event to recalling the one immediately following it (Fig.~\ref{fig:list-learning}B).
 However, equally noteworthy are the typical free recall results \textit{not} recovered in these analyses, as each highlights a fundamental difference between the list-learning paradigm and naturalistic memory paradigms like the one employed in the present study.
-The most noticeable departure from hallmark free recall dynamics in these findings is the apparent lack of a serial position effect in Figure \ref{fig:list-learning}C, which instead shows greater and lesser recall probabilities for events distributed across the video.
+The most noticeable departure from hallmark free recall dynamics in these findings is the apparent lack of a serial position effect in Figure \ref{fig:list-learning}C, which instead shows greater and lesser recall probabilities for events distributed across the episode.
 Stimuli in free recall experiments most often comprise lists of simple, common words, presented to participants in a random order.
@@
 The second novel metric we introduce (\textit{distinctiveness}) is based on analyzing of the correlational structure of an individual's full set of recall events, and reflects the specificity of their memory for a single experienced event.
-We find that both of these metrics relate to the overall number of video events participants successfully recalled, and that our precision metric additionally relates to \cite{ChenEtal17}'s hand-annotated memory memory scores.
+We find that both of these metrics relate to the overall number of episode events participants successfully recalled, and that our precision metric additionally relates to \cite{ChenEtal17}'s hand-annotated memory memory scores.
 
@@
 In other words, both an extensive description of a scene's content and a brief mention of some subset of its content were (binarily) considered equally successful recalls.
-By contrast, we identify the event structure in participants' recalls in an unsupervised manner, independent of the video event-timeseries, prior to mapping between video and recall content.
+By contrast, we identify the event structure in participants' recalls in an unsupervised manner, independent of the episode event-timeseries, prior to mapping between episode and recall content.
 Our HMM-based event-segmentation produces boundaries between timepoints where the topic proportions shift in a substantial way, and because a small handful of words is unlikely to contribute significantly to the topic proportions for any sliding window, such brief scene descriptions will most often not result in a sufficiently large shift in the resulting topic proportions for the HMM to identify an event boundary.
@@
 
-In the analyses outlined in Figure \ref{fig:brainz}, we identified two networks of brain regions whose responses during video viewing were consistent with the temporal structure of the video and recall topic trajectories, respectively.
-The network identified by the video trajectory analysis included the ventromedial prefrontal cortex, left anterior temporal lobe, superior parietal and dorsal anterior cingulate cortex.
-The network from the video-recall trajectory analysis also included the ventromedial prefrontal and superior parietal cortices, in addition to the posterior medial cortex (PMC) and the inferior temporal regions.
+In the analyses outlined in Figure \ref{fig:brainz}, we identified two networks of brain regions whose responses during episode viewing were consistent with the temporal structure of the episode and recall topic trajectories, respectively.
+The network identified by the episode trajectory analysis included the ventromedial prefrontal cortex, left anterior temporal lobe, superior parietal and dorsal anterior cingulate cortex.
+The network from the episode-recall trajectory analysis also included the ventromedial prefrontal and superior parietal cortices, in addition to the posterior medial cortex (PMC) and the inferior temporal regions.
 Notably, \cite{ChenEtal17} also observed the PMC in a number of analyses including one that searched for regions whose activity patterns during encoding were reinstated during free recall.
@@
 Further, the PMC is part of the "posterior medial" system, a network of brain regions thought to represent situation models~\citep{ZackEtal07} in support of memory, spatial navigation and social cognition~\citep{RangRitc12}.
-Given that we constructed our video-recall searchlight model to capture temporal structure in the episode's semantic content (and how one's later recall aligns with that structure), we speculate that the PMC may play a role in constructing mnemonic events from meaningfully structured experiences.
+Given that we constructed our episode-recall searchlight model to capture temporal structure in the episode's semantic content (and how one's later recall aligns with that structure), we speculate that the PMC may play a role in constructing mnemonic events from meaningfully structured experiences.
 
 Decoding the associated significance maps with \texttt{Neurosynth} revealed two intriguing results.
-First, the top 10 terms returned for the video-driven searchlight significance map were centered around themes of language and semantic meaning (Fig.~\ref{fig:neurosynth}A).
-In other words, the voxels identified as more reflective of the video content's temporal structure (i.e., voxels with lower permutation correction-derived $p$-values), as defined by our model, were most likely to be reported as active in studies focused on the the neural underpinnings of semantic processing.
-This finding is interesting, as our model specifically captures the temporal structure of the video's \textit{semantic} content (e.g., as opposed to that of the visual, auditory, or affective content).
+First, the top 10 terms returned for the episode-driven searchlight significance map were centered around themes of language and semantic meaning (Fig.~\ref{fig:neurosynth}A).
+In other words, the voxels identified as more reflective of the episode content's temporal structure (i.e., voxels with lower permutation correction-derived $p$-values), as defined by our model, were most likely to be reported as active in studies focused on the the neural underpinnings of semantic processing.
+This finding is interesting, as our model specifically captures the temporal structure of the episode's \textit{semantic} content (e.g., as opposed to that of the visual, auditory, or affective content).
 This suggests that the network of structures displayed in Figure \ref{fig:brainz}C may play a roll in processing the evolving semantic content of ongoing experiences.
 
-Our second searchlight analysis identified a partially overlapping network of regions (Fig.~\ref{fig:brainz}D) whose patterns of activity as participants viewed the video reflected the idiosyncratic structure of each individual's later recalls.
+Our second searchlight analysis identified a partially overlapping network of regions (Fig.~\ref{fig:brainz}D) whose patterns of activity as participants viewed the episode reflected the idiosyncratic structure of each individual's later recalls.
 The associated significance map yielded a set of \texttt{Neurosynth} terms that primarily reflected names of specific structural regions (such as ``thalamus," ``anterior insula," ``anterior cingulate" and ``inferior frontal"; Fig.~\ref{fig:neurosynth}B).
@@
 After preprocessing the fMRI data and warping the images into a standard (3~mm$^3$ MNI) space, the voxel activations were $z$-scored (within voxel) and spatially smoothed using a 6~mm (full width at half maximum) Gaussian kernel.
-The fMRI data were also cropped so that all video-viewing data were aligned across participants.
+The fMRI data were also cropped so that all episode-viewing data were aligned across participants.
 This included a constant 3 TR (4.5~s) shift to account for the lag in the hemodynamic response.
@@
 All statistical tests performed in the neural data analyses were two-sided, except for the permutation-based thresholding, which was one-sided.
-In this case, we were specifically interested in identifying voxels whose activation time series reflected the temporal structure of the video and recall trajectories to a \textit{greater} extent than that of the phase-shifted trajectories.
+In this case, we were specifically interested in identifying voxels whose activation time series reflected the temporal structure of the episode and recall trajectories to a \textit{greater} extent than that of the phase-shifted trajectories.
 % ------ NOTE: ------
@@
 
-\subsection*{Modeling the dynamic content of the video and recall transcripts}
+\subsection*{Modeling the dynamic content of the episode and recall transcripts}
 \subsubsection*{Topic modeling}
-The input to the topic model we trained to characterize the dynamic content of the video comprised 998 hand-generated annotations of short (mean: 2.96s) scenes spanning the video clip~(\citealp{ChenEtal17} generated 1000 annotations total; we removed two annotations referring to a break between the first and second scan sessions, during which no fMRI data was collected).
+The input to the topic model we trained to characterize the dynamic content of the episode comprised 998 hand-generated annotations of short (mean: 2.96s) scenes spanning the video clip~(\citealp{ChenEtal17} generated 1000 annotations total; we removed two annotations referring to a break between the first and second scan sessions, during which no fMRI data was collected).
 We concatenated the text for all of the annotated features within each segment, creating a ``bag of words'' describing each scene and performed some minor preprocessing (e.g., stemming possessive nouns and removing punctuation).
@@
 In other words, we estimated the ``context'' for each scene using the text descriptions of the preceding 25 scenes, the present scene, and the following 24 scenes.
-To model the context for scenes near the beginning of the video (i.e., within 25 scenes of the beginning or end), we created overlapping sliding windows that grew in size from one scene to the full length.
-We also tapered the sliding window lengths at the end of the video, whereby scenes within fewer than 24 scenes of the end of the video were assigned sliding windows that extended to the end of the video.
+To model the context for scenes near the beginning of the episode (i.e., within 25 scenes of the beginning or end), we created overlapping sliding windows that grew in size from one scene to the full length.
+We also tapered the sliding window lengths at the end of the episode, whereby scenes within fewer than 24 scenes of the end of the episode were assigned sliding windows that extended to the end of the episode.
 This procedure ensured that each scene's content was represented in the text corpus an equal number of times.
@@
 
-We created similar topic proportions matrices using hand-annotated transcripts of each participant's verbal recall of the video~\citep[annotated by][]{ChenEtal17}.
-We tokenized the transcript into a list of sentences, and then re-organized the list into overlapping sliding windows spanning (up to) 10 sentences each, analogously to how we parsed the video annotations.
-In turn, we transformed each window's sentences into a word count vector (using the same vocabulary as for the video model), and then we used the topic model already trained on the video scenes to compute the most probable topic proportions for each sliding window.
+We created similar topic proportions matrices using hand-annotated transcripts of each participant's verbal recall of the episode~\citep[annotated by][]{ChenEtal17}.
+We tokenized the transcript into a list of sentences, and then re-organized the list into overlapping sliding windows spanning (up to) 10 sentences each, analogously to how we parsed the episode annotations.
+In turn, we transformed each window's sentences into a word count vector (using the same vocabulary as for the episode model), and then we used the topic model already trained on the episode scenes to compute the most probable topic proportions for each sliding window.
 This yielded a number-of-windows (range: 83--312) by number-of-topics (100) topic proportions matrix for each participant.
 These reflected the dynamic content of each participant's recalls.
-Note: for details on how we selected the video and recall window lengths and number of topics, see \textit{Supporting Information} and Figure~\topicopt.
+Note: for details on how we selected the episode and recall window lengths and number of topics, see \textit{Supporting Information} and Figure~\topicopt.
 
 \subsubsection*{Parsing topic trajectories into events using Hidden Markov Models}
-We parsed the topic trajectories of the video and participants' recalls into events using Hidden Markov Models~\citep[HMMs;][]{Rabi89}.
+We parsed the topic trajectories of the episode and participants' recalls into events using Hidden Markov Models~\citep[HMMs;][]{Rabi89}.
 Given the topic proportions matrix (describing the mix of topics at each timepoint) and a number of states, $K$, an HMM recovers the set of state transitions that segments the timeseries into $K$ discrete states.
@@
 Prior studies on narrative structure and processing have shown that we both perceive and internally represent the world around us at multiple, hierarchical timescales \citep[e.g.,][]{HassEtal08, LernEtal11, HassEtal15, ChenEtal17, BaldEtal17, BaldEtal18}.
-However, for the purposes of our framework, we sought to identify the single timeseries of event-representations that is emphasized \textit{most heavily} in the temporal structure of the video and of each participant's recall.
+However, for the purposes of our framework, we sought to identify the single timeseries of event-representations that is emphasized \textit{most heavily} in the temporal structure of the episode and of each participant's recall.
 We quantified this as the set of $K$ states that maximized the similarity between topic vectors for timepoints comprising each state, while minimizing the similarity between topic vectors for timepoints across different states.
@@
 We computed the first Wasserstein distance ($W_{1}$; also known as \textit{Earth mover's distance}; \citealp{Dobr70, RamdEtal17}) between these distributions for a large range of possible $K$-values (range [2, 50]), and selected the $K$ that yielded the maximum value.
-Figure~\ref{fig:model}B displays the event boundaries returned for the video, and Figure~\corrmats~displays the event boundaries returned for each participant's recalls.
-See Figure \kopt~for the optimization functions for the video and recalls.
+Figure~\ref{fig:model}B displays the event boundaries returned for the episode, and Figure~\corrmats~displays the event boundaries returned for each participant's recalls.
+See Figure \kopt~for the optimization functions for the episode and recalls.
 After obtaining these event boundaries, we created stable estimates of the content represented in each event by averaging the topic vectors across timepoints between each pair of event boundaries.
-This yielded a number-of-events by number-of-topics matrix for the video and recalls from each participant.
+This yielded a number-of-events by number-of-topics matrix for the episode and recalls from each participant.
 
@@
 In traditional list-learning experiments, participants view a list of items (e.g., words) and then recall the items later.
-Our video-recall event matching approach affords us the ability to analyze memory in a similar way.
-The video and recall events can be treated analogously to studied and recalled ``items'' in a list-learning study.
-We can then extend classic analyses of memory performance and dynamics (originally designed for list-learning experiments) to the more naturalistic video recall task used in this study.
+Our episode-recall event matching approach affords us the ability to analyze memory in a similar way.
+The episode and recall events can be treated analogously to studied and recalled ``items'' in a list-learning study.
+We can then extend classic analyses of memory performance and dynamics (originally designed for list-learning experiments) to the more naturalistic episode recall task used in this study.
 
-Perhaps the simplest and most widely used measure of memory performance is \textit{accuracy}---i.e., the proportion of studied (experienced) items (in this case, video events) that the participant later remembered.
+Perhaps the simplest and most widely used measure of memory performance is \textit{accuracy}---i.e., the proportion of studied (experienced) items (in this case, episode events) that the participant later remembered.
 \cite{ChenEtal17} used this method to rate each participant's memory quality by computing the proportion of (50, manually identified) scenes mentioned in their recall.
-We found a strong across-participants correlation between these independent ratings and the proportion of 30 HMM-identified video events matched to participants' recalls (Pearson's $r(15) = 0.71, p = 0.002$).
+We found a strong across-participants correlation between these independent ratings and the proportion of 30 HMM-identified episode events matched to participants' recalls (Pearson's $r(15) = 0.71, p = 0.002$).
 We further considered a number of more nuanced memory performance measures that are typically associated with list-learning studies.
@@
 \paragraph{Probability of first recall (PFR).}  PFR curves~\citep{WelcBurn24, PostPhil65, AtkiShif68} reflect the probability that an item will be recalled first as a function of its serial position during encoding.
-To carry out this analysis, we initialized a number-of-participants (17) by number-of-video-events (30) matrix of zeros.
-Then for each participant, we found the index of the video event that was recalled first (i.e., the video event whose topic vector was most strongly correlated with that of the first recall event) and filled in that index in the matrix with a 1.
-Finally, we averaged over the rows of the matrix, resulting in a 1 by 30 array representing the proportion of participants that recalled an event first, as a function of the order of the event's appearance in the video (Fig.~\ref{fig:list-learning}A).
+To carry out this analysis, we initialized a number-of-participants (17) by number-of-episode-events (30) matrix of zeros.
+Then for each participant, we found the index of the episode event that was recalled first (i.e., the episode event whose topic vector was most strongly correlated with that of the first recall event) and filled in that index in the matrix with a 1.
+Finally, we averaged over the rows of the matrix, resulting in a 1 by 30 array representing the proportion of participants that recalled an event first, as a function of the order of the event's appearance in the episode (Fig.~\ref{fig:list-learning}A).
 % ------ NOTE: ------
@@
 \paragraph{Serial position curve (SPC).} SPCs~\citep{Murd62a} reflect the proportion of participants that remember each item as a function of the items' serial positions during encoding.
-We initialized a number-of-participants (17) by number-of-video-events (30) matrix of zeros.
-Then, for each recalled event, for each participant, we found the index of the video event that the recalled event most closely matched (via the correlation between the events' topic vectors) and entered a 1 into that position in the matrix.
+We initialized a number-of-participants (17) by number-of-episode-events (30) matrix of zeros.
+Then, for each recalled event, for each participant, we found the index of the episode event that the recalled event most closely matched (via the correlation between the events' topic vectors) and entered a 1 into that position in the matrix.
 This resulted in a matrix whose entries indicated whether or not each event was recalled by each participant (depending on whether the corresponding entires were set to one or zero).
-Finally, we averaged over the rows of the matrix to yield a 1 by 30 array representing the proportion of participants that recalled each event as a function of the events' order appearance in the video (Fig.~\ref{fig:list-learning}C).
+Finally, we averaged over the rows of the matrix to yield a 1 by 30 array representing the proportion of participants that recalled each event as a function of the events' order appearance in the episode (Fig.~\ref{fig:list-learning}C).
 
 \paragraph{Temporal clustering scores.} Temporal clustering describes a participant's tendency to organize their recall sequences by the learned items' encoding positions.
-For instance, if a participant recalled the video events in the exact order they occurred (or in exact reverse order), this would yield a score of 1.
+For instance, if a participant recalled the episode events in the exact order they occurred (or in exact reverse order), this would yield a score of 1.
 If a participant recalled the events in random order, this would yield an expected score of 0.5.
-For each recall event transition (and separately for each participant), we sorted all not-yet-recalled events according to their absolute lag (i.e., distance away in the video).
+For each recall event transition (and separately for each participant), we sorted all not-yet-recalled events according to their absolute lag (i.e., distance away in the episode).
 We then computed the percentile rank of the next event the participant recalled.
@@
 Thus, the similarity between the semantic content for two events can be computed by correlating their respective topic vectors.
-For each recall event transition, we sorted all not-yet-recalled events according to how correlated the topic vector \textit{of the closest-matching video event} was to the topic vector of the closest-matching video event to the just-recalled event.
+For each recall event transition, we sorted all not-yet-recalled events according to how correlated the topic vector \textit{of the closest-matching episode event} was to the topic vector of the closest-matching episode event to the just-recalled event.
 We then computed the percentile rank of the observed next recall.
@@
 
-% To quantify the similarity between the video topic trajectory and individual recall topic trajectories, we considered several novel metrics.
-First, we tested whether each participant's recall trajectory matched the video trajectory in a general sense.
-For each participant, we filtered the video trajectory to only include the events that the participant remembered.
-We then computed the root mean squared difference (RMSD) between the remaining video events and the (closest-matching) recalled events.
-For example, if the topic vectors for a participant's recall event topic vectors matched the corresponding video event topic vectors exactly (and in order), the expected RMSD for those events would be 0.
-However, if the participant's recall events did not perfectly match the video events, or if they were out of order, then the RMSD would be greater than 0.
-To assess the significance of the match between the video and recall trajectories, we carried out a permutation procedure whereby, for each of 10000 repetitions, we circularly shifted the recall trajectories (in time) by a random amount and then re-computed the RMSD each time.
+% To quantify the similarity between the episode topic trajectory and individual recall topic trajectories, we considered several novel metrics.
+First, we tested whether each participant's recall trajectory matched the episode trajectory in a general sense.
+For each participant, we filtered the episode trajectory to only include the events that the participant remembered.
+We then computed the root mean squared difference (RMSD) between the remaining episode events and the (closest-matching) recalled events.
+For example, if the topic vectors for a participant's recall event topic vectors matched the corresponding episode event topic vectors exactly (and in order), the expected RMSD for those events would be 0.
+However, if the participant's recall events did not perfectly match the episode events, or if they were out of order, then the RMSD would be greater than 0.
+To assess the significance of the match between the episode and recall trajectories, we carried out a permutation procedure whereby, for each of 10000 repetitions, we circularly shifted the recall trajectories (in time) by a random amount and then re-computed the RMSD each time.
 This yielded a distribution of ``null'' RMSD values for each participant.
@@
 (For the remaining participants this test yielded $0.05 \leq p < 0.25$.)  The observed RMSD values were also reliably correlated with hand-annotated memory performance across participants (Pearson's $r(15) = -0.57, p = 0.016$).
-In other words, a closer match between the video and recall topic trajectories was related to better overall recall performance.
+In other words, a closer match between the episode and recall topic trajectories was related to better overall recall performance.
 % ------ NOTE: ------
@@
 We tested whether participants who recalled more events were also more \textit{precise} in their recollections.
-For each participant, we computed the average correlation between the topic vectors for each recall event and those of its closest-matching video event.
+For each participant, we computed the average correlation between the topic vectors for each recall event and those of its closest-matching episode event.
 This gave a single value per participant representing the average precision across all recalled events.
-We then correlated these values with both hand-annotated and model-derived (i.e., the number of unique video events matched by a participant's recall events) memory performance.
+We then correlated these values with both hand-annotated and model-derived (i.e., the number of unique episode events matched by a participant's recall events) memory performance.
 
@@
 We also considered the \textit{distinctiveness} of each recalled event.
-That is, how unique a participant's description of a video event was, versus their descriptions of other video events.
+That is, how unique a participant's description of a episode event was, versus their descriptions of other episode events.
 We hypothesized that participants with high memory performance might describe each event in a more distinctive way (relative to those with lower memory performance who might describe events in a more general way).
@@
 
-\subsubsection*{Visualizing the video and recall topic trajectories}
+\subsubsection*{Visualizing the episode and recall topic trajectories}
 We used the UMAP algorithm~\citep{McInEtal18} to project the 100-dimensional topic space onto a two-dimensional space for visualization (Figs.~\ref{fig:trajectory}, \ref{fig:topics}).
-To ensure that all of the trajectories were projected onto the \textit{same} lower dimensional space, we computed the low-dimensional embedding on a ``stacked'' matrix created by vertically concatenating the events-by-topics topic proportions matrices for the video, across-participants average recall and all 17 individual participants' recalls.
-We then separated the rows of the result (a total-number-of-events by two matrix) back into individual matrices for the video topic trajectory, across-participant average recall trajectory and the trajectories for each individual participant's recalls (Fig.~\ref{fig:trajectory}).
+To ensure that all of the trajectories were projected onto the \textit{same} lower dimensional space, we computed the low-dimensional embedding on a ``stacked'' matrix created by vertically concatenating the events-by-topics topic proportions matrices for the episode, across-participants average recall and all 17 individual participants' recalls.
+We then separated the rows of the result (a total-number-of-events by two matrix) back into individual matrices for the episode topic trajectory, across-participant average recall trajectory and the trajectories for each individual participant's recalls (Fig.~\ref{fig:trajectory}).
 This general approach for discovering a shared low-dimensional embedding for a collections of high-dimensional observations follows \cite{HeusEtal18a}.
 
-We optimized the manifold space for visualization based on two criteria: First, that the 2D embedding of the video trajectory should reflect its original 100-dimensional structure as faithfully as possible.
-Second, that the path traversed by the embedded video trajectory should intersect itself a minimal number of times.
-The first criteria helps bolster the validity of visual intuitions about relationships between sections of video content, based on their locations in the embedding space.
-The second criteria was motivated by the observed low off-diagonal values in the video trajectory's temporal correlation matrix (suggesting that the same topic-space coordinates should not be revisited; see Figure~2A in the main text).
+We optimized the manifold space for visualization based on two criteria: First, that the 2D embedding of the episode trajectory should reflect its original 100-dimensional structure as faithfully as possible.
+Second, that the path traversed by the embedded episode trajectory should intersect itself a minimal number of times.
+The first criteria helps bolster the validity of visual intuitions about relationships between sections of episode content, based on their locations in the embedding space.
+The second criteria was motivated by the observed low off-diagonal values in the episode trajectory's temporal correlation matrix (suggesting that the same topic-space coordinates should not be revisited; see Figure~2A in the main text).
 For further details on how we created this low-dimensional embedding space, see \textit{Supporting Information}.
@@
 \subsection*{Searchlight fMRI analyses}
-In Figure~\ref{fig:brainz}, we present two analyses aimed at identifying brain regions whose responses (as participants viewed the video) exhibited a particular temporal structure.
-We developed a searchlight analysis wherein we constructed a 5 x 5 x 5 cube of voxels (following \citealp{ChenEtal17}) centered on each voxel in the brain, and for each of these cubes, computed the temporal correlation matrix of the voxel responses during video viewing.
-Specifically, for each of the 1976 volumes collected during video viewing, we correlated the activity patterns in the given cube with the activity patterns (in the same cube) collected during every other timepoint.
+In Figure~\ref{fig:brainz}, we present two analyses aimed at identifying brain regions whose responses (as participants viewed the episode) exhibited a particular temporal structure.
+We developed a searchlight analysis wherein we constructed a 5 x 5 x 5 cube of voxels (following \citealp{ChenEtal17}) centered on each voxel in the brain, and for each of these cubes, computed the temporal correlation matrix of the voxel responses during episode viewing.
+Specifically, for each of the 1976 volumes collected during episode viewing, we correlated the activity patterns in the given cube with the activity patterns (in the same cube) collected during every other timepoint.
 This yielded a 1976 by 1976 correlation matrix for each cube.
@@
 Next, we constructed a series of ``template'' matrices.
-The first template reflected the timecourse of the video's topic trajectory, and the others reflected the timecourse of each participant's recall trajectory.
-To construct the video template, we computed the correlations between the topic proportions estimated for every pair of TRs (prior to segmenting the trajectory into discrete events; i.e., the correlation matrix shown in Figs.~\ref{fig:model}B and \ref{fig:brainz}A).
+The first template reflected the timecourse of the episode's topic trajectory, and the others reflected the timecourse of each participant's recall trajectory.
+To construct the episode template, we computed the correlations between the topic proportions estimated for every pair of TRs (prior to segmenting the trajectory into discrete events; i.e., the correlation matrix shown in Figs.~\ref{fig:model}B and \ref{fig:brainz}A).
 We constructed similar temporal correlation matrices for each participant's recall topic trajectory (Figs.~\ref{fig:model}D, \corrmats).
-However, to correct for length differences and potential non-linear transformations between viewing time and recall time, we first used dynamic time warping~\citep{BernClif94} to temporally align participants' recall topic trajectories with the video topic trajectory.
+However, to correct for length differences and potential non-linear transformations between viewing time and recall time, we first used dynamic time warping~\citep{BernClif94} to temporally align participants' recall topic trajectories with the episode topic trajectory.
 An example correlation matrix before and after warping is shown in Fig.~\ref{fig:brainz}B.
-This yielded a 1976 by 1976 correlation matrix for the video template and for each participant's recall template.
+This yielded a 1976 by 1976 correlation matrix for the episode template and for each participant's recall template.
 
-The temporal structure of the video's content (as described by our model) is captured in the block-diagonal structure of the video's temporal correlation matrix (e.g., Figs.~\ref{fig:model}B, \ref{fig:brainz}A), with time periods of thematic stability represented as dark blocks of varying sizes.
-Inspecting the video correlation matrix suggests that the video's semantic content is highly temporally specific (i.e., the correlations between topic vectors from distant timepoints are almost all near zero).
+The temporal structure of the episode's content (as described by our model) is captured in the block-diagonal structure of the episode's temporal correlation matrix (e.g., Figs.~\ref{fig:model}B, \ref{fig:brainz}A), with time periods of thematic stability represented as dark blocks of varying sizes.
+Inspecting the episode correlation matrix suggests that the episode's semantic content is highly temporally specific (i.e., the correlations between topic vectors from distant timepoints are almost all near zero).
 By contrast, the activity patterns of individual (cubes of) voxels can encode relatively limited information on their own, and their activity frequently contributes to multiple separate functions \citep{FreeEtal01, SigmDeha08, CharKoec10, RishEtal13}.
 By nature, these two attributes give rise to similarities in activity across large timescales that may not necessarily reflect a single task.
-To enable a more sensitive analysis of brain regions whose shifts in activity patterns mirrored shifts in the semantic content of the video or recalls, we restricted the temporal correlations we considered to the timescale of semantic information captured by our model.
-Specifically, we isolated the upper triangle of the video correlation matrix and created a ``proximal correlation mask'' that included only diagonals from the upper triangle of the video correlation matrix up to the first diagonal that contained no positive correlations.
-Applying this mask to the full video correlation matrix was analogous to excluding diagonals beyond the corner of the largest diagonal block.
-In other words, the timescale of temporal correlations we considered corresponded to the longest period of thematic stability in the video, and by extension the longest expected period of thematic stability in participants' recalls and the longest period of stability we might expect to see in voxel activity arising from processing or encoding video content.
-Figure \ref{fig:brainz} shows this proximal correlation mask applied to the temporal correlation matrices for the video, an example participant's (warped) recall, and an example cube of voxels from our searchlight analyses.
+To enable a more sensitive analysis of brain regions whose shifts in activity patterns mirrored shifts in the semantic content of the episode or recalls, we restricted the temporal correlations we considered to the timescale of semantic information captured by our model.
+Specifically, we isolated the upper triangle of the episode correlation matrix and created a ``proximal correlation mask'' that included only diagonals from the upper triangle of the episode correlation matrix up to the first diagonal that contained no positive correlations.
+Applying this mask to the full episode correlation matrix was analogous to excluding diagonals beyond the corner of the largest diagonal block.
+In other words, the timescale of temporal correlations we considered corresponded to the longest period of thematic stability in the episode, and by extension the longest expected period of thematic stability in participants' recalls and the longest period of stability we might expect to see in voxel activity arising from processing or encoding episode content.
+Figure \ref{fig:brainz} shows this proximal correlation mask applied to the temporal correlation matrices for the episode, an example participant's (warped) recall, and an example cube of voxels from our searchlight analyses.
 
-To determine which (cubes of) voxel responses matched the video template, we correlated the proximal diagonals from the upper triangle of the voxel correlation matrix for each cube with the proximal diagonals from video template matrix~\citep{KrieEtal08b}.
+To determine which (cubes of) voxel responses matched the episode template, we correlated the proximal diagonals from the upper triangle of the voxel correlation matrix for each cube with the proximal diagonals from episode template matrix~\citep{KrieEtal08b}.
 This yielded, for each participant, a voxelwise map of correlation values.
 We then performed a one-sample $t$-test on the distribution of (Fisher $z$-transformed) correlations at each voxel, across participants.
-This resulted in a value for each voxel (cube), describing how reliably its timecourse followed that of the video.
+This resulted in a value for each voxel (cube), describing how reliably its timecourse followed that of the episode.
 
-We further sought to ensure that our analysis identified regions where the activations’ temporal structure specifically reflected that of the video, rather than regions whose activity was simply autocorrelated at a width similar to the video template’s diagonal.
-To achieve this, we used a phase shift-based permutation procedure, whereby we circularly shifted the video’s topic trajectory by a random number of timepoints, computed the resulting ``null” video template, and re-ran the searchlight analysis, in full.
+We further sought to ensure that our analysis identified regions where the activations’ temporal structure specifically reflected that of the episode, rather than regions whose activity was simply autocorrelated at a width similar to the episode template’s diagonal.
+To achieve this, we used a phase shift-based permutation procedure, whereby we circularly shifted the episode’s topic trajectory by a random number of timepoints, computed the resulting ``null” episode template, and re-ran the searchlight analysis, in full.
 (For each of the 100 permutations, the same random shift was used for all participants).
 We $z$-scored the observed (unshifted) result at each voxel against the distribution of permutation-derived ``null” results, and estimated a $p$-value by computing the proportion of shifted results that yielded larger values.
-To create the map in Figure~\ref{fig:brainz}C, we thresholded out any voxels whose similarity to the unshifted video’s structure fell below the 95\textsuperscript{th} percentile of the permutation-derived similarity results.
+To create the map in Figure~\ref{fig:brainz}C, we thresholded out any voxels whose similarity to the unshifted episode’s structure fell below the 95\textsuperscript{th} percentile of the permutation-derived similarity results.
 
@@
 For each participant, we correlated the proximal diagonals from the upper triangle of the correlation matrix for each cube of voxels with the proximal diagonals from the upper triangle of their (time-warped) recall correlation matrix.
-As in the video template analysis, this yielded a voxelwise map of correlation coefficients per participant.
-However, whereas the video analysis compared every participant's responses to the same template, here the recall templates were unique for each participant.
-As in the analysis described above, we $t$-scored the (Fisher $z$-transformed) voxelwise correlations, and used the same permutation procedure we developed for the video responses to ensure specificity to the recall timeseries and assign significance values.
+As in the episode template analysis, this yielded a voxelwise map of correlation coefficients per participant.
+However, whereas the episode analysis compared every participant's responses to the same template, here the recall templates were unique for each participant.
+As in the analysis described above, we $t$-scored the (Fisher $z$-transformed) voxelwise correlations, and used the same permutation procedure we developed for the episode responses to ensure specificity to the recall timeseries and assign significance values.
 To create the map in Figure~\ref{fig:brainz}D we again thresholded out any voxels whose scores were below the 95\textsuperscript{th} percentile of the permutation-derived null distribution.
@@
 Our permutation procedure yielded, for each of the two searchlight analyses, a voxelwise map of significance ($p$-statistic) values.
-These maps describe the extent to which each voxel \textit{specifically} reflected the temporal structure of the video or individuals' recalls (i.e., for each voxel, the proportion of phase-shifted topic vector correlation matrices less similar to the voxel activity correlation matrix than the unshifted video's correlation matrix).
+These maps describe the extent to which each voxel \textit{specifically} reflected the temporal structure of the episode or individuals' recalls (i.e., for each voxel, the proportion of phase-shifted topic vector correlation matrices less similar to the voxel activity correlation matrix than the unshifted episode's correlation matrix).
 We inputted the two statistical maps described above to \texttt{Neurosynth} to create a list of the 10 most representative terms for each map.

### 2020-08-20 paper/supporting_information.tex
recompiled with updated figures

@@
 \subsection*{Optimizing topic model parameters}
-In order to create accurate video and recall models, we used an optimization method that was driven by our ability to explain hand-annotated memory performance metrics collected by \cite{ChenEtal17}.
-Specifically, we used a grid search to compute the $\omega$ (video sliding window duration, in scenes), $\rho$ (recall sliding window duration, in sentences), and $K$ (number of topics) that satisfied
+In order to create accurate episode and recall models, we used an optimization method that was driven by our ability to explain hand-annotated memory performance metrics collected by \cite{ChenEtal17}.
+Specifically, we used a grid search to compute the $\omega$ (episode sliding window duration, in scenes), $\rho$ (recall sliding window duration, in sentences), and $K$ (number of topics) that satisfied
 \[
@@
 \]
-where $\mathrm{corr}(\mu, \nu)$ is the per-participant correlation between the temporal correlation matrices of the video ($\mu$) and recall ($\nu$) trajectory, and $\theta$ is the per-participant hand-annotated memory performance.
+where $\mathrm{corr}(\mu, \nu)$ is the per-participant correlation between the temporal correlation matrices of the episode ($\mu$) and recall ($\nu$) trajectory, and $\theta$ is the per-participant hand-annotated memory performance.
 We searched over a grid of pre-specified values for each of these parameters; the resulting correlations are displayed in Figure~\ref{fig:paramsearch}.
 The optimal parameters were $\omega = 50$, $\rho = 10$, and $K = 100$.
-In subsequent refinements of our topic modeling approach, we made various improvements to how we parse the video and recall text and construct the trajectories' timeseries, but maintained these optimized parameters throughout.
+In subsequent refinements of our topic modeling approach, we made various improvements to how we parse the episode and recall text and construct the trajectories' timeseries, but maintained these optimized parameters throughout.
 
@@
 \includegraphics[width=1\textwidth]{figs/parameter_search}
-\caption{\small \textbf{Optimizing topic model parameters.}  We performed a grid search over video sliding window length ($\omega \in \{5, 10, 25, 50, 100 \}$), recall sliding window length ($\rho \in \{5, 10, 25, 50, 100 \}$), and number of topics ($K \in \{5, 10, 25, 50, 100 \}$).
-The reported correlations are between per-subject video-recall trajectory correlations and per-subject hand-annotated memory performance ratings.}
+\caption{\small \textbf{Optimizing topic model parameters.}  We performed a grid search over episode sliding window length ($\omega \in \{5, 10, 25, 50, 100 \}$), recall sliding window length ($\rho \in \{5, 10, 25, 50, 100 \}$), and number of topics ($K \in \{5, 10, 25, 50, 100 \}$).
+The reported correlations are between per-subject episode-recall trajectory correlations and per-subject hand-annotated memory performance ratings.}
 \label{fig:paramsearch}
@@
 
-The optimized model converged on 32 unique topics that were assigned non-zero weights over the course of the video.
+The optimized model converged on 32 unique topics that were assigned non-zero weights over the course of the episode.
 We provide a list of the top ten highest-weighted words from each topic in Figure~\ref{fig:topics}.
@@
 \subsection*{Feature importance analyses}
-To determine the contribution of each feature to the structure of the video topic proportions, we conducted a ``leave one out'' analysis.
-Specifically, we compared the original video topic trajectory (created using all hand-annotated features from the 998 hand-annotated scenes spanning the \textit{Sherlock} episode; see \textit{Methods} for a full list of features) with video trajectories created using all but one type of feature.
+To determine the contribution of each feature to the structure of the episode topic proportions, we conducted a ``leave one out'' analysis.
+Specifically, we compared the original episode topic trajectory (created using all hand-annotated features from the 998 hand-annotated scenes spanning the \textit{Sherlock} episode; see \textit{Methods} for a full list of features) with episode trajectories created using all but one type of feature.
 We created temporal correlation matrices for each trajectory (using the topic proportions matrices) and correlated the proximal diagonals from the upper triangles of each impoverished trajectory with the original feature-complete trajectory (see \textit{Methods} for details on how we isolated proximal temporal correlations).

### 2020-08-20 paper/supporting_information.tex
updated video -> episode in supplement

@@
 \includegraphics[width=1\textwidth]{figs/feature_value}
-\caption{\small \textbf{Feature importance analysis.} \textbf{A.} Contributions of each feature type to the structure of the video trajectory.
-The bar heights reflect the correlation between the video trajectory computed using all features with a video trajectory computed using all features except the indicated feature.
-(Lower bars reflect features that contribute more substantially to the video trajectory's shape.) \textbf{B.} Which features are preserved during recall?
-The bar heights reflect the (average) across-participant correlations between the video and recall trajectories.
+\caption{\small \textbf{Feature importance analysis.} \textbf{A.} Contributions of each feature type to the structure of the episode trajectory.
+The bar heights reflect the correlation between the episode trajectory computed using all features with a episode trajectory computed using all features except the indicated feature.
+(Lower bars reflect features that contribute more substantially to the episode trajectory's shape.) \textbf{B.} Which features are preserved during recall?
+The bar heights reflect the (average) across-participant correlations between the episode and recall trajectories.
 Error bars denote bootstrap-estimated standard error of the mean.
 \textbf{C.} Feature correlation matrix.
-Each entry displays the correlation between video topic trajectories created using only the indicated (row/column) features.}
+Each entry displays the correlation between episode topic trajectories created using only the indicated (row/column) features.}
 \label{fig:feature-importance}
@@
 
-We also carried out an analysis of which annotated features tended to shape aspects of the video topic trajectory's structure that were preserved in participants' recalls.
-Specifically, we computed the timepoint-by-timepoint correlation matrix of the video topic trajectory, and correlated the proximal diagonals from its upper triangle with those of the timepoint-by-timepoint correlation matrices for each participant's recall topic trajectory (resampled using linear interpolation to have the same number of timepoints as the video trajectory).
+We also carried out an analysis of which annotated features tended to shape aspects of the episode topic trajectory's structure that were preserved in participants' recalls.
+Specifically, we computed the timepoint-by-timepoint correlation matrix of the episode topic trajectory, and correlated the proximal diagonals from its upper triangle with those of the timepoint-by-timepoint correlation matrices for each participant's recall topic trajectory (resampled using linear interpolation to have the same number of timepoints as the episode trajectory).
 This yielded a single correlation coefficient for each participant.
 We then repeated this analysis with each annotated feature held out in turn.
-Observing a lower correlation between the video and recall trajectories (when a given feature was held out) would indicate that participants utilize changes in that feature's content to discriminate between sections of the video when organizing their recalls.
-We found that hand-annotated narrative details were the most heavily utilized type of feature, whereas changes in the text present on-screen, the indoor/outdoor distinction between scenes, the camera angle, the names of the various characters on screen, and which character was speaking tended not to impact participants' recall structures (i.e., removing those features resulted in a \textit{greater} video-recall topic vector correlation than including them; Fig.~\ref{fig:feature-importance}B).
+Observing a lower correlation between the episode and recall trajectories (when a given feature was held out) would indicate that participants utilize changes in that feature's content to discriminate between sections of the episode when organizing their recalls.
+We found that hand-annotated narrative details were the most heavily utilized type of feature, whereas changes in the text present on-screen, the indoor/outdoor distinction between scenes, the camera angle, the names of the various characters on screen, and which character was speaking tended not to impact participants' recall structures (i.e., removing those features resulted in a \textit{greater} episode-recall topic vector correlation than including them; Fig.~\ref{fig:feature-importance}B).
 
@@
 For example, knowing which character is in focus during a given scene may also provide information about which character is speaking.
-We computed video topic trajectories from annotations of each individual feature, in turn, and then compared the proximal diagonals from the upper triangles of the temporal correlation matrices of all pairs of features.
+We computed episode topic trajectories from annotations of each individual feature, in turn, and then compared the proximal diagonals from the upper triangles of the temporal correlation matrices of all pairs of features.
 This provided additional confirmation that the shape of the full trajectory (including all types of features) was largely driven by narrative details.
@@
 \subsection*{Creating a low-dimensional embedding space}
-Figures~7 and 8C in the main text display two-dimensional projections of the 100-dimensional topic trajectories for the video (7A, 8C), average recall (7B), and each individual's recall (7C, 8C).
+Figures~7 and 8C in the main text display two-dimensional projections of the 100-dimensional topic trajectories for the episode (7A, 8C), average recall (7B), and each individual's recall (7C, 8C).
 We created these embeddings using the Uniform Manifold Approximation and Projection algorithm \citep[UMAP;][]{McInEtal18} called from our high-dimensional visualization and text analysis software, \texttt{HyperTools}~\citep{HeusEtal18a}.
 An advantage of the UMAP algorithm over comparable manifold learning techniques (such as $t$-SNE) is that UMAP explicitly attempts to preserve the global structure of the data \citep{McInEtal18,BechEtal19} by constructing a space where distance on the manifold is standard Euclidean distance, with respect to the global coordinate system.
-This was important in our use case, as we wanted to visualize both the evolving structure of the video and the spatial relationships between presented and recalled content.
+This was important in our use case, as we wanted to visualize both the evolving structure of the episode and the spatial relationships between presented and recalled content.
 
@@
 Two other parameters ultimately affect this balance between preserving local and global structure: the seed ($\tau$) for the (pseudo-)random number generator, and the order of the observations (i.e., trajectories) to be embedded ($\varphi$).
-As described in \textit{Methods}, we ensured the video and recall events were projected onto the \textit{same} low-dimensional manifold by fitting the embedding model to a stacked matrix of all video, average recall, and individuals' recall events.
+As described in \textit{Methods}, we ensured the episode and recall events were projected onto the \textit{same} low-dimensional manifold by fitting the embedding model to a stacked matrix of all episode, average recall, and individuals' recall events.
 After initializing the low-dimensional simplicial set (by default, using a spectral embedding of the high-dimensional simplicial set's fuzzy 1-skeleton), UMAP optimizes the embedding using stochastic gradient descent with cross-entropy as a cost function.
@@
 
-We performed a grid search over pre-specified values of these hyper-parameters, and optimized the manifold space for visualization based on two criteria: First, that the 2D embedding of the video trajectory should reflect its original 100-dimensional structure as faithfully as possible.
-Second, that the path traversed by the embedded video trajectory should intersect itself a minimal number of times.
-The first criteria helps bolster the validity of visual intuitions about relationships between sections of video content, based on their locations in the embedding space.
-The second criteria was motivated by the observed low off-diagonal values in the video trajectory's temporal correlation matrix (suggesting that the same topic-space coordinates should not be revisited; see Figure~2A in the main text) and the inability to accurately describe the consistency of participants' transitions through topic space at locations where those transitions frequently occurred in multiple, orthogonal directions (see \textit{Methods} for analysis details).
+We performed a grid search over pre-specified values of these hyper-parameters, and optimized the manifold space for visualization based on two criteria: First, that the 2D embedding of the episode trajectory should reflect its original 100-dimensional structure as faithfully as possible.
+Second, that the path traversed by the embedded episode trajectory should intersect itself a minimal number of times.
+The first criteria helps bolster the validity of visual intuitions about relationships between sections of episode content, based on their locations in the embedding space.
+The second criteria was motivated by the observed low off-diagonal values in the episode trajectory's temporal correlation matrix (suggesting that the same topic-space coordinates should not be revisited; see Figure~2A in the main text) and the inability to accurately describe the consistency of participants' transitions through topic space at locations where those transitions frequently occurred in multiple, orthogonal directions (see \textit{Methods} for analysis details).
 We formalized this optimization as the combination of hyper-parameter values that satisfied
@@
 \]
-$\xi$ is the video's trajectory through the manifold space; $\chi$ is the original, 100-dimensional video trajectory; $\Upsilon$ is a function that computes a condensed matrix of pairwise distances between event vectors (computed using correlation distance in the original topic space and Euclidean distance in the manifold space); $\mathrm{corr}\left(\Upsilon\left(\xi\right), \Upsilon\left(\chi\right)\right)$ is the correlation between the sets of pairwise distances, and $\Gamma$ is the number of instances in which lines drawn between consecutive video event embeddings intersected each other.
-The sets of hyper-parameter values we searched over comprised: $K \in \{10x \in \mathbb{Z}~|~10 < x <  22\} \cup \{161\}$ (a range roughly centered on half the total number of events, 161, in order to balance representations of local and global structure); $\gamma \in \{1, 3, 5, 7, 9\}$; $\delta \in \{0.1, 0.3, 0.5, 0.7, 0.9\}$; $\tau \in \{x \in \mathbb{Z}~|~0 < x < 101\}$; and $\varphi \in {S\choose3},~\mathrm{where}~S=\{\mathrm{video~events,~average~recall~events, individual~recall~events}\}$.
-The optimal parameters (that yielded $\Phi=0$) were $K=170$, $\gamma=7$, $\delta=0.7$, $\tau=41$, with the order of sequence $\varphi$ as the average recall events, video events, and individuals' recall events, vertically concatenated, in order.
+$\xi$ is the episode's trajectory through the manifold space; $\chi$ is the original, 100-dimensional episode trajectory; $\Upsilon$ is a function that computes a condensed matrix of pairwise distances between event vectors (computed using correlation distance in the original topic space and Euclidean distance in the manifold space); $\mathrm{corr}\left(\Upsilon\left(\xi\right), \Upsilon\left(\chi\right)\right)$ is the correlation between the sets of pairwise distances, and $\Gamma$ is the number of instances in which lines drawn between consecutive episode event embeddings intersected each other.
+The sets of hyper-parameter values we searched over comprised: $K \in \{10x \in \mathbb{Z}~|~10 < x <  22\} \cup \{161\}$ (a range roughly centered on half the total number of events, 161, in order to balance representations of local and global structure); $\gamma \in \{1, 3, 5, 7, 9\}$; $\delta \in \{0.1, 0.3, 0.5, 0.7, 0.9\}$; $\tau \in \{x \in \mathbb{Z}~|~0 < x < 101\}$; and $\varphi \in {S\choose3},~\mathrm{where}~S=\{\mathrm{episode~events,~average~recall~events, individual~recall~events}\}$.
+The optimal parameters (that yielded $\Phi=0$) were $K=170$, $\gamma=7$, $\delta=0.7$, $\tau=41$, with the order of sequence $\varphi$ as the average recall events, episode events, and individuals' recall events, vertically concatenated, in order.
 
@@
 \includegraphics[width=\textwidth]{figs/matchmats}
-\caption{\small \textbf{Video-recall event correlation matrices.}  Each panel is in the same format as Figure~2G in the main text.
-The yellow boxes mark the matched video event for each recall event (i.e., the maximum correlation in each column).}
+\caption{\small \textbf{episode-recall event correlation matrices.}  Each panel is in the same format as Figure~2G in the main text.
+The yellow boxes mark the matched episode event for each recall event (i.e., the maximum correlation in each column).}
 \label{fig:matchmats}
@@
 \includegraphics[width=.9\textwidth]{figs/k_optimization}
-\caption{\small \textbf{Video and recall trajectory \textit{K}-optimization functions.}  We selected the optimal $K$-value for the video and each recall trajectory, using the formula described in \textit{Methods}.
+\caption{\small \textbf{episode and recall trajectory \textit{K}-optimization functions.}  We selected the optimal $K$-value for the episode and each recall trajectory, using the formula described in \textit{Methods}.
 This computation resulted in a curve for each trajectory, describing the Wasserstein distance between the distributions of within-event and across-event topic vector correlations, as a function of $K$.}

### 2020-08-20 paper/supporting_information.tex
minor edits to supplement

@@
 \usepackage{setspace}
+\usepackage{hyperref}
 \usepackage{placeins}
-%\doublespacing
 
@@
 \caption{\small \textbf{Optimizing topic model parameters.}  We performed a grid search over episode sliding window length ($\omega \in \{5, 10, 25, 50, 100 \}$), recall sliding window length ($\rho \in \{5, 10, 25, 50, 100 \}$), and number of topics ($K \in \{5, 10, 25, 50, 100 \}$).
-The reported correlations are between per-subject episode-recall trajectory correlations and per-subject hand-annotated memory performance ratings.}
+The reported correlations are between per-subject episode-recall trajectory correlations and per-subject hand-generated memory performance scores.}
 \label{fig:paramsearch}
@@
 \subsection*{Feature importance analyses}
-To determine the contribution of each feature to the structure of the episode topic proportions, we conducted a ``leave one out'' analysis.
-Specifically, we compared the original episode topic trajectory (created using all hand-annotated features from the 998 hand-annotated scenes spanning the \textit{Sherlock} episode; see \textit{Methods} for a full list of features) with episode trajectories created using all but one type of feature.
-We created temporal correlation matrices for each trajectory (using the topic proportions matrices) and correlated the proximal diagonals from the upper triangles of each impoverished trajectory with the original feature-complete trajectory (see \textit{Methods} for details on how we isolated proximal temporal correlations).
-Observing a lower correlation between an impoverished trajectory (holding out a particular feature) and the feature-complete trajectory would suggest that the given feature played a more prominent role in shaping the temporal structure of the feature-complete trajectory.
-We found that hand-annotated narrative details provided the most structure to the feature-complete trajectory, whereas the name of the character(s) in focus for each shot provided the least structure (Fig.~\ref{fig:feature-importance}A).
+To determine the contribution of each feature to the shape of the episode topic trajectory, we conducted a ``leave one out'' analysis.
+Specifically, we compared the original episode topic trajectory (created using all hand-annotated features from the 998 manually identified scenes spanning the \textit{Sherlock} episode; see \textit{Methods} for a full list of features) with episode trajectories created using all but one type of feature.
+For each impoverished episode trajectory, we computed the timepoint-by-timepoint correlation matrix, and correlated the proximal diagonals from the upper right triangle with those from the temporal correlation matrix of the feature-complete trajectory (for details on how we isolated proximal temporal correlations, see \textit{Methods}).
+Observing a lower correlation between an impoverished trajectory (with a particular feature removed) and the feature-complete trajectory would suggest that the held-out feature contributed more prominently to the full episode trajectory's temporal structure.
+We found that hand-annotated narrative details played the greatest roll in determining the shape of the episode, whereas the name of the character(s) in focus for each shot contributed least (Fig.~\ref{fig:feature-importance}A).
 
@@
 
-We also carried out an analysis of which annotated features tended to shape aspects of the episode topic trajectory's structure that were preserved in participants' recalls.
-Specifically, we computed the timepoint-by-timepoint correlation matrix of the episode topic trajectory, and correlated the proximal diagonals from its upper triangle with those of the timepoint-by-timepoint correlation matrices for each participant's recall topic trajectory (resampled using linear interpolation to have the same number of timepoints as the episode trajectory).
+Next, we sought to determine which annotated features contributed aspects of the episode trajectory's shape that were preserved in participants' later recalls.
+Specifically, we computed the timepoint-by-timepoint correlation matrix of the episode topic trajectory, and correlated the proximal diagonals from its upper triangle with those from the timepoint-by-timepoint correlation matrices for each participant's recall topic trajectory (stretched via linear interpolation to have the same number of timepoints as the episode trajectory).
 This yielded a single correlation coefficient for each participant.
 We then repeated this analysis with each annotated feature held out in turn.
-Observing a lower correlation between the episode and recall trajectories (when a given feature was held out) would indicate that participants utilize changes in that feature's content to discriminate between sections of the episode when organizing their recalls.
-We found that hand-annotated narrative details were the most heavily utilized type of feature, whereas changes in the text present on-screen, the indoor/outdoor distinction between scenes, the camera angle, the names of the various characters on screen, and which character was speaking tended not to impact participants' recall structures (i.e., removing those features resulted in a \textit{greater} episode-recall topic vector correlation than including them; Fig.~\ref{fig:feature-importance}B).
+Observing a lower correlation between the episode and recall trajectories (constructed in the absence of a given feature) would indicate that participants utilize changes in that feature's content to discriminate between sections of the episode when organizing their recalls.
+We found that hand-annotated narrative details were the most heavily utilized feature, whereas changes in the text present on-screen, the indoor/outdoor distinction between scenes, the camera angle, the names of the various characters on screen, and the location in which the scene took place tended not to impact participants' recall structures (i.e., removing those features resulted in a \textit{greater} episode-recall topic vector correlation than including them; Fig.~\ref{fig:feature-importance}B).
 
-Next, we wondered how the different types of features might relate.
+We also wondered how the different types of features might relate.
 For example, knowing which character is in focus during a given scene may also provide information about which character is speaking.
-We computed episode topic trajectories from annotations of each individual feature, in turn, and then compared the proximal diagonals from the upper triangles of the temporal correlation matrices of all pairs of features.
-This provided additional confirmation that the shape of the full trajectory (including all types of features) was largely driven by narrative details.
+We computed topic trajectories from the annotations for each individual feature, in turn, and (using the same technique as in the above analyses) compared the proximal temporal correlation structure of each single-feature trajectory to each other, as well as to that of the full episode.
+This provided additional confirmation that the shape of the full episode trajectory was largely driven by narrative details.
 We also found that character-driven features (characters on screen, characters speaking, and characters in focus) were strongly correlated.
@@
 We created these embeddings using the Uniform Manifold Approximation and Projection algorithm \citep[UMAP;][]{McInEtal18} called from our high-dimensional visualization and text analysis software, \texttt{HyperTools}~\citep{HeusEtal18a}.
-An advantage of the UMAP algorithm over comparable manifold learning techniques (such as $t$-SNE) is that UMAP explicitly attempts to preserve the global structure of the data \citep{McInEtal18,BechEtal19} by constructing a space where distance on the manifold is standard Euclidean distance, with respect to the global coordinate system.
+An advantage of the UMAP algorithm over comparable manifold learning techniques (e.g., $t$-SNE) is that UMAP explicitly attempts to preserve the global structure of the data \citep{McInEtal18,BechEtal19} by constructing a space where distance on the manifold is standard Euclidean distance, with respect to the global coordinate system.
 This was important in our use case, as we wanted to visualize both the evolving structure of the episode and the spatial relationships between presented and recalled content.

### 2020-08-26 paper/main.tex
inputted JRM notes to results section

@@
 
-Occasionally, this gradual ``drift" of our ongoing experience is punctuated by sudden changes, or ``shifts"~\citep[e.g., when we walk through a doorway; ][]{RadvZack17}.
+Occasionally, this gradual ``drift'' of our ongoing experience is punctuated by sudden changes, or ``shifts''~\citep[e.g., when we walk through a doorway; ][]{RadvZack17}.
 Prior research suggests that these sharp transitions (termed \textit{event boundaries}) help to discretize our experiences (and their mental representations) into \textit{events}~\citep{RadvZack17, BrunEtal18, HeusEtal18b, ClewDava17, EzzyDava11, DuBrDava13}.
@@
 We took from these annotations the union of all unique words (excluding stop words, such as ``and,'' ``or,'' ``but,'' etc.) across all features and scenes as the ``vocabulary'' for the topic model.
-We then concatenated the sets of words across all features contained in overlapping sliding windows of (up to) 50 scenes, and treated each window as a single ``document" for the purpose of fitting the topic model.
+We then concatenated the sets of words across all features contained in overlapping sliding windows of (up to) 50 scenes, and treated each window as a single ``document'' for the purpose of fitting the topic model.
 Next, we fit a topic model with (up to) $K = 100$ topics to this collection of documents.
@@
 \caption{\small \textbf{Topic weights in episode and recall content.} We used hand-annotated descriptions of each manually identified scene from the episode to fit a topic model.
-Three example video frames (first row) and their associated descriptions (second row) are displayed.
+Three example episode frames (first row) and their associated descriptions (second row) are displayed.
 The third row shows an example participant's later recalls of the same three scenes.
@@
 The 32 topics we found were heavily character-focused (i.e., the top-weighted word in each topic was nearly always a character) and could be roughly divided into themes centered around Sherlock Holmes (the titular character), John Watson (Sherlock's close confidant and assistant), supporting characters (e.g., Inspector Lestrade, Sergeant Donovan, or Sherlock's brother Mycroft), or the interactions between various groupings of these characters (see Fig.~\topics).
+This likely follows from the frequency with which these terms appeared in the episode annotations.
 Several of the identified topics were highly similar, which we hypothesized might allow us to distinguish between subtle narrative differences if the distinctions between those overlapping topics were meaningful.
-The topic vectors for each timepoint were also \textit{sparse}, in that only a small number (typically one or two) of topics tended to be ``active" in any given timepoint (see Fig.~\ref{fig:model}A).
+The topic vectors for each timepoint were also \textit{sparse}, in that only a small number (typically one or two) of topics tended to be ``active'' in any given timepoint (see Fig.~\ref{fig:model}A).
 Further, the dynamics of the topic activations appeared to exhibit \textit{persistence} (i.e., given that a topic was active in one timepoint, it was likely to be active in the following timepoint) along with \textit{occasional rapid changes} (i.e., occasionally topics would appear to spring into or out of existence).
-These two properties of the topic dynamics may be seen in the block diagonal structure of the timepoint-by-timepoint correlation matrix (Fig.~\ref{fig:model}B) and reflect the gradual drift and sudden shifts fundamental to the temporal dynamics of real-world experiences.
+These two properties of the topic dynamics may be seen in the block diagonal structure of the timepoint-by-timepoint correlation matrix (Fig.~\ref{fig:model}B) and reflect the gradual drift and sudden shifts fundamental to the temporal dynamics of many real-world experiences, as well as television episodes.
 Given this observation, we adapted an approach devised by \cite{BaldEtal17}, and used a hidden Markov model (HMM) to identify the \textit{event boundaries} where the topic activations changed rapidly (i.e., the boundaries of the blocks in the temporal correlation matrix; event boundaries identified by the HMM are outlined in yellow in Fig.~\ref{fig:model}B).
-Part of our model fitting procedure required selecting an appropriate number of ``events" into which the topic trajectory should be segmented.
+Part of our model fitting procedure required selecting an appropriate number of ``events'' into which the topic trajectory should be segmented.
 To accomplish this, we used an optimization procedure that maximized the difference between the topic weights for timepoints within an event versus timepoints across multiple events (see \textit{Methods} for additional details).
@@
 We applied the same topic model (already trained on the episode annotations) to each participant's recalls.
-Analogously to how we parsed the time-varying content of the episode, to obtain similar estimates for each participant's recall, we treated each overlapping  window of (up to 10) sentences from their transcript as a ``document," and computed the most probable mix of topics reflected in each timepoint's sentences.
+Analogously to how we parsed the time-varying content of the episode, to obtain similar estimates for each participant's recall transcript, we treated each overlapping  window of (up to 10) sentences from their transcript as a ``document,'' and computed the most probable mix of topics reflected in each timepoint's sentences.
 This yielded, for each participant, a number-of-windows by number-of-topics topic proportions matrix that characterized how the topics identified in the original episode were reflected in the participant's recalls.
-Note that an important feature of our approach is that it allows us to compare participants' recalls to events from the original episode, despite different participants using widely varying language to describe the events, and that those descriptions often diverged in content and quality from the episode annotations.
-This is a substantial benefit of projecting the episode and recalls into a shared ``topic'' space.
+An important feature of our approach is that it allows us to compare participants' recalls to events from the original episode, despite that different participants used widely varying language to describe the events, and that those descriptions often diverged in content and quality from the episode annotations.
+This ability to match up conceptually related text that differs in specific vocabulary, detail, and length is an important benefit of projecting the episode and recalls into a shared ``topic'' space.
 An example topic proportions matrix from one participant's recalls is shown in Figure~\ref{fig:model}D.
@@
 As in the episode correlation matrix (Fig.~\ref{fig:model}B), the example participant's recall correlation matrix has a strong block diagonal structure, indicating that their recalls are discretized into separated events.
-As for the episode correlation matrix, we leveraged an HMM-based optimization procedure (see \textit{Methods}) to determine how many events are reflected in the participant's recalls and where specifically the event boundaries fall (outlined in yellow).
-We carried out a similar analysis on all 17 participants' recall topic proportions matrices (Fig.~\corrmats).
+We used the same HMM-based optimization procedure that we had applied to the episode's topic proportions matrix (see \textit{Methods}) to estimate an analogous set of event boundaries in the participant's recounting of the episode (outlined in yellow).
+We carried out this analysis on all 17 participants' recall topic proportions matrices (Fig.~\corrmats).
 
@@
 While some participants' recall topic proportions segmented into just a few events (e.g., Participants P4, P5, and P7), others' segmented into many shorter duration events (e.g., Participants P12, P13, and P17).
-This suggests that different participants may be recalling the episode with different levels of detail---i.e., some might touch on just the major plot points, whereas others might attempt to recall every minor scene or action.
+This suggests that different participants may be recalling the episode with different levels of detail---i.e., some might recount only high-level essential plot details, whereas others might recount low-level details instead (or in addition).
 The second clear pattern present in every individual participant's recall correlation matrix was that, unlike in the episode correlation matrix, there were substantial off-diagonal correlations.
@@
 
-The above results indicate that both the structure of the original episode and participants' recalls of the episode exhibit event boundaries that can be identified automatically by characterizing the dynamic content using a shared topic model and segmenting the content into events via HMMs.
+The above results demonstrate that topic models capture the dynamic conceptual content of the episode and participants' recalls of the episode.
+Further, the episode and recalls exhibit event boundaries that can be identified automatically using HMMs to segment the dynamic content.
 Next, we asked whether some correspondence might be made between the specific content of the events the participants experienced in the episode, and the events they later recalled.
-One approach to linking the experienced (episode) and recalled events is to label each recalled event as matching the episode event with the most similar (i.e., most highly correlated) topic vector (Figs.~\ref{fig:model}G, \matchmats).
-This yields a sequence of ``presented" events from the original episode, and a (potentially differently ordered) sequence of ``recalled" events for each participant.
+We labeled each recalled event as matching the episode event with the most similar (i.e., most highly correlated) topic vector (Figs.~\ref{fig:model}G, \matchmats).
+This yielded a sequence of ``presented'' events from the original episode, and a (potentially differently ordered) sequence of ``recalled'' events for each participant.
 Analogous to classic list-learning studies, we can then examine participants' recall sequences by asking which events they tended to recall first~\citep[probability of first recall; Fig.~\ref{fig:list-learning}A;][]{AtkiShif68, PostPhil65, WelcBurn24}; how participants most often transition between recalls of the events as a function of the temporal distance between them~\citep[lag-conditional response probability; Fig.~\ref{fig:list-learning}B;][]{Kaha96}; and which events they were likely to remember overall~\citep[serial position recall analyses; Fig.~\ref{fig:list-learning}C;][]{Murd62a}.
-Interestingly, for two of these analyses (probability of first recall and lag-conditional response probability curves) we observed patterns comparable to classic effects from list-learning literature: namely, a higher probability of initiating recall with the first event in the sequence (Fig.~\ref{fig:list-learning}A) and a higher probability of transitioning to neighboring events with an asymmetric forward bias (Fig.~\ref{fig:list-learning}B).
-In contrast, we did not observe a pattern comparable to the serial position effect (Fig.~\ref{fig:list-learning}C), but rather greater memory for specific events distributed approximately evenly throughout the episode.
+Some of the patterns we observed appeared to be similar to classic effects from the list-learning literature.
+For example, participants had a higher probability of initiating recall with the first event in the sequence (Fig.~\ref{fig:list-learning}A) and a higher probability of transitioning to neighboring events with an asymmetric forward bias (Fig.~\ref{fig:list-learning}B).
+However, unlike what is typically observed in list-learning studies, we did not observe patterns comparable to the primacy or recency serial position effects (Fig.~\ref{fig:list-learning}C).
+We hypothesized that participants might be leveraging the meaningful narrative associations and references over long timescales throughout the episode.
 
-We can also apply two list-learning-native analyses that describe how participants group items in their recall sequences: temporal clustering and semantic clustering \citep[][see \textit{Methods} for details]{PolyEtal09}.~Temporal clustering refers to the extent to which participants group their recall responses according to encoding position.
-Overall, we found that sequentially viewed episode events were clustered heavily in participants' recall event sequences (mean clustering score: 0.767, SEM: 0.029), and that participants with higher temporal clustering scores tended to perform better according to both \cite{ChenEtal17}'s hand-annotated memory scores (Pearson's $r(15) = 0.62,~p = 0.008$) and our model's estimate (Pearson's $r(15) = 0.54,~p = 0.024$).
+Clustering scores are often used by memory researchers to characterize how people organize their memories of words on a studied list~\citep[for review, see][]{PolyEtal09}.
+We defined analogous measures to characterize how participants organized their memories for episodic events (see \textit{Methods} for details).
+Temporal clustering refers to the extent to which participants group their recall responses according to encoding position.
+Overall, we found that sequentially viewed episode events tended to appear nearby in participants' recall event sequences (mean clustering score: 0.767, SEM: 0.029).
+Participants with higher temporal clustering scores tended to exhibit better overall memory for the episode, according to both \cite{ChenEtal17}'s hand-counted numbers of recalled scenes from the episode (Pearson's $r(15) = 0.62,~p = 0.008$) and the numbers of episode events that best-matched at least one recalled event (i.e., model-estimated number of recalled events; Pearson's $r(15) = 0.49, p = 0.0046$).
 Semantic clustering measures the extent to which participants cluster their recall responses according to semantic similarity.
-We found that participants tended to recall semantically similar episode events together (mean clustering score: 0.787, SEM: 0.018), and that semantic clustering score was also related to both hand-annotated  (Pearson's $r(15) = 0.65,~p = 0.004$) and model-derived (Pearson's $r(15) = 0.63,~p = 0.007$) memory performance.
-% NOTE:
-% Semantic and temporal clustering are both positively correlated with n_events -- r=0.49; p=0.046 and r=0.61; p=0.009, respectively.
-% - Paxton
+We found that participants tended to recall semantically similar episode events together (mean clustering score: 0.787, SEM: 0.018), and that semantic clustering score was also related to both hand-annotated  (Pearson's $r(15) = 0.65,~p = 0.004$) and model-estimated (Pearson's $r(15) = 0.61,~p = 0.0092$) numbers of recalled events.
 
@@
 \end{figure}
-% Need to reconcile the description of distinctiveness with how we computed it... - Andy
 
-Statistical models of memory studies often treat recall success as binary (in other words, an item either was or was not recalled), or occasionally categorical \citep[e.g., to distinguish familiarity from recollection;][]{YoneEtal02}.
-Such approaches are tenable in classical list-learning or recognition memory paradigms, as the presented stimuli tend to be very simple (e.g., a sequence of individual words or items).
-However, memory for naturalistic experiences is much more nuanced.
-For example, certain aspects of an experience might be correctly remembered at varying levels of detail, or distorted, or forgotten entirely.
-Further, each remembering is itself a richly structured phenomenon.
-Our framework produces a content-based model of individual episode and recall events by projecting the dynamic content of the episode and participants' recalls into a shared topic space.
-This allows for direct, quantitative comparisons between all stimulus and recall events, as well as between the recall events themselves.
-Leveraging these content-based models of the stimulus/recall events, we developed two novel, \textit{continuous} metrics for analyzing naturalistic memory:~\textit{precision} and \textit{distinctiveness}.
-Precision is intended to capture the ``completeness'' of recall, or how fully the presented content was recapitulated in memory.
+The above analyses illustrate how our framework for characterizing the dynamic conceptual content of naturalistic episodes enables us to carry out analyses that have traditionally been applied to much simpler list-learning paradigms.
+However, perhaps the most interesting aspects of memory for naturalistic episodes are those that have no list-learning analogs.
+The nuances of how one's memory for an event might capture some details, yet distort or neglect others, is central to how we use our memory systems in daily life.
+Yet when researchers study memory in highly simplified paradigms, those nuances are not typically observable.
+We next developed two novel continuous metrics, termed precision and distinctiveness, aimed at characterizing distortions in the conceptual content of individual recalled events, and the conceptual overlap between how people described different events.
+
+\textit{Precision} is intended to capture the ``completeness'' of recall, or how fully the presented content was recapitulated in memory.
 We define a recall event's precision as the maximum correlation between the topic proportions of that recall event and any episode event (Fig.~\ref{fig:precision-distinctiveness}).
-A second novel metric we introduce here is \textit{distinctiveness}, which is intended to capture the ``specificity'' of recall.
-In other words, distinctiveness quantifies the extent to which a given recalled event reflects the most similar presented event moreso than it does other presented events.
-To compute a recall event's distinctiveness, we first identify the episode event to which its topic vector is most strongly correlated.
-We then define distinctiveness as one minus the average correlation between the given recall event and all \textit{other} episode events.
-In addition to individual events, one may also use these metrics to describe each participant's overall performance by averaging across a participant's event-wise precision or distinctiveness scores.
-Participants whose recall events are more veridical descriptions of what happened in the episode event will presumably have higher precision scores.
-We find that, across participants, higher precision scores are positively correlated with both hand-annotated memory performance (as collected by Chen et al., 2017; Pearson's $r(15) = 0.60, p = 0.010$) and the number of episode events successfully remembered, as determined by our model (Pearson's $r(15) = 0.90, p < 0.001$).
-We also hypothesized that participants who recounted events in a more distinctive way would display better overall memory.
-We find that participants' distinctiveness scores were positively
-correlated with our model's estimated number of recall events (Pearson's $r(15) = 0.55, p = 0.021$).
-However, we found no evidence that distinctiveness scores were correlated with hand-annotated memory performance (Pearson's $r(15) = 0.28, p = 0.275$).
-We elaborate on this potential discrepency in the \textit{Discussion} section.
+In other words, given that a recalled event best matches a particular episode event, more precisely recalled events overlap more strongly with the conceptual content of the original episode event.
+When a given event is assigned a blend of several topics, as is often the case (Fig.~\ref{fig:model}), a high precision score requires recapitulating the relative topic proportions during recall.
+
+A second novel metric we developed is \textit{distinctiveness}, which is intended to capture the ``specificity'' of recall.
+In other words, distinctiveness quantifies the extent to which a given recalled event reflects the most similar episode event over and above its reflection of other episode events.
+Intuitively, distinctiveness is like a normalized variant of our precision metric.
+Whereas precision solely measures how much detail about an episode was captured in someone's recall, distinctiveness penalizes details that also pertain to other episode events.
+We define the distinctiveness of an event's recall as its precision expressed in standard deviation units with respect to other episode events.
+Specifically, for a given recall event, we compute the correlation between its topic vector and that of each episode event.
+This yields a distribution of correlation coefficients (one per episode event).
+We subtract the mean and divide by the standard deviation of this distribution to $z$-score the coefficients.
+The maximum value in this distribution (which, by definition, belongs to the episode event that best matches the given recall event) is the recall event's distinctiveness score.
+In this way, recall events that match one episode event far better than all other episode events will receive a high distinctiveness score.
+By contrast, a recall event that matches all episode events roughly equally will receive a comparatively low distinctiveness score.
+
+In addition to examining how precisely and distinctively participants recalled individual events, one may also use these metrics to summarize each participant's performance by averaging across a participant's event-wise precision or distinctiveness scores.
+This enables us to quantify how precisely a participant tended to recall subtle within-event details, as well as how specific (distinctive) those details were to individual events from the episode.
+Participants' average precision and distinctiveness scores were strongly correlated ($r(15) = 0.90, p < 10^{-5}$).
+This indicates that participants who tended to precisely recount low-level details of episode events also tended to do so in an event-specific way (e.g., as opposed to detailing recurring themes that were present in most or all episode events; this strategy would have resulted in high precision but low distinctiveness).
+We found that, across participants, higher precision scores were positively correlated with both the hand-annotated ($r(15) = 0.60, p = 0.010$) and model-estimated ($r(15) = 0.90, p < 0.001$) numbers of events that participants recalled.
+Participants' average distinctiveness scores were also correlated with both the hand-annotated ($r(15) = 0.45, p = 0.068$) and model-estimated ($r(15) = 0.71, p = 0.001$) numbers of recalled events.
 
@@
 episode events are ordered along the $x$-axis by the average precision with which they were remembered.
-\textbf{B.} The set of ``Narrative Details" episode annotations (generated by \citealp{ChenEtal17}) for scenes comprising an example episode event (22) identified by the HMM.
+\textbf{B.} The set of ``Narrative Details'' episode annotations (generated by \citealp{ChenEtal17}) for scenes comprising an example episode event (22) identified by the HMM.
 Each action or feature is highlighted in a different color.
@@
 Kernel density estimates for each episode event's distribution of recall distinctiveness scores, analogous to Fig.~\ref{fig:precision-detail}A.
-\textbf{B.} The sets of ``Narrative Details" episode annotations (generated by \citealp{ChenEtal17}) for scenes comprising episode events described by the example participants in panel C.
+\textbf{B.} The sets of ``Narrative Details'' episode annotations (generated by \citealp{ChenEtal17}) for scenes comprising episode events described by the example participants in panel C.
 Each event's text is highlighted in a different color.
@@
 
-Further intuition for the behaviors captured by these two metrics may be gained by directly examining the content of the episode and recalls our framework models.
-In Figure \ref{fig:precision-detail}, we contrast recalls for the same episode event (event 22) from two participants: one with a high precision score (P17), the other with a low precision score (P6).
+Examining individual recalls of the same episode event can provide insights into how the above precision and distinctiveness scores may be used to characterize similarities and differences in how different people describe the same shared experience.
+In Figure \ref{fig:precision-detail}, we compare recalls for the same episode event (event 22) from two participants: one with a high precision score (P17), and the other with a low precision score (P6).
 From the HMM-identified event boundaries, we recovered the set of annotations describing the content of an example episode event (Fig.~\ref{fig:precision-detail}B), and divided them into different color-coded sections for each action or feature described.
-We then similarly recovered the set of sentences comprising the corresponding recall event for each of the two example participants.
-Because the recall sliding windows overlap heavily, and each recall event spans multiple recall timepoints (i.e., windows), we have stripped any sentences from the beginning and end that describe earlier or later episode events for the sake of readability.
-In other words, Fig.~\ref{fig:precision-detail}C shows a subset of the full recall event text, comprising sentences between the first and last descriptions of content from the example episode event.
-We then colored all words describing actions and features coded in panel B by their corresponding color.
-Visual comparison of these example transcripts reveals that the more precise recall captures more of the episode event's content, and with more detail.
+We used an analogous approach to identify the set of sentences comprising the corresponding recall events for each of the two example participants.
+Because the recall sliding windows overlap heavily, and each recall event spans multiple recall timepoints (i.e., windows), we have (manually) stripped any sentences from the beginning and end that describe earlier or later episode events for the sake of readability.
+In other words, Fig.~\ref{fig:precision-detail}C shows excerpts of two participants' recall transcripts that comprised sentences between the first and last descriptions of content from the example episode event.
+We then colored all words describing actions and features in the transcripts shown in Panel C according to the color-coded annotations in Panel B.
+Visual comparison of these example recalls reveals that the more precise recall captures more of the episode event's content, and in greater detail.
 
-Figure \ref{fig:distinctiveness-detail} similarly contrasts two example participants' recalls for a common episode event (event 19) to illustrate the tangible differences between high and low distinctiveness scores.
-Here, we have extracted the full set of sentences comprising the most distinctive recall event (P13) and least distinctive recall event (P11) matched to the example episode event (Fig.~\ref{fig:distinctiveness-detail}C).
+Figure \ref{fig:distinctiveness-detail} illustrates the differences between high and low distinctiveness scores for the same event detailed in Figure~\ref{fig:precision-detail} (i.e., event 22).
+Here, we have extracted the set of sentences comprising the most distinctive recall event (P9) and least distinctive recall event (P6) matched to the example episode event (Fig.~\ref{fig:distinctiveness-detail}C).
 We also extracted the annotations for the example episode event, as well as those from each other episode event whose content the example participants' single recall events described (Fig.~\ref{fig:distinctiveness-detail}B).
-We then shaded the annotation text for each episode event with a different color, and shaded each word of the example participants' recall text by the color of the episode event it describes.
-The majority of the most distinctive recall event text describes episode event 19's content, with the first five and last one sentence describing the episode events immediately preceding and succeeding the current one, respectively.
+We assigned each episode event a unique color (Panel B) and colored each recalled phrase or sentence (Panel C) according to the episode events they best matched.
+The majority of the most distinctive recall event text describes episode event 22's content, with the first five and last one sentence describing the episode events immediately preceding and succeeding the current one, respectively.
 In contrast, the least distinctive recall of episode event 19 blends the content from five separate episode events, does not transition between them in order, and often combines descriptions of two episode events' content in the same sentence.
 
-The prior analyses leverage the correspondence between the 100-dimensional topic proportion matrices for the episode and participants' recalls to characterize recall.
-However, it is difficult to gain deep insights into the content of (or relationships between) experiences and memories solely by examining these topic proportions (e.g., Figs.~\ref{fig:model}A, D) or the corresponding correlation matrices (Figs.~\ref{fig:model}B, E, \corrmats).
-And while we can directly examine the original text underlying these topic vectors (e.g., Figs.~\ref{fig:precision-detail},~\ref{fig:distinctiveness-detail}) to show how relationships between them reflect real-world behavior, this comparison becomes prohibitively cumbersome at larger timescales.
-To visualize the time-varying high-dimensional content in a more intuitive way~\citep{HeusEtal18a}, we projected the topic proportions matrices onto a two-dimensional space using Uniform Manifold Approximation and Projection~\citep[UMAP; ][]{McInEtal18}.
+The preceding analyses sought to characterize how participants' recountings of individual episode events captured the low-level details of each event.
+Next we sought to characterize how participants' recountings of the full episode captured its high-level essence-- i.e., the shape of the episode's trajectory through topic space.
+To visualize the essence of the episode and each participant's recall trajectory~\citep{HeusEtal18a}, we projected the topic proportions matrices for the episode and recalls onto a shared two-dimensional space using Uniform Manifold Approximation and Projection~\citep[UMAP; ][]{McInEtal18}.
 In this lower-dimensional space, each point represents a single episode or recall event, and the distances between the points reflect the distances between the events' associated topic vectors (Fig.~\ref{fig:trajectory}).
@@
 We observed that the locations traversed by nearly the entire episode trajectory exhibited such peaks.
-In other words, participants exhibited similar trajectories that also matched the trajectory of the original episode (Fig.~\ref{fig:trajectory}C).
-This is especially notable when considering the fact that the number of events participants recalled (dots in Fig.~\ref{fig:trajectory}C) varied considerably across people, and that every participant used different words to describe what they had remembered happening in the episode.
+In other words, participants' recalls exhibited similar trajectories to each other that also matched the trajectory of the original episode (Fig.~\ref{fig:trajectory}C).
+This is especially notable when considering the fact that the numbers of events participants recalled (dots in Fig.~\ref{fig:trajectory}C) varied considerably across people, and that every participant used different words to describe what they had remembered happening in the episode.
 Differences in the numbers of remembered events appear in participants' trajectories as differences in the sampling resolution along the trajectory.
-We note that this framework also provides a means of disentangling classic ``proportion recalled'' measures (i.e., the proportion of episode events described in participants' recalls) from participants' abilities to recapitulate the overall unfolding of the original episode's content (i.e., the similarity between the shapes of the original episode trajectory and that defined by each participant's recounting of the episode).
-% ------ NOTE: ------
-% not sure it's accurate to use "topic space" in paragraph above.  These analyses were all conducted in the 2D manifold space
-% - Paxton
-% I added "reduced" before the first reference and second reference to topic space to make it clear the analyses were performed on the 2D space. - Andy
+We note that this framework also provides a means of disentangling classic ``proportion recalled'' measures (i.e., the proportion of episode events described in participants' recalls) from participants' abilities to recapitulate the episode's essence (i.e., the similarity between the shapes of the original episode trajectory and that defined by each participant's recounting of the episode).
 
-In addition to the more ``holistic'' measure of memory described in the previous section, our framework also affords the ability to drill down to individual words and quantify how each word relates to the  memorability of each event.
+In addition to enabling us to visualize the episode's high-level essence, describing the episode as a geometric trajectory also enables us to drill down to individual words and quantify how each word relates to the memorability of each event.
+This provides another approach to examining participants' recall for low-level details beyond the precision and distinctiveness measures we defined above.
 The results displayed in Figures \ref{fig:list-learning}C and \ref{fig:precision-detail}A suggest that certain events were remembered better than others.
-Given this, we next asked asked whether the events were generally remembered well or poorly tended to reflect particular content.
+Given this, we next asked asked whether the events were generally remembered precisely or imprecisely tended to reflect particular content.
 Because our analysis framework projects the dynamic episode content and participants' recalls into a shared space, and because the dimensions of that space represent topics (which are, in turn, sets of weights over known words in the vocabulary), we are able to recover the weighted combination of words that make up any point (i.e., topic vector) in this space.
@@
 We then computed a weighted average of the topic vectors for each episode event, where the weights reflected how reliably each event was recalled.
-To visualize the result, we created a ``wordle'' image~\citep{MuelEtal18} where words weighted more heavily by better-remembered topics appear in a larger font (Fig.~\ref{fig:topics}B, green box).
-Across the full episode, content that reflected topics necessary to convey the central focus of the episode (e.g., the names of the two main characters, ``Sherlock'' and ``John,'' and the address of a major recurring location, ``221B Baker Street") were best remembered.
-An analogous analysis revealed which themes were poorly remembered.
-Here in computing the weighted average over events' topic vectors, we weighted each event in \textit{inverse} proportion to how well it was remembered (Fig.~\ref{fig:topics}B, red box).
-The least well-remembered episode content reflected information not necessary to later convey a general summary of the episode, such as the proper names of relatively minor characters (e.g., ``Mike," ``Molly," and ``Lestrade") and locations (e.g., ``St.
-Bartholomew's Hospital").
-%, as well as the brief, animated clip participants viewed at the beginning of each of the two scan session (involving ``singing" ``cartoon" characters).
+To visualize the result, we created a ``wordle'' image~\citep{MuelEtal18} where words weighted more heavily by more precisely-remembered topics appear in a larger font (Fig.~\ref{fig:topics}B, green box).
+Across the full episode, content that reflected topics necessary to convey the central focus of the episode (e.g., the names of the two main characters, ``Sherlock'' and ``John,'' and the address of a major recurring location, ``221B Baker Street'') were best remembered.
+An analogous analysis revealed which themes were less-precisely remembered.
+Here in computing the weighted average over events' topic vectors, we weighted each event in \textit{inverse} proportion to how precisely it was remembered (Fig.~\ref{fig:topics}B, red box).
+The least precisely remembered episode content reflected information not necessary to later convey a general summary of the episode, such as the proper names of relatively minor characters (e.g., ``Mike,'' ``Molly,'' and ``Lestrade'') and locations (e.g., ``St.
+Bartholomew's Hospital'').
 
@@
 We ran \texttt{Neurosynth} on the significance maps for the episode- and recall-driven searchlight analyses.
-These maps, along with the 10 terms with maximally similar meta-analysis images identified by \texttt{Neurosynth} are shown in Figure \ref{fig:neurosynth}.
+These maps, along with the 10 terms with maximally similar meta-analysis images identified by \texttt{Neurosynth} are shown in Figure \ref{fig:brainz}.
 
-\begin{figure}[t]
-\centering
-\includegraphics[width=1\textwidth]{figs/neurosynth_decoding}
-\caption{\small \textbf{Decoding distributed statistical maps via Neurosynth meta-analyses.} \textbf{A.} episode-searchlight significance and top 10 decoded terms.
+% \begin{figure}[tp]
+% \centering
+% \includegraphics[width=1\textwidth]{figs/neurosynth_decoding}
+% \caption{\small \textbf{Decoding distributed statistical maps via Neurosynth meta-analyses.} \textbf{A.} episode-searchlight significance and top 10 decoded terms.
 We constructed a map of the permutation-derived $p$-values for the episode-driven searchlight analysis (Fig.~\ref{fig:brainz}A, C) at each voxel with a positive permutation-derived $z$-score.
@@
 The top 10 terms decoded from this significance map are shown in blue.}
-\label{fig:neurosynth}
-\end{figure}
-\FloatBarrier
+% \label{fig:neurosynth}
+% \end{figure}
 
@@
 
-In extending classical free recall analyses to our naturalistic memory framework, we recovered two patterns of recall dynamics central to list-learning studies: a heightened probability of initiating recall with the first presented ``item" (in our case, episode events; Fig.~\ref{fig:list-learning}A) and a strong bias toward transitioning from recalling a given event to recalling the one immediately following it (Fig.~\ref{fig:list-learning}B).
+In extending classical free recall analyses to our naturalistic memory framework, we recovered two patterns of recall dynamics central to list-learning studies: a heightened probability of initiating recall with the first presented ``item'' (in our case, episode events; Fig.~\ref{fig:list-learning}A) and a strong bias toward transitioning from recalling a given event to recalling the one immediately following it (Fig.~\ref{fig:list-learning}B).
 However, equally noteworthy are the typical free recall results \textit{not} recovered in these analyses, as each highlights a fundamental difference between the list-learning paradigm and naturalistic memory paradigms like the one employed in the present study.
@@
 As a result, each moment of our experience tends to be inherently more similar to surrounding moments than to those in the distant past or future.
-Memory literature has termed this strong temporal autocorrelation ``context," and in various media that depict real-world events (e.g., movies or written stories), we recognize it as a \textit{narrative structure}.
+Memory literature has termed this strong temporal autocorrelation ``context,'' and in various media that depict real-world events (e.g., movies or written stories), we recognize it as a \textit{narrative structure}.
 While a random word list (by definition) has no such structure, the logical progression between ideas and actions in a naturalistic stimulus prompts the rememberer to recount presented events in order, starting with the beginning.
@@
 In an attempt to address this shortcoming, we have developed a framework in the present study that characterizes the explicit semantic content of the stimulus and subsequent recalls.
-However, sensitivity to stimulus and recall content introduces a new challenge: distinguishing between levels of recall quality for a stimulus (e.g., an event) that is considered to have been ``remembered."  When modeling memory in an experimental setting, recall quality for individual events is often cast as binary (e.g., a given list item was simply either remembered or not remembered).
+However, sensitivity to stimulus and recall content introduces a new challenge: distinguishing between levels of recall quality for a stimulus (e.g., an event) that is considered to have been ``remembered.''  When modeling memory in an experimental setting, recall quality for individual events is often cast as binary (e.g., a given list item was simply either remembered or not remembered).
 Various models of memory (e.g., \citealp{Yone02}) attempt to improve upon this by including confidence ratings, rendering this binary judgement instead categorical.
 To better evaluate naturalistic memory quality, we introduce a continuous metric (\textit{precision}), which reflects the level of completeness of a participant's recall for a feature-rich experience.
-Additionally, recall quality for a single event is typically assessed independently from that for all other events (e.g., it is difficult to ``compare" a participant's binary recall success for list item 1 to that of list item 10).
+Additionally, recall quality for a single event is typically assessed independently from that for all other events (e.g., it is difficult to ``compare'' a participant's binary recall success for list item 1 to that of list item 10).
 The second novel metric we introduce (\textit{distinctiveness}) is based on analyzing of the correlational structure of an individual's full set of recall events, and reflects the specificity of their memory for a single experienced event.
@@
 Decoding the associated significance maps with \texttt{Neurosynth} revealed two intriguing results.
-First, the top 10 terms returned for the episode-driven searchlight significance map were centered around themes of language and semantic meaning (Fig.~\ref{fig:neurosynth}A).
+First, the top 10 terms returned for the episode-driven searchlight significance map were centered around themes of language and semantic meaning (Fig.~\ref{fig:brainz}).
 In other words, the voxels identified as more reflective of the episode content's temporal structure (i.e., voxels with lower permutation correction-derived $p$-values), as defined by our model, were most likely to be reported as active in studies focused on the the neural underpinnings of semantic processing.
@@
 Our second searchlight analysis identified a partially overlapping network of regions (Fig.~\ref{fig:brainz}D) whose patterns of activity as participants viewed the episode reflected the idiosyncratic structure of each individual's later recalls.
-The associated significance map yielded a set of \texttt{Neurosynth} terms that primarily reflected names of specific structural regions (such as ``thalamus," ``anterior insula," ``anterior cingulate" and ``inferior frontal"; Fig.~\ref{fig:neurosynth}B).
-Interestingly, these regions share membership in a common, large-scale functional network (termed the ``salience network") involved in detecting and processing affective cues.
+The associated significance map yielded a set of \texttt{Neurosynth} terms that primarily reflected names of specific structural regions (such as ``thalamus,'' ``anterior insula,'' ``anterior cingulate'' and ``inferior frontal''; Fig.~\ref{fig:brainz}).
+Interestingly, these regions share membership in a common, large-scale functional network (termed the ``salience network'') involved in detecting and processing affective cues.
 In particular, the latter three regions have been implicated in functions relevant to assigning personal meaning to an experience, including: ascribing subjective value to raw, sensory input \citep{MedfCrit10}; modulating semantic and phonological processing in response to personally salient stimuli \citep{KellEtal07b}; and directing and reallocating attention and working memory resources towards the most relevant stimuli \citep{MenoUddi10}.
@@
 
-The video stimulus was divided into 1,000 fine-grained ``scenes" and annotated by an independent coder.
+The video stimulus was divided into 1,000 fine-grained ``scenes'' and annotated by an independent coder.
 For each of these 1,000 scenes, the following information was recorded: a brief narrative description of what was happening, the location where the scene took place, whether that location was indoors or outdoors, the names of all characters on-screen, the name(s) of the character(s) in focus in the shot, the name(s) of the character(s) currently speaking, the camera angle of the shot, a transcription of any text appearing on-screen, and whether or not there was music present in the background.
@@
 To assess the significance of the match between the episode and recall trajectories, we carried out a permutation procedure whereby, for each of 10000 repetitions, we circularly shifted the recall trajectories (in time) by a random amount and then re-computed the RMSD each time.
-This yielded a distribution of ``null'' RMSD values for each participant.
+This yielded a distribution of ``null" RMSD values for each participant.
 The observed RMSD values reached significance (i.e., $p < 0.05$, reflecting that more than 95\% of the null RMSD values were greater than the observed RMSD value) for nine of the participants (3, 4, 8--13, and 17).
@@
 We further sought to ensure that our analysis identified regions where the activations’ temporal structure specifically reflected that of the episode, rather than regions whose activity was simply autocorrelated at a width similar to the episode template’s diagonal.
-To achieve this, we used a phase shift-based permutation procedure, whereby we circularly shifted the episode’s topic trajectory by a random number of timepoints, computed the resulting ``null” episode template, and re-ran the searchlight analysis, in full.
+To achieve this, we used a phase shift-based permutation procedure, whereby we circularly shifted the episode’s topic trajectory by a random number of timepoints, computed the resulting ``null'' episode template, and re-ran the searchlight analysis, in full.
 (For each of the 100 permutations, the same random shift was used for all participants).
-We $z$-scored the observed (unshifted) result at each voxel against the distribution of permutation-derived ``null” results, and estimated a $p$-value by computing the proportion of shifted results that yielded larger values.
+We $z$-scored the observed (unshifted) result at each voxel against the distribution of permutation-derived ``null'' results, and estimated a $p$-value by computing the proportion of shifted results that yielded larger values.
 To create the map in Figure~\ref{fig:brainz}C, we thresholded out any voxels whose similarity to the unshifted episode’s structure fell below the 95\textsuperscript{th} percentile of the permutation-derived similarity results.

### 2020-08-28 paper/main.tex
added paxton's distinctiveness figure from slack, minor formatting tweaks
detailed pass through paper up until end of discussion section, with major edits to discussion.  still need to go through methods section carefully

@@
 We also demonstrate how \textit{memories} may also be modeled as trajectories through the same spaces.
-According to this view, encoding an experience into memory entails geometrically distorting or transforming the \textit{shape} of the original experience's trajectory.
-This translates qualitative, neuropsychological questions about how we remember naturalistic experiences into quantitive, geometric questions about the spatial configurations of trajectory shapes.
+According to this view, encoding an experience into memory entails geometrically preserving, distorting, or transforming the \textit{shape} of the original experience's trajectory.
+This translates qualitative neuropsychological questions about how we remember naturalistic experiences into quantitive geometric questions about the spatial configurations of trajectory shapes.
 We applied our framework to data collected as participants watched and verbally recounted a television episode while undergoing functional neuroimaging.
-We found that the trajectories of participants' recountings of the episode nearly all captured the coarse spatial properties of the original episode's trajectory (i.e., the essential plot points), but participants differed in their memory for fine details.
+We found that the trajectories of participants' recountings of the episode nearly all captured the coarse spatial properties of the original episode's trajectory (i.e., the essential plot points), but participants differed in their memory for low-level details.
 We also identified a network of brain structures that were sensitive to the shape of the episode's trajectory through word embedding space, and an overlapping network that predicted, at the time of encoding, how people would distort (transform) the episode's trajectory when they recounted the episode later.
-Our work provides insights into how our brains distort and transform our ongoing experiences when we encode them into episodic memories.
+Our work provides insights into how our brains preserve, distort, and transform our ongoing experiences when we encode them into episodic memories.
 \end{abstract}
@@
 What does it mean to \textit{remember} something?
-In traditional episodic memory experiments \citep[e.g., list-learning or trial-based experiments;][]{Murd62a, Kaha96}, remembering is often cast as a discrete and binary operation: each studied item may be separated from the rest of one's experience and singularly labeled as having been recalled or forgotten.
-More nuanced studies might incorporate self-reported confidence measures as a proxy for memory strength, or ask participants to discriminate between ``recollecting'' the (contextual) details of an experience or having a general feeling of ``familiarity'' \citep{Yone02}.
-Using well-controlled, trial-based experimental designs, the field has amassed a wealth of information regarding human episodic memory.
+In traditional episodic memory experiments \citep[e.g., list-learning or trial-based experiments;][]{Murd62a, Kaha96}, remembering is often cast as a discrete binary operation: each studied item may be separated from the rest of one's experience and labeled as having been either recalled or forgotten.
+More nuanced studies might incorporate self-reported confidence measures as a proxy for memory strength, or ask participants to discriminate between recollecting the (contextual) details of an experience or having a general feeling of familiarity~\citep{Yone02}.
+Using well-controlled, trial-based experimental designs, the field has amassed a wealth of information regarding human episodic memory~\citep[for review see][]{Kaha12}.
 However, there are fundamental properties of the external world and our memories that trial-based experiments are not well suited to capture~\citep[for review, also see][]{KoriGold94, HukEtal18}.
-First, our experiences and memories are continuous, rather than discrete---isolating a (naturalistic) event from the context in which it occurs can substantially change its meaning.
+First, our experiences and memories are continuous, rather than discrete---isolating a naturalistic event from the context in which it occurs can substantially change its meaning.
 Second, whether or not the rememberer has precisely reproduced a specific set of words in describing a given experience is nearly orthogonal to how well they were actually able to remember it.
 In classic (e.g., list-learning) memory studies, by contrast, the number or proportion of \textit{exact} recalls is often considered to be a primary metric for assessing the quality of participants' memories.
-Third, one might remember the \textit{essence} (or a general summary) of an experience but forget (or neglect to recount) particular details.
-Capturing the essence of what happened is often a main goal of recounting an episodic memory to a listener, whereas the inclusion of specific, low-level details is often less pertinent.
+Third, one might remember the essence (or a general summary) of an experience but forget (or neglect to recount) particular low-level details.
+Capturing the essence of what happened is often a main goal of recounting an episodic memory to a listener, whereas the inclusion of specific low-level details is often less pertinent.
 
@@
 
-Occasionally, this gradual ``drift'' of our ongoing experience is punctuated by sudden changes, or ``shifts''~\citep[e.g., when we walk through a doorway; ][]{RadvZack17}.
+Occasionally, this gradual drift of our ongoing experience is punctuated by sudden changes, or shifts~\citep[e.g., when we walk through a doorway; ][]{RadvZack17}.
 Prior research suggests that these sharp transitions (termed \textit{event boundaries}) help to discretize our experiences (and their mental representations) into \textit{events}~\citep{RadvZack17, BrunEtal18, HeusEtal18b, ClewDava17, EzzyDava11, DuBrDava13}.
-The interplay between the stable (within-event) and transient (across-event) temporal dynamics of an experience also provides a potential framework for transforming experiences into memories that distills those experiences down to their essence.
+The interplay between the stable (within-event) and transient (across-event) temporal dynamics of an experience also provides a potential framework for transforming experiences into memories that distills those experiences down to their essences.
 For example, prior work has shown that event boundaries can influence how we learn sequences of items~\citep{HeusEtal18b, DuBrDava13}, navigate~\citep{BrunEtal18}, and remember and understand narratives~\citep{ZwaaRadv98, EzzyDava11}.
@@
 
-Here, we sought to examine how the temporal dynamics of a ``naturalistic'' experience were later reflected in participants' memories.
-We also sought to leverage the above conceptual insights into the distinctions between an experience's essence and low-level details to build models that explicitly quantified these distinctions.
-We analyzed an open dataset that comprised behavioral and functional Magnetic Resonance Imaging (fMRI) data collected as participants viewed and then verbally recounted an episode of the BBC television series \textit{Sherlock}~\citep{ChenEtal17}.
+Here, we sought to examine how the temporal dynamics of a naturalistic experience were later reflected in participants' memories.
+We also sought to leverage the above conceptual insights into the distinctions between an experience's essence and its low-level details to build models that explicitly quantified these distinctions.
+We analyzed an open dataset that comprised behavioral and functional Magnetic Resonance Imaging (fMRI) data collected as participants viewed and then verbally recounted an episode of the BBC television show \textit{Sherlock}~\citep{ChenEtal17}.
 We developed a computational framework for characterizing the temporal dynamics of the moment-by-moment content of the episode, and of participants' verbal recalls.
-Specifically, we use topic modeling~\citep{BleiEtal03} to characterize the thematic conceptual (semantic) content present in each moment of the episode and recalls, and hidden Markov models~\citep{Rabi89, BaldEtal17} to discretize this evolving semantic content into events.
+Our framework uses topic modeling~\citep{BleiEtal03} to characterize the thematic conceptual (semantic) content present in each moment of the episode and recalls and hidden Markov models~\citep{Rabi89, BaldEtal17} to discretize this evolving semantic content into events.
 In this way, we cast both naturalistic experiences and memories of those experiences as geometric \textit{trajectories} that describe how they evolve over time.
-Under this framework, successful remembering entails verbally ``traversing'' the content trajectory of the episode, thereby reproducing the shape (essence) of the original experience.
+Under this framework, successful remembering entails verbally traversing the content trajectory of the episode, thereby reproducing the shape (essence) of the original experience.
 Our framework captures the episode's essence in the sequence of geometric coordinates for its events, and its low-level details by examining its within-event geometric properties.
@@
 Comparing the overall shapes of the topic trajectories for the episode and participants' recalls reveals which aspects of the episode's essence were preserved (or discarded) in the translation into memory.
-We also develop two metrics for assessing participants' memories for low-level details: (1) the \textit{precision} with which a participant recounts details about each event, and (2) the \textit{distinctiveness} of each recall event, relative to other recalled events.
+We also develop two metrics for assessing participants' memories for low-level details: (1) the \textit{precision} with which a participant recounts details about each event, and (2) the \textit{distinctiveness} of each recalled event, relative to other events.
 We examine how these metrics relate to overall memory performance as judged by third-party human annotators.
 We also compare and contrast our general approach to studying memory for naturalistic experiences with standard metrics for assessing performance on more traditional memory tasks, such as list-learning.
-Last, we leverage our framework to identify networks of brain structures whose responses (as participants watched the episode) reflected the temporal dynamics of either the episode or how participants would later recount it.
+Last, we leverage our framework to identify networks of brain structures whose responses (as participants watched the episode) reflected the temporal dynamics of the episode and/or how participants would later recount it.
 
@@
 This information included: a brief narrative description of what was happening, the location where the scene took place, the names of any characters on the screen, and other similar details (for a full list of annotated features, see \textit{Methods}).
-We took from these annotations the union of all unique words (excluding stop words, such as ``and,'' ``or,'' ``but,'' etc.) across all features and scenes as the ``vocabulary'' for the topic model.
-We then concatenated the sets of words across all features contained in overlapping sliding windows of (up to) 50 scenes, and treated each window as a single ``document'' for the purpose of fitting the topic model.
+We took from these annotations the union of all unique words (excluding stop words, such as ``and,'' ``or,'' ``but,'' etc.) across all features and scenes as the vocabulary for the topic model.
+We then concatenated the sets of words across all features contained in overlapping sliding windows of (up to) 50 scenes, and treated each window as a single document for the purpose of fitting the topic model.
 Next, we fit a topic model with (up to) $K = 100$ topics to this collection of documents.
 We found that 32 unique topics (with non-zero weights) were sufficient to describe the time-varying content of the episode (see \textit{Methods}; Figs.~\ref{fig:schematic}, \topics).
-Note that our approach is similar in some respects to Dynamic Topic Models~\citep{BleiLaff06}, in that we sought to characterize how the thematic content of the episode evolved over time.
+We note that our approach is similar in some respects to Dynamic Topic Models~\citep{BleiLaff06}, in that we sought to characterize how the thematic content of the episode evolved over time.
 However, whereas Dynamic Topic Models are designed to characterize how the properties of \textit{collections} of documents change over time, our sliding window approach allows us to examine the topic dynamics within a single document (or video).
@@
 Three example episode frames (first row) and their associated descriptions (second row) are displayed.
-The third row shows an example participant's later recalls of the same three scenes.
+The third row shows an example participant's recountings of the same three scenes.
 We used the topic model (fit to the episode annotations) to estimate topic vectors for each moment of the episode and each sentence of participants' recalls.
@@
 The topic vectors for each timepoint were also \textit{sparse}, in that only a small number (typically one or two) of topics tended to be ``active'' in any given timepoint (see Fig.~\ref{fig:model}A).
-Further, the dynamics of the topic activations appeared to exhibit \textit{persistence} (i.e., given that a topic was active in one timepoint, it was likely to be active in the following timepoint) along with \textit{occasional rapid changes} (i.e., occasionally topics would appear to spring into or out of existence).
+Further, the dynamics of the topic activations appeared to exhibit \textit{persistence} (i.e., given that a topic was active in one timepoint, it was likely to be active in the following timepoint) along with \textit{occasional rapid changes} (i.e., occasionally topic weights would change abruptly from one timepoint to the next).
 These two properties of the topic dynamics may be seen in the block diagonal structure of the timepoint-by-timepoint correlation matrix (Fig.~\ref{fig:model}B) and reflect the gradual drift and sudden shifts fundamental to the temporal dynamics of many real-world experiences, as well as television episodes.
 Given this observation, we adapted an approach devised by \cite{BaldEtal17}, and used a hidden Markov model (HMM) to identify the \textit{event boundaries} where the topic activations changed rapidly (i.e., the boundaries of the blocks in the temporal correlation matrix; event boundaries identified by the HMM are outlined in yellow in Fig.~\ref{fig:model}B).
-Part of our model fitting procedure required selecting an appropriate number of ``events'' into which the topic trajectory should be segmented.
+Part of our model fitting procedure required selecting an appropriate number of events into which the topic trajectory should be segmented.
 To accomplish this, we used an optimization procedure that maximized the difference between the topic weights for timepoints within an event versus timepoints across multiple events (see \textit{Methods} for additional details).
-We then created a stable ``summary'' of the content within each episode event by averaging the topic vectors across the timepoints spanned by each event (Fig.~\ref{fig:model}C).
+We then created a stable summary of the content within each episode event by averaging the topic vectors across the timepoints spanned by each event (Fig.~\ref{fig:model}C).
 
@@
 \end{figure}
-% I'm all for citing software packages, but where what's the distinction between packages we do cite (seaborn, brainiak, sklearn, hypertools, quail, umap, etc.) and don't cite (wordcloud, nilearn, fastdtw, etc.)?
-% - Paxton
-% I also flagged the seaborn reference for removal here. Def not critical to understanding the figure - Andy
 
@@
 We applied the same topic model (already trained on the episode annotations) to each participant's recalls.
-Analogously to how we parsed the time-varying content of the episode, to obtain similar estimates for each participant's recall transcript, we treated each overlapping  window of (up to 10) sentences from their transcript as a ``document,'' and computed the most probable mix of topics reflected in each timepoint's sentences.
+Analogously to how we parsed the time-varying content of the episode, to obtain similar estimates for each participant's recall transcript, we treated each overlapping  window of (up to 10) sentences from their transcript as a document, and computed the most probable mix of topics reflected in each timepoint's sentences.
 This yielded, for each participant, a number-of-windows by number-of-topics topic proportions matrix that characterized how the topics identified in the original episode were reflected in the participant's recalls.
 An important feature of our approach is that it allows us to compare participants' recalls to events from the original episode, despite that different participants used widely varying language to describe the events, and that those descriptions often diverged in content and quality from the episode annotations.
-This ability to match up conceptually related text that differs in specific vocabulary, detail, and length is an important benefit of projecting the episode and recalls into a shared ``topic'' space.
+This ability to match up conceptually related text that differs in specific vocabulary, detail, and length is an important benefit of projecting the episode and recalls into a shared topic space.
 An example topic proportions matrix from one participant's recalls is shown in Figure~\ref{fig:model}D.
@@
 This yielded a sequence of ``presented'' events from the original episode, and a (potentially differently ordered) sequence of ``recalled'' events for each participant.
-Analogous to classic list-learning studies, we can then examine participants' recall sequences by asking which events they tended to recall first~\citep[probability of first recall; Fig.~\ref{fig:list-learning}A;][]{AtkiShif68, PostPhil65, WelcBurn24}; how participants most often transition between recalls of the events as a function of the temporal distance between them~\citep[lag-conditional response probability; Fig.~\ref{fig:list-learning}B;][]{Kaha96}; and which events they were likely to remember overall~\citep[serial position recall analyses; Fig.~\ref{fig:list-learning}C;][]{Murd62a}.
+Analogous to classic list-learning studies, we can then examine participants' recall sequences by asking which events they tended to recall first~\citep[probability of first recall; Fig.~\ref{fig:list-learning}A;][]{AtkiShif68, PostPhil65, WelcBurn24}; how participants most often transitioned between recalls of the events as a function of the temporal distance between them~\citep[lag-conditional response probability; Fig.~\ref{fig:list-learning}B;][]{Kaha96}; and which events they were likely to remember overall~\citep[serial position recall analyses; Fig.~\ref{fig:list-learning}C;][]{Murd62a}.
 Some of the patterns we observed appeared to be similar to classic effects from the list-learning literature.
@@
 
-\begin{figure}[t]
+\begin{figure}[tp]
   \centering
@@
 The example participant's overall precision score was computed as the average across correlation values in the yellow boxes.
-Their distinctiveness score was computed as the average (over recall events) of 1 minus the average correlation between each recall event and all other recall events that do not display a box in the same row.
-\textbf{B.} The (Pearson's) correlation between precision and hand-annotated memory performance.
-\textbf{C.} The correlation between distinctiveness and hand-annotated memory performance.
+Their distinctiveness score was computed as the average (over recall events) of the $z$-scored (within column) event precisions.
+\textbf{B.} The (Pearson's) correlation between precision and hand-counted number of recalled scenes.
+\textbf{C.} The correlation between distinctiveness and hand-counted number of recalled scenes.
 \textbf{D.} The correlation between precision and the number of episode events successfully recalled, as determined by our model.
@@
 
-\textit{Precision} is intended to capture the ``completeness'' of recall, or how fully the presented content was recapitulated in memory.
+\textit{Precision} is intended to capture the ``completeness'' of recall, or how fully the presented content was recapitulated in a participant's recounting.
 We define a recall event's precision as the maximum correlation between the topic proportions of that recall event and any episode event (Fig.~\ref{fig:precision-distinctiveness}).
@@
 
-A second novel metric we developed is \textit{distinctiveness}, which is intended to capture the ``specificity'' of recall.
+\textit{Distinctiveness} is intended to capture the ``specificity'' of recall.
 In other words, distinctiveness quantifies the extent to which a given recalled event reflects the most similar episode event over and above its reflection of other episode events.
@@
 We subtract the mean and divide by the standard deviation of this distribution to $z$-score the coefficients.
-The maximum value in this distribution (which, by definition, belongs to the episode event that best matches the given recall event) is the recall event's distinctiveness score.
+The maximum value in this distribution (which, by definition, belongs to the episode event that best matches the given recall event) is that recall event's distinctiveness score.
 In this way, recall events that match one episode event far better than all other episode events will receive a high distinctiveness score.
@@
 Participants' average precision and distinctiveness scores were strongly correlated ($r(15) = 0.90, p < 10^{-5}$).
-This indicates that participants who tended to precisely recount low-level details of episode events also tended to do so in an event-specific way (e.g., as opposed to detailing recurring themes that were present in most or all episode events; this strategy would have resulted in high precision but low distinctiveness).
+This indicates that participants who tended to precisely recount low-level details of episode events also tended to do so in an event-specific way (e.g., as opposed to detailing recurring themes that were present in most or all episode events; this behavior would have resulted in high precision but low distinctiveness).
 We found that, across participants, higher precision scores were positively correlated with both the hand-annotated ($r(15) = 0.60, p = 0.010$) and model-estimated ($r(15) = 0.90, p < 0.001$) numbers of events that participants recalled.
@@
 Each action or feature is highlighted in a different color.
-\textbf{C.} A subset of the sentences comprising the most precise (P17) and least precise (P6) participants' recalls of episode event 22.
-Descriptions of specific actions or features reflecting those highlighted in panel B are highlighted in the corresponding color.}
+\textbf{C.} Excerpts from the most precise (P17) and least precise (P6) participants' recalls of episode event 22.
+Descriptions of specific actions or features reflecting those highlighted in Panel B are highlighted in the corresponding color.
+The text highlighted in gray denotes a (rare) false recall.
+The unhighlighted text denotes correctly recalled information about other episode events.}
   \label{fig:precision-detail}
@@
 Each event's text is highlighted in a different color.
-\textbf{C.} The sentences comprising the most distinctive (P13) and least distinctive (P11) participants' recalls of episode event 19.
-Sections of recall describing each each episode event in panel B are highlighted with the corresponding color.}
+\textbf{C.} The sentences comprising the most distinctive (P9) and least distinctive (P6) participants' recalls of episode event 22.
+Sections of recall describing each each episode event in Panel B are highlighted with the corresponding color.}
   \label{fig:distinctiveness-detail}
@@
 We used an analogous approach to identify the set of sentences comprising the corresponding recall events for each of the two example participants.
-Because the recall sliding windows overlap heavily, and each recall event spans multiple recall timepoints (i.e., windows), we have (manually) stripped any sentences from the beginning and end that describe earlier or later episode events for the sake of readability.
-In other words, Fig.~\ref{fig:precision-detail}C shows excerpts of two participants' recall transcripts that comprised sentences between the first and last descriptions of content from the example episode event.
+Figure~\ref{fig:precision-detail}C shows excerpts of two participants' recall transcripts that comprised sentences between the first and last descriptions of content from the example episode event.
 We then colored all words describing actions and features in the transcripts shown in Panel C according to the color-coded annotations in Panel B.
@@
 We assigned each episode event a unique color (Panel B) and colored each recalled phrase or sentence (Panel C) according to the episode events they best matched.
-The majority of the most distinctive recall event text describes episode event 22's content, with the first five and last one sentence describing the episode events immediately preceding and succeeding the current one, respectively.
-In contrast, the least distinctive recall of episode event 19 blends the content from five separate episode events, does not transition between them in order, and often combines descriptions of two episode events' content in the same sentence.
+Visual inspection of Panel C reveals that the most distinctive recall's content is tightly concentrated around event 22, whereas the least distinctive recall incorporates content from a much wider range of episode events.
 
@@
 To assess the consistency of these recall trajectories across participants, we asked: given that a participant's recall trajectory had entered a particular location in the reduced topic space, could the position of their \textit{next} recalled event be predicted reliably?
-For each location in the the reduced topic space, we computed the set of line segments connecting successively recalled events (across all participants) that intersected that location (see \textit{Methods} for additional details).
+For each location in the reduced topic space, we computed the set of line segments connecting successively recalled events (across all participants) that intersected that location (see \textit{Methods} for additional details).
 We then computed (for each location) the distribution of angles formed by the lines defined by those line segments and a fixed reference line (the $x$-axis).
@@
 Because our analysis framework projects the dynamic episode content and participants' recalls into a shared space, and because the dimensions of that space represent topics (which are, in turn, sets of weights over known words in the vocabulary), we are able to recover the weighted combination of words that make up any point (i.e., topic vector) in this space.
-We first computed the average precision with which participants recalled each of the 30 episode events (Fig.~\ref{fig:topics}A; note that this result is analogous to a serial position curve created from our continuous recall quality metric).
-We then computed a weighted average of the topic vectors for each episode event, where the weights reflected how reliably each event was recalled.
+We first computed the average precision with which participants recalled each of the 30 episode events (Fig.~\ref{fig:topics}A; note that this result is analogous to a serial position curve created from our precision metric).
+We then computed a weighted average of the topic vectors for each episode event, where the weights reflected how precisely each event was recalled.
 To visualize the result, we created a ``wordle'' image~\citep{MuelEtal18} where words weighted more heavily by more precisely-remembered topics appear in a larger font (Fig.~\ref{fig:topics}B, green box).
@@
 An analogous analysis revealed which themes were less-precisely remembered.
-Here in computing the weighted average over events' topic vectors, we weighted each event in \textit{inverse} proportion to how precisely it was remembered (Fig.~\ref{fig:topics}B, red box).
-The least precisely remembered episode content reflected information not necessary to later convey a general summary of the episode, such as the proper names of relatively minor characters (e.g., ``Mike,'' ``Molly,'' and ``Lestrade'') and locations (e.g., ``St.
+Here in computing the weighted average over events' topic vectors, we weighted each event in \textit{inverse} proportion to its average precision (Fig.~\ref{fig:topics}B, red box).
+The least precisely remembered episode content reflected information that was extraneous to the episode's essence, such as the proper names of relatively minor characters (e.g., ``Mike,'' ``Molly,'' and ``Lestrade'') and locations (e.g., ``St.
 Bartholomew's Hospital'').
@@
 \includegraphics[width=1\textwidth]{figs/topics}
-\caption{\small \textbf{Language used in the most and least memorable events.} \textbf{A.} Average precision (episode event-recall event topic vector correlation) across participants for each episode event.
+\caption{\small \textbf{Language used in the most and least precisely remembered events.} \textbf{A.} Average precision (episode event-recall event topic vector correlation) across participants for each episode event.
+Here we defined each episode event's precision for each participant as the correlation between its topic vector and the most-correlated recall event's topic vector from that participant.
 Error bars denote bootstrap-derived across-participant 95\% confidence intervals.
-The stars denote the three best-remembered events (green) and worst-remembered events (red).
+The stars denote the three most precisely remembered events (green) and least precisely remembered events (red).
 \textbf{B.} Wordles comprising the top 200 highest-weighted words reflected in the weighted-average topic vector across episode events.
-Green: episode events were weighted by how well the topic vectors derived from recalls of those events matched the episode events' topic vectors (Panel A).
-Red: episode events were weighted by the inverse of how well their topic vectors matched the recalled topic vectors.
+Green: episode events were weighted their precision (Panel A).
+Red: episode events were weighted by the inverse of their precision.
 \textbf{C.}  The set of all episode and recall events is projected onto the two-dimensional space derived in Figure~\ref{fig:trajectory}.
-The dots outlined in black denote episode events (dot size reflects the average correlation between the episode event's topic vector and the topic vectors from the closest matching recalled events from each participant; bigger dots denote stronger correlations).
-The dots without black outlines denote recalled events.
+The dots outlined in black denote episode events (dot size is proportional to each event's precision).
+The dots without black outlines denote recall events from each participant.
 All dots are colored using the same scheme as Figure~\ref{fig:trajectory}A.
-Wordles for several example events are displayed (green: three best-remembered events; red: three worst-remembered events).
+Wordles for several example events are displayed (green: three most precisely remembered events; red: three least precisely remembered events).
 Within each circular wordle, the left side displays words associated with the topic vector for the episode event, and the right side displays words associated with the (average) recall event topic vector, across all recall events matched to the given episode event.}
@@
 A similar result emerged from assessing the topic vectors for individual episode and recall events (Fig.~\ref{fig:topics}C).
-Here, for each of the three best- and worst-remembered episode events, we have constructed two wordles: one from the original episode event's topic vector (left) and a second from the average recall topic vector for that event (right).
-The three best-remembered events (circled in green) correspond to scenes integral to the central plot-line: a mysterious figure spying on John in a phone booth; John meeting Sherlock at Baker St.
+Here, for each of the three most and least precisely remembered episode events, we have constructed two wordles: one from the original episode event's topic vector (left) and a second from the average recall topic vector for that event (right).
+The three most precisely remembered events (circled in green) correspond to scenes integral to the central plot-line: a mysterious figure spying on John in a phone booth; John meeting Sherlock at Baker St.
 to discuss the murders; and Sherlock laying a trap to catch the killer.
-Meanwhile, the three worst-remembered events (circled in red) reflect scenes that are non-essential to summarizing the narrative's structure: the video of singing cartoon characters participants viewed in an introductory clip prior to the main episode; John asking Molly about Sherlock's habit of over-analyzing people; and Sherlock noticing evidence of Anderson's and Donovan's affair.
+Meanwhile, the least precisely remembered events (circled in red) reflect scenes that comprise minor plot points: a video of singing cartoon characters that participants viewed in an introductory clip prior to the main episode; John asking Molly about Sherlock's habit of over-analyzing people; and Sherlock noticing evidence of Anderson's and Donovan's affair.
 
@@
 We used a searchlight procedure to identify clusters of voxels whose activity patterns displayed a proximal temporal correlation structure (as participants watched the episode) matching that of the original episode's topic proportions (Fig.~\ref{fig:brainz}A; see \textit{Methods} for additional details).
-In a second analysis, we sought to identify brain structures whose responses (during episode viewing) reflected how each participant would later structure their recounting of the episode.
-We used an analogous searchlight procedure to identify clusters of voxels whose proximal temporal correlation matrices matched that of the topic proportions for each individual's recall (Figs.~\ref{fig:brainz}B; see \textit{Methods} for additional details).
-To ensure our searchlight procedure identified regions \textit{specifically} sensitive to the temporal structure of the episode or recalls (i.e., rather than those with a temporal autocorrelation length similar to that of the episode/recalls), we performed a phase shift-based permutation correction (see \textit{Methods} for additional details).
+In a second analysis, we sought to identify brain structures whose responses (during episode viewing) reflected how each participant would later structure their \textit{recounting} of the episode.
+We used a searchlight procedure to identify clusters of voxels whose proximal temporal correlation matrices matched that of the topic proportions matrix for each participant's recall transcript (Figs.~\ref{fig:brainz}B; see \textit{Methods} for additional details).
+To ensure our searchlight procedure identified regions \textit{specifically} sensitive to the temporal structure of the episode or recalls (i.e., rather than those with a temporal autocorrelation length similar to that of the episode and recalls), we performed a phase shift-based permutation correction (see \textit{Methods} for additional details).
 As shown in Figure~\ref{fig:brainz}C, the episode-driven searchlight analysis revealed a distributed network of regions that may play a role in processing information relevant to the narrative structure of the episode.
 Similarly, the recall-driven searchlight analysis revealed a second network of regions (Fig.~\ref{fig:brainz}D) that may facilitate a person-specific transformation of one's experience into memory.
-In identifying regions whose responses to ongoing experiences reflect how those experiences will be remembered later, this latter analysis extends classic \textit{subsequent memory analyses}~\citep[e.g.,][]{PallWagn02} to domain of naturalistic stimuli.
+The top ten \texttt{Neurosynth} terms~\citep{YarkEtal11} associated with each (unthresholded) map are displayed in each panel.
+In identifying regions whose responses to ongoing experiences reflect how those experiences will be remembered later, this latter analysis extends classic \textit{subsequent memory analyses}~\citep[e.g.,][]{PallWagn02} to the domain of naturalistic experiences.
 
-\begin{figure}[t]
+\begin{figure}[tp]
 \centering
@@
 \textbf{C.} We identified a network of regions sensitive to the narrative structure of participants' ongoing experience.
-The map shown is thresholded at at $p < 0.05$, corrected.
+The map shown is thresholded at $p < 0.05$, corrected.
+The top ten \texttt{Neurosynth} terms displayed in the panel were computed using the unthresholded map.
 \textbf{D}.
 We also identified a network or regions sensitive to how individuals would later structure the episode's content in their recalls.
-The map shown is thresholded at at $p < 0.05$, corrected.}
+The map shown is thresholded at $p < 0.05$, corrected.
+The top ten \texttt{Neurosynth} terms displayed in the panel were computed using the unthresholded map.}
 \label{fig:brainz}
@@
 
-% \begin{figure}[tp]
-% \centering
-% \includegraphics[width=1\textwidth]{figs/neurosynth_decoding}
-% \caption{\small \textbf{Decoding distributed statistical maps via Neurosynth meta-analyses.} \textbf{A.} episode-searchlight significance and top 10 decoded terms.
-We constructed a map of the permutation-derived $p$-values for the episode-driven searchlight analysis (Fig.~\ref{fig:brainz}A, C) at each voxel with a positive permutation-derived $z$-score.
-The top 10 terms decoded from this significance map are shown in red.
-\textbf{B.} Recall-searchlight significance and top 10 decoded terms.
-We constructed a map of the permutation-derived $p$-values for the recall-driven searchlight analysis (Fig.~\ref{fig:brainz}A, C) at each voxel with a positive permutation-derived $z$-score.
-The top 10 terms decoded from this significance map are shown in blue.}
-% \label{fig:neurosynth}
-% \end{figure}
-
 \section*{Discussion}
@@
 
-Our work casts remembering as reproducing (behaviorally and neurally) the topic trajectory, or shape, of an experience.
-This view draws inspiration from prior work aimed at elucidating the neural and behavioral underpinnings of how we process dynamic naturalistic experiences and remember them later.
-One approach to identifying neural responses to naturalistic stimuli (including experiences) entails building a model of the stimulus and searching for brain regions whose responses are consistent with the model.
-In prior work, a series of studies from Uri Hasson's group~\citep{LernEtal11, SimoEtal16, ChenEtal17, BaldEtal17, ZadbEtal17} have extended this approach with a clever twist: rather than building an explicit stimulus model, these studies instead search for brain responses (while experiencing the stimulus) that are reliably similar across individuals.
-So called \textit{inter-subject correlation} (ISC) and \textit{inter-subject functional connectivity} (ISFC) analyses effectively treat other people's brain responses to the stimulus as a ``model'' of how its features change over time.
-By contrast, in our present work, we use topic models to construct an explicit content model directly from the stimulus (i.e., the topic trajectory of the episode).
-Projecting each participant's recall into a space shared by both the stimulus and other participants then allows us to compare recalls both directly to the stimulus and to each other.
-Similarly, prior work introducing the use of HMMs to discover latent event structure in naturalistic stimuli and recall \citep{BaldEtal17} used between-subjects cross-validation to identify event boundaries shared across participants, and between stimulus and recall.
-Our framework allows us to break from the restriction of a common, shared event-timeseries and identify the unique \textit{resolution} of each participant's recall event structure, and how that may differ from the episode and that of other participants.
-% @JEREMY @ANDY PLEASE CHECK THIS TO MAKE SURE I'M NOT MISCHARACTERIZING BALDETAL17
+Explicitly modeling the dynamic content of a naturalistic stimulus and participants' memories enabled us to connect the present study of naturalistic recall with an extensive prior literature on using list-learning paradigms to study memory~\citep[for review see][]{Kaha12}, as in Figure~\ref{fig:list-learning}.
+We found some similarities between how participants in the present study recounted a television episode and how participants typically recall memoized random word lists.
+However, our broader claim is that word lists miss out on fundamental aspects of naturalistic memory more like the sort of memory we rely on in everyday life.
+For example, there are no random word list analogs of character interactions, conceptual dependencies between temporally distant episode events, the sense of solving a mystery that pervades the \textit{Sherlock} episode, or the myriad other features of the episode that convey deep meaning.
+Nevertheless, each of these properties affects how people process the ongoing episode as they are watching it, and how they remember it later.
+The overarching goal of the present study is to characterize how the rich dynamics of the episode affect the rich behavioral and neural dynamics of how people remember it.
 
-Word embedding models are a rapidly growing area of machine learning research.  Early approaches including latent
-  semantic analysis~\citep{LandDuma97} use word co-occurrence statistics (i.e., how often pairs of words occur in the same documents contained in the corpus) to derive a unique feature vector for each word.
+Our work casts remembering as reproducing (behaviorally and neurally) the topic trajectory, or ``shape,'' of an experience.
+When we characterized memory for a television episode using this framework, we found that every participant's recounting of the episode recapitulated the low spatial frequency details of the shape of its trajectory through topic space.
+We termed this narrative scaffolding the episode's \textit{essence}.
+Where participants' behaviors varied most was in their tendencies to recount specific low-level details from each episode event.
+Geometrically, this appears as high spatial frequency distortions in participants' recall trajectories relative to the trajectory of the original episode.
+We developed metrics to characterize the precision (recovery of any and all event-level information) and distinctiveness (recovery of event-specific information).
+We also used word cloud visualizations to interpret the details of these event-level distortions.
+
+The neural analyses we carried out (Fig.~\ref{fig:brainz}) also leveraged our geometric framework for characterizing the shapes of the episode and participants' recountings.
+We identified one network of regions whose responses tracked with temporal correlations in the conceptual content of the episode (as quantified by topic models applied to a set of annotations about the episode).
+This network included orbitofrontal cortex, ventromedial prefrontal cortex, striatum, among others.
+As reviewed by \cite{RangRitc12}, several of these regions are members of the \textit{anterior temporal system}, which has been implicated in assessing the familiarity of ongoing experiences, emotional processing, social cognition, and rewards.
+A second network we identified tracked with temporal correlations in the idiosyncratic conceptual content of participants' recountings of the episode.
+This network included occipital cortex, extrastriate cortex, fusiform gyrus, and the precuneus.
+Several of these regions are members of the \textit{posterior medial system}~\citep{RangRitc12}, which has been implicated in matching incoming cues about the current situation to internally maintained \textit{situation models} that specify the parameters and expectations inherent to the current situation~\citep[also see][]{ZackEtal07, ZwaaRadv98}.
+Taken together, our results support the notion that these two (partially overlapping) networks work in coordination to make sense of our ongoing experiences, distort them in a way that links them with our prior knowledge and experiences, and encodes those distorted representations into memory for our later use.
+
+Our general approach draws inspiration from prior work aimed at elucidating the neural and behavioral underpinnings of how we process dynamic naturalistic experiences and remember them later.
+Our approach to identifying neural responses to naturalistic stimuli (including experiences) entails building an explicit model of the stimulus and searching for brain regions whose responses are consistent with the model~\citep[also see][]{HuthEtal12, HuthEtal16}.
+In prior work, a series of studies from Uri Hasson's group~\citep{LernEtal11, SimoEtal16, ChenEtal17, BaldEtal17, ZadbEtal17} have developed a clever alternative approach: rather than building an explicit stimulus model, these studies instead search for brain responses (while experiencing the stimulus) that are reliably similar across individuals.
+So called \textit{inter-subject correlation} (ISC) and \textit{inter-subject functional connectivity} (ISFC) analyses effectively treat other people's brain responses to the stimulus as a ``model'' of how its features change over time~\citep[also see][]{SimoChan20}.
+These purely brain-driven approaches are well-suited to identifying which brain structures exhibit similar stimulus-driven responses across individuals.
+Further, because neural response dynamics are observed data (rather than model approximations), such approaches do not require a detailed understanding of which stimulus properties or features might be driving the observed responses.
+However, this also means that the specific stimulus features driving those responses are typically opaque to the researcher.
+Our approach is complementary.
+By explicitly modeling the stimulus dynamics, we are able to relate specific stimulus features to behavioral and neural dynamics.
+However, when our model fails to accurately capture the stimulus dynamics that are truly driving behavioral and neural responses, our approach necessarily yields an incomplete characterization of the neural basis of the processes we are studying.
+
+Other recent work has used HMMs to discover laten event structure in neural responses to naturalistic stimuli~\citep{BaldEtal17}.
+By applying HMMs to our explicit models of stimulus and memory dynamics, we gain a more direct understanding of those state dynamics.
+For example, we found that although the events comprising each participant's recalls recapitulated the episode's essence, participants different in the \textit{resolution} of their recounting of low-level details.
+In turn, these individual behavioral differences were reflected in differences in neural activity dynamics as participants watched the television episode.
+
+Our approach also draws inspiration from the growing field of word embedding models.
+The topic models~\citep{BleiEtal03} we used to embed text from the episode annotations and participants' recall transcripts are just one of many models that have been studied in an extensive literature.
+The earliest approaches to word embedding, including latent
+semantic analysis~\citep{LandDuma97}, used word co-occurrence statistics (i.e., how often pairs of words occur in the same documents contained in the corpus) to derive a unique feature vector for each word.
 The feature vectors are constructed so that words that co-occur more frequently have feature vectors that are closer (in Euclidean distance).
-Related approaches, such as latent dirichlet
-  allocation~\citep{BleiEtal03} attempt to explicitly model the underlying causes of word co-occurrences by automatically identifying the set of themes or topics reflected across the documents in the corpus.
+Topic models are essentially an extension of those early models, in that they attempt to explicitly model the underlying causes of word co-occurrences by automatically identifying the set of themes or topics reflected across the documents in the corpus.
 More recent work on these types of semantic models, including word2vec~\citep{MikoEtal13}, the Universal Sentence Encoder~\citep{CerEtal18}, GPT-2~\citep{RadfEtal19}, and GTP-3~\citep{BrowEtal20} use deep neural networks to attempt to identify the deeper conceptual representations underlying each word.
-Despite the growing popularity of more sophisticated deep learning-based embedding models, here we leverage latent dirichlet allocation (i.e., topic modeling) to embed episode and recall text.
-This decision was motivated by several factors.
-First, topic models capture the \textit{essence} of a text passage devoid of the specific set and order of words used.
-This was an important feature of our model since different people may accurately recall a scene using very different language.
-Second, words can mean different things in different contexts (e.g.
-``bat'' may be the act of hitting a baseball, the object used for that action, or as a flying mammal).
-Topic models are robust to this, allowing words to exist as part of multiple topics.
-Last, topic models provide a straightforward means of recovering the weights for the particular words comprising a topic, enabling straightforward interpretation of an event's contents (e.g.
-Fig.~\ref{fig:topics}).
-Other models such as the Universal Sentence Encoder, GPT-2, and GPT-3 offer context-sensitive encoding of text passages, but the encoding space is complex and non-linear, and thus recovering the original words used to fit the model is not straightforward.
-However, it is worth pointing out that our general framework is divorced from the particular choice of language model.
-Moreover, many of the aspects of our framework could be swapped out for other choices.
-For example, the language model, the timeseries segmentation model and the episode-recall matching function could all be customized to suit a particular question space or application.
-Indeed for some questions, recovery of the particular words used to describe a memory may not be necessary, and thus other text-modeling approaches (including the deep learning-based embedding models described above) may be preferable.
-Future work will explore the influence of particular model choices on the framework's efficacy.
-
-In extending classical free recall analyses to our naturalistic memory framework, we recovered two patterns of recall dynamics central to list-learning studies: a heightened probability of initiating recall with the first presented ``item'' (in our case, episode events; Fig.~\ref{fig:list-learning}A) and a strong bias toward transitioning from recalling a given event to recalling the one immediately following it (Fig.~\ref{fig:list-learning}B).
-However, equally noteworthy are the typical free recall results \textit{not} recovered in these analyses, as each highlights a fundamental difference between the list-learning paradigm and naturalistic memory paradigms like the one employed in the present study.
-The most noticeable departure from hallmark free recall dynamics in these findings is the apparent lack of a serial position effect in Figure \ref{fig:list-learning}C, which instead shows greater and lesser recall probabilities for events distributed across the episode.
-Stimuli in free recall experiments most often comprise lists of simple, common words, presented to participants in a random order.
-\citep[In fact, numerous word pools have been developed based on these criteria; e.g.,][]{FrieEtal82}.
-These stimulus qualities enable two assumptions that are central to word list analyses, but frequently do not hold for real-world experiences.
-First, researchers conducting list-learning studies may assume that the content at each presentation index is essentially equal, and does not possess attributes that would render it, on average, more or less memorable than others.
-Such is rarely the case with real-world experiences or experiments meant to approximate them, and the effects of both intrinsic and observer-dependent factors on stimulus memorability are well established \citep[for review see][]{ChunTurk07, ByliEtal15, TyngEtal17}.
-Second, the random ordering of list items ensures that (across participants, on average) there is no relationship between the thematic similarity of individual stimuli and their presentation positions---in other words, two successively presented items are no more likely to be highly semantically similar than they are to be highly dissimilar.
-In most cases, the exact opposite is true of real-world episodes.
-Our internal thoughts, our actions, and the physical state of the world around us all tend to follow a direct (often causal) progression.
-As a result, each moment of our experience tends to be inherently more similar to surrounding moments than to those in the distant past or future.
-Memory literature has termed this strong temporal autocorrelation ``context,'' and in various media that depict real-world events (e.g., movies or written stories), we recognize it as a \textit{narrative structure}.
-While a random word list (by definition) has no such structure, the logical progression between ideas and actions in a naturalistic stimulus prompts the rememberer to recount presented events in order, starting with the beginning.
-This tendency is reflected in our findings' second departure from typical free recall dynamics: a lack of increased probability of first recall for end-of-sequence events (Fig.~\ref{fig:list-learning}A).
-
-Because they disregard presentation order-dependent variability in the stimulus content, analyses such as those in Figure \ref{fig:list-learning} enable a more sensitive analysis of presentation order-dependent temporal dynamics in free recall.
-Yet by the same token, they paint a wholly incomplete picture of memory for naturalistic episodes.
-In an attempt to address this shortcoming, we have developed a framework in the present study that characterizes the explicit semantic content of the stimulus and subsequent recalls.
-However, sensitivity to stimulus and recall content introduces a new challenge: distinguishing between levels of recall quality for a stimulus (e.g., an event) that is considered to have been ``remembered.''  When modeling memory in an experimental setting, recall quality for individual events is often cast as binary (e.g., a given list item was simply either remembered or not remembered).
-Various models of memory (e.g., \citealp{Yone02}) attempt to improve upon this by including confidence ratings, rendering this binary judgement instead categorical.
-To better evaluate naturalistic memory quality, we introduce a continuous metric (\textit{precision}), which reflects the level of completeness of a participant's recall for a feature-rich experience.
-Additionally, recall quality for a single event is typically assessed independently from that for all other events (e.g., it is difficult to ``compare'' a participant's binary recall success for list item 1 to that of list item 10).
-The second novel metric we introduce (\textit{distinctiveness}) is based on analyzing of the correlational structure of an individual's full set of recall events, and reflects the specificity of their memory for a single experienced event.
-We find that both of these metrics relate to the overall number of episode events participants successfully recalled, and that our precision metric additionally relates to \cite{ChenEtal17}'s hand-annotated memory memory scores.
-
-We did not find evidence that participants' average recall distinctiveness was related to their hand-annotated memory scores computed by~\cite{ChenEtal17}.
-One possible explanation is that, in hand-scoring each participant's verbal recall for each of 50 (manually-deliniated) scenes, ``[a] scene was counted as recalled if the participant described any part of the scene''~\citep{ChenEtal17}.
-In other words, both an extensive description of a scene's content and a brief mention of some subset of its content were (binarily) considered equally successful recalls.
-By contrast, we identify the event structure in participants' recalls in an unsupervised manner, independent of the episode event-timeseries, prior to mapping between episode and recall content.
-Our HMM-based event-segmentation produces boundaries between timepoints where the topic proportions shift in a substantial way, and because a small handful of words is unlikely to contribute significantly to the topic proportions for any sliding window, such brief scene descriptions will most often not result in a sufficiently large shift in the resulting topic proportions for the HMM to identify an event boundary.
-Instead, they will be grouped with a neighboring event, consequently lowering that event's distinctiveness score and by extension, the participant's overall distinctiveness score.
-This is in essence the qualitative difference between distinctive and indistinctive recall, and reflects the comparison shown in Figure \ref{fig:distinctiveness-detail}C.
-Intriguingly, prior studies show that pattern separation, or the ability to cleanly discriminate between similar experiences, is impaired in many cognitive disorders as well as natural aging \citep{StarEtal10, YassEtal11c, YassStar11b}.
-Future work might explore whether and how these metrics compare between cognitively impoverished groups and healthy controls.
-
-In the analyses outlined in Figure \ref{fig:brainz}, we identified two networks of brain regions whose responses during episode viewing were consistent with the temporal structure of the episode and recall topic trajectories, respectively.
-The network identified by the episode trajectory analysis included the ventromedial prefrontal cortex, left anterior temporal lobe, superior parietal and dorsal anterior cingulate cortex.
-The network from the episode-recall trajectory analysis also included the ventromedial prefrontal and superior parietal cortices, in addition to the posterior medial cortex (PMC) and the inferior temporal regions.
-Notably, \cite{ChenEtal17} also observed the PMC in a number of analyses including one that searched for regions whose activity patterns during encoding were reinstated during free recall.
-The PMC has been consistently identified in studies involving stimuli with meaningfully structured events~\citep{CohnRang17}.
-Further, the PMC is part of the "posterior medial" system, a network of brain regions thought to represent situation models~\citep{ZackEtal07} in support of memory, spatial navigation and social cognition~\citep{RangRitc12}.
-Given that we constructed our episode-recall searchlight model to capture temporal structure in the episode's semantic content (and how one's later recall aligns with that structure), we speculate that the PMC may play a role in constructing mnemonic events from meaningfully structured experiences.
-
-Decoding the associated significance maps with \texttt{Neurosynth} revealed two intriguing results.
-First, the top 10 terms returned for the episode-driven searchlight significance map were centered around themes of language and semantic meaning (Fig.~\ref{fig:brainz}).
-In other words, the voxels identified as more reflective of the episode content's temporal structure (i.e., voxels with lower permutation correction-derived $p$-values), as defined by our model, were most likely to be reported as active in studies focused on the the neural underpinnings of semantic processing.
-This finding is interesting, as our model specifically captures the temporal structure of the episode's \textit{semantic} content (e.g., as opposed to that of the visual, auditory, or affective content).
-This suggests that the network of structures displayed in Figure \ref{fig:brainz}C may play a roll in processing the evolving semantic content of ongoing experiences.
-
-Our second searchlight analysis identified a partially overlapping network of regions (Fig.~\ref{fig:brainz}D) whose patterns of activity as participants viewed the episode reflected the idiosyncratic structure of each individual's later recalls.
-The associated significance map yielded a set of \texttt{Neurosynth} terms that primarily reflected names of specific structural regions (such as ``thalamus,'' ``anterior insula,'' ``anterior cingulate'' and ``inferior frontal''; Fig.~\ref{fig:brainz}).
-Interestingly, these regions share membership in a common, large-scale functional network (termed the ``salience network'') involved in detecting and processing affective cues.
-In particular, the latter three regions have been implicated in functions relevant to assigning personal meaning to an experience, including: ascribing subjective value to raw, sensory input \citep{MedfCrit10}; modulating semantic and phonological processing in response to personally salient stimuli \citep{KellEtal07b}; and directing and reallocating attention and working memory resources towards the most relevant stimuli \citep{MenoUddi10}.
-This suggests that the network of structures displayed in Figure \ref{fig:brainz}D may be play a roll in transforming and restructuring ongoing experiences through the lens of one's prior experience and subjective emotions as they are encoded in memory.
+Despite the availability of these sophisticated deep learning-based embedding models, we chose to prioritize interpretability of the embedding dimensions (e.g., Fig.~\ref{fig:topics}) over raw performance, e.g.
+by a predefined benchmark.
+Nevertheless, we note that our general framework is, in principle, robust to the specific choice of language model as well as other aspects of our computational pipeline.
+For example, the word embedding model, timeseries segmentation model, and the episode-recall matching function could all be customized to suit a particular question space or application.
+Indeed, for some questions, interpretability of the embeddings may not be a priority, and thus other text embedding approaches (including the deep learning-based models described above) may be preferable.
+Future work will be needed to explore the influence of particular models on our framework's predictions and performance.
 

### 2020-08-28 paper/boneyard.tex

@@
-% Supplemental materials
+Despite the growing popularity of more sophisticated deep learning-based embedding models, here we leverage latent dirichlet allocation (i.e., topic modeling) to embed episode and recall text.
+This decision was motivated by several factors.
+First, topic models capture the \textit{essence} of a text passage devoid of the specific set and order of words used.
+This was an important feature of our model since different people may accurately recall a scene using very different language.
+Second, words can mean different things in different contexts (e.g.
+``bat'' may be the act of hitting a baseball, the object used for that action, or as a flying mammal).
+Topic models are robust to this, allowing words to exist as part of multiple topics.
+Last, topic models provide a straightforward means of recovering the weights for the particular words comprising a topic, enabling straightforward interpretation of an event's contents (e.g.
+Fig.~\ref{fig:topics}).
+Other models such as the Universal Sentence Encoder, GPT-2, and GPT-3 offer context-sensitive encoding of text passages, but the encoding space is complex and non-linear, and thus recovering the original words used to fit the model is not straightforward.
+However, it is worth pointing out that our general framework is divorced from the particular choice of language model.
+Moreover, many of the aspects of our framework could be swapped out for other choices.
+For example, the language model, the timeseries segmentation model and the episode-recall matching function could all be customized to suit a particular question space or application.
+Indeed for some questions, recovery of the particular words used to describe a memory may not be necessary, and thus other text-modeling approaches (including the deep learning-based embedding models described above) may be preferable.
+Future work will explore the influence of particular model choices on the framework's efficacy.
+
+In extending classical free recall analyses to our naturalistic memory framework, we recovered two patterns of recall dynamics central to list-learning studies: a heightened probability of initiating recall with the first presented ``item'' (in our case, episode events; Fig.~\ref{fig:list-learning}A) and a strong bias toward transitioning from recalling a given event to recalling the one immediately following it (Fig.~\ref{fig:list-learning}B).
+However, equally noteworthy are the typical free recall results \textit{not} recovered in these analyses, as each highlights a fundamental difference between the list-learning paradigm and naturalistic memory paradigms like the one employed in the present study.
+The most noticeable departure from hallmark free recall dynamics in these findings is the apparent lack of a serial position effect in Figure \ref{fig:list-learning}C, which instead shows greater and lesser recall probabilities for events distributed across the episode.
+Stimuli in free recall experiments most often comprise lists of simple, common words, presented to participants in a random order.
+\citep[In fact, numerous word pools have been developed based on these criteria; e.g.,][]{FrieEtal82}.
+These stimulus qualities enable two assumptions that are central to word list analyses, but frequently do not hold for real-world experiences.
+First, researchers conducting list-learning studies may assume that the content at each presentation index is essentially equal, and does not possess attributes that would render it, on average, more or less memorable than others.
+Such is rarely the case with real-world experiences or experiments meant to approximate them, and the effects of both intrinsic and observer-dependent factors on stimulus memorability are well established \citep[for review see][]{ChunTurk07, ByliEtal15, TyngEtal17}.
+Second, the random ordering of list items ensures that (across participants, on average) there is no relationship between the thematic similarity of individual stimuli and their presentation positions---in other words, two successively presented items are no more likely to be highly semantically similar than they are to be highly dissimilar.
+In most cases, the exact opposite is true of real-world episodes.
+Our internal thoughts, our actions, and the physical state of the world around us all tend to follow a direct (often causal) progression.
+As a result, each moment of our experience tends to be inherently more similar to surrounding moments than to those in the distant past or future.
+Memory literature has termed this strong temporal autocorrelation ``context,'' and in various media that depict real-world events (e.g., movies or written stories), we recognize it as a \textit{narrative structure}.
+While a random word list (by definition) has no such structure, the logical progression between ideas and actions in a naturalistic stimulus prompts the rememberer to recount presented events in order, starting with the beginning.
+This tendency is reflected in our findings' second departure from typical free recall dynamics: a lack of increased probability of first recall for end-of-sequence events (Fig.~\ref{fig:list-learning}A).
+
+Because they disregard presentation order-dependent variability in the stimulus content, analyses such as those in Figure \ref{fig:list-learning} enable a more sensitive analysis of presentation order-dependent temporal dynamics in free recall.
+Yet by the same token, they paint a wholly incomplete picture of memory for naturalistic episodes.
+In an attempt to address this shortcoming, we have developed a framework in the present study that characterizes the explicit semantic content of the stimulus and subsequent recalls.
+However, sensitivity to stimulus and recall content introduces a new challenge: distinguishing between levels of recall quality for a stimulus (e.g., an event) that is considered to have been ``remembered.''  When modeling memory in an experimental setting, recall quality for individual events is often cast as binary (e.g., a given list item was simply either remembered or not remembered).
+Various models of memory (e.g., \citealp{Yone02}) attempt to improve upon this by including confidence ratings, rendering this binary judgement instead categorical.
+To better evaluate naturalistic memory quality, we introduce a continuous metric (\textit{precision}), which reflects the level of completeness of a participant's recall for a feature-rich experience.
+Additionally, recall quality for a single event is typically assessed independently from that for all other events (e.g., it is difficult to ``compare'' a participant's binary recall success for list item 1 to that of list item 10).
+The second novel metric we introduce (\textit{distinctiveness}) is based on analyzing of the correlational structure of an individual's full set of recall events, and reflects the specificity of their memory for a single experienced event.
+We find that both of these metrics relate to the overall number of episode events participants successfully recalled, and that our precision metric additionally relates to \cite{ChenEtal17}'s hand-annotated memory memory scores.
+
+We did not find evidence that participants' average recall distinctiveness was related to their hand-annotated memory scores computed by~\cite{ChenEtal17}.
+One possible explanation is that, in hand-scoring each participant's verbal recall for each of 50 (manually-deliniated) scenes, ``[a] scene was counted as recalled if the participant described any part of the scene''~\citep{ChenEtal17}.
+In other words, both an extensive description of a scene's content and a brief mention of some subset of its content were (binarily) considered equally successful recalls.
+By contrast, we identify the event structure in participants' recalls in an unsupervised manner, independent of the episode event-timeseries, prior to mapping between episode and recall content.
+Our HMM-based event-segmentation produces boundaries between timepoints where the topic proportions shift in a substantial way, and because a small handful of words is unlikely to contribute significantly to the topic proportions for any sliding window, such brief scene descriptions will most often not result in a sufficiently large shift in the resulting topic proportions for the HMM to identify an event boundary.
+Instead, they will be grouped with a neighboring event, consequently lowering that event's distinctiveness score and by extension, the participant's overall distinctiveness score.
+This is in essence the qualitative difference between distinctive and indistinctive recall, and reflects the comparison shown in Figure \ref{fig:distinctiveness-detail}C.
+Intriguingly, prior studies show that pattern separation, or the ability to cleanly discriminate between similar experiences, is impaired in many cognitive disorders as well as natural aging \citep{StarEtal10, YassEtal11c, YassStar11b}.
+Future work might explore whether and how these metrics compare between cognitively impoverished groups and healthy controls.
+
+In the analyses outlined in Figure \ref{fig:brainz}, we identified two networks of brain regions whose responses during episode viewing were consistent with the temporal structure of the episode and recall topic trajectories, respectively.
+The network identified by the episode trajectory analysis included the ventromedial prefrontal cortex, left anterior temporal lobe, superior parietal and dorsal anterior cingulate cortex.
+The network from the episode-recall trajectory analysis also included the ventromedial prefrontal and superior parietal cortices, in addition to the posterior medial cortex (PMC) and the inferior temporal regions.
+Notably, \cite{ChenEtal17} also observed the PMC in a number of analyses including one that searched for regions whose activity patterns during encoding were reinstated during free recall.
+The PMC has been consistently identified in studies involving stimuli with meaningfully structured events~\citep{CohnRang17}.
+Further, the PMC is part of the "posterior medial" system, a network of brain regions thought to represent situation models~\citep{ZackEtal07} in support of memory, spatial navigation and social cognition~\citep{RangRitc12}.
+Given that we constructed our episode-recall searchlight model to capture temporal structure in the episode's semantic content (and how one's later recall aligns with that structure), we speculate that the PMC may play a role in constructing mnemonic events from meaningfully structured experiences.
+
+Decoding the associated significance maps with \texttt{Neurosynth} revealed two intriguing results.
+First, the top 10 terms returned for the episode-driven searchlight significance map were centered around themes of language and semantic meaning (Fig.~\ref{fig:brainz}).
+In other words, the voxels identified as more reflective of the episode content's temporal structure (i.e., voxels with lower permutation correction-derived $p$-values), as defined by our model, were most likely to be reported as active in studies focused on the the neural underpinnings of semantic processing.
+This finding is interesting, as our model specifically captures the temporal structure of the episode's \textit{semantic} content (e.g., as opposed to that of the visual, auditory, or affective content).
+This suggests that the network of structures displayed in Figure \ref{fig:brainz}C may play a roll in processing the evolving semantic content of ongoing experiences.
+
+Our second searchlight analysis identified a partially overlapping network of regions (Fig.~\ref{fig:brainz}D) whose patterns of activity as participants viewed the episode reflected the idiosyncratic structure of each individual's later recalls.
+The associated significance map yielded a set of \texttt{Neurosynth} terms that primarily reflected names of specific structural regions (such as ``thalamus,'' ``anterior insula,'' ``anterior cingulate'' and ``inferior frontal''; Fig.~\ref{fig:brainz}).
+Interestingly, these regions share membership in a common, large-scale functional network (termed the ``salience network'') involved in detecting and processing affective cues.
+In particular, the latter three regions have been implicated in functions relevant to assigning personal meaning to an experience, including: ascribing subjective value to raw, sensory input \citep{MedfCrit10}; modulating semantic and phonological processing in response to personally salient stimuli \citep{KellEtal07b}; and directing and reallocating attention and working memory resources towards the most relevant stimuli \citep{MenoUddi10}.
+This suggests that the network of structures displayed in Figure \ref{fig:brainz}D may be play a roll in transforming and restructuring ongoing experiences through the lens of one's prior experience and subjective emotions as they are encoded in memory.
+
+%
+
+Supplemental materials
 

### 2020-08-28 paper/main.tex

@@
 
-Explicitly modeling the dynamic content of a naturalistic stimulus and participants' memories enabled us to connect the present study of naturalistic recall with an extensive prior literature on using list-learning paradigms to study memory~\citep[for review see][]{Kaha12}, as in Figure~\ref{fig:list-learning}.
-We found some similarities between how participants in the present study recounted a television episode and how participants typically recall memoized random word lists.
+Explicitly modeling the dynamic content of a naturalistic stimulus and participants' memories enabled us to connect the present study of naturalistic recall with an extensive prior literature that has used list-learning paradigms to study memory~\citep[for review see][]{Kaha12}, as in Figure~\ref{fig:list-learning}.
+We found some similarities between how participants in the present study recounted a television episode and how participants typically recall memorized random word lists.
 However, our broader claim is that word lists miss out on fundamental aspects of naturalistic memory more like the sort of memory we rely on in everyday life.

### 2020-08-28 paper/main.tex
YATF -- yet another typo fix

@@
 By applying HMMs to our explicit models of stimulus and memory dynamics, we gain a more direct understanding of those state dynamics.
-For example, we found that although the events comprising each participant's recalls recapitulated the episode's essence, participants different in the \textit{resolution} of their recounting of low-level details.
+For example, we found that although the events comprising each participant's recalls recapitulated the episode's essence, participants differed in the \textit{resolution} of their recounting of low-level details.
 In turn, these individual behavioral differences were reflected in differences in neural activity dynamics as participants watched the television episode.

### 2020-09-01 paper/main.tex
caught a typo

@@
-\documentclass{article}
+\documentclass[10pt]{article}
 \usepackage[utf8]{inputenc}
@@
 \usepackage{geometry}
-\usepackage{natbib}
+\usepackage[sort]{natbib}
 \usepackage{pxfonts}
@@
 \begin{document}
+\begin{titlepage}
   \maketitle
+  \end{titlepage}
 
 \begin{abstract}
-Our ongoing subjective experience reflects external sensory information from each moment, along with additional information from our past that we carry with us into that moment.
-The blend of memories, knowledge, emotions, goals, and other internal perceptual and mental states that color our subjective experience provides a \textit{context} for interpreting new information and conceptually linking what is happening now with our prior experiences.
-Because this contextual information is often person-specific, the subjective experience that each person encodes into their memory is often idiosyncratic, even for shared experiences and sensory perspectives.
-We sought to study which aspects of a shared naturalistic experience were preserved or distorted, and how those distortions compared across individuals.
-To this end, we developed a geometric framework for mathematically characterizing the subjective conceptual content of dynamic naturalistic experiences.
-We model experiences as \textit{trajectories} through word embedding spaces whose coordinates reflect the universe of thoughts under consideration.
-We also demonstrate how \textit{memories} may also be modeled as trajectories through the same spaces.
-According to this view, encoding an experience into memory entails geometrically preserving, distorting, or transforming the \textit{shape} of the original experience's trajectory.
-This translates qualitative neuropsychological questions about how we remember naturalistic experiences into quantitive geometric questions about the spatial configurations of trajectory shapes.
-We applied our framework to data collected as participants watched and verbally recounted a television episode while undergoing functional neuroimaging.
-We found that the trajectories of participants' recountings of the episode nearly all captured the coarse spatial properties of the original episode's trajectory (i.e., the essential plot points), but participants differed in their memory for low-level details.
-We also identified a network of brain structures that were sensitive to the shape of the episode's trajectory through word embedding space, and an overlapping network that predicted, at the time of encoding, how people would distort (transform) the episode's trajectory when they recounted the episode later.
-Our work provides insights into how our brains preserve, distort, and transform our ongoing experiences when we encode them into episodic memories.
+The mental contexts in which we interpret experiences are often person-specific, even when the experiences themselves are shared.
+We developed a geometric framework for mathematically characterizing the subjective conceptual content of dynamic naturalistic experiences.
+We model experiences and memories as \textit{trajectories} through word embedding spaces whose coordinates reflect the universe of thoughts under consideration.
+Memory encoding can then be modeled as geometrically preserving or distorting the \textit{shape} of the original experience.
+We applied our approach to data collected as participants watched and verbally recounted a television episode while undergoing functional neuroimaging.
+Participants’ recountings all preserved coarse spatial properties (essential narrative elements), but not fine spatial scale (low-level) details, of the episode’s trajectory.
+We also identified networks of brain structures sensitive to these trajectory shapes.
+Our work provides insights into how our brains preserve and distort our ongoing experiences when we encode them into episodic memories.
 \end{abstract}
@@
 We developed a computational framework for characterizing the temporal dynamics of the moment-by-moment content of the episode, and of participants' verbal recalls.
-Our framework uses topic modeling~\citep{BleiEtal03} to characterize the thematic conceptual (semantic) content present in each moment of the episode and recalls and hidden Markov models~\citep{Rabi89, BaldEtal17} to discretize this evolving semantic content into events.
-In this way, we cast both naturalistic experiences and memories of those experiences as geometric \textit{trajectories} that describe how they evolve over time.
+Our framework uses topic modeling~\citep{BleiEtal03} to characterize the thematic conceptual (semantic) content present in each moment of the episode and recalls by projecting each moment into a word embedding space.
+We then use hidden Markov models~\citep{Rabi89, BaldEtal17} to discretize this evolving semantic content into events.
+In this way, we cast both naturalistic experiences and memories of those experiences as geometric \textit{trajectories} through word embedding space that describe how they evolve over time.
 Under this framework, successful remembering entails verbally traversing the content trajectory of the episode, thereby reproducing the shape (essence) of the original experience.
@@
 We applied the same topic model (already trained on the episode annotations) to each participant's recalls.
-Analogously to how we parsed the time-varying content of the episode, to obtain similar estimates for each participant's recall transcript, we treated each overlapping  window of (up to 10) sentences from their transcript as a document, and computed the most probable mix of topics reflected in each timepoint's sentences.
+Analogously to how we parsed the time-varying content of the episode, to obtain similar estimates for each participant's recall transcript, we treated each overlapping  window of (up to) 10 sentences from their transcript as a document, and computed the most probable mix of topics reflected in each timepoint's sentences.
 This yielded, for each participant, a number-of-windows by number-of-topics topic proportions matrix that characterized how the topics identified in the original episode were reflected in the participant's recalls.
@@
 Similarly, although there do appear to be periods of stability in the recall topic dynamics (i.e., most topics are active or inactive over contiguous blocks of time), the changes in topic activations that define event boundaries appear less clearly delineated in participants' recalls than in the episode's annotations.
-To examine these patterns in detail, we computed the timepoint-by-timepoint correlation matrix for the example participant's recall trajectory (Fig.~\ref{fig:model}E).
+To examine these patterns in detail, we computed the timepoint-by-timepoint correlation matrix for the example participant's recall topic proportions matrix (Fig.~\ref{fig:model}E).
 As in the episode correlation matrix (Fig.~\ref{fig:model}B), the example participant's recall correlation matrix has a strong block diagonal structure, indicating that their recalls are discretized into separated events.
@@
 Some of the patterns we observed appeared to be similar to classic effects from the list-learning literature.
-For example, participants had a higher probability of initiating recall with the first event in the sequence (Fig.~\ref{fig:list-learning}A) and a higher probability of transitioning to neighboring events with an asymmetric forward bias (Fig.~\ref{fig:list-learning}B).
+For example, participants had a higher probability of initiating recall with early events (Fig.~\ref{fig:list-learning}A) and a higher probability of transitioning to neighboring events with an asymmetric forward bias (Fig.~\ref{fig:list-learning}B).
 However, unlike what is typically observed in list-learning studies, we did not observe patterns comparable to the primacy or recency serial position effects (Fig.~\ref{fig:list-learning}C).
-We hypothesized that participants might be leveraging the meaningful narrative associations and references over long timescales throughout the episode.
+We hypothesized that participants might be leveraging meaningful narrative associations and references over long timescales throughout the episode.
 
@@
   \includegraphics[width=1\textwidth]{figs/precision_distinctiveness}
-  \caption{\small \textbf{Novel content-based metrics of naturalistic memory: precision and distinctiveness.} \textbf{A.} The episode-recall correlation matrix for a representative participant (17).
+  \caption{\small \textbf{Novel content-based metrics of naturalistic memory: precision and distinctiveness.} \textbf{A.} The episode-recall correlation matrix for a representative participant (P17).
 The yellow boxes highlight the maximum correlation in each column.
@@
 \textbf{C.} The correlation between distinctiveness and hand-counted number of recalled scenes.
-\textbf{D.} The correlation between precision and the number of episode events successfully recalled, as determined by our model.
-\textbf{E.} The correlation between distinctiveness and the number of episode events successfully recalled, as determined by our model.}
+\textbf{D.} The correlation between precision and the number of recalled episode events, as determined by our model.
+\textbf{E.} The correlation between distinctiveness and the number of recalled episode events, as determined by our model.}
   \label{fig:precision-distinctiveness}
@@
   \includegraphics[width=1\textwidth]{figs/precision_detail}
-  \caption{\small \textbf{Precision metric reflects completeness of recall.} \textbf{A.} Recall precision by episode event.
+  \caption{\small \textbf{Precision reflects the completeness of recall, whereas distinctiveness reflects recall specificity.} \textbf{A.} Recall precision by episode event.
 Grey violin plots display kernel density estimates for the distribution of recall precision scores for a single episode event.
@@
 The text highlighted in gray denotes a (rare) false recall.
-The unhighlighted text denotes correctly recalled information about other episode events.}
+The unhighlighted text denotes correctly recalled information about other episode events.
+\textbf{D.} Recall distinctiveness by episode event.
+Kernel density estimates for each episode event's distribution of recall distinctiveness scores, analogous to Panel A.
+\textbf{E.} The sets of ``Narrative Details'' episode annotations (generated by \citealp{ChenEtal17}) for scenes comprising episode events described by the example participants in Panel F.
+Each event's text is highlighted in a different color.
+\textbf{F.} The sentences comprising the most distinctive (P9) and least distinctive (P6) participants' recalls of episode event 22.
+Sections of recall describing each each episode event in Panel E are highlighted with the corresponding color.}
   \label{fig:precision-detail}
@@
 
-\begin{figure}[tp]
-  \centering
-  \includegraphics[width=1\textwidth]{figs/distinctiveness_detail}
-  \caption{\small \textbf{Distinctiveness metric reflects specificity of recall.} \textbf{A.} Recall distinctiveness by episode event.
-Kernel density estimates for each episode event's distribution of recall distinctiveness scores, analogous to Fig.~\ref{fig:precision-detail}A.
-\textbf{B.} The sets of ``Narrative Details'' episode annotations (generated by \citealp{ChenEtal17}) for scenes comprising episode events described by the example participants in panel C.
-Each event's text is highlighted in a different color.
-\textbf{C.} The sentences comprising the most distinctive (P9) and least distinctive (P6) participants' recalls of episode event 22.
-Sections of recall describing each each episode event in Panel B are highlighted with the corresponding color.}
-  \label{fig:distinctiveness-detail}
-\end{figure}
-
 Examining individual recalls of the same episode event can provide insights into how the above precision and distinctiveness scores may be used to characterize similarities and differences in how different people describe the same shared experience.
-In Figure \ref{fig:precision-detail}, we compare recalls for the same episode event (event 22) from two participants: one with a high precision score (P17), and the other with a low precision score (P6).
+In Figure \ref{fig:precision-detail}, we compare recalls for the same episode event (event 22) from different participants: one with a high precision score (P17), and the other with a low precision score (P6).
 From the HMM-identified event boundaries, we recovered the set of annotations describing the content of an example episode event (Fig.~\ref{fig:precision-detail}B), and divided them into different color-coded sections for each action or feature described.
@@
 
-Figure \ref{fig:distinctiveness-detail} illustrates the differences between high and low distinctiveness scores for the same event detailed in Figure~\ref{fig:precision-detail} (i.e., event 22).
-Here, we have extracted the set of sentences comprising the most distinctive recall event (P9) and least distinctive recall event (P6) matched to the example episode event (Fig.~\ref{fig:distinctiveness-detail}C).
-We also extracted the annotations for the example episode event, as well as those from each other episode event whose content the example participants' single recall events described (Fig.~\ref{fig:distinctiveness-detail}B).
-We assigned each episode event a unique color (Panel B) and colored each recalled phrase or sentence (Panel C) according to the episode events they best matched.
-Visual inspection of Panel C reveals that the most distinctive recall's content is tightly concentrated around event 22, whereas the least distinctive recall incorporates content from a much wider range of episode events.
+Figure \ref{fig:precision-detail} also illustrates the differences between high and low distinctiveness scores for the same event detailed in Figure~\ref{fig:precision-detail}B (i.e., event 22).
+Here, we have extracted the set of sentences comprising the most distinctive recall event (P9) and least distinctive recall event (P6) matched to the example episode event (Fig.~\ref{fig:precision-detail}F).
+We also extracted the annotations for the example episode event, as well as those from each other episode event whose content the example participants' single recall events described (Fig.~\ref{fig:precision-detail}E).
+We assigned each episode event a unique color (Panel E) and colored each recalled phrase or sentence (Panel F) according to the episode events they best matched.
+Visual inspection of Panel F reveals that the most distinctive recall's content is tightly concentrated around event 22, whereas the least distinctive recall incorporates content from a much wider range of episode events.
 
 The preceding analyses sought to characterize how participants' recountings of individual episode events captured the low-level details of each event.
-Next we sought to characterize how participants' recountings of the full episode captured its high-level essence-- i.e., the shape of the episode's trajectory through topic space.
+Next we sought to characterize how participants' recountings of the full episode captured its high-level essence-- i.e., the shape of the episode's trajectory through word embedding (topic) space.
 To visualize the essence of the episode and each participant's recall trajectory~\citep{HeusEtal18a}, we projected the topic proportions matrices for the episode and recalls onto a shared two-dimensional space using Uniform Manifold Approximation and Projection~\citep[UMAP; ][]{McInEtal18}.
@@
 To visualize the result, we created a ``wordle'' image~\citep{MuelEtal18} where words weighted more heavily by more precisely-remembered topics appear in a larger font (Fig.~\ref{fig:topics}B, green box).
-Across the full episode, content that reflected topics necessary to convey the central focus of the episode (e.g., the names of the two main characters, ``Sherlock'' and ``John,'' and the address of a major recurring location, ``221B Baker Street'') were best remembered.
+Across the full episode, content that weighted heavily on topics and words central to the major foci of the episode (e.g., the names of the two main characters, ``Sherlock'' and ``John,'' and the address of a major recurring location, ``221B Baker Street'') were best remembered.
 An analogous analysis revealed which themes were less-precisely remembered.
@@
 \textbf{B.} Wordles comprising the top 200 highest-weighted words reflected in the weighted-average topic vector across episode events.
-Green: episode events were weighted their precision (Panel A).
+Green: episode events were weighted by their precision (Panel A).
 Red: episode events were weighted by the inverse of their precision.
 \textbf{C.}  The set of all episode and recall events is projected onto the two-dimensional space derived in Figure~\ref{fig:trajectory}.
-The dots outlined in black denote episode events (dot size is proportional to each event's precision).
-The dots without black outlines denote recall events from each participant.
+The dots outlined in black denote episode events (dot size is proportional to each event's average precision).
+The dots without black outlines denote individual recall events from each participant.
 All dots are colored using the same scheme as Figure~\ref{fig:trajectory}A.
@@
 Here, for each of the three most and least precisely remembered episode events, we have constructed two wordles: one from the original episode event's topic vector (left) and a second from the average recall topic vector for that event (right).
-The three most precisely remembered events (circled in green) correspond to scenes integral to the central plot-line: a mysterious figure spying on John in a phone booth; John meeting Sherlock at Baker St.
-to discuss the murders; and Sherlock laying a trap to catch the killer.
+The three most precisely remembered events (circled in green) correspond to scenes integral to the central plot-line: a mysterious figure spying on John in a phone booth; John meeting Sherlock at Baker St.\~to discuss the murders; and Sherlock laying a trap to catch the killer.
 Meanwhile, the least precisely remembered events (circled in red) reflect scenes that comprise minor plot points: a video of singing cartoon characters that participants viewed in an introductory clip prior to the main episode; John asking Molly about Sherlock's habit of over-analyzing people; and Sherlock noticing evidence of Anderson's and Donovan's affair.
@@
 The results thus far inform us about which aspects of the dynamic content in the episode participants watched were preserved or altered in participants' memories.
-We next carried out a series of analyses aimed at understanding which brain structures might facilitate these preservations and transformations between the external world and memory.
+We next carried out a series of analyses aimed at understanding which brain structures might facilitate these preservations and transformations between the participants' shared experience of watching the episode and their subsequent memories of the episode.
 In the first analysis, we sought to identify brain structures that were sensitive to the dynamic unfolding of the episode's content, as characterized by its topic trajectory.
@@
 The top ten \texttt{Neurosynth} terms~\citep{YarkEtal11} associated with each (unthresholded) map are displayed in each panel.
-In identifying regions whose responses to ongoing experiences reflect how those experiences will be remembered later, this latter analysis extends classic \textit{subsequent memory analyses}~\citep[e.g.,][]{PallWagn02} to the domain of naturalistic experiences.
+In identifying regions whose responses to ongoing experiences reflect how those experiences will be remembered later, this latter analysis extends classic \textit{subsequent memory effect analyses}~\citep[e.g.,][]{PallWagn02} to the domain of naturalistic experiences.
 
@@
 \textbf{D}.
-We also identified a network or regions sensitive to how individuals would later structure the episode's content in their recalls.
+We also identified a network of regions sensitive to how individuals would later structure the episode's content in their recalls.
 The map shown is thresholded at $p < 0.05$, corrected.
@@
 
-The searchlight analyses described above yielded two distributed networks of brain regions, whose activity timecourses mirrored to the temporal structure of the episode (Fig.~\ref{fig:brainz}C) or participants' eventual recalls (Fig.~\ref{fig:brainz}D).
+The searchlight analyses described above yielded two distributed networks of brain regions, whose activity timecourses tracked with the temporal structure of the episode (Fig.~\ref{fig:brainz}C) or participants' subsequent recalls (Fig.~\ref{fig:brainz}D).
 We next sought to gain greater insight into the structures and functional networks our results reflected.
@@
 However, our broader claim is that word lists miss out on fundamental aspects of naturalistic memory more like the sort of memory we rely on in everyday life.
-For example, there are no random word list analogs of character interactions, conceptual dependencies between temporally distant episode events, the sense of solving a mystery that pervades the \textit{Sherlock} episode, or the myriad other features of the episode that convey deep meaning.
-Nevertheless, each of these properties affects how people process the ongoing episode as they are watching it, and how they remember it later.
+For example, there are no random word list analogs of character interactions, conceptual dependencies between temporally distant episode events, the sense of solving a mystery that pervades the \textit{Sherlock} episode, or the myriad other features of the episode that convey deep meaning and capture interest.
+Nevertheless, each of these properties affects how people process and engage with the episode as they are watching it, and how they remember it later.
 The overarching goal of the present study is to characterize how the rich dynamics of the episode affect the rich behavioral and neural dynamics of how people remember it.
@@
 Our work casts remembering as reproducing (behaviorally and neurally) the topic trajectory, or ``shape,'' of an experience.
-When we characterized memory for a television episode using this framework, we found that every participant's recounting of the episode recapitulated the low spatial frequency details of the shape of its trajectory through topic space.
+When we characterized memory for a television episode using this framework, we found that every participant's recounting of the episode recapitulated the low spatial frequency details of the shape of its trajectory through topic space (Fig.~\ref{fig:trajectory}).
 We termed this narrative scaffolding the episode's \textit{essence}.
 Where participants' behaviors varied most was in their tendencies to recount specific low-level details from each episode event.
-Geometrically, this appears as high spatial frequency distortions in participants' recall trajectories relative to the trajectory of the original episode.
+Geometrically, this appears as high spatial frequency distortions in participants' recall trajectories relative to the trajectory of the original episode (Fig.~\ref{fig:topics}).
 We developed metrics to characterize the precision (recovery of any and all event-level information) and distinctiveness (recovery of event-specific information).
@@
 This network included orbitofrontal cortex, ventromedial prefrontal cortex, striatum, among others.
-As reviewed by \cite{RangRitc12}, several of these regions are members of the \textit{anterior temporal system}, which has been implicated in assessing the familiarity of ongoing experiences, emotional processing, social cognition, and rewards.
-A second network we identified tracked with temporal correlations in the idiosyncratic conceptual content of participants' recountings of the episode.
+As reviewed by \cite{RangRitc12}, several of these regions are members of the \textit{anterior temporal system}, which has been implicated in assessing and processing the familiarity of ongoing experiences, emotions, social cognition, and reward.
+A second network we identified tracked with temporal correlations in the idiosyncratic conceptual content of participants' subsequent recountings of the episode.
 This network included occipital cortex, extrastriate cortex, fusiform gyrus, and the precuneus.
@@
 Our general approach draws inspiration from prior work aimed at elucidating the neural and behavioral underpinnings of how we process dynamic naturalistic experiences and remember them later.
-Our approach to identifying neural responses to naturalistic stimuli (including experiences) entails building an explicit model of the stimulus and searching for brain regions whose responses are consistent with the model~\citep[also see][]{HuthEtal12, HuthEtal16}.
+Our approach to identifying neural responses to naturalistic stimuli (including experiences) entails building an explicit model of the stimulus dynamics and searching for brain regions whose responses are consistent with the model~\citep[also see][]{HuthEtal12, HuthEtal16}.
 In prior work, a series of studies from Uri Hasson's group~\citep{LernEtal11, SimoEtal16, ChenEtal17, BaldEtal17, ZadbEtal17} have developed a clever alternative approach: rather than building an explicit stimulus model, these studies instead search for brain responses (while experiencing the stimulus) that are reliably similar across individuals.
@@
 
-Other recent work has used HMMs to discover laten event structure in neural responses to naturalistic stimuli~\citep{BaldEtal17}.
+Other recent work has used HMMs to discover latent event structure in neural responses to naturalistic stimuli~\citep{BaldEtal17}.
 By applying HMMs to our explicit models of stimulus and memory dynamics, we gain a more direct understanding of those state dynamics.
@@
 More recent work on these types of semantic models, including word2vec~\citep{MikoEtal13}, the Universal Sentence Encoder~\citep{CerEtal18}, GPT-2~\citep{RadfEtal19}, and GTP-3~\citep{BrowEtal20} use deep neural networks to attempt to identify the deeper conceptual representations underlying each word.
-Despite the availability of these sophisticated deep learning-based embedding models, we chose to prioritize interpretability of the embedding dimensions (e.g., Fig.~\ref{fig:topics}) over raw performance, e.g.
-by a predefined benchmark.
+Despite the growing popularity of these sophisticated deep learning-based embedding models, we chose to prioritize interpretability of the embedding dimensions (e.g., Fig.~\ref{fig:topics}) over raw performance (e.g., with respect to some predefined benchmark).
 Nevertheless, we note that our general framework is, in principle, robust to the specific choice of language model as well as other aspects of our computational pipeline.
-For example, the word embedding model, timeseries segmentation model, and the episode-recall matching function could all be customized to suit a particular question space or application.
+For example, the word embedding model, timeseries segmentation model, and the episode-recall matching function could each be customized to suit a particular question space or application.
 Indeed, for some questions, interpretability of the embeddings may not be a priority, and thus other text embedding approaches (including the deep learning-based models described above) may be preferable.
-Future work will be needed to explore the influence of particular models on our framework's predictions and performance.
+Further work will be needed to explore the influence of particular models on our framework's predictions and performance.
 
@@
 Our work indicates that this approach is only loosely related to what educators might really want to measure: how well did the students understand the key ideas presented in the course?
-Under this typical framework of assessment, the same exam score of 50\% could be ascribed to two very different students: one who attended the full course but struggled to learn more than a broad overview of the material, and one who attended only half of the course but understood the material perfectly.
-Instead, one could apply our computational framework to build explicit content models of the course material and exam questions.
+Under this typical framework of assessment, the same exam score of 50\% could be ascribed to two very different students: one who attended to the full course but struggled to learn more than a broad overview of the material, and one who attended to only half of the course but understood the attended material perfectly.
+Instead, one could apply our computational framework to build explicit dynamic content models of the course material and exam questions.
 This approach would provide a more nuanced and specific view into which aspects of the material students had learned well (or poorly).
-In clinical settings, memory measures that incorporate such explicit content models might also provide more direct evaluations of patients' memories.
+In clinical settings, memory measures that incorporate such explicit content models might also provide more direct evaluations of patients' memories, and of doctor-patient interactions.
 
@@
 Data were collected by \cite{ChenEtal17}.
-In brief, participants ($n=22$) viewed the first 48 minutes of ``A Study in Pink'', the first episode of the BBC television series \textit{Sherlock}, while fMRI volumes were collected (TR = 1500~ms).
+In brief, participants ($n=22$) viewed the first 48 minutes of ``A Study in Pink,'' the first episode of the BBC television show \textit{Sherlock}, while fMRI volumes were collected (TR = 1500~ms).
 Participants were pre-screened to ensure they had never seen any episode of the show before.
@@
 \subsubsection*{Topic modeling}
-The input to the topic model we trained to characterize the dynamic content of the episode comprised 998 hand-generated annotations of short (mean: 2.96s) scenes spanning the video clip~(\citealp{ChenEtal17} generated 1000 annotations total; we removed two annotations referring to a break between the first and second scan sessions, during which no fMRI data was collected).
+The input to the topic model we trained to characterize the dynamic content of the episode comprised 998 hand-generated annotations of short (mean: 2.96s) scenes spanning the video clip~(\citealp{ChenEtal17} generated 1000 annotations total; we removed two annotations referring to a break between the first and second scan sessions, during which no fMRI data were collected).
 We concatenated the text for all of the annotated features within each segment, creating a ``bag of words'' describing each scene and performed some minor preprocessing (e.g., stemming possessive nouns and removing punctuation).
@@
 
-\subsubsection*{Parsing topic trajectories into events using Hidden Markov Models}
-We parsed the topic trajectories of the episode and participants' recalls into events using Hidden Markov Models~\citep[HMMs;][]{Rabi89}.
+\subsubsection*{Segmenting topic proportions matrices into discrete events using hidden Markov Models}
+We parsed the topic proportions matrices of the episode and participants' recalls into discrete events using hidden Markov Models~\citep[HMMs;][]{Rabi89}.
 Given the topic proportions matrix (describing the mix of topics at each timepoint) and a number of states, $K$, an HMM recovers the set of state transitions that segments the timeseries into $K$ discrete states.
@@
 
-\subsubsection*{Novel naturalistic memory metrics}
-
-\paragraph*{Precision.}
-We tested whether participants who recalled more events were also more \textit{precise} in their recollections.
-For each participant, we computed the average correlation between the topic vectors for each recall event and those of its closest-matching episode event.
-This gave a single value per participant representing the average precision across all recalled events.
-We then correlated these values with both hand-annotated and model-derived (i.e., the number of unique episode events matched by a participant's recall events) memory performance.
-
-\paragraph*{Distinctiveness.}
-We also considered the \textit{distinctiveness} of each recalled event.
-That is, how unique a participant's description of a episode event was, versus their descriptions of other episode events.
-We hypothesized that participants with high memory performance might describe each event in a more distinctive way (relative to those with lower memory performance who might describe events in a more general way).
-To test this hypothesis we define a distinctiveness score for each recall event $i$ as
-
-\[
-  d(i) = 1 - \frac{1}{N - 1} \sum_{j = \\i}\mathrm{corr}\left(\mathrm{event}_i, \mathrm{event}_j\right) 
-\]
-where the average is taken over the correlation between the recall event $i$'s topic vector and the topic vectors from all other recall events from that participant.
-We averaged these distinctiveness scores across all of the events recalled by the given participant to get the participant's distinctiveness score.
-We correlated these distinctiveness scores with hand-annotated and model-derived memory performance scores across-subjects, as above.
-
-\paragraph*{Averaging correlations}
-In all instances where we performed statistical tests involving precision or distinctiveness scores, we used the Fisher $z$-transformation~\citep{Fish25} to stabilize the variance across the distribution of correlation values prior to performing the test.
+\subsubsection*{Averaging correlations}
+In all instances where we performed statistical tests involving precision or distinctiveness scores (Fig.~\ref{fig:precision-detail}, we used the Fisher $z$-transformation~\citep{Fish25} to stabilize the variance across the distribution of correlation values prior to performing the test.
 Similarly, when averaging precision or distinctiveness scores, we $z$-transformed the scores prior to computing the mean, and inverse $z$-transformed the result.
@@
 In Figure~\ref{fig:trajectory}B, we present an analysis aimed at characterizing locations in topic space that different participants move through in a consistent way (via their recall topic trajectories).
-The two-dimensional topic space used in our visualizations (Fig.~\ref{fig:trajectory}) comprised a 60 x 60 (arbitrary units) square.
-We tiled this space with a 50 x 50 grid of evenly spaced vertices, and defined a circular area centered on each vertex whose radius was two times the distance between adjacent vertices (i.e., 2.4 units).
+The two-dimensional topic space used in our visualizations (Fig.~\ref{fig:trajectory}) comprised a $60 \times 60$ (arbitrary units) square.
+We tiled this space with a $50 \times 50$ grid of evenly spaced vertices, and defined a circular area centered on each vertex whose radius was two times the distance between adjacent vertices (i.e., 2.4 units).
 For each vertex, we examined the set of line segments formed by connecting each pair successively recalled events, across all participants, that passed through this circle.
@@
 In Figure~\ref{fig:brainz}, we present two analyses aimed at identifying brain regions whose responses (as participants viewed the episode) exhibited a particular temporal structure.
-We developed a searchlight analysis wherein we constructed a 5 x 5 x 5 cube of voxels (following \citealp{ChenEtal17}) centered on each voxel in the brain, and for each of these cubes, computed the temporal correlation matrix of the voxel responses during episode viewing.
+We developed a searchlight analysis wherein we constructed a $5 \times 5 \times 5$ cube of voxels (following \citealp{ChenEtal17}) centered on each voxel in the brain, and for each of these cubes, computed the temporal correlation matrix of the voxel responses during episode viewing.
 Specifically, for each of the 1976 volumes collected during episode viewing, we correlated the activity patterns in the given cube with the activity patterns (in the same cube) collected during every other timepoint.
-This yielded a 1976 by 1976 correlation matrix for each cube.
-Note: participant 5's scan ended 75s early, and in \citealp{ChenEtal17}'s publicly released dataset, their scan data was padded to match the length of the other participants'.
-For our searchlight analyses, we removed this padded data (i.e., the last 50 TRs), resulting in a 1925 by 1925 correlation matrix for each cube in participant 5's brain.
+This yielded a $1976 \times 1976$ correlation matrix for each cube.
+Note: participant 5's scan ended 75s early, and in \citealp{ChenEtal17}'s publicly released dataset, their scan data was zero-padded to match the length of the other participants'.
+For our searchlight analyses, we removed this padded data (i.e., the last 50 TRs), resulting in a $1925 \times 1925$ correlation matrix for each cube in participant 5's brain.
 
@@
 An example correlation matrix before and after warping is shown in Fig.~\ref{fig:brainz}B.
-This yielded a 1976 by 1976 correlation matrix for the episode template and for each participant's recall template.
+This yielded a $1976 \times 1976$ correlation matrix for the episode template and for each participant's recall template.
 
@@
 Specifically, we isolated the upper triangle of the episode correlation matrix and created a ``proximal correlation mask'' that included only diagonals from the upper triangle of the episode correlation matrix up to the first diagonal that contained no positive correlations.
-Applying this mask to the full episode correlation matrix was analogous to excluding diagonals beyond the corner of the largest diagonal block.
-In other words, the timescale of temporal correlations we considered corresponded to the longest period of thematic stability in the episode, and by extension the longest expected period of thematic stability in participants' recalls and the longest period of stability we might expect to see in voxel activity arising from processing or encoding episode content.
+Applying this mask to the full episode correlation matrix was equivalent to excluding diagonals beyond the corner of the largest diagonal block.
+In other words, the timescale of temporal correlations we considered corresponded to the longest period of thematic stability in the episode, and by extension the longest period of thematic stability in participants' recalls and the longest period of stability we might expect to see in voxel activity arising from processing or encoding episode content.
 Figure \ref{fig:brainz} shows this proximal correlation mask applied to the temporal correlation matrices for the episode, an example participant's (warped) recall, and an example cube of voxels from our searchlight analyses.
@@
 
-We further sought to ensure that our analysis identified regions where the activations’ temporal structure specifically reflected that of the episode, rather than regions whose activity was simply autocorrelated at a width similar to the episode template’s diagonal.
+We further sought to ensure that our analysis identified regions where the activations’ temporal structure specifically reflected that of the episode, rather than regions whose activity was simply autocorrelated at a timescale similar to the episode template’s diagonal.
 To achieve this, we used a phase shift-based permutation procedure, whereby we circularly shifted the episode’s topic trajectory by a random number of timepoints, computed the resulting ``null'' episode template, and re-ran the searchlight analysis, in full.
@@
 For each participant, we correlated the proximal diagonals from the upper triangle of the correlation matrix for each cube of voxels with the proximal diagonals from the upper triangle of their (time-warped) recall correlation matrix.
-As in the episode template analysis, this yielded a voxelwise map of correlation coefficients per participant.
+As in the episode template analysis, this yielded a voxelwise map of correlation coefficients for each participant.
 However, whereas the episode analysis compared every participant's responses to the same template, here the recall templates were unique for each participant.
@@
 Given a novel image (tagged with its value type; e.g., $t$-, $F$- or $p$-statistics), \texttt{Neurosynth} returns a list of terms whose meta-analysis images are most similar.
-Our permutation procedure yielded, for each of the two searchlight analyses, a voxelwise map of significance ($p$-statistic) values.
-These maps describe the extent to which each voxel \textit{specifically} reflected the temporal structure of the episode or individuals' recalls (i.e., for each voxel, the proportion of phase-shifted topic vector correlation matrices less similar to the voxel activity correlation matrix than the unshifted episode's correlation matrix).
+Our permutation procedure yielded, for each of the two searchlight analyses, a voxelwise map of $z$-values.
+These maps describe the extent to which each voxel \textit{specifically} reflected the temporal structure of the episode or individuals' recalls (i.e., relative to the null distributions of phase-shifted values).
 We inputted the two statistical maps described above to \texttt{Neurosynth} to create a list of the 10 most representative terms for each map.

### 2020-09-01 paper/supporting_information.tex
minor edits to main.tex, full pass through supplement

@@
 
+\newcommand{\methodsdemo}{1}
+\newcommand{\topicprops}{2}
+\newcommand{\listlearning}{3}
+\newcommand{\precisiondistinctiveness}{4}
+\newcommand{\precisiondistinctivenessdetail}{5}
+\newcommand{\trajectories}{6}
+\newcommand{\wordles}{7}
+\newcommand{\brains}{8}
+
 \title{\textit{Supporting Information for}: Geometric models reveal behavioral and neural signatures of how naturalistic experiences are transformed into episodic memories}
@@
 \begin{document}
+\begin{titlepage}
   \maketitle
+\end{titlepage}
 
@@
 In order to create accurate episode and recall models, we used an optimization method that was driven by our ability to explain hand-annotated memory performance metrics collected by \cite{ChenEtal17}.
-Specifically, we used a grid search to compute the $\omega$ (episode sliding window duration, in scenes), $\rho$ (recall sliding window duration, in sentences), and $K$ (number of topics) that satisfied
+In an earlier variant of our study~\citep{HeusMann18}, we used a grid search to compute the $\omega$ (episode sliding window duration, in scenes), $\rho$ (recall sliding window duration, in sentences), and $K$ (number of topics) that satisfied
 \[
@@
 \]
-where $\mathrm{corr}(\mu, \nu)$ is the per-participant correlation between the temporal correlation matrices of the episode ($\mu$) and recall ($\nu$) trajectory, and $\theta$ is the per-participant hand-annotated memory performance.
+where $\mathrm{corr}(\mu, \nu)$ is the per-participant correlation between the temporal correlation matrices of the episode ($\mu$) and recall ($\nu$) topic proportions matrices, and $\theta$ is the per-participant hand-counted number of recalled scenes.
 We searched over a grid of pre-specified values for each of these parameters; the resulting correlations are displayed in Figure~\ref{fig:paramsearch}.
 The optimal parameters were $\omega = 50$, $\rho = 10$, and $K = 100$.
-In subsequent refinements of our topic modeling approach, we made various improvements to how we parse the episode and recall text and construct the trajectories' timeseries, but maintained these optimized parameters throughout.
+In our current paper we made a number of improvements to how we preprocessed text and fit topic models (see \textit{Methods}), but we carried the same optimal parameters forward from \cite{HeusMann18} without performing any additional optimization.
 
-\begin{figure}[]
+\begin{figure}[b]
 \centering
@@
 \caption{\small \textbf{Optimizing topic model parameters.}  We performed a grid search over episode sliding window length ($\omega \in \{5, 10, 25, 50, 100 \}$), recall sliding window length ($\rho \in \{5, 10, 25, 50, 100 \}$), and number of topics ($K \in \{5, 10, 25, 50, 100 \}$).
-The reported correlations are between per-subject episode-recall trajectory correlations and per-subject hand-generated memory performance scores.}
+The reported correlations are between per-subject episode-recall correlations and per-participant hand-counted numbers of recalled scenes.}
 \label{fig:paramsearch}
@@
 
-The optimized model converged on 32 unique topics that were assigned non-zero weights over the course of the episode.
-We provide a list of the top ten highest-weighted words from each topic in Figure~\ref{fig:topics}.
+The optimized model converged on 32 unique topics that were assigned non-zero weights.  We provide a list of the top ten highest-weighted words from each topic in Figure~\ref{fig:topics}.
 
-\begin{figure}[]
+\begin{figure}[p]
 \centering
 \includegraphics[width=0.65\textwidth]{figs/topic_words}
-\caption{\small \textbf{Topics discovered in \textit{Sherlock}.} We applied a topic model to hand-annotated information about 1000 scenes spanning the 45 minute episode.
+\caption{\small \textbf{Topics discovered in \textit{Sherlock}.} We applied a topic model to hand-annotated information about 1000 scenes spanning the 48 minute episode.
 We identified 32 unique topics with non-zero weights (we used $K=100$ topics to fit the model).
@@
 \subsection*{Feature importance analyses}
-To determine the contribution of each feature to the shape of the episode topic trajectory, we conducted a ``leave one out'' analysis.
-Specifically, we compared the original episode topic trajectory (created using all hand-annotated features from the 998 manually identified scenes spanning the \textit{Sherlock} episode; see \textit{Methods} for a full list of features) with episode trajectories created using all but one type of feature.
-For each impoverished episode trajectory, we computed the timepoint-by-timepoint correlation matrix, and correlated the proximal diagonals from the upper right triangle with those from the temporal correlation matrix of the feature-complete trajectory (for details on how we isolated proximal temporal correlations, see \textit{Methods}).
-Observing a lower correlation between an impoverished trajectory (with a particular feature removed) and the feature-complete trajectory would suggest that the held-out feature contributed more prominently to the full episode trajectory's temporal structure.
-We found that hand-annotated narrative details played the greatest roll in determining the shape of the episode, whereas the name of the character(s) in focus for each shot contributed least (Fig.~\ref{fig:feature-importance}A).
+To determine the contribution of each feature to the temporal structure of the episode topic proportions matrix, we conducted a ``leave one out'' analysis.
+Specifically, we compared the original episode's topic proportions matrix (created using all hand-annotated features from the 998 manually identified scenes spanning the \textit{Sherlock} episode; see \textit{Methods} for a full list of features) with topic proportions matrices created using all but one type of feature.
+For each impoverished topic proportions matrix, we computed the timepoint-by-timepoint correlation matrix, and correlated the proximal diagonals from the upper right triangle with those from the temporal correlation matrix of the feature-complete matrix (for details on how we isolated proximal temporal correlations, see \textit{Methods}).
+Observing a lower correlation between an impoverished matrix (with a particular feature removed) and the feature-complete matrix would suggest that the held-out feature contributed more prominently to the full episode topic proportion matrix's temporal structure.
+We found that hand-annotated narrative details played the greatest roll in determining the temporal structure of the episode, whereas the name of the character(s) in focus for each shot contributed least (Fig.~\ref{fig:feature-importance}A).
 
@@
 \includegraphics[width=1\textwidth]{figs/feature_value}
-\caption{\small \textbf{Feature importance analysis.} \textbf{A.} Contributions of each feature type to the structure of the episode trajectory.
-The bar heights reflect the correlation between the episode trajectory computed using all features with a episode trajectory computed using all features except the indicated feature.
-(Lower bars reflect features that contribute more substantially to the episode trajectory's shape.) \textbf{B.} Which features are preserved during recall?
+\caption{\small \textbf{Feature importance analysis.} \textbf{A.} Contributions of each feature type to the structure of the episode topic proportions matrix.
+The bar heights reflect the correlation between the episode topic proportions matrix computed using all features with an episode topic proportions matrix computed using all features except the indicated feature.
+(Lower bars reflect features that contribute more substantially to the episode's temporal structure.) \textbf{B.} Which features are preserved during recall?
 The bar heights reflect the (average) across-participant correlations between the episode and recall trajectories.
@@
 
-Next, we sought to determine which annotated features contributed aspects of the episode trajectory's shape that were preserved in participants' later recalls.
-Specifically, we computed the timepoint-by-timepoint correlation matrix of the episode topic trajectory, and correlated the proximal diagonals from its upper triangle with those from the timepoint-by-timepoint correlation matrices for each participant's recall topic trajectory (stretched via linear interpolation to have the same number of timepoints as the episode trajectory).
+Next, we sought to determine which annotated features contributed aspects of the episode's temporal structure that were preserved in participants' later recalls.
+Specifically, we computed the timepoint-by-timepoint correlation matrix of the episode's topic proportions matrix, and correlated the proximal diagonals from its upper triangle with those from the timepoint-by-timepoint correlation matrices for each participant's recall topic proportions matrices (stretched via linear interpolation to have the same number of timepoints as the episode topic proportions matrix).
 This yielded a single correlation coefficient for each participant.
 We then repeated this analysis with each annotated feature held out in turn.
-Observing a lower correlation between the episode and recall trajectories (constructed in the absence of a given feature) would indicate that participants utilize changes in that feature's content to discriminate between sections of the episode when organizing their recalls.
-We found that hand-annotated narrative details were the most heavily utilized feature, whereas changes in the text present on-screen, the indoor/outdoor distinction between scenes, the camera angle, the names of the various characters on screen, and the location in which the scene took place tended not to impact participants' recall structures (i.e., removing those features resulted in a \textit{greater} episode-recall topic vector correlation than including them; Fig.~\ref{fig:feature-importance}B).
+Observing a lower correlation between the episode and recall topic proportions matrices (constructed in the absence of a given feature) would indicate that participants utilize changes in that feature's content to discriminate between sections of the episode when organizing their recalls.
+We found that hand-annotated narrative details were the most heavily utilized feature, whereas changes in the text present on-screen, the indoor/outdoor distinction between scenes, the camera angle, the names of the various characters on screen, and the location in which the scene took place tended not to impact participants' recall structures (i.e., removing those features resulted in a \textit{greater} episode-recall correlation than including them; Fig.~\ref{fig:feature-importance}B).
 
@@
 For example, knowing which character is in focus during a given scene may also provide information about which character is speaking.
-We computed topic trajectories from the annotations for each individual feature, in turn, and (using the same technique as in the above analyses) compared the proximal temporal correlation structure of each single-feature trajectory to each other, as well as to that of the full episode.
-This provided additional confirmation that the shape of the full episode trajectory was largely driven by narrative details.
+We computed topic proportions matrices from the annotations for each individual feature, in turn, and (using the same technique as in the above analyses) compared the proximal temporal correlation structure of each single-feature topic proportions matrix to each other, as well as to that of the full episode.
+This provided additional confirmation that the full episode's temporal structure was largely driven by narrative details.
 We also found that character-driven features (characters on screen, characters speaking, and characters in focus) were strongly correlated.
-Other details, such as the presence or absence of music, led to very different topic trajectories (Fig.~\ref{fig:feature-importance}C).
+Other details, such as the presence or absence of music, led to very different topic proportions matrices (Fig.~\ref{fig:feature-importance}C).
 %\FloatBarrier
@@
 \subsection*{Creating a low-dimensional embedding space}
-Figures~7 and 8C in the main text display two-dimensional projections of the 100-dimensional topic trajectories for the episode (7A, 8C), average recall (7B), and each individual's recall (7C, 8C).
+Figures~\trajectories~and~\wordles C in the main text display two-dimensional projections of the 100-dimensional topic trajectories for the episode (Figs.~\trajectories A,~\wordles C), average recall (Fig.~\trajectories B), and each individual's recall (Figs.~\trajectories C,~\wordles C).
 We created these embeddings using the Uniform Manifold Approximation and Projection algorithm \citep[UMAP;][]{McInEtal18} called from our high-dimensional visualization and text analysis software, \texttt{HyperTools}~\citep{HeusEtal18a}.
@@
 
-UMAP achieves a balance between representing local and global structure via a subset of its hyper-parameters: \texttt{n\_neighbors} , \texttt{spread}, and \texttt{min\_dist}.
-The \texttt{n\_neighbors} hyper-parameter ($K$) denotes the number of nearest neighbors to consider in constructing the high-dimensional fuzzy simplicial set for each datapoint.
-\texttt{Spread} ($\gamma$) and \texttt{min\_dist} ($\delta$) function together to create the differentiable decay curve used to approximate the injective function for mapping between high- and low-dimensional fuzzy simplicial sets.
-In essence, \texttt{min\_dist} determines the degree to which nearby points are clustered or expanded, relative to to the overall \texttt{spread}.
+UMAP achieves a balance between representing local and global structure via a subset of its hyperparameters: \texttt{n\_neighbors} , \texttt{spread}, and \texttt{min\_dist}.
+The \texttt{n\_neighbors} hyperparameter ($K$) denotes the number of nearest neighbors to consider in constructing the high-dimensional fuzzy simplicial set for each datapoint.
+The \texttt{spread} ($\gamma$) and \texttt{min\_dist} ($\delta$) hyperparameters function together to create the differentiable decay curve used to approximate the injective function for mapping between high- and low-dimensional fuzzy simplicial sets.
+In brief, \texttt{min\_dist} determines the degree to which nearby points are clustered or expanded, relative to to the overall \texttt{spread}.
 
-Two other parameters ultimately affect this balance between preserving local and global structure: the seed ($\tau$) for the (pseudo-)random number generator, and the order of the observations (i.e., trajectories) to be embedded ($\varphi$).
+Two other parameters ultimately affect this balance between preserving local versus global structure: the seed ($\tau$) for the (pseudo-)random number generator (RNG), and the order of the observations (i.e., trajectories) to be embedded ($\varphi$).
 As described in \textit{Methods}, we ensured the episode and recall events were projected onto the \textit{same} low-dimensional manifold by fitting the embedding model to a stacked matrix of all episode, average recall, and individuals' recall events.
@@
 
-We performed a grid search over pre-specified values of these hyper-parameters, and optimized the manifold space for visualization based on two criteria: First, that the 2D embedding of the episode trajectory should reflect its original 100-dimensional structure as faithfully as possible.
-Second, that the path traversed by the embedded episode trajectory should intersect itself a minimal number of times.
+We performed a grid search over pre-specified values of these hyperparameters, and optimized the manifold space for visualization based on two criteria.
+First, the 2D embedding of the episode trajectory should reflect its original 100-dimensional structure as faithfully as possible.
+Second, the path traversed by the embedded episode trajectory should intersect itself a minimal number of times.
 The first criteria helps bolster the validity of visual intuitions about relationships between sections of episode content, based on their locations in the embedding space.
-The second criteria was motivated by the observed low off-diagonal values in the episode trajectory's temporal correlation matrix (suggesting that the same topic-space coordinates should not be revisited; see Figure~2A in the main text) and the inability to accurately describe the consistency of participants' transitions through topic space at locations where those transitions frequently occurred in multiple, orthogonal directions (see \textit{Methods} for analysis details).
-We formalized this optimization as the combination of hyper-parameter values that satisfied
+The second criteria was motivated by the observed low off-diagonal values in the episode topic proportions matrix's temporal correlation matrix (suggesting that the same topic-space coordinates should not be revisited; see Figure~\topicprops A in the main text).
+Further, we found through simulation that our statistical procedure for testing the consistency of trajectory directions across participants (Fig.~\trajectories B, also see \textit{Methods}) can be confounded when and where the topic trajectory intersects itself.
+We formalized this optimization as the combination of hyperparameter values that satisfied
 \[
@@
 $\xi$ is the episode's trajectory through the manifold space; $\chi$ is the original, 100-dimensional episode trajectory; $\Upsilon$ is a function that computes a condensed matrix of pairwise distances between event vectors (computed using correlation distance in the original topic space and Euclidean distance in the manifold space); $\mathrm{corr}\left(\Upsilon\left(\xi\right), \Upsilon\left(\chi\right)\right)$ is the correlation between the sets of pairwise distances, and $\Gamma$ is the number of instances in which lines drawn between consecutive episode event embeddings intersected each other.
-The sets of hyper-parameter values we searched over comprised: $K \in \{10x \in \mathbb{Z}~|~10 < x <  22\} \cup \{161\}$ (a range roughly centered on half the total number of events, 161, in order to balance representations of local and global structure); $\gamma \in \{1, 3, 5, 7, 9\}$; $\delta \in \{0.1, 0.3, 0.5, 0.7, 0.9\}$; $\tau \in \{x \in \mathbb{Z}~|~0 < x < 101\}$; and $\varphi \in {S\choose3},~\mathrm{where}~S=\{\mathrm{episode~events,~average~recall~events, individual~recall~events}\}$.
+The sets of hyperparameter values we searched over comprised: $K \in \{10x \in \mathbb{Z}~|~10 < x <  22\} \cup \{161\}$ (a range roughly centered on half the total number of events, 161, in order to balance representations of local and global structure); $\gamma \in \{1, 3, 5, 7, 9\}$; $\delta \in \{0.1, 0.3, 0.5, 0.7, 0.9\}$; $\tau \in \{x \in \mathbb{Z}~|~0 < x < 101\}$; and $\varphi \in {S\choose3},~\mathrm{where}~S=\{\mathrm{episode~events,~average~recall~events, individual~recall~events}\}$.
 The optimal parameters (that yielded $\Phi=0$) were $K=170$, $\gamma=7$, $\delta=0.7$, $\tau=41$, with the order of sequence $\varphi$ as the average recall events, episode events, and individuals' recall events, vertically concatenated, in order.
 
-\FloatBarrier
+% \FloatBarrier
+\newpage
+\begin{centering}
+ \vspace*{\fill}
     \section*{Participant-level figures referenced in the main text}
+    \vspace*{\fill}
+  \end{centering}
 
@@
 \includegraphics[width=\textwidth]{figs/corrmats}
-\caption{\small \textbf{Recall trajectory temporal correlation matrices and event segmentation fits.} Each panel is in the same format as Figure~2E in the main text.
+\caption{\small \textbf{Recall temporal correlation matrices and event segmentation fits.} Each panel is in the same format as Figure~\topicprops E in the main text.
 The yellow boxes indicate HMM-identified event boundaries.}
@@
 \includegraphics[width=\textwidth]{figs/matchmats}
-\caption{\small \textbf{episode-recall event correlation matrices.}  Each panel is in the same format as Figure~2G in the main text.
+\caption{\small \textbf{Episode-recall event correlation matrices.}  Each panel is in the same format as Figure~2G in the main text.
 The yellow boxes mark the matched episode event for each recall event (i.e., the maximum correlation in each column).}
@@
 \centering
-\includegraphics[width=.9\textwidth]{figs/k_optimization}
-\caption{\small \textbf{episode and recall trajectory \textit{K}-optimization functions.}  We selected the optimal $K$-value for the episode and each recall trajectory, using the formula described in \textit{Methods}.
-This computation resulted in a curve for each trajectory, describing the Wasserstein distance between the distributions of within-event and across-event topic vector correlations, as a function of $K$.}
+\includegraphics[width=\textwidth]{figs/k_optimization}
+\caption{\small \textbf{Episode and recall topic proportions matrix \textit{K}-optimization functions.}  We selected the optimal $K$-value for the episode and each recall topic proportions matrix, using the formula described in \textit{Methods}.
+This computation resulted in a curve for each matrix, describing the Wasserstein distance between the distributions of within-event and across-event topic vector correlations, as a function of $K$.}
 \label{fig:k_optimization}
 \end{figure}
-
-\FloatBarrier
 

### 2020-09-02 paper/supporting_information.tex
updated title

@@
 
-\title{\textit{Supporting Information for}: Geometric models reveal behavioral and neural signatures of how naturalistic experiences are transformed into episodic memories}
+\title{\textit{Supporting Information for}: Geometric models reveal behavioral and neural signatures of transforming naturalistic experiences into episodic memories}
 \author{Andrew C.

### 2020-09-02 paper/main.tex
recompiled pdf with updated figs
center fig 5
updated title

@@
 
-\title{Geometric models reveal behavioral and neural signatures of how naturalistic experiences are transformed into episodic memories}
+\title{Geometric models reveal behavioral and neural signatures of transforming naturalistic experiences into episodic memories}
 
@@
 In traditional episodic memory experiments \citep[e.g., list-learning or trial-based experiments;][]{Murd62a, Kaha96}, remembering is often cast as a discrete binary operation: each studied item may be separated from the rest of one's experience and labeled as having been either recalled or forgotten.
-More nuanced studies might incorporate self-reported confidence measures as a proxy for memory strength, or ask participants to discriminate between recollecting the (contextual) details of an experience or having a general feeling of familiarity~\citep{Yone02}.
+More nuanced studies might incorporate self-reported confidence measures as a proxy for memory strength, or ask participants to discriminate between recollecting the (contextual) details of an experience and having a general feeling of familiarity~\citep{Yone02}.
 Using well-controlled, trial-based experimental designs, the field has amassed a wealth of information regarding human episodic memory~\citep[for review see][]{Kaha12}.
@@
   \centering
-  \includegraphics[width=1\textwidth]{figs/precision_detail}
+  \vspace*{-1cm}
+  \includegraphics[width=.8\textwidth]{figs/precision_distinctiveness_detail}
   \caption{\small \textbf{Precision reflects the completeness of recall, whereas distinctiveness reflects recall specificity.} \textbf{A.} Recall precision by episode event.

### 2020-09-03 paper/main.tex
removed all uses of the word experiment in reference to our study and chen et al, as per reviewer 3 request

@@
 
-\cite{ChenEtal17} collected hand-annotated information about each of 1,000 (manually identified) scenes spanning the roughly 50 minute video used in their experiment.
+\cite{ChenEtal17} collected hand-annotated information about each of 1,000 (manually identified) scenes spanning the roughly 50 minute video used in their study.
 This information included: a brief narrative description of what was happening, the location where the scene took place, the names of any characters on the screen, and other similar details (for a full list of annotated features, see \textit{Methods}).
@@
   \vspace*{-1cm}
-  \includegraphics[width=.8\textwidth]{figs/precision_distinctiveness_detail}
+  \includegraphics[width=.68\textwidth]{figs/precision_distinctiveness_detail}
   \caption{\small \textbf{Precision reflects the completeness of recall, whereas distinctiveness reflects recall specificity.} \textbf{A.} Recall precision by episode event.
@@
 
-\subsection*{Experimental design and data collection}
+\subsection*{Paradigm and data collection}
 Data were collected by \cite{ChenEtal17}.
@@
 Participants were then allowed to speak for as long as they wished, and verbally indicated when they were finished (e.g., `I’m done').''  Five participants were dropped from the original dataset due to excessive head motion (2 participants), insufficient recall length (2 participants), or falling asleep during stimulus viewing (1 participant), resulting in a final sample size of $n=17$.
-For additional details about the experimental procedure and scanning parameters, see \cite{ChenEtal17}.
-The experimental protocol was approved by Princeton University's Institutional Review Board.
+For additional details about the testing procedures and scanning parameters, see \cite{ChenEtal17}.
+The testing protocol was approved by Princeton University's Institutional Review Board.
 

### 2020-09-03 paper/main.tex
shrank fig 5
inputted Andy's edits -- "ship it!"

@@
 This indicates that participants who tended to precisely recount low-level details of episode events also tended to do so in an event-specific way (e.g., as opposed to detailing recurring themes that were present in most or all episode events; this behavior would have resulted in high precision but low distinctiveness).
-We found that, across participants, higher precision scores were positively correlated with both the hand-annotated ($r(15) = 0.60, p = 0.010$) and model-estimated ($r(15) = 0.90, p < 0.001$) numbers of events that participants recalled.
+We found that, across participants, higher precision scores were positively correlated with the numbers of both hand-annotated scenes ($r(15) = 0.60, p = 0.010$) and model-estimated events ($r(15) = 0.90, p < 0.001$) that participants recalled.
 Participants' average distinctiveness scores were also correlated with both the hand-annotated ($r(15) = 0.45, p = 0.068$) and model-estimated ($r(15) = 0.71, p = 0.001$) numbers of recalled events.

### 2020-09-03 paper/main.tex
tweaked precision/distinctiveness details and fixed panel refs

@@
 Examining individual recalls of the same episode event can provide insights into how the above precision and distinctiveness scores may be used to characterize similarities and differences in how different people describe the same shared experience.
-In Figure \ref{fig:precision-detail}, we compare recalls for the same episode event (event 22) from different participants: one with a high precision score (P17), and the other with a low precision score (P6).
-From the HMM-identified event boundaries, we recovered the set of annotations describing the content of an example episode event (Fig.~\ref{fig:precision-detail}B), and divided them into different color-coded sections for each action or feature described.
-We used an analogous approach to identify the set of sentences comprising the corresponding recall events for each of the two example participants.
-Figure~\ref{fig:precision-detail}C shows excerpts of two participants' recall transcripts that comprised sentences between the first and last descriptions of content from the example episode event.
-We then colored all words describing actions and features in the transcripts shown in Panel C according to the color-coded annotations in Panel B.
+In Figure \ref{fig:precision-detail}, we compare recalls for the same episode event from the participants with the highest (P17) and lowest (P6) precision scores.
+From the HMM-identified episode event boundaries, we recovered the set of annotations describing the content of a single episode event (event 22; Fig.~\ref{fig:precision-detail}C), and divided them into different color-coded sections for each action or feature described.
+Next, we used an analogous approach to identify the set of sentences comprising the corresponding recall event from each of the two example participants (Fig.~\ref{fig:precision-detail}D).
+We then colored all words describing actions and features in the transcripts shown in Panel D according to the color-coded annotations in Panel C.
 Visual comparison of these example recalls reveals that the more precise recall captures more of the episode event's content, and in greater detail.
 
-Figure \ref{fig:precision-detail} also illustrates the differences between high and low distinctiveness scores for the same event detailed in Figure~\ref{fig:precision-detail}B (i.e., event 22).
-Here, we have extracted the set of sentences comprising the most distinctive recall event (P9) and least distinctive recall event (P6) matched to the example episode event (Fig.~\ref{fig:precision-detail}F).
-We also extracted the annotations for the example episode event, as well as those from each other episode event whose content the example participants' single recall events described (Fig.~\ref{fig:precision-detail}E).
-We assigned each episode event a unique color (Panel E) and colored each recalled phrase or sentence (Panel F) according to the episode events they best matched.
+Figure \ref{fig:precision-detail} also similarly illustrates the differences between high and low distinctiveness scores.
+We extracted the set of sentences comprising the most distinctive recall event (P9) and least distinctive recall event (P6) corresponding to the example episode event shown in Panel C (event 22).
+We also extracted the annotations for all episode events whose content these participants' single recall events described .
+We assigned each episode event a unique color (Fig.~\ref{fig:precision-detail}E), and colored each recall sentence (Panel F) according to the episode events they best matched.
 Visual inspection of Panel F reveals that the most distinctive recall's content is tightly concentrated around event 22, whereas the least distinctive recall incorporates content from a much wider range of episode events.

### 2020-09-03 paper/main.tex
also updated fig 5 caption

@@
   \vspace*{-1cm}
-  \includegraphics[width=.68\textwidth]{figs/precision_distinctiveness_detail}
+  \includegraphics[width=.7\textwidth]{figs/precision_distinctiveness_detail}
   \caption{\small \textbf{Precision reflects the completeness of recall, whereas distinctiveness reflects recall specificity.} \textbf{A.} Recall precision by episode event.
@@
 Colored dots within each violin plot represent individual participants' recall precision for the given event.
-episode events are ordered along the $x$-axis by the average precision with which they were remembered.
-\textbf{B.} The set of ``Narrative Details'' episode annotations (generated by \citealp{ChenEtal17}) for scenes comprising an example episode event (22) identified by the HMM.
+\textbf{B.} Recall distinctiveness by episode event.
+analogous to Panel A.
+\textbf{C.} The set of ``Narrative Details'' episode annotations (generated by \citealp{ChenEtal17}) comprising an example episode event (22) identified by the HMM.
 Each action or feature is highlighted in a different color.
-\textbf{C.} Excerpts from the most precise (P17) and least precise (P6) participants' recalls of episode event 22.
+\textbf{D.} Sentences comprising the most precise (P17) and least precise (P6) participants' recalls of episode event 22.
 Descriptions of specific actions or features reflecting those highlighted in Panel B are highlighted in the corresponding color.
@@
 The unhighlighted text denotes correctly recalled information about other episode events.
-\textbf{D.} Recall distinctiveness by episode event.
-Kernel density estimates for each episode event's distribution of recall distinctiveness scores, analogous to Panel A.
 \textbf{E.} The sets of ``Narrative Details'' episode annotations (generated by \citealp{ChenEtal17}) for scenes comprising episode events described by the example participants in Panel F.

### 2020-09-04 paper/main.tex
edits through pg 21

@@
 Fitzpatrick\textsuperscript{1, \textdagger}, and Jeremy R.
-Manning\textsuperscript{1, *}\\\textsuperscript{1}Department of Psychological and Brain Sciences\\Dartmouth College, Hanover, NH 03755, USA\\\textsuperscript{2}Akili Interactive\\Boston, MA 02110\\\textsuperscript{\textdagger}Denotes equal contribution\\\textsuperscript{*}Corresponding author: Jeremy.R.Manning@Dartmouth.edu}
+Manning\textsuperscript{1, *}\\\textsuperscript{1}Department of Psychological and Brain Sciences\\Dartmouth College, Hanover, NH 03755, USA\\\textsuperscript{2}Akili Interactive Labs\\Boston, MA 02110\\\textsuperscript{\textdagger}Denotes equal contribution\\\textsuperscript{*}Corresponding author: Jeremy.R.Manning@Dartmouth.edu}
 
@@
 What does it mean to \textit{remember} something?
-In traditional episodic memory experiments \citep[e.g., list-learning or trial-based experiments;][]{Murd62a, Kaha96}, remembering is often cast as a discrete binary operation: each studied item may be separated from the rest of one's experience and labeled as having been either recalled or forgotten.
+In traditional episodic memory experiments \citep[e.g., list-learning or trial-based experiments;][]{Murd62a, Kaha96}, remembering is often cast as a discrete, binary operation: each studied item may be separated from the rest of one's experience and labeled as having been either recalled or forgotten.
 More nuanced studies might incorporate self-reported confidence measures as a proxy for memory strength, or ask participants to discriminate between recollecting the (contextual) details of an experience and having a general feeling of familiarity~\citep{Yone02}.
@@
 For example, prior work has shown that event boundaries can influence how we learn sequences of items~\citep{HeusEtal18b, DuBrDava13}, navigate~\citep{BrunEtal18}, and remember and understand narratives~\citep{ZwaaRadv98, EzzyDava11}.
-This work also suggests a means of distinguishing the essence of an experience from its low-level details.
-The overall structure of events and event transitions reflects how the high-level experience unfolds (i.e., its essence), while subtler event-level properties reflect low-level details.
+This work also suggests a means of distinguishing the essence of an experience from its low-level details:  The overall structure of events and event transitions reflects how the high-level experience unfolds (i.e., its essence), while subtler event-level properties reflect low-level details.
 Prior research has also implicated a network of brain regions (including the hippocampus and the medial prefrontal cortex) in playing a critical role in transforming experiences into structured and consolidated memories ~\citep{TompDava17}.
@@
 We analyzed an open dataset that comprised behavioral and functional Magnetic Resonance Imaging (fMRI) data collected as participants viewed and then verbally recounted an episode of the BBC television show \textit{Sherlock}~\citep{ChenEtal17}.
-We developed a computational framework for characterizing the temporal dynamics of the moment-by-moment content of the episode, and of participants' verbal recalls.
+We developed a computational framework for characterizing the temporal dynamics of the moment-by-moment content of the episode and of participants' verbal recalls.
 Our framework uses topic modeling~\citep{BleiEtal03} to characterize the thematic conceptual (semantic) content present in each moment of the episode and recalls by projecting each moment into a word embedding space.
@@
 Comparing the overall shapes of the topic trajectories for the episode and participants' recalls reveals which aspects of the episode's essence were preserved (or discarded) in the translation into memory.
-We also develop two metrics for assessing participants' memories for low-level details: (1) the \textit{precision} with which a participant recounts details about each event, and (2) the \textit{distinctiveness} of each recalled event, relative to other events.
+We also develop two metrics for assessing participants' memories for low-level details: (1) the \textit{precision} with which a participant recounts details about each event, and (2) the \textit{distinctiveness} of their recall for each event, relative to other events.
 We examine how these metrics relate to overall memory performance as judged by third-party human annotators.
@@
 The entries in the topics matrix reflect how each word in the vocabulary is weighted by each discovered topic.
-For example, a detective-themed topic might weight heavily on words like ``crime,'' and ``search.''  The second output is a \textit{topic proportions matrix}, with one row per document and one column per topic.
+For example, a detective-themed topic might weight heavily on words like ``crime,'' and ``search.''  The second output is a \textit{topic proportions matrix} with one row per document and one column per topic.
 The topic proportions matrix describes the mixture of discovered topics reflected in each document.
 
-\cite{ChenEtal17} collected hand-annotated information about each of 1,000 (manually identified) scenes spanning the roughly 50 minute video used in their study.
-This information included: a brief narrative description of what was happening, the location where the scene took place, the names of any characters on the screen, and other similar details (for a full list of annotated features, see \textit{Methods}).
-We took from these annotations the union of all unique words (excluding stop words, such as ``and,'' ``or,'' ``but,'' etc.) across all features and scenes as the vocabulary for the topic model.
-We then concatenated the sets of words across all features contained in overlapping sliding windows of (up to) 50 scenes, and treated each window as a single document for the purpose of fitting the topic model.
+\cite{ChenEtal17} collected hand-annotated information about each of 1,000 (manually delineated) time segments spanning the roughly 50 minute video used in their study.
+Each annotation included: a brief narrative description of what was happening, the location where the action took place, the names of any characters on the screen, and other similar details (for a full list of annotated features, see \textit{Methods}).
+We the union of all unique words (excluding stop words, such as ``and,'' ``or,'' ``but,'' etc.) across all features from all annotations as the vocabulary for the topic model.
+We then concatenated the sets of words across all features contained in overlapping sliding windows of (up to) 50 annotations, and treated each window as a single document for the purpose of fitting the topic model.
 Next, we fit a topic model with (up to) $K = 100$ topics to this collection of documents.
 We found that 32 unique topics (with non-zero weights) were sufficient to describe the time-varying content of the episode (see \textit{Methods}; Figs.~\ref{fig:schematic}, \topics).
-We note that our approach is similar in some respects to Dynamic Topic Models~\citep{BleiLaff06}, in that we sought to characterize how the thematic content of the episode evolved over time.
+We note that our approach is similar in some respects to Dynamic Topic Models~\citep{BleiLaff06} in that we sought to characterize how the thematic content of the episode evolved over time.
 However, whereas Dynamic Topic Models are designed to characterize how the properties of \textit{collections} of documents change over time, our sliding window approach allows us to examine the topic dynamics within a single document (or video).
@@
 \includegraphics[width=1\textwidth]{figs/schematic}
-\caption{\small \textbf{Topic weights in episode and recall content.} We used hand-annotated descriptions of each manually identified scene from the episode to fit a topic model.
-Three example episode frames (first row) and their associated descriptions (second row) are displayed.
-The third row shows an example participant's recountings of the same three scenes.
+\caption{\small \textbf{Topic weights in episode and recall content.} We used detailed, hand-generated annotations describing each manually identified time segment from the episode to fit a topic model.
+Three example frames from the episode (first row) are displayed, along with their descriptions from the corresponding episode annotation (second row) and an example participant's recall transcript (third row).
 We used the topic model (fit to the episode annotations) to estimate topic vectors for each moment of the episode and each sentence of participants' recalls.
@@
 \end{figure}
-% add an x-label under the "
 
@@
 Several of the identified topics were highly similar, which we hypothesized might allow us to distinguish between subtle narrative differences if the distinctions between those overlapping topics were meaningful.
-The topic vectors for each timepoint were also \textit{sparse}, in that only a small number (typically one or two) of topics tended to be ``active'' in any given timepoint (see Fig.~\ref{fig:model}A).
+The topic vectors for each timepoint were also \textit{sparse}, in that only a small number of topics (typically one or two) tended to be ``active'' in any given timepoint (see Fig.~\ref{fig:model}A).
 Further, the dynamics of the topic activations appeared to exhibit \textit{persistence} (i.e., given that a topic was active in one timepoint, it was likely to be active in the following timepoint) along with \textit{occasional rapid changes} (i.e., occasionally topic weights would change abruptly from one timepoint to the next).
@@
 First, although every individual participant's recalls could be segmented into discrete events (i.e., every individual participant's recall correlation matrix exhibited clear block diagonal structure; Fig.~\corrmats), each participant appeared to have a unique \textit{recall resolution}, reflected in the sizes of those blocks.
-While some participants' recall topic proportions segmented into just a few events (e.g., Participants P4, P5, and P7), others' segmented into many shorter duration events (e.g., Participants P12, P13, and P17).
+While some participants' recall topic proportions segmented into just a few events (e.g., Participants P4, P5, and P7), others' segmented into many shorter-duration events (e.g., Participants P12, P13, and P17).
 This suggests that different participants may be recalling the episode with different levels of detail---i.e., some might recount only high-level essential plot details, whereas others might recount low-level details instead (or in addition).
@@
 Further, the episode and recalls exhibit event boundaries that can be identified automatically using HMMs to segment the dynamic content.
-Next, we asked whether some correspondence might be made between the specific content of the events the participants experienced in the episode, and the events they later recalled.
-We labeled each recalled event as matching the episode event with the most similar (i.e., most highly correlated) topic vector (Figs.~\ref{fig:model}G, \matchmats).
+Next, we asked whether some correspondence might be made between the specific content of the events the participants experienced while viewing the episode, and the events they later recalled.
+We labeled each recall event as matching the episode event with the most similar (i.e., most highly correlated) topic vector (Figs.~\ref{fig:model}G, \matchmats).
 This yielded a sequence of ``presented'' events from the original episode, and a (potentially differently ordered) sequence of ``recalled'' events for each participant.
@@
 Temporal clustering refers to the extent to which participants group their recall responses according to encoding position.
-Overall, we found that sequentially viewed episode events tended to appear nearby in participants' recall event sequences (mean clustering score: 0.767, SEM: 0.029).
-Participants with higher temporal clustering scores tended to exhibit better overall memory for the episode, according to both \cite{ChenEtal17}'s hand-counted numbers of recalled scenes from the episode (Pearson's $r(15) = 0.62,~p = 0.008$) and the numbers of episode events that best-matched at least one recalled event (i.e., model-estimated number of recalled events; Pearson's $r(15) = 0.49, p = 0.0046$).
+Overall, we found that sequentially viewed episode events tended to appear nearby in participants' recall event sequences (mean clustering score: 0.732, SEM: 0.033).
+Participants with higher temporal clustering scores tended to exhibit better overall memory for the episode, according to both \cite{ChenEtal17}'s hand-counted numbers of recalled scenes from the episode (Pearson's $r(15) = 0.49,~p = 0.046$) and the numbers of episode events that best-matched at least one recall event (i.e., model-estimated number of events recalled; Pearson's $r(15) = 0.59,~p = 0.013$).
 Semantic clustering measures the extent to which participants cluster their recall responses according to semantic similarity.
-We found that participants tended to recall semantically similar episode events together (mean clustering score: 0.787, SEM: 0.018), and that semantic clustering score was also related to both hand-annotated  (Pearson's $r(15) = 0.65,~p = 0.004$) and model-estimated (Pearson's $r(15) = 0.61,~p = 0.0092$) numbers of recalled events.
+We found that participants tended to recall semantically similar episode events together (mean clustering score: 0.650, SEM: 0.032), and that semantic clustering score was also related to both hand-annotated  (Pearson's $r(15) = 0.65,~p = 0.005$) and model-estimated (Pearson's $r(15) = 0.58,~p = 0.015$) numbers of recalled events.
 
@@
 The yellow boxes highlight the maximum correlation in each column.
-The example participant's overall precision score was computed as the average across correlation values in the yellow boxes.
+The example participant's overall precision score was computed as the average across (Fisher $z$-transformed) correlation values in the yellow boxes.
 Their distinctiveness score was computed as the average (over recall events) of the $z$-scored (within column) event precisions.
@@
 Yet when researchers study memory in highly simplified paradigms, those nuances are not typically observable.
-We next developed two novel continuous metrics, termed precision and distinctiveness, aimed at characterizing distortions in the conceptual content of individual recalled events, and the conceptual overlap between how people described different events.
+We next developed two novel, continuous metrics, termed \textit{precision} and \textit{distinctiveness}, aimed at characterizing distortions in the conceptual content of individual recall events, and the conceptual overlap between how people described different events.
 
@@
 \textit{Distinctiveness} is intended to capture the ``specificity'' of recall.
-In other words, distinctiveness quantifies the extent to which a given recalled event reflects the most similar episode event over and above its reflection of other episode events.
+In other words, distinctiveness quantifies the extent to which a given recall event reflects the most similar episode event over and above other episode events.
 Intuitively, distinctiveness is like a normalized variant of our precision metric.
@@
 This enables us to quantify how precisely a participant tended to recall subtle within-event details, as well as how specific (distinctive) those details were to individual events from the episode.
-Participants' average precision and distinctiveness scores were strongly correlated ($r(15) = 0.90, p < 10^{-5}$).
+Participants' average precision and distinctiveness scores were strongly correlated ($r(15) = 0.90, p < 0.001$).
 This indicates that participants who tended to precisely recount low-level details of episode events also tended to do so in an event-specific way (e.g., as opposed to detailing recurring themes that were present in most or all episode events; this behavior would have resulted in high precision but low distinctiveness).
@@
 The preceding analyses sought to characterize how participants' recountings of individual episode events captured the low-level details of each event.
-Next we sought to characterize how participants' recountings of the full episode captured its high-level essence-- i.e., the shape of the episode's trajectory through word embedding (topic) space.
+Next, we sought to characterize how participants' recountings of the full episode captured its high-level essence---i.e., the shape of the episode's trajectory through word embedding (topic) space.
 To visualize the essence of the episode and each participant's recall trajectory~\citep{HeusEtal18a}, we projected the topic proportions matrices for the episode and recalls onto a shared two-dimensional space using Uniform Manifold Approximation and Projection~\citep[UMAP; ][]{McInEtal18}.
@@
 In other words, participants' recalls exhibited similar trajectories to each other that also matched the trajectory of the original episode (Fig.~\ref{fig:trajectory}C).
-This is especially notable when considering the fact that the numbers of events participants recalled (dots in Fig.~\ref{fig:trajectory}C) varied considerably across people, and that every participant used different words to describe what they had remembered happening in the episode.
-Differences in the numbers of remembered events appear in participants' trajectories as differences in the sampling resolution along the trajectory.
+This is especially notable when considering the fact that the number of HMM-identified recall events (dots in Fig.~\ref{fig:trajectory}C) varied considerably across people, and that every participant used different words to describe what they had remembered happening in the episode.
+Differences in the numbers of recall events appear in participants' trajectories as differences in the sampling resolution along the trajectory.
 We note that this framework also provides a means of disentangling classic ``proportion recalled'' measures (i.e., the proportion of episode events described in participants' recalls) from participants' abilities to recapitulate the episode's essence (i.e., the similarity between the shapes of the original episode trajectory and that defined by each participant's recounting of the episode).
@@
 
-The searchlight analyses described above yielded two distributed networks of brain regions, whose activity timecourses tracked with the temporal structure of the episode (Fig.~\ref{fig:brainz}C) or participants' subsequent recalls (Fig.~\ref{fig:brainz}D).
+The searchlight analyses described above yielded two distributed networks of brain regions whose activity timecourses tracked with the temporal structure of the episode (Fig.~\ref{fig:brainz}C) or participants' subsequent recalls (Fig.~\ref{fig:brainz}D).
 We next sought to gain greater insight into the structures and functional networks our results reflected.

### 2020-09-04 paper/main.tex
a couple more updates to results

@@
 Each action or feature is highlighted in a different color.
-\textbf{D.} Sentences comprising the most precise (P17) and least precise (P6) participants' recalls of episode event 22.
+\textbf{D.} Sentences comprising the most precise (P17) and least precise (P6) participants' recalls of episode event 21.
 Descriptions of specific actions or features reflecting those highlighted in Panel B are highlighted in the corresponding color.
@@
 Each event's text is highlighted in a different color.
-\textbf{F.} The sentences comprising the most distinctive (P9) and least distinctive (P6) participants' recalls of episode event 22.
+\textbf{F.} The sentences comprising the most distinctive (P9) and least distinctive (P6) participants' recalls of episode event 21.
 Sections of recall describing each each episode event in Panel E are highlighted with the corresponding color.}
@@
 In Figure \ref{fig:precision-detail}, we compare recalls for the same episode event from the participants with the highest (P17) and lowest (P6) precision scores.
-From the HMM-identified episode event boundaries, we recovered the set of annotations describing the content of a single episode event (event 22; Fig.~\ref{fig:precision-detail}C), and divided them into different color-coded sections for each action or feature described.
+From the HMM-identified episode event boundaries, we recovered the set of annotations describing the content of a single episode event (event 21; Fig.~\ref{fig:precision-detail}C), and divided them into different color-coded sections for each action or feature described.
 Next, we used an analogous approach to identify the set of sentences comprising the corresponding recall event from each of the two example participants (Fig.~\ref{fig:precision-detail}D).
@@
 Figure \ref{fig:precision-detail} also similarly illustrates the differences between high and low distinctiveness scores.
-We extracted the set of sentences comprising the most distinctive recall event (P9) and least distinctive recall event (P6) corresponding to the example episode event shown in Panel C (event 22).
+We extracted the set of sentences comprising the most distinctive recall event (P9) and least distinctive recall event (P6) corresponding to the example episode event shown in Panel C (event 21).
 We also extracted the annotations for all episode events whose content these participants' single recall events described .
 We assigned each episode event a unique color (Fig.~\ref{fig:precision-detail}E), and colored each recall sentence (Panel F) according to the episode events they best matched.
-Visual inspection of Panel F reveals that the most distinctive recall's content is tightly concentrated around event 22, whereas the least distinctive recall incorporates content from a much wider range of episode events.
+Visual inspection of Panel F reveals that the most distinctive recall's content is tightly concentrated around event 21, whereas the least distinctive recall incorporates content from a much wider range of episode events.
 
@@
 Similarly, the recall-driven searchlight analysis revealed a second network of regions (Fig.~\ref{fig:brainz}D) that may facilitate a person-specific transformation of one's experience into memory.
-The top ten \texttt{Neurosynth} terms~\citep{YarkEtal11} associated with each (unthresholded) map are displayed in each panel.
 In identifying regions whose responses to ongoing experiences reflect how those experiences will be remembered later, this latter analysis extends classic \textit{subsequent memory effect analyses}~\citep[e.g.,][]{PallWagn02} to the domain of naturalistic experiences.
@@
 To accomplish this, we performed an additional, exploratory analysis using \texttt{Neurosynth} \citep{YarkEtal11}.
-Given an arbitrary statistical map as input, \texttt{Neurosynth} performs a massive automated meta-analysis, returning a ranked list of terms reported in papers with similar significance maps.
-We ran \texttt{Neurosynth} on the significance maps for the episode- and recall-driven searchlight analyses.
-These maps, along with the 10 terms with maximally similar meta-analysis images identified by \texttt{Neurosynth} are shown in Figure \ref{fig:brainz}.
+Given an arbitrary statistical map as input, \texttt{Neurosynth} performs a massive automated meta-analysis, returning a ranked list of terms frequently used in neuroimaging papers that report similar statistical maps.
+We ran \texttt{Neurosynth} on the (unthresholded) permutation-corrected maps for the episode- and recall-driven searchlight analyses.
+The top ten terms with maximally similar meta-analysis images identified by \texttt{Neurosynth} are shown in Figure \ref{fig:brainz}.
 

### 2020-09-04 paper/main.tex
edits through end of main

@@
 So called \textit{inter-subject correlation} (ISC) and \textit{inter-subject functional connectivity} (ISFC) analyses effectively treat other people's brain responses to the stimulus as a ``model'' of how its features change over time~\citep[also see][]{SimoChan20}.
-These purely brain-driven approaches are well-suited to identifying which brain structures exhibit similar stimulus-driven responses across individuals.
+These purely brain-driven approaches are well suited to identifying which brain structures exhibit similar stimulus-driven responses across individuals.
 Further, because neural response dynamics are observed data (rather than model approximations), such approaches do not require a detailed understanding of which stimulus properties or features might be driving the observed responses.
@@
 
-The video stimulus was divided into 1,000 fine-grained ``scenes'' and annotated by an independent coder.
-For each of these 1,000 scenes, the following information was recorded: a brief narrative description of what was happening, the location where the scene took place, whether that location was indoors or outdoors, the names of all characters on-screen, the name(s) of the character(s) in focus in the shot, the name(s) of the character(s) currently speaking, the camera angle of the shot, a transcription of any text appearing on-screen, and whether or not there was music present in the background.
-Each scene was also tagged with its onset and offset time, in both seconds and TRs.
+The video stimulus was divided into 1,000 fine-grained ``time segments'' and annotated by an independent coder.
+For each of these 1,000 annotations, the following information was recorded: a brief narrative description of what was happening, the location where the time segment took place, whether that location was indoors or outdoors, the names of all characters on-screen, the name(s) of the character(s) in focus in the shot, the name(s) of the character(s) currently speaking, the camera angle of the shot, a transcription of any text appearing on-screen, and whether or not there was music present in the background.
+Each time segment was also tagged with its onset and offset time, in both seconds and TRs.
 
@@
 \subsubsection*{Topic modeling}
-The input to the topic model we trained to characterize the dynamic content of the episode comprised 998 hand-generated annotations of short (mean: 2.96s) scenes spanning the video clip~(\citealp{ChenEtal17} generated 1000 annotations total; we removed two annotations referring to a break between the first and second scan sessions, during which no fMRI data were collected).
-We concatenated the text for all of the annotated features within each segment, creating a ``bag of words'' describing each scene and performed some minor preprocessing (e.g., stemming possessive nouns and removing punctuation).
-We then re-organized the text descriptions into overlapping sliding windows spanning (up to) 50 scenes each.
-In other words, we estimated the ``context'' for each scene using the text descriptions of the preceding 25 scenes, the present scene, and the following 24 scenes.
-To model the context for scenes near the beginning of the episode (i.e., within 25 scenes of the beginning or end), we created overlapping sliding windows that grew in size from one scene to the full length.
-We also tapered the sliding window lengths at the end of the episode, whereby scenes within fewer than 24 scenes of the end of the episode were assigned sliding windows that extended to the end of the episode.
-This procedure ensured that each scene's content was represented in the text corpus an equal number of times.
+The input to the topic model we trained to characterize the dynamic content of the episode comprised 998 hand-generated annotations of short (mean: 2.96s) time segments spanning the video clip~(\citealp{ChenEtal17} generated 1000 annotations total; we removed two annotations referring to a break between the first and second scan sessions, during which no fMRI data were collected).
+We concatenated the text for all of the annotated features within each segment, creating a ``bag of words'' describing its content and performed some minor preprocessing (e.g., stemming possessive nouns and removing punctuation).
+We then re-organized the text descriptions into overlapping sliding windows spanning (up to) 50 annotations each.
+In other words, we estimated the ``context'' for each annotated segment using the text descriptions of the preceding 25 annotations, the present annotations, and the following 24 annotations.
+To model the context for annotations near the beginning of the episode (i.e., within 25 of the beginning or end), we created overlapping sliding windows that grew in size from one annotation to the full length.
+We also tapered the sliding window lengths at the end of the episode, whereby time segments within fewer than 24 annotations of the end of the episode were assigned sliding windows that extended to the end of the episode.
+This procedure ensured that each annotation's content was represented in the text corpus an equal number of times.
 % ------ NOTE: ------
@@
 We trained our model using these overlapping text samples with \texttt{scikit-learn}~\citep[version 0.19.1; ][]{PedrEtal11}, called from our high-dimensional visualization and text analysis software, \texttt{HyperTools}~\citep{HeusEtal18a}.
-Specifically, we used the \texttt{CountVectorizer} class to transform the text from each window into a vector of word counts (using the union of all words across all scenes as the ``vocabulary,'' excluding English stop words); this yielded a number-of-windows by number-of-words \textit{word count} matrix.
+Specifically, we used the \texttt{CountVectorizer} class to transform the text from each window into a vector of word counts (using the union of all words across all annotations as the ``vocabulary,'' excluding English stop words); this yielded a number-of-windows by number-of-words \textit{word count} matrix.
 We then used the \texttt{LatentDirichletAllocation} class (topics=100, method=`batch') to fit a topic model~\citep{BleiEtal03} to the word count matrix, yielding a number-of-windows (1047) by number-of-topics (100) \textit{topic proportions} matrix.
-The topic proportions matrix describes the gradually evolving mix of topics (latent themes) present in each scene.
+The topic proportions matrix describes the gradually evolving mix of topics (latent themes) present in each annotated time segment of the episode.
 Next, we transformed the topic proportions matrix to match the 1976 fMRI volume acquisition times.
-We assigned each topic vector to the timepoint (in seconds) midway between the beginning of the first scene and the end of the last scene in its corresponding sliding text window.
+We assigned each topic vector to the timepoint (in seconds) midway between the beginning of the first annotation and the end of the last annotation in its corresponding sliding text window.
 By doing so, we warped the linear temporal distance between consecutive topic vectors to align with the inconsistent temporal distance between consecutive annotations (whose durations varied greatly).
@@
 We tokenized the transcript into a list of sentences, and then re-organized the list into overlapping sliding windows spanning (up to) 10 sentences each, analogously to how we parsed the episode annotations.
-In turn, we transformed each window's sentences into a word count vector (using the same vocabulary as for the episode model), and then we used the topic model already trained on the episode scenes to compute the most probable topic proportions for each sliding window.
+In turn, we transformed each window's sentences into a word count vector (using the same vocabulary as for the episode model), then used the topic model already trained on the episode scenes to compute the most probable topic proportions for each sliding window.
 This yielded a number-of-windows (range: 83--312) by number-of-topics (100) topic proportions matrix for each participant.
@@
 
-\paragraph{Probability of first recall (PFR).}  PFR curves~\citep{WelcBurn24, PostPhil65, AtkiShif68} reflect the probability that an item will be recalled first as a function of its serial position during encoding.
+\paragraph{Probability of first recall (PFR).}  PFR curves~\citep{WelcBurn24, PostPhil65, AtkiShif68} reflect the probability that an item will be recalled first, as a function of its serial position during encoding.
 To carry out this analysis, we initialized a number-of-participants (17) by number-of-episode-events (30) matrix of zeros.
-Then for each participant, we found the index of the episode event that was recalled first (i.e., the episode event whose topic vector was most strongly correlated with that of the first recall event) and filled in that index in the matrix with a 1.
+Then, for each participant, we found the index of the episode event that was recalled first (i.e., the episode event whose topic vector was most strongly correlated with that of the first recall event) and filled in that index in the matrix with a 1.
 Finally, we averaged over the rows of the matrix, resulting in a 1 by 30 array representing the proportion of participants that recalled an event first, as a function of the order of the event's appearance in the episode (Fig.~\ref{fig:list-learning}A).
@@
 
-\paragraph{Serial position curve (SPC).} SPCs~\citep{Murd62a} reflect the proportion of participants that remember each item as a function of the items' serial positions during encoding.
+\paragraph{Serial position curve (SPC).} SPCs~\citep{Murd62a} reflect the proportion of participants that remember each item as a function of the item's serial positions during encoding.
 We initialized a number-of-participants (17) by number-of-episode-events (30) matrix of zeros.
@@
 To ensure that all of the trajectories were projected onto the \textit{same} lower dimensional space, we computed the low-dimensional embedding on a ``stacked'' matrix created by vertically concatenating the events-by-topics topic proportions matrices for the episode, across-participants average recall and all 17 individual participants' recalls.
-We then separated the rows of the result (a total-number-of-events by two matrix) back into individual matrices for the episode topic trajectory, across-participant average recall trajectory and the trajectories for each individual participant's recalls (Fig.~\ref{fig:trajectory}).
+We then separated the rows of the result (a total-number-of-events by two matrix) back into individual matrices for the episode topic trajectory, across-participant average recall trajectory, and the trajectories for each individual participant's recalls (Fig.~\ref{fig:trajectory}).
 This general approach for discovering a shared low-dimensional embedding for a collections of high-dimensional observations follows \cite{HeusEtal18a}.
@@
 We computed the distribution of angles formed by those segments and the $x$-axis, and used a Rayleigh test to determine whether the distribution of angles was reliably ``peaked'' (i.e., consistent across all transitions that passed through that local portion of topic space).
-To create Figure~\ref{fig:trajectory}B we drew an arrow originating from each grid vertex, pointing in the direction of the average angle formed by the line segments that passed within 2.4 units.
+To create Figure~\ref{fig:trajectory}B, we drew an arrow originating from each grid vertex, pointing in the direction of the average angle formed by the line segments that passed within 2.4 units.
 We set the arrow lengths to be inversely proportional to the $p$-values of the Rayleigh tests at each vertex.
@@
 \texttt{Neurosynth} parses a massive online database of over 14,000 neuroimaging studies and constructs meta-analysis images for over 13,000 psychology- and neuroscience-related terms, based on NIfTI images accompanying studies where those terms appear at a high frequency.
-Given a novel image (tagged with its value type; e.g., $t$-, $F$- or $p$-statistics), \texttt{Neurosynth} returns a list of terms whose meta-analysis images are most similar.
+Given a novel image (tagged with its value type; e.g., $z$-, $t$-, $F$- or $p$-statistics), \texttt{Neurosynth} returns a list of terms whose meta-analysis images are most similar.
 Our permutation procedure yielded, for each of the two searchlight analyses, a voxelwise map of $z$-values.

### 2020-09-04 paper/main.tex

@@
 
-Occasionally, this gradual drift of our ongoing experience is punctuated by sudden changes, or shifts~\citep[e.g., when we walk through a doorway; ][]{RadvZack17}.
+Occasionally, this gradual drift of our ongoing experience is punctuated by sudden changes, or shifts~\citep[e.g., when we walk through a doorway;][]{RadvZack17}.
 Prior research suggests that these sharp transitions (termed \textit{event boundaries}) help to discretize our experiences (and their mental representations) into \textit{events}~\citep{RadvZack17, BrunEtal18, HeusEtal18b, ClewDava17, EzzyDava11, DuBrDava13}.
@@
 Colored dots within each violin plot represent individual participants' recall precision for the given event.
-\textbf{B.} Recall distinctiveness by episode event.
-analogous to Panel A.
+\textbf{B.} Recall distinctiveness by episode event, analogous to Panel A.
 \textbf{C.} The set of ``Narrative Details'' episode annotations (generated by \citealp{ChenEtal17}) comprising an example episode event (22) identified by the HMM.
@@
 
-Figure \ref{fig:precision-detail} also similarly illustrates the differences between high and low distinctiveness scores.
+Figure \ref{fig:precision-detail} also illustrates the differences between high and low distinctiveness scores.
 We extracted the set of sentences comprising the most distinctive recall event (P9) and least distinctive recall event (P6) corresponding to the example episode event shown in Panel C (event 21).
@@
 In this case, we were specifically interested in identifying voxels whose activation time series reflected the temporal structure of the episode and recall trajectories to a \textit{greater} extent than that of the phase-shifted trajectories.
-% ------ NOTE: ------
-% from the Nature Human Behavior submission requirements: "Specify whether tests were one- or two-tailed, and justify the use of one-tailed tests."
-% - Paxton
 
@@
 This procedure ensured that each annotation's content was represented in the text corpus an equal number of times.
-% ------ NOTE: ------
-% need to refine explanation here a little bit
-% - Paxton
 

### 2020-09-04 paper/supporting_information.tex
minor changes to supp

@@
 \]
-where $\mathrm{corr}(\mu, \nu)$ is the per-participant correlation between the temporal correlation matrices of the episode ($\mu$) and recall ($\nu$) topic proportions matrices, and $\theta$ is the per-participant hand-counted number of recalled scenes.
+where $\mathrm{corr}(\mu, \nu)$ is the per-participant correlation between the episode ($\mu$) and recall ($\nu$) topic proportions matrices, and $\theta$ is the per-participant hand-counted number of recalled scenes.
 We searched over a grid of pre-specified values for each of these parameters; the resulting correlations are displayed in Figure~\ref{fig:paramsearch}.
@@
 \caption{\small \textbf{Optimizing topic model parameters.}  We performed a grid search over episode sliding window length ($\omega \in \{5, 10, 25, 50, 100 \}$), recall sliding window length ($\rho \in \{5, 10, 25, 50, 100 \}$), and number of topics ($K \in \{5, 10, 25, 50, 100 \}$).
-The reported correlations are between per-subject episode-recall correlations and per-participant hand-counted numbers of recalled scenes.}
+The reported correlations are between per-participant episode-recall correlations and per-participant hand-counted numbers of recalled scenes.}
 \label{fig:paramsearch}
@@
 \includegraphics[width=0.65\textwidth]{figs/topic_words}
-\caption{\small \textbf{Topics discovered in \textit{Sherlock}.} We applied a topic model to hand-annotated information about 1000 scenes spanning the 48 minute episode.
+\caption{\small \textbf{Topics discovered in \textit{Sherlock}.} We applied a topic model to hand-annotated information about 1000 scenes spanning the 48-minute episode.
 We identified 32 unique topics with non-zero weights (we used $K=100$ topics to fit the model).
@@
 Specifically, we compared the original episode's topic proportions matrix (created using all hand-annotated features from the 998 manually identified scenes spanning the \textit{Sherlock} episode; see \textit{Methods} for a full list of features) with topic proportions matrices created using all but one type of feature.
-For each impoverished topic proportions matrix, we computed the timepoint-by-timepoint correlation matrix, and correlated the proximal diagonals from the upper right triangle with those from the temporal correlation matrix of the feature-complete matrix (for details on how we isolated proximal temporal correlations, see \textit{Methods}).
+For each impoverished topic proportions matrix, we computed the timepoint-by-timepoint correlation matrix, and correlated the proximal diagonals from the upper triangle with those from the temporal correlation matrix of the feature-complete matrix (for details on how we isolated proximal temporal correlations, see \textit{Methods}).
 Observing a lower correlation between an impoverished matrix (with a particular feature removed) and the feature-complete matrix would suggest that the held-out feature contributed more prominently to the full episode topic proportion matrix's temporal structure.
@@
 Observing a lower correlation between the episode and recall topic proportions matrices (constructed in the absence of a given feature) would indicate that participants utilize changes in that feature's content to discriminate between sections of the episode when organizing their recalls.
-We found that hand-annotated narrative details were the most heavily utilized feature, whereas changes in the text present on-screen, the indoor/outdoor distinction between scenes, the camera angle, the names of the various characters on screen, and the location in which the scene took place tended not to impact participants' recall structures (i.e., removing those features resulted in a \textit{greater} episode-recall correlation than including them; Fig.~\ref{fig:feature-importance}B).
+We found that hand-annotated narrative details were the most heavily utilized feature, whereas changes in the text present on-screen, the indoor/outdoor distinction between shots, the camera angle, the names of the various characters on screen, and the shot's location tended not to impact participants' recall structures (i.e., removing those features resulted in a \textit{greater} episode-recall correlation than including them; Fig.~\ref{fig:feature-importance}B).
 
@@
 \renewcommand{\refname}{Supplemental references}
-% \bibliography{../../CDL-bibliography/memlab}
 \bibliography{CDL-bibliography/memlab}

### 2020-09-04 paper/supporting_information.tex
tightened fig s6 width

@@
 \centering
-\includegraphics[width=\textwidth]{figs/k_optimization}
-\caption{\small \textbf{Episode and recall topic proportions matrix \textit{K}-optimization functions.}  We selected the optimal $K$-value for the episode and each recall topic proportions matrix, using the formula described in \textit{Methods}.
+\includegraphics[width=.92\textwidth]{figs/k_optimization}
+\caption{\small \textbf{Episode and recall topic proportions matrix \textit{K}-optimization functions.}  We selected the optimal $K$-value for the episode and each recall topic proportions matrix using the formula described in \textit{Methods}.
 This computation resulted in a curve for each matrix, describing the Wasserstein distance between the distributions of within-event and across-event topic vector correlations, as a function of $K$.}

### 2020-09-04 paper/supporting_information.tex

@@
 \caption{\small \textbf{Feature importance analysis.} \textbf{A.} Contributions of each feature type to the structure of the episode topic proportions matrix.
-The bar heights reflect the correlation between the episode topic proportions matrix computed using all features with an episode topic proportions matrix computed using all features except the indicated feature.
+The bar heights reflect the correlation between the proximal temporal structures of the episode topic proportions matrix computed using all features, and that of an episode topic proportions matrix computed using all features except the indicated feature.
 (Lower bars reflect features that contribute more substantially to the episode's temporal structure.) \textbf{B.} Which features are preserved during recall?
-The bar heights reflect the (average) across-participant correlations between the episode and recall trajectories.
-Error bars denote bootstrap-estimated standard error of the mean.
+The bar heights reflect the (average) across-participant correlations between the proximal temporal structures of episode and recall trajectories constructed in the absence of the given feature.
+Error bars denote standard error of the mean.
 \textbf{C.} Feature correlation matrix.

### 2020-09-04 paper/main.tex
JRM final pass through main text, updated diff file

@@
 We also identified networks of brain structures sensitive to these trajectory shapes.
-Our work provides insights into how our brains preserve and distort our ongoing experiences when we encode them into episodic memories.
+Our work provides insights into how we preserve and distort our ongoing experiences when we encode them into episodic memories.
 \end{abstract}
@@
 For example, prior work has shown that event boundaries can influence how we learn sequences of items~\citep{HeusEtal18b, DuBrDava13}, navigate~\citep{BrunEtal18}, and remember and understand narratives~\citep{ZwaaRadv98, EzzyDava11}.
-This work also suggests a means of distinguishing the essence of an experience from its low-level details:  The overall structure of events and event transitions reflects how the high-level experience unfolds (i.e., its essence), while subtler event-level properties reflect low-level details.
+This work also suggests a means of distinguishing the essence of an experience from its low-level details:  The overall structure of events and event transitions reflects how the high-level experience unfolds (i.e., its essence), while subtler event-level properties reflect its low-level details.
 Prior research has also implicated a network of brain regions (including the hippocampus and the medial prefrontal cortex) in playing a critical role in transforming experiences into structured and consolidated memories ~\citep{TompDava17}.
@@
 
-Comparing the overall shapes of the topic trajectories for the episode and participants' recalls reveals which aspects of the episode's essence were preserved (or discarded) in the translation into memory.
+Comparing the overall shapes of the topic trajectories for the episode and participants' recalls reveals which aspects of the episode's essence were preserved (or lost) in the translation into memory.
 We also develop two metrics for assessing participants' memories for low-level details: (1) the \textit{precision} with which a participant recounts details about each event, and (2) the \textit{distinctiveness} of their recall for each event, relative to other events.
@@
 Each annotation included: a brief narrative description of what was happening, the location where the action took place, the names of any characters on the screen, and other similar details (for a full list of annotated features, see \textit{Methods}).
-We the union of all unique words (excluding stop words, such as ``and,'' ``or,'' ``but,'' etc.) across all features from all annotations as the vocabulary for the topic model.
+We took the union of all unique words (excluding stop words, such as ``and,'' ``or,'' ``but,'' etc.) across all features from all annotations as the vocabulary for the topic model.
 We then concatenated the sets of words across all features contained in overlapping sliding windows of (up to) 50 annotations, and treated each window as a single document for the purpose of fitting the topic model.
@@
 
-The 32 topics we found were heavily character-focused (i.e., the top-weighted word in each topic was nearly always a character) and could be roughly divided into themes centered around Sherlock Holmes (the titular character), John Watson (Sherlock's close confidant and assistant), supporting characters (e.g., Inspector Lestrade, Sergeant Donovan, or Sherlock's brother Mycroft), or the interactions between various groupings of these characters (see Fig.~\topics).
+The 32 topics we found were heavily character-focused (i.e., the top-weighted word in each topic was nearly always a character) and could be roughly divided into themes centered around Sherlock Holmes (the titular character), John Watson (Sherlock's close confidant and assistant), supporting characters (e.g., Inspector Lestrade, Sergeant Donovan, or Sherlock's brother Mycroft), or the interactions between various groupings of these characters (Fig.~\topics).
 This likely follows from the frequency with which these terms appeared in the episode annotations.
 Several of the identified topics were highly similar, which we hypothesized might allow us to distinguish between subtle narrative differences if the distinctions between those overlapping topics were meaningful.
-The topic vectors for each timepoint were also \textit{sparse}, in that only a small number of topics (typically one or two) tended to be ``active'' in any given timepoint (see Fig.~\ref{fig:model}A).
+The topic vectors for each timepoint were also \textit{sparse}, in that only a small number of topics (typically one or two) tended to be ``active'' in any given timepoint (Fig.~\ref{fig:model}A).
 Further, the dynamics of the topic activations appeared to exhibit \textit{persistence} (i.e., given that a topic was active in one timepoint, it was likely to be active in the following timepoint) along with \textit{occasional rapid changes} (i.e., occasionally topic weights would change abruptly from one timepoint to the next).
@@
 Part of our model fitting procedure required selecting an appropriate number of events into which the topic trajectory should be segmented.
-To accomplish this, we used an optimization procedure that maximized the difference between the topic weights for timepoints within an event versus timepoints across multiple events (see \textit{Methods} for additional details).
+To accomplish this, we used an optimization procedure that maximized the difference between the topic weights for timepoints within an event versus timepoints across multiple events (see \textit{Methods}).
 We then created a stable summary of the content within each episode event by averaging the topic vectors across the timepoints spanned by each event (Fig.~\ref{fig:model}C).
@@
 This yielded, for each participant, a number-of-windows by number-of-topics topic proportions matrix that characterized how the topics identified in the original episode were reflected in the participant's recalls.
-An important feature of our approach is that it allows us to compare participants' recalls to events from the original episode, despite that different participants used widely varying language to describe the events, and that those descriptions often diverged in content and quality from the episode annotations.
+An important feature of our approach is that it allows us to compare participants' recalls to events from the original episode, despite that different participants used widely varying language to describe the events, and that those descriptions often diverged in content, quality, and quantity from the episode annotations.
 This ability to match up conceptually related text that differs in specific vocabulary, detail, and length is an important benefit of projecting the episode and recalls into a shared topic space.
@@
 Semantic clustering measures the extent to which participants cluster their recall responses according to semantic similarity.
-We found that participants tended to recall semantically similar episode events together (mean clustering score: 0.650, SEM: 0.032), and that semantic clustering score was also related to both hand-annotated  (Pearson's $r(15) = 0.65,~p = 0.005$) and model-estimated (Pearson's $r(15) = 0.58,~p = 0.015$) numbers of recalled events.
+We found that participants tended to recall semantically similar episode events together (mean clustering score: 0.650, SEM: 0.032), and that semantic clustering score was also related to both hand-counted  (Pearson's $r(15) = 0.65,~p = 0.005$) and model-estimated (Pearson's $r(15) = 0.58,~p = 0.015$) numbers of recalled events.
 
@@
 The yellow boxes highlight the maximum correlation in each column.
-The example participant's overall precision score was computed as the average across (Fisher $z$-transformed) correlation values in the yellow boxes.
+The example participant's overall precision score was computed as the average across the (Fisher $z$-transformed) correlation values in the yellow boxes.
 Their distinctiveness score was computed as the average (over recall events) of the $z$-scored (within column) event precisions.
@@
 We define a recall event's precision as the maximum correlation between the topic proportions of that recall event and any episode event (Fig.~\ref{fig:precision-distinctiveness}).
-In other words, given that a recalled event best matches a particular episode event, more precisely recalled events overlap more strongly with the conceptual content of the original episode event.
+In other words, given that a recall event best matches a particular episode event, more precisely recalled events overlap more strongly with the conceptual content of the original episode event.
 When a given event is assigned a blend of several topics, as is often the case (Fig.~\ref{fig:model}), a high precision score requires recapitulating the relative topic proportions during recall.
@@
 We extracted the set of sentences comprising the most distinctive recall event (P9) and least distinctive recall event (P6) corresponding to the example episode event shown in Panel C (event 21).
-We also extracted the annotations for all episode events whose content these participants' single recall events described .
-We assigned each episode event a unique color (Fig.~\ref{fig:precision-detail}E), and colored each recall sentence (Panel F) according to the episode events they best matched.
+We also extracted the annotations for all episode events whose content these participants' single recall events described.
+We assigned each episode event a unique color (Fig.~\ref{fig:precision-detail}E), and colored each recalled sentence (Panel F) according to the episode events they best matched.
 Visual inspection of Panel F reveals that the most distinctive recall's content is tightly concentrated around event 21, whereas the least distinctive recall incorporates content from a much wider range of episode events.
@@
 To assess the consistency of these recall trajectories across participants, we asked: given that a participant's recall trajectory had entered a particular location in the reduced topic space, could the position of their \textit{next} recalled event be predicted reliably?
-For each location in the reduced topic space, we computed the set of line segments connecting successively recalled events (across all participants) that intersected that location (see \textit{Methods} for additional details).
+For each location in the reduced topic space, we computed the set of line segments connecting successively recalled events (across all participants) that intersected that location (see \textit{Methods}).
 We then computed (for each location) the distribution of angles formed by the lines defined by those line segments and a fixed reference line (the $x$-axis).
@@
 The results displayed in Figures \ref{fig:list-learning}C and \ref{fig:precision-detail}A suggest that certain events were remembered better than others.
-Given this, we next asked asked whether the events were generally remembered precisely or imprecisely tended to reflect particular content.
+Given this, we next asked asked whether the events that were generally remembered precisely or imprecisely tended to reflect particular content.
 Because our analysis framework projects the dynamic episode content and participants' recalls into a shared space, and because the dimensions of that space represent topics (which are, in turn, sets of weights over known words in the vocabulary), we are able to recover the weighted combination of words that make up any point (i.e., topic vector) in this space.
@@
 To visualize the result, we created a ``wordle'' image~\citep{MuelEtal18} where words weighted more heavily by more precisely-remembered topics appear in a larger font (Fig.~\ref{fig:topics}B, green box).
-Across the full episode, content that weighted heavily on topics and words central to the major foci of the episode (e.g., the names of the two main characters, ``Sherlock'' and ``John,'' and the address of a major recurring location, ``221B Baker Street'') were best remembered.
+Across the full episode, content that weighted heavily on topics and words central to the major foci of the episode (e.g., the names of the two main characters, ``Sherlock'' and ``John,'' and the address of a major recurring location, ``221B Baker Street'') was best remembered.
 An analogous analysis revealed which themes were less-precisely remembered.
@@
 Here, for each of the three most and least precisely remembered episode events, we have constructed two wordles: one from the original episode event's topic vector (left) and a second from the average recall topic vector for that event (right).
-The three most precisely remembered events (circled in green) correspond to scenes integral to the central plot-line: a mysterious figure spying on John in a phone booth; John meeting Sherlock at Baker St.\~to discuss the murders; and Sherlock laying a trap to catch the killer.
+The three most precisely remembered events (circled in green) correspond to scenes integral to the central plot-line: a mysterious figure spying on John in a phone booth; John meeting Sherlock at Baker St.~to discuss the murders; and Sherlock laying a trap to catch the killer.
 Meanwhile, the least precisely remembered events (circled in red) reflect scenes that comprise minor plot points: a video of singing cartoon characters that participants viewed in an introductory clip prior to the main episode; John asking Molly about Sherlock's habit of over-analyzing people; and Sherlock noticing evidence of Anderson's and Donovan's affair.
 
-The results thus far inform us about which aspects of the dynamic content in the episode participants watched were preserved or altered in participants' memories.
+The results this far inform us about which aspects of the dynamic content in the episode participants watched were preserved or altered in participants' memories.
 We next carried out a series of analyses aimed at understanding which brain structures might facilitate these preservations and transformations between the participants' shared experience of watching the episode and their subsequent memories of the episode.
@@
 We used a searchlight procedure to identify clusters of voxels whose proximal temporal correlation matrices matched that of the topic proportions matrix for each participant's recall transcript (Figs.~\ref{fig:brainz}B; see \textit{Methods} for additional details).
-To ensure our searchlight procedure identified regions \textit{specifically} sensitive to the temporal structure of the episode or recalls (i.e., rather than those with a temporal autocorrelation length similar to that of the episode and recalls), we performed a phase shift-based permutation correction (see \textit{Methods} for additional details).
+To ensure our searchlight procedure identified regions \textit{specifically} sensitive to the temporal structure of the episode or recalls (i.e., rather than those with a temporal autocorrelation length similar to that of the episode and recalls), we performed a phase shift-based permutation correction (see \textit{Methods}).
 As shown in Figure~\ref{fig:brainz}C, the episode-driven searchlight analysis revealed a distributed network of regions that may play a role in processing information relevant to the narrative structure of the episode.
-Similarly, the recall-driven searchlight analysis revealed a second network of regions (Fig.~\ref{fig:brainz}D) that may facilitate a person-specific transformation of one's experience into memory.
+The recall-driven searchlight analysis revealed a second network of regions (Fig.~\ref{fig:brainz}D) that may facilitate a person-specific transformation of one's experience into memory.
 In identifying regions whose responses to ongoing experiences reflect how those experiences will be remembered later, this latter analysis extends classic \textit{subsequent memory effect analyses}~\citep[e.g.,][]{PallWagn02} to the domain of naturalistic experiences.
@@
 We identified one network of regions whose responses tracked with temporal correlations in the conceptual content of the episode (as quantified by topic models applied to a set of annotations about the episode).
-This network included orbitofrontal cortex, ventromedial prefrontal cortex, striatum, among others.
+This network included orbitofrontal cortex, ventromedial prefrontal cortex, and striatum, among others.
 As reviewed by \cite{RangRitc12}, several of these regions are members of the \textit{anterior temporal system}, which has been implicated in assessing and processing the familiarity of ongoing experiences, emotions, social cognition, and reward.
@@
 Our approach to identifying neural responses to naturalistic stimuli (including experiences) entails building an explicit model of the stimulus dynamics and searching for brain regions whose responses are consistent with the model~\citep[also see][]{HuthEtal12, HuthEtal16}.
-In prior work, a series of studies from Uri Hasson's group~\citep{LernEtal11, SimoEtal16, ChenEtal17, BaldEtal17, ZadbEtal17} have developed a clever alternative approach: rather than building an explicit stimulus model, these studies instead search for brain responses (while experiencing the stimulus) that are reliably similar across individuals.
+In prior work, a series of studies from Uri Hasson's group~\citep{LernEtal11, SimoEtal16, ChenEtal17, BaldEtal17, ZadbEtal17} have presented a clever alternative approach: rather than building an explicit stimulus model, these studies instead search for brain responses to the stimulus that are reliably similar across individuals.
 So called \textit{inter-subject correlation} (ISC) and \textit{inter-subject functional connectivity} (ISFC) analyses effectively treat other people's brain responses to the stimulus as a ``model'' of how its features change over time~\citep[also see][]{SimoChan20}.
@@
 All statistical tests performed in the neural data analyses were two-sided, except for the permutation-based thresholding, which was one-sided.
-In this case, we were specifically interested in identifying voxels whose activation time series reflected the temporal structure of the episode and recall trajectories to a \textit{greater} extent than that of the phase-shifted trajectories.
+In this case, we were specifically interested in identifying voxels whose activation time series reflected the temporal structure of the episode and recall topic proportions matrices to a \textit{greater} extent than that of the phase-shifted matrices.
 
@@
 Following \cite{BaldEtal17}, we imposed an additional set of constraints on the discovered state transitions that ensured that each state was encountered exactly once (i.e., never repeated).
-We used the BrainIAK toolbox~\citep{Brainiak} to implement this segmentation.
+We used the \texttt{BrainIAK} toolbox~\citep{Brainiak} to implement this segmentation.
 
@@
 
-\paragraph{Serial position curve (SPC).} SPCs~\citep{Murd62a} reflect the proportion of participants that remember each item as a function of the item's serial positions during encoding.
+\paragraph{Serial position curve (SPC).} SPCs~\citep{Murd62a} reflect the proportion of participants that remember each item as a function of the item's serial position during encoding.
 We initialized a number-of-participants (17) by number-of-episode-events (30) matrix of zeros.
@@
 
-% To quantify the similarity between the episode topic trajectory and individual recall topic trajectories, we considered several novel metrics.
-First, we tested whether each participant's recall trajectory matched the episode trajectory in a general sense.
-For each participant, we filtered the episode trajectory to only include the events that the participant remembered.
-We then computed the root mean squared difference (RMSD) between the remaining episode events and the (closest-matching) recalled events.
-For example, if the topic vectors for a participant's recall event topic vectors matched the corresponding episode event topic vectors exactly (and in order), the expected RMSD for those events would be 0.
-However, if the participant's recall events did not perfectly match the episode events, or if they were out of order, then the RMSD would be greater than 0.
-To assess the significance of the match between the episode and recall trajectories, we carried out a permutation procedure whereby, for each of 10000 repetitions, we circularly shifted the recall trajectories (in time) by a random amount and then re-computed the RMSD each time.
-This yielded a distribution of ``null" RMSD values for each participant.
-The observed RMSD values reached significance (i.e., $p < 0.05$, reflecting that more than 95\% of the null RMSD values were greater than the observed RMSD value) for nine of the participants (3, 4, 8--13, and 17).
-(For the remaining participants this test yielded $0.05 \leq p < 0.25$.)  The observed RMSD values were also reliably correlated with hand-annotated memory performance across participants (Pearson's $r(15) = -0.57, p = 0.016$).
-In other words, a closer match between the episode and recall topic trajectories was related to better overall recall performance.
-% ------ NOTE: ------
-% Andy was thinking about including this in the revision early on.  It wasn't in the preprint version, and with how much else we have in here, I don't think it's worth including anymore.
-% - Paxton
-% I agree that we can take it out. -AH
-
 \subsubsection*{Averaging correlations}
-In all instances where we performed statistical tests involving precision or distinctiveness scores (Fig.~\ref{fig:precision-detail}, we used the Fisher $z$-transformation~\citep{Fish25} to stabilize the variance across the distribution of correlation values prior to performing the test.
+In all instances where we performed statistical tests involving precision or distinctiveness scores (Fig.~\ref{fig:precision-detail}), we used the Fisher $z$-transformation~\citep{Fish25} to stabilize the variance across the distribution of correlation values prior to performing the test.
 Similarly, when averaging precision or distinctiveness scores, we $z$-transformed the scores prior to computing the mean, and inverse $z$-transformed the result.
@@
 The first criteria helps bolster the validity of visual intuitions about relationships between sections of episode content, based on their locations in the embedding space.
-The second criteria was motivated by the observed low off-diagonal values in the episode trajectory's temporal correlation matrix (suggesting that the same topic-space coordinates should not be revisited; see Figure~2A in the main text).
+The second criteria was motivated by the observed low off-diagonal values in the episode trajectory's temporal correlation matrix (suggesting that the same topic-space coordinates should not be revisited; see Fig.~2A).
 For further details on how we created this low-dimensional embedding space, see \textit{Supporting Information}.
@@
 In Figure~\ref{fig:brainz}, we present two analyses aimed at identifying brain regions whose responses (as participants viewed the episode) exhibited a particular temporal structure.
-We developed a searchlight analysis wherein we constructed a $5 \times 5 \times 5$ cube of voxels (following \citealp{ChenEtal17}) centered on each voxel in the brain, and for each of these cubes, computed the temporal correlation matrix of the voxel responses during episode viewing.
+We developed a searchlight analysis wherein we constructed a $5 \times 5 \times 5$ cube of voxels~\citep[following][]{ChenEtal17} centered on each voxel in the brain, and for each of these cubes, computed the temporal correlation matrix of the voxel responses during episode viewing.
 Specifically, for each of the 1976 volumes collected during episode viewing, we correlated the activity patterns in the given cube with the activity patterns (in the same cube) collected during every other timepoint.
 This yielded a $1976 \times 1976$ correlation matrix for each cube.
-Note: participant 5's scan ended 75s early, and in \citealp{ChenEtal17}'s publicly released dataset, their scan data was zero-padded to match the length of the other participants'.
+Note: participant 5's scan ended 75s early, and in~\cite{ChenEtal17}'s publicly released dataset, their scan data was zero-padded to match the length of the other participants'.
 For our searchlight analyses, we removed this padded data (i.e., the last 50 TRs), resulting in a $1925 \times 1925$ correlation matrix for each cube in participant 5's brain.
@@
 Next, we constructed a series of ``template'' matrices.
-The first template reflected the timecourse of the episode's topic trajectory, and the others reflected the timecourse of each participant's recall trajectory.
-To construct the episode template, we computed the correlations between the topic proportions estimated for every pair of TRs (prior to segmenting the trajectory into discrete events; i.e., the correlation matrix shown in Figs.~\ref{fig:model}B and \ref{fig:brainz}A).
-We constructed similar temporal correlation matrices for each participant's recall topic trajectory (Figs.~\ref{fig:model}D, \corrmats).
-However, to correct for length differences and potential non-linear transformations between viewing time and recall time, we first used dynamic time warping~\citep{BernClif94} to temporally align participants' recall topic trajectories with the episode topic trajectory.
+The first template reflected the timecourse of the episode's topic proportions matrix, and the others reflected the timecourse of each participant's recall topic proportions matrix.
+To construct the episode template, we computed the correlations between the topic proportions estimated for every pair of TRs (prior to segmenting the topic proportions matrices into discrete events; i.e., the correlation matrix shown in Figs.~\ref{fig:model}B and \ref{fig:brainz}A).
+We constructed similar temporal correlation matrices for each participant's recall topic proportions matrix (Figs.~\ref{fig:model}D, \corrmats).
+However, to correct for length differences and potential non-linear transformations between viewing time and recall time, we first used dynamic time warping~\citep{BernClif94} to temporally align participants' recall topic proportions matrices with the episode topic proportions matrix.
 An example correlation matrix before and after warping is shown in Fig.~\ref{fig:brainz}B.
@@
 We further sought to ensure that our analysis identified regions where the activations’ temporal structure specifically reflected that of the episode, rather than regions whose activity was simply autocorrelated at a timescale similar to the episode template’s diagonal.
-To achieve this, we used a phase shift-based permutation procedure, whereby we circularly shifted the episode’s topic trajectory by a random number of timepoints, computed the resulting ``null'' episode template, and re-ran the searchlight analysis, in full.
+To achieve this, we used a phase shift-based permutation procedure, whereby we circularly shifted the episode’s topic proportions matrix by a random number of timepoints (rows), computed the resulting ``null'' episode template, and re-ran the searchlight analysis, in full.
 (For each of the 100 permutations, the same random shift was used for all participants).

### 2020-09-05 paper/supporting_information.tex
updated Fig S3 caption

--- 2020-09-04 paper/supporting_information.tex
@@
 \caption{\small \textbf{Feature importance analysis.} \textbf{A.} Contributions of each feature type to the structure of the episode topic proportions matrix.
-The bar heights reflect the correlation between the episode topic proportions matrix computed using all features with an episode topic proportions matrix computed using all features except the indicated feature.
-(Lower bars reflect features that contribute more substantially to the episode's temporal structure.) \textbf{B.} Which features are preserved during recall?
-The bar heights reflect the (average) across-participant correlations between the episode and recall trajectories.
-Error bars denote bootstrap-estimated standard error of the mean.
+The bar heights reflect the correlation between the proximal temporal structure (see \textit{Methods}) of the episode topic proportions matrix computed using all features, and that of an episode topic proportions matrix computed using all features except the indicated feature.
+Lower bars reflect features that contribute more substantially to the episode's temporal structure.
+\textbf{B.} Which features are preserved during recall?
+The bar heights reflect the (average) across-participant correlations between the proximal temporal structure of episode and recall topic proportions matrices constructed in the absence of the given feature.
+Error bars denote standard error of the mean.
 \textbf{C.} Feature correlation matrix.
-Each entry displays the correlation between episode topic trajectories created using only the indicated (row/column) features.}
+Each entry displays the correlation between episode topic portions matrices created using only the indicated (row/column) features.}
 \label{fig:feature-importance}

### 2020-10-09 paper/main.tex
removed duplicate page numbering in main text and supplement

@@
   \maketitle
+  \thispagestyle{empty}
   \end{titlepage}
@@
 The second clear pattern present in every individual participant's recall correlation matrix was that, unlike in the episode correlation matrix, there were substantial off-diagonal correlations.
-Whereas each event in the original episode was (largely) separable from the others (Fig.~\ref{fig:model}B), in transforming those separable events into memory, participants appeared to be integrating across multiple events, blending elements of previously recalled and not-yet-recalled content into each newly recalled event~\citep[Figs.~\ref{fig:model}E, \corrmats; also see][]{MannEtal11, HowaEtal12, Mann19}.
+One potential explanation for this finding is that the topic models, trained only on episode annotations, do not capture topic proportions in participants' ``held-out'' recalls as accurately.
+A second possibility is that, whereas each event in the original episode was (largely) separable from the others (Fig.~\ref{fig:model}B), in transforming those separable events into memory, participants appeared to be integrating across multiple events, blending elements of previously recalled and not-yet-recalled content into each newly recalled event~\citep[Figs.~\ref{fig:model}E, \corrmats; also see][]{MannEtal11, HowaEtal12, Mann19}.
 
@@
 \textbf{B.} We used dynamic time warping \citep{BernClif94} to align each participant's recall timeseries to the TR timeseries of the episode.
-We then applied the same diagonal mask used in Panel A to isolate the proximal temporal correlations and searched for brain regions whose activation timeseries for an individual consistently exhibited a similar proximal correlational structure to each individual's recall.
+We then computed the temporal correlation matrix of each participant's warped recalls.
+Next, we applied the same diagonal mask used in Panel A to isolate the proximal temporal correlations and searched for brain regions whose activation timeseries for an individual consistently exhibited a similar proximal correlational structure to each individual's recalls.
 \textbf{C.} We identified a network of regions sensitive to the narrative structure of participants' ongoing experience.
@@
 Taken together, our results support the notion that these two (partially overlapping) networks work in coordination to make sense of our ongoing experiences, distort them in a way that links them with our prior knowledge and experiences, and encodes those distorted representations into memory for our later use.
+Our work also provides a potential framework for modeling and elucidating \textit{memory schemas}-- i.e., cognitive abstractions that may be applied to multiple related experiences~\citep[e.g.,][]{GilbMarl17, BaldEtal18}.
+For example, the event-level geometric scaffolding of an experience (e.g., Fig.~\ref{fig:trajectory}A) might reflect its underlying schema, and experiences that share similar schemas might have similar shapes.
+This could also help explain how brain structures including the ventromedial prefrontal cortex~\citep[Fig.~\ref{fig:brainz}; also see][]{GilbMarl17} might acquire or apply schema knowledge across different experiences (i.e., by learning patterns in the schema's shape).
 
@@
 Our approach to identifying neural responses to naturalistic stimuli (including experiences) entails building an explicit model of the stimulus dynamics and searching for brain regions whose responses are consistent with the model~\citep[also see][]{HuthEtal12, HuthEtal16}.
+Building an explicit model of these dynamics also enables us to match up different people's recountings of a common shared experience, despite individual differences~\cite[also see][]{GagnEtal20}.
 In prior work, a series of studies from Uri Hasson's group~\citep{LernEtal11, SimoEtal16, ChenEtal17, BaldEtal17, ZadbEtal17} have presented a clever alternative approach: rather than building an explicit stimulus model, these studies instead search for brain responses to the stimulus that are reliably similar across individuals.
@@
 Topic models are essentially an extension of those early models, in that they attempt to explicitly model the underlying causes of word co-occurrences by automatically identifying the set of themes or topics reflected across the documents in the corpus.
-More recent work on these types of semantic models, including word2vec~\citep{MikoEtal13}, the Universal Sentence Encoder~\citep{CerEtal18}, GPT-2~\citep{RadfEtal19}, and GTP-3~\citep{BrowEtal20} use deep neural networks to attempt to identify the deeper conceptual representations underlying each word.
+More recent work on these types of semantic models, including word2vec~\citep{MikoEtal13a}, the Universal Sentence Encoder~\citep{CerEtal18}, GPT-2~\citep{RadfEtal19}, and GTP-3~\citep{BrowEtal20} use deep neural networks to attempt to identify the deeper conceptual representations underlying each word.
 Despite the growing popularity of these sophisticated deep learning-based embedding models, we chose to prioritize interpretability of the embedding dimensions (e.g., Fig.~\ref{fig:topics}) over raw performance (e.g., with respect to some predefined benchmark).

### 2020-10-09 paper/main.tex
added responses to rev2 reviewers

@@
 
-Our work casts remembering as reproducing (behaviorally and neurally) the topic trajectory, or ``shape,'' of an experience.
+Our work casts remembering as reproducing (behaviorally and neurally) the topic trajectory, or ``shape,'' of an experience, thereby drawing implicit analogies between mentally navigating through word embedding spaces and physically navigating through spatial environments~\citep[e.g.,][]{BellEtal18, BellEtal20, ConsEtal16}.
 When we characterized memory for a television episode using this framework, we found that every participant's recounting of the episode recapitulated the low spatial frequency details of the shape of its trajectory through topic space (Fig.~\ref{fig:trajectory}).

### 2020-10-13 paper/main.tex
working on reformatting paper to fit NHB guidelines

@@
 \usepackage{geometry}
-\usepackage[sort]{natbib}
+\usepackage[sort&compress, numbers, super]{natbib}
 \usepackage{pxfonts}
@@
 \usepackage{placeins}
+\usepackage[nofiglist, fighead]{endfloat}
+\renewcommand{\includegraphics}[2][]{}
 
@@
 
-\title{Geometric models reveal behavioral and neural signatures of transforming naturalistic experiences into episodic memories}
+\title{Geometric models reveal behavioral and neural signatures of transforming experiences into memories}
 
@@
 Fitzpatrick\textsuperscript{1, \textdagger}, and Jeremy R.
-Manning\textsuperscript{1, *}\\\textsuperscript{1}Department of Psychological and Brain Sciences\\Dartmouth College, Hanover, NH 03755, USA\\\textsuperscript{2}Akili Interactive Labs\\Boston, MA 02110\\\textsuperscript{\textdagger}Denotes equal contribution\\\textsuperscript{*}Corresponding author: Jeremy.R.Manning@Dartmouth.edu}
-
-\bibliographystyle{apa}
+Manning\textsuperscript{1, *}\\\textsuperscript{1}Department of Psychological and Brain Sciences\\Dartmouth College, Hanover, NH 03755, USA\\\textsuperscript{2}Akili Interactive Labs\\Boston, MA 02110, USA\\\textsuperscript{\textdagger}Denotes equal contribution\\\textsuperscript{*}Corresponding author: Jeremy.R.Manning@Dartmouth.edu}
 
@@
 We developed a geometric framework for mathematically characterizing the subjective conceptual content of dynamic naturalistic experiences.
-We model experiences and memories as \textit{trajectories} through word embedding spaces whose coordinates reflect the universe of thoughts under consideration.
-Memory encoding can then be modeled as geometrically preserving or distorting the \textit{shape} of the original experience.
+We model experiences and memories as ``trajectories'' through word embedding spaces whose coordinates reflect the universe of thoughts under consideration.
+Memory encoding can then be modeled as geometrically preserving or distorting the ``shape'' of the original experience.
 We applied our approach to data collected as participants watched and verbally recounted a television episode while undergoing functional neuroimaging.
@@
 \section*{Introduction}
-What does it mean to \textit{remember} something?
+What does it mean to remember something?
 In traditional episodic memory experiments \citep[e.g., list-learning or trial-based experiments;][]{Murd62a, Kaha96}, remembering is often cast as a discrete, binary operation: each studied item may be separated from the rest of one's experience and labeled as having been either recalled or forgotten.
@@
 Second, whether or not the rememberer has precisely reproduced a specific set of words in describing a given experience is nearly orthogonal to how well they were actually able to remember it.
-In classic (e.g., list-learning) memory studies, by contrast, the number or proportion of \textit{exact} recalls is often considered to be a primary metric for assessing the quality of participants' memories.
+In classic (e.g., list-learning) memory studies, by contrast, the number or proportion of exact recalls is often considered to be a primary metric for assessing the quality of participants' memories.
 Third, one might remember the essence (or a general summary) of an experience but forget (or neglect to recount) particular low-level details.
@@
 
-How might we formally characterize the \textit{essence} of an experience, and whether it has been recovered by the rememberer?
+How might we formally characterize the ``essence'' of an experience, and whether it has been recovered by the rememberer?
 And how might we distinguish an experience's overarching essence from its low-level details?
@@
 Therefore, the timecourse describing how an event unfolds is fundamental to its overall meaning.
-Further, this hierarchy formed by our subjective experiences at different timescales defines a \textit{context} for each new moment~\citep[e.g.,][]{HowaKaha02a, HowaEtal14}, and plays an important role in how we interpret that moment and remember it later~\citep[for review see][]{MannEtal15, Mann20}.
+Further, this hierarchy formed by our subjective experiences at different timescales defines a context for each new moment~\citep[e.g.,][]{HowaKaha02a, HowaEtal14}, and plays an important role in how we interpret that moment and remember it later~\citep[for review see][]{MannEtal15, Mann20}.
 Our memory systems can leverage these associations to form predictions that help guide our behaviors~\citep{RangRitc12}.
@@
 Occasionally, this gradual drift of our ongoing experience is punctuated by sudden changes, or shifts~\citep[e.g., when we walk through a doorway;][]{RadvZack17}.
-Prior research suggests that these sharp transitions (termed \textit{event boundaries}) help to discretize our experiences (and their mental representations) into \textit{events}~\citep{RadvZack17, BrunEtal18, HeusEtal18b, ClewDava17, EzzyDava11, DuBrDava13}.
+Prior research suggests that these sharp transitions (termed ``event boundaries'') help to discretize our experiences (and their mental representations) into ``events''~\citep{RadvZack17, BrunEtal18, HeusEtal18b, ClewDava17, EzzyDava11, DuBrDava13}.
 The interplay between the stable (within-event) and transient (across-event) temporal dynamics of an experience also provides a potential framework for transforming experiences into memories that distills those experiences down to their essences.
@@
 We then use hidden Markov models~\citep{Rabi89, BaldEtal17} to discretize this evolving semantic content into events.
-In this way, we cast both naturalistic experiences and memories of those experiences as geometric \textit{trajectories} through word embedding space that describe how they evolve over time.
+In this way, we cast both naturalistic experiences and memories of those experiences as geometric ``trajectories'' through word embedding space that describe how they evolve over time.
 Under this framework, successful remembering entails verbally traversing the content trajectory of the episode, thereby reproducing the shape (essence) of the original experience.
@@
 Comparing the overall shapes of the topic trajectories for the episode and participants' recalls reveals which aspects of the episode's essence were preserved (or lost) in the translation into memory.
-We also develop two metrics for assessing participants' memories for low-level details: (1) the \textit{precision} with which a participant recounts details about each event, and (2) the \textit{distinctiveness} of their recall for each event, relative to other events.
+We also develop two metrics for assessing participants' memories for low-level details: (1) the ``precision'' with which a participant recounts details about each event, and (2) the ``distinctiveness'' of their recall for each event, relative to other events.
 We examine how these metrics relate to overall memory performance as judged by third-party human annotators.
@@
 Topic models take as inputs a vocabulary of words to consider and a collection of text documents, and return two output matrices.
-The first of these is a \textit{topics matrix} whose rows are \textit{topics} (or latent themes) and whose columns correspond to words in the vocabulary.
+The first of these is a ``topics matrix'' whose rows are ``topics'' (or latent themes) and whose columns correspond to words in the vocabulary.
 The entries in the topics matrix reflect how each word in the vocabulary is weighted by each discovered topic.
-For example, a detective-themed topic might weight heavily on words like ``crime,'' and ``search.''  The second output is a \textit{topic proportions matrix} with one row per document and one column per topic.
+For example, a detective-themed topic might weight heavily on words like ``crime,'' and ``search.''  The second output is a ``topic proportions matrix'' with one row per document and one column per topic.
 The topic proportions matrix describes the mixture of discovered topics reflected in each document.
@@
 Next, we fit a topic model with (up to) $K = 100$ topics to this collection of documents.
-We found that 32 unique topics (with non-zero weights) were sufficient to describe the time-varying content of the episode (see \textit{Methods}; Figs.~\ref{fig:schematic}, \topics).
+We found that 32 unique topics (with non-zero weights) were sufficient to describe the time-varying content of the episode (see \textit{Methods}; Fig.~\ref{fig:schematic}, Supp.
+Fig.~\topics).
 We note that our approach is similar in some respects to Dynamic Topic Models~\citep{BleiLaff06} in that we sought to characterize how the thematic content of the episode evolved over time.
-However, whereas Dynamic Topic Models are designed to characterize how the properties of \textit{collections} of documents change over time, our sliding window approach allows us to examine the topic dynamics within a single document (or video).
-Specifically, our approach yielded (via the topic proportions matrix) a single \textit{topic vector} for each sliding window of annotations transformed by the topic model.
+However, whereas Dynamic Topic Models are designed to characterize how the properties of collections of documents change over time, our sliding window approach allows us to examine the topic dynamics within a single document (or video).
+Specifically, our approach yielded (via the topic proportions matrix) a single ``topic vector'' for each sliding window of annotations transformed by the topic model.
 We then stretched (interpolated) the resulting windows-by-topics matrix to match the time series of the 1,976 fMRI volumes collected as participants viewed the episode.
@@
 Three topic dimensions are shown (the highest-weighted topics for each of the three example scenes, respectively), along with the 10 highest-weighted words for each topic.
-Figure~\topics~provides a full list of the top 10 words from each of the discovered topics.}
+Supplementary Figure~\topics~provides a full list of the top 10 words from each of the discovered topics.}
 \label{fig:schematic}
@@
 
-The 32 topics we found were heavily character-focused (i.e., the top-weighted word in each topic was nearly always a character) and could be roughly divided into themes centered around Sherlock Holmes (the titular character), John Watson (Sherlock's close confidant and assistant), supporting characters (e.g., Inspector Lestrade, Sergeant Donovan, or Sherlock's brother Mycroft), or the interactions between various groupings of these characters (Fig.~\topics).
+The 32 topics we found were heavily character-focused (i.e., the top-weighted word in each topic was nearly always a character) and could be roughly divided into themes centered around Sherlock Holmes (the titular character), John Watson (Sherlock's close confidant and assistant), supporting characters (e.g., Inspector Lestrade, Sergeant Donovan, or Sherlock's brother Mycroft), or the interactions between various groupings of these characters (Supp.
+Fig.~\topics).
 This likely follows from the frequency with which these terms appeared in the episode annotations.
 Several of the identified topics were highly similar, which we hypothesized might allow us to distinguish between subtle narrative differences if the distinctions between those overlapping topics were meaningful.
-The topic vectors for each timepoint were also \textit{sparse}, in that only a small number of topics (typically one or two) tended to be ``active'' in any given timepoint (Fig.~\ref{fig:model}A).
-Further, the dynamics of the topic activations appeared to exhibit \textit{persistence} (i.e., given that a topic was active in one timepoint, it was likely to be active in the following timepoint) along with \textit{occasional rapid changes} (i.e., occasionally topic weights would change abruptly from one timepoint to the next).
+The topic vectors for each timepoint were also sparse, in that only a small number of topics (typically one or two) tended to be ``active'' in any given timepoint (Fig.~\ref{fig:model}A).
+Further, the dynamics of the topic activations appeared to exhibit persistence (i.e., given that a topic was active in one timepoint, it was likely to be active in the following timepoint) along with occasional rapid changes (i.e., occasionally topic weights would change abruptly from one timepoint to the next).
 These two properties of the topic dynamics may be seen in the block diagonal structure of the timepoint-by-timepoint correlation matrix (Fig.~\ref{fig:model}B) and reflect the gradual drift and sudden shifts fundamental to the temporal dynamics of many real-world experiences, as well as television episodes.
-Given this observation, we adapted an approach devised by \cite{BaldEtal17}, and used a hidden Markov model (HMM) to identify the \textit{event boundaries} where the topic activations changed rapidly (i.e., the boundaries of the blocks in the temporal correlation matrix; event boundaries identified by the HMM are outlined in yellow in Fig.~\ref{fig:model}B).
+Given this observation, we adapted an approach devised by \cite{BaldEtal17}, and used a hidden Markov model (HMM) to identify the ``event boundaries'' where the topic activations changed rapidly (i.e., the boundaries of the blocks in the temporal correlation matrix; event boundaries identified by the HMM are outlined in yellow in Fig.~\ref{fig:model}B).
 Part of our model fitting procedure required selecting an appropriate number of events into which the topic trajectory should be segmented.
@@
 Event boundaries detected by the HMM are denoted in yellow (22 events detected).
-For similar plots for all participants, see Figure~\corrmats.
+For similar plots for all participants, see Supplementary Figure~\corrmats.
 \textbf{F.} Average topic vectors for each of the 22 recall events from the example participant.
 \textbf{G.} Correlations between the topic vectors for every pair of episode events (Panel C) and recall events (from the example participant; Panel F).
-For similar plots for all participants, see Figure~\matchmats.
+For similar plots for all participants, see Supplementary Figure~\matchmats.
 \textbf{H.} Average correlations between each pair of episode events and recall events (across all 17 participants).
@@
 We used the same HMM-based optimization procedure that we had applied to the episode's topic proportions matrix (see \textit{Methods}) to estimate an analogous set of event boundaries in the participant's recounting of the episode (outlined in yellow).
-We carried out this analysis on all 17 participants' recall topic proportions matrices (Fig.~\corrmats).
+We carried out this analysis on all 17 participants' recall topic proportions matrices (Supp.
+Fig.~\corrmats).
 
 Two clear patterns emerged from this set of analyses.
-First, although every individual participant's recalls could be segmented into discrete events (i.e., every individual participant's recall correlation matrix exhibited clear block diagonal structure; Fig.~\corrmats), each participant appeared to have a unique \textit{recall resolution}, reflected in the sizes of those blocks.
+First, although every individual participant's recalls could be segmented into discrete events (i.e., every individual participant's recall correlation matrix exhibited clear block diagonal structure; Supp.
+Fig.~\corrmats), each participant appeared to have a unique ``recall resolution,'' reflected in the sizes of those blocks.
 While some participants' recall topic proportions segmented into just a few events (e.g., Participants P4, P5, and P7), others' segmented into many shorter-duration events (e.g., Participants P12, P13, and P17).
@@
 One potential explanation for this finding is that the topic models, trained only on episode annotations, do not capture topic proportions in participants' ``held-out'' recalls as accurately.
-A second possibility is that, whereas each event in the original episode was (largely) separable from the others (Fig.~\ref{fig:model}B), in transforming those separable events into memory, participants appeared to be integrating across multiple events, blending elements of previously recalled and not-yet-recalled content into each newly recalled event~\citep[Figs.~\ref{fig:model}E, \corrmats; also see][]{MannEtal11, HowaEtal12, Mann19}.
+A second possibility is that, whereas each event in the original episode was (largely) separable from the others (Fig.~\ref{fig:model}B), in transforming those separable events into memory, participants appeared to be integrating across multiple events, blending elements of previously recalled and not-yet-recalled content into each newly recalled event~\citep[Fig.~\ref{fig:model}E, Supp.
+Fig.~\corrmats; also see][]{MannEtal11, HowaEtal12, Mann19}.
 
@@
 Next, we asked whether some correspondence might be made between the specific content of the events the participants experienced while viewing the episode, and the events they later recalled.
-We labeled each recall event as matching the episode event with the most similar (i.e., most highly correlated) topic vector (Figs.~\ref{fig:model}G, \matchmats).
+We labeled each recall event as matching the episode event with the most similar (i.e., most highly correlated) topic vector (Fig.~\ref{fig:model}G, Supp.
+Fig.~\matchmats).
 This yielded a sequence of ``presented'' events from the original episode, and a (potentially differently ordered) sequence of ``recalled'' events for each participant.
@@
   \includegraphics[width=1\textwidth]{figs/precision_distinctiveness}
-  \caption{\small \textbf{Novel content-based metrics of naturalistic memory: precision and distinctiveness.} \textbf{A.} The episode-recall correlation matrix for a representative participant (P17).
+  \caption{\small \textbf{Novel content-based metrics of naturalistic memory: precision and distinctiveness.} \textbf{A.} The episode-recall correlation matrix for a representative participant (P17), chosen for their large number of recall events (for analogous figures for other participants, see Supp.
+Fig.~\corrmats).
 The yellow boxes highlight the maximum correlation in each column.
@@
 Yet when researchers study memory in highly simplified paradigms, those nuances are not typically observable.
-We next developed two novel, continuous metrics, termed \textit{precision} and \textit{distinctiveness}, aimed at characterizing distortions in the conceptual content of individual recall events, and the conceptual overlap between how people described different events.
+We next developed two novel, continuous metrics, termed ``precision'' and ``distinctiveness,'' aimed at characterizing distortions in the conceptual content of individual recall events, and the conceptual overlap between how people described different events.
 
-\textit{Precision} is intended to capture the ``completeness'' of recall, or how fully the presented content was recapitulated in a participant's recounting.
+Precision is intended to capture the ``completeness'' of recall, or how fully the presented content was recapitulated in a participant's recounting.
 We define a recall event's precision as the maximum correlation between the topic proportions of that recall event and any episode event (Fig.~\ref{fig:precision-distinctiveness}).
@@
 
-\textit{Distinctiveness} is intended to capture the ``specificity'' of recall.
+Distinctiveness is intended to capture the ``specificity'' of recall.
 In other words, distinctiveness quantifies the extent to which a given recall event reflects the most similar episode event over and above other episode events.
@@
 We found that, across participants, higher precision scores were positively correlated with the numbers of both hand-annotated scenes ($r(15) = 0.60, p = 0.010$) and model-estimated events ($r(15) = 0.90, p < 0.001$) that participants recalled.
-Participants' average distinctiveness scores were also correlated with both the hand-annotated ($r(15) = 0.45, p = 0.068$) and model-estimated ($r(15) = 0.71, p = 0.001$) numbers of recalled events.
+Participants' average distinctiveness scores were also marginally correlated with both the hand-annotated ($r(15) = 0.45, p = 0.068$) and model-estimated ($r(15) = 0.71, p = 0.001$) numbers of recalled events.
 
@@
 First, the topic trajectory of the episode (which reflects its dynamic content; Fig.~\ref{fig:trajectory}A) is captured nearly perfectly by the averaged topic trajectories of participants' recalls (Fig.~\ref{fig:trajectory}B).
-To assess the consistency of these recall trajectories across participants, we asked: given that a participant's recall trajectory had entered a particular location in the reduced topic space, could the position of their \textit{next} recalled event be predicted reliably?
+To assess the consistency of these recall trajectories across participants, we asked: given that a participant's recall trajectory had entered a particular location in the reduced topic space, could the position of their next recalled event be predicted reliably?
 For each location in the reduced topic space, we computed the set of line segments connecting successively recalled events (across all participants) that intersected that location (see \textit{Methods}).
@@
 An analogous analysis revealed which themes were less-precisely remembered.
-Here in computing the weighted average over events' topic vectors, we weighted each event in \textit{inverse} proportion to its average precision (Fig.~\ref{fig:topics}B, red box).
+Here in computing the weighted average over events' topic vectors, we weighted each event in inverse proportion to its average precision (Fig.~\ref{fig:topics}B, red box).
 The least precisely remembered episode content reflected information that was extraneous to the episode's essence, such as the proper names of relatively minor characters (e.g., ``Mike,'' ``Molly,'' and ``Lestrade'') and locations (e.g., ``St.
@@
 We used a searchlight procedure to identify clusters of voxels whose activity patterns displayed a proximal temporal correlation structure (as participants watched the episode) matching that of the original episode's topic proportions (Fig.~\ref{fig:brainz}A; see \textit{Methods} for additional details).
-In a second analysis, we sought to identify brain structures whose responses (during episode viewing) reflected how each participant would later structure their \textit{recounting} of the episode.
+In a second analysis, we sought to identify brain structures whose responses (during episode viewing) reflected how each participant would later structure their recounting of the episode.
 We used a searchlight procedure to identify clusters of voxels whose proximal temporal correlation matrices matched that of the topic proportions matrix for each participant's recall transcript (Figs.~\ref{fig:brainz}B; see \textit{Methods} for additional details).
-To ensure our searchlight procedure identified regions \textit{specifically} sensitive to the temporal structure of the episode or recalls (i.e., rather than those with a temporal autocorrelation length similar to that of the episode and recalls), we performed a phase shift-based permutation correction (see \textit{Methods}).
+To ensure our searchlight procedure identified regions specifically sensitive to the temporal structure of the episode or recalls (i.e., rather than those with a temporal autocorrelation length similar to that of the episode and recalls), we performed a phase shift-based permutation correction (see \textit{Methods}).
 As shown in Figure~\ref{fig:brainz}C, the episode-driven searchlight analysis revealed a distributed network of regions that may play a role in processing information relevant to the narrative structure of the episode.
 The recall-driven searchlight analysis revealed a second network of regions (Fig.~\ref{fig:brainz}D) that may facilitate a person-specific transformation of one's experience into memory.
-In identifying regions whose responses to ongoing experiences reflect how those experiences will be remembered later, this latter analysis extends classic \textit{subsequent memory effect analyses}~\citep[e.g.,][]{PallWagn02} to the domain of naturalistic experiences.
+In identifying regions whose responses to ongoing experiences reflect how those experiences will be remembered later, this latter analysis extends classic ``subsequent memory effect analyses''~\citep[e.g.,][]{PallWagn02} to the domain of naturalistic experiences.
 
@@
 When we characterized memory for a television episode using this framework, we found that every participant's recounting of the episode recapitulated the low spatial frequency details of the shape of its trajectory through topic space (Fig.~\ref{fig:trajectory}).
-We termed this narrative scaffolding the episode's \textit{essence}.
+We termed this narrative scaffolding the episode's essence.
 Where participants' behaviors varied most was in their tendencies to recount specific low-level details from each episode event.
@@
 This network included orbitofrontal cortex, ventromedial prefrontal cortex, and striatum, among others.
-As reviewed by \cite{RangRitc12}, several of these regions are members of the \textit{anterior temporal system}, which has been implicated in assessing and processing the familiarity of ongoing experiences, emotions, social cognition, and reward.
+As reviewed by \cite{RangRitc12}, several of these regions are members of the ``anterior temporal system,'' which has been implicated in assessing and processing the familiarity of ongoing experiences, emotions, social cognition, and reward.
 A second network we identified tracked with temporal correlations in the idiosyncratic conceptual content of participants' subsequent recountings of the episode.
 This network included occipital cortex, extrastriate cortex, fusiform gyrus, and the precuneus.
-Several of these regions are members of the \textit{posterior medial system}~\citep{RangRitc12}, which has been implicated in matching incoming cues about the current situation to internally maintained \textit{situation models} that specify the parameters and expectations inherent to the current situation~\citep[also see][]{ZackEtal07, ZwaaRadv98}.
+Several of these regions are members of the ``posterior medial system''~\citep{RangRitc12}, which has been implicated in matching incoming cues about the current situation to internally maintained ``situation models'' that specify the parameters and expectations inherent to the current situation~\citep[also see][]{ZackEtal07, ZwaaRadv98}.
 Taken together, our results support the notion that these two (partially overlapping) networks work in coordination to make sense of our ongoing experiences, distort them in a way that links them with our prior knowledge and experiences, and encodes those distorted representations into memory for our later use.
-Our work also provides a potential framework for modeling and elucidating \textit{memory schemas}-- i.e., cognitive abstractions that may be applied to multiple related experiences~\citep[e.g.,][]{GilbMarl17, BaldEtal18}.
+Our work also provides a potential framework for modeling and elucidating ``memory schemas''-- i.e., cognitive abstractions that may be applied to multiple related experiences~\citep[e.g.,][]{GilbMarl17, BaldEtal18}.
 For example, the event-level geometric scaffolding of an experience (e.g., Fig.~\ref{fig:trajectory}A) might reflect its underlying schema, and experiences that share similar schemas might have similar shapes.
@@
 In prior work, a series of studies from Uri Hasson's group~\citep{LernEtal11, SimoEtal16, ChenEtal17, BaldEtal17, ZadbEtal17} have presented a clever alternative approach: rather than building an explicit stimulus model, these studies instead search for brain responses to the stimulus that are reliably similar across individuals.
-So called \textit{inter-subject correlation} (ISC) and \textit{inter-subject functional connectivity} (ISFC) analyses effectively treat other people's brain responses to the stimulus as a ``model'' of how its features change over time~\citep[also see][]{SimoChan20}.
+So called ``inter-subject correlation'' (ISC) and ``inter-subject functional connectivity'' (ISFC) analyses effectively treat other people's brain responses to the stimulus as a ``model'' of how its features change over time~\citep[also see][]{SimoChan20}.
 These purely brain-driven approaches are well suited to identifying which brain structures exhibit similar stimulus-driven responses across individuals.
@@
 By applying HMMs to our explicit models of stimulus and memory dynamics, we gain a more direct understanding of those state dynamics.
-For example, we found that although the events comprising each participant's recalls recapitulated the episode's essence, participants differed in the \textit{resolution} of their recounting of low-level details.
+For example, we found that although the events comprising each participant's recalls recapitulated the episode's essence, participants differed in the resolution of their recounting of low-level details.
 In turn, these individual behavioral differences were reflected in differences in neural activity dynamics as participants watched the television episode.
@@
 
-Our work has broad implications for how we characterize and assess memory in real-world settings, such as the classroom or physician's office.
+Speculatively, our work may have broad implications for how we characterize and assess memory in real-world settings, such as the classroom or physician's office.
 For example, the most commonly used classroom evaluation tools involve simply computing the proportion of correctly answered exam questions.
-Our work indicates that this approach is only loosely related to what educators might really want to measure: how well did the students understand the key ideas presented in the course?
+Our work suggests that this approach is only loosely related to what educators might really want to measure: how well did the students understand the key ideas presented in the course?
 Under this typical framework of assessment, the same exam score of 50\% could be ascribed to two very different students: one who attended to the full course but struggled to learn more than a broad overview of the material, and one who attended to only half of the course but understood the attended material perfectly.
 Instead, one could apply our computational framework to build explicit dynamic content models of the course material and exam questions.
-This approach would provide a more nuanced and specific view into which aspects of the material students had learned well (or poorly).
+This approach might provide a more nuanced and specific view into which aspects of the material students had learned well (or poorly).
 In clinical settings, memory measures that incorporate such explicit content models might also provide more direct evaluations of patients' memories, and of doctor-patient interactions.
@@
 \subsection*{Paradigm and data collection}
-Data were collected by \cite{ChenEtal17}.
+Data were collected by \citeauthor{ChenEtal17}~\citep{ChenEtal17}.
 In brief, participants ($n=22$) viewed the first 48 minutes of ``A Study in Pink,'' the first episode of the BBC television show \textit{Sherlock}, while fMRI volumes were collected (TR = 1500~ms).
@@
 
-\subsection*{Data and code availability}
-The fMRI data we analyzed are available online \href{http://dataspace.princeton.edu/jspui/handle/88435/dsp01nz8062179}{\underline{here}}.
-The behavioral data and all of our analysis code may be downloaded \href{https://github.com/ContextLab/sherlock-topic-model-paper}{\underline{here}}.
-
 \subsection*{Statistics}
@@
 All statistical tests performed in the neural data analyses were two-sided, except for the permutation-based thresholding, which was one-sided.
-In this case, we were specifically interested in identifying voxels whose activation time series reflected the temporal structure of the episode and recall topic proportions matrices to a \textit{greater} extent than that of the phase-shifted matrices.
+In this case, we were specifically interested in identifying voxels whose activation time series reflected the temporal structure of the episode and recall topic proportions matrices to a greater extent than that of the phase-shifted matrices.
 
@@
 We trained our model using these overlapping text samples with \texttt{scikit-learn}~\citep[version 0.19.1; ][]{PedrEtal11}, called from our high-dimensional visualization and text analysis software, \texttt{HyperTools}~\citep{HeusEtal18a}.
-Specifically, we used the \texttt{CountVectorizer} class to transform the text from each window into a vector of word counts (using the union of all words across all annotations as the ``vocabulary,'' excluding English stop words); this yielded a number-of-windows by number-of-words \textit{word count} matrix.
-We then used the \texttt{LatentDirichletAllocation} class (topics=100, method=`batch') to fit a topic model~\citep{BleiEtal03} to the word count matrix, yielding a number-of-windows (1047) by number-of-topics (100) \textit{topic proportions} matrix.
+Specifically, we used the \texttt{CountVectorizer} class to transform the text from each window into a vector of word counts (using the union of all words across all annotations as the ``vocabulary,'' excluding English stop words); this yielded a number-of-windows by number-of-words ``word count'' matrix.
+We then used the \texttt{LatentDirichletAllocation} class (topics=100, method=`batch') to fit a topic model~\citep{BleiEtal03} to the word count matrix, yielding a number-of-windows (1047) by number-of-topics (100) ``topic proportions'' matrix.
 The topic proportions matrix describes the gradually evolving mix of topics (latent themes) present in each annotated time segment of the episode.
@@
 These reflected the dynamic content of each participant's recalls.
-Note: for details on how we selected the episode and recall window lengths and number of topics, see \textit{Supporting Information} and Figure~\topicopt.
+Note: for details on how we selected the episode and recall window lengths and number of topics, see \textit{Supplementary Information} and Supplementary Figure~\topicopt.
 
@@
 Prior studies on narrative structure and processing have shown that we both perceive and internally represent the world around us at multiple, hierarchical timescales \citep[e.g.,][]{HassEtal08, LernEtal11, HassEtal15, ChenEtal17, BaldEtal17, BaldEtal18}.
-However, for the purposes of our framework, we sought to identify the single timeseries of event-representations that is emphasized \textit{most heavily} in the temporal structure of the episode and of each participant's recall.
+However, for the purposes of our framework, we sought to identify the single timeseries of event-representations that is emphasized most heavily in the temporal structure of the episode and of each participant's recall.
 We quantified this as the set of $K$ states that maximized the similarity between topic vectors for timepoints comprising each state, while minimizing the similarity between topic vectors for timepoints across different states.
@@
 where $a$ was the distribution of within-state topic vector correlations, and $b$ was the distribution of across-state topic vector correlations .
-We computed the first Wasserstein distance ($W_{1}$; also known as \textit{Earth mover's distance}; \citealp{Dobr70, RamdEtal17}) between these distributions for a large range of possible $K$-values (range [2, 50]), and selected the $K$ that yielded the maximum value.
-Figure~\ref{fig:model}B displays the event boundaries returned for the episode, and Figure~\corrmats~displays the event boundaries returned for each participant's recalls.
-See Figure \kopt~for the optimization functions for the episode and recalls.
+We computed the first Wasserstein distance~\citep[$W_{1}$; also known as ``Earth mover's distance'';][]{Dobr70, RamdEtal17} between these distributions for a large range of possible $K$-values (range [2, 50]), and selected the $K$ that yielded the maximum value.
+Figure~\ref{fig:model}B displays the event boundaries returned for the episode, and Supplementary Figure~\corrmats~displays the event boundaries returned for each participant's recalls.
+See Supplementary Figure \kopt~for the optimization functions for the episode and recalls.
 After obtaining these event boundaries, we created stable estimates of the content represented in each event by averaging the topic vectors across timepoints between each pair of event boundaries.
@@
 
-Perhaps the simplest and most widely used measure of memory performance is \textit{accuracy}---i.e., the proportion of studied (experienced) items (in this case, episode events) that the participant later remembered.
+Perhaps the simplest and most widely used measure of memory performance is ``accuracy''---i.e., the proportion of studied (experienced) items (in this case, episode events) that the participant later remembered.
 \cite{ChenEtal17} used this method to rate each participant's memory quality by computing the proportion of (50, manually identified) scenes mentioned in their recall.
@@
 Thus, the similarity between the semantic content for two events can be computed by correlating their respective topic vectors.
-For each recall event transition, we sorted all not-yet-recalled events according to how correlated the topic vector \textit{of the closest-matching episode event} was to the topic vector of the closest-matching episode event to the just-recalled event.
+For each recall event transition, we sorted all not-yet-recalled events according to how correlated the topic vector of the closest-matching episode event was to the topic vector of the closest-matching episode event to the just-recalled event.
 We then computed the percentile rank of the observed next recall.
@@
 We used the UMAP algorithm~\citep{McInEtal18} to project the 100-dimensional topic space onto a two-dimensional space for visualization (Figs.~\ref{fig:trajectory}, \ref{fig:topics}).
-To ensure that all of the trajectories were projected onto the \textit{same} lower dimensional space, we computed the low-dimensional embedding on a ``stacked'' matrix created by vertically concatenating the events-by-topics topic proportions matrices for the episode, across-participants average recall and all 17 individual participants' recalls.
+To ensure that all of the trajectories were projected onto the same lower dimensional space, we computed the low-dimensional embedding on a ``stacked'' matrix created by vertically concatenating the events-by-topics topic proportions matrices for the episode, across-participants average recall and all 17 individual participants' recalls.
 We then separated the rows of the result (a total-number-of-events by two matrix) back into individual matrices for the episode topic trajectory, across-participant average recall trajectory, and the trajectories for each individual participant's recalls (Fig.~\ref{fig:trajectory}).
@@
 The second criteria was motivated by the observed low off-diagonal values in the episode trajectory's temporal correlation matrix (suggesting that the same topic-space coordinates should not be revisited; see Fig.~2A).
-For further details on how we created this low-dimensional embedding space, see \textit{Supporting Information}.
+For further details on how we created this low-dimensional embedding space, see \textit{Supplementary Information}.
 
@@
 To construct the episode template, we computed the correlations between the topic proportions estimated for every pair of TRs (prior to segmenting the topic proportions matrices into discrete events; i.e., the correlation matrix shown in Figs.~\ref{fig:model}B and \ref{fig:brainz}A).
-We constructed similar temporal correlation matrices for each participant's recall topic proportions matrix (Figs.~\ref{fig:model}D, \corrmats).
+We constructed similar temporal correlation matrices for each participant's recall topic proportions matrix (Fig.~\ref{fig:model}D, Supp.
+Fig.~\corrmats).
 However, to correct for length differences and potential non-linear transformations between viewing time and recall time, we first used dynamic time warping~\citep{BernClif94} to temporally align participants' recall topic proportions matrices with the episode topic proportions matrix.
@@
 Our permutation procedure yielded, for each of the two searchlight analyses, a voxelwise map of $z$-values.
-These maps describe the extent to which each voxel \textit{specifically} reflected the temporal structure of the episode or individuals' recalls (i.e., relative to the null distributions of phase-shifted values).
+These maps describe the extent to which each voxel specifically reflected the temporal structure of the episode or individuals' recalls (i.e., relative to the null distributions of phase-shifted values).
 We inputted the two statistical maps described above to \texttt{Neurosynth} to create a list of the 10 most representative terms for each map.
 
-% \bibliography{../../CDL-bibliography/memlab}
-\bibliography{CDL-bibliography/memlab}
+\section*{Data availability}
+The fMRI data we analyzed are available online \href{http://dataspace.princeton.edu/jspui/handle/88435/dsp01nz8062179}{\underline{here}}.
+The behavioral data is available  \href{https://github.com/ContextLab/sherlock-topic-model-paper}{\underline{here}}.
 
-\section*{Supporting information}
-Supporting information is available in the online version of the paper.
+\section*{Code availability}
+All of our analysis code may be downloaded \href{https://github.com/ContextLab/sherlock-topic-model-paper}{\underline{here}}.
+
+%\bibliographystyle{naturemag}
+%\bibliography{CDL-bibliography/memlab}
+\begin{thebibliography}{10}
+\expandafter\ifx\csname url\endcsname\relax
+  \def\url#1{\texttt{#1}}\fi
+\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
+\providecommand{\bibinfo}[2]{#2}
+\providecommand{\eprint}[2][]{\url{#2}}
+
+\bibitem{Murd62a}
+\bibinfo{author}{Murdock, B.~B.}
+\newblock \bibinfo{title}{The serial position effect of free recall}.
+\newblock \emph{\bibinfo{journal}{Journal of Experimental Psychology}}
+  \textbf{\bibinfo{volume}{64}}, \bibinfo{pages}{482--488}
+  (\bibinfo{year}{1962}).
+
+\bibitem{Kaha96}
+\bibinfo{author}{Kahana, M.~J.}
+\newblock \bibinfo{title}{Associative retrieval processes in free recall}.
+\newblock \emph{\bibinfo{journal}{Memory \& Cognition}}
+  \textbf{\bibinfo{volume}{24}}, \bibinfo{pages}{103--109}
+  (\bibinfo{year}{1996}).
+
+\bibitem{Yone02}
+\bibinfo{author}{Yonelinas, A.~P.}
+\newblock \bibinfo{title}{The nature of recollection and familiarity: A review
+  of 30 years of research}.
+\newblock \emph{\bibinfo{journal}{Journal of Memory and Language}}
+  \textbf{\bibinfo{volume}{46}}, \bibinfo{pages}{441--517}
+  (\bibinfo{year}{2002}).
+
+\bibitem{Kaha12}
+\bibinfo{author}{Kahana, M.~J.}
+\newblock \emph{\bibinfo{title}{Foundations of Human Memory}}
+  (\bibinfo{publisher}{Oxford University Press}, \bibinfo{address}{New York,
+  NY}, \bibinfo{year}{2012}).
+
+\bibitem{KoriGold94}
+\bibinfo{author}{Koriat, A.} \& \bibinfo{author}{Goldsmith, M.}
+\newblock \bibinfo{title}{Memory in naturalistic and laboratory contexts:
+  distinguishing accuracy-oriented and quantity-oriented approaches to memory
+  assessment}.
+\newblock \emph{\bibinfo{journal}{Journal of Experimental Psychology: General}}
+  \textbf{\bibinfo{volume}{123}}, \bibinfo{pages}{297--315}
+  (\bibinfo{year}{1994}).
+
+\bibitem{HukEtal18}
+\bibinfo{author}{Huk, A.}, \bibinfo{author}{Bonnen, K.} \& \bibinfo{author}{He,
+  B.~J.}
+\newblock \bibinfo{title}{Beyond trial-based paradigms: continuous behavior,
+  ongoing neural activity, and naturalistic stimuli}.
+\newblock \emph{\bibinfo{journal}{Journal of Neuroscience}}
+  \textbf{\bibinfo{volume}{10.1523/JNEUROSCI.1920-17.2018}}
+  (\bibinfo{year}{2018}).
+
+\bibitem{LernEtal11}
+\bibinfo{author}{Lerner, Y.}, \bibinfo{author}{Honey, C.~J.},
+  \bibinfo{author}{Silbert, L.~J.} \& \bibinfo{author}{Hasson, U.}
+\newblock \bibinfo{title}{Topographic mapping of a hierarchy of temporal
+  receptive windows using a narrated story}.
+\newblock \emph{\bibinfo{journal}{Journal of Neuroscience}}
+  \textbf{\bibinfo{volume}{31}}, \bibinfo{pages}{2906--2915}
+  (\bibinfo{year}{2011}).
+
+\bibitem{Mann19}
+\bibinfo{author}{Manning, J.~R.}
+\newblock \bibinfo{title}{Episodic memory: mental time travel or a quantum
+  'memory wave' function?}
+\newblock \emph{\bibinfo{journal}{PsyArXiv}}
+  \textbf{\bibinfo{volume}{doi:10.31234/osf.io/6zjwb}} (\bibinfo{year}{2019}).
+
+\bibitem{Mann20}
+\bibinfo{author}{Manning, J.~R.}
+\newblock \bibinfo{title}{Context reinstatement}.
+\newblock In \bibinfo{editor}{Kahana, M.~J.} \& \bibinfo{editor}{Wagner, A.~D.}
+  (eds.) \emph{\bibinfo{booktitle}{Handbook of Human Memory}}
+  (\bibinfo{publisher}{Oxford University Press}, \bibinfo{year}{2020}).
+
+\bibitem{HowaKaha02a}
+\bibinfo{author}{Howard, M.~W.} \& \bibinfo{author}{Kahana, M.~J.}
+\newblock \bibinfo{title}{A distributed representation of temporal context}.
+\newblock \emph{\bibinfo{journal}{Journal of Mathematical Psychology}}
+  \textbf{\bibinfo{volume}{46}}, \bibinfo{pages}{269--299}
+  (\bibinfo{year}{2002}).
+
+\bibitem{HowaEtal14}
+\bibinfo{author}{Howard, M.~W.} \emph{et~al.}
+\newblock \bibinfo{title}{A unified mathematical framework for coding time,
+  space, and sequences in the medial temporal lobe}.
+\newblock \emph{\bibinfo{journal}{Journal of Neuroscience}}
+  \textbf{\bibinfo{volume}{34}}, \bibinfo{pages}{4692--4707}
+  (\bibinfo{year}{2014}).
+
+\bibitem{MannEtal15}
+\bibinfo{author}{Manning, J.~R.}, \bibinfo{author}{Norman, K.~A.} \&
+  \bibinfo{author}{Kahana, M.~J.}
+\newblock \bibinfo{title}{The role of context in episodic memory}.
+\newblock In \bibinfo{editor}{Gazzaniga, M.} (ed.)
+  \emph{\bibinfo{booktitle}{The Cognitive Neurosciences, Fifth edition}},
+  \bibinfo{pages}{557--566} (\bibinfo{publisher}{{MIT} Press},
+  \bibinfo{year}{2015}).
+
+\bibitem{RangRitc12}
+\bibinfo{author}{Ranganath, C.} \& \bibinfo{author}{Ritchey, M.}
+\newblock \bibinfo{title}{Two cortical systems for memory-guided behavior}.
+\newblock \emph{\bibinfo{journal}{Nature Reviews Neuroscience}}
+  \textbf{\bibinfo{volume}{13}}, \bibinfo{pages}{713 -- 726}
+  (\bibinfo{year}{2012}).
+
+\bibitem{ZackEtal07}
+\bibinfo{author}{Zacks, J.~M.}, \bibinfo{author}{Speer, N.~K.},
+  \bibinfo{author}{Swallow, K.~M.}, \bibinfo{author}{Braver, T.~S.} \&
+  \bibinfo{author}{Reynolds, J.~R.}
+\newblock \bibinfo{title}{Event perception: a mind-brain perspective}.
+\newblock \emph{\bibinfo{journal}{Psychological Bulletin}}
+  \textbf{\bibinfo{volume}{133}}, \bibinfo{pages}{273--293}
+  (\bibinfo{year}{2007}).
+
+\bibitem{ZwaaRadv98}
+\bibinfo{author}{Zwaan, R.~A.} \& \bibinfo{author}{Radvansky, G.~A.}
+\newblock \bibinfo{title}{Situation models in language comprehension and
+  memory}.
+\newblock \emph{\bibinfo{journal}{Psychological Bulletin}}
+  \textbf{\bibinfo{volume}{123}}, \bibinfo{pages}{162 -- 185}
+  (\bibinfo{year}{1998}).
+
+\bibitem{RadvZack17}
+\bibinfo{author}{Radvansky, G.~A.} \& \bibinfo{author}{Zacks, J.~M.}
+\newblock \bibinfo{title}{Event boundaries in memory and cognition}.
+\newblock \emph{\bibinfo{journal}{Curr Opin Behav Sci}}
+  \textbf{\bibinfo{volume}{17}}, \bibinfo{pages}{133--140}
+  (\bibinfo{year}{2017}).
+
+\bibitem{BrunEtal18}
+\bibinfo{author}{Brunec, I.~K.}, \bibinfo{author}{Moscovitch, M.~M.} \&
+  \bibinfo{author}{Barense, M.~D.}
+\newblock \bibinfo{title}{Boundaries shape cognitive representations of spaces
+  and events}.
+\newblock \emph{\bibinfo{journal}{{Trends in Cognitive Sciences}}}
+  \textbf{\bibinfo{volume}{22}}, \bibinfo{pages}{637--650}
+  (\bibinfo{year}{2018}).
+
+\bibitem{HeusEtal18b}
+\bibinfo{author}{Heusser, A.~C.}, \bibinfo{author}{Ezzyat, Y.},
+  \bibinfo{author}{Shiff, I.} \& \bibinfo{author}{Davachi, L.}
+\newblock \bibinfo{title}{Perceptual boundaries cause mnemonic trade-offs
+  between local boundary processing and across-trial associative binding}.
+\newblock \emph{\bibinfo{journal}{Journal of Experimental Psychology Learning,
+  Memory, and Cognition}} \textbf{\bibinfo{volume}{44}},
+  \bibinfo{pages}{1075--1090} (\bibinfo{year}{2018}).
+
+\bibitem{ClewDava17}
+\bibinfo{author}{Clewett, D.} \& \bibinfo{author}{Davachi, L.}
+\newblock \bibinfo{title}{The ebb and flow of experience determines the
+  temporal structure of memory}.
+\newblock \emph{\bibinfo{journal}{Curr Opin Behav Sci}}
+  \textbf{\bibinfo{volume}{17}}, \bibinfo{pages}{186--193}
+  (\bibinfo{year}{2017}).
+
+\bibitem{EzzyDava11}
+\bibinfo{author}{Ezzyat, Y.} \& \bibinfo{author}{Davachi, L.}
+\newblock \bibinfo{title}{What constitutes an episode in episodic memory?}
+\newblock \emph{\bibinfo{journal}{Psychological Science}}
+  \textbf{\bibinfo{volume}{22}}, \bibinfo{pages}{243--252}
+  (\bibinfo{year}{2011}).
+
+\bibitem{DuBrDava13}
+\bibinfo{author}{DuBrow, S.} \& \bibinfo{author}{Davachi, L.}
+\newblock \bibinfo{title}{The influence of contextual boundaries on memory for
+  the sequential order of events}.
+\newblock \emph{\bibinfo{journal}{Journal of Experimental Psychology: General}}
+  \textbf{\bibinfo{volume}{142}}, \bibinfo{pages}{1277--1286}
+  (\bibinfo{year}{2013}).
+
+\bibitem{TompDava17}
+\bibinfo{author}{Tompary, A.} \& \bibinfo{author}{Davachi, L.}
+\newblock \bibinfo{title}{Consolidation promotes the emergence of
+  representational overlap in the hippocampus and medial prefrontal cortex}.
+\newblock \emph{\bibinfo{journal}{Neuron}} \textbf{\bibinfo{volume}{96}},
+  \bibinfo{pages}{228--241} (\bibinfo{year}{2017}).
+
+\bibitem{ChenEtal17}
+\bibinfo{author}{Chen, J.} \emph{et~al.}
+\newblock \bibinfo{title}{Shared memories reveal shared structure in neural
+  activity across individuals}.
+\newblock \emph{\bibinfo{journal}{Nature Neuroscience}}
+  \textbf{\bibinfo{volume}{20}}, \bibinfo{pages}{115} (\bibinfo{year}{2017}).
+
+\bibitem{BleiEtal03}
+\bibinfo{author}{Blei, D.~M.}, \bibinfo{author}{Ng, A.~Y.} \&
+  \bibinfo{author}{Jordan, M.~I.}
+\newblock \bibinfo{title}{Latent dirichlet allocation}.
+\newblock \emph{\bibinfo{journal}{Journal of Machine Learning Research}}
+  \textbf{\bibinfo{volume}{3}}, \bibinfo{pages}{993 -- 1022}
+  (\bibinfo{year}{2003}).
+
+\bibitem{Rabi89}
+\bibinfo{author}{Rabiner, L.}
+\newblock \bibinfo{title}{A tutorial on {Hidden Markov Models} and selected
+  applications in speech recognition}.
+\newblock \emph{\bibinfo{journal}{Proceedings of the IEEE}}
+  \textbf{\bibinfo{volume}{77}}, \bibinfo{pages}{257--286}
+  (\bibinfo{year}{1989}).
+
+\bibitem{BaldEtal17}
+\bibinfo{author}{Baldassano, C.} \emph{et~al.}
+\newblock \bibinfo{title}{Discovering event structure in continuous narrative
+  perception and memory}.
+\newblock \emph{\bibinfo{journal}{Neuron}} \textbf{\bibinfo{volume}{95}},
+  \bibinfo{pages}{709--721} (\bibinfo{year}{2017}).
+
+\bibitem{BleiLaff06}
+\bibinfo{author}{Blei, D.~M.} \& \bibinfo{author}{Lafferty, J.~D.}
+\newblock \bibinfo{title}{Dynamic topic models}.
+\newblock In \emph{\bibinfo{booktitle}{Proceedings of the 23rd International
+  Conference on Machine Learning}}, ICML '06, \bibinfo{pages}{113--120}
+  (\bibinfo{publisher}{ACM}, \bibinfo{address}{New York, NY, US},
+  \bibinfo{year}{2006}).
+
+\bibitem{MannEtal11}
+\bibinfo{author}{Manning, J.~R.}, \bibinfo{author}{Polyn, S.~M.},
+  \bibinfo{author}{Baltuch, G.}, \bibinfo{author}{Litt, B.} \&
+  \bibinfo{author}{Kahana, M.~J.}
+\newblock \bibinfo{title}{Oscillatory patterns in temporal lobe reveal context
+  reinstatement during memory search}.
+\newblock \emph{\bibinfo{journal}{Proceedings of the National Academy of
+  Sciences, USA}} \textbf{\bibinfo{volume}{108}}, \bibinfo{pages}{12893--12897}
+  (\bibinfo{year}{2011}).
+
+\bibitem{HowaEtal12}
+\bibinfo{author}{Howard, M.~W.}, \bibinfo{author}{Viskontas, I.~V.},
+  \bibinfo{author}{Shankar, K.~H.} \& \bibinfo{author}{Fried, I.}
+\newblock \bibinfo{title}{Ensembles of human {MTL} neurons ``jump back in
+  time'' in response to a repeated stimulus}.
+\newblock \emph{\bibinfo{journal}{Hippocampus}} \textbf{\bibinfo{volume}{22}},
+  \bibinfo{pages}{1833--1847} (\bibinfo{year}{2012}).
+
+\bibitem{AtkiShif68}
+\bibinfo{author}{Atkinson, R.~C.} \& \bibinfo{author}{Shiffrin, R.~M.}
+\newblock \bibinfo{title}{Human memory: {A} proposed system and its control
+  processes}.
+\newblock In \bibinfo{editor}{Spence, K.~W.} \& \bibinfo{editor}{Spence, J.~T.}
+  (eds.) \emph{\bibinfo{booktitle}{The psychology of learning and motivation}},
+  vol.~\bibinfo{volume}{2}, \bibinfo{pages}{89--105}
+  (\bibinfo{publisher}{Academic Press}, \bibinfo{address}{New York},
+  \bibinfo{year}{1968}).
+
+\bibitem{PostPhil65}
+\bibinfo{author}{Postman, L.} \& \bibinfo{author}{Phillips, L.~W.}
+\newblock \bibinfo{title}{Short-term temporal changes in free recall}.
+\newblock \emph{\bibinfo{journal}{Quarterly Journal of Experimental
+  Psychology}} \textbf{\bibinfo{volume}{17}}, \bibinfo{pages}{132--138}
+  (\bibinfo{year}{1965}).
+
+\bibitem{WelcBurn24}
+\bibinfo{author}{Welch, G.~B.} \& \bibinfo{author}{Burnett, C.~T.}
+\newblock \bibinfo{title}{Is primacy a factor in association-formation}.
+\newblock \emph{\bibinfo{journal}{American Journal of Psychology}}
+  \textbf{\bibinfo{volume}{35}}, \bibinfo{pages}{396--401}
+  (\bibinfo{year}{1924}).
+
+\bibitem{PolyEtal09}
+\bibinfo{author}{Polyn, S.~M.}, \bibinfo{author}{Norman, K.~A.} \&
+  \bibinfo{author}{Kahana, M.~J.}
+\newblock \bibinfo{title}{A context maintenance and retrieval model of
+  organizational processes in free recall}.
+\newblock \emph{\bibinfo{journal}{Psychological Review}}
+  \textbf{\bibinfo{volume}{116}}, \bibinfo{pages}{129--156}
+  (\bibinfo{year}{2009}).
+
+\bibitem{HeusEtal18a}
+\bibinfo{author}{Heusser, A.~C.}, \bibinfo{author}{Ziman, K.},
+  \bibinfo{author}{Owen, L. L.~W.} \& \bibinfo{author}{Manning, J.~R.}
+\newblock \bibinfo{title}{{HyperTools}: a {Python} toolbox for gaining
+  geometric insights into high-dimensional data}.
+\newblock \emph{\bibinfo{journal}{{Journal of Machine Learning Research}}}
+  \textbf{\bibinfo{volume}{18}}, \bibinfo{pages}{1--6} (\bibinfo{year}{2018}).
+
+\bibitem{McInEtal18}
+\bibinfo{author}{McInnes, L.}, \bibinfo{author}{Healy, J.} \&
+  \bibinfo{author}{Melville, J.}
+\newblock \bibinfo{title}{{UMAP}: Uniform manifold approximation and projection
+  for dimension reduction}.
+\newblock \emph{\bibinfo{journal}{arXiv}} \textbf{\bibinfo{volume}{1802}}
+  (\bibinfo{year}{2018}).
+
+\bibitem{MuelEtal18}
+\bibinfo{author}{Mueller, A.} \emph{et~al.}
+\newblock \bibinfo{title}{{WordCloud 1.5.0: a little word cloud generator in
+  Python}}.
+\newblock \emph{\bibinfo{journal}{Zenodo}}
+  \textbf{\bibinfo{volume}{https://zenodo.org/record/1322068\#.W4tPKZNKh24}}
+  (\bibinfo{year}{2018}).
+
+\bibitem{PallWagn02}
+\bibinfo{author}{Paller, K.~A.} \& \bibinfo{author}{Wagner, A.~D.}
+\newblock \bibinfo{title}{Observing the transformation of experience into
+  memory}.
+\newblock \emph{\bibinfo{journal}{Trends in Cognitive Sciences}}
+  \textbf{\bibinfo{volume}{6}}, \bibinfo{pages}{93--102}
+  (\bibinfo{year}{2002}).
+
+\bibitem{YarkEtal11}
+\bibinfo{author}{Yarkoni, T.}, \bibinfo{author}{Poldrack, R.~A.},
+  \bibinfo{author}{Nichols, T.~E.}, \bibinfo{author}{Van~Essen, D.~C.} \&
+  \bibinfo{author}{Wager, T.~D.}
+\newblock \bibinfo{title}{Large-scale automated synthesis of human functional
+  neuroimaging data}.
+\newblock \emph{\bibinfo{journal}{Nature Methods}}
+  \textbf{\bibinfo{volume}{8}}, \bibinfo{pages}{665} (\bibinfo{year}{2011}).
+
+\bibitem{BellEtal18}
+\bibinfo{author}{Bellmund, J. L.~S.}, \bibinfo{author}{G\"{a}rdenfors, P.},
+  \bibinfo{author}{Moser, E.~I.} \& \bibinfo{author}{Doeller, C.~F.}
+\newblock \bibinfo{title}{Navigating cognition: spatial codes for human
+  thinking}.
+\newblock \emph{\bibinfo{journal}{Science}} \textbf{\bibinfo{volume}{362}}
+  (\bibinfo{year}{2018}).
+
+\bibitem{BellEtal20}
+\bibinfo{author}{Bellmund, J. L.~S.} \emph{et~al.}
+\newblock \bibinfo{title}{Deforming the metric of cognitive maps distorts
+  memory}.
+\newblock \emph{\bibinfo{journal}{Nature Human Behavior}}
+  \textbf{\bibinfo{volume}{4}}, \bibinfo{pages}{177--188}
+  (\bibinfo{year}{2020}).
+
+\bibitem{ConsEtal16}
+\bibinfo{author}{Constantinescu, A.~O.}, \bibinfo{author}{O'Reilly, J.~X.} \&
+  \bibinfo{author}{Behrens, T. E.~J.}
+\newblock \bibinfo{title}{Organizing conceptual knowledge in humans with a
+  gridlike code}.
+\newblock \emph{\bibinfo{journal}{Science}} \textbf{\bibinfo{volume}{352}},
+  \bibinfo{pages}{1464--1468} (\bibinfo{year}{2016}).
+
+\bibitem{GilbMarl17}
+\bibinfo{author}{Gilboa, A.} \& \bibinfo{author}{Marlatte, H.}
+\newblock \bibinfo{title}{Neurobiology of schemas and schema-mediated memory}.
+\newblock \emph{\bibinfo{journal}{Trends Cogn Sci}}
+  \textbf{\bibinfo{volume}{21}}, \bibinfo{pages}{618--631}
+  (\bibinfo{year}{2017}).
+
+\bibitem{BaldEtal18}
+\bibinfo{author}{Baldassano, C.}, \bibinfo{author}{Hasson, U.} \&
+  \bibinfo{author}{Norman, K.~A.}
+\newblock \bibinfo{title}{Representation of real-world event schemas during
+  narrative perception}.
+\newblock \emph{\bibinfo{journal}{{Journal of Neuroscience}}}
+  \textbf{\bibinfo{volume}{38}}, \bibinfo{pages}{9689--9699}
+  (\bibinfo{year}{2018}).
+
+\bibitem{HuthEtal12}
+\bibinfo{author}{Huth, A.~G.}, \bibinfo{author}{Nisimoto, S.},
+  \bibinfo{author}{Vu, A.~T.} \& \bibinfo{author}{Gallant, J.~L.}
+\newblock \bibinfo{title}{A continuous semantic space describes the
+  representation of thousands of object and action categories across the human
+  brain}.
+\newblock \emph{\bibinfo{journal}{Neuron}} \textbf{\bibinfo{volume}{76}},
+  \bibinfo{pages}{1210--1224} (\bibinfo{year}{2012}).
+
+\bibitem{HuthEtal16}
+\bibinfo{author}{Huth, A.~G.}, \bibinfo{author}{de~Heer, W.~A.},
+  \bibinfo{author}{Griffiths, T.~L.}, \bibinfo{author}{Theunissen, F.~E.} \&
+  \bibinfo{author}{Gallant, J.~L.}
+\newblock \bibinfo{title}{Natural speech reveals the semantic maps that tile
+  human cerebral cortex}.
+\newblock \emph{\bibinfo{journal}{Nature}} \textbf{\bibinfo{volume}{532}},
+  \bibinfo{pages}{453--458} (\bibinfo{year}{2016}).
+
+\bibitem{GagnEtal20}
+\bibinfo{author}{Gagnepain, P.} \emph{et~al.}
+\newblock \bibinfo{title}{Collective memory shapes the organization of
+  individual memories in the medial prefrontal cortex}.
+\newblock \emph{\bibinfo{journal}{Nature Human Behavior}}
+  \textbf{\bibinfo{volume}{4}}, \bibinfo{pages}{189--200}
+  (\bibinfo{year}{2020}).
+
+\bibitem{SimoEtal16}
+\bibinfo{author}{Simony, E.}, \bibinfo{author}{Honey, C.~J.},
+  \bibinfo{author}{Chen, J.} \& \bibinfo{author}{Hasson, U.}
+\newblock \bibinfo{title}{Dynamic reconfiguration of the default mode network
+  during narrative comprehension}.
+\newblock \emph{\bibinfo{journal}{Nature Communications}}
+  \textbf{\bibinfo{volume}{7}}, \bibinfo{pages}{1--13} (\bibinfo{year}{2016}).
+
+\bibitem{ZadbEtal17}
+\bibinfo{author}{Zadbood, A.}, \bibinfo{author}{Chen, J.},
+  \bibinfo{author}{Leong, Y.~C.}, \bibinfo{author}{Norman, K.~A.} \&
+  \bibinfo{author}{Hasson, U.}
+\newblock \bibinfo{title}{How we transmit memories to other brains:
+  Constructing shared neural representations via communication}.
+\newblock \emph{\bibinfo{journal}{Cereb Cortex}} \textbf{\bibinfo{volume}{27}},
+  \bibinfo{pages}{4988--5000} (\bibinfo{year}{2017}).
+
+\bibitem{SimoChan20}
+\bibinfo{author}{Simony, E.} \& \bibinfo{author}{Chang, C.}
+\newblock \bibinfo{title}{Analysis of stimulus-induced brain dynamics during
+  naturalistic paradigms}.
+\newblock \emph{\bibinfo{journal}{{N}euro{I}mage}}
+  \textbf{\bibinfo{volume}{216}}, \bibinfo{pages}{116461}
+  (\bibinfo{year}{2020}).
+
+\bibitem{LandDuma97}
+\bibinfo{author}{Landauer, T.~K.} \& \bibinfo{author}{Dumais, S.~T.}
+\newblock \bibinfo{title}{A solution to {P}lato's problem: the latent semantic
+  analysis theory of acquisition, induction, and representation of knowledge}.
+\newblock \emph{\bibinfo{journal}{Psychological Review}}
+  \textbf{\bibinfo{volume}{104}}, \bibinfo{pages}{211--240}
+  (\bibinfo{year}{1997}).
+
+\bibitem{MikoEtal13a}
+\bibinfo{author}{Mikolov, T.}, \bibinfo{author}{Chen, K.},
+  \bibinfo{author}{Corrado, G.} \& \bibinfo{author}{Dean, J.}
+\newblock \bibinfo{title}{Efficient estimation of word representations in
+  vector space}.
+\newblock \emph{\bibinfo{journal}{{arXiv}}}
+  \textbf{\bibinfo{volume}{1301.3781}} (\bibinfo{year}{2013}).
+
+\bibitem{CerEtal18}
+\bibinfo{author}{Cer, D.} \emph{et~al.}
+\newblock \bibinfo{title}{Universal sentence encoder}.
+\newblock \emph{\bibinfo{journal}{{arXiv}}}
+  \textbf{\bibinfo{volume}{1803.11175}} (\bibinfo{year}{2018}).
+
+\bibitem{RadfEtal19}
+\bibinfo{author}{Radford, A.} \emph{et~al.}
+\newblock \bibinfo{title}{Language models are unsupervised multitask learners}.
+\newblock \emph{\bibinfo{journal}{OpenAI Blog}} \textbf{\bibinfo{volume}{1}}
+  (\bibinfo{year}{2019}).
+
+\bibitem{BrowEtal20}
+\bibinfo{author}{Brown, T.~B.} \emph{et~al.}
+\newblock \bibinfo{title}{Language models are few-shot learners}.
+\newblock \emph{\bibinfo{journal}{{arXiv}}}
+  \textbf{\bibinfo{volume}{2005.14165}} (\bibinfo{year}{2020}).
+
+\bibitem{PedrEtal11}
+\bibinfo{author}{Pedregosa, F.} \emph{et~al.}
+\newblock \bibinfo{title}{Scikit-learn: Machine learning in {P}ython}.
+\newblock \emph{\bibinfo{journal}{Journal of Machine Learning Research}}
+  \textbf{\bibinfo{volume}{12}}, \bibinfo{pages}{2825--2830}
+  (\bibinfo{year}{2011}).
+
+\bibitem{Brainiak}
+\bibinfo{author}{Capota, M.} \emph{et~al.}
+\newblock \bibinfo{title}{Brain imaging analysis kit} (\bibinfo{year}{2017}).
+\newblock \urlprefix\url{https://doi.org/10.5281/zenodo.59780}.
+
+\bibitem{HassEtal08}
+\bibinfo{author}{Hasson, U.}, \bibinfo{author}{Yang, E.},
+  \bibinfo{author}{Vallines, I.}, \bibinfo{author}{Heeger, D.~J.} \&
+  \bibinfo{author}{Rubin, N.}
+\newblock \bibinfo{title}{A hierarchy of temporal receptive windows in human
+  cortex}.
+\newblock \emph{\bibinfo{journal}{Journal of Neuroscience}}
+  \textbf{\bibinfo{volume}{28}}, \bibinfo{pages}{2539--2550}
+  (\bibinfo{year}{2008}).
+
+\bibitem{HassEtal15}
+\bibinfo{author}{Hasson, U.}, \bibinfo{author}{Chen, J.} \&
+  \bibinfo{author}{Honey, C.~J.}
+\newblock \bibinfo{title}{Hierarchical process memory: memory as an integral
+  component of information processing}.
+\newblock \emph{\bibinfo{journal}{Trends in Cognitive Science}}
+  \textbf{\bibinfo{volume}{19}}, \bibinfo{pages}{304--315}
+  (\bibinfo{year}{2015}).
+
+\bibitem{Dobr70}
+\bibinfo{author}{Dobrushin, R.~L.}
+\newblock \bibinfo{title}{Prescribing a system of random variables by
+  conditional distributions}.
+\newblock \emph{\bibinfo{journal}{Theory of Probability \& Its Applications}}
+  \textbf{\bibinfo{volume}{15}}, \bibinfo{pages}{458--486}
+  (\bibinfo{year}{1970}).
+
+\bibitem{RamdEtal17}
+\bibinfo{author}{Ramdas, A.}, \bibinfo{author}{Trillos, N.} \&
+  \bibinfo{author}{Cuturi, M.}
+\newblock \bibinfo{title}{On wasserstein two-sample testing and related
+  families of nonparametric tests}.
+\newblock \emph{\bibinfo{journal}{Entropy}} \textbf{\bibinfo{volume}{19}},
+  \bibinfo{pages}{47} (\bibinfo{year}{2017}).
+
+\bibitem{HeusEtal17b}
+\bibinfo{author}{Heusser, A.~C.}, \bibinfo{author}{Fitzpatrick, P.~C.},
+  \bibinfo{author}{Field, C.~E.}, \bibinfo{author}{Ziman, K.} \&
+  \bibinfo{author}{Manning, J.~R.}
+\newblock \bibinfo{title}{Quail: a {Python} toolbox for analyzing and plotting
+  free recall data}.
+\newblock \emph{\bibinfo{journal}{The Journal of Open Source Software}}
+  \textbf{\bibinfo{volume}{10.21105/joss.00424}} (\bibinfo{year}{2017}).
+
+\bibitem{Fish25}
+\bibinfo{author}{Fisher, R.~A.}
+\newblock \emph{\bibinfo{title}{Statistical Methods for Research Workers}}
+  (\bibinfo{publisher}{Oliver and Boyd}, \bibinfo{year}{1925}).
+
+\bibitem{BernClif94}
+\bibinfo{author}{Berndt, D.~J.} \& \bibinfo{author}{Clifford, J.}
+\newblock \bibinfo{title}{Using dynamic time warping to find patterns in time
+  series}.
+\newblock In \emph{\bibinfo{booktitle}{{KDD workshop}}},
+  vol.~\bibinfo{volume}{10}, \bibinfo{pages}{359--370} (\bibinfo{year}{1994}).
+
+\bibitem{FreeEtal01}
+\bibinfo{author}{Freedman, D.}, \bibinfo{author}{Riesenhuber, M.},
+  \bibinfo{author}{Poggio, T.} \& \bibinfo{author}{Miller, E.}
+\newblock \bibinfo{title}{Categorical representation of visual stimuli in the
+  primate prefrontal cortex}.
+\newblock \emph{\bibinfo{journal}{Science}} \textbf{\bibinfo{volume}{291}},
+  \bibinfo{pages}{312--316} (\bibinfo{year}{2001}).
+
+\bibitem{SigmDeha08}
+\bibinfo{author}{Sigman, M.} \& \bibinfo{author}{Dehaene, S.}
+\newblock \bibinfo{title}{Brain mechanisms of serial and parallel processing
+  during dual-task performance}.
+\newblock \emph{\bibinfo{journal}{Journal of Neuroscience}}
+  \textbf{\bibinfo{volume}{28}}, \bibinfo{pages}{7585--7589}
+  (\bibinfo{year}{2008}).
+
+\bibitem{CharKoec10}
+\bibinfo{author}{Charron, S.} \& \bibinfo{author}{Koechlin, E.}
+\newblock \bibinfo{title}{Divided representations of current goals in the human
+  frontal lobes}.
+\newblock \emph{\bibinfo{journal}{Science}} \textbf{\bibinfo{volume}{328}},
+  \bibinfo{pages}{360--363} (\bibinfo{year}{2010}).
+
+\bibitem{RishEtal13}
+\bibinfo{author}{Rishel, C.~A.}, \bibinfo{author}{Huang, G.} \&
+  \bibinfo{author}{Freedman, D.~J.}
+\newblock \bibinfo{title}{Independent category and spatial encoding in parietal
+  cortex}.
+\newblock \emph{\bibinfo{journal}{Neuron}} \textbf{\bibinfo{volume}{77}},
+  \bibinfo{pages}{969--979} (\bibinfo{year}{2013}).
+
+\bibitem{KrieEtal08b}
+\bibinfo{author}{Kriegeskorte, N.}, \bibinfo{author}{Mur, M.} \&
+  \bibinfo{author}{Bandettini, P.}
+\newblock \bibinfo{title}{Representational similarity analysis -- connecting
+  the branches of systems neuroscience}.
+\newblock \emph{\bibinfo{journal}{Frontiers in Systems Neuroscience}}
+  \textbf{\bibinfo{volume}{2}}, \bibinfo{pages}{1 -- 28}
+  (\bibinfo{year}{2008}).
+
+\end{thebibliography}
 
@@
 The content is solely the responsibility of the authors and does not necessarily represent the official views of our supporting organizations.
+The funders had no role in study design, data collection and analysis, decision to publish or preparation of the manuscript.
 
@@
 
-\section*{Author information}
-The authors declare no competing financial interests.  Correspondence and requests for materials should be addressed to J.R.M. (jeremy.r.manning@dartmouth.edu).
+\section*{Competing interests}
+The authors declare no competing interests.
 

### 2020-10-14 code/sherlock_helpers/sherlock_helpers/functions.py
made add_arrows more customizable; keyword args only

@@ -138,9 +138,12 @@ def z2r(z):
 #               PLOTTING               #
 ########################################
 
-def add_arrows(axes, x, y, **kwargs):
+def add_arrows(axes, x, y, *, aspace=None, head_width=None, **kwargs):
     # spacing of arrows
-    aspace = .05 * GRID_SCALE
+    if aspace is None:
+        aspace = .05 * GRID_SCALE
+    if head_width is None:
+        head_width = aspace / 3
     # distance spanned between pairs of points
     r = [0]
     for i in range(1, len(x)):
@@ -180,7 +183,7 @@ def add_arrows(axes, x, y, **kwargs):
                    ay,
                    np.sin(theta) * aspace / 10,
                    np.cos(theta) * aspace / 10,
-                   head_width=aspace / 3,
+                   head_width=head_width,
                    **kwargs)
 
 

### 2020-10-14 paper/supporting_information.tex
removed duplicate page numbering in main text and supplement

@@
 
-\title{\textit{Supporting Information for}: Geometric models reveal behavioral and neural signatures of transforming naturalistic experiences into episodic memories}
+\title{\textit{Supporting Information for}: Geometric models reveal behavioral and neural signatures of transforming experiences into memories}
 \author{Andrew C.
@@
 Fitzpatrick\textsuperscript{1, \textdagger}, and Jeremy R.
-Manning\textsuperscript{1, *}\\\textsuperscript{1}Department of Psychological and Brain Sciences\\Dartmouth College, Hanover, NH 03755, USA\\\textsuperscript{2}Akili Interactive Labs\\Boston, MA 02110\\\textsuperscript{\textdagger}Denotes equal contribution\\\textsuperscript{*}Corresponding author: Jeremy.R.Manning@Dartmouth.edu}
+Manning\textsuperscript{1, *}\\\textsuperscript{1}Department of Psychological and Brain Sciences\\Dartmouth College, Hanover, NH 03755, USA\\\textsuperscript{2}Akili Interactive Labs\\Boston, MA 02110, USA\\\textsuperscript{\textdagger}Denotes equal contribution\\\textsuperscript{*}Corresponding author: Jeremy.R.Manning@Dartmouth.edu}
 
@@
 \begin{document}
-\begin{titlepage}
-  \maketitle
-\end{titlepage}
+
+\renewcommand{\figurename}{Supplementary Figure}
+
+%\begin{titlepage}
+%  \maketitle
+%  \thispagestyle{empty}
+%\end{titlepage}
 
@@
 \makeatletter
-\renewcommand{\theequation}{S\arabic{equation}}
-\renewcommand{\thefigure}{S\arabic{figure}}
+%\renewcommand{\theequation}{S\arabic{equation}}
+%\renewcommand{\thefigure}{S\arabic{figure}}
 \renewcommand{\bibnumfmt}[1]{[S#1]}
@@
 
-\section*{Overview}
-This document provides additional details about the methods we used in the main text.  We also include some additional analyses referenced in the main text.
+%\section*{Overview}
+%This document provides additional details about the methods we used in the main text.  We also %include some additional analyses referenced in the main text.
 
-\section*{Additional details about topic modeling methods and results}
+\section*{Supplementary methods}
 \subsection*{Optimizing topic model parameters}
@@
   \vspace*{\fill}
-    \section*{Participant-level figures referenced in the main text}
+  \section*{Supplementary figures}
+    \subsection*{Participant-level figures referenced in the main text}
     \vspace*{\fill}
@@
 \newpage
-\renewcommand{\refname}{Supplemental references}
+\renewcommand{\refname}{Supplementary references}
 \bibliography{CDL-bibliography/memlab}

### 2020-10-14 code/sherlock_helpers/sherlock_helpers/functions.py
confidence interval calculation for pearson correlation

@@ -14,6 +14,7 @@ from fastdtw import fastdtw
 from IPython.display import display, HTML
 from IPython.core.oinspect import pylight
 from scipy.spatial.distance import correlation
+from scipy.stats import norm
 
 from .constants import EDGECOLOR, GRID_SCALE, RAW_DIR, RECALL_WSIZE
 
@@ -132,6 +133,15 @@ def r2z(r):
 def z2r(z):
     with np.errstate(invalid='ignore', divide='ignore'):
         return (np.exp(2 * z) - 1) / (np.exp(2 * z) + 1)
+
+
+def pearsonr_ci(r, n, alpha=0.05):
+    z = r2z(r)
+    std_err = 1 / ((n - 3) ** 0.5)
+    z_a = norm.ppf(0.5 * (1 + alpha))    # 2-tailed
+    ci_low = z - z_a * std_err
+    ci_high = z + z_a * std_err
+    return z2r(ci_low), z2r(ci_high)
 
 
 ########################################

### 2020-10-14 paper/main.tex
remove merge markers and recompile
reformatted to satisfy NHB requirements and did some minor wording edits throughout

@@
 
-\newcommand{\topicopt}{S1}
-\newcommand{\topics}{S2}
-\newcommand{\featureimportance}{S3}
-\newcommand{\corrmats}{S4}
-\newcommand{\matchmats}{S5}
-\newcommand{\kopt}{S6}
+\newcommand{\topicopt}{1}
+\newcommand{\topics}{2}
+\newcommand{\featureimportance}{3}
+\newcommand{\corrmats}{4}
+\newcommand{\matchmats}{5}
+\newcommand{\kopt}{6}
+\newcommand{\arrows}{7}
 
@@
 What does it mean to remember something?
-In traditional episodic memory experiments \citep[e.g., list-learning or trial-based experiments;][]{Murd62a, Kaha96}, remembering is often cast as a discrete, binary operation: each studied item may be separated from the rest of one's experience and labeled as having been either recalled or forgotten.
+In traditional episodic memory experiments (e.g., list-learning or trial-based experiments\citep{Murd62a, Kaha96}), remembering is often cast as a discrete, binary operation: each studied item may be separated from the rest of one's experience and labeled as having been either recalled or forgotten.
 More nuanced studies might incorporate self-reported confidence measures as a proxy for memory strength, or ask participants to discriminate between recollecting the (contextual) details of an experience and having a general feeling of familiarity~\citep{Yone02}.
-Using well-controlled, trial-based experimental designs, the field has amassed a wealth of information regarding human episodic memory~\citep[for review see][]{Kaha12}.
-However, there are fundamental properties of the external world and our memories that trial-based experiments are not well suited to capture~\citep[for review, also see][]{KoriGold94, HukEtal18}.
+Using well-controlled, trial-based experimental designs, the field has amassed a wealth of information regarding human episodic memory~\citep{Kaha12}.
+However, there are fundamental properties of the external world and our memories that trial-based experiments are not well suited to capture~\citep{KoriGold94, HukEtal18}.
 First, our experiences and memories are continuous, rather than discrete---isolating a naturalistic event from the context in which it occurs can substantially change its meaning.
@@
 Therefore, the timecourse describing how an event unfolds is fundamental to its overall meaning.
-Further, this hierarchy formed by our subjective experiences at different timescales defines a context for each new moment~\citep[e.g.,][]{HowaKaha02a, HowaEtal14}, and plays an important role in how we interpret that moment and remember it later~\citep[for review see][]{MannEtal15, Mann20}.
+Further, this hierarchy formed by our subjective experiences at different timescales defines a context for each new moment~\citep{HowaKaha02a, HowaEtal14}, and plays an important role in how we interpret that moment and remember it later~\citep{MannEtal15, Mann20}.
 Our memory systems can leverage these associations to form predictions that help guide our behaviors~\citep{RangRitc12}.
@@
 
-Occasionally, this gradual drift of our ongoing experience is punctuated by sudden changes, or shifts~\citep[e.g., when we walk through a doorway;][]{RadvZack17}.
+Occasionally, this gradual drift of our ongoing experience is punctuated by sudden changes, or shifts (e.g., when we walk through a doorway~\citep{RadvZack17}).
 Prior research suggests that these sharp transitions (termed ``event boundaries'') help to discretize our experiences (and their mental representations) into ``events''~\citep{RadvZack17, BrunEtal18, HeusEtal18b, ClewDava17, EzzyDava11, DuBrDava13}.
@@
 
-\cite{ChenEtal17} collected hand-annotated information about each of 1,000 (manually delineated) time segments spanning the roughly 50 minute video used in their study.
+Chen et al.
+(2017) collected hand-annotated information about each of 1,000 (manually delineated) time segments spanning the roughly 50 minute video used in their study~\cite{ChenEtal17}.
 Each annotation included: a brief narrative description of what was happening, the location where the action took place, the names of any characters on the screen, and other similar details (for a full list of annotated features, see \textit{Methods}).
@@
 Next, we fit a topic model with (up to) $K = 100$ topics to this collection of documents.
-We found that 32 unique topics (with non-zero weights) were sufficient to describe the time-varying content of the episode (see \textit{Methods}; Fig.~\ref{fig:schematic}, Supp.
-Fig.~\topics).
+We found that 32 unique topics (with non-zero weights) were sufficient to describe the time-varying content of the episode (see \textit{Methods}; Fig.~\ref{fig:schematic}, Supp.\ Fig.~\topics).
 We note that our approach is similar in some respects to Dynamic Topic Models~\citep{BleiLaff06} in that we sought to characterize how the thematic content of the episode evolved over time.
@@
 
-The 32 topics we found were heavily character-focused (i.e., the top-weighted word in each topic was nearly always a character) and could be roughly divided into themes centered around Sherlock Holmes (the titular character), John Watson (Sherlock's close confidant and assistant), supporting characters (e.g., Inspector Lestrade, Sergeant Donovan, or Sherlock's brother Mycroft), or the interactions between various groupings of these characters (Supp.
-Fig.~\topics).
+The 32 topics we found were heavily character-focused (i.e., the top-weighted word in each topic was nearly always a character) and could be roughly divided into themes centered around Sherlock Holmes (the titular character), John Watson (Sherlock's close confidant and assistant), supporting characters (e.g., Inspector Lestrade, Sergeant Donovan, or Sherlock's brother Mycroft), or the interactions between various groupings of these characters (Supp.\ Fig.~\topics).
 This likely follows from the frequency with which these terms appeared in the episode annotations.
@@
 These two properties of the topic dynamics may be seen in the block diagonal structure of the timepoint-by-timepoint correlation matrix (Fig.~\ref{fig:model}B) and reflect the gradual drift and sudden shifts fundamental to the temporal dynamics of many real-world experiences, as well as television episodes.
-Given this observation, we adapted an approach devised by \cite{BaldEtal17}, and used a hidden Markov model (HMM) to identify the ``event boundaries'' where the topic activations changed rapidly (i.e., the boundaries of the blocks in the temporal correlation matrix; event boundaries identified by the HMM are outlined in yellow in Fig.~\ref{fig:model}B).
+Given this observation, we adapted an approach devised by Baldassano et al.
+(2017)~\cite{BaldEtal17}, and used a hidden Markov model (HMM) to identify the ``event boundaries'' where the topic activations changed rapidly (i.e., the boundaries of the blocks in the temporal correlation matrix; event boundaries identified by the HMM are outlined in yellow in Fig.~\ref{fig:model}B).
 Part of our model fitting procedure required selecting an appropriate number of events into which the topic trajectory should be segmented.
@@
 We used the same HMM-based optimization procedure that we had applied to the episode's topic proportions matrix (see \textit{Methods}) to estimate an analogous set of event boundaries in the participant's recounting of the episode (outlined in yellow).
-We carried out this analysis on all 17 participants' recall topic proportions matrices (Supp.
-Fig.~\corrmats).
+We carried out this analysis on all 17 participants' recall topic proportions matrices (Supp.\ Fig.~\corrmats).
 
 Two clear patterns emerged from this set of analyses.
-First, although every individual participant's recalls could be segmented into discrete events (i.e., every individual participant's recall correlation matrix exhibited clear block diagonal structure; Supp.
-Fig.~\corrmats), each participant appeared to have a unique ``recall resolution,'' reflected in the sizes of those blocks.
+First, although every individual participant's recalls could be segmented into discrete events (i.e., every individual participant's recall correlation matrix exhibited clear block diagonal structure; Supp.\ Fig.~\corrmats), each participant appeared to have a unique ``recall resolution,'' reflected in the sizes of those blocks.
 While some participants' recall topic proportions segmented into just a few events (e.g., Participants P4, P5, and P7), others' segmented into many shorter-duration events (e.g., Participants P12, P13, and P17).
@@
 One potential explanation for this finding is that the topic models, trained only on episode annotations, do not capture topic proportions in participants' ``held-out'' recalls as accurately.
-A second possibility is that, whereas each event in the original episode was (largely) separable from the others (Fig.~\ref{fig:model}B), in transforming those separable events into memory, participants appeared to be integrating across multiple events, blending elements of previously recalled and not-yet-recalled content into each newly recalled event~\citep[Fig.~\ref{fig:model}E, Supp.
-Fig.~\corrmats; also see][]{MannEtal11, HowaEtal12, Mann19}.
+A second possibility is that, whereas each event in the original episode was (largely) separable from the others (Fig.~\ref{fig:model}B), in transforming those separable events into memory, participants appeared to be integrating across multiple events, blending elements of previously recalled and not-yet-recalled content into each newly recalled event (Fig.~\ref{fig:model}E, Supp.\ Fig.~\corrmats)~\citep{MannEtal11, HowaEtal12, Mann19}.
 
@@
 Next, we asked whether some correspondence might be made between the specific content of the events the participants experienced while viewing the episode, and the events they later recalled.
-We labeled each recall event as matching the episode event with the most similar (i.e., most highly correlated) topic vector (Fig.~\ref{fig:model}G, Supp.
-Fig.~\matchmats).
+We labeled each recall event as matching the episode event with the most similar (i.e., most highly correlated) topic vector (Fig.~\ref{fig:model}G, Supp.\ Fig.~\matchmats).
 This yielded a sequence of ``presented'' events from the original episode, and a (potentially differently ordered) sequence of ``recalled'' events for each participant.
-Analogous to classic list-learning studies, we can then examine participants' recall sequences by asking which events they tended to recall first~\citep[probability of first recall; Fig.~\ref{fig:list-learning}A;][]{AtkiShif68, PostPhil65, WelcBurn24}; how participants most often transitioned between recalls of the events as a function of the temporal distance between them~\citep[lag-conditional response probability; Fig.~\ref{fig:list-learning}B;][]{Kaha96}; and which events they were likely to remember overall~\citep[serial position recall analyses; Fig.~\ref{fig:list-learning}C;][]{Murd62a}.
+Analogous to classic list-learning studies, we can then examine participants' recall sequences by asking which events they tended to recall first (probability of first recall~\citep{AtkiShif68, PostPhil65, WelcBurn24}; Fig.~\ref{fig:list-learning}A); how participants most often transitioned between recalls of the events as a function of the temporal distance between them (lag-conditional response probability~\citep{Kaha96}; Fig.~\ref{fig:list-learning}B); and which events they were likely to remember overall (serial position recall analyses~\citep{Murd62a}; Fig.~\ref{fig:list-learning}C).
 Some of the patterns we observed appeared to be similar to classic effects from the list-learning literature.
@@
 We hypothesized that participants might be leveraging meaningful narrative associations and references over long timescales throughout the episode.
-
-Clustering scores are often used by memory researchers to characterize how people organize their memories of words on a studied list~\citep[for review, see][]{PolyEtal09}.
-We defined analogous measures to characterize how participants organized their memories for episodic events (see \textit{Methods} for details).
-Temporal clustering refers to the extent to which participants group their recall responses according to encoding position.
-Overall, we found that sequentially viewed episode events tended to appear nearby in participants' recall event sequences (mean clustering score: 0.732, SEM: 0.033).
-Participants with higher temporal clustering scores tended to exhibit better overall memory for the episode, according to both \cite{ChenEtal17}'s hand-counted numbers of recalled scenes from the episode (Pearson's $r(15) = 0.49,~p = 0.046$) and the numbers of episode events that best-matched at least one recall event (i.e., model-estimated number of events recalled; Pearson's $r(15) = 0.59,~p = 0.013$).
-Semantic clustering measures the extent to which participants cluster their recall responses according to semantic similarity.
-We found that participants tended to recall semantically similar episode events together (mean clustering score: 0.650, SEM: 0.032), and that semantic clustering score was also related to both hand-counted  (Pearson's $r(15) = 0.65,~p = 0.005$) and model-estimated (Pearson's $r(15) = 0.58,~p = 0.015$) numbers of recalled events.
 
@@
 
+Clustering scores are often used by memory researchers to characterize how people organize their memories of words on a studied list~\citep{PolyEtal09}.
+We defined analogous measures to characterize how participants organized their memories for episodic events (see \textit{Methods} for details).
+Temporal clustering refers to the extent to which participants group their recall responses according to encoding position.
+Overall, we found that sequentially viewed episode events tended to appear nearby in participants' recall event sequences (mean clustering score: 0.732, SEM: 0.033).
+Participants with higher temporal clustering scores tended to exhibit better overall memory for the episode, according to both Chen et al.
+(2017)~\cite{ChenEtal17}'s hand-counted numbers of recalled scenes from the episode (Pearson's $r(15) = 0.49,~p = 0.046$) and the numbers of episode events that best-matched at least one recall event (i.e., model-estimated number of events recalled; Pearson's $r(15) = 0.59,~p = 0.013$).
+Semantic clustering measures the extent to which participants cluster their recall responses according to semantic similarity~\citep{MannKaha12}.
+We found that participants tended to recall semantically similar episode events together (mean clustering score: 0.650, SEM: 0.032), and that semantic clustering score was also related to both hand-counted  (Pearson's $r(15) = 0.65,~p = 0.005$) and model-estimated (Pearson's $r(15) = 0.58,~p = 0.015$) numbers of recalled events.
+
 \begin{figure}[tp]
@@
   \includegraphics[width=1\textwidth]{figs/precision_distinctiveness}
-  \caption{\small \textbf{Novel content-based metrics of naturalistic memory: precision and distinctiveness.} \textbf{A.} The episode-recall correlation matrix for a representative participant (P17), chosen for their large number of recall events (for analogous figures for other participants, see Supp.
-Fig.~\corrmats).
+  \caption{\small \textbf{Novel content-based metrics of naturalistic memory: precision and distinctiveness.} \textbf{A.} The episode-recall correlation matrix for a representative participant (P17), chosen for their large number of recall events (for analogous figures for other participants, see Supp.\ Fig.~\corrmats).
 The yellow boxes highlight the maximum correlation in each column.
@@
 Their distinctiveness score was computed as the average (over recall events) of the $z$-scored (within column) event precisions.
-\textbf{B.} The (Pearson's) correlation between precision and hand-counted number of recalled scenes.
+\textbf{B.} The across-participants (Pearson's) correlation between precision and hand-counted number of recalled scenes.
 \textbf{C.} The correlation between distinctiveness and hand-counted number of recalled scenes.
@@
 Grey violin plots display kernel density estimates for the distribution of recall precision scores for a single episode event.
-Colored dots within each violin plot represent individual participants' recall precision for the given event.
+Colored dots within each violin plot represent individual participants' recall precisions for the given event.
 \textbf{B.} Recall distinctiveness by episode event, analogous to Panel A.
-\textbf{C.} The set of ``Narrative Details'' episode annotations (generated by \citealp{ChenEtal17}) comprising an example episode event (22) identified by the HMM.
+\textbf{C.} The set of ``Narrative Details'' episode annotations~\citep{ChenEtal17} comprising an example episode event (22) identified by the HMM.
 Each action or feature is highlighted in a different color.
@@
 The unhighlighted text denotes correctly recalled information about other episode events.
-\textbf{E.} The sets of ``Narrative Details'' episode annotations (generated by \citealp{ChenEtal17}) for scenes comprising episode events described by the example participants in Panel F.
+\textbf{E.} The sets of ``Narrative Details'' episode annotations~\citep{ChenEtal17} for scenes comprising episode events described by the example participants in Panel F.
 Each event's text is highlighted in a different color.
@@
 Next, we sought to characterize how participants' recountings of the full episode captured its high-level essence---i.e., the shape of the episode's trajectory through word embedding (topic) space.
-To visualize the essence of the episode and each participant's recall trajectory~\citep{HeusEtal18a}, we projected the topic proportions matrices for the episode and recalls onto a shared two-dimensional space using Uniform Manifold Approximation and Projection~\citep[UMAP; ][]{McInEtal18}.
+To visualize the essence of the episode and each participant's recall trajectory~\citep{HeusEtal18a}, we projected the topic proportions matrices for the episode and recalls onto a shared two-dimensional space using Uniform Manifold Approximation and Projection (UMAP)~\citep{McInEtal18}.
 In this lower-dimensional space, each point represents a single episode or recall event, and the distances between the points reflect the distances between the events' associated topic vectors (Fig.~\ref{fig:trajectory}).
@@
 The arrows reflect the average transition direction through topic space taken by any participants whose trajectories crossed that part of topic space; blue denotes reliable agreement across participants via a Rayleigh test ($p < 0.05$, corrected).
+For additional detail see \textit{Methods} and Supplementary Figure~\arrows.
 \textbf{C.} The recall topic trajectories (gray) taken by each individual participant (P1--P17).
@@
 To assess the consistency of these recall trajectories across participants, we asked: given that a participant's recall trajectory had entered a particular location in the reduced topic space, could the position of their next recalled event be predicted reliably?
-For each location in the reduced topic space, we computed the set of line segments connecting successively recalled events (across all participants) that intersected that location (see \textit{Methods}).
+For each location in the reduced topic space, we computed the set of line segments connecting successively recalled events (across all participants) that intersected that location (see \textit{Methods}, Supp.\ Fig.~\arrows).
 We then computed (for each location) the distribution of angles formed by the lines defined by those line segments and a fixed reference line (the $x$-axis).
@@
 An analogous analysis revealed which themes were less-precisely remembered.
-Here in computing the weighted average over events' topic vectors, we weighted each event in inverse proportion to its average precision (Fig.~\ref{fig:topics}B, red box).
+Here, in computing the weighted average over events' topic vectors, we weighted each event in inverse proportion to its average precision (Fig.~\ref{fig:topics}B, red box).
 The least precisely remembered episode content reflected information that was extraneous to the episode's essence, such as the proper names of relatively minor characters (e.g., ``Mike,'' ``Molly,'' and ``Lestrade'') and locations (e.g., ``St.
@@
 The recall-driven searchlight analysis revealed a second network of regions (Fig.~\ref{fig:brainz}D) that may facilitate a person-specific transformation of one's experience into memory.
-In identifying regions whose responses to ongoing experiences reflect how those experiences will be remembered later, this latter analysis extends classic ``subsequent memory effect analyses''~\citep[e.g.,][]{PallWagn02} to the domain of naturalistic experiences.
+In identifying regions whose responses to ongoing experiences reflect how those experiences will be remembered later, this latter analysis extends classic ``subsequent memory effect analyses''~\citep{PallWagn02} to the domain of naturalistic experiences.
 
@@
 We then computed the temporal correlation matrix of each participant's warped recalls.
-Next, we applied the same diagonal mask used in Panel A to isolate the proximal temporal correlations and searched for brain regions whose activation timeseries for an individual consistently exhibited a similar proximal correlational structure to each individual's recalls.
+Next, we applied the same diagonal mask used in Panel A to isolate the proximal temporal correlations and searched for brain regions whose activation timeseries for each participant consistently exhibited a similar proximal correlational structure to that participant's recalls.
 \textbf{C.} We identified a network of regions sensitive to the narrative structure of participants' ongoing experience.
@@
 We next sought to gain greater insight into the structures and functional networks our results reflected.
-To accomplish this, we performed an additional, exploratory analysis using \texttt{Neurosynth} \citep{YarkEtal11}.
-Given an arbitrary statistical map as input, \texttt{Neurosynth} performs a massive automated meta-analysis, returning a ranked list of terms frequently used in neuroimaging papers that report similar statistical maps.
+To accomplish this, we performed an additional, exploratory analysis using \texttt{Neurosynth}~\citep{YarkEtal11}.
+Given an arbitrary statistical map as input, \texttt{Neurosynth} performs a massive automated meta-analysis, returning a frequency-ranked list of terms used in neuroimaging papers that report similar statistical maps.
 We ran \texttt{Neurosynth} on the (unthresholded) permutation-corrected maps for the episode- and recall-driven searchlight analyses.
@@
 
-Explicitly modeling the dynamic content of a naturalistic stimulus and participants' memories enabled us to connect the present study of naturalistic recall with an extensive prior literature that has used list-learning paradigms to study memory~\citep[for review see][]{Kaha12}, as in Figure~\ref{fig:list-learning}.
+Explicitly modeling the dynamic content of a naturalistic stimulus and participants' memories enabled us to connect the present study of naturalistic recall with an extensive prior literature that has used list-learning paradigms to study memory~\citep{Kaha12}, as in Figure~\ref{fig:list-learning}.
 We found some similarities between how participants in the present study recounted a television episode and how participants typically recall memorized random word lists.
@@
 
-Our work casts remembering as reproducing (behaviorally and neurally) the topic trajectory, or ``shape,'' of an experience, thereby drawing implicit analogies between mentally navigating through word embedding spaces and physically navigating through spatial environments~\citep[e.g.,][]{BellEtal18, BellEtal20, ConsEtal16}.
+Our work casts remembering as reproducing (behaviorally and neurally) the topic trajectory, or ``shape,'' of an experience, thereby drawing implicit analogies between mentally navigating through word embedding spaces and physically navigating through spatial environments~\citep{BellEtal18, BellEtal20, ConsEtal16}.
 When we characterized memory for a television episode using this framework, we found that every participant's recounting of the episode recapitulated the low spatial frequency details of the shape of its trajectory through topic space (Fig.~\ref{fig:trajectory}).
@@
 This network included orbitofrontal cortex, ventromedial prefrontal cortex, and striatum, among others.
-As reviewed by \cite{RangRitc12}, several of these regions are members of the ``anterior temporal system,'' which has been implicated in assessing and processing the familiarity of ongoing experiences, emotions, social cognition, and reward.
+As reviewed by Ranganath and Ritchey (2012)~\cite{RangRitc12}, several of these regions are members of the ``anterior temporal system,'' which has been implicated in assessing and processing the familiarity of ongoing experiences, emotions, social cognition, and reward.
 A second network we identified tracked with temporal correlations in the idiosyncratic conceptual content of participants' subsequent recountings of the episode.
 This network included occipital cortex, extrastriate cortex, fusiform gyrus, and the precuneus.
-Several of these regions are members of the ``posterior medial system''~\citep{RangRitc12}, which has been implicated in matching incoming cues about the current situation to internally maintained ``situation models'' that specify the parameters and expectations inherent to the current situation~\citep[also see][]{ZackEtal07, ZwaaRadv98}.
+Several of these regions are members of the ``posterior medial system''~\citep{RangRitc12}, which has been implicated in matching incoming cues about the current situation to internally maintained ``situation models'' that specify the parameters and expectations inherent to the current situation~\citep{ZackEtal07, ZwaaRadv98}.
 Taken together, our results support the notion that these two (partially overlapping) networks work in coordination to make sense of our ongoing experiences, distort them in a way that links them with our prior knowledge and experiences, and encodes those distorted representations into memory for our later use.
-Our work also provides a potential framework for modeling and elucidating ``memory schemas''-- i.e., cognitive abstractions that may be applied to multiple related experiences~\citep[e.g.,][]{GilbMarl17, BaldEtal18}.
+Our work also provides a potential framework for modeling and elucidating ``memory schemas''-- i.e., cognitive abstractions that may be applied to multiple related experiences~\citep{GilbMarl17, BaldEtal18}.
 For example, the event-level geometric scaffolding of an experience (e.g., Fig.~\ref{fig:trajectory}A) might reflect its underlying schema, and experiences that share similar schemas might have similar shapes.
-This could also help explain how brain structures including the ventromedial prefrontal cortex~\citep[Fig.~\ref{fig:brainz}; also see][]{GilbMarl17} might acquire or apply schema knowledge across different experiences (i.e., by learning patterns in the schema's shape).
+This could also help explain how brain structures including the ventromedial prefrontal cortex~\citep{GilbMarl17} (Fig.~\ref{fig:brainz}) might acquire or apply schema knowledge across different experiences (i.e., by learning patterns in the schema's shape).
 
 Our general approach draws inspiration from prior work aimed at elucidating the neural and behavioral underpinnings of how we process dynamic naturalistic experiences and remember them later.
-Our approach to identifying neural responses to naturalistic stimuli (including experiences) entails building an explicit model of the stimulus dynamics and searching for brain regions whose responses are consistent with the model~\citep[also see][]{HuthEtal12, HuthEtal16}.
-Building an explicit model of these dynamics also enables us to match up different people's recountings of a common shared experience, despite individual differences~\cite[also see][]{GagnEtal20}.
+Our approach to identifying neural responses to naturalistic stimuli (including experiences) entails building an explicit model of the stimulus dynamics and searching for brain regions whose responses are consistent with the model~\citep{HuthEtal12, HuthEtal16}.
+Building an explicit model of these dynamics also enables us to match up different people's recountings of a common shared experience, despite individual differences~\cite{GagnEtal20}.
 In prior work, a series of studies from Uri Hasson's group~\citep{LernEtal11, SimoEtal16, ChenEtal17, BaldEtal17, ZadbEtal17} have presented a clever alternative approach: rather than building an explicit stimulus model, these studies instead search for brain responses to the stimulus that are reliably similar across individuals.
-So called ``inter-subject correlation'' (ISC) and ``inter-subject functional connectivity'' (ISFC) analyses effectively treat other people's brain responses to the stimulus as a ``model'' of how its features change over time~\citep[also see][]{SimoChan20}.
+So called ``inter-subject correlation'' (ISC) and ``inter-subject functional connectivity'' (ISFC) analyses effectively treat other people's brain responses to the stimulus as a ``model'' of how its features change over time~\citep{SimoChan20}.
 These purely brain-driven approaches are well suited to identifying which brain structures exhibit similar stimulus-driven responses across individuals.
@@
 Topic models are essentially an extension of those early models, in that they attempt to explicitly model the underlying causes of word co-occurrences by automatically identifying the set of themes or topics reflected across the documents in the corpus.
-More recent work on these types of semantic models, including word2vec~\citep{MikoEtal13a}, the Universal Sentence Encoder~\citep{CerEtal18}, GPT-2~\citep{RadfEtal19}, and GTP-3~\citep{BrowEtal20} use deep neural networks to attempt to identify the deeper conceptual representations underlying each word.
+More recent work on these types of semantic models, including word2vec~\citep{MikoEtal13a}, the Universal Sentence Encoder~\citep{CerEtal18}, and Generative Pre-trained Transformers (e.g., GPT-2~\citep{RadfEtal19} and GTP-3~\citep{BrowEtal20}) use deep neural networks to attempt to identify the deeper conceptual representations underlying each word.
 Despite the growing popularity of these sophisticated deep learning-based embedding models, we chose to prioritize interpretability of the embedding dimensions (e.g., Fig.~\ref{fig:topics}) over raw performance (e.g., with respect to some predefined benchmark).
@@
 \subsection*{Paradigm and data collection}
-Data were collected by \citeauthor{ChenEtal17}~\citep{ChenEtal17}.
+Data were collected by Chen et al.
+(2017)~\citep{ChenEtal17}.
 In brief, participants ($n=22$) viewed the first 48 minutes of ``A Study in Pink,'' the first episode of the BBC television show \textit{Sherlock}, while fMRI volumes were collected (TR = 1500~ms).
@@
 The stimulus was divided into a 23~min (946~TR) and a 25~min (1030~TR) segment to mitigate technical issues related to the scanner.
-After finishing the clip, participants were instructed to \citep[quoting from][]{ChenEtal17} ``describe what they recalled of the [episode] in as much detail as they could, to try to recount events in the original order they were viewed in, and to speak for at least 10 minutes if possible but that longer was better.
+After finishing the clip, participants were instructed to ``describe what they recalled of the [episode] in as much detail as they could, to try to recount events in the original order they were viewed in, and to speak for at least 10 minutes if possible but that longer was better.
 They were told that completeness and detail were more important than temporal order, and that if at any point they realized they had missed something, to return to it.
-Participants were then allowed to speak for as long as they wished, and verbally indicated when they were finished (e.g., `I’m done').''  Five participants were dropped from the original dataset due to excessive head motion (2 participants), insufficient recall length (2 participants), or falling asleep during stimulus viewing (1 participant), resulting in a final sample size of $n=17$.
-For additional details about the testing procedures and scanning parameters, see \cite{ChenEtal17}.
+Participants were then allowed to speak for as long as they wished, and verbally indicated when they were finished (e.g., `I’m done').''~\citep{ChenEtal17}  Five participants were dropped from the original dataset due to excessive head motion (2 participants), insufficient recall length (2 participants), or falling asleep during stimulus viewing (1 participant), resulting in a final sample size of $n=17$.
+For additional details about the testing procedures and scanning parameters, see Chen et al.
+(2017)~\cite{ChenEtal17}.
 The testing protocol was approved by Princeton University's Institutional Review Board.
@@
 This included a constant 3 TR (4.5~s) shift to account for the lag in the hemodynamic response.
-\citep[All of these preprocessing steps followed][where additional details may be found.]{ChenEtal17}
-
-The video stimulus was divided into 1,000 fine-grained ``time segments'' and annotated by an independent coder.
-For each of these 1,000 annotations, the following information was recorded: a brief narrative description of what was happening, the location where the time segment took place, whether that location was indoors or outdoors, the names of all characters on-screen, the name(s) of the character(s) in focus in the shot, the name(s) of the character(s) currently speaking, the camera angle of the shot, a transcription of any text appearing on-screen, and whether or not there was music present in the background.
+All of these preprocessing steps followed Chen et al.
+(2017)~\citep{ChenEtal17}, where additional details may be found.
+
+The video stimulus was divided into 1000 fine-grained ``time segments'' and annotated by an independent coder.
+For each of these 1000 annotations, the following information was recorded: a brief narrative description of what was happening, the location where the time segment took place, whether that location was indoors or outdoors, the names of all characters on-screen, the name(s) of the character(s) in focus in the shot, the name(s) of the character(s) currently speaking, the camera angle of the shot, a transcription of any text appearing on-screen, and whether or not there was music present in the background.
 Each time segment was also tagged with its onset and offset time, in both seconds and TRs.
@@
 \subsubsection*{Topic modeling}
-The input to the topic model we trained to characterize the dynamic content of the episode comprised 998 hand-generated annotations of short (mean: 2.96s) time segments spanning the video clip~(\citealp{ChenEtal17} generated 1000 annotations total; we removed two annotations referring to a break between the first and second scan sessions, during which no fMRI data were collected).
-We concatenated the text for all of the annotated features within each segment, creating a ``bag of words'' describing its content and performed some minor preprocessing (e.g., stemming possessive nouns and removing punctuation).
+The input to the topic model we trained to characterize the dynamic content of the episode comprised 998 hand-generated annotations of short (mean: 2.96s) time segments spanning the video clip~(Chen et al., 2017~\citep{ChenEtal17} generated 1000 annotations total; we removed two annotations referring to a break between the first and second scan sessions, during which no fMRI data were collected).
+We concatenated the text for all of the annotated features within each segment, creating a ``bag of words'' describing its content, and performed some minor preprocessing (e.g., stemming possessive nouns and removing punctuation).
 We then re-organized the text descriptions into overlapping sliding windows spanning (up to) 50 annotations each.
@@
 
-We trained our model using these overlapping text samples with \texttt{scikit-learn}~\citep[version 0.19.1; ][]{PedrEtal11}, called from our high-dimensional visualization and text analysis software, \texttt{HyperTools}~\citep{HeusEtal18a}.
+We trained our model using these overlapping text samples with \texttt{scikit-learn} version 0.19.1~\citep{PedrEtal11}, called from our high-dimensional visualization and text analysis software, \texttt{HyperTools}~\citep{HeusEtal18a}.
 Specifically, we used the \texttt{CountVectorizer} class to transform the text from each window into a vector of word counts (using the union of all words across all annotations as the ``vocabulary,'' excluding English stop words); this yielded a number-of-windows by number-of-words ``word count'' matrix.
@@
 
-We created similar topic proportions matrices using hand-annotated transcripts of each participant's verbal recall of the episode~\citep[annotated by][]{ChenEtal17}.
+We created similar topic proportions matrices using hand-annotated transcripts of each participant's verbal recall of the episode~\citep{ChenEtal17}.
 We tokenized the transcript into a list of sentences, and then re-organized the list into overlapping sliding windows spanning (up to) 10 sentences each, analogously to how we parsed the episode annotations.
@@
 These reflected the dynamic content of each participant's recalls.
-Note: for details on how we selected the episode and recall window lengths and number of topics, see \textit{Supplementary Information} and Supplementary Figure~\topicopt.
+For details on how we selected the episode and recall window lengths and number of topics, see \textit{Supplementary Information} and Supplementary Figure~\topicopt.
 
 \subsubsection*{Segmenting topic proportions matrices into discrete events using hidden Markov Models}
-We parsed the topic proportions matrices of the episode and participants' recalls into discrete events using hidden Markov Models~\citep[HMMs;][]{Rabi89}.
+We parsed the topic proportions matrices of the episode and participants' recalls into discrete events using hidden Markov Models (HMMs)~\citep{Rabi89}.
 Given the topic proportions matrix (describing the mix of topics at each timepoint) and a number of states, $K$, an HMM recovers the set of state transitions that segments the timeseries into $K$ discrete states.
-Following \cite{BaldEtal17}, we imposed an additional set of constraints on the discovered state transitions that ensured that each state was encountered exactly once (i.e., never repeated).
+Following Baldassano et al.
+(2017)~\cite{BaldEtal17}, we imposed an additional set of constraints on the discovered state transitions that ensured that each state was encountered exactly once (i.e., never repeated).
 We used the \texttt{BrainIAK} toolbox~\citep{Brainiak} to implement this segmentation.
@@
 We used an optimization procedure to select the appropriate $K$ for each topic proportions matrix.
-Prior studies on narrative structure and processing have shown that we both perceive and internally represent the world around us at multiple, hierarchical timescales \citep[e.g.,][]{HassEtal08, LernEtal11, HassEtal15, ChenEtal17, BaldEtal17, BaldEtal18}.
-However, for the purposes of our framework, we sought to identify the single timeseries of event-representations that is emphasized most heavily in the temporal structure of the episode and of each participant's recall.
+Prior studies on narrative structure and processing have shown that we both perceive and internally represent the world around us at multiple, hierarchical timescales~\citep{HassEtal08, LernEtal11, HassEtal15, ChenEtal17, BaldEtal17, BaldEtal18}.
+However, for the purposes of our framework, we sought to identify the single timeseries of event representations that was emphasized most heavily in the temporal structure of the episode and of each participant's recall.
 We quantified this as the set of $K$ states that maximized the similarity between topic vectors for timepoints comprising each state, while minimizing the similarity between topic vectors for timepoints across different states.
@@
 where $a$ was the distribution of within-state topic vector correlations, and $b$ was the distribution of across-state topic vector correlations .
-We computed the first Wasserstein distance~\citep[$W_{1}$; also known as ``Earth mover's distance'';][]{Dobr70, RamdEtal17} between these distributions for a large range of possible $K$-values (range [2, 50]), and selected the $K$ that yielded the maximum value.
+We computed the first Wasserstein distance ($W_{1}$, also known as ``Earth mover's distance''~\citep{Dobr70, RamdEtal17}) between these distributions for a large range of possible $K$-values (range [2, 50]), and selected the $K$ that yielded the maximum value.
 Figure~\ref{fig:model}B displays the event boundaries returned for the episode, and Supplementary Figure~\corrmats~displays the event boundaries returned for each participant's recalls.
@@
 Perhaps the simplest and most widely used measure of memory performance is ``accuracy''---i.e., the proportion of studied (experienced) items (in this case, episode events) that the participant later remembered.
-\cite{ChenEtal17} used this method to rate each participant's memory quality by computing the proportion of (50, manually identified) scenes mentioned in their recall.
+Chen et al.
+(2017)~\cite{ChenEtal17} used this method to rate each participant's memory quality by computing the proportion of (50 manually identified) scenes mentioned in their recall.
 We found a strong across-participants correlation between these independent ratings and the proportion of 30 HMM-identified episode events matched to participants' recalls (Pearson's $r(15) = 0.71, p = 0.002$).
@@
 Finally, we averaged over the rows of the matrix, resulting in a 1 by 30 array representing the proportion of participants that recalled an event first, as a function of the order of the event's appearance in the episode (Fig.~\ref{fig:list-learning}A).
-% ------ NOTE: ------
-% reiterate meaning of error ribbons in list-learning figure? (already noted in figure caption)
-% - Paxton
-
-\paragraph{Lag conditional probability curve (lag-CRP).} The lag-CRP curve~\citep{Kaha96} reflects the probability of recalling a given item after the just-recalled item, as a function of their relative encoding positions (or \textit{lag}).
+
+\paragraph{Lag conditional probability curve (lag-CRP).} The lag-CRP curve~\citep{Kaha96} reflects the probability of recalling a given item after the just-recalled item, as a function of their relative encoding positions (lag).
 In other words, a lag of 1 indicates that a recalled item was presented immediately after the previously recalled item, and a lag of -3 indicates that a recalled item came 3 items before the previously recalled item.
@@
 We used the UMAP algorithm~\citep{McInEtal18} to project the 100-dimensional topic space onto a two-dimensional space for visualization (Figs.~\ref{fig:trajectory}, \ref{fig:topics}).
-To ensure that all of the trajectories were projected onto the same lower dimensional space, we computed the low-dimensional embedding on a ``stacked'' matrix created by vertically concatenating the events-by-topics topic proportions matrices for the episode, across-participants average recall and all 17 individual participants' recalls.
-We then separated the rows of the result (a total-number-of-events by two matrix) back into individual matrices for the episode topic trajectory, across-participant average recall trajectory, and the trajectories for each individual participant's recalls (Fig.~\ref{fig:trajectory}).
-This general approach for discovering a shared low-dimensional embedding for a collections of high-dimensional observations follows \cite{HeusEtal18a}.
+To ensure that all of the trajectories were projected onto the same lower dimensional space, we computed the low-dimensional embedding on a ``stacked'' matrix created by vertically concatenating the events-by-topics topic proportions matrices for the episode, the across-participants average recalls and all 17 individual participants' recalls.
+We then separated the rows of the result (a total-number-of-events by two matrix) back into individual matrices for the episode topic trajectory, the across-participant average recall trajectory, and the trajectories for each individual participant's recalls (Fig.~\ref{fig:trajectory}).
+This general approach for discovering a shared low-dimensional embedding for a collections of high-dimensional observations follows our prior work on manifold learning~\cite{HeusEtal18a}.
 
@@
 \subsubsection*{Estimating the consistency of flow through topic space across participants}
-In Figure~\ref{fig:trajectory}B, we present an analysis aimed at characterizing locations in topic space that different participants move through in a consistent way (via their recall topic trajectories).
+In Figure~\ref{fig:trajectory}B, we present an analysis aimed at characterizing locations in topic space that different participants move through in a consistent way (via their recall topic trajectories; also see Supp.\ Fig.~\arrows).
 The two-dimensional topic space used in our visualizations (Fig.~\ref{fig:trajectory}) comprised a $60 \times 60$ (arbitrary units) square.
@@
 In Figure~\ref{fig:brainz}, we present two analyses aimed at identifying brain regions whose responses (as participants viewed the episode) exhibited a particular temporal structure.
-We developed a searchlight analysis wherein we constructed a $5 \times 5 \times 5$ cube of voxels~\citep[following][]{ChenEtal17} centered on each voxel in the brain, and for each of these cubes, computed the temporal correlation matrix of the voxel responses during episode viewing.
+We developed a searchlight analysis wherein we constructed a $5 \times 5 \times 5$ cube of voxels centered on each voxel in the brain~\citep{ChenEtal17}, and for each of these cubes, computed the temporal correlation matrix of the voxel responses during episode viewing.
 Specifically, for each of the 1976 volumes collected during episode viewing, we correlated the activity patterns in the given cube with the activity patterns (in the same cube) collected during every other timepoint.
 This yielded a $1976 \times 1976$ correlation matrix for each cube.
-Note: participant 5's scan ended 75s early, and in~\cite{ChenEtal17}'s publicly released dataset, their scan data was zero-padded to match the length of the other participants'.
+Note: participant 5's scan ended 75s early, and in Chen et al.
+(2017)~\cite{ChenEtal17}'s publicly released dataset, their scan data was zero-padded to match the length of the other participants'.
 For our searchlight analyses, we removed this padded data (i.e., the last 50 TRs), resulting in a $1925 \times 1925$ correlation matrix for each cube in participant 5's brain.
@@
 To construct the episode template, we computed the correlations between the topic proportions estimated for every pair of TRs (prior to segmenting the topic proportions matrices into discrete events; i.e., the correlation matrix shown in Figs.~\ref{fig:model}B and \ref{fig:brainz}A).
-We constructed similar temporal correlation matrices for each participant's recall topic proportions matrix (Fig.~\ref{fig:model}D, Supp.
-Fig.~\corrmats).
+We constructed similar temporal correlation matrices for each participant's recall topic proportions matrix (Fig.~\ref{fig:model}D, Supp.\ Fig.~\corrmats).
 However, to correct for length differences and potential non-linear transformations between viewing time and recall time, we first used dynamic time warping~\citep{BernClif94} to temporally align participants' recall topic proportions matrices with the episode topic proportions matrix.
@@
 By nature, these two attributes give rise to similarities in activity across large timescales that may not necessarily reflect a single task.
-To enable a more sensitive analysis of brain regions whose shifts in activity patterns mirrored shifts in the semantic content of the episode or recalls, we restricted the temporal correlations we considered to the timescale of semantic information captured by our model.
+To identify brain regions whose shifts in activity patterns mirrored shifts in the semantic content of the episode or recalls, we restricted the temporal correlations we considered to the timescale of semantic information captured by our model.
 Specifically, we isolated the upper triangle of the episode correlation matrix and created a ``proximal correlation mask'' that included only diagonals from the upper triangle of the episode correlation matrix up to the first diagonal that contained no positive correlations.
@@
 \subsection*{Neurosynth decoding analyses}
-\texttt{Neurosynth} parses a massive online database of over 14,000 neuroimaging studies and constructs meta-analysis images for over 13,000 psychology- and neuroscience-related terms, based on NIfTI images accompanying studies where those terms appear at a high frequency.
+\texttt{Neurosynth}~\citep{YarkEtal11} parses a massive online database of over 14000 neuroimaging studies and constructs meta-analysis images for over 13000 psychology- and neuroscience-related terms, based on NIfTI images accompanying studies where those terms appear at a high frequency.
 Given a novel image (tagged with its value type; e.g., $z$-, $t$-, $F$- or $p$-statistics), \texttt{Neurosynth} returns a list of terms whose meta-analysis images are most similar.
@@
 %\bibliography{CDL-bibliography/memlab}
+
 \begin{thebibliography}{10}
@@
 
+\bibitem{MannKaha12}
+\bibinfo{author}{Manning, J.~R.} \& \bibinfo{author}{Kahana, M.~J.}
+\newblock \bibinfo{title}{Interpreting semantic clustering effects in free
+  recall}.
+\newblock \emph{\bibinfo{journal}{Memory}} \textbf{\bibinfo{volume}{20}},
+  \bibinfo{pages}{511--517} (\bibinfo{year}{2012}).
+
 \bibitem{HeusEtal18a}
@@
 \section*{Acknowledgements}
-We thank Luke Chang, Janice Chen, Chris Honey, Lucy Owen, Emily Whitaker, and Kirsten Ziman for feedback and scientific discussions.
-We also thank Janice Chen, Yuan Chang Leong, Kenneth Norman, and Uri Hasson for sharing the data used in our study.
+We thank Luke Chang, Janice Chen, Chris Honey, Caroline Lee, Lucy Owen, Emily Whitaker, Xinming Xu, and Kirsten Ziman for feedback and scientific discussions.
+We also thank Janice Chen, Yuan Chang Leong, Chris Honey, Chung Yong, Kenneth Norman, and Uri Hasson for sharing the data used in our study.
 Our work was supported in part by NSF EPSCoR Award Number 1632738.

### 2020-10-14 paper/main.tex
overwrote merge conflict

@@
 Chen et al.
-(2017) collected hand-annotated information about each of 1,000 (manually delineated) time segments spanning the roughly 50 minute video used in their study~\cite{ChenEtal17}.
+(2017) collected hand-annotated information about each of 1000 (manually delineated) time segments spanning the roughly 50 minute video used in their study~\cite{ChenEtal17}.
 Each annotation included: a brief narrative description of what was happening, the location where the action took place, the names of any characters on the screen, and other similar details (for a full list of annotated features, see \textit{Methods}).

### 2020-10-14 paper/old.tex
overwrote merge conflict

@@
 \newcommand{\featureimportance}{S3}
-\newcommand{\listlearning}{S4}
-\newcommand{\corrmats}{S5}
-\newcommand{\matchmats}{S6}
+\newcommand{\corrmats}{S4}
+\newcommand{\matchmats}{S5}
+\newcommand{\kopt}{S6}
 
@@
 
-\title{How is experience transformed into memory?}
+\title{Geometric models reveal behavioral and neural signatures of transforming naturalistic experiences into episodic memories}
+
 \author{Andrew C.
-Heusser, Paxton C.
-Fitzpatrick, and Jeremy R.
-Manning\\Department of Psychological and Brain Sciences\\Dartmouth College, Hanover, NH 03755, USA\\Corresponding author: jeremy.r.manning@dartmouth.edu}
+Heusser\textsuperscript{1, 2, \textdagger}, Paxton C.
+Fitzpatrick\textsuperscript{1, \textdagger}, and Jeremy R.
+Manning\textsuperscript{1, *}\\\textsuperscript{1}Department of Psychological and Brain Sciences\\Dartmouth College, Hanover, NH 03755, USA\\\textsuperscript{2}Akili Interactive Labs\\Boston, MA 02110\\\textsuperscript{\textdagger}Denotes equal contribution\\\textsuperscript{*}Corresponding author: Jeremy.R.Manning@Dartmouth.edu}
 
@@
 \begin{document}
+\begin{titlepage}
   \maketitle
+  \thispagestyle{empty}
+  \end{titlepage}
 
 \begin{abstract}
-The ways our experiences unfold over time define unique \textit{trajectories} through the relevant representational spaces.
-Within this geometric framework, one can compare the shape of the trajectory formed by an experience to that defined by our later remembering of that experience.
-We propose a framework for mapping naturalistic experiences onto geometric spaces that characterize how they unfold over time.
-We apply this approach to a naturalistic memory experiment which had participants view and recount a video.
-We found that the shapes of the trajectories formed by participants' recountings were all highly similar to that of the original video, but participants differed in the level of detail they remembered.
-We also identified a network of brain structures that are sensitive to the ``shapes'' of our ongoing experiences, and an overlapping network that is sensitive to how we will later remember those experiences.
+The mental contexts in which we interpret experiences are often person-specific, even when the experiences themselves are shared.
+We developed a geometric framework for mathematically characterizing the subjective conceptual content of dynamic naturalistic experiences.
+We model experiences and memories as \textit{trajectories} through word embedding spaces whose coordinates reflect the universe of thoughts under consideration.
+Memory encoding can then be modeled as geometrically preserving or distorting the \textit{shape} of the original experience.
+We applied our approach to data collected as participants watched and verbally recounted a television episode while undergoing functional neuroimaging.
+Participants’ recountings all preserved coarse spatial properties (essential narrative elements), but not fine spatial scale (low-level) details, of the episode’s trajectory.
+We also identified networks of brain structures sensitive to these trajectory shapes.
+Our work provides insights into how we preserve and distort our ongoing experiences when we encode them into episodic memories.
 \end{abstract}
@@
 \section*{Introduction}
+What does it mean to \textit{remember} something?
+In traditional episodic memory experiments \citep[e.g., list-learning or trial-based experiments;][]{Murd62a, Kaha96}, remembering is often cast as a discrete, binary operation: each studied item may be separated from the rest of one's experience and labeled as having been either recalled or forgotten.
+More nuanced studies might incorporate self-reported confidence measures as a proxy for memory strength, or ask participants to discriminate between recollecting the (contextual) details of an experience and having a general feeling of familiarity~\citep{Yone02}.
+Using well-controlled, trial-based experimental designs, the field has amassed a wealth of information regarding human episodic memory~\citep[for review see][]{Kaha12}.
+However, there are fundamental properties of the external world and our memories that trial-based experiments are not well suited to capture~\citep[for review, also see][]{KoriGold94, HukEtal18}.
+First, our experiences and memories are continuous, rather than discrete---isolating a naturalistic event from the context in which it occurs can substantially change its meaning.
+Second, whether or not the rememberer has precisely reproduced a specific set of words in describing a given experience is nearly orthogonal to how well they were actually able to remember it.
+In classic (e.g., list-learning) memory studies, by contrast, the number or proportion of \textit{exact} recalls is often considered to be a primary metric for assessing the quality of participants' memories.
+Third, one might remember the essence (or a general summary) of an experience but forget (or neglect to recount) particular low-level details.
+Capturing the essence of what happened is often a main goal of recounting an episodic memory to a listener, whereas the inclusion of specific low-level details is often less pertinent.
 
-What does it mean to \textit{remember} something?
-In traditional episodic memory experiments \citep[e.g., list-learning or trial-based experiments;][]{Murd62a, Kaha96}, remembering is often cast as a discrete and binary operation: each studied item may be separated from the rest of one's experiences, and that item may be labeled as having been recalled versus forgotten.
-More nuanced studies might incorporate self-reported confidence measures as a proxy for memory strength, or ask participants to discriminate between ``recollecting'' the (contextual) details of an experience or having a general feeling of ``familiarity'' \citep{Yone02}.
-However, characterizing and evaluating memory in more realistic contexts (e.g., recounting a recent experience to a friend) is fundamentally different in at least three ways~\citep[for review also see][]{KoriGold94, HukEtal18}.
-First, real world recall is continuous, rather than discrete.
-Unlike in trial-based experiments, removing a (naturalistic) event from the context in which it occurs can substantially change its meaning.
-Second, the specific words used to describe an experience have little bearing on whether the experience should be considered to have been ``remembered.''  Asking whether the rememberer has precisely reproduced a specific set of words to describe a given experience is nearly orthogonal to whether they were actually able to remember it.
-In classic (e.g., list-learning) memory studies, by contrast, counting the number or proportion of precise recalls is often a primary metric of assessing the quality of participants' memories.
-Third, one might remember the \textit{gist} or essence of an experience but forget (or neglect to recount) particular details.
-Capturing the gist of what happened is typically the main ``point'' of recounting a memory to a listener whereas, depending on the circumstances, accurate recall of any specific detail may be irrelevant.
-There is no analog of the gist of an experience in most traditional memory experiments; rather we tend to assess participants' abilities to recover specific details (e.g., computing the proportion of specific stimuli they remember, which presentation positions the remembered stimuli came from, etc.).
+How might we formally characterize the \textit{essence} of an experience, and whether it has been recovered by the rememberer?
+And how might we distinguish an experience's overarching essence from its low-level details?
+One approach is to start by considering some fundamental properties of the dynamics of our experiences.
+Each given moment of an experience tends to derive meaning from surrounding moments, as well as from longer-range temporal associations~\citep{LernEtal11, Mann19, Mann20}.
+Therefore, the timecourse describing how an event unfolds is fundamental to its overall meaning.
+Further, this hierarchy formed by our subjective experiences at different timescales defines a \textit{context} for each new moment~\citep[e.g.,][]{HowaKaha02a, HowaEtal14}, and plays an important role in how we interpret that moment and remember it later~\citep[for review see][]{MannEtal15, Mann20}.
+Our memory systems can leverage these associations to form predictions that help guide our behaviors~\citep{RangRitc12}.
+For example, as we navigate the world, the features of our subjective experiences tend to change gradually (e.g., the room or situation we find ourselves in at any given moment is strongly temporally autocorrelated), allowing us to form stable estimates of our current situation and behave accordingly~\citep{ZackEtal07, ZwaaRadv98}.
 
-How might one go about formally characterizing the gist of an experience, or whether that gist has been recovered by the rememberer?
-Any given moment of an experience derives meaning from surrounding moments, as well as from longer-range temporal associations~\citep[e.g., ][]{LernEtal11}.
-Therefore the timecourse describing how an event unfolds is fundamental to its overall meaning.
-Further, this hierarchy formed by our subjective experiences at different timescales defines a \textit{context} for each new moment~\citep[e.g., ][]{HowaKaha02, HowaEtal14}, and plays an important role in how we interpret that moment and remember it later~\citep[for review see][]{MannEtal15}.
-Our memory systems can then leverage these associations to form predictions that help guide our behaviors~\citep{RangRitc12}.
-For example, as we navigate the world, the features of our subjective experiences tend to change gradually (e.g., the room or situation we are in is strongly temporally autocorrelated), allowing us to form stable estimates of our current situation and behave accordingly~\citep{ZackEtal07, ZwaaRadv98}.
-Although our experiences most often change gradually, they also occasionally change suddenly~\citep[e.g., when we walk through a doorway; ][]{RadvZack17}.
-Prior research suggests that these sharp transitions (termed \textit{event boundaries}) during an experience help to discretize our experiences into \textit{events}~\citep{RadvZack17, BrunEtal18, HeusEtal18b, ClewDava17, EzzyDava11, DuBrDava13}.
-The interplay between the stable (within event) and transient (across event) temporal dynamics of an experience also provides a potential framework for transforming experiences into memories that distill those experiences down to their essence-- i.e., their gists.
+Occasionally, this gradual drift of our ongoing experience is punctuated by sudden changes, or shifts~\citep[e.g., when we walk through a doorway;][]{RadvZack17}.
+Prior research suggests that these sharp transitions (termed \textit{event boundaries}) help to discretize our experiences (and their mental representations) into \textit{events}~\citep{RadvZack17, BrunEtal18, HeusEtal18b, ClewDava17, EzzyDava11, DuBrDava13}.
+The interplay between the stable (within-event) and transient (across-event) temporal dynamics of an experience also provides a potential framework for transforming experiences into memories that distills those experiences down to their essences.
 For example, prior work has shown that event boundaries can influence how we learn sequences of items~\citep{HeusEtal18b, DuBrDava13}, navigate~\citep{BrunEtal18}, and remember and understand narratives~\citep{ZwaaRadv98, EzzyDava11}.
+This work also suggests a means of distinguishing the essence of an experience from its low-level details:  The overall structure of events and event transitions reflects how the high-level experience unfolds (i.e., its essence), while subtler event-level properties reflect its low-level details.
+Prior research has also implicated a network of brain regions (including the hippocampus and the medial prefrontal cortex) in playing a critical role in transforming experiences into structured and consolidated memories ~\citep{TompDava17}.
 
-Here we sought to examine how the temporal dynamics of a ``naturalistic'' experience were reflected in participants' later memories of that experience.
-We analyzed an open dataset that comprised behavioral and functional Magnetic Resonance Imaging (fMRI) data collected as participants viewed and then verbally recalled an episode of the BBC television series \textit{Sherlock}~\citep{ChenEtal17}.
+Here, we sought to examine how the temporal dynamics of a naturalistic experience were later reflected in participants' memories.
+We also sought to leverage the above conceptual insights into the distinctions between an experience's essence and its low-level details to build models that explicitly quantified these distinctions.
+We analyzed an open dataset that comprised behavioral and functional Magnetic Resonance Imaging (fMRI) data collected as participants viewed and then verbally recounted an episode of the BBC television show \textit{Sherlock}~\citep{ChenEtal17}.
 We developed a computational framework for characterizing the temporal dynamics of the moment-by-moment content of the episode and of participants' verbal recalls.
-Specifically, we use topic modeling~\citep{BleiEtal03} to characterize the thematic conceptual (semantic) content present in each moment of the episode and recalls, and we use Hidden Markov Models~\citep{Rabi89, BaldEtal17} to discretize the evolving semantic content into events.
-In this way, we cast naturalistic experiences (and recalls of those experiences) as \textit{topic trajectories} that describe how the experiences evolve over time.
-In other words, the episode's topic trajectory is a formalization of its gist.
-Under this framework, successful remembering entails verbally ``traversing'' the topic trajectory of the original episode, thereby reproducing the original episode's gist.
-In addition, comparing the shapes of the topic trajectories of the original episode and of participants' retellings of the episode reveals which aspects of the episode were preserved (or lost) in the translation into memory.
-We also identified a network of brain structures whose responses (as participants watched the episode) reflected the gist of the episode, and a second network whose responses reflected how participants would later recount the episode.
+Our framework uses topic modeling~\citep{BleiEtal03} to characterize the thematic conceptual (semantic) content present in each moment of the episode and recalls by projecting each moment into a word embedding space.
+We then use hidden Markov models~\citep{Rabi89, BaldEtal17} to discretize this evolving semantic content into events.
+In this way, we cast both naturalistic experiences and memories of those experiences as geometric \textit{trajectories} through word embedding space that describe how they evolve over time.
+Under this framework, successful remembering entails verbally traversing the content trajectory of the episode, thereby reproducing the shape (essence) of the original experience.
+Our framework captures the episode's essence in the sequence of geometric coordinates for its events, and its low-level details by examining its within-event geometric properties.
+
+Comparing the overall shapes of the topic trajectories for the episode and participants' recalls reveals which aspects of the episode's essence were preserved (or lost) in the translation into memory.
+We also develop two metrics for assessing participants' memories for low-level details: (1) the \textit{precision} with which a participant recounts details about each event, and (2) the \textit{distinctiveness} of their recall for each event, relative to other events.
+We examine how these metrics relate to overall memory performance as judged by third-party human annotators.
+We also compare and contrast our general approach to studying memory for naturalistic experiences with standard metrics for assessing performance on more traditional memory tasks, such as list-learning.
+Last, we leverage our framework to identify networks of brain structures whose responses (as participants watched the episode) reflected the temporal dynamics of the episode and/or how participants would later recount it.
 
 \section*{Results}
-To characterize the gists of the \textit{Sherlock} episode participants watched and their subsequent recountings of the episode, we used a topic model~\citep{BleiEtal03} to discover the latent thematic content in the video.
-Topic models take as inputs a vocabulary of words to consider and a collection of text documents; they return as output two matrices.
-The first output is a \textit{topics matrix} whose rows are topics (latent themes) and whose columns correspond to words in the vocabulary.
-The entries of the topics matrix define how each word in the vocabulary is weighted by each discovered topic.
-For example, a detective-themed topic might weight heavily on words like ``crime,'' and ``search.''  The second output is a \textit{topic proportions matrix}, with one row per document and one column per topic.
-The topic proportions matrix describes which mix topics is reflected in each document.
+To characterize the dynamic content of the \textit{Sherlock} episode and participants' subsequent recountings, we used a topic model~\citep{BleiEtal03} to discover the episode's latent themes.
+Topic models take as inputs a vocabulary of words to consider and a collection of text documents, and return two output matrices.
+The first of these is a \textit{topics matrix} whose rows are \textit{topics} (or latent themes) and whose columns correspond to words in the vocabulary.
+The entries in the topics matrix reflect how each word in the vocabulary is weighted by each discovered topic.
+For example, a detective-themed topic might weight heavily on words like ``crime,'' and ``search.''  The second output is a \textit{topic proportions matrix} with one row per document and one column per topic.
+The topic proportions matrix describes the mixture of discovered topics reflected in each document.
 
-\cite{ChenEtal17} collected hand-annotated information about each of 1000 (manually identified) scenes spanning the roughly 45 minute video used in their experiment.
-This information included: a brief narrative description of what was happening; whether the scene took place indoors vs.
-outdoors; names of any characters on the screen; names of any characters who were in focus in the camera shot; names of characters who were speaking; the location where the scene took place; the camera angle (close up, medium, long, etc.); whether or not background music was present; and other similar details (for a full list of annotated features see \textit{Methods}).
-We took from these annotations the union of all unique words (excluding stop words, such as ``and,'' ``or,'' ``but,'' etc.) across all features and scenes as the ``vocabulary'' for the topic model.
-We then concatenated the sets of words across all features contained in overlapping 50-scene sliding windows, and treated each 50-scene sequence as a single ``document'' for the purposes of fitting the topic model.
+\cite{ChenEtal17} collected hand-annotated information about each of 1,000 (manually delineated) time segments spanning the roughly 50 minute video used in their study.
+Each annotation included: a brief narrative description of what was happening, the location where the action took place, the names of any characters on the screen, and other similar details (for a full list of annotated features, see \textit{Methods}).
+We took the union of all unique words (excluding stop words, such as ``and,'' ``or,'' ``but,'' etc.) across all features from all annotations as the vocabulary for the topic model.
+We then concatenated the sets of words across all features contained in overlapping sliding windows of (up to) 50 annotations, and treated each window as a single document for the purpose of fitting the topic model.
 Next, we fit a topic model with (up to) $K = 100$ topics to this collection of documents.
-We found that 27 unique topics (with non-zero weights) were sufficient to describe the time-varying content of the video (see \textit{Methods}; Figs.~\ref{fig:schematic}, \topics).
-Note that our approach is similar in some respects to Dynamic Topic Models~\citep{BleiLaff06}, in that we sought to characterize how the thematic content of the episode evolved over time.
+We found that 32 unique topics (with non-zero weights) were sufficient to describe the time-varying content of the episode (see \textit{Methods}; Figs.~\ref{fig:schematic}, \topics).
+We note that our approach is similar in some respects to Dynamic Topic Models~\citep{BleiLaff06} in that we sought to characterize how the thematic content of the episode evolved over time.
 However, whereas Dynamic Topic Models are designed to characterize how the properties of \textit{collections} of documents change over time, our sliding window approach allows us to examine the topic dynamics within a single document (or video).
-Specifically, our approach yielded (via the topic proportions matrix) a single \textit{topic vector} for each timepoint of the episode (we set timepoints to match the acquisition times of the 1976 fMRI volumes collected as participants viewed the episode).
+Specifically, our approach yielded (via the topic proportions matrix) a single \textit{topic vector} for each sliding window of annotations transformed by the topic model.
+We then stretched (interpolated) the resulting windows-by-topics matrix to match the time series of the 1,976 fMRI volumes collected as participants viewed the episode.
 
@@
 \includegraphics[width=1\textwidth]{figs/schematic}
-\caption{\small \textbf{Methods overview.} We used hand-annotated descriptions of each moment of video to fit a topic model.
-Three example video frames and their associated descriptions are displayed (top two rows).
-Participants later recalled the video (in the third row, we show example recalls of the same three scenes from participant 13).
-We used the topic model (fit to the annotations) to estimate topic vectors for each moment of video and each sentence the participants recalled.
-Example topic vectors are displayed in the bottom row (blue: video annotations; green: example participant's recalls).
-Three topic dimensions are shown (the highest-weighted topics for each of the three example scenes, respectively).
-We also show the ten highest-weighted words for each topic.
+\caption{\small \textbf{Topic weights in episode and recall content.} We used detailed, hand-generated annotations describing each manually identified time segment from the episode to fit a topic model.
+Three example frames from the episode (first row) are displayed, along with their descriptions from the corresponding episode annotation (second row) and an example participant's recall transcript (third row).
+We used the topic model (fit to the episode annotations) to estimate topic vectors for each moment of the episode and each sentence of participants' recalls.
+Example topic vectors are displayed in the bottom row (blue: episode annotations; green: example participant's recalls).
+Three topic dimensions are shown (the highest-weighted topics for each of the three example scenes, respectively), along with the 10 highest-weighted words for each topic.
 Figure~\topics~provides a full list of the top 10 words from each of the discovered topics.}
@@
 
-The topics we found were heavily character-focused (e.g., the top-weighted word in each topic was nearly always a character) and could be roughly divided into themes that were primarily Sherlock Holmes-focused (Sherlock is the titular character); primarily John Watson-focused (John is Sherlock's close confidant and assistant); or that involved Sherlock and John interacting (Fig.~\topics).
-Several of the topics were highly similar, which we hypothesized might allow us to distinguish between subtle narrative differences (if the distinctions between those overlapping topics were meaningful; also see Fig.~\featureimportance).
-The topic vectors for each timepoint were \textit{sparse}, in that only a small number (usually one or two) of topics tended to be ``active'' in any given timepoint (Fig.~\ref{fig:model}A).
-Further, the dynamics of the topic activations appeared to exhibit \textit{persistance} (i.e., given that a topic was active in one timepoint, it was likely to be active in the following timepoint) along with \textit{occasional rapid changes} (i.e., occasionally topics would appear to spring into or out of existence).
-These two properties of the topic dynamics may be seen in the block diagonal structure of the timepoint-by-timepoint correlation matrix (Fig.~\ref{fig:model}B).
-Following \cite{BaldEtal17}, we used a Hidden Markov Model (HMM) to identify the \textit{event boundaries} where the topic activations changed rapidly (i.e., at the boundaries of the blocks in the correlation matrix; event boundaries identified by the HMM are outlined in yellow).
-Part of our model fitting procedure required selecting an appropriate number of ``events'' to segment the timeseries into.
-We used an optimization procedure to identify the number of events that maximized within-event stability while also minimizing across-event correlations (see \textit{Methods} for additional details).
-To create a stable ``summary'' of the video, we computed the average topic vector within each event (Fig.~\ref{fig:model}C).
+The 32 topics we found were heavily character-focused (i.e., the top-weighted word in each topic was nearly always a character) and could be roughly divided into themes centered around Sherlock Holmes (the titular character), John Watson (Sherlock's close confidant and assistant), supporting characters (e.g., Inspector Lestrade, Sergeant Donovan, or Sherlock's brother Mycroft), or the interactions between various groupings of these characters (Fig.~\topics).
+This likely follows from the frequency with which these terms appeared in the episode annotations.
+Several of the identified topics were highly similar, which we hypothesized might allow us to distinguish between subtle narrative differences if the distinctions between those overlapping topics were meaningful.
+The topic vectors for each timepoint were also \textit{sparse}, in that only a small number of topics (typically one or two) tended to be ``active'' in any given timepoint (Fig.~\ref{fig:model}A).
+Further, the dynamics of the topic activations appeared to exhibit \textit{persistence} (i.e., given that a topic was active in one timepoint, it was likely to be active in the following timepoint) along with \textit{occasional rapid changes} (i.e., occasionally topic weights would change abruptly from one timepoint to the next).
+These two properties of the topic dynamics may be seen in the block diagonal structure of the timepoint-by-timepoint correlation matrix (Fig.~\ref{fig:model}B) and reflect the gradual drift and sudden shifts fundamental to the temporal dynamics of many real-world experiences, as well as television episodes.
+Given this observation, we adapted an approach devised by \cite{BaldEtal17}, and used a hidden Markov model (HMM) to identify the \textit{event boundaries} where the topic activations changed rapidly (i.e., the boundaries of the blocks in the temporal correlation matrix; event boundaries identified by the HMM are outlined in yellow in Fig.~\ref{fig:model}B).
+Part of our model fitting procedure required selecting an appropriate number of events into which the topic trajectory should be segmented.
+To accomplish this, we used an optimization procedure that maximized the difference between the topic weights for timepoints within an event versus timepoints across multiple events (see \textit{Methods}).
+We then created a stable summary of the content within each episode event by averaging the topic vectors across the timepoints spanned by each event (Fig.~\ref{fig:model}C).
 
@@
 \includegraphics[width=\textwidth]{figs/eventseg}
-\caption{\small \textbf{Modelling naturalistic stimuli and recalls.} All panels: darker colors indicate greater values; range: [0, 1].
-\textbf{A.} Topic vectors ($K = 100$) for each of the 1976 video timepoints.
+\caption{\small \textbf{Modeling naturalistic stimuli and recalls.} All panels: darker colors indicate greater values; range: [0, 1].
+\textbf{A.} Topic vectors ($K = 100$) for each of the 1976 episode timepoints.
 \textbf{B.} Timepoint-by-timepoint correlation matrix of the topic vectors displayed in Panel A.
-Event boundaries detected by the HMM are denoted in yellow (34 events detected).
-\textbf{C.} Average topic vectors for each of the 34 video events.
-\textbf{D.} Topic vectors for each of 294 sentences spoken by an example participant while recalling the video.
+Event boundaries discovered by the HMM are denoted in yellow (30 events detected).
+\textbf{C.} Average topic vectors for each of the 30 episode events.
+\textbf{D.} Topic vectors for each of 265 sliding windows of sentences spoken by an example participant while recalling the episode.
 \textbf{E.} Timepoint-by-timepoint correlation matrix of the topic vectors displayed in Panel D.
-Event boundaries detected by the HMM are denoted in yellow (27 events detected).
-\textbf{F.} Average topic vectors for each of the 27 recalled events from the example participant.
-\textbf{G.} Correlations between the topic vectors for every pair of video events (Panel C) and recalled events (from the example participant; Panel F).
-For similar plots for all participants see Figure~\matchmats.
-\textbf{H.} Average correlations between each pair of video events and recalled events (across all 17 participants).
-To create the figure, each recalled event was assigned to the video event with the most correlated topic vector (yellow boxes in panels G and H).
-The heat maps in each panel were created using \texttt{Seaborn}~\citep{WaskEtal16}.}
+Event boundaries detected by the HMM are denoted in yellow (22 events detected).
+For similar plots for all participants, see Figure~\corrmats.
+\textbf{F.} Average topic vectors for each of the 22 recall events from the example participant.
+\textbf{G.} Correlations between the topic vectors for every pair of episode events (Panel C) and recall events (from the example participant; Panel F).
+For similar plots for all participants, see Figure~\matchmats.
+\textbf{H.} Average correlations between each pair of episode events and recall events (across all 17 participants).
+To create the figure, each recalled event was assigned to the episode event with the most correlated topic vector (yellow boxes in panels G and H).}
 \label{fig:model}
@@
 
-Given that the time-varying content of the video could be segmented cleanly into discrete events, we wondered whether participants' recalls of the video also displayed a similar structure.
-We applied the same topic model (already trained on the video annotations) to each participant's recalls.
-Analogous to how we analyzed the time-varying content of the video, to obtain similar estimates for participants' recalls, we treated each (overlapping) 10 sentence ``window'' of their transcript as a ``document'' and then computed the most probable mix of topics reflected in each timepoint's sentences.
-This yielded, for each participant, a number-of-sentences by number-of-topics topic proportions matrix that characterized how the topics identified in the original video were reflected in the participant's recalls.
-Note that an important feature of our approach is that it allows us to compare participant's recalls to events from the original video, despite that different participants may have used different language to describe the same event, and that those descriptions may not match the original annotations.
-This is a huge benefit of projecting the video and recalls into a shared ``topic'' space.
+Given that the time-varying content of the episode could be segmented cleanly into discrete events, we wondered whether participants' recalls of the episode also displayed a similar structure.
+We applied the same topic model (already trained on the episode annotations) to each participant's recalls.
+Analogously to how we parsed the time-varying content of the episode, to obtain similar estimates for each participant's recall transcript, we treated each overlapping  window of (up to) 10 sentences from their transcript as a document, and computed the most probable mix of topics reflected in each timepoint's sentences.
+This yielded, for each participant, a number-of-windows by number-of-topics topic proportions matrix that characterized how the topics identified in the original episode were reflected in the participant's recalls.
+An important feature of our approach is that it allows us to compare participants' recalls to events from the original episode, despite that different participants used widely varying language to describe the events, and that those descriptions often diverged in content, quality, and quantity from the episode annotations.
+This ability to match up conceptually related text that differs in specific vocabulary, detail, and length is an important benefit of projecting the episode and recalls into a shared topic space.
 An example topic proportions matrix from one participant's recalls is shown in Figure~\ref{fig:model}D.
 
-Although the example participant's recall topic proportions matrix has some visual similarity to the video topic proportions matrix, the time-varying topic proportions for the example participant's recalls are not as sparse as for the video (e.g., compare Figs.~\ref{fig:model}A and D).
-Similarly, although there do appear to be periods of stability in the recall topic dynamics (e.g., most topics are active or inactive over contiguous blocks of time), the overall timecourses are not as cleanly delineated as the video topics are.
-To examine these patterns in detail, we computed the timepoint-by-timepoint correlation matrix for the example participant's recall topic proportions (Fig.~\ref{fig:model}E).
-As in the video correlation matrix (Fig.~\ref{fig:model}B), the example participant's recall correlation matrix has a strong block diagonal structure, indicating that their recalls are discretized into separated events.
-As for the video correlation matrix, we can use an HMM, along with the aforementioned number-of-events optimization procedure (also see \textit{Methods}) to determine how many events are reflected in the participant's recalls and where specifically the event boundaries fall (outlined in yellow).
-We carried out a similar analysis on all 17 participants' recall topic proportions matrices (Fig.~\corrmats).
+Although the example participant's recall topic proportions matrix has some visual similarity to the episode topic proportions matrix, the time-varying topic proportions for the example participant's recalls are not as sparse as those for the episode (compare Figs.~\ref{fig:model}A and D).
+Similarly, although there do appear to be periods of stability in the recall topic dynamics (i.e., most topics are active or inactive over contiguous blocks of time), the changes in topic activations that define event boundaries appear less clearly delineated in participants' recalls than in the episode's annotations.
+To examine these patterns in detail, we computed the timepoint-by-timepoint correlation matrix for the example participant's recall topic proportions matrix (Fig.~\ref{fig:model}E).
+As in the episode correlation matrix (Fig.~\ref{fig:model}B), the example participant's recall correlation matrix has a strong block diagonal structure, indicating that their recalls are discretized into separated events.
+We used the same HMM-based optimization procedure that we had applied to the episode's topic proportions matrix (see \textit{Methods}) to estimate an analogous set of event boundaries in the participant's recounting of the episode (outlined in yellow).
+We carried out this analysis on all 17 participants' recall topic proportions matrices (Fig.~\corrmats).
 
@@
 First, although every individual participant's recalls could be segmented into discrete events (i.e., every individual participant's recall correlation matrix exhibited clear block diagonal structure; Fig.~\corrmats), each participant appeared to have a unique \textit{recall resolution}, reflected in the sizes of those blocks.
-For example, some participants' recall topic proportions segmented into just a few events (e.g., Participants P1, P4, and P15), while others' recalls segmented into many shorter duration events (e.g., Participants P12, P13, and P17).
-This suggests that different participants may be recalling the video with different levels of detail-- e.g., some might touch on just the major plot points, whereas others might attempt to recall every minor scene.
-The second clear pattern present in every individual participant's recall correlation matrix is that, unlike in the video correlation matrix, there are substantial off-diagonal correlations in participant's recalls.
-Whereas each event in the original video (was largely) separable from the others (Fig.~\ref{fig:model}B), in transforming those separable events into memory participants appear to be integrating \textit{across} different events, blending elements of previously recalled and not-yet-recalled events into each newly recalled event~\citep[Figs.~\ref{fig:model}D, \corrmats; also see][]{MannEtal11, HowaEtal12}.
+While some participants' recall topic proportions segmented into just a few events (e.g., Participants P4, P5, and P7), others' segmented into many shorter-duration events (e.g., Participants P12, P13, and P17).
+This suggests that different participants may be recalling the episode with different levels of detail---i.e., some might recount only high-level essential plot details, whereas others might recount low-level details instead (or in addition).
+The second clear pattern present in every individual participant's recall correlation matrix was that, unlike in the episode correlation matrix, there were substantial off-diagonal correlations.
+Whereas each event in the original episode was (largely) separable from the others (Fig.~\ref{fig:model}B), in transforming those separable events into memory, participants appeared to be integrating across multiple events, blending elements of previously recalled and not-yet-recalled content into each newly recalled event~\citep[Figs.~\ref{fig:model}E, \corrmats; also see][]{MannEtal11, HowaEtal12, Mann19}.
 
-The above results indicate that both the structure of the original video and participants' recalls of the video exhibit event boundaries that can be identified automatically by characterizing the dynamic content using a shared topic model and segmenting the content into events using HMMs.
-Next we asked whether some correspondence might be made between the specific content of the events the participants experienced in the video, and the events they later recalled.
-One approach to linking the experienced (video) and recalled events is to label each recalled event as matching the video event with the most similar (i.e., most highly correlated) topic vector (Figs.~\ref{fig:model}G, \matchmats).
-This yields a sequence of ``presented'' events from the original video, and a sequence of (potentially differently ordered) ``recalled'' events for each participant.
-Analogous to classic list-learning studies, we can then examine participants' recall sequences by asking which events they tended to recall first~\citep[probability of first recall; Fig.~\listlearning A;][]{WelcBurn24, PostPhil65, AtkiShif68}; how participants most often transition between recalls of the events as a function of the temporal distance between them~\citep[lag-conditional response probability; Fig.~\listlearning B;][]{Kaha96}; and which events they were likely to remember overall~\citep[serial position recall analyses; Fig.~\listlearning C;][]{Murd62a}.
-In list-learning studies, this set of three analyses may be used to gain a nearly complete view into the sequences of recalls participants made~\citep[e.g., ][]{Kaha12}.
-Extending these analyses to apply to naturalistic stimuli and recall~\citep{HeusEtal17b} highlights that, in naturalistic recall, these analyses provide a wholly incomplete picture: they leave out any attempt to quantify participants' abilities to capture the \textit{content} of what occurred in the video-- their only experimental instruction!
+The above results demonstrate that topic models capture the dynamic conceptual content of the episode and participants' recalls of the episode.
+Further, the episode and recalls exhibit event boundaries that can be identified automatically using HMMs to segment the dynamic content.
+Next, we asked whether some correspondence might be made between the specific content of the events the participants experienced while viewing the episode, and the events they later recalled.
+We labeled each recall event as matching the episode event with the most similar (i.e., most highly correlated) topic vector (Figs.~\ref{fig:model}G, \matchmats).
+This yielded a sequence of ``presented'' events from the original episode, and a (potentially differently ordered) sequence of ``recalled'' events for each participant.
+Analogous to classic list-learning studies, we can then examine participants' recall sequences by asking which events they tended to recall first~\citep[probability of first recall; Fig.~\ref{fig:list-learning}A;][]{AtkiShif68, PostPhil65, WelcBurn24}; how participants most often transitioned between recalls of the events as a function of the temporal distance between them~\citep[lag-conditional response probability; Fig.~\ref{fig:list-learning}B;][]{Kaha96}; and which events they were likely to remember overall~\citep[serial position recall analyses; Fig.~\ref{fig:list-learning}C;][]{Murd62a}.
+Some of the patterns we observed appeared to be similar to classic effects from the list-learning literature.
+For example, participants had a higher probability of initiating recall with early events (Fig.~\ref{fig:list-learning}A) and a higher probability of transitioning to neighboring events with an asymmetric forward bias (Fig.~\ref{fig:list-learning}B).
+However, unlike what is typically observed in list-learning studies, we did not observe patterns comparable to the primacy or recency serial position effects (Fig.~\ref{fig:list-learning}C).
+We hypothesized that participants might be leveraging meaningful narrative associations and references over long timescales throughout the episode.
 
-The dynamic content of the video and participants' recalls is quantified in the corresponding topic proportion matrices.
-However, it is difficult to gain deep insights into that content solely by examining the topic proportion matrices (e.g., Figs.~\ref{fig:model}A, D) or the corresponding correlation matrices (Figs.~\ref{fig:model}B, E, \corrmats).
-To visualize the time-varying high-dimensional content in a more intuitive way~\citep{HeusEtal18a} we projected the topic proportions matrices onto a two-dimensional space using Uniform Manifold Approximation and Projection~\citep[UMAP; ][]{McInHeal18}.
-In this lower-dimensional space, each point represents a single video or recall event, and the distances between the points reflect the distances between the events' associated topic vectors (Fig.~\ref{fig:trajectory}).
+Clustering scores are often used by memory researchers to characterize how people organize their memories of words on a studied list~\citep[for review, see][]{PolyEtal09}.
+We defined analogous measures to characterize how participants organized their memories for episodic events (see \textit{Methods} for details).
+Temporal clustering refers to the extent to which participants group their recall responses according to encoding position.
+Overall, we found that sequentially viewed episode events tended to appear nearby in participants' recall event sequences (mean clustering score: 0.732, SEM: 0.033).
+Participants with higher temporal clustering scores tended to exhibit better overall memory for the episode, according to both \cite{ChenEtal17}'s hand-counted numbers of recalled scenes from the episode (Pearson's $r(15) = 0.49,~p = 0.046$) and the numbers of episode events that best-matched at least one recall event (i.e., model-estimated number of events recalled; Pearson's $r(15) = 0.59,~p = 0.013$).
+Semantic clustering measures the extent to which participants cluster their recall responses according to semantic similarity.
+We found that participants tended to recall semantically similar episode events together (mean clustering score: 0.650, SEM: 0.032), and that semantic clustering score was also related to both hand-counted  (Pearson's $r(15) = 0.65,~p = 0.005$) and model-estimated (Pearson's $r(15) = 0.58,~p = 0.015$) numbers of recalled events.
+
+\begin{figure}[tp]
+  \centering
+  \includegraphics[width=1\textwidth]{figs/list_learning}
+  \caption{\small \textbf{Naturalistic extensions of classic list-learning memory analyses.} \textbf{A.} The probability of first recall as a function of the serial position of the event in the episode.
+\textbf{B}.
+The probability of recalling each event, conditioned on having most recently recalled the event \textit{lag} events away in the episode.
+\textbf{C.} The proportion of participants who recalled each event, as a function of the serial position of the events in the episode.
+All panels: error ribbons denote bootstrap-estimated standard error of the mean.}
+  \label{fig:list-learning}
+\end{figure}
+
+\begin{figure}[tp]
+  \centering
+  \includegraphics[width=1\textwidth]{figs/precision_distinctiveness}
+  \caption{\small \textbf{Novel content-based metrics of naturalistic memory: precision and distinctiveness.} \textbf{A.} The episode-recall correlation matrix for a representative participant (P17).
+The yellow boxes highlight the maximum correlation in each column.
+The example participant's overall precision score was computed as the average across the (Fisher $z$-transformed) correlation values in the yellow boxes.
+Their distinctiveness score was computed as the average (over recall events) of the $z$-scored (within column) event precisions.
+\textbf{B.} The (Pearson's) correlation between precision and hand-counted number of recalled scenes.
+\textbf{C.} The correlation between distinctiveness and hand-counted number of recalled scenes.
+\textbf{D.} The correlation between precision and the number of recalled episode events, as determined by our model.
+\textbf{E.} The correlation between distinctiveness and the number of recalled episode events, as determined by our model.}
+  \label{fig:precision-distinctiveness}
+\end{figure}
+
+The above analyses illustrate how our framework for characterizing the dynamic conceptual content of naturalistic episodes enables us to carry out analyses that have traditionally been applied to much simpler list-learning paradigms.
+However, perhaps the most interesting aspects of memory for naturalistic episodes are those that have no list-learning analogs.
+The nuances of how one's memory for an event might capture some details, yet distort or neglect others, is central to how we use our memory systems in daily life.
+Yet when researchers study memory in highly simplified paradigms, those nuances are not typically observable.
+We next developed two novel, continuous metrics, termed \textit{precision} and \textit{distinctiveness}, aimed at characterizing distortions in the conceptual content of individual recall events, and the conceptual overlap between how people described different events.
+
+\textit{Precision} is intended to capture the ``completeness'' of recall, or how fully the presented content was recapitulated in a participant's recounting.
+We define a recall event's precision as the maximum correlation between the topic proportions of that recall event and any episode event (Fig.~\ref{fig:precision-distinctiveness}).
+In other words, given that a recall event best matches a particular episode event, more precisely recalled events overlap more strongly with the conceptual content of the original episode event.
+When a given event is assigned a blend of several topics, as is often the case (Fig.~\ref{fig:model}), a high precision score requires recapitulating the relative topic proportions during recall.
+
+\textit{Distinctiveness} is intended to capture the ``specificity'' of recall.
+In other words, distinctiveness quantifies the extent to which a given recall event reflects the most similar episode event over and above other episode events.
+Intuitively, distinctiveness is like a normalized variant of our precision metric.
+Whereas precision solely measures how much detail about an episode was captured in someone's recall, distinctiveness penalizes details that also pertain to other episode events.
+We define the distinctiveness of an event's recall as its precision expressed in standard deviation units with respect to other episode events.
+Specifically, for a given recall event, we compute the correlation between its topic vector and that of each episode event.
+This yields a distribution of correlation coefficients (one per episode event).
+We subtract the mean and divide by the standard deviation of this distribution to $z$-score the coefficients.
+The maximum value in this distribution (which, by definition, belongs to the episode event that best matches the given recall event) is that recall event's distinctiveness score.
+In this way, recall events that match one episode event far better than all other episode events will receive a high distinctiveness score.
+By contrast, a recall event that matches all episode events roughly equally will receive a comparatively low distinctiveness score.
+
+In addition to examining how precisely and distinctively participants recalled individual events, one may also use these metrics to summarize each participant's performance by averaging across a participant's event-wise precision or distinctiveness scores.
+This enables us to quantify how precisely a participant tended to recall subtle within-event details, as well as how specific (distinctive) those details were to individual events from the episode.
+Participants' average precision and distinctiveness scores were strongly correlated ($r(15) = 0.90, p < 0.001$).
+This indicates that participants who tended to precisely recount low-level details of episode events also tended to do so in an event-specific way (e.g., as opposed to detailing recurring themes that were present in most or all episode events; this behavior would have resulted in high precision but low distinctiveness).
+We found that, across participants, higher precision scores were positively correlated with the numbers of both hand-annotated scenes ($r(15) = 0.60, p = 0.010$) and model-estimated events ($r(15) = 0.90, p < 0.001$) that participants recalled.
+Participants' average distinctiveness scores were also correlated with both the hand-annotated ($r(15) = 0.45, p = 0.068$) and model-estimated ($r(15) = 0.71, p = 0.001$) numbers of recalled events.
+
+\begin{figure}[tp]
+  \centering
+  \vspace*{-1cm}
+  \includegraphics[width=.7\textwidth]{figs/precision_distinctiveness_detail}
+  \caption{\small \textbf{Precision reflects the completeness of recall, whereas distinctiveness reflects recall specificity.} \textbf{A.} Recall precision by episode event.
+Grey violin plots display kernel density estimates for the distribution of recall precision scores for a single episode event.
+Colored dots within each violin plot represent individual participants' recall precision for the given event.
+\textbf{B.} Recall distinctiveness by episode event, analogous to Panel A.
+\textbf{C.} The set of ``Narrative Details'' episode annotations (generated by \citealp{ChenEtal17}) comprising an example episode event (22) identified by the HMM.
+Each action or feature is highlighted in a different color.
+\textbf{D.} Sentences comprising the most precise (P17) and least precise (P6) participants' recalls of episode event 21.
+Descriptions of specific actions or features reflecting those highlighted in Panel B are highlighted in the corresponding color.
+The text highlighted in gray denotes a (rare) false recall.
+The unhighlighted text denotes correctly recalled information about other episode events.
+\textbf{E.} The sets of ``Narrative Details'' episode annotations (generated by \citealp{ChenEtal17}) for scenes comprising episode events described by the example participants in Panel F.
+Each event's text is highlighted in a different color.
+\textbf{F.} The sentences comprising the most distinctive (P9) and least distinctive (P6) participants' recalls of episode event 21.
+Sections of recall describing each each episode event in Panel E are highlighted with the corresponding color.}
+  \label{fig:precision-detail}
+\end{figure}
+
+Examining individual recalls of the same episode event can provide insights into how the above precision and distinctiveness scores may be used to characterize similarities and differences in how different people describe the same shared experience.
+In Figure \ref{fig:precision-detail}, we compare recalls for the same episode event from the participants with the highest (P17) and lowest (P6) precision scores.
+From the HMM-identified episode event boundaries, we recovered the set of annotations describing the content of a single episode event (event 21; Fig.~\ref{fig:precision-detail}C), and divided them into different color-coded sections for each action or feature described.
+Next, we used an analogous approach to identify the set of sentences comprising the corresponding recall event from each of the two example participants (Fig.~\ref{fig:precision-detail}D).
+We then colored all words describing actions and features in the transcripts shown in Panel D according to the color-coded annotations in Panel C.
+Visual comparison of these example recalls reveals that the more precise recall captures more of the episode event's content, and in greater detail.
+
+Figure \ref{fig:precision-detail} also illustrates the differences between high and low distinctiveness scores.
+We extracted the set of sentences comprising the most distinctive recall event (P9) and least distinctive recall event (P6) corresponding to the example episode event shown in Panel C (event 21).
+We also extracted the annotations for all episode events whose content these participants' single recall events described.
+We assigned each episode event a unique color (Fig.~\ref{fig:precision-detail}E), and colored each recalled sentence (Panel F) according to the episode events they best matched.
+Visual inspection of Panel F reveals that the most distinctive recall's content is tightly concentrated around event 21, whereas the least distinctive recall incorporates content from a much wider range of episode events.
+
+The preceding analyses sought to characterize how participants' recountings of individual episode events captured the low-level details of each event.
+Next, we sought to characterize how participants' recountings of the full episode captured its high-level essence---i.e., the shape of the episode's trajectory through word embedding (topic) space.
+To visualize the essence of the episode and each participant's recall trajectory~\citep{HeusEtal18a}, we projected the topic proportions matrices for the episode and recalls onto a shared two-dimensional space using Uniform Manifold Approximation and Projection~\citep[UMAP; ][]{McInEtal18}.
+In this lower-dimensional space, each point represents a single episode or recall event, and the distances between the points reflect the distances between the events' associated topic vectors (Fig.~\ref{fig:trajectory}).
+In other words, events that are nearer to each other in this space are more semantically similar, and those that are farther apart are less so.
 
@@
 \textbf{B.} The average two-dimensional trajectory captured by participants' recall sequences, with the same format and coloring as the trajectory in Panel A.
-To compute the event positions, we matched each recalled event with an event from the original video (see \textit{Results}), and then we averaged the positions of all events with the same label.
+To compute the event positions, we matched each recalled event with an event from the original episode (see \textit{Results}), and then we averaged the positions of all events with the same label.
 The arrows reflect the average transition direction through topic space taken by any participants whose trajectories crossed that part of topic space; blue denotes reliable agreement across participants via a Rayleigh test ($p < 0.05$, corrected).
 \textbf{C.} The recall topic trajectories (gray) taken by each individual participant (P1--P17).
-The video's trajectory is shown in black for reference.
-(Same format and coloring as Panel A.)}
+The episode's trajectory is shown in black for reference.
+Here, events (dots) are colored by their matched episode event (Panel A).}
 \label{fig:trajectory}
@@
 
-Visual inspection of the video and recall topic trajectories reveals a striking pattern.
-First, the topic trajectory of the video (which reflects its dynamic content; Fig.~\ref{fig:trajectory}A) is captured nearly perfectly by the averaged topic trajectories of participants' recalls (Fig.~\ref{fig:trajectory}B).
-To assess the consistency of these recall trajectories across participants, we asked: given that a participant's recall trajectory had entered a particular location in topic space, could the position of their \textit{next} recalled event be predicted reliably?
-For each location in topic space, we computed the set of line segments connecting successively recalled events (across all participants) that intersected that location (see \textit{Methods} for additional details).
+Visual inspection of the episode and recall topic trajectories reveals a striking pattern.
+First, the topic trajectory of the episode (which reflects its dynamic content; Fig.~\ref{fig:trajectory}A) is captured nearly perfectly by the averaged topic trajectories of participants' recalls (Fig.~\ref{fig:trajectory}B).
+To assess the consistency of these recall trajectories across participants, we asked: given that a participant's recall trajectory had entered a particular location in the reduced topic space, could the position of their \textit{next} recalled event be predicted reliably?
+For each location in the reduced topic space, we computed the set of line segments connecting successively recalled events (across all participants) that intersected that location (see \textit{Methods}).
 We then computed (for each location) the distribution of angles formed by the lines defined by those line segments and a fixed reference line (the $x$-axis).
 Rayleigh tests revealed the set of locations in topic space at which these across-participant distributions exhibited reliable peaks (blue arrows in Fig.~\ref{fig:trajectory}B reflect significant peaks at $p < 0.05$, corrected).
-We observed that the locations traversed by nearly the entire video trajectory exhibited such peaks.
-In other words, participants exhibited similar trajectories that also matched the trajectory of the original video (Fig.~\ref{fig:trajectory}C).
-This is especially notable when considering the fact that the number of events participants recalled (dots in Fig.~\ref{fig:trajectory}C) varied considerably across people, and that every participant used different words to describe what they had remembered happening in the video.
-Differences in the numbers of remembered events appear in participants' trajectories as differences in the sampling resolution along the trajectory.
-We note that this framework also provides a means of detangling classic ``proportion recalled'' measures (i.e., the proportion of video events referenced in participants' recalls) from participants' abilities to recapitulate the full gist of the original video (i.e., the similarity in the shape of the original video trajectory and that defined by each participant's recounting of the video).
+We observed that the locations traversed by nearly the entire episode trajectory exhibited such peaks.
+In other words, participants' recalls exhibited similar trajectories to each other that also matched the trajectory of the original episode (Fig.~\ref{fig:trajectory}C).
+This is especially notable when considering the fact that the number of HMM-identified recall events (dots in Fig.~\ref{fig:trajectory}C) varied considerably across people, and that every participant used different words to describe what they had remembered happening in the episode.
+Differences in the numbers of recall events appear in participants' trajectories as differences in the sampling resolution along the trajectory.
+We note that this framework also provides a means of disentangling classic ``proportion recalled'' measures (i.e., the proportion of episode events described in participants' recalls) from participants' abilities to recapitulate the episode's essence (i.e., the similarity between the shapes of the original episode trajectory and that defined by each participant's recounting of the episode).
 
-Because our analysis framework projects the dynamic video content and participants' recalls onto a shared topic space, and because the dimensions of that space are known (i.e., each topic dimension is a set of weights over words in the vocabulary; Fig.~\topics), we can examine the topic trajectories to understand which specific content was remembered well (or poorly).
-For each video event, we can ask: what was the average correlation (across participants) between the video event's topic vector and the closest matching recall event topic vectors from each participant?
-This yields a single correlation coefficient for each video event, describing how closely participants' recalls of the event tended to reliably capture its content (Fig.~\ref{fig:topics}A).
-(We also examined how different comparisons between each video event's topic vector and the corresponding recall event topic vectors related to hand-annotated characterizations of memory performance; see \textit{Supporting Information}).
-Given this summary of which events were recalled reliably (or not), we next asked whether the better-remembered or worse-remembered events tended to reflect particular topics.
-We computed a weighted average of the topic vectors for each video event, where the weights reflected how reliably each event was recalled.
-To visualize the result, we created a ``wordle'' image~\citep{MuelEtal18} where words weighted more heavily by better-remembered topics appear in a larger font (Fig.~\ref{fig:topics}B, green box).
-Events that reflected topics weighting heavily on characters like ``Sherlock'' and ``John'' (i.e., the main characters) and locations like ``221b Baker Street'' (i.e., a major recurring location and the address of the flat that Sherlock and John share) were best remembered.
-An analogous analysis revealed which themes were poorly remembered.
-Here in computing the weighted average over events' topic vectors we weighted each event in \textit{inverse} proportion to how well it was remembered (Fig.~\ref{fig:topics}B, red box).
-This revealed that events with relatively minor characters such as ``Mike,'' ``Jeffrey,'' and ``Molly,'' as well as less-integral plot locations (e.g., ``hospital'' and ``office'') were least well-remembered.
-This suggests that what is retained in memory are the major plot elements (i.e., the overall ``gist'' of what happened), whereas the more minor details are prone to pruning.
-
-In addition to constructing overall summaries, assessing the video and recall topic vectors from individual recalls can provide further insights.
-Specifically, for any given event we can construct two wordles: one from the original video event's topic vector, and a second from the average topic vectors produced by all participants' recalls of that event.
-We can then examine those wordles visually to gain an intuition for which aspects of the video event were recapitulated in participants' recalls of that event.
-Several example wordles are displayed in Figure~\ref{fig:topics}C (wordles from the three best-remembered events are circled in green; wordles from the three worst-remembered events are circled in red).
-Using wordles to visually compare the topical content of each video event and the (average) corresponding recall event reveals the specific content from the specific events that is reliably retained in the transformation into memory (green events) or not (red events).
+In addition to enabling us to visualize the episode's high-level essence, describing the episode as a geometric trajectory also enables us to drill down to individual words and quantify how each word relates to the memorability of each event.
+This provides another approach to examining participants' recall for low-level details beyond the precision and distinctiveness measures we defined above.
+The results displayed in Figures \ref{fig:list-learning}C and \ref{fig:precision-detail}A suggest that certain events were remembered better than others.
+Given this, we next asked asked whether the events that were generally remembered precisely or imprecisely tended to reflect particular content.
+Because our analysis framework projects the dynamic episode content and participants' recalls into a shared space, and because the dimensions of that space represent topics (which are, in turn, sets of weights over known words in the vocabulary), we are able to recover the weighted combination of words that make up any point (i.e., topic vector) in this space.
+We first computed the average precision with which participants recalled each of the 30 episode events (Fig.~\ref{fig:topics}A; note that this result is analogous to a serial position curve created from our precision metric).
+We then computed a weighted average of the topic vectors for each episode event, where the weights reflected how precisely each event was recalled.
+To visualize the result, we created a ``wordle'' image~\citep{MuelEtal18} where words weighted more heavily by more precisely-remembered topics appear in a larger font (Fig.~\ref{fig:topics}B, green box).
+Across the full episode, content that weighted heavily on topics and words central to the major foci of the episode (e.g., the names of the two main characters, ``Sherlock'' and ``John,'' and the address of a major recurring location, ``221B Baker Street'') was best remembered.
+An analogous analysis revealed which themes were less-precisely remembered.
+Here in computing the weighted average over events' topic vectors, we weighted each event in \textit{inverse} proportion to its average precision (Fig.~\ref{fig:topics}B, red box).
+The least precisely remembered episode content reflected information that was extraneous to the episode's essence, such as the proper names of relatively minor characters (e.g., ``Mike,'' ``Molly,'' and ``Lestrade'') and locations (e.g., ``St.
+Bartholomew's Hospital'').
 
@@
 \includegraphics[width=1\textwidth]{figs/topics}
-\caption{\small \textbf{Transforming experience into memory.} \textbf{A.} Average correlations (across participants) between the topic vectors from each video event and the closest-matching recall events.
+\caption{\small \textbf{Language used in the most and least precisely remembered events.} \textbf{A.} Average precision (episode event-recall event topic vector correlation) across participants for each episode event.
+Here we defined each episode event's precision for each participant as the correlation between its topic vector and the most-correlated recall event's topic vector from that participant.
 Error bars denote bootstrap-derived across-participant 95\% confidence intervals.
-The stars denote the three best-remembered events (green) and worst-remembered events (red).
-\textbf{B.} Wordles comprising the top 200 highest-weighted words reflected in the weighted-average topic vector across video events.
-Green: video events were weighted by how well the topic vectors derived from recalls of those events matched the video events' topic vectors (Panel A).
-Red: video events were weighted by the inverse of how well their topic vectors matched the recalled topic vectors.
-\textbf{C.}  The set of all video and recall events is projected onto the two-dimensional space derived in Figure~\ref{fig:trajectory}.
-The dots outlined in black denote video events (dot size reflects the average correlation between the video event's topic vector and the topic vectors from the closest matching recalled events from each participant; bigger dots denote stronger correlations).
-The dots without black outlines denote recalled events.
+The stars denote the three most precisely remembered events (green) and least precisely remembered events (red).
+\textbf{B.} Wordles comprising the top 200 highest-weighted words reflected in the weighted-average topic vector across episode events.
+Green: episode events were weighted by their precision (Panel A).
+Red: episode events were weighted by the inverse of their precision.
+\textbf{C.}  The set of all episode and recall events is projected onto the two-dimensional space derived in Figure~\ref{fig:trajectory}.
+The dots outlined in black denote episode events (dot size is proportional to each event's average precision).
+The dots without black outlines denote individual recall events from each participant.
 All dots are colored using the same scheme as Figure~\ref{fig:trajectory}A.
-Wordles for several example events are displayed (green: three best-remembered events; red: three worst-remembered events).
-Within each circular wordle, the left side displays words associated with the topic vector for the video event, and the right side displays words associated with the (average) recall event topic vector, across all recall events matched to the given video event.}
+Wordles for several example events are displayed (green: three most precisely remembered events; red: three least precisely remembered events).
+Within each circular wordle, the left side displays words associated with the topic vector for the episode event, and the right side displays words associated with the (average) recall event topic vector, across all recall events matched to the given episode event.}
 \label{fig:topics}
@@
 
-The results thus far inform us about which aspects of the dynamic content in the episode participants watched were preserved or altered in participants' memories of the episode.
-We next carried out a series of analyses aimed at understanding which brain structures might implement these processes.
-In one analysis we sought to identify which brain structures were sensitive to the video's dynamic content, as characterized by its topic trajectory.
-Specifically, we used a searchlight procedure to identify the extent to which each cluster of voxels exhibited a timecourse (as the participants watched the video) whose temporal correlation matrix matched the temporal correlation matrix of the original video's topic proportion matrix (Fig.~\ref{fig:model}B).
-As shown in Figure~\ref{fig:brainz}A, the analysis revealed a network of regions including bilateral frontal cortex and cingulate cortex, suggesting that these regions may play a role in maintaining information relevant to the narrative structure of the video.
-In a second analysis, we sought to identify which brain structures' responses (while viewing the video) reflected how each participant would later \textit{recall} the video.
-We used an analogous searchlight procedure to identify clusters of voxels whose temporal correlation matrices reflected the temporal correlation matrix of the topic proportions for each individual's recalls (Figs.~\ref{fig:model}D, \corrmats).
-As shown in Figure~\ref{fig:brainz}B, the analysis revealed a network of regions including the ventromedial prefrontal cortex (vmPFC), anterior cingulate cortex, and right medial temporal lobe (rMTL), suggesting that these regions may play a role in transforming each individual's experience into memory.
-In identifying regions whose responses to ongoing experiences reflect how those experiences will be remembered later, this latter analysis extends classic \textit{subsequent memory analyses}~\citep[e.g.,][]{PallWagn02} to domain of naturalistic stimuli.
+A similar result emerged from assessing the topic vectors for individual episode and recall events (Fig.~\ref{fig:topics}C).
+Here, for each of the three most and least precisely remembered episode events, we have constructed two wordles: one from the original episode event's topic vector (left) and a second from the average recall topic vector for that event (right).
+The three most precisely remembered events (circled in green) correspond to scenes integral to the central plot-line: a mysterious figure spying on John in a phone booth; John meeting Sherlock at Baker St.~to discuss the murders; and Sherlock laying a trap to catch the killer.
+Meanwhile, the least precisely remembered events (circled in red) reflect scenes that comprise minor plot points: a video of singing cartoon characters that participants viewed in an introductory clip prior to the main episode; John asking Molly about Sherlock's habit of over-analyzing people; and Sherlock noticing evidence of Anderson's and Donovan's affair.
+
+The results this far inform us about which aspects of the dynamic content in the episode participants watched were preserved or altered in participants' memories.
+We next carried out a series of analyses aimed at understanding which brain structures might facilitate these preservations and transformations between the participants' shared experience of watching the episode and their subsequent memories of the episode.
+In the first analysis, we sought to identify brain structures that were sensitive to the dynamic unfolding of the episode's content, as characterized by its topic trajectory.
+We used a searchlight procedure to identify clusters of voxels whose activity patterns displayed a proximal temporal correlation structure (as participants watched the episode) matching that of the original episode's topic proportions (Fig.~\ref{fig:brainz}A; see \textit{Methods} for additional details).
+In a second analysis, we sought to identify brain structures whose responses (during episode viewing) reflected how each participant would later structure their \textit{recounting} of the episode.
+We used a searchlight procedure to identify clusters of voxels whose proximal temporal correlation matrices matched that of the topic proportions matrix for each participant's recall transcript (Figs.~\ref{fig:brainz}B; see \textit{Methods} for additional details).
+To ensure our searchlight procedure identified regions \textit{specifically} sensitive to the temporal structure of the episode or recalls (i.e., rather than those with a temporal autocorrelation length similar to that of the episode and recalls), we performed a phase shift-based permutation correction (see \textit{Methods}).
+As shown in Figure~\ref{fig:brainz}C, the episode-driven searchlight analysis revealed a distributed network of regions that may play a role in processing information relevant to the narrative structure of the episode.
+The recall-driven searchlight analysis revealed a second network of regions (Fig.~\ref{fig:brainz}D) that may facilitate a person-specific transformation of one's experience into memory.
+In identifying regions whose responses to ongoing experiences reflect how those experiences will be remembered later, this latter analysis extends classic \textit{subsequent memory effect analyses}~\citep[e.g.,][]{PallWagn02} to the domain of naturalistic experiences.
 
@@
 \includegraphics[width=1\textwidth]{figs/searchlights}
-\caption{\small \textbf{Brain structures that underlie the transformation of experience into memory.} \textbf{A.} We searched for regions whose responses (as participants watched the video) matched the temporal correlation matrix of the video topic proportions.
-These regions are sensitive to the narrative structure of the video.
-\textbf{B.} We searched for regions whose responses (as participants watched the video) matched the temporal correlation matrix of the topic proportions derived from each individual's later recall of video.
-These regions are sensitive to how the narrative structure of the video is transformed into a memory of the video.
-Both panels: the maps are thresholded at $p < 0.05$, corrected.}
+\caption{\small \textbf{Brain structures that underlie the transformation of experience into memory.} \textbf{A.} We isolated the proximal diagonals from the upper triangle of the episode correlation matrix, and applied this same diagonal mask to the voxel response correlation matrix for each cube of voxels in the brain.
+We then searched for brain regions whose activation timeseries consistently exhibited a similar proximal correlational structure to the episode model, across participants.
+\textbf{B.} We used dynamic time warping \citep{BernClif94} to align each participant's recall timeseries to the TR timeseries of the episode.
+We then applied the same diagonal mask used in Panel A to isolate the proximal temporal correlations and searched for brain regions whose activation timeseries for an individual consistently exhibited a similar proximal correlational structure to each individual's recall.
+\textbf{C.} We identified a network of regions sensitive to the narrative structure of participants' ongoing experience.
+The map shown is thresholded at $p < 0.05$, corrected.
+The top ten \texttt{Neurosynth} terms displayed in the panel were computed using the unthresholded map.
+\textbf{D}.
+We also identified a network of regions sensitive to how individuals would later structure the episode's content in their recalls.
+The map shown is thresholded at $p < 0.05$, corrected.
+The top ten \texttt{Neurosynth} terms displayed in the panel were computed using the unthresholded map.}
 \label{fig:brainz}
 \end{figure}
+
+The searchlight analyses described above yielded two distributed networks of brain regions whose activity timecourses tracked with the temporal structure of the episode (Fig.~\ref{fig:brainz}C) or participants' subsequent recalls (Fig.~\ref{fig:brainz}D).
+We next sought to gain greater insight into the structures and functional networks our results reflected.
+To accomplish this, we performed an additional, exploratory analysis using \texttt{Neurosynth} \citep{YarkEtal11}.
+Given an arbitrary statistical map as input, \texttt{Neurosynth} performs a massive automated meta-analysis, returning a ranked list of terms frequently used in neuroimaging papers that report similar statistical maps.
+We ran \texttt{Neurosynth} on the (unthresholded) permutation-corrected maps for the episode- and recall-driven searchlight analyses.
+The top ten terms with maximally similar meta-analysis images identified by \texttt{Neurosynth} are shown in Figure \ref{fig:brainz}.
 
@@
 
-Our work casts remembering as reproducing (behaviorally and neurally) the topic trajectory, or ``gist,'' of the original experience.
-This view draws inspiration from prior work aimed at elucidating the neural and behavioral underpinnings of how we process dynamic naturalistic experiences and remember them later.
-One approach to identifying neural responses to naturalistic stimuli (including experiences) entails building a model of the stimulus and searching for brain regions whose responses are consistent with the model.
-In prior work, a series of studies from Uri Hasson's group~\citep{LernEtal11, SimoEtal16, ChenEtal17, BaldEtal17, ZadbEtal17} have extended this approach with a clever twist.
-Rather than building an explicit stimulus model, these studies instead search for brain responses (while experiencing the stimulus) that are reliably similar across individuals.
-So called \textit{inter-subject correlation} (ISC) and \textit{inter-subject functional connectivity} (ISFC) analyses effectively treat other people's brain responses to the stimulus as a ``model'' of how its features change over time.
-By contrast, in our present work we used topic models and HMMs to construct an explicit stimulus model (i.e., the topic trajectory of the video).
-When we searched for brain structures whose responses are consistent with the video's topic trajectory, we identified a network of structures that overlapped strongly with the ``long temporal receptive window'' network reported by the Hasson group~\citep[e.g., compare our Fig.~\ref{fig:brainz}A with the map of long temporal receptive window voxels in][]{LernEtal11}.
-This provides support for the notion that part of the long temporal receptive window network may be maintaining an explicit model of the stimulus dynamics.
-When we performed a similar analysis after swapping out the video's topic trajectory with the recall topic trajectories of each individual participant, this allowed us to identify brain regions whose responses (as the participants viewed the video) reflected how the video trajectory would be transformed in memory (as reflected by the recall topic trajectories).
-The analysis revealed that the rMTL and vmPFC may play a role in this person-specific transformation from experience into memory.
-The role of the MTL in episodic memory encoding has been well-reported~\citep[e.g., ][]{PallWagn02, DavaEtAl03, RangEtal04, Dava06}.
-Prior work has also implicated the medial prefrontal cortex in representing ``schema'' knowledge~\citep[i.e., general knowledge about the format of an ongoing experience given prior similar experiences; ][]{KestEtal12, SchlPres15, GilbMarl17, SpalEtal18}.
-Integrating across our study and this prior work, one interpretation is that the person-specific transformations mediated (or represented) by the rMTL and vmPFC may reflect schema knowledge being leveraged, formed, or updated, incorporating ongoing experience into previously acquired knowledge.
+Explicitly modeling the dynamic content of a naturalistic stimulus and participants' memories enabled us to connect the present study of naturalistic recall with an extensive prior literature that has used list-learning paradigms to study memory~\citep[for review see][]{Kaha12}, as in Figure~\ref{fig:list-learning}.
+We found some similarities between how participants in the present study recounted a television episode and how participants typically recall memorized random word lists.
+However, our broader claim is that word lists miss out on fundamental aspects of naturalistic memory more like the sort of memory we rely on in everyday life.
+For example, there are no random word list analogs of character interactions, conceptual dependencies between temporally distant episode events, the sense of solving a mystery that pervades the \textit{Sherlock} episode, or the myriad other features of the episode that convey deep meaning and capture interest.
+Nevertheless, each of these properties affects how people process and engage with the episode as they are watching it, and how they remember it later.
+The overarching goal of the present study is to characterize how the rich dynamics of the episode affect the rich behavioral and neural dynamics of how people remember it.
 
-Our work has broad implications for how we characterize and assess memory in real-world settings such as the classroom or physician's office.
-For example, the most commonly used classroom evaluation tools involve computing the proportion of correctly answered exam questions.
+Our work casts remembering as reproducing (behaviorally and neurally) the topic trajectory, or ``shape,'' of an experience.
+When we characterized memory for a television episode using this framework, we found that every participant's recounting of the episode recapitulated the low spatial frequency details of the shape of its trajectory through topic space (Fig.~\ref{fig:trajectory}).
+We termed this narrative scaffolding the episode's \textit{essence}.
+Where participants' behaviors varied most was in their tendencies to recount specific low-level details from each episode event.
+Geometrically, this appears as high spatial frequency distortions in participants' recall trajectories relative to the trajectory of the original episode (Fig.~\ref{fig:topics}).
+We developed metrics to characterize the precision (recovery of any and all event-level information) and distinctiveness (recovery of event-specific information).
+We also used word cloud visualizations to interpret the details of these event-level distortions.
+
+The neural analyses we carried out (Fig.~\ref{fig:brainz}) also leveraged our geometric framework for characterizing the shapes of the episode and participants' recountings.
+We identified one network of regions whose responses tracked with temporal correlations in the conceptual content of the episode (as quantified by topic models applied to a set of annotations about the episode).
+This network included orbitofrontal cortex, ventromedial prefrontal cortex, and striatum, among others.
+As reviewed by \cite{RangRitc12}, several of these regions are members of the \textit{anterior temporal system}, which has been implicated in assessing and processing the familiarity of ongoing experiences, emotions, social cognition, and reward.
+A second network we identified tracked with temporal correlations in the idiosyncratic conceptual content of participants' subsequent recountings of the episode.
+This network included occipital cortex, extrastriate cortex, fusiform gyrus, and the precuneus.
+Several of these regions are members of the \textit{posterior medial system}~\citep{RangRitc12}, which has been implicated in matching incoming cues about the current situation to internally maintained \textit{situation models} that specify the parameters and expectations inherent to the current situation~\citep[also see][]{ZackEtal07, ZwaaRadv98}.
+Taken together, our results support the notion that these two (partially overlapping) networks work in coordination to make sense of our ongoing experiences, distort them in a way that links them with our prior knowledge and experiences, and encodes those distorted representations into memory for our later use.
+
+Our general approach draws inspiration from prior work aimed at elucidating the neural and behavioral underpinnings of how we process dynamic naturalistic experiences and remember them later.
+Our approach to identifying neural responses to naturalistic stimuli (including experiences) entails building an explicit model of the stimulus dynamics and searching for brain regions whose responses are consistent with the model~\citep[also see][]{HuthEtal12, HuthEtal16}.
+In prior work, a series of studies from Uri Hasson's group~\citep{LernEtal11, SimoEtal16, ChenEtal17, BaldEtal17, ZadbEtal17} have presented a clever alternative approach: rather than building an explicit stimulus model, these studies instead search for brain responses to the stimulus that are reliably similar across individuals.
+So called \textit{inter-subject correlation} (ISC) and \textit{inter-subject functional connectivity} (ISFC) analyses effectively treat other people's brain responses to the stimulus as a ``model'' of how its features change over time~\citep[also see][]{SimoChan20}.
+These purely brain-driven approaches are well suited to identifying which brain structures exhibit similar stimulus-driven responses across individuals.
+Further, because neural response dynamics are observed data (rather than model approximations), such approaches do not require a detailed understanding of which stimulus properties or features might be driving the observed responses.
+However, this also means that the specific stimulus features driving those responses are typically opaque to the researcher.
+Our approach is complementary.
+By explicitly modeling the stimulus dynamics, we are able to relate specific stimulus features to behavioral and neural dynamics.
+However, when our model fails to accurately capture the stimulus dynamics that are truly driving behavioral and neural responses, our approach necessarily yields an incomplete characterization of the neural basis of the processes we are studying.
+
+Other recent work has used HMMs to discover latent event structure in neural responses to naturalistic stimuli~\citep{BaldEtal17}.
+By applying HMMs to our explicit models of stimulus and memory dynamics, we gain a more direct understanding of those state dynamics.
+For example, we found that although the events comprising each participant's recalls recapitulated the episode's essence, participants differed in the \textit{resolution} of their recounting of low-level details.
+In turn, these individual behavioral differences were reflected in differences in neural activity dynamics as participants watched the television episode.
+
+Our approach also draws inspiration from the growing field of word embedding models.
+The topic models~\citep{BleiEtal03} we used to embed text from the episode annotations and participants' recall transcripts are just one of many models that have been studied in an extensive literature.
+The earliest approaches to word embedding, including latent
+semantic analysis~\citep{LandDuma97}, used word co-occurrence statistics (i.e., how often pairs of words occur in the same documents contained in the corpus) to derive a unique feature vector for each word.
+The feature vectors are constructed so that words that co-occur more frequently have feature vectors that are closer (in Euclidean distance).
+Topic models are essentially an extension of those early models, in that they attempt to explicitly model the underlying causes of word co-occurrences by automatically identifying the set of themes or topics reflected across the documents in the corpus.
+More recent work on these types of semantic models, including word2vec~\citep{MikoEtal13a}, the Universal Sentence Encoder~\citep{CerEtal18}, GPT-2~\citep{RadfEtal19}, and GTP-3~\citep{BrowEtal20} use deep neural networks to attempt to identify the deeper conceptual representations underlying each word.
+Despite the growing popularity of these sophisticated deep learning-based embedding models, we chose to prioritize interpretability of the embedding dimensions (e.g., Fig.~\ref{fig:topics}) over raw performance (e.g., with respect to some predefined benchmark).
+Nevertheless, we note that our general framework is, in principle, robust to the specific choice of language model as well as other aspects of our computational pipeline.
+For example, the word embedding model, timeseries segmentation model, and the episode-recall matching function could each be customized to suit a particular question space or application.
+Indeed, for some questions, interpretability of the embeddings may not be a priority, and thus other text embedding approaches (including the deep learning-based models described above) may be preferable.
+Further work will be needed to explore the influence of particular models on our framework's predictions and performance.
+
+Our work has broad implications for how we characterize and assess memory in real-world settings, such as the classroom or physician's office.
+For example, the most commonly used classroom evaluation tools involve simply computing the proportion of correctly answered exam questions.
 Our work indicates that this approach is only loosely related to what educators might really want to measure: how well did the students understand the key ideas presented in the course?
-One could apply the computational framework we developed to construct topic trajectories for the video and participants' recalls to build explicit content models of the course material and exam questions.
+Under this typical framework of assessment, the same exam score of 50\% could be ascribed to two very different students: one who attended to the full course but struggled to learn more than a broad overview of the material, and one who attended to only half of the course but understood the attended material perfectly.
+Instead, one could apply our computational framework to build explicit dynamic content models of the course material and exam questions.
 This approach would provide a more nuanced and specific view into which aspects of the material students had learned well (or poorly).
-In clinical settings, memory measures that incorporate such explicit content models might also provide more direct evaluations of patients' memories.
+In clinical settings, memory measures that incorporate such explicit content models might also provide more direct evaluations of patients' memories, and of doctor-patient interactions.
 
@@
 
-\subsection*{Experimental design and data collection}
+\subsection*{Paradigm and data collection}
 Data were collected by \cite{ChenEtal17}.
-In brief, participants ($n=17$) viewed the first 48 minutes of ``A Study in Pink'', the first episode of the BBC television series \textit{Sherlock}, while fMRI volumes were collected (TR = 1500~ms).
+In brief, participants ($n=22$) viewed the first 48 minutes of ``A Study in Pink,'' the first episode of the BBC television show \textit{Sherlock}, while fMRI volumes were collected (TR = 1500~ms).
+Participants were pre-screened to ensure they had never seen any episode of the show before.
 The stimulus was divided into a 23~min (946~TR) and a 25~min (1030~TR) segment to mitigate technical issues related to the scanner.
@@
 They were told that completeness and detail were more important than temporal order, and that if at any point they realized they had missed something, to return to it.
-Participants were then allowed to speak for as long as they wished, and verbally indicated when they were finished (e.g., `I’m done').''  For additional details about the experimental procedure and scanning parameters see \cite{ChenEtal17}.
-The experimental protocol was approved by Princeton University's Institutional Review Board.
+Participants were then allowed to speak for as long as they wished, and verbally indicated when they were finished (e.g., `I’m done').''  Five participants were dropped from the original dataset due to excessive head motion (2 participants), insufficient recall length (2 participants), or falling asleep during stimulus viewing (1 participant), resulting in a final sample size of $n=17$.
+For additional details about the testing procedures and scanning parameters, see \cite{ChenEtal17}.
+The testing protocol was approved by Princeton University's Institutional Review Board.
 
 After preprocessing the fMRI data and warping the images into a standard (3~mm$^3$ MNI) space, the voxel activations were $z$-scored (within voxel) and spatially smoothed using a 6~mm (full width at half maximum) Gaussian kernel.
-The fMRI data were also cropped so that all video-viewing data were aligned across participants.
+The fMRI data were also cropped so that all episode-viewing data were aligned across participants.
 This included a constant 3 TR (4.5~s) shift to account for the lag in the hemodynamic response.
 \citep[All of these preprocessing steps followed][where additional details may be found.]{ChenEtal17}
+
+The video stimulus was divided into 1,000 fine-grained ``time segments'' and annotated by an independent coder.
+For each of these 1,000 annotations, the following information was recorded: a brief narrative description of what was happening, the location where the time segment took place, whether that location was indoors or outdoors, the names of all characters on-screen, the name(s) of the character(s) in focus in the shot, the name(s) of the character(s) currently speaking, the camera angle of the shot, a transcription of any text appearing on-screen, and whether or not there was music present in the background.
+Each time segment was also tagged with its onset and offset time, in both seconds and TRs.
 
@@
 \subsection*{Statistics}
-All statistical tests we performed were two-sided.
+All statistical tests performed in the behavioral analyses were two-sided.
+All statistical tests performed in the neural data analyses were two-sided, except for the permutation-based thresholding, which was one-sided.
+In this case, we were specifically interested in identifying voxels whose activation time series reflected the temporal structure of the episode and recall topic proportions matrices to a \textit{greater} extent than that of the phase-shifted matrices.
 
-\subsection*{Modeling the dynamic content of the video and recall transcripts}
+\subsection*{Modeling the dynamic content of the episode and recall transcripts}
 \subsubsection*{Topic modeling}
-The input to the topic model we trained to characterize the dynamic content of the video comprised hand-generated annotations of each of 1000 scenes spanning the video clip~\citep[generated by][]{ChenEtal17}.
-The features included: narrative details (a sentence or two describing what happened in that scene); whether the scene took place indoors or outdoors; names of any characters that appeared in the scene; name(s) of characters in camera focus; name(s) of characters who were speaking in the scene; the location (in the story) that the scene took place; camera angle (close up, medium, long, top, tracking, over the shoulder, etc.); whether music was playing in the scene or not; and a transcription of any on-screen text.
-We concatenated the text for all of these features within each segment, creating a ``bag of words'' describing each scene.
-We then re-organized the text descriptions into overlapping sliding windows spanning 50 scenes each.
-In other words, the first text sample comprised the combined text from the first 50 scenes (i.e., 1--50), the second comprised the text from scenes 2--51, and so on.
+The input to the topic model we trained to characterize the dynamic content of the episode comprised 998 hand-generated annotations of short (mean: 2.96s) time segments spanning the video clip~(\citealp{ChenEtal17} generated 1000 annotations total; we removed two annotations referring to a break between the first and second scan sessions, during which no fMRI data were collected).
+We concatenated the text for all of the annotated features within each segment, creating a ``bag of words'' describing its content and performed some minor preprocessing (e.g., stemming possessive nouns and removing punctuation).
+We then re-organized the text descriptions into overlapping sliding windows spanning (up to) 50 annotations each.
+In other words, we estimated the ``context'' for each annotated segment using the text descriptions of the preceding 25 annotations, the present annotations, and the following 24 annotations.
+To model the context for annotations near the beginning of the episode (i.e., within 25 of the beginning or end), we created overlapping sliding windows that grew in size from one annotation to the full length.
+We also tapered the sliding window lengths at the end of the episode, whereby time segments within fewer than 24 annotations of the end of the episode were assigned sliding windows that extended to the end of the episode.
+This procedure ensured that each annotation's content was represented in the text corpus an equal number of times.
+
 We trained our model using these overlapping text samples with \texttt{scikit-learn}~\citep[version 0.19.1; ][]{PedrEtal11}, called from our high-dimensional visualization and text analysis software, \texttt{HyperTools}~\citep{HeusEtal18a}.
-Specifically, we use the \texttt{CountVectorizer} class to transform the text from each scene into a vector of word counts (using the union of all words across all scenes as the ``vocabulary,'' excluding English stop words); this yields a number-of-scenes by number-of-words \textit{word count} matrix.
-We then use the \texttt{LatentDirichletAllocation} class (topics=100, method=`batch') to fit a topic model~\citep{BleiEtal03} to the word count matrix, yielding a number-of-scenes (1000) by number-of-topics (100) \textit{topic proportions} matrix.
-The topic proportions matrix describes which mix of topics (latent themes) is present in each scene.
+Specifically, we used the \texttt{CountVectorizer} class to transform the text from each window into a vector of word counts (using the union of all words across all annotations as the ``vocabulary,'' excluding English stop words); this yielded a number-of-windows by number-of-words \textit{word count} matrix.
+We then used the \texttt{LatentDirichletAllocation} class (topics=100, method=`batch') to fit a topic model~\citep{BleiEtal03} to the word count matrix, yielding a number-of-windows (1047) by number-of-topics (100) \textit{topic proportions} matrix.
+The topic proportions matrix describes the gradually evolving mix of topics (latent themes) present in each annotated time segment of the episode.
 Next, we transformed the topic proportions matrix to match the 1976 fMRI volume acquisition times.
-For each fMRI volume, we took the topic proportions from whatever scene was displayed for most of that volume's 1500~ms acquisition time.
-This yielded a new number-of-TRs (1976) by number-of-topics (100) topic proportions matrix.
+We assigned each topic vector to the timepoint (in seconds) midway between the beginning of the first annotation and the end of the last annotation in its corresponding sliding text window.
+By doing so, we warped the linear temporal distance between consecutive topic vectors to align with the inconsistent temporal distance between consecutive annotations (whose durations varied greatly).
+We then rescaled these timepoints to 1.5s TR units, and used linear interpolation to estimate a topic vector for each TR.
+This resulted in a number-of-TRs (1976) by number-of-topics (100) matrix.
 
-We created similar topic proportions matrices using hand-annotated transcripts of each participant's recall of the video~\citep[annotated by ][]{ChenEtal17}.
-We tokenized the transcript into a list of sentences, and then re-organized the list into overlapping sliding windows spanning 10 sentences each; in turn we transformed each window's sentences into a word count vector (using the same vocabulary as for the video model).
-We then used the topic model already trained on the video scenes to compute the most probable topic proportions for each sliding window.
-This yielded a number-of-sentences (range: 68--294) by number-of-topics (100) topic proportions matrix, for each participant.
+We created similar topic proportions matrices using hand-annotated transcripts of each participant's verbal recall of the episode~\citep[annotated by][]{ChenEtal17}.
+We tokenized the transcript into a list of sentences, and then re-organized the list into overlapping sliding windows spanning (up to) 10 sentences each, analogously to how we parsed the episode annotations.
+In turn, we transformed each window's sentences into a word count vector (using the same vocabulary as for the episode model), then used the topic model already trained on the episode scenes to compute the most probable topic proportions for each sliding window.
+This yielded a number-of-windows (range: 83--312) by number-of-topics (100) topic proportions matrix for each participant.
 These reflected the dynamic content of each participant's recalls.
-Note: for details on how we selected the video and recall window lengths and number of topics, see \textit{Supporting Information} and Figure~\topicopt.
+Note: for details on how we selected the episode and recall window lengths and number of topics, see \textit{Supporting Information} and Figure~\topicopt.
 
-\subsubsection*{Parsing topic trajectories into events using Hidden Markov Models}
-We parsed the topic trajectories of the video and participants' recalls into events using Hidden Markov Models~\citep{Rabi89}.
+\subsubsection*{Segmenting topic proportions matrices into discrete events using hidden Markov Models}
+We parsed the topic proportions matrices of the episode and participants' recalls into discrete events using hidden Markov Models~\citep[HMMs;][]{Rabi89}.
 Given the topic proportions matrix (describing the mix of topics at each timepoint) and a number of states, $K$, an HMM recovers the set of state transitions that segments the timeseries into $K$ discrete states.
 Following \cite{BaldEtal17}, we imposed an additional set of constraints on the discovered state transitions that ensured that each state was encountered exactly once (i.e., never repeated).
-We used the BrainIAK toolbox~\citep{Brainiak} to implement this segmentation.
+We used the \texttt{BrainIAK} toolbox~\citep{Brainiak} to implement this segmentation.
 
-We used an optimization procedure to select the appropriate $K$ for each topic proportions matrix.  Specifically, we computed (for each matrix)
+We used an optimization procedure to select the appropriate $K$ for each topic proportions matrix.
+Prior studies on narrative structure and processing have shown that we both perceive and internally represent the world around us at multiple, hierarchical timescales \citep[e.g.,][]{HassEtal08, LernEtal11, HassEtal15, ChenEtal17, BaldEtal17, BaldEtal18}.
+However, for the purposes of our framework, we sought to identify the single timeseries of event-representations that is emphasized \textit{most heavily} in the temporal structure of the episode and of each participant's recall.
+We quantified this as the set of $K$ states that maximized the similarity between topic vectors for timepoints comprising each state, while minimizing the similarity between topic vectors for timepoints across different states.
+Specifically, we computed (for each matrix)
 \[
-  \argmax_K \left[\frac{a}{b} - \frac{K}{\alpha}\right],
+  \argmax_K \left[W_{1}(a, b)\right],
 \]
-where $a$ was the average correlation between the topic vectors of timepoints within the same state; $b$ was the average correlation between the topic vectors of timepoints within \textit{different} states; and $\alpha$ was a regularization parameter that we set to 5 times the window length (i.e., 250 scenes for the video topic trajectory and 50 sentences for the recall topic trajectories).
-Figure~\ref{fig:model}B displays the event boundaries returned for the video, and Figure~\corrmats~displays the event boundaries returned for each participant's recalls.
-After obtaining these event boundaries, we created stable estimates of each topic proportions matrix by averaging the topic vectors within each event.
-This yielded a number-of-events by number-of-topics matrix for the video and recalls from each participant.
+where $a$ was the distribution of within-state topic vector correlations, and $b$ was the distribution of across-state topic vector correlations .
+We computed the first Wasserstein distance ($W_{1}$; also known as \textit{Earth mover's distance}; \citealp{Dobr70, RamdEtal17}) between these distributions for a large range of possible $K$-values (range [2, 50]), and selected the $K$ that yielded the maximum value.
+Figure~\ref{fig:model}B displays the event boundaries returned for the episode, and Figure~\corrmats~displays the event boundaries returned for each participant's recalls.
+See Figure \kopt~for the optimization functions for the episode and recalls.
+After obtaining these event boundaries, we created stable estimates of the content represented in each event by averaging the topic vectors across timepoints between each pair of event boundaries.
+This yielded a number-of-events by number-of-topics matrix for the episode and recalls from each participant.
 
-\subsubsection*{Visualizing the video and recall topic trajectories}
-We used the UMAP algorithm~\citep{McInHeal18} to project the 100-dimensional topic space onto a two-dimensional space for visualization (Figs.~\ref{fig:trajectory}, \ref{fig:topics}).
-To ensure that all of the trajectories were projected onto the \textit{same} lower dimensional space, we computed the low-dimensional embedding on a ``stacked'' matrix created by vertically concatenating the events-by-topics topic proportions matrices for the video and all 17 participants' recalls.
-We then divided the rows of the result (a total-number-of-events by two matrix) back into separate matrices for the video topic trajectory and the trajectories for each participant's recalls (Fig.~\ref{fig:trajectory}).
+\subsubsection*{Naturalistic extensions of classic list-learning analyses}
+In traditional list-learning experiments, participants view a list of items (e.g., words) and then recall the items later.
+Our episode-recall event matching approach affords us the ability to analyze memory in a similar way.
+The episode and recall events can be treated analogously to studied and recalled ``items'' in a list-learning study.
+We can then extend classic analyses of memory performance and dynamics (originally designed for list-learning experiments) to the more naturalistic episode recall task used in this study.
+
+Perhaps the simplest and most widely used measure of memory performance is \textit{accuracy}---i.e., the proportion of studied (experienced) items (in this case, episode events) that the participant later remembered.
+\cite{ChenEtal17} used this method to rate each participant's memory quality by computing the proportion of (50, manually identified) scenes mentioned in their recall.
+We found a strong across-participants correlation between these independent ratings and the proportion of 30 HMM-identified episode events matched to participants' recalls (Pearson's $r(15) = 0.71, p = 0.002$).
+We further considered a number of more nuanced memory performance measures that are typically associated with list-learning studies.
+We also provide a software package, \texttt{Quail}, for carrying out these analyses~\citep{HeusEtal17b}.
+
+\paragraph{Probability of first recall (PFR).}  PFR curves~\citep{WelcBurn24, PostPhil65, AtkiShif68} reflect the probability that an item will be recalled first, as a function of its serial position during encoding.
+To carry out this analysis, we initialized a number-of-participants (17) by number-of-episode-events (30) matrix of zeros.
+Then, for each participant, we found the index of the episode event that was recalled first (i.e., the episode event whose topic vector was most strongly correlated with that of the first recall event) and filled in that index in the matrix with a 1.
+Finally, we averaged over the rows of the matrix, resulting in a 1 by 30 array representing the proportion of participants that recalled an event first, as a function of the order of the event's appearance in the episode (Fig.~\ref{fig:list-learning}A).
+% ------ NOTE: ------
+% reiterate meaning of error ribbons in list-learning figure? (already noted in figure caption)
+% - Paxton
+
+\paragraph{Lag conditional probability curve (lag-CRP).} The lag-CRP curve~\citep{Kaha96} reflects the probability of recalling a given item after the just-recalled item, as a function of their relative encoding positions (or \textit{lag}).
+In other words, a lag of 1 indicates that a recalled item was presented immediately after the previously recalled item, and a lag of -3 indicates that a recalled item came 3 items before the previously recalled item.
+For each recall transition (following the first recall), we computed the lag between the current recall event and the next recall event, normalizing by the total number of possible transitions.
+This yielded a number-of-participants (17) by number-of-lags (-29 to +29; 58 lags total excluding lags of 0) matrix.
+We averaged over the rows of this matrix to obtain a group-averaged lag-CRP curve (Fig.~\ref{fig:list-learning}B).
+
+\paragraph{Serial position curve (SPC).} SPCs~\citep{Murd62a} reflect the proportion of participants that remember each item as a function of the item's serial position during encoding.
+We initialized a number-of-participants (17) by number-of-episode-events (30) matrix of zeros.
+Then, for each recalled event, for each participant, we found the index of the episode event that the recalled event most closely matched (via the correlation between the events' topic vectors) and entered a 1 into that position in the matrix.
+This resulted in a matrix whose entries indicated whether or not each event was recalled by each participant (depending on whether the corresponding entires were set to one or zero).
+Finally, we averaged over the rows of the matrix to yield a 1 by 30 array representing the proportion of participants that recalled each event as a function of the events' order appearance in the episode (Fig.~\ref{fig:list-learning}C).
+
+\paragraph{Temporal clustering scores.} Temporal clustering describes a participant's tendency to organize their recall sequences by the learned items' encoding positions.
+For instance, if a participant recalled the episode events in the exact order they occurred (or in exact reverse order), this would yield a score of 1.
+If a participant recalled the events in random order, this would yield an expected score of 0.5.
+For each recall event transition (and separately for each participant), we sorted all not-yet-recalled events according to their absolute lag (i.e., distance away in the episode).
+We then computed the percentile rank of the next event the participant recalled.
+We averaged these percentile ranks across all of the participant's recalls to obtain a single temporal clustering score for the participant.
+
+\paragraph{Semantic clustering scores.} Semantic clustering describes a participant's tendency to recall semantically similar presented items together in their recall sequences.
+Here, we used the topic vectors for each event as a proxy for its semantic content.
+Thus, the similarity between the semantic content for two events can be computed by correlating their respective topic vectors.
+For each recall event transition, we sorted all not-yet-recalled events according to how correlated the topic vector \textit{of the closest-matching episode event} was to the topic vector of the closest-matching episode event to the just-recalled event.
+We then computed the percentile rank of the observed next recall.
+We averaged these percentile ranks across all of the participant's recalls to obtain a single semantic clustering score for the participant.
+
+\subsubsection*{Averaging correlations}
+In all instances where we performed statistical tests involving precision or distinctiveness scores (Fig.~\ref{fig:precision-detail}), we used the Fisher $z$-transformation~\citep{Fish25} to stabilize the variance across the distribution of correlation values prior to performing the test.
+Similarly, when averaging precision or distinctiveness scores, we $z$-transformed the scores prior to computing the mean, and inverse $z$-transformed the result.
+
+\subsubsection*{Visualizing the episode and recall topic trajectories}
+We used the UMAP algorithm~\citep{McInEtal18} to project the 100-dimensional topic space onto a two-dimensional space for visualization (Figs.~\ref{fig:trajectory}, \ref{fig:topics}).
+To ensure that all of the trajectories were projected onto the \textit{same} lower dimensional space, we computed the low-dimensional embedding on a ``stacked'' matrix created by vertically concatenating the events-by-topics topic proportions matrices for the episode, across-participants average recall and all 17 individual participants' recalls.
+We then separated the rows of the result (a total-number-of-events by two matrix) back into individual matrices for the episode topic trajectory, across-participant average recall trajectory, and the trajectories for each individual participant's recalls (Fig.~\ref{fig:trajectory}).
 This general approach for discovering a shared low-dimensional embedding for a collections of high-dimensional observations follows \cite{HeusEtal18a}.
+
+We optimized the manifold space for visualization based on two criteria: First, that the 2D embedding of the episode trajectory should reflect its original 100-dimensional structure as faithfully as possible.
+Second, that the path traversed by the embedded episode trajectory should intersect itself a minimal number of times.
+The first criteria helps bolster the validity of visual intuitions about relationships between sections of episode content, based on their locations in the embedding space.
+The second criteria was motivated by the observed low off-diagonal values in the episode trajectory's temporal correlation matrix (suggesting that the same topic-space coordinates should not be revisited; see Fig.~2A).
+For further details on how we created this low-dimensional embedding space, see \textit{Supporting Information}.
 
@@
 In Figure~\ref{fig:trajectory}B, we present an analysis aimed at characterizing locations in topic space that different participants move through in a consistent way (via their recall topic trajectories).
-The two-dimensional topic space used in our visualizations (Fig.~\ref{fig:trajectory}) ranged from -5 to 5 (arbitrary) units in the $x$ dimension and from -6.5 to 2 units in the $y$ dimension.
-We divided this space into a grid of vertices spaced 0.25~units apart.
-For each vertex, we examined the set of line segments formed by connecting each pair successively recalled events, across all participants, that passed within 0.5 units.
+The two-dimensional topic space used in our visualizations (Fig.~\ref{fig:trajectory}) comprised a $60 \times 60$ (arbitrary units) square.
+We tiled this space with a $50 \times 50$ grid of evenly spaced vertices, and defined a circular area centered on each vertex whose radius was two times the distance between adjacent vertices (i.e., 2.4 units).
+For each vertex, we examined the set of line segments formed by connecting each pair successively recalled events, across all participants, that passed through this circle.
 We computed the distribution of angles formed by those segments and the $x$-axis, and used a Rayleigh test to determine whether the distribution of angles was reliably ``peaked'' (i.e., consistent across all transitions that passed through that local portion of topic space).
-To create Figure~\ref{fig:trajectory}B we drew an arrow originating from each grid vertex, pointing in the direction of the average angle formed by line segments that passed within 0.5 units.
+To create Figure~\ref{fig:trajectory}B, we drew an arrow originating from each grid vertex, pointing in the direction of the average angle formed by the line segments that passed within 2.4 units.
 We set the arrow lengths to be inversely proportional to the $p$-values of the Rayleigh tests at each vertex.
-Specifically, for each vertex we converted all of the angles of segments that passed within 0.5 units to unit vectors, and we set the arrow lengths at each vertex proportional to the length of the (circular) mean vector.
+Specifically, for each vertex we converted all of the angles of segments that passed within 2.4 units to unit vectors, and we set the arrow lengths at each vertex proportional to the length of the (circular) mean vector.
 We also indicated any significant results ($p < 0.05$, corrected using the Benjamani-Hochberg procedure) by coloring the arrows in blue (darker blue denotes a lower $p$-value, i.e., a longer mean vector); all tests with $p \geq 0.05$ are displayed in gray and given a lower opacity value.
@@
 \subsection*{Searchlight fMRI analyses}
-In Figure~\ref{fig:brainz}, we present two analyses aimed at identifying brain structures whose responses (as participants viewed the video) exhibited particular temporal correlations.
-We developed a searchlight analysis whereby we constructed a cube centered on each voxel (radius: 5~voxels).
-For each of these cubes, we computed the temporal correlation matrix of the voxel responses during video viewing.
-Specifically, for each of the 1976 volumes collected during video viewing, we correlated the activity patterns in the given cube with the activity patterns (in the same cube) collected during every other timepoint.
-This yielded a 1976 by 1976 correlation matrix for each cube.
+In Figure~\ref{fig:brainz}, we present two analyses aimed at identifying brain regions whose responses (as participants viewed the episode) exhibited a particular temporal structure.
+We developed a searchlight analysis wherein we constructed a $5 \times 5 \times 5$ cube of voxels~\citep[following][]{ChenEtal17} centered on each voxel in the brain, and for each of these cubes, computed the temporal correlation matrix of the voxel responses during episode viewing.
+Specifically, for each of the 1976 volumes collected during episode viewing, we correlated the activity patterns in the given cube with the activity patterns (in the same cube) collected during every other timepoint.
+This yielded a $1976 \times 1976$ correlation matrix for each cube.
+Note: participant 5's scan ended 75s early, and in~\cite{ChenEtal17}'s publicly released dataset, their scan data was zero-padded to match the length of the other participants'.
+For our searchlight analyses, we removed this padded data (i.e., the last 50 TRs), resulting in a $1925 \times 1925$ correlation matrix for each cube in participant 5's brain.
 
-Next, we constructed two sets of ``template'' matrices: one reflected the video's topic trajectory and the other reflected each participant's recall topic trajectory.
-To construct the video template, we computed the correlations between the topic proportions estimated for every pair of TRs (prior to segmenting the trajectory into discrete events; i.e., the correlation matrix shown in Figs.~\ref{fig:model}B and \ref{fig:brainz}A).
-We constructed similar temporal correlation matrices for each participant's recall topic trajectory (Figs.~\ref{fig:model}D, \corrmats).
-However, to correct for length differences and potential non-linear transformations between viewing time and recall time, we first used dynamic time warping~\citep{BernClif94} to temporally align participants' recall topic trajectories with the video topic trajectory (an example correlation matrix before and after warping is shown in Fig.~\ref{fig:brainz}B).
-This yielded a 1976 by 1976 correlation matrix for the video template and for each participant's recall template.
+Next, we constructed a series of ``template'' matrices.
+The first template reflected the timecourse of the episode's topic proportions matrix, and the others reflected the timecourse of each participant's recall topic proportions matrix.
+To construct the episode template, we computed the correlations between the topic proportions estimated for every pair of TRs (prior to segmenting the topic proportions matrices into discrete events; i.e., the correlation matrix shown in Figs.~\ref{fig:model}B and \ref{fig:brainz}A).
+We constructed similar temporal correlation matrices for each participant's recall topic proportions matrix (Figs.~\ref{fig:model}D, \corrmats).
+However, to correct for length differences and potential non-linear transformations between viewing time and recall time, we first used dynamic time warping~\citep{BernClif94} to temporally align participants' recall topic proportions matrices with the episode topic proportions matrix.
+An example correlation matrix before and after warping is shown in Fig.~\ref{fig:brainz}B.
+This yielded a $1976 \times 1976$ correlation matrix for the episode template and for each participant's recall template.
 
-To determine which (cubes of) voxel responses reliably matched the video template, we correlated the upper triangle of the voxel correlation matrix for each cube with the upper triangle of the video template matrix~\citep{KrieEtal08b}.
-This yielded, for each participant, a single correlation value.
-We computed the average (Fisher $z$-transformed) correlation coefficient across participants.
-We used a permutation-based procedure to assess significance, whereby we re-computed the average correlations for each of 100 ``null'' video templates (constructed by circularly shifting the template by a random number of timepoints).
-(For each permutation, the same shift was used for all participants.)  We then estimated a $p$-value by computing the proportion of shifted correlations that were larger than the observed (unshifted) correlation.
-To create the map in Figure~\ref{fig:brainz}A we thresholded out any voxels whose correlation values fell below the 95\textsuperscript{th} percentile of the permutation-derived null distribution.
+The temporal structure of the episode's content (as described by our model) is captured in the block-diagonal structure of the episode's temporal correlation matrix (e.g., Figs.~\ref{fig:model}B, \ref{fig:brainz}A), with time periods of thematic stability represented as dark blocks of varying sizes.
+Inspecting the episode correlation matrix suggests that the episode's semantic content is highly temporally specific (i.e., the correlations between topic vectors from distant timepoints are almost all near zero).
+By contrast, the activity patterns of individual (cubes of) voxels can encode relatively limited information on their own, and their activity frequently contributes to multiple separate functions \citep{FreeEtal01, SigmDeha08, CharKoec10, RishEtal13}.
+By nature, these two attributes give rise to similarities in activity across large timescales that may not necessarily reflect a single task.
+To enable a more sensitive analysis of brain regions whose shifts in activity patterns mirrored shifts in the semantic content of the episode or recalls, we restricted the temporal correlations we considered to the timescale of semantic information captured by our model.
+Specifically, we isolated the upper triangle of the episode correlation matrix and created a ``proximal correlation mask'' that included only diagonals from the upper triangle of the episode correlation matrix up to the first diagonal that contained no positive correlations.
+Applying this mask to the full episode correlation matrix was equivalent to excluding diagonals beyond the corner of the largest diagonal block.
+In other words, the timescale of temporal correlations we considered corresponded to the longest period of thematic stability in the episode, and by extension the longest period of thematic stability in participants' recalls and the longest period of stability we might expect to see in voxel activity arising from processing or encoding episode content.
+Figure \ref{fig:brainz} shows this proximal correlation mask applied to the temporal correlation matrices for the episode, an example participant's (warped) recall, and an example cube of voxels from our searchlight analyses.
 
-We used a similar procedure to identify which voxels' responses reflected the recall templates.
-For each participant, we correlated the upper triangle of the correlation matrix for each cube of voxels with their (time warped) recall correlation matrix.
-As in the video template analysis this yielded a single correlation coefficient for each participant.
-However, whereas the video analysis compared every participant's responses to the same template, here the recall templates were unique for each participant.
-We computed the average $z$-transformed correlation coefficient across participants, and used the same permutation procedure we developed for the video responses to assess significant correlations.
-To create the map in Figure~\ref{fig:brainz}B we thresholded out any voxels whose correlation values fell below the 95\textsuperscript{th} percentile of the permutation-derived null distribution.
+To determine which (cubes of) voxel responses matched the episode template, we correlated the proximal diagonals from the upper triangle of the voxel correlation matrix for each cube with the proximal diagonals from episode template matrix~\citep{KrieEtal08b}.
+This yielded, for each participant, a voxelwise map of correlation values.
+We then performed a one-sample $t$-test on the distribution of (Fisher $z$-transformed) correlations at each voxel, across participants.
+This resulted in a value for each voxel (cube), describing how reliably its timecourse followed that of the episode.
 
-\bibliography{memlab}
+We further sought to ensure that our analysis identified regions where the activations’ temporal structure specifically reflected that of the episode, rather than regions whose activity was simply autocorrelated at a timescale similar to the episode template’s diagonal.
+To achieve this, we used a phase shift-based permutation procedure, whereby we circularly shifted the episode’s topic proportions matrix by a random number of timepoints (rows), computed the resulting ``null'' episode template, and re-ran the searchlight analysis, in full.
+(For each of the 100 permutations, the same random shift was used for all participants).
+We $z$-scored the observed (unshifted) result at each voxel against the distribution of permutation-derived ``null'' results, and estimated a $p$-value by computing the proportion of shifted results that yielded larger values.
+To create the map in Figure~\ref{fig:brainz}C, we thresholded out any voxels whose similarity to the unshifted episode’s structure fell below the 95\textsuperscript{th} percentile of the permutation-derived similarity results.
+
+We used an analogous procedure to identify which voxels' responses reflected the recall templates.
+For each participant, we correlated the proximal diagonals from the upper triangle of the correlation matrix for each cube of voxels with the proximal diagonals from the upper triangle of their (time-warped) recall correlation matrix.
+As in the episode template analysis, this yielded a voxelwise map of correlation coefficients for each participant.
+However, whereas the episode analysis compared every participant's responses to the same template, here the recall templates were unique for each participant.
+As in the analysis described above, we $t$-scored the (Fisher $z$-transformed) voxelwise correlations, and used the same permutation procedure we developed for the episode responses to ensure specificity to the recall timeseries and assign significance values.
+To create the map in Figure~\ref{fig:brainz}D we again thresholded out any voxels whose scores were below the 95\textsuperscript{th} percentile of the permutation-derived null distribution.
+
+\subsection*{Neurosynth decoding analyses}
+\texttt{Neurosynth} parses a massive online database of over 14,000 neuroimaging studies and constructs meta-analysis images for over 13,000 psychology- and neuroscience-related terms, based on NIfTI images accompanying studies where those terms appear at a high frequency.
+Given a novel image (tagged with its value type; e.g., $z$-, $t$-, $F$- or $p$-statistics), \texttt{Neurosynth} returns a list of terms whose meta-analysis images are most similar.
+Our permutation procedure yielded, for each of the two searchlight analyses, a voxelwise map of $z$-values.
+These maps describe the extent to which each voxel \textit{specifically} reflected the temporal structure of the episode or individuals' recalls (i.e., relative to the null distributions of phase-shifted values).
+We inputted the two statistical maps described above to \texttt{Neurosynth} to create a list of the 10 most representative terms for each map.
+
+% \bibliography{../../CDL-bibliography/memlab}
+\bibliography{CDL-bibliography/memlab}
 

### 2020-10-14 paper/main.tex
minor typo fixes

--- 2020-10-13 paper/main.tex
@@
 
-The 32 topics we found were heavily character-focused (i.e., the top-weighted word in each topic was nearly always a character) and could be roughly divided into themes centered around Sherlock Holmes (the titular character), John Watson (Sherlock's close confidant and assistant), supporting characters (e.g., Inspector Lestrade, Sergeant Donovan, or Sherlock's brother Mycroft), or the interactions between various groupings of these characters (Supp.
-Fig.~\topics).
+The 32 topics we found were heavily character-focused (i.e., the top-weighted word in each topic was nearly always a character) and could be roughly divided into themes centered around Sherlock Holmes (the titular character), John Watson (Sherlock's close confidant and assistant), supporting characters (e.g., Inspector Lestrade, Sergeant Donovan, or Sherlock's brother Mycroft), or the interactions between various groupings of these characters (Supp.~Fig.~\topics).
 This likely follows from the frequency with which these terms appeared in the episode annotations.
@@
 
-%\bibliographystyle{naturemag}
+\bibliographystyle{naturemag}
 %\bibliography{CDL-bibliography/memlab}

### 2020-10-14 code/sherlock_helpers/sherlock_helpers/functions.py
bootstrap CI function for pearson's r

@@ -125,6 +125,27 @@ def corr_mean(rs, axis=0):
     return z2r(np.nanmean([r2z(r) for r in rs], axis=axis))
 
 
+def pearsonr_ci(x, y, ci=95, n_boots=1000):
+    x = np.asarray(x)
+    y = np.asarray(y)
+    rand_ixs = np.random.randint(0, x.shape[0], size=(n_boots, x.shape[0]))
+    # (n_boots, n) paired subsample arrays
+    x_boots = x[rand_ixs]
+    y_boots = y[rand_ixs]
+    # difference from mean for each subsample
+    x_mdiffs = x_boots - x_boots.mean(axis=1)[:, None]
+    y_mdiffs = y_boots - y_boots.mean(axis=1)[:, None]
+    # sum of squares
+    x_ss = np.einsum('ij, ij -> i', x_mdiffs, x_mdiffs)
+    y_ss = np.einsum('ij, ij -> i', y_mdiffs, y_mdiffs)
+    # pearson correlation for each subsample
+    r_boots = np.einsum('ij, ij -> i', x_mdiffs, y_mdiffs) / np.sqrt(x_ss * y_ss)
+    # upper and lower bounds for confidence interval
+    ci_low = np.percentile(r_boots, (100 - ci) / 2)
+    ci_high = np.percentile(r_boots, (ci + 100) / 2)
+    return ci_low, ci_high
+
+
 def r2z(r):
     with np.errstate(invalid='ignore', divide='ignore'):
         return 0.5 * (np.log(1 + r) - np.log(1 - r))
@@ -133,15 +154,6 @@ def r2z(r):
 def z2r(z):
     with np.errstate(invalid='ignore', divide='ignore'):
         return (np.exp(2 * z) - 1) / (np.exp(2 * z) + 1)
-
-
-def pearsonr_ci(r, n, alpha=0.05):
-    z = r2z(r)
-    std_err = 1 / ((n - 3) ** 0.5)
-    z_a = norm.ppf(0.5 * (1 + alpha))    # 2-tailed
-    ci_low = z - z_a * std_err
-    ci_high = z + z_a * std_err
-    return z2r(ci_low), z2r(ci_high)
 
 
 ########################################

### 2020-10-14 code/sherlock_helpers/sherlock_helpers/functions.py
confidence interval calculation for list-learning and precision/distinctiveness analyses

@@ -125,20 +125,20 @@ def corr_mean(rs, axis=0):
     return z2r(np.nanmean([r2z(r) for r in rs], axis=axis))
 
 
-def pearsonr_ci(x, y, ci=95, n_boots=1000):
+def pearsonr_ci(x, y, ci=95, n_boots=10000):
     x = np.asarray(x)
     y = np.asarray(y)
     rand_ixs = np.random.randint(0, x.shape[0], size=(n_boots, x.shape[0]))
-    # (n_boots, n) paired subsample arrays
+    # (n_boots, n_observations) paired arrays
     x_boots = x[rand_ixs]
     y_boots = y[rand_ixs]
-    # difference from mean for each subsample
+    # differences from means
     x_mdiffs = x_boots - x_boots.mean(axis=1)[:, None]
     y_mdiffs = y_boots - y_boots.mean(axis=1)[:, None]
-    # sum of squares
+    # sums of squares
     x_ss = np.einsum('ij, ij -> i', x_mdiffs, x_mdiffs)
     y_ss = np.einsum('ij, ij -> i', y_mdiffs, y_mdiffs)
-    # pearson correlation for each subsample
+    # pearson correlations
     r_boots = np.einsum('ij, ij -> i', x_mdiffs, y_mdiffs) / np.sqrt(x_ss * y_ss)
     # upper and lower bounds for confidence interval
     ci_low = np.percentile(r_boots, (100 - ci) / 2)

### 2020-10-14 paper/main.tex
added confidence intervals to in-text statistics

--- 2020-10-14 paper/main.tex
@@
 Participants with higher temporal clustering scores tended to exhibit better overall memory for the episode, according to both Chen et al.
-(2017)~\cite{ChenEtal17}'s hand-counted numbers of recalled scenes from the episode (Pearson's $r(15) = 0.49,~p = 0.046$) and the numbers of episode events that best-matched at least one recall event (i.e., model-estimated number of events recalled; Pearson's $r(15) = 0.59,~p = 0.013$).
+(2017)~\cite{ChenEtal17}'s hand-counted numbers of recalled scenes from the episode (Pearson's $r(15) = 0.49,~p = 0.046,~95\%~CI~[0.25, 0.76]$) and the numbers of episode events that best-matched at least one recall event (i.e., model-estimated number of events recalled; Pearson's $r(15) = 0.59,~p = 0.013,~95\%~CI~[0.31, 0.80]$).
 Semantic clustering measures the extent to which participants cluster their recall responses according to semantic similarity~\citep{MannKaha12}.
-We found that participants tended to recall semantically similar episode events together (mean clustering score: 0.650, SEM: 0.032), and that semantic clustering score was also related to both hand-counted  (Pearson's $r(15) = 0.65,~p = 0.005$) and model-estimated (Pearson's $r(15) = 0.58,~p = 0.015$) numbers of recalled events.
+We found that participants tended to recall semantically similar episode events together (mean clustering score: 0.650, SEM: 0.032), and that semantic clustering score was also related to both hand-counted  (Pearson's $r(15) = 0.65,~p = 0.004,~95\%~CI~[0.31, 0.85]$) and model-estimated (Pearson's $r(15) = 0.58,~p = 0.015,~95\%~CI~[0.10, 0.83]$) numbers of recalled events.
 
@@
 This enables us to quantify how precisely a participant tended to recall subtle within-event details, as well as how specific (distinctive) those details were to individual events from the episode.
-Participants' average precision and distinctiveness scores were strongly correlated ($r(15) = 0.90, p < 0.001$).
+Participants' average precision and distinctiveness scores were strongly correlated ($r(15) = 0.90,~p < 0.001,~95\%~CI~[0.66, 0.96]$).
 This indicates that participants who tended to precisely recount low-level details of episode events also tended to do so in an event-specific way (e.g., as opposed to detailing recurring themes that were present in most or all episode events; this behavior would have resulted in high precision but low distinctiveness).
-We found that, across participants, higher precision scores were positively correlated with the numbers of both hand-annotated scenes ($r(15) = 0.60, p = 0.010$) and model-estimated events ($r(15) = 0.90, p < 0.001$) that participants recalled.
-Participants' average distinctiveness scores were also marginally correlated with both the hand-annotated ($r(15) = 0.45, p = 0.068$) and model-estimated ($r(15) = 0.71, p = 0.001$) numbers of recalled events.
+We found that, across participants, higher precision scores were positively correlated with the numbers of both hand-annotated scenes ($r(15) = 0.60,~p = 0.010,~95\%~CI~[0.02, 0.83]$) and model-estimated events ($r(15) = 0.90,~p < 0.001,~95\%~CI~[0.54, 0.96]$) that participants recalled.
+Participants' average distinctiveness scores were also marginally correlated with both the hand-annotated ($r(15) = 0.45,~p = 0.068,~95\%~CI~[-0.21, 0.79]$) and model-estimated ($r(15) = 0.71,~p = 0.001,~95\%~CI~[-0.07, 0.90]$) numbers of recalled events.
 
@@
 Taken together, our results support the notion that these two (partially overlapping) networks work in coordination to make sense of our ongoing experiences, distort them in a way that links them with our prior knowledge and experiences, and encodes those distorted representations into memory for our later use.
-Our work also provides a potential framework for modeling and elucidating ``memory schemas''-- i.e., cognitive abstractions that may be applied to multiple related experiences~\citep{GilbMarl17, BaldEtal18}.
+Our work also provides a potential framework for modeling and elucidating ``memory schemas''---i.e., cognitive abstractions that may be applied to multiple related experiences~\citep{GilbMarl17, BaldEtal18}.
 For example, the event-level geometric scaffolding of an experience (e.g., Fig.~\ref{fig:trajectory}A) might reflect its underlying schema, and experiences that share similar schemas might have similar shapes.
@@
 Perhaps the simplest and most widely used measure of memory performance is ``accuracy''---i.e., the proportion of studied (experienced) items (in this case, episode events) that the participant later remembered.
-Chen et al.
-(2017)~\cite{ChenEtal17} used this method to rate each participant's memory quality by computing the proportion of (50 manually identified) scenes mentioned in their recall.
-We found a strong across-participants correlation between these independent ratings and the proportion of 30 HMM-identified episode events matched to participants' recalls (Pearson's $r(15) = 0.71, p = 0.002$).
+Chen et al.~(2017)~\cite{ChenEtal17} used this method to rate each participant's memory quality by computing the proportion of (50 manually identified) scenes mentioned in their recall.
+We found a strong across-participants correlation between these independent ratings and the proportion of 30 HMM-identified episode events matched to participants' recalls (Pearson's $r(15) = 0.71, p = 0.002,~95\%~CI~[0.39, 0.88]$).
 We further considered a number of more nuanced memory performance measures that are typically associated with list-learning studies.

### 2020-10-15 paper/main.tex
reworded caption

@@
 \textbf{C.} The proportion of participants who recalled each event, as a function of the serial position of the events in the episode.
-All panels: error ribbons denote bootstrap-estimated standard error of the mean.}
+All panels: error ribbons denote the bootstrap-estimated 95\% confidence interval.}
   \label{fig:list-learning}
@@
   \includegraphics[width=1\textwidth]{figs/precision_distinctiveness}
-  \caption{\small \textbf{Novel content-based metrics of naturalistic memory: precision and distinctiveness.} \textbf{A.} The episode-recall correlation matrix for a representative participant (P17), chosen for their large number of recall events (for analogous figures for other participants, see Supp.\ Fig.~\corrmats).
+  \caption{\small \textbf{Novel content-based metrics of naturalistic memory: precision and distinctiveness.} \textbf{A.} The episode-recall correlation matrix for an example participant (P17), chosen for their large number of recall events (for analogous figures for other participants, see Supp.\ Fig.~\corrmats).
 The yellow boxes highlight the maximum correlation in each column.

### 2020-10-16 paper/supplementary_information.tex
added caption for new supplemental figure, formatting edits

--- 2020-10-14 paper/supporting_information.tex
@@
 \newpage
-\begin{centering}
+%\begin{centering}
+%  \vspace*{\fill}
+  \section*{Supplementary figures}
+
+\newpage
+\begin{figure}[tp]
+\centering
+%\includegraphics[width=1\textwidth]{figs/}
+\caption{\small \textbf{Methods detail for recall trajectory analysis displayed in Figure~\trajectories B} \textbf{A.} This panel replicates Figure~\trajectories B in the \textit{Main text}, but with two additions.
+First, individual participants' recall trajectories are displayed (faintly) as light gray lines.
+Second, three locations on the trajectory have been highlighted (blue, yellow, and red circles).
+\textbf{B.}  These zoomed-in views of the locations highlighted in Panel A show the average trajectory (black) and individual participants' trajectories (gray lines) that intersect the given region of topic space.
+\textbf{C.} For each circular region of topic space tiling the 2D embedding plane displayed in Panel A, we compute the distribution of angles formed between each participant's trajectory segment (i.e., the point at which the trajectory enters and exists the region of topic space) and the $x$-axis.
+The distributions of angles for these three example regions are displayed in the colored rose plots.
+We use Rayleigh tests to assign an arrow direction, length, and color for that region of topic space.
+Arrows displayed in blue are significant at the $p < 0.05$ level (corrected).
+The arrow directions are oriented according to the circular means of each distribution, and the arrow lengths are proportional to the lengths of those mean vectors.
+The example regions have been oriented from left to right in decreasing order of consistency across participants.}
+\label{fig:arrows-methods}
+\end{figure}
 \vspace*{\fill}
-  \section*{Supplementary figures}
+
+\newpage
     \subsection*{Participant-level figures referenced in the main text}
-    \vspace*{\fill}
-  \end{centering}
+    %\vspace*{\fill}
+  %\end{centering}
 

### 2020-10-16 paper/main.tex
updated supp fig numbers
added caption for new supplemental figure, formatting edits
udpated notes on formatting checklist, minor edits to main text

--- 2020-10-14 paper/main.tex
@@
 \newcommand{\featureimportance}{3}
-\newcommand{\corrmats}{4}
-\newcommand{\matchmats}{5}
-\newcommand{\kopt}{6}
-\newcommand{\arrows}{7}
+\newcommand{\corrmats}{5}
+\newcommand{\matchmats}{6}
+\newcommand{\kopt}{7}
+\newcommand{\arrows}{4}
 
@@
 Participants with higher temporal clustering scores tended to exhibit better overall memory for the episode, according to both Chen et al.
-(2017)~\cite{ChenEtal17}'s hand-counted numbers of recalled scenes from the episode (Pearson's $r(15) = 0.49,~p = 0.046,~95\%~CI~[0.25, 0.76]$) and the numbers of episode events that best-matched at least one recall event (i.e., model-estimated number of events recalled; Pearson's $r(15) = 0.59,~p = 0.013,~95\%~CI~[0.31, 0.80]$).
+(2017)~\cite{ChenEtal17}'s hand-counted numbers of recalled scenes from the episode (Pearson's $r(15) = 0.49,~p = 0.046,~95\%~\mathrm{CI} = [0.25, 0.76]$) and the numbers of episode events that best-matched at least one recall event (i.e., model-estimated number of events recalled; Pearson's $r(15) = 0.59,~p = 0.013,~95\%~\mathrm{CI} = [0.31, 0.80]$).
 Semantic clustering measures the extent to which participants cluster their recall responses according to semantic similarity~\citep{MannKaha12}.
-We found that participants tended to recall semantically similar episode events together (mean clustering score: 0.650, SEM: 0.032), and that semantic clustering score was also related to both hand-counted  (Pearson's $r(15) = 0.65,~p = 0.004,~95\%~CI~[0.31, 0.85]$) and model-estimated (Pearson's $r(15) = 0.58,~p = 0.015,~95\%~CI~[0.10, 0.83]$) numbers of recalled events.
+We found that participants tended to recall semantically similar episode events together (mean clustering score: 0.650, SEM: 0.032), and that semantic clustering score was also related to both hand-counted  (Pearson's $r(15) = 0.65,~p = 0.004,~95\%~\mathrm{CI} = [0.31, 0.85]$) and model-estimated (Pearson's $r(15) = 0.58,~p = 0.015,~95\%~\mathrm{CI} = [0.10, 0.83]$) numbers of recalled events.
 
@@
 This enables us to quantify how precisely a participant tended to recall subtle within-event details, as well as how specific (distinctive) those details were to individual events from the episode.
-Participants' average precision and distinctiveness scores were strongly correlated ($r(15) = 0.90,~p < 0.001,~95\%~CI~[0.66, 0.96]$).
+Participants' average precision and distinctiveness scores were strongly correlated ($r(15) = 0.90,~p < 0.001,~95\%~\mathrm{CI} = [0.66, 0.96]$).
 This indicates that participants who tended to precisely recount low-level details of episode events also tended to do so in an event-specific way (e.g., as opposed to detailing recurring themes that were present in most or all episode events; this behavior would have resulted in high precision but low distinctiveness).
-We found that, across participants, higher precision scores were positively correlated with the numbers of both hand-annotated scenes ($r(15) = 0.60,~p = 0.010,~95\%~CI~[0.02, 0.83]$) and model-estimated events ($r(15) = 0.90,~p < 0.001,~95\%~CI~[0.54, 0.96]$) that participants recalled.
-Participants' average distinctiveness scores were also marginally correlated with both the hand-annotated ($r(15) = 0.45,~p = 0.068,~95\%~CI~[-0.21, 0.79]$) and model-estimated ($r(15) = 0.71,~p = 0.001,~95\%~CI~[-0.07, 0.90]$) numbers of recalled events.
+We found that, across participants, higher precision scores were positively correlated with the numbers of both hand-annotated scenes ($r(15) = 0.60,~p = 0.010,~95\%~\mathrm{CI} = [0.02, 0.83]$) and model-estimated events ($r(15) = 0.90,~p < 0.001,~95\%~\mathrm{CI} = [0.54, 0.96]$) that participants recalled.
+Participants' average distinctiveness scores were also marginally correlated with both the hand-annotated ($r(15) = 0.45,~p = 0.068,~95\%~\mathrm{CI} = [-0.21, 0.79]$) and model-estimated ($r(15) = 0.71,~p = 0.001,~95\%~\mathrm{CI} = [-0.07, 0.90]$) numbers of recalled events.
 
@@
 In this case, we were specifically interested in identifying voxels whose activation time series reflected the temporal structure of the episode and recall topic proportions matrices to a greater extent than that of the phase-shifted matrices.
+The 95\% confidence intervals we reported for each correlation were estimated by generating 10000 ``bootstrap'' distributions of correlation coefficients by sampling (with replacement) from the observed data.
 
@@
 Chen et al.~(2017)~\cite{ChenEtal17} used this method to rate each participant's memory quality by computing the proportion of (50 manually identified) scenes mentioned in their recall.
-We found a strong across-participants correlation between these independent ratings and the proportion of 30 HMM-identified episode events matched to participants' recalls (Pearson's $r(15) = 0.71, p = 0.002,~95\%~CI~[0.39, 0.88]$).
+We found a strong across-participants correlation between these independent ratings and the proportion of 30 HMM-identified episode events matched to participants' recalls (Pearson's $r(15) = 0.71, p = 0.002,~95\%~\mathrm{CI} = [0.39, 0.88]$).
 We further considered a number of more nuanced memory performance measures that are typically associated with list-learning studies.

### 2020-10-16 paper/main.tex
minor typo fixes in main document, regenerated diffs

@@
 Specifically, our approach yielded (via the topic proportions matrix) a single ``topic vector'' for each sliding window of annotations transformed by the topic model.
-We then stretched (interpolated) the resulting windows-by-topics matrix to match the time series of the 1,976 fMRI volumes collected as participants viewed the episode.
+We then stretched (interpolated) the resulting windows-by-topics matrix to match the time series of the 1976 fMRI volumes collected as participants viewed the episode.
 
@@
 Semantic clustering measures the extent to which participants cluster their recall responses according to semantic similarity~\citep{MannKaha12}.
-We found that participants tended to recall semantically similar episode events together (mean clustering score: 0.650, SEM: 0.032), and that semantic clustering score was also related to both hand-counted  (Pearson's $r(15) = 0.65,~p = 0.004,~95\%~\mathrm{CI} = [0.31, 0.85]$) and model-estimated (Pearson's $r(15) = 0.58,~p = 0.015,~95\%~\mathrm{CI} = [0.10, 0.83]$) numbers of recalled events.
+We found that participants tended to recall semantically similar episode events together (mean clustering score: 0.650, SEM: 0.032), and that semantic clustering scores were also related to both hand-counted  (Pearson's $r(15) = 0.65,~p = 0.004,~95\%~\mathrm{CI} = [0.31, 0.85]$) and model-estimated (Pearson's $r(15) = 0.58,~p = 0.015,~95\%~\mathrm{CI} = [0.10, 0.83]$) numbers of recalled events.
 
@@
 Intuitively, distinctiveness is like a normalized variant of our precision metric.
-Whereas precision solely measures how much detail about an episode was captured in someone's recall, distinctiveness penalizes details that also pertain to other episode events.
+Whereas precision solely measures how much detail about an event was captured in someone's recall, distinctiveness penalizes details that also pertain to other episode events.
 We define the distinctiveness of an event's recall as its precision expressed in standard deviation units with respect to other episode events.
@@
 We extracted the set of sentences comprising the most distinctive recall event (P9) and least distinctive recall event (P6) corresponding to the example episode event shown in Panel C (event 21).
-We also extracted the annotations for all episode events whose content these participants' single recall events described.
+We also extracted the annotations for all episode events whose content these participants' single recall events touched on.
 We assigned each episode event a unique color (Fig.~\ref{fig:precision-detail}E), and colored each recalled sentence (Panel F) according to the episode events they best matched.
@@
 The results displayed in Figures \ref{fig:list-learning}C and \ref{fig:precision-detail}A suggest that certain events were remembered better than others.
-Given this, we next asked asked whether the events that were generally remembered precisely or imprecisely tended to reflect particular content.
+Given this, we next asked whether the events that were generally remembered precisely or imprecisely tended to reflect particular content.
 Because our analysis framework projects the dynamic episode content and participants' recalls into a shared space, and because the dimensions of that space represent topics (which are, in turn, sets of weights over known words in the vocabulary), we are able to recover the weighted combination of words that make up any point (i.e., topic vector) in this space.
@@
 We then computed a weighted average of the topic vectors for each episode event, where the weights reflected how precisely each event was recalled.
-To visualize the result, we created a ``wordle'' image~\citep{MuelEtal18} where words weighted more heavily by more precisely-remembered topics appear in a larger font (Fig.~\ref{fig:topics}B, green box).
+To visualize the result, we created a ``wordle'' image~\citep{MuelEtal18} where words weighted more heavily by more precisely remembered topics appear in a larger font (Fig.~\ref{fig:topics}B, green box).
 Across the full episode, content that weighted heavily on topics and words central to the major foci of the episode (e.g., the names of the two main characters, ``Sherlock'' and ``John,'' and the address of a major recurring location, ``221B Baker Street'') was best remembered.

### 2020-10-22 paper/main.tex
replaced data and code hyperlinks in with urls

@@
 \section*{Data availability}
-The fMRI data we analyzed are available online \href{http://dataspace.princeton.edu/jspui/handle/88435/dsp01nz8062179}{\underline{here}}.
-The behavioral data is available  \href{https://github.com/ContextLab/sherlock-topic-model-paper}{\underline{here}}.
+The fMRI data we analyzed are available online at:
+
+https://dataspace.princeton.edu/jspui/handle/88435/dsp01nz8062179
+
+\noindent The behavioral data is available at:
+
+https://github.com/ContextLab/sherlock-topic-model-paper/tree/master/data/raw
 
 \section*{Code availability}
-All of our analysis code may be downloaded \href{https://github.com/ContextLab/sherlock-topic-model-paper}{\underline{here}}.
+All of our analysis code may be downloaded from:
+
+https://github.com/ContextLab/sherlock-topic-model-paper
 

### 2020-10-22 paper/main.tex
disable figure placement markers
fixed phrasing of reporting margially significant correlation

@@
 \usepackage{placeins}
-\usepackage[nofiglist, fighead]{endfloat}
+\usepackage[nofiglist, nomarkers, fighead]{endfloat}
 \renewcommand{\includegraphics}[2][]{}
@@
 This indicates that participants who tended to precisely recount low-level details of episode events also tended to do so in an event-specific way (e.g., as opposed to detailing recurring themes that were present in most or all episode events; this behavior would have resulted in high precision but low distinctiveness).
-We found that, across participants, higher precision scores were positively correlated with the numbers of both hand-annotated scenes ($r(15) = 0.60,~p = 0.010,~95\%~\mathrm{CI} = [0.02, 0.83]$) and model-estimated events ($r(15) = 0.90,~p < 0.001,~95\%~\mathrm{CI} = [0.54, 0.96]$) that participants recalled.
-Participants' average distinctiveness scores were also marginally correlated with both the hand-annotated ($r(15) = 0.45,~p = 0.068,~95\%~\mathrm{CI} = [-0.21, 0.79]$) and model-estimated ($r(15) = 0.71,~p = 0.001,~95\%~\mathrm{CI} = [-0.07, 0.90]$) numbers of recalled events.
+We found that, across participants, higher precision scores were positively correlated with the numbers of both model-estimated events ($r(15) = 0.90,~p < 0.001,~95\%~\mathrm{CI} = [0.54, 0.96]$) and hand-annotated scenes ($r(15) = 0.60,~p = 0.010,~95\%~\mathrm{CI} = [0.02, 0.83]$) that participants recalled.
+Participants' average distinctiveness scores were also correlated with their numbers of model-estimated recalled events ($r(15) = 0.71,~p = 0.001,~95\%~\mathrm{CI} = [-0.07, 0.90]$) and marginally significantly correlated with their numbers of hand-annotated ($r(15) = 0.45,~p = 0.068,~95\%~\mathrm{CI} = [-0.21, 0.79]$).
 

### 2020-10-23 paper/supplementary_information.tex
recompiled diff file

@@
 
+\subsubsection*{Binary features}
+Two categories of annotations, ``Music presence'' and ``Indoor vs outdoor,'' comprise a single word that can each take on one of two possible values (music: ``yes'' or ``no''; indoor vs outdoor: ``indoor'' or ``outdoor'').
+Participants are unlikely to use the words ``yes'' or ``no'' to specifically refer to the presence or absence of music when they recount the episode.
+In fact, the word ``no'' is filtered out at the start of our analysis pipeline (see \textit{Methods}), since it appears so frequently throughout the annotations and recalls that it cannot provide reliable event-specific information.
+
+In contrast, the word ``yes'' is a comparatively rare word (both in the episode annotations and participants’ recall transcripts).
+The rarity of the word ``yes'' in the annotations makes it a potentially informative feature for the topic models.
+For example, the presence of music often co-occurs with the presence of specific characters, actions, locations, and plot elements.
+In this way, the ``Music presence'' annotations provide a (likely relatively weak) signal for when these associated themes appear.
+Further, when participants reference those themes in their recalls through their uses of other words associated with those themes (e.g., even if they don’t specifically use the word ``yes''), our modeling framework will still ``match'' references to music-related themes (i.e., semantic features or topics in the episode that co-occur with the presence or absence of music) with other words associated with those semantic features or topics.
+
+The ``Indoor vs outdoor'' annotations are treated similarly.
+Again, although participant may not refer to a particular scene as having taken place indoors versus outdoors, they may refer to other themes that co-occur with these annotations.
+In general, the notion that annotations and recalls do not need to use the same words (or in the same ways)—is a central feature of our modeling framework.
+We think solving the ``matching problem'' (i.e., labeling specific things participants say with specific events they experienced) in a way that is robust to wording differences is an important advance in studying naturalistic memory behaviors.
+
 \subsection*{Creating a low-dimensional embedding space}
@@
 
+\subsection*{Additional comments on the searchlight analyses (Fig.~\brains)}
+The final ``stage'' shown for the episode template pipeline (Fig.
+\brains A) displays the correlations between pairs of episode topic vectors at nearby timepoints, while the final stage shown for the recall template pipeline (Fig.
+\brains B) displays the correlations between pairs of recall topic vectors at nearby timepoints.
+The ``proximal correlation matrices'' we mention in the figure and main text denote that we have taken temporal autocorrelation matrices and masked out everything above the $n$th diagonal (where $n$ is the duration, in TRs, of the longest episode event).
+When we say ``correlations at nearby timepoints,'' we are referring to the unmasked parts of these proximal correlation matrices.
+
+To compute proximal correlation matrices for the episode, or for a given searchlight’s activity patterns, we simply correlate the topic vectors (or voxel responses) from every pair of timepoints, and then mask out anything beyond the $n$th diagonal.
+In this way, the RSA analysis that we designed to identify searchlights whose responses show a similar (proximal) correlation structure to the episode’s topics (Fig.
+\brains C) does not require any further temporal alignment, since both the topic timeseries and voxel responses are computed at the same timepoints.
+
+However, computing the proximal correlation matrix for participants’ recalls requires an additional ``warping'' step to bring the behavioral data (during recall) and neural data (while viewing the episode) into temporal alignment.
+For example, different participants take different amounts of time to recount the episode, and their transcripts have different lengths.
+These differences occur at the ``episode'' level (i.e., with respect to total recall duration and/or transcript length) and also at the ``event'' level (i.e., a given participant's recounting of a particular event may be more or less detailed, and take more or less time, than another participant's recounting of the same event).
+The purpose of the warping step is to temporally stretch or compress the topic timecourse of each participants’ recounting so that it is temporally aligned with the voxel responses recorded as the participants were watching the episode.
+That warping step is what we are highlighting in the two rightmost matrices in Figure~\brains B.
+
+The transition between the 1st and 2nd stage of the pipeline shown in Figure~\brains B shows the effect of using dynamic time warping to temporally align an example participant’s recall topic proportions matrix with the episode’s topic proportions matrix.
+The rightmost matrix (stage 1) shows the correlation between the topic vectors for each unwarped recall timepoint (i.e., sliding text window) and each episode timepoint (TR).
+The middle matrix (stage 2) shows the correlation between the topic vectors for each warped recall timepoint (i.e., TR) and each episode timepoint (TR).
+In both matrices, the row (episode timepoint) matched to each column (recall timepoint) by the dynamic time warping algorithm is indicated in yellow.
+We chose to visualize this step by correlating the example recall trajectory with the episode (rather than with itself, as in the other matrices) before versus after warping.
+We felt this would help to illustrate how the diagonal ``straightens'' as a result of the non-linear ``stretching'' the algorithm performs to align the two timeseries.
+An important feature of the warping algorithm is that it is a monotonic transformation-- i.e., it does not change the relative orders of the recalled timepoints; it only stretches or compresses different parts of the recall topic proportions matrix while preserving its temporal order.
+
+The 3rd (leftmost) stage shown in Fig.~\brains B then displays the proximal correlation matrix for the example participant’s recalls.
+In other words, we computed the correlation matrix for that participant’s warped recall topic proportions (i.e., after they have been temporally aligned to the episode), and then masked out everything beyond the $n$th diagonal.
+We label axes corresponding to the warped recall trajectory as “Warped recall time (TR)” rather than “Viewing time (TR)” to help differentiate them from axes corresponding to the episode trajectory, as well as to maintain consistency with how we labeled video-recall and recall-recall correlation matrices in other figures.
+
 % \FloatBarrier
@@
 
-\newpage
 \begin{figure}[tp]
 \centering
-%\includegraphics[width=1\textwidth]{figs/}
+\includegraphics[width=0.6\textwidth]{figs/topic_space_flow}
 \caption{\small \textbf{Methods detail for recall trajectory analysis displayed in Figure~\trajectories B} \textbf{A.} This panel replicates Figure~\trajectories B in the \textit{Main text}, but with two additions.
@@
 We use Rayleigh tests to assign an arrow direction, length, and color for that region of topic space.
-Arrows displayed in blue are significant at the $p < 0.05$ level (corrected).
+Arrows displayed in color are significant at the $p < 0.05$ level (corrected).
 The arrow directions are oriented according to the circular means of each distribution, and the arrow lengths are proportional to the lengths of those mean vectors.

### 2020-11-23 paper/supplementary_information.tex

@@
 where $\mathrm{corr}(\mu, \nu)$ is the per-participant correlation between the episode ($\mu$) and recall ($\nu$) topic proportions matrices, and $\theta$ is the per-participant hand-counted number of recalled scenes.
-We searched over a grid of pre-specified values for each of these parameters; the resulting correlations are displayed in Figure~\ref{fig:paramsearch}.
+We searched over a grid of pre-specified values for each of these parameters; the resulting correlations are displayed in Supplementary Figure~\ref{fig:paramsearch}.
 The optimal parameters were $\omega = 50$, $\rho = 10$, and $K = 100$.
@@
 
-The optimized model converged on 32 unique topics that were assigned non-zero weights.  We provide a list of the top ten highest-weighted words from each topic in Figure~\ref{fig:topics}.
+The optimized model converged on 32 unique topics that were assigned non-zero weights.
+We provide a list of the top ten highest-weighted words from each topic in Supplementary Figure~\ref{fig:topics}.
 
@@
 Observing a lower correlation between an impoverished matrix (with a particular feature removed) and the feature-complete matrix would suggest that the held-out feature contributed more prominently to the full episode topic proportion matrix's temporal structure.
-We found that hand-annotated narrative details played the greatest roll in determining the temporal structure of the episode, whereas the name of the character(s) in focus for each shot contributed least (Fig.~\ref{fig:feature-importance}A).
+We found that hand-annotated narrative details played the greatest roll in determining the temporal structure of the episode, whereas the name of the character(s) in focus for each shot contributed least (Supp.
+Fig.~\ref{fig:feature-importance}A).
 
@@
 Observing a lower correlation between the episode and recall topic proportions matrices (constructed in the absence of a given feature) would indicate that participants utilize changes in that feature's content to discriminate between sections of the episode when organizing their recalls.
-We found that hand-annotated narrative details were the most heavily utilized feature, whereas changes in the text present on-screen, the indoor/outdoor distinction between shots, the camera angle, the names of the various characters on screen, and the shot's location tended not to impact participants' recall structures (i.e., removing those features resulted in a \textit{greater} episode-recall correlation than including them; Fig.~\ref{fig:feature-importance}B).
+We found that hand-annotated narrative details were the most heavily utilized feature, whereas changes in the text present on-screen, the indoor/outdoor distinction between shots, the camera angle, the names of the various characters on screen, and the shot's location tended not to impact participants' recall structures (i.e., removing those features resulted in a \textit{greater} episode-recall correlation than including them; Supp.
+Fig.~\ref{fig:feature-importance}B).
 
@@
 We also found that character-driven features (characters on screen, characters speaking, and characters in focus) were strongly correlated.
-Other details, such as the presence or absence of music, led to very different topic proportions matrices (Fig.~\ref{fig:feature-importance}C).
+Other details, such as the presence or absence of music, led to very different topic proportions matrices (Supp.
+Fig.~\ref{fig:feature-importance}C).
 %\FloatBarrier
@@
 \includegraphics[width=\textwidth]{figs/matchmats}
-\caption{\small \textbf{Episode-recall event correlation matrices.}  Each panel is in the same format as Figure~2G in the main text.
+\caption{\small \textbf{Episode-recall event correlation matrices.}  Each panel is in the same format as Figure~\topicprops G in the main text.
 The yellow boxes mark the matched episode event for each recall event (i.e., the maximum correlation in each column).}

### 2020-11-24 paper/main.tex

@@
 \begin{abstract}
+How do we preserve and distort our ongoing experiences when encoding them into episodic memories?
 The mental contexts in which we interpret experiences are often person-specific, even when the experiences themselves are shared.
@@
 We also identified networks of brain structures sensitive to these trajectory shapes.
-Our work provides insights into how we preserve and distort our ongoing experiences when we encode them into episodic memories.
 \end{abstract}

### 2020-11-24 paper/extended_data.tex
moved supp figs 4-7 to extended data doc

--- 2020-10-16 paper/supplementary_information.tex
@@
 
-\newcommand{\argmax}{\mathop{\mathrm{argmax}}\limits}
-\newcommand{\argmin}{\mathop{\mathrm{argmin}}\limits}
-
 \newcommand{\methodsdemo}{1}
@@
 
-\title{\textit{Supporting Information for}: Geometric models reveal behavioral and neural signatures of transforming experiences into memories}
-\author{Andrew C.
-Heusser\textsuperscript{1, 2, \textdagger}, Paxton C.
-Fitzpatrick\textsuperscript{1, \textdagger}, and Jeremy R.
-Manning\textsuperscript{1, *}\\\textsuperscript{1}Department of Psychological and Brain Sciences\\Dartmouth College, Hanover, NH 03755, USA\\\textsuperscript{2}Akili Interactive Labs\\Boston, MA 02110, USA\\\textsuperscript{\textdagger}Denotes equal contribution\\\textsuperscript{*}Corresponding author: Jeremy.R.Manning@Dartmouth.edu}
-
 \bibliographystyle{apa}
@@
 \begin{document}
+\renewcommand{\figurename}{Supplementary Figure}
+\setcounter{figure}{3}
+\setcounter{page}{1}
+\makeatletter
 
-\renewcommand{\figurename}{Supplementary Figure}
-
-%\begin{titlepage}
-%  \maketitle
-%  \thispagestyle{empty}
-%\end{titlepage}
-
-\setcounter{equation}{0}
-\setcounter{figure}{0}
-\setcounter{table}{0}
-\setcounter{page}{1}
-\setcounter{section}{0}
-\makeatletter
-%\renewcommand{\theequation}{S\arabic{equation}}
-%\renewcommand{\thefigure}{S\arabic{figure}}
-\renewcommand{\bibnumfmt}[1]{[S#1]}
-\renewcommand{\citenumfont}[1]{S#1}
-
-%\section*{Overview}
-%This document provides additional details about the methods we used in the main text.  We also %include some additional analyses referenced in the main text.
-
-\section*{Supplementary methods}
-\subsection*{Optimizing topic model parameters}
-In order to create accurate episode and recall models, we used an optimization method that was driven by our ability to explain hand-annotated memory performance metrics collected by \cite{ChenEtal17}.
-In an earlier variant of our study~\citep{HeusMann18}, we used a grid search to compute the $\omega$ (episode sliding window duration, in scenes), $\rho$ (recall sliding window duration, in sentences), and $K$ (number of topics) that satisfied
-\[
-\argmax_{\omega, \rho, K} \left[\mathrm{corr}\left(\mathrm{corr}\left(\mu\left(\omega, \rho, K\right), \nu\left(\omega, \rho, K\right)\right), \theta\right)\right],
-\]
-where $\mathrm{corr}(\mu, \nu)$ is the per-participant correlation between the episode ($\mu$) and recall ($\nu$) topic proportions matrices, and $\theta$ is the per-participant hand-counted number of recalled scenes.
-We searched over a grid of pre-specified values for each of these parameters; the resulting correlations are displayed in Figure~\ref{fig:paramsearch}.
-The optimal parameters were $\omega = 50$, $\rho = 10$, and $K = 100$.
-In our current paper we made a number of improvements to how we preprocessed text and fit topic models (see \textit{Methods}), but we carried the same optimal parameters forward from \cite{HeusMann18} without performing any additional optimization.
-
-\begin{figure}[b]
-\centering
-\includegraphics[width=1\textwidth]{figs/parameter_search}
-\caption{\small \textbf{Optimizing topic model parameters.}  We performed a grid search over episode sliding window length ($\omega \in \{5, 10, 25, 50, 100 \}$), recall sliding window length ($\rho \in \{5, 10, 25, 50, 100 \}$), and number of topics ($K \in \{5, 10, 25, 50, 100 \}$).
-The reported correlations are between per-participant episode-recall correlations and per-participant hand-counted numbers of recalled scenes.}
-\label{fig:paramsearch}
-\end{figure}
-
-The optimized model converged on 32 unique topics that were assigned non-zero weights.  We provide a list of the top ten highest-weighted words from each topic in Figure~\ref{fig:topics}.
-
-\begin{figure}[p]
-\centering
-\includegraphics[width=0.65\textwidth]{figs/topic_words}
-\caption{\small \textbf{Topics discovered in \textit{Sherlock}.} We applied a topic model to hand-annotated information about 1000 scenes spanning the 48-minute episode.
-We identified 32 unique topics with non-zero weights (we used $K=100$ topics to fit the model).
-Each topic comprises a distribution of weights over all words in the vocabulary.
-For each topic, we show the words with the 10 largest weights, along with a suggested description of the topic.}
-\label{fig:topics}
-\end{figure}
-%\FloatBarrier
-
-\subsection*{Feature importance analyses}
-To determine the contribution of each feature to the temporal structure of the episode topic proportions matrix, we conducted a ``leave one out'' analysis.
-Specifically, we compared the original episode's topic proportions matrix (created using all hand-annotated features from the 998 manually identified scenes spanning the \textit{Sherlock} episode; see \textit{Methods} for a full list of features) with topic proportions matrices created using all but one type of feature.
-For each impoverished topic proportions matrix, we computed the timepoint-by-timepoint correlation matrix, and correlated the proximal diagonals from the upper triangle with those from the temporal correlation matrix of the feature-complete matrix (for details on how we isolated proximal temporal correlations, see \textit{Methods}).
-Observing a lower correlation between an impoverished matrix (with a particular feature removed) and the feature-complete matrix would suggest that the held-out feature contributed more prominently to the full episode topic proportion matrix's temporal structure.
-We found that hand-annotated narrative details played the greatest roll in determining the temporal structure of the episode, whereas the name of the character(s) in focus for each shot contributed least (Fig.~\ref{fig:feature-importance}A).
-
-\begin{figure}[]
-\centering
-\includegraphics[width=1\textwidth]{figs/feature_value}
-\caption{\small \textbf{Feature importance analysis.} \textbf{A.} Contributions of each feature type to the structure of the episode topic proportions matrix.
-The bar heights reflect the correlation between the proximal temporal structure (see \textit{Methods}) of the episode topic proportions matrix computed using all features, and that of an episode topic proportions matrix computed using all features except the indicated feature.
-Lower bars reflect features that contribute more substantially to the episode's temporal structure.
-\textbf{B.} Which features are preserved during recall?
-The bar heights reflect the (average) across-participant correlations between the proximal temporal structure of episode and recall topic proportions matrices constructed in the absence of the given feature.
-Error bars denote standard error of the mean.
-\textbf{C.} Feature correlation matrix.
-Each entry displays the correlation between episode topic portions matrices created using only the indicated (row/column) features.}
-\label{fig:feature-importance}
-\end{figure}
-
-Next, we sought to determine which annotated features contributed aspects of the episode's temporal structure that were preserved in participants' later recalls.
-Specifically, we computed the timepoint-by-timepoint correlation matrix of the episode's topic proportions matrix, and correlated the proximal diagonals from its upper triangle with those from the timepoint-by-timepoint correlation matrices for each participant's recall topic proportions matrices (stretched via linear interpolation to have the same number of timepoints as the episode topic proportions matrix).
-This yielded a single correlation coefficient for each participant.
-We then repeated this analysis with each annotated feature held out in turn.
-Observing a lower correlation between the episode and recall topic proportions matrices (constructed in the absence of a given feature) would indicate that participants utilize changes in that feature's content to discriminate between sections of the episode when organizing their recalls.
-We found that hand-annotated narrative details were the most heavily utilized feature, whereas changes in the text present on-screen, the indoor/outdoor distinction between shots, the camera angle, the names of the various characters on screen, and the shot's location tended not to impact participants' recall structures (i.e., removing those features resulted in a \textit{greater} episode-recall correlation than including them; Fig.~\ref{fig:feature-importance}B).
-
-We also wondered how the different types of features might relate.
-For example, knowing which character is in focus during a given scene may also provide information about which character is speaking.
-We computed topic proportions matrices from the annotations for each individual feature, in turn, and (using the same technique as in the above analyses) compared the proximal temporal correlation structure of each single-feature topic proportions matrix to each other, as well as to that of the full episode.
-This provided additional confirmation that the full episode's temporal structure was largely driven by narrative details.
-We also found that character-driven features (characters on screen, characters speaking, and characters in focus) were strongly correlated.
-Other details, such as the presence or absence of music, led to very different topic proportions matrices (Fig.~\ref{fig:feature-importance}C).
-%\FloatBarrier
-
-\subsection*{Creating a low-dimensional embedding space}
-Figures~\trajectories~and~\wordles C in the main text display two-dimensional projections of the 100-dimensional topic trajectories for the episode (Figs.~\trajectories A,~\wordles C), average recall (Fig.~\trajectories B), and each individual's recall (Figs.~\trajectories C,~\wordles C).
-We created these embeddings using the Uniform Manifold Approximation and Projection algorithm \citep[UMAP;][]{McInEtal18} called from our high-dimensional visualization and text analysis software, \texttt{HyperTools}~\citep{HeusEtal18a}.
-An advantage of the UMAP algorithm over comparable manifold learning techniques (e.g., $t$-SNE) is that UMAP explicitly attempts to preserve the global structure of the data \citep{McInEtal18,BechEtal19} by constructing a space where distance on the manifold is standard Euclidean distance, with respect to the global coordinate system.
-This was important in our use case, as we wanted to visualize both the evolving structure of the episode and the spatial relationships between presented and recalled content.
-
-UMAP achieves a balance between representing local and global structure via a subset of its hyperparameters: \texttt{n\_neighbors} , \texttt{spread}, and \texttt{min\_dist}.
-The \texttt{n\_neighbors} hyperparameter ($K$) denotes the number of nearest neighbors to consider in constructing the high-dimensional fuzzy simplicial set for each datapoint.
-The \texttt{spread} ($\gamma$) and \texttt{min\_dist} ($\delta$) hyperparameters function together to create the differentiable decay curve used to approximate the injective function for mapping between high- and low-dimensional fuzzy simplicial sets.
-In brief, \texttt{min\_dist} determines the degree to which nearby points are clustered or expanded, relative to to the overall \texttt{spread}.
-
-Two other parameters ultimately affect this balance between preserving local versus global structure: the seed ($\tau$) for the (pseudo-)random number generator (RNG), and the order of the observations (i.e., trajectories) to be embedded ($\varphi$).
-As described in \textit{Methods}, we ensured the episode and recall events were projected onto the \textit{same} low-dimensional manifold by fitting the embedding model to a stacked matrix of all episode, average recall, and individuals' recall events.
-After initializing the low-dimensional simplicial set (by default, using a spectral embedding of the high-dimensional simplicial set's fuzzy 1-skeleton), UMAP optimizes the embedding using stochastic gradient descent with cross-entropy as a cost function.
-During optimization, indices of the data are sampled at random, and thus the local minimum achieved by the optimization is dependent on both the state of the RNG and the sequence in which observations are concatenated.
-
-We performed a grid search over pre-specified values of these hyperparameters, and optimized the manifold space for visualization based on two criteria.
-First, the 2D embedding of the episode trajectory should reflect its original 100-dimensional structure as faithfully as possible.
-Second, the path traversed by the embedded episode trajectory should intersect itself a minimal number of times.
-The first criteria helps bolster the validity of visual intuitions about relationships between sections of episode content, based on their locations in the embedding space.
-The second criteria was motivated by the observed low off-diagonal values in the episode topic proportions matrix's temporal correlation matrix (suggesting that the same topic-space coordinates should not be revisited; see Figure~\topicprops A in the main text).
-Further, we found through simulation that our statistical procedure for testing the consistency of trajectory directions across participants (Fig.~\trajectories B, also see \textit{Methods}) can be confounded when and where the topic trajectory intersects itself.
-We formalized this optimization as the combination of hyperparameter values that satisfied
-\[
-\argmax_{\left\{K, \gamma, \delta, \tau, \varphi~\in~E~\mathrm{|}~\Phi\left(K, \gamma, \delta, \tau, \varphi \right) \right\}} \left[\mathrm{corr}\left(\Upsilon\left(\xi_{K, \gamma, \delta, \tau, \varphi}\right),~\Upsilon\left(\chi\right)\right)\right],~\mathrm{where}
-\]
-\[
-\Phi\left(K, \gamma, \delta, \tau, \varphi \right) = \argmin_{K, \gamma, \delta, \tau, \varphi} \left[\Gamma\left(\xi_{K, \gamma, \delta, \tau, \varphi}\right)\right],
-\]
-$\xi$ is the episode's trajectory through the manifold space; $\chi$ is the original, 100-dimensional episode trajectory; $\Upsilon$ is a function that computes a condensed matrix of pairwise distances between event vectors (computed using correlation distance in the original topic space and Euclidean distance in the manifold space); $\mathrm{corr}\left(\Upsilon\left(\xi\right), \Upsilon\left(\chi\right)\right)$ is the correlation between the sets of pairwise distances, and $\Gamma$ is the number of instances in which lines drawn between consecutive episode event embeddings intersected each other.
-The sets of hyperparameter values we searched over comprised: $K \in \{10x \in \mathbb{Z}~|~10 < x <  22\} \cup \{161\}$ (a range roughly centered on half the total number of events, 161, in order to balance representations of local and global structure); $\gamma \in \{1, 3, 5, 7, 9\}$; $\delta \in \{0.1, 0.3, 0.5, 0.7, 0.9\}$; $\tau \in \{x \in \mathbb{Z}~|~0 < x < 101\}$; and $\varphi \in {S\choose3},~\mathrm{where}~S=\{\mathrm{episode~events,~average~recall~events, individual~recall~events}\}$.
-The optimal parameters (that yielded $\Phi=0$) were $K=170$, $\gamma=7$, $\delta=0.7$, $\tau=41$, with the order of sequence $\varphi$ as the average recall events, episode events, and individuals' recall events, vertically concatenated, in order.
-
-% \FloatBarrier
-\newpage
-%\begin{centering}
-%  \vspace*{\fill}
-  \section*{Supplementary figures}
-
-\newpage
 \begin{figure}[tp]
 \centering
-%\includegraphics[width=1\textwidth]{figs/}
+\includegraphics[width=0.6\textwidth]{figs/topic_space_flow}
 \caption{\small \textbf{Methods detail for recall trajectory analysis displayed in Figure~\trajectories B} \textbf{A.} This panel replicates Figure~\trajectories B in the \textit{Main text}, but with two additions.
@@
 \end{figure}
-\vspace*{\fill}
+\FloatBarrier
 
@@
 \subsection*{Participant-level figures referenced in the main text}
-    %\vspace*{\fill}
-  %\end{centering}
+\vspace*{\fill}
 
@@
 \end{figure}
-
-\newpage
-\renewcommand{\refname}{Supplementary references}
-\bibliography{CDL-bibliography/memlab}
-
 \end{document}

### 2020-11-24 paper/supplementary_information.tex
moved supp figs 4-7 to extended data doc

@@
 
-% \FloatBarrier
-\newpage
-%\begin{centering}
-%  \vspace*{\fill}
-  \section*{Supplementary figures}
-
-\begin{figure}[tp]
-\centering
-\includegraphics[width=0.6\textwidth]{figs/topic_space_flow}
-\caption{\small \textbf{Methods detail for recall trajectory analysis displayed in Figure~\trajectories B} \textbf{A.} This panel replicates Figure~\trajectories B in the \textit{Main text}, but with two additions.
+%% \FloatBarrier
+%\newpage
+%%\begin{centering}
+%%  \vspace*{\fill}
+%  \section*{Supplementary figures}
+%
+%\begin{figure}[tp]
+%\centering
+%\includegraphics[width=0.6\textwidth]{figs/topic_space_flow}
+%\caption{\small \textbf{Methods detail for recall trajectory analysis displayed in Figure~\trajectories B} \textbf{A.} This panel replicates Figure~\trajectories B in the \textit{Main text}, but with two additions.
 First, individual participants' recall trajectories are displayed (faintly) as light gray lines.
@@
 The example regions have been oriented from left to right in decreasing order of consistency across participants.}
-\label{fig:arrows-methods}
-\end{figure}
-\vspace*{\fill}
-
-\newpage
-    \subsection*{Participant-level figures referenced in the main text}
+%\label{fig:arrows-methods}
+%\end{figure}
 %\vspace*{\fill}
-  %\end{centering}
-
-\begin{figure}[p!]
-\centering
-\includegraphics[width=\textwidth]{figs/corrmats}
-\caption{\small \textbf{Recall temporal correlation matrices and event segmentation fits.} Each panel is in the same format as Figure~\topicprops E in the main text.
+%
+%\newpage
+%    \subsection*{Participant-level figures referenced in the main text}
+%    %\vspace*{\fill}
+%  %\end{centering}
+%
+%\begin{figure}[p!]
+%\centering
+%\includegraphics[width=\textwidth]{figs/corrmats}
+%\caption{\small \textbf{Recall temporal correlation matrices and event segmentation fits.} Each panel is in the same format as Figure~\topicprops E in the main text.
 The yellow boxes indicate HMM-identified event boundaries.}
-\label{fig:corrmats}
-\end{figure}
-
-\begin{figure}[p!]
-\centering
-\includegraphics[width=\textwidth]{figs/matchmats}
-\caption{\small \textbf{Episode-recall event correlation matrices.}  Each panel is in the same format as Figure~\topicprops G in the main text.
+%\label{fig:corrmats}
+%\end{figure}
+%
+%\begin{figure}[p!]
+%\centering
+%\includegraphics[width=\textwidth]{figs/matchmats}
+%\caption{\small \textbf{Episode-recall event correlation matrices.}  Each panel is in the same format as Figure~\topicprops G in the main text.
 The yellow boxes mark the matched episode event for each recall event (i.e., the maximum correlation in each column).}
-\label{fig:matchmats}
-\end{figure}
-
-\begin{figure}[p!]
-\centering
-\includegraphics[width=.92\textwidth]{figs/k_optimization}
-\caption{\small \textbf{Episode and recall topic proportions matrix \textit{K}-optimization functions.}  We selected the optimal $K$-value for the episode and each recall topic proportions matrix using the formula described in \textit{Methods}.
+%\label{fig:matchmats}
+%\end{figure}
+%
+%\begin{figure}[p!]
+%\centering
+%\includegraphics[width=.92\textwidth]{figs/k_optimization}
+%\caption{\small \textbf{Episode and recall topic proportions matrix \textit{K}-optimization functions.}  We selected the optimal $K$-value for the episode and each recall topic proportions matrix using the formula described in \textit{Methods}.
 This computation resulted in a curve for each matrix, describing the Wasserstein distance between the distributions of within-event and across-event topic vector correlations, as a function of $K$.}
-\label{fig:k_optimization}
-\end{figure}
+%\label{fig:k_optimization}
+%\end{figure}
 

### 2020-11-26 paper/main.tex
removed date
moved extended data figs to main text file, renumbered, updated refs

@@
 \newcommand{\featureimportance}{3}
-\newcommand{\corrmats}{5}
-\newcommand{\matchmats}{6}
-\newcommand{\kopt}{7}
-\newcommand{\arrows}{4}
 
@@
 Manning\textsuperscript{1, *}\\\textsuperscript{1}Department of Psychological and Brain Sciences\\Dartmouth College, Hanover, NH 03755, USA\\\textsuperscript{2}Akili Interactive Labs\\Boston, MA 02110, USA\\\textsuperscript{\textdagger}Denotes equal contribution\\\textsuperscript{*}Corresponding author: Jeremy.R.Manning@Dartmouth.edu}
+
+\date{}
 
@@
 Event boundaries detected by the HMM are denoted in yellow (22 events detected).
-For similar plots for all participants, see Supplementary Figure~\corrmats.
+For similar plots for all participants, see Extended Data Figure~\ref{fig:corrmats}.
 \textbf{F.} Average topic vectors for each of the 22 recall events from the example participant.
 \textbf{G.} Correlations between the topic vectors for every pair of episode events (Panel C) and recall events (from the example participant; Panel F).
-For similar plots for all participants, see Supplementary Figure~\matchmats.
+For similar plots for all participants, see Extended Data Figure~\ref{fig:matchmats}.
 \textbf{H.} Average correlations between each pair of episode events and recall events (across all 17 participants).
@@
 We used the same HMM-based optimization procedure that we had applied to the episode's topic proportions matrix (see \textit{Methods}) to estimate an analogous set of event boundaries in the participant's recounting of the episode (outlined in yellow).
-We carried out this analysis on all 17 participants' recall topic proportions matrices (Supp.\ Fig.~\corrmats).
+We carried out this analysis on all 17 participants' recall topic proportions matrices (Extended Data Fig.~\ref{fig:corrmats}).
 
 Two clear patterns emerged from this set of analyses.
-First, although every individual participant's recalls could be segmented into discrete events (i.e., every individual participant's recall correlation matrix exhibited clear block diagonal structure; Supp.\ Fig.~\corrmats), each participant appeared to have a unique ``recall resolution,'' reflected in the sizes of those blocks.
+First, although every individual participant's recalls could be segmented into discrete events (i.e., every individual participant's recall correlation matrix exhibited clear block diagonal structure; Extended Data Fig.~\ref{fig:corrmats}), each participant appeared to have a unique ``recall resolution,'' reflected in the sizes of those blocks.
 While some participants' recall topic proportions segmented into just a few events (e.g., Participants P4, P5, and P7), others' segmented into many shorter-duration events (e.g., Participants P12, P13, and P17).
@@
 One potential explanation for this finding is that the topic models, trained only on episode annotations, do not capture topic proportions in participants' ``held-out'' recalls as accurately.
-A second possibility is that, whereas each event in the original episode was (largely) separable from the others (Fig.~\ref{fig:model}B), in transforming those separable events into memory, participants appeared to be integrating across multiple events, blending elements of previously recalled and not-yet-recalled content into each newly recalled event (Fig.~\ref{fig:model}E, Supp.\ Fig.~\corrmats)~\citep{MannEtal11, HowaEtal12, Mann19}.
+A second possibility is that, whereas each event in the original episode was (largely) separable from the others (Fig.~\ref{fig:model}B), in transforming those separable events into memory, participants appeared to be integrating across multiple events, blending elements of previously recalled and not-yet-recalled content into each newly recalled event (Fig.~\ref{fig:model}E, Extended Data Fig.~\ref{fig:corrmats})~\citep{MannEtal11, HowaEtal12, Mann19}.
 
@@
 Next, we asked whether some correspondence might be made between the specific content of the events the participants experienced while viewing the episode, and the events they later recalled.
-We labeled each recall event as matching the episode event with the most similar (i.e., most highly correlated) topic vector (Fig.~\ref{fig:model}G, Supp.\ Fig.~\matchmats).
+We labeled each recall event as matching the episode event with the most similar (i.e., most highly correlated) topic vector (Fig.~\ref{fig:model}G, Extended Data Fig.~\ref{fig:matchmats}).
 This yielded a sequence of ``presented'' events from the original episode, and a (potentially differently ordered) sequence of ``recalled'' events for each participant.
@@
   \includegraphics[width=1\textwidth]{figs/precision_distinctiveness}
-  \caption{\small \textbf{Novel content-based metrics of naturalistic memory: precision and distinctiveness.} \textbf{A.} The episode-recall correlation matrix for an example participant (P17), chosen for their large number of recall events (for analogous figures for other participants, see Supp.\ Fig.~\corrmats).
+  \caption{\small \textbf{Novel content-based metrics of naturalistic memory: precision and distinctiveness.} \textbf{A.} The episode-recall correlation matrix for an example participant (P17), chosen for their large number of recall events (for analogous figures for other participants, see Extended Data Fig.~\ref{fig:corrmats}).
 The yellow boxes highlight the maximum correlation in each column.
@@
 The arrows reflect the average transition direction through topic space taken by any participants whose trajectories crossed that part of topic space; blue denotes reliable agreement across participants via a Rayleigh test ($p < 0.05$, corrected).
-For additional detail see \textit{Methods} and Supplementary Figure~\arrows.
+For additional detail see \textit{Methods} and Extended Data Figure~\ref{fig:arrows-methods}.
 \textbf{C.} The recall topic trajectories (gray) taken by each individual participant (P1--P17).
@@
 To assess the consistency of these recall trajectories across participants, we asked: given that a participant's recall trajectory had entered a particular location in the reduced topic space, could the position of their next recalled event be predicted reliably?
-For each location in the reduced topic space, we computed the set of line segments connecting successively recalled events (across all participants) that intersected that location (see \textit{Methods}, Supp.\ Fig.~\arrows).
+For each location in the reduced topic space, we computed the set of line segments connecting successively recalled events (across all participants) that intersected that location (see \textit{Methods}, Extended Data Fig.~\ref{fig:arrows-methods}).
 We then computed (for each location) the distribution of angles formed by the lines defined by those line segments and a fixed reference line (the $x$-axis).
@@
 We computed the first Wasserstein distance ($W_{1}$, also known as ``Earth mover's distance''~\citep{Dobr70, RamdEtal17}) between these distributions for a large range of possible $K$-values (range [2, 50]), and selected the $K$ that yielded the maximum value.
-Figure~\ref{fig:model}B displays the event boundaries returned for the episode, and Supplementary Figure~\corrmats~displays the event boundaries returned for each participant's recalls.
-See Supplementary Figure \kopt~for the optimization functions for the episode and recalls.
+Figure~\ref{fig:model}B displays the event boundaries returned for the episode, and Extended Data Figure~\ref{fig:corrmats}~displays the event boundaries returned for each participant's recalls.
+See Extended Data Figure~\ref{fig:k_optimization}~for the optimization functions for the episode and recalls.
 After obtaining these event boundaries, we created stable estimates of the content represented in each event by averaging the topic vectors across timepoints between each pair of event boundaries.
@@
 \subsubsection*{Estimating the consistency of flow through topic space across participants}
-In Figure~\ref{fig:trajectory}B, we present an analysis aimed at characterizing locations in topic space that different participants move through in a consistent way (via their recall topic trajectories; also see Supp.\ Fig.~\arrows).
+In Figure~\ref{fig:trajectory}B, we present an analysis aimed at characterizing locations in topic space that different participants move through in a consistent way (via their recall topic trajectories; also see Extended Data Fig.~\ref{fig:arrows-methods}).
 The two-dimensional topic space used in our visualizations (Fig.~\ref{fig:trajectory}) comprised a $60 \times 60$ (arbitrary units) square.
@@
 To construct the episode template, we computed the correlations between the topic proportions estimated for every pair of TRs (prior to segmenting the topic proportions matrices into discrete events; i.e., the correlation matrix shown in Figs.~\ref{fig:model}B and \ref{fig:brainz}A).
-We constructed similar temporal correlation matrices for each participant's recall topic proportions matrix (Fig.~\ref{fig:model}D, Supp.\ Fig.~\corrmats).
+We constructed similar temporal correlation matrices for each participant's recall topic proportions matrix (Fig.~\ref{fig:model}D, Extended Data Fig.~\ref{fig:corrmats}).
 However, to correct for length differences and potential non-linear transformations between viewing time and recall time, we first used dynamic time warping~\citep{BernClif94} to temporally align participants' recall topic proportions matrices with the episode topic proportions matrix.
@@
 
+\begin{figure}
+\renewcommand{\figurename}{Extended Data Figure}
+\setcounter{figure}{0}
+\centering
+\includegraphics[width=0.6\textwidth]{figs/topic_space_flow}
+\caption{\small \textbf{Methods detail for recall trajectory analysis displayed in Figure~\ref{fig:trajectory}B} \textbf{A.} This panel replicates Figure~\ref{fig:trajectory}B, but with two additions.
+First, individual participants' recall trajectories are displayed (faintly) as light gray lines.
+Second, three locations on the trajectory have been highlighted (blue, yellow, and red circles).
+\textbf{B.}  These zoomed-in views of the locations highlighted in Panel A show the average trajectory (black) and individual participants' trajectories (gray lines) that intersect the given region of topic space.
+\textbf{C.} For each circular region of topic space tiling the 2D embedding plane displayed in Panel A, we compute the distribution of angles formed between each participant's trajectory segment (i.e., the point at which the trajectory enters and exists the region of topic space) and the $x$-axis.
+The distributions of angles for these three example regions are displayed in the colored rose plots.
+We use Rayleigh tests to assign an arrow direction, length, and color for that region of topic space.
+Arrows displayed in color are significant at the $p < 0.05$ level (corrected).
+The arrow directions are oriented according to the circular means of each distribution, and the arrow lengths are proportional to the lengths of those mean vectors.
+The example regions have been oriented from left to right in decreasing order of consistency across participants.}
+\label{fig:arrows-methods}
+\end{figure}
+
+\begin{figure}
+\renewcommand{\figurename}{Extended Data Figure}
+\setcounter{figure}{1}
+\centering
+\includegraphics[width=\textwidth]{figs/corrmats}
+\caption{\small \textbf{Recall temporal correlation matrices and event segmentation fits.} Each panel is in the same format as Figure~\label{fig:model}E.
+The yellow boxes indicate HMM-identified event boundaries.}
+\label{fig:corrmats}
+\end{figure}
+
+\begin{figure}
+\renewcommand{\figurename}{Extended Data Figure}
+\setcounter{figure}{2}
+\centering
+\includegraphics[width=\textwidth]{figs/matchmats}
+\caption{\small \textbf{Episode-recall event correlation matrices.}  Each panel is in the same format as Figure~\label{fig:model}G.
+The yellow boxes mark the matched episode event for each recall event (i.e., the maximum correlation in each column).}
+\label{fig:matchmats}
+\end{figure}
+
+\begin{figure}
+\renewcommand{\figurename}{Extended Data Figure}
+\setcounter{figure}{3}
+\centering
+\includegraphics[width=.92\textwidth]{figs/k_optimization}
+\caption{\small \textbf{Episode and recall topic proportions matrix \textit{K}-optimization functions.}  We selected the optimal $K$-value for the episode and each recall topic proportions matrix using the formula described in \textit{Methods}.
+This computation resulted in a curve for each matrix, describing the Wasserstein distance between the distributions of within-event and across-event topic vector correlations, as a function of $K$.}
+\label{fig:k_optimization}
+\end{figure}
+
 \end{document}

### 2020-11-26 paper/main.tex

--- 2020-11-24 paper/main.tex
@@
 \newcommand{\featureimportance}{3}
-\newcommand{\corrmats}{5}
-\newcommand{\matchmats}{6}
-\newcommand{\kopt}{7}
-\newcommand{\arrows}{4}
+
+\newcommand{\arrows}{1}
+\newcommand{\corrmats}{2}
+\newcommand{\matchmats}{3}
+\newcommand{\kopt}{4}
 
@@
 Event boundaries detected by the HMM are denoted in yellow (22 events detected).
-For similar plots for all participants, see Supplementary Figure~\corrmats.
+For similar plots for all participants, see Extended Data Figure~\corrmats.
 \textbf{F.} Average topic vectors for each of the 22 recall events from the example participant.
 \textbf{G.} Correlations between the topic vectors for every pair of episode events (Panel C) and recall events (from the example participant; Panel F).
-For similar plots for all participants, see Supplementary Figure~\matchmats.
+For similar plots for all participants, see Extended Data Figure~\matchmats.
 \textbf{H.} Average correlations between each pair of episode events and recall events (across all 17 participants).
@@
 We used the same HMM-based optimization procedure that we had applied to the episode's topic proportions matrix (see \textit{Methods}) to estimate an analogous set of event boundaries in the participant's recounting of the episode (outlined in yellow).
-We carried out this analysis on all 17 participants' recall topic proportions matrices (Supp.\ Fig.~\corrmats).
+We carried out this analysis on all 17 participants' recall topic proportions matrices (Extended Data Fig.~\corrmats).
 
 Two clear patterns emerged from this set of analyses.
-First, although every individual participant's recalls could be segmented into discrete events (i.e., every individual participant's recall correlation matrix exhibited clear block diagonal structure; Supp.\ Fig.~\corrmats), each participant appeared to have a unique ``recall resolution,'' reflected in the sizes of those blocks.
+First, although every individual participant's recalls could be segmented into discrete events (i.e., every individual participant's recall correlation matrix exhibited clear block diagonal structure; Extended Data Fig.~\corrmats), each participant appeared to have a unique ``recall resolution,'' reflected in the sizes of those blocks.
 While some participants' recall topic proportions segmented into just a few events (e.g., Participants P4, P5, and P7), others' segmented into many shorter-duration events (e.g., Participants P12, P13, and P17).
@@
 One potential explanation for this finding is that the topic models, trained only on episode annotations, do not capture topic proportions in participants' ``held-out'' recalls as accurately.
-A second possibility is that, whereas each event in the original episode was (largely) separable from the others (Fig.~\ref{fig:model}B), in transforming those separable events into memory, participants appeared to be integrating across multiple events, blending elements of previously recalled and not-yet-recalled content into each newly recalled event (Fig.~\ref{fig:model}E, Supp.\ Fig.~\corrmats)~\citep{MannEtal11, HowaEtal12, Mann19}.
+A second possibility is that, whereas each event in the original episode was (largely) separable from the others (Fig.~\ref{fig:model}B), in transforming those separable events into memory, participants appeared to be integrating across multiple events, blending elements of previously recalled and not-yet-recalled content into each newly recalled event (Fig.~\ref{fig:model}E, Extended Data Fig.~\corrmats)~\citep{MannEtal11, HowaEtal12, Mann19}.
 
@@
 Next, we asked whether some correspondence might be made between the specific content of the events the participants experienced while viewing the episode, and the events they later recalled.
-We labeled each recall event as matching the episode event with the most similar (i.e., most highly correlated) topic vector (Fig.~\ref{fig:model}G, Supp.\ Fig.~\matchmats).
+We labeled each recall event as matching the episode event with the most similar (i.e., most highly correlated) topic vector (Fig.~\ref{fig:model}G, Extended Data Fig.~\matchmats).
 This yielded a sequence of ``presented'' events from the original episode, and a (potentially differently ordered) sequence of ``recalled'' events for each participant.
@@
   \includegraphics[width=1\textwidth]{figs/precision_distinctiveness}
-  \caption{\small \textbf{Novel content-based metrics of naturalistic memory: precision and distinctiveness.} \textbf{A.} The episode-recall correlation matrix for an example participant (P17), chosen for their large number of recall events (for analogous figures for other participants, see Supp.\ Fig.~\corrmats).
+  \caption{\small \textbf{Novel content-based metrics of naturalistic memory: precision and distinctiveness.} \textbf{A.} The episode-recall correlation matrix for an example participant (P17), chosen for their large number of recall events (for analogous figures for other participants, see Extended Data Fig.~\corrmats).
 The yellow boxes highlight the maximum correlation in each column.
@@
 The arrows reflect the average transition direction through topic space taken by any participants whose trajectories crossed that part of topic space; blue denotes reliable agreement across participants via a Rayleigh test ($p < 0.05$, corrected).
-For additional detail see \textit{Methods} and Supplementary Figure~\arrows.
+For additional detail see \textit{Methods} and Extended Data Figure~\arrows.
 \textbf{C.} The recall topic trajectories (gray) taken by each individual participant (P1--P17).
@@
 To assess the consistency of these recall trajectories across participants, we asked: given that a participant's recall trajectory had entered a particular location in the reduced topic space, could the position of their next recalled event be predicted reliably?
-For each location in the reduced topic space, we computed the set of line segments connecting successively recalled events (across all participants) that intersected that location (see \textit{Methods}, Supp.\ Fig.~\arrows).
+For each location in the reduced topic space, we computed the set of line segments connecting successively recalled events (across all participants) that intersected that location (see \textit{Methods}, Extended Data Fig.~\arrows).
 We then computed (for each location) the distribution of angles formed by the lines defined by those line segments and a fixed reference line (the $x$-axis).
@@
 We computed the first Wasserstein distance ($W_{1}$, also known as ``Earth mover's distance''~\citep{Dobr70, RamdEtal17}) between these distributions for a large range of possible $K$-values (range [2, 50]), and selected the $K$ that yielded the maximum value.
-Figure~\ref{fig:model}B displays the event boundaries returned for the episode, and Supplementary Figure~\corrmats~displays the event boundaries returned for each participant's recalls.
-See Supplementary Figure \kopt~for the optimization functions for the episode and recalls.
+Figure~\ref{fig:model}B displays the event boundaries returned for the episode, and Extended Data Figure~\corrmats~displays the event boundaries returned for each participant's recalls.
+See Extended Data Figure~\kopt~for the optimization functions for the episode and recalls.
 After obtaining these event boundaries, we created stable estimates of the content represented in each event by averaging the topic vectors across timepoints between each pair of event boundaries.
@@
 \subsubsection*{Estimating the consistency of flow through topic space across participants}
-In Figure~\ref{fig:trajectory}B, we present an analysis aimed at characterizing locations in topic space that different participants move through in a consistent way (via their recall topic trajectories; also see Supp.\ Fig.~\arrows).
+In Figure~\ref{fig:trajectory}B, we present an analysis aimed at characterizing locations in topic space that different participants move through in a consistent way (via their recall topic trajectories; also see Extended Data Fig.~\arrows).
 The two-dimensional topic space used in our visualizations (Fig.~\ref{fig:trajectory}) comprised a $60 \times 60$ (arbitrary units) square.
@@
 To construct the episode template, we computed the correlations between the topic proportions estimated for every pair of TRs (prior to segmenting the topic proportions matrices into discrete events; i.e., the correlation matrix shown in Figs.~\ref{fig:model}B and \ref{fig:brainz}A).
-We constructed similar temporal correlation matrices for each participant's recall topic proportions matrix (Fig.~\ref{fig:model}D, Supp.\ Fig.~\corrmats).
+We constructed similar temporal correlation matrices for each participant's recall topic proportions matrix (Fig.~\ref{fig:model}D, Extended Data Fig.~\corrmats).
 However, to correct for length differences and potential non-linear transformations between viewing time and recall time, we first used dynamic time warping~\citep{BernClif94} to temporally align participants' recall topic proportions matrices with the episode topic proportions matrix.

### 2020-11-26 paper/supplementary_information.tex

--- 2020-11-23 paper/supplementary_information.tex
@@
 
-% \FloatBarrier
-\newpage
-%\begin{centering}
-%  \vspace*{\fill}
-  \section*{Supplementary figures}
-
-\begin{figure}[tp]
-\centering
-\includegraphics[width=0.6\textwidth]{figs/topic_space_flow}
-\caption{\small \textbf{Methods detail for recall trajectory analysis displayed in Figure~\trajectories B} \textbf{A.} This panel replicates Figure~\trajectories B in the \textit{Main text}, but with two additions.
-First, individual participants' recall trajectories are displayed (faintly) as light gray lines.
-Second, three locations on the trajectory have been highlighted (blue, yellow, and red circles).
-\textbf{B.}  These zoomed-in views of the locations highlighted in Panel A show the average trajectory (black) and individual participants' trajectories (gray lines) that intersect the given region of topic space.
-\textbf{C.} For each circular region of topic space tiling the 2D embedding plane displayed in Panel A, we compute the distribution of angles formed between each participant's trajectory segment (i.e., the point at which the trajectory enters and exists the region of topic space) and the $x$-axis.
-The distributions of angles for these three example regions are displayed in the colored rose plots.
-We use Rayleigh tests to assign an arrow direction, length, and color for that region of topic space.
-Arrows displayed in color are significant at the $p < 0.05$ level (corrected).
-The arrow directions are oriented according to the circular means of each distribution, and the arrow lengths are proportional to the lengths of those mean vectors.
-The example regions have been oriented from left to right in decreasing order of consistency across participants.}
-\label{fig:arrows-methods}
-\end{figure}
-\vspace*{\fill}
-
-\newpage
-    \subsection*{Participant-level figures referenced in the main text}
-    %\vspace*{\fill}
-  %\end{centering}
-
-\begin{figure}[p!]
-\centering
-\includegraphics[width=\textwidth]{figs/corrmats}
-\caption{\small \textbf{Recall temporal correlation matrices and event segmentation fits.} Each panel is in the same format as Figure~\topicprops E in the main text.
-The yellow boxes indicate HMM-identified event boundaries.}
-\label{fig:corrmats}
-\end{figure}
-
-\begin{figure}[p!]
-\centering
-\includegraphics[width=\textwidth]{figs/matchmats}
-\caption{\small \textbf{Episode-recall event correlation matrices.}  Each panel is in the same format as Figure~\topicprops G in the main text.
-The yellow boxes mark the matched episode event for each recall event (i.e., the maximum correlation in each column).}
-\label{fig:matchmats}
-\end{figure}
-
-\begin{figure}[p!]
-\centering
-\includegraphics[width=.92\textwidth]{figs/k_optimization}
-\caption{\small \textbf{Episode and recall topic proportions matrix \textit{K}-optimization functions.}  We selected the optimal $K$-value for the episode and each recall topic proportions matrix using the formula described in \textit{Methods}.
-This computation resulted in a curve for each matrix, describing the Wasserstein distance between the distributions of within-event and across-event topic vector correlations, as a function of $K$.}
-\label{fig:k_optimization}
-\end{figure}
-
 \newpage

### 2021-02-19 paper/old.tex

@@
 
-\newcommand{\topicopt}{S1}
-\newcommand{\topics}{S2}
-\newcommand{\featureimportance}{S3}
-\newcommand{\corrmats}{S4}
-\newcommand{\matchmats}{S5}
-\newcommand{\kopt}{S6}
+\newcommand{\topicopt}{1}
+\newcommand{\topics}{2}
+\newcommand{\featureimportance}{3}
+\newcommand{\corrmats}{5}
+\newcommand{\matchmats}{6}
+\newcommand{\kopt}{7}
+\newcommand{\arrows}{4}
 
@@
 \section*{Introduction}
-What does it mean to \textit{remember} something?
-In traditional episodic memory experiments \citep[e.g., list-learning or trial-based experiments;][]{Murd62a, Kaha96}, remembering is often cast as a discrete, binary operation: each studied item may be separated from the rest of one's experience and labeled as having been either recalled or forgotten.
+What does it mean to remember something?
+In traditional episodic memory experiments (e.g., list-learning or trial-based experiments\citep{Murd62a, Kaha96}), remembering is often cast as a discrete, binary operation: each studied item may be separated from the rest of one's experience and labeled as having been either recalled or forgotten.
 More nuanced studies might incorporate self-reported confidence measures as a proxy for memory strength, or ask participants to discriminate between recollecting the (contextual) details of an experience and having a general feeling of familiarity~\citep{Yone02}.
-Using well-controlled, trial-based experimental designs, the field has amassed a wealth of information regarding human episodic memory~\citep[for review see][]{Kaha12}.
-However, there are fundamental properties of the external world and our memories that trial-based experiments are not well suited to capture~\citep[for review, also see][]{KoriGold94, HukEtal18}.
+Using well-controlled, trial-based experimental designs, the field has amassed a wealth of information regarding human episodic memory~\citep{Kaha12}.
+However, there are fundamental properties of the external world and our memories that trial-based experiments are not well suited to capture~\citep{KoriGold94, HukEtal18}.
 First, our experiences and memories are continuous, rather than discrete---isolating a naturalistic event from the context in which it occurs can substantially change its meaning.
 Second, whether or not the rememberer has precisely reproduced a specific set of words in describing a given experience is nearly orthogonal to how well they were actually able to remember it.
-In classic (e.g., list-learning) memory studies, by contrast, the number or proportion of \textit{exact} recalls is often considered to be a primary metric for assessing the quality of participants' memories.
+In classic (e.g., list-learning) memory studies, by contrast, the number or proportion of exact recalls is often considered to be a primary metric for assessing the quality of participants' memories.
 Third, one might remember the essence (or a general summary) of an experience but forget (or neglect to recount) particular low-level details.
@@
 Therefore, the timecourse describing how an event unfolds is fundamental to its overall meaning.
-Further, this hierarchy formed by our subjective experiences at different timescales defines a \textit{context} for each new moment~\citep[e.g.,][]{HowaKaha02a, HowaEtal14}, and plays an important role in how we interpret that moment and remember it later~\citep[for review see][]{MannEtal15, Mann20}.
+Further, this hierarchy formed by our subjective experiences at different timescales defines a context for each new moment~\citep{HowaKaha02a, HowaEtal14}, and plays an important role in how we interpret that moment and remember it later~\citep{MannEtal15, Mann20}.
 Our memory systems can leverage these associations to form predictions that help guide our behaviors~\citep{RangRitc12}.
@@
 
-Occasionally, this gradual drift of our ongoing experience is punctuated by sudden changes, or shifts~\citep[e.g., when we walk through a doorway;][]{RadvZack17}.
-Prior research suggests that these sharp transitions (termed \textit{event boundaries}) help to discretize our experiences (and their mental representations) into \textit{events}~\citep{RadvZack17, BrunEtal18, HeusEtal18b, ClewDava17, EzzyDava11, DuBrDava13}.
+Occasionally, this gradual drift of our ongoing experience is punctuated by sudden changes, or shifts (e.g., when we walk through a doorway~\citep{RadvZack17}).
+Prior research suggests that these sharp transitions (termed ``event boundaries'') help to discretize our experiences (and their mental representations) into ``events''~\citep{RadvZack17, BrunEtal18, HeusEtal18b, ClewDava17, EzzyDava11, DuBrDava13}.
 The interplay between the stable (within-event) and transient (across-event) temporal dynamics of an experience also provides a potential framework for transforming experiences into memories that distills those experiences down to their essences.
@@
 Topic models take as inputs a vocabulary of words to consider and a collection of text documents, and return two output matrices.
-The first of these is a \textit{topics matrix} whose rows are \textit{topics} (or latent themes) and whose columns correspond to words in the vocabulary.
+The first of these is a ``topics matrix'' whose rows are ``topics'' (or latent themes) and whose columns correspond to words in the vocabulary.
 The entries in the topics matrix reflect how each word in the vocabulary is weighted by each discovered topic.
-For example, a detective-themed topic might weight heavily on words like ``crime,'' and ``search.''  The second output is a \textit{topic proportions matrix} with one row per document and one column per topic.
+For example, a detective-themed topic might weight heavily on words like ``crime,'' and ``search.''  The second output is a ``topic proportions matrix'' with one row per document and one column per topic.
 The topic proportions matrix describes the mixture of discovered topics reflected in each document.
 
-\cite{ChenEtal17} collected hand-annotated information about each of 1,000 (manually delineated) time segments spanning the roughly 50 minute video used in their study.
+Chen et al.
+(2017) collected hand-annotated information about each of 1000 (manually delineated) time segments spanning the roughly 50 minute video used in their study~\cite{ChenEtal17}.
 Each annotation included: a brief narrative description of what was happening, the location where the action took place, the names of any characters on the screen, and other similar details (for a full list of annotated features, see \textit{Methods}).
@@
 Next, we fit a topic model with (up to) $K = 100$ topics to this collection of documents.
-We found that 32 unique topics (with non-zero weights) were sufficient to describe the time-varying content of the episode (see \textit{Methods}; Figs.~\ref{fig:schematic}, \topics).
+We found that 32 unique topics (with non-zero weights) were sufficient to describe the time-varying content of the episode (see \textit{Methods}; Fig.~\ref{fig:schematic}, Supp.\ Fig.~\topics).
 We note that our approach is similar in some respects to Dynamic Topic Models~\citep{BleiLaff06} in that we sought to characterize how the thematic content of the episode evolved over time.
-However, whereas Dynamic Topic Models are designed to characterize how the properties of \textit{collections} of documents change over time, our sliding window approach allows us to examine the topic dynamics within a single document (or video).
-Specifically, our approach yielded (via the topic proportions matrix) a single \textit{topic vector} for each sliding window of annotations transformed by the topic model.
-We then stretched (interpolated) the resulting windows-by-topics matrix to match the time series of the 1,976 fMRI volumes collected as participants viewed the episode.
+However, whereas Dynamic Topic Models are designed to characterize how the properties of collections of documents change over time, our sliding window approach allows us to examine the topic dynamics within a single document (or video).
+Specifically, our approach yielded (via the topic proportions matrix) a single ``topic vector'' for each sliding window of annotations transformed by the topic model.
+We then stretched (interpolated) the resulting windows-by-topics matrix to match the time series of the 1976 fMRI volumes collected as participants viewed the episode.
 
@@
 
-The 32 topics we found were heavily character-focused (i.e., the top-weighted word in each topic was nearly always a character) and could be roughly divided into themes centered around Sherlock Holmes (the titular character), John Watson (Sherlock's close confidant and assistant), supporting characters (e.g., Inspector Lestrade, Sergeant Donovan, or Sherlock's brother Mycroft), or the interactions between various groupings of these characters (Fig.~\topics).
+The 32 topics we found were heavily character-focused (i.e., the top-weighted word in each topic was nearly always a character) and could be roughly divided into themes centered around Sherlock Holmes (the titular character), John Watson (Sherlock's close confidant and assistant), supporting characters (e.g., Inspector Lestrade, Sergeant Donovan, or Sherlock's brother Mycroft), or the interactions between various groupings of these characters (Supp.\ Fig.~\topics).
 This likely follows from the frequency with which these terms appeared in the episode annotations.
 Several of the identified topics were highly similar, which we hypothesized might allow us to distinguish between subtle narrative differences if the distinctions between those overlapping topics were meaningful.
-The topic vectors for each timepoint were also \textit{sparse}, in that only a small number of topics (typically one or two) tended to be ``active'' in any given timepoint (Fig.~\ref{fig:model}A).
-Further, the dynamics of the topic activations appeared to exhibit \textit{persistence} (i.e., given that a topic was active in one timepoint, it was likely to be active in the following timepoint) along with \textit{occasional rapid changes} (i.e., occasionally topic weights would change abruptly from one timepoint to the next).
+The topic vectors for each timepoint were also sparse, in that only a small number of topics (typically one or two) tended to be ``active'' in any given timepoint (Fig.~\ref{fig:model}A).
+Further, the dynamics of the topic activations appeared to exhibit persistence (i.e., given that a topic was active in one timepoint, it was likely to be active in the following timepoint) along with occasional rapid changes (i.e., occasionally topic weights would change abruptly from one timepoint to the next).
 These two properties of the topic dynamics may be seen in the block diagonal structure of the timepoint-by-timepoint correlation matrix (Fig.~\ref{fig:model}B) and reflect the gradual drift and sudden shifts fundamental to the temporal dynamics of many real-world experiences, as well as television episodes.
-Given this observation, we adapted an approach devised by \cite{BaldEtal17}, and used a hidden Markov model (HMM) to identify the \textit{event boundaries} where the topic activations changed rapidly (i.e., the boundaries of the blocks in the temporal correlation matrix; event boundaries identified by the HMM are outlined in yellow in Fig.~\ref{fig:model}B).
+Given this observation, we adapted an approach devised by Baldassano et al.
+(2017)~\cite{BaldEtal17}, and used a hidden Markov model (HMM) to identify the ``event boundaries'' where the topic activations changed rapidly (i.e., the boundaries of the blocks in the temporal correlation matrix; event boundaries identified by the HMM are outlined in yellow in Fig.~\ref{fig:model}B).
 Part of our model fitting procedure required selecting an appropriate number of events into which the topic trajectory should be segmented.
@@
 We used the same HMM-based optimization procedure that we had applied to the episode's topic proportions matrix (see \textit{Methods}) to estimate an analogous set of event boundaries in the participant's recounting of the episode (outlined in yellow).
-We carried out this analysis on all 17 participants' recall topic proportions matrices (Fig.~\corrmats).
+We carried out this analysis on all 17 participants' recall topic proportions matrices (Supp.\ Fig.~\corrmats).
 
 Two clear patterns emerged from this set of analyses.
-First, although every individual participant's recalls could be segmented into discrete events (i.e., every individual participant's recall correlation matrix exhibited clear block diagonal structure; Fig.~\corrmats), each participant appeared to have a unique \textit{recall resolution}, reflected in the sizes of those blocks.
+First, although every individual participant's recalls could be segmented into discrete events (i.e., every individual participant's recall correlation matrix exhibited clear block diagonal structure; Supp.\ Fig.~\corrmats), each participant appeared to have a unique ``recall resolution,'' reflected in the sizes of those blocks.
 While some participants' recall topic proportions segmented into just a few events (e.g., Participants P4, P5, and P7), others' segmented into many shorter-duration events (e.g., Participants P12, P13, and P17).
@@
 The second clear pattern present in every individual participant's recall correlation matrix was that, unlike in the episode correlation matrix, there were substantial off-diagonal correlations.
-Whereas each event in the original episode was (largely) separable from the others (Fig.~\ref{fig:model}B), in transforming those separable events into memory, participants appeared to be integrating across multiple events, blending elements of previously recalled and not-yet-recalled content into each newly recalled event~\citep[Figs.~\ref{fig:model}E, \corrmats; also see][]{MannEtal11, HowaEtal12, Mann19}.
+One potential explanation for this finding is that the topic models, trained only on episode annotations, do not capture topic proportions in participants' ``held-out'' recalls as accurately.
+A second possibility is that, whereas each event in the original episode was (largely) separable from the others (Fig.~\ref{fig:model}B), in transforming those separable events into memory, participants appeared to be integrating across multiple events, blending elements of previously recalled and not-yet-recalled content into each newly recalled event (Fig.~\ref{fig:model}E, Supp.\ Fig.~\corrmats)~\citep{MannEtal11, HowaEtal12, Mann19}.
 
@@
 Next, we asked whether some correspondence might be made between the specific content of the events the participants experienced while viewing the episode, and the events they later recalled.
-We labeled each recall event as matching the episode event with the most similar (i.e., most highly correlated) topic vector (Figs.~\ref{fig:model}G, \matchmats).
+We labeled each recall event as matching the episode event with the most similar (i.e., most highly correlated) topic vector (Fig.~\ref{fig:model}G, Supp.\ Fig.~\matchmats).
 This yielded a sequence of ``presented'' events from the original episode, and a (potentially differently ordered) sequence of ``recalled'' events for each participant.
-Analogous to classic list-learning studies, we can then examine participants' recall sequences by asking which events they tended to recall first~\citep[probability of first recall; Fig.~\ref{fig:list-learning}A;][]{AtkiShif68, PostPhil65, WelcBurn24}; how participants most often transitioned between recalls of the events as a function of the temporal distance between them~\citep[lag-conditional response probability; Fig.~\ref{fig:list-learning}B;][]{Kaha96}; and which events they were likely to remember overall~\citep[serial position recall analyses; Fig.~\ref{fig:list-learning}C;][]{Murd62a}.
+Analogous to classic list-learning studies, we can then examine participants' recall sequences by asking which events they tended to recall first (probability of first recall~\citep{AtkiShif68, PostPhil65, WelcBurn24}; Fig.~\ref{fig:list-learning}A); how participants most often transitioned between recalls of the events as a function of the temporal distance between them (lag-conditional response probability~\citep{Kaha96}; Fig.~\ref{fig:list-learning}B); and which events they were likely to remember overall (serial position recall analyses~\citep{Murd62a}; Fig.~\ref{fig:list-learning}C).
 Some of the patterns we observed appeared to be similar to classic effects from the list-learning literature.
@@
 \textbf{C.} The proportion of participants who recalled each event, as a function of the serial position of the events in the episode.
-All panels: error ribbons denote bootstrap-estimated standard error of the mean.}
+All panels: error ribbons denote the bootstrap-estimated 95\% confidence interval.}
   \label{fig:list-learning}
 \end{figure}
+
+Clustering scores are often used by memory researchers to characterize how people organize their memories of words on a studied list~\citep{PolyEtal09}.
+We defined analogous measures to characterize how participants organized their memories for episodic events (see \textit{Methods} for details).
+Temporal clustering refers to the extent to which participants group their recall responses according to encoding position.
+Overall, we found that sequentially viewed episode events tended to appear nearby in participants' recall event sequences (mean clustering score: 0.732, SEM: 0.033).
+Participants with higher temporal clustering scores tended to exhibit better overall memory for the episode, according to both Chen et al.
+(2017)~\cite{ChenEtal17}'s hand-counted numbers of recalled scenes from the episode (Pearson's $r(15) = 0.49,~p = 0.046,~95\%~\mathrm{CI} = [0.25, 0.76]$) and the numbers of episode events that best-matched at least one recall event (i.e., model-estimated number of events recalled; Pearson's $r(15) = 0.59,~p = 0.013,~95\%~\mathrm{CI} = [0.31, 0.80]$).
+Semantic clustering measures the extent to which participants cluster their recall responses according to semantic similarity~\citep{MannKaha12}.
+We found that participants tended to recall semantically similar episode events together (mean clustering score: 0.650, SEM: 0.032), and that semantic clustering scores were also related to both hand-counted  (Pearson's $r(15) = 0.65,~p = 0.004,~95\%~\mathrm{CI} = [0.31, 0.85]$) and model-estimated (Pearson's $r(15) = 0.58,~p = 0.015,~95\%~\mathrm{CI} = [0.10, 0.83]$) numbers of recalled events.
 
@@
   \includegraphics[width=1\textwidth]{figs/precision_distinctiveness}
-  \caption{\small \textbf{Novel content-based metrics of naturalistic memory: precision and distinctiveness.} \textbf{A.} The episode-recall correlation matrix for a representative participant (P17).
+  \caption{\small \textbf{Novel content-based metrics of naturalistic memory: precision and distinctiveness.} \textbf{A.} The episode-recall correlation matrix for an example participant (P17), chosen for their large number of recall events (for analogous figures for other participants, see Supp.\ Fig.~\corrmats).
 The yellow boxes highlight the maximum correlation in each column.
@@
 
-\textit{Distinctiveness} is intended to capture the ``specificity'' of recall.
+Distinctiveness is intended to capture the ``specificity'' of recall.
 In other words, distinctiveness quantifies the extent to which a given recall event reflects the most similar episode event over and above other episode events.
 Intuitively, distinctiveness is like a normalized variant of our precision metric.
-Whereas precision solely measures how much detail about an episode was captured in someone's recall, distinctiveness penalizes details that also pertain to other episode events.
+Whereas precision solely measures how much detail about an event was captured in someone's recall, distinctiveness penalizes details that also pertain to other episode events.
 We define the distinctiveness of an event's recall as its precision expressed in standard deviation units with respect to other episode events.
@@
 This enables us to quantify how precisely a participant tended to recall subtle within-event details, as well as how specific (distinctive) those details were to individual events from the episode.
-Participants' average precision and distinctiveness scores were strongly correlated ($r(15) = 0.90, p < 0.001$).
+Participants' average precision and distinctiveness scores were strongly correlated ($r(15) = 0.90,~p < 0.001,~95\%~\mathrm{CI} = [0.66, 0.96]$).
 This indicates that participants who tended to precisely recount low-level details of episode events also tended to do so in an event-specific way (e.g., as opposed to detailing recurring themes that were present in most or all episode events; this behavior would have resulted in high precision but low distinctiveness).
-We found that, across participants, higher precision scores were positively correlated with the numbers of both hand-annotated scenes ($r(15) = 0.60, p = 0.010$) and model-estimated events ($r(15) = 0.90, p < 0.001$) that participants recalled.
-Participants' average distinctiveness scores were also correlated with both the hand-annotated ($r(15) = 0.45, p = 0.068$) and model-estimated ($r(15) = 0.71, p = 0.001$) numbers of recalled events.
+We found that, across participants, higher precision scores were positively correlated with the numbers of both hand-annotated scenes ($r(15) = 0.60,~p = 0.010,~95\%~\mathrm{CI} = [0.02, 0.83]$) and model-estimated events ($r(15) = 0.90,~p < 0.001,~95\%~\mathrm{CI} = [0.54, 0.96]$) that participants recalled.
+Participants' average distinctiveness scores were also marginally correlated with both the hand-annotated ($r(15) = 0.45,~p = 0.068,~95\%~\mathrm{CI} = [-0.21, 0.79]$) and model-estimated ($r(15) = 0.71,~p = 0.001,~95\%~\mathrm{CI} = [-0.07, 0.90]$) numbers of recalled events.
 
@@
 First, the topic trajectory of the episode (which reflects its dynamic content; Fig.~\ref{fig:trajectory}A) is captured nearly perfectly by the averaged topic trajectories of participants' recalls (Fig.~\ref{fig:trajectory}B).
-To assess the consistency of these recall trajectories across participants, we asked: given that a participant's recall trajectory had entered a particular location in the reduced topic space, could the position of their \textit{next} recalled event be predicted reliably?
-For each location in the reduced topic space, we computed the set of line segments connecting successively recalled events (across all participants) that intersected that location (see \textit{Methods}).
+To assess the consistency of these recall trajectories across participants, we asked: given that a participant's recall trajectory had entered a particular location in the reduced topic space, could the position of their next recalled event be predicted reliably?
+For each location in the reduced topic space, we computed the set of line segments connecting successively recalled events (across all participants) that intersected that location (see \textit{Methods}, Supp.\ Fig.~\arrows).
 We then computed (for each location) the distribution of angles formed by the lines defined by those line segments and a fixed reference line (the $x$-axis).
@@
 We then computed a weighted average of the topic vectors for each episode event, where the weights reflected how precisely each event was recalled.
-To visualize the result, we created a ``wordle'' image~\citep{MuelEtal18} where words weighted more heavily by more precisely-remembered topics appear in a larger font (Fig.~\ref{fig:topics}B, green box).
+To visualize the result, we created a ``wordle'' image~\citep{MuelEtal18} where words weighted more heavily by more precisely remembered topics appear in a larger font (Fig.~\ref{fig:topics}B, green box).
 Across the full episode, content that weighted heavily on topics and words central to the major foci of the episode (e.g., the names of the two main characters, ``Sherlock'' and ``John,'' and the address of a major recurring location, ``221B Baker Street'') was best remembered.
 An analogous analysis revealed which themes were less-precisely remembered.
-Here in computing the weighted average over events' topic vectors, we weighted each event in \textit{inverse} proportion to its average precision (Fig.~\ref{fig:topics}B, red box).
+Here, in computing the weighted average over events' topic vectors, we weighted each event in inverse proportion to its average precision (Fig.~\ref{fig:topics}B, red box).
 The least precisely remembered episode content reflected information that was extraneous to the episode's essence, such as the proper names of relatively minor characters (e.g., ``Mike,'' ``Molly,'' and ``Lestrade'') and locations (e.g., ``St.
@@
 We used a searchlight procedure to identify clusters of voxels whose activity patterns displayed a proximal temporal correlation structure (as participants watched the episode) matching that of the original episode's topic proportions (Fig.~\ref{fig:brainz}A; see \textit{Methods} for additional details).
-In a second analysis, we sought to identify brain structures whose responses (during episode viewing) reflected how each participant would later structure their \textit{recounting} of the episode.
+In a second analysis, we sought to identify brain structures whose responses (during episode viewing) reflected how each participant would later structure their recounting of the episode.
 We used a searchlight procedure to identify clusters of voxels whose proximal temporal correlation matrices matched that of the topic proportions matrix for each participant's recall transcript (Figs.~\ref{fig:brainz}B; see \textit{Methods} for additional details).
-To ensure our searchlight procedure identified regions \textit{specifically} sensitive to the temporal structure of the episode or recalls (i.e., rather than those with a temporal autocorrelation length similar to that of the episode and recalls), we performed a phase shift-based permutation correction (see \textit{Methods}).
+To ensure our searchlight procedure identified regions specifically sensitive to the temporal structure of the episode or recalls (i.e., rather than those with a temporal autocorrelation length similar to that of the episode and recalls), we performed a phase shift-based permutation correction (see \textit{Methods}).
 As shown in Figure~\ref{fig:brainz}C, the episode-driven searchlight analysis revealed a distributed network of regions that may play a role in processing information relevant to the narrative structure of the episode.
 The recall-driven searchlight analysis revealed a second network of regions (Fig.~\ref{fig:brainz}D) that may facilitate a person-specific transformation of one's experience into memory.
-In identifying regions whose responses to ongoing experiences reflect how those experiences will be remembered later, this latter analysis extends classic \textit{subsequent memory effect analyses}~\citep[e.g.,][]{PallWagn02} to the domain of naturalistic experiences.
+In identifying regions whose responses to ongoing experiences reflect how those experiences will be remembered later, this latter analysis extends classic ``subsequent memory effect analyses''~\citep{PallWagn02} to the domain of naturalistic experiences.
 
@@
 \textbf{B.} We used dynamic time warping \citep{BernClif94} to align each participant's recall timeseries to the TR timeseries of the episode.
-We then applied the same diagonal mask used in Panel A to isolate the proximal temporal correlations and searched for brain regions whose activation timeseries for an individual consistently exhibited a similar proximal correlational structure to each individual's recall.
+We then computed the temporal correlation matrix of each participant's warped recalls.
+Next, we applied the same diagonal mask used in Panel A to isolate the proximal temporal correlations and searched for brain regions whose activation timeseries for each participant consistently exhibited a similar proximal correlational structure to that participant's recalls.
 \textbf{C.} We identified a network of regions sensitive to the narrative structure of participants' ongoing experience.
@@
 
-Our work casts remembering as reproducing (behaviorally and neurally) the topic trajectory, or ``shape,'' of an experience.
+Our work casts remembering as reproducing (behaviorally and neurally) the topic trajectory, or ``shape,'' of an experience, thereby drawing implicit analogies between mentally navigating through word embedding spaces and physically navigating through spatial environments~\citep{BellEtal18, BellEtal20, ConsEtal16}.
 When we characterized memory for a television episode using this framework, we found that every participant's recounting of the episode recapitulated the low spatial frequency details of the shape of its trajectory through topic space (Fig.~\ref{fig:trajectory}).
-We termed this narrative scaffolding the episode's \textit{essence}.
+We termed this narrative scaffolding the episode's essence.
 Where participants' behaviors varied most was in their tendencies to recount specific low-level details from each episode event.
@@
 This network included orbitofrontal cortex, ventromedial prefrontal cortex, and striatum, among others.
-As reviewed by \cite{RangRitc12}, several of these regions are members of the \textit{anterior temporal system}, which has been implicated in assessing and processing the familiarity of ongoing experiences, emotions, social cognition, and reward.
+As reviewed by Ranganath and Ritchey (2012)~\cite{RangRitc12}, several of these regions are members of the ``anterior temporal system,'' which has been implicated in assessing and processing the familiarity of ongoing experiences, emotions, social cognition, and reward.
 A second network we identified tracked with temporal correlations in the idiosyncratic conceptual content of participants' subsequent recountings of the episode.
 This network included occipital cortex, extrastriate cortex, fusiform gyrus, and the precuneus.
-Several of these regions are members of the \textit{posterior medial system}~\citep{RangRitc12}, which has been implicated in matching incoming cues about the current situation to internally maintained \textit{situation models} that specify the parameters and expectations inherent to the current situation~\citep[also see][]{ZackEtal07, ZwaaRadv98}.
+Several of these regions are members of the ``posterior medial system''~\citep{RangRitc12}, which has been implicated in matching incoming cues about the current situation to internally maintained ``situation models'' that specify the parameters and expectations inherent to the current situation~\citep{ZackEtal07, ZwaaRadv98}.
 Taken together, our results support the notion that these two (partially overlapping) networks work in coordination to make sense of our ongoing experiences, distort them in a way that links them with our prior knowledge and experiences, and encodes those distorted representations into memory for our later use.
+Our work also provides a potential framework for modeling and elucidating ``memory schemas''---i.e., cognitive abstractions that may be applied to multiple related experiences~\citep{GilbMarl17, BaldEtal18}.
+For example, the event-level geometric scaffolding of an experience (e.g., Fig.~\ref{fig:trajectory}A) might reflect its underlying schema, and experiences that share similar schemas might have similar shapes.
+This could also help explain how brain structures including the ventromedial prefrontal cortex~\citep{GilbMarl17} (Fig.~\ref{fig:brainz}) might acquire or apply schema knowledge across different experiences (i.e., by learning patterns in the schema's shape).
 
 Our general approach draws inspiration from prior work aimed at elucidating the neural and behavioral underpinnings of how we process dynamic naturalistic experiences and remember them later.
-Our approach to identifying neural responses to naturalistic stimuli (including experiences) entails building an explicit model of the stimulus dynamics and searching for brain regions whose responses are consistent with the model~\citep[also see][]{HuthEtal12, HuthEtal16}.
+Our approach to identifying neural responses to naturalistic stimuli (including experiences) entails building an explicit model of the stimulus dynamics and searching for brain regions whose responses are consistent with the model~\citep{HuthEtal12, HuthEtal16}.
+Building an explicit model of these dynamics also enables us to match up different people's recountings of a common shared experience, despite individual differences~\cite{GagnEtal20}.
 In prior work, a series of studies from Uri Hasson's group~\citep{LernEtal11, SimoEtal16, ChenEtal17, BaldEtal17, ZadbEtal17} have presented a clever alternative approach: rather than building an explicit stimulus model, these studies instead search for brain responses to the stimulus that are reliably similar across individuals.
-So called \textit{inter-subject correlation} (ISC) and \textit{inter-subject functional connectivity} (ISFC) analyses effectively treat other people's brain responses to the stimulus as a ``model'' of how its features change over time~\citep[also see][]{SimoChan20}.
+So called ``inter-subject correlation'' (ISC) and ``inter-subject functional connectivity'' (ISFC) analyses effectively treat other people's brain responses to the stimulus as a ``model'' of how its features change over time~\citep{SimoChan20}.
 These purely brain-driven approaches are well suited to identifying which brain structures exhibit similar stimulus-driven responses across individuals.
@@
 \subsection*{Paradigm and data collection}
-Data were collected by \cite{ChenEtal17}.
+Data were collected by Chen et al.
+(2017)~\citep{ChenEtal17}.
 In brief, participants ($n=22$) viewed the first 48 minutes of ``A Study in Pink,'' the first episode of the BBC television show \textit{Sherlock}, while fMRI volumes were collected (TR = 1500~ms).
@@
 This included a constant 3 TR (4.5~s) shift to account for the lag in the hemodynamic response.
-\citep[All of these preprocessing steps followed][where additional details may be found.]{ChenEtal17}
+All of these preprocessing steps followed Chen et al.
+(2017)~\citep{ChenEtal17}, where additional details may be found.
 
-The video stimulus was divided into 1,000 fine-grained ``time segments'' and annotated by an independent coder.
-For each of these 1,000 annotations, the following information was recorded: a brief narrative description of what was happening, the location where the time segment took place, whether that location was indoors or outdoors, the names of all characters on-screen, the name(s) of the character(s) in focus in the shot, the name(s) of the character(s) currently speaking, the camera angle of the shot, a transcription of any text appearing on-screen, and whether or not there was music present in the background.
+The video stimulus was divided into 1000 fine-grained ``time segments'' and annotated by an independent coder.
+For each of these 1000 annotations, the following information was recorded: a brief narrative description of what was happening, the location where the time segment took place, whether that location was indoors or outdoors, the names of all characters on-screen, the name(s) of the character(s) in focus in the shot, the name(s) of the character(s) currently speaking, the camera angle of the shot, a transcription of any text appearing on-screen, and whether or not there was music present in the background.
 Each time segment was also tagged with its onset and offset time, in both seconds and TRs.
-
-\subsection*{Data and code availability}
-The fMRI data we analyzed are available online \href{http://dataspace.princeton.edu/jspui/handle/88435/dsp01nz8062179}{\underline{here}}.
-The behavioral data and all of our analysis code may be downloaded \href{https://github.com/ContextLab/sherlock-topic-model-paper}{\underline{here}}.
 
@@
 All statistical tests performed in the neural data analyses were two-sided, except for the permutation-based thresholding, which was one-sided.
-In this case, we were specifically interested in identifying voxels whose activation time series reflected the temporal structure of the episode and recall topic proportions matrices to a \textit{greater} extent than that of the phase-shifted matrices.
+In this case, we were specifically interested in identifying voxels whose activation time series reflected the temporal structure of the episode and recall topic proportions matrices to a greater extent than that of the phase-shifted matrices.
+The 95\% confidence intervals we reported for each correlation were estimated by generating 10000 ``bootstrap'' distributions of correlation coefficients by sampling (with replacement) from the observed data.
 
@@
 
-We trained our model using these overlapping text samples with \texttt{scikit-learn}~\citep[version 0.19.1; ][]{PedrEtal11}, called from our high-dimensional visualization and text analysis software, \texttt{HyperTools}~\citep{HeusEtal18a}.
-Specifically, we used the \texttt{CountVectorizer} class to transform the text from each window into a vector of word counts (using the union of all words across all annotations as the ``vocabulary,'' excluding English stop words); this yielded a number-of-windows by number-of-words \textit{word count} matrix.
-We then used the \texttt{LatentDirichletAllocation} class (topics=100, method=`batch') to fit a topic model~\citep{BleiEtal03} to the word count matrix, yielding a number-of-windows (1047) by number-of-topics (100) \textit{topic proportions} matrix.
+We trained our model using these overlapping text samples with \texttt{scikit-learn} version 0.19.1~\citep{PedrEtal11}, called from our high-dimensional visualization and text analysis software, \texttt{HyperTools}~\citep{HeusEtal18a}.
+Specifically, we used the \texttt{CountVectorizer} class to transform the text from each window into a vector of word counts (using the union of all words across all annotations as the ``vocabulary,'' excluding English stop words); this yielded a number-of-windows by number-of-words ``word count'' matrix.
+We then used the \texttt{LatentDirichletAllocation} class (topics=100, method=`batch') to fit a topic model~\citep{BleiEtal03} to the word count matrix, yielding a number-of-windows (1047) by number-of-topics (100) ``topic proportions'' matrix.
 The topic proportions matrix describes the gradually evolving mix of topics (latent themes) present in each annotated time segment of the episode.
@@
 These reflected the dynamic content of each participant's recalls.
-Note: for details on how we selected the episode and recall window lengths and number of topics, see \textit{Supporting Information} and Figure~\topicopt.
+For details on how we selected the episode and recall window lengths and number of topics, see \textit{Supplementary Information} and Supplementary Figure~\topicopt.
 
 \subsubsection*{Segmenting topic proportions matrices into discrete events using hidden Markov Models}
-We parsed the topic proportions matrices of the episode and participants' recalls into discrete events using hidden Markov Models~\citep[HMMs;][]{Rabi89}.
+We parsed the topic proportions matrices of the episode and participants' recalls into discrete events using hidden Markov Models (HMMs)~\citep{Rabi89}.
 Given the topic proportions matrix (describing the mix of topics at each timepoint) and a number of states, $K$, an HMM recovers the set of state transitions that segments the timeseries into $K$ discrete states.
-Following \cite{BaldEtal17}, we imposed an additional set of constraints on the discovered state transitions that ensured that each state was encountered exactly once (i.e., never repeated).
+Following Baldassano et al.
+(2017)~\cite{BaldEtal17}, we imposed an additional set of constraints on the discovered state transitions that ensured that each state was encountered exactly once (i.e., never repeated).
 We used the \texttt{BrainIAK} toolbox~\citep{Brainiak} to implement this segmentation.
@@
 We used an optimization procedure to select the appropriate $K$ for each topic proportions matrix.
-Prior studies on narrative structure and processing have shown that we both perceive and internally represent the world around us at multiple, hierarchical timescales \citep[e.g.,][]{HassEtal08, LernEtal11, HassEtal15, ChenEtal17, BaldEtal17, BaldEtal18}.
-However, for the purposes of our framework, we sought to identify the single timeseries of event-representations that is emphasized \textit{most heavily} in the temporal structure of the episode and of each participant's recall.
+Prior studies on narrative structure and processing have shown that we both perceive and internally represent the world around us at multiple, hierarchical timescales~\citep{HassEtal08, LernEtal11, HassEtal15, ChenEtal17, BaldEtal17, BaldEtal18}.
+However, for the purposes of our framework, we sought to identify the single timeseries of event representations that was emphasized most heavily in the temporal structure of the episode and of each participant's recall.
 We quantified this as the set of $K$ states that maximized the similarity between topic vectors for timepoints comprising each state, while minimizing the similarity between topic vectors for timepoints across different states.
@@
 where $a$ was the distribution of within-state topic vector correlations, and $b$ was the distribution of across-state topic vector correlations .
-We computed the first Wasserstein distance ($W_{1}$; also known as \textit{Earth mover's distance}; \citealp{Dobr70, RamdEtal17}) between these distributions for a large range of possible $K$-values (range [2, 50]), and selected the $K$ that yielded the maximum value.
-Figure~\ref{fig:model}B displays the event boundaries returned for the episode, and Figure~\corrmats~displays the event boundaries returned for each participant's recalls.
-See Figure \kopt~for the optimization functions for the episode and recalls.
+We computed the first Wasserstein distance ($W_{1}$, also known as ``Earth mover's distance''~\citep{Dobr70, RamdEtal17}) between these distributions for a large range of possible $K$-values (range [2, 50]), and selected the $K$ that yielded the maximum value.
+Figure~\ref{fig:model}B displays the event boundaries returned for the episode, and Supplementary Figure~\corrmats~displays the event boundaries returned for each participant's recalls.
+See Supplementary Figure \kopt~for the optimization functions for the episode and recalls.
 After obtaining these event boundaries, we created stable estimates of the content represented in each event by averaging the topic vectors across timepoints between each pair of event boundaries.
@@
 
-Perhaps the simplest and most widely used measure of memory performance is \textit{accuracy}---i.e., the proportion of studied (experienced) items (in this case, episode events) that the participant later remembered.
-\cite{ChenEtal17} used this method to rate each participant's memory quality by computing the proportion of (50, manually identified) scenes mentioned in their recall.
-We found a strong across-participants correlation between these independent ratings and the proportion of 30 HMM-identified episode events matched to participants' recalls (Pearson's $r(15) = 0.71, p = 0.002$).
+Perhaps the simplest and most widely used measure of memory performance is ``accuracy''---i.e., the proportion of studied (experienced) items (in this case, episode events) that the participant later remembered.
+Chen et al.~(2017)~\cite{ChenEtal17} used this method to rate each participant's memory quality by computing the proportion of (50 manually identified) scenes mentioned in their recall.
+We found a strong across-participants correlation between these independent ratings and the proportion of 30 HMM-identified episode events matched to participants' recalls (Pearson's $r(15) = 0.71, p = 0.002,~95\%~\mathrm{CI} = [0.39, 0.88]$).
 We further considered a number of more nuanced memory performance measures that are typically associated with list-learning studies.
@@
 Finally, we averaged over the rows of the matrix, resulting in a 1 by 30 array representing the proportion of participants that recalled an event first, as a function of the order of the event's appearance in the episode (Fig.~\ref{fig:list-learning}A).
-% ------ NOTE: ------
-% reiterate meaning of error ribbons in list-learning figure? (already noted in figure caption)
-% - Paxton
 
-\paragraph{Lag conditional probability curve (lag-CRP).} The lag-CRP curve~\citep{Kaha96} reflects the probability of recalling a given item after the just-recalled item, as a function of their relative encoding positions (or \textit{lag}).
+\paragraph{Lag conditional probability curve (lag-CRP).} The lag-CRP curve~\citep{Kaha96} reflects the probability of recalling a given item after the just-recalled item, as a function of their relative encoding positions (lag).
 In other words, a lag of 1 indicates that a recalled item was presented immediately after the previously recalled item, and a lag of -3 indicates that a recalled item came 3 items before the previously recalled item.
@@
 We used the UMAP algorithm~\citep{McInEtal18} to project the 100-dimensional topic space onto a two-dimensional space for visualization (Figs.~\ref{fig:trajectory}, \ref{fig:topics}).
-To ensure that all of the trajectories were projected onto the \textit{same} lower dimensional space, we computed the low-dimensional embedding on a ``stacked'' matrix created by vertically concatenating the events-by-topics topic proportions matrices for the episode, across-participants average recall and all 17 individual participants' recalls.
-We then separated the rows of the result (a total-number-of-events by two matrix) back into individual matrices for the episode topic trajectory, across-participant average recall trajectory, and the trajectories for each individual participant's recalls (Fig.~\ref{fig:trajectory}).
-This general approach for discovering a shared low-dimensional embedding for a collections of high-dimensional observations follows \cite{HeusEtal18a}.
+To ensure that all of the trajectories were projected onto the same lower dimensional space, we computed the low-dimensional embedding on a ``stacked'' matrix created by vertically concatenating the events-by-topics topic proportions matrices for the episode, the across-participants average recalls and all 17 individual participants' recalls.
+We then separated the rows of the result (a total-number-of-events by two matrix) back into individual matrices for the episode topic trajectory, the across-participant average recall trajectory, and the trajectories for each individual participant's recalls (Fig.~\ref{fig:trajectory}).
+This general approach for discovering a shared low-dimensional embedding for a collections of high-dimensional observations follows our prior work on manifold learning~\cite{HeusEtal18a}.
 
@@
 The second criteria was motivated by the observed low off-diagonal values in the episode trajectory's temporal correlation matrix (suggesting that the same topic-space coordinates should not be revisited; see Fig.~2A).
-For further details on how we created this low-dimensional embedding space, see \textit{Supporting Information}.
+For further details on how we created this low-dimensional embedding space, see \textit{Supplementary Information}.
 
 \subsubsection*{Estimating the consistency of flow through topic space across participants}
-In Figure~\ref{fig:trajectory}B, we present an analysis aimed at characterizing locations in topic space that different participants move through in a consistent way (via their recall topic trajectories).
+In Figure~\ref{fig:trajectory}B, we present an analysis aimed at characterizing locations in topic space that different participants move through in a consistent way (via their recall topic trajectories; also see Supp.\ Fig.~\arrows).
 The two-dimensional topic space used in our visualizations (Fig.~\ref{fig:trajectory}) comprised a $60 \times 60$ (arbitrary units) square.
@@
 To construct the episode template, we computed the correlations between the topic proportions estimated for every pair of TRs (prior to segmenting the topic proportions matrices into discrete events; i.e., the correlation matrix shown in Figs.~\ref{fig:model}B and \ref{fig:brainz}A).
-We constructed similar temporal correlation matrices for each participant's recall topic proportions matrix (Figs.~\ref{fig:model}D, \corrmats).
+We constructed similar temporal correlation matrices for each participant's recall topic proportions matrix (Fig.~\ref{fig:model}D, Supp.\ Fig.~\corrmats).
 However, to correct for length differences and potential non-linear transformations between viewing time and recall time, we first used dynamic time warping~\citep{BernClif94} to temporally align participants' recall topic proportions matrices with the episode topic proportions matrix.
@@
 \subsection*{Neurosynth decoding analyses}
-\texttt{Neurosynth} parses a massive online database of over 14,000 neuroimaging studies and constructs meta-analysis images for over 13,000 psychology- and neuroscience-related terms, based on NIfTI images accompanying studies where those terms appear at a high frequency.
+\texttt{Neurosynth}~\citep{YarkEtal11} parses a massive online database of over 14000 neuroimaging studies and constructs meta-analysis images for over 13000 psychology- and neuroscience-related terms, based on NIfTI images accompanying studies where those terms appear at a high frequency.
 Given a novel image (tagged with its value type; e.g., $z$-, $t$-, $F$- or $p$-statistics), \texttt{Neurosynth} returns a list of terms whose meta-analysis images are most similar.
 Our permutation procedure yielded, for each of the two searchlight analyses, a voxelwise map of $z$-values.
-These maps describe the extent to which each voxel \textit{specifically} reflected the temporal structure of the episode or individuals' recalls (i.e., relative to the null distributions of phase-shifted values).
+These maps describe the extent to which each voxel specifically reflected the temporal structure of the episode or individuals' recalls (i.e., relative to the null distributions of phase-shifted values).
 We inputted the two statistical maps described above to \texttt{Neurosynth} to create a list of the 10 most representative terms for each map.
 
-% \bibliography{../../CDL-bibliography/memlab}
-\bibliography{CDL-bibliography/memlab}
+\section*{Data availability}
+The fMRI data we analyzed are available online \href{http://dataspace.princeton.edu/jspui/handle/88435/dsp01nz8062179}{\underline{here}}.
+The behavioral data is available  \href{https://github.com/ContextLab/sherlock-topic-model-paper}{\underline{here}}.
 
-\section*{Supporting information}
-Supporting information is available in the online version of the paper.
+\section*{Code availability}
+All of our analysis code may be downloaded \href{https://github.com/ContextLab/sherlock-topic-model-paper}{\underline{here}}.
+
+%\bibliographystyle{naturemag}
+%\bibliography{CDL-bibliography/memlab}
+
+\begin{thebibliography}{10}
+\expandafter\ifx\csname url\endcsname\relax
+  \def\url#1{\texttt{#1}}\fi
+\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
+\providecommand{\bibinfo}[2]{#2}
+\providecommand{\eprint}[2][]{\url{#2}}
+
+\bibitem{Murd62a}
+\bibinfo{author}{Murdock, B.~B.}
+\newblock \bibinfo{title}{The serial position effect of free recall}.
+\newblock \emph{\bibinfo{journal}{Journal of Experimental Psychology}}
+  \textbf{\bibinfo{volume}{64}}, \bibinfo{pages}{482--488}
+  (\bibinfo{year}{1962}).
+
+\bibitem{Kaha96}
+\bibinfo{author}{Kahana, M.~J.}
+\newblock \bibinfo{title}{Associative retrieval processes in free recall}.
+\newblock \emph{\bibinfo{journal}{Memory \& Cognition}}
+  \textbf{\bibinfo{volume}{24}}, \bibinfo{pages}{103--109}
+  (\bibinfo{year}{1996}).
+
+\bibitem{Yone02}
+\bibinfo{author}{Yonelinas, A.~P.}
+\newblock \bibinfo{title}{The nature of recollection and familiarity: A review
+  of 30 years of research}.
+\newblock \emph{\bibinfo{journal}{Journal of Memory and Language}}
+  \textbf{\bibinfo{volume}{46}}, \bibinfo{pages}{441--517}
+  (\bibinfo{year}{2002}).
+
+\bibitem{Kaha12}
+\bibinfo{author}{Kahana, M.~J.}
+\newblock \emph{\bibinfo{title}{Foundations of Human Memory}}
+  (\bibinfo{publisher}{Oxford University Press}, \bibinfo{address}{New York,
+  NY}, \bibinfo{year}{2012}).
+
+\bibitem{KoriGold94}
+\bibinfo{author}{Koriat, A.} \& \bibinfo{author}{Goldsmith, M.}
+\newblock \bibinfo{title}{Memory in naturalistic and laboratory contexts:
+  distinguishing accuracy-oriented and quantity-oriented approaches to memory
+  assessment}.
+\newblock \emph{\bibinfo{journal}{Journal of Experimental Psychology: General}}
+  \textbf{\bibinfo{volume}{123}}, \bibinfo{pages}{297--315}
+  (\bibinfo{year}{1994}).
+
+\bibitem{HukEtal18}
+\bibinfo{author}{Huk, A.}, \bibinfo{author}{Bonnen, K.} \& \bibinfo{author}{He,
+  B.~J.}
+\newblock \bibinfo{title}{Beyond trial-based paradigms: continuous behavior,
+  ongoing neural activity, and naturalistic stimuli}.
+\newblock \emph{\bibinfo{journal}{Journal of Neuroscience}}
+  \textbf{\bibinfo{volume}{10.1523/JNEUROSCI.1920-17.2018}}
+  (\bibinfo{year}{2018}).
+
+\bibitem{LernEtal11}
+\bibinfo{author}{Lerner, Y.}, \bibinfo{author}{Honey, C.~J.},
+  \bibinfo{author}{Silbert, L.~J.} \& \bibinfo{author}{Hasson, U.}
+\newblock \bibinfo{title}{Topographic mapping of a hierarchy of temporal
+  receptive windows using a narrated story}.
+\newblock \emph{\bibinfo{journal}{Journal of Neuroscience}}
+  \textbf{\bibinfo{volume}{31}}, \bibinfo{pages}{2906--2915}
+  (\bibinfo{year}{2011}).
+
+\bibitem{Mann19}
+\bibinfo{author}{Manning, J.~R.}
+\newblock \bibinfo{title}{Episodic memory: mental time travel or a quantum
+  'memory wave' function?}
+\newblock \emph{\bibinfo{journal}{PsyArXiv}}
+  \textbf{\bibinfo{volume}{doi:10.31234/osf.io/6zjwb}} (\bibinfo{year}{2019}).
+
+\bibitem{Mann20}
+\bibinfo{author}{Manning, J.~R.}
+\newblock \bibinfo{title}{Context reinstatement}.
+\newblock In \bibinfo{editor}{Kahana, M.~J.} \& \bibinfo{editor}{Wagner, A.~D.}
+  (eds.) \emph{\bibinfo{booktitle}{Handbook of Human Memory}}
+  (\bibinfo{publisher}{Oxford University Press}, \bibinfo{year}{2020}).
+
+\bibitem{HowaKaha02a}
+\bibinfo{author}{Howard, M.~W.} \& \bibinfo{author}{Kahana, M.~J.}
+\newblock \bibinfo{title}{A distributed representation of temporal context}.
+\newblock \emph{\bibinfo{journal}{Journal of Mathematical Psychology}}
+  \textbf{\bibinfo{volume}{46}}, \bibinfo{pages}{269--299}
+  (\bibinfo{year}{2002}).
+
+\bibitem{HowaEtal14}
+\bibinfo{author}{Howard, M.~W.} \emph{et~al.}
+\newblock \bibinfo{title}{A unified mathematical framework for coding time,
+  space, and sequences in the medial temporal lobe}.
+\newblock \emph{\bibinfo{journal}{Journal of Neuroscience}}
+  \textbf{\bibinfo{volume}{34}}, \bibinfo{pages}{4692--4707}
+  (\bibinfo{year}{2014}).
+
+\bibitem{MannEtal15}
+\bibinfo{author}{Manning, J.~R.}, \bibinfo{author}{Norman, K.~A.} \&
+  \bibinfo{author}{Kahana, M.~J.}
+\newblock \bibinfo{title}{The role of context in episodic memory}.
+\newblock In \bibinfo{editor}{Gazzaniga, M.} (ed.)
+  \emph{\bibinfo{booktitle}{The Cognitive Neurosciences, Fifth edition}},
+  \bibinfo{pages}{557--566} (\bibinfo{publisher}{{MIT} Press},
+  \bibinfo{year}{2015}).
+
+\bibitem{RangRitc12}
+\bibinfo{author}{Ranganath, C.} \& \bibinfo{author}{Ritchey, M.}
+\newblock \bibinfo{title}{Two cortical systems for memory-guided behavior}.
+\newblock \emph{\bibinfo{journal}{Nature Reviews Neuroscience}}
+  \textbf{\bibinfo{volume}{13}}, \bibinfo{pages}{713 -- 726}
+  (\bibinfo{year}{2012}).
+
+\bibitem{ZackEtal07}
+\bibinfo{author}{Zacks, J.~M.}, \bibinfo{author}{Speer, N.~K.},
+  \bibinfo{author}{Swallow, K.~M.}, \bibinfo{author}{Braver, T.~S.} \&
+  \bibinfo{author}{Reynolds, J.~R.}
+\newblock \bibinfo{title}{Event perception: a mind-brain perspective}.
+\newblock \emph{\bibinfo{journal}{Psychological Bulletin}}
+  \textbf{\bibinfo{volume}{133}}, \bibinfo{pages}{273--293}
+  (\bibinfo{year}{2007}).
+
+\bibitem{ZwaaRadv98}
+\bibinfo{author}{Zwaan, R.~A.} \& \bibinfo{author}{Radvansky, G.~A.}
+\newblock \bibinfo{title}{Situation models in language comprehension and
+  memory}.
+\newblock \emph{\bibinfo{journal}{Psychological Bulletin}}
+  \textbf{\bibinfo{volume}{123}}, \bibinfo{pages}{162 -- 185}
+  (\bibinfo{year}{1998}).
+
+\bibitem{RadvZack17}
+\bibinfo{author}{Radvansky, G.~A.} \& \bibinfo{author}{Zacks, J.~M.}
+\newblock \bibinfo{title}{Event boundaries in memory and cognition}.
+\newblock \emph{\bibinfo{journal}{Curr Opin Behav Sci}}
+  \textbf{\bibinfo{volume}{17}}, \bibinfo{pages}{133--140}
+  (\bibinfo{year}{2017}).
+
+\bibitem{BrunEtal18}
+\bibinfo{author}{Brunec, I.~K.}, \bibinfo{author}{Moscovitch, M.~M.} \&
+  \bibinfo{author}{Barense, M.~D.}
+\newblock \bibinfo{title}{Boundaries shape cognitive representations of spaces
+  and events}.
+\newblock \emph{\bibinfo{journal}{{Trends in Cognitive Sciences}}}
+  \textbf{\bibinfo{volume}{22}}, \bibinfo{pages}{637--650}
+  (\bibinfo{year}{2018}).
+
+\bibitem{HeusEtal18b}
+\bibinfo{author}{Heusser, A.~C.}, \bibinfo{author}{Ezzyat, Y.},
+  \bibinfo{author}{Shiff, I.} \& \bibinfo{author}{Davachi, L.}
+\newblock \bibinfo{title}{Perceptual boundaries cause mnemonic trade-offs
+  between local boundary processing and across-trial associative binding}.
+\newblock \emph{\bibinfo{journal}{Journal of Experimental Psychology Learning,
+  Memory, and Cognition}} \textbf{\bibinfo{volume}{44}},
+  \bibinfo{pages}{1075--1090} (\bibinfo{year}{2018}).
+
+\bibitem{ClewDava17}
+\bibinfo{author}{Clewett, D.} \& \bibinfo{author}{Davachi, L.}
+\newblock \bibinfo{title}{The ebb and flow of experience determines the
+  temporal structure of memory}.
+\newblock \emph{\bibinfo{journal}{Curr Opin Behav Sci}}
+  \textbf{\bibinfo{volume}{17}}, \bibinfo{pages}{186--193}
+  (\bibinfo{year}{2017}).
+
+\bibitem{EzzyDava11}
+\bibinfo{author}{Ezzyat, Y.} \& \bibinfo{author}{Davachi, L.}
+\newblock \bibinfo{title}{What constitutes an episode in episodic memory?}
+\newblock \emph{\bibinfo{journal}{Psychological Science}}
+  \textbf{\bibinfo{volume}{22}}, \bibinfo{pages}{243--252}
+  (\bibinfo{year}{2011}).
+
+\bibitem{DuBrDava13}
+\bibinfo{author}{DuBrow, S.} \& \bibinfo{author}{Davachi, L.}
+\newblock \bibinfo{title}{The influence of contextual boundaries on memory for
+  the sequential order of events}.
+\newblock \emph{\bibinfo{journal}{Journal of Experimental Psychology: General}}
+  \textbf{\bibinfo{volume}{142}}, \bibinfo{pages}{1277--1286}
+  (\bibinfo{year}{2013}).
+
+\bibitem{TompDava17}
+\bibinfo{author}{Tompary, A.} \& \bibinfo{author}{Davachi, L.}
+\newblock \bibinfo{title}{Consolidation promotes the emergence of
+  representational overlap in the hippocampus and medial prefrontal cortex}.
+\newblock \emph{\bibinfo{journal}{Neuron}} \textbf{\bibinfo{volume}{96}},
+  \bibinfo{pages}{228--241} (\bibinfo{year}{2017}).
+
+\bibitem{ChenEtal17}
+\bibinfo{author}{Chen, J.} \emph{et~al.}
+\newblock \bibinfo{title}{Shared memories reveal shared structure in neural
+  activity across individuals}.
+\newblock \emph{\bibinfo{journal}{Nature Neuroscience}}
+  \textbf{\bibinfo{volume}{20}}, \bibinfo{pages}{115} (\bibinfo{year}{2017}).
+
+\bibitem{BleiEtal03}
+\bibinfo{author}{Blei, D.~M.}, \bibinfo{author}{Ng, A.~Y.} \&
+  \bibinfo{author}{Jordan, M.~I.}
+\newblock \bibinfo{title}{Latent dirichlet allocation}.
+\newblock \emph{\bibinfo{journal}{Journal of Machine Learning Research}}
+  \textbf{\bibinfo{volume}{3}}, \bibinfo{pages}{993 -- 1022}
+  (\bibinfo{year}{2003}).
+
+\bibitem{Rabi89}
+\bibinfo{author}{Rabiner, L.}
+\newblock \bibinfo{title}{A tutorial on {Hidden Markov Models} and selected
+  applications in speech recognition}.
+\newblock \emph{\bibinfo{journal}{Proceedings of the IEEE}}
+  \textbf{\bibinfo{volume}{77}}, \bibinfo{pages}{257--286}
+  (\bibinfo{year}{1989}).
+
+\bibitem{BaldEtal17}
+\bibinfo{author}{Baldassano, C.} \emph{et~al.}
+\newblock \bibinfo{title}{Discovering event structure in continuous narrative
+  perception and memory}.
+\newblock \emph{\bibinfo{journal}{Neuron}} \textbf{\bibinfo{volume}{95}},
+  \bibinfo{pages}{709--721} (\bibinfo{year}{2017}).
+
+\bibitem{BleiLaff06}
+\bibinfo{author}{Blei, D.~M.} \& \bibinfo{author}{Lafferty, J.~D.}
+\newblock \bibinfo{title}{Dynamic topic models}.
+\newblock In \emph{\bibinfo{booktitle}{Proceedings of the 23rd International
+  Conference on Machine Learning}}, ICML '06, \bibinfo{pages}{113--120}
+  (\bibinfo{publisher}{ACM}, \bibinfo{address}{New York, NY, US},
+  \bibinfo{year}{2006}).
+
+\bibitem{MannEtal11}
+\bibinfo{author}{Manning, J.~R.}, \bibinfo{author}{Polyn, S.~M.},
+  \bibinfo{author}{Baltuch, G.}, \bibinfo{author}{Litt, B.} \&
+  \bibinfo{author}{Kahana, M.~J.}
+\newblock \bibinfo{title}{Oscillatory patterns in temporal lobe reveal context
+  reinstatement during memory search}.
+\newblock \emph{\bibinfo{journal}{Proceedings of the National Academy of
+  Sciences, USA}} \textbf{\bibinfo{volume}{108}}, \bibinfo{pages}{12893--12897}
+  (\bibinfo{year}{2011}).
+
+\bibitem{HowaEtal12}
+\bibinfo{author}{Howard, M.~W.}, \bibinfo{author}{Viskontas, I.~V.},
+  \bibinfo{author}{Shankar, K.~H.} \& \bibinfo{author}{Fried, I.}
+\newblock \bibinfo{title}{Ensembles of human {MTL} neurons ``jump back in
+  time'' in response to a repeated stimulus}.
+\newblock \emph{\bibinfo{journal}{Hippocampus}} \textbf{\bibinfo{volume}{22}},
+  \bibinfo{pages}{1833--1847} (\bibinfo{year}{2012}).
+
+\bibitem{AtkiShif68}
+\bibinfo{author}{Atkinson, R.~C.} \& \bibinfo{author}{Shiffrin, R.~M.}
+\newblock \bibinfo{title}{Human memory: {A} proposed system and its control
+  processes}.
+\newblock In \bibinfo{editor}{Spence, K.~W.} \& \bibinfo{editor}{Spence, J.~T.}
+  (eds.) \emph{\bibinfo{booktitle}{The psychology of learning and motivation}},
+  vol.~\bibinfo{volume}{2}, \bibinfo{pages}{89--105}
+  (\bibinfo{publisher}{Academic Press}, \bibinfo{address}{New York},
+  \bibinfo{year}{1968}).
+
+\bibitem{PostPhil65}
+\bibinfo{author}{Postman, L.} \& \bibinfo{author}{Phillips, L.~W.}
+\newblock \bibinfo{title}{Short-term temporal changes in free recall}.
+\newblock \emph{\bibinfo{journal}{Quarterly Journal of Experimental
+  Psychology}} \textbf{\bibinfo{volume}{17}}, \bibinfo{pages}{132--138}
+  (\bibinfo{year}{1965}).
+
+\bibitem{WelcBurn24}
+\bibinfo{author}{Welch, G.~B.} \& \bibinfo{author}{Burnett, C.~T.}
+\newblock \bibinfo{title}{Is primacy a factor in association-formation}.
+\newblock \emph{\bibinfo{journal}{American Journal of Psychology}}
+  \textbf{\bibinfo{volume}{35}}, \bibinfo{pages}{396--401}
+  (\bibinfo{year}{1924}).
+
+\bibitem{PolyEtal09}
+\bibinfo{author}{Polyn, S.~M.}, \bibinfo{author}{Norman, K.~A.} \&
+  \bibinfo{author}{Kahana, M.~J.}
+\newblock \bibinfo{title}{A context maintenance and retrieval model of
+  organizational processes in free recall}.
+\newblock \emph{\bibinfo{journal}{Psychological Review}}
+  \textbf{\bibinfo{volume}{116}}, \bibinfo{pages}{129--156}
+  (\bibinfo{year}{2009}).
+
+\bibitem{MannKaha12}
+\bibinfo{author}{Manning, J.~R.} \& \bibinfo{author}{Kahana, M.~J.}
+\newblock \bibinfo{title}{Interpreting semantic clustering effects in free
+  recall}.
+\newblock \emph{\bibinfo{journal}{Memory}} \textbf{\bibinfo{volume}{20}},
+  \bibinfo{pages}{511--517} (\bibinfo{year}{2012}).
+
+\bibitem{HeusEtal18a}
+\bibinfo{author}{Heusser, A.~C.}, \bibinfo{author}{Ziman, K.},
+  \bibinfo{author}{Owen, L. L.~W.} \& \bibinfo{author}{Manning, J.~R.}
+\newblock \bibinfo{title}{{HyperTools}: a {Python} toolbox for gaining
+  geometric insights into high-dimensional data}.
+\newblock \emph{\bibinfo{journal}{{Journal of Machine Learning Research}}}
+  \textbf{\bibinfo{volume}{18}}, \bibinfo{pages}{1--6} (\bibinfo{year}{2018}).
+
+\bibitem{McInEtal18}
+\bibinfo{author}{McInnes, L.}, \bibinfo{author}{Healy, J.} \&
+  \bibinfo{author}{Melville, J.}
+\newblock \bibinfo{title}{{UMAP}: Uniform manifold approximation and projection
+  for dimension reduction}.
+\newblock \emph{\bibinfo{journal}{arXiv}} \textbf{\bibinfo{volume}{1802}}
+  (\bibinfo{year}{2018}).
+
+\bibitem{MuelEtal18}
+\bibinfo{author}{Mueller, A.} \emph{et~al.}
+\newblock \bibinfo{title}{{WordCloud 1.5.0: a little word cloud generator in
+  Python}}.
+\newblock \emph{\bibinfo{journal}{Zenodo}}
+  \textbf{\bibinfo{volume}{https://zenodo.org/record/1322068\#.W4tPKZNKh24}}
+  (\bibinfo{year}{2018}).
+
+\bibitem{PallWagn02}
+\bibinfo{author}{Paller, K.~A.} \& \bibinfo{author}{Wagner, A.~D.}
+\newblock \bibinfo{title}{Observing the transformation of experience into
+  memory}.
+\newblock \emph{\bibinfo{journal}{Trends in Cognitive Sciences}}
+  \textbf{\bibinfo{volume}{6}}, \bibinfo{pages}{93--102}
+  (\bibinfo{year}{2002}).
+
+\bibitem{YarkEtal11}
+\bibinfo{author}{Yarkoni, T.}, \bibinfo{author}{Poldrack, R.~A.},
+  \bibinfo{author}{Nichols, T.~E.}, \bibinfo{author}{Van~Essen, D.~C.} \&
+  \bibinfo{author}{Wager, T.~D.}
+\newblock \bibinfo{title}{Large-scale automated synthesis of human functional
+  neuroimaging data}.
+\newblock \emph{\bibinfo{journal}{Nature Methods}}
+  \textbf{\bibinfo{volume}{8}}, \bibinfo{pages}{665} (\bibinfo{year}{2011}).
+
+\bibitem{BellEtal18}
+\bibinfo{author}{Bellmund, J. L.~S.}, \bibinfo{author}{G\"{a}rdenfors, P.},
+  \bibinfo{author}{Moser, E.~I.} \& \bibinfo{author}{Doeller, C.~F.}
+\newblock \bibinfo{title}{Navigating cognition: spatial codes for human
+  thinking}.
+\newblock \emph{\bibinfo{journal}{Science}} \textbf{\bibinfo{volume}{362}}
+  (\bibinfo{year}{2018}).
+
+\bibitem{BellEtal20}
+\bibinfo{author}{Bellmund, J. L.~S.} \emph{et~al.}
+\newblock \bibinfo{title}{Deforming the metric of cognitive maps distorts
+  memory}.
+\newblock \emph{\bibinfo{journal}{Nature Human Behavior}}
+  \textbf{\bibinfo{volume}{4}}, \bibinfo{pages}{177--188}
+  (\bibinfo{year}{2020}).
+
+\bibitem{ConsEtal16}
+\bibinfo{author}{Constantinescu, A.~O.}, \bibinfo{author}{O'Reilly, J.~X.} \&
+  \bibinfo{author}{Behrens, T. E.~J.}
+\newblock \bibinfo{title}{Organizing conceptual knowledge in humans with a
+  gridlike code}.
+\newblock \emph{\bibinfo{journal}{Science}} \textbf{\bibinfo{volume}{352}},
+  \bibinfo{pages}{1464--1468} (\bibinfo{year}{2016}).
+
+\bibitem{GilbMarl17}
+\bibinfo{author}{Gilboa, A.} \& \bibinfo{author}{Marlatte, H.}
+\newblock \bibinfo{title}{Neurobiology of schemas and schema-mediated memory}.
+\newblock \emph{\bibinfo{journal}{Trends Cogn Sci}}
+  \textbf{\bibinfo{volume}{21}}, \bibinfo{pages}{618--631}
+  (\bibinfo{year}{2017}).
+
+\bibitem{BaldEtal18}
+\bibinfo{author}{Baldassano, C.}, \bibinfo{author}{Hasson, U.} \&
+  \bibinfo{author}{Norman, K.~A.}
+\newblock \bibinfo{title}{Representation of real-world event schemas during
+  narrative perception}.
+\newblock \emph{\bibinfo{journal}{{Journal of Neuroscience}}}
+  \textbf{\bibinfo{volume}{38}}, \bibinfo{pages}{9689--9699}
+  (\bibinfo{year}{2018}).
+
+\bibitem{HuthEtal12}
+\bibinfo{author}{Huth, A.~G.}, \bibinfo{author}{Nisimoto, S.},
+  \bibinfo{author}{Vu, A.~T.} \& \bibinfo{author}{Gallant, J.~L.}
+\newblock \bibinfo{title}{A continuous semantic space describes the
+  representation of thousands of object and action categories across the human
+  brain}.
+\newblock \emph{\bibinfo{journal}{Neuron}} \textbf{\bibinfo{volume}{76}},
+  \bibinfo{pages}{1210--1224} (\bibinfo{year}{2012}).
+
+\bibitem{HuthEtal16}
+\bibinfo{author}{Huth, A.~G.}, \bibinfo{author}{de~Heer, W.~A.},
+  \bibinfo{author}{Griffiths, T.~L.}, \bibinfo{author}{Theunissen, F.~E.} \&
+  \bibinfo{author}{Gallant, J.~L.}
+\newblock \bibinfo{title}{Natural speech reveals the semantic maps that tile
+  human cerebral cortex}.
+\newblock \emph{\bibinfo{journal}{Nature}} \textbf{\bibinfo{volume}{532}},
+  \bibinfo{pages}{453--458} (\bibinfo{year}{2016}).
+
+\bibitem{GagnEtal20}
+\bibinfo{author}{Gagnepain, P.} \emph{et~al.}
+\newblock \bibinfo{title}{Collective memory shapes the organization of
+  individual memories in the medial prefrontal cortex}.
+\newblock \emph{\bibinfo{journal}{Nature Human Behavior}}
+  \textbf{\bibinfo{volume}{4}}, \bibinfo{pages}{189--200}
+  (\bibinfo{year}{2020}).
+
+\bibitem{SimoEtal16}
+\bibinfo{author}{Simony, E.}, \bibinfo{author}{Honey, C.~J.},
+  \bibinfo{author}{Chen, J.} \& \bibinfo{author}{Hasson, U.}
+\newblock \bibinfo{title}{Dynamic reconfiguration of the default mode network
+  during narrative comprehension}.
+\newblock \emph{\bibinfo{journal}{Nature Communications}}
+  \textbf{\bibinfo{volume}{7}}, \bibinfo{pages}{1--13} (\bibinfo{year}{2016}).
+
+\bibitem{ZadbEtal17}
+\bibinfo{author}{Zadbood, A.}, \bibinfo{author}{Chen, J.},
+  \bibinfo{author}{Leong, Y.~C.}, \bibinfo{author}{Norman, K.~A.} \&
+  \bibinfo{author}{Hasson, U.}
+\newblock \bibinfo{title}{How we transmit memories to other brains:
+  Constructing shared neural representations via communication}.
+\newblock \emph{\bibinfo{journal}{Cereb Cortex}} \textbf{\bibinfo{volume}{27}},
+  \bibinfo{pages}{4988--5000} (\bibinfo{year}{2017}).
+
+\bibitem{SimoChan20}
+\bibinfo{author}{Simony, E.} \& \bibinfo{author}{Chang, C.}
+\newblock \bibinfo{title}{Analysis of stimulus-induced brain dynamics during
+  naturalistic paradigms}.
+\newblock \emph{\bibinfo{journal}{{N}euro{I}mage}}
+  \textbf{\bibinfo{volume}{216}}, \bibinfo{pages}{116461}
+  (\bibinfo{year}{2020}).
+
+\bibitem{LandDuma97}
+\bibinfo{author}{Landauer, T.~K.} \& \bibinfo{author}{Dumais, S.~T.}
+\newblock \bibinfo{title}{A solution to {P}lato's problem: the latent semantic
+  analysis theory of acquisition, induction, and representation of knowledge}.
+\newblock \emph{\bibinfo{journal}{Psychological Review}}
+  \textbf{\bibinfo{volume}{104}}, \bibinfo{pages}{211--240}
+  (\bibinfo{year}{1997}).
+
+\bibitem{MikoEtal13a}
+\bibinfo{author}{Mikolov, T.}, \bibinfo{author}{Chen, K.},
+  \bibinfo{author}{Corrado, G.} \& \bibinfo{author}{Dean, J.}
+\newblock \bibinfo{title}{Efficient estimation of word representations in
+  vector space}.
+\newblock \emph{\bibinfo{journal}{{arXiv}}}
+  \textbf{\bibinfo{volume}{1301.3781}} (\bibinfo{year}{2013}).
+
+\bibitem{CerEtal18}
+\bibinfo{author}{Cer, D.} \emph{et~al.}
+\newblock \bibinfo{title}{Universal sentence encoder}.
+\newblock \emph{\bibinfo{journal}{{arXiv}}}
+  \textbf{\bibinfo{volume}{1803.11175}} (\bibinfo{year}{2018}).
+
+\bibitem{RadfEtal19}
+\bibinfo{author}{Radford, A.} \emph{et~al.}
+\newblock \bibinfo{title}{Language models are unsupervised multitask learners}.
+\newblock \emph{\bibinfo{journal}{OpenAI Blog}} \textbf{\bibinfo{volume}{1}}
+  (\bibinfo{year}{2019}).
+
+\bibitem{BrowEtal20}
+\bibinfo{author}{Brown, T.~B.} \emph{et~al.}
+\newblock \bibinfo{title}{Language models are few-shot learners}.
+\newblock \emph{\bibinfo{journal}{{arXiv}}}
+  \textbf{\bibinfo{volume}{2005.14165}} (\bibinfo{year}{2020}).
+
+\bibitem{PedrEtal11}
+\bibinfo{author}{Pedregosa, F.} \emph{et~al.}
+\newblock \bibinfo{title}{Scikit-learn: Machine learning in {P}ython}.
+\newblock \emph{\bibinfo{journal}{Journal of Machine Learning Research}}
+  \textbf{\bibinfo{volume}{12}}, \bibinfo{pages}{2825--2830}
+  (\bibinfo{year}{2011}).
+
+\bibitem{Brainiak}
+\bibinfo{author}{Capota, M.} \emph{et~al.}
+\newblock \bibinfo{title}{Brain imaging analysis kit} (\bibinfo{year}{2017}).
+\newblock \urlprefix\url{https://doi.org/10.5281/zenodo.59780}.
+
+\bibitem{HassEtal08}
+\bibinfo{author}{Hasson, U.}, \bibinfo{author}{Yang, E.},
+  \bibinfo{author}{Vallines, I.}, \bibinfo{author}{Heeger, D.~J.} \&
+  \bibinfo{author}{Rubin, N.}
+\newblock \bibinfo{title}{A hierarchy of temporal receptive windows in human
+  cortex}.
+\newblock \emph{\bibinfo{journal}{Journal of Neuroscience}}
+  \textbf{\bibinfo{volume}{28}}, \bibinfo{pages}{2539--2550}
+  (\bibinfo{year}{2008}).
+
+\bibitem{HassEtal15}
+\bibinfo{author}{Hasson, U.}, \bibinfo{author}{Chen, J.} \&
+  \bibinfo{author}{Honey, C.~J.}
+\newblock \bibinfo{title}{Hierarchical process memory: memory as an integral
+  component of information processing}.
+\newblock \emph{\bibinfo{journal}{Trends in Cognitive Science}}
+  \textbf{\bibinfo{volume}{19}}, \bibinfo{pages}{304--315}
+  (\bibinfo{year}{2015}).
+
+\bibitem{Dobr70}
+\bibinfo{author}{Dobrushin, R.~L.}
+\newblock \bibinfo{title}{Prescribing a system of random variables by
+  conditional distributions}.
+\newblock \emph{\bibinfo{journal}{Theory of Probability \& Its Applications}}
+  \textbf{\bibinfo{volume}{15}}, \bibinfo{pages}{458--486}
+  (\bibinfo{year}{1970}).
+
+\bibitem{RamdEtal17}
+\bibinfo{author}{Ramdas, A.}, \bibinfo{author}{Trillos, N.} \&
+  \bibinfo{author}{Cuturi, M.}
+\newblock \bibinfo{title}{On wasserstein two-sample testing and related
+  families of nonparametric tests}.
+\newblock \emph{\bibinfo{journal}{Entropy}} \textbf{\bibinfo{volume}{19}},
+  \bibinfo{pages}{47} (\bibinfo{year}{2017}).
+
+\bibitem{HeusEtal17b}
+\bibinfo{author}{Heusser, A.~C.}, \bibinfo{author}{Fitzpatrick, P.~C.},
+  \bibinfo{author}{Field, C.~E.}, \bibinfo{author}{Ziman, K.} \&
+  \bibinfo{author}{Manning, J.~R.}
+\newblock \bibinfo{title}{Quail: a {Python} toolbox for analyzing and plotting
+  free recall data}.
+\newblock \emph{\bibinfo{journal}{The Journal of Open Source Software}}
+  \textbf{\bibinfo{volume}{10.21105/joss.00424}} (\bibinfo{year}{2017}).
+
+\bibitem{Fish25}
+\bibinfo{author}{Fisher, R.~A.}
+\newblock \emph{\bibinfo{title}{Statistical Methods for Research Workers}}
+  (\bibinfo{publisher}{Oliver and Boyd}, \bibinfo{year}{1925}).
+
+\bibitem{BernClif94}
+\bibinfo{author}{Berndt, D.~J.} \& \bibinfo{author}{Clifford, J.}
+\newblock \bibinfo{title}{Using dynamic time warping to find patterns in time
+  series}.
+\newblock In \emph{\bibinfo{booktitle}{{KDD workshop}}},
+  vol.~\bibinfo{volume}{10}, \bibinfo{pages}{359--370} (\bibinfo{year}{1994}).
+
+\bibitem{FreeEtal01}
+\bibinfo{author}{Freedman, D.}, \bibinfo{author}{Riesenhuber, M.},
+  \bibinfo{author}{Poggio, T.} \& \bibinfo{author}{Miller, E.}
+\newblock \bibinfo{title}{Categorical representation of visual stimuli in the
+  primate prefrontal cortex}.
+\newblock \emph{\bibinfo{journal}{Science}} \textbf{\bibinfo{volume}{291}},
+  \bibinfo{pages}{312--316} (\bibinfo{year}{2001}).
+
+\bibitem{SigmDeha08}
+\bibinfo{author}{Sigman, M.} \& \bibinfo{author}{Dehaene, S.}
+\newblock \bibinfo{title}{Brain mechanisms of serial and parallel processing
+  during dual-task performance}.
+\newblock \emph{\bibinfo{journal}{Journal of Neuroscience}}
+  \textbf{\bibinfo{volume}{28}}, \bibinfo{pages}{7585--7589}
+  (\bibinfo{year}{2008}).
+
+\bibitem{CharKoec10}
+\bibinfo{author}{Charron, S.} \& \bibinfo{author}{Koechlin, E.}
+\newblock \bibinfo{title}{Divided representations of current goals in the human
+  frontal lobes}.
+\newblock \emph{\bibinfo{journal}{Science}} \textbf{\bibinfo{volume}{328}},
+  \bibinfo{pages}{360--363} (\bibinfo{year}{2010}).
+
+\bibitem{RishEtal13}
+\bibinfo{author}{Rishel, C.~A.}, \bibinfo{author}{Huang, G.} \&
+  \bibinfo{author}{Freedman, D.~J.}
+\newblock \bibinfo{title}{Independent category and spatial encoding in parietal
+  cortex}.
+\newblock \emph{\bibinfo{journal}{Neuron}} \textbf{\bibinfo{volume}{77}},
+  \bibinfo{pages}{969--979} (\bibinfo{year}{2013}).
+
+\bibitem{KrieEtal08b}
+\bibinfo{author}{Kriegeskorte, N.}, \bibinfo{author}{Mur, M.} \&
+  \bibinfo{author}{Bandettini, P.}
+\newblock \bibinfo{title}{Representational similarity analysis -- connecting
+  the branches of systems neuroscience}.
+\newblock \emph{\bibinfo{journal}{Frontiers in Systems Neuroscience}}
+  \textbf{\bibinfo{volume}{2}}, \bibinfo{pages}{1 -- 28}
+  (\bibinfo{year}{2008}).
+
+\end{thebibliography}
 
 \section*{Acknowledgements}
-We thank Luke Chang, Janice Chen, Chris Honey, Lucy Owen, Emily Whitaker, and Kirsten Ziman for feedback and scientific discussions.
-We also thank Janice Chen, Yuan Chang Leong, Kenneth Norman, and Uri Hasson for sharing the data used in our study.
+We thank Luke Chang, Janice Chen, Chris Honey, Caroline Lee, Lucy Owen, Emily Whitaker, Xinming Xu, and Kirsten Ziman for feedback and scientific discussions.
+We also thank Janice Chen, Yuan Chang Leong, Chris Honey, Chung Yong, Kenneth Norman, and Uri Hasson for sharing the data used in our study.
 Our work was supported in part by NSF EPSCoR Award Number 1632738.
 The content is solely the responsibility of the authors and does not necessarily represent the official views of our supporting organizations.
+The funders had no role in study design, data collection and analysis, decision to publish or preparation of the manuscript.
 
